\begin{textsample}{NEG Dim 6 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_47.txt}  \label{ex:f6_neg_073}
The commercial begins with a close, low-angle view of a table covered with prepared food.
Several taco- or burrito-like items, bowls, and toppings are visible in the foreground, with blurred people standing or sitting in the background.
A prominent on-screen graphic appears near the center : the Taco Bell logo with the text “ WAKE UP ” and “ LIVE MÁS. ” Small fine print appears along the bottom but is too small to read clearly.
The image then cuts briefly to black.
Next, the commercial shows a close-up of a dark wooden surface, possibly a box, plaque, or book cover.
It bears an ornate emblem with wings and mechanical/technical-looking linework, along with the words “ INNOVATORS CLUB. ” Below the emblem, the text “ FIVE YEARS OUT ” is visible.
In the lower-left corner, white text identifies a person : “ Serena S, ” “ Industrial Designer, ” and “ Member Since 2009. ” The scene then changes to a warmly lit interior gathering with a \textbf{formal}, old-fashioned or period-style atmosphere.
Several adults are dressed in suits, waistcoats, dresses, and \textbf{formal} \textbf{attire}.
A woman with dark hair stands near the center, facing a man in a suit, while other people stand around them.
A table lamp glows in the middle foreground, and seated figures are partially visible at the bottom of the frame.
The setting appears like a private club, parlor, or \textbf{formal} social room, but the exact location is not specified by the frames.
The commercial then cuts to a black screen with centered white text reading : “ Are You Five Years Out? ” This same black title card remains through the final sampled frame.

% matched lemmas: attire, formal
\end{textsample}
