\begin{textsample}{NEG Dim 6 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_106.txt}  \label{ex:f6_neg_071}
The commercial opens on a rocky ocean shoreline.
Churning water and pale foam fill the view, washing over dark rocks in a greenish, faded color palette typical of old film.
The sea surface glitters and shifts, then the image moves across wide stretches of surf, with waves rolling toward a rugged coast and breaking into spray around black, jagged rocks.
The ocean scene gives way to a \textbf{modern} interior with large, slanted floor-to-ceiling windows overlooking the same restless sea.
Inside, in front of the windows, stands a mid-century wooden stereo cabinet.
It is a long rectangular console on short tapered legs, with lighter wood panels on each side and a darker central section of narrow vertical slats, suggesting speaker grille or cabinet doors.
Chairs and small furnishings sit to either side, making the space feel like a stylish living room or showroom with an ocean view.
The cabinet is then presented more directly against the windows, centered on a low platform.
The sea continues to fill the background beyond the glass.
As the product is introduced in the audio as RCA Victor Total Sound Stereo, the cabinet remains the visual focus : polished wood, clean lines, and a balanced, symmetrical front.
A close view reveals the top of the stereo opened to its controls.
A black record lies on the turntable in the center, with the tone arm resting over it.
On both sides are rectangular control panels with round knobs and dials arranged neatly, showing the cabinet as both furniture and audio equipment.
Another close-up isolates one control area : metallic circular knobs sit in a vertical row beside a long, slim control strip.
A separate view shows a radio tuner panel with a vertical frequency scale, three round knobs to the side, and the edge of the record player nearby, matching the audio references to the record changer and AM-FM radio.
The commercial returns briefly to the cabinet in the ocean-view room, then cuts back to the coast.
Waves slide along a sandy shoreline, then crash hard against cliffs and rock faces.
Foam explodes upward and spreads across the rocks, sometimes filling almost the entire image with pale spray.
Wider views show tall, rugged rock formations rising from the surf as water surges around them, emphasizing the scale and force of the sea.
The ocean image gradually blends into a studio display of several RCA Victor stereo cabinets.
The products are arranged on curved, tiered platforms in a softly lit showroom setting.
Multiple wooden cabinet styles are visible : a central rectangular console with vertical grille slats, a lower cabinet to the left, a more ornate cabinet to the right with shaped panels and legs, and additional cabinet fronts or models elevated behind them.
The display suggests a range of furniture styles, from simple \textbf{modern} panels to more traditional decorative fronts, all in warm wood tones.
A small matching rectangular unit stands near the center-right, possibly a speaker or accessory.
Near the end, the product display fades behind a large circular RCA Victor emblem.
Inside the circle is a line drawing of the famous dog listening to a gramophone, the “ His Master ’s Voice ” image : the dog stands beside the horn of the phonograph, facing it attentively.
The background darkens so the emblem stands out.
Finally, the closing graphic forms around a circular record-like design.
The letters “ RCA ” appear large in the center of a red circle, with a lightning-bolt-like mark beneath.
Below, white \textbf{text} reads, “ The Most Trusted Name in Sound, ” matching the closing slogan in the audio.

% matched lemmas: modern, text
\end{textsample}
