\begin{textsample}{NEG Dim 6 – 2010 – Score -1.00 – 2010/tv\_com\_2010\_43.txt}  \label{ex:f6_neg_016}
A sunny suburban driveway appears in front of a tan house with white trim, black shutters, a small porch, and a green lawn.
Parked on the driveway is a small mint-green compact car, clean and new-looking, with rounded headlights and a blank license plate.
On the left, a tall Black man in a plaid short-sleeve shirt and dark pants stands near the driveway, smiling.
Near the porch, a young woman with a high curly puff hairstyle walks toward the car.
She wears a pink zip-up hoodie over a light blue T-shirt with a large sunrise graphic, pale green pants, and sneakers.
As she gets close to the car, she looks stunned and delighted, touching the windshield area and then putting a hand to her forehead as if overwhelmed.
The scene shifts to an urban parking lot near brick industrial buildings and an elevated roadway.
A black sedan sits in a marked parking space, but it has been stripped : the wheels are gone, the car is propped up on \textbf{concrete} blocks, parts of the front bumper and grille are missing, and the wheel hubs are exposed.
A light-skinned man in a gray suit, white shirt, and tie approaches from the right, looking alarmed.
Nearby, a red stop sign and stacks of wooden pallets sit in the background.
Across the lot, an older light-skinned man wearing glasses, a green apron, and white sleeves stands in the open doorway of a red brick building, holding a white cloth and watching.
Back at the suburban house, the young woman continues reacting to the mint-green car with excited disbelief, smiling broadly and touching her head.
The tall man by the driveway smiles warmly at her from beside the hedge.
In the urban lot, the suited man stands beside the damaged black sedan with his hands raised and palms out, his face tense and frustrated.
The older apron-wearing man remains in the doorway, still holding the cloth, as if commenting on the situation from a distance.
The commercial alternates between the cheerful driveway moment and the disastrous parking-lot moment : the young woman laughs in front of her new car, while the suited man clenches his fists and gestures angrily beside the stripped sedan.
The story then moves into a State Farm office.
Through glass doors, the tall man and the young woman enter or stand near the entrance while the suited man passes inside.
A red rectangular sign on the right reads “ StateFarm ” in white letters and shows the company ’s three-circle logo.
Small white legal \textbf{text} appears along the bottom of the screen.
The suited man walks forward inside the bright office lobby, looking worn out but composed.
Large white on-screen \textbf{text} appears over him reading “ Car Insurance, ” with the State Farm sign still visible beside him.
Outside the State Farm office, the tall man and young woman come out through the glass doors and down the steps together.
The storefront has large windows, metal railings, and another red State Farm sign visible through the glass.
Large white \textbf{text} now reads “ Car Loans. ” The pair smile and walk side by side ; the man places an arm around the young woman ’s shoulders, and she moves with a light, happy bounce, still wearing the pink hoodie and sunrise T-shirt.
A red graphic wash begins to cover the scene, and the words “ Here to ” appear alongside the “ Car Loans ” \textbf{text}.
The commercial ends on a full red screen with white \textbf{text} reading “ Here to help, ” with small fine print along the bottom.

% matched lemmas: concrete, text
\end{textsample}
