\begin{textsample}{NEG Dim 6 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_79.txt}  \label{ex:f6_neg_030}
A straight two-lane highway stretches through a desert landscape lined with tall cacti and scrub.
The sky is dark and dramatic, with heavy clouds opening to a bright patch of light near the horizon.
Far down the road, a tiny vehicle approaches along the center of the empty pavement.
A close view shows a male-presenting highway patrol officer in a wide-brimmed tan hat and mirrored aviator sunglasses.
He has a serious, alert expression and faces another uniformed person whose back and hat brim are visible in the foreground.
Reflected in the officer ’s sunglasses are the road and desert surroundings.
The approaching vehicle becomes a low, dark car seen from far ahead, wavering in heat haze as it grows larger.
Its front end is broad and dark, and then pairs of round headlights glow near the ground.
The officer ’s face fills the view again, his mirrored lenses now reflecting another uniformed patrolman standing outside in the desert.
The scene shifts to two highway patrol officers beside a white patrol car with a red-and-blue light bar on the roof.
Both wear tan uniforms, brimmed hats, belts, and dark shoes.
One stands with hands near his hips, watching the road ; the other stands near the car.
The patrol car has blue striping and large highway-patrol markings.
Small white \textbf{text} appears at the bottom : “ Performance based on regular use. ” A hand holds a bright red STP bottle and tilts it downward into the filler opening of a white vehicle.
The bottle is labeled with the white STP oval logo and large white words “ GAS TREATMENT, ” seen upside down as it is poured.
The long red neck of the bottle is inserted into the car ’s opening, suggesting the product is being added to the fuel system.
The same small disclaimer remains along the bottom.
The image blends to the rear of a dark, wide-bodied car driving along the desert road at dusk.
Its round rear lights glow red against a purple-pink sky, with cactus silhouettes and low mountains around it.
The car comes closer from behind, centered in the lane, its broad rear end and dark roofline filling more of the view.
In daylight again, the dark car speeds past in the foreground, briefly obscuring the two officers and their patrol car.
Once it passes, the officers are visible beside the white cruiser ; one bends or reaches near the side of the car while the other stands upright, ready and watching.
Close details of the patrol car ’s lettering flash by, including large yellow letters from “ HIGHWAY ” and the red-and-blue light bar.
The white highway patrol car then moves along the road, shown from the side with its blue stripe, star-shaped badge emblem on the door, roof light bar, side mirror, and driver visible through the window.
It continues past scrubby desert vegetation.
Finally, the patrol car turns onto the highway or pulls away sharply, kicking up a pale cloud of dust behind its rear wheels.
Dark mountains, tall cacti, and the fading sky frame the road as the cruiser heads off into the desert.

% matched lemmas: text
\end{textsample}
