\begin{textsample}{NEG Dim 6 – 2010 – Score -1.00 – 2010/tv\_com\_2010\_68.txt}  \label{ex:f6_neg_014}
It opens in a bright white ballet studio, seen from just outside a doorway.
An adult woman ballet dancer stands near tall windows on the right, wearing a dark burgundy Under Armour sports bra-style top, matching brief-cut bottoms, and pale pink pointe shoes.
Her hair is pinned up in a loose bun.
Behind her, wooden ballet barres run along the wall, white pipes line the baseboard, and a radiator sits beneath the windows.
Sunlight cuts across the pale floor.
She stands tall with one leg crossed in front of the other, poised and still.
The focus shifts to her lower legs and feet.
Her calves are strongly defined, and her pointe shoes are scuffed and wrapped around the ankles with ribbons.
She rises through her feet, crossing one ankle over the other and lifting higher until she is balanced on the tips of both pointe shoes.
Her legs stay tightly crossed and controlled as she makes tiny adjustments, the muscles in her calves and ankles visibly working.
The shoes press into the smooth floor, then lift and settle again with precise, delicate pressure.
In an extreme close view, the flattened tips of the worn pointe shoes fill the image, showing frayed fabric, chalky dust, and the hard edges of the toe boxes as they bear her weight.
From behind, she raises both arms overhead in a rounded ballet position.
The small white Under Armour logo is visible at the back of her burgundy top, centered between her shoulder blades.
Her back and shoulders are muscular and defined.
She continues balancing and shifting on pointe, then a wider view shows her alone in the sunlit studio, upright and centered, one foot lifted and crossed as her hands hover softly beside her body.
A close view of her face follows.
She has medium-brown skin, dark eyes, and a calm, focused expression.
Her hair is swept into a bun with loose wisps around it.
She looks slightly downward and to the side, composed and inwardly concentrated, with the bright window behind her turning the background pale and soft.
The setting changes to a dark theatrical space.
Warm yellow stage lights shine from the right side in a vertical row, creating flares and haze across a mostly black background.
The dancer appears in profile under the golden light, still in the same dark burgundy dancewear and pointe shoes.
Her face is serious and intent.
She opens her chest and lifts her chin slightly, then begins to move with broad, deliberate arm gestures.
She steps into a larger performance area : a raised black stage with tall pale panels and vertical columns of glowing yellow bulbs on both sides.
At times she is seen as a small figure against a large white backdrop ; at other moments she is closer, her body silhouetted by the lights.
She turns, opens her arms, and travels across the floor on pointe.
The stage is minimal and geometric, with glossy dark flooring that reflects her legs and the lights.
She extends one leg high to the side while balancing on the other, arms spread wide for counterbalance.
In another close view, her upper body twists, one arm reaching forward and the other bent behind her, wrists and fingers shaped in expressive ballet lines.
Her shoulders, arms, and torso show strength as she transitions through positions.
She lowers one arm, lifts the other, and continues moving across the stage, alternating between controlled poses and quick turns.
The dancer passes in front of the bright yellow bulbs, becoming partly silhouetted in the glare.
She brings her arms in toward her body and then opens them again, turning with her head and shoulders leading.
Brief closer views show her torso and hips as she pivots ; the dark briefs have subtle contrasting trim at the sides.
Her pointe shoes skim and tap the black floor as she crosses her legs and rises through her ankles.
In a wider view, she travels from the back of the stage toward the center with arms lifted.
She turns near a glowing vertical light strip, then faces different directions in quick succession, one hand at her waist and the other arm extending outward.
She remains alone throughout, the empty stage emphasizing her movement.
She launches into a powerful grand jeté, suspended in the air against a pale backdrop.
Her legs stretch into a full split from front to back, toes pointed, arms reaching high overhead.
As she continues through the leap, her front leg lowers slightly and her arms open, her body arcing upward and forward before she descends out of the jump.
She returns to turning and posing beneath the warm lights.
From behind, the Under Armour logo appears again on the back of her top, briefly glowing through the haze.
A closer view shows her face and shoulders as she turns her head ; her expression remains concentrated, with a hint of determination.
Loose hair strands lift around her bun as she moves.
Her arms pass through soft curved shapes near her face and then extend outward at shoulder height.
The final wide view reveals the entire stage set inside a vast, dark, arched industrial hall or hangar.
The stage sits like a large box in the center, with pale panels, overhead lights, and vertical rows of yellow bulbs.
The dancer is a small solitary figure in the middle.
White on-screen \textbf{text} appears at the bottom : “ MISTY COPELAND | BALLERINA SOLOIST ” on the first line, and “ AMERICAN BALLET THEATRE ” beneath it.
The last image is a close-up of her facing forward against a cool gray-blue background.
She looks directly ahead with a steady, composed expression, her face softly lit and her hair still slightly tousled from dancing.

% matched lemmas: text
\end{textsample}
