\begin{textsample}{NEG Dim 6 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_24.txt}  \label{ex:f6_neg_028}
A huge mosquito fills the screen in extreme close-up, far larger than life.
Its body is dark and glossy with purplish highlights, covered in bristly hairs, and its large green compound eyes glitter with a dotted texture.
Its long needle-like proboscis points forward while its thin legs and translucent wings blur around it against a hazy purple-gray background, making it look as if it is hovering or closing in.
The view then cuts to a living room at night or in dim bluish-purple light.
A young teenage boy sits centered on a pale couch, facing a large dark television set in the foreground with his hands held low as if using a game controller.
He has short brown hair, light skin, and wears a loose beige T-shirt with a barcode-like design across the chest.
Around him are casual household items : a plaid blanket draped over the couch to his right, papers or magazines on the cushions, and furniture and stairs visible in the background.
He looks tense and alert, staring toward the television.
The mosquito returns in another close-up, now head-on, its two green eyes dominating the image as its proboscis points downward.
A brief distorted, kaleidoscopic visual effect repeats the boy ’s face and upper body many times in a swirling pattern, as if his anxious gaze and the insect ’s threat are being visually mixed together.
Back on the couch, the boy turns his eyes sideways with a wary, uneasy expression.
The mosquito is then shown in profile perched on human skin, its spindly legs planted among visible fine hairs.
Its pale, translucent wings glow at the edges, and its long proboscis presses into the skin as if biting.
The commercial switches to video game footage : first a fighting game scene with stone columns, statues, and a blue background, with two characters battling while a rating box marked “ MA-13 ” sits at the lower right and small \textbf{text} along the bottom says that Sega Genesis game screens are shown.
One fighter is knocked or thrown across the screen.
Then basketball game footage appears in a crowded arena, with players in bright uniforms leaping near the hoop ; a “ GA ” rating box appears at the lower right, and small white game-screen \textbf{text} remains along the bottom.
After the game images, the mosquito is shown again on skin in glowing purple light, its abdomen swollen and reddish-orange, \textbf{implying} it has fed.
It clings to the skin with long black legs while the proboscis remains near or in the surface.
The boy is then seen in a close-up from above, seated on the couch, rolling his eyes upward.
A tiny dark mosquito sits directly in the middle of his forehead.
A rolled-up newspaper or magazine suddenly rises in front of his face, covering him from forehead to chin.
The visible page is a crossword puzzle ; red handwritten letters fill the squares to spell “ WELCOME TO THE NEXT LEVEL. ” The final image is a white background with the word “ SEGA ” written in thick, smeared dark red letters, surrounded by splatters and streaks like a messy stamped or swatted mark.

% matched lemmas: imply, text
\end{textsample}
