\begin{textsample}{NEG Dim 6 – 2020 – Score 1.00 – 2020/tv\_com\_2020\_38.txt}  \label{ex:f6_neg_090}
The commercial opens on a restaurant table filled with plated food.
The setting appears to be an IHOP-style dining area, with warm lighting and a blurred person moving in the background.
The food spread includes items resembling burgers with fries, pancakes, fried items, and dessert-like plates with whipped cream.
The scene then cuts to a man seated at a table in the restaurant.
He has a moustache and is dressed in a vest, tie, and shirt, with a visible name badge, suggesting an employee or server role.
He holds up a bite of food on a fork and looks at it.
In front of him are several dishes, including a burger with fries, a glass of Pepsi, fried items, pancakes, an IHOP-branded mug, and another plate of food.
Behind him, a blue IHOP sign is visible, while other diners are blurred in the background.
The commercial then returns to the wide shot of the table covered with multiple plates of food.
Over this shot, promotional text appears.
Visible text includes “ \$5 Menu, ” “ \$6 in some locations, ” “ 2–10pm Everyday, ” and “ Free Delivery on IHOP.com. ” A stylized “ IHOPPY HOUR ” graphic is also visible near the top.
In the final frame, the same food spread remains on screen, now with a brighter, clearer neon-style sign reading “ IHOPPY HOUR ” with the IHOP logo above it.
The large “ \$5 Menu ” text remains on the right, along with “ \$6 in some locations. ” The time range “ 2–10pm Everyday ” appears below the sign, and “ Free Delivery on IHOP.com ” appears along the bottom, with smaller fine-print text beneath it.
The background remains softly blurred, keeping the focus on the food and the promotional graphics.

% matched lemmas: 
\end{textsample}
