\begin{textsample}{NEG Dim 6 – 1990 – Score -3.00 – 1990/tv\_com\_1990\_12.txt}  \label{ex:f6_neg_051}
The commercial unfolds as a rapid montage combining live-action, stylized imagery, title cards, and video-game footage.
It opens with a dark, blurred image dominated by red and black tones, with a small multicolored “ N ” logo visible near the lower right.
This cuts to a very bright, washed-out shot in what appears to be a crowded setting ; a pale rounded object or head is centered, but the details are unclear.
A green-tinted close-up follows, showing several people in a crowded environment.
A young woman leans toward the camera while another person sits or stands behind her.
The lighting is artificial and club-like.
The sequence then cuts to a title card reading “ TUROK ” with smaller text underneath that appears to say “ DINOSAUR HUNTER, ” set against a pale pink and white textured background.
The title flashes or changes brightness in the following frame.
The next shots continue the intense green visual style : a close-up of part of a face and hair fills the right side of the frame while \textbf{shadowy} figures appear on the left.
This is followed by an aerial view of a city intersection with cars and streets seen from above.
The montage then cuts into first-person video-game footage with an orange-tinted sky or landscape, a weapon visible at the bottom right, and a small HUD element at the bottom left.
A bright white-pink transition washes the frame.
A blue-lit close-up shows a face or mask on the left side of the screen, with a pale raised hand and blurred figures in the background.
This transitions to first-person shooter gameplay in a gray interior corridor : a gun is visible in the foreground, with human figures ahead.
A title card then appears reading “ GOLDENEYE 007 ” on a \textbf{greenish} textured background.
More gameplay follows in a four-panel split-screen layout, showing first-person views and weapon elements.
Another first-person game view appears outdoors or on a bridge/road, with a weapon visible and a dark landscape ahead.
The commercial then shifts to a bright live-action corridor or transit-like interior.
Uniformed or formally dressed people walk through the space, while yellow/orange costumed or brightly dressed figures move in the background.
This is followed by very overexposed close-up shots where yellow/orange and blue-white shapes are visible but not clearly identifiable.
A gold title card appears reading “ STAR WARS SHADOWS OF THE EMPIRE. ” After that, game footage shows a vehicle or craft moving through a pale desert- or snow-like environment toward a large blocky structure.
Another game shot shows a humanoid or robotic enemy in a tiled interior, with HUD labels including “ Health ” and “ Laser. ” The next section uses stark white lighting.
A line or group of people in white clothing is shown against a nearly white background.
Then a person dressed in bright red appears among many white-clad figures.
A wider shot shows a large crowd of people arranged across the frame, most in white, with one or more red-clad figures standing out near the center.
Another title card appears with the text “ EXTREME-G ” on a pale blue-white background.
It cuts to a red/orange glowing title or graphic, but the text is too overexposed to read clearly.
A pale blue-white flash follows.
Then racing-game footage appears : a futuristic vehicle rides along a bright orange/yellow track, with green scenery and HUD elements including a position marker, a timer, and speed/indicator graphics.
Near the end, the commercial cuts to a dark \textbf{nighttime} city shot looking up at a building with lit windows and streetlights.
The final frames show a black background with white text reading “ get N or get out. ” The “ N ” is a multicolored Nintendo 64-style logo.
Below it is the website “ www.nintendo.com. ” The last frame centers the multicolored “ N ” logo with thin horizontal lines extending from it and the same website address at the bottom.

% matched lemmas: greenish, nighttime, shadowy
\end{textsample}
