\begin{textsample}{NEG Dim 6 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_53.txt}  \label{ex:f6_neg_070}
A Texaco gas station sits beyond a wide, divided roadway in a dry, open landscape under warm, late-day light.
The large black sign above the station reads “ TEXACO ” in red letters, with the Texaco star symbol at the right.
In the nearer foreground are gas pumps marked “ ZX, ” with cars parked among them, including a white coupe.
The Texaco station itself is across the road, separated by \textbf{guardrails} and a broad stretch of pavement.
Near one of the foreground pumps, a balding middle-aged man in a dark, patterned short-sleeve shirt gets out of an older car.
He leans awkwardly over the open driver ’s door, beside a pump with a visible nozzle and “ ZX ” labels.
He looks down and around the pump area, then straightens up, his expression shifting into a faint, self-satisfied or knowing smile.
Behind him, large red “ ZX ” letters are visible on the station wall.
Inside the nearby white coupe, a younger adult man with curly brown hair, wearing a pale yellow or cream polo shirt and light trousers, leans out through the open driver ’s door.
He looks across the forecourt with a cautious, alert expression, as if noticing the Texaco station in the distance.
He then climbs out of the car and heads away from it toward the divided roadway.
The man in the pale shirt crosses the broad, empty road on foot.
From a high, wide view, the road stretches far into the horizon, split by a long central barrier.
He walks across one side of the pavement, steps over or around the center divider, and continues toward the opposite side, visually turning the phrase “ going the extra mile ” into a literal journey across a huge span of road.
Back at the pump area, the balding man stands by his car and pump, watching with a slightly puzzled, stern, or skeptical look.
The “ ZX ” pump and the large red “ Z ” lettering remain behind him.
The younger man is now at a Texaco pump.
The pump has black panels, red and white Texaco branding, and the Texaco star emblem on a red lower section.
He reaches for a nozzle, lifting it from the pump, then looks off to the side as if checking the distance back to his car.
A later wide view shows him near the center divider again, holding the gas nozzle, with a long black hose stretching away across the pavement.
Returning to the white coupe, he opens the car ’s fuel door and brings the nozzle to the gas tank.
He stands beside the rear quarter panel, one hand holding the fuel door open and the other guiding the nozzle into place.
The hose trails from his hand back out of view, \textbf{implying} it has been stretched all the way from the Texaco pump.
In the background, the balding man and the ZX pumps are still nearby, contrasting with the Texaco source of the fuel.
After fueling, the younger man stands at a service window or cashier counter.
Behind the glass is a blonde woman, likely a station attendant, wearing a black-and-white striped Texaco shirt with the red star logo on the chest.
Shelves behind her hold bottles, containers, and convenience-store items.
She turns toward him, smiles, and hands him small items or paperwork through the window.
He reaches in to receive them.
Their exchange is friendly and efficient, with the clerk smiling as she completes the transaction.
The commercial returns to the wide exterior view.
The Texaco station and its red-letter sign are again visible across the broad roadway.
In the foreground, the balding man is beside a pump and car ; he looks toward the Texaco station in the distance.
He then turns and starts walking away from the pump area in that direction, leaving the pump behind as the Texaco sign remains prominent across the road.

% matched lemmas: guardrail, imply
\end{textsample}
