\begin{textsample}{NEG Dim 6 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_6.txt}  \label{ex:f6_neg_026}
The commercial opens in a dim, glossy nightclub-like space lit with red, blue, green, and amber lights.
At center, an adult woman with long dark wavy hair poses beside a vertical metal pole on a raised stage.
She wears a shiny black corset-style outfit with garter straps, dark thigh-high stockings, and high heels, with a large pale feather boa draped around both arms.
One knee is bent and lifted, her foot resting near the pole or a low rail, while her hands settle at her waist.
The floor reflects the colored lights, and curved neon lines and metal structures glow in the background, giving the setting a staged, cabaret atmosphere.
She continues to pose slowly and confidently, shifting her weight as the feather boa hangs in thick plumes down either side of her body.
Her head tilts downward at first, then she raises her face and turns slightly, looking off to one side.
The vertical pole remains directly behind her, and the lights sweep across the dark \textbf{club} interior.
As she straightens, her bent leg lowers out of the pose, and she stands more upright with both hands on her hips, framed by the soft, pale feathers.
The image then changes to a black background with the title “ Tomb Raider II ” appearing in large, shimmering, icy white-blue letters.
The words look distorted and electronic, as if made from static or flickering light, with the red Roman numeral “ II ” \textbf{implied} as part of the game title styling.
A game scene follows, bordered by black around the image.
A low-polygon animated woman, Lara Croft, stands in a bright outdoor field of tall grass.
She has a brown braid, a teal sleeveless top, brown shorts, black gloves, and dark thigh holsters, with mountains and a blue sky with white clouds behind her.
She holds her arms slightly out as if ready to move, looking alert in the open landscape.
A brief close-up of abstract title graphics flashes by, with oversized pale letters and a bright blue-white streak cutting through them.
The lettering is fragmented and hard to read, but it matches the metallic, electronic visual style of the Tomb Raider title.
The gameplay footage then shows Lara in a sunlit architectural setting resembling an old European city, with cream-colored walls, balconies, arched windows, and a brick wall rising to the right.
On-screen graphics appear : a “ T ” rating icon in the upper left, a PlayStation logo in the lower left, a colored health bar near the upper right, and the “ TOMB RAIDER II ” logo in orange and red at the lower right.
Lara is seen from behind in the center, looking upward between the tall buildings as if navigating or climbing through the narrow space.
The action shifts to a canal scene.
A small motorboat speeds along greenish water between stone walls and wooden crates, sending white splashes outward.
The boat heads toward and under a stone bridge in a tight passageway, with the same PlayStation, rating, health bar, and Tomb Raider II logo graphics remaining on-screen.
Wooden boxes line the right side, and the water churns behind the boat as it passes through the canal.
Next, Lara swims underwater in a blue-green ruin.
Stone columns and walls rise around her, and her body is horizontal as she moves through the submerged space.
A blue bar appears near the top right, suggesting an underwater status meter, while the Tomb Raider II branding remains at the lower right.
The scene has a murky, ancient-temple look, with Lara moving between columns in the dim water.
The gameplay moves indoors to a yellow-lit stone corridor with a checkered floor and carved walls.
Lara runs forward into a dark opening at the far end, her small figure centered in the passage.
The health bar is still visible near the top right, the rating icon remains at top left, the PlayStation logo at bottom left, and the Tomb Raider II logo at bottom right.
The corridor grows darker as she advances, with columns and patterned stone panels sliding past on either side.
The commercial ends back in the nightclub setting with the same woman in the black corset outfit and feather boa.
She is shown closer now from about the waist up, standing with one hand at her hip and the other hand raised near her mouth or chin in a teasing pose.
The \textbf{club} ’s curved neon lines and blue light glow behind her.
At the lower left, the white “ EIDOS ” logo appears, identifying the publisher, while the Tomb Raider II branding is partially visible at the lower right.

% matched lemmas: club, imply
\end{textsample}
