\begin{textsample}{NEG Dim 6 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_32.txt}  \label{ex:f6_neg_046}
A dark, glossy studio space appears, lit by strong white-blue spotlights.
At first, a female-presenting adult model is mostly a silhouette, standing near tall, angular structures in the shadows.
The space feels like a fashion runway or stage, with reflective black flooring and beams of light cutting through haze.
Large block-like letter shapes are seen in close detail, suggesting the word “ IPEX, ” and the lighting glints off their hard, metallic or illuminated surfaces.
A blonde adult model appears in a tight close-up.
Her long, loose hair falls across one side of her face, partly covering one eye.
One hand is raised into her hair, and she looks directly forward with a serious, composed expression.
Another blonde model is shown in a black bra, turned partly sideways, her head tilted down and her long pale hair falling over her face and shoulder.
The imagery stays dramatic and high-contrast, with soft skin tones against dark backgrounds and bright light panels.
A close-up isolates a woman ’s eye framed by strands of brown hair, then a brunette adult model in a pale blue bra poses with both arms lifted behind her head.
Her long wavy hair spreads out as if caught in motion, and a wall of round bulbs glows behind her.
The product is clearly presented on her body : a smooth, molded, pale blue bra with a low, rounded shape.
The word “ IPEX ” then dominates the scene in enormous capital letters made from rows of small bright lights.
The letters fill the background and flare intensely, with sparkling white bursts and reflections on the glossy floor.
After this, the brunette model in the pale blue bra walks toward the viewer in front of warm circular lights.
Her hair partly covers one eye, her expression remains calm and serious, and the bra is centered prominently as she advances.
A second adult model appears in a pink bra and matching panties, standing in front of a wall of bright dot lights.
She faces forward and lightly touches or adjusts the waistband of the panties while shifting her pose.
The pink bra is also smooth and molded, similar in shape to the blue one.
Another blonde model in a pale blue set bends forward dramatically, her long hair flying outward ; her hands rest near her thigh as she arches and poses under the bright stage lights.
The brunette in the pale blue set is then shown from a low angle, making the giant illuminated letters and overhead spotlights loom behind her.
She stands with one hip shifted, then turns her head over her shoulder in close-up.
Her hair is tousled around her face, and the pale blue bra fills the lower part of the image.
A wider view reveals her full figure in the matching pale blue bra and panties, standing in high heels before the massive “ IPEX ” letters, arms opening outward in a runway-style pose.
Another adult model with short, curly dark hair appears beside a vertical panel of exposed round bulbs.
She wears a white bra and raises one arm overhead, leaning against or near the light panel.
Her expression is poised and direct.
The pink-clad model returns, moving her arm across her torso and lifting a hand near her head while posing in front of the bright letter-shaped backdrop.
A blonde model in the pale blue bra is shown close-up, looking downward as she touches or lifts one strap near her shoulder.
Her hair falls across her face, and the glowing circular lights behind her create a halo-like pattern.
A different blonde model in a black bra and black panties is briefly shown in profile against a dark background, one hand near her hip as she poses.
The brunette in the pale blue set walks again in front of the giant “ IPEX ” letters.
The angle is low, emphasizing her long legs, high heels, and the reflective runway beneath her.
She steps forward steadily, one arm relaxed and the other slightly raised, while the lit letters tower behind her.
Another blonde model in the pale blue set tosses her hair upward and then lets it fall around her shoulders, standing under a single bright backlight that outlines her body.
A close profile of the brunette follows.
Against a nearly black background, her long brown hair frames her face as she looks downward and slightly forward, her expression reserved.
Then she appears full-length on the runway, first turned to the side with the “ IPEX ” letters behind her, then walking forward.
The runway is lined with bright rectangular lights along both sides, and the glossy black floor mirrors her legs and the glowing set.
The same pale blue set remains the main visible product as she continues down the runway.
She lifts one hand to her hair, then lowers it as she walks.
The giant “ IPEX ” letters remain centered behind her, with white-blue spotlights shining from above and from the sides.
The reflective stage and symmetrical rows of lights give the scene a polished fashion-show look.
The pink-bra model appears again in a close side pose against a dark background.
She turns her head back over her shoulder, hair falling in loose waves, with a faint, controlled smile or softened expression.
Her pink molded bra is clearly visible from the side.
A bright title-like graphic appears : “ VICTORIA ’S SECRET ” in glowing white capital letters, stretched across the dark screen with a flare of light at the center.
The scene then returns to the runway, where a model in the pale blue bra and panties walks straight toward the viewer between rows of rectangular floor lights.
The large “ IPEX ” letters stand behind her, and her reflection is visible beneath her feet.
Finally, the screen fills with enormous illuminated \textbf{text} reading “ DO YOU IPEX. ” The words are stacked, with “ DO YOU ” above “ IPEX, ” all in bold block capitals made of bright light rows.
The letters flare brighter and brighter, with sparkling white bursts washing over the \textbf{text} until the image becomes a mass of glowing white shapes and glittering light.

% matched lemmas: text
\end{textsample}
