\begin{textsample}{NEG Dim 6 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_94.txt}  \label{ex:f6_neg_080}
A wooden Zenith stereo console is seen from above against a plain blue studio background.
Its top is open, revealing a black vinyl record on the turntable at the right, a radio or amplifier control panel at the left with a horizontal dial and round knobs below it, and a large wood speaker section on the far right.
The cabinet is long and low, with warm wood grain and short tapered legs.
As the view comes closer, the record fills more of the image.
It has a red center label, and the tonearm rests near the right side of the turntable.
The Zenith name is visible on the metal turntable base.
A man ’s hand and wrist, the sleeve of a dark suit jacket visible, reaches in from the right.
He grips the end of the tonearm and moves it over the spinning black record.
From above, the hand deliberately places the cartridge near the middle of the record, then shifts it around rather freely, demonstrating contact with the record surface.
The red label on the record is readable enough to show it is a Columbia record.
The tonearm itself is light-colored, with a rectangular cartridge at the end and a slim arm extending back to its pivot.
Closer side views show the tonearm and cartridge just above or on the glossy record surface.
The hand holds the cartridge between thumb and fingers, lowering it and lifting it again.
A tall metal center spindle rises from the middle of the turntable, and another horizontal support arm is visible in the background.
The demonstrator presses the cartridge down lightly with a fingertip, then slides it across the record surface and over the red label area.
The action looks intentionally rough for a record player demonstration : the cartridge is dropped, dragged, lifted, and set down again, while the record ’s shiny grooves reflect light.
No face or full person appears, only the hand performing the demonstration.
The close-up continues with the cartridge moving from the black grooved area toward the red label, then back across the record.
The hand repeatedly lifts the tonearm a small distance above the record and lets it return, emphasizing that the needle pressure is very light.
The cartridge rests on the spinning disc without any visible gouging or tearing.
The surrounding turntable parts are metallic gray and cream-colored, with vertical posts and the central spindle framing the action.
The image then shifts to a more technical-looking close-up of the tonearm over the turntable, now with the record surface appearing darker and more diagram-like.
A small shiny coin-like weight is placed by the hand on the end of a narrow balance or lever near the stylus area.
White on-screen \textbf{text} appears near the upper right : “ ONLY 1/14th OUNCE. ” The small weight sits at the far end of the light-colored lever while the cartridge and tonearm hover nearby, visually illustrating the tiny amount of pressure being discussed.
The hand withdraws, leaving the weight and tonearm arrangement in view.
This demonstration image blends into a product display of a full wooden console stereo.
Large white \textbf{text} reading “ ZENITH STEREO ” appears above and behind the cabinet.
The console is centered on a blue, misty studio background.
It has a long rectangular body, pale speaker grilles at both ends, and carved or arched wood paneling across the middle.
The cabinet stands on slim legs and is presented like fine furniture rather than just electronics.
The console changes to another cabinet style.
The background becomes warmer and pinkish, and the new stereo is more \textbf{modern} and boxy, with a long, low profile on angled legs.
Its front has vertical slats at both ends and lighter vertical panels through the center.
The cabinet is shown straight on, isolated against the plain studio backdrop.
A small, simplified electronic component then appears in the center of the cabinet, as if revealed from inside it.
The cabinet fades away, leaving the component enlarged : a metal amplifier chassis with cylindrical silver parts, black rectangular blocks, and a blue-gray base.
White \textbf{text} appears above the amplifier : “ ZENITH SOLID STATE 240W AMPLIFIER. ” The amplifier sits alone on the warm studio background, angled slightly so its front and side are visible.
It has a sturdy metal base, a few front openings and controls, several shiny cylindrical capacitors rising vertically, and black components lined up behind them.
Later the \textbf{text} changes to “ 240 WATTS PEAK MUSIC POWER, ” with a smaller line of technical output \textbf{text} at the bottom.
The amplifier remains prominent, cleanly lit, and mechanical-looking, contrasting with the earlier furniture cabinets.
The amplifier image fades into a furnished room setting.
A mid-century wooden Zenith console sits against a textured blue wall.
It is long and low, with vertical slatted sections and a central wood panel, supported by angled legs.
A decorative shallow bowl rests on top.
To the right is a light yellow upholstered armchair with wooden legs, and behind it a tall potted plant resembling bamboo.
A framed wall decoration hangs above the console.
The floor has an irregular stone-pattern design.
A large white, italicized “ ZENITH ” logo appears across the upper part of the scene.
The same large Zenith logo remains as the setting changes to another room.
A more traditional wood console stands against patterned wallpaper.
It has pale speaker grilles at each end and curved raised wood panels in the center.
A dark wooden chair with a light seat sits to the left, and an ornate wall clock hangs above and to the right.
The stereo has a polished furniture look, with the electronics hidden inside the cabinet.
Finally, another room display appears with a different Zenith console.
This cabinet is warmer reddish wood, with decorative curved legs, pale speaker grilles at both ends, and double doors or panels in the center.
A vase of flowers sits on top at the left, a framed picture hangs above, and a light-colored chair stands to the right near heavy curtains.
The large Zenith logo stays over the upper portion of the image, reinforcing the brand while the visuals show the stereo offered in several furniture cabinet styles.

% matched lemmas: modern, text
\end{textsample}
