\begin{textsample}{NEG Dim 6 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_106.txt}  \label{ex:f6_neg_031}
The commercial begins with an outdoor coastal/nature image.
The first frame shows a textured, rocky or plant-covered surface, with the scene appearing grainy and \textbf{greenish}.
An archival “ MyFootage.com ” watermark, an ID number, and a timecode overlay are visible.
It then cuts to waves crashing against a large dark rock or mound near the shore.
Water sprays upward and across the rock, emphasizing surf and natural motion.
The next shots shift to close-ups of a piece of audio or television equipment.
One frame shows a wooden or wood-grain cabinet surface with a long rectangular control panel and several round knobs or dials aligned along one side.
Another close-up shows a vertical scale or tuning display beside three round knobs, suggesting radio/television controls.
Part of a dark circular or oval object is visible at the right edge, but its full form is unclear.
The commercial then shows a home interior with a large console television or cabinet-style set placed in front of wide windows.
Through the windows, ocean waves are visible outside.
The room also contains chairs or side furniture, giving the setting a living-room or lounge-like appearance.
After this, the imagery returns to coastal scenery : a sloping shoreline with waves washing along the beach, followed by a rocky cliffside with surf breaking at its base.
These shots continue the ocean/nature motif.
The final sampled frame displays a centered RCA logo inside a circular graphic.
Beneath it is the visible text : “ The Most Trusted Name in Sound. ” The frame retains the same archival watermark, ID number, and timecode overlay.

% matched lemmas: greenish
\end{textsample}
