\begin{textsample}{NEG Dim 6 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_6.txt}  \label{ex:f6_neg_053}
The commercial opens with a very dark, low-contrast shot.
A human figure or possibly a character is centered, but the details are too obscured to identify clearly.
It then cuts rapidly into high-contrast, blue-white, abstract close-ups.
These look like enlarged glowing letters or graphic textures, with heavy scanline/noise effects and motion blur.
The forms are not fully legible at first.
A computer-generated female adventurer appears in a widescreen-framed shot standing in tall grass.
She wears a fitted outfit with shorts and gear/holsters, and she is positioned in a mountainous outdoor landscape under a blue sky.
She looks alert and faces slightly to one side.
The commercial returns to the blue-white abstract typography.
Large glowing letters become clearer, spelling “ Lara Croft ” across two frames, though the style is \textbf{distorted} and flickering.
Next, gameplay footage is shown.
The lower right reads “ TOMB RAIDER, ” and a PlayStation logo appears at the lower left.
An ESRB “ T ” rating icon is visible in the upper left.
The gameplay shows a third-person character moving through environments : first near a rocky or temple-like wall with a climbing or action scene, then through a narrow water-filled passage between walls with crates or structures, and later running inside a golden-lit interior with columns and a tiled floor.
A health/status bar is visible near the top in these gameplay frames.
The clip briefly returns to the abstract blue-white typography again, with oversized glowing letter fragments filling the screen.
The visible letters are partial and not fully readable.
The final shots show a live-action woman in a nightclub or stage-like setting with colored lights and curved neon-like lines in the background.
She wears a dark, shiny corset-style outfit and a large pale \textbf{feather} boa draped around her arms.
She stands in a confident pose, looking off to the side.
The “ EIDOS ” logo appears at the lower left, and another logo appears at the lower right, though it is partially unclear in the sampled frames.

% matched lemmas: distorted, feather
\end{textsample}
