\begin{textsample}{NEG Dim 6 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_61.txt}  \label{ex:f6_neg_034}
The commercial is shown in black and white and appears to begin with a fade-in from darkness.
At the start, the first sampled frame is almost entirely black, with no clearly visible objects or people.
The next visible scene is a bedroom at night.
A man in vertically striped pajamas is in bed under blankets, propped partly upright.
A bedside lamp is visible on the left, and a dark bedframe/headboard is behind him.
Another mound or figure under the bedding is visible on the right side of the bed, but details are unclear.
The camera then moves to a closer view of the man ’s upper body and face.
He is lying against pillows, still in striped pajamas, looking toward the right side of the frame.
Beside him is a pillow or bedding surface with a bold line drawing or cartoon-like illustration on it.
Later, the shot widens again.
The man remains in bed, with the bedside lamp and a small container or package on the nightstand at left.
A large cartoon-like or graphic figure appears near him over the bed area on the right ; it has a pale body and a long striped protruding shape, but its exact identity is not clear from the sampled frame.
The man appears to be holding or interacting with something near his chest.
In the following close-up, the man is still lying in bed.
His expression has changed to a slight smile, and he looks more relaxed or pleased.
The striped pajama top and dark headboard remain visible.
The final frame is a product end card on a dark background.
On the left, large white text reads : “ New \textbf{nighttime} colds medicine from Vicks. ” On the right is a product image showing a bottle/package labeled “ NEW, ” “ Vicks NyQuil, ” and “ \textbf{NIGHTTIME} COLDS MEDICINE. ”

% matched lemmas: nighttime
\end{textsample}
