\begin{textsample}{NEG Dim 6 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_115.txt}  \label{ex:f6_neg_035}
Stephen Curry appears in a warmly lit hallway, stepping out from a room at the left.
He has short dark hair and a close-cropped beard, and wears a pale teal button-up overshirt open over a white T-shirt with brown pants.
The space feels like a home or private lounge : cream-colored walls, wood trim, wall sconces with white shades, framed photos, a console table, plants, and abstract wall art.
He walks slowly toward the viewer, relaxed and conversational, sometimes tilting his head, smiling slightly, and gesturing with his hands as if explaining something.
As he continues down the narrow hallway, more framed photographs line the right wall, evenly spaced under the warm sconces.
His posture remains casual, shoulders loose, hands moving lightly at his sides or opening outward for emphasis.
The hallway extends behind him into a dimmer room, while the ceiling lighting creates a soft glow along the corridor.
Shelving appears on the right with decorative objects—rounded bowls, vases, and sculptural pieces—followed by a small side table with a plant and framed artwork.
Curry keeps moving forward, his expression shifting between thoughtful, amused, and matter-of-fact, as though reflecting on habits and routines.
The setting changes to a large indoor basketball gym.
A bright doorway at the far end silhouettes Curry as he enters from the back of the court.
The polished wooden floor reflects the doorway ’s light.
To the right are teal bleachers rising in rows ; to the left are dark double doors set into a wood-paneled wall.
Curry is now dressed for practice in a dark athletic T-shirt, black \textbf{leggings} or slim training pants, and bright neon-accented basketball shoes.
He walks onto the court toward the playing area.
On the court, an older bald man in a dark blazer, light shirt, tan pants, and dark shoes stands holding a basketball.
He faces Curry and tosses the ball to him in a gentle pass.
Curry receives it near the three-point area, cradles it, then lowers into a shooting stance.
The older man walks away across the court while Curry dribbles once or settles the ball, bends his knees, and rises into a jump shot.
A hoop and backboard hang on the right side, and a few other people are visible far in the background near the center of the gym.
After releasing the shot, Curry lands and walks forward while the older man looks toward the basket.
A close-up focuses on Curry ’s hands holding a gray foldable smartphone, with a basketball pressed against his left side and a black watch on his wrist.
The phone has a large camera module on the back.
He opens it like a small book, revealing a black inner screen.
Tiny \textbf{text} at the bottom reads “ Screen simulated. ” As the device unfolds fully, the display lights up to a large square screen showing the time “ 9:30 ” at the top and an image or video of a person standing on a bright green \textbf{golf} course.
A row of circular app icons and a dark rounded search or command bar sit along the bottom of the screen.
Curry then appears in the gym holding the opened phone in one hand, the gray back with the Google “ G ” logo visible beside the black inner display.
He looks up with a small, knowing smile and a raised-brow expression, as if acknowledging the significance of the change.
The gym ’s wooden ceiling beams and overhead lights fill the background.
The commercial ends on a dark product display.
Several gray Google Pixel phones stand upright against a black background, showing different backs and camera designs.
Large \textbf{text} on the left reads “ Google. ” On the right, large \textbf{text} reads “ Pixel 10, ” with smaller \textbf{text} underneath reading “ with Gemini ” beside the Gemini sparkle mark.

% matched lemmas: golf, leggings, text
\end{textsample}
