\begin{textsample}{NEG Dim 6 – 1950 – Score 1.00 – 1950/tv\_com\_1950\_118.txt}  \label{ex:f6_neg_087}
A rectangular Kodak package appears first, floating against a soft gray studio background.
The box is light-toned with the word “ Kodak ” printed large on the long side and again on the top, with a dark checkerboard-like band along the bottom edge.
As the package fades away, it gives way to a staged home exterior or patio setting.
Ozzie, a clean-shaven adult man with neatly combed dark hair, stands in front of a house façade with multi-pane windows, low shrubs, and leafy plants.
He wears a tailored suit jacket, a light shirt, a dark tie, and a pocket square.
He holds a compact, box-shaped Kodak Brownie Turret movie camera in both hands at chest height.
The camera has a shiny rectangular body, a small viewfinder on top, and a distinctive cluster of three round lenses mounted together on the front.
He looks down at the camera while walking slightly across the set, then turns toward the viewer and presents it with a friendly, demonstrative expression.
He brings the camera closer to his body and begins showing its controls.
His hands rotate and point around the front lens assembly.
The view moves in close to the camera itself : the metal body fills most of the image, with Ozzie ’s suit fabric behind it.
His fingers steady the side while his other hand points to the circular lenses.
The three lenses are arranged like a small triangular cluster on a rotating turret, with one lens positioned for use and the others nearby.
He indicates one lens, then another, making clear that each circular opening has a different purpose.
He turns the turret with his fingertips, and the lens cluster rotates so a different lens comes into position at the front of the camera.
After demonstrating the lenses, Ozzie lifts the camera to his eye.
The scene changes to what the camera is aimed at : a backyard game in progress.
Two young male players, likely teenagers or young adults, stand on opposite sides of a badminton net.
One is farther away on the left, wearing a light shirt and light trousers ; the other is nearer on the right, seen mostly from behind in a short-sleeved shirt and trousers.
A white picket fence runs behind the net, with shrubs and trees beyond it.
The players hold rackets and rally a small shuttlecock back and forth.
In this first view, the whole playing area is visible, including both players, the net, and much of the fence and yard.
The image returns to Ozzie in front of the windows and bushes.
He lowers the camera, smiles, and continues explaining.
He turns the turret again, keeping the camera in both hands at mid-chest.
Then he raises it once more to his eye, bracing it with one hand underneath and the other at the side.
The backyard game appears again, now framed more tightly on the player across the net.
He stands with his legs apart behind the net, holding his racket ready, and the picket fence and foliage fill the background.
He moves the racket across his body as the shuttlecock comes toward him, then shifts his stance to continue the play.
This view gives less of the surrounding yard and more attention to the player ’s upper body and racket movement.
Back with Ozzie, he smiles broadly beside the house windows and lowers the camera.
He turns the turret once more, looking down briefly as his hands work the front lens assembly.
He raises the Brownie Turret to his eye again.
The game appears a third time, now much closer on one player near the fence.
The young man ’s light open-collar shirt, dark hair, and focused face are more visible.
He holds the racket in front of him, then swings and follows the shuttlecock with his eyes.
The net appears as a blurred horizontal band across the lower foreground, while the picket fence and leafy plants sit behind him.
Ozzie reappears holding the camera, then lowers it and opens his hands slightly as if emphasizing how simple the demonstration was.
He remains in the same spot in front of the windows and shrubs, showing that he has not moved around the set.
The Brownie Turret rests in one hand as he gestures with the other, then he brings the camera back to the center of his body.
The scene fades into a studio product display.
Several box-style Brownie cameras are arranged on a glossy surface under bright studio lighting.
Four cameras are visible : one Brownie Turret is elevated at the back center with its three-lens turret facing forward, while three other cameras sit lower in front, spread left, center, and right.
The front-center camera also faces forward with multiple round lenses visible ; the side cameras are angled slightly inward, showing their boxy bodies and top viewfinders.
The display has a clean, symmetrical showroom feel, with the featured turret camera raised above the others.
The other cameras gradually fall partly out of view as attention centers on the elevated Brownie Turret.
The featured camera sits alone against a smooth gray background, its three round lenses projecting from the front and its top viewfinder standing upright.
Large white block lettering appears over the product : “ BROWNIE TURRET ” across the top and middle, and “ \$6.00 DOWN ” below, with the large numeral 6 especially prominent.
The \textbf{text} overlays the camera while it remains visible behind the words.
The price \textbf{text} disappears, returning to the single Brownie Turret camera on the studio surface.
Finally, a large bright “ Kodak ” logo appears across the front of the image, spanning much of the width of the screen and partially covering the camera behind it.

% matched lemmas: text
\end{textsample}
