\begin{textsample}{NEG Dim 6 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_91.txt}  \label{ex:f6_neg_064}
At first, a compact shower radio hangs against glossy light-blue bathroom tiles.
A wet hand reaches up and turns the black control knobs on its white lower panel.
The unit has a black ribbed front, a white “ Splash Dance ” script logo near the top, a rectangular radio tuning scale in the middle, and three round knobs along the bottom labeled for volume, band, and tuning.
It hangs by two dark straps from the shower pipe, close to a white showerhead spraying water.
A young adult woman with wet, slicked-back brown hair stands under the spray beside the radio.
Only her bare shoulders and upper chest are visible, as in a shower setting.
She smiles broadly, dimples showing, and leans toward the water while facing the radio.
She raises a hand near her face, then touches the controls and gestures as if keeping time.
Water runs over her cheeks and neck.
She turns her face into the spray, closes her eyes, and rubs water through her hair with one hand, looking relaxed and playful.
The radio remains hanging just to her right, water droplets visible on its black front but the controls and tuning window still clear.
The view moves closer to the woman ’s face and ear as she rubs her wet hair and then lowers her hand.
She tilts her chin upward under the shower stream, then moves forward so the radio is centered behind her.
The “ Splash Dance ” logo is prominent on the black ribbed front, with the silver tuning scale and three knobs below.
As the woman drifts out of view, the product remains alone against the blue tile, hanging steadily beneath the shower pipe.
A dark blue title screen appears with the words “ Splash Dance ” in large, white, brush-style script, matching the logo on the product.
The product is then shown in close detail.
The black front fills most of the view, with the “ Splash Dance ” logo at the upper left.
Lower down, the radio display and controls are shown : a small “ Pollenex ” nameplate, the words “ AM/FM shower radio, ” a horizontal AM/FM tuning scale, and three black knobs on the white panel.
The labels beneath the knobs read “ VOLUME, ” “ BAND, ” and “ TUNING, ” with small markings such as “ OFF ” and “ MAX ” near the volume control and “ FM ” and “ AM ” near the band control.
A side-by-side demonstration shows two ways the radio can be placed in a shower.
On the left, the unit is mounted flat on the blue tiled wall, with bold white \textbf{text} below it reading “ Affixes to wall. ” On the right, another unit hangs from the shower pipe by straps near the spraying showerhead, with white \textbf{text} beside it reading “ Clips to pipe. ” The split view makes both installation positions visible at once.
Back in the shower, the young woman appears beside the hanging radio again.
Her wet hand passes in front of the black grille and logo, then she moves away from the unit, smiling and gesturing with her fingers near her face.
Water beads on her skin and on the radio ’s front.
She looks toward the viewer and opens her mouth as if singing along, her expression bright and animated.
Her wet hair swings slightly behind her as she faces forward, smiling with an open-mouthed, enthusiastic expression.
A young adult man is then shown in the same kind of blue-tiled shower.
He has short dark wet hair and bare shoulders.
The white showerhead sprays diagonally behind him, and the Splash Dance radio hangs on the wall to his right.
He rubs his hands together as if washing, holding or working with a white bar of soap.
He points upward toward the showerhead and then toward the radio, glancing between the product and the viewer.
His expression shifts from focused to playful.
He lowers his hands, then breaks into an exaggerated cheerful pose, raising both arms with bent elbows as if dancing in the shower, mouth open in a big grin.
The radio remains visible to his side, hanging near the spray.
The radio is shown mounted directly on the tiled wall while a hand turns the right-hand tuning knob.
The fingers grip the black knob and rotate it ; then the hand drops away, leaving the unit centered on the blue tile.
The “ Splash Dance ” logo, tuning scale, and three knobs remain visible.
The setting changes to a bathtub : an adult blonde woman reclines in a white tub filled with water, bare shoulders above the surface.
Her short, wet blonde hair is swept back.
She rests both arms along the tub edges, eyes relaxed, with a calm smile.
The Splash Dance radio is fixed on the tiled wall above and behind her, within easy reach but away from the waterline.
She looks comfortable and still, appearing to enjoy the bath while the product sits prominently in the background.
The earlier showering woman reappears in close view, wet hair slicked back, one hand near her ear and cheek.
The hanging radio is beside her again, its black front wet with droplets.
She tilts her head back slightly, then moves forward and to the side, leaving the radio more fully visible.
The product hangs steady from its straps against the blue tiles, with the white controls below the black grille.
Finally, a bold graphic fills the screen : a large pale-yellow ring or letter-like curve against a dark blue background, cropped so only part of the shape is visible.

% matched lemmas: text
\end{textsample}
