\begin{textsample}{NEG Dim 6 – 2020 – Score -2.00 – 2020/tv\_com\_2020\_69.txt}  \label{ex:f6_neg_040}
The commercial opens on a bright white centre surrounded by Samsung phones arranged like a colourful ring.
Only the backs of the phones are visible at first, showing rectangular black camera modules with three lenses and a flash.
The phones come in red, pale mint green, lavender pink, and dark navy blue.
In the middle, black \textbf{text} reads “ Galaxy S20 Fan Edition 5G, ” then \textbf{updates} to “ Galaxy S20 FE 5G, ” with very small legal \textbf{text} along the bottom about colour availability.
The ring of phones breaks apart into a swirling pattern.
Phones of different colours rotate and stretch outward in several curved streams, some showing their backs and others showing their screens with portrait images of people.
The white background stays clean and glossy, making the phones look like they are moving through a bright studio space.
A close view of dark navy phones follows.
They stand upright in a staggered line, emphasizing their matte backs and the vertical triple-camera module near the top corner.
Black on-screen \textbf{text} appears beside them : “ Pro-grade camera, ” later expanding to “ Pro-grade camera for \#nofilter fans. ” A thin line like a visual pulse runs horizontally behind the devices.
The focus shifts to the camera zoom feature.
Several upright phones stand in a row, and the central phone displays a camera app interface.
On its screen is a young adult with a black beanie and a burgundy T-shirt, standing with arms folded against a blue background.
To the left, \textbf{text} counts up through “ 21x Space Zoom, ” “ 29x Space Zoom, ” and “ 30x Space Zoom. ” As the phone ’s camera interface zooms closer, the person ’s full body becomes a tight profile and then a close-up of their face.
The \textbf{text} changes to “ 30x Space Zoom for close-up fans. ” The phone screen briefly turns white, then shows the finished close-up portrait filling the display.
Next, long rows of pale mint green phones form a symmetrical corridor on a glossy white floor.
The lighting gradually darkens until the space becomes almost black, with the mint phones faintly glowing along both sides.
Two large phone screens rise at the far end, then one central phone shows a staged portrait of two young adults seated inside a mint-coloured set made of blocks and steps.
One person, wearing a dark jacket over a blue shirt, sits casually with one arm bent near their head.
Beside them, a person with very short bleached hair wears a fitted red top, pale pink trousers, and white sneakers, sitting with one knee raised. \textbf{Text} appears around the phone : “ Night mode ” on the left and “ for party all-night fans ” on the right.
The screen brightens, making the two seated people clear despite the surrounding darkness.
The scene returns to a bright white background as lavender phones sweep past in the foreground.
More lavender phones stand in a line, again showing the triple-camera module.
The display demonstration changes to a front-facing phone showing the Instagram app.
The feed scrolls vertically through posts from “ samsungmobile, ” including colourful images of young performers and group scenes.
On the left, the refresh-rate number rises through “ 64Hz, ” “ 78Hz, ” and “ 102Hz, ” then becomes “ 120Hz display. ” As the Instagram feed continues moving smoothly, the \textbf{text} grows into “ 120Hz display for smooth scrolling fans. ” The phone screen shows familiar Instagram icons, likes, captions, and multiple posts, including groups of people dancing and bright rainbow-like colour bursts.
The phones then appear from above in sweeping curved rows, forming spiral and circular patterns across the white floor.
Some phones show their screens with faces and performance images ; others show their coloured backs.
Red, lavender, mint, and navy devices alternate in bands, creating a large, decorative arrangement of many Galaxy phones.
A series of close-ups highlights the colour choices.
A mint green phone fills the right side with its triple-camera module visible, while \textbf{text} on the left reads “ With colors for every fan. ” The phone colour changes through red, lavender, and navy blue, each time showing the same vertical black camera panel with three lenses and a flash.
More phones then slide into view, overlapping in mint, red, lavender, and navy.
The final product lineup appears on a white background.
Several phones stand upright in a loose row, mixing backs and screens.
On the screens are large portrait images : a person with very short blond hair in a light top, a smiling person behind them, and another person in a yellow outfit on a lavender phone.
To the right, bold black \textbf{text} reads “ The new Galaxy S20 FE 5G, ” followed by the smaller line “ All you want, to do all you love. ” At the end, “ Available now ” appears beneath the slogan, while fine-print legal information runs along the bottom of the screen.

% matched lemmas: text, update
\end{textsample}
