\begin{textsample}{NEG Dim 6 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_54.txt}  \label{ex:f6_neg_067}
A silver, stretch-looking sedan is parked beside Shell gas pumps under a yellow canopy with red Shell lettering.
The Shell logo appears on the pumps, and black fuel hoses hang from their sides.
The car ’s front end moves into prominence, its chrome grille and rectangular headlights filling the view.
Its front license plate reads “ JUDGES, ” setting up the idea that the people inside are evaluating the service.
A Shell attendant, a light-skinned adult man with short dark hair, wearing a red polo shirt, khaki trousers, and light shoes, rushes into action beside the car.
He moves with exaggerated, energetic, almost dance-like gestures.
At the pump, he grabs the fuel nozzle, swings the hose around, and turns toward the car with a focused expression.
The sedan ’s fuel door is open, exposing the dark filler opening.
In a close view, the blue-handled nozzle is guided into the fuel inlet.
The attendant stands by the rear side of the silver car as the nozzle sits in place, then spins away with his arms extended, as if moving from one service task to the next.
He lifts the car ’s hood at the front, leaning over the chrome grille beneath the Shell canopy and station lights.
With the hood open, the engine compartment is visible in the foreground while the attendant works beyond it, reaching in and checking something under the hood.
The setting remains a bright outdoor service station, with the station building and forecourt visible behind him.
A display of gray plastic bottles, likely automotive service products, appears in neat rows ; each bottle has a black cap and a Shell-colored label with red and yellow panels.
A hand reaches down and selects one bottle from the lineup.
Back outside, the attendant appears beneath the large Shell sign, still in his red shirt and khakis, moving briskly through the service routine.
Later, the fuel nozzle is shown being removed from the car ’s filler opening.
In a close view, the metal nozzle is held out while the attendant wipes or polishes it with a red cloth, treating even the nozzle as something to be cleaned carefully.
Through the car window, a woman inside watches him, her face partially framed by the dark interior and the window opening.
From inside the car looking outward, the attendant stands outside the window in front of the station building.
He poses with one hand on his hip and the other arm raised, as if presenting his completed service for judgment.
Inside the dark, limousine-like passenger compartment sit several formally dressed adults in suits, including a woman and older men.
They hold up large white scorecards with bold black numbers.
Cards marked “ 10, ” “ 9, ” and “ 6 ” are raised and shuffled into view above their laps and near the roof opening.
The front of the silver sedan is shown with scorecards protruding above the roofline.
At first the visible scores include “ 10 ” and “ 6, ” then the judges ’ cards change until three “ 10 ” cards are displayed across the top of the car.
Another card marked “ 9 ” appears at the side.
The car ’s chrome grille and hood ornament remain centered below the cards, reinforcing the judging theme.
The final image becomes more graphic and stylized.
The silver car remains at the center while the scorecards hover above it, reading “ 10 10 10 9. ” Pale, sweeping shapes pass around the vehicle like animated panels or a visual wipe.
The Shell pecten logo appears large and centered over the car ’s windshield and grille.
Across the lower left and bottom of the image, bold white \textbf{text} comes into view reading “ The Move Is On, ” paired with the Shell logo as the commercial ’s closing visual.

% matched lemmas: text
\end{textsample}
