\begin{textsample}{NEG Dim 6 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_59.txt}  \label{ex:f6_neg_025}
The commercial begins with a static graphic that does not yet show a car.
On a dark background, white text reads “ Prince Superoni / Prince Ave. / Lowell, Mass. / 01853. ” A small portrait of a man appears in a rectangular inset at upper right, and a dark product package labeled “ SUPERONI ” is shown across the lower portion of the frame.
The scene then cuts to an outdoor car setting.
A light-colored hatchback or wagon is parked with its rear liftgate open.
An adult person stands near the open cargo area.
Large translucent block letters spelling “ NISSAN ” are superimposed across the center of the image.
Trees and daylight are visible in the background.
The following shots use heavy dissolves and overlapping images, making some details unclear.
A light-colored car is shown from the side under leafy trees, with reflections or double exposure effects over the body.
The camera then appears to move to the front/driver area of a car, with the windshield and dashboard area visible through layered imagery.
A person inside or near the car is partially visible, but the overlapping frames make their exact position unclear.
The commercial shifts to driving imagery.
A red car is seen on a road near a coastline or body of water, with hills or greenery in the background.
The road and scenery are sunlit.
This is followed by a close-up of a smiling adult male driver, seen through or reflected on a windshield, overlaid with an exterior view of a red vehicle.
He appears to be seated behind the steering wheel, though the layered dissolve makes the view partly ambiguous.
More driving footage follows.
A light-colored car is seen from the side on a road bordered by trees, again with a superimposed image of the driver ’s face and interior reflections.
The montage then shows a red sports car or coupe from a low, \textbf{tilted} angle, driving or cornering on a paved road with trees and hillside in the background.
The commercial ends on a black background with a large red “ NISSAN ” logo.
Beneath it, in white italic lettering, is the phrase “ MAJOR MOTION. ” A small Nissan badge or logo appears centered near the bottom.

% matched lemmas: tilted
\end{textsample}
