\begin{textsample}{NEG Dim 6 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_73.txt}  \label{ex:f6_neg_081}
The commercial begins in black and white with a large RCA emblem centered against a dark, starry-looking background.
The letters “ RCA ” sit inside a circle, with a small lightning-bolt-like mark beneath them.
A cartoon alarm clock appears next.
It is an old-fashioned round clock with two bells on top, little legs, and animated arms.
Its face has large numerals and exaggerated hands, and it behaves like a noisy, bothersome character.
It rocks and dances around, its bell cap bouncing, its arms flailing, and its clock face changing into a grimacing, toothy expression.
A pale human hand reaches in from the right and presses down on the top of the clock, squashing it low and flattening its animated face into a strained frown.
When the hand lifts away, the clock pops back upright.
The cartoon image then gives way to a darker bedroom setting, with the alarm clock briefly still visible in a spotlight-like circle before the scene changes fully to a real room.
In the bedroom, an adult woman lies in bed beside a nightstand.
She has dark, wavy hair and is under light-colored sheets, with a padded, tufted headboard behind her.
On the nightstand sits the RCA Victor clock radio : a rectangular, light-colored unit with a round clock dial on the left, a speaker grille in the middle, and a circular tuning dial on the right.
A table lamp with a broad shade stands behind it.
The woman is shown asleep, turned toward the clock radio.
She begins to stir gently, opens her eyes, and smiles faintly.
She raises herself slightly, then relaxes back into the pillow, appearing comfortable rather than startled.
A large transparent clock face is superimposed over the bedroom scene, its numerals and hands filling much of the screen while the woman remains visible beneath it.
As the clock graphic remains over the bed, the woman continues lying down.
Later, she wakes more abruptly, lifting her head and opening her mouth as if responding to a later alarm signal.
The visual emphasis is on the passage of time and the clock radio ’s timed waking function.
The product is then shown in close-up on the nightstand.
A hand adjusts the circular clock dial on the front left side.
Around the dial are large printed numbers, and small protruding tabs or indicators sit near the dial ’s edge.
The hand turns or sets the clock mechanism, then moves away, leaving the clock radio ’s front clearly visible : clock on the left, horizontal speaker grille on the right side of that earlier model view, and clean, simple 1950s styling.
The commercial next presents another close view of the clock radio ’s control panel, now centered against a plain background.
The face is darker, with two round controls : a small clock or timing dial on the left and a larger radio tuning dial on the right.
The RCA Victor name is printed on the lower right of the panel.
The layout is plain and symmetrical, emphasizing the functional dials and the brand mark.
The radio is turned around to show its back panel.
A hand rests on top and then points to different features on the back.
The rear is a dark rectangular panel with a printed instruction or information label in the center, a round opening or socket on the right, and smaller sockets or switches on the lower left.
The hand points first toward the central label, then down toward the lower-left connections.
A cord is brought in and plugged into one of the back-panel outlets.
The hand steadies the radio while inserting the plug, then withdraws.
As the plugged-in cord trails away from the back of the radio, a tall metal coffee maker appears to the left on the same surface.
It has a cylindrical body, a handle, and a lid, with its cord looping across to the clock radio.
The arrangement shows the coffee maker connected through the radio ’s built-in outlet, with the radio acting as the timer or controller for the appliance.
The scene returns to the bedroom at night.
The lamp on the nightstand is lit, the clock radio sits beside it, and the woman lies asleep on her pillow.
The bed, tufted headboard, and soft bedding fill the right side of the scene, while the radio and lamp are on the left.
The woman ’s face is calm, her eyes closed.
In a closer view, the radio remains beside her, its dials and central grille visible.
Then the room darkens : the lamp goes out, leaving the radio and the sleeping woman in dimmer light.
The visual suggests the device has turned off the bedside lamp automatically while she sleeps.
The clock radio is then isolated against a plain dark background, shown as a clean product display.
It is light-colored, rectangular, with the round clock on the left, a central vertical grille of close horizontal slats, and the radio tuning dial on the right.
Two small knobs sit beneath the grille.
The RCA Victor name is printed near the lower right corner.
A stylized profile of a human head appears over the speaker grille, like a graphic emblem associated with sound or tone, centered between the two dials.
A large price graphic appears over the product : “ \$39.95 ” in bold, raised-looking white lettering.
Beneath it, smaller capital letters read, “ SLIGHTLY HIGHER IN FAR WEST AND SOUTH. ” The price \textbf{text} sits across the face of the clock radio, partially covering the central grille and dials.
After the price fades, the radio remains centered while the view broadens to reveal other RCA Victor radios arranged around it on shelves or display stands.
The clock radio stays in the middle.
Above left is a light-colored portable-style radio with a handle and a large circular dial.
Above right is a squarer radio with a large grille front and a handle-like frame.
Below and around the central clock radio are additional table and portable models, including darker rectangular units and lighter radios with rounded dials or grille fronts.
The display becomes a wall of different RCA Victor radio styles, with the featured clock radio at the center.
The final image overlays the brand identity over the display.
Large words “ RCA Victor ” appear across the upper center.
Below them is the familiar RCA Victor dog, seated and leaning toward the horn of an old gramophone.
Under the dog and gramophone, the slogan “ HIS MASTER ’S VOICE ” appears in quotation marks.
The closing visual holds on this brand mark, with the dog, gramophone, and large RCA Victor lettering dominating the screen.

% matched lemmas: text
\end{textsample}
