\begin{textsample}{NEG Dim 6 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_24.txt}  \label{ex:f6_neg_065}
A small child stands inside a white crib or playpen in a softly lit home interior, gripping the top rail.
She has light, curly hair and wears a pale pink shirt under light-colored overalls.
An adult, likely her mother, is partly visible beside her in pale blue clothing, moving away from the playpen.
As the adult leaves, the child watches with a serious, curious expression, then brightens and raises one hand to wave.
A warm table lamp glows behind her, adding to the domestic nursery-like setting.
A large yellow bottle of Brite floor cleaner is then placed prominently on the shiny floor in front of the playpen.
The label is black with a fan-shaped yellow-to-red burst above the large white word “ Brite. ” Smaller label \textbf{text} reads, “ Cleans \& Shines No-Wax Floors Without Build-Up. ” The child remains in the background behind the white rails, while an adult hand reaches in from the side, grasps the bottle, and lifts it away.
The child is later sitting inside the playpen among toys, including bright-colored balls and a plush toy.
She holds the yellow Brite bottle upright with both hands, studying it as if fascinated by the container.
She turns it and fiddles around the cap area, her face intent and absorbed.
The bottle fills the view in close-up again, emphasizing the Brite label and its sunburst-style graphic.
An adult hand tilts the yellow bottle sideways, and a pale stream of liquid pours from the open spout.
The product is then spread across dark square floor tiles with a flat mop or applicator.
The applicator glides along the floor, leaving behind a wet, glossy strip that reflects light clearly.
The treated section looks darker and shinier than the surrounding tile, with the grout lines still visible beneath the sheen.
The child ’s face appears in close-up, her eyes widening and mouth slightly open as she watches.
A close view of the floor shows the applicator at the far end of a long, wet-looking glossy path, the shine reflecting vertical shapes above it.
The child is then held by the adult woman near the playpen.
The woman, visible mostly in profile and wearing a blue top, lifts the child up and over the white rail.
The child ’s legs and pink slippers dangle as she is carried out, and then the playpen is left empty in the bright room.
The child lies on her stomach on the newly shined tile floor near a bright doorway or window.
She reaches out with one hand and pats or rubs the surface, examining the shine closely.
Her other arm supports her body as she looks down at the reflective tiles, then up, as though reacting to what she sees.
The floor appears smooth, dark, and mirrorlike, reflecting the room ’s light.
A wider view of the polished floor shows glossy square tiles stretching across the room.
The child ’s pink slippered feet step into view, and she stands on the shiny surface in her pale overalls.
She takes small, unsteady steps, then lowers herself awkwardly, one hand reaching toward the floor for balance.
She ends up sitting on the floor with one leg extended and the other bent, still surrounded by the bright reflections on the tile.
In the final product display, the yellow Brite bottle stands large in the foreground on the polished floor.
Behind it, the home interior is visible : the adult woman stands to the left, the child sits farther back near the center, and the room has large windows, a white playpen railing, hanging plants, and a ceiling with colored rectangular panels.
The floor remains glossy and reflective.
White on-screen \textbf{text} appears along the bottom : “ TURN ON A Brite SHINE, ” with “ Brite ” written in a script style matching the brand emphasis.

% matched lemmas: text
\end{textsample}
