\begin{textsample}{NEG Dim 6 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_29.txt}  \label{ex:f6_neg_005}
A white toilet sits centered in a tidy, old-fashioned bathroom with floral wallpaper, a bathtub on the right, a vanity on the left, a potted plant on the floor, and a toilet paper roll mounted behind it.
The scene then moves quickly through many different bathrooms and toilet styles.
A mint-green toilet appears in a tiled bathroom, with a dark Clorox bottle on the floor beside it.
Next is a childlike yellow-tiled bathroom : a small toilet has a fuzzy blue seat cover, toys and a step stool are scattered nearby, and a little potty seat sits to the right.
A glossy black toilet stands in a more polished bathroom with pale marble flooring and a tall black pedestal sink reflected in a mirror.
Then a retro bathroom with orange patterned wallpaper and shag carpet shows only the lower half of a person perched on the toilet, bare feet on the closed lid, wearing a colorful robe or garment ; a Clorox container sits on the floor near the vanity.
A deep red toilet follows in a narrow bathroom with textured white walls, a fern on the floor, a red wastebasket, and a Clorox toilet cleaner bottle standing near the base.
The images continue with a plain \textbf{modern} toilet against a wood-paneled wall, flanked by a toilet paper stand and a sculptural white vase, with a blue Clorox bottle on the floor.
A white urinal appears in a public restroom stall with green tile behind it.
Outdoors, a rustic wooden outhouse stands among dense greenery, with a crescent moon cut into its door and a wheelbarrow and shovel nearby.
Another institutional-looking toilet is mounted low in a stark \textbf{concrete} corner, with chain fixtures on the wall and a metal fence along one side.
More toilets appear in varied home settings : a small bathroom with a sink in the foreground, slippers on the floor, and a compact toilet at the back ; a white tiled bathroom with a high tank, a wooden toilet seat, a basin on the floor, and a Clorox bottle nearby ; and a sleek metallic wall-mounted toilet set into a dark blue tiled alcove.
A white toilet with a black seat is shown in a tiled bathroom beside a pedestal sink and a stacked toilet paper holder.
Another toilet is tucked into a narrow space between tall stacks of books, with a plant behind it, a pink toilet brush, and a tan seat cover.
A toilet with shiny gold-colored seat and lid stands in a marble-walled bathroom with a gold-toned toilet paper holder.
In a wood-paneled bathroom, a pink toilet seat with a simple face-like design on the lid is visible, and a Dalmatian dog stands in the foreground looking off to the side.
The montage then shifts to active cleaning : in a public restroom, a person wearing blue gloves wipes the outside of a small white toilet with a cloth.
Cleaning supplies sit on the floor, including a caddy and a Clorox-branded bottle.
A white toilet in a floral-wallpapered bathroom is shown with a Clorox bottle on the floor nearby, along with a plunger and pink robe or towel hanging to the side.
A pale blue toilet appears in a pastel-tiled bathroom beside a blue bathtub and shower.
Then a person in cuffed jeans and white shoes holds a blue Clorox toilet bowl cleaner bottle over an open toilet bowl, applying the cleaner inside the rim.
Another bright bathroom shows a white toilet with its lid up, a plunger beside it, folded towels stacked on shelves to the right, and a Clorox product placed high on the shelf.
The sequence continues with a \textbf{vintage} pink toilet against green and black tile, accompanied by a scale and wastebasket.
In a wood-paneled, old-fashioned bathroom, a small white toilet with a wooden seat stands near a claw-foot bathtub ; only the lower half of a person in black shoes and a long white apron is visible beside it.
Finally, that apron-wearing person leans in toward the toilet holding a Clorox bottle, preparing to clean it, with the wooden seat raised and the toilet centered against the dark wood wall.

% matched lemmas: concrete, modern, vintage
\end{textsample}
