\begin{textsample}{NEG Dim 6 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_93.txt}  \label{ex:f6_neg_007}
The commercial opens in a dark, high-contrast setting with a runner ’s lower leg and foot visible near a metal starting block.
The runner wears a white athletic shoe with bright neon yellow on the toe and sole.
Mist or smoke hangs around the floor.
The shoe presses into the angled starting block, then pushes off powerfully, lifting away as the block remains behind and a cloud of white vapor billows around it.
A tall, pale \textbf{concrete} slab then fills the view, its surface rough and speckled.
From the left, a bare human foot extends toward it, attached to a leg in dark clothing.
The sole strikes the \textbf{concrete}, and the slab bursts apart at the impact point.
White dust, powder, and broken fragments fly outward, making the foot ’s kick look forceful enough to smash through the material.
The imagery shifts to a car in the same moody, smoky atmosphere.
A wheel and the lower rear of a vivid blue Lexus sedan appear close to the ground.
Vapor swirls around the tire and the rear bumper, and a round exhaust outlet is visible.
The blue car accelerates away on a dark racetrack, its red taillights glowing as it moves along a wide paved curve bordered by low white barriers and lit by bright overhead track lights.
Small legal \textbf{text} appears near the bottom of some driving shots, but it is very small and not fully legible.
The blue Lexus continues through the night course, seen from different angles as it sweeps along the track.
Its glossy blue body catches the light, with sharp body lines, dark windows, and angular red taillights.
A silver or light gray Lexus sedan then appears facing forward on the track, its headlights on and the Lexus emblem centered in the grille.
The blue car is visible off to the side as the silver car advances, suggesting the two vehicles are driving together or crossing paths on the course.
The focus shifts to the silver Lexus sedan in profile, moving quickly along the barrier-lined track.
Its low, sleek body, dark wheels, and sculpted side panels are visible under bright track lighting.
In another close rear-side view, the silver car ’s rear wheel and taillight pass through drifting tire smoke or road haze.
The car continues around the course, with the blue Lexus ahead or nearby in the distance, both leaving a sense of speed and controlled motion on the dark track.
The commercial ends with three Lexus sedans parked side by side in a dark studio-like space under a cool overhead light.
From left to right, there is a blue sedan, a white sedan in the center, and a silver sedan on the right, all facing forward with their grilles and headlights visible. \textbf{Text} beneath them identifies the models and power figures : under the blue car, “ IS 200t ” and “ 241HP ” ; under the center white car, “ IS 350 / IS 350 AWD ” and “ 306HP ” ; and under the silver car, “ IS 300 AWD ” and “ 255HP. ”

% matched lemmas: concrete, text
\end{textsample}
