\begin{textsample}{NEG Dim 6 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_15.txt}  \label{ex:f6_neg_004}
At first, a small white desk fan sits on a bright work surface in a clean, \textbf{modern} office or studio.
Only part of a person is visible : light-skinned hands and the sleeve of a lavender-blue button-down shirt.
One hand steadies the fan ’s base while the other touches the white protective grille around the circular fan head.
On the desk nearby are a computer mouse in the foreground, papers or a notebook, and the edge of an open laptop.
The fan has a narrow pedestal, a round cage, and visible grey blades inside.
As the view widens, the person holding the fan is revealed as an older white man with short grey hair, wearing the same lavender-blue shirt.
He holds the conventional fan in front of him, angled slightly toward the viewer, with his left hand resting on the grille.
His expression is serious and focused, as if explaining what is wrong with this familiar design.
The imagery then shifts into older-looking footage.
In black and white, a man in a suit jacket sits at a desk beside a \textbf{vintage} metal fan with a wire cage and exposed blades.
He reaches toward papers on the desk near the fan, then toward the fan ’s controls or base.
The fan ’s round guard and metal stand look heavy and mechanical, and the scene has the grainy appearance of an old demonstration or period film.
More dated fan examples follow.
In a muted, old-colour kitchen, a red-bladed desk fan sits on a red countertop in the foreground.
Behind it, a woman in a sleeveless patterned dress stands near the sink and cabinets.
The kitchen has floral wallpaper and cream-coloured cupboards, giving it a mid-century domestic feel.
The fan ’s red blades are enclosed by a metal wire cage, and the centre hub is cream and red.
A closer view fills the image with the fan ’s grille and spinning red blades, which blur into a translucent red circle behind the metal spokes.
Another older-style domestic scene appears in a bedroom.
A man bends over a bed, packing or arranging clothes in an open \textbf{suitcase}.
In the foreground on the right, a large blue-bladed fan stands on a white pedestal, its wire grille facing into the room.
The bedspread is patterned in pale green and blue, and the fan dominates the right side of the scene while the man works behind it.
The commercial then moves into an abstract visual explanation of airflow.
Against a dark background, pale blue and green translucent shapes rotate around a small central hub like ghostly fan blades.
The shapes overlap and pulse in uneven lobes, suggesting disturbed, chopped-up air moving around a spinning propeller.
A close view returns to a conventional fan base.
A light-skinned finger presses down on a grey rectangular button set into a white plastic control panel, as if turning the fan off or changing its setting.
After this, the older grey-haired man in the lavender shirt is shown again from the shoulders up.
He faces forward with a calm, intent expression, continuing the explanation.
The final images present the Dyson Air Multiplier.
Against a black background, a smooth grey ring appears in close detail, with no visible blades or grille.
The ring has a thick, rounded airfoil-like edge and an open hollow centre.
Wispy, pale streams of air become visible along the side of the ring, flowing evenly from left to right across the dark background.
As more of the product is shown, the circular loop sits on a short cylindrical base.
A broad, steady, horizontal band of mist-like airflow extends from the bladeless ring, smooth and continuous rather than broken into bursts.

% matched lemmas: modern, suitcase, vintage
\end{textsample}
