\begin{textsample}{POS Dim 6 – 1970 – Score 12.00 – 1970/tv\_com\_1970\_13.txt}  \label{ex:f6_pos_041}
The commercial opens in a warmly lit living room with a 1970s homey look.
A middle-aged man with short dark hair sits in a high-backed, patterned armchair beside a brick fireplace and a glowing table lamp.
He wears a rust-orange sweater over a wide white \textbf{collared} shirt.
On a low table in front of him are papers or a magazine, a mug or small canister, and a few oatmeal cookies.
He reads from the paper, then pauses and looks toward the cookies.
Still holding the paper in one hand, he leans forward, reaches across the table, and \textbf{picks} up a cookie.
He brings it to his mouth, \textbf{takes} a bite, and chews thoughtfully.
His expression changes from neutral concentration to surprise and interest ; his eyebrows lift, and he looks down at the cookie in his hand as if reconsidering it.
He continues chewing, then looks up with a more convinced, \textbf{impressed} expression while still holding the partly eaten cookie near his chest.
The scene changes to a close view of freshly baked oatmeal cookies on a metal baking sheet.
A hand wearing or holding a red oven mitt steadies the tray.
The cookies are golden brown, irregularly rounded, and bumpy with oats and small morsel-like \textbf{pieces}.
A flat metal spatula slides under one cookie and lifts it from the tray.
Several cookies are transferred onto a dark, glossy \textbf{plate} in the foreground, where they pile up in a tempting stack.
Behind the cookies, a pale Nestlé \textbf{package} begins to come into view.
As the \textbf{plate} fills, the \textbf{package} is shown more clearly : large red “ Nestlé ” lettering across the top, with “ BUTTERSCOTCH ” in bold dark letters on a patterned band, and “ flavored morsels ” visible to the side.
The bag sits upright behind the cookies, making the product and the finished oatmeal cookies appear together.
The \textbf{package} remains prominent among the cookies.
The front of the bag shows the Nestlé name in large red letters and the word “ BUTTERSCOTCH ” across the middle.
A small oval \textbf{illustration} near the lower part of the bag shows morsels, with the phrase “ Original Toll House Morsels ” curved around it.
The cookies in front are golden and textured, with visible bits embedded throughout.
The commercial then shows a mixing bowl from above.
Inside is a thick oatmeal cookie mixture with pale flour or dry ingredients around the edges and a \textbf{mound} of small round butterscotch morsels in the center.
The Nestlé Butterscotch \textbf{package} is partly visible in the background.
A wooden \textbf{spoon} enters the bowl and begins stirring, folding the morsels into the dough.
The \textbf{spoon} pushes through the mixture repeatedly, dragging the dry ingredients and morsels together into a thicker batter.
As the stirring continues, the product bag behind the bowl becomes clearer again, with “ Nestlé ” and “ BUTTERSCOTCH ” filling much of the background.
A blond boy, around elementary-school age, appears next.
He has straight, light blond hair that falls over his forehead and wears large round \textbf{eyeglasses}.
He is dressed in a dark top with a warm yellow or orange \textbf{collar} and shoulder area.
He holds a cookie near his mouth, chewing and reacting with visible enjoyment.
His eyes close briefly as he leans back slightly, then he smiles and tilts his head, looking pleased.
He looks forward, then downward toward the cookie, and back up again, continuing to speak or react with a satisfied expression.
His face suggests approval, especially as he smiles softly after \textbf{tasting}.
The commercial closes on a product-and-cookie display.
A Nestlé Butterscotch Flavored Morsels bag lies angled in the foreground, its large red “ Nestlé ” name and bold “ BUTTERSCOTCH ” label clearly \textbf{readable}.
Behind it sits a dark \textbf{plate} heaped with oatmeal cookies, their rough oat texture and pale morsel \textbf{pieces} visible on top.
The warm brown background keeps the focus on the \textbf{package} and cookies.
Finally, the words “ Oatmeal Scotchies ” appear in light-colored text above the \textbf{plate}, identifying the finished cookies shown beside the Nestlé Butterscotch morsels.

% matched lemmas: collar, eyeglass, illustration, impressed, mound, package, pick, piece, plate, readable, spoon, take, taste
\end{textsample}
