\begin{textsample}{POS Dim 6 – 1980 – Score 11.00 – 1980/tv\_com\_1980\_108.txt}  \label{ex:f6_pos_036}
A white graphic background frames a rounded rectangular view of a home kitchen, with the red oval “ Post ” logo overlapping the upper left corner.
Inside the kitchen view, a young girl with long dark hair in two braids sits beside an adult man who appears to be her father.
She wears a yellow plaid shirt and sits at a breakfast table.
The man, with short brown hair, wears a light shirt under a gray-brown sweater vest.
The girl holds out a white cereal bowl toward him, and he \textbf{takes} it with a smile.
A purple Post Raisin Bran cereal box is visible on the left side of the table, showing large white “ RAISIN BRAN ” lettering and a \textbf{picture} of cereal.
The kitchen setting becomes clearer : \textbf{pots} and pans hang in the background, with shelves and household items behind them.
The girl beams happily as the man looks down at the bowl and begins to use a \textbf{spoon}.
On the table are two bowls of cereal, a glass of \textbf{milk}, a glass of orange juice, a \textbf{plate} with toast, and a white mug, arranged like a morning breakfast.
The commercial shifts to a product display.
A bowl filled with bran flakes and dark raisins sits against a purple background.
A diagonal white banner across the lower right reads “ NEW IMPROVED ” in large red letters and “ BETTER \textbf{TASTING} ” beneath it in black.
A wheat stalk graphic appears near the bottom right.
The purple Raisin Bran \textbf{package} then fills the view, with big white words “ RAISIN BRAN, ” the red “ Post ” logo near the top, and the line “ The Fruit and Cereal Lover ’s Cereal ” printed below the name.
The \textbf{package} front shows a bowl of cereal with flakes and raisins.
Back at the breakfast table, the Raisin Bran box stands prominently on the left.
The girl and the man each lean over their bowls with \textbf{spoons}, eating.
The girl looks intent and pleased, while the man raises a \textbf{spoonful} toward his mouth.
The table setting remains neatly arranged with \textbf{milk}, juice, toast, and a mug in front of them.
A clean demonstration graphic appears on a white background.
Three small red \textbf{packets} labeled “ PLUMP RAISINS ” sit along the top, and dark raisins pour down into a rounded pink-outlined rectangle marked with the red “ Post ” logo.
At the bottom, small black text reads “ 20 and 25 oz sizes. ” The raisins tumble and pile up, visually emphasizing their quantity and plump shape.
The scene returns to the kitchen.
The girl and the man sit close together, both holding \textbf{spoons} over their bowls.
The Raisin Bran box remains upright at the left edge of the table.
The man leans toward the girl as if sharing her reaction, and she looks down at her cereal with a pleased expression.
Another product demonstration follows on a white background : golden-brown bran flakes fall from above into the same pink-outlined rectangle with the “ Post ” logo.
The flakes cascade down over a \textbf{mound} of dark raisins, building a mixed pile of cereal and fruit.
In a close view at the table, the girl lifts a \textbf{spoonful} to her open mouth while the man, beside her, also eats from a \textbf{spoon}.
She \textbf{takes} a bite, then looks over at him with wide eyes and a satisfied, playful expression.
He turns toward her and smiles warmly.
They look at each other closely, sharing the moment over their bowls, before he looks back down to continue eating.
The cereal itself is shown in extreme close detail : rough, crinkled bran flakes surround glossy dark raisins, with small pools and streaks of \textbf{milk} visible between the \textbf{pieces}.
A metal \textbf{spoon} slides through the flakes, lifting and shifting them so the texture of the large flakes and the dark raisins stands out.
The commercial ends on a simple white background with a large purple rounded rectangle carrying the red “ Post ” logo and bold white “ RAISIN BRAN ” lettering.
A diagonal stamp reads “ NEW IMPROVED ” and “ BETTER \textbf{TASTING}, ” and below it the slogan appears in black : “ The fruit and cereal lovers cereal. ” Finally, the rounded kitchen window returns : the girl leans affectionately against the man ’s shoulder while he looks down at the table, both still seated together at breakfast, with the Post logo above and the same slogan printed beneath.

% matched lemmas: milk, mound, package, packet, picture, piece, plate, pot, spoon, spoonful, take, taste
\end{textsample}
