\begin{textsample}{POS Dim 6 – 2010 – Score 5.00 – 2010/tv\_com\_2010\_65.txt}  \label{ex:f6_pos_089}
It opens on a plain white screen with the FedEx logo centered in purple and orange, and small text underneath reading “ fedex.com/delivery. ” The scene then changes to a sunlit, luxurious backyard.
Tall cream-colored curtains frame the view like an outdoor cabana.
Beyond them is a rectangular reflecting pool or spa leading toward a large white two-story house with black shutters, balconies, and wide open doors.
The lawn is bright green, with lounge chairs and potted plants arranged around the pool, creating a polished resort-like atmosphere.
On the patio, an adult woman with long, wavy light-brown hair sits at a table.
She wears a fitted teal sleeveless dress, jewelry, and polished makeup.
She holds a clear glass mug of dark coffee in one hand and looks down at papers or a script on the table, then glances up.
A man approaches from the house carrying a gray \textbf{drink} tray with several white \textbf{cups}.
He is an adult man with short brown hair, light stubble, and black rectangular glasses.
He wears a light blue shirt, dark tie, dark vest or apron, and leather-like apron straps, giving him the look of a café barista.
He faces her with the tray held in front of him, appearing to offer coffee.
The woman stands near the poolside patio, still holding her glass mug.
She faces the man with a composed, slightly serious expression, as if beginning a conversation.
The man remains opposite her, holding the tray, looking puzzled and concerned.
She gestures subtly with the mug and then smiles, lifting the \textbf{drink} as if to show confidence in what she has.
The man responds by leaning forward and gesturing with one hand, his brow furrowed, while the woman keeps the mug near her face and smiles knowingly.
The woman \textbf{takes} a sip from the clear mug, which is filled with dark coffee topped by a pale layer of foam.
She gives a pleased, almost teasing smile.
The man stands by the patio furniture, one hand resting near a striped chair, still facing her as if questioning her choice.
She then appears with a tall clear iced \textbf{drink} instead of the small mug.
The \textbf{drink} is dark, with ice and a straw, and she holds it upright in front of her while smiling toward him.
The man ’s expression becomes more intense and curious ; he \textbf{removes} or holds his glasses in his hands while leaning forward, \textbf{trying} to understand.
The woman now holds a tall layered iced latte in a clear glass.
The bottom is dark coffee, the middle is white \textbf{milk}, and the top is a caramel-brown coffee layer, with ice visible and a straw \textbf{sticking} out.
She cradles the glass with one hand underneath and sips through the straw while maintaining eye contact with the man.
Her earrings and bracelets catch the light as she \textbf{drinks}.
The man gestures with both hands open, still in his barista-style outfit, looking incredulous.
She smiles, tilts her head, and gently stirs or touches the straw, clearly enjoying the \textbf{drink}.
Then she turns away from him and walks back toward the house in black high heels, her teal dress visible from behind.
The man bends over the patio table, where \textbf{cups} and papers remain, while she exits toward the interior.
Inside, the setting shifts to a bright modern white kitchen with glossy \textbf{counters}, pendant lights, a sink, flowers, and bowls of fruit.
On the \textbf{counter} sits the Ninja Coffee Bar machine, black and stainless steel with a clear water reservoir and a glass carafe beneath the brew area.
A lower-left graphic reads “ NINJA COFFEE BAR. ” The woman stands behind the \textbf{counter} beside the machine, animatedly presenting it.
Several finished \textbf{drinks} are arranged around the appliance : a black glass carafe to the left, a light-brown coffee \textbf{drink} in a glass mug, a layered latte, a small white \textbf{cup}, and a tall dark iced \textbf{drink}.
The barista man is partly visible at the left edge, watching from across the \textbf{counter}.
The woman places her hands near the top of the Ninja Coffee Bar as she demonstrates it.
A close view shows coffee streaming into the glass carafe on the machine.
The front control panel is visible with a digital display reading “ 11:15 ” and buttons and brew settings.
Another close view shows a manicured hand turning a round selector dial.
Around the dial are labeled size options with icons : “ TRAVEL, ” “ \textbf{CUP}, ” “ HALF, ” and “ FULL. ” Below the dial, a label reads “ CLASSIC BREW. ” The selector points toward the full carafe setting.
A display of \textbf{drinks} follows : the black Ninja carafe sits on a tray beside two clear glass mugs, one filled with a creamy tan coffee and one with dark coffee.
Then a close view shows a finger pressing a rectangular button labeled “ OVER ICE BREW, ” marked with a snowflake icon.
Beneath it is another button labeled “ SPECIALTY BREW ( CONCENTRATED COFFEE ). ” The “ OVER ICE BREW ” button lights up with a pale blue glow.
Back in the kitchen, the woman continues speaking and gesturing beside the machine, with the \textbf{drinks} lined up neatly around it.
The final product arrangement fills the \textbf{counter}.
The Ninja Coffee Bar stands centered, with the black-and-silver brewer in front, a clear ribbed water reservoir on the right, and a glass carafe under the spout.
To the left are the black carafe and a glass mug of tan coffee ; to the right are layered and iced \textbf{drinks} in clear glasses, including a dark iced coffee.
Large on-screen text appears to the left of the machine : “ NINJA ” in black, “ COFFEE BAR ” in white letters inside an orange rectangle, and “ NINJACOFFEEBAR.COM ” below.
Smaller text reads “ Available at ” with the Kohl ’s and Walmart logos underneath.
The product remains centered and brightly lit against the clean white kitchen background.

% matched lemmas: counter, cup, drink, milk, remove, stick, take, try
\end{textsample}
