\begin{textsample}{POS Dim 6 – 1970 – Score 10.00 – 1970/tv\_com\_1970\_43.txt}  \label{ex:f6_pos_044}
The commercial opens on a warm, reddish, out-of-focus image that quickly gives way to a small sailboat on calm water.
A young person with medium-length brown hair, wearing an orange life vest, crouches low in the white boat, hands braced on either side of the cockpit.
A large triangular sail rises behind them in broad diagonal blocks of dark blue, pale blue, and yellow.
The boat sits on smooth, silvery water under a pale sky, creating a quiet summer sailing scene.
The setting shifts to a sandy beach.
A little girl with light brown hair in two pigtails stands close to the viewer, wearing a light-colored swimsuit and holding a bright yellow plastic bucket against her chest.
Behind her are beachgoers sitting on the sand, a striped beach umbrella, a colorful beach ball, and sailboats near the shore.
She smiles and lifts the bucket forward, then tips it toward the viewer so that sand or water splashes across the image, filling the screen with yellowish blur.
Through the splash, the scene changes into a kitchen.
A smiling adult woman with short brown hair, wearing a loose pale pink top, stands in front of wood cabinets and a cream-colored refrigerator.
She holds a large glass jar of mayonnaise toward the viewer.
The label is visible and reads “ Hellmann ’s Real Mayonnaise ” in a dark blue panel on a yellowish background.
She beams broadly, presenting the jar as if introducing it.
The view widens to show her at a kitchen \textbf{counter} filled with food ingredients.
In front of her are a large white bowl of cubed potatoes, red \textbf{tomatoes}, leafy greens, long pale-green stalks, eggs or white oval vegetables, and a round wooden cutting board with diced ham and cheese.
The open jar of Hellmann ’s sits prominently on the \textbf{counter}.
The woman sets the jar down, gestures toward the bowl, and points to the ingredients, preparing to combine them.
A close view of the \textbf{counter} shows the bowl of potato salad base in the foreground, with pale potato cubes and herbs visible.
The woman tilts the round wooden cutting board over the bowl.
Small pink cubes of ham and pale yellow cheese cubes slide toward the edge.
Using a broad kitchen knife as a scraper, she pushes the ham and cheese off the board and into the bowl.
The jar of Hellmann ’s remains to the right, close to the bowl, with its label partly visible.
Back at the \textbf{counter}, the woman uses a wooden \textbf{spoon} to scoop mayonnaise from the open jar and add it to the potato mixture.
The creamy white mayonnaise sits in soft dollops among the potato cubes, ham, cheese, and herbs.
In close-up, she stirs the mixture with the \textbf{spoon}, folding the mayonnaise through the salad.
The bowl fills the foreground, with red \textbf{tomatoes} behind it and the Hellmann ’s jar standing immediately to the right.
The salad becomes increasingly coated, the white creaminess spreading over the cubes as she mixes.
The scene moves outdoors to a picnic beside a lake or waterfront.
The woman, still in her pink top, carries a large bowl or \textbf{platter} of the prepared salad to a round wooden picnic table.
A man with short dark hair in a black-and-white striped polo shirt reaches eagerly across the table to \textbf{take} it.
A young girl with pigtails sits nearby, and the colorful sail from earlier is visible in the background near the water.
The table is full of summer food : bowls, \textbf{plates}, glasses, skewers or grilled items, and the potato salad.
The man receives the \textbf{dish} while smiling, and the little girl looks delighted.
A closer view shows the girl seated beside the man.
She wears a light-colored top and smiles toward the table, while the man \textbf{serves} or prepares food on his \textbf{plate}.
The \textbf{plate} in front of them holds a generous portion of creamy potato salad alongside other picnic food.
Another guest arrives at the table : a young adult man with curly light-brown hair, bare-chested, with a towel draped around his neck and blue shorts.
He leans in from the side as the woman offers him a \textbf{plate} piled with the creamy salad.
He \textbf{accepts} it and sits with the group.
The waterfront remains visible behind them, with a stone edge, calm water, and distant shoreline.
The little girl is then shown close-up at the table with the lake behind her.
She lifts a forkful of potato salad from her \textbf{plate} and brings it to her mouth.
She eats, looks down at the \textbf{plate}, and continues holding the \textbf{fork}, appearing pleased and focused on the food.
A small \textbf{piece} of other picnic food rests on the \textbf{plate} beside the salad.
The young man with the towel is shown in close-up next.
He leans over his \textbf{plate}, raises a forkful of salad, and \textbf{takes} a bite.
He chews with a satisfied expression, looking out slightly toward the table and water.
The lakeside background stays soft and bright behind him.
The group is then seen together around the picnic table.
The woman sits with her back partly turned, the striped-shirt man \textbf{serves} from the center, the young man eats on the right, and the girl sits on the left.
The atmosphere is relaxed and summery, with the lake and pale sky beyond them.
In the final product display, the people at the picnic table become softly blurred in the background.
In the foreground, a \textbf{platter} of creamy potato salad sits on the table, garnished with colorful vegetables, and a large glass jar of Hellmann ’s Real Mayonnaise stands prominently to the right.
The label is clear : “ HELLMANN ’S REAL MAYONNAISE. ” Large white on-screen text appears to the left of the jar reading “ The BEST. ” The commercial ends with the jar and the words “ The BEST ” dominating the image while the family picnic continues in the background.

% matched lemmas: accept, counter, dish, fork, piece, plate, platter, serve, spoon, take, tomato
\end{textsample}
