\begin{textsample}{POS Dim 6 – 2020 – Score 11.00 – 2020/tv\_com\_2020\_2.txt}  \label{ex:f6_pos_003}
The commercial opens with a \textbf{tight} close-up of a bald, middle-aged man in a black suit, white shirt, and black tie against a plain white background.
His face is expressive, and he appears to be addressing the camera.
The scene then widens to a bright white \textbf{bathroom}.
The same man is \textbf{kneeling} beside an open toilet, wearing bright pink rubber \textbf{gloves} while still dressed in the suit.
Around him are \textbf{cleaning} \textbf{supplies} : a blue bucket filled with cloths and bottles, a blue \textbf{towel} hanging on the bathtub, a toilet paper roll, and a small potted plant on the toilet \textbf{tank}.
He holds a spray bottle and a \textbf{cleaning} cloth or sponge.
The \textbf{bathroom} shot continues, with the man positioned beside the toilet.
A \textbf{transparent} bottle is visible on the left side of the frame, suggesting a product close-up or a split-screen transition, while the man remains on the right beside the toilet.
A split-screen-style visual follows : on the left is a close-up of a dirty or \textbf{stained} surface with a round dial or gauge-like object ; on the right, the man is still in the \textbf{bathroom} near the toilet, wearing the pink \textbf{gloves} and holding cleaning items.
The setting then changes to a different room with a white brick wall.
A globe and a table lamp stand on the left, while a metal safe or cabinet is open on the right and appears filled with many paper items.
A spray bottle sits on top of the cabinet.
The man, still in his suit, leans in from the right side of the frame, looking toward the camera.
Next, the man appears beside a framed portrait of himself.
He holds a spray bottle and a cloth, as if \textbf{cleaning} the glass or frame.
The left edge of the frame shows part of another close-up image, including a hand and wristwatch, suggesting another split-screen or transitional montage.
The commercial returns to the \textbf{bathroom}, where the man is now lying in a bathtub filled with many small paper slips or money-like pieces.
He is still wearing the black suit, with a blue patterned shower cap on his head. \textbf{Towels} and \textbf{bathroom} shelving are visible nearby.
A product display then appears on a \textbf{clean} white background.
Four cleaning products are lined up : three spray bottles containing blue, pink, and yellow liquids, and a clear pump bottle.
Above them is the word “ BLUELAND ” in large blue lettering, and below it is a dark rectangular button reading “ SHOP NOW. ” Small tablet-like objects or packaging pieces are placed in front of the bottles.
The smaller text on the product labels is not clearly readable.
The final shots return to the \textbf{bathroom}.
The man \textbf{kneels} beside the open toilet again, wearing pink \textbf{gloves}.
He sprays or holds a pink liquid spray bottle and uses a blue cloth near the toilet seat.
In the last frame, he faces the camera while holding the spray bottle in one hand and the blue cloth in the other, with the bucket of \textbf{cleaning} \textbf{supplies} still visible on the \textbf{floor} nearby.

% matched lemmas: bathroom, clean, floor, glove, kneel, stain, supply, tank, tight, towel, transparent
\end{textsample}
