\begin{textsample}{POS Dim 6 – 2020 – Score 9.00 – 2020/tv\_com\_2020\_17.txt}  \label{ex:f6_pos_062}
In a bright, home kitchen with wooden cabinets and soft daylight, an adult woman with long light-brown hair stands facing a young girl across a white kitchen island.
The woman wears a loose blue \textbf{short-sleeved} button-up shirt and looks down toward the child with a calm, matter-of-fact expression.
A large red Eggo logo briefly appears centered over her torso.
The girl, who has long brown hair and wears a pink-and-magenta striped long-sleeved top, sits at the \textbf{counter} with her hands folded, looking up at the woman as if responding to breakfast choices.
The woman then holds up a yellow Eggo waffle box at the kitchen island, angled toward the girl.
The girl turns toward it from her seat.
The kitchen feels lived-in and domestic : a stove and microwave are visible behind them, \textbf{utensils} sit near the \textbf{counter}, and a \textbf{plate} or bowl of fruit is blurred in the foreground on the island.
The scene shifts to a middle-aged man with curly dark hair and a full beard, wearing a pale striped button-down shirt over a white undershirt.
He stands in a yellow-walled room near a white door, staring forward with a serious, slightly suspicious expression.
Over several moments, his eyes shift and his face remains tense and puzzled, as if he is reacting to something unexpected off-screen.
He gradually moves out of view to the left, leaving the background softly blurred.
A black-and-white dog with large upright ears and a bright blue \textbf{collar} sits in another part of the home, facing forward.
Its mouth is open, giving the impression of an eager or excited reaction.
Behind the dog is a wooden cabinet or dresser, a framed family photograph on the wall, and warm household decor, reinforcing that this is the same family home.
The commercial then focuses closely on the food.
A golden-brown waffle sits on a \textbf{plate} with a square pat of butter melting on top.
Amber syrup streams down over the waffle ’s grid, pooling in the square pockets and \textbf{dripping} over the edge onto another waffle beneath it.
The syrup continues to flow in glossy ribbons, emphasizing the \textbf{crisp} ridges and soft-looking interior.
Hands hold a waffle close to the viewer and begin pulling it apart.
A yellow circular graphic appears on the left with red and black text reading “ 0 \% artificial colors or flavors, ” and small white text below reads “ *Homestyle Waffles. ” As the waffle separates, its fluffy pale interior tears open between the \textbf{crisp} golden edges.
Back at the kitchen table, the young girl holds a waffle with both hands and \textbf{takes} a bite.
A white \textbf{plate} with another waffle sits in front of her, with a \textbf{spoon} nearby and a syrup container partly visible at the lower left.
In the background on the \textbf{counter}, the yellow Eggo box is visible.
The girl closes her eyes and leans back slightly, smiling with satisfaction as she chews.
The final image is a bright yellow product display.
On the left, red text reads “ L’Eggo my Eggo. ” On the right sits a yellow Eggo Homestyle waffle box, showing a \textbf{picture} of a waffle with butter.
The box includes visible claims such as “ 0 \% artificial ” and “ No high fructose corn syrup, ” with the red Eggo logo large on the front.

% matched lemmas: collar, counter, crisp, drip, picture, plate, short-sleeved, spoon, take, utensil
\end{textsample}
