\begin{textsample}{POS Dim 6 – 1950 – Score 4.00 – 1950/tv\_com\_1950\_34.txt}  \label{ex:f6_pos_085}
The commercial is in black and white and appears to be staged against curtain-like studio backdrops.
At the beginning, the frame shows only a textured curtain or draped background, with no people or products visible.
The next scene shows a woman in front of a curtain backdrop.
She wears a soft, textured hat and a coat or jacket.
She is holding a small hand mirror in one hand and appears to be \textbf{wiping} or \textbf{applying} something to her cheek with a \textbf{pad}, cloth, or tissue in the other hand.
Her gaze is \textbf{directed} toward the mirror as she attends to her face.
Later, a different woman is shown facing forward, framed between ornate decorative mirror edges.
She holds a white \textbf{pad}, cloth, or tissue to one side of her face, as if cleansing or \textbf{applying} a facial product.
The background is again a shimmering or curtained studio backdrop.
The next scene cuts to a man in a dark suit and tie, positioned in front of a curtain backdrop.
Behind him on the left is a large display or oversized product-shaped sign resembling a bottle.
Some text is visible on it but not fully legible in the sampled frame.
The man faces the camera with a slight smile, suggesting a presenter role visually, though no audio content can be inferred.
The final frame is a close-up of a retail display package containing two bottle-shaped containers.
A sign above them reads “ FACIAL CLEANSING LOTION ” and prominently “ Special 89¢. ” At the bottom, the display includes pricing or savings text, including “ Save 51¢. ” The product labels on the bottles are partially visible but not fully clear in the frame.
The overall visual emphasis at the end is on the packaged facial cleansing lotion offer.

% matched lemmas: apply, direct, pad, wipe
\end{textsample}
