\begin{textsample}{POS Dim 6 – 2020 – Score 7.00 – 2020/tv\_com\_2020\_40.txt}  \label{ex:f6_pos_066}
Inside a brightly lit refrigerator, food and \textbf{drinks} are arranged like a small stage.
A blue Ensure Original nutrition shake bottle and a white Ensure Max Protein \textbf{carton} stand upright in the center, both animated with small white arms.
Around them are an orange juice \textbf{carton}, condiments, broccoli, \textbf{tomatoes}, an onion, jars, and other refrigerator items.
The Ensure Max Protein \textbf{carton} is white with purple and brown accents and a chocolate splash at the bottom of the label ; it faces forward as the featured product, while the blue Ensure bottle stands nearby.
The white Ensure Max Protein \textbf{carton} moves into prominence among the other refrigerator items.
A large on-screen graphic appears to its right reading “ MORE ENERGY in just 2 WEEKS, ” with the number 2 inside a purple circle and radiating lines around it.
A sliced orange sits in the foreground, and an anthropomorphic tomato-like character with eyes is partly visible to the right.
A thin line of small disclaimer text runs along the bottom of the image.
The Max Protein \textbf{carton} raises one arm with a confident, presenting gesture, standing in front of \textbf{milk} jugs, broccoli, and condiments.
The scene shifts to another part of the refrigerator.
A yellow pear with tiny eyes and white arms stands beside the tall orange juice \textbf{carton}.
The blue Ensure Original bottle is partly visible on the left.
The pear reaches toward the orange juice \textbf{carton} as if \textbf{trying} to handle it.
The Ensure Max Protein \textbf{carton} appears from the right side of the orange juice \textbf{carton} and begins to \textbf{take} hold of it, placing its white arms against the \textbf{carton}.
The orange juice \textbf{carton} is large and yellow-orange, with a splash design and the words “ orange juice ” near the top.
As the Max Protein \textbf{carton} pushes or carries it aside, the pear watches.
The orange juice \textbf{carton} slides across the refrigerator shelf, revealing celery stalks, a carrot, and a smiling banana behind it.
The pear relaxes and smiles while the Max Protein \textbf{carton} continues moving the juice \textbf{carton}, leaning into the effort with its arms stretched out.
The imagery then becomes a close-up of a creamy chocolate-colored \textbf{drink} pouring into a pool of the same liquid.
The stream plunges into the surface, creating a rounded splash, ripples, and droplets.
The liquid looks thick and glossy, with warm brown highlights.
As the pouring continues, a blue rectangular graphic appears on the right reading “ 30g PROTEIN ” in white and dark lettering.
The chocolate liquid swirls and splashes around the pouring stream.
A second blue graphic appears below it reading “ 1g SUGAR, ” emphasizing the nutrition numbers while the \textbf{drink} continues to ripple and bubble.
The commercial ends on a clean product display against a light blue background.
Three Ensure Max Protein \textbf{cartons} stand side by side : \textbf{milk} chocolate, French vanilla, and café mocha.
Small flavor-related items sit in front of them, including chocolate \textbf{pieces}, a vanilla flower, and coffee beans or mocha \textbf{pieces}.
To the right, the Ensure logo appears with the words “ STRENGTH \& ENERGY. ” Beneath it is a colorful circular graphic labeled for immune system support, with nutrient names around the ring, including protein, vitamins, zinc, and vitamin D.
A small footnote at the bottom mentions vitamins C and E as part of a healthy diet, along with Abbott \textbf{copyright} text.

% matched lemmas: carton, copyright, drink, milk, piece, take, tomato, try
\end{textsample}
