\begin{textsample}{POS Dim 6 – 1950 – Score 13.00 – 1950/tv\_com\_1950\_5.txt}  \label{ex:f6_pos_014}
Against a plain, light background, a simple black-line cartoon character appears : a plump hen with an egg-shaped head, a little neck scarf, rounded body feathers, thin legs, and a cheerful face.
She holds up a white egg in one wing, then bounces and gestures around it as if presenting it.
Large black lettering begins to appear beside her, first “ the, ” then the bold, slanted words “ WHOLE-EGG. ” The hen moves playfully over and around the words, the white egg shape darting across the letters as a bright spot.
The phrase “ the WHOLE-EGG ” stretches diagonally across the screen while the hen poses on top of it, peeks over it, and walks along it, reinforcing the “ whole egg ” idea visually.
The animated scene gives way to a dark rectangular sign with large white lettering : “ Best Foods ” at the top, “ REAL ” in the middle, and “ Mayonnaise ” below.
A white egg shape lands near the center of the words.
Simple line-drawn hands appear around it, \textbf{cupping} it between them.
The egg cracks open into two shell halves, centered between the words “ Best Foods ” and “ Mayonnaise. ” The cartoon hen steps in from the left and stands beside the sign, smiling and looking toward the cracked egg and the product name.
A jar of Best Foods Real Mayonnaise then slides into view beside the cartoon hen.
The jar is white, rounded, and capped with a striped lid.
Its dark front label reads “ Best Foods ” in large white letters, with “ REAL ” on a ribbon shape and “ Mayonnaise ” below in an oval.
Near the bottom of the label, smaller text reads “ The Best Foods Inc. ” The hen stands to the left with one wing extended toward the jar, as if proudly introducing it.
The jar tilts slightly and grows larger in the composition, keeping the label clearly visible while the hen remains as a line drawing at its side.
The scene changes to a real \textbf{tabletop} set in black and white.
Two decorative salad \textbf{plates} sit near the front, one on the left and one on the right.
Each \textbf{plate} holds a composed salad arranged on a leafy base, with several rounded \textbf{pieces} and pale curved \textbf{pieces} topped with small garnishes.
A long \textbf{spoon} lies horizontally near the back of the table, and a small bowl or \textbf{cup} sits to the upper right.
A person, visible only from the torso and hands, wears a light-colored dress or blouse and brings the Best Foods jar down between the two salads.
The jar is opened, with its cap placed off to the right.
One hand steadies the jar while the other uses a \textbf{spoon} to dip into the thick mayonnaise.
A rounded \textbf{spoonful} rises from the open jar, holding its shape in a smooth \textbf{mound}.
The \textbf{spoonful} of mayonnaise is carried over the salads.
The person places a generous dollop onto one salad, then smooths and spreads it across the top.
The jar remains upright in the background with the Best Foods label facing forward.
Another large \textbf{spoonful} is lifted and added to the other salad, creating a thick, creamy white topping that contrasts with the darker leafy base and the rounded salad ingredients.
The hands work carefully and deliberately, decorating the salads with visible swaths of mayonnaise.
The food \textbf{preparation} shifts to a stovetop or cooking surface.
An open Best Foods jar stands to the left with its label facing outward, and its lid rests nearby.
In the center is a clear glass saucepan or bowl sitting on a dark circular burner.
A hand stirs a pale creamy mixture inside with a \textbf{spoon} or small \textbf{utensil}.
Another \textbf{spoonful} of mayonnaise is added into the glass \textbf{vessel}, then stirred in.
The mixture looks smooth and light-colored as the \textbf{spoon} moves in small circular motions.
A glass container is then tipped over the saucepan, pouring in a pale liquid while the other hand continues stirring.
The transcript context identifies the mixture as an easy sauce made with Best Foods mayonnaise, \textbf{milk}, and lemon juice ; visually, the action shows mayonnaise and liquid being blended into a creamy sauce.
The creamy sauce is then poured from a small glass \textbf{pitcher} over a large \textbf{platter} of vegetables.
The \textbf{platter} is filled edge to edge with arranged vegetables : many small round \textbf{pieces} clustered in the center and front, long pale spears or strips \textbf{laid} along the sides, and darker textured clusters around the outer edges.
The sauce flows in a thick white stream from the \textbf{pitcher}, spreading across the center and forming a glossy band over the vegetables.
The pour continues until a broad creamy layer covers the middle, with the vegetables still visible around and beneath it.
A long \textbf{spoon} rests on the table behind the \textbf{platter}.
The cartoon hen reappears at the left edge beside the finished vegetable \textbf{platter}, smiling and extending a wing toward it.
The Best Foods mayonnaise jar slides back in next to her, again tilted slightly with the label facing forward.
The \textbf{platter} remains partly visible behind it at first, then the jar becomes the dominant image.
The label “ Best Foods REAL Mayonnaise ” is held large and clear, with the hen ’s line-drawn body partly visible to the side as she continues to present the product.
In the final moments, the jar fills most of the view, angled slightly, while the cartoon hen peeks and steps alongside it, smiling as the product name remains prominent.

% matched lemmas: cup, lay, milk, mound, piece, pitcher, plate, platter, preparation, spoon, spoonful, tabletop, utensil, vessel
\end{textsample}
