\begin{textsample}{POS Dim 6 – 1960 – Score 16.00 – 1960/tv\_com\_1960\_65.txt}  \label{ex:f6_pos_022}
The commercial is in black and white.
It begins outside in a dense city setting.
A young adult woman with shoulder-length, softly curled hair steps out from a building entrance onto an exterior stair or stoop.
She wears a light-colored \textbf{coat} and carries a dark handbag or bundle close to her body.
Tall office-like buildings rise in the background, and a dark metal railing cuts diagonally across the foreground as she descends toward the street.
She appears next on a subway platform beside a train.
A large sign with the number “ 57 ” hangs behind her.
Still in her light \textbf{coat}, with a dark handbag hanging from her arm, she stands among other commuters, including a woman in a hat close behind her.
She faces the train windows, then raises a hand as if steadying herself or preparing to board.
Inside the subway car, she is surrounded by standing passengers in \textbf{coats} and hats.
Overhead hand straps hang in rows above them.
She holds a folded newspaper up in front of her and reads with a calm, concentrated expression while commuters face different directions around her.
The setting changes to an office or workplace refreshment area.
The same woman is now seated at a desk, no longer in her \textbf{coat}, wearing a neat dress.
File cabinets line the background, and another woman sits behind her working with papers.
In the foreground, hands from men in dark suits pass a tray of \textbf{pastries} and a small \textbf{cup} across the desk.
A large shiny cylindrical coffee urn stands to the right.
The seated woman looks down at the food and \textbf{drink} being offered, then looks up toward the person \textbf{serving} her.
Her expression softens into a polite smile.
Papers, pencils in a holder, and office equipment sit on the desk, giving the space a busy, professional look.
She then returns to a residential building.
From above, a small entry hall is visible with a bold black-and-white checkerboard floor, paneled doors, and a stair railing.
The woman comes up the stairs carrying a potted plant or bouquet with tall \textbf{stems} and leaves, her dark handbag tucked at her side.
She moves along the hallway toward an apartment door marked “ 4, ” while a neighboring door marked “ 6 ” is visible nearby.
A wall lamp casts a bright cone of light beside the door.
She stops at apartment 4, holding the plant against her chest as she works at the door, then enters.
Inside a compact kitchen, a paper bag of flour stands prominently on the \textbf{counter} beside a clear glass mixing bowl.
The \textbf{package} is \textbf{readable} : “ Gold Medal ” in a round logo and “ ENRICHED FLOUR ” printed below.
Around it are small kitchen appliances and containers, including what looks like a toaster or small countertop appliance and a coffee \textbf{pot} or kettle.
The woman, now wearing an apron over her dress, moves through the tight space. \textbf{Utensils} and pans hang on the wall, and cabinets and \textbf{counters} are close together, emphasizing the smallness of the kitchen.
She reaches up and around the stove area, then uses a lit match near the burners or oven.
In a wider view of the narrow kitchen, pans hang neatly on a wall rack, and she bends low with the match, lighting or checking a low oven.
The flame glows clearly in her hand as she crouches in front of the appliance.
After attending to the oven, she returns to the \textbf{counter} where the Gold Medal flour bag remains in clear view beside the glass bowl.
She opens the flour bag and dips in a metal \textbf{measuring} \textbf{cup}.
Holding the filled \textbf{cup} above the bag, she levels the flour with a straight \textbf{utensil}, likely a knife, scraping the top smooth.
The flour looks fine and soft, heaped cleanly in the \textbf{cup}.
A close view shows the \textbf{cup} filled to the brim with white flour against the Gold Medal bag behind it.
She tips the \textbf{cup} into a glass bowl, pouring the flour directly in.
No sifter is visible ; the flour goes straight from \textbf{cup} to bowl.
From above, the work surface is arranged with baking tools : a hand mixer with beaters, bowls, a \textbf{measuring} \textbf{cup}, and small \textbf{dishes}.
The woman cracks or adds ingredients into a mixing bowl and then begins using the electric hand mixer.
In a closer view, the white mixer ’s twin beaters churn batter inside a glass bowl.
Another glass bowl filled with flour sits to the side, and a small measuring \textbf{cup} or glass stands nearby.
She reaches into the flour bowl with a \textbf{measuring} scoop, adds flour to the mixing bowl, and continues mixing.
The batter clings to the sides of the glass bowl while the beaters spin through it.
As she works, her hand moves between the flour bowl and the mixer bowl.
She scoops, adds, and tests the texture with her fingertips.
At one point her fingers dip into the flour, then lift with a light dusting of white on them.
The close views emphasize the flour, the glass bowls, and her hands as she bakes carefully and confidently in the small kitchen.
The final scene presents the finished baking.
The woman smiles gently behind a tray of desserts.
On the tray are neatly arranged cakes : a sliced \textbf{piece} on a small \textbf{plate} and a larger \textbf{frosted} cake with a cut section showing pale cake layers separated by a dark filling.
The frosting on the larger cake is glossy and spread in soft swirls over the top and sides.
A small \textbf{cup} sits near the sliced \textbf{piece}.
The woman ’s face remains just behind the tray, pleased and serene, as the view centers more and more on the cake ’s cut face and thick frosting.
A pale, translucent stream or ribbon-like overlay appears over the cake, visually suggesting a white, floury or creamy “ touch ” descending onto the finished dessert.
The cake remains the focus : light interior layers, dark filling line, and shiny frosting surrounding it, with the woman ’s lower face and soft smile partly visible in the background.

% matched lemmas: coat, counter, cup, dish, drink, frosted, measure, package, pastry, piece, plate, pot, readable, serve, stem, utensil
\end{textsample}
