\begin{textsample}{POS Dim 6 – 2000 – Score 10.00 – 2000/tv\_com\_2000\_18.txt}  \label{ex:f6_pos_051}
A group of young adults stands packed together in warm sunlight, all facing forward with serious, slightly squinting expressions as if waiting for a decision.
In the center is a young man with short dark hair, wearing a pale striped button-down shirt over a blue T-shirt.
On one side is another young man with short dark hair ; on the other, a person in a patterned head wrap.
A blonde woman stands behind them.
The central man raises a taco in his hand, holding it out in front of him at chest height, then bringing it closer to his mouth.
He wears several dark wristbands, and his face remains focused and intense as he studies the taco.
The view moves across more people in the same sunny crowd and settles on another young man with shoulder-length dark hair, wearing a white shirt.
He holds out a taco or folded tortilla topped with bright green lettuce and other fillings.
His eyes are partly closed at first, then he looks down at the food with a doubtful, weighing expression, as if comparing it with the first taco.
The setting changes to a bright, rustic kitchen or dining room with a Mexican-inspired feel.
Sunlight fills the space, and a large wooden table is covered with taco ingredients, including tortillas, vegetables, bowls, and \textbf{serving} items.
Several people gather around.
A man in a tan shirt stands near a large upright decision wheel, decorated with a red-and-green center and small circular spaces around the edge.
A woman in a light dress stands nearby holding greens, and a child stands close to the wheel.
The room has shelves, plants, pottery, and warm yellow walls, giving it a homey, festive atmosphere.
A little girl with straight dark hair and \textbf{bangs}, wearing a pale pink sleeveless top with ruffled edges, stands beside the wheel.
She looks up and to the side, then speaks with a confident, matter-of-fact expression.
A subtitle appears at the bottom in yellow text on a dark rectangle : “ Why don't we have both? ” Her suggestion visually redirects the choice away from one taco type versus the other.
The mood becomes celebratory.
Outdoors, against a vivid blue sky and a backdrop of tall green cacti, a group of adults and children cheer with their arms raised.
The little girl is lifted high in the center by an adult, smiling broadly with both arms stretched overhead.
Around her, people grin, shout, and reach upward, creating a jubilant group pose.
The product is then displayed on a rustic \textbf{tabletop}.
In the center stands a bright yellow Old El Paso box labeled “ Hard \& Soft Taco Kit, ” with the brand ’s red-and-yellow logo at the top.
Beside it are additional yellow Old El Paso \textbf{packages}, including taco shells and seasoning.
In front, soft tortillas are folded on a round wooden board, and a row of \textbf{crisp} yellow hard taco shells sits to the right.
Fresh ingredients surround the boxes : red \textbf{tomatoes}, cut limes, green avocados, and small bowls of salsa or toppings.
Behind the table, people continue celebrating, blurred in the background.
A filled hard taco appears in close detail on an orange \textbf{plate}.
Its \textbf{crisp} yellow shell is packed with browned seasoned meat, \textbf{shredded} green lettuce, red \textbf{tomato} \textbf{pieces}, pale strips of cheese, and glossy red salsa.
The ingredients are layered high so the taco looks full and freshly assembled.
Next, two soft tacos made with folded flour tortillas are shown close up, stacked slightly one above the other.
They are filled with the same kind of seasoned meat, lettuce, red \textbf{tomato}, green diced vegetables, and salsa, emphasizing the soft option alongside the crunchy one.
At the end, the scene returns to the \textbf{lively} dining setting.
A man in a tan shirt sits at the table and \textbf{takes} a large bite from a taco, leaning into it with obvious enjoyment.
Beside him, the little girl in the pink top smiles while holding her own taco with both hands.
The table in front of them is covered with colorful ingredients, including \textbf{tomatoes}, limes, greens, and \textbf{serving} bowls, along with a clay jug and a striped cloth.
In the background, other people continue to gather and celebrate in the bright, festive room.

% matched lemmas: bang, crisp, lively, package, piece, plate, serve, shredded, tabletop, take, tomato
\end{textsample}
