\begin{textsample}{POS Dim 6 – 1960 – Score 14.00 – 1960/tv\_com\_1960\_37.txt}  \label{ex:f6_pos_024}
It opens in a warm, faded reddish tone and quickly reveals a staged, old-fashioned kitchen.
The set is simple and theatrical, with a pale background, decorative wrought-iron-looking supports on both sides, hanging \textbf{spoons} and \textbf{utensils}, a dark stove in the center, and a small wooden worktable on the right.
A male-presenting chef, dressed in a tall white chef ’s hat, a striped chef ’s jacket, loose trousers, and a white apron tied behind him, hurries around the stove and worktable.
He bends, reaches, turns back and forth, and fusses with the cooking area as if in the middle of an invention or experiment.
In closer view, he has a prominent \textbf{moustache} and dark side hair, and he looks pleased and intent as he examines a small round snack held between his fingers.
He holds it up near his face, turns it, and forms an “ okay ” circle with his hand, visually echoing the round shape of the snack before presenting it with satisfaction.
A large word, “ now, ” fills the screen in bold lowercase letters.
It is followed by a thick, looping line that wiggles across the pale background and then transforms into a stylized red whistle shape with a pale curled tube inside it.
The image resolves into a product \textbf{package} for Whistles.
The box has a bold top band reading “ SNACK! ” and large white lettering reading “ Whistles. ” The lower part of the \textbf{package} shows a striped bowl piled high with small ring-like snacks, colored in the same warm red and pink tones as the rest of the commercial.
The snack itself is then shown very close up, held between fingertips with long, neatly manicured nails.
It is a short hollow cylinder or tube, rough and bubbly on the outside, with an open hole through the center.
The hand slowly turns it so the viewer can see both the circular opening and the textured crust along the side.
A young adult woman with light skin and short, softly curled blonde hair brings one of the Whistles to her mouth.
She wears makeup with defined eyeliner and looks at the snack with a small, pleased expression before placing it between her lips, biting, and chewing.
After she \textbf{tastes} it, she glances toward the viewer with a mild, satisfied look.
Whistles are then presented as a \textbf{serving} food.
A Whistles \textbf{package} is tipped over a \textbf{plate} already holding a colorful arrangement of food, including leafy greens and small clusters that look like salad or garnish.
The tube-shaped snacks tumble from the box onto the \textbf{plate} and scatter around the other food.
Another hand dips a Whistle into a round bowl of thick white dip sprinkled with dark herb flecks, pressing the snack into the creamy surface.
A stemmed glass \textbf{dish} filled with Whistles appears next ; a hand reaches down from above and selects one from the top of the pile.
The Whistles box returns prominently.
The large “ SNACK!
Whistles ” label fills the image, then the \textbf{package} is shown smaller against a pale background.
To its right appears bold printed text : “ suddenly... snacks are in great shape! ” The slogan sits beside the \textbf{package}, with the box on the left and the words stacked vertically on the right.
A simplified General Mills “ G ” logo graphic appears next, set inside a rounded, horn-like emblem.
The second half shifts to another historical-looking scene.
A flat, line-drawn \textbf{illustration} of an antique open car fills the screen, with sketched trees and a countryside background behind it.
A real male-presenting actor sits in the driver ’s seat, wearing a dark suit and a brimmed hat.
He tips his hat with one hand, then settles both hands near the steering wheel.
The drawn car has large spoked wheels, an upright windshield, and a horn mounted near the front ; pale steam or smoke rises near the hood.
The actor looks down into the car, reaches for a tall paper container or bag, and pulls out \textbf{pieces} of snack food.
He holds the bag upright in his lap, \textbf{takes} a \textbf{piece}, and brings it to his mouth, chewing while still seated in the illustrated antique car.
Again, the word “ now ” appears large on a plain pale background.
A wavy line snakes across the screen and becomes another stylized horn graphic, this time suggesting the shape of a bugle.
A Bugles \textbf{package} appears.
The box has the same strong graphic style : a top band reading “ SNACK! ” and large block letters spelling “ BUGLES. ” The lower panel shows a bowl or circular \textbf{dish} filled with \textbf{pointed}, horn-shaped snacks.
A Bugle is shown in extreme close detail between fingertips.
It is a small cone-shaped snack, tapered to a point at one end and open at the other, with a rough, bubbled corn-chip texture.
The hand rotates it slowly, first showing the \textbf{pointed} horn shape from the side, then turning it so the hollow circular opening faces forward.
A young adult man with short dark hair holds a Bugle near his mouth.
He examines it briefly, then bites into it, chews, and smiles slightly, as though enjoying the crunch and flavor.
Bugles are then shown with different foods and snack settings.
On a \textbf{tabletop}, a white mug sits beside a \textbf{plate} piled with Bugles.
A hand lowers a hamburger onto the \textbf{plate}, placing it behind the snacks so the Bugles sit in front as a side snack.
Another \textbf{serving} arrangement shows a \textbf{shallow} tray heaped with Bugles, with a small dark glass bottle standing upright behind them ; part of the bottle label shows the letters “ Co, ” suggesting a cola bottle.
A hand reaches into the tray and \textbf{picks} up one of the horn-shaped \textbf{pieces}.
Near the end, a Bugles box sits close to the viewer with its top open.
Behind it, a young man is partly visible, leaning forward and reaching into the box.
The \textbf{package} front clearly reads “ SNACK!
BUGLES ” in bold lettering.
The image then returns to the \textbf{package} alone, filling most of the space before pulling back to show the full box against a pale background.
The final layout mirrors the earlier Whistles ending : the Bugles \textbf{package} is on the left, and to its right the printed slogan appears again, “ suddenly... snacks are in great shape! ”

% matched lemmas: dish, illustration, moustache, package, pick, piece, plate, pointed, serve, shallow, spoon, tabletop, take, taste, utensil
\end{textsample}
