\begin{textsample}{POS Dim 6 – 1950 – Score 18.00 – 1950/tv\_com\_1950\_66.txt}  \label{ex:f6_pos_002}
In black and white, a clean-shaven adult man with dark, neatly combed hair stands in a tidy 1950s-style kitchen or dining nook.
He wears a light-colored suit jacket, white shirt, and dark tie with a tie clip.
Behind him are patterned curtains with a plaid border and patterned wallpaper, giving the space a staged but domestic look.
He faces forward as if speaking directly to the viewer, hands clasped together near his chest, then shifts through several expressive gestures : rubbing or folding his hands, glancing off to his right, smiling, laughing, and raising both hands with palms down as he talks.
He turns and steps to a rounded, mid-century refrigerator at the right side of the kitchen.
The refrigerator has separate upper and lower doors with horizontal chrome handles.
He reaches for the upper freezer compartment, pulls the door open, and reveals several boxed frozen \textbf{dinners} stacked inside.
He reaches into the freezer and \textbf{removes} one flat rectangular \textbf{carton}.
The \textbf{carton} front has a TV-screen-shaped \textbf{picture} area showing a compartmented \textbf{dinner} ; the large letters “ TV ” are visible, and the product context identifies it as a Swanson TV Turkey \textbf{Dinner}.
He holds the \textbf{carton} at chest level, angled toward the viewer, while the open freezer behind him still shows more boxed \textbf{dinners}.
A second adult man enters from the right.
He is also clean-shaven, with darker, combed-back hair and a slightly more formal dark suit with a light tie.
He reaches to the freezer handle and closes the upper refrigerator door while the first man keeps holding the \textbf{dinner} \textbf{carton}.
The two men stand side by side in front of the refrigerator.
The first man, still smiling, displays the box ; the second man \textbf{takes} over the visual focus, facing forward and gesturing with clasped hands as if explaining the product.
The first man occasionally looks down at the \textbf{carton} and back at him.
The scene shifts to a close view of a stove and oven.
Hands open or slide the \textbf{dinner} from its cardboard \textbf{carton}, revealing a shiny foil tray with a crimped, reflective cover.
The cardboard \textbf{carton} is set on the stovetop near the back, while the foil tray is held in front of the oven controls and burners.
A hand pulls down the oven door, exposing the dark oven interior and wire rack.
The foil \textbf{dinner} tray is slid onto the rack beside another similar tray already inside.
The hand adjusts the trays so they sit side by side, then withdraws.
The oven door closes upward.
As the oven door fills the view, large white words appear centered on it : “ HEAT and \textbf{SERVE}. ” The lettering is bold, all caps except for the smaller “ and, ” and stands out clearly against the plain oven door.
The same words remain visible as the image transitions into a \textbf{tabletop} \textbf{dinner} setting.
A prepared TV \textbf{dinner} tray appears from above on a table, now uncovered and arranged for eating.
The rectangular metal tray has divided compartments.
One section holds a \textbf{mound} of small round peas ; another contains a soft \textbf{mound} that appears to be dressing ; the larger area holds slices of turkey covered with gravy ; and another section holds a smooth mashed or whipped side \textbf{dish}.
Around the tray are \textbf{utensils} : a \textbf{fork} and knife to the left and a \textbf{spoon} and knife to the right.
At the upper left is a small bread \textbf{plate} with rolls or bread \textbf{pieces}.
At the back of the tray are small decorative or condiment items, including a turkey-shaped figurine and a small glass container.
A hand with a \textbf{fork} enters from the left and points to or \textbf{samples} different parts of the meal, moving from the peas toward the center and across the tray, visually emphasizing the separate foods in the \textbf{dinner}.
The first man returns in the kitchen setting, holding the Swanson TV Turkey \textbf{Dinner} \textbf{carton} upright in both hands.
He smiles broadly and presents it squarely to the viewer.
The front of the box shows the large “ TV ” lettering and a \textbf{picture} of the meal in a divided tray ; “ TURKEY \textbf{DINNER} ” is \textbf{readable} near the lower left of the label.
He lowers the box slightly, then raises and tilts it again as he continues speaking, keeping it prominent in front of his suit jacket.
The commercial ends with a close product display : the Swanson TV Turkey \textbf{Dinner} \textbf{carton} fills the center of the image.
The \textbf{package} front shows the TV-shaped \textbf{illustration} of the prepared meal, the large letters “ TV, ” and the words “ TURKEY \textbf{DINNER}, ” with smaller \textbf{package} details around the edges that are less legible in the black-and-white image.
The box is framed against the same curtained kitchen background, leaving the product as the final visual focus.

% matched lemmas: carton, dinner, dish, fork, illustration, mound, package, picture, piece, plate, readable, remove, sample, serve, spoon, tabletop, take, utensil
\end{textsample}
