\begin{textsample}{POS Dim 6 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_62.txt}  \label{ex:f6_pos_047}
A brief opening image shows a sunny outdoor scene with several young adults gathered around a dark car in a park-like setting, with a statue and greenery behind them.
Large white script across the lower part of the image reads “ Coke adds life, ” and a red Coca-Cola case sits near the car.
The scene then changes to a laundromat with a row of orange front-loading washing machines in the background.
Over the lower part of the laundromat scene, white on-screen text reads “ Actual Interview. ” At a folding \textbf{counter} in the laundromat, a young adult woman with light skin stands sorting laundry.
Her hair is wrapped in a large pale blue headscarf or towel, and she wears a blue jacket with a fuzzy light-colored \textbf{collar} over a dark top.
In front of her are piles of clothes, including a white shirt with a small repeating pattern.
An older light-skinned man with neatly combed white hair steps in beside her.
He is dressed formally in a light gray suit, white shirt, and dark tie.
He holds up a bill in one hand, presenting it toward her while she lifts the patterned white shirt from the pile.
The woman turns toward him, looking curious and amused, while he keeps the money visible between them.
The woman raises the white patterned shirt higher, partly blocking herself from view as she holds it up by the shoulders.
The man continues showing the bill, and they look at each other as if negotiating over the shirt.
Her expression softens into a smile, then a close view of her face shows her smiling broadly and looking down shyly, then back up toward the man.
She appears to \textbf{accept} the arrangement ; in the wider view she now holds the money while the man \textbf{takes} the shirt.
The man holds the patterned shirt out in front of them and begins manipulating it at the top seam, using his hands to separate or prepare it for a demonstration.
The woman, still holding the money, watches closely and laughs, at times covering her mouth with one hand.
He spreads the shirt wider, showing the front, then pulls it into two sections.
Soon he has the shirt divided into two loose halves or comparable portions, one in each hand.
He holds the fabric \textbf{pieces} up between them while speaking and gesturing, as if explaining that the two parts will be washed differently.
The woman looks down at the fabric and listens, smiling.
A close-up shows Clorox liquid bleach being poured from a white plastic jug into clear glass \textbf{measuring} \textbf{cups} on top of a washer or \textbf{counter}.
The liquid streams steadily from the jug ’s spout.
The jug ’s blue label with the red-outlined black diamond and large white “ CLOROX ” lettering is visible as it tilts.
Two glass measuring \textbf{cups} sit side by side, and the clear liquid level rises in one of them.
Back at the laundromat \textbf{counter}, the patterned white shirt is \textbf{laid} flat across the surface with a straight divider or crease running down the middle, visually splitting it into two sides.
The Clorox jug stands upright to the left of the shirt, label facing outward.
The man ’s hands smooth and arrange the fabric while the woman stands to the right, watching.
Behind them, the orange washing machines and their round black doors remain visible, reinforcing the laundromat setting.
The woman is shown again in close-up, looking down and speaking with a thoughtful, \textbf{impressed} expression.
The image then blends into a product close-up : a large Clorox bleach container fills the screen.
The label is blue with the central black diamond bordered in red, and the word “ CLOROX ” appears in bold white capital letters.
Smaller text near the bottom includes “ BLEACH, ” and a \textbf{copyright} line for The Clorox Company is visible.
The final images move closer to the label until the “ CLOROX ” name dominates the screen.

% matched lemmas: accept, collar, copyright, counter, cup, impressed, lay, measure, piece, take
\end{textsample}
