\begin{textsample}{POS Dim 6 – 2020 – Score 9.00 – 2020/tv\_com\_2020\_39.txt}  \label{ex:f6_pos_064}
A close view opens on a dark wooden picnic table outdoors.
Taco Bell wrappers with orange and purple patterns, red and orange sauce \textbf{packets}, napkins, a paper bag, and a turquoise plastic \textbf{drink} \textbf{cup} sit scattered across the table.
A young woman ’s hands, wearing a tan jacket over dark sleeves, pull open a white-and-purple Taco Bell wrapper.
As she peels it back, a folded taco appears, filled with lettuce, cheese, \textbf{tomatoes}, and seasoned beef.
Bright animated graphics begin bursting around the food : red splashes, yellow lightning bolts, white streaks, and purple-and-yellow rings spread outward across the \textbf{tabletop} as if the taco is releasing color.
The woman steadies the taco with one hand while smoothing the wrapper with the other.
The rings grow wider, turning the picnic table into a vivid, cartoon-like surface layered over the real wood.
The view widens to reveal three young adults seated at the picnic table in a sunny park with grass and trees behind them.
On the left, a young man with short dark hair wears a blue denim jacket over a light gray hoodie and holds a turquoise \textbf{drink}.
In the middle, a blonde young woman in a cream sweater sits with a taco in front of her.
On the right, the curly-haired young woman in the tan jacket looks down at the taco she has just unwrapped.
Taco Bell paper bags, wrapped food, \textbf{drinks}, napkins, and sauce \textbf{packets} are spread around them.
Behind and around the group, large animated arches in purple, yellow, and pink rise like rainbow outlines, framing the park scene.
The colorful stripes continue sweeping over the table.
The blonde woman lifts her taco and smiles as she leans in to \textbf{take} a bite.
Animated details appear on her body : her sweater sleeves turn into bright yellow cartoon sleeves, a purple headband appears over her hair, and small yellow shapes and lightning marks pop around her.
The young man beside her watches with a faint smile while she bites into the taco.
A Taco Bell \textbf{drink} \textbf{cup} with a straw sits to her right, and a brown Taco Bell paper bag stands upright near the edge of the table.
More animated color spreads across the scene.
The young man on the left now has purple cartoon sunglasses and a purple hood drawn over his real clothing.
A looping green animated vine curls around him and across the table, dotted with small illustrated sauce \textbf{packets} and playful shapes.
He holds a taco near his mouth while the blonde woman continues eating.
Tiny white legal fine print appears along the bottom of the screen during this portion.
In the park behind them, a skateboarder rides along the path.
The skateboarder becomes partly stylized with animation : a bright yellow jacket, purple cap, and dark pants stand out against the real greenery.
A huge turquoise-blue cartoon wave rolls in behind the skateboarder, edged with white foam and streaks of red, orange, purple, and blue.
A large orange “ \$1 ” graphic appears on the wave, surrounded by small animated lightning marks, while the skateboarder glides along the path in front of it.
The focus returns to the food.
A hand holds a taco upright while another hand squeezes sauce from a small red \textbf{packet} over the top.
The taco is packed with \textbf{shredded} lettuce, yellow cheese, red \textbf{tomato} \textbf{pieces}, and meat inside a folded shell or tortilla.
As the sauce \textbf{drips} down, animated splashes and lightning bolts explode around the taco in white, red, yellow, and blue, emphasizing the added flavor.
The hand finishes squeezing and pulls the sauce \textbf{packet} away, leaving the loaded taco centered against the blurred green park background.
The product is then displayed on the picnic table on a white Taco Bell wrapper.
The taco lies open enough to show its fillings : \textbf{shredded} lettuce spilling out, yellow cheese, red \textbf{tomato} \textbf{pieces}, and seasoned beef at one end.
Around it are sauce \textbf{packets}, wrappers, and the same colorful animated stripes curling along the edges of the table.
Above the taco, bold on-screen text reads “ \$1 LOADED NACHO TACO, ” with the dollar sign and number in large yellow-orange lettering and the product name in chunky yellow and red letters outlined in dark color.
Small white legal text remains along the bottom.
The final view pulls back to the whole park setting.
The three friends sit together at the picnic table in the distance, surrounded by playful animated elements : a tall purple Taco Bell sign with the white bell logo and the words “ TACO BELL, ” cartoon clouds in the sky, red flame-like shapes near the table, green curling vines across the grass, and a large red circular graphic on the right covered with repeated “ HOT ” and “ FIRE ” sauce-style \textbf{wording}.
The real park, with trees and open grass, remains visible underneath the bright Taco Bell-inspired animation.

% matched lemmas: cup, drink, drip, packet, piece, shredded, tabletop, take, tomato, wording
\end{textsample}
