\begin{textsample}{POS Dim 6 – 1970 – Score 11.00 – 1970/tv\_com\_1970\_23.txt}  \label{ex:f6_pos_043}
A smiling adult woman with short dark brown hair and large round tinted \textbf{eyeglasses} is shown in a warm, softly lit indoor setting.
She wears a light-colored blouse and looks down toward a \textbf{spoonful} of yellow cake near her mouth.
A white lower-third caption identifies her by name and location, with “ Houston, Texas ” visible.
She raises the \textbf{spoon}, smiling with anticipation, opens her mouth, \textbf{takes} the bite, and then draws the \textbf{spoon} out while chewing, her expression relaxed and pleased.
Another adult woman appears next, with reddish hair styled up and small dangling earrings.
She wears a patterned blouse and looks down toward her \textbf{spoon}.
A white caption at the lower left identifies her as “ Jane Trahan ” from “ Scottsboro, Alabama. ” She brings a \textbf{spoonful} of cake to her mouth, \textbf{takes} the bite, and closes her lips around the \textbf{spoon}, then smiles subtly as she \textbf{tastes} it.
The focus shifts to a white \textbf{plate} on a warm-toned \textbf{tabletop} holding a thick slice of layered yellow cake with dark chocolate frosting between the layers and around the outside.
A metal \textbf{spoon} presses into the front edge of the slice and scoops out a soft bite, showing the pale yellow \textbf{crumb} inside.
The \textbf{spoon} lifts the bite away from the cake, leaving a neat hollow in the slice and a bit of frosting clinging to the cake and \textbf{spoon}.
A box of Pillsbury Plus Yellow Cake mix fills the scene against a pink-red background.
The \textbf{package} is cream-colored with a dark round Pillsbury logo near the upper left and large black lettering reading “ Pillsbury Plus. ” Smaller text reads “ Yellow Cake ” and “ There ’s Pudding in the Mix. ” The front of the box shows a photograph of yellow cake with chocolate frosting, including a \textbf{spoon} lifting a \textbf{frosted} bite.
Across the lower part of the screen, white text reads, “ Ingredients added, according to directions. ” A \textbf{spoonful} of cake briefly enters near the right side of the box, visually connecting the product \textbf{package} to the \textbf{tasting}.
Another adult woman, with medium brown hair and a plaid blouse, is shown in a softly blurred home-like interior.
A lower-third caption identifies her as “ Pat Lundquist ” from “ Shawnee Mission, Kansas. ” She opens her mouth for a \textbf{spoonful} of cake, \textbf{takes} the bite, and closes her lips around the \textbf{spoon}.
Her face remains calm and absorbed as she \textbf{tastes}.
A fourth adult woman with light brown, shoulder-length hair appears, seated in a warm, dim interior.
A caption identifies her as “ Linda Suter ” from “ Norcross, Georgia. ” She holds a \textbf{spoonful} of cake near her face while looking forward, then turns her attention to the \textbf{spoon} and \textbf{takes} a bite.
Her hand, with a ring visible, guides the \textbf{spoon} to her mouth, and she withdraws it as she begins to chew.
The Pillsbury Plus Yellow Cake box returns, again showing the large “ Pillsbury Plus ” name and the phrase “ There ’s Pudding in the Mix ” on the front.
The cake photo on the \textbf{package} remains prominent, with the yellow cake and dark frosting presented as moist and soft-looking.
A \textbf{spoonful} of cake passes near the top edge of the \textbf{package}.
A rapid series of very tight views follows, focusing on mouths and \textbf{spoons} rather than full faces.
Different women open their mouths as \textbf{spoons} carrying small yellow cake bites approach.
The cake \textbf{pieces} look soft and crumbly, sometimes with a bit of darker frosting attached.
Each bite is placed into the mouth, the lips close around the \textbf{spoon}, and the \textbf{spoon} slides out cleanly.
The repeated images emphasize the act of \textbf{tasting} : open mouth, \textbf{spoonful} of yellow cake, bite \textbf{taken}, \textbf{spoon} withdrawn.
The commercial ends on the Pillsbury Plus Yellow Cake box, held steadily against the warm red-pink background.
The cream-colored \textbf{package}, dark Pillsbury logo, bold “ Pillsbury Plus ” lettering, “ Yellow Cake, ” and “ There ’s Pudding in the Mix ” remain clearly visible, along with the appetizing \textbf{picture} of the \textbf{frosted} yellow cake on the front.

% matched lemmas: crumb, eyeglass, frosted, package, picture, piece, plate, spoon, spoonful, tabletop, take, taste
\end{textsample}
