\begin{textsample}{POS Dim 6 – 1950 – Score 4.00 – 1950/tv\_com\_1950\_40.txt}  \label{ex:f6_pos_084}
The commercial is in black and white and appears to focus on dishwashing or \textbf{cleaning}.
At the beginning, the frame shows a \textbf{kitchen} or washing-up area with a large quantity of dirty dishes.
Several plates are stacked, and serving dishes or bowls are visible.
The dishes appear heavily soiled with food \textbf{residue} or grease, suggesting a challenging washing-up task.
The next scene shifts to a \textbf{sink} area.
A hand places or holds a dark cylindrical container labeled “ LUX ” with the word “ LIQUID ” visible below it.
The container is positioned near a faucet and \textbf{sink} basin, indicating it is being used in connection with washing dishes.
The person ’s sleeve is visible, but their face is not shown.
Later, the scene shows dirty plates or glass dishes in or near the \textbf{sink}.
The dishes have prominent streaks or \textbf{residue} around the rims.
The “ LUX ” container is visible in the background on the left, linking the product to the cleaning task.
A hand appears to be holding or moving the dishes, though the exact action is not fully clear from the sampled frame.
In the final frame, a man in a suit is shown seated indoors, holding up the same “ LUX ” liquid container toward the camera.
He appears to be smiling or speaking, though no audio content is available.
A microphone is visible in front of him, suggesting a presenter or spokesperson format.
The background includes domestic furnishings such as a lamp and curtains or a textured wall.

% matched lemmas: clean, kitchen, residue, sink
\end{textsample}
