\begin{textsample}{POS Dim 6 – 1980 – Score 13.00 – 1980/tv\_com\_1980\_100.txt}  \label{ex:f6_pos_034}
A man sits at a breakfast tray in a dark, wood-panelled room decorated with Western objects.
He wears a large pale cowboy hat, a light blue suit jacket with darker blue panels, a white shirt, and a blue tie.
Behind him are a bright curtained window, a small rearing-horse statue, a model oil derrick, a horse painting, and stacked books.
On the tray in front of him are a glass of orange juice, a bowl or \textbf{plate} of \textbf{Frosted} Mini-Wheats, a white \textbf{dish}, a pink napkin, and a red Kellogg ’s \textbf{Frosted} Mini-Wheats cereal box standing upright beside him.
He holds a \textbf{spoon} with a square cereal \textbf{piece} on it and speaks toward the viewer, then looks down at his food and gestures with his free hand, as if explaining the cereal ’s two sides.
The red box is clearly visible, with “ Kellogg ’s \textbf{Frosted} Mini-Wheats ” printed on the front and a \textbf{picture} of the cereal in a bowl.
As he lowers his head, the brim of the cowboy hat hides much of his face.
When he lifts his face again, a young boy is now sitting in the same place, wearing the oversized cowboy hat and the same light blue jacket and tie.
The hat sits broadly around his small face.
He smiles eagerly, holding up the \textbf{spoonful} of cereal, with the cereal box still upright to his right and the orange juice in front of him.
He leans forward with an excited expression, looking straight ahead as if addressing the viewer.
The scene changes to a ballet dressing room.
An adult ballerina sits at a dressing table in a white tutu with feathery trim and a small tiara or headpiece in her hair.
The room has a theatrical backstage feel : a lit vanity mirror glows on the left, costumes hang in the background, and a shaft of light falls from above.
On the \textbf{tabletop} are a bowl of cereal, a red \textbf{Frosted} Mini-Wheats box, a white \textbf{pitcher} of \textbf{milk}, a mug, and a \textbf{plate} with breakfast food.
The ballerina holds a \textbf{spoon} in one hand and extends it outward while speaking.
She sits upright and poised, her expression calm and composed, with the cereal box prominently beside her.
The ballerina continues holding the \textbf{spoon} near shoulder height, then the person at the table changes into a little girl dressed as a ballerina.
The child has a white tutu, a small sparkling headpiece, and short dark hair partly covered by white feathers.
She smiles brightly at the viewer, holding the \textbf{spoon} over a pink bowl filled with Mini-Wheats.
The red cereal box remains beside her, almost as tall as her seated torso.
She brings her other hand to her chest in a delighted gesture, then looks down toward the \textbf{spoon} and bowl with a pleased, giggling expression.
A product display follows.
The red Kellogg ’s \textbf{Frosted} Mini-Wheats box stands centered on a red \textbf{tabletop}.
Around it are breakfast items : a glass of \textbf{milk}, a glass of orange juice, a white \textbf{milk} \textbf{pitcher} shaped like a small jug, a bowl of Mini-Wheats in the foreground, and a \textbf{plate} of toast or pancakes with a pat of butter.
The box front again shows the brand name “ Kellogg ’s \textbf{Frosted} Mini-Wheats ” and a \textbf{serving} suggestion image of the cereal in a bowl.
Small \textbf{copyright} text for Kellogg appears near the bottom.
The view moves to a close look at a white bowl with a yellow rim, filled with rectangular \textbf{shredded} wheat biscuits.
At first the \textbf{pieces} look beige and fibrous, showing the woven \textbf{shredded} wheat texture.
Then the visible \textbf{pieces} appear with a white \textbf{frosted} coating, speckled with darker shredded-wheat flecks.
The cereal fills the bowl in chunky rectangular pillows.
Beneath the bowl, pink on-screen text reads “ Delicious \& Nutritious. ” The final setting is a martial arts room with a glossy black table in front and pale grid-like shoji screens behind.
Red panels with circular designs hang on the back wall, and a vertical wall scroll with Asian characters is visible to the side.
A young boy with straight dark hair sits at the low table wearing a white martial arts uniform with dark patterned trim and round patches.
In front of him are a bowl of cereal, a glass of \textbf{milk}, a glass of orange juice, and a small dark teapot-like \textbf{vessel}.
The red \textbf{Frosted} Mini-Wheats box stands to his right.
He holds a \textbf{spoon} with a cereal \textbf{piece} and looks forward, speaking with a serious, focused expression that turns into a small smile.
The boy raises one hand beside the cereal box and lifts a small pinkish cereal \textbf{piece} or Mini-Wheat in a demonstrative gesture.
A close view then shows a single rectangular Mini-Wheat resting on a \textbf{spoon} : first the plain \textbf{shredded} wheat side is visible, beige and fibrous, then the \textbf{piece} is shown with its white \textbf{frosted} side facing outward.
The \textbf{frosted} coating looks thick and sugary, with tiny dark flecks of wheat showing through.
Back in the martial arts room, an adult man now sits in the same place, wearing the same style of white martial arts uniform with dark trim and a round chest patch.
He has short dark hair and smiles broadly while holding a \textbf{spoonful} of cereal.
The red \textbf{Frosted} Mini-Wheats box remains beside him.
He gestures toward the viewer with the \textbf{spoon}, then makes a flat-handed chopping motion in front of the box, as if punctuating his words.
At the end, he lifts a rectangular \textbf{piece} of toast or breakfast bread in his other hand, holding it up beside his face while still smiling, with the cereal bowl and product box in front of him.

% matched lemmas: copyright, dish, frosted, milk, picture, piece, pitcher, plate, serve, shredded, spoon, spoonful, tabletop, vessel
\end{textsample}
