\begin{textsample}{POS Dim 6 – 1960 – Score 14.00 – 1960/tv\_com\_1960\_44.txt}  \label{ex:f6_pos_025}
A black-and-white scene opens inside an old-fashioned soda fountain or confectionery shop.
A long \textbf{counter} runs from the foreground toward the back, with a row of round stools tucked neatly along it.
Shelves and glass cases line the walls, and a bright doorway glows at the far end.
A small boy approaches the \textbf{counter}, entering the shop ’s warm, busy-looking interior.
The boy, about elementary-school age, wears a light-colored brimmed cap with a band and a long-sleeved shirt.
He reaches up with one hand on the \textbf{counter} and peers over it, looking expectant.
Behind him, shelves are stacked with wrapped goods or \textbf{pastries}.
Soon another boy comes up beside him, wearing a small dark cap and a \textbf{short-sleeved} shirt.
A little girl with curled hair and short \textbf{bangs} appears between them, smiling broadly as she pushes forward to the \textbf{counter}.
More children gather close together, their faces turned upward toward someone behind the \textbf{counter}, as if placing an eager order.
Close views show the children ’s excited expressions one at a time.
The little girl with curled \textbf{bangs} smiles directly ahead, bright-eyed.
A light-haired boy smiles and talks, his face filling the view.
Another boy with short curly hair appears, his mouth moving as if speaking.
The children look pleased and animated, leaning forward over the \textbf{counter} and watching for a response.
The counterman is an elderly man with very light hair, balding on top, wearing large \textbf{eyeglasses}, a white shirt, a dark vest, and a bow tie.
He stands behind the \textbf{counter} in front of shelves filled with rows of glasses.
He looks puzzled and then attentive, speaking to the children with expressive gestures.
He raises a hand as if questioning them, then leans forward, listening.
His eyebrows lift behind his glasses, and he smiles as the conversation continues.
He reaches down into a freezer or refrigerated case.
Inside are several wrapped ice cream bars, stacked in a tray.
A hand selects one rectangular \textbf{package} from among the others.
The wrapper is light and dark with printed lettering, though the details are not fully legible in the moving view.
The wrapped bar is lifted out and handed forward.
A curly-haired boy receives the wrapped treat and holds it up near his face.
He peels or pulls the wrapper back, revealing a dark, rectangular ice cream bar on a \textbf{stick}.
The bar has rounded corners and a smooth chocolate-coated surface.
He studies it closely, then lowers the wrapper and looks satisfied.
Nearby, the little girl is shown again, now holding a partly unwrapped bar on a \textbf{stick}.
The top has been bitten or exposed, showing a lighter interior beneath the darker coating.
She talks while holding it upright beside her face.
The elderly counterman continues reacting with curiosity.
He glances upward, thinks, and taps or rests a finger near his chin, as if \textbf{trying} to understand the product.
Then he points upward with one finger, smiling as though he has just had an idea.
The children watch him, clustered together at the \textbf{counter}, several holding their Jolli-Lolli bars.
A wider view shows a group of children lined up shoulder to shoulder.
On the left, the curly-haired boy eats from his bar.
Beside him, the boy in the small dark cap holds his treat upright.
To the right, the first boy in the brimmed cap and the little girl are also visible among the group.
They look toward the counterman while eating or waiting, their bars partly unwrapped.
The counterman unwraps a bar for himself.
He \textbf{removes} the paper, revealing the same rectangular chocolate-coated ice \textbf{milk} bar on a \textbf{stick}.
He holds it up in front of his chest, examines it with interest, and \textbf{takes} a bite from the top edge.
The bite breaks through the dark coating to a lighter inside.
He chews thoughtfully, looking at the bar, then gestures toward it with his other hand as if explaining what is inside.
His expression changes from surprise to pleased approval.
He points at the bitten area, studying the interior, then \textbf{takes} another \textbf{taste} and looks increasingly delighted.
Holding the bar upright near his shoulder, he speaks animatedly, his eyes widening behind his glasses.
A light-haired boy ’s face appears again, smiling softly, as if pleased by the counterman ’s discovery.
The elderly man then leans in with a playful, inquisitive look, still holding the bitten bar close to his face.
The commercial shifts into a simple product demonstration against a light background.
A single dark rectangular bar on a \textbf{stick} floats by itself, shown large and cleanly outlined.
Its smooth coating and rounded corners are emphasized.
A darker circular shape appears within or behind the bar, suggesting the lollipop hidden inside.
The circle grows larger until it fills the view as a glossy round lollipop shape.
The final view presents the product box.
The \textbf{package} is a rectangular \textbf{carton} with a \textbf{picture} of a Jolli-Lolli bar and circular lollipop graphics on the front. \textbf{Readable} text includes the Fairmont brand name, “ 4 PACK, ” and large lettering that says “ new Jolli-lolli. ” The box design also shows an image of the bar with a bite revealing the inside, visually reinforcing the idea of a chocolate-coated ice \textbf{milk} bar with a lollipop center.

% matched lemmas: bang, carton, counter, eyeglass, milk, package, pastry, picture, readable, remove, short-sleeved, stick, take, taste, try
\end{textsample}
