\begin{textsample}{POS Dim 6 – 1970 – Score 5.00 – 1970/tv\_com\_1970\_97.txt}  \label{ex:f6_pos_057}
The commercial begins with a black frame, with no visible content.
After this, the scene cuts to a \textbf{bathroom} interior.
Several \textbf{towels} or washcloths are hanging on wall-mounted rails or hooks against light-colored tiled walls.
The visible \textbf{towels} are in red, white, and dark blue.
A radiator or heater-like fixture is below them.
The next shot shows an adult man in a plaid shirt in the \textbf{bathroom} or \textbf{adjacent} doorway area.
He is shown from the chest up, leaning slightly and looking off to the side.
His expression appears relaxed or smiling.
The scene then cuts to a young girl standing in the \textbf{bathroom} beside the hanging \textbf{towels}.
She has light-colored hair tied with red hair accessories and wears a floral-patterned top.
She holds a large red \textbf{towel} close to her face and appears to rub or \textbf{press} it against her cheek.
Blue and white \textbf{towels} are visible hanging behind her.
Later, a young boy is shown in a close shot.
He wears a white sweatshirt with red trim and a large number “ 16 ” on the front.
Adult hands rest on his shoulders from behind.
He looks upward toward someone off-frame.
Part of the girl in the floral top is visible at the right edge.
The following shot widens to show a family group in the \textbf{bathroom} : the adult man in the plaid shirt, an adult woman in a light floral blouse, the boy in the “ 16 ” sweatshirt, and the girl with hair ribbons.
They stand close together near a \textbf{sink} and mirror.
The adults look down toward the children, while the girl faces the boy. \textbf{Towels} in red, white, and blue are visible in the background.
The final frame is a product display.
Stacks of folded \textbf{towels} in red, white, and blue are arranged around a central package labeled “ BONUS. ” Large on-screen text at the bottom reads : “ Red, white and blue \textbf{towels}. ”

% matched lemmas: adjacent, bathroom, press, sink, towel
\end{textsample}
