\begin{textsample}{POS Dim 6 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_118.txt}  \label{ex:f6_pos_042}
The commercial opens on a nearly black frame with only a small bottom-right “ 90 ’s commercials ” style watermark visible.
It then cuts to a product display : several Pine-Sol bottles arranged in a receding line from left to right.
The closest bottle is large in the foreground with a yellow cap and a green/yellow “ Pine-Sol ” label.
Behind it are smaller bottles, some with large red “ 2 ” graphics on the front or positioned in front of the bottles.
The background is dark and studio-like, with reflective lighting on the bottles.
Next, the setting changes to an interior home space, likely a \textbf{kitchen} area.
A large white range hood dominates the frame, mounted against a blue wall.
Small green pine-tree decorations appear on or near the hood.
A shelf with jars or containers is visible below, and wooden ceiling beams are visible above.
The commercial then cuts to a \textbf{bathroom} \textbf{floor} seen from above.
The \textbf{floor} is white tile with small dark diamond accents.
Around the edges are \textbf{bathroom} fixtures : part of a bathtub, a pedestal \textbf{sink} base, and a toilet.
Large yellow block letters spelling “ STAPH ” are overlaid or drawn across the tile \textbf{floor}, visually suggesting a germ or contamination concept.
A close-up of a Pine-Sol bottle follows.
The label fills most of the frame, with “ Pine-Sol ” in large yellow letters on a green background.
Along the bottom of the label, smaller text includes “ \textbf{CLEANS} • DISINFECTS • DEODOR … ” though the final word is partly cut off.
To the right of the bottle, a three-dimensional green word “ SOLVED ” appears, as if extending from or beside the product name.
The next shot shows a circular, \textbf{cloudy} yellow-brown \textbf{stain} or dirty \textbf{patch} on a light tiled surface.
The image is soft and somewhat abstract, so the exact substance is unclear, but it appears to represent dirt, \textbf{residue}, or contamination on a \textbf{floor}.
The final frame shows large three-dimensional text reading “ Pine-Solved ” on a pale tiled \textbf{floor}. “ Pine ” and “ -Sol ” are in bold yellow letters, while “ ved ” is green, forming the phrase visually.
A small green object or blur appears near the bottom edge, but it is not clear what it is.
The bottom-right watermark remains visible.

% matched lemmas: bathroom, clean, cloudy, floor, kitchen, patch, residue, sink, stain
\end{textsample}
