\begin{textsample}{POS Dim 6 – 1950 – Score 15.00 – 1950/tv\_com\_1950\_48.txt}  \label{ex:f6_pos_004}
The commercial opens in black and white on a breakfast-table arrangement.
At first, a decorative fan-shaped striped object partly covers the left side of the scene, and a small smiling female figure or \textbf{illustration} in a frilly outfit appears briefly in front of the food.
As this opening decoration clears away, the main display is revealed : a large white \textbf{plate} filled with glossy sweet rolls, their tops covered in chopped nuts and dark caramel streaks.
Behind and around the \textbf{plate} are breakfast items : a striped \textbf{cup} and \textbf{saucer} with a dark \textbf{drink} on the left, a tall glass of light-colored liquid on a \textbf{saucer} toward the back right, a \textbf{spoon} near the back, a \textbf{fork} on the right, and a folded newspaper or printed \textbf{package} along the left edge of the table.
The view lingers on the \textbf{plate} of finished rolls.
Seven rolls are visible, arranged in a loose circle with one near the center.
Each roll has a spiral shape, with a shiny, uneven topping that looks sticky and textured from the nuts.
The rolls sit on a patterned \textbf{tabletop}, and the surrounding \textbf{dishes} frame them like a Sunday breakfast setting.
The images gradually emphasize the rolls more closely, making the chopped nut topping and darker caramel patches stand out against the pale baked dough.
The scene changes to a food-preparation demonstration.
A \textbf{shallow} round cake pan sits on the table, already holding a rough layer of crumbly topping.
An adult hand reaches into the pan and breaks the topping apart with the fingers, scattering and spreading the irregular \textbf{pieces} across the bottom.
The mixture looks chunky, with small nut-like bits and larger \textbf{pieces} of caramel topping.
The hand repeatedly \textbf{pinches}, crumbles, and pushes the mixture so it covers more of the pan ’s surface.
A \textbf{spoon} appears above the pan with liquid in it, and drops fall from the \textbf{spoon} onto the crumbly topping.
A small glass or \textbf{measuring} \textbf{cup} is visible nearby.
Behind the pan are opened product materials : an unwrapped cylindrical dough \textbf{package} on the left and a Pillsbury can on the right with a round logo and a \textbf{picture} of rolls on the label.
The demonstration keeps the pan centered while the topping is moistened and prepared.
Next, hands handle the opened dough \textbf{package}.
A pale round \textbf{piece} of dough is lifted out and placed onto the topping inside the pan.
The hand presses it lightly into position near the front edge.
Another round dough \textbf{piece} is set beside it, and then another is placed along the right side.
The dough \textbf{pieces} are smooth, light-colored, and sliced into thick rounds, contrasting with the rough, darker, nutty topping beneath them.
Only part of the process is shown, but the visible action clearly demonstrates placing the rolls directly on top of the caramel-nut mixture.
The image then returns to the finished \textbf{serving} \textbf{plate}.
The baked rolls are back on the white \textbf{plate}, glossy and topped with chopped nuts and caramel.
The breakfast setting reappears around them, with the striped \textbf{cup} and \textbf{saucer}, the glass on its \textbf{saucer}, silverware, and the newspaper or printed item at the side.
A product \textbf{package} graphic fades in over the breakfast \textbf{plate} : a Pillsbury Quick Caramel Nut Rolls can, shown horizontally with a \textbf{picture} of the nut-topped rolls on the label.
Large on-screen text appears beneath it reading, “ at your Grocer ’s Dairy Case. ” The background simplifies until the can and the words are isolated on a light backdrop.
The final display shows three Pillsbury refrigerated dough products arranged around a small sign that reads “ at your grocer ’s dairy case. ” The Quick Caramel Nut Rolls can is at the lower left, with its roll image visible.
A Pillsbury Buttermilk Biscuits can sits above it, and a Pillsbury Quick Cinnamon Rolls can sits at the lower right.
The products are presented as a small group of related Pillsbury cans, all against a plain light background.

% matched lemmas: cup, dish, drink, fork, illustration, measure, package, picture, piece, pinch, plate, saucer, serve, shallow, spoon, tabletop
\end{textsample}
