\begin{textsample}{POS Dim 6 – 1970 – Score 8.00 – 1970/tv\_com\_1970\_90.txt}  \label{ex:f6_pos_049}
A very young girl fills the screen, looking directly forward as if addressing someone just above her.
She has long dark hair with straight \textbf{bangs} and pigtails tied with large pale purple ribbons.
Her head is tilted slightly to one side, and she wears a soft, hopeful smile that turns into speaking, her mouth opening and closing as she makes a request.
The view moves closer on her face until her eyes, cheeks, and small smile dominate the image.
The scene changes to a young Black boy in a blue top, seated or standing against a softly patterned background that looks like curtains or wallpaper.
He faces forward with a serious, expectant expression, his mouth moving as he speaks.
His face gradually fills more of the \textbf{picture}, his eyes glancing slightly upward, then back ahead.
Another child appears, a light-skinned boy wearing a dark baseball cap turned sideways and a light shirt with dark trim.
He looks back over his shoulder toward the viewer, with a bright orange flower-like shape on the wall behind him, and speaks with a slightly insistent expression.
Then there is an extreme close view of another child ’s lower face and oversized dark-rimmed glasses ; only part of the nose, mouth, and glasses are visible at first.
The wider view reveals a child with a straight dark bowl haircut, large round glasses, and a yellow sleeveless top with a large pale \textbf{collar}, leaning on one hand as if waiting or asking for attention.
More close views of children ’s mouths and faces follow in quick succession : lips forming words, cheeks and chins filling the image, then the Black boy ’s face again, then the child in glasses, then a freckled or lightly spotted face seen mostly around the nose and mouth.
Visually, the children appear to be repeatedly asking for \textbf{drinks} or attention, each shown very close and directly facing the viewer.
The imagery then shifts from the children to a kitchen wall with warm wood paneling.
Hanging on the wall is a Dixie kitchen \textbf{cup} dispenser : a vertical stack of small disposable paper \textbf{cups} held in a wire or plastic holder, with the bottom \textbf{cup} protruding downward.
The \textbf{cups} have horizontal colored stripes around the nested stack, and the visible bottom \textbf{cups} are decorated with large looping swirl patterns in yellow, orange, green, and cream.
To the left, copper-colored hanging \textbf{utensils} are visible ; to the right is a greenish louvered cabinet door with white knobs, giving the setting a home kitchen feel.
The dispenser is shown more closely, focusing on the bottom \textbf{cup}.
A small child ’s hand reaches in from the right, grips the lowest \textbf{cup}, and pulls it straight down.
That \textbf{cup} slips free cleanly, leaving the next patterned \textbf{cup} ready at the bottom.
The action repeats : a hand comes in, grasps the new bottom \textbf{cup}, and pulls it away, showing that the \textbf{cups} dispense one at a time.
Several \textbf{cup} colors and patterns appear as each lower \textbf{cup} is \textbf{removed}, including orange-and-yellow swirls, green-and-yellow swirls, and pale yellow designs.
Near the end of this demonstration, an orange Dixie refill-cup \textbf{package} appears beside the wall-mounted dispenser.
The \textbf{package} is printed with repeated white “ DIXIE ” logos and the visible words “ Kitchen Refill \textbf{Cups}, ” with small images of the patterned \textbf{cups} near the bottom.
The \textbf{package} and the hanging dispenser are displayed side by side against the same wood-paneled kitchen wall.
Finally, the young girl with dark \textbf{bangs} and purple hair ribbons returns in close view.
She looks forward with bright eyes and a pleased, slightly proud expression, her mouth moving as she speaks.
Her smile grows wider as she continues, appearing satisfied and cheerful, though no \textbf{cup} or \textbf{drink} is visible in her hands during these final close-ups.

% matched lemmas: bang, collar, cup, drink, package, picture, remove, utensil
\end{textsample}
