\begin{textsample}{POS Dim 6 – 1950 – Score 10.00 – 1950/tv\_com\_1950\_59.txt}  \label{ex:f6_pos_020}
The commercial opens in black and white with a staged household display partly visible behind large script lettering.
A woman stands in a kitchen-like setting behind a table with food and a Saran-Wrap box, while bright cursive words appear across the \textbf{picture}.
The view becomes a plain title card with the words “ The most AMAZING FOOD WRAP ever developed. ” “ The most ” and “ ever developed ” are in flowing script, while “ AMAZING FOOD WRAP ” appears in bold block capitals.
A long rectangular Saran-Wrap \textbf{package} then slides diagonally across the lettering, \textbf{taking} over the screen.
The box is dark in grayscale with large white “ Saran-Wrap ” lettering and a small Dow diamond logo, plus small \textbf{pictures} on the left end that look like wrapped food.
A light-skinned adult woman with neatly curled 1950s hair, small earrings, and a light blouse with a white \textbf{collar} and a dark bow at the neck appears in a tidy kitchen.
Behind her are cabinets, a window or glass-front cupboard, a range hood, and countertop items.
She smiles broadly and holds the Saran-Wrap box horizontally with both hands, close to her face, presenting the label toward the viewer.
She then lowers the box, looks down, and begins opening or handling it.
Holding the \textbf{carton} in one hand, she pulls out a sheet of thin, transparent plastic wrap with the other.
The film catches the light in crinkled highlights but remains see-through ; her blouse, face, and the cabinets can be seen through it.
She raises a loose strip high, then lets it drape and flutter as she draws out a larger sheet.
She spreads the clear film across a \textbf{platter} of food on the \textbf{counter}.
The \textbf{platter} contains assorted party-style foods : sliced meats or sandwiches, crackers or canapés, and rounded garnish-like \textbf{pieces}.
A Saran-Wrap box rests behind the \textbf{platter} with the label facing forward.
In close view, the clear plastic sheet lies over the food, its edges extending beyond the rim of the oval \textbf{plate}.
Hands press the wrap down around the \textbf{plate} ’s edge, smoothing and tucking it so it clings tightly.
The wrap becomes a taut, shiny cover over the food, with small wrinkles and light reflections showing where the plastic stretches across the surface.
The woman lifts the covered \textbf{platter} and holds it in front of her in the kitchen, looking pleased as she presents the neatly sealed food.
The covered \textbf{plate} fills the lower part of the \textbf{picture}, with the transparent wrap gleaming over the food inside.
The scene changes to an overhead view of several party trays on a table.
A large round tray in the center is arranged with canapés, crackers, sandwich wedges, and small decorative toppings in a circular pattern.
Smaller \textbf{plates} sit above it to the left and right, also filled with snacks and covered or partly covered with shiny plastic.
Hands enter from both sides and adjust the clear wrap around the central tray, pulling the edges outward, smoothing them, and pressing them down around the rim.
The plastic is almost invisible except for its crinkles and bright reflections, making the food underneath still plainly visible.
As the wrap is finished around the tray, the woman ’s face gradually appears within the circular shape of the \textbf{platter}, and the image resolves back to her speaking in the kitchen.
Next, a round wheel of cheese sits on a wooden board, with a wedge already cut out of the front.
Clear plastic wrap lies around and under it.
Hands pull the wrap from both sides, stretching it over and around the cheese.
The film is lifted, tightened, and pressed against the cheese surface and the board.
The hands then peel the wrap back, revealing the cheese again, and pull the plastic into place once more, demonstrating that the same clear sheet can be opened and reused.
The cheese remains cleanly visible through the wrap, while the plastic forms glossy highlights across the board.
The cheese changes from a nearly whole round to a smaller remaining \textbf{piece}, suggesting that the amount has been used down over time.
Hands again bring the clear wrap in from the sides around this smaller \textbf{piece}.
As the wrapping action continues, the woman ’s face blends back into view through the transparent plastic.
She appears again in the kitchen holding a wrapped \textbf{piece} of cheese upright in one hand, the smooth light-colored cheese visible beneath the tight clear film.
She points to or taps the wrapped cheese with her other hand while speaking, then smiles.
For the final product presentation, she raises the Saran-Wrap box again at chest height, holding it with both hands so the “ Saran-Wrap ” name is centered and easy to read.
The \textbf{package} remains dark with bold white lettering, a small Dow diamond mark, and small food \textbf{illustrations} at the left end.
Her face stays just above the box as she smiles and addresses the viewer.
The woman fades away, leaving the Saran-Wrap box alone against a plain textured background.
The \textbf{package} grows larger and fills more of the screen, with “ Saran-Wrap ” still prominent.
Finally, a large dark diamond-shaped Dow logo slides over the box and expands to dominate the image.
The last view is the Dow diamond centered on the plain background, with “ Dow ” in large white letters.

% matched lemmas: carton, collar, counter, illustration, package, picture, piece, plate, platter, take
\end{textsample}
