\begin{textsample}{POS Dim 6 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_119.txt}  \label{ex:f6_pos_073}
A hand in a long-sleeved shirt opens a pale cabinet or closet door by a round white knob.
As the door slides aside, a neatly arranged linen shelf appears, filled with soft white towels and pillows.
On the shelf is a display of small, rounded pottery air fresheners in front of a box labeled “ Country Pottery. ” The \textbf{pieces} look like little handmade jars : white on the upper half, colored on the lower half, with small rounded caps.
Several color versions are grouped around the \textbf{package}, including warm peach, gray-blue, and tan tones.
The \textbf{package} has a floral, country-style design, and the scent name “ Country Garden ” is visible near the bottom.
In a bright bathroom, an adult hand places one of the little pottery jars on a glossy white \textbf{counter} beside a sink.
The \textbf{counter} reflects the light, and chrome faucet handles, a soap \textbf{dish}, towels, and a pale bottle sit near a window in the background.
The jar has a white upper body, a peach-colored lower body, and a pinkish cap.
The hand steadies it, then lets it stand upright near the sink.
Another pottery jar is carried to a small polished wooden table.
The setting has a homey, decorative feel, with a trailing green plant and a pair of tan leather gloves lying nearby.
The hand sets down a tan-bottomed jar near the edge of the table, then withdraws, leaving the small \textbf{pot} as part of the \textbf{tabletop} arrangement.
A product display follows against a plain studio-like background.
Several pottery jars stand around an open box labeled “ Country Pottery. ” The central box shows one jar inside and a blue label reading “ Soft Powder. ” The jars have the same rounded white upper shape but different colored lower halves and caps, including gray-blue, peach, and rose.
The packaging uses a large arched blue-and-white “ Country Pottery ” label.
The scene changes to a bedside table.
A gold-toned \textbf{picture} frame holds a portrait of a person in a blue dress, and beside it are pale yellow flowers in a slender glass vase, a small brass alarm clock, folded papers, and a white teacup on a \textbf{saucer}.
A gray-blue-bottomed Country Pottery jar appears on the \textbf{tabletop} near these personal objects, its small dark cap visible above the white rim.
On an ornate mantel or shelf, surrounded by white flowers, framed photos, and decorative containers, a hand wearing a ring and metal wristwatch places another peach-bottomed pottery jar near the front edge.
The hand releases it carefully, leaving it centered among the soft cream and white décor.
A paper calendar lies on a \textbf{tabletop}, with large printed dates visible, including 16, 23, and 30.
A tissue box and scattered papers sit nearby.
A hand places a peach-bottomed jar directly over the calendar area, holding it by the small cap, then lets go.
The pink cap remains visible on top as the jar stands upright on the calendar page.
In a child ’s or nursery-like area, plush toys sit on a shelf or \textbf{tabletop} : a pink stuffed rabbit with long ears, a purple teddy bear, a round pastel ball, and small toy figures under a lamp.
A hand sets down a gray-blue-bottomed pottery jar in the foreground near a small yellow object and folded papers.
Once the hand moves away, the jar remains among the toys and soft pastel decorations.
In a warm kitchen setting, a hand carries a wooden tray or board through the foreground while a peach-bottomed pottery jar sits in the background on a windowsill or \textbf{counter}.
Around it are kitchen items : glass jars filled with amber and green liquids, \textbf{utensils} such as a whisk and a slotted \textbf{spoon}, a small potted plant, and a window with square panes.
As the tray passes out of view, the jar remains clearly visible beside the jars and greenery, lit by warm daylight.
The commercial ends with a final product arrangement on a neutral surface : a Country Pottery box in the center with several small pottery jars grouped around it.
The Johnson Wax logo appears to the upper right, and large white text across the bottom reads, “ Put Out The Pottery. ”

% matched lemmas: counter, dish, package, picture, piece, pot, saucer, spoon, tabletop, utensil
\end{textsample}
