\begin{textsample}{POS Dim 6 – 1970 – Score 7.00 – 1970/tv\_com\_1970\_98.txt}  \label{ex:f6_pos_054}
The commercial opens at night or in a dark exterior setting outside a storefront.
Through the lit front window, a sign reads “ Chicken Lickin ’, ” with smaller red text below that is partly legible and appears to include “ King ” and “ Pizza. ” The number “ 874 ” is visible above the door.
A dark car is parked or passing in the foreground, partly blocking the lower right of the storefront.
The scene cuts inside to a restaurant \textbf{kitchen}.
A man in a white uniform and a white paper hat with a colored band is holding a black corded telephone receiver to his ear.
Stainless-steel \textbf{kitchen} surfaces and equipment are visible behind him.
The camera moves closer to his face as he continues using the phone.
A wider \textbf{kitchen} view shows the same worker standing near a large blue trash can or bucket and a bottle labeled “ liquid cleaner ” or similar.
He holds the telephone while looking downward, apparently dealing with \textbf{cleaning} \textbf{supplies}.
Fluorescent ceiling lights and shelves with stacked cups or containers are visible.
The next shot shows him standing near a counter with a large dark window behind him.
The window bears reversed red lettering, including “ Chicken Lickin ’ ” and “ pizza, ” indicating it is being viewed from inside the store.
He still holds the phone and a \textbf{cleaning} tool handle rests against or near him.
The commercial then cuts to close-up \textbf{cleaning} action.
A hand dips or \textbf{presses} a sponge or cloth into a yellow bucket filled with liquid.
Nearby, part of an orange box with the words “ Spic Span ” is visible.
The \textbf{floor} appears dirty or \textbf{stained} around the bucket.
A high-angle shot shows the worker mopping or scrubbing a large, dirty \textbf{kitchen} \textbf{floor}.
A yellow bucket and a blue bucket sit on the \textbf{floor}, and a wide \textbf{patch} of white foam or \textbf{cleaner} spreads across the surface.
Counters, shelves, and \textbf{kitchen} equipment surround the space.
The worker uses a long-handled cleaning tool.
A closer shot focuses on the yellow-handled scrubber moving across the foamy \textbf{floor}.
The head of the tool is rectangular and appears to be pushing or scrubbing through the white cleaner.
The man then bends or moves downward in the \textbf{kitchen}, partly out of frame, with shelves and bottles behind him.
The next close-up shows a rectangular scrubbing attachment with a yellow sponge on top and a black base with raised triangular studs underneath.
The worker is shown again holding the telephone receiver while also holding or looking at the scrubber attachment near his chest.
The quilted or metallic \textbf{kitchen} wall behind him is visible.
The final product shot shows an orange box labeled “ Spic Span ” on a counter.
Large white text beside it reads : “ Gets the dirt liquid cleaners leave behind. ” A black telephone lies on the counter in front of the box, and stacked plates and \textbf{kitchen} shelves appear in the background.
The commercial then cuts to black.

% matched lemmas: clean, floor, kitchen, patch, press, stain, supply
\end{textsample}
