\begin{textsample}{POS Dim 6 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_26.txt}  \label{ex:f6_pos_016}
A black-and-white domestic scene opens on a young blonde woman with light skin, neatly swept-back hair, earrings, and a patterned dress with a \textbf{crisp} white \textbf{collar} and small dark bow.
She stands in front of a curtained window, looking slightly upward and smiling softly, with a dreamy, pleased expression.
As she lowers her gaze, she brings up a delicate light-colored garment, holding it carefully in both hands.
It looks like a fine nightgown or lingerie \textbf{piece}, sheer and ruffled, with short sleeves, a rounded yoke, and long hanging ribbons down the front.
She lifts it wide at shoulder height, admiring it and smiling.
The view widens to a bedroom with floral wallpaper, a window, a dresser, and a mirror.
The blonde woman stands at the foot or side of a bed, surrounded by two other young women.
One brunette sits or kneels on the left, another dark-haired woman in a light dress sits on the right.
The bed is covered with folded and draped light fabrics, suggesting a trousseau display.
The blonde woman holds up the delicate garment for the others to see, while the two seated women lean in, smile, and handle the soft linens.
Two of the women then sit closer together on the bed.
One brunette, wearing a light \textbf{short-sleeved} dress, lifts a filmy, ruffled garment against herself as if \textbf{trying} it on or showing how it would look.
She poses playfully with her shoulders back and the garment held at her chest, while the other woman watches and smiles, holding a folded white textile in her lap.
The mood is friendly and admiring, with the women focused on the fine clothing and linens.
The blonde woman appears again holding a large, thick, light-colored folded blanket or comforter.
She raises it in front of her chest, then hugs it against her cheek and shoulder with both arms.
The blanket looks plush and lofty, with satin-like edging and layered folds along the bottom.
She smiles broadly and strokes the surface with her hand, pressing her cheek into it to show its softness.
Her bracelet and ring are visible as her hand glides over the smooth, fluffy surface.
The setting shifts to a laundry or kitchen area.
The same blonde woman now has her hair down in soft waves and wears a light dress with puffed sleeves and a full skirt.
She bends over an open washing machine or laundry tub, working with light garments inside.
Another young brunette woman stands to her left, holding a \textbf{piece} of laundry and watching.
Behind them are wall cabinets and decorative round \textbf{plates} on the wall.
The brunette reaches up into an overhead cabinet and pulls down a large box marked in bold capital letters “ DETERGENT. ” She holds it out at chest height, angled toward the blonde woman.
The blonde, still beside the open machine, looks at it and then turns toward the cabinet as if choosing something else.
The blonde reaches up into the cabinet and brings down a dark box of Ivory Snow.
She holds the \textbf{package} proudly in both hands, smiling.
The front of the box has large white lettering reading “ IVORY SNOW, ” with smaller text near the top and a small illustrated baby or child figure near the lower right.
The brunette ’s face brightens as she looks at the box, while the older “ DETERGENT ” box remains visible in or near the cabinet.
The blonde sets the Ivory Snow box near the washing area and prepares to use it.
A close view shows the Ivory Snow \textbf{carton} tilted over a small clear measuring \textbf{cup} or glass held in one hand.
White granulated soap pours from the opened spout into the \textbf{cup}, forming a \textbf{mound}.
The \textbf{package} fills much of the view, with “ IVORY SNOW ” clearly \textbf{readable} in large letters.
The pouring continues until the \textbf{cup} is full, then the box is lowered.
The arm in a puffed sleeve extends toward the washing area, and the white contents are added out of view, suggesting they are going into the machine or tub.
Soft white suds or a bright, gauzy overlay fills the image, leading into a close view of a hand smoothing a broad white blanket or bed covering.
The hand presses and glides over the surface, flattening it gently.
The fabric appears thick, smooth, and even, with a soft sheen in the black-and-white light.
Back in the bedroom, the bed is covered with a large, clean-looking white blanket.
A folded stack of white laundry rests near the head of the bed.
The blonde woman, still in her puff-sleeved dress, stands at the left side of the bed and places both hands on the folded items, while the dark-haired woman sits on the right edge of the bed, watching.
The blonde lifts the folded laundry, holding it carefully at waist height, and shows it to the seated woman.
The seated woman looks up at her, attentive and pleased.
The room is neat and simple, with a padded chair behind the bed, small framed \textbf{pictures} on the wall, and a dresser to one side.
The blonde turns toward the dresser with the folded white laundry in her arms.
The dresser has several drawers, an oval mirror above it, and small bottles or containers arranged on top.
Her reflection appears in the mirror as she opens a drawer and places the folded items inside.
She smooths them down with both hands, then glances back with a satisfied smile before turning away from the drawer.
The bedroom fades into a display of garments hanging on a rotating clothes rack or circular clothesline against a plain studio-like background.
Light dresses, slips, linens, and a large rectangular white cloth hang from rods around a central pole.
The rack slowly turns, bringing different \textbf{pieces} into view : sheer dresses, darker garments behind them, pale nightgown-like \textbf{pieces}, and a broad white towel or blanket.
The fabrics sway slightly as they rotate, showing a collection of clean laundry arranged all around the circular frame.
The rotating laundry gradually gives way to a product display.
A box of Ivory Snow appears centered in a \textbf{mound} of white, snow-like flakes.
White flakes fall from above against a dark background, creating the look of gentle snowfall around the \textbf{package}.
The \textbf{carton} stands upright with the large words “ IVORY SNOW ” clearly visible.
In the final image, bold text appears across the lower foreground : “ 99 44/100 \% PURE, ” with smaller words beneath reading “ WITH BEAUTY GLOW. ” The box remains centered in the snowy \textbf{mound} as the flakes continue to fall.

% matched lemmas: carton, collar, crisp, cup, mound, package, picture, piece, plate, readable, short-sleeved, try
\end{textsample}
