\begin{textsample}{POS Dim 6 – 1970 – Score 8.00 – 1970/tv\_com\_1970\_36.txt}  \label{ex:f6_pos_053}
The commercial begins with a nearly black frame, with only archive watermarks visible.
It then cuts to a \textbf{kitchen} scene.
A woman stands at a \textbf{sink} surrounded by dishes and \textbf{kitchen} items.
The counter and \textbf{sink} area look cluttered, with stacked plates on the left and a bottle of drain-cleaning product on the right side of the \textbf{sink}.
The woman appears to be working at or looking down into the \textbf{sink}.
The next shot is a close-up of a white plastic bottle tilted as if being poured.
The label reads “ Liquid-Plumr, ” with a blue burst-style graphic on the front.
The bottle cap is off or open, and the neck of the bottle is visible against a plain background.
The setting changes to a \textbf{bathroom}.
A bald man is \textbf{kneeling} or leaning beside a bathtub.
He is holding or \textbf{wiping} a metal pot or container over the tub.
A bottle of the same product sits on the edge of the tub at the left.
The tub contains some \textbf{cloudy} or dirty-looking water or \textbf{residue}.
A close-up of a drain appears next, with the word “ LATER ” in bold black letters at the bottom of the frame.
The drain is surrounded by swirling or \textbf{cloudy} liquid, suggesting time has passed.
The commercial returns to the \textbf{bathroom}.
The man holds the metal pot at the side of the bathtub and appears to be inspecting it or pouring/emptying it near the tub.
The \textbf{bathroom} background includes cabinets and hanging \textbf{towels}.
The final frame shows a product display in a \textbf{sink}.
Two white bottles labeled “ Liquid-Plumr ” stand on the right, and large bold black text on the left reads : “ Just pour it in and it works. ” The \textbf{sink} drain is visible beneath the text, and a faucet is in the background.

% matched lemmas: bathroom, cloudy, kitchen, kneel, residue, sink, towel, wipe
\end{textsample}
