\begin{textsample}{POS Dim 6 – 1950 – Score 13.00 – 1950/tv\_com\_1950\_15.txt}  \label{ex:f6_pos_012}
In black and white, the commercial begins with a shiny \textbf{spoon} held upright.
In the curved bowl of the \textbf{spoon}, a man ’s face appears as a distorted reflection, stretched and narrowed by the metal surface.
The reflected face looks comic and slightly puzzled.
The image then shifts into a \textbf{tabletop} setting, where a jar of Pream comes into view beside a white coffee \textbf{cup} on a \textbf{saucer}.
The Pream jar is placed prominently in the foreground, centered on the table.
It has a dark body, a light screw cap, and a large light label.
The label reads “ NEW DELUXE Pream ” in bold lettering, with “ 100 \% DAIRY PRODUCT ” beneath it.
A small \textbf{picture} on the label shows a \textbf{spoon} near a \textbf{cup}, suggesting the product being used in coffee.
Behind the jar, slightly out of focus, are parts of a domestic table setting : a white \textbf{cup} and \textbf{saucer}, a \textbf{spoon} standing in or near the \textbf{cup}, and a reflective coffee \textbf{pot} or \textbf{serving} \textbf{vessel} to the right.
A person ’s hand rests on the table in the background, but the product remains the main visible object.
The jar grows larger in view, filling more of the image so the label is easier to read.
The words “ NEW DELUXE Pream ” and “ 100 \% DAIRY PRODUCT ” are the clearest text.
The \textbf{package} is presented steadily, upright, with the label facing forward.
A hand with a ring reaches down to the top of the jar and grips the cap.
The fingers twist and lift the cap away, revealing the open mouth of the jar.
Inside, a pale powder fills the top.
A \textbf{spoon} enters the jar and dips into the powder.
The \textbf{spoon} scrapes through the surface, then lifts out a heaping \textbf{mound} of the light, granular creamer.
The \textbf{mound} sits high on the \textbf{spoon}, uneven and soft-looking, with small peaks and clumps.
The \textbf{spoon} carrying the creamer moves away from the jar across the \textbf{tabletop}.
The jar remains nearby, its label still partly visible, while the \textbf{spoon} travels toward a white coffee \textbf{cup}.
The \textbf{cup} is filled with very dark coffee, nearly black against the white porcelain.
The \textbf{spoon} hovers over the \textbf{cup}, then tips, dropping the pale creamer onto the surface.
The powder lands in floating patches and clumps, spreading across the dark liquid.
The \textbf{spoon} begins stirring.
At first, white \textbf{pieces} of creamer float on top in scattered chunks.
As the \textbf{spoon} circles through the coffee, the pale patches break apart and swirl.
The liquid becomes streaked with lighter ribbons, then gradually turns more evenly cloudy.
The contrast between the dark coffee and the light creamer softens as the product dissolves.
By the end of the stirring, the coffee looks smoother and lighter, with only a few faint swirls remaining.
A man and woman appear seated together in the same domestic setting.
The man, a young to middle-aged adult with dark neatly combed hair, wears a light dress shirt and a dark tie.
He smiles warmly and looks toward the woman beside him.
The woman is seen mostly from the side at the right edge of the image ; she has dark styled hair and holds a light-colored \textbf{cup} near her face.
The man ’s expression is pleased and animated as he glances between her and his \textbf{cup}.
Both hold \textbf{cups}.
The man raises his \textbf{cup} with both hands and \textbf{takes} a sip.
He looks over the rim toward the woman, then lowers the \textbf{cup} slightly with a satisfied smile.
The woman remains turned toward him, also holding her \textbf{cup}, suggesting they are sharing coffee at the table.
A large close-up of the Pream label fills the screen.
The visible text reads “ NEW DELUXE Pream ” and “ 100 \% DAIRY PRODUCT, ” with the word “ Pream ” especially large and bold.
The scalloped shape of the label border is visible around the text.
The man reappears in profile, still seated at the table, sipping from his \textbf{cup}.
He lowers it and smiles, looking pleased.
As the view widens, the Pream jar returns to the foreground on the table.
To the right are a white \textbf{cup} and \textbf{saucer}, a reflective coffee \textbf{pot}, and a decorative bowl filled with rounded fruit, likely grapes or similar small fruit.
A rectangular light-colored card or \textbf{package} leans near the fruit bowl, adding to the arranged \textbf{tabletop} display.
The man ’s shirt sleeve and tie are visible on the left as he holds his \textbf{cup}.
The final arrangement presents the Pream jar standing upright on the left side of the table, label facing forward.
The fruit bowl and coffee service sit to the right, with the \textbf{cup} and \textbf{saucer} behind.
Large superimposed text appears over the \textbf{tabletop} display : “ THE CREAMIEST \textbf{TASTING} PREAM EVER. ” Beneath it is an oval seal resembling a Good Housekeeping-style approval mark, though the smaller \textbf{wording} is partly blurred.
The commercial ends with the product jar and the slogan sharing the screen.

% matched lemmas: cup, mound, package, picture, piece, pot, saucer, serve, spoon, tabletop, take, taste, vessel, wording
\end{textsample}
