\begin{textsample}{POS Dim 6 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_12.txt}  \label{ex:f6_pos_045}
The commercial opens on a sunlit mission-like building with a pale stone dome and bell tower under a deep blue sky.
Across the scene, huge dark block letters, part of the Nescafé name, briefly overlay the architecture before fading.
The image blends into a close view of a middle-aged man with medium skin tone wearing a dark brimmed hat and light shirt.
He stands or sits under an arched structure, with the domed building still visible behind him, and lifts a clear, round glass \textbf{cup} filled with dark coffee to his lips.
He \textbf{drinks} slowly, eyes focused ahead, then lowers the \textbf{cup} slightly with a satisfied, faintly smiling expression.
The image then blends to an older light-skinned man wearing a dark beret against a bright blue sky.
He also holds a clear glass \textbf{cup} of dark coffee close to his mouth, sips, and looks off into the distance with a calm, pleased expression.
His face is warmly lit, showing wrinkles around his eyes and cheeks.
As he lowers the \textbf{cup}, the scene dissolves into a wide coastal landscape : a white camper or recreational vehicle is parked on a dry, rocky bluff above the ocean.
Waves break around large dark rocks below, and hazy hills stretch along the shoreline in the distance.
Near the cliff edge, two people sit with picnic items spread on the ground, including \textbf{cookware} and \textbf{cups}, suggesting an outdoor coffee break.
A close view of the picnic setup follows.
Two Nescafé jars stand upright on a rough rock surface.
The jar on the left has a red-orange label and an orange lid, with “ NESCAFÉ ” in large white letters and an orange \textbf{cup} \textbf{pictured} on the label.
The jar on the right has a green lid and green-toned label, also marked “ NESCAFÉ, ” with a green \textbf{cup} \textbf{pictured} ; this is the decaffeinated version.
Beside them is a distinctive clear glass mug shaped like a globe, decorated with white latitude and longitude lines and map shapes.
In front, a metal pan and other picnic \textbf{cookware} sit partly out of focus.
A light-skinned man with sandy blond hair and a mustache appears by the ocean, holding the same round glass \textbf{cup} of dark coffee.
He sips, looks down at the \textbf{cup}, then smiles with visible dimples, as if enjoying the \textbf{taste}.
The commercial then shows a close demonstration of the product : an open Nescafé regular jar fills the view, its red-orange label reading “ NESCAFÉ ” and “ instant coffee. ” A \textbf{spoon} dips into the granules and lifts out a \textbf{spoonful}.
The \textbf{spoon} moves over the globe-shaped glass mug, and the dark granules drop inside.
A stream of hot water is poured into the mug, making the coffee swirl from golden brown to a deeper brown as steam rises.
A Nescafé jar stands blurred in the background.
The image blends into a close-up of the green-labeled jar.
The label is clearly \textbf{readable} : “ NESCAFÉ decaffeinated instant coffee, ” with a green \textbf{cup} \textbf{illustration} and the words “ 97 \% caffeine free. ” The jar fills more and more of the screen, emphasizing the green lid and green label.
This then dissolves to a light-skinned woman with short, curly brown hair wearing a patterned jacket or sweater.
She holds the round glass \textbf{cup} with both fingers around the handle, sips the dark coffee, and then smiles gently, her eyes bright and relaxed.
The woman is then seen sitting outdoors on the rocky coast with the sandy-haired man.
The ocean and dark rocks are behind them.
He sits to the left in a blue jacket or shirt, holding his glass \textbf{cup} close and \textbf{drinking}.
She sits to the right, facing him, holding her \textbf{cup} and smiling.
They appear to be sharing a quiet coffee break together on the rocks ; she raises her \textbf{cup} and \textbf{drinks} while he glances toward her and then down at his own \textbf{cup}.
At the end, the two Nescafé jars are displayed prominently on a rock in the foreground, sharply in focus.
The regular Nescafé jar with the red-orange label and orange lid stands on the left, and the Nescafé decaffeinated jar with the green label and green lid stands on the right.
Behind them, softly blurred, the couple remains seated by the sea with their \textbf{cups}.
Along the bottom, white script-like text appears reading, “ we can sure please you, ” while the product jars remain the main visual focus.

% matched lemmas: cookware, cup, drink, drinking, illustration, picture, readable, spoon, spoonful, taste
\end{textsample}
