\begin{textsample}{POS Dim 6 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_79.txt}  \label{ex:f6_pos_031}
The commercial begins on a black screen.
A bright domestic kitchen/interior then appears.
A very young child/toddler in a \textbf{beige} textured outfit is shown close up, with an older curly-haired child partly visible beside them.
The toddler looks downward while an adult or child ’s hand moves near the foreground.
The scene shifts to the toddler sitting near a low surface with household \textbf{kitchen} items : a \textbf{frying} pan, utensils, and other cooking-related objects.
The child appears to be handling or \textbf{reaching} toward a long wooden spoon or similar utensil.
A separate shot shows a green basket filled with \textbf{cleaning} items, including a yellow-labeled bottle reading “ pine, ” sponges, a brush, and cloths.
Another quick \textbf{kitchen} shot shows food ingredients on a counter, including carrots, leafy herbs/greens, and what appears to be raw poultry on a plate.
The toddler is then shown seated in a high chair or at a white tray with red food mess smeared across the surface and around the child ’s mouth.
The child looks down at the mess.
A lime-green spray-style \textbf{cleaning} product bottle is introduced in close-up.
Its front label shows a muscular bald cartoon man in a white shirt, with large red text reading “ MR. \textbf{CLEAN} M.NET ” and additional text including “ Antibacterial ” and “ Multi-purpose / Multi-usages. ” The camera moves closer to the illustrated figure and label.
The product is shown standing upright against a bright, \textbf{clean} \textbf{kitchen} background.
A cleaning demonstration follows.
A grayish dirty \textbf{patch} is visible on a white surface while an arm passes over or \textbf{wipes} nearby.
Small on-screen text at the bottom reads : “ 13 total strokes.
Full \textbf{strength} use. ” The product bottle reappears with small white text near the bottom of the screen mentioning “ E. coli \& salmonella ” and instructions such as “ Use as \textbf{directed}.
Full \textbf{strength} use. ” The earlier green basket of \textbf{cleaning} \textbf{supplies} is also shown again with similar small text overlaid.
The camera then pushes in \textbf{tighter} on the product label, emphasizing the brand name “ MR. \textbf{CLEAN} M.NET, ” “ Antibacterial, ” and the yellow “ Multi-purpose / Multi-usages ” area, plus a small lemon graphic near the bottom of the label.
The next scene returns to the bright home interior.
A woman in a light blue shirt stands beside a white high-chair tray with red food mess.
Next to her is a life-sized flat/cartoon standee or cutout of the muscular bald Mr.
Clean character with \textbf{crossed} arms.
The woman \textbf{wipes} the tray.
A close-up shows the illustrated Mr.
Clean face on or near a white surface while a blue cloth \textbf{wipes} across the frame.
The toddler is shown on the \textbf{floor}, crawling or sitting near the white tile.
A green bucket is in the background, and the lower legs and white shoes of the Mr.
Clean cutout/figure are visible beside the child.
The toddler looks toward the figure/shoe area.
Another shot briefly shows the older curly-haired child from above, moving through the bright room.
The woman sits with the toddler and the older child near a green bucket.
They are gathered closely together, and the woman ’s arm is around the children.
A website address, “ www.mrclean.com, ” appears at the bottom right.
A product \textbf{lineup} appears in an overexposed bright shot : three bottles in different colors, likely pink, blue, and yellow/green, all with similar “ Mr.
Clean ” branding.
The website “ www.mrclean.com ” is again visible at the bottom right.
The toddler is then shown touching or \textbf{wiping} the \textbf{floor} tile with one hand, with the green bucket still in the background.
The final family scene shows the woman sitting on the \textbf{floor} with the two children in a \textbf{clean}, sunlit room.
The Mr.
Clean cutout stands behind them with arms \textbf{crossed}.
A blue bucket is nearby, and the older child holds or wears a blue bucket or basin over the head/face area.
The group appears relaxed and smiling.
The commercial ends by returning to the bright product \textbf{lineup} with the website at the bottom right.

% matched lemmas: beige, clean, cross, direct, floor, fry, kitchen, lineup, patch, reach, strength, supply, tight, wipe
\end{textsample}
