\begin{textsample}{POS Dim 6 – 1990 – Score 4.00 – 1990/tv\_com\_1990\_104.txt}  \label{ex:f6_pos_050}
The commercial begins on a nearly black frame, with only a small channel or archive-style watermark visible in the lower-right corner.
It then cuts to a close product shot of two Tide detergent containers in warm, bright household lighting.
On the left is a large orange Tide bottle with a handle ; on the right is a white bottle labeled “ Ultra Tide Refill. ” The labels are large and colorful, dominated by the Tide logo and orange/yellow circular background.
Some smaller text is visible but not fully legible in the sampled frame.
The next shot moves to a low-angle view of a \textbf{clean} tiled \textbf{floor} inside a home.
The background is softly lit and out of focus, with potted plants and furniture legs visible, suggesting a \textbf{kitchen}, laundry area, or domestic interior.
A rapid sequence follows in very shallow focus.
The imagery is blurred, but it appears to show a hand or finger \textbf{reaching} toward or releasing a small white object with a Tide label.
Across several frames, this small white, packet-like or bottle-like object moves from the left side toward the right side of the frame against a warm, softly blurred household background.
The object remains difficult to identify clearly because of motion blur and soft focus, but the Tide branding is intermittently visible.
The background includes indistinct shelves, plants, and light-colored interior surfaces.
The commercial then cuts back to a clear product display : a white “ Ultra Tide Refill ” container standing upright on the tiled \textbf{floor}.
The setting remains bright and domestic, with a potted plant and window or light source in the background.
At the bottom of the screen, small white text reads : “ COSTS LESS PER USE. ” In the final frame, the product appears lower in the frame and looks compressed or collapsed, with the Tide logo still visible.
Large centered white text overlays the scene : “ LESS MONEY ” on the first line and “ LESS WASTE ” on the second.
The bottom caption “ COSTS LESS PER USE ” remains visible.
The warm indoor background and lower-right watermark remain present.

% matched lemmas: clean, floor, kitchen, reach
\end{textsample}
