\begin{textsample}{POS Dim 6 – 1980 – Score 16.00 – 1980/tv\_com\_1980\_102.txt}  \label{ex:f6_pos_032}
A Betty Crocker SuperMoist cake mix box stands upright, filling most of the view.
The \textbf{package} is dark brown with a large yellow “ SuperMoist ” name across the top, the red Betty Crocker \textbf{spoon} logo beneath it, and “ CAKE MIX ” printed in white.
A photo of a dark chocolate cake with glossy frosting appears on the front.
The background is softly blurred, suggesting a kitchen or home setting.
A white tub of Betty Crocker Creamy Deluxe frosting is then held in someone ’s hands near the cake mix box and a dark chocolate cake.
The tub has a brown-and-gold label with the Betty Crocker logo and the words “ Creamy Deluxe ” and “ FROSTING ” visible.
A \textbf{spoon} dips into the open container and lifts out a thick scoop of dark chocolate frosting.
The frosting clings heavily to the \textbf{spoon}, looking shiny and smooth.
The scene widens to a warm domestic kitchen.
A woman with dark, curled shoulder-length hair, wearing a light plaid shirt, leans over a chocolate cake with a young girl beside her.
The girl has long hair with straight \textbf{bangs} and wears a pale dress with puffed sleeves.
Both are close together at the \textbf{counter}, smiling and concentrating on the cake.
The frosting tub sits nearby, label facing outward.
The woman appears to guide or assist while the child helps spread the chocolate frosting over the cake with a \textbf{utensil}.
The cake is round and covered with glossy swirls of frosting.
The girl looks delighted as she works, and the woman watches her with an affectionate smile.
They continue frosting together, their heads nearly touching over the cake.
The girl smiles broadly and looks down at the dessert, then up at the woman.
Their faces turn toward each other in a pleased, shared moment, as if admiring what they have made.
The kitchen background includes light cabinets, a window area with plants or greenery, and soft daylight.
The woman and child then move with the finished cake.
The girl carries the cake on a white \textbf{plate}, holding it carefully in front of her with both hands, while the woman bends close behind her, guiding and supporting her.
The cake ’s chocolate frosting is thick and shiny, with rounded ridges and swirls over the top.
The girl smiles proudly as she brings it forward.
They present the cake to a man seated at a table.
He appears to be an adult with short dark hair, wearing a light blue shirt.
He reaches out with both hands to \textbf{take} the \textbf{plate}.
The woman and girl lean in from the left, watching his reaction.
A white \textbf{cup} and \textbf{saucer} sit on the table in front of him.
The girl beams as the man \textbf{accepts} the cake, and he looks pleasantly \textbf{surprised}, holding the \textbf{plate} up to admire it.
A close view focuses on the cake ’s frosting : smooth, golden-brown chocolate frosting spread in thick, glossy waves across the dark cake.
The surface catches the light, emphasizing the creamy texture and decorative swirls.
The man is then shown in close view.
He looks toward the cake and the others, raises a finger near his mouth as if \textbf{tasting} or reacting to the frosting, and his expression shifts into a satisfied smile.
A slice of dark chocolate cake appears on a \textbf{fork}, lifted away from the cake.
The inside looks dense and moist, with a layer of frosting across the top and another layer between the cake layers.
As the \textbf{fork} pulls the \textbf{piece} away, the \textbf{crumb} appears soft and tender, with frosting stretching slightly at the edge.
The view lingers on the cut side of the cake, showing the dark, moist interior and the thick frosting along the top. \textbf{Crumbs} cling to the frosting where the bite has been \textbf{removed}, and the glossy frosting forms a soft peak at the top edge.
The products are then displayed together : the Betty Crocker SuperMoist cake mix box stands on the left, and the white tub of Creamy Deluxe frosting sits in front on the right.
Behind them is a white mixing bowl with a spatula or \textbf{spoon} handle standing inside it.
On the cake mix box, the large yellow “ SuperMoist ” name, red Betty Crocker logo, “ CAKE MIX, ” and a yellow circle reading “ PUDDING IN THE MIX ” are visible.
The frosting tub again shows the Betty Crocker logo, “ Creamy Deluxe, ” and “ FROSTING. ” Finally, the woman and girl appear together again in the kitchen.
A red Betty Crocker \textbf{spoon} logo is displayed at the upper left of the image.
The girl looks up at the woman with a happy, proud expression, and the woman bends close to her, smiling warmly.
They face each other affectionately, sharing the pleased result of baking and decorating the cake together.

% matched lemmas: accept, bang, counter, crumb, cup, fork, package, piece, plate, remove, saucer, spoon, surprised, take, taste, utensil
\end{textsample}
