\begin{textsample}{POS Dim 6 – 2020 – Score 5.00 – 2020/tv\_com\_2020\_89.txt}  \label{ex:f6_pos_013}
The commercial opens with a close-up product shot of a fried chicken sandwich against a bright orange background.
The sandwich has a glossy bun, a thick piece of craggy fried chicken, visible pickle slices, and a pale sauce on the bottom bun.
The scene then cuts to the interior of a fast-food \textbf{kitchen}.
Stainless-steel equipment, \textbf{fry} stations, counters, trays, and orange-and-white packaging are visible.
Employees in orange shirts, black aprons, \textbf{gloves}, and caps are working in the \textbf{kitchen}.
One worker moves quickly near metal equipment, partially blurred by motion.
A closer, angled shot shows part of an employee in an orange uniform beside large metal \textbf{kitchen} equipment.
The framing is \textbf{tight} and slightly tilted, emphasizing movement and the work environment.
The next shot focuses on a fryer basket being \textbf{lifted} or drained, with liquid or oil dripping down from above into or near the basket.
The background is blurred, but the setting remains the \textbf{kitchen}.
A wider \textbf{kitchen} shot shows an employee holding a golden fryer basket over a white rectangular tub.
Another employee stands nearby wearing \textbf{gloves}.
The basket appears to contain fried food being transferred or drained.
The worker then places or handles the contents in the white tub while another \textbf{gloved} employee stands beside the station.
The stainless-steel \textbf{kitchen} surfaces and food-preparation area remain visible.
The commercial cuts back to extreme close-ups of the chicken sandwich.
The fried chicken texture fills most of the frame, with the pickle slices and sauce visible underneath.
Very small white legal/disclaimer text appears along the bottom edge, but it is too small and blurred to read clearly in the sampled frames.
Another close-up continues to show the sandwich from the side, emphasizing the rough, crunchy breading, green pickle slices, and sauce.
A wider product shot follows : the sandwich sits on branded wrapping paper with \textbf{fries} placed around it.
The bun is glossy, and the fried chicken extends beyond the edges of the bun.
A hand and orange-and-white container are blurred in the background.
Small white disclaimer text appears at the bottom, but it is not legible in these frames.
The scene returns to the \textbf{kitchen}.
An employee in Popeyes colors stands in the foreground, and large white letters begin appearing across the image, spaced out as part of an on-screen brand graphic.
The visible letters form “ Popeyes ” as the logo animation progresses.
The final frame shows the \textbf{kitchen} from a wider angle with workers and trays of fried chicken visible.
A large white “ POPEYES ” logo is centered on screen, with “ LOUISIANA \textbf{KITCHEN} ” underneath.
The employee in orange and black stands behind the overlaid logo, and the stainless-steel \textbf{kitchen} continues into the background.

% matched lemmas: fry, glove, kitchen, lift, tight
\end{textsample}
