\begin{textsample}{POS Dim 6 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_31.txt}  \label{ex:f6_pos_015}
It begins with a pale title card for the television program.
Large block letters read “ DO YOU TRUST YOUR WIFE, ” arranged in three lines, with flat star shapes scattered around the words.
The \textbf{picture} is black and white, with the lettering dark against a light background.
The program title fades into a product display.
A square Jell-O \textbf{package} appears centered over a busy patterned background filled with repeated words such as “ BUSY DAY DESSERT. ” The front of the box reads “ JELL-O ” at the top, “ New ” on a dark diagonal label, “ INSTANT PUDDING ” in large lettering, and “ 7 FLAVORS ” along the bottom.
The box remains prominent, slightly three-dimensional, as the busy-day \textbf{wording} repeats behind it.
The imagery shifts to a simple line-drawn animation on a plain light background.
A clock-like symbol appears : two dark hands with arrowheads pivot from a central dot.
The hands swing around rapidly, leaving faint circular rings behind them, visually suggesting time rushing by.
A small cartoon car then enters from the right.
Inside are two simplified cartoon figures, drawn with thin black outlines.
The front figure has a long \textbf{pointed} nose and curly hair ; a second smaller figure sits behind.
The car moves across the scene while the clock hands continue to spin behind it.
The clock motif continues as the car exits.
A cartoon adult figure appears, leaning forward with a mop or long-handled cleaning tool, as if mopping the floor.
The figure has a simple triangular body, curly hair, and a \textbf{pointed} nose.
The drawing is spare and humorous, with the body angled as though hurrying through a chore.
Brief abstract vertical shapes appear during the sequence, then another cartoon domestic scene appears : the curly-haired adult stands with a basket tucked against one side while a small childlike figure stands nearby.
The adult ’s posture and the repeated clock arrows behind them continue the sense of a crowded, hurried day.
A large oval clock face fills the scene, with a vertical arrowed hand running from bottom to top through a central dot.
The same cartoon adult stands at the right edge, looking up toward the clock.
The figure ’s body droops slightly, suggesting fatigue or concern as the day reaches \textbf{dinner} time.
The clock graphic transforms into a large circular shape, and the adult raises a hand to the face with a relieved, smiling expression.
A product message then appears over the pale background.
Large text reads “ JELL-O, ” and behind it, inside a soft oval, are the words “ New INSTANT PUDDING. ” A dark tilted label at lower left reads “ No Cooking BUSY-DAY Dessert. ” The Jell-O Instant Pudding box is then shown alone in three-quarter view, sitting against a plain light background.
The same front-panel \textbf{wording} is visible : “ JELL-O, ” “ New, ” and “ INSTANT PUDDING, ” with the dark “ No Cooking BUSY-DAY Dessert ” label on the lower left of the box.
The commercial moves into a live-action \textbf{preparation} demonstration.
A clear glass mixing bowl sits on a \textbf{counter}, partly filled with \textbf{milk}.
To the right of the bowl lies an electric hand mixer with two metal beaters.
A hand holds the Jell-O Instant Pudding box over the bowl and pours the dry pudding mix into the \textbf{milk}.
Powder falls in a steady stream, forming pale \textbf{mounds} and darker patches on the \textbf{milk} ’s surface.
The \textbf{package} is then set down to the left of the bowl, front facing outward so the Jell-O branding remains visible.
A hand brings the electric mixer over the bowl.
The two beaters are lowered straight down into the \textbf{milk} and powder mixture.
The beaters begin to turn, churning the contents ; the surface ripples and thickens as the dry mix is drawn into the liquid.
The box remains placed to the left as a visual reference while the bowl stays centered.
The prepared dessert is then presented on a round \textbf{serving} tray.
Four footed glass dessert \textbf{cups} are arranged on small \textbf{saucers}, each filled with a smooth, light-colored pudding.
The tops look softly \textbf{mounded} or swirled, with a creamy texture.
A hand places one of the \textbf{cups} into the front center position, completing the arrangement.
The tray has a polished, reflective surface and a slightly raised rim, giving the dessert presentation a tidy, formal serving-table look.
The final product display returns to the Jell-O Instant Pudding box against a pale background.
Large floating words behind and above it read “ GOOD GOOD ” and “ BUSY-DAY DESSERT. ” The box again shows “ JELL-O, ” the dark diagonal “ New ” label, “ INSTANT PUDDING, ” and “ 7 FLAVORS ” near the bottom, ending with the \textbf{package} centered as the main visual focus.

% matched lemmas: counter, cup, dinner, milk, mound, package, picture, pointed, preparation, saucer, serve, wording
\end{textsample}
