\begin{textsample}{POS Dim 6 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_6.txt}  \label{ex:f6_pos_008}
The commercial begins in black and white, fading from darkness to an overhead view of a small, neatly set dining place.
A round \textbf{plate} sits in the centre of a table, surrounded by a folded napkin on the left, \textbf{fork} and other \textbf{utensils} on both sides, and a \textbf{drinking} glass near the upper right.
On the \textbf{plate} is a sparse-looking diet meal, with a few small portions arranged separately rather than a hearty serving.
The table setting is formal and tidy, but the meal itself looks modest and unsatisfying.
The plain \textbf{plate} slowly gives way to a much fuller \textbf{dish} : an oval bowl or deep \textbf{plate} filled with chunky beef stew, set on a larger \textbf{dinner} \textbf{plate}.
The stew appears thick and abundant, with many cubed \textbf{pieces} and irregular chunks visible in gravy.
The place setting remains around it, with silverware and a glass nearby, making it look like a complete \textbf{dinner} rather than a small diet portion.
A hand places a cylindrical can on a \textbf{tabletop} and then withdraws, leaving the can standing upright.
The label is clearly shown : “ GOOD \textbf{MEASURE} ” in large letters, “ BRAND DIET \textbf{DINNER}, ” “ BEEF STEW, ” and a dark circular badge reading “ 300 CALORIES. ” The lower part of the label includes small food \textbf{illustrations}, including a plated meal and other meal-related items.
The can is presented alone against a simple studio background, with the label facing forward.
The stew returns in a \textbf{serving} \textbf{dish}, now shown more closely.
It fills the bowl generously, with many visible cubes and chunks in sauce.
The image moves progressively closer until the stew fills almost the entire view, emphasizing the \textbf{pieces} of meat, potatoes, and vegetables.
Over this close-up, white on-screen text appears : “ lose as much weight as on the liquid diets. ” The words sit over the stew, contrasting with the darker and lighter food textures beneath them.
The screen then becomes dark with the word “ impossible? ” in white lowercase letters, placed toward the right side.
The same word briefly remains as the scene changes to a simple \textbf{tabletop} or platform with two small metal containers or bottles standing upright.
A rectangular sign or display sits to the left, raised on a stand.
The arrangement resembles a \textbf{measuring} or weighing setup, suggesting calculation or precision.
A large scale-like graphic fills the screen next : a curved row of black vertical tick marks with a dark pointer rising from below.
The pointer moves across the marks.
Behind this \textbf{measuring} graphic, images of food ingredients appear layered in, including large vegetables and \textbf{pieces} of meat or stew ingredients.
The ingredients are arranged close together, as if being \textbf{measured} or balanced, while the pointer and tick marks stay prominent over them.
The scene changes to a domestic dining table where a man and woman sit together eating.
The man, on the left, appears to be an adult with short dark hair, wearing a dark suit jacket, white shirt, and tie.
He holds a \textbf{spoon} and looks down toward his \textbf{plate}.
The woman, on the right, appears to be an adult with light, short, styled hair, wearing a simple \textbf{short-sleeved} dress.
She also holds a \textbf{spoon} and smiles slightly as she eats.
The table is set with \textbf{plates}, glasses, and a floral centrepiece.
Behind them are home-like details, including a window area, curtains or blinds, and a doorway or louvered panel, giving the scene a comfortable dining-room atmosphere.
A closer view isolates the woman ’s face and shoulders.
She looks down toward her food, then forward, calm and composed, with a small satisfied expression.
Her hair is neatly shaped around her face, and a decorative button or pin is visible near one shoulder of her dress.
The plated stew appears again, then is framed inside a shield-shaped border that resembles the shape of the Good \textbf{Measure} label.
Within this label-shaped window, different prepared meals are displayed one after another.
First is a \textbf{plate} of the chunky beef stew.
Then a lighter-coloured \textbf{dish} appears, likely the chicken with noodles mentioned in the commercial context, \textbf{served} in a \textbf{shallow} bowl on a place setting.
Finally, a darker, thicker \textbf{dish} appears in the same shield-shaped window, consistent with chili con carne, filling a bowl with a dense, textured surface.
The product label returns large on screen, again showing “ GOOD \textbf{MEASURE}, ” “ BRAND DIET \textbf{DINNER}, ” “ BEEF STEW, ” and the “ 300 CALORIES ” badge.
The can then appears with other Good \textbf{Measure} cans beside it.
Three cans stand in a row on a plain surface under studio lighting.
The centre can is “ BEEF STEW. ” The left can is another Good \textbf{Measure} variety, with \textbf{wording} indicating a chicken-and-noodles \textbf{dinner}, and the right can reads “ CHILI CON CARNE. ” Each can carries the same prominent “ 300 ” calorie badge, and all are arranged front-facing like a product lineup.

% matched lemmas: dinner, dish, drinking, fork, illustration, measure, piece, plate, serve, shallow, short-sleeved, spoon, tabletop, utensil, wording
\end{textsample}
