\begin{textsample}{POS Dim 6 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_13.txt}  \label{ex:f6_pos_018}
The commercial is in black and white.
It opens on a polished \textbf{tabletop} arranged like an elegant still life.
At the center sits a cylindrical metal can with a large oval label reading “ YUBAN COFFEE ” in bold letters.
The can rests on a \textbf{mound} of loose coffee beans spread over a \textbf{piece} of textured cloth.
To the right is a white coffee \textbf{cup} on a \textbf{saucer}, filled with dark coffee.
To the left and behind the can are glass \textbf{vessels} and \textbf{stemmed} glasses containing dark liquid, evoking wine.
The lighting is bright and glossy, making the can lid, glassware, and white \textbf{cup} gleam.
The view gradually reveals more of the table.
Around the Yuban can are wine bottles, a decanter, several wine glasses, tall pepper-mill-like grinders, and covered \textbf{dishes}.
The coffee beans form a dark, pebbled carpet across the foreground.
The \textbf{cup} remains near the can, while the wine glasses and bottles fill the left side of the arrangement.
As the display continues, more foods appear : a cheese board with a round cheese and cut \textbf{pieces}, a \textbf{dish} of grapes or small fruit, and a basket holding bottles and glasses.
The setting looks staged and abundant, with brick or tiled wall texture in the background and reflective \textbf{tabletop} surfaces.
The food display expands further to include a large steak or roast on a grill-like tray in the foreground.
It is placed beside the cheeses and wine, with a lidded \textbf{serving} \textbf{vessel} behind it.
The steak ’s surface is highlighted, and the surrounding props—bottles, glasses, cheese, and fruit—suggest rich, mature, carefully chosen foods.
The Yuban can is no longer central in this part ; the food and \textbf{drink} examples dominate the table.
The image changes to a close-up of coffee beans filling the entire screen.
The beans are oval, ridged, and densely piled, with light catching their curved surfaces.
The texture of the beans becomes the main visual focus.
Then the product arrangement returns : the Yuban can and the filled \textbf{cup} sit again among loose beans.
A hand enters from the right, grasping the handle of the white \textbf{cup}.
The hand lifts the \textbf{cup} from its \textbf{saucer}, leaving the \textbf{saucer} behind on the bean-covered cloth.
The \textbf{cup} rises past the wine glasses and decanter in the background.
A light-skinned adult woman appears in profile as the \textbf{cup} is brought to her lips.
She has neatly styled 1950s hair, swept back with curled detail near the ear, and wears decorative earrings.
Her face is calm and composed.
Holding the \textbf{cup} delicately by the handle, she leans in and sips.
Her eyes are lowered toward the \textbf{cup}.
After \textbf{drinking}, she remains poised, with a faint satisfied expression as the \textbf{cup} hovers near her mouth.
The scene returns to the product still life : the Yuban can with its oval “ YUBAN COFFEE ” label sits beside the white \textbf{cup} on its \textbf{saucer}, both surrounded by coffee beans and soft cloth.
The background again includes the elegant table objects, such as a covered \textbf{dish} and tall mills.
A new demonstration begins with an open burlap sack filled with coffee beans.
Hands scoop up beans from the sack and let them fall back in a small stream.
Large white on-screen text appears over the sack reading “ green beans. ” The hands continue stirring and lifting the beans, emphasizing their small, pale, raw-looking appearance in the black-and-white image.
The coarse weave of the burlap sack frames the \textbf{mound}.
The comparison widens into two side-by-side bean displays.
On the left, a hand holds a scoop or cloth full of darker beans, labeled with large white text “ aged beans. ” On the right, another hand holds a lighter-looking handful labeled “ green beans. ” The two labels sit near the bottom of the screen, each aligned with its respective \textbf{sample}.
The left-hand aged beans appear darker and richer in tone, while the right-hand green beans appear lighter.
Behind them, sacks of coffee beans are stacked, and a worker, seen from behind in a plaid shirt, moves among the sacks in a warehouse-like storage space.
The hands hold the two \textbf{samples} forward for comparison while the worker and sacks remain in the background.
The focus tightens to a close-up of hands \textbf{cupping} a \textbf{mound} of the darker aged beans.
The beans fill the palms, piled high, with individual ridges and rounded shapes clearly visible.
The hands tilt slightly, and the beans begin to cascade forward.
The falling beans visually transform into a filled white coffee \textbf{cup} : the stream of beans gives way to the dark surface of coffee inside the \textbf{cup}.
Small pale bubbles or highlights float on the coffee ’s surface.
A hand steadies the \textbf{cup} and \textbf{saucer} near the rim and edge, presenting the \textbf{drink} close to the viewer.
The \textbf{cup} remains in close-up, full of dark coffee with a few light bubbles on top.
Fingers hover and adjust around the \textbf{cup} and \textbf{saucer}, then the \textbf{cup} is lifted.
The background becomes darker and softer, and the \textbf{cup} moves toward a person in formal clothing.
A light-skinned adult man appears, clean-shaven, with neatly combed dark hair.
He wears a dark suit jacket, a light dress shirt, and a tie.
He holds the white \textbf{cup} by its handle at chest level, looking down toward it.
His expression is restrained and thoughtful.
He raises the \textbf{cup} to his lips and sips, keeping his posture upright.
The background behind him is softly lit and patterned with bright highlights, suggesting an elegant interior.
The image returns one final time to the product arrangement.
The Yuban Coffee can is placed on the left, its “ YUBAN COFFEE ” label clearly visible, and the white \textbf{cup} of coffee sits on a \textbf{saucer} to the right.
Both rest on the spread of coffee beans and textured cloth.
In the background are the same refined table props : glassware, a covered \textbf{dish}, and tall mills.
The composition holds steady on the can and \textbf{cup}, with the beans filling the foreground and the product name prominently displayed.

% matched lemmas: cup, dish, drink, drinking, mound, piece, sample, saucer, serve, stem, tabletop, vessel
\end{textsample}
