\begin{textsample}{POS Dim 6 – 1970 – Score 5.00 – 1970/tv\_com\_1970\_57.txt}  \label{ex:f6_pos_058}
The sequence begins with a very dark, low-lit shot of a stemmed glass containing pale liquid.
Over the image is large white text reading, “ Paul Masson will sell no wine before its time. ” Archive watermarks are also visible over the frame.
After a large time jump, the visuals cut abruptly to a close-up cleaning demonstration.
A hand holds a yellow sponge or scrub \textbf{pad} against a shiny, reflective surface, apparently \textbf{wiping} or scouring it.
The shot is \textbf{tight} and somewhat blurred, so the exact object being \textbf{cleaned} is unclear.
The next shot moves closer to the work surface : a hand \textbf{presses} a yellow sponge-like \textbf{pad} across a flat surface, possibly a countertop or dish surface.
The image is low and soft-focused, emphasizing the motion of scrubbing.
The commercial then shows two hands \textbf{cleaning} the inside of a shiny metal pot or pan with the same yellow \textbf{pad}.
Bold white on-screen text at the bottom reads, “ Tougher than a steel \textbf{pad}. ” A following close-up shows the \textbf{pad} being rubbed against the side of a reflective metal pot or cookware item.
A shiny lid or cookware piece sits to the right.
White text at the bottom reads, “ Scours without scratching. ” The product is then revealed on a countertop : a bright yellow and orange box labeled “ NEW Scrunge ” stands behind a rectangular sponge \textbf{pad} with a blue scrubbing surface and yellow base.
Metal cookware remains in the background, linking the product to the cleaning demonstration.
The final frame moves in closer on the product box and sponge.
The large brand name “ Scrunge ” is clearly visible on the box, and a white on-screen caption at the bottom reads “ Johnson wax. ” Small packaging text is present but not fully legible in the sampled frame.

% matched lemmas: clean, pad, press, tight, wipe
\end{textsample}
