\begin{textsample}{POS Dim 6 – 1980 – Score 16.00 – 1980/tv\_com\_1980\_104.txt}  \label{ex:f6_pos_033}
The commercial opens on a white Hamburger Helper box standing upright on a red-and-white \textbf{checked} tablecloth in a warm, dimly lit kitchen setting.
The front of the box reads “ FOR LASAGNE ” above the large blue “ Hamburger Helper ” logo, with “ ADD TO 1 LB.
HAMBURGER ” below.
A smaller label on the right says “ LASAGNE MACARONI \& ITALIAN STYLE SAUCE MIX. ” Near the bottom is a \textbf{picture} of the prepared pasta meal and a yellow \textbf{starburst} announcing a new, more Italian flavor.
Beside the box sits a decorative bottle-shaped candle holder with a flame, and kitchen items such as jars and canisters blur softly in the background, giving the scene a cozy dining-table feel.
The setting shifts to a stovetop and \textbf{counter}.
A wide skillet is filled with a hot, saucy lasagne-style pasta mixture : curly-edged noodles, browned meat, and glossy reddish-brown sauce.
Steam rises faintly.
To the right of the pan is the Hamburger Helper mascot, a white animated glove character with a face on its palm.
It has black eyebrows, a curled black \textbf{moustache}, a round red nose, and wears a floppy white chef ’s hat tilted over one side.
The glove stands on a small orange base like feet.
It gestures animatedly toward the skillet, leaning and bouncing as if presenting the meal.
A red kettle and a \textbf{checked} cloth sit behind it on the \textbf{counter}.
A middle-aged man with curly dark hair, a receding hairline, and a thick dark \textbf{moustache} \textbf{tastes} from a \textbf{fork}.
He wears a plaid shirt.
His face fills the scene as he chews, then his expression changes from considering to pleased and \textbf{surprised}.
His eyes widen, his eyebrows lift, and he smiles slightly, suggesting he likes the flavor.
Back by the skillet, the glove mascot continues performing beside the steaming pasta.
It points with its raised fingers and leans toward the pan, its chef ’s hat flopping as it moves.
The pasta remains in the foreground, browned meat and curled noodles visible in the sauce.
A young girl with light brown hair in \textbf{bangs} and curled ends \textbf{tastes} from a \textbf{fork}.
She has large eyes and a round, youthful face.
After \textbf{taking} a bite, she looks forward with widened eyes and a small, satisfied smile, as if pleasantly surprised.
Soon after, a young boy with straight brown hair cut in a bowl shape \textbf{tastes} from a \textbf{spoon}.
He wears a green \textbf{collared} shirt.
He chews, holds his lips together, and then smiles with bright eyes, clearly enjoying the bite.
The food is then shown in rich detail on a \textbf{plate} and \textbf{spoon}.
Curly lasagne noodles, browned hamburger, and thick tomato-colored sauce fill the screen.
A \textbf{spoon} lifts a heaping bite from the \textbf{mound}, pulling up soft noodles and meat.
The sauce glistens under the light, and wisps of steam drift upward, emphasizing that the meal is hot.
The \textbf{spoonful} rises and pauses above the \textbf{plate}, showing the ruffled pasta edges and chunky meat clinging together in sauce.
The glove mascot appears again alone on the kitchen \textbf{counter}, still wearing its floppy chef ’s hat.
It faces forward like a tiny host, moving its “ fingers ” as if speaking and emphasizing points.
Its red nose and black \textbf{moustache} stand out against the white glove.
Around it are the red kettle, a folded red-and-white \textbf{checked} cloth, and small flowers or kitchen decorations in the background.
The \textbf{preparation} process is briefly demonstrated.
A skillet of browned ground beef sits on a stovetop, with the Hamburger Helper box standing behind it to the left as a product reference.
A hand enters with a wooden \textbf{spoon} and stirs the crumbled meat around the pan.
The scene then shows the skillet transformed into the finished \textbf{dish} : the same pan now holds the saucy curly noodles and meat mixture.
The wooden \textbf{spoon} stirs through the pasta, spreading the noodles and sauce evenly, while the box remains visible in the background.
More close views of the finished meal follow.
The pasta is piled high, glossy with sauce, with browned meat distributed throughout.
A \textbf{spoon} slides in from the side and lifts another generous serving.
The lifted bite stretches upward from the \textbf{mound}, showing curly noodle ribbons, chunks of hamburger, and thick sauce holding the ingredients together.
Steam continues to rise against a dark background, making the food look hot and hearty.
Near the end, the family sits together at a dining table in a warmly decorated home interior.
On the left is an adult woman with curly light-brown hair wearing a pale pink or lavender blouse.
Beside her sits the moustached man in his plaid shirt.
To his right is the young boy in the green shirt, and another child is partially visible at the far right with long light-brown hair. \textbf{Plates} of the pasta meal are set in front of them, with a small container of breadsticks or crackers and a dark condiment shaker or jar in the center of the table.
The adults and children turn toward one another, appearing engaged and pleased as they eat together.
The final product display returns to the red-and-white \textbf{checked} tablecloth against a dark background.
The Hamburger Helper Lasagne box stands on the left, and the white glove mascot stands on the right, angled playfully with its chef ’s hat drooping to one side.
Large white text appears above them reading “ New Zestier Lasagne. ” The glove bobs and gestures beside the box, presenting the product as the box ’s front remains visible with the Hamburger Helper logo, “ ADD TO 1 LB.
HAMBURGER, ” the prepared meal image, and the yellow “ new ” flavor \textbf{starburst}.

% matched lemmas: bang, checked, collar, counter, dish, fork, mound, moustache, picture, plate, preparation, spoon, spoonful, starburst, surprised, take, taste
\end{textsample}
