\begin{textsample}{POS Dim 6 – 1980 – Score 12.00 – 1980/tv\_com\_1980\_118.txt}  \label{ex:f6_pos_035}
The commercial begins in a warm, orange-tinted close view of a white toy oven on a \textbf{tabletop}.
Its front looks like a small microwave : a dark square door on the left, and on the right a control panel with an orange keypad area, a small display, and a large round dial below.
Along the base, a black label reads “ Easy-Bake Mini-Wave Oven, ” and small white \textbf{copyright} text at the bottom reads “ {\EmojiFont ©} CPG Products Corp. 1982. ” The toy has rectangular side \textbf{pieces} extending from both sides, suggesting a pass-through tray or handle.
The view widens to reveal the toy oven sitting on a kitchen table in a homey kitchen.
A young girl, about elementary-school age, with light brown hair pulled back and wearing a white high-neck blouse under a pink pinafore-style dress, stands behind the table.
Beside her is a young blond boy wearing large round glasses and a dark blue top.
Both children smile and look toward the toy and toward an adult woman at the left.
The adult woman has long reddish hair with \textbf{bangs} and wears a pale blue top. \textbf{Plates}, a small mixing bowl, and baking accessories sit around the oven on the table.
The girl reaches toward the woman, who hands her a small round baked treat or cake.
The girl \textbf{accepts} it with both hands, smiling broadly, while the boy watches with an eager grin.
White on-screen text appears near the bottom : “ LIGHT BULB NOT INCLUDED. ” The girl is then shown closer, smiling down at a brown mixing bowl with pale yellow batter inside.
She holds a small \textbf{spoon} and stirs or scoops the mixture, glancing upward with a pleased, excited expression before looking back down into the bowl.
The warm kitchen background includes hanging \textbf{utensils} and softly lit shelves.
The toy oven returns to the center of attention on the table.
A child ’s hand operates the side mechanism, sliding a pale tray or handle into the left side of the white oven.
The dark front door and orange control panel remain visible, with the “ Easy-Bake ” label along the bottom.
The action suggests the small batter pan is being moved through or into the oven.
The girl ’s face fills the scene as she waits and smiles, her eyes shifting to the side with anticipation.
The boy ’s face appears beside her in close-up ; he looks up through his large glasses with a small smile, sharing the expectant mood.
Then the three gather around the toy oven at the table : the woman leans in from the left, the boy stands in the middle, and the girl stands on the right.
All three react with open-mouthed delight as the girl holds a long orange tool or pusher extending from the oven ’s side, as if \textbf{removing} or presenting the finished treat.
A close view shows a small round cake on a \textbf{plate} or napkin being covered with glossy chocolate frosting.
A white plastic spatula spreads the thick frosting in looping swirls over the top while fingers steady the cake at the edge.
The frosting is smoothed across the surface, leaving shiny ridges and rounded chocolate curves.
The adult woman \textbf{tastes} a small \textbf{piece} of the \textbf{frosted} cake.
She brings it to her mouth, \textbf{takes} a bite, and widens her eyes in an exaggerated pleased reaction while holding the remaining \textbf{piece} in her fingers.
The girl then \textbf{takes} a bite from a \textbf{piece} of cake and smiles with satisfaction, looking forward as she chews.
The blond boy follows, holding a \textbf{frosted} \textbf{piece} in both hands near his mouth ; he bites in enthusiastically, his eyes partly closing as he enjoys it, and frosting is visible around his mouth as he lowers the treat.
The commercial ends on a product display against a plain warm background.
The white Easy-Bake Mini-Wave Oven is centered, with its dark door, orange keypad, and dial visible.
Arranged neatly in front are accessories : a long orange pusher tool, two small round metal pans, several flat \textbf{packets} that appear to be mixes, and a folded paper leaflet or instruction sheet.
Large orange text across the bottom reads : “ Betty Crocker Easy-Bake MINI-WAVE OVEN. ”

% matched lemmas: accept, bang, copyright, frosted, packet, piece, plate, remove, spoon, tabletop, take, taste, utensil
\end{textsample}
