\begin{textsample}{POS Dim 6 – 2010 – Score 14.00 – 2010/tv\_com\_2010\_29.txt}  \label{ex:f6_pos_021}
The commercial unfolds as a rapid visual montage centered on toilets in many different \textbf{bathroom} settings, followed by product-pack shots on a black background.
At the beginning, a white toilet is shown front-on in a decorated \textbf{bathroom} with floral wallpaper, a plant, a bathtub edge, a wastebasket, and a toilet paper holder.
The view then cuts to a mint-green toilet in a tiled \textbf{bathroom}, with a visible Clorox-branded bottle on the \textbf{floor} beside it.
Another cut shows a white toilet in a yellow-tiled \textbf{bathroom} with a fuzzy blue seat cover, children ’s bath items, \textbf{towels}, toys, and a small stool.
The montage continues with a glossy black toilet in a minimalist, polished \textbf{bathroom} with a matching black \textbf{sink} reflected in a mirror.
Next, a retro-looking \textbf{bathroom} appears with orange patterned wallpaper and shag carpeting ; only the lower body of a person is visible, standing on or over a \textbf{beige} toilet while \textbf{reaching} toward one \textbf{foot}.
The scene then cuts to a dark red toilet in a narrow \textbf{bathroom}, with a plant, matching red wastebasket, and a Clorox-branded bottle on the \textbf{floor}.
A series of more varied toilet environments follows.
A white toilet is shown against a wood-paneled wall in a modern, concrete-looking \textbf{bathroom}, with toilet paper and a Clorox-branded bottle nearby.
This is followed by a white urinal mounted on green tiled walls.
The commercial then cuts outdoors to a rustic wooden outhouse surrounded by greenery, with a crescent-moon cutout in the door and a wheelbarrow nearby.
Another cut shows a small institutional-looking toilet in a \textbf{tight} space with a chain-link fence on one side and a wall-mounted flushing mechanism.
The next shots return to domestic \textbf{bathrooms} : a compact white toilet in a narrow room with a \textbf{sink} in the foreground, slippers and a wastebasket on the \textbf{floor} ; then another white toilet with a dark wooden seat, a Clorox-branded bottle, and a detached or open toilet seat/lid lying on the \textbf{floor} nearby.
A metallic wall-mounted fixture appears in a stall-like space with dark blue tiled walls.
Then a white toilet with a black seat is shown beside a pedestal \textbf{sink} and a stack of toilet paper rolls.
The montage becomes increasingly eclectic.
A toilet is placed between stacks of books in a narrow room, with a plant, clock, plunger, and small \textbf{rug}.
Another toilet has a gold-colored seat and lid in a \textbf{bathroom} with marbled or heavily patterned walls.
A pink-accented toilet appears in a wood-paneled room ; a Dalmatian dog is visible in the foreground on the right, looking toward the camera area.
The commercial then briefly shows cleaning actions.
In one \textbf{bathroom}, a person wearing blue \textbf{gloves} \textbf{wipes} a small white toilet ; \textbf{cleaning} \textbf{supplies}, including a Clorox-branded bottle and other items, are visible on the \textbf{floor}.
Another \textbf{bathroom} shows a wall-mounted toilet with patterned wallpaper, a plunger, and a Clorox-branded bottle nearby.
A blue toilet appears in a tiled \textbf{bathroom} beside a blue bathtub and shower enclosure.
A person ’s lower body is then shown in a white-tiled \textbf{bathroom} ; the person pours liquid from a blue Clorox-branded bottle into a white toilet bowl.
The next frame shows a \textbf{clean} white toilet in a tidy \textbf{bathroom} with a shower, black-and-white \textbf{floor} tiles, folded \textbf{towels} on shelving, and a plunger.
More toilet variations follow : a \textbf{beige} or pale pink toilet against teal and black tiles ; then a white toilet with a gold-colored open seat in a wood-paneled \textbf{bathroom} with a bathtub nearby.
Near the end, the montage cuts to a product display on a black background.
A large white Clorox \textbf{bleach} jug is centered, flanked by Clorox product packaging, including a green box on the left and a blue “ ToiletWand ” box on the right.
In the final frame, the product arrangement changes : a blue Clorox bottle with a red angled cap is prominent in front, with other Clorox products behind it.
White text reads “ still shining since 1913, ” and small text at the bottom includes “ ODE TO THE COMMODE.COM. ”

% matched lemmas: bathroom, beige, bleach, clean, floor, foot, glove, reach, rug, sink, supply, tight, towel, wipe
\end{textsample}
