\begin{textsample}{POS Dim 6 – 1950 – Score 15.00 – 1950/tv\_com\_1950\_10.txt}  \label{ex:f6_pos_007}
In black and white, the scene opens at a drugstore soda fountain.
A middle-aged woman with dark, curled, chin-length hair stands behind the \textbf{counter} in a light blouse, cardigan, and apron.
She is working at shiny soda taps set against a speckled tile wall.
A female customer in a dark \textbf{coat} is seen from behind at the left edge, holding something near her face while waiting.
The woman behind the \textbf{counter} holds a glass under the tap, but her face is tense and weary ; she shuts her eyes and grimaces as if uncomfortable.
She continues \textbf{trying} to fill the glass, then draws it away from the tap and turns toward the \textbf{counter}.
The soda fountain area widens into view.
Shelves behind the \textbf{counter} are lined with bottles, boxes, and drugstore goods.
An older male clerk or druggist, wearing glasses, a white shirt, dark bow tie, and dark trousers, works in the background.
At the \textbf{counter} sits a male customer in a suit and dark hat.
The woman behind the \textbf{counter} reaches across and sets a tall dark \textbf{drink} in front of him, near a \textbf{saucer} and other \textbf{counter} items.
Her movements look distracted and strained.
After \textbf{serving} him, she bends down behind the \textbf{counter} and searches near her apron or a lower shelf, then brings out a small bottle.
She opens it and shakes tablets into her hand while the customer in the hat lifts his \textbf{drink}.
The focus shifts closer to the woman behind the \textbf{counter}.
Her face fills more of the scene, with shelves of \textbf{packaged} goods behind her and the older clerk moving nearby.
She looks tired and serious, speaking while glancing down.
The older clerk steps closer, holding a small bottle.
The woman opens her palm, revealing two small round white tablets.
The clerk raises his own open hand above hers, showing two larger, capsule-shaped white tablets.
The two kinds of medicine are compared directly : the woman ’s round tablets rest in the lower palm, while the oblong Vanquish tablets are displayed above.
The word “ VANQUISH ” appears in bold white capital letters above the capsule-shaped tablets, making the product name clear.
Back at the \textbf{counter}, the older clerk stands beside the woman as she looks down at her hand and the medicine.
A small bottle sits upright on the \textbf{counter} near them.
She studies the tablets closely, then reaches for a pair of dark-framed glasses and puts them on, as if to read a label or examine the product more carefully.
The clerk turns away to the shelves behind the \textbf{counter} and begins searching among stacked boxes and \textbf{packages}.
The woman, now wearing the glasses, holds the small container and looks at it with concentration.
Around her, the drugstore shelves are crowded with bottles, \textbf{cartons}, and paper goods, and a large register or display unit sits on the \textbf{counter}.
A man in a hat passes close in the foreground, briefly blocking part of the view, while the woman continues examining the medicine.
The older clerk reaches up to a shelf and retrieves an item.
Another male customer appears at the left side of the \textbf{counter}.
The woman stands near a small \textbf{tabletop} display and keeps the product in her hands, reading or inspecting it.
The older clerk returns toward the \textbf{counter}, and the two face each other.
He brings out a rectangular \textbf{package} or folded paper item and hands it toward her.
She holds it open in her palm and looks down, reading, while he watches attentively and gestures slightly, as if explaining.
The woman ’s posture is more focused than pained now ; she seems to be considering what he is showing her.
The setting shifts back to the soda fountain \textbf{counter}.
The older clerk leans over a notepad or order pad on the \textbf{counter}, \textbf{writing} with a pencil.
The woman stands beside him, now looking more relaxed and alert.
She holds a tall ice cream soda or sundae glass piled with a foamy topping and a \textbf{spoon} \textbf{sticking} out.
She sets the glass on the \textbf{counter} in front of him, near the notepad.
The clerk looks toward her as she slides the treat into place.
She smiles faintly and gestures toward the work area behind the \textbf{counter}, where another worker in an apron is busy near the soda equipment.
The woman then turns away from the clerk and \textbf{resumes} her duties behind the \textbf{counter}.
The older clerk, left at the \textbf{counter} with the sundae, shifts closer to it.
He smiles, steadies the glass with one hand, and \textbf{picks} up the \textbf{spoon}.
A woman customer with long light hair sits or stands nearby on the right, facing the \textbf{counter}.
In the background, the first woman continues working at the soda fountain, and another employee prepares items farther back.
The clerk bends over the sundae and \textbf{takes} a \textbf{spoonful}, appearing pleased.
The medicine comparison returns in an enlarged view : two round tablets in one open palm, then two oblong capsule-shaped tablets in another palm above them.
The capsule-shaped tablets are again visually contrasted with the round ones.
The image transitions into a product display : a box labeled “ VANQUISH ” sits on a dark surface beside a small open bottle with a light-colored cap and two oblong tablets lying in front.
The final display adds large white text above the product : “ Relief so long lasting, most headaches don't come back. ” The Vanquish box, bottle, and two tablets remain arranged below the slogan.

% matched lemmas: carton, coat, counter, drink, package, pick, resume, saucer, serve, spoon, spoonful, stick, tabletop, take, try, write
\end{textsample}
