\begin{textsample}{POS Dim 6 – 2020 – Score 7.00 – 2020/tv\_com\_2020\_22.txt}  \label{ex:f6_pos_067}
A small glass object filled with dark red liquid tumbles onto a light wood floor at the edge of a pale, textured rug.
It hits hard and bursts open, sending red liquid and clear fragments outward in a jagged splash.
The stain spreads across the wood and up to the rug ’s border, with wet red splatters radiating in all directions.
Another mess follows at a dining area : a teal bowl or \textbf{plate} loaded with spaghetti and sauce tips off the seat of a light gray upholstered chair beside a round white table.
Noodles slide down the chair cushion and leg, leaving orange-red sauce smears on the fabric and dropping in tangled piles onto the wood floor.
In a bright living room with large windows, a rust-colored sofa, and a pale area rug, an adult woman-presenting person enters carrying the Shark EveryMess machine by its handle.
Only her lower body and hands are mostly visible : she wears dark blue jeans, white slip-on shoes, a pale pink top, and bracelets and rings.
The appliance is boxy and portable, with a bright green body, dark teal top and handle, black base, black hose, and a Shark label on the front.
Large white on-screen text appears beside it : “ Shark EVERY MESS, ” with smaller \textbf{wording} underneath identifying “ Wet Vac + Dry Vac + Stain System. ” A small “ Shark EVERYMESS ” mark also appears in the upper right.
She sets the machine on the pale rug near the red spill.
Beside it are attachments : a black floor nozzle, a clear triangular stain-removal head, and a white spray bottle with a red trigger and a blue-and-red liquid label.
The mess sits partly on the wood floor and partly on the rug : brownish-red liquid on the wood and a red stain on the rug.
White text across the scene reads, “ THE ONLY PORTABLE 3-IN-1 TOOL, ” with “ ONLY ” underlined in green.
She reaches toward the red-stained area, preparing the tools.
The dry vacuum feature is shown first.
A black cylindrical hose nozzle with a blue rim hovers over the wood floor, where red liquid and clear broken \textbf{pieces} are scattered at the rug ’s edge.
Large white text reads “ DRY VAC. ” The nozzle passes over small glass fragments and debris, drawing them up.
Tiny fine print at the bottom warns to follow Shark ’s instructions for glass pickup.
The wet vacuum feature follows : a wide black floor tool marked “ Shark ” is pressed flat against the wet wood floor.
The words “ WET VAC ” appear above it as the tool moves over the puddle, leaving the wood visibly clearer and drier behind it.
For stain removal, a clear triangular cleaning head labeled “ Shark StainForce ” is pressed into a red-stained patch on the pale rug.
The tool ’s transparent face shows moisture and red-tinted liquid being pulled upward inside.
Large white text reads “ \textbf{REMOVE} TOUGH STAINS, ” and a small badge at the lower left says “ POWERED BY STAINFORCE. ” The cleaner moves over the stained carpet, reducing the red coloration.
The commercial then shows the tool handling a different kitchen-style mess on a countertop : white powder, colorful sprinkles, a cracked egg yolk, and clear liquid are spread across the surface.
A hand guides the black hose nozzle through the mixture.
A glass bowl full of rainbow sprinkles, a whisk, and other baking items sit in the background.
White text reads “ EVERY TYPE OF CLEANUP. ” The nozzle sucks up powder and wet egg, leaving a cleaner path through the messy surface.
A close view shows the white StainForce spray bottle in a hand.
The bottle has a red trigger and nozzle, a black band near the top, and a label split into magenta and blue sections.
The label reads “ Shark STAINFORCE ” and shows two formulas, including “ Deep Clean Max ” on the magenta side and “ Oxy Multiplier Max ” on the blue side, with “ 30X MORE ” near the bottom.
The hand squeezes the trigger, and a fine pink-tinted mist sprays outward.
A small graphic at the lower left reads “ STAINFORCE TECHNOLOGY. ” The spray is then shown over the pale rug near the Shark machine, aimed at a remaining pink-red stain.
Large white text appears : “ 30X MORE STAIN-FIGHTING POWER, ” with fine print underneath comparing it to another Shark formula.
The stain-removal head is also demonstrated on a black car seat or dark upholstery outdoors or near greenery.
The clear triangular head presses onto a damp, speckled section of the seat.
On-screen text reads “ 2X MORE STAIN-GRABBING SUCTION, ” with a “ Powered by StainForce ” badge and fine print along the bottom.
As the tool moves, the treated area looks less wet and more uniform.
A split-screen view shows two messes being cleaned at once.
On the left, the black hose nozzle sucks up spaghetti noodles and orange sauce from upholstery.
The noodles disappear into the nozzle, leaving a smeared but reduced mess.
On the right, the clear stain tool is pushed across a gray upholstered chair seat with orange sauce marks, lifting a cleaner rectangular path through the stains.
The orange marks fade where the tool passes.
The dirty collection container inside the Shark machine is shown from above, filled with sucked-up spaghetti, sauce, and cloudy liquid.
Hands lift the container out of the green machine.
The mess inside is visible through the translucent plastic, with noodles gathered at the bottom and sauce streaks on the sides.
For cleaning the tool afterward, the Shark EveryMess sits on a white countertop beside a clear glass of water.
The woman holds the black hose nozzle over the glass, then dips it into the water.
A graphic at the lower left reads “ RINSE \& READY TECHNOLOGY. ” She swirls or runs the nozzle in the water while the hose remains attached to the machine.
The view shifts to the side of the green machine, where the translucent tank shows cloudy water moving inside.
Large white text across the machine reads “ SELF-CLEANS IN SECONDS, ” reinforcing the rinse-cleaning step.
Near the end, the black Shark floor nozzle glides across a glossy white floor, \textbf{picking} up small dark \textbf{crumbs} or dirt.
Another scene shows the cylindrical dry nozzle pressed into a \textbf{mound} of soil, mulch, and small leaves.
The nozzle draws the loose dirt inward, creating a \textbf{shallow} cleared trench in the pile.
The clear StainForce head returns on the pale rug, moving forward between the woman ’s knees as she kneels behind it.
The rug ahead is clean and light-colored ; the tool ’s transparent chamber shows moisture and foam being pulled through as it passes.
The bottle of StainForce cleaner stands upright nearby.
The final product display shows the Shark EveryMess and its accessories arranged on a clean white \textbf{counter} in a bright modern home with large windows and wood ceiling beams.
The green-and-teal main unit sits centered with its black hose coiled along the base.
To one side are smaller attachments, including a black Shark floor tool and the clear triangular StainForce head ; to the other side is the white-and-red StainForce spray bottle with its red-and-blue label.
Large white text on the left reads “ Shark EVERY MESS, ” with smaller text beneath : “ Wet Vac + Dry Vac + Stain System. ” Fine print along the bottom says, “ Colors \& accessories may vary. ”

% matched lemmas: counter, crumb, mound, pick, piece, plate, remove, shallow, wording
\end{textsample}
