\begin{textsample}{POS Dim 6 – 1960 – Score 13.00 – 1960/tv\_com\_1960\_22.txt}  \label{ex:f6_pos_028}
The commercial is in black and white and \textbf{takes} place in a busy supermarket.
Shelves packed with cans and \textbf{packaged} goods fill the background, and shoppers move behind the main action.
At a \textbf{counter} in the foreground stands a slim, clean-cut man in a dark suit, white shirt, tie, and thick dark-rimmed glasses.
Beside him is a woman shopper with dark, bouffant-styled hair, wearing a light-colored \textbf{coat} or blouse with a wide \textbf{collar}.
A \textbf{pitcher} and several small \textbf{drinking} glasses sit on the \textbf{counter}, along with small cans.
A young boy briefly turns toward the camera laughing and then moves out of the way, while the man and woman smile as if beginning a demonstration.
The woman gives a cheerful wave, and the man turns his attention to the \textbf{counter} and the product.
A closer view shows the man holding up a small cylindrical can in one hand.
The label is \textbf{readable} as “ Awake, ” with “ New! ” and a Birdseye-style brand mark above it.
The label describes it as a frozen concentrate for an orange-flavored breakfast \textbf{drink}, and a tall glass of the \textbf{drink} is \textbf{pictured} on the right side of the can.
The man presents the can squarely, with the label facing outward.
Back at the \textbf{counter}, he keeps the can visible while the woman stands ready with two small glasses in front of her.
He gestures toward the glasses and \textbf{pitcher}, then offers or indicates the first glass.
The woman lifts the glass to her mouth and \textbf{takes} a sip, looking thoughtful as she \textbf{tastes} it.
She lowers the glass and looks toward the man.
The man then reaches toward the \textbf{counter} and indicates another glass.
The woman holds one \textbf{drink} in one hand and \textbf{takes} the second glass in the other, comparing them.
She brings the new glass to her lips and sips.
Her expression remains \textbf{measured} and slightly amused rather than surprised.
A closer view of her face shows her looking down, then sideways toward the man as if giving her judgment.
The man, shown in close-up, smiles broadly through his dark glasses and reacts with exaggerated enthusiasm, raising his eyebrows and opening his mouth as he speaks.
The product is then shown again on the \textbf{counter} in a product display.
The Awake can stands upright on the right, label facing forward.
A hand places a small cube-shaped block beside it, printed with “ MORE C. ” More blocks are stacked on top, forming a vertical column labeled “ MORE C, ” “ MORE B1, ” and “ MORE A, ” visually representing added vitamins.
The can remains beside the stack as the comparison is made.
The scene returns to the man and woman at the supermarket \textbf{counter}, where the woman continues holding and sipping from the small glasses, still appearing unconvinced that the flavor differs.
Another product comparison follows.
The Awake can is placed on the left, and two taller narrow cans are set beside it.
The two comparison cans are labeled “ 6 oz.
Frozen Concentrated Orange Juice. ” Hands align the cans so the labels face outward : Awake on the left, two orange juice concentrate cans on the right.
The arrangement visually suggests that one can of Awake is being compared with two six-ounce cans of frozen concentrated orange juice.
Immediately after, a close-up shows fingers stacking coins into a small pile on a flat surface, reinforcing the cost comparison.
The woman is shown again in close-up, speaking while looking slightly downward and then to the side.
Her expression is honest and mildly playful ; she tilts her head and rolls her eyes upward briefly, as if conceding a point but not changing her view of the flavor.
The man appears in close-up next, smirking with raised brows, then breaking into a wide grin.
His eyes widen behind his glasses as he responds animatedly.
He then appears from the chest up in front of the supermarket shelves, holding the Awake can near his shoulder with the label facing forward.
He points to the can and gestures with his other hand, counting or emphasizing points with his fingers while keeping the product visible.
As he continues presenting the can, the woman steps in close from the side.
She reaches up to his tie and \textbf{collar} area and \textbf{straightens} or adjusts his tie while looking at him with a small smile.
He tilts his head toward her, smiling back, and lets her fix it.
Their interaction is light and familiar, with the man still holding the product and the woman ’s attention shifting from the \textbf{tasting} to him.
The final image shows a clean product end card : on the left is a square “ GF ” logo with the words “ GENERAL FOODS KITCHENS ” beneath it, and on the right a hand holds the Awake can close to the viewer.
The can label again prominently reads “ Awake, ” with the \textbf{pictured} glass of orange \textbf{drink} on the label.

% matched lemmas: coat, collar, counter, drink, drinking, measure, package, picture, pitcher, readable, straighten, take, taste
\end{textsample}
