\begin{textsample}{POS Dim 6 – 2020 – Score 7.00 – 2020/tv\_com\_2020\_21.txt}  \label{ex:f6_pos_069}
The commercial opens in a bright, stainless-steel commercial kitchen or food-prep area.
A Black woman, apparently an adult chef or kitchen worker, is shown from the chest up.
She wears a white chef ’s \textbf{coat} and a royal-blue bandana with a white paisley pattern over long dark hair.
Shelves behind her hold food containers, jars, produce, and kitchen supplies.
She looks downward, as if reading something on a \textbf{counter} in front of her, then speaks while keeping a serious, evaluating expression.
Across from her is the Mr.
Clean character : a bald, muscular, light-skinned man with thick white eyebrows, a fitted white T-shirt, and long yellow rubber gloves.
He stands confidently in the same kitchen setting, arms crossed over his chest, smiling slightly as if in a job interview.
Behind him are metal storage racks filled with tubs, containers, and cleaning or kitchen supplies.
The visuals shift to a product demonstration on a dirty grey floor, split vertically into two side-by-side panels.
On the left, a string mop labeled “ Leading Competitor ” moves across a grimy surface.
On the right, another mop is associated with the red, white, and blue “ Mr.
Clean Professional ” logo and bold blue text reading “ \textbf{REMOVES} GRIME IN HALF THE TIME. ” As the mops move, the left side leaves behind a darker, streaky, still-dirty path, while the right side clears a much brighter, white strip of floor.
The comparison continues as both yellow mop heads are pushed along : the competitor side remains grey and heavily streaked, while the Mr.
Clean Professional side shows a clean white lane widening behind the mop.
Small fine print appears beneath the claim, but it is too small to read clearly.
Back in the kitchen, the floor is now glossy and bright white.
Mr.
Clean stands to the left beside a yellow mop bucket and wringer, holding a mop upright with its head resting on the floor.
The chef in the blue bandana stands nearby with her hands on her hips.
Two other kitchen staff stand to her right : a young adult man in a white shirt, dark apron, and backward cap holding a large metal bowl filled with red \textbf{tomatoes}, and a woman in a white shirt with a black tie and black pants holding a tray.
Stainless ovens, pans, shelves, and prep equipment fill the background, reinforcing the professional kitchen setting.
The chef and the two staff members look toward the cleaned floor or toward Mr.
Clean with \textbf{surprised}, \textbf{impressed} expressions.
The chef ’s mouth is open slightly, her hands still planted at her hips.
The young man holds the bowl of \textbf{tomatoes} at waist height, looking down or forward with a reserved expression, while the woman beside him watches with a small, approving smile.
Mr.
Clean is then shown again in front of hanging \textbf{pots} and pans.
He smiles with a calm, confident expression, his posture relaxed, as if \textbf{accepting} the decision made by the kitchen team.
The commercial ends on a blue gradient background with large branding text.
First, the words “ IT ’S NOT JUST CLEAN, IT ’S ” appear in white above the large red-and-white “ Mr.
Clean ” logo and the blue word “ PROFESSIONAL. ” A large green jug of Mr.
Clean Professional appears on the right.
Its label shows the Mr.
Clean character and reads “ Mr.
Clean Professional, ” with additional visible text identifying it as “ DEGREASING FLOOR CLEANER ” and “ COMMERCIAL GRADE. ”

% matched lemmas: accept, coat, counter, impressed, pot, remove, surprised, tomato
\end{textsample}
