\begin{textsample}{POS Dim 6 – 2010 – Score 8.00 – 2010/tv\_com\_2010\_104.txt}  \label{ex:f6_pos_026}
The commercial takes place in a \textbf{clean}, light-colored \textbf{bathroom} with pale blue walls and white fixtures. 1. **Opening \textbf{bathroom} view** : The first frame shows a white toilet in the foreground, with three small blue dome-shaped objects sitting on the toilet \textbf{tank} lid.
They resemble cartoon-like cleaning characters or caps.
In the background, slightly out of focus, a man stands in a doorway or near a \textbf{bathroom} entrance, \textbf{reaching} toward a wall or light switch.
The \textbf{bathroom} contains a \textbf{towel} and storage items on the right side.
An “ iSpot.tv ” watermark appears in the lower left. 2. **Close-up of blue characters on the toilet tank** : The next shot moves closer to the toilet \textbf{tank} lid.
Three small blue animated-looking characters are visible, each with eyes and facial expressions.
They sit on small white scrub-brush-like bases.
Their faces are turned in different directions, giving them a lively, personified appearance. 3. **Demonstration inside the toilet bowl** : A hand holds a blue toilet-cleaning gel applicator over the inside rim of a white toilet bowl.
A pale blue gel or applicator \textbf{pad} is \textbf{pressed} near the bowl surface.
The shot focuses on the hand, the blue tube-like product, and the toilet bowl.
Small text near the bottom left reads “ dramatization, ” indicating the action is being represented visually rather than necessarily shown literally. 4. **Dark transition** : The fourth sampled frame is mostly black or very dark, likely a transition between scenes.
No clear product action or setting is visible beyond the persistent “ iSpot.tv ” watermark. 5. **Product pack shot with on-screen text** : The scene cuts to a product display on a \textbf{bathroom} \textbf{sink} or counter.
A green box labeled **“Scrubbing Bubbles Toilet \textbf{Cleaning} Gel”** stands upright in front of a blue applicator lying horizontally.
Large white uppercase text appears at the upper left : **“WE WORK HARD SO YOU DO N’T HAVE TO.”** In the background, a white toilet with the lid or seat raised is visible.
A small Facebook icon and a web address appear near the bottom right, though the exact URL is small. 6. **Final product shot with character** : The final frame keeps the same product display and slogan.
A blue Scrubbing Bubbles character appears partly behind or above the green product box, adding a personified brand element to the pack shot.
The blue applicator remains on the counter to the left, and the \textbf{bathroom} setting stays visible in the background.

% matched lemmas: bathroom, clean, pad, press, reach, sink, tank, towel
\end{textsample}
