\begin{textsample}{POS Dim 6 – 2000 – Score 7.00 – 2000/tv\_com\_2000\_16.txt}  \label{ex:f6_pos_059}
A tub of Smart Balance Buttery Spread sits alone on a rugged, tan, rock-like surface, centered against a vivid studio background that fades from pink near the horizon to bright blue above.
The product is small at first, perched on the highest slab like a display pedestal.
As the view moves closer, the yellow tub with a white lid fills more of the scene.
The large black words “ SMART BALANCE ” become clearer on the front label, with red and green bands above it.
The upper label includes health-related text, including “ Patented blend to help improve cholesterol ratio, ” and a red band that refers to no trans fatty acids and no hydrogenated oil.
The product image gives way to a simple medical-style bar chart over a muted, textured background.
A vertical scale on the left is marked 50, 100, 150, and 200.
Three bars are labeled along the bottom : “ Total Cholesterol, ” “ LDL ‘ Bad, ’ ” and “ HDL ‘ Good. ’ ” The total cholesterol bar is tallest, near 200 ; the LDL bar is lower, around the middle ; and the HDL bar is shorter, around 100.
Small fine print runs along the bottom explaining that total cholesterol is composed of HDL and LDL, with a small additional amount of VLDL.
The chart fades into food imagery.
A square white bowl of bright green cut beans sits on a pale gray surface.
Small reddish flecks are scattered among the beans.
A soft yellow dollop of buttery spread appears on top of the beans, resting near the center and standing out against the green.
The scene changes to a warm, brown \textbf{serving} bowl filled with a chunky orange-brown baked \textbf{dish} or casserole.
A pale yellow dollop of spread sits on top.
From the right, a hand uses a metal \textbf{serving} \textbf{spoon} to lift a portion from the bowl.
The \textbf{spoon} carries the \textbf{serving} across to a yellow \textbf{plate} on the right, where a lemon slice and a small green garnish are already arranged.
The portion lands on the \textbf{plate} with some of the spread visible on top, suggesting it is being \textbf{served} as part of the \textbf{dish}.
Next is a plated meal : a white \textbf{plate} holds a large pale fish fillet sprinkled with herbs, a \textbf{mound} of light-colored rice or grain, a lemon wedge, and broccoli florets.
A small dollop of the spread sits on top of the broccoli.
A green parsley-like garnish lies near the front edge of the fish.
The background remains clean and blue, giving the food a bright, appetizing look.
The imagery shifts to a close view of a \textbf{piece} of salmon on a grill.
Metal tongs hold and turn the glossy orange fish over dark grill bars.
The salmon has browned grill marks and a shiny surface, with steam or heat haze rising around it.
The tongs release it as it settles onto the grill.
The final food scene shows a breakfast-style \textbf{plate} on a striped tablecloth.
In the center are thick \textbf{pieces} of toast or pancakes with melting pale-yellow spread on top, surrounded by red berries.
To the left is a small glass bowl full of strawberries, and to the right is a yellow mug with a dark rim.
The background is a smooth blue, and the food is arranged like a complete breakfast setting.
At the end, the Smart Balance products return on the rocky display surface against the pink-and-blue backdrop.
Multiple \textbf{packages} are grouped together : a large upright tub in back with the “ SMART BALANCE ” label, and smaller Smart Balance \textbf{packages} in front, including a rectangular \textbf{carton} and another yellow tub.
The arrangement presents the brand family prominently, with the labels facing forward.

% matched lemmas: carton, dish, mound, package, piece, plate, serve, spoon
\end{textsample}
