\begin{textsample}{POS Dim 6 – 2020 – Score 5.00 – 2020/tv\_com\_2020\_102.txt}  \label{ex:f6_pos_017}
The commercial opens on a bright blue sky with scattered white clouds.
A white scripted “ febreze ” logo appears centered against the sky.
The logo then enlarges rapidly, filling the frame so that only oversized parts of the letters are visible.
As the large white lettering moves across the screen, it transitions to a sunny exterior scene.
An adult woman with curly hair is walking through a tidy front garden toward a white front door.
The house façade has windows, climbing greenery, potted plants, and flowers.
She carries a bag over one shoulder and approaches the entrance.
The scene cuts inside the home.
The woman is now standing just inside the front door, wearing a light blue shirt and holding a dark jacket and a brown bag.
Around the room, several pale green, \textbf{cloudy} animated odor-like forms are visible.
One appears near a plant or pet area, another near the ceiling with a shoe-like object inside it, and others hover around the entryway.
The woman looks upward toward one of these green clouds.
The commercial then shifts to a product pack shot.
A Febreze Plug package is shown on the left, containing a white plug-in device and a small bottle labeled “ Linen \& Sky. ” The Febreze logo appears large on the right.
The packaging includes a yellow label at the top reading “ FADE DEFY PLUG ” and the device itself is labeled “ PLUG. ” Next, a \textbf{clean} demonstration graphic appears.
A white plug-in air freshener is shown in a wall outlet, with a pale blue scent stream curving away from it.
To the right, a circular arrow icon surrounds a large “ 2, ” with the text “ COMPLEMENTARY SCENTS. ” The scene returns to the interior hallway/living area.
Multiple green odor clouds are still visible around the room, including near the door, \textbf{floor}, furniture, and hanging items.
Blue animated scent ribbons sweep through the space from the plug-in area, visually \textbf{crossing} the room and passing through or around the green clouds.
A close-up of the woman follows.
She looks upward with a calm, pleased expression while translucent blue scent bands move across the foreground.
Beside her is a blue circular graphic reading “ UP TO 2 DAYS, ” with arrows forming a loop around the number.
The next shot shows a wider living room.
A child sits on the \textbf{floor} with a large dog in front of a sofa, while the woman sits on the sofa behind them.
The room has plants, a window with curtains, cushions, a coffee table, and soft lighting.
Blue scent-like bands continue to move horizontally across the room, suggesting freshened air.
The commercial ends with a product \textbf{lineup} on a blue sky-and-cloud background.
Several Febreze Plug packages are displayed, with the main package in front showing the white plug-in unit and “ Linen \& Sky ” refill.
Large white text on the right reads “ febreze PLUG, ” and a small circular P\&G logo appears in the upper-right corner.

% matched lemmas: clean, cloudy, cross, floor, lineup
\end{textsample}
