\begin{textsample}{POS Dim 6 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_116.txt}  \label{ex:f6_pos_072}
A woman sits comfortably on a light-colored sofa in a warm living room, facing forward as if speaking directly to the viewer.
She appears to be a young adult with long dark curly hair, wearing a loose red button-up shirt over a light top and beige pants.
An orange-red patterned throw blanket is draped over the sofa beside her, and a lamp, flowers, and home décor sit softly out of focus behind her.
She smiles and gestures with her hands while talking.
The scene shifts to a bright white kitchen.
A man, also a young adult, with short brown hair and a light blue button-down shirt over a white T-shirt, stands near the stove and \textbf{counter}.
He gathers up a large, awkward pile of dirty \textbf{dishes} and \textbf{cookware}, clutching bowls, \textbf{plates}, and \textbf{pots} against his chest.
The stack looks unstable, and he leans forward carefully as he carries it through the kitchen.
He sets the \textbf{dishes} down near the sink and dishwasher, sliding items from his arms onto the \textbf{counter} and into the work area.
Back on the sofa, the woman continues speaking, now with a more matter-of-fact expression.
In the kitchen, the man holds a dirty patterned \textbf{plate} in one hand and a \textbf{spoon} in the other.
He scrapes at the \textbf{plate}, bringing the \textbf{spoon} toward his mouth as if \textbf{removing} bits of leftover food before washing.
He examines the \textbf{plate}, then continues scraping and nibbling from it in an exaggerated, comic way.
The woman is shown in a closer view, her red shirt filling much of the image.
Her hands move in front of her chest, palms and fingers opening and closing as she emphasizes her point.
Her face comes fully into view again, calm and confident, as she finishes the thought with a small smile.
The man kneels at an open dishwasher in the white kitchen.
The lower rack is pulled out and is packed with dirty \textbf{pots}, pans, \textbf{plates}, glasses, \textbf{utensils}, and reddish food residue.
He places more \textbf{cookware} into the rack, \textbf{trying} to fit large items among the already crowded \textbf{dishes}.
From above, the dishwasher looks heavily loaded, with a \textbf{pot}, glassware, a red item, and \textbf{utensils} squeezed together.
He pushes and adjusts \textbf{pieces} with both hands.
Then he reaches for a green Cascade box and tips it over the detergent \textbf{cup} on the inside of the dishwasher door, pouring in the product.
The commercial moves into a demonstration against a vivid blue background.
A clear glass \textbf{plate} appears divided down the center by a vertical black line.
It is covered with orange-red food soil, and water begins surging across both sides.
White splashes and streams rush over the \textbf{plate}.
As the water continues, the two halves are compared side by side.
On-screen labels appear : “ LEADING BRANDS ” over the left side and “ CASCADE ” over the right.
The left side remains visibly dotted with spots and residue, while the right side becomes clearer and cleaner.
The Cascade side is shown looking nearly spotless, and the clean \textbf{plate} half slides away to the right, leaving the spotted comparison side behind.
Back in the kitchen, the man holds up a sparkling clear glass \textbf{plate} and points to its surface, presenting it proudly.
The woman steps in behind him, smiling, with her hands resting on his shoulders.
He faces forward with a satisfied, slightly pleased expression while she leans close, grinning warmly.
He turns toward her as she nuzzles or kisses near his cheek, and the clean glass \textbf{plate} remains held up beside them, catching the light.
The final image is a product display on a kitchen \textbf{counter} : a yellow Cascade bottle stands next to a green Cascade box.
Large white text appears to the right : “ So Clean, It ’s Virtually Spotless. ”

% matched lemmas: cookware, counter, cup, dish, piece, plate, pot, remove, spoon, try, utensil
\end{textsample}
