\begin{textsample}{POS Dim 6 – 2010 – Score 7.00 – 2010/tv\_com\_2010\_2.txt}  \label{ex:f6_pos_086}
A hand slides a pale, scalloped glass \textbf{plate} onto a dark \textbf{tabletop} near a softly lit window.
The \textbf{plate} is filled with small, foil-wrapped chocolates in Valentine colours : bright pink, red, and white.
The hand, with dark nail polish, gently adjusts the candies and then lifts one pink-wrapped \textbf{piece} from the edge of the \textbf{plate}.
Warm daylight streams across the face of a young adult woman with long, dark brown hair.
Her face is partly hidden at first by a hazy veil of steam or bright window glare, then becomes clearer as she looks downward with a small, pleased smile.
She appears relaxed and thoughtful, in a softly lit café-like setting.
At a patterned café table, the woman opens a glossy burgundy clutch purse.
Beside it sits a \textbf{cup} of coffee topped with pale foam.
She reaches into the purse and pulls out small pink foil-wrapped Dove chocolates.
She places several of them onto a small tray already holding coins, positioning the chocolates among the change as though leaving an extra treat along with payment or a tip.
The rich pink wrappers stand out against the metal coins and the decorative \textbf{tabletop}.
The setting widens to reveal a café \textbf{counter}.
A young adult barista with short curly hair, wearing a light shirt over a darker long-sleeved top, works at an espresso machine.
A chalkboard menu behind the \textbf{counter} lists \textbf{drinks} such as café latte, mocha, Americano, and tea.
The dark-haired woman is visible in the background, seated or standing nearby, while the barista appears focused on preparing coffee.
Outside on a residential street, a pink mailbox stands in the foreground with a simple hand-drawn heart on its side.
In the background, the same dark-haired woman approaches along the sidewalk, wearing a brown \textbf{coat} and carrying something small in one hand.
The mailbox door is open, revealing a red interior.
Inside, she places a Valentine-style card or small envelope decorated with a pale ribbon design and a shiny red heart-shaped candy or sticker attached near the bottom.
Her gloved or coat-sleeved hand slides the item neatly into the mailbox, leaving it visible inside.
Back indoors by bright curtains, the woman holds up a silver Dove chocolate wrapper close to her face.
The wrapper has a white heart shape printed on it with the words “ Be my valentine. ” and the Dove logo beneath.
She looks toward it and then toward the viewer with a playful, satisfied smile, presenting the wrapper like a small Valentine message.
She then reclines in a cream-coloured chair near sheer curtains glowing with sunlight.
She wears a pink top and light grey pants, with a bracelet or watch on her wrist.
A red Valentine card or envelope rests in her lap, along with pink Dove chocolate wrapping.
She brings a \textbf{piece} of chocolate toward her mouth, settling comfortably into the chair as she enjoys it.
The imagery shifts to a close view of glossy melted chocolate swirling in smooth, circular ripples.
The chocolate surface is dark brown with lighter highlights, moving like a thick, silky whirlpool.
Finally, Dove chocolate \textbf{packages} appear arranged on a flowing bed of melted chocolate.
Three pink and red \textbf{packages} stand upright, each prominently showing the black Dove logo.
The front pink \textbf{package} includes decorative heart graphics and images of individually wrapped chocolates.
The red \textbf{package} at the back suggests a dark chocolate variety, while another pink \textbf{package} sits to the right.
At the bottom of the image, small white text reads “ facebook.com/dovechocolate. ”

% matched lemmas: coat, counter, cup, drink, package, piece, plate, tabletop
\end{textsample}
