\begin{textsample}{POS Dim 6 – 2020 – Score 14.00 – 2020/tv\_com\_2020\_22.txt}  \label{ex:f6_pos_001}
The commercial opens on a black screen with the white **“Shark”** logo centered.
It then cuts to household messes : a small red-and-black object or spill is shown near the edge of a light-colored \textbf{rug} on a wooden \textbf{floor}, followed by a \textbf{turquoise} bowl or container with spaghetti-like food spilled onto an upholstered dining chair beside a white table.
The next scene shows an adult user, visible from the torso down, standing in a bright living room holding a green and dark teal portable Shark cleaning machine.
The room includes a light \textbf{rug}, wooden \textbf{floor}, orange sofa, and large windows.
Onscreen branding in the upper right reads **“Shark EVERYMESS.”** The user \textbf{kneels} beside the machine on the \textbf{rug}.
A reddish \textbf{stain} is visible on the carpet, and an orange liquid spill is spread across the \textbf{adjacent} wood \textbf{floor}.
A spray bottle and attachments sit nearby.
Close-up shots show a black Shark vacuum attachment working along the edge where the \textbf{rug} meets the hardwood \textbf{floor}, near the liquid spill.
A small disclaimer appears at the bottom : **“Follow Shark ’s instructions for mess pickup.”** A low-angle shot shows the wet spill on the wood \textbf{floor} with the green Shark unit and user blurred in the background.
A black \textbf{floor} \textbf{nozzle} then moves into the foreground ; white text over it reads **“WET VAC,”** and the \textbf{nozzle} has a large **“Shark”** logo.
The commercial then shifts to upholstery cleaning.
A close-up shows a hand squeezing a white-and-pink trigger sprayer.
Another close-up shows a \textbf{transparent} extraction tool labeled **“Shark STAINFORCE”** being used on a dark upholstered surface, possibly a car or vehicle seat.
Small bottom text references testing : **“Based on ASTM F558 vs. the portable \textbf{stain} cleaner market leader…”** though the full line is very small.
A product shot presents a Shark cleaning solution spray bottle.
The label reads **“Shark STAINFORCE”** and includes \textbf{claims} such as **“30X MORE”** and icons including **“OXY MAX.”** The trigger and \textbf{nozzle} are shown in close-up, with a lower-left graphic reading **“STAINFORCE TECHNOLOGY.”** The user then sprays the reddish carpet \textbf{stain} while the Shark portable unit and attachments are visible nearby.
Large onscreen text appears : **“30X MORE”** and partially visible wording about stain-fighting power.
The extraction tool is then used over the \textbf{stained} carpet.
A split-screen \textbf{comparison} follows : on the left, a black vacuum \textbf{nozzle} collects a pile of food debris resembling \textbf{fries} and pasta ; on the right, the \textbf{transparent} extraction tool \textbf{cleans} an orange \textbf{stain} from upholstery or fabric.
The machine ’s internal collection \textbf{tank} is shown from above with dirty water and spaghetti-like debris inside.
Hands \textbf{remove} or handle the \textbf{tank} components.
Another shot shows the green Shark unit on a countertop beside a clear container of water, while the user holds a hose attachment.
The ad then shows more suction examples : a black Shark \textbf{floor} \textbf{nozzle} moves across a glossy white hard surface ; another close-up shows a hose attachment vacuuming a mound of dry dirt, leaves, and debris.
The \textbf{transparent} Shark StainForce extraction head is again shown cleaning carpet, with a StainForce bottle standing nearby.
Near the end, the products are arranged on a white surface in a bright modern interior : the green portable Shark machine in the center, a black \textbf{nozzle} attachment on the left, a \textbf{transparent} extraction head and a StainForce spray bottle on the right.
Small text at the bottom says **“Colors \& accessories may vary.”** The final frame is a polished product packshot.
Large white text on the left reads **“Shark EVERY MESS,”** with smaller text underneath : **“WET VAC + DRY VAC + \textbf{STAIN} SYSTEM.”** The green Shark unit and accessories remain displayed on the right.

% matched lemmas: adjacent, claim, clean, comparison, floor, fry, kneel, nozzle, remove, rug, stain, tank, transparent, turquoise
\end{textsample}
