\begin{textsample}{POS Dim 6 – 2020 – Score 7.00 – 2020/tv\_com\_2020\_38.txt}  \label{ex:f6_pos_068}
A polished wooden table in an IHOP dining room is covered edge to edge with plated food.
In the background, softly out of focus, a person in a magenta top stands or moves near a booth.
Across the table are several white \textbf{plates} : burgers with fries, fried chicken \textbf{pieces}, stacks of pancakes, breakfast items with eggs and bacon, golden fried appetizers with dipping sauce, and a sweet \textbf{dish} topped with whipped cream and chocolate chips.
The restaurant setting feels warm and casual, with the food brightly lit against a darker, blurred dining area.
The view moves in closer to the breakfast and dessert items.
In the foreground, a \textbf{plate} holds two sunny-side-up eggs, strips of bacon, and a browned rectangular breakfast item.
To the left are fries and a bowl of fried appetizers.
Behind them sits a dessert \textbf{plate} with rolled pancakes or crepes filled with a cream-like filling, topped with a tall swirl of whipped cream and scattered chocolate chips.
Large white text begins appearing over the food, building into “ \$5 at IHOP, ” with the IHOP wordmark and its red smile underneath.
The food arrangement changes to another close display.
A stack of pancakes with butter and syrup sits near the center-left, with crispy fried chicken beside it.
A burger with cheese, lettuce, \textbf{tomato}, red onion, and fries fills the right side.
In the background are another burger, hash browns, and fried appetizers with a small \textbf{cup} of red dipping sauce.
The white “ \$5 at IHOP ” text remains centered over the \textbf{plates}, and smaller white text underneath reads “ \$6 in some locations. ” The \textbf{plates} are arranged like a menu spread, emphasizing variety : pancakes, burgers, fries, chicken, hash browns, and appetizers all visible at once.
A close-up focuses on a short stack of pancakes on a white \textbf{plate}.
Syrup \textbf{drips} down the sides, a scoop of butter sits on top, and a \textbf{fork} enters from the upper left, pressing into a cut \textbf{piece} of pancake.
Fried chicken is visible to the right of the stack, and a white IHOP \textbf{cup} is blurred in the background.
The scene then shows a man seated at a restaurant \textbf{counter} or table.
He appears middle-aged, with light-to-medium skin, dark slicked-back hair, and a thick dark mustache.
He wears a light blue dress shirt, dark vest, tie, an ID badge on a lanyard, and a round patch on his vest, giving him a staff or manager-like appearance.
In front of him are several \textbf{plates} : a burger and fries to his left, a glass of Pepsi, fried appetizers and pancakes in the center, and an IHOP coffee mug to his right.
A large blue IHOP sign is blurred behind him, with other diners seated in the background.
He holds a \textbf{fork} with a bite of food near his mouth, then lowers it and looks toward the burger and fries, chewing with a serious, satisfied concentration before leaning forward toward the \textbf{plates}.
The commercial ends on a final menu-style layout.
The table of food returns, with many \textbf{plates} spread across the foreground.
At the top left, a dark sign glows with blue neon-style text reading “ IHOPPY HOUR. ” On the right, large white text reads “ \$5 Menu, ” with smaller text below : “ \$6 in some locations. ” Near the lower left, white text says “ 2 - 10pm Everyday. ” Along the bottom center, bold white text reads “ Free Delivery on IHOP.com, ” followed by smaller fine print about delivery availability and hours.
The background remains an IHOP dining room with a blurred person in magenta on the right, while the food and promotional text stay sharp and prominent.

% matched lemmas: counter, cup, dish, drip, fork, piece, plate, tomato
\end{textsample}
