\begin{textsample}{POS Dim 6 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_22.txt}  \label{ex:f6_pos_009}
It begins in darkness, then opens into a black-and-white cartoon barnyard or chicken-coop setting.
A plump animated chicken sits on straw in front of a chicken-wire fence.
The bird has a dark body, lighter chest feathers, a small comb on top of its head, and exaggerated cartoon eyes and beak.
It looks around, raises its wings, and bobs its body as if performing.
The chicken suddenly stretches upward and hops, leaving a large pale egg sitting in the straw beneath it.
The view centers on the egg as fine cracks spread across its shell.
The top breaks open, and one chick pops up, followed by several more.
Four small cartoon chicks crowd together inside the cracked shell, each with round eyes and tiny beaks, their heads pushed close together.
The chicks fade behind a glowing \textbf{package} of Baker ’s 4 in 1 Sweet Cocoa Mix.
The \textbf{package} is a rectangular box or canister, shown front-facing with a bright halo around it.
The label reads “ BAKER ’S 4 in 1, ” with smaller \textbf{wording} identifying it as a sweet cocoa mix.
Four listed uses are visible on the front : “ Instant Cocoa, ” “ Frosting, ” “ Fudge, ” and “ Sauce. ” The \textbf{package} remains centered, then is surrounded by examples of the four treats : a \textbf{cup} of cocoa on a \textbf{saucer} to the left, a tall glass behind it, a \textbf{frosted} cake or cake slice on a \textbf{plate} to the right, a dessert \textbf{dish} with sauce at the lower left, and a \textbf{plate} of small chocolate \textbf{pieces} at the lower right.
The product sits in the middle as the foods form a neat display around it.
The arrangement shifts so that a larger Baker ’s 4 in 1 \textbf{package} stands on the left beside a steaming \textbf{cup} of cocoa on a \textbf{saucer} on the right.
Large white lettering appears across the foreground, first reading “ You Can't Lose, ” then changing to the bigger message “ DOUBLE YOUR MONEY BACK. ” Behind this text, the \textbf{package} label remains visible with the four uses listed down its front.
The scene changes to a grocery-store display.
A large freestanding rack is packed with many identical Baker ’s 4 in 1 boxes arranged in rows and tiers.
A sign at the top includes the word “ CHOCOLATE, ” and the display is surrounded by shelves and \textbf{counters} typical of a store.
The view moves closer to the lower part of the display, where a promotional panel shows the Baker ’s 4 in 1 \textbf{package}, a \textbf{cup} of cocoa, and bold text about being “ doubly delicious ” and “ DOUBLE your money back. ” Next to the panel is a coupon holder or envelope area marked “ FREE! ” The boxes remain stacked above and behind this lower sign.
A close-up fills the screen with the actual coupon.
It has an ornate border and reads at the top, “ This coupon is a Double-your-money-back Guarantee on BAKER ’S 4 in 1. ” The center contains dense printed instructions, and the lower half has blank lines for “ Your name, ” “ Address, ” “ City, ” “ State, ” and “ Price paid. ” A small \textbf{picture} of the Baker ’s 4 in 1 \textbf{package} appears on the right side of the coupon.
The coupon then appears beside a kitchen table scene with two children.
On the left is a young girl with dark hair pulled back with ribbons, wearing a dark dress with a large white \textbf{collar}.
She holds a patterned teacup with both hands and smiles toward a boy seated beside her.
A Baker ’s 4 in 1 \textbf{package} sits on the table near her.
The boy, about the same age, has neatly combed light hair and wears a \textbf{short-sleeved} checkered shirt.
He lifts his \textbf{cup} and \textbf{drinks}, then lowers it slightly and smiles.
Each child has a \textbf{saucer} in front of them.
They look pleased and relaxed, sharing \textbf{cups} of cocoa in a home kitchen with cabinets in the background.
The coupon graphic returns, again filling most of the screen with the guarantee text and blank form lines.
It then fades back into the product-and-cocoa \textbf{tabletop} arrangement : the Baker ’s 4 in 1 \textbf{package} stands large on the left, and a \textbf{cup} of cocoa on a \textbf{saucer} sits on the right with faint steam rising from the \textbf{cup}.
The label on the \textbf{package} remains \textbf{readable} enough to show “ BAKER ’S 4 in 1 ” and the four uses : instant cocoa, frosting, fudge, and sauce.
Large white words appear over this final product scene, building again into the promise “ DOUBLE YOUR MONEY BACK, ” with the \textbf{package} and steaming \textbf{cup} still visible behind the lettering.

% matched lemmas: collar, counter, cup, dish, drink, frosted, package, picture, piece, plate, readable, saucer, short-sleeved, tabletop, wording
\end{textsample}
