\begin{textsample}{POS Dim 6 – 2010 – Score 19.00 – 2010/tv\_com\_2010\_99.txt}  \label{ex:f6_pos_081}
A plain white screen displays a green-and-blue geometric “ N ” logo beside the word “ nerdwallet ” in bright green, with the smaller line “ TURN TO THE NERDS ” underneath.
The commercial then shifts into an extremely bright yellow kitchen.
Everything is coordinated in sunny yellow tones : glossy cabinets, yellow chairs, yellow \textbf{dishes}, and a white round tablecloth at a small table.
A young adult man with short dark hair, wearing a yellow-and-white striped polo shirt, carries food to the table where a young adult blonde woman in a yellow cardigan sits smiling.
On the table are yellow bowls, cutlery, glasses of water, and a small yellow casserole \textbf{dish}.
The man sets down a \textbf{dish} of macaroni and cheese topped with reddish bacon \textbf{pieces}.
A close view shows the creamy yellow macaroni in a small yellow handled \textbf{pot} on a woven placemat, beside an orange napkin and a \textbf{fork} and knife.
A \textbf{fork} scoops up a bite of macaroni, then the focus returns to the woman.
She smiles softly as she holds the \textbf{fork}, then \textbf{notices} a single yellow potato chip in her other hand.
She raises the chip with a pleased, curious expression, brings it to her mouth, and eats it.
She chews with a satisfied look, glancing toward the man.
At the table, the couple sit side by side with \textbf{plates} and bowls in front of them.
A bag of Lay ’s appears upright in the foreground between them, labeled “ Lay ’s Cheddar Bacon Mac \& Cheese, ” with \textbf{pictures} of macaroni, bacon, and a potato chip on the \textbf{package}.
The man and woman continue smiling at each other ; he lifts a chip and offers it to her as they lean together over the bright yellow table setting.
The scene changes to a warm café-like setting.
A clear glass \textbf{cup} of cappuccino sits on a glass \textbf{saucer}, topped with white foam art, with cinnamon \textbf{sticks} resting beside it.
Hands place the \textbf{cup} neatly on the table.
A young adult Asian man with short dark hair, wearing a pale gray sweater over a white shirt, sits in front of a tiled white backsplash with a coffee maker and \textbf{pastries} behind him.
He holds the \textbf{cup}, then looks at a single potato chip in his hand with a thoughtful, slightly amused expression.
He turns the chip, studies it, and eats it.
As he chews, a small line of fine print appears along the bottom, indicating the cappuccino flavor does not contain caffeine.
He then gives a knowing, pleased look.
A beige-and-white Lay ’s bag labeled “ Cappuccino ” stands upright on the table near him, with a cappuccino image on the front.
He reaches into the bag and brings another chip to his mouth.
The next setting is a colorful patio kitchen or outdoor entertaining area.
Two young adult women stand behind a brick \textbf{counter} in front of red horizontal slatted panels, with green plants and fruit around them.
One woman has dark hair pulled back and wears a bright pink top ; the other has long wavy brown hair and wears a coral-orange dress with a pale pink cardigan.
The \textbf{counter} is covered with fresh produce and cooking props : mangoes, \textbf{tomatoes}, peppers, limes, bowls, a cutting board, and a red \textbf{pitcher}.
They prepare salsa together, smiling and talking.
One tosses a \textbf{tomato} upward, and the other watches it with a playful expression.
A close view of the cutting board shows a \textbf{mound} of diced yellow mango and red \textbf{pieces} beside a large glass bowl.
The chopped salsa is suddenly \textbf{replaced} visually by a pile of ridged potato chips.
A knife slides the chips off the cutting board into the glass bowl, where they tumble in and collect.
The two women each eat a chip, facing each other with \textbf{surprised}, \textbf{impressed} expressions as they chew.
Back at the \textbf{counter}, they stand with the bowl of chips between them.
A red-and-white bag of “ Lay ’s Wavy Mango Salsa ” appears upright in the foreground, surrounded by fruit and vegetables.
The woman in the coral dress lifts the glass bowl high as both women move off to the side, leaving the Lay ’s Wavy Mango Salsa bag centered on the \textbf{counter}.
The commercial then moves to a restaurant-style table with a soft peach and green color palette.
A server ’s hands place long white rectangular \textbf{plates} in front of diners seated around bamboo placemats.
Each \textbf{plate} has small garnishes : a green wasabi-like \textbf{mound} shaped like a leaf and a pink rosette resembling pickled ginger.
Small square \textbf{dishes} of dark soy sauce and pairs of chopsticks sit on the table.
In a close view, the white \textbf{plate} first holds the green and pink garnishes ; then the pink garnish is \textbf{replaced} by a light yellow potato chip, then the green garnish is \textbf{replaced} as well, until several pale kettle-style chips lie on the \textbf{plate}.
A young adult man with dark hair, wearing a light green button-down shirt, eats one of the chips with chopsticks.
He chews and looks to the side, appearing pleasantly \textbf{surprised}.
Around the table, other diners also use chopsticks, including a young Black woman in a pale peach top on his left and another person in coral on the opposite side.
A white-and-green Lay ’s bag stands in the middle of the table, labeled “ Kettle Cooked, ” with the flavor clarified by the ad context as wasabi ginger.
The man grins as he reaches with chopsticks toward a \textbf{plate} of chips, and the group continues eating from the small \textbf{plates}.
The final screen is a golden yellow product display.
A wooden cutting-board-shaped logo near the top reads “ Do Us a Flavor ” with “ Choose My Chip ” beneath it.
One by one, the four finalist Lay ’s bags appear in a row : “ Cheddar Bacon Mac \& Cheese ” in a yellow-accented bag, “ Cappuccino ” in a beige bag, “ Wavy Mango Salsa ” in a red bag, and “ Kettle Cooked Wasabi Ginger ” in a green bag.
Large white text along the bottom says, “ Vote at DoUsAFlavor.com, ” with smaller fine print beneath it.

% matched lemmas: counter, cup, dish, fork, impressed, mound, notice, package, pastry, picture, piece, pitcher, plate, pot, replace, saucer, stick, surprised, tomato
\end{textsample}
