\begin{textsample}{POS Dim 6 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_72.txt}  \label{ex:f6_pos_046}
The commercial opens on a studio-like gray background with an adult woman facing forward.
She has short, dark, neatly shaped hair, a warm smile, and wears a reddish cardigan over a pale yellow \textbf{collared} shirt.
She speaks directly toward the viewer, then lifts a small green can of tuna beside her face.
The front label is visible : “ Chicken of the Sea ” in large white lettering, with a red block reading “ TUNA. ” She holds the can near her cheek, presenting it with a confident, slightly playful smile.
She turns the can so the metal end faces outward.
The circular end of the can fills more of the view, and she points to the printed inspection seal with one finger.
The lettering around the metal circle becomes \textbf{readable} : “ Department of Commerce, ” “ Packed under Federal Inspection, ” and “ United States of America, ” arranged in rings around the lid with small stars separating parts of the text.
Her polished fingernail rests near the edge of the seal as she draws attention to it.
The image then shifts back to the woman holding an oval \textbf{serving} \textbf{plate}.
On it are pale chunks or flakes of tuna arranged with colorful garnishes, including leafy greens, a red \textbf{tomato}, and orange slices that look like carrots.
She holds the \textbf{plate} at chest height, angled toward the viewer, as if offering a \textbf{serving} suggestion.
She lowers the \textbf{plate} and turns slightly, revealing a dining setup beside her.
A family meal scene appears around a small round table covered with a light tablecloth that has a \textbf{checked} or crisscross pattern and fringed edges.
The same woman sits on the left.
Next to her is a young girl with light brown hair, wearing a pink \textbf{turtleneck} or long-sleeved top, holding a sandwich with both hands.
To the girl ’s right sits a young boy with light brown hair swept to one side, wearing a dark shirt with wide tan stripes, also holding a sandwich.
On the far right, an adult man in a tan sweater sits with his back partly toward the viewer, facing the children.
The table holds \textbf{plates} of food, white \textbf{cups} and \textbf{saucers}, sandwiches, and small items in the center such as condiments or \textbf{serving} \textbf{pieces}.
The setting is simple and staged against the same plain gray background, with wooden dining chairs visible behind them.
The children eat while the woman gestures across the table, watching them with an approving smile.
The girl keeps both hands around her sandwich ; the boy looks down at his food and then toward the others.
The man holds food in his hand and leans slightly toward the children.
The family appears relaxed and cheerful, sharing the meal together.
A large circular inspection seal begins to surround the family scene, as though the table is inside the printed seal shown earlier on the can.
The words around the ring are large and bold : “ Department of Commerce, ” “ Packed Under Federal Inspection, ” and “ United States of America. ” The family remains seated at the table in the center of this ring, continuing to eat and pass food, while the seal forms a graphic border around them.
The view widens into a more imaginative product display : the family at the table appears small, sitting inside the circular inspection seal on top of a giant Chicken of the Sea tuna can.
The can is green, with a silver metal top.
On the front, the white “ Chicken of the Sea ” brand name is prominent, and a red rectangle below reads “ TUNA. ” A small mermaid figure is visible on the side of the green label.
The large federal inspection seal sits like a lid emblem, with the family meal centered inside it, visually linking the product label and inspection seal to the family eating scene.
The family then reappears closer together.
The woman leans in from the left with her arms around the two children.
The girl in pink beams broadly, still holding part of a sandwich, while the boy in the striped shirt smiles toward her and then toward the viewer.
The woman presses close to the girl ’s cheek, puckering as if giving her a kiss, and all three look happy and affectionate.
The commercial returns to a close view of the can ’s metal end with the circular seal.
A hand holds the can upright, fingers visible around the sides.
The seal text is again clear : “ Department of Commerce, ” “ Packed Under Federal Inspection, ” and “ United States of America. ” The hand tilts and rotates the can downward so the green front label comes into view.
The final product image shows the can held steadily against the plain background, with the white “ Chicken of the Sea ” name centered on the green label and the red “ TUNA ” panel below it.

% matched lemmas: checked, collar, cup, piece, plate, readable, saucer, serve, tomato, turtleneck
\end{textsample}
