\begin{textsample}{POS Dim 6 – 1960 – Score 15.00 – 1960/tv\_com\_1960\_1.txt}  \label{ex:f6_pos_023}
In black and white, a single apple appears against a plain studio background.
It is round and glossy, with a small \textbf{stem} and leaf at the top.
Drops or speckles on its skin make it look fresh.
Bite-shaped chunks vanish from the apple ’s side, then more of the apple disappears, leaving pale flesh exposed.
The dark peel shrinks away until the apple is reduced to a mostly eaten core with the leaf still attached.
The image changes to a square toaster \textbf{pastry} floating against the same plain background.
It has a crimped edge and a patterned surface marked with small X-shaped vents.
Bite marks appear along the right side, then the left side, narrowing the \textbf{pastry} into an hourglass shape as if it is being eaten from both sides.
A small apple leaf appears on top of the \textbf{pastry}, visually linking it to the apple shown earlier.
A small breakfast scene follows.
An elderly woman with short, light-colored hair sits alone at a round table covered with a cloth.
She wears a light cardigan over a patterned top and leans forward toward a \textbf{plate}.
A \textbf{cup} and \textbf{saucer}, a \textbf{spoon}, and a vase or bowl of flowers sit on the table.
She holds a small \textbf{piece} of food near her mouth and \textbf{takes} a bite, looking down at her breakfast.
The setting shifts to a larger breakfast.
An adult man with dark hair sits at a table wearing a light shirt.
In front of him are several \textbf{dishes} : \textbf{plates} piled with breakfast foods, a bowl, a \textbf{cup}, a glass, and a tall \textbf{pitcher} or coffee \textbf{pot}.
He lifts food with one hand while holding something in the other, actively eating amid a full spread.
A young boy appears at a breakfast table with a Toastem product box in the foreground and a toaster beside it.
The box shows the Toastem name and an \textbf{illustration} of rectangular \textbf{pastries} with fruit imagery.
The toaster is a boxy, mid-century style appliance with a vertical control on the front.
The boy sits behind it, watching as a \textbf{pastry} is handled at the toaster.
He reaches toward the top, \textbf{removes} a rectangular \textbf{pastry}, and brings it toward his mouth.
He turns slightly and \textbf{takes} a bite, with the Toastem box still prominently displayed beside the toaster.
The view widens to a family gathered around a checkered tablecloth.
Four people sit together : an adult man on the left, the young boy facing forward, an adult woman on the right, and a young girl with long light hair in the foreground with her back partly turned.
The toaster and Toastem box sit near the center of the table along with \textbf{cups}, \textbf{plates}, and a \textbf{pitcher}.
The family members hold and eat the \textbf{pastries} around the breakfast table.
A close view of the \textbf{pastry} surface fills the screen.
Its bumpy, baked crust has small X-shaped indentations.
The \textbf{pastry} splits open down the middle, revealing a thick, shiny filling inside. \textbf{Crumbs} cling to the edges as the two halves pull apart, emphasizing the soft interior.
A young girl with straight \textbf{bangs} and freckles is then shown close up.
She holds a \textbf{pastry} with both hands and opens her mouth wide to bite into it.
She bites down, then chews while looking slightly to the side, her face filling most of the image.
Finally, a young boy is shown in close-up, holding a bitten \textbf{piece} of \textbf{pastry} near his mouth.
He opens wide, puts more of it in, and bites down, his expression relaxed and pleased as he eats.

% matched lemmas: bang, crumb, cup, dish, illustration, pastry, piece, pitcher, plate, pot, remove, saucer, spoon, stem, take
\end{textsample}
