\begin{textsample}{POS Dim 6 – 1980 – Score 3.00 – 1980/tv\_com\_1980\_7.txt}  \label{ex:f6_pos_080}
The commercial opens with a close-up of a blond toddler, unclothed from the waist up, standing in front of a light tiled wall.
The child looks slightly upward and to the side while holding or touching an orange object or line near the lower right of the frame.
Behind the child, a red-orange zigzag line is visible on the tiled background.
The next shot shows the same child in side profile, still bare-shouldered, looking downward with a focused or serious expression.
The tiled wall remains in the background, again with a red-orange zigzag line \textbf{crossing} behind the child.
Later, the framing widens.
The child is now shown standing in a room with a grid-like tiled wall and a blue diagonal line in the background.
Shelving or boxes appear on the left side of the frame, including a red box with light-colored markings or characters, though the text is not clearly readable.
The child smiles and looks downward, with one arm lowered as if \textbf{reaching} for or handling something out of frame.
In the final frame, the child is smiling broadly while tangled in or \textbf{lifting} long pale strips of material, resembling toilet paper or ribbon.
Several strips hang over the child ’s head, shoulders, and torso.
The tiled background with the blue diagonal line remains visible.
The visual emphasis shifts from the child ’s face and attentive expressions to playful interaction with the hanging strips.

% matched lemmas: cross, lift, reach
\end{textsample}
