\begin{textsample}{POS Dim 6 – 2000 – Score 6.00 – 2000/tv\_com\_2000\_82.txt}  \label{ex:f6_pos_038}
The commercial begins with a nearly black frame, with only a small red heart-shaped watermark/logo visible at the lower right.
It then cuts to a close-up of a blue Kleenex container on a \textbf{kitchen} counter.
The packaging is clearly visible and reads “ New, ” “ Moist Cloth, ” and “ Kleenex. ” A hand \textbf{reaches} into the open white-lidded top and \textbf{pulls} out or touches a white cloth.
Plates and a newspaper-like object are blurred in the background.
Next, an adult man is shown seated in a bright \textbf{kitchen}, holding or sitting behind a newspaper.
He \textbf{presses} a white cloth to the side of his face.
The Kleenex container is partly visible in the foreground, with its lid open.
The \textbf{kitchen} background includes cabinets, shelving, and appliances.
The following frame moves closer to the man as he bends his head down and \textbf{wipes} across his face with the cloth, covering much of his nose and mouth area.
Behind him are a \textbf{sink}, window, countertop, and \textbf{kitchen} items such as a bowl of fruit.
The focus then shifts to a toddler seated in a high chair.
The child is eating from a bowl on the high-chair tray and has a hand near the mouth.
The setting remains the same bright kitchen/dining area, with large windows and pale cabinetry.
A second close view of the toddler shows the child smiling broadly while seated in the high chair.
A white bowl and spoon are on the tray, with some food visible on or near the tray surface.
The background includes a refrigerator or tall \textbf{kitchen} unit and a microwave-like appliance.
The commercial then cuts to a wide shot of the whole kitchen/dining space.
The adult man sits at the center behind a large open newspaper.
Young children in high chairs are positioned on either side.
The room is bright, with tall windows, shelves filled with dishes, and a long table or counter in the foreground.
White text appears along the bottom reading : “ Thank goodness for male bonding. ” The final frame remains on the same wide \textbf{kitchen} shot.
The bottom text changes to include the Kleenex branding, reading “ Thank goodness for Kleenex, ” with a blue horizontal bar beneath it and the Kleenex logo styled in white.
The small red heart-shaped watermark/logo remains at the lower right.
No dialogue, music, or voice-over is visible in the frames.

% matched lemmas: kitchen, press, pull, reach, sink, wipe
\end{textsample}
