\begin{textsample}{POS Dim 1 – 1950 – Score 10.00 – 1950/tv\_com\_1950\_41.txt}  \label{ex:f1_pos_006}
Now, here 's a question I have for you ladies.
What will they think of next?
Here 's Evelyn Patrick to tell you about a combination they did think of next.
Snow Peach and Futurama.
Yes, \textbf{girls}, for \textbf{color} that \textbf{puts} a new \textbf{light} on your lips that is pure allure, you 'll want Revlon 's shade of Snow Peach lipstick.
And, of course, you 'll want it in a glamorous Futurama like this.
The engraved white enamel case is just perfect for any fashion and bound to \textbf{give} you that feeling of elegance every woman wants.
With Futurama within \textbf{easy} reach, you 're at your best.
But the marvelous part about this stunning Futurama is it \textbf{looks} expensive, but it 's not.
And \textbf{remember}, with Futurama, you 're getting a permanent case because all you need ever \textbf{buy} again is a Revlon refill that clicks in and out as easily as this.
That means a saving of 35 cents on every single lipstick you \textbf{buy}.
So, \textbf{girls}, when you say...... the \textbf{light}, bright shade that 's bound to \textbf{give} you a \textbf{look} of summer brilliance, say, Snow Peach in a Futurama.
That 's \textbf{right}, \textbf{girls}. \textbf{Give} yourself a gift of a Snow Peach in a Futurama tomorrow.
And, folks, \textbf{remember}, Futurama is the perfect gift for graduations, bridesmaids, birthdays, an anniversary, really nearly anything.
Thank you.
Try it.

% matched lemmas: buy, color, easy, girl, give, light, look, put, remember, right
\end{textsample}
