\begin{textsample}{NEG Dim 5 – 1950 – Score -8.00 – 1950/tv\_com\_1950\_53.txt}  \label{ex:f5_neg_041}
Hello there.
Friends, here 's an \textbf{amazing} free offer for everyone who 's overweight.
Even though you 've tried other methods and failed, you can still lose ugly fat fast.
Now thousands can tell you that the calimetric reducing formula is the only safe, sure, effective way to reduce.
This package includes the wonder 10-day diet that \textbf{lets} you \textbf{eat} three delicious meals a day, plus a bedtime snack, and even includes a jog for your willpower.
And yet you take only three calimetric \textbf{tablets} per day.
And now here 's that sensational free offer I was going to tell you about.
A 30-day supply of wonderful calimetric \textbf{tablets}, a certified \$3.50 value, when you buy the regular calimetric way to \textbf{weight} \textbf{control}.
You save \$3.50.
That 's a \$7 value for only \$3.50, a 50 \% saving.
And how can you get your free bottle of calimetric \textbf{tablets}?
Just send in this calimetric box top with your name and address, and your druggist will give you a postage \textbf{paid} envelope already addressed to the calimetric company.
So don't lose hope, lose \textbf{weight}.
Get calimetric reducing formula at your drugstore.
Send the box top in the free post page envelope, and get your \$3.50 bottle of calimetric \textbf{tablets} absolutely free.
Friends, believe me when I say don't wait.
Act right now.

% matched lemmas: amazing, control, eat, let, pay, tablet, weight
\end{textsample}
