\begin{textsample}{POS Dim 4 – 2020 – Score 22.00 – 2020/tv\_com\_2020\_16.txt}  \label{ex:f4_pos_003}
Inside a bright, plant-filled \textbf{living} \textbf{room}, a shaggy black-and-white \textbf{dog} \textbf{lounges} upright on a \textbf{cream} \textbf{sofa}, surrounded by beige and green cushions.
A TV remote rests on the seat in front of it.
Through the large window behind the \textbf{sofa}, a bearded adult man in a tan shirt is outside in the \textbf{garden}, handling a lawn-spraying container.
The \textbf{dog} ’s posture looks idle and cooped up, with its fluffy \textbf{paws} raised and its head turned toward the window.
The \textbf{dog} reclines against the cushions with a smartphone \textbf{propped} in front of it.
On the phone screen, videos of \textbf{dogs} outdoors appear, including a \textbf{dog} standing in green grass and then an image of a bright yellow fire hydrant.
The \textbf{dog} ’s furry \textbf{paw} lifts and swipes near the screen, as if scrolling.
As the phone remains on the cushion, the \textbf{dog} turns its head toward the window, where the man outside comes into clearer view.
He stands on the \textbf{patio} in a \textbf{sunny}, green \textbf{backyard}, holding a white jug with a hose and spray wand.
The jug has a bold red label that reads “ WEED KILLER. ” He looks toward the \textbf{dog} through the glass while holding the container and sprayer, with \textbf{garden} plants and a \textbf{patio} umbrella behind him.
Back on the \textbf{sofa}, the \textbf{dog} lies partly on its side with a smartphone pressed near its head, as though using it.
Then the \textbf{dog} faces a television across the \textbf{room}.
On the TV screen is a bright \textbf{garden} scene featuring Spruce packaging : a green container with a spray wand.
Large on-screen text reads, “ SAFE FOR USE AROUND PEOPLE, \textbf{PETS} \& BEES, ” with \textbf{paw} and bee icons above it and a smaller note below indicating “ when used as directed. ” The TV image changes to a person outdoors holding the Spruce product near a landscaped area, while the same safety message remains large on the right side of the screen.
The \textbf{dog} suddenly becomes animated.
It sits upright on the \textbf{sofa}, mouth open and tongue visible, then springs forward off the cushions.
A set of keys with a paw-shaped keychain lies on a round wooden coffee \textbf{table}.
The \textbf{dog} rushes up to the \textbf{table}, stretches its muzzle over the edge, and grabs the keys in its mouth.
A close view shows its fluffy white \textbf{paw} and muzzle near a car door and ignition area, with the paw-shaped keychain dangling from the keys.
The scene then moves outside to the rear of a small white vintage convertible on a quiet, tree-lined suburban street.
Its license plate reads “ IH8WDZ, ” and the car drives away down the road.
In a \textbf{garden} center or home-improvement store, the same shaggy \textbf{dog} sits obediently in front of a tall, bright green Spruce display stocked with bottles and containers.
The display is topped with the large white brand name “ Spruce. ” A woman with long dark hair, wearing a dark top and a light apron tied at the waist, stands beside the display, looking at the products.
Shelves of \textbf{garden} supplies and large \textbf{potted} plants fill the surrounding aisle.
The \textbf{dog} is then shown riding in the white convertible, presented comically as if it is in the driver ’s seat.
It wears pale yellow goggles over its eyes, its long fur \textbf{blowing} back, with its front \textbf{paws} resting near the steering wheel.
A green Spruce container sits upright beside the wheel on the front seat area, label facing outward.
The background is a blur of lush greenery and palm-lined streets, reinforcing the sense of motion and open air.
Outside a house in a landscaped front yard, a casually dressed adult man in a white T-shirt, dark shorts, and sandals uses a green Spruce container with an attached spray wand.
He points the wand downward toward small weeds growing between paving stones near the edge of the lawn.
The shaggy \textbf{dog} stands nearby on the grass, facing away toward the yard, while \textbf{flowers}, shrubs, rocks, and a porch frame the \textbf{domestic} \textbf{garden} setting.
A simple side-by-side demonstration appears against dark soil.
On the left, a small green plant is labeled “ UNTREATED ” in white text on a green tag.
On the right, another small plant is marked with a green label reading “ \textbf{TREAT}, ” indicating the \textbf{treated} side.
The \textbf{treated} plant appears smaller and more wilted, with \textbf{little} white marks or drops around it on the soil, while the untreated plant looks fresher and more upright.
The man kneels beside the \textbf{dog} in the yard, smiling down at it and gently \textbf{petting} its head.
The Spruce container stands upright between them, its green label visible, with the spray wand attached along the side.
The \textbf{dog} sits calmly, wearing a collar, in front of the \textbf{home} ’s \textbf{garden} and trees.
A dark gray pickup truck is parked in a driveway or residential street with several \textbf{dogs} leaning out of the open windows.
A large green Spruce retail display, stocked with bottles, is positioned upright in the truck bed.
The \textbf{dogs} look outward from the cab, including a white \textbf{dog} hanging its front \textbf{paws} over the window edge and another black-and-white \textbf{dog} visible in the back.
A large yellow graphic shape sweeps across the scene, transitioning into the final product display.
The commercial ends on a clean green-and-yellow graphic background with a large Spruce Weed \& Grass Killer container on the right.
The product is a green-and-white jug with an attached green spray wand and yellow nozzle.
Visible label details include the Spruce brand name, “ Weed \& Grass Killer, ” “ Visible Results 1 hr, ” and claims about killing weeds and grass to the roots.
Icons on the label refer to use around people, \textbf{pets}, and bees when used as directed.
Large yellow text on the left reads, “ \textbf{PET} FRIENDLY. ”

% matched lemmas: backyard, blow, cream, dog, domestic, flower, garden, home, little, living, lounge, patio, paw, pet, potted, prop, room, sofa, sunny, table, treat
\end{textsample}
