\begin{textsample}{POS Dim 4 – 2020 – Score 22.00 – 2020/tv\_com\_2020\_102.txt}  \label{ex:f4_pos_004}
A white Febreze logo appears centered against a bright blue sky with soft clouds.
The scene moves to a \textbf{sunny} front \textbf{garden} outside a neat white house.
An adult woman with short, \textbf{curly} dark hair walks along the path toward the door.
She wears a dark blazer over a light blue shirt, loose brown trousers, and carries a dark \textbf{bag} over one shoulder.
The small \textbf{garden} is full of \textbf{potted} plants and \textbf{flowers}, with ivy climbing the wall, a bench near the window, and other houses visible beyond a hedge.
As she approaches, the front door comes into view.
Its design looks almost like a smiling face : two round windows near the top resemble eyes, a circular door knocker sits like a nose, and a curved mail slot forms a smile.
The woman pauses in front of it, facing the door, while sunlight casts \textbf{leafy} shadows across the white wall.
Inside the \textbf{home}, the woman stands just inside the \textbf{entryway} holding her dark jacket and \textbf{bags}.
The \textbf{cheerful} door is now behind her, but the air around the \textbf{room} is filled with visible yellow-green, smoky odor clouds.
One cloud surrounds a red sneaker floating near the ceiling, another hovers near the left side of the \textbf{room}, and another lingers by a plant and \textbf{chair} on the right.
The woman looks around, then tilts her gaze upward toward the sneaker cloud with a concerned, wary expression.
A product display appears on a bright, clean background : Febreze Plug packaging beside the Febreze logo.
The package shows the white plug-in device and a refill labeled “ Linen \& Sky, ” with a yellow badge reading “ Fade Defy Plug. ” The plug-in device is then shown close up as a white oval unit with a clear lower reservoir, plugged into a wall outlet.
Beside it, blue circular-arrow graphics surround the words “ FADE DEFY PLUG. ” Another demonstration shows the plug-in on the wall releasing two pale blue streams upward, next to a blue graphic that reads “ 2 COMPLEMENTARY SCENTS. ” Back in the \textbf{entryway}, the Febreze Plug is visible in an outlet on the right wall.
Bright blue scent streams sweep through the \textbf{room} in broad, flowing bands, passing across the coat rack, shoes, plants, and front door area.
The earlier yellow-green odor clouds remain visible at first, including the cloud around the sneaker and another around a small \textbf{dog} in a bed near the floor, but the blue \textbf{waves} visually take over the space.
The woman now appears in a different \textbf{room} wearing a teal-blue sweater.
Blue scent streams and tiny sparkling particles move across the foreground.
She looks upward and around with a softened, pleased expression.
A large circular blue graphic beside her counts upward, changing from “ UP TO 3 DAYS ” to “ 11, ” then “ 41, ” and finally “ UP TO 50 DAYS, ” with small text at the bottom reading “ *low setting. ” The final \textbf{home} scene is a \textbf{cozy} \textbf{living} \textbf{room} washed with blue freshness \textbf{waves}.
A child with \textbf{curly} hair sits on a \textbf{rug} beside a large light-colored \textbf{dog}, \textbf{petting} or resting a hand on it.
The woman relaxes on a \textbf{sofa} in the background.
The \textbf{room} has soft \textbf{furnishings}, a coffee \textbf{table} with household items, plants, \textbf{curtains}, and warm lamps, giving it a calm, comfortable feel.
The commercial ends on a clean blue background with Febreze Plug products arranged in a row.
The front package again shows the white plug-in and “ Linen \& Sky ” refill, with the yellow “ Fade Defy ” badge.
Large white text reads “ febreze PLUG, ” and a small P\&G logo appears in the upper right.

% matched lemmas: bag, chair, cheerful, cozy, curly, curtain, dog, entryway, flower, furnishing, garden, home, leafy, living, pet, potted, room, rug, sofa, sunny, table, wave
\end{textsample}
