\begin{textsample}{POS Dim 4 – 2020 – Score 9.00 – 2020/tv\_com\_2020\_39.txt}  \label{ex:f4_pos_035}
The commercial unfolds in a bright \textbf{outdoor} park setting, centered on a picnic table where several \textbf{young} adults are eating Taco Bell food. 1. **Opening close-up at the picnic table** : A hand reaches into or opens a white paper food wrapper with \textbf{purple} and orange graphics.
On the wooden table are other wrappers, small red sauce packets, pieces of brown paper, and a translucent green \textbf{drink} cup. 2. **Wider \textbf{group} shot** : The camera cuts to three \textbf{young} adults seated around the picnic table in a grassy park.
They have Taco Bell-style paper bags, wrapped food items, sauce packets, and plastic cups on the table.
Bright, animated \textbf{purple} graphics begin to arc and loop across the scene, visually connecting the people and the food. 3. **Table-level food close-up** : A low close-up shows wrapped food on the table while thick animated stripes in \textbf{purple}, red, yellow, and white sweep horizontally across the foreground, as if flowing over the tabletop. 4. **Blonde woman with food** : A \textbf{young} woman in a cream sweater holds a small wrapped item or taco-like food and smiles.
A \textbf{young} man sits beside her.
A large \textbf{drink} cup with a \textbf{straw} and a branded paper bag are visible on the table.
Animated color bands continue across the lower part of the frame, and small drawn spark effects appear near the food. 5. **Animated transformation around the woman** : The same woman leans her head toward the food she is holding.
Bright cartoon-style splashes and strokes appear around her body, including yellow coloring over her sleeves, \textbf{purple} coloring around her hair, and white splash marks radiating outward.
The \textbf{young} man beside her remains seated and smiling slightly. 6. **Two-person park-table shot** : The \textbf{young} man in a denim jacket holds a \textbf{drink} cup while the \textbf{blonde} woman holds food.
The picnic table remains covered with wrappers, sauce packets, a paper bag, and \textbf{drinks}. \textbf{Colorful} animated ribbons in green, \textbf{purple}, red, and yellow curl across the table and foreground. 7. **Sauce being added to food** : A close-up shows a hand squeezing sauce from a small red packet over an open taco or wrap filled with lettuce, diced tomatoes, cheese, and other ingredients.
White animated spark shapes appear around the food.
Small legal-style text appears along the bottom of the frame, but most of it is too small to read clearly. 8. **Product beauty shot** : A loaded taco or folded flatbread item sits open on branded paper on the picnic table, with visible lettuce, tomato, cheese/sauce, and a browned filling.
Red and orange sauce packets lie nearby.
Large animated text appears above the food, reading “ \$1 LOADED NAC … ” with the final part partially unclear in the sampled frame.
Fine-print text remains along the bottom, mostly illegible at this resolution. 9. **Wide brand reveal in the park** : The scene pulls back to a wide view of the picnic table in the grassy park.
A large animated Taco Bell sign stands prominently at the left, with the \textbf{purple} bell logo and the words “ TACO BELL. ” The \textbf{group} is small in the center at the table.
The frame includes additional playful illustrated elements : cartoon clouds, sweeping colored lines, and a large red circular graphic on the right with repeated words including “ FREE ” and “ \textbf{HOT}, ” though the full text is partly cut off. 10. **Final wide frame** : The same park-wide composition remains, with the large Taco Bell sign on the left and the picnic table \textbf{group} in the middle distance.
Red animated flame-like shapes appear around the base of the table, while the \textbf{colorful} illustrated landscape elements continue around the edges.

% matched lemmas: blonde, colorful, drink, group, hot, outdoor, purple, straw, young
\end{textsample}
