\begin{textsample}{POS Dim 4 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_104.txt}  \label{ex:f4_pos_081}
The commercial is in black and white and shows women modeling or handling swimwear/undergarment-like garments in an \textbf{outdoor} \textbf{resort} or \textbf{poolside} setting.
A “ www.PublicDomainFootage.com ” watermark is visible across many frames.
At the beginning, two women are indoors in what appears to be a changing or dressing area.
One woman is partly covered with a towel, while the other wears a strapless fitted swimsuit or corset-like garment and looks down at something she is holding.
The camera then cuts closer to the standing woman ’s torso as she holds up a pale, brief-like garment in both hands.
The scene moves outdoors to a \textbf{sunny} patio or \textbf{pool} terrace.
Three women in swimsuits are shown : one seated on a \textbf{chair}, one standing, and one seated in a \textbf{lounge} \textbf{chair}.
The setting includes walls, doors, and patio furniture.
The commercial then shows several women descending an exterior staircase, suggesting they are moving from a building down to the \textbf{pool} or terrace area.
Next, a wide \textbf{outdoor} shot shows the women crossing an open courtyard near a staircase and a building with distinctive rooflines.
A closer frontal shot follows, with three women in swimsuits \textbf{walking} or running toward the camera with their arms slightly extended, as if posing or moving in formation.
The focus shifts to a diving-board area.
One woman \textbf{walks} out along a diving board while another stands nearby on the platform.
A close-up then emphasizes a woman ’s torso and \textbf{hips} in a strapless swimsuit with \textbf{gathered} or ruched fabric around the lower front, her hands placed at her waist.
The commercial returns to a patio seating area.
Two women sit at a table, smiling ; objects on the table appear to include cards or small flat items, though the exact \textbf{activity} is not completely clear.
A closer overhead angle shows the same or similar women laughing and looking down at the tabletop.
Another shot shows a woman smiling at the camera while standing under or beside a large umbrella or parasol ; she \textbf{touches} her face or ear with one hand.
Later, a woman stands beside a reclining woman on a deck \textbf{chair}.
The standing woman wears a strapless fitted swimsuit and appears to be showing or adjusting the lower portion of the garment, while the reclining woman looks up toward her.
A close-up isolates the standing woman ’s \textbf{hip} and hem area, with the reclining woman ’s hand visible near the garment, suggesting attention to its fit or construction.
Near the end, a close-up shows a smiling woman holding or adjusting a pale cup-like or fabric piece near the top of a dark strapless swimsuit ; the exact item is not clear from the sampled frame.
The final shots show a line of women in swimsuits \textbf{walking} along a narrow raised edge or wall near a rocky waterfront.
They extend their arms outward for balance while moving in single file, with the \textbf{lead} woman smiling as she \textbf{steps} forward.

% matched lemmas: activity, chair, gather, hip, lead, lounge, outdoor, pool, poolside, resort, step, sunny, touch, walk
\end{textsample}
