\begin{textsample}{POS Dim 4 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_68.txt}  \label{ex:f4_pos_055}
The commercial opens in a cluttered, laboratory-like \textbf{room}.
Two adults in white lab coats sit close together at a desk, watching a small monitor on a shelf.
The man, who has glasses and tied-back hair, leans in from the left ; the woman, with dark hair and glasses, sits on the right and gestures toward the screen.
Several blue-and-green Swiffer Wet packages are stacked in front of them, making the product name clearly visible.
Shelves behind them hold books and scientific-looking \textbf{props}, giving the scene a mock research-lab feeling.
The setting shifts to a bright, colourful daycare classroom with glossy white floors, blue and yellow walls, low \textbf{tables}, small \textbf{chairs}, toys, drawings, and children playing.
A blonde adult woman, likely a caregiver, walks through the \textbf{room} wearing an orange short-sleeved top, white cropped pants, and white shoes.
Young children sit and play at \textbf{tables} and on the floor.
In one area, toddlers gather around a yellow play \textbf{bin} with toy vehicles and blocks.
A close view of the product shows a blue-and-green Swiffer Wet box behind a green plastic tray filled with folded white wet \textbf{cloths}.
A pale hand presses a finger into the thick \textbf{cloth}, showing its softness and moisture, while the light blue mop head and handle rest on top.
The Swiffer Wet logo is large and readable on the package.
Back in the daycare, a small blonde child in a white shirt looks up while holding a thin object like a paintbrush or stick, wide-eyed and \textbf{curious}.
Then a man in a white lab coat appears in the doorway holding a small white puppy and a Swiffer mop.
He lowers the puppy onto the shiny floor.
The puppy trots forward, leaving a trail of dark muddy \textbf{paw} prints across the white surface.
Toys and children ’s \textbf{chairs} sit nearby, and several children watch from around the \textbf{room}.
The lab-coated man steps back toward the doorway as the \textbf{dog} wanders among the children.
The puppy continues across the floor, leaving more black \textbf{paw} marks.
A child peers from inside a large plastic play structure, mouth open in surprise.
Several children gather around the puppy and reach out to \textbf{pet} it while the muddy \textbf{paw} prints spread around them.
The \textbf{dog} stands calmly in the middle of the group as small hands touch its back and sides.
The blonde caregiver in the orange shirt stands near the blue wall, one hand on her hip, looking down at the mess.
A \textbf{little} girl with long dark hair stands close beside her.
The caregiver points toward the floor where the \textbf{paw} prints are scattered, then looks thoughtful but composed.
She begins cleaning with the Swiffer Wet mop.
The rectangular mop head glides over the glossy white floor, passing directly across the muddy \textbf{paw} prints.
As it moves, the dark marks disappear, leaving a clean, shiny surface behind.
The caregiver lifts the mop and turns it toward herself, showing the underside of the white cleaning pad now darkened with collected dirt.
She looks at the soiled pad with a satisfied, slightly \textbf{amused} expression.
More muddy \textbf{paw} prints appear across the floor, and the mop is pushed through them in smooth strokes.
The blue mop head moves between children ’s shoes and around classroom \textbf{furniture}, wiping away the \textbf{paw} marks.
The caregiver walks through the \textbf{room}, continuing to clean as children sit along a bench and at small \textbf{tables}.
She maneuvers the mop around \textbf{chair} legs and past toys, including a small blue cup lying on the floor, without needing a bucket or traditional wringer nearby.
Near a \textbf{blue-and-white} wastebasket, the caregiver crouches and reaches for it.
She lifts the \textbf{bin}, then carries or tilts it as she continues managing the cleanup.
In another part of the \textbf{room}, children watch as she moves confidently through the classroom with the Swiffer mop.
One boy kneels on the floor holding a grey trash can with a yellow lid while the mop lies nearby, and another child stands beside the mop handle.
The caregiver smiles broadly as she peels the dirty wet \textbf{cloth} from the mop head.
The \textbf{cloth} is visibly dark and grimy on one side, with a clean white strip still showing along the edge.
She holds it up proudly, then lifts it away for disposal.
A boy holding the grey trash can looks up at her.
She bends down toward him, smiling and gesturing as if praising or instructing him, while he holds the can steady and then smiles toward the viewer.
The commercial ends with the product displayed on the clean white floor : a blue Swiffer Wet box with the large white “ Swiffer Wet ” logo and green accents.
Dark muddy \textbf{paw} prints surround the package, visually tying the product to the daycare cleanup shown throughout.

% matched lemmas: amuse, bin, blue-and-white, chair, cloth, curious, dog, furniture, little, paw, pet, prop, room, table
\end{textsample}
