\begin{textsample}{POS Dim 4 – 1970 – Score 6.00 – 1970/tv\_com\_1970\_75.txt}  \label{ex:f4_pos_065}
The commercial begins with a dark background containing a smaller rectangular image, as if a film or slide is being shown within the frame.
Inside that inset image, a baby is in a bathtub or sink-like basin.
An adult leans over the child, with hands near the \textbf{water} and the child ’s body.
The colors are \textbf{warm} and slightly washed out.
The image of the baby bathing becomes more central and larger.
The adult ’s upper body and hair are visible as they bend over the baby.
The baby is partly submerged or seated in the basin, with one arm resting forward.
The setting appears to be a bathroom, with tiled or vertical surfaces in the background.
The sequence then shifts into a multi-panel or sliding-screen layout.
The baby-bath image remains on the left while a new image appears on the right : a close-up of a baby sitting in a bath, with an adult woman leaning close beside the child.
The woman ’s long hair falls forward as she looks down toward the baby.
The baby faces forward with a neutral or slightly serious expression.
A bathroom window or wall fixture is visible behind them.
The baby-and-woman image fills the frame for a moment.
The woman remains bent close to the baby, and the baby ’s upper body and arms are visible above the edge of the tub or basin.
The lighting remains \textbf{warm} and yellowish.
Another sliding transition introduces a new panel on the right : a close-up of an adult man ’s face.
He appears to be \textbf{touching} or pressing his fingers against his cheek or around his mouth/chin area, as if checking or washing his face.
He has dark hair and a mustache.
The background behind him has vertical striped or tiled patterns.
The man ’s face then occupies the central frame.
His hands remain raised to his face, with fingers on his cheek and chin.
The camera stays close, emphasizing facial skin and grooming or washing action.
A split-screen transition follows.
On the left, the man ’s close-up remains partially visible ; on the right, a new image appears of an adult woman with short or wet-looking hair, seen from the shoulders up against a bright pale background.
She raises one arm behind her head, suggesting bathing or washing.
Her shoulders are bare or minimally covered.
The word “ Today ” appears centered over this image in dark text.
The commercial then cuts to a close-up of a \textbf{blonde} woman wearing a headband.
She has visible white foam or cream on both cheeks and around the nose/mouth area.
Her hands are on her face, spreading or rubbing the foam.
The shot emphasizes face washing or lathering.
The next major visual is a product shot : a boxed \textbf{bar} of Safeguard soap placed on a reflective surface.
The \textbf{package} is cream-colored with dark and colored graphic elements.
The brand name “ Safeguard ” is large and prominent.
Smaller text on the box includes “ deodorant and antibacterial soap, ” though some of the smaller wording is difficult to read clearly.
A decorative glass or plant-like object appears to the right in the background.
The final product shot shows another boxed Safeguard \textbf{package}, labeled “ Beige Safeguard. ” The box is centered against a simple background.
Large on-screen text beneath the \textbf{package} reads : “ New deodorant Safeguard with twice the lather. ” The commercial then cuts to black.

% matched lemmas: bar, blonde, package, touch, warm, water
\end{textsample}
