\begin{textsample}{POS Dim 4 – 2020 – Score 16.00 – 2020/tv\_com\_2020\_103.txt}  \label{ex:f4_pos_012}
An adult man stands in a bright \textbf{living} \textbf{room}, holding and folding a soft grey item, possibly \textbf{laundry}.
He has short dark \textbf{curly} hair, a goatee, and wears a light grey sweater with grey pants.
Around him are a blue \textbf{sofa} with patterned and yellow pillows, houseplants, framed wall \textbf{art}, shelves, and a \textbf{staircase} with a gallery wall, giving the \textbf{room} a warm family-home feel.
A young girl appears in another sunlit area of the \textbf{home}, near a glass-paned door and children ’s storage shelves.
She has dark hair in two braids and wears \textbf{denim} \textbf{overalls} over a \textbf{striped} \textbf{long-sleeve} shirt, a red backpack, \textbf{bracelets}, and white sneakers with colourful accents.
She walks through the \textbf{room} dragging a floppy, beige stuffed bunny by one ear or \textbf{paw}.
Close to the floor, the plush toy trails along the wood floor beside her shoes, its long ears and soft body brushing the ground as she steps forward.
The girl lifts the stuffed bunny up to her face and presses it against her mouth and nose, cuddling it closely with both hands.
Her eyes peek over the toy.
The man is then seen in close-up, looking alert and concerned, as if he has noticed the toy being dragged and then hugged.
Back in the \textbf{living} \textbf{room}, the girl smiles and swings the stuffed bunny forward.
The man suddenly lunges across the \textbf{room} in an exaggerated protective pose, arms spread wide and body stretched out horizontally, as if diving to intercept the toy.
Large bold white words appear across the scene : “ PROTECT MODE. ” The phrase stays on screen as he flies past the blue \textbf{sofa}, mouth open and eyes wide, reaching toward the plush bunny at the right side of the \textbf{room}.
The moment is playful and dramatic, with the father presented like a superhero reacting to a possible mess or germ risk.
The man lands back in motion holding the stuffed bunny, while the girl ’s arm remains outstretched from the right side of the \textbf{room}.
A small line of text appears near the bottom : “ Use as directed. ” The bunny is dropped into a white \textbf{laundry} basket filled with clothes.
Inside the basket, a white bottle with a blue cap is visible among the fabrics.
The label identifies it as Lysol Laundry Sanitizer, with “ 0 \% Bleach ” visible on the front.
The product is then shown more clearly on a laundry-room counter.
A hand holds the white Lysol Laundry Sanitizer bottle upright, label facing forward.
The bottle has a rounded shape, a blue cap, and a \textbf{blue-and-white} label with the Lysol logo and “ Laundry Sanitizer ” prominently displayed.
A pale yellow \textbf{laundry} bottle sits blurred in the background.
The stuffed bunny appears inside a front-loading washing machine, surrounded by light-coloured \textbf{laundry}.
The man ’s hand closes the round glass door, leaving the bunny visible through the window at the center.
The “ Use as directed ” text remains near the bottom.
The man then stands beside the washer with the Lysol Laundry Sanitizer bottle on the counter and the blue cap in his other hand, suggesting he is adding it to the \textbf{laundry} routine.
After washing, the girl sits on the blue \textbf{sofa} holding the stuffed bunny close to her chest.
She smiles broadly, then squeezes the bunny in a hug, looking happy and comfortable.
The \textbf{living} \textbf{room} background remains softly lit, with the \textbf{staircase} and wall \textbf{art} behind her.
The commercial ends with a product display on a white surface : two bottles of Lysol Laundry Sanitizer with blue caps stand side by side, one larger and one smaller.
A red label above the smaller bottle reads “ NEW TRIAL SIZE. ” Large white text on the right says, “ TRY FOR UNDER \$5. ”

% matched lemmas: art, blue-and-white, bracelet, curly, denim, home, laundry, live, living, long-sleeve, overall, paw, room, sofa, staircase, striped
\end{textsample}
