\begin{textsample}{POS Dim 4 – 1970 – Score 17.00 – 1970/tv\_com\_1970\_76.txt}  \label{ex:f4_pos_082}
The commercial opens on a black background with a bright, \textbf{decorative} title card.
In glowing pink and orange lettering, surrounded by a flower-like retro border, the words “ Once Upon a Time ” appear.
The scene changes to a small, theatrical boutique display packed with mannequins, clothing, accessories, shiny shelves, and hanging globe lights.
The lighting is saturated and dreamlike, with deep black shadows and washes of hot pink, blue, green, and purple.
In the center foreground sits a feminine mannequin dressed entirely in pink : a soft pink dress with long \textbf{sleeves}, large round pink \textbf{sunglasses}, \textbf{curly} pink hair or wig styled in bunches at the sides, and long \textbf{necklaces} hanging over her chest.
Her face has a doll-like, fixed expression, with a small open mouth and \textbf{decorative} spots or \textbf{flowers} on the \textbf{cheeks}.
Around her are other mannequin figures : to the left, a blue mannequin in a hooded blue outfit with a dramatic \textbf{necklace} and one arm raised ; to the right, a green mannequin in flowing green clothing with a veil or long scarf over the head, a large black star painted over one eye, and an arm lifted as if posed mid-dance.
Behind them are more fashion display figures and hanging lights, including a pale mannequin head in \textbf{sunglasses}.
A dark-haired, adult feminine figure in a yellow or gold outfit moves among the displays behind the pink mannequin.
She wears a \textbf{sleeveless} or short-sleeved yellow \textbf{garment} with a matching scarf or vest, and her dark hair is styled in a rounded bob.
She leans toward the seated pink mannequin, looking down near the mannequin ’s arm and wrist, as if noticing what is missing from the outfit.
The pink mannequin remains seated with both arms slightly lifted, \textbf{palms} open, her \textbf{sunglasses} catching the colored light.
A close view of her face emphasizes her oversized glasses, curled pink hair, and blank, sad-looking doll expression.
The yellow-clad figure then turns toward the green mannequin, who stands partly hidden by a blue vertical panel and reflective shop fixtures.
The green mannequin ’s face, with the star over one eye and scattered small dots, is shown more closely under bright globe lights.
She wears a head covering or veil that \textbf{drapes} down the sides of her face, and long strands or beads hang over her chest.
The mood remains like a fashionable, nighttime window display.
Attention shifts to the blue mannequin on the left.
She is posed in a flowing blue outfit, with one arm bent above her head and the other hand at her waist.
Large layered \textbf{necklaces} hang down the front of the \textbf{garment}.
The yellow-clad figure moves nearby and gestures toward the blue mannequin ’s wrist area, again drawing attention to the absence of a watch.
The boutique set is dense with \textbf{props} : chrome poles, small shelves, \textbf{colorful} purses, hats, jewelry, and bright plastic-looking accessories.
Back in the central display, the pink mannequin sits with the yellow-clad figure standing behind her.
The yellow figure gestures and then moves away toward the left side of the boutique.
The pink mannequin turns her head, still wearing her round \textbf{sunglasses}, as if becoming alert.
The display becomes a still, balanced tableau again : the blue mannequin on the left, the pink mannequin at center, and the green mannequin on the right beneath glowing hanging lights.
Then the mannequins appear to come to life.
The pink mannequin shifts from her seated pose, lowers her arms, and begins moving through the display.
The green mannequin on the right leans and raises an arm, her flowing \textbf{sleeve} and veil catching the green and magenta light.
The figures seem to awaken within the shop window, moving carefully among the shelves and hanging lamps.
The pink mannequin stands in her short pink dress, one hand resting near a small round \textbf{table} or shelf beside her.
She turns toward a display of accessories.
In profile, her curled pink hair, \textbf{sunglasses}, and long \textbf{necklace} are visible beneath bright globe bulbs.
She brings a hand up near her face as if thinking, then looks toward a collection of fashion items.
A small open case or trunk appears among the accessories.
It has a pale interior and shiny trim, with fringe-like strips hanging from the upper part.
The Timex name is visible inside the pale lid.
Around and inside the case are \textbf{colorful} objects : folded scarves or fabrics in pink and orange, a red rounded purse or case, a yellow spotted accessory, and multiple wristwatches laid out like jewelry.
The watches have different strap colors and styles, including white, black, and darker bands, with small metallic round or square faces.
The arrangement looks like a treasure box of fashion watches spilled over bright fabric.
The view lingers on the watch selection.
Several watches rest on soft, swirling pink and orange \textbf{cloth}, their metal cases glinting under the colored lights.
A white strap watch lies to the left, a dark strap watch with a round face lies toward the right, and other small watches with shiny faces are arranged across the fabric.
The open Timex case remains in the background, reinforcing the brand.
The pink mannequin bends over the accessories and reaches toward the display.
Her pink-sleeved arms move near the chrome shelf and the scattered watches, as if choosing one.
A close view then isolates one watch : a small, elegant wristwatch with a pale face and light-colored strap set against a textured deep pink background.
Its case is rounded-square with a shiny metal edge, and the Timex name is faintly visible on the dial.
The hands and simple hour markers are clearly shown.
Another mannequin ’s blue-gloved or blue-painted hands reach into the watch display.
The blue figure handles a watch delicately near the open case, lifting it from the fabrics.
A close view shows a different watch style : a round-faced watch with a \textbf{decorative} top loop and dangling ornament or chain-like piece below, presented against a rich blue background.
The face is pale with simple hour markers, and the case is silver-toned, resembling a jewelry-style watch or pendant-like fashion piece.
The green mannequin is shown reclining or leaning back in her flowing green outfit.
She raises one arm, then brings her wrist toward herself.
In close views, pale green hands fasten a watch around the wrist.
The watch has a white or light dial and a dark strap.
A close-up follows, showing the watch face large against green fabric : a round, silver-toned case, pale face, dark hour markers, and a dark strap, with the Timex name visible on the dial.
The pink mannequin, now more animated, lifts a soft green scarf or piece of fabric near her face and chest, trying it as an accessory while standing at the shelf.
She tilts her head upward, still in round \textbf{sunglasses}, as if admiring the look.
Nearby, a \textbf{striped} hat or stack of \textbf{striped} accessories sits on the shelf above her.
The blue mannequin also examines her wrist near the shelves, her blue face and hooded outfit lit by bright magenta and blue light.
She adjusts or checks a watch while standing beside a small red mannequin-hand display and the same chrome shelving.
The group returns to a wide boutique arrangement.
The blue mannequin stands left in her \textbf{draped} blue \textbf{garment} and jewelry ; the pink mannequin stands center in her pink dress, one hand on her hip and the other arm extended ; the green mannequin stands right in flowing green, holding an arm outward.
The boutique feels full of movement and color, with glowing bulbs and reflective surfaces all around them.
The watches are shown again on the bright fabrics near the open Timex case.
Several styles remain spread out : small round and square faces, light and dark straps, and shiny metal cases.
The display emphasizes variety, with the watches \textbf{treated} like fashion accessories among scarves, purses, and jewelry.
The commercial ends on a black background with another bright retro title card.
In a pink \textbf{decorative} border, blue and white glowing text reads “ TIMEX FASHION WATCHES, ” with prices underneath shown as “ 9.95–19.95. ”

% matched lemmas: cheek, cloth, colorful, curly, decorative, drape, flower, garment, necklace, palm, prop, sleeve, sleeveless, striped, sunglasses, table, treat
\end{textsample}
