\begin{textsample}{POS Dim 4 – 1980 – Score 13.00 – 1980/tv\_com\_1980\_110.txt}  \label{ex:f4_pos_048}
A shadowy male-presenting young adult stands in the foreground at the entrance of a spacious, elegant \textbf{room}.
He is mostly in silhouette, with broad shoulders and a loose, light-colored shirt barely visible in the dim light.
Beyond him, the \textbf{room} opens into a sleek, staged-looking interior with pale walls, soft \textbf{built-in} lighting, a low circular seating area, glossy flooring, and tall blue-lit windows.
Near the windows, a young adult woman reclines on a white \textbf{lounge} \textbf{chair}.
She wears a blue-green swimsuit, round dark \textbf{sunglasses}, and small pale earrings, with her wavy hair pushed back as she rests in a relaxed, sunbathing pose.
The man ’s face is shown in deep shadow, then partly lit : he has \textbf{curly} hair, light eyes, and a watchful expression.
Across the \textbf{room}, the woman remains stretched out on the \textbf{lounge} \textbf{chair} against the glowing blue window backdrop.
In the foreground are sculptural \textbf{decorative} objects and a low glass \textbf{table}, giving the \textbf{room} a polished, modern feel.
A red Coca-Cola can briefly comes into view near the man, its white lettering recognizable as “ Coke. ” He appears to be holding it while looking toward the woman.
The woman is seen close up, still wearing her round mirrored \textbf{sunglasses}.
Her lips are slightly parted, and one hand rests near her mouth in a poised, \textbf{curious} gesture.
A hand then reaches to the top of a chilled red Coke can covered in water droplets.
Fingers hook under the pull tab and open it.
The can ’s red surface and large white Coke lettering fill the view, with condensation beading on the metal.
The woman lifts both hands to her \textbf{sunglasses} and raises them from her eyes.
Her expression is calm and intrigued, her face softly lit with dark eye makeup visible once the lenses move upward.
The man, now more visible, gives a small, confident smile from the shadows, his light shirt catching highlights while one side of his face remains dark.
He tilts the red Coke can, but instead of the liquid simply falling downward, a glossy brown stream of cola pours out sideways in a smooth, ribbon-like line.
The can is held in his hand against his shirt, the white “ Coke ” name clear on the red label.
The stream stretches out from the can as though traveling through the \textbf{room} on its own, catching highlights like a dark, sparkling \textbf{wave}.
The woman reclines in profile, her head resting against the \textbf{lounge} \textbf{chair} ’s white frame and black woven backing.
Her hair moves slightly around her face, and she turns her attention toward the approaching drink.
The cola stream passes through the elegant \textbf{room}, near a glass \textbf{table} with a metal vase of white \textbf{flowers}.
Droplets or reflections glint around the surface, emphasizing the liquid ’s motion.
A small terrier-like \textbf{dog} with wiry white and gray fur sits on a cushioned \textbf{sofa}, wearing a red collar with a round tag.
The \textbf{dog} looks alertly toward the action, ears perked.
Elsewhere in the \textbf{room}, a black grand piano stands beside a small bench, with \textbf{flowers} on top and sheet music open on the music stand.
The ribbon of cola passes in front of the open sheet music, making the pages flutter and bend as it moves by.
The piano brand lettering is faintly visible on the front.
The Coke can appears again in the man ’s hand, still tilted, with a few drops trailing from its opening.
A hand places or steadies a tall empty glass on a tabletop beside a clear ice bucket filled with ice.
The woman ’s round \textbf{sunglasses} now rest nearby at the base of the glass, linking the setup to her.
The cola stream continues across the pale wall like a thin, dark line, still suspended rather than spilling.
The woman lies back on the \textbf{lounge} \textbf{chair}, her blue-green swimsuit visible against the blue glow of the windows.
A tall glass is then shown at an angle as the cola stream enters it.
Ice inside the glass churns and flashes with bright reflections while the brown liquid swirls and rises, creating bubbles and foam near the top.
Finally, the woman lifts the filled glass to her mouth.
The drink is dark amber-brown with ice and a thick foamy head at the rim.
She takes a sip while looking forward with wide, direct eyes.
The foam brushes her upper lip as she drinks, and the glass catches bright highlights against the dim, stylish \textbf{room} behind her.

% matched lemmas: built-in, chair, curious, curly, decorative, dog, flower, lounge, room, sofa, sunglasses, table, wave
\end{textsample}
