\begin{textsample}{POS Dim 4 – 2020 – Score 19.00 – 2020/tv\_com\_2020\_48.txt}  \label{ex:f4_pos_005}
At an outdoor racquet club bar in bright daylight, a young woman with blonde hair in a high \textbf{ponytail} stands at the counter beside a young man in an orange athletic shirt.
She wears a \textbf{sleeveless} maroon tennis-style top with orange trim and dark \textbf{sunglasses}.
Tennis and pickleball courts, \textbf{patio} umbrellas, and people sitting and walking in the background establish a busy club setting.
She adjusts her \textbf{sunglasses}, smiles, and turns toward someone off to the side as if making a casual request or proposal.
A close view shows Michelob \textbf{ULTRA} being poured from a tap into a tall branded glass ; pale golden beer foams up, with the blue “ Michelob \textbf{ULTRA} ” logo and red vertical mark visible on the glass.
Back at the bar, the young woman and her male partner lean forward while two older players across from them listen.
The older woman has shoulder-length blonde hair and wears a navy-and-cream sporty sweater over a dark \textbf{long-sleeve} top ; the older man has short sandy-gray hair and wears a navy track jacket with white stripes.
Both rest near the counter, looking relaxed but alert.
Two full glasses of beer sit between the groups.
The older woman smiles knowingly, and the older man watches with a measured, slightly \textbf{amused} expression.
The young woman ’s expression shifts from confident to mildly uncertain as the conversation continues.
The scene moves onto a \textbf{sunny} pickleball court.
The young woman, now on court in her maroon top and pleated red-orange \textbf{skirt}, holds a paddle in one hand and a yellow pickleball in the other, standing behind the net with a confident posture. \textbf{Opposite} her, the older man and woman take their positions with paddles.
The older man smiles broadly, then lowers into a ready stance, gripping his paddle with focus.
The young woman serves, and the rally begins.
The older man swings hard, and the yellow \textbf{ball} flashes across the court.
The young pair, now both holding paddles, watch from their side with surprise.
The young woman ’s \textbf{ponytail} whips as she turns, and her expression tightens into disbelief.
The older man gives a smug, closed-mouth smile ; the older woman, equally composed, swings through another shot.
The young man in orange tries to return the \textbf{ball}, but the older pair remain in control.
After the point, the young woman is back at the bar looking sweaty and stunned, her hair \textbf{messier} and her face serious.
Her partner stands beside her, looking over toward the winners.
The older woman slides into view holding a tall Michelob \textbf{ULTRA} draft with a thick white head.
She beams, and the older man joins her with another full glass.
The two older players smile at each other and clink their tall beer glasses together, clearly pleased with their win.
The glasses are golden, branded with Michelob \textbf{ULTRA} markings, and held prominently in the foreground.
The older pair then walk down a wet, reflective corridor between chain-link court fences, carrying racquet \textbf{bags} and paddles.
Large bold white text appears over them : “ THE \textbf{ULTRA} HUSTLE. ” They stride forward with calm confidence, dressed like seasoned club players on a mission.
A fast series of matches follows, showing the older pair hustling different pickleball players in different locations.
The older man, now in a plain white athletic shirt, plays intensely against a younger curly-haired man in a blue shirt and headband.
Split-screen panels divide the action, showing the older man grimacing with effort, the opponent bracing for a return, and the older woman in dark \textbf{sunglasses} striking the \textbf{ball} with a steady, determined face.
Another opponent in a green shirt and black cap lunges in a separate panel.
On a rooftop court surrounded by tall city buildings, a muscular man swings at a yellow \textbf{ball}, and the \textbf{ball} fills the view before revealing a reward : a cluster of Michelob \textbf{ULTRA} bottles.
A man at a bar slides four brown glass Michelob \textbf{ULTRA} bottles forward, their white labels with blue and red accents facing outward.
The older pair continue scouting for beer.
From a grassy hilltop at golden hour, they stand beneath a large tree, both wearing light-colored sporty outfits and carrying \textbf{bags}.
The older man holds binoculars to his eyes.
Through the binocular-like view, two younger players sit on a bench in the sand beside a cooler filled with cans and bottles of Michelob \textbf{ULTRA}.
The older man points toward them while the older woman, in a white bucket hat and navy-and-white outfit, looks on.
At a seaside pickleball court near the ocean, the sun hangs low over the water.
The older woman in her bucket hat swings, then the older man follows with a shot, both playing in warm sunset light.
The younger pair are shown holding up their cooler full of Michelob \textbf{ULTRA}, looking resigned as if surrendering the prize.
A split-screen product exchange follows.
On one side, hands hold a cooler stocked with Michelob \textbf{ULTRA} cans and bottles ; on the other, hands lift a white, blue, and red Michelob \textbf{ULTRA} bottle carrier.
The packaging is clearly branded “ \textbf{ULTRA}, ” with visible numbers such as “ 95 ” on the side, reinforcing the product ’s low-calorie branding.
More hands pass around boxed Michelob \textbf{ULTRA} packs, showing the beer as the stake or prize of each match.
The older man keeps playing, now in a \textbf{sleeveless} gray athletic top, returning a yellow \textbf{ball} with sharp concentration.
A younger woman with long \textbf{curly} hair and yellow-tinted glasses tries to return a shot on a \textbf{sunny} court.
The older man laughs afterward, relaxed and delighted, still holding his paddle.
Another match shows two opponents in matching light-blue shirts on a pickleball court.
The shirts read “ PRO vs PRO Pickleball Jamboree 2025, ” marking them as serious or professional players.
One is a woman with a \textbf{ponytail}, and the other is a tall Black man with a short beard ; both hold paddles and move in ready stances.
The man spreads his arms in disbelief, as if questioning the older pair.
The older woman, wearing \textbf{sunglasses} and a \textbf{cream} textured short-sleeve top over black \textbf{sleeves}, calmly returns a shot.
She then raises one finger with a composed, lecturing gesture, looking unbothered.
Split-screen panels show her on the left while the blue-shirted woman smiles tensely on the right, and other panels show a red-shirted player gripping a yellow pickleball.
The older woman continues talking and gesturing with cool assurance.
A close-up of the older man appears in a darker, more dramatic setting.
He wears large black wraparound \textbf{sunglasses} ; reflected in the lenses are bright indoor lights and glimpses of the commercial ’s pickleball and beer imagery.
His face is serious, almost calculating.
The image then opens into a large indoor pickleball arena with stands full of spectators.
Large wall graphics read “ Michelob \textbf{ULTRA} ” and “ GLEAM Pickleball. ” The court is dark \textbf{teal} and black, with “ \textbf{ULTRA} ” branding along the sideline.
In the arena match, the older man in the gray \textbf{sleeveless} top swings powerfully.
Across the net, a female professional-looking player in a \textbf{teal} outfit and white cap prepares and then hits a return.
The older blonde woman, now in a black-and-white outfit, strikes the \textbf{ball} on the other side.
The rally becomes more athletic and dramatic : one teal-clad male player watches the \textbf{ball} overhead, while the older man leaps high near the net, paddle raised, and smashes the \textbf{ball} down.
The \textbf{ball} lands inside the court near a white boundary line.
The older man lifts both arms in victory, paddle in one hand, as the blurred crowd behind him stands and reacts.
The victory image dissolves into a dim, elegant \textbf{lounge} or trophy \textbf{room}.
Tall refrigerated cases on both sides are stocked with Michelob \textbf{ULTRA} packs, glowing cool white in the dark \textbf{room}.
A large silver trophy sits on a pedestal near the center, and shelves of beer packaging line the back wall.
The refrigerator doors slide past rows of white, blue, and red Michelob \textbf{ULTRA} packaging.
A final close-up returns to the product : beer pours into a tilted Michelob \textbf{ULTRA} glass, golden bubbles rising beneath a white foam head.
Across the center of the image, white capital letters read : “ SUPERIOR IS WORTH PLAYING FOR. ” In the closing view, the older man stands in the \textbf{lounge} holding up a full Michelob \textbf{ULTRA} draft glass, smiling with quiet satisfaction.
The older woman sits beside him with her own beer, smiling warmly.
Behind them are the trophy, stocked refrigerators, and shelves of Michelob \textbf{ULTRA}.
The final logo appears large in the center : “ Michelob \textbf{ULTRA}, ” with “ SUPERIOR LIGHT BEER ” beneath it, while small responsible-drinking and legal text runs along the bottom.

% matched lemmas: amuse, bag, ball, cream, curly, long-sleeve, lounge, messy, opposite, patio, ponytail, room, skirt, sleeve, sleeveless, sunglasses, sunny, teal, ultra
\end{textsample}
