\begin{textsample}{POS Dim 4 – 1950 – Score 16.00 – 1950/tv\_com\_1950\_3.txt}  \label{ex:f4_pos_034}
The commercial opens in a carefully arranged, black-and-white \textbf{home} interior with no people present.
A bright, smooth floor fills much of the foreground, laid out in large irregular geometric sections with dark dividing lines.
To the left is a \textbf{striped} \textbf{sofa} with rounded arms, pillows, a small side \textbf{table}, and a shaded lamp.
Plants stand near a central wall.
Through a large rounded archway in the background is a dining area with a round \textbf{table}, several \textbf{chairs}, \textbf{striped} wall treatment, \textbf{potted} plants, and a large globe-shaped hanging light.
The emphasis remains on the clean, light-coloured floor stretching between the \textbf{living} and dining spaces.
The setting changes to another \textbf{room}, like a \textbf{home} office or den.
A glossy patterned floor dominates the lower half of the scene, reflecting the \textbf{table} and \textbf{chair} legs.
The floor has a bold star-like or crisscross design made from contrasting light and dark strips.
Against the back wall are \textbf{built-in} shelves with books and \textbf{decorative} objects.
In front of them is a small writing \textbf{table} or desk with thin metal legs, a \textbf{chair}, papers or accessories on top, and a large old-fashioned telephone or office machine sitting to one side.
A small round side \textbf{table} and an upholstered \textbf{chair} appear to the right as the \textbf{room} widens into view.
Another \textbf{home} interior appears, this time a \textbf{living} \textbf{room} with a fireplace.
A plaid \textbf{sofa} sits on the left, an upholstered \textbf{chair} on the right, and a small glass-topped \textbf{table} stands between them.
The fireplace opening is dark, with small \textbf{decorative} objects on the hearth and mantel.
The floor is highly polished, with large square panels bordered by dark strips, forming a grid.
Reflections from the \textbf{furniture} and light shimmer on the surface, again drawing attention to the floor ’s shine and pattern.
The scene then changes to a bright kitchen or breakfast nook.
White cabinets line the left side, a door with frosted or patterned glass is on the right, and a small writing desk or counter with a white \textbf{chair} sits in the centre back.
A vase of \textbf{flowers} rests on the desk, with a \textbf{leafy} \textbf{potted} plant beside it.
The floor is a checkerboard of light and dark square tiles.
Bold white capital letters appear across the lower part of the screen : “ KENTILE EASY CLEAN VINYL. ” The view settles lower on the checkerboard floor, and more text appears near the bottom : “ \$33.95 FOR 8X10 AREA. ” The price remains over the floor while the \textbf{chair}, plant, desk, and glass door stay in the background.
A woman is then shown kneeling on the floor during installation.
She appears to be a young adult, with curled, mid-length hair, wearing a practical button-front top with rolled \textbf{sleeves} and light trousers or work clothes.
Beside her is an open can of adhesive.
She uses a brush to spread dark adhesive over an existing floor surface, working close to the base of a cabinet or wall.
Dark marbled vinyl tiles are already being placed in a row beside her.
She dips the brush into the can, then smooths adhesive onto the floor in broad strokes.
In a close view, the woman smiles as she holds a dark marbled tile in her hands and cuts it with scissors.
The tile bends slightly as she trims it, showing it is thin enough to cut by hand.
The scissors make a neat cut through the vinyl, and a narrow piece separates from the larger square.
She then returns to the floor and presses tile pieces into place along the edge of a cabinet or wall, using her hands to smooth and align them.
A rectangular tile is fitted into a corner area, and she adjusts it carefully so it sits flush with the surrounding tiles.
A graphic demonstration follows : a stack or layered arrangement of dark marbled vinyl squares is shown against a plain background.
Over it, the word “ VINYL ” repeats vertically in large white letters across the screen, visually stressing that the material is vinyl throughout.
The layered tiles overlap like thin sheets, with their marbled pattern visible on the exposed surfaces.
The kitchen checkerboard floor returns with a dark greasy spill spread across one light square tile.
At the bottom of the screen, bold white text reads “ GREASEPROOF. ” A mop or squeegee enters from the right and pushes through the spill.
As it passes over the tile, it clears away the dark mess, leaving the light square visibly clean behind it.
The tool continues across the tile, gathering the spill into a smaller area and demonstrating that the surface wipes clean.
The woman now stands in the kitchen wearing a neat mid-century dress with a fitted waist and full \textbf{skirt}, dark low heels, and styled hair.
She mops the checkerboard floor near the white \textbf{chair} and flower-filled desk.
The floor looks clean and glossy.
She finishes mopping, lifts the mop upright, and steps toward the glass door on the right, carrying the mop with an easy, tidy posture.
She exits out of view, leaving the spotless checkerboard kitchen visible.
The kitchen fades into a close view of an open telephone directory or classified pages lying on a surface, with a pencil across the page and a rotary telephone behind it.
Listings and advertisements are visible ; one section includes flooring-related text and “ KENTILE ” in an ad.
Over the open directory, a boxed logo appears in large block letters : “ KENTILE FLOORS. ” The logo sits centred over the printed pages.
Finally, the commercial returns to a close view of the checkerboard vinyl floor.
The dark tiles have a marbled streaked texture, and the light tiles are plain and bright.
Across the centre, in a flowing script, the words “ Easy Clean Vinyl ” appear, ending on the product name over the clean tiled surface.

% matched lemmas: built-in, chair, decorative, flower, furniture, home, leafy, live, living, potted, room, skirt, sleeve, sofa, striped, table
\end{textsample}
