\begin{textsample}{POS Dim 4 – 2020 – Score 16.00 – 2020/tv\_com\_2020\_48.txt}  \label{ex:f4_pos_031}
The commercial begins at an \textbf{outdoor} racquet-sport venue in bright daylight.
Several people stand near a court-side counter or \textbf{bar} area.
A \textbf{young} man in an orange athletic shirt holds dark gear, while a \textbf{young} woman in a burgundy-red tennis-style outfit and sunglasses stands beside him.
Other people and umbrellas are visible in the background near fenced courts.
The next shot is a close-up of beer being poured into a \textbf{tall}, tilted glass.
The glass is branded “ Michelob ULTRA, ” with pale golden beer and foam forming inside.
The scene returns to the \textbf{outdoor} venue.
A middle-aged \textbf{blonde} woman and a middle-aged man in navy athletic jackets lean over a table or counter, looking toward someone off-camera.
Two glasses of beer are blurred in the foreground.
The pair appear amused and attentive, with the man slightly behind the woman.
Subsequent close-ups show them continuing to look off to the side, smiling or reacting.
The man and woman then appear \textbf{walking} near fenced courts.
The man, still in a navy track jacket, smiles broadly while moving forward.
The \textbf{blonde} woman stands farther back, holding a paddle and watching.
The action shifts onto a \textbf{sunny} \textbf{outdoor} court.
The \textbf{young} woman in the burgundy-red outfit prepares to play, holding a paddle and a yellow ball.
In a wider view, she stands with the \textbf{young} man in the orange athletic shirt, both holding paddles and facing the court.
Other players are visible in the background.
The \textbf{young} woman then turns and \textbf{walks} near the net, her hair moving as she looks across the court.
The \textbf{blonde} woman in the white \textbf{sleeveless} sweater over a dark long-sleeve top appears in motion on the court, holding a paddle.
She looks upward and swings or moves as if tracking the ball.
Her expression is focused and energetic.
A cut returns to the \textbf{young} pair at the bar/counter area.
The \textbf{young} woman looks tired or unimpressed, leaning forward slightly, while the \textbf{young} man stands beside her in the orange shirt, holding his hands near his chest.
The middle-aged man then appears on a court in a white T-shirt, turning his body and extending an arm as if making or following a shot.
The setting remains outdoors, with court fencing and distant buildings visible.
The commercial then moves to a different \textbf{outdoor} location near the coast at \textbf{sunset} or golden hour.
From a distance, two people are seen on a grassy \textbf{rise} under a large tree.
Another shot, framed as if viewed through binoculars, shows two people seated on sand near a cooler filled with cans or bottles.
A wide aerial view shows a curved coastal court or recreation area beside the ocean, with long shadows and the sun low over the \textbf{water}.
A closer shot shows a man and a woman by the ocean holding or carrying a cooler full of \textbf{colorful} cans or bottles.
The woman wears a white cap and \textbf{sleeveless} white top ; the man wears a white T-shirt.
They look toward someone off-frame.
The action returns to racquet-sport play.
The middle-aged man now wears a \textbf{sleeveless} gray athletic top and holds a paddle overhead, preparing to hit.
A \textbf{young} woman with long hair in a white top and patterned skirt or shorts also swings a paddle on an \textbf{outdoor} court.
Another \textbf{group} appears wearing matching light-blue shirts.
A Black man in a blue shirt smiles and gestures with arms extended while holding a paddle.
The shirt has visible white text including “ PRO vs PRO, ” though the smaller text is not fully legible.
A wide shot shows him and a female teammate positioned on a court, both ready to play.
The woman in the blue shirt is then shown running or turning near the net.
The commercial shifts to a nighttime or indoor-stadium-like court with spectators.
The middle-aged man in the gray \textbf{sleeveless} top makes an intense swinging motion.
A man in a \textbf{teal} shirt and backward cap looks upward, with a large green wall behind him showing “ Michelob ULTRA ” branding.
Another shot shows the court surface and boundary line, suggesting a ball has landed near the line, though the ball is not clearly visible in that frame.
The middle-aged man then raises both arms in celebration while holding his paddle, with a blurred crowd cheering or reacting behind him.
The final scene takes place indoors in a sleek, dimly lit room resembling a \textbf{lounge} or retail display space.
Illuminated refrigerators line the sides, and shelves or product displays appear in the background.
A large silver trophy sits on a \textbf{pedestal} behind the two main older players.
The man stands holding a glass of beer ; the \textbf{blonde} woman sits in front of him, smiling and also holding a beer.
Small legal/disclaimer text appears along the bottom but is too small to read fully in the sampled frame.
The final frame overlays the product branding prominently in the center : “ Michelob ULTRA ” with the red vertical mark, and below it the text “ SUPERIOR LIGHT BEER. ” The man raises his glass slightly while the woman smiles below the logo.
The trophy and product displays remain visible in the background.

% matched lemmas: bar, blonde, colorful, group, lounge, outdoor, pedestal, rise, sleeveless, sunny, sunset, tall, teal, walk, water, young
\end{textsample}
