\begin{textsample}{POS Dim 4 – 1970 – Score 5.00 – 1970/tv\_com\_1970\_17.txt}  \label{ex:f4_pos_070}
The commercial opens on a beach beside the ocean.
Two people ride horses along the shoreline, moving across the frame with the sea and pale sky behind them.
The image is soft and slightly blurred, with a “ Classic Commercial Archives ” watermark visible.
A close-up follows of a \textbf{blonde} woman in profile, outdoors against a bright blue sky.
Her hair is \textbf{blown} back by the wind, suggesting the same seaside setting.
The scene then returns to the riders at a closer distance.
A shirtless man is in the foreground on a horse, with the \textbf{blonde} woman behind him on another horse.
They appear relaxed and smiling.
The beach/ocean background remains visible.
Next, the man and woman are shown together at a low angle.
The man holds a dark glass bottle close to his mouth, while the woman stands beside him holding a rounded wine glass containing a pale golden \textbf{drink}.
She is wearing a swimsuit or beachwear.
The sky fills most of the background.
A soft dissolve overlays the man, the woman, a filled wine glass, and a \textbf{tall} bottle, creating a layered, dreamy image.
The bottle is visible on the right, but the label is not clear in this frame.
There is then a close-up of the \textbf{blonde} woman ’s face, warmly lit and slightly soft-focused.
She looks toward the camera or just past it, with the bright \textbf{outdoor} background behind her.
The commercial cuts to a product shot : three bottles standing side by side.
They appear to be different varieties or colors—green, dark/purple, and reddish.
Each bottle has a label with a central red emblem or flower-like design and a triangular mark below it.
Most label text is too blurred to read clearly.
The final frame returns to the beach.
A person rides a white horse in the distance, seen through \textbf{tall} grasses or reeds in the foreground.
Large black on-screen text reads : “ Giroblaza someone tonight. ” Smaller text appears near the bottom, but it is too blurred to read reliably.

% matched lemmas: blonde, blow, drink, outdoor, tall
\end{textsample}
