\begin{textsample}{POS Dim 4 – 1990 – Score 13.00 – 1990/tv\_com\_1990\_49.txt}  \label{ex:f4_pos_077}
At dawn, a warm, sunlit bedroom is shown with tall windows and \textbf{sheer} white \textbf{curtains} glowing orange from the morning light.
A large bed with white \textbf{bedding} fills the \textbf{room}, and a person lies mostly hidden under the covers, only a head visible near the right side.
A small bedside \textbf{table}, lamp, \textbf{chair}, and a neat, \textbf{cozy} arrangement of \textbf{furniture} create a lived-in \textbf{home} atmosphere.
Over the bedroom scene, the product name appears in white and red : “ Kellogg ’s Nutri-Grain Bars. ” The person in bed stirs and sits up abruptly under the white comforter, suggesting a rushed start to the morning.
The scene moves into a bright bathroom with pale walls, a sink, mirror, towels on a rail, and louvered windows throwing strong bands of sunlight across the \textbf{room}.
A light-skinned adult man, likely in his thirties, stands in a white dress shirt and dark trousers, hurriedly working at a dark tie around his neck.
His short brown hair is neatly styled, but his posture is tense and bent forward toward the mirror as if trying to get ready quickly.
He keeps one hand at his collar and tie, glancing toward the doorway with a worried, distracted expression.
A light-skinned adult woman, also likely in her thirties, appears in a doorway.
She has voluminous \textbf{curly} brown hair, round earrings, and a polished work outfit in a warm tan or reddish-brown color.
She raises both hands slightly in a calming or “ wait ” gesture, then moves briskly past the doorway.
Her expression is alert but upbeat, and she seems to be taking charge of the hurried morning.
In the kitchen, morning light streams through large windows and a glass-paned back door.
The \textbf{room} is bright and \textbf{domestic}, with a refrigerator on the left, white cabinetry, a counter or small \textbf{table} on the right, and papers or work items near an open cereal-bar box.
The woman stands by the counter holding a red-wrapped bar.
The man, now wearing a dark suit jacket over his white shirt with a patterned tie, steps in beside her.
She offers him the bar, and he looks down at it as he takes it, still appearing preoccupied.
The product is then shown prominently.
A white box with large red lettering reads “ Kellogg ’s Nutri-Grain, ” with pictures of strawberries and bars filled with red \textbf{fruit}.
Smaller text on the front says “ Made with real \textbf{fruit} ” and “ No preservatives, ” and the flavor shown is “ Strawberry. ” A hand reaches into the open box and pulls out a red individual wrapper.
The wrapper itself reads “ Kellogg ’s Nutri-Grain Cereal Bar Strawberry ” in large white letters on a red background.
The woman is shown in close view as she speaks, smiling and looking toward the man.
Her curled hair catches the backlight, and her gold-toned earrings are visible.
She appears confident and encouraging, as if explaining the bar to him.
Fingers tear open the red wrapper, peeling it back to reveal a golden-brown rectangular bar with a soft, textured crust.
As more of the wrapper is pulled down, the baked crust is shown close up, with a reddish \textbf{fruit} filling visible along the edge.
The bar is displayed even more closely : its tan, grainy surface fills the view, held between fingers at both ends.
A crack opens through the middle of the crust, widening to reveal a moist red strawberry filling inside.
Small copyright text appears at the lower right during this product close-up : “ {\EmojiFont ©} 1991 Kellogg Company ” and “ {\EmojiFont ®} Kellogg Company. ” Back in the kitchen, the man bites into the partly unwrapped Nutri-Grain bar.
His face tightens briefly as he takes the bite, then he chews, his expression shifting from skepticism to approval.
He looks forward with a more settled, pleased face, as if surprised that he likes it.
The kitchen scene returns to both adults.
The woman, still in her tan suit, swings a matching shoulder \textbf{bag} onto her arm and begins getting ready to leave.
The man stands by the counter with the open Nutri-Grain box in front of him, holding the red-wrapped bar in one hand and chewing.
He gestures and looks toward her while she adjusts her purse strap.
She leans toward the counter and pulls out or opens a large tan work \textbf{bag} or portfolio with a dotted pattern, checking inside as if gathering papers for the day.
The man fusses with his suit jacket and tie, still holding the bar, while the box remains clearly visible on the counter between them.
The woman finishes closing or arranging the large \textbf{bag} and moves toward the door.
The man turns with her, both now facing the glass-paned exit.
She carries her shoulder \textbf{bag}, and he follows with the bar still in hand.
The kitchen remains bathed in soft morning light, reinforcing the sense of a busy weekday departure.
The commercial ends with a clean product display against a dark background : the white Kellogg ’s Nutri-Grain Cereal Bars box, strawberry flavor, with red strawberries and images of the golden bars with red filling on the front.
Across the bottom, large white text reads, “ Start your morning off right. ”

% matched lemmas: bag, bedding, chair, cozy, curly, curtain, domestic, fruit, furniture, home, room, sheer, table
\end{textsample}
