\begin{textsample}{POS Dim 4 – 1990 – Score 14.00 – 1990/tv\_com\_1990\_95.txt}  \label{ex:f4_pos_074}
A sleek white twin-propeller airplane flies head-on over rugged, reddish-brown canyon terrain.
Its long, narrow wings stretch wide with upturned tips, and the two propellers blur as they spin.
The aircraft passes over rock formations, then over a blue body of water bordered by dry land, and finally appears from below against a clear blue sky, banking so its underside, tail, small oval windows, and red registration markings are visible.
The scene shifts to a spacious, warmly lit \textbf{living} \textbf{room} with a soft pink \textbf{carpet} filling the foreground.
Sunlight casts long horizontal bands across the \textbf{carpet}.
Floral upholstered \textbf{chairs} sit on both sides, with side \textbf{tables} and lamps nearby ; a fireplace is on the left, framed pictures hang on the walls, and an open doorway at the back reveals another \textbf{room} and a \textbf{staircase}.
Near a bright window, a baby with bare shoulders and a round face is held up by an adult woman with \textbf{curly} light-brown hair.
The baby smiles broadly and reaches toward her.
The woman faces the baby closely, smiling back.
The baby is lifted higher, leaning forward over the woman ’s face, both of them framed in soft, glowing light from the window behind them.
Back in the \textbf{living} \textbf{room}, a small white \textbf{ball} or soft round object bounces or rolls across the pink \textbf{carpet}, emphasizing the \textbf{carpet} ’s surface.
The setting changes to a theatrical stage.
In the foreground, dark silhouettes of seated audience members are visible.
Onstage, under hazy purple and amber lighting, a young woman with long dark hair performs in a vivid magenta and purple dress or wrap with shimmering details. \textbf{Decorative} stage scenery, \textbf{draped} \textbf{curtains}, plants, and ornate painted panels surround her.
She walks and turns gracefully, swinging a flowing pink fabric around her body.
The fabric fans outward in a wide circle, catching the colored light.
In closer views, she faces forward with a composed expression, wearing red earrings and an off-the-shoulder, glossy magenta \textbf{garment} trimmed with gold-like accents.
The translucent fabric sweeps across her face and body, then she poses with one arm raised, lit from behind by bright stage lights.
The commercial returns to the \textbf{living} \textbf{room}.
The white \textbf{ball} rolls across the pink \textbf{carpet} as two boys rush in from the right, playing roughly with hockey sticks.
An older boy, wearing a light shirt, jeans, and padded gloves, lunges low across the \textbf{carpet}, stretching toward the \textbf{ball} with a stick.
A younger boy in a dark sports-style top with \textbf{striped} \textbf{sleeves} clings to or rides on his back, his mouth open in excitement.
The older boy slides forward on his stomach, gloves scraping the \textbf{carpet}, while hockey sticks lie across the foreground.
The younger boy keeps hold of him as they tumble and skid together.
Other children join the pile, including a small blond child in a blue top, and they roll and scramble on the \textbf{carpet} in a playful heap.
As the children continue moving in the background, large bold white letters spelling “ BASF ” appear centered over the \textbf{living} \textbf{room} scene, filling much of the screen.

% matched lemmas: ball, carpet, chair, curly, curtain, decorative, drape, garment, live, room, sleeve, staircase, striped, table
\end{textsample}
