\begin{textsample}{POS Dim 4 – 1960 – Score 13.00 – 1960/tv\_com\_1960\_18.txt}  \label{ex:f4_pos_071}
The commercial begins with a nearly black screen.
A small white “ Nostalgic X’er ” watermark appears at the lower right and remains throughout the sampled frames.
A close-up then shows a \textbf{purple} billiard ball on a \textbf{pool} table, lit warmly with a blurred bright shape in the background.
The next shots reveal a \textbf{young} man leaning low over the \textbf{pool} table, aiming a cue.
Other billiard balls are visible on the felt.
A close-up shows his face as he looks forward with a slight smirk or concentrated expression.
The scene shifts to a \textbf{young} woman standing indoors near venetian blinds.
She wears a \textbf{sleeveless}, high-neck top and appears to be smiling or reacting to someone off-screen.
The lighting is \textbf{warm} and contrasty.
A tabletop or bar-like surface appears with several glass bottles and glassware ; patterned wallpaper is visible behind them.
A hand moves near the bottles, but the exact action is not fully clear from the sampled frame.
Next, numbered cards or squares are shown on a wall or board, with visible numbers “ 21, ” “ 22, ” “ 19, ” and “ 20. ” A hand points or moves near the numbers.
This is followed by a shot of a wall with windows or blinds, then a close side profile of a woman ’s face in soft, sepia-toned light.
A darker shot shows two people close together in profile or partial silhouette, but their faces and actions are hard to distinguish.
A product close-up follows : the top of a bottle cap is shown clearly, reading “ Canada Dry ” and “ Ginger Ale. ” The camera then shows the bottle cap and bottle at an angle among bright, sparkling liquid or ice-like reflections.
Another close-up shows the cap and bottle moving or resting inside a container or tray with strong highlights.
The setting changes to a \textbf{swimming} \textbf{pool} or \textbf{water} scene.
A person is visible in the \textbf{water}, with ripples and reflected light around them.
The figure is partly backlit and not clearly identifiable.
After a blurred transitional shot, the commercial moves into what appears to be a crowded indoor social or \textbf{bar} setting.
Bodies and faces are partially obscured by foreground figures.
A seated man is visible between people ; another person stands behind him.
The lighting remains \textbf{warm} and dim, with strong highlights.
A man in dark clothing is seen seated or leaning at a table, looking toward the surrounding \textbf{activity}.
Several \textbf{quick}, soft-focus shots show people moving in the crowded space.
A \textbf{blonde} woman appears backlit, her face overexposed and indistinct.
A wider shot shows her standing near tables or a \textbf{bar} area, with other people around her ; bottles and glasses are visible on a table in front.
Brickwork and framed wall \textbf{décor} appear in the background.
A close-up shows hands holding or \textbf{touching} a glass.
Then a medium shot shows a man and a \textbf{blonde} woman sitting or standing close together at a table.
A dark glass bottle with a label is in the foreground between them.
The man looks toward the woman, and she faces him in profile.
Another close-up shows a hand holding a bottle at an angle, label partly visible but blurred.
The final shots show a container or bucket filled with several dark glass bottles.
In the last frame, a Canada Dry Ginger Ale bottle is clearly visible lying among other bottles, its label facing the camera.
The scene ends on this product-focused image.

% matched lemmas: activity, bar, blonde, décor, pool, purple, quick, sleeveless, swimming, touch, warm, water, young
\end{textsample}
