\begin{textsample}{POS Dim 4 – 1970 – Score 15.00 – 1970/tv\_com\_1970\_51.txt}  \label{ex:f4_pos_084}
A brightly decorated dance hall appears, with several couples slow-dancing on a polished wooden floor.
Streamers and balloons hang against wood-paneled walls, giving the \textbf{room} the look of a school dance or community social.
In the foreground, a young Black couple dances closely.
The young man wears a white jacket, and his back faces the viewer.
The young woman wears a pale pink dress with \textbf{puffed} \textbf{sleeves}, a pearl \textbf{necklace}, and dangling earrings.
She smiles warmly over his shoulder while holding him with one arm.
As they turn, she raises a wrapped Hershey ’s chocolate bar behind his shoulder, placing it where it is clearly visible beside his neck.
The wrapper is dark brown with large white “ HERSHEY ’S ” lettering.
She keeps smiling directly outward, her face animated and \textbf{cheerful}, while the candy bar remains tucked near the young man ’s shoulder as if she is presenting it while dancing.
The scene changes to a puppet-theater setting outdoors or in a public children ’s area.
A group of children gathers around a bright red puppet booth set against a brick wall.
From the booth ’s black opening, a \textbf{colorful} puppet leans out.
The puppet has an orange face, a large purple beak-like mouth, big expressive eyes with heavy lids, and yellow petal-like shapes radiating around its head like a \textbf{flower} or sunburst.
A boy with straight brown hair, wearing a light blue \textbf{striped} polo shirt, stands closest to the puppet and holds a Hershey ’s bar upright in his hand.
Other children, mostly seen from the back with blond or light-colored hair, cluster in the foreground watching.
The puppet turns its head from side to side and leans toward the boy, its mouth opening wide in an exaggerated, friendly way.
The boy smiles and lifts the Hershey ’s bar closer to his mouth.
He takes a bite from the end of the bar while the puppet hovers beside him, appearing \textbf{curious} and delighted.
The boy lowers the bar, still smiling, while the puppet continues to bob and tilt its head, sometimes looking at the boy and sometimes upward or outward.
The wrapped chocolate bar remains visible in the boy ’s hand, with the Hershey ’s name readable on the brown wrapper.
The setting shifts to a busy city street lined with brick apartment buildings, parked cars, and \textbf{leafy} trees.
A blonde woman in a dark police or traffic officer ’s uniform stands in the middle of the road.
She wears a dark \textbf{skirt} suit, a light blue shirt, a dark tie, and a peaked cap with a badge on the front.
A black shoulder \textbf{bag} hangs at her side.
Cars and yellow taxis pass rapidly in front of and behind her, often blurring across the view.
She stands upright in heels, gesturing with one hand as if directing traffic, while holding a Hershey ’s bar in the other.
As vehicles stream by, the officer smiles and lifts the chocolate bar.
The view comes closer to her face and upper body.
She pauses from directing traffic and takes a bite from the bar, holding the wrapper in one hand near her mouth.
She chews with a pleased expression, then holds the Hershey ’s bar upright beside her face so the wrapper is visible.
Her expression is composed and satisfied, and she looks outward while the moving traffic continues to pass around her.
The scene changes again to the open rear platform of a cable car.
A young white couple stands side by side at the railing.
The man, with \textbf{curly} brown hair, wears a \textbf{cream} turtleneck sweater under a light beige jacket.
The woman, with long dark brown hair, wears a bright yellow sweater over a collared shirt.
Each holds a Hershey ’s bar.
They smile together, standing close, with the cable car ’s dark doorway and metal railings behind them.
The man raises one hand in a small \textbf{wave} while still holding his chocolate, and the woman brushes back her hair and then \textbf{waves} more broadly.
As the cable car moves down a steep city hill, the view widens to show the rear signboard.
The sign reads “ MARKET STREET ” across the top, with a large “ 23 ” below and smaller route signs on the left, including “ POWELL, ” “ MARKET, ” and “ HYDE. ” The couple remains on the rear platform, smiling and \textbf{waving}, each still holding a Hershey ’s bar.
The cable car continues down tracks set into the center of the street.
Another cable car is visible on the left, and parked or moving vehicles line the right side.
Far ahead, water and boats are visible through a hazy, pale sky, suggesting a waterfront city view.
The cable car recedes down the hill, growing smaller as it travels toward the bay.
At the end, large white block letters reading “ HERSHEY ’S ” appear across the lower part of the screen, over the street and cable car view.
Beneath the brand name, smaller white text reads “ The Great American Chocolate Bar. ”

% matched lemmas: bag, cheerful, colorful, cream, curious, curly, flower, leafy, necklace, puff, room, skirt, sleeve, striped, wave
\end{textsample}
