\begin{textsample}{POS Dim 4 – 2020 – Score 17.00 – 2020/tv\_com\_2020\_8.txt}  \label{ex:f4_pos_009}
A middle-aged Black man sits centered on a light-colored \textbf{sofa} in a bright, \textbf{airy} \textbf{living} \textbf{room}.
He wears a loose white hoodie and pale gray pants, with white cushions on both sides of him.
Behind him are soft \textbf{neutral} walls, framed artwork, a floor lamp, and a \textbf{leafy} green plant, giving the \textbf{room} a calm, polished \textbf{home} setting.
He leans forward slightly, smiling and speaking directly toward the viewer.
His hands move in front of him as if introducing an idea ; he clasps them, separates them, and gestures with open \textbf{palms}.
A white Disney+ logo briefly appears over the lower part of his hoodie as he continues talking.
The scene shifts into a montage of streaming titles, each identified by small on-screen branding near the bottom : the Disney+ logo, the green Hulu logo, and the title of the show or film.
In a stainless-steel professional kitchen labeled “ The Bear, ” two restaurant workers in dark aprons stand at a prep counter under bright overhead lights.
One is a Black woman wearing a white T-shirt, a dark apron, and a patterned headscarf ; another worker stands behind her.
The kitchen has metal shelves, counters, and cooking equipment.
A bearded white man in a black shirt then appears in the same restaurant environment, looking downward and speaking to someone just off to the side ; the blurred edge of another person ’s head is visible in the foreground.
Next, in a warm \textbf{domestic} kitchen and \textbf{living} area labeled “ Freakier Friday, ” two white women sit side by side on a couch in front of a coffee \textbf{table}.
The older woman has long silver-gray hair, glasses, and blue pajamas with white piping ; she holds a pink mug.
The younger woman has long red hair and wears pale pink pajamas ; she holds a jar or container.
Bowls and plates sit on the \textbf{table} in front of them.
The older woman looks animated and concerned, while the younger woman turns toward her with a questioning expression.
A scene labeled “ High Potential ” shows a blonde white woman seated at a desk in what looks like an office or police station.
She wears a leopard-print coat and faces someone whose back is visible in the foreground.
Behind her, people sit and move around near desks and glass-paneled doors.
The same blonde woman appears later at night outdoors or in a dimly lit setting, now wearing a plush \textbf{turquoise} coat and dangling earrings.
She looks upward with a thoughtful, alert expression, lit warmly against a dark background.
In a \textbf{sunny} suburban street scene labeled “ Paradise, ” a Black man in a white dress shirt and black tie runs straight ahead on a quiet road.
His tie flaps as he moves, and large houses, trees, and trimmed lawns line the street behind him.
He looks focused and urgent, pumping his arms as he runs.
A diner or casual restaurant scene labeled “ Avengers : Endgame ” shows the Hulk, a large green-skinned humanoid figure with dark hair and black-framed glasses.
He wears a gray T-shirt under a thick dark cardigan and gestures with both hands while speaking to people seated nearby.
Behind him are tiled walls, metal shelves, and restaurant staff.
Two young people stand or sit to the side, watching him.
In a warmly lit indoor setting labeled “ Abbott Elementary, ” a young Black woman with shoulder-length \textbf{curly} hair sits among other people.
She wears a pale yellow sweatshirt with darker tie-dye-like patches and a small \textbf{necklace}.
Window blinds and other adults are visible behind her.
She smiles broadly and talks with bright, playful expressions, leaning forward slightly as if reacting enthusiastically to someone nearby.
A darker, more severe-looking scene labeled “ The Handmaid ’s Tale ” shows a pale white woman wearing a deep red cloak and a large white bonnet that frames her face.
Her face is tense and serious, her eyes fixed upward toward someone or something out of view.
The lighting is low and cool, with shadows around her.
A reality-style \textbf{living} \textbf{room} scene labeled “ The Secret Lives of Mormon Wives ” shows a young white woman with long, highlighted light-brown hair reclining on a pale couch.
She wears a gray top and a cross \textbf{necklace}.
White pillows and a large white vase sit behind her.
She gestures emphatically with long manicured nails, sweeping her hands outward and turning her head to the side as if explaining or reacting to a conversation.
The host reappears on the same light \textbf{sofa} in the bright \textbf{living} \textbf{room}.
Now a large mint-green insulated tumbler with a handle and straw sits in his hand or just in front of him.
He leans forward, eyes widened, reacting with amused intensity.
He points and gestures toward the tumbler and off to the side, then brings it closer.
His posture is engaged and animated, as if responding to the montage of stories.
Another brief scene from “ The Secret Lives of Mormon Wives ” appears : a young white woman in a beige cardigan over a white top holds a bowl or cup near her chest while standing or sitting in a softly lit \textbf{home} interior.
She looks down with a pursed, skeptical expression.
Back on the \textbf{sofa}, the host relaxes slightly.
He raises the mint-green tumbler and sips through the bright green straw while looking toward the viewer with an amused, knowing expression.
He lowers the cup and sits forward again, attentive and composed.
The commercial ends on a dark \textbf{teal} gradient background.
A glowing Disney+ logo appears first, then the full white Disney+ logo sits beside the green Hulu wordmark.
Beneath them, clear white text reads, “ All of these and more now streaming. ” Smaller text below shows “ DisneyPlus.com, ” with tiny fine print along the bottom.

% matched lemmas: airy, curly, domestic, home, leafy, live, living, necklace, neutral, palm, room, sofa, sunny, table, teal, turquoise
\end{textsample}
