\begin{textsample}{POS Dim 4 – 1960 – Score 17.00 – 1960/tv\_com\_1960\_116.txt}  \label{ex:f4_pos_063}
The commercial opens in black and white with a close view of the Penny Brite doll ’s face.
She has a small smiling face, large dark eyes, a short light-colored bob with curled ends, and a large \textbf{bow} on top of her head.
She wears a neat \textbf{little} dress with a white Peter Pan collar and light vertical panels, and one arm is raised as if \textbf{waving}.
The view widens to place her in a miniature outdoor setting : a toy house stands to the left, a white picket fence stretches across the background, and a gate opens around her.
She stands upright on a small sidewalk in front of the fence, posed with one arm bent.
A tree appears behind her in another yard-like setup, and she is arranged with one leg crossed in front of the other and an arm extended, as if striking a playful pose.
A young girl, about preschool or early elementary age, with dark hair in bangs and a \textbf{ponytail}, appears behind and beside the doll, wearing a simple dress with a white collar.
She copies the doll ’s pose with her arms out and one leg crossed, smiling down toward the toy.
Penny Brite is then shown between hanging doll outfits displayed on a line.
Tiny \textbf{garments} hang on \textbf{little} \textbf{curly} hangers : a checked coat, a dark sailor-style dress with a white collar and \textbf{sleeve} stripes, a frilly light dress, and other small separates.
The doll stands in the center, her arms positioned outward as if presenting the wardrobe.
The girl ’s smiling face fills the scene beside the doll ; she holds Penny Brite close to her \textbf{cheek} and looks at her fondly.
The doll ’s dress resembles the girl ’s tidy childlike style, with a similar white collar and simple shape, visually reinforcing that the doll is meant to be dressed and posed like a child.
A schoolroom play scene follows.
Penny Brite stands near a small chalkboard on an easel with the handwritten words “ 2+2=4 ” and “ DOLL. ” Behind her are shelves and classroom decorations.
She then sits at a tiny school desk, holding an open book or workbook, with a \textbf{little} school \textbf{bag} or lunchbox on the floor beside her.
She faces forward from the \textbf{chair} with her feet dangling, posed like a student at work.
The young girl appears again holding the doll upright in her hands.
The girl smiles and brings the doll closer to her face ; the doll ’s arms are bent around the girl ’s \textbf{cheek} in a cuddling position, as though hugging her.
The toy world expands to a small car scene.
A miniature convertible sits on a textured surface, with Penny Brite standing beside it in an outfit that looks like a coat or dress.
A small dog-like toy or accessory is placed near her feet, and a hat rests in or near the car.
Penny Brite is then shown lying on a \textbf{striped} surface in another outfit, with her head tilted and one arm bent near her face.
A small telephone-like \textbf{prop} sits beside her, suggesting a bedroom or play-at-home moment.
The scene changes to a full miniature bedroom : Penny Brite lies on her side on a four-poster canopy bed with ruffled trim and a fancy headboard.
To the right is a \textbf{little} vanity \textbf{table} with a round mirror, a lamp, and a small stool.
The bedspread and canopy have lace-like edges, giving the \textbf{room} a frilly, \textbf{decorative} look.
A beauty parlor setup comes next.
Penny Brite reclines in a small salon \textbf{chair} under a dome-shaped hair dryer.
The \textbf{room} has a salon backdrop, a vanity or counter with a mirror to the right, and a small stool in front.
She sits with her legs stretched forward, posed calmly as if having her hair done.
A closer view shows the hair dryer over her head and the salon \textbf{furnishings} around her.
The doll returns to classroom play in close-up, wearing a checkered jumper-style school outfit with her \textbf{bow} still in place.
She sits at the desk with the chalkboard and shelves behind her.
The writing on the board remains visible : “ 2+2=4 ” and “ DOLL. ” She holds the \textbf{little} book open as if reading or studying.
Penny Brite is then placed in a kitchen and dining-room playset.
She stands near a miniature stove and counter on the left, with tiny pots or kitchen accessories visible.
To the right is a small dining \textbf{table} with two modern-looking \textbf{chairs} and a wall shelf above it holding tiny household items.
The doll wears a fuller dress or apron-like outfit and is posed with her hands near a small \textbf{chair} or kitchen accessory, as though helping in the kitchen or preparing a meal.
The \textbf{room} has a staged, box-like interior with patterned walls and neatly arranged \textbf{furniture}.
The wardrobe case is shown in detail.
A hand opens or reaches into a tall rectangular case that stands upright like a tiny closet, with a light-colored door swung open on the left and a dark interior on the right.
Doll clothes hang inside on small hangers, and a frilly dress is lifted or displayed by the hand.
Small accessories, including tiny shoes and a round hat-like item, sit at the bottom of the case.
The outfit is then shown packaged in a flat display box with a \textbf{decorative} border and a clear window ; the “ Penny Brite ” name appears on the package.
Other boxed wardrobe sets appear, showing different small clothing pieces and accessories arranged neatly inside, including tops, pants, a \textbf{bag}, and other tiny items.
A play interaction follows at a real child-sized \textbf{table}.
Penny Brite sits on a small \textbf{chair} on the tabletop with both arms raised.
The young girl sits nearby in a folding \textbf{chair} and mirrors the doll ’s pose, lifting her own arms high while crossing one leg over the other.
On the \textbf{table} beside the doll are tiny \textbf{table} \textbf{props}, including a plate-like item and small cups, creating a miniature dining or play setting.
The girl looks toward the doll and appears pleased, using her own body to imitate the doll ’s pose.
The accessory \textbf{rooms} are then presented like open-front display cases.
First, a bedroom case shows the canopy bed, vanity, lamp, mirror, stool, and Penny Brite sitting or standing on the bed.
Then other rectangular \textbf{room} sets appear stacked or side by side : a beauty parlor scene with the salon \textbf{chair} and hair dryer, a kitchen and dining \textbf{room} scene with the stove and \textbf{table}, a classroom scene with a chalkboard and desk, and a car scene with the convertible and accessories.
Each set is arranged like a miniature stage, with the doll placed inside to demonstrate the different environments.
Near the end, the smiling young girl returns in close-up, holding Penny Brite upright beside her face.
The doll ’s \textbf{bow}, short curled hair, white collar, and paneled dress are clearly visible, and her \textbf{little} arms are bent upward.
The girl turns slightly and raises the doll higher, looking at her with a broad smile.
A final product display appears : Penny Brite stands inside a tall clear-front carrying case or box on the left, posed with one arm raised.
To the right, large cursive writing reads “ Penny Brite. ” In the last view, the same product case and name remain on screen, and the Topper Toys logo appears below the lettering.

% matched lemmas: bag, bow, chair, cheek, curly, decorative, furnishing, furniture, garment, little, ponytail, prop, room, sleeve, striped, table, wave
\end{textsample}
