\begin{textsample}{POS Dim 4 – 2020 – Score 14.00 – 2020/tv\_com\_2020\_95.txt}  \label{ex:f4_pos_020}
A couple sits on a light-colored \textbf{sofa} in a bright, tidy \textbf{living} \textbf{room} that opens into a white kitchen.
The man, with \textbf{curly} dark hair and a full beard, wears a green \textbf{long-sleeve} polo and dark pants ; he holds a small black remote in his right hand and faces the television.
Beside him, a woman with short dark hair wears a dark patterned \textbf{blouse} and blue jeans, sitting curled up with one leg tucked under her and her hand near her face.
A blue patterned pillow rests to the man ’s side, and on the coffee \textbf{table} in front of them are a bowl of chips and a pale drink in a glass.
Both look focused on what they are watching.
Their television sits within a white \textbf{built-in} wall unit with shelves holding books, vases, and \textbf{decorative} objects.
On the screen, a Black woman tennis player in a dark athletic outfit appears in action on a tennis court, then the image changes to Wonder Woman standing in a sunlit mall-like atrium with white columns and a glass ceiling.
The TV alternates between the tennis player preparing a shot and Wonder Woman in her red, gold, and blue armor.
Glowing golden lasso-like streaks sweep across Wonder Woman, and the images begin to visually merge.
The screen darkens, then a glowing outline forms around a figure holding a tennis racket.
The figure resolves into Serena Williams dressed as Wonder Woman : gold headpiece, red-and-gold armored bodice, blue \textbf{skirt}, silver bracers, and a tennis racket held like a weapon.
She stands in the middle of a busy, polished indoor shopping mall.
The couple reacts from the couch, still facing forward, the man lifting the remote slightly.
On the TV, the mall scene expands into a playful battle.
Several spider-like machines move across the shiny floor.
They have multiple jointed legs, blue and green mechanical bodies, clear domes filled with bright yellow tennis \textbf{balls}, red lights, and cannon-like tubes.
They scuttle through the atrium near stairs, planters, café \textbf{tables}, and passersby.
On an escalator, an elderly white-haired woman in a \textbf{cream} outfit grips the railing while a man in \textbf{sunglasses} and a tan sweater recoils beside her.
A tennis \textbf{ball} bounces near them, and both appear startled.
Serena, as Wonder Woman, watches intensely, her face framed by wavy light-brown hair and the gold headband.
Her expression is serious and focused.
A green tennis-ball robot creeps near a planter while people in the background hurry away.
Nearby, an older white-haired man in a white tennis polo with a blue stripe and white shorts—visually resembling John McEnroe—stands among café \textbf{chairs} holding an orange tray.
He looks down at the tray as red sauce or food dangles messily from it, then looks up with a strained, incredulous expression.
Serena ’s face returns in close view, steady and stern.
One blue-and-white-legged robot positions itself on a stair landing and launches a tennis \textbf{ball} from its clear \textbf{ball} chamber.
Serena lunges into action in the mall café area, racket in hand.
She twists her body, swings powerfully, and strikes back.
Her costume ’s gold and red armor catches the warm mall lighting, while rows of small ceiling lights form a dotted pattern above her.
The returned \textbf{ball} slams into a robot near the stairs.
The machine bursts apart in a bright spray of sparks, scattering dozens of yellow tennis \textbf{balls} and mechanical pieces across the floor.
Serena turns and continues swinging, looking over her shoulder as more robots and tennis \textbf{balls} move through the mall.
From a low angle near her boots, another green robot is hit near a cluster of plants ; sparks fly, smoke rises, and parts skid across the glossy floor while people and additional robots remain in the background.
The action is then seen again on the couple ’s television within the white shelving unit.
Serena, still dressed as Wonder Woman, leans forward on the screen, then swings her racket as a tennis \textbf{ball} flies past.
Large white text appears over the TV image, building to the slogan “ GET YOUR TV TOGETHER ” across the center-left of the screen.
The commercial returns to the couple on the \textbf{sofa}.
Both remain seated in the same \textbf{living} \textbf{room}, watching with wide, absorbed expressions, the man still holding the remote and the woman leaning in with her hand near her face.

% matched lemmas: ball, blouse, built-in, chair, cream, curly, decorative, living, long-sleeve, room, skirt, sofa, sunglasses, table
\end{textsample}
