\begin{textsample}{POS Dim 4 – 1950 – Score 13.00 – 1950/tv\_com\_1950\_93.txt}  \label{ex:f4_pos_039}
The commercial opens in a simple black-and-white cartoon bedroom.
A drawn man in pajamas sits slumped on a bed, one leg bent, looking tired and uncomfortable.
He holds a folding fan above his head and \textbf{waves} it at himself.
Wavy lines around the bed, lamp, and \textbf{furniture} suggest heavy heat.
The \textbf{room} has a bedside \textbf{table} with a lamp on the left and a bedpost on the right, giving the scene a stuffy nighttime feeling.
The cartoon image gives way to a \textbf{live} \textbf{domestic} \textbf{room}.
An adult woman presenter with light, curled 1950s-style hair stands beside a window-mounted Westinghouse \textbf{room} air conditioner.
She wears a light long-sleeved \textbf{blouse} with the \textbf{sleeves} pushed up and a dark high-waisted \textbf{skirt}.
Behind her are \textbf{curtains} and venetian blinds, with a glimpse of foliage outside the window.
A small framed picture hangs on the wall to the left.
The air conditioner sits below the window, its front facing outward into the \textbf{room}.
It is a wide, rectangular unit with three separate front grille sections.
Long, narrow paper ribbons are attached to the grilles, hanging down and fluttering to show the air movement.
As the woman stands to the left of the unit, large handwritten-style words appear across the front of the scene : “ COOLS IN SUMMER. ” The words fill much of the right side, overlapping the air conditioner and window.
Then the message changes to “ FRESHENS THE AIR, ” again in large white script.
A third message follows : “ WARMS IN WINTER. ” The woman remains beside the appliance, facing forward, then turns toward it as if preparing to demonstrate its features.
She places a hand on the top of the air conditioner and lifts or opens an upper panel.
The top section rises, revealing a control area along the upper front edge.
A closer view shows her hand operating the control panel : a row of small buttons or levers set into a long horizontal strip.
She points to and presses one of the controls, illustrating that the unit can be adjusted with a simple push.
The view returns to the full front of the air conditioner.
The upper panel is open, and the three front grille sections are clearly visible below, each with ribbons hanging and moving in the airflow.
The woman reaches across the open top and draws up a large filter assembly from inside the unit.
The filter rises vertically behind the front casing.
It has a distinctive honeycomb or circular-cell pattern, divided into rectangular sections, making it look like a grid of many round openings.
She holds it up so the entire filter surface is visible above the air conditioner, then begins guiding it back down into place.
After displaying the filter, she lowers it back inside the unit and closes the top panel.
Her hand smooths the lid shut across the top.
The front grilles continue to \textbf{blow} the hanging ribbons outward and downward.
The ribbons flutter steadily rather than whipping sharply, reinforcing the demonstration of controlled airflow.
The woman then demonstrates the adjustable grilles.
Her hand enters from the left and grasps the left grille section.
She turns or pivots it, changing the direction of the slats.
The ribbons attached to that section shift as the grille is angled.
She adjusts it again, showing that the air outlet can be directed.
The three grille sections remain separated by vertical \textbf{decorative} dividers, and the paper ribbons on all sections continue moving in the air stream.
The scene changes to a full-screen sign with ornamental flourishes.
The text reads, “ Certified Dealer ” at the top, “ for Westinghouse ” in the middle, and “ \textbf{ROOM} AIR CONDITIONERS ” in large block letters across the lower portion.
The sign is framed by \textbf{decorative} white scrollwork against a dark background.
The air conditioner appears again front and center, still installed below the window.
The ribbons continue to flutter from the three grille openings.
Large white handwritten text fades in over the unit : “ AS \textbf{LITTLE} AS \$3.25 A WEEK. ” The price is written prominently across the center, partially covering the grilles and ribbons.
For the final message, the air conditioner remains in view with the ribbons moving.
White script appears across the upper part of the image : “ You can be SURE … ” Then more words are added : “ if it ’s, ” followed by the large Westinghouse name across the lower center.
The final composition layers the slogan over the front of the appliance, ending with the Westinghouse brand name dominant over the still-running air conditioner.

% matched lemmas: blouse, blow, curtain, decorative, domestic, furniture, little, live, room, skirt, sleeve, table, wave
\end{textsample}
