\begin{textsample}{POS Dim 4 – 1980 – Score 14.00 – 1980/tv\_com\_1980\_55.txt}  \label{ex:f4_pos_044}
A young adult woman with long dark hair appears in bright beach light, wearing a very wide woven straw sunhat and oversized white \textbf{sunglasses}.
She holds the \textbf{sunglasses} at one side, lowers them down her nose, and looks directly ahead with a poised, slightly playful expression.
As she removes the glasses, her face is framed by the pale brim of the hat.
A thin \textbf{necklace} and small earrings are visible, and the straps of a red-orange swimsuit appear at her shoulders.
More of the beachside setting comes into view.
The woman is now seen from the chest up in a red-orange one-piece swimsuit, still under the broad hat.
Behind her are blue \textbf{lounge} \textbf{chairs}, \textbf{pool} ladders or railings, a beach umbrella, \textbf{palm} fronds, and a bright, hazy shoreline beyond.
She turns slightly to her side, smiling, then raises one hand toward her \textbf{cheek} as if reacting with amused surprise.
The setting feels like a \textbf{sunny} resort beside the sea, with strong white light and saturated tropical colors.
The scene changes to a dark silhouette of a saxophone player standing near the water at sunset.
The musician ’s body and saxophone are black against a deep orange sky, with the ocean stretching behind and a row of \textbf{palm} trees at the left.
The figure leans back while holding the saxophone upward, creating a dramatic outline against the glowing horizon.
A promotional graphic appears over two windsurfers skimming across blue water.
Their yellow and orange sails stand upright as they move through small white splashes.
Large white text reads “ American ’s Caribbean ” and “ \$399, ” with smaller text reading “ Per person double occupancy. ” The price dominates the center of the image, layered over the ocean action.
A smiling child stands in a \textbf{flower} market or \textbf{garden} stall, surrounded by dense bunches of bright purple, yellow, and white \textbf{flowers}.
The child, wearing a light-colored short-sleeved shirt, extends a bouquet of pale yellow-white lilies toward the viewer, as if offering them.
Underwater, several fish glide through blue-green water over a textured coral or rocky seabed.
Dark fish pass across the foreground, and a lighter silver fish moves through the center, its body catching the light as it swims.
A relaxed couple lies close together on a \textbf{striped} beach towel.
The woman, in a \textbf{colorful} bikini top, smiles with her head near the man ’s shoulder ; he lies beside her, also relaxed.
Sunlight casts \textbf{striped} shadows across them.
At the bottom of the screen, white text reads, “ Includes \textbf{hotel} and air fare. ” A snorkeler emerges from the ocean, facing forward.
The person wears a dark mask and snorkel, with water streaming heavily over the face and shoulders.
The sea and pale blue sky fill the background as the water splashes up around the swimmer.
At sunset, two silhouetted adults walk side by side along the edge of the beach.
The ocean glitters with orange reflections, \textbf{palm} trees line the shore in the distance, and their legs and reflections are visible in the wet sand.
One figure carries something low at their side, and the pair lean close together as they walk.
The woman in the red-orange swimsuit returns, now reclining on a beach towel or \textbf{lounge} surface under her wide straw hat.
She drinks through a straw from a coconut decorated with a large pink \textbf{flower}.
The sandy beach and water are softly visible behind her.
She pauses and looks forward while still holding the coconut, her white \textbf{bracelet} visible on one wrist.
The image then blends into an American Airlines airplane in flight.
The silver fuselage fills the view, with the large red “ American ” lettering along the side and red, white, and blue striping beneath the windows.
The landing gear is down, and engine pods are visible under the wing as the plane angles upward against a pale sky.
As more of the aircraft comes into view, the tail shows the “ AA ” marking.
The final image places the airplane in the sky with a large promotional title beneath it.
On-screen text reads “ American ’s Caribbean, ” “ \$399, ” and “ Includes \textbf{hotel} and airfare. ” Smaller text at the bottom says, “ Call your travel agent for details and restrictions. ”

% matched lemmas: bracelet, chair, cheek, colorful, flower, garden, hotel, lounge, necklace, palm, pool, striped, sunglasses, sunny
\end{textsample}
