\begin{textsample}{POS Dim 4 – 1970 – Score 12.00 – 1970/tv\_com\_1970\_14.txt}  \label{ex:f4_pos_088}
A young woman with shoulder-length light brown hair crouches beside a large golden-brown \textbf{dog}, likely a retriever, in a simple indoor \textbf{room} with a yellow-green wall.
She wears a \textbf{teal} cardigan over a pale collared \textbf{blouse} and dark bottoms.
The \textbf{dog} stands close against her, wearing a collar, while she hugs and \textbf{pets} it around the neck and shoulders.
A wooden \textbf{chair} and a small \textbf{table} covered with a \textbf{blue-and-white} checked \textbf{cloth} sit to the right, suggesting a \textbf{home} setting.
The woman smiles warmly, then rises to standing as the \textbf{dog} drops lower and moves partly out of view.
She turns toward the right side of the \textbf{room} and begins reaching for \textbf{props}, shifting the scene from \textbf{petting} the \textbf{dog} to demonstrating the product visually.
Against the plain yellow-green background, she lifts a rectangular sign toward the viewer.
It is tan or brown with large bold pink letters spelling “ PROTEIN. ” Holding it at chest height, she gestures to her left, then brings in a second matching block so the words become “ HIGH PROTEIN. ” The pink lettering is large and blocky, with a bright, almost neon look against the tan panels.
She raises the words near her face, then releases them into position on the left side of the screen as if they are floating or mounted there.
Next, she reaches to the right and brings in another long tan sign with the word “ Purina ” in turquoise-blue lettering.
She places this above “ HIGH PROTEIN, ” creating a stacked product-title graphic : “ Purina ” over “ HIGH PROTEIN. ” She continues assembling the display.
Holding a square tan panel printed with photographs or illustrations of several active \textbf{dogs}, she positions it below the words.
The \textbf{dog} images show multiple breeds in motion, including black-and-white and brown \textbf{dogs} running or leaping, arranged across the lower part of the panel.
She smiles and aligns this dog-picture panel under the “ Purina HIGH PROTEIN ” heading, then steps aside and reaches for more pieces.
She brings in another long panel with pink lettering and places it between the title area and the \textbf{dog} images ; as she adjusts it, the full package wording becomes visible : “ Purina HIGH PROTEIN \textbf{DOG} MEAL. ” The product name is now presented as a large, flat, tan-orange package front, with “ Purina ” near the top, “ HIGH PROTEIN \textbf{DOG} MEAL ” in big pink letters in the middle, and the running \textbf{dogs} pictured below.
The display grows into an oversized dog-food \textbf{bag}.
The woman lifts a long top strip with a \textbf{blue-and-white} checkerboard pattern and places it across the top of the package, matching the Purina checkerboard identity mentioned in the audio context.
She then bends down and adds a matching checkerboard strip along the bottom.
The result is a giant bag-like product graphic that nearly covers her body from shoulders to knees.
The tan-orange \textbf{bag} front fills most of the screen, with the \textbf{blue-and-white} checker pattern at the top and bottom and the \textbf{dog} images across the lower front.
The woman remains partly visible behind and beside it, using both hands to steady and present it.
She stands to the right of the enormous package, smiling and gesturing toward the printed words and the \textbf{dog} images as if highlighting key features.
At one point she points near the “ HIGH PROTEIN ” text, then shifts behind the \textbf{bag} again so only parts of her face, hair, or arms appear at the side.
The big package dominates the view, with “ Purina HIGH PROTEIN \textbf{DOG} MEAL ” clearly readable in large pink letters.
Near the end, a separate horizontal “ HIGH PROTEIN ” block slides or is held across the center of the package, covering part of the printed words while the woman ’s face peeks through the gap behind it.
A small red-and-white checkerboard cube or logo element appears near the lower right, reinforcing the Purina checkerboard motif as the product package remains centered and prominent.

% matched lemmas: bag, blouse, blue-and-white, chair, cloth, dog, home, pet, prop, room, table, teal
\end{textsample}
