\begin{textsample}{POS Dim 4 – 2010 – Score 18.00 – 2010/tv\_com\_2010\_63.txt}  \label{ex:f4_pos_025}
A dark-haired adult man sits outdoors at night at a \textbf{backyard} \textbf{pool} party, wearing a light beige short-sleeved button-up shirt.
He smiles and raises one index finger as if making a confident point.
Around him, people in casual summer clothes move near a glowing \textbf{swimming} \textbf{pool} and \textbf{patio} \textbf{furniture}.
A wider view reveals he is seated at a round \textbf{patio} \textbf{table} with two other adult men ; bowls of snacks and bottles sit on the tabletop, and a modern house or \textbf{pool} house glows warmly in the background.
The focus shifts to a small dark jewelry box held in someone ’s hands.
The lid opens to reveal a sparkling diamond ring inside.
In a bright jewelry store, an older silver-haired man in a dark jacket stands behind a glass display counter and holds out the open ring box.
Across from him, a younger dark-haired man in a brown leather jacket over a burgundy shirt smiles, leaning toward the counter under warm pendant lights.
A close view shows two hands resting together on someone ’s lap.
Both wear rings : one hand has a wedding band, and the other has a diamond ring and band.
The hands gently overlap, suggesting a married couple.
The scene then moves to the inside of an airplane cabin.
A young adult man with dark hair sits beside a blonde young adult woman.
He leans his head toward her shoulder while she sits upright in her seat, glancing sideways with a restrained expression.
The cabin is crowded, with passengers in rows behind them and a person in a dark shirt standing in the aisle.
Other passengers, including a child visible in the background, fill the surrounding seats.
In a hospital \textbf{room}, the blonde woman lies in a bed wearing a patterned hospital gown.
Her hair is pulled up messily, and her face tightens with the intensity of labor or pain.
A dark-haired man in a gray shirt is close beside her, holding or steadying her hand while also gripping a small handheld device near the bed.
Medical equipment and a monitor are visible on the left, and a round examination lamp hangs above.
Later, the couple sits in a warm, industrial-style apartment with brick walls, large windows, and city buildings visible outside.
A baby sits between them in a small carrier or seat on the dining \textbf{table}.
The \textbf{table} is scattered with everyday items, and pendant lights hang overhead.
The woman sits at the \textbf{table} facing the baby, while the man leans back in a \textbf{chair}, both appearing settled into \textbf{domestic} life.
In daylight, they are now outside a white suburban house with black \textbf{shutters} and a trimmed front lawn.
A dark classic car is parked in the driveway on the left.
The man stands near the hedges in front of the house, while the woman stands near the porch with a small child in a bright pink outfit.
A \textbf{colorful} plastic outdoor toy sits on the grass.
Tiny white legal text stretches along the bottom of the screen, too small to read clearly.
A close view shows a soapy yellow sponge sliding across the wet hood of a vehicle, spreading suds over dark paint.
The wider view reveals the man washing a gray minivan in the driveway of a \textbf{leafy} neighborhood.
He wears a casual plaid shirt and shorts, leaning over the front of the vehicle with a blue bucket and an orange bottle of car-wash soap nearby.
Inside a \textbf{home}, a white wall along a \textbf{staircase} is covered with children ’s crayon drawings and scribbles in many colors.
The man kneels near the wall, scrubbing at the marks with a sponge or \textbf{cloth}.
A yellow container filled with supplies sits on the floor.
The blonde woman enters carrying a large \textbf{lime-green} \textbf{laundry} basket, wearing jeans and a \textbf{striped} sweater over a blue shirt.
She walks past the stair railing, then turns back with a smile as the man looks up at her.
The commercial ends on a solid red screen with centered white text reading, “ For all the nevers in life. ” The final red screen shows the white State Farm three-oval logo and the words “ State Farm, ” with “ AUTO ” underneath.
Along the bottom are “ 800-STATE-FARM ” and “ statefarm.com. ”

% matched lemmas: backyard, chair, cloth, colorful, domestic, furniture, home, laundry, leafy, lime-green, patio, pool, room, shutter, staircase, striped, swimming, table
\end{textsample}
