\begin{textsample}{POS Dim 4 – 1990 – Score 8.00 – 1990/tv\_com\_1990\_3.txt}  \label{ex:f4_pos_045}
The commercial opens in a very dark shot of a woman seated or crouched in a narrow space.
Details are difficult to see because the frame is underexposed.
It then cuts to a brightly lit, stylized set dominated by large orange cylindrical forms arranged like oversized columns or containers.
A \textbf{young} woman with dark, shoulder-length hair appears in a \textbf{sleeveless} blue dress.
She is positioned among the orange forms, with strong sunlight and hard shadows creating white and blue patches in the background.
She repeatedly \textbf{touches} and adjusts her hair : first with both hands near her head, then covering part of her face, then smoothing or lifting her hair.
The camera alternates between medium shots and a close-up of her face with eyes lowered, emphasizing her makeup, lips, and hair.
A wide shot shows her standing full-length in a corridor-like space formed by multiple large orange cylinders on both sides, under a vivid blue sky.
She is centered, wearing the blue dress and dark shoes.
The setting looks highly artificial and graphic, with saturated orange, blue, and white color contrasts.
The woman continues posing against the orange-and-white background.
She \textbf{touches} the sides of her neck and hair, then smiles and looks downward.
A blurred orange transition follows.
Text appears over a blurred background of the orange cylindrical forms.
The on-screen text reads : “ THE VIDAL SASSOON ACADEMY ” The text is white, in large serif-like capitals, positioned mainly on the left side.
A brief bright white flash or overexposed transition interrupts and then the same “ THE VIDAL SASSOON ACADEMY ” text reappears.
The commercial then shifts to product imagery.
A blurred close-up resolves into a red bottle with a white-and-gold label reading “ VIDAL SASSOON. ” Below it, the label reads “ ALCOHOL-FREE SPRAY-ON GEL. ” The bottle is shown against a bright blue background.
A row of multiple identical red bottles is then displayed along a white \textbf{ledge} or platform, receding into the distance under a blue sky.
Another close-up focuses tightly on the words “ ALCOHOL-FREE SPRAY-ON ” on the red bottle.
A woman with wet or slicked dark hair is shown from the shoulders up against an orange background while a hand holds the red spray bottle near her head.
The product is being sprayed or positioned as if being applied, though the spray mist is not clearly visible in the sampled frame.
The product appears again standing on a white \textbf{ledge} in front of a large orange curved form and a blue sky.
The commercial then introduces additional models.
A \textbf{blonde} woman with a short bob haircut and blunt bangs appears smiling close to a dark-haired woman seen from behind.
The \textbf{blonde} woman wears a thin-strap top.
Another shot shows the original dark-haired woman smiling softly with her chin resting on her hand, her hair styled in a smooth bob-like shape.
Two women—the \textbf{blonde} woman in a \textbf{purple} or burgundy thin-strap top and the dark-haired woman in the blue dress—stand together smiling, with arms around each other or shoulders touching.
The lighting is very bright and sometimes overexposed, giving the skin and background a washed-out glow.
A \textbf{group} shot shows the back of a dark bob haircut in the center, with the \textbf{blonde} woman at left and the dark-haired woman at right, all close together.
A close-up presents the dark-haired woman facing the camera with a smooth, rounded bob hairstyle, smiling against an orange-and-white background.
The \textbf{blonde} and dark-haired women are then shown together again, laughing and looking at each other.
A highly overexposed close-up of the \textbf{blonde} woman follows, her short haircut and red lipstick still visible despite the brightness.
Near the end, text appears over a \textbf{warm}, blurred background.
The visible words read : “ STYLE THAT ’S PERFECTLY YOU ” The word “ STYLE ” is smaller and positioned to the left of “ THAT ’S. ” The text is white and centered/left-centered over the soft-focus image.
A large blurred white letter or graphic shape briefly fills much of the frame, then the commercial ends with a bright, sunlit close-up of the \textbf{blonde} woman and the dark-haired woman side by side, facing toward the right.
Their hair is smooth and styled ; the image remains highly saturated and overexposed, with blue sky visible behind them.

% matched lemmas: blonde, group, ledge, purple, sleeveless, touch, warm, young
\end{textsample}
