\begin{textsample}{POS Dim 4 – 1980 – Score 13.00 – 1980/tv\_com\_1980\_34.txt}  \label{ex:f4_pos_050}
A young boy opens a door from a bright porch into a \textbf{laundry} area.
He has light brown hair and wears an orange sports jersey with black-and-white trim and a large black number 7 on the front.
A dark brown stain is clearly visible on the right side of his chest, with a few drips below it.
He stands still, looking up into the \textbf{room}, while sunlight and greenery are visible behind him through the porch railing.
A blonde woman, likely his mother, turns toward him with a knowing, slightly \textbf{amused} expression.
Her hair is pulled back in a \textbf{ponytail}, and she wears a loose \textbf{blue-and-white} \textbf{striped} button-down shirt.
The scene widens to show them together in a \textbf{home} \textbf{laundry} \textbf{room} : the boy stands near the open door, and the woman stands beside a counter with a white \textbf{laundry} basket full of clothes, including a bright red item and a purple \textbf{garment}.
A washer and dryer area, wall shelves, hooks, and household \textbf{laundry} items are visible around them.
She looks down at the boy, then reaches out and touches his shoulder and upper chest area, focusing on the stained jersey as if assessing the damage.
The product is then shown by itself against a dark background : a green-and-white cylindrical container labeled “ Spray ’ n Wash Stain Stick, ” with “ Tough Stain Remover ” and “ for Laundry ” printed below.
The label includes a small white shirt icon and blue \textbf{wave} graphics near the bottom.
Back in the \textbf{laundry} \textbf{room}, the woman helps the boy take off the stained orange jersey.
He raises both arms above his head while she pulls the shirt upward.
His bare torso is visible as the jersey slides over his face and then off, the stained fabric bunching and stretching as it is removed.
The woman holds the Stain Stick container in her hands.
She removes the green cap, revealing a white solid stick applicator, similar in shape to a deodorant stick.
The label is visible as she turns it : “ Spray ’ n Wash Stain Stick. ” She then brings the product to the orange jersey, which is laid flat.
The large brown stain and a smaller stained patch are visible near the black number 7.
Holding the fabric steady with one hand, she rubs the white end of the Stain Stick directly over the stained areas, moving it back and forth across the brown marks.
The \textbf{treated} area begins to look damp or coated, with a lighter, slightly glossy film spread across the fabric.
She lifts and tilts the jersey, showing the stain area covered with the applied treatment.
A large calendar-style graphic appears, with oversized black weekday names at the top and metal rings as if pages are hanging from a binder.
The first page reads “ Saturday. ” Within the calendar page, the same \textbf{laundry} \textbf{room} is visible, and the woman stands holding the orange jersey and product.
The calendar then flips forward to “ Sunday, ” where she now wears an orange outfit while the \textbf{treated} jersey hangs near the washer.
It flips to “ Monday, ” and she appears in a blue-and-black exercise leotard, holding the jersey with one hand and a small orange object in the other. “ Tuesday ” follows, with the woman dressed in \textbf{colorful} summer clothes, \textbf{sunglasses}, and shorts ; a beach \textbf{ball} sits nearby, while the orange jersey remains hanging by the washer.
On “ Wednesday, ” she wears a yellow raincoat and matching rain hat, with an umbrella visible at the side ; the jersey is still hanging in the \textbf{laundry} area.
On “ Thursday, ” she wears a fitted red dress and gestures with one hand while the jersey remains beside the washer.
On “ Friday, ” she wears a pale yellow top and holds the orange jersey, suggesting the \textbf{treated} shirt has waited through the week.
The woman then appears close up in the \textbf{laundry} \textbf{room} wearing the pale yellow top.
She holds the Spray ’ n Wash Stain Stick near her face, looks at it with satisfaction, and smiles directly toward the viewer.
The product label is partly visible in her hand.
The commercial ends with a product display on a reflective dark surface.
In front is the open Stain Stick container with its white applicator exposed and green cap placed beside it.
Behind it are larger green Spray ’ n Wash bottles with the red-and-orange “ Spray ’ n Wash ” logo and blue \textbf{wave} graphics.
The orange jersey is laid next to the products, its black trim and number partly visible.
A large red stamped graphic appears over the shirt reading “ MISSION ACCOMPLISHED, ” reinforcing that the stain-removal task has been completed.

% matched lemmas: amuse, ball, blue-and-white, colorful, garment, home, laundry, ponytail, room, striped, sunglasses, treat, wave
\end{textsample}
