\begin{textsample}{POS Dim 4 – 2010 – Score 11.00 – 2010/tv\_com\_2010\_65.txt}  \label{ex:f4_pos_007}
The clip opens on a clean white screen with the FedEx logo centered and a small web address below it ( “ fedex.com/delivery ” ).
It then cuts to a bright, upscale \textbf{outdoor} patio at a large white house.
The view looks across a rectangular \textbf{pool} and \textbf{lounge} area toward the house, framed by light curtains in the foreground.
The setting is \textbf{sunny}, with manicured landscaping, \textbf{lounge} \textbf{chairs}, and a polished courtyard.
A woman with long light-brown hair, wearing a fitted \textbf{teal} \textbf{sleeveless} dress, sits at an \textbf{outdoor} table.
She holds a dark beverage in a clear mug and looks down at papers or a document in front of her.
A man wearing glasses, a shirt and tie, and a dark apron appears nearby holding a metal tray or caddy with cups.
The setting behind him shows an airy interior room with plants and light-colored furnishings.
The woman looks up from the papers, appearing attentive or surprised.
The man stands facing her with the tray.
They are shown in alternating shots from each other ’s perspective : she remains near the patio/pool area holding her \textbf{drink}, while he stands at the edge of the indoor-outdoor space.
The woman smiles slightly and raises the mug.
The man gestures with his hands and later sets or lowers the tray near the table.
The woman \textbf{drinks} from the clear mug.
In later shots, her \textbf{drink} changes to a layered iced beverage with a \textbf{straw} : dark coffee at the top, a pale milk/cream layer below, and ice visible.
She sips through the \textbf{straw} while looking toward the man.
The man, still in apron and glasses, gestures animatedly, including pointing or making small hand motions, as if explaining something.
A wider shot shows them both on the patio : the man stands by a round table with a vase of white \textbf{flowers}, cups, and a tray, while the woman stands in heels beside the table.
The commercial then shifts to product-focused shots of a Ninja coffee machine.
A close-up shows dark coffee dispensing into a glass mug beside the machine.
The machine ’s digital display and control panel are visible.
The lower-left corner displays a small “ NINJA COFFEE \textbf{BAR} ” graphic.
A close-up of the control dial shows a hand with white nail polish turning or pressing the selector near labeled options including “ TRAVEL ” and “ CUP. ” Another product shot shows a glass carafe, a latte-like \textbf{drink} in a mug, and a dark coffee in a clear mug arranged on a countertop.
A further close-up shows a finger pressing a button labeled “ OVER ICE, ” with nearby text reading “ SPECIALTY BREW ( CONCENTRATED COFFEE ). ” The woman then appears in a bright kitchen behind the Ninja Coffee Bar machine, smiling and gesturing with both hands.
Several \textbf{drinks} are arranged on the counter : a carafe, a \textbf{hot} coffee in a mug, a layered iced \textbf{drink}, and a dark iced \textbf{drink}.
The “ NINJA COFFEE \textbf{BAR} ” graphic \textbf{remains} in the lower-left corner.
The final product shots show the Ninja Coffee Bar machine centered on a kitchen counter, surrounded by the glass carafe and multiple prepared beverages.
The last frame adds large on-screen text : “ NINJA COFFEE \textbf{BAR}, ” with the website “ NINJACOFFEEBAR.COM ” and availability text showing “ Kohl ’s ” and “ Walmart. ”

% matched lemmas: bar, chair, drink, flower, hot, lounge, outdoor, pool, remains, sleeveless, straw, sunny, teal
\end{textsample}
