\begin{textsample}{POS Dim 4 – 2010 – Score 18.00 – 2010/tv\_com\_2010\_30.txt}  \label{ex:f4_pos_026}
An animated family of bright red bears enters a \textbf{sunny} \textbf{hotel} \textbf{room} decorated for a beach vacation.
The \textbf{room} has wooden floors, a blue bed at the left, a dresser and \textbf{leafy} green plant at the right, framed beach \textbf{art} on the wall, and an open bathroom door in the center with a white toilet visible inside.
A small cub in front wears a blue snorkel mask and carries a snorkel ; another cub nearby hugs a red-and-yellow beach \textbf{ball} and has purple straps over the shoulders.
Behind them, a large adult bear wears a blue Hawaiian-style shirt with light \textbf{flower} patterns and carries a brown suitcase.
Another adult bear follows from the doorway wearing white \textbf{sunglasses} and a small white \textbf{flower} on the head.
The cubs rush excitedly across the \textbf{room} toward the beach outing, while the adult in the blue shirt slows down near the bathroom.
The bear in the blue shirt tosses the suitcase aside and gestures broadly, then turns and heads into the bathroom.
The sunglasses-wearing adult bear stays near the open \textbf{room} door, lifting a \textbf{paw} to the \textbf{sunglasses} as if looking on.
The bathroom door swings shut, leaving the sunglasses-wearing bear standing alone in the \textbf{hotel} \textbf{room}.
The vacation setting is bright and relaxed, with sunlight and palm-like shadows across the walls.
A closer view shows the sunglasses-wearing adult bear without the \textbf{sunglasses} now, with a \textbf{little} white \textbf{flower} on the head, standing at a large beige suitcase on the bed.
The bear leans over the luggage and appears concerned or focused while handling it.
The door behind is closed, and the beach picture remains on the wall.
As the suitcase is opened, a pair of white \textbf{sunglasses} lies on the bed in the foreground.
The bear in the blue shirt suddenly reappears from the bathroom doorway, looking alarmed, with mouth open and eyes wide, and hurries toward the suitcase.
He stops beside the other adult bear, who is still bent over the suitcase.
The bear in the blue shirt holds up a plain white roll of toilet paper in one \textbf{paw} and studies it closely.
He turns it, points at it, and pulls at the loose end.
His expression shifts from puzzled to worried as he stretches out a length of paper between both \textbf{paws}.
The paper looks smooth, thin, and flat, without visible texture.
He looks down at the strip as though dissatisfied.
The flower-wearing adult bear then presents a large red-and-white Charmin \textbf{Ultra} Strong package.
The package is held between the two adult bears and fills much of the view.
It has the blue Charmin logo in white script, the words “ \textbf{ULTRA} STRONG ” in bold white letters on a red background, and “ MEGA ” near the top.
A picture on the package shows the Charmin bear characters with a toilet.
The bear in the blue shirt brightens and takes hold of the package, smiling.
The other adult bear lets go and steps aside, while the blue-shirted bear proudly holds the package up toward the viewer.
A product demonstration follows in a bathroom-like setting.
A white roll of toilet paper sits on a small wooden bench with a green \textbf{rug} below and a blurred white toilet in the background.
A sheet unrolls forward.
At first the paper appears plain and smooth.
As it continues to roll out, the surface changes to a raised, quilted texture with swirls, loops, and patterned embossing.
The texture becomes more pronounced, covering the sheet in a soft, washcloth-like raised pattern as it \textbf{drapes} over the bench.
Another comparison demonstration appears on a bright blue background split vertically into two halves.
On both sides, a strip of white toilet paper is stretched horizontally with small metal weights or cylinders stacked on top.
A hand above each strip uses a dropper to add liquid.
The left side is labeled with a purple badge reading “ Leading Bargain Brand x4, ” while the right side shows the “ Charmin \textbf{Ultra} Strong ” logo.
Small white text across the top states : “ Elapsed Time 4 sec, 20 ml of water, Leading bargain brand vs.
Charmin Double Roll. ” Larger text appears above the strips : on the left, “ 4 SHEETS, ” and on the right, “ 1 SHEET. ” The left strip sags, tears, and drops the stacked weights, while the single sheet on the Charmin side remains stretched and supports the weights.
The scene returns to the beach.
The red bear family is now on a \textbf{sunny} tropical shoreline with pale sand, blue water in the foreground, rows of \textbf{palm} trees, and hazy mountains in the distance.
One adult red bear stands near the water with hands on hips, chest out, looking pleased.
The sunglasses-wearing adult bear reclines on a blue \textbf{lounge} \textbf{chair}, wearing white \textbf{sunglasses} and holding a pineapple-shaped tropical drink with a straw, \textbf{fruit} garnish, and small umbrella.
Two smaller cubs run off to the right in the background.
The standing adult bear begins to move playfully along the edge of the water, stepping and swinging the arms as if dancing or celebrating.
The reclining bear watches from the \textbf{lounge} \textbf{chair}, smiling and holding the pineapple drink.
In a closer view, the \textbf{lounging} bear adjusts the white \textbf{sunglasses} with one \textbf{paw} while still holding the drink in the other.
The standing bear comes into the foreground beside the \textbf{lounge} \textbf{chair}, leaning in affectionately.
The two adult bears face each other, smiling ; the standing bear gestures near the other bear ’s chin, and the reclining bear smiles back.
The commercial ends on a clean light-blue background with a large Charmin logo : a dark blue cloud shape with “ Charmin ” in white script.
A white ribbon of toilet paper curls beneath it, carrying the words “ enjoy the go ” in light blue lowercase letters.
A red Charmin bear walks in from the right, stops beside the logo, and raises one \textbf{paw} in a friendly \textbf{wave} while smiling.

% matched lemmas: art, ball, chair, drape, flower, fruit, hotel, leafy, little, lounge, palm, paw, room, rug, sunglasses, sunny, ultra, wave
\end{textsample}
