\begin{textsample}{POS Dim 4 – 2010 – Score 27.00 – 2010/tv\_com\_2010\_76.txt}  \label{ex:f4_pos_021}
A bright red background fills the screen as glossy brown Kit Kat chocolate fingers stand upright in a neat group.
The bars are long, narrow, and rectangular, with the Kit Kat name molded into their surfaces.
One finger appears alone across the red field, with a pale yellow diagonal band at the bottom edge.
It snaps cleanly in two, exposing crisp wafer layers inside the chocolate ; small crumbs and chocolate flecks float around the broken ends.
The animation repeats from different angles, showing close views of the chocolate surface and the break.
The Kit Kat logo appears below the two separated pieces, and large bold text fills the red background : “ HAVE A BREAK! ” above “ HAVE A KIT KAT! ” The scene shifts to a dark, theatrical setting.
Several women with styled blonde hair wear black strappy dresses and stand against a black background, lit from above and the side so their faces and shoulders are partly in shadow.
One woman is seen from behind with a red \textbf{flower} tucked into her hair, while two similar-looking women face inward from either side like reflections.
A young man with dark hair looks downward at a large open newspaper or document, his face serious and concentrated.
Another sequence shows an elderly man with long white hair, a white beard, and small round glasses, dressed formally in a black \textbf{bow} tie, leaning close to a young woman with \textbf{curly} blonde hair and a sparkling gold outfit.
They appear to be in an intimate conversation, their faces warmly lit against the dark.
Two women in dark maid-like uniforms with white collars and cuffs pour liquid from white teapots into a curved white surface.
A chandelier with lit \textbf{candles} hangs in darkness above a patterned floor.
Over the young man ’s face, the word “ OF ” appears in large pale letters.
A new outdoor scene shows a large house with steep roofs and chimneys, surrounded by a \textbf{sunny} lawn where many people dressed mostly in white are gathered for an elegant \textbf{garden} party.
Long \textbf{tables} are covered with white \textbf{cloths} and trays of small desserts.
Three older adults in light-colored clothing stand beside a dessert \textbf{table}, holding plates and talking.
Suddenly their expressions change to alarm ; one woman lifts her plate defensively while the men recoil.
A blue vehicle has crashed into the party area near a tree, scattering \textbf{furniture} and debris across the grass.
Inside the vehicle, a curly-haired driver wearing glasses is visible through a windshield partly covered with \textbf{leafy} branches.
The driver first appears to be laughing or smiling broadly, then looks forward with a more startled expression.
Outside a \textbf{garden} center, a young couple walks hand in hand past pale stone \textbf{garden} statues.
The woman has long dark hair and wears jeans, a white top under a black-and-green argyle vest, and carries a tan shoulder \textbf{bag} ; she holds a pink frozen \textbf{treat} or ice \textbf{cream}.
The man wears jeans and a light \textbf{striped} short-sleeve shirt and also holds a pink \textbf{treat}.
Behind them, a sign reads “ SMYTH \& SONS \textbf{GARDEN} CENTER, ” and shelves of \textbf{colorful} large planters sit to the right.
As they stroll, several large yellow-and-green \textbf{bags} suddenly tumble through the foreground, obscuring them.
The man is knocked or swept out of view, while the woman remains standing, mouth open in shock, still holding her pink \textbf{treat}.
A wider view reveals a forklift to the right and a pile of spilled \textbf{bags} on the ground between the forklift and the woman.
The forklift operator, an older man with a white beard, tan shirt, and cap, leans from the driver ’s seat with a concerned look.
Another suburban scene shows a man mowing a green front lawn in front of a house and garage.
A cloud of dust or smoke bursts around the red lawn mower, and the mower tips or lurches.
The man steps back and then stands looking down, appearing stunned.
A white front door opens inside a warmly lit \textbf{home}, and a middle-aged woman in business attire enters with a rolling suitcase.
She wears a gray dress, a black cardigan, a large \textbf{necklace}, and carries a shoulder \textbf{bag}.
In a \textbf{living} \textbf{room}, a large \textbf{dog} sits calmly on an ottoman while two women stand near a \textbf{sofa} : one in a short dark outfit and high heels holds up a black feathery \textbf{garment}, and another older woman in a pink robe stands barefoot beside her.
The business-dressed woman at the doorway looks in with a firm, surprised expression.
A website interface appears with the brand name “ Avvo ” and the tagline “ Legal.
Easier. ” A black-and-white image of a woman leaning on a couch sits above three columns labeled “ Q\&A, ” “ Advisor, ” and “ Directory. ” The directory option is highlighted in red, with a button below that reads “ Find Your Lawyer. ” Another page shows a lawyer profile for “ Staycie Renee Sena, ” with an “ Avvo Rating ” of “ 10 ” and a “ Client Rating ” shown with red stars.
The Avvo logo then appears large and blurred on a white background.
The Gain Botanicals portion begins in a bright, soft-focus meadow filled with green grass and many small purple and white \textbf{flowers}.
A young adult woman with glasses, dark hair pulled back, small earrings, and a white top wears a vivid green scarf around her neck.
Her eyes are closed and she smiles peacefully, as if enjoying the outdoor air.
She opens her eyes and smiles more broadly.
The imagery overlaps into a dreamy double exposure as she lifts the green scarf to her \textbf{cheek} and neck, holding the fabric with both hands and tilting her head back with a delighted expression.
She then brings the scarf up over her nose and mouth and inhales from it, eyes closed.
The setting is revealed to be an office cubicle rather than an actual meadow.
The woman sits at a desk, still holding the bright green scarf to her face.
Behind her is a large wall poster of a flowered field with the word “ Switzerland ” visible across the top, visually echoing the meadow fantasy.
Across the cubicle wall, a male coworker with glasses and short hair peeks over while holding a mug, watching her with a puzzled or \textbf{curious} expression.
A wider view shows rows of gray cubicles under fluorescent office lights, with computer monitors, papers, and other workers in the background.
The woman remains seated in her cubicle, absorbed in smelling the scarf.
The product appears against a blurred office background : a pale yellow bottle of Gain Botanicals \textbf{laundry} detergent with a bright green cap and \textbf{built-in} handle.
The front label shows the red “ Gain ” logo and botanical imagery.
To the right, large white text reads “ PLANT-BASED DETERGENT*. ” Small fine print appears below.
A canopy of \textbf{flowers} and \textbf{fruit} descends across the top of the image—white blossoms, orange \textbf{flowers}, green leaves, and round orange citrus-like fruit—framing the bottle.
The final product display keeps the Gain Botanicals bottle on the left, the “ PLANT-BASED DETERGENT* ” text on the right, and adds the line “ SERIOUSLY GOOD SCENT ” underneath.

% matched lemmas: bag, bow, built-in, candle, cheek, cloth, colorful, cream, curious, curly, dog, flower, fruit, furniture, garden, garment, home, laundry, leafy, live, necklace, room, sofa, striped, sunny, table, treat
\end{textsample}
