\begin{textsample}{POS Dim 4 – 2020 – Score 15.00 – 2020/tv\_com\_2020\_4.txt}  \label{ex:f4_pos_019}
A bright, modern \textbf{living} \textbf{room} appears, mostly white and pale gray.
A bald, middle-aged Black man with a trimmed goatee sits centered on a light gray \textbf{sofa}, wearing a dark jacket over a black shirt and black pants. \textbf{Decorative} patterned pillows and blue accent pillows sit along the \textbf{sofa}, with \textbf{sheer} \textbf{curtains} and small high windows behind him.
On the glass coffee \textbf{table} in front of him are Aroma360 products : a tall silver cylindrical diffuser and a small clear scent bottle.
White promotional text in the upper left reads “ 25 \% OFF ” with “ USE CODE : DJ25, ” and the Aroma360 logo sits near the lower left.
The man faces forward and speaks directly to the viewer, using his hands expressively.
As he leans slightly to one side and raises a hand near his face, bold black-and-white text appears across the middle : “ GIVE YOU A TIP! ” The view tightens on his face and upper body as he continues gesturing, smiling slightly and emphasizing his point with open \textbf{palms} and small hand motions.
The screen briefly washes to white, then the man is standing in a long, bright white hallway inside a modern \textbf{home}.
He walks toward the viewer between white walls, doors, framed artwork, a small window, and a round wall control or thermostat on the right.
He keeps his hands in front of him, then lifts them upward as if presenting an idea.
Large text builds across the center and reads “ WOW FACTOR, ” with “ WOW ” in a black rectangle and “ FACTOR ” in white letters beside it.
The same “ 25 \% OFF ” code remains in the upper left, with the Aroma360 logo at the lower left.
The setting returns to a white \textbf{living} \textbf{room} with a tufted white \textbf{sofa}.
A young adult woman with long wavy brown hair, light skin, and black clothing sits sideways on the \textbf{sofa}.
She wears a black jacket over a fitted black top and dark pants.
An open magazine lies beside her on the cushion.
Behind her are large black-and-white pop-art style portraits on the wall, and a white \textbf{table} lamp sits to the left.
A silver cylindrical diffuser stands in the foreground on a glass \textbf{table}.
The woman turns toward it and extends her arm, holding a small remote control.
Gray text appears on the right : “ LARGE LIBRARY OF SCENTS. ” She points the remote toward the diffuser, suggesting she is activating or adjusting it.
A series of elegant hotel-like interiors follows.
One is a spacious \textbf{lounge} with tall windows, white \textbf{curtains}, soft seating, plants, large pendant lights, and a large graphic portrait at the far end.
Over the center appears a black label reading “ Top Scents, ” then “ MY WAY, ” with smaller text beneath : “ Inspired by 1 \textbf{Hotel}. ” Another refined lobby-like \textbf{room} appears with symmetrical \textbf{chairs}, a chandelier, polished floors, and an abstract artwork at the back.
Its label reads “ Top Scents, ” “ DREAM ON, ” and “ Inspired by Westin Hotels. ” A third luxury \textbf{lounge} appears with patterned black-and-white wall panels, high ceilings, white \textbf{sofas}, and \textbf{tables}.
Its label reads “ Top Scents, ” “ 24K MAGIC, ” and “ Inspired by W Hotel. ” A QR code labeled “ SCAN ME ” appears at the lower right and remains through much of the rest of the commercial.
The man reappears in a sleek kitchen or open \textbf{living} area with matte gray cabinetry, \textbf{built-in} appliances, and a light stone or concrete wall.
He stands near a counter, facing forward with his hands together, speaking calmly.
The “ 25 \% OFF USE CODE : DJ25 ” text remains in the upper left, and the QR code with “ SCAN ME ” remains at the lower right.
A close view presents a black Aroma360 diffuser on a countertop.
It is tall, cylindrical, and slim, standing on a round base.
A small rectangular remote lies on the counter beside it.
White text to the right reads “ COLD AIR DIFFUSION. ” The background is softly blurred, with the kitchen area and a plant visible.
The man is then seen smiling and laughing with the same woman in the modern kitchen area.
He stands on the left in his dark jacket, and she stands on the right, now wearing a tan or golden-brown top.
Both face each other with open, \textbf{cheerful} expressions.
The top of a black diffuser is visible between them near the bottom of the image, reinforcing that the product is part of the space.
A silver cylindrical diffuser is shown again on a glass \textbf{table} in front of the white tufted \textbf{sofa}, with a remote control placed beside it.
The device is upright and cleanly designed, matching the bright, minimalist décor.
The woman and man sit together on the white \textbf{sofa}.
She holds the silver diffuser upright in one hand as if showing it, while he sits beside her in a black outfit, hands together, watching her.
On the glass \textbf{table} in front of them are additional Aroma360 items, including a black diffuser and small scent bottles.
The woman then holds a small clear bottle close to her nose and smells it, eyes relaxed.
White text appears beside her : “ HEALTHY LUXURY SCENTING. ” Her dark nail polish is visible as she grips the bottle.
The image fades through a soft white wash, then both people are seated side by side on the \textbf{sofa} again, facing forward.
The woman sits on the left, composed and attentive ; the man sits on the right, gesturing as he speaks.
On the glass \textbf{table} in front of them are the silver and black cylindrical diffusers and several small clear bottles arranged neatly.
A dark rectangular website graphic appears across the lower center reading “ aroma360.com, ” with a visible cursor pointer nearby.
The QR code remains at the lower right.
The commercial ends on a clean off-white promotional card.
Centered near the top is the Aroma360 logo.
Large black text reads “ 25 \% OFF, ” with “ USE CODE : DJ25 ” underneath.
To the right is a QR code labeled “ SCAN ME. ”

% matched lemmas: built-in, chair, cheerful, curtain, decorative, home, hotel, live, living, lounge, palm, room, sheer, sofa, table
\end{textsample}
