\begin{textsample}{POS Dim 4 – 1970 – Score 6.00 – 1970/tv\_com\_1970\_51.txt}  \label{ex:f4_pos_066}
The commercial begins with a nearly dark/blank frame, with archival watermarks visible.
It then cuts to a bright street-side or storefront scene with several children \textbf{gathered} around a puppet-theater window.
The booth or frame is red, set beside a brick wall.
A \textbf{colorful} puppet with a round, sun- or lion-like face appears in the window, facing a boy standing closest to it.
The boy appears to be holding a small wrapped rectangular item, possibly a candy \textbf{bar}, though the exact label is not clear in this frame.
Other children are seen from behind or in partial profile watching.
The next scene shifts to a city street.
A \textbf{blonde} woman in a dark outfit and peaked cap stands near the roadway while cars pass by, including a yellow taxi moving across the frame.
Parked cars and building fronts are visible in the background.
Her clothing and cap give the impression of a uniform, but the specific role is not visually confirmed.
A brief bright, washed-out transition follows, obscuring most detail.
The woman is then shown in close-up, still wearing the peaked cap.
She holds a small wrapped bar-shaped item close to her mouth or chin.
The foreground is partly blurred, as if shot through or past a passing vehicle or reflective surface, making the packaging difficult to read clearly.
The final frame shows a wide downhill city street \textbf{leading} toward a bay or waterfront in the distance.
Large white superimposed text reads “ HERSHEY ’S, ” with smaller text below reading “ The Great American Chocolate \textbf{Bar}. ” Cars and buildings line the street, and \textbf{water} and distant land or boats are visible beyond.

% matched lemmas: bar, blonde, colorful, gather, lead, water
\end{textsample}
