\begin{textsample}{POS Dim 4 – 1960 – Score 17.00 – 1960/tv\_com\_1960\_91.txt}  \label{ex:f4_pos_064}
The commercial opens in black and white at night outside a modern two-storey \textbf{home}.
Large rectangular windows glow from within behind \textbf{sheer} \textbf{curtains}, and the dark \textbf{swimming} \textbf{pool} in front mirrors the bright window shapes and vertical \textbf{curtain} lines.
A low \textbf{patio} edge, a \textbf{pool} ladder, and dark shrubs or small trees frame the house, with the water surface acting like a glossy reflection.
The image gradually blends into a spacious \textbf{living} \textbf{room}.
The \textbf{room} has a highly polished floor that reflects \textbf{furniture} and light almost like still water.
On the left are floor-to-ceiling \textbf{curtains}, a lamp on a side \textbf{table}, and part of a \textbf{sofa}.
Near the centre sits a light-coloured upholstered armchair.
On the right, a fireplace burns brightly, flanked by two tall \textbf{decorative} stands filled with rounded, stacked ornaments or plants.
A second lamp and shelves are visible in the background.
The floor ’s shine is emphasised by the clear reflections of the \textbf{chair}, lamps, fireplace, and flames.
A large product package appears over the \textbf{living} \textbf{room} scene on the left.
It is a tall bottle or can with a cap and a bold label reading “ klear.
FLOOR WAX. ” Smaller visible label text includes “ New Formula ” and “ WO N’T YELLOW ANY FLOOR. ” To the right of the package, large white capital letters read “ NEW FORMULA KLEAR. ” The product and text sit in the foreground while the elegant \textbf{living} \textbf{room} remains visible behind them.
The product graphic disappears, returning to the empty \textbf{living} \textbf{room}.
The attention moves visually toward the fireplace and the shining floor in front of it.
The flames flicker between two tall andirons, and their bright shapes are reflected on the glossy floor below.
Large white capital letters appear along the bottom of the image : “ DEEP LOOK SHINE. ” The words stretch across the lower part of the scene, directly over the floor reflection, reinforcing the mirror-like finish.
An adult woman then appears in a closer view, facing forward as if addressing the viewer.
She has a neat, curled 1960s hairstyle and wears a smooth, light-toned \textbf{blouse} or dress with buttons, a \textbf{decorative} \textbf{bow} or folded detail near one shoulder, and a short pearl \textbf{necklace}.
She smiles broadly at first.
Both hands are raised near shoulder level, with her thumbs or fingers extended in emphatic gestures.
As she continues, she turns slightly and gestures to either side, then lowers her hands and speaks more directly, her expression becoming focused and confident.
The image blends back to the fireplace and polished floor.
The flames continue to rise and shift, and their reflection shimmers on the floor surface.
The “ DEEP LOOK SHINE ” text appears again in large white capitals across the lower portion of the scene while the fire, andirons, flanking \textbf{decorative} stands, and glossy floor remain centered.
At the end, the product package returns in the foreground on the left, again showing the “ klear.
FLOOR WAX ” label with “ New Formula ” above it and “ WO N’T YELLOW ANY FLOOR ” on the front.
Large white text to the right reads “ NEW FORMULA KLEAR. ” Behind the product, the \textbf{living} \textbf{room} with its armchair, \textbf{curtains}, lamp, fireplace, and reflective floor remains visible, presenting the wax as connected with the \textbf{room} ’s clear, deep shine.

% matched lemmas: blouse, bow, chair, curtain, decorative, furniture, home, live, living, necklace, patio, pool, room, sheer, sofa, swimming, table
\end{textsample}
