\begin{textsample}{POS Dim 4 – 2020 – Score 27.00 – 2020/tv\_com\_2020\_1.txt}  \label{ex:f4_pos_001}
The commercial opens on a white flag with a \textbf{turquoise} stripe along the bottom, fluttering against a bright blue sky.
In bold dark letters across the flag is the Orbitz name and logo.
The scene shifts to a \textbf{sunny} beach : a slim, shirtless young man with light skin, \textbf{curly} dark hair, and a small mustache stands near the shoreline with his hands on his hips.
He wears red-and-white vertically striped swim briefs.
Behind him, pale sand curves toward a tall white lighthouse, with rows of blue beach umbrellas and a few people in the distance.
A small open-air cart drives along a narrow road lined with trees and dense greenery.
A middle-aged Black woman with voluminous \textbf{curly} hair sits upright in the back seat, facing forward.
She wears a patterned pink top, red pants, sandals, \textbf{bracelets}, and holds a large woven \textbf{bag} beside her.
The cart has red upholstery and \textbf{decorative} red elements hanging from its roof.
A driver in white is partly visible in front.
On the roadside to the right is a green sign with white writing, including the word “ VYTILLA. ” On the left, a few people stand near the road, one lifting an object above his head as the cart passes.
Inside a \textbf{cozy} ski-lodge-like \textbf{room}, two adults in winter gear stand near a row of skis.
One, presenting as male, wears a red jacket, black pants, ski goggles pushed up on his head, and has one hand on his hip.
Beside him, another adult presenting as female wears a gray-and-white plaid ski jacket, white snow pants, a green hood or hat, purple earflaps or hair framing the face, glasses, and holds a pair of skis upright.
Behind them are large windows looking out onto snowy mountains, wooden walls, snowshoes, skis, and lodge \textbf{furnishings}.
Other people sit or stand in the background, bundled for winter.
At a modern tropical resort, an older Black man stands shirtless on an upper balcony beside a glass railing.
He wears a dark sarong or wrap \textbf{skirt} with a large floral pattern.
Below him is a \textbf{turquoise} \textbf{swimming} \textbf{pool}, white \textbf{hotel} balconies, \textbf{lounge} \textbf{chairs}, umbrellas, \textbf{palm} trees, and bright sun.
A closer view shows the floral wrap tied at his waist and his hand resting confidently on his hip.
Then his face is seen more clearly : he is bald with a gray beard, looking steady and self-assured, with lush greenery and blue sky behind him.
In a \textbf{hotel} bedroom, a young couple lies side by side under a dark \textbf{blanket} on a large bed with a tufted \textbf{cream} headboard.
The young man, in light blue pajamas, lies on his back looking toward the young woman.
The young woman, in a pale patterned pajama top, lies beside him, turned slightly toward him, her hands resting over the \textbf{blanket}.
The \textbf{room} is softly lit, with a bedside \textbf{table} and lamp visible.
A wider view of the same bed shows the covers rising into a tent-like mound over the middle of the mattress, while the rest of the \textbf{room} remains neat and symmetrical, with lamps on both sides and a service tray or drinks \textbf{table} to the right.
On a bright outdoor terrace overlooking the ocean, two people relax in separate square wooden soaking tubs.
A man sits in the left tub with his arms \textbf{draped} over the rim, smiling toward the woman in the right tub.
The woman, wearing \textbf{sunglasses} and a head covering, smiles back from her own tub.
Large \textbf{potted} tropical plants frame the scene, and the sea stretches out beyond a low wall.
Beside a resort \textbf{pool}, an elderly woman reclines on a turquoise-cushioned \textbf{lounge} \textbf{chair}.
She has light skin, a blonde beehive-like hairstyle or wrapped hair, oversized white round \textbf{sunglasses}, large earrings, and a pale pink flowing cover-up over a \textbf{decorative} swimsuit or \textbf{necklace}.
Her legs are stretched out, and she appears relaxed and \textbf{amused}.
The \textbf{pool} water gleams beside her, with \textbf{palm} trees, white umbrellas, and the ocean in the background.
A person in white walks near the \textbf{pool} behind her, carrying cleaning or \textbf{pool} equipment.
A closer view shows her smiling slightly from behind the large white \textbf{sunglasses}.
Back in the ski lodge, the two winter-dressed adults stand closer to the foreground, facing forward.
The person in the red jacket stands solidly with one hand on the hip ; the person in the plaid jacket holds skis upright at their side.
Their expressions are calm and resolved, with racks of skis and wooden wall panels behind them.
The beach scene returns to the slim young man in \textbf{striped} swim briefs.
Now he lifts a pair of reflective \textbf{sunglasses} to his face with one hand.
The white lighthouse rises blurred behind him, and the sunlit beach and blue umbrellas remain in the background.
The elderly woman at the \textbf{pool} appears again in profile on her \textbf{lounge} \textbf{chair}, still wearing her white \textbf{sunglasses} and looking relaxed, with the ocean and a \textbf{pool} worker behind her.
A wide green golf course appears, lined with tall \textbf{palm} trees and dotted with sand traps.
Two golfers stand on the fairway near a small golf cart.
One golfer, a light-skinned man wearing a white shirt, yellow argyle sweater vest, blue pants, cap, \textbf{sunglasses}, and a golf glove, holds a smartphone in one hand while a golf club rests nearby.
Another golfer stands behind him in a blue-and-red top and tan pants, watching.
A close view shows the smartphone in the golfer ’s hand.
The Orbitz mobile \textbf{app} is open, with the Orbitz logo at the top and a list of \textbf{hotel} options displayed below, including small \textbf{hotel} \textbf{photos}, star ratings, and prices.
A thumb scrolls or taps the screen.
The display changes to a \textbf{hotel} detail page with a \textbf{photo} of a bedroom at the top, text beneath it, and a prominent blue action button near the lower right, suggesting a booking step.
The final scene returns to the golf course.
The golfer in the argyle vest stands on the fairway holding a flagpole with a blue Orbitz flag.
The flag flutters in the open air among tall \textbf{palm} trees, green grass, and bright sun, echoing the opening image of the Orbitz-branded flag.

% matched lemmas: amuse, app, bag, blanket, bracelet, chair, cozy, cream, curly, decorative, drape, furnishing, hotel, lounge, necklace, palm, photo, pool, potted, room, skirt, striped, sunglasses, sunny, swimming, table, turquoise
\end{textsample}
