\begin{textsample}{POS Dim 4 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_98.txt}  \label{ex:f4_pos_042}
The commercial begins with a very dark, nearly black image ; no clear objects or setting are visible in the first sampled frame.
It then cuts or dissolves into a montage of wildlife and \textbf{water} scenes.
A watery shoreline scene appears with \textbf{tall} reeds or grasses in the background.
In the foreground, animals are partially visible in shallow \textbf{water} ; the image has a soft, layered quality, as if one shot is dissolving into another.
The next frame continues the watery setting, showing several birds on the surface of the \textbf{water}.
A white bird stands or moves at the right, while other birds are lower in the \textbf{water}.
The frame still appears superimposed with grasses or vegetation, suggesting an ongoing dissolve between nature shots.
The montage then shifts to open \textbf{water}.
A sea otter or similar marine mammal \textbf{floats} on its back in blue \textbf{water}, holding or \textbf{touching} something near its chest.
The animal is centered, with the \textbf{water} filling the background.
Another dissolve brings a close-up of a marine mammal ’s head, possibly an otter or seal/sea lion, with its mouth open.
The image is overlaid with another coastal or marine scene, creating a double-exposure effect.
The sequence then shows a beach or icy shoreline with penguins standing and \textbf{walking}.
Several penguins are visible in the foreground and midground, with pale \textbf{water} or surf behind them.
The image again appears blended with another animal scene.
Next, a \textbf{group} of seals or sea lions appears lying close together on a rocky or sandy surface.
Their pale bodies fill much of the frame, and the shot is softly tinted with \textbf{pink} and \textbf{purple} tones.
Some animals face upward or toward each other.
The montage then transitions to dolphins leaping above the ocean at \textbf{sunset}.
Several dolphins are silhouetted or semi-silhouetted against a \textbf{warm} pink-orange sky, with the sea and horizon visible behind them.
Faint remnants of the previous wildlife imagery remain layered underneath, indicating another dissolve.
The final frame is a black background with a white DuPont logo centered.
Beneath it, in italic white text, the slogan reads : “ Better things for better living. ”

% matched lemmas: float, group, pink, purple, sunset, tall, touch, walk, warm, water
\end{textsample}
