\begin{textsample}{POS Dim 4 – 2020 – Score 8.00 – 2020/tv\_com\_2020\_51.txt}  \label{ex:f4_pos_037}
The commercial begins with a close-up of a white tube of **Gold Bond Ultimate Crepe Corrector Age Defense**.
The packaging uses \textbf{purple} and gold accents, with “ NEW ” visible near the top.
It then cuts to a \textbf{warm} \textbf{outdoor} scene at \textbf{sunset} : a blond adult wearing a large backpack looks back while moving through a dry, open landscape.
The light is soft and golden.
Next, an adult with tattoos lies on a bed with two \textbf{young} children.
They are smiling and laughing together in a bright, domestic setting with white bedding.
The sequence shifts to a fitness setting.
A woman with a high ponytail, wearing a black athletic top, holds a dumbbell and appears to be exercising or strength training.
The background suggests an indoor gym or studio.
A close-up follows of two adults sitting closely together.
One person looks ahead while the other leans in smiling ; the scene is softly lit and intimate.
The ad then shows an extreme close-up of a hand \textbf{touching} or stroking light-toned skin near the neck or upper shoulder area. \textbf{Blonde} hair is visible at the edge of the frame, emphasizing skin texture and \textbf{touch}.
Another lifestyle image appears : an adult with very short light hair and a \textbf{young} child lie on green grass, smiling and embracing.
The camera looks down from above.
A close-up of skin and a hand appears with large pale-yellow text overlaid reading **“JUST.”** The background is sunlit and \textbf{warm}.
The product returns in a centered shot : a tube of **Gold Bond Ultimate Crepe Corrector Age Defense** stands in the foreground, while a blurred figure or body part appears in the background.
The commercial then shows a product lineup on a dark \textbf{teal} surface : multiple Gold Bond products are arranged together, including tubes and a pump bottle.
The packaging is primarily white with \textbf{purple} and gold branding.
The lighting dims, and the product lineup becomes mostly silhouetted against the \textbf{teal} background.
Large gold letters begin to slide or appear over the products.
The final frame shows the products darkened behind a bold, all-caps gold message : **“CHAMPION YOUR SKIN.”** The word “ SKIN ” appears slightly motion-blurred or still resolving in the sampled frame.

% matched lemmas: blonde, outdoor, purple, sunset, teal, touch, warm, young
\end{textsample}
