\begin{textsample}{POS Dim 4 – 2000 – Score 8.00 – 2000/tv\_com\_2000\_2.txt}  \label{ex:f4_pos_030}
The commercial opens on a nearly black frame, with no clear visible content.
It then cuts to a bright beach scene.
Several people are playing volleyball on sand near the ocean.
A net stretches across the foreground/midground, with beach umbrellas and seated beachgoers around the court.
The \textbf{water} and waves are visible in the background.
The next shots focus more closely on the volleyball action : a close-up of a player ’s \textbf{legs} in black shorts with yellow flame-like trim, then low-angle shots near the net as players look upward and reach for the ball.
Small white legal text appears near the bottom in some of these shots ; one line appears to refer to “ Subway ” as a registered trademark, though the full text is partly difficult to read.
A wider beach shot shows the ocean horizon, a \textbf{purple} beach umbrella, and a person running or moving across the sand.
The volleyball is shown isolated against a pale blue sky, followed by a shirtless man in black shorts preparing to receive or catch it.
Another shot from behind the net shows a woman in a \textbf{pink} \textbf{sleeveless} top looking upward, with other players behind her.
The setting remains the beach.
A low shot shows the volleyball net across the frame, with the sea and sand beyond.
The scene then changes to a large mound of sand, with parts of a human body or bodies partly buried or protruding from the sand ; the exact arrangement is somewhat unclear.
In a later shot, a man ’s head and face are visible at the right side of a large sand mound, suggesting he is buried in or covered by sand, while other people stand nearby.
White disclaimer text appears at the bottom ; it is partially legible and appears to state that results are not typical and involve a reduced-calorie diet including Subway low-fat sandwiches.
Another beach shot shows several people \textbf{gathered} near the buried person, apparently interacting with the sand around him.
The ocean remains in the background.
The commercial then presents a \textbf{group} shot by the \textbf{water}.
A shirtless heavier man stands on the left, while a man in a \textbf{purple} outfit stands center.
Large white on-screen text reads : “ Jared Fogle ” and “ Lost 245 lbs. ” Other beachgoers stand around them.
The scene cuts to close-up product imagery : several Subway-style sandwiches with bread, lettuce, tomato, olives, and other fillings.
One close-up shows the sandwich ingredients in detail, including green peppers or lettuce, tomato slices, and olives.
Part of a Subway-branded paper or wrapper is visible.
The setting then moves indoors to a Subway restaurant.
A \textbf{group} of people, including the man in \textbf{purple}, stand or \textbf{walk} inside with Subway logos visible on the windows behind them.
White text at the bottom reads : “ Ask your doctor before starting any weight-loss plan. ” A close-up shows the man in \textbf{purple} seated indoors, wearing glasses, eating a sandwich.
The final branded shot shows him chewing while holding the sandwich.
The Subway logo appears large on-screen with the phrase “ eat fresh. ” A website address, “ www.subway.com, ” is visible at the bottom left.
After this branded end frame, the sampled sequence continues into abstract or transitional visuals : first a solid orange-brown screen, then a brown-and-tan checkerboard pattern, followed by a higher-contrast black-and-white checkerboard pattern.
No people or product are visible in these final checkerboard frames.

% matched lemmas: gather, group, leg, pink, purple, sleeveless, walk, water
\end{textsample}
