\begin{textsample}{POS Dim 4 – 2020 – Score 16.00 – 2020/tv\_com\_2020\_3.txt}  \label{ex:f4_pos_014}
A bright \textbf{home} \textbf{entryway} or mudroom is seen with an open wooden glass-panel door leading to a \textbf{sunny} green yard.
Along the left wall are white \textbf{built-in} shelves and cupboards with coats hanging on a rail, a backpack, \textbf{bags}, boots, a watering can, and other household items.
A woman with shoulder-length dark wavy hair and bangs enters carrying a large soft white \textbf{laundry} tote or \textbf{bag} against her chest.
She wears a mustard-yellow textured \textbf{blouse}, \textbf{teal} pants, and white sneakers.
Behind her, a man with short dark hair and a mustache follows through the doorway in a dusty-pink polo shirt, tan pants, and light shoes.
As the woman moves farther inside, she slows and reacts strongly to something unpleasant.
In close-up, she clutches the white \textbf{bag} near her chest, wrinkles her nose, and squints with a disgusted expression.
She turns her head, points or gestures toward the \textbf{bag} or the space around her, and looks off to the side as if identifying the source of the smell.
Her face shifts between grimacing, talking, and wincing, with her shoulders slightly hunched and one hand held near her chest.
The man is then shown closer, standing in the same \textbf{entryway} near the open door and hanging coats.
He closes his eyes tightly and makes a strained, repulsed expression, his mouth opening as if reacting to the same odor.
An elderly woman with short white hair appears near the doorway, wearing a red cardigan over a light gray top and a \textbf{colorful} beaded \textbf{necklace}.
She faces inward toward the others, her expression alert and slightly stern, speaking or reacting while standing in the daylight from the open door with the \textbf{garden} behind her.
The group gathers in the mudroom.
The woman stands on the left, now covering part of her face with her hand in a disgusted or embarrassed gesture.
The man stands beside her holding the large white \textbf{laundry} \textbf{bag}.
Behind them, the elderly woman remains near the doorway, and a young boy with \textbf{curly} brown hair stands in front of her wearing a bright \textbf{turquoise} T-shirt and dark shorts.
The boy looks up toward the adults while the man and woman focus on the \textbf{bag} and the smell.
The scene shifts to a close view inside a closet or coat area.
A hand hangs a DampRid Hanging Moisture Absorber from a white closet rod among clothing on black hangers.
The product is a rectangular hanging pouch with a white upper section and a darker clear lower collection chamber.
The DampRid logo appears prominently on the front in red letters over a \textbf{teal} swoosh.
Coats and sweaters hang around it, including a tan knit \textbf{garment} and a \textbf{denim} item.
White on-screen text appears beside the product reading, “ Traps excess moisture. ” A blue arrow graphic points inward from the lower left toward the hanging pouch, visually suggesting moisture being drawn into the absorber.

% matched lemmas: bag, blouse, built-in, colorful, curly, denim, entryway, garden, garment, home, laundry, necklace, sunny, teal, turquoise
\end{textsample}
