\begin{textsample}{POS Dim 4 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_16.txt}  \label{ex:f4_pos_036}
The commercial begins in black-and-white animation at a small dining \textbf{table} in a \textbf{cozy} \textbf{home} setting.
A young adult couple sits facing each other with a \textbf{curtained} window behind them and patterned wallpaper covered with small heart shapes.
On the left, a dark-haired man in a black dinner jacket and \textbf{bow} tie smiles across the \textbf{table}.
On the right, a blonde woman with a smooth bob hairstyle wears a dark dress and a short \textbf{necklace}, seated in a high-backed \textbf{chair}.
Between them is a round frosted cake, with a slice missing, and each has a small plate with a slice of cake.
The woman holds a fork lightly as the man looks pleased and animated, turning toward her as if praising the cake.
The man leans closer across the \textbf{table}, smiling broadly.
The woman smiles back, then lowers her gaze shyly and closes her eyes with a pleased expression.
He reaches toward her, places a hand on her shoulder, and moves around or leans in beside her.
His posture becomes affectionate and congratulatory, while she sits demurely, smiling with her eyes closed.
He wraps an arm around her, drawing close, and kisses her on the \textbf{cheek}.
She responds with a contented smile.
Then she holds up a large award-like rosette or badge between them.
It has a round center with bold lettering and ribbon-like edges, visually presenting her as a “ Gold Medal ” baker.
The rosette fills the picture.
Large readable text in the center says “ Gold Medal, ” and below it, on stacked labels, “ BAKING ” and “ EXPERT. ” The badge is shown close-up, held by cartoon hands, with radiating lines around it that make it look like a prize or seal of achievement.
The animation gives way to a live-action kitchen.
For a moment, the same “ Gold Medal Baking Expert ” badge remains large in front of the scene, then it disappears to reveal a smiling woman standing in a bright, tidy 1950s kitchen.
She appears to be an adult woman with light hair styled neatly back from her face.
She wears a dark dress or \textbf{blouse} with a light collar detail.
Behind her are \textbf{built-in} shelves holding dishes and \textbf{decorative} kitchen items, a stove area, and smooth countertops.
She faces forward, speaking directly to the viewer.
A man in a suit and tie gradually becomes visible at her left.
He stands beside her behind the counter, looking toward her with a friendly expression.
On the counter in front of them sits a \textbf{bag} of Gold Medal flour and a plate with a thick slice of layer cake.
The woman remains centered and composed, hands near the counter, while the man watches her.
Large white block letters appear across the lower part of the picture, building word by word over the counter area.
The text grows into the phrase “ EXPERT RESULTS WITH EVERYTHING YOU BAKE. ” The flour \textbf{bag} remains visible near the left side of the cake slice, reinforcing the product being discussed.
The live-action kitchen setting stays clean and orderly, with shelves and dishes forming a \textbf{domestic} backdrop.
A close-up then shows the product and cake together.
On the left is a paper \textbf{bag} labeled with the Betty Crocker mark at the top and a large circular “ Gold Medal ” logo.
The word “ FLOUR ” appears in large letters near the bottom of the \textbf{bag}.
To the right is a frosted layer cake slice on a plate, with dark cake layers and a light frosting layer through the middle and on top.
The flour package and the finished cake are placed side by side as a clear product-and-result display.
The woman appears again in a closer view in the kitchen, smiling and speaking toward the viewer.
Her expression is confident and friendly.
The open shelving and dishes remain behind her.
She looks straight ahead for much of this part, occasionally changing her expression as she continues.
The view widens back to include the man at her left and the counter.
The Gold Medal flour \textbf{bag} stands upright in front of them, and the layer cake slice rests on its plate beside it.
The woman reaches for the cake and lifts the plate with both hands, presenting it at about chest height.
She smiles while holding the cake forward.
The man stands beside her, also facing forward, as if joining in the presentation.
The scene then returns to the animated dining \textbf{room}.
The cartoon husband is again beside the blonde wife at the \textbf{table}, his arm around her shoulders.
The heart-patterned wallpaper and \textbf{curtained} window reappear in the background, with the cake still on the \textbf{table}.
He leans in affectionately, and she smiles, closing her eyes as he kisses her \textbf{cheek}.
The woman then holds up the same prize badge again, smiling toward him.
The final images return to the close-up of the cartoon rosette.
Its center reads “ Gold Medal, ” with “ BAKING ” and “ EXPERT ” on labels beneath.
Cartoon hands hold it at the sides, and bold radiating lines around the badge make it look like a proud award for successful baking.

% matched lemmas: bag, blouse, bow, built-in, chair, cheek, cozy, curtain, decorative, domestic, home, necklace, room, table
\end{textsample}
