\begin{textsample}{POS Dim 4 – 2010 – Score 22.00 – 2010/tv\_com\_2010\_96.txt}  \label{ex:f4_pos_023}
A woman with shoulder-length dark brown hair stands indoors against a softly blurred garage or home-workspace background.
She appears to be an adult, wearing a \textbf{sleeveless} floral \textbf{blouse} with ruffled shoulders and a small \textbf{necklace}.
She faces forward, first with a closed-mouth smile, then breaking into a broad laugh.
Behind her, indistinct shapes suggest a bicycle, wall \textbf{art}, shelves, and household storage.
The view opens to show her full body standing in the doorway of a garage framed by green ivy.
She wears gray pants with the floral \textbf{blouse} and raises one hand in a casual \textbf{wave}.
The garage interior is bright and tidy, with a bicycle on the left, storage shelves along the back, and \textbf{bins} or equipment on the right.
White lowercase text appears across the middle : “ noom stories. ” The scene changes to a \textbf{backyard} \textbf{pool} area.
A young adult woman with long dark hair dyed reddish-purple at the ends stands beside the \textbf{pool}, facing forward.
She wears glasses, a purple \textbf{sleeveless} crop top, and dark patterned shorts.
Behind her are two red circular woven \textbf{patio} \textbf{chairs}, a small black side \textbf{table}, dense green hedges, and the blue edge of the \textbf{swimming} \textbf{pool} on the right.
The white “ noom ” logo sits in the upper-right corner.
Small lower text identifies her as a Noom user.
She gestures outward with both hands, then lets her arms rest at her sides, her expression shifting from matter-of-fact to more relaxed.
The woman from the garage returns, now standing centered in the ivy-framed garage opening.
Small white text near her reads “ Katelyn ” and “ Noom User. ” She clasps her hands in front of her and speaks toward the viewer.
A closer view follows, with the “ noom ” logo in the upper-right corner ; her floral \textbf{blouse} and \textbf{necklace} are clearer, and she gestures lightly near her chest while maintaining direct eye contact.
Back by the \textbf{pool}, the woman in purple smiles in the \textbf{sunny} \textbf{garden} setting, still positioned between the red \textbf{chairs} and the \textbf{pool}.
Then a man appears in a bright white kitchen.
He is an adult with dark hair and a full beard, wearing a navy short-sleeve henley shirt.
He stands near a kitchen island, holding a white towel or \textbf{cloth} in one hand.
The background includes white cabinets, a refrigerator covered with family \textbf{photos} or small notes, a window, a \textbf{fruit} bowl with oranges, and a phone lying on the counter.
On-screen text identifies him as “ Mike ” and “ Noom User, ” with the “ noom ” logo in the upper-right corner.
A blonde woman named “ Sarah, ” identified by small white text as a Noom user, sits in a softly lit bedroom.
She has long straight hair and wears a pale floral off-the-shoulder \textbf{blouse}.
Behind her is a white tufted headboard, pillows, and bright \textbf{sheer} \textbf{curtains} glowing with daylight.
She speaks while seated, looking forward, then the view widens to show the whole bedroom : pale blue walls with sloped ceilings, a bed centered under the window, bedside \textbf{tables}, a dresser on the left, a \textbf{decorative} stand with a hat and scarf, wicker baskets on the right, and a light \textbf{rug} on a wooden floor.
Sarah stands at the foot of the bed, leaning back on her hands for a moment, then turns and walks a few steps beside the bed before facing forward again with a smile.
Mike reappears in the white kitchen, first shown from the waist up and then closer.
The refrigerator \textbf{photos} and notes are visible behind him, and the “ noom ” logo remains in the upper-right.
He looks straight ahead as if giving his testimonial.
The poolside woman returns, standing still and smiling gently in the \textbf{garden}, with the red \textbf{patio} \textbf{chairs} behind her and the \textbf{pool} edge on the right.
A closer view shows her from the waist up against a \textbf{leafy} green background ; she glances slightly downward with a small, satisfied smile.
The “ noom ” logo stays in the upper-right, and faint fine print runs along the bottom.
The final visible image is a flat coral-red graphic screen.
It has minimal white dotted elements : a short dotted horizontal line on the left, another on the right, and a small vertical row of white dots near the top, suggesting a simple app-style or brand graphic transition.

% matched lemmas: art, backyard, bin, blouse, chair, cloth, curtain, decorative, fruit, garden, leafy, necklace, patio, photo, pool, rug, sheer, sleeveless, sunny, swimming, table, wave
\end{textsample}
