\begin{textsample}{POS Dim 4 – 2000 – Score 18.00 – 2000/tv\_com\_2000\_76.txt}  \label{ex:f4_pos_052}
A bright beach scene opens with dark silhouettes against a pale sky and ocean.
An adult figure walks along the sand near the water, with two small children following at different distances.
The figures are mostly in shadow, stretched out by the sunlight, with \textbf{waves} and a wide blue sky behind them.
A close view then shows a \textbf{little} blonde girl, preschool age, standing in front of dense green leaves.
She wears a \textbf{denim} jacket over a pink \textbf{striped} top.
On her head is a folded, \textbf{colorful} paper hat, like a homemade crown or newspaper hat, decorated with bright images.
She holds the sides of the hat with both hands, adjusting it while looking forward with a small, pleased smile.
On the beach, three girls sit together among tall dune grass.
The oldest, with shoulder-length brown hair, is wrapped partly in a large yellow \textbf{blanket}.
A younger curly-haired child sits close beside her.
The blonde girl sits on the right, smiling broadly, wearing a red-and-orange beret, a pink \textbf{striped} top, a dark scarf, dark leggings, and chunky shoes.
The three children face one another and then look outward, relaxed and \textbf{cheerful} in the sun.
The blonde girl appears again on a wooden boardwalk with railings on both sides, surrounded by sandy beach plants.
She wears a bright, mismatched outfit and carries or drags fabric around her as she moves along the planks, suggesting dress-up play.
Indoors, the older brown-haired girl sits on a soft \textbf{chair} or couch, wearing a light cardigan and pants, writing or drawing in a notebook with a pencil.
She looks down with concentration, then turns her head toward the bright window beside her.
Near that window, the blonde girl reclines in a \textbf{chair} in a pink \textbf{striped} outfit.
Outside the window, a hanging \textbf{flower} basket with purple blooms is visible.
She wears an oversized, playful hat covered with small toys or decorations and holds a wand-like object topped with a dark star and curling ribbons.
She studies it with absorbed attention, her legs stretched out in yellow pants with large dark polka dots.
Outside in front of a \textbf{leafy} hedge, the blonde girl models more imaginative outfits.
First she turns in a pink \textbf{striped} shirt with a huge, pale straw or raffia \textbf{skirt} flaring around her hips, white leggings, and heavy dark shoes.
Then she stands inside a large terracotta flowerpot, dressed like a \textbf{flower} : a pink \textbf{striped} dress belted in red, with a large red-orange flower-like headpiece.
She stands still and upright against the green hedge as if posing.
She then looks down at herself while wearing the same pink \textbf{striped} dress, now layered with a fluffy \textbf{lavender} feather boa around her shoulders and black fuzzy mitts or \textbf{sleeves} on her hands.
She grips and spreads the boa, checking the front of the dress beneath it.
The pink dress is central to the outfit, visible through the feathers.
On a porch or sunroom, the blonde girl sits in a white wicker \textbf{chair} at the left, still in pink stripes, holding a small container and spoon.
An adult passes briefly in the foreground, and in the background a woman with brown hair sits in a white \textbf{chair}, wearing a blue top and holding reading material.
A white \textbf{laundry} basket is nearby.
The porch is bright, with white walls, windows, and \textbf{flowers} at the edge.
A close view of the blonde girl shows her eating from the small cup with a spoon.
A dark red-brown food stain is smeared around her mouth and drips down the front of her pink \textbf{striped} shirt.
She raises the spoon to her mouth, scoops more, then looks satisfied, smiling with her lips closed as the stain remains clearly visible on the fabric.
The product appears prominently : a red plastic bottle of Tide with Bleach Alternative sits on a patterned surface in front of a sunlit window.
The large Tide logo fills the label, with the words “ Tide, ” “ Bleach, ” and “ Alternative ” visible.
Small white website text, “ www.clothesline.com, ” appears along the lower right of the image.
The bottle has a gray cap and a \textbf{built-in} handle on the right side.
A clean pink \textbf{striped} dress hangs neatly on a blue paneled wall from a flower-shaped hook.
A Tide logo graphic is placed over the lower part of the dress, visually linking the \textbf{garment} to the detergent.
The dress looks bright and intact, with its pink color preserved.
Later, the blonde girl wears the pink \textbf{striped} dress outdoors on a wooden swing.
She leans back, holding the rope with one hand, her pale legs extended forward, and green grass fills the background.
In another skyward scene, several small kites or wind toys float against a deep blue sky with soft clouds.
Back on the beach, the blonde girl, still in the pink \textbf{striped} dress, laughs and looks upward while interacting with another small child whose \textbf{curly} blond head is in the foreground.
The ocean and pale sand stretch behind them.
She holds something orange near her chest and gazes up with an open, delighted expression, her hair \textbf{blown} across her face by the wind.
The commercial ends with silhouetted figures among tall beach grass against a bright sky.
Over them, a large Tide with Bleach Alternative logo appears in the center, orange and yellow behind the bold dark “ Tide ” lettering and white “ Bleach Alternative ” text.
Beneath the logo, the on-screen slogan reads, “ IT ’S GOT TO BE TIDE. ”

% matched lemmas: blanket, blow, built-in, chair, cheerful, colorful, curly, denim, flower, garment, laundry, lavender, leafy, little, skirt, sleeve, striped, wave
\end{textsample}
