\begin{textsample}{POS Dim 4 – 2010 – Score 17.00 – 2010/tv\_com\_2010\_117.txt}  \label{ex:f4_pos_029}
A bright, \textbf{airy} \textbf{living} \textbf{room} appears, with white carpeting, floor-to-ceiling windows, and a wide green lawn and trees visible outside.
A small fluffy white \textbf{dog} sits on the pale \textbf{carpet} near a round glass coffee \textbf{table}.
The \textbf{room} is neat and modern : a light gray \textbf{sofa} with pillows and a throw \textbf{blanket} sits behind the \textbf{table}, a wooden cabinet stands to the left, and the coffee \textbf{table} holds a tall beige vase and a clear glass vessel.
The \textbf{little} \textbf{dog} turns and trots toward the \textbf{sofa}, then springs up onto it.
It stands on the cushions, its white fur blending with the light upholstery.
A young adult woman with long light-brown hair, fair skin, a pale gray short-sleeved top, blue jeans, and light shoes walks in from the right.
She looks toward the \textbf{dog} with a gentle smile.
A closer view of her face shows her smiling softly, eyes lowered as if watching the \textbf{dog} or the floor.
She kneels on the \textbf{carpet} beside the coffee \textbf{table}.
A red trigger spray bottle stands upright next to her, and she uses a white \textbf{cloth} to scrub a spot on the \textbf{carpet}.
The \textbf{dog} lies on the \textbf{sofa} behind her, watching over the edge of the cushion.
The woman ’s posture is bent forward and focused, one hand braced on the \textbf{carpet} while the other rubs with the \textbf{cloth}.
The \textbf{room} remains spotless-looking and sunlit, with the pale \textbf{carpet} dominating the space.
The view pulls upward to reveal the \textbf{living} \textbf{room} arranged inside a large, shallow, circular dish, like a petri dish.
Furniture, the woman, and the \textbf{dog} become small within the round white boundary.
Pale gray circular marks and purple blotches begin to appear across the \textbf{carpeted} area, visually suggesting hidden contamination spreading around the clean-looking \textbf{room}.
The woman then walks across the \textbf{living} \textbf{room} toward a wooden cabinet.
She opens a lower cabinet door.
Inside, a blue Woolite spray bottle sits on a shelf in front of stacked wooden slats and folded \textbf{cloths}.
The bottle has a gray trigger with a \textbf{lime-green} nozzle and label accents.
Its front label reads “ Woolite ” and “ sanitize, ” with additional smaller pet-stain-and-odor wording.
Small white legal text appears along the bottom of the screen, stating that Woolite is a trademark of Reckitt Benckiser licensed to BISSELL Homecare, Inc.
The woman reaches in, grips the bottle by the neck, and lifts it out.
Back by the \textbf{sofa} and \textbf{carpet}, she holds the Woolite bottle in one hand and leans down toward the floor.
A close view shows her wiping the \textbf{carpet} again with a white \textbf{cloth}.
A faint brownish stain is visible on the pale \textbf{carpet}.
She brings the blue Woolite trigger bottle into view, aiming its nozzle toward the stain.
Her wrist has a simple \textbf{bracelet}, and her hand holds the sprayer steadily above the spot.
The product label is partly visible as she positions it over the stained area.
The imagery then shifts to an enlarged, stylized view of \textbf{carpet} fibers.
Beige looped strands of \textbf{carpet} rise like soft columns, and small purple and green germ-like shapes cling among the fibers.
Blue on-screen text appears across the center : “ KILLS 99.9 \% OF BACTERIA. ” The bacteria-like shapes remain scattered among the fibers while the bold text stays prominent.
The woman is then back in the \textbf{living} \textbf{room}, kneeling on the pale \textbf{carpet} and smiling broadly.
The \textbf{little} white \textbf{dog} rushes into her arms, and she laughs visually, leaning forward with delight as she gathers it close.
The blue Woolite spray bottle now stands upright on the \textbf{carpet} near her knee, with the white \textbf{cloth} nearby.
She cuddles the \textbf{dog} against her chest, holding it securely while it faces outward, its dark eyes visible through its fluffy white fur.
The \textbf{sofa}, coffee \textbf{table}, pillows, and \textbf{sunny} windows remain in the background, reinforcing the clean, bright \textbf{home} setting.
The product is then presented alone on the pale \textbf{carpet} in front of a softly blurred window.
The blue Woolite Advanced Pet Stain and Odor Remover plus Sanitize bottle stands upright beside a crumpled white cleaning \textbf{cloth}.
A dark badge near the top of the label reads “ KILLS 99.9 \%. ” Blue text appears to the right : “ DO N’T JUST CLEAN.
SANITIZE. ” A light blue curved graphic sweeps behind the text.
Finally, the product lineup appears against a clean pale blue-white background.
The central bottle is the same Woolite “ sanitize ” trigger spray.
Additional Woolite cleaning products stand on either side, including tall aerosol-style cans with bright green caps.
Large blue “ Woolite ” branding appears to the right, completing the product display.

% matched lemmas: airy, blanket, bracelet, carpet, cloth, dog, home, lime-green, little, live, living, room, sofa, sunny, table
\end{textsample}
