\begin{textsample}{POS Dim 4 – 2000 – Score 10.00 – 2000/tv\_com\_2000\_58.txt}  \label{ex:f4_pos_027}
The commercial opens on a close-up of a small red circular light or button set into a pale, smooth surface.
It then cuts to a glossy \textbf{purple} circular object or lens against a saturated blue background, with a bright white flare at its center.
A fast, abstract transition follows : a glowing yellow triangular shape, resembling a “ play ” arrow, fills the frame with blurred imagery inside it.
The sequence then shifts into a \textbf{warm}, soft-focus close-up of a smiling woman with a \textbf{young} child beside her, followed by a bright close-up of a small child looking toward the camera.
The montage changes to a highly stylized \textbf{outdoor} shot of a \textbf{young} man with dark hair and glasses.
He is seated or posed in front of a vivid yellow building under a blue sky ; the camera angle is low and distorted, making his \textbf{legs} and the architecture appear exaggerated.
Next, there is a low-angle shot inside what appears to be a vehicle or aircraft-like interior, where two people in blue clothing are seated close together ; one person in front wears yellow-tinted eyewear or a blindfold-like covering.
Later, the man with glasses appears again in an urban setting between \textbf{tall} buildings.
He wears dark-framed glasses and headphones around his neck, smiling as the camera moves close to his face.
A low street-level shot shows the lower part of a yellow scooter or small vehicle moving along a city street past parked cars.
The montage continues with the same man in a blue shirt and dark vest, shown against a blurred blue-green background, as if moving quickly.
This is followed by \textbf{quick} close-ups of other people : a smiling child lit by cool blue light ; a woman in a red top looking upward or to the side in bright daylight ; silhouetted figures running or playing near \textbf{water} at \textbf{sunset} with a yellow inflatable object or board in the foreground ; and a laughing person in blue-green lighting.
Another action-oriented shot shows a person in a white shirt and dark pants falling, jumping, or flipping near a bright yellow edge against a deep blue background.
The exact \textbf{activity} is unclear from the sampled frame.
The commercial ends on a blue, glossy, bubble-like background with a centered brand card.
The visible text reads : “ Telocity ” with a yellow swoosh, “ High-Velocity Internet, ” “ www.telocity.com, ” and “ 1-800-TELOCITY. ”

% matched lemmas: activity, leg, outdoor, purple, quick, sunset, tall, warm, water, young
\end{textsample}
