\begin{textsample}{POS Dim 4 – 2010 – Score 17.00 – 2010/tv\_com\_2010\_84.txt}  \label{ex:f4_pos_028}
In a bright, formal banquet \textbf{room}, a young female-presenting server in a white dress shirt, black vest, black \textbf{bow} tie, and name tag stands among round \textbf{tables} set with white tablecloths, plates, cups, and folded napkins.
She has short dark hair and holds a yellow-and-red Starburst candy pack in one hand while looking down at it, as if considering the candy.
Behind her, a young male-presenting server in the same black-and-white waiter uniform works at another \textbf{table}, arranging place settings.
The \textbf{room} is pale and elegant, with many empty \textbf{chairs}, \textbf{draped} \textbf{curtains}, and buffet equipment in the background.
The male server becomes the focus.
He turns from his work and looks to the side, then toward the person he is addressing, wearing a faint, knowing expression.
His black \textbf{bow} tie, black vest, and name tag are visible against the white shirt as he appears to explain something.
The visual setting then shifts into an exaggerated imagined scene : a warm \textbf{living} \textbf{room} with \textbf{striped} green wallpaper, a framed \textbf{flower} picture on the wall, a \textbf{sunny} window, a green armchair, a blue \textbf{sofa}, a \textbf{potted} plant, and a vase of bright \textbf{flowers}.
A tiny dark fighter jet streaks into this \textbf{domestic} space, first glimpsed as a blur passing near the bouquet and then as a small aircraft hovering or flying around the \textbf{room} near the plant and \textbf{furniture}.
From inside the tiny jet, a transparent targeting display overlays the \textbf{living} \textbf{room}.
Through the cockpit view, the suited male server appears seated in the green armchair, holding Starburst candy, while a light-colored shaggy \textbf{dog} sits on the floor nearby.
The jet ’s controls and glowing green circular graphics sit along the bottom of the view, making the \textbf{living} \textbf{room} look like a miniature combat zone.
The pilot is then shown close up : an adult man in a red flight helmet marked with a yellow emblem, a gray oxygen mask covering his mouth and nose, and a green flight suit with straps and patches.
His eyes are focused and serious as he faces forward in the cockpit.
The tiny fighter jet flies low through the \textbf{living} \textbf{room}, seen from behind with wings outstretched and small pods under them.
Purple exhaust or vapor glows behind it as it heads toward the seated server.
White streaks trail through the air.
In an extreme close view, the server holds a small pink square Starburst candy between his fingers and opens his mouth to eat it.
Thin white streams or trails appear to shoot into or across the candy as he brings it to his lips, visually matching the idea from the dialogue context that “ juiciness ” is being fired into the Starburst.
Back in the cockpit, the pilot glances around with wide, excited eyes as the \textbf{room} blurs behind him.
The action then cuts to the shaggy cream-colored \textbf{dog} on the floor.
The \textbf{dog} looks upward with its mouth open, then is hit by the same white gust-like streams.
Its long fur and ears flap outward dramatically, first \textbf{blown} back and then settling as the \textbf{dog} sits there looking startled but unharmed.
The commercial returns to the banquet \textbf{room}.
The young male server, now in close-up, looks unsettled and thoughtful, his eyes lowered as if reacting to the bizarre explanation.
The female server stands in the foreground, slightly out of focus, still composed in her \textbf{bow} tie and vest, while he remains behind her, looking off to the side with a wary, confused expression.
The formal dining \textbf{room} remains calm and orderly, contrasting with the chaotic tiny-jet fantasy.

% matched lemmas: blow, bow, chair, curtain, dog, domestic, drape, flower, furniture, live, living, potted, room, sofa, striped, sunny, table
\end{textsample}
