\begin{textsample}{POS Dim 4 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_45.txt}  \label{ex:f4_pos_038}
In black and white, an adult woman stands in a tidy, staged \textbf{home} \textbf{laundry} area that resembles a 1950s kitchen.
She has short, neatly \textbf{waved} dark hair and wears a dark \textbf{sleeveless} dress or jumper over a light short-sleeved \textbf{blouse}, with a small \textbf{necklace} or brooch at the collar.
She faces forward with a bright smile, one hand resting on the broad white top of a counter-height \textbf{laundry} appliance.
Behind her is a window with ruffled \textbf{curtains} and small \textbf{decorative} items or plants on the sill ; patterned wallpaper and a wall ornament add to the \textbf{domestic} setting.
To her right stands a tall white appliance with a rounded top and a circular handle or control on its side-facing front edge.
She remains beside the main washer area, smiling and speaking toward the viewer, presenting the appliance as if inviting someone into her \textbf{laundry} \textbf{room}.
Her hand stays lightly on the machine ’s top surface, near a low rear control panel with small dials or labels that are too small to read clearly.
The white washer stretches across the foreground like a \textbf{built-in} counter, with a faucet or curved fixture near the center and a stack of folded light-colored \textbf{laundry} placed on the right side of the work surface.
As she continues, she turns her head and upper body toward the washer controls.
She leans slightly forward and reaches with one hand toward the rear control panel, indicating a specific setting or dial.
Her attention shifts from the viewer to the machine, and she bends close enough to make the gesture precise, as if pointing out a special feature.
After touching or indicating the control, she turns back with a pleased expression, returning her hand to the smooth top of the washer.
The focus then moves visually to the right side of the \textbf{laundry} setup, where the folded linens are stacked neatly near the edge of the counter.
The woman stands between the counter-height appliance and the tall white appliance at her side, smiling and resting one hand near the folded stack.
She glances down toward the lower front of the appliance area and points toward a cabinet-like door or handle below the counter, suggesting the drying part of the \textbf{laundry} system.
Her posture is confident and demonstrative, with each gesture guiding attention from the washer controls to the drying area.
She reaches down and then lifts a light-colored \textbf{garment} into view.
Holding it up with one hand at first, she raises it above the counter in front of the folded towels.
The \textbf{garment} is soft, pale, and limp, likely a piece of delicate clothing or lingerie ; it hangs loosely as she brings it toward her body.
She gathers it with both hands, spreading and smoothing the fabric so its shape becomes clearer.
The \textbf{cloth} \textbf{drapes} over her forearms and down in front of her dark dress, making the light fabric stand out sharply against her clothing.
She then holds the \textbf{garment} higher, gripping it near the top corners as if displaying how clean or dry it is.
For a moment it is stretched open in front of her chest, its lightweight material forming a soft, rounded shape.
She looks down at it with a pleased smile, then back toward the viewer, continuing to present it.
Finally, she folds or gathers the \textbf{garment} neatly in her hands against her torso, still standing beside the white Hotpoint \textbf{laundry} appliances in the bright, orderly \textbf{home} setting.

% matched lemmas: blouse, built-in, cloth, curtain, decorative, domestic, drape, garment, home, laundry, necklace, room, sleeveless, wave
\end{textsample}
