\begin{textsample}{POS Dim 4 – 1970 – Score 16.00 – 1970/tv\_com\_1970\_35.txt}  \label{ex:f4_pos_083}
The commercial opens in a warmly lit \textbf{living} \textbf{room}.
An older man with thinning light hair sits low in a cushioned armchair, wearing a black-and-white plaid shirt and dark trousers.
He holds a newspaper across his lap but looks slumped and uncomfortable, with his mouth downturned and his eyes partly closed.
Behind him stands an older woman with short, curled gray hair, dressed in a light beige coat over a gray outfit with an orange scarf at her neck.
She rests one hand gently on the back of his \textbf{chair} and then on his shoulder, looking down at him with a concerned but pleasant expression.
The \textbf{room} feels \textbf{domestic} and lived-in : a large \textbf{table} lamp stands to the left, a fireplace and fire tools are on the right, shelves and framed pictures line the wall, and a coffee \textbf{table} in the foreground holds a rounded bouquet of orange and white \textbf{flowers} and several magazines.
The scene shifts to a busy store, likely a drugstore or pharmacy section.
The same woman stands among shelves crowded with household and health items.
Behind her are racks of \textbf{sunglasses} and displays filled with boxes and bottles.
In the foreground and to her right are rows of large dark blue bottles with white caps and pink labels.
The label is dominated by large block letters reading “ M-O, ” with smaller visible text identifying it as Haley ’s M-O flavored laxative.
The woman looks toward the display, steps closer, and studies the bottles.
Other shoppers move nearby, including a man in a light jacket passing behind her.
She reaches out with her right hand, touches one of the blue bottles, and lifts it from the row, bringing the label forward so the big “ M-O ” letters and the pink product panel are clearly visible.
The product then appears in a bathroom or medicine-cabinet setting with an older man in a burgundy cardigan and an open-collared shirt.
He stands at a sink or cabinet, seen partly in profile and partly reflected in a mirror, smiling as he handles the same dark blue bottle.
His hand turns near the white cap as if opening or closing it.
The medicine cabinet door is open, revealing glass shelves with everyday bathroom items : white containers, a red cup or jar, a pale blue box, an aerosol can with a \textbf{teal} cap, and a small dark bottle.
He places the large Haley ’s M-O bottle on the middle shelf, front-facing, so the label is centered and readable among the other toiletries.
The bottle remains displayed prominently in the cabinet.
The setting changes to a \textbf{sunny} \textbf{garden} or \textbf{backyard}.
The older man now appears active and \textbf{cheerful}, wearing a mustard-colored cardigan over a dark shirt and dark trousers.
A medium-sized brown \textbf{dog} stands and jumps near him on the lawn.
The man gestures playfully with both hands, raising them above his head as if encouraging the \textbf{dog}, and tosses or pretends to toss a \textbf{ball}.
The \textbf{garden} is lush, with dark green shrubs and trees forming a \textbf{leafy} backdrop, a neat lawn, and \textbf{flower} beds with \textbf{potted} orange and white blooms along the right side.
The older woman reappears in the \textbf{garden} wearing a light blue cardigan and pale trousers, holding a handbag or basket with a bunch of orange \textbf{flowers}.
She watches the man and \textbf{dog} with a warm smile.
The man approaches her, smiling broadly, and they meet face to face, laughing together.
They briefly hold hands or touch hands as they pass, suggesting he is feeling better and more energetic.
She moves off to the side while he turns back toward the lawn and continues playing.
At the end, the man stands on the grass with one arm extended, throwing an object for the \textbf{dog}, which runs after it.
Large white on-screen text appears over the \textbf{garden} reading, “ Get back in the swing. ” A product image of the Haley ’s M-O bottle appears at the lower right beside the text, reinforcing the brand and product visually as the \textbf{dog} darts across the lawn.

% matched lemmas: backyard, ball, chair, cheerful, dog, domestic, flower, garden, leafy, living, potted, room, sunglasses, sunny, table, teal
\end{textsample}
