\begin{textsample}{POS Dim 4 – 2020 – Score 23.00 – 2020/tv\_com\_2020\_94.txt}  \label{ex:f4_pos_002}
The commercial opens in a bright, toy-like miniature neighborhood.
From above, a gray road curves in a loop through green lawns, tiny trees, \textbf{colorful} \textbf{little} houses, and soft cottony clouds around the edges.
A small red delivery vehicle moves along the road.
The whole world looks like a handcrafted model, with saturated colors and neat, playful shapes.
The red vehicle passes a PetSmart storefront with the large “ PETSMART ” sign on the building.
In the open-top vehicle sits a small, shaggy white \textbf{dog} with gray-tan patches on its ears and around one eye.
The \textbf{dog} sits upright like the driver or passenger, mouth slightly open as if panting.
Behind it are red delivery \textbf{bags} branded with PetSmart and DoorDash.
The vehicle itself is also labeled with PetSmart and DoorDash marks, making it look like a tiny branded delivery car.
It rolls past stylized houses, rounded shrubs, and puffy clouds in the painted-blue sky.
A closer view focuses on the vehicle ’s black tires and red side panel as it passes in front of a house with a bright blue front door.
As the car moves away, a red delivery \textbf{bag} is left standing neatly on the doorstep between two round \textbf{potted} shrubs.
The \textbf{bag} has white text and logos reading “ PETSMART ” and “ DOORDASH. ” It sits upright like a completed doorstep delivery.
The scene then glides past greenery into another miniature yard.
A yellow camper-shaped \textbf{pet} \textbf{home} with a \textbf{teal} door sits behind a white picket fence.
The camper has playful details, including rounded windows and cat-like pointed shapes along the top, giving it a whimsical pet-house look.
A red PetSmart/DoorDash delivery \textbf{bag} waits on the grass to the right of the doorway.
In front are \textbf{pet} toys and yard \textbf{props} : a small red \textbf{lounge} \textbf{chair}, \textbf{balls}, a rope-like toy, and pink flamingo lawn ornaments near trimmed hedges.
The shaggy white \textbf{dog} pops out of the \textbf{teal} doorway and bounds down the \textbf{little} steps toward the lawn.
It moves toward the toys and the red \textbf{bag}, head low for a moment as if inspecting what has arrived.
The view passes through more bushes into an indoor \textbf{pet} space that still looks like part of the same miniature world.
The \textbf{room} has warm \textbf{cream} walls, arched openings, small wall decorations, and a patterned \textbf{rug}.
On the left is a gray, multi-level cat-tree or \textbf{pet} play structure with ramps and platforms.
Near the center is a large green reptile or tortoise-like \textbf{pet} resting among stones, \textbf{leafy} shapes, and scattered food pellets.
On the right, another red PetSmart/DoorDash delivery \textbf{bag} stands beside the \textbf{pet} area.
Around it are \textbf{pet} supplies and greenery, suggesting the delivery includes items for different kinds of animals, not only \textbf{dogs}.
The \textbf{room} looks \textbf{cozy} and staged like a tiny \textbf{pet} apartment.
The greenery gives way to a glass-walled aquarium-like \textbf{home}.
Inside, a bright orange fish swims in a \textbf{room} filled with fanciful miniature \textbf{furniture} : a black grand piano, a small white \textbf{chair}, pink gravel covering the floor, a chandelier-like decoration overhead, and a tall green aquatic plant on the right.
A red delivery \textbf{bag} sits outside the glass structure on the right side, again marked for PetSmart and DoorDash.
The fish floats in the center of this underwater \textbf{living} \textbf{room}, while the \textbf{bag} waits just outside, continuing the playful idea that many kinds of \textbf{pets} can receive supplies.
The shaggy white \textbf{dog} returns in the red open-top delivery car, now seen closer at neighborhood level.
It sits upright in the vehicle, framed by simple modern houses and rounded green hills in the background.
The \textbf{dog} ’s fur is fluffy and cream-white, with darker patches on its floppy ears.
Its mouth is open, tongue visible, and it looks alert and \textbf{cheerful}.
The small windshield is in front of it, and the car ’s side still shows PetSmart and DoorDash branding.
As the car continues, the \textbf{dog} faces forward, then slightly to the side, remaining the active guide through the miniature \textbf{pet} neighborhood.
The setting changes into a real \textbf{home} interior.
A small white-and-gray \textbf{dog}, matching the one from the miniature scenes, looks up from a low angle.
An adult man with short dark hair, a trimmed beard, and a friendly expression stands above the \textbf{dog}.
He wears a red, white, and dark plaid overshirt open over a pale blue T-shirt, with casual pants.
Behind him is a warm \textbf{living} \textbf{room} with beige walls, \textbf{leafy} green houseplants, a wall shelf with small \textbf{decorative} items, and a soft, homey light.
He holds up a large red PetSmart/DoorDash delivery \textbf{bag} in one hand, showing it to the \textbf{dog}.
A wider view reveals the \textbf{room} more fully.
The \textbf{dog} lies or sits on a red-and-white \textbf{pet} bed shaped like the same \textbf{little} delivery car, placed on a patterned \textbf{rug}.
The man bends down beside it and sets the red \textbf{bag} on the floor.
Behind them are framed pictures arranged in a grid on the wall, including pet-themed images, plus a light-colored armchair, a side \textbf{table} with a lamp, and more plants.
The man reaches toward the \textbf{dog} with a gentle, affectionate gesture, \textbf{petting} or greeting it as the \textbf{dog} looks up from its car-shaped bed.
The commercial ends on a clean graphic background in pale blue with soft abstract shapes.
On the left is the “ PETSMART ” logo with the tagline “ Anything for \textbf{Pets}. ” A vertical line separates it from the red DoorDash logo and the word “ DOORDASH ” on the right.
The \textbf{little} red delivery car drives across the bottom of the screen with the shaggy white \textbf{dog} seated inside and red delivery \textbf{bags} stacked behind it.
As the car passes in front of the logos, black text appears underneath : “ Get more from your neighborhood. ” The \textbf{dog} continues riding toward the right edge as the PetSmart and DoorDash logos remain centered.

% matched lemmas: bag, ball, chair, cheerful, colorful, cozy, cream, decorative, dog, furniture, home, leafy, little, living, lounge, pet, potted, prop, room, rug, table, teal
\end{textsample}
