\begin{textsample}{POS Dim 4 – 2000 – Score 12.00 – 2000/tv\_com\_2000\_8.txt}  \label{ex:f4_pos_059}
The commercial begins in a sleek, modern \textbf{hotel} lobby with polished floors, white walls, and a long reception counter glowing warmly from below.
A man in a tan jacket and light trousers walks toward the front desk, pulling a small dark rolling suitcase behind him and carrying a shoulder \textbf{bag}.
Other guests and staff move through the space : a suited man crosses the lobby on the left, a luggage cart stacked with dark \textbf{bags} stands to the right, and a uniformed \textbf{hotel} worker in a white shirt pushes it across the foreground.
In the background are black metal stairs, framed artwork, tall windows, and a few people waiting or walking, giving the lobby a busy but upscale atmosphere.
At the reception counter, the guest faces a male front-desk clerk.
The clerk is a pale-skinned adult man with straight, chin-length black hair cut in a sharp bob.
He wears a black suit jacket, a dark blue shirt, and a matching tie, with a small hoop earring visible in one ear.
His expression is attentive and formal.
The guest, a light-skinned adult man with short \textbf{curly} dark hair, wears an olive-tan blazer over a light blue button-up shirt.
He stands slightly hunched over the counter, focused on the clerk, looking a \textbf{little} cautious or uncertain as he answers questions.
The two men continue the check-in process.
The guest leans in, looks down, and handles papers or a card on the counter.
The clerk remains composed behind the desk, looking at him and occasionally looking down at the work surface.
Behind them, a blonde woman in a bright pink top with a dark vest walks through the lobby, and other guests sit or pass by in the softly lit background.
The guest reaches out across the counter, and the clerk extends his hand ; they appear to exchange a small item, likely part of the check-in paperwork or \textbf{room} key.
The guest then rests both hands near the edge of the counter and bends over, as if filling something out or signing.
The clerk stands neatly on the \textbf{opposite} side, watching and waiting.
As the conversation continues, the clerk ’s face fills the view several times.
He keeps steady eye contact with the guest and speaks with a polished, professional demeanor.
His features are very still and controlled, and the curving branches of a \textbf{potted} plant behind him create a \textbf{decorative} shape over his shoulder.
The guest, seen in return, looks up at the clerk with widened eyes, then glances down and to the side as if considering what he has just been offered.
He seems to agree, then looks slightly hesitant but still cooperative.
The scene shifts to a \textbf{hotel} bedroom.
A red animated M\&M ’s character lies on his back on a white pillow, tucked on top of the bed linens like a person placed there for turn-down service.
He is round and glossy red, with large white oval eyes, black pupils, a small smiling mouth, white gloves, and white shoes.
A large white lowercase “ m ” is printed on the top of his candy shell.
His arms are bent with gloved hands resting near his sides, and his legs are raised comfortably, making him look relaxed and expectant.
A wider view reveals the red M\&M on one side of a double bed, sharing the bed area with the human guest.
The guest lies under white sheets and a dark \textbf{blanket} on the other side, his head on a pillow, wearing light-colored sleepwear.
He is turned slightly toward the red M\&M, looking uneasy or surprised by the candy character lying beside him.
The \textbf{room} is warmly lit by matching bedside lamps on small wooden nightstands, with a wood headboard behind the pillows.
The \textbf{overall} bedroom is \textbf{cozy} and dim, in contrast to the bright lobby.
The red M\&M remains positioned on the pillow beside the guest, visually turning the \textbf{hotel} ’s “ complimentary chocolate on your pillow ” idea into a full-sized \textbf{living} candy character in bed.

% matched lemmas: bag, blanket, cozy, curly, decorative, hotel, little, living, opposite, overall, potted, room
\end{textsample}
