\begin{textsample}{POS Dim 4 – 2020 – Score 13.00 – 2020/tv\_com\_2020\_1.txt}  \label{ex:f4_pos_032}
The commercial begins on a black frame, then cuts to a close-up of a white-and-blue flag waving against a bright blue sky.
The flag carries a stylized wordmark that appears to read something like “ SABITZ, ” though the folds make the lettering partly unclear.
It then cuts to a \textbf{sunny} beach scene.
A shirtless \textbf{young} man with curly dark hair stands in shallow \textbf{water} or at the shoreline, wearing red-and-white vertically striped swim trunks.
His skin appears noticeably sunburned.
Behind him are a sandy beach, rows of blue umbrellas, palm trees, and a \textbf{tall} white lighthouse.
Next, the setting shifts to a tree-lined path or \textbf{resort} road.
A woman in bright pink/red clothing sits in a small open vehicle or cart, facing forward.
Other people stand in the background.
A green roadside sign with white writing is visible, but the text is too small/unclear to read.
The commercial then cuts indoors to a rustic, wood-paneled room with ski equipment.
Several people are present ; two people in the foreground wear winter/ski clothing and stand near skis and gear.
Large windows show mountains or a snowy-looking \textbf{outdoor} landscape in the distance.
The scene changes to a bright modern \textbf{resort} with a turquoise \textbf{swimming} \textbf{pool}, white balconies, palm trees, and \textbf{lounge} \textbf{chairs}.
A shirtless middle-aged man in patterned swim shorts stands on an upper walkway or balcony, looking outward with his hands on his \textbf{hips}.
A closer shot follows, showing his shorts and \textbf{legs} near a glass railing, then another closer shot of his upper body and face on the same balcony.
The commercial cuts to a bedroom.
A \textbf{young} man and a woman lie side by side under bedding in a large tufted bed.
They look toward each other in the overhead shot.
A wider view follows from the doorway, showing the bed centered between bedside lamps, with curtains and a small table or tray area to one side.
Next, two people are shown relaxing separately in square wooden hot-tub-like tubs on an \textbf{outdoor} terrace overlooking the ocean.
Only their heads and upper shoulders are visible above the tub edges.
Large potted plants frame the scene.
The setting then moves to a \textbf{poolside} area.
An older woman reclines on a turquoise-striped chaise \textbf{lounge} beside a large \textbf{pool}.
She wears oversized white sunglasses, a head covering, earrings, and a light-colored cover-up.
A person in white clothing \textbf{walks} in the background near the \textbf{pool}.
A closer shot shows the woman smiling and turning slightly while seated on the \textbf{lounge}.
The commercial cuts back briefly to the wood-paneled ski room.
The two people in ski clothing stand in front of racks of skis and look forward.
It then returns to the beach.
The sunburned \textbf{young} man is shown in close-up, lifting or adjusting green-tinted sunglasses on his face.
The lighthouse and blue beach umbrellas are visible behind him.
Another close-up returns to the older woman at the \textbf{poolside} \textbf{lounge}.
She is shown in profile/three-quarter view, still wearing the white sunglasses, with the \textbf{pool} and a person in white in the background.
The final sequence takes place on a golf course with many palm trees, bright green grass, sand traps, and a golf cart.
A wide shot shows two golfers on the course.
A closer shot shows a man wearing a light-colored patterned sweater vest, cap, and blue trousers holding a smartphone up in one hand, with another golfer behind him.
A close-up of the smartphone screen follows.
The phone displays a travel-booking-style interface with a dark header that appears to say “ ORBITZ ” or a similar wordmark.
Below it are rows of listings with small thumbnail images and prices or text, though most details are too small to read.
A finger interacts with the screen.
The golfer is then shown near a flagstick on the green.
A blue-and-white flag with the same stylized logo/wordmark waves in the wind.
The man stands beside it, and the golf course with palm trees stretches behind him.
The final shot returns to a close-up of the waving blue-and-white branded flag against the sky, with the lettering again partly obscured by motion and folds.

% matched lemmas: chair, hip, leg, lounge, outdoor, pool, poolside, resort, sunny, swimming, tall, walk, water, young
\end{textsample}
