\begin{textsample}{POS Dim 4 – 1980 – Score 23.00 – 1980/tv\_com\_1980\_38.txt}  \label{ex:f4_pos_041}
A small child dressed like a firefighter trots along a sidewalk in front of a white picket fence.
The child wears a shiny red fire helmet, a red-and-white \textbf{striped} shirt, red pants with dark suspenders, and black boots.
A spotted Dalmatian \textbf{dog} moves ahead, pulling or leading a red wooden wagon with white rails and black wheels.
Inside the wagon sit several Dalmatian puppies, their black-and-white heads peeking over the sides.
The child holds the wagon handle and hurries happily after the \textbf{dog} as the \textbf{little} wagon rolls along beside a green lawn and \textbf{flower} beds.
The scene shifts to a \textbf{leafy} \textbf{garden} where a large, playful dragon costume fills the view.
The dragon has a round gray head with a big eye, shaggy orange and yellow fringe, and a long green body with orange triangular spikes along its back.
Pink blossoms blur in the foreground, giving the \textbf{garden} a soft, magical look.
A young child in a bright green one-piece outfit runs beside the dragon ’s green tail, reaching out with both hands as if chasing or trying to catch it.
The child follows the dragon past a stone \textbf{garden} lantern and across the grass.
Next, at a decorated birthday party, a smiling blonde woman in a white \textbf{blouse} carries a white frosted birthday cake on a plate toward a blonde \textbf{little} girl in a white dress with pink ribbons in her hair.
Behind them are white lattice panels, balloons, streamers, \textbf{flowers}, and large block letters spelling part of “ BIRTHDAY. ” The girl beams up at the cake, then leans forward toward several pink \textbf{candles}.
The woman holds the cake steady and watches warmly as the girl \textbf{blows} at the \textbf{candles} ; the child ’s \textbf{cheeks} \textbf{puff} slightly and the \textbf{candle} flames flicker and disappear.
A white wall or fence then appears with a large Clorox 2 logo centered on it : bold black “ CLOROX ” over a black “ 2, ” inside a red-orange diamond outline. \textbf{Flowers} line the base of the wall.
The firefighter child and Dalmatian \textbf{dog} briefly run past the logo, linking the earlier outdoor play scene to the product name.
The commercial moves into a product demonstration on a dark blue studio background.
A blue box labeled “ CLOROX 2 ” and “ Color Safe Bleach ” is tipped downward by a hand, and white powder pours from the box.
The powder then streams into a clear glass vessel marked with the Clorox 2 diamond logo.
Water and powder mix inside the glass.
Close-up views follow of \textbf{laundry} fabrics moving through water : a bright white \textbf{garment} floats among \textbf{colorful} yellow and red \textbf{cloths}, with bubbles and ripples around them.
The white fabric stays visibly clean and bright while the colored fabrics remain vivid in the same wash.
In a \textbf{home} \textbf{laundry} \textbf{room}, a blonde adult woman in a \textbf{sleeveless} coral top and blue jeans stands beside a washer and a folding \textbf{table}.
A box of Clorox 2 sits prominently on the \textbf{table} near neatly folded colored clothes and a white \textbf{laundry} basket full of bright \textbf{garments}.
The woman lifts a white child ’s dress or top, shakes it open, and holds it up with both hands to inspect it.
The \textbf{garment} looks crisp and bright against the blue-toned \textbf{laundry} \textbf{room}, with an arched window and shelves in the background.
The scene changes to a sunlit field of \textbf{flowers} near a pond.
A young Black girl with a large \textbf{ponytail} tied with a purple \textbf{bow} runs through tall pink and purple blossoms.
She wears a purple dress with white \textbf{puff} \textbf{sleeves} and a white collar, and she smiles while reaching toward a small butterfly fluttering in front of her.
The grass and \textbf{flowers} sway around her as she moves lightly through the meadow.
Back at the birthday party, the blonde woman and the blonde \textbf{little} girl lean close together over the decorated cake.
Both smile broadly ; the girl nestles against the woman ’s \textbf{cheek}, and they share an affectionate hug among the balloons and pink party decorations.
The final outdoor celebration gathers many children on a grassy lawn bordered by a white picket fence and \textbf{flower} beds.
The firefighter child runs with another smaller child in a matching red firefighter-style hat and red pants.
Other children follow, including the girl in the purple dress, a blonde girl in a white dress, a girl in a purple top and pink \textbf{skirt}, and a child in a yellow shirt and shorts.
They carry or run beneath bright balloons and long, rainbow-colored streamers or kite tails.
A Dalmatian \textbf{dog} runs across the foreground.
The Clorox 2 diamond logo is visible again on the white wall in the background as the children rush past, laughing and playing.
The commercial ends with a product display against a blue sky with white clouds : a large Clorox 2 powder box stands beside a blue handled jug labeled “ LIQUID CLOROX 2, ” both using the same bold black lettering and red-orange diamond logo.

% matched lemmas: blouse, blow, bow, candle, cheek, cloth, colorful, dog, flower, garden, garment, home, laundry, leafy, little, ponytail, puff, room, skirt, sleeve, sleeveless, striped, table
\end{textsample}
