\begin{textsample}{POS Dim 4 – 2020 – Score 15.00 – 2020/tv\_com\_2020\_72.txt}  \label{ex:f4_pos_015}
A warm, floor-level view begins on wide brown wood-look planks, their grain and seams catching light across a \textbf{living} \textbf{room} floor.
A pale \textbf{rug} lies along the right edge.
As the view opens up, \textbf{colorful} wooden blocks appear scattered ahead, and a toddler with \textbf{curly} hair, wearing a light plaid shirt, plays among them.
Behind the child sits an adult with glasses and short dark hair, wearing a tan sweater, smiling and watching closely.
The \textbf{room} feels bright and \textbf{domestic}, with French doors in the background, upholstered \textbf{chairs}, a fireplace, pillows, and soft daylight.
White on-screen product text appears near the lower right : “ SMARTCORE Vinyl Flooring, ” with a visible price range from about “ \$2.78 - \$3.99 ” per square foot.
The toddler crawls forward through the blocks, pushing and reaching for red, blue, yellow, and green pieces while the adult remains seated behind, attentive and \textbf{cheerful}.
The child comes very close to the floor-level view, filling the foreground with their face and hands as they crawl over the blocks.
The background shifts past the child to show more of the \textbf{living} \textbf{room} : a white fireplace with a black screen, a beige \textbf{chair}, a knitted round pouf, a floor lamp, and loose blocks spread across the smooth vinyl surface.
A round black robotic vacuum then enters from the right and glides across the wood-look floor, its glossy top reflecting the \textbf{room} as it moves near the base of a \textbf{chair}.
The scene changes to a soft, blue-toned \textbf{carpet} seen from very low down, emphasizing the plush texture.
Ahead is a \textbf{blanket} fort made from \textbf{draped} sheets, with pillows and stuffed toys arranged around the entrance.
A teddy bear sits to the left, and warm \textbf{string} lights glow inside the fort.
White product text appears at the lower right : “ STAINMASTER \textbf{carpet}, ” with pricing shown as “ starting at \$2.28 ” per square foot.
As the view gets closer, a handmade sign over the fort entrance reads “ SCARY STORIES CLUB. ” Inside, children lie or sit on the \textbf{carpet} around an open book or notebook, while a person in red clothing, partly hidden by the hanging sheets, appears to be telling or acting out a story.
The warm lights overhead make the fort feel \textbf{cozy} and secretive.
A large white promotional graphic overlays the center : “ Free \textbf{Carpet} Installation, ” with “ minimum purchase \$499, ” framed by a simple roofline icon.
Fine-print disclaimer text stretches along the bottom.
Inside the fort, the children react animatedly, smiling and laughing with open mouths as the person in red leans in from the right with raised hands, as if playfully startling them.
The open book remains on the \textbf{carpet} in the center.
The “ Free \textbf{Carpet} Installation ” offer stays large and centered, while the STAINMASTER \textbf{carpet} price remains visible at the lower right for part of this section.
The fort fabric and warm lights fill the background as the figures move closer together in the small space.
The promotional overlay changes to “ Book Now ” with smaller text underneath : “ and have yours installed by the holidays. ” Below it is a “ Lowe ’s safe ” badge and the website “ Lowes.com/HolidayInstall, ” with fine print along the bottom.
Behind the text, the scene shows \textbf{carpet} installation in a \textbf{home}.
A large roll of \textbf{carpet} lies horizontally across the foreground.
One masked installer kneels on the floor near the roll, working with tools ; he wears work clothes and a dark vest.
Another installer, also in a dark Lowe ’s vest, stands or climbs on a ladder at the right near a doorway and white cabinetry.
The \textbf{room} is bright with \textbf{neutral} walls, and work tools are visible nearby, reinforcing that this is an in-home installation.
The final images keep the installer on the ladder at the right, seen from a low angle as he works near the doorway.
A large white Lowe ’s logo appears centered over the scene, first as a house-shaped outline around the word “ LOWE ’S, ” then settling into the familiar Lowe ’s house logo.
Small copyright text appears near the bottom as the installer remains in the background, still positioned on the ladder in the customer ’s \textbf{home}.

% matched lemmas: blanket, carpet, chair, cheerful, colorful, cozy, curly, domestic, drape, home, live, neutral, room, rug, string
\end{textsample}
