\begin{textsample}{POS Dim 4 – 2020 – Score 18.00 – 2020/tv\_com\_2020\_98.txt}  \label{ex:f4_pos_008}
In a dim, modern open-plan \textbf{home}, a young woman with long dark hair tied back stands facing a tall, narrow Mirror device \textbf{propped} against the wall near a kitchen and \textbf{lounge} area.
She wears a pale blue sports bra, matching high-waisted leggings, and white sneakers.
The \textbf{room} has warm cabinet lighting, a kitchen island on the left, and low grey seating on the right.
The Mirror ’s glossy surface reflects the \textbf{room} and shows the white word “ MIRROR ” across it.
Closer in, the woman faces her reflection with a focused, \textbf{neutral} expression.
The Mirror interface begins to appear over the reflective surface.
The word “ INTRO ” is visible near the top, and a small full-body instructor figure in a white outfit appears inside the mirror display.
The woman follows along, extending one arm across her chest in a shoulder stretch, her other hand pulling it in place while she watches the screen.
The scene changes to a softer, sunlit workout \textbf{room} with exposed ceiling beams, large plants, and a Mirror mounted on a white wall.
A woman in a dusty pink sports bra and matching leggings walks toward it.
The Mirror surface shows a row of circular profile bubbles across the lower area, suggesting other people connected to the workout.
Some usernames and locations are readable, including “ melisaatt, New York, NY, ” “ candice\_309, Dallas, TX, ” “ buckminster, San Diego, CA, ” and “ yogapants, Burlington, VT. ” The user bubbles contain small images or initials, and they float over the woman ’s reflection.
The pink-clad woman smiles broadly and raises both hands, \textbf{waving} at the Mirror.
In the reflective display, other participants appear as blurred or small video images, as if greeting her back.
Another participant appears in a separate \textbf{home} : a smiling woman with very short bleached hair, wearing a burgundy sports bra and dark leggings, stands in front of her own Mirror.
She \textbf{waves} with one hand, grinning, while the same row of circular community icons runs along the bottom of the display.
A muscular man with dark skin and tied-up hair is then seen in profile, backlit by beige \textbf{curtains}.
He wears a dark \textbf{sleeveless} top and lifts a pair of dumbbells near his shoulders.
His face is serious and concentrated as he prepares for the movement.
His Mirror display appears next : in a wood-paneled \textbf{room}, the reflective surface shows the man exercising while a male instructor in a light \textbf{sleeveless} top and white shorts appears as a full-body figure on the left side of the screen.
On-screen workout text reads “ CURL TO PRESS, ” with small progress information and a “ COOL DOWN ” label near the top.
At the bottom, numbers and a colored progress bar track the workout.
The man curls the dumbbells up and presses them overhead while watching the instructor.
The short-haired woman in burgundy now performs the same dumbbell movement in front of her Mirror.
She holds one dumbbell raised overhead and keeps the other arm lifted, her expression determined and slightly smiling.
The instructor ’s translucent figure remains visible in the Mirror above and beside her, demonstrating the exercise.
The first woman in pale blue appears again through her Mirror interface.
Large white text on the display reads “ FACE OFF. ” Two circular competitor panels appear near the bottom with usernames and locations, including “ mountainbiker33, San Diego, CA ” and “ candice\_309, Dallas, TX, ” along with rising scores.
She jogs or moves in place, her \textbf{ponytail} swinging, while the instructor figure and score circles overlay her reflection.
The commercial then shows two Mirror screens side by side, each in a different \textbf{home}.
On the left, the woman in pale blue works out in the warm kitchen-living \textbf{room} ; on the right, the muscular man works out in his \textbf{room}.
Both screens show the Mirror interface with workout labels such as “ SPRINT, ” “ COOL DOWN, ” and “ FACE OFF, ” plus circular score panels.
They appear to be exercising simultaneously and competing or training together through the connected display.
In a bright attic-like \textbf{room} with patterned green wallpaper, skylights, \textbf{built-in} window seats, white drawers, and \textbf{leafy} plants, the short-haired woman in burgundy performs a wide squat facing a wall-mounted Mirror.
A pair of dumbbells lies on the floor nearby, and an orange \textbf{chair} sits to one side.
She rises from the squat with one hand on her hip, watching the instructor and her own reflection.
A family follows along in a \textbf{cozy} \textbf{living} \textbf{room}.
An adult man in a grey T-shirt holds a small child against his chest while raising his hands in a prayer-like pose.
Beside him, a young girl in a \textbf{teal} sweatshirt and a blond young boy mimic the same movement, lifting their hands and arms toward the front of the \textbf{room}.
The adults and children all face the same direction, suggesting they are following a workout or mindfulness class together.
Back in the bright \textbf{room} with beams and plants, the woman in the pink workout set stands facing the Mirror and performs a graceful balance.
She lifts one leg and opens both arms out wide, then raises them into a soft ballet-like shape.
Her posture is upright and controlled, with the Mirror centered on the wall in front of her and plants and a \textbf{chair} around the \textbf{room}.
The muscular man is shown again in his \textbf{home}, doing quick lower-body movements in front of the Mirror.
He shifts from a wide squat into a standing stance, facing the reflective screen.
Medicine \textbf{balls} or weighted \textbf{balls} sit on the floor near the wall, and warm \textbf{curtains} glow at the side of the \textbf{room}.
Another \textbf{home} space appears, framed by blue doorways and filled with surfboards leaning against the walls, a large plant, a \textbf{sofa}, and a workout mat on the floor.
A person in a light \textbf{sleeveless} top, black shorts, and white sneakers performs squat jumps or quick squats on the mat, bending low and then springing upright while facing into the \textbf{room}.
A promotional offer overlays the workout imagery.
Large white text fills the center : “ NOW AS LOW AS \$42/mo with affirm. ” Small fine print runs along the bottom, including details about “ \$42 a month with 0 \% APR for 36 months ” and eligibility through Affirm.
Behind the text, the woman in pale blue moves in the dim kitchen-living space, and then the woman in pink walks through the bright plant-filled \textbf{room}.
The final screen keeps the bright \textbf{room} in view with the Mirror mounted on the wall.
Large bold white text reads “ MIRROR, ” with smaller text underneath : “ from lululemon. ” Below that is “ MIRROR.COM. ” The woman in pink walks out of the \textbf{room} toward the right edge of the screen while the Mirror remains centered in the background, surrounded by plants, wood flooring, and soft daylight.

% matched lemmas: ball, built-in, chair, cozy, curtain, home, leafy, living, lounge, neutral, ponytail, prop, room, sleeveless, sofa, teal, wave
\end{textsample}
