\begin{textsample}{POS Dim 4 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_34.txt}  \label{ex:f4_pos_056}
A young man in a dark suit jacket and light shirt walks up the path of a tidy suburban house with a white picket fence and gate.
Behind him, across the street, a red car is parked in front of single-story \textbf{homes}.
Inside the house, two children peer out through a white-paned window with \textbf{sheer} \textbf{curtains} : first a dark-haired boy, then an older girl leaning in beside him.
They look excited and intent as they watch the young man approach.
A close view of his hand shows him carrying a small brown shopping \textbf{bag} filled with white tissue paper.
The \textbf{bag} is printed with the white “ JARED ” logo, identifying it as from Jared The Galleria of Jewelry.
The scene moves through the \textbf{home} as family members react.
In a warm, traditional kitchen with wooden cabinets, a white stove, a sink under a \textbf{curtained} window, and \textbf{fruit} on the counter, an elderly woman in glasses and a cardigan stands beside a middle-aged woman in a pink button-down shirt.
They pause together, smiling and looking toward the commotion.
In another \textbf{room}, a middle-aged man in a blue shirt sits with a phone to his ear while the same woman in pink leans through a doorway behind him, clearly sharing the news.
Outside at the front door, the young man stands close to a dark blue door marked with the house number “ 244, ” reaching toward the doorbell or handle.
The door opens, and the young man faces a whole welcoming cluster of people packed into the \textbf{entryway}.
An elderly woman, a boy, a middle-aged man, the woman in pink, and a young red-haired woman all smile at him.
The red-haired young woman, wearing a light blue button-down shirt, steps forward from the group.
She beams, moves past the others, and comes out through the doorway toward him.
The young man, still in his dark jacket, follows her inside, looking slightly nervous but pleased as the family watches closely from just inside the door.
A jewelry store interior appears, bright and spacious, with glass display cases arranged throughout the \textbf{room}.
Sales associates in dark suits help customers at the counters, while other shoppers browse.
In the foreground, a suited male associate smiles and presents items to a blonde woman leaning over a case ; other customers and staff move among illuminated displays in the background.
The store feels open and polished, with jewelry cases lining the walls and center of the \textbf{room}.
Gold jewelry is then displayed against a black background : curved \textbf{necklaces}, \textbf{bracelets}, chains, and textured pieces arranged neatly so their yellow-gold shine stands out.
Some pieces are smooth and modern, others braided or beaded.
Small on-screen text near the upper right reads “ speak gold, ” alongside a circular gold-themed logo.
Back at the \textbf{home}, the young couple sit side by side on a blue \textbf{sofa} in a \textbf{living} \textbf{room}.
The red-haired young woman sits on the left, watching with an expectant smile.
The young man sits on the right with the brown Jared \textbf{bag} in his lap, pulling out a small white jewelry box from the tissue paper.
Behind them are dining \textbf{chairs}, framed \textbf{art}, and a \textbf{staircase}.
He turns toward her with the box in hand, smiling, and she looks down shyly as he prepares to give it to her.
The Jared \textbf{bag} remains visible on the \textbf{sofa} or beside him, its white rope handles and logo facing outward.
A close view shows his hands opening the white jewelry box.
Inside, resting on a white cushion, is a gold \textbf{bracelet} or bangle with a smooth, gleaming surface.
The inside of the lid has the Jared name printed faintly.
The young woman takes the box and looks at it, then suddenly leans across the \textbf{sofa} to hug him.
He wraps an arm around her as she embraces him tightly, the open jewelry box still in her hand.
While they hug, several family members sit together on the \textbf{staircase} in the background, watching with delighted expressions.
The elderly woman, the woman in pink, the boy, and the middle-aged man crowd together on the steps, smiling at the couple ’s private moment from a not-so-private distance.
A close view of the young woman over the young man ’s shoulder shows her smiling broadly, holding the open white jewelry box near his back so the \textbf{bracelet} is still visible.
The commercial ends outside a Jared store.
The storefront has a large dark entrance tower with bright white signage reading “ JARED ” and, beneath it, “ The Galleria Of Jewelry. ” Cars are parked in front, and a couple walks toward the entrance.
Large white text at the lower right reads “ jared.com. ”

% matched lemmas: art, bag, bracelet, chair, curtain, entryway, fruit, home, live, necklace, room, sheer, sofa, staircase
\end{textsample}
