\begin{textsample}{POS Dim 4 – 1970 – Score 5.00 – 1970/tv\_com\_1970\_13.txt}  \label{ex:f4_pos_069}
The commercial begins in a dimly lit interior, apparently a living room or study.
A man sits in a \textbf{chair}, viewed in profile, holding and looking at a sheet of paper or document.
The background includes shelves or furniture, and the lighting is \textbf{warm} and subdued.
A “ Classic Commercial Archives ” watermark appears at the lower left.
The scene then transitions into a close-up of baked goods or a dessert-like item.
During the transition, large product branding is partially visible over the image, including the word “ Nestle ” and references to “ butterscotch, ” though the overlapping dissolve makes some details unclear.
Next, the image crossfades to a close-up of a \textbf{young} child with blond hair and large round eyeglasses.
The child faces forward.
Product imagery or packaging remains faintly superimposed across the frame during the dissolve, making the shot somewhat layered and soft.
The commercial then cuts to a clearer product close-up : a \textbf{package} labeled “ Nestle ” and “ Butterscotch flavored morsels ” is shown in front of baked cookies or \textbf{bars}.
The \textbf{package} is angled across the lower half of the frame, with the baked goods behind it.
The final frame is a composed product shot.
A Nestle Butterscotch flavored morsels \textbf{package} sits in front of a plate or tray of cookies.
Large on-screen text at the upper right reads “ Oatmeal Scotchies. ” The background includes \textbf{warm} kitchen-like objects, possibly a container or utensil, but details are not fully clear.
The archival watermark remains visible near the lower left.

% matched lemmas: bar, chair, package, warm, young
\end{textsample}
