\begin{textsample}{POS Dim 4 – 2010 – Score 9.00 – 2010/tv\_com\_2010\_39.txt}  \label{ex:f4_pos_010}
The commercial opens with a static product shot : a yellow Old El Paso “ Hard ’ n Soft Taco Kit ” box on a tabletop, with tomatoes, a lime, and a small dish nearby.
The background is softly blurred and appears to show people in a \textbf{warm}, kitchen-like or dining setting.
The text “ oldelpaso.com.au ” is visible near the bottom of the product shot.
It then cuts abruptly to a washed-out, cinematic shot of a lone figure standing on top of a rocky cliff or outcrop.
The person is small in the frame, silhouetted against a pale sky.
Next, a woman in a green dress appears in a rocky or cave-like environment.
She is smiling and looking toward something off-frame.
A vertical pinkish light or glow is visible along the right edge of the frame.
The sequence then shows a shirtless bearded man in dark swim briefs standing upright against a plain blue-gray background, possibly sky or \textbf{water}.
He raises one arm straight upward, as if signaling or posing.
The commercial shifts to a dense jungle setting.
An older gray-haired, bearded man in a light suit jacket and open-collared shirt \textbf{walks} through thick vegetation.
Behind him are people with painted faces and tribal-style accessories.
The lighting is dramatic, with strong shafts of light and shadows through leaves.
A bright flare or burst of light floods the jungle frame in red and white tones, partially obscuring the older man.
The next shots show him continuing through the foliage, framed by large leaves and bamboo-like plants, with another painted person partly visible behind him.
A close-up follows of a person with red face paint, earrings, and a beaded necklace.
The person is shown in profile or three-quarter view, mouth open, reaching upward or holding onto something just outside the frame.
The setting changes to a medical or clinical environment.
A bearded man lies back while people in light-colored medical clothing \textbf{gather} around him.
One woman with a stethoscope smiles while looking toward a small white animal, possibly a dog, visible through or beyond a glass partition.
In a wider shot, several medical staff or attendants stand around the reclining bearded man, smiling or laughing.
Overhead medical lighting is visible.
The next scene shows three monkeys in a misty \textbf{outdoor} setting, possibly \textbf{hot} springs or \textbf{water}.
They have distinctive red or pale faces and wet-looking fur.
One appears to hold something close to its mouth, while the others look around.
The final part moves to a dark \textbf{bar} or \textbf{lounge}.
The older gray-haired, bearded man sits at a table with two women and another person partially seen at the left edge.
On the table are \textbf{tall} glasses of beer with foam, green beer bottles, and small items including a red ashtray.
The \textbf{group} appears to be conversing or reacting to one another.
Small white text appears along the bottom, but it is too small to read clearly in the frame.
A close-up then centers on a green Dos Equis beer bottle on a coaster, with a \textbf{tall} glass of beer beside it and the red ashtray in the background.
The bottle label is visible, showing the Dos Equis branding with two red X marks.
The commercial ends with a portrait-style shot of the older bearded man against a dark background.
To his left is the Dos Equis logo and text reading “ CERVEZA XX DOS EQUIS, ” with the slogan “ STAY THIRSTY, my friends ” below it.
Additional small text appears near the bottom, including a responsible drinking message, though it is partially difficult to read.

% matched lemmas: bar, gather, group, hot, lounge, outdoor, tall, walk, warm, water
\end{textsample}
