\begin{textsample}{POS Dim 4 – 2020 – Score 17.00 – 2020/tv\_com\_2020\_114.txt}  \label{ex:f4_pos_011}
A warmly lit \textbf{home} is decorated for the holidays.
A middle-aged man with a dark moustache and short brown hair sits at a dining \textbf{table} behind a silver Microsoft laptop, its Windows logo centered on the back.
He wears a thick brown sweater and looks focused at the screen.
Around him are holiday details : a Christmas tree glowing at the right, \textbf{strings} of colored lights around doorways and windows, greenery and pinecones on the \textbf{table}, and family members sitting in the adjoining \textbf{room}.
A woman with glasses sits in another \textbf{cozy} \textbf{living} \textbf{room}, also facing a silver Microsoft laptop on a low \textbf{table}.
She appears to be an adult, with dark hair pulled back, wearing a light cardigan or vest over a patterned top.
Behind her, a person in a green sweater decorates a Christmas tree, while another person sits farther back near the window.
A golden-colored \textbf{dog} lies on the floor to the right beside a red \textbf{pet} bowl or toy.
The space feels busy and \textbf{domestic}, with pillows, \textbf{blankets}, and holiday decorations scattered around.
A smiling adult man sits at a \textbf{table} with a silver Microsoft laptop in front of him.
He has short dark hair and wears a dark sweatshirt.
Behind him is another holiday-decorated \textbf{room}, with a Christmas tree on the left, garlands and lights along the walls, and a child or young person seated at a \textbf{table} in the background.
Food ingredients and a navy cap sit on the \textbf{table} in front of him, suggesting a casual \textbf{home} activity.
The view moves to a Windows desktop interface.
Along the bottom taskbar are familiar app icons, including the multicolored Copilot icon.
A small rounded Copilot control panel opens above the taskbar.
It contains several icons : the Copilot logo, a glasses-like symbol, a glowing microphone symbol in the center, a gear for settings, and an X to close.
The microphone icon is highlighted, visually suggesting voice interaction.
Back with the moustached man in the brown sweater, he continues looking at his laptop with concentration.
Then the laptop screen is shown from his side of the \textbf{table}.
On screen is a dark smart-lighting control page, with sliders on the left, a large color wheel, rows of colored swatches, and control sections on the right.
A small Copilot-style floating control bar sits near the bottom of the screen, and tiny text at the bottom reads “ Screen simulated. ” His hands rest near the keyboard and trackpad as the color selection changes on the interface, shifting from a blue-green tone to a bright red-pink.
In the \textbf{room} behind the laptop, \textbf{colorful} holiday lights glow around the windows, visually matching the idea of syncing or adjusting lights.
The man is then seen again from the front, still seated at the decorated \textbf{table}, with the windows behind him now glowing in red and green colors.
The setting changes to a richly decorated workshop-like \textbf{room} filled with shelves of toys, boxes, clocks, and holiday objects.
At the center, an older man with very long white hair and a full white beard, wearing a red top and suspenders, sits at a large desk with a silver Microsoft laptop.
His appearance strongly resembles Santa Claus.
Other people in festive clothing work in the background, including someone in green and red facing shelves on the right and an older woman at the left.
The desk is crowded with old-fashioned objects, tools, papers, and shiny \textbf{decorative} items.
The bearded man looks down at the laptop with a serious, slightly concerned expression.
His laptop screen shows a presentation-style document with red accents.
Large visible text reads “ WORKSHOP QUARTERLY STATUS REPORT. ” The page includes \textbf{photos} of groups of people or activity scenes, colored bullet points, and a slide navigation column on the left.
His hand moves near the trackpad, and a small Copilot control bar remains visible near the bottom of the screen, again with “ Screen simulated ” shown in tiny text.
After this, the older bearded man is seen again at the desk, still focused on the laptop.
The older woman in the red patterned jacket and white turtleneck turns toward him from the side of the \textbf{room}, looking over with a \textbf{curious}, questioning expression.
Her gray \textbf{curly} hair frames her face, and a globe and warm holiday lights sit behind her.
The woman with glasses returns, seated at her laptop in the \textbf{living} \textbf{room}.
She leans toward the screen with a thoughtful, slightly intent expression.
Behind her, holiday decorating continues, and the golden \textbf{dog} remains on the floor at the right.
The scene then shifts back to the smiling man from earlier, now clearly in a kitchen or dining area.
He wears a plaid holiday apron over his dark shirt and stands behind the laptop with bowls, measuring cups, tomatoes, and other cooking ingredients spread across the counter.
He holds two tomatoes in one hand while looking toward the computer, as if asking for help with a recipe.
In the background, a person sits at a \textbf{table}, and a decorated Christmas tree and \textbf{string} lights add to the festive setting.
The moustached man in the brown sweater appears again at his dining \textbf{table}, now looking more concerned or puzzled as he faces the laptop.
On his screen, two windows are open side by side.
On the left is an image or video window showing a large inflatable reindeer in a front yard at night, standing near a house decorated with lights.
On the right is a document with the bold title “ HOA GUIDELINES. ” The document is laid out like a formal rules page with paragraphs beneath the title.
The man ’s hands rest near the keyboard and trackpad, and the Copilot control bar sits along the bottom edge of the screen.
Through the windows behind the laptop, colored holiday lights glow outside and around the \textbf{room}.
The man is then seen from behind, seated alone at the long \textbf{table}, facing a wall of windows framed by garlands and \textbf{strings} of lights.
The \textbf{room} is filled with warm holiday color : red and green reflections, small lit decorations, and a Christmas tree or illuminated display near the right side.
White on-screen text appears across the center : “ Ready for the holidays? ” A moment later the text changes to : “ Meet the computer you can talk to. ” The final image is a soft, bright pastel background with subtle sparkles and the Copilot logo beside the words “ Copilot on Windows 11. ”

% matched lemmas: blanket, colorful, cozy, curious, curly, decorative, dog, domestic, home, live, living, pet, photo, room, string, table
\end{textsample}
