\begin{textsample}{POS Dim 4 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_111.txt}  \label{ex:f4_pos_053}
The clip begins with a static green advertising layout.
In the upper center is a small inset image of a \textbf{young} \textbf{couple} outdoors.
Large white text at lower left reads “ Fresh and Clean as a Whistle, ” and a black product panel at lower right shows “ Irish Spring ” with a shamrock graphic and the phrase “ THE DEODORANT SOAP. ” This opening frame is visually distinct from the later McDonald ’s material.
After the cut, the setting changes to an \textbf{outdoor} public plaza or shopping area in front of glass storefronts.
A \textbf{group} of performers in coordinated red, white, and yellow athletic outfits appear to be dancing or doing a street-performance routine.
Several costumes display McDonald’s-style golden-arches graphics.
A crowd stands and sits around them watching, some holding white bags.
The dancers move in pairs and small \textbf{groups}.
One performer in red and white is lifted or perched high above another person ’s shoulders, while others face each other in \textbf{quick} footwork.
Several wear red earmuffs, yellow socks or \textbf{leg} warmers, white sneakers, and red track-style jackets or tops.
The choreography includes bouncing \textbf{steps}, hand gestures, bending forward, and circling movements.
The background repeatedly shows glass doors/windows and a large golden-arches sign, supporting the McDonald ’s setting.
The commercial intercuts the dancing with close-up food shots.
Golden-brown breaded pieces are shown against a dark background, falling or tumbling in slow motion.
Hands hold and pull apart a breaded piece, revealing a pale interior.
Another close-up shows a breaded piece being dipped into a white sauce inside a round white container.
Later, stacked McDonald ’s “ Chicken McNuggets ” boxes are shown, with a white clamshell-style container on top.
Hands remove the top container/box from the stack.
The performance continues between these product shots.
A male dancer in a red jacket and white pants interacts with the other performers.
At moments, one dancer bends low while another points or gestures toward the movement.
The crowd remains visible, watching from the edges of the plaza.
Near the end, white on-screen text appears over the dancing scene : “ IT ’S A GOOD TIME FOR THE GREAT TASTE, ” alongside a red McDonald ’s logo panel with the golden \textbf{arches}.
The final shots move closer to the performers ’ faces : a smiling \textbf{young} woman in a red-and-white outfit with a yellow hat or cap is shown seated or leaning back among the \textbf{group}.
She smiles toward the camera and makes a small hand gesture, while other performers smile around her.

% matched lemmas: arch, couple, group, leg, outdoor, quick, step, young
\end{textsample}
