\begin{textsample}{POS Dim 4 – 1990 – Score 15.00 – 1990/tv\_com\_1990\_32.txt}  \label{ex:f4_pos_072}
The commercial opens in a softly lit, elegant bedroom and bathroom area.
A young adult woman with her hair pinned up stands at a white sink, wearing a short white \textbf{sleeveless} outfit.
Behind her, through an open doorway, there is a bed with a \textbf{decorative} metal headboard and pale \textbf{bedding}, with tall windows and \textbf{sheer} \textbf{curtains} filling the \textbf{room} with hazy light.
Over this scene, white centered text reads “ DURASOFT INTRODUCES ” and, beneath it in larger serif lettering, “ FreshLook. ” The woman stands side-on at the sink, as if getting ready in the morning.
The image blends into an extreme close view of a single eye.
At first the iris is brown, with the word “ Simulation ” faintly printed near the bottom.
The eyelid slowly closes, then opens to reveal the iris changed to a vivid light blue, with a patterned ring and dark pupil.
This demonstration is followed by a close view of a young woman ’s face in dramatic shadow.
One side of her face is softly lit and the other is dark ; her eyes are bright blue, and she looks directly forward with a small, confident smile.
White text appears over her face : “ DISPOSABLE COLOR CONTACTS. ” A fingertip then holds a clear, flexible contact lens against a cool blue, out-of-focus background.
The tiny lens is transparent and bowl-shaped, catching highlights as it hovers above the finger.
The lens appears delicate and almost weightless.
The scene changes to a bright children ’s \textbf{art} \textbf{room} or classroom.
A smiling adult woman with short \textbf{curly} dark hair sits at a small wooden \textbf{table} with young children.
The children wear light blue smocks and stand close to her ; paint bowls and brushes sit on the tabletop.
In the background are easels with \textbf{colorful} paintings, including a red painted picture, and another child stands near shelves and artwork.
The adult leans in warmly as the children gather around her, suggesting a playful, affectionate moment.
Another eye demonstration follows.
A blue iris fills the screen, then the eyelid closes and opens again to reveal a green iris.
The green eye is followed by the adult woman from the classroom in a close view.
She has \textbf{curly} hair, small earrings, and a warm smile.
Her eyes appear light, and she looks slightly upward and off to the side, smiling as if responding to one of the children.
Two young adult women appear outdoors or in a public urban setting, walking side by side in soft purplish light.
One wears a dark top and smiles broadly ; the other, with her hair pulled back, turns toward her.
Their hair moves slightly as they walk, and they seem to be laughing or sharing a friendly moment.
The commercial returns to the eye demonstration : a blue eye blinks and reopens as a golden hazel-brown color.
A young woman with medium-brown skin and hair pulled back smiles in a close view, looking sideways with dimples visible and a relaxed, \textbf{cheerful} expression.
The eye demonstration continues again.
A hazel eye blinks and reopens with a violet or lavender-colored iris.
This is followed by a close view of a dark-haired young woman smiling.
Her long hair frames her face, and her eyes appear pale violet.
She turns her gaze sideways, smiling with a playful, knowing expression.
A darker, abstract scene appears with soft silhouettes and bluish light.
Faint centered white text reads “ AND CLEAR WHEN YOU DO N’T, ” referring visually to clear contacts as an option when color change is not desired.
The silhouettes are indistinct, like figures or objects seen through glass or reflections.
The setting shifts to a bright café or restaurant.
A young adult woman with dark hair pulled back, wearing small dangling earrings, is shown in profile and three-quarter view near a sunlit window.
Her eyes look natural brown or dark, and she gazes across the \textbf{room} with a poised, slightly flirtatious expression.
The background is bright and blurred, with hints of \textbf{colorful} signs or street light outside.
Across from her, a young adult man in a dark jacket and white shirt sits at a restaurant \textbf{table} holding an open menu.
Wooden \textbf{chairs}, white tablecloths, and other diners are visible around him.
He turns his head and looks toward her, appearing attentive and intrigued.
Faint text briefly returns over this restaurant scene : “ DISPOSABLE COLOR CONTACTS. ” The clear contact lens appears again on a fingertip against the blue, softly mottled background.
The transparent lens catches the light as it rests near the tip of a finger, emphasizing its thin, curved shape.
The children ’s classroom returns in a close, affectionate moment.
The curly-haired adult woman is partly behind two children.
A young girl with medium-brown skin and \textbf{curly} hair smiles directly forward ; a blonde child ’s face is partly visible beside her.
A small paint-covered hand, bright red with paint, rests on the smiling girl ’s \textbf{cheek} and shoulder, adding a playful splash of color.
The girl ’s eyes appear light \textbf{greenish}, and she smiles calmly despite the \textbf{messy} hand.
The woman in the café appears once more.
She turns her eyes sideways, then faces more forward, her expression serious and intent before softening slightly.
The background remains bright and sunlit with blurred greens and whites, and her face is lit with a pinkish glow.
The commercial ends on the blue-eyed young woman from earlier, her face mostly in shadow with both bright blue eyes visible.
Large white serif text centered over her face reads “ FreshLook. ” Beneath it, smaller capital letters read “ COLOR AND CLEAR DISPOSABLE CONTACTS. ” At the bottom, smaller white text reads “ See your eye care professional. ” She glances upward and sideways with a subtle smile, holding the final image on her vivid blue eyes and the product name.

% matched lemmas: art, bedding, chair, cheek, cheerful, colorful, curly, curtain, decorative, greenish, messy, room, sheer, sleeveless, table
\end{textsample}
