\begin{textsample}{POS Dim 4 – 1990 – Score 14.00 – 1990/tv\_com\_1990\_114.txt}  \label{ex:f4_pos_075}
A misty, softly lit outdoor setting appears, like a miniature forest or \textbf{garden} with trees and \textbf{leafy} plants in the background.
From the right side, a huge blue Snuggle Singles package fills more and more of the scene.
Its front shows the familiar cream-colored Snuggle teddy bear illustration above large rounded blue letters spelling “ Snuggle, ” with “ Singles ” written below in yellow script.
Near the lower front of the oversized box, a bright white dispensing area glows and opens outward like a small shelf or slot.
A small animated teddy bear mascot, matching the bear on the package, stands below the giant box.
He is cream-colored and plush, with round ears, dark button-like eyes, a small black nose, and a friendly smiling mouth.
He looks up toward the glowing dispenser, then turns toward the viewer as if inviting attention.
The setting remains dreamy and soft, with warm haze and greenery around the enormous product package.
The scene changes to a bright, \textbf{airy} \textbf{laundry} \textbf{room}.
White \textbf{curtains} and tall windows let in a lot of light.
Pastel-colored \textbf{laundry} is visible in a white wicker basket on the right, with pale pink, blue, and \textbf{peach} fabrics piled inside and \textbf{draped} nearby.
The Snuggle bear peeks in from the left, holding a small blue Snuggle Singles box against his body.
The package has the same blue-and-yellow Snuggle branding and a small clear or open area near the bottom where sheets can come out.
The bear hugs the box, tilts it forward, and presents it proudly.
He demonstrates the product by holding the box close and gesturing with one \textbf{paw}.
A single white dryer sheet appears from the package ’s dispensing opening, separated from the others rather than pulled from a loose stack.
The bear looks toward the \textbf{laundry} basket and then toward the \textbf{room}, moving his \textbf{paw} as if explaining how easy it is to use.
He keeps the Snuggle Singles box tucked against him while his other \textbf{paw} points and \textbf{waves}.
The view shifts to the inside of a white front-loading dryer.
Pastel clothing tumbles in the round opening : \textbf{peach}, pale blue, white, yellow, and \textbf{striped} fabrics roll over one another.
A white dryer sheet is visible among the clothes as the fabrics circulate.
The tumbling \textbf{laundry} fills the circular dryer window, showing the sheet mixing in with the load.
The imagery becomes more fantasy-like and close-up.
A large peach-pink piece of fabric billows and folds like a soft landscape.
The Snuggle bear appears beside it, partly hidden by the flowing \textbf{cloth}.
He reaches toward the fabric, then snuggles into it.
The \textbf{cloth} wraps around him like a \textbf{blanket}, and he rubs his face and \textbf{paws} against it, suggesting softness.
His eyes soften and his expression looks content as he nestles into the plush folds.
The bear continues cuddling the pink fabric, holding it close to his \textbf{cheek} and chest.
He looks up toward the viewer while wrapped in the soft material, then smiles with the fabric gathered around him.
The emphasis visually is on the texture : the fabric appears fluffy, warm, and thick, and the bear ’s small \textbf{paws} press into it.
The scene returns to the bear holding the Snuggle Singles box against a bright pale background.
The package front is clearly visible again with “ Snuggle ” and “ Singles ” on the blue box.
The bear faces forward, smiling.
He pulls or releases another single white sheet from the dispensing area, and it flutters out to the right.
The final scene returns to the oversized Snuggle Singles package in the misty \textbf{garden} setting.
The small Snuggle bear stands in front of it, still holding the smaller product box.
Behind him, the giant package dominates the background, with the large “ Snuggle Singles ” logo across the front and a dotted dispenser outline near the lower portion ; the smaller text inside the outline is partly readable and appears to refer to a dryer sheet dispenser.
White dryer sheets float or drift near the right side, reinforcing the idea of individual sheets coming out separately.
The bear remains centered near the bottom, smiling in front of the towering package as the product name stays large and prominent.

% matched lemmas: airy, blanket, cheek, cloth, curtain, drape, garden, laundry, leafy, paw, peach, room, striped, wave
\end{textsample}
