\begin{textsample}{POS Dim 4 – 2000 – Score 33.00 – 2000/tv\_com\_2000\_61.txt}  \label{ex:f4_pos_051}
The commercial begins outdoors in warm sunlight in front of a large, white, two-story house with blue trim, many windows, a blue front door, and broad steps leading up through a \textbf{garden}.
Two young children sit close to the foreground.
On the left is a blond child in blue \textbf{denim} \textbf{overalls}, holding a small blue bottle of bubble solution and lifting a bubble wand.
On the right is a dark-haired child in a red or pink top with \textbf{striped} \textbf{sleeves}, also holding a wand and \textbf{concentrating} on \textbf{blowing} bubbles.
As the children dip and raise their wands, translucent soap bubbles drift upward across the house and \textbf{garden}, catching pink and gold highlights from the sun.
More and more bubbles float through the space until they fill much of the view.
The children then appear from above, smiling up from a patch of grass while sitting or kneeling on a large star-shaped quilt or \textbf{blanket}.
The quilt has pointed edges and a repeating diamond pattern in soft reds, blues, \textbf{creams}, and pinks, radiating outward like a many-pointed star.
The blond child still holds the blue bubble bottle and wand, grinning upward, while the dark-haired child smiles behind.
The quilt pattern becomes the focus, now indoors as a large \textbf{cream} fabric with a red geometric star design spreads over a dining \textbf{table}.
At first it fills the view like a close-up of a textile, then the \textbf{room} around it becomes clear : a formal dining \textbf{room} with polished dark floors, a round or oval \textbf{table}, wooden \textbf{chairs}, pale warm walls, \textbf{decorative} plates on one wall, and a hanging light fixture overhead whose design echoes the star pattern.
An adult woman, partly obscured by the \textbf{cloth} at first, stands behind the dining \textbf{table} and lowers or smooths the patterned fabric over it.
The fabric billows slightly over the tabletop before settling, transforming the star-like outdoor picnic image into a coordinated interior dining-room element.
The setting changes to a bright \textbf{room} painted lavender-purple.
An elderly Black man, wearing a black flat cap, a \textbf{cream} cardigan over a light shirt, and dark trousers, stands with a small child who wears a pale blue shirt.
He holds a small bouquet of delicate purple \textbf{flowers}, likely \textbf{lavender}, near the child ’s face.
The child tilts their head up toward him and the \textbf{flowers}, looking \textbf{curious} and engaged.
The man ’s arm rests protectively around the child, and he smiles warmly as they share the bouquet.
The \textbf{room} is \textbf{airy} and sunlit, with white \textbf{shutters} open at the windows, white \textbf{furniture}, and purple walls that match the \textbf{flowers}, creating a soft, floral atmosphere.
A young girl then dances in a pastel bedroom.
She has \textbf{curly} blond hair and wears a pink crown or flowered headpiece, a black top with pale \textbf{decorative} trim, a large white tutu, white tights, and ballet slippers.
The \textbf{room} is painted in dreamy colors : lavender-blue walls with green and \textbf{peach} accents, and a \textbf{peach} castle-like mural or bed alcove on the right with a canopy-like shape around the bed.
A small \textbf{table} and \textbf{chairs} sit to the left, with toys and playful \textbf{furnishings} throughout.
The girl twirls and balances with her arms extended, moving like a ballerina across a \textbf{rug} in front of the bed.
Close views show her smiling, turning her head, and lifting her arms with theatrical, childlike confidence.
The crown and tutu emphasize a princess or fairy-tale role, while the painted castle shapes on the wall make the \textbf{room} feel like an imagined stage.
The mood shifts to a quiet, symmetrical bedroom or meditation space with orange-red walls and soft blue panels.
A light-skinned adult man sits cross-legged on a low bed or platform between two pillows.
He wears a white \textbf{sleeveless} shirt and loose gray pants.
His hands rest on his knees, \textbf{palms} relaxed, and his head is \textbf{bowed} at first.
Behind him is a square orange panel with white floral or branch-like shapes, and above him hangs a glowing round pendant light.
The \textbf{room} is arranged almost evenly on both sides, with dark side \textbf{tables} and simple \textbf{decorative} objects.
He slowly lifts his head and looks forward, seated still and composed against the warm orange background.
Next is a vivid green \textbf{room} with pink trim around a wide doorway.
Through the doorway, a dining or study area is visible with a \textbf{table} and \textbf{chairs} and pale \textbf{striped} wallpaper.
A child in a white shirt and light pants moves through the inner \textbf{room} holding a \textbf{string} or stick, chasing or guiding a large green-and-red parrot-like object that glides overhead.
The object looks like a bird, kite, or \textbf{decorative} mobile, with a green body, red head, and outstretched wing shapes.
The child reaches upward, animated and playful, stepping and lunging as it moves across the doorway from right to left.
The surrounding \textbf{room} is highly \textbf{colorful} : \textbf{lime-green} walls, rosy trim, a small green \textbf{chair} to the right, shoes on the floor, and a vase of \textbf{flowers} on a \textbf{table} to the left.
The commercial then moves into a Sherwin-Williams retail environment.
Inside, a light-skinned female store associate with dark hair pulled back, wearing a gray blazer, blue shirt, and rectangular name badge, smiles while speaking with a customer, a light-skinned woman with auburn hair in a \textbf{ponytail} wearing a pale yellow top.
Behind them are shelves filled with tall binders or sample books, and another person browses in the background.
The associate ’s expression is open and helpful, and the customer faces her attentively.
Outside, a Sherwin-Williams Paints store appears in daylight.
The building has a \textbf{blue-and-white} facade and large front windows, with the sign “ SHERWIN-WILLIAMS PAINTS ” in big letters across the top.
Several people walk toward and around the entrance, and cars are parked nearby.
The storefront establishes the place where customers can get help with paint and color choices.
Back inside the store, customers sit at a consultation \textbf{table} covered with open books, papers, and large design or color sample materials.
A female associate in the same gray blazer leans over the \textbf{table}, pointing to pages and turning samples.
Beside her sit a woman and a small red-haired child in a pink top and dark vest, both watching closely.
The child looks at the open material with interest.
Shelves of binders line the wall behind them, and other customers and staff work at \textbf{tables} in the background.
The associate actively guides the selection process by showing pages and placing her hands on the samples while the family follows along.
The scene returns briefly to the pastel princess bedroom, now focused on a wall mural.
A person wearing a peach-orange short-sleeved shirt uses a sponge or soft applicator against the painted wall, adding green, cloud-like areas around \textbf{peach} turret shapes on a blue background.
The hand presses and blends color near a castle-like roofline, showing a \textbf{decorative} paint technique being applied directly to the wall.
The mural ’s soft edges and layered colors match the fantasy \textbf{room} seen earlier.
The \textbf{little} ballerina reappears in that completed \textbf{room}, standing proudly in front of the \textbf{peach} castle bed alcove.
She raises her arms outward and slightly upward, smiling and posing as if finishing a dance.
Her white tutu flares around her, and the painted castle setting surrounds her like a stage.
The commercial ends on a wider exterior view of the Sherwin-Williams Paints store under a pink-and-blue sky.
People continue walking near the entrance.
Large white on-screen text appears over the lower part of the image : “ For a store near you : ” followed by “ 1-800-4-SHERWIN, ” with “ www.sherwin-williams.com ” beneath it.
The store sign “ SHERWIN-WILLIAMS PAINTS ” remains visible on the building above the front windows.

% matched lemmas: airy, blanket, blow, blue-and-white, bow, chair, cloth, colorful, concentrate, cream, curious, curly, decorative, denim, flower, furnishing, furniture, garden, lavender, lime-green, little, overall, palm, peach, ponytail, room, rug, shutter, sleeve, sleeveless, string, striped, table
\end{textsample}
