\begin{textsample}{POS Dim 4 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_18.txt}  \label{ex:f4_pos_022}
The commercial opens with close-up shots of a \textbf{group} of people standing outdoors in \textbf{warm} sunlight.
Several faces are visible in the foreground : a \textbf{young} man in the center, people on either side, and more people behind them.
Their expressions appear serious or intent, as if they are looking toward something off-camera.
The camera then moves or cuts rapidly through the crowd.
The next few frames are heavily blurred, showing indistinct faces and bodies, suggesting \textbf{quick} motion or a fast transition.
The background includes \textbf{greenery} and warm-toned architecture, but details are not clear.
The scene changes to a bright kitchen or dining room.
Several people are \textbf{gathered} around a table covered with food and cooking items.
A large circular object resembling a game wheel or target stands in the room ; it has a red center and a ring of light-colored circular \textbf{spots} around it.
A woman and a child are near the wheel, while other people sit or stand around the table.
The setting is domestic, \textbf{colorful}, and well lit.
A close-up follows of a \textbf{young} girl in a \textbf{pink} \textbf{sleeveless} top standing near the large circular object.
Potted cactus plants are visible behind her on a windowsill or shelf.
She looks slightly to the side, with a calm or expectant expression.
The setting then shifts dramatically to an \textbf{outdoor} desert-like scene with \textbf{tall} green cacti \textbf{rising} against a bright blue sky.
A \textbf{group} of smiling people \textbf{gathers} together, and a \textbf{young} girl is lifted or held up among them.
The \textbf{group} appears celebratory, with several people looking upward toward the girl.
Next, the product is shown on a table in the foreground.
Three yellow Old El Paso \textbf{packages} are visible, including hard and soft taco-related products ; the brand name “ Old El Paso ” can be read on the boxes.
Around the \textbf{packages} are taco shells, tomatoes, a lime, and other ingredients.
People are visible in the background, out of focus, suggesting a festive or social gathering.
The commercial then cuts to close-up food shots.
One frame shows a filled hard taco shell containing seasoned meat, lettuce, tomato, and other toppings.
Another frame shows several soft tacos or folded tortillas stacked together, filled with meat, lettuce, tomato, and green pieces that appear to be vegetables.
In the final frame, the scene returns to a lively table setting.
A man at the table bites into a taco while a \textbf{young} girl beside him holds food and looks toward him.
Other people stand and move in the background, with \textbf{colorful} decorations visible.
The table includes vegetables, a bowl, and a patterned cloth, reinforcing the meal or party setting.

% matched lemmas: colorful, gather, greenery, group, outdoor, package, pink, quick, rise, sleeveless, spot, tall, warm, young
\end{textsample}
