\begin{textsample}{NEG Dim 2 – 2020 – Score 1.00 – 2020/tv\_com\_2020\_82.txt}  \label{ex:f2_neg_088}
The commercial opens on a solid magenta screen with a centered white square containing the magenta T-Mobile “ T ” logo.
It then cuts to a desert road in warm sunlight.
A large light-colored pickup truck drives toward the camera on a long, straight, cracked road bordered by dry scrubland.
The headlights are on, and the landscape appears remote and arid.
The next shot moves inside the vehicle.
A middle-aged man wearing a black baseball cap and a plaid shirt is driving.
He is shown in profile from the passenger side, holding the steering wheel and looking ahead.
The background through the window shows desert vegetation and a bright blue sky.
The truck then passes through or near a roadside area.
In a low, exterior side view, the front of the pickup moves from left to right across the frame, with desert ground, a road, signposts, and distant mountains visible behind it.
A very low shot follows from near ground level, looking underneath the vehicle.
A small animal, possibly a rodent or ground squirrel, is visible in the distance beneath or beyond the vehicle ’s underside.
The ground is dusty and sunlit.
The commercial then reveals a large roadside sign.
A tall magenta T-Mobile “ T ” logo stands above an oval sign that reads “ Best Network ” or similar wording ; the exact smaller text is not fully clear.
The pickup is parked or slowing at the left side of the frame, and the driver is visible through the window.
The setting remains a desert roadside location with mountains in the background.
A close shot shows the same man standing outdoors, facing the camera.
He is still wearing the black cap and plaid shirt.
Behind him are a road, desert terrain, and a blurred roadside sign.
White on-screen text appears near the bottom reading “ T-Mobile Best Mobile Network in the U.S. ” with smaller fine print below that is too small to read clearly.
The scene then cuts to the exterior of a roadside building, possibly a motel, diner, or service stop.
The façade has retro styling, glass \textbf{double} doors, window blinds, stars as decoration, and a large neon-style sign along the roofline, though the full wording is partly cut off and unclear.
The man walks from right to left across the front of the building.
A vending-machine-like sign or display stands on the right side of the entrance area.
The commercial ends on a plain magenta screen, with no visible text or logo in the sampled final frame.

% matched lemmas: double
\end{textsample}
