\begin{textsample}{NEG Dim 2 – 2020 – Score 1.00 – 2020/tv\_com\_2020\_64.txt}  \label{ex:f2_neg_058}
A bright, white laundry room appears with a woman standing near a washer and dryer.
She has shoulder-length blonde hair, wears a royal blue short-sleeved top, dark pants, and a small necklace, and faces forward while holding up a light gray T-shirt.
Behind her are white cabinets, shelves, a laundry basket with pastel clothes, hanging garments, and orange Tide containers on a shelf.
She lifts the gray shirt higher and turns her attention to it, pinching the fabric near the shoulder and inspecting it closely, as if showing that it may look clean at first glance.
The shirt is then laid flat on a white surface in dimmer, more dramatic lighting.
Only the woman ’s hands and lower body are partly visible at the top edge as she spreads the T-shirt out.
The gray shirt fills the center of the scene, wrinkled and plain at first.
Under a bluish-purple ultraviolet-style light, bright glowing blue patches appear across the shirt, especially down the center and near the upper chest.
A small label at the bottom reads “ UV light, ” and large white text appears on the right reading “ Invisible Dirt. ” The glowing spots make the unseen dirt visible against the dark blue background.
The scene flashes white and returns to the laundry room.
The woman now stands beside an open top-loading washing machine.
An orange Tide Pods container sits on the counter in front of the washer, and another is visible on the shelf behind her.
She holds a single laundry pod in one hand while facing forward.
The pod is a small, clear, cushion-like packet with swirls of dark blue, green, and white liquid inside.
A small safety warning appears along the bottom of the screen : “ Keep out of reach of children. ” She gestures toward the open washer, then looks down toward it as she prepares to use the pod.
A close view shows her hand holding the Tide pod over the open washer drum.
The pod is glossy and squishy-looking, with the colored liquids pressed into distinct curved sections.
She releases it into the empty white drum.
From above, the pod drops into the center of the washer, while bold blue text in the upper right reads “ 10X ACTIVE INGREDIENTS. ” A bright glow forms around the pod, and small colored spheres appear in a ring around it, suggesting concentrated cleaning components.
The pod remains centered as the spheres hover around it in a clean, white, highly polished graphic style.
The imagery then shifts to a magnified, animated view of fabric.
The surface looks like thick, looping white fibers, like tiny strands of yarn woven together.
Translucent bubbles or capsules hover above and between the fibers, with yellowish dirt-like material inside some of them.
Small points of colored light sparkle across the fabric surface.
The bubbles appear to lift dirt up and away from the loops of fabric ; as they rise and disappear, the white fibers look cleaner and clearer.
A comparison appears under the same blue UV-style lighting.
The screen is split vertically.
On the left, a shirt labeled “ BEFORE ” glows with many bright blue patches and spots.
In the middle near the bottom is the small label “ UV light. ” On the right, a shirt labeled “ AFTER ” appears much darker and more even, with little to no glowing residue.
The Tide logo and the words “ HYGIENIC CLEAN ” appear at the upper right, linking the cleaned result to the product.
Back in the bright laundry room, the woman stands behind a white counter with two large orange Tide Pods containers in front of her.
She rests her hands near the containers while speaking toward the viewer.
The containers are rounded, tub-like packages with the Tide logo and “ Hygienic Clean ” labeling on the front ; one has a darker blue label and the other a pink-purple label.
Shelves behind her hold folded towels and more orange Tide containers, reinforcing the laundry setting.
The products are then displayed in a clean lineup on a white surface : a red bottle of Tide Hygienic Clean liquid detergent on the left, a large orange Tide Power Pods Hygienic Clean container in the center, and a smaller orange Tide Hygienic Clean container on the right.
The Tide logo is prominent on all three packages, and the center and right containers show the multicolored pod graphic on their labels.
Fine-print guarantee text appears near the bottom but is very small.
The commercial ends on a solid red background.
Large white text reads “ It ’s got to be ” beside the round yellow-and-orange Tide logo.
A small blue P\&G logo sits in the upper right corner.

% matched lemmas: 
\end{textsample}
