\begin{textsample}{NEG Dim 2 – 2020 – Score 2.00 – 2020/tv\_com\_2020\_29.txt}  \label{ex:f2_neg_089}
The commercial begins in a dark studio setting.
A woman is seen in front of a large bright studio light, with camera or production equipment visible around her.
White on-screen text appears over the scene reading “ Go with pro me, ” with “ pro ” and “ me ” emphasized in bold.
The scene then cuts to a product shot against a soft pink background.
A box labeled “ CLAIROL ” and “ pro fixer ” stands upright on a narrow grey ledge or shelf.
A small “ CLAIROL ” logo also appears in the upper-right corner of the frame.
Next, the woman appears against the same pink backdrop.
She has a short, straight bob haircut and is wearing a pink off-the-shoulder top.
She holds up a section of her dark hair and looks at it with a concerned or dissatisfied expression.
White text appears around her, including “ my ” on the left and a partially visible “ pro-tip ” on the right.
The “ CLAIROL ” logo remains in the upper-right corner.
The commercial then shows a close-up of hair, filling the frame.
The hair appears smooth and reddish-brown under the lighting.
This is followed by a close-up of a hair parting, where a white applicator nozzle dispenses a white cream or liquid product directly along the scalp line.
The word “ apply ” appears over the image, and the “ CLAIROL ” logo is still visible in the upper-right corner.
After application, the woman is shown in profile with her head tilted downward.
Her hair now appears sleek, glossy, and a rich dark brown or reddish-brown tone.
The pink studio background continues.
The next shot shows her facing the camera with a slight smile, holding the Clairol “ pro fixer ” box next to her face.
Her hair looks smooth, straight, and neatly styled in a bob.
The pink studio setting and the small “ CLAIROL ” logo in the upper-right corner remain visible.
The final frame widens slightly : the woman poses in the pink off-the-shoulder top, puckering her lips while holding the product box up beside her face.
Large white text above her reads “ CLAIROL ” with “ IT ’S ” underneath.
The product packaging is clearly displayed, with “ pro fixer ” visible on the front.

% matched lemmas: 
\end{textsample}
