\begin{textsample}{NEG Dim 2 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_28.txt}  \label{ex:f2_neg_032}
In a home kitchen, a close view shows a cutting board beside a sink area.
Several lemon halves sit on the left, with a whole lemon and a knife on the board.
Behind them are pantry jars with yellow lids, a small brown mortar and pestle, and cookbooks or boxed items.
A young adult woman ’s hands, sleeves of a white blouse visible, handle the knife and lemons as if preparing to use them.
She wears a peach sleeveless sweater over the blouse, and as the view widens, her long brown hair is held back with a small clip.
Another woman steps in beside and slightly behind her, carrying a large brown paper grocery bag.
She appears to be an adult woman with short, curly blonde hair, wearing a light blue sweater over a white collared shirt.
A pale yellow bottle with a green cap is visible poking out of the grocery bag.
The younger woman turns from the lemons to look at her, holding lemon pieces in both hands.
They stand close together at the counter in a wood-cabinet kitchen, with a built-in oven or microwave behind them.
The younger woman gestures toward the lemons and the nearby sink, where a dishwashing setup and piles of dishes are visible at the edge of the counter.
The blonde woman smiles and responds by pulling the yellow bottle from the grocery bag.
She holds it upright in front of her, and the label clearly reads “ JOY ” in large colored letters, with Lemon Fresh indicated on the bottle.
She presents it to the younger woman, pointing at or tapping the top and label as she talks.
The younger woman watches with a skeptical, uncertain expression.
The blonde woman brings the bottle close to the younger woman ’s face, letting her smell it.
The younger woman leans in slightly ; her expression shifts from doubtful to interested, and she looks back at the blonde woman as if reassured.
The imagery then focuses on a hand holding a lemon-shaped object coated in thick white suds.
The foam blankets the surface in a rounded mound, sparkling with tiny bubbles.
Fingers slide along the suds, showing their thickness and sheen.
The sudsy lemon-like form fills most of the view, with warm light behind it, emphasizing the glossy bubbles.
A clear dinner plate is then held up in both hands.
The young woman ’s smiling face is visible through the plate, slightly softened by the transparent glass.
Circular ridges in the plate catch the light, making it look clean and shiny.
Her hands frame the plate on either side, and the plate appears spotless.
The scene moves to a dining area with large windows and many green \textbf{houseplants}, creating a bright, homey setting.
A round table covered with a peach-colored cloth is set with white plates, glasses, silverware, tall pale candles, and a small flower arrangement in the center.
The young woman, still in her peach sweater and red skirt, places dishes around the table.
She handles the plates confidently, setting them out as if preparing for a meal.
The blonde woman joins her at the table, holding the Joy bottle.
The younger woman looks pleased and gestures broadly toward the clean place settings, showing off the finished table.
The blonde woman smiles and holds the bottle at chest height, turning it so the label faces outward.
They look at each other and at the table, with the clean dishes arranged neatly between them.
The younger woman reaches toward the bottle and touches or points near the label, acknowledging the product, while the blonde woman keeps holding it and smiling.
The commercial ends with a product display on a wooden surface.
A yellow bottle of Joy Lemon Fresh stands upright in the foreground, its green cap on top and the large “ JOY ” logo prominent on the front.
A halved lemon rests beside the bottle, with whole lemons to the right.
Behind them, a clear, shiny plate stands upright, reflecting the Joy bottle in its surface.
At the bottom of the screen, white text appears : “ A lemon fresh clean that shines. ”

% matched lemmas: houseplant
\end{textsample}
