\begin{textsample}{NEG Dim 2 – 1970 – Score -4.00 – 1970/tv\_com\_1970\_44.txt}  \label{ex:f2_neg_001}
The commercial begins with a very dark, indistinct frame.
No clear objects or people are visible, apart from the \textbf{archival} watermarking over the image.
By around 6 seconds, the scene has changed to a brighter live-action shot.
Several people are visible near what appears to be an entrance or doorway, with greenery outside or behind them.
On the left, an older man in a dark suit leans slightly forward and appears to be interacting with or handing something to a woman on the right.
The woman wears a light yellow coat and a gray head covering or hat, and she is smiling or looking down toward the object between them.
A man in a light-colored shirt stands in the background, centered behind them.
The image has some motion blur or \textbf{double} \textbf{exposure}, making details unclear.
There is also a reddish/orange horizontal object in the lower foreground, but its \textbf{identity} is not clear from the sampled frame.
The commercial ends on a static title card with a plain light background.
Large black text reads : “ People use our money to get the most out of life. ” Below the text is a red circular logo containing the letters “ HFC. ” Smaller text underneath reads “ AN EQUAL OPPORTUNITY LENDER. ” \textbf{Archival} watermark text is visible across the frame, with a “ Classic Commercial Archives ” logo at the lower left.

% matched lemmas: archival, double, exposure, identity
\end{textsample}
