\begin{textsample}{NEG Dim 2 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_90.txt}  \label{ex:f2_neg_076}
A bathroom medicine cabinet is open, with glass shelves and blurred bottles at the edges.
A young adult woman with medium skin, long dark hair, and a white camisole looks into the cabinet.
She stands calmly in front of the mirror, her face centered between the shelves, and reaches toward a razor lying on the shelf in front of her.
She picks it up with a small, pleased smile.
The bathroom comes into fuller view.
The woman, wearing thin white straps and a small \textbf{pendant} necklace, holds a dark men’s-style razor near her chest.
Behind her, through a steamy glass shower area, a young adult man is visible from the back, bare-shouldered and turned away.
Wooden blinds line the left side of the room.
The woman glances sideways toward him as if checking whether he sees her, then moves out of the foreground, leaving the man blurred in the shower behind the glass.
The scene shifts to a product display against a dark, smoky background.
A pink and silver razor handle fills the screen, sleek and curved, with an oval “ Quattro ” logo set into the pink grip.
The handle turns to reveal its shape : silver edges, textured pink grip areas, and a metal-like finish.
The razor head comes into view, with a green strip across the top and a rectangular blade cartridge.
The head is shown close up, facing forward, so the four thin blades and protective guard details are visible.
A small “ Schick Quattro for Women ” logo appears near the lower right during these product views.
Back in the bathroom cabinet, the man now appears at the open shelf.
He has medium skin, short curly dark hair, and wears a white tank top.
Bottles and grooming items sit on both sides of the cabinet.
He looks straight ahead with a neutral, slightly uncertain expression, then reaches toward the shelf and picks up the pink razor.
He studies it, holding the pink handle upright with the white-and-green razor head near his face.
The woman reappears behind him, smiling over his shoulder.
He begins to smile too, still holding the women ’s razor up as if tempted to use it.
She leans in close beside him, amused, and reaches forward.
Her hand comes across in front of him, and the pink razor blurs as she takes it away from his hand.
He turns his eyes toward her, still smiling, while she stays close at his shoulder with a playful, knowing expression.
The final image returns to the dark smoky product background.
The pink Schick Quattro for Women razor stands upright, angled slightly, with its green-topped blade head at the top.
Large white text across the middle reads, “ Now women have the power of 4, ” with the number 4 oversized.
Below it is the “ Schick Quattro for Women ” logo, and near the bottom is the website “ QuattroForWomen.com. ”

% matched lemmas: pendant
\end{textsample}
