\begin{textsample}{NEG Dim 2 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_32.txt}  \label{ex:f2_neg_090}
A warm pink-toned airplane cabin appears, with red carpeting, light-colored seats, and an oval window.
At first only the lower half of a young woman is visible as she walks down the narrow aisle in high heels and a short skirt or suit.
She carries a small, light-colored handbag.
A seated man is partly visible on the right, and as she passes, a hand from the seat reaches toward the back of her skirt, briefly touching or catching the fabric before she continues forward.
The woman is then seated by the airplane window.
She has short, dark, neatly styled hair and wears a patterned jacket or suit.
Beside her sits a young man in a dark suit, white shirt, and tie.
Both are looking down at reading material, with another passenger seated behind them.
The man glances sideways toward her, his expression shifting into a pleased smile.
She notices him, turns her eyes toward him, and smiles back.
Her smile is broad and polished, showing her teeth.
She raises her hand to her mouth, covers her lips, then puckers and blows a kiss.
The man reacts with surprise and delight ; a dark lipstick kiss mark is now visible on his cheek as he turns his head, grinning and speaking animatedly.
The scene changes to a product display on a dark red background with a glowing light behind it.
Large bold white letters read “ new toothpaste! ” Above a long rectangular toothpaste carton.
The carton is labeled “ ultra brite, ” with smaller words beneath and a toothbrush graphic on the right side of the package.
The lettering is large, raised-looking, and slanted for emphasis.
Back in the airplane cabin, the woman sits near the window while the suited man leans toward her from the aisle side.
She lowers her eyes, then looks sideways at him with a knowing smile.
A close view centers on her mouth : glossy lips part into a clean, bright smile, showing her front teeth.
The view widens again to her face as she laughs openly, dimples visible, her teeth prominent and bright.
The pair then appear standing or leaning together in the cabin aisle area near the seats.
The woman faces the man, smiling, while other passengers move in the background.
She lifts her hand to her mouth again, covers her lips, and blows another kiss toward him.
He leans close, then turns outward with a surprised, amused expression ; another lipstick mark is visible on his cheek.
She laughs beside him, leaning in close with \textbf{obvious} delight.
The two look at each other warmly, smiling face to face, while the airplane seats and passengers remain behind them.
The commercial ends on another product display.
Large white text reads “ new ultra brite ” above the same long toothpaste carton labeled “ ultra brite, ” again shown on a dark red background with a glowing spotlight effect and the toothbrush illustration on the right side of the box.

% matched lemmas: obvious
\end{textsample}
