\begin{textsample}{NEG Dim 2 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_7.txt}  \label{ex:f2_neg_062}
A simple hand-drawn cartoon home interior appears against a mostly white background.
On the right, a blonde adult woman in a pink dress sits comfortably in a large blue armchair with her feet up on a matching footstool.
A yellow-curtained window is behind her, and a dark navy scarf with red stripes lies partly across her lap and trails onto the floor.
On the left, an adult man in a white shirt, red bow tie, brown pants, and black shoes walks in looking unwell.
His nose area is exaggerated into a large red swollen bulb, with a brown, heavy-looking shape strapped across it like a visual symbol of blockage or pressure.
He leans forward slightly, his face drooping with discomfort, while the woman looks toward him from the chair.
The man is then shown closer against the plain white background.
His cheeks and nose are red, his eyebrows tilt upward, and he looks miserable.
He gestures with both hands, spreading his arms, then lifting his palms beside his face, as if explaining how bad he feels.
The large red nose and brown obstruction remain centered on his face, making his congestion visible as a comic physical burden.
A visual transition returns to the living room, with the words “ Later that day ” written along the bottom.
The man now stands beside the seated woman.
His red swollen nose is gone, but he looks oddly dazed.
His body remains in place while his head stretches upward on a thin, string-like neck, then floats above his shoulders like a balloon.
The woman watches from the blue chair, still holding or working with the striped scarf.
The floating head and separated neck make his “ disconnected ” feeling visible.
The woman is then shown closer in the armchair, smiling and looking confident.
She raises a white and red box toward the viewer.
The box reads “ Non-Drowsy SUDAFED ” and “ Maximum Strength Nasal Decongestant, ” with smaller wording about nasal and sinus congestion due to colds and allergies.
She points toward the package as she presents it.
The scene shifts to a plain white background where two small red tablet-like circles move across the screen.
Black text appears : “ Opens Nasal Passages ” and “ Relieves Sinus Pressure. ” At the bottom, smaller grey text reads, “ Use only as directed. ” The Sudafed box then appears large on a light blue background, again labeled “ Non-Drowsy SUDAFED, ” “ Maximum Strength, ” and “ Nasal Decongestant, ” with “ Use only as directed ” underneath.
Back in the home, the man now stands smiling in front of a beige door with a round yellow doorknob.
He looks clear-headed and cheerful.
The woman stands behind him, smiling too, and wraps the navy scarf with red stripes around his neck.
He stands upright with his hands near his waist, looking pleased and alert, while she adjusts the scarf over his shoulders and around his collar.
The motion is lively and slightly overlapping, with the scarf flipping and swinging as she finishes arranging it.
The man turns his head toward the woman and smiles.
She moves close behind him, then reaches around and places her hands on his cheeks, gently checking his face and nose.
He puckers his lips briefly as she presses his cheeks, then smiles again.
They end standing close together by the door, both cheerful ; her hand rests on his shoulder and his hands settle confidently at his sides.
The final image returns to the Sudafed package on the light blue background, prominently displaying “ Non-Drowsy SUDAFED Maximum Strength Nasal Decongestant. ”

% matched lemmas: 
\end{textsample}
