\begin{textsample}{NEG Dim 2 – 2000 – Score -2.00 – 2000/tv\_com\_2000\_49.txt}  \label{ex:f2_neg_073}
A young man with shaggy dark hair sits stiffly in a \textbf{high-backed} leather chair in a dim, book-lined room.
He wears a dark suit jacket over a white shirt, tie, and red sweater vest, giving him a formal, slightly old-fashioned look.
Around him are shelves of books, a wooden desk with papers and a glowing desk lamp, and a bed or cot to one side, creating the feel of a private study or dorm room.
He faces forward as if addressing the viewer.
Outside in a leafy public area, a notice board or kiosk is covered with layers of flyers and papers.
Large red spray-painted letters stretch across the papers.
The suited young man stands at the left, arm raised near the board as if he has just written or pointed something out.
Several young people with punk or goth styling stand to the right watching him : one has tall black spiked hair, red pants, and dark clothing ; another wears a black sleeveless top ; another has a shaved head ; and others cluster nearby.
Their body language suggests they are observing or judging him rather than joining in.
The scene shifts to a bookstore or library counter.
The same dark-haired young man now appears as a clerk or student worker, wearing a red vest over a white shirt and tie, with a name tag on his chest.
He holds papers or a receipt and an open book, looking down at them while speaking to a young blonde woman across the counter.
She has her hair pulled back in a ponytail and wears a white shirt with a pale pink sweater draped around her shoulders.
Behind them are shelves of books and stacks of hardcovers.
As he reads from the paper, she watches with her arms crossed and a restrained, \textbf{unimpressed} expression.
In a blue-lit bedroom, the young man lies on his side beneath or beside a bed frame, hugging a stuffed animal tightly against his chest.
The lighting is cool and shadowy, and the slats of the bed loom above him.
His eyes look upward and sideways, wide and anxious, making him appear isolated and awkward.
Back in the dark study, he sits again in the leather chair with one leg crossed over the other, surrounded by books and the desk lamp.
Then, in a school hallway, two large young men in blue football jerseys walk toward him.
One jersey has a yellow number 9, the other a yellow number 12.
The player wearing number 9 stands close, facing the dark-haired young man with a hard, challenging expression while other students move in the background.
Outside again near a large tree, the punk-styled group reacts around the suited young man.
One person bends forward as if laughing, while another leans in with exaggerated body movement.
The young man stands in the middle, looking out of place among them.
The group ’s posture and gestures make him seem the target of teasing or ridicule.
The blonde woman at the counter reappears, still across from the red-vested clerk, now speaking or reacting more directly while holding her position near the books.
The young man in the study gestures with one hand as he talks, then a silver mobile phone is shown close up in someone ’s hand against a dark background.
It is a compact Kyocera slider-style phone : rounded silver body, small screen at the top, circular navigation button below, and a \textbf{keypad} revealed lower down.
On the screen is a simple circular “ S”-like logo.
He then holds the phone out toward the viewer from the study, bringing it forward so it fills the foreground while his face and bookshelves blur behind it.
The slider is open, clearly showing the \textbf{keypad} and central round control.
The phone ’s effect is shown through the people who had seemed dismissive before.
The football player in the blue number 9 jersey now stands in a locker-room or hallway area, calmly looking down at the silver phone in his hand.
Behind him, other players in matching blue jerseys bend over sports bags and gear.
Outside among the punk group, the young woman with the dramatic black spiked hair holds the phone and looks at it with interest.
She wears dark makeup, a black top, red sleeves or gloves, and studded accessories.
Behind her, other punk-styled friends move around casually under the trees.
At the library or bookstore counter, the blonde woman now smiles and leans forward slightly, holding a red book against her chest.
The red-vested young man has the phone raised in his hand, showing it to her.
She appears more engaged and friendly than before.
A wider view shows him seated or leaning at the counter, holding the small silver phone up between them while she faces him.
A small Kyocera logo appears at the lower left of the screen.
The young man returns to the book-lined study, holding the phone beside his face while addressing the viewer.
The Kyocera logo and the words “ the intelligent phone ” appear on screen near the lower left.
The final product display shows the silver Kyocera slider phone resting on a surface beside chess pieces.
Large white text reads “ \$15 Instant Gift Card, ” with smaller text indicating it is available at Best Buy.
Along the bottom are brand and partner logos, including Kyocera, “ Slider V5, ” the red Virgin Mobile logo, an MTV mark, and the yellow Best Buy price-tag logo.

% matched lemmas: high-backed, keypad, unimpressed
\end{textsample}
