\begin{textsample}{NEG Dim 2 – 2010 – Score 2.00 – 2010/tv\_com\_2010\_120.txt}  \label{ex:f2_neg_079}
The commercial opens on a rural farm landscape with a stone house, fields, hills, fencing, and a cart in the background.
The imagery has a stylized, model-like or animated appearance.
In the yard, a small boy dressed in white stands near an older woman who is working with wood near a chopping block.
The view moves closer : the older woman raises an axe over a log while the boy, in a white outfit and cap, stands nearby holding a brick.
A close-up then shows the boy smiling and holding a rectangular red brick with both hands, with a cart full of bricks behind him.
Next, the boy is shown pulling or pushing a heavily loaded wheelbarrow piled with bricks near the stone house.
The older woman stands behind it holding the handles or frame, suggesting the boy is helping move the load.
The scene cuts indoors to a framed black-and-white photograph on a mantel or shelf.
The photo shows the same boy standing beside an older woman who is smiling.
A clock is visible beside the photograph.
A door then opens from inside the house.
A bald, muscular man in an all-white outfit is seen at the doorway, holding a yellow-green bottle with a blue cap.
He smiles while presenting the bottle.
A close-up shows the bottle label clearly : it features the bald man ’s face and the “ Mr.
Clean ” branding.
Inside a rustic kitchen, the man stands beside the older woman.
She holds or examines the product bottle while he stands with one hand on his hip.
The room contains a stove, windows, shelves, and household objects.
The commercial then demonstrates cleaning uses.
A white kitchen surface with a dark spill is shown, with large white text over the image : “ 2.5X MORE POWER PER DROP. ” Small fine-print text appears along the bottom but is too small to read clearly in full.
Another shot shows the older woman ’s hand cleaning a white sink, with the product bottle placed nearby.
A close-up follows of the yellow-green liquid being poured from the bottle into a clear bucket of water.
Another shot shows a floor with muddy footprints being cleaned with a mop ; the mop passes over the marks, and fine-print text remains at the bottom.
The older woman and the white-clad man are then shown standing together in a hallway or kitchen area, facing each other as if in conversation or instruction.
The man ’s posture remains confident and upright.
Near the end, the product bottle is again held up in close-up against the rural outdoor background.
The final outdoor shots show the bald man standing in the field holding the bottle, with a hay cart and a person working in the background.
Large on-screen text appears : “ WHEN IT COMES TO CLEAN THERE ’S ONLY ONE Mr. ” The word “ Mr. ” is large and red.
A small website address appears near the bottom : “ MRCLEAN.COM. ” The final frame shows the man smiling toward the viewer, holding the product forward in the farm setting.

% matched lemmas: 
\end{textsample}
