\begin{textsample}{NEG Dim 2 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_79.txt}  \label{ex:f2_neg_041}
The commercial begins on a plain white screen with the blue Volkswagen emblem centered above the words “ Das Auto. ” and the small \textbf{web} address “ vw.com ” below.
It then changes to a close view of a black BlackBerry smartphone held upright in two hands against a dark background.
The phone has a touchscreen on top and a compact physical QWERTY keyboard below.
The BlackBerry name is visible above the display.
On the screen, a grid of colorful tiles fills the home screen : a browser tile with a beach image, a “ BlackBerry World ” tile showing “ MAD MEN, ” a Skype tile, and a BBM tile with a woman ’s portrait.
A thumb hovers near the lower part of the touchscreen and keyboard, ready to interact.
The user taps and navigates on the phone.
A small dialog appears reading “ Posting to Facebook, ” with a spinning progress circle and a “ Cancel ” button beneath it.
The phone then shows “ BlackBerry Hub, ” a unified message list.
Several accounts and notifications appear stacked together, including Facebook items, a message from “ Leo Ballard, ” an @ChadUte mention, and LinkedIn.
The interface has a light list area with a blue header, while a darker panel is partly visible to the side, suggesting the user is sliding between screens.
The hand continues to hold the phone securely while the thumb swipes across the display.
The home screen returns, again showing the tile layout.
Now the tiles include “ The New York Times, ” the browser tile with a tropical beach image, “ BlackBerry World ” with the “ MAD MEN ” artwork, and Skype.
The thumb moves across the tiles and taps the browser tile.
A \textbf{web} page opens with the heading “ BEACH ESCAPES. ” The page is bright and white, with vacation imagery : first a large photo of a yellow tropical fish in blue water, then a wide beach scene with pale sand, turquoise water, and a small green headland in the distance.
At the bottom, the browser address bar shows “ bluedreambeach.com, ” with navigation icons nearby.
The user \textbf{scrolls} or moves through the page using the thumb, keeping the physical keyboard visible below.
A dark vertical browser menu slides over the right side of the screen.
The left side still shows part of the “ BEACH ESCAPES ” page, while the menu lists options with small icons : “ Site Info, ” “ Add to Home Screen, ” “ Add Bookmark, ” “ Reader, ” “ Find on Page, ” “ Reload, ” and “ Share. ” The thumb rests near the lower menu options, indicating the user is choosing a sharing action.
The view shifts closer to a messaging screen.
At the top is a contact named “ Klara, ” marked “ Available, ” with a small woman ’s profile photo.
In the message entry field, the \textbf{web} address “ bluedreambeach.com ” is typed, and a yellow smiley icon sits to the right.
Below and along the bottom are messaging icons, including a back arrow, a contact or chat icon, an attachment icon, and a BlackBerry Messenger-style icon.
The message is sent to a conversation where “ David Nelson, ” shown with a small male profile photo, appears in the thread.
His message bubble contains the linked text “ bluedreambeach.com, ” with the time “ 2:25 PM. ” The user then types a response in the message field : “ Let ’s honeymoon. ” Word suggestions appear above the keyboard, including “ honeymoon, ” “ honeycomb, ” and “ honeysuckle, ” with the thumb pressing near the suggested word area.
The message is completed and appears in the conversation as “ Let ’s honeymoon again. ” followed by a small smiley face.
The phone remains centered in the hands, emphasizing the touchscreen, the physical keyboard, and the messaging interface as the final visible action continues on the BlackBerry screen.

% matched lemmas: scroll, web
\end{textsample}
