\begin{textsample}{NEG Dim 2 – 1970 – Score 1.00 – 1970/tv\_com\_1970\_83.txt}  \label{ex:f2_neg_027}
At a supermarket produce display, several hands move over piles of fruit.
In the foreground are rough-skinned cantaloupes arranged in rows ; behind them are shiny red tomatoes, oranges, bananas, and other produce.
A person in a bright blue sleeve presses a hand down on a cantaloupe, while another hand hovers over the tomatoes, as if testing their firmness.
A middle-aged male store employee, balding with dark hair at the sides, a small mustache, and glasses worn low on his nose, turns his head toward the produce area.
He wears a white store coat and a black bow tie, giving him the look of a grocery manager.
In the store aisle behind him, shelves and displays are softly visible.
An older male-presenting uniformed officer in a black coat and shiny peaked cap looks back with a serious, slightly puzzled expression.
The manager and the officer face each other closely, talking.
The manager ’s expression is earnest and concerned, and he gestures as if explaining a problem.
The view returns briefly to the produce display, where the blue-sleeved hand continues pressing the cantaloupes while another hand reaches among the tomatoes.
Then the manager speaks animatedly to the officer, his glasses slipping low as he looks over them.
The two men turn their attention toward another part of the store.
Farther down the aisle, several women stand in front of a large Charmin bathroom tissue display.
Behind them, a hand-lettered sign reads, in large black letters : “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” The women are holding soft, bulky multi-roll packages with a baby ’s face printed on the front and the brand name “ Charmin ” in large letters.
One woman has dark hair and wears a black dress or blouse with white polka dots and an orange scarf at her neck.
Another is a smiling red-haired woman in a pale, high-necked outfit.
A younger blonde woman in a pale yellow dress stands nearby with another package.
They cradle the packages against their chests and press their fingers into the sides, visibly squeezing them.
A close view of the packages shows the Charmin name prominently across the lower front, with a baby pictured above it.
The packs appear in pastel colors, including pale blue, cream, and pinkish tones.
The women ’s hands press into the plastic-wrapped tissue, denting it slightly to show its softness.
The red-haired woman smiles with \textbf{obvious} delight while holding a cream-colored package ; the dark-haired woman squeezes a pale blue package beside her.
The officer and manager approach the display.
The officer, still stern, faces the women and the sign, while the manager stands beside him in his white coat.
The women keep their packages in hand, looking caught but cheerful rather than ashamed.
The sign fills the background again, its message unmistakable : “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” Beneath it are stacked Charmin packages, each with the baby image and brand name visible.
Two of the women face forward holding their Charmin packages at chest level.
The dark-haired woman looks more guarded at first, with wide eyes and a tight expression, while the red-haired woman smiles brightly.
They continue to hold and gently squeeze the packages.
The dark-haired woman glances sideways, then down at her pack, and gradually smiles.
The red-haired woman looks pleased and confident, presenting the package as if inviting attention to how soft it is.
The younger blonde woman steps into prominence holding a Charmin package in both hands.
She raises it toward the officer and manager, then presses the package outward, presenting it for inspection.
The red-haired woman beside her keeps smiling, hugging her own package.
The blonde woman ’s expression is earnest and persuasive as she offers the tissue pack forward.
The officer takes or holds a cream-colored Charmin package against his chest.
The manager stands close at his side, pointing at the package and then placing a hand near it, as if controlling the situation.
The officer ’s face is stiff and duty-bound, but his hands close around the soft package.
The manager raises one palm in a cautioning gesture, as if stopping him from squeezing too much.
The officer looks from the manager to the package, uncertain.
Left alone with the package in his hands, the officer studies it.
He presses his fingers into the sides and front, testing the softness.
His stern expression softens into curiosity.
He lifts the package closer to his face, almost against his nose and mouth, as if checking its scent or feel.
The baby picture on the package faces outward, and the large “ Charmin ” name remains partly visible at the bottom.
The officer looks sideways while still clutching the package, now clearly absorbed by it.
The women react with amusement.
The dark-haired woman smiles broadly, and the red-haired woman looks down at her own package with a delighted grin.
The red-haired woman lifts the Charmin close to her face and smiles into it, while the dark-haired woman keeps squeezing her pale blue pack.
Both women look pleased, sharing a knowing, playful reaction to the officer ’s interest.
The officer continues holding the Charmin package in front of his black uniform, speaking while looking at it and then off to the side.
He turns his head and notices the store manager.
The manager is now holding and squeezing a pale blue Charmin package himself.
He looks down at it with a private, satisfied smile, his fingers pressing into the soft bundle.
The officer turns toward him with a surprised, accusing look, while the manager keeps smiling, caught in the same irresistible act.
The manager, in close view, beams down at the package with a sheepish, delighted grin.
His glasses sit low on his nose, and his black bow tie is visible under his white coat.
He glances upward as if realizing he has been found out, then looks back down with a pleased smile.
The commercial ends with the manager holding the pale blue Charmin package centered in front of his chest.
The packaging fills the view : a baby ’s face at the top, “ Charmin ” in large blue letters across the lower front, and smaller text about softness and Procter \& Gamble printed near the top.
Finally, the display returns : a large sign above stacked packages again reads, “ PLEASE DO N’T SQUEEZE THE CHARMIN, ” with several pastel Charmin packs lined up below it.

% matched lemmas: obvious
\end{textsample}
