\begin{textsample}{NEG Dim 2 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_96.txt}  \label{ex:f2_neg_031}
A young adult couple sits close together on a white sofa in a dim, cozy living room.
The man, with dark hair and a light-colored shirt, is on the left ; the woman, with long blonde hair and a purple outfit, is on the right.
A warm table lamp glows in the background, and pillows line the sofa.
They face forward as if watching or responding to something in front of them, smiling and leaning toward each other.
A telephone sits on a low table in the foreground, gradually becoming the visual focus.
The phone is shown more prominently : a gray push-button telephone base with a large \textbf{keypad} and a dark handset resting across the top.
The couple remains behind it on the sofa, partially blurred by the focus on the phone.
The image then isolates the phone against a dark background, placing the \textbf{keypad} squarely in the center.
Over this, bold commercial graphics appear : the title “ WINNERS! ” in large red-orange letters, with the \textbf{subtitle} “ The 24-Hour Telephone Trivia Game ” underneath.
Across the bottom, in large yellow-green numbers, is “ 1-900-999-9000. ” The couple reappears, now against a bright, showy backdrop instead of the dim living room.
Behind them are shimmering pink and purple metallic streamers and a large “ WINNERS ” sign, making the sofa look as if it has been transported into a game-show-like set.
The same phone number remains stretched across the bottom of the screen.
As the view widens, the scene reveals more colorful decorations around them, including bright panels and a lamp at the side, blending a living-room setup with a flashy studio atmosphere.
The man and woman look at one another and smile, sitting close together as if sharing the experience.
A man is then shown beside or in front of a large television screen displaying bright fireworks.
He has short dark hair and wears a blue shirt.
He turns toward the viewer with a pleased smile while the fireworks fill the TV screen behind him.
The phone number stays visible along the bottom.
A close-up follows of a blonde woman holding up her wrist to show a small watch.
She smiles widely with an excited, open-mouthed expression, her eyes bright and directed toward the viewer.
The watch has a slim band and a small round face, positioned near the left side of her face.
The phone number remains across the lower part of the image.
The service \textbf{categories} appear as large purple block letters over the dark phone background : “ MUSIC, ” “ SPORTS, ” and “ TV/MOVIES. ” The phone number continues at the bottom.
A demonstration-style graphic then shows a large telephone \textbf{keypad} on the right, with raised square number buttons, while a small red-bordered inset on the left shows the original couple close together, the man holding a telephone handset near his face and the woman beside him.
This visually connects using the phone \textbf{keypad} with playing the trivia game.
Another prize image appears : a white cruise ship moves across open water on the right side of the screen.
In the upper left, a red-bordered inset shows a smiling couple posing together ; the man wears a reddish or orange top with a dark collar, and the blonde woman wears a blue jacket.
The same large phone number remains along the bottom, tying the prize imagery back to the call-in service.
The commercial ends on a final graphic with the gray \textbf{keypad} phone centered under the “ WINNERS! ” title and the \textbf{subtitle} “ The 24-Hour Telephone Trivia Game. ” Large text reads “ CALL 1-900-999-9000. ” Smaller print underneath says, “ To Play by \textbf{mail} send a S.A.S.E. to : PO Box 491416 Los Angeles CA 90049, ” followed by “ 95¢ a minute.
No Toll. ”

% matched lemmas: category, keypad, mail, subtitle
\end{textsample}
