\begin{textsample}{NEG Dim 2 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_64.txt}  \label{ex:f2_neg_086}
In black-and-white, the commercial begins in a dark studio setting with food isolated against a black background.
A clear, crinkly plastic bag lies partly open, holding long pale stalks that look like celery.
A pair of adult hands reaches in through the loose plastic, gathers the bag ’s opening aside, and removes one stalk.
The plastic catches the light in bright wrinkles and diagonal streaks as the hands pull it taut.
The person holds the celery-like stalk with both hands, then bends and breaks it, presenting the food as crisp and fresh.
A large wedge of watermelon with dark seeds is shown inside a clear plastic bag.
Hands pull the shiny plastic away from the rind and fruit, stretching it open as the wedge slides free.
A young boy, about elementary-school age, with short neatly combed hair and a striped shirt, holds the watermelon slice in both hands.
He raises it to his mouth, smiles slightly, and bites into it, his eyes looking upward and to the side with a pleased expression.
A clear plastic bag filled with round cookies appears next.
An adult hand reaches into the bag and lifts out a cookie.
A young girl, also elementary-school age, with straight bangs and two braided pigtails tied with light ribbons, looks down happily and brings the cookie to her mouth.
She bites it, chews, and smiles softly against the same dark, uncluttered background.
The food preparation continues with a clear bag full of pale, leafy or sliced sandwich fillings.
A hand smooths the plastic over the contents, then removes pieces and places them onto a small stack of bread.
Close hands assemble a sandwich : a slice of bread, folded layers of filling, and loose leafy edges are stacked neatly.
Another slice of bread is set on top, and the hand presses down gently, flattening the sandwich into a tidy square.
A rectangular Baggies box is then displayed by hand.
The package has large bold letters reading “ BAGGIES ” across the side, with smaller text indicating a food-wrap size and a visible “ 50 ” count marking near one end.
The hand turns and holds the box horizontally.
Another hand pulls a transparent bag or sheet from the box opening ; the plastic stretches downward in long glossy folds, showing how thin and flexible it is while still staying in one piece.
The demonstration changes to a comparison setup.
Two clear plastic bags hang side by side from flat supports, with small glass containers full of coins positioned above them.
The left bag is labeled on-screen “ BAGGIES, ” while the right is labeled “ Next largest seller. ” Coins begin pouring from both containers into the bags.
The Baggies bag on the left bulges and sags under the weight but continues to hold the coins.
On the right, coins fall through and drop out below the bag, visibly spilling downward while the bag deforms.
The labels remain beneath the bags, making the comparison clear : “ BAGGIES ” on the left and “ Next largest seller ” on the right.
A young adult woman with short, styled hair and small earrings appears in profile against the dark background.
She holds a long pale stick of food, likely celery, and bites into it.
Her expression shifts into a satisfied smile as she chews.
The earlier comparison image briefly overlaps visually before fully giving way to her face.
The commercial returns to the children tasting food.
The boy again holds the seeded watermelon wedge close to his mouth, biting and chewing with a small smile.
The girl with braided pigtails is shown chewing her cookie and looking content.
A young adult man then appears in close profile, holding a thick sandwich in one hand.
He opens his mouth wide, bites into the sandwich, and chews, his expression relaxed and pleased.
Near the end, an arrangement of fresh foods is displayed on a dark tabletop : long celery-like stalks in front, a leafy head of lettuce or cabbage, a round pale vegetable or fruit, scattered small slices, and a large cut half of a seeded melon standing upright in the back.
A hand places a long Baggies box across the food display, the large “ BAGGIES ” name facing forward.
More Baggies boxes are added at angles around the foods, suggesting different package sizes.
The final arrangement shows the bold Baggies branding surrounded by the fresh produce and sandwich ingredients, all lit dramatically against the black background.

% matched lemmas: 
\end{textsample}
