\begin{textsample}{NEG Dim 2 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_117.txt}  \label{ex:f2_neg_061}
A bright, white kitchen is seen in soft, warm light.
An adult woman with light skin, large curly blond hair, dangling earrings, and a loose yellow top stands behind a pale counter.
She holds a yellow sponge in one hand and a white trigger-spray bottle of Fantastik in the other.
Around her are domestic kitchen details : stacked white plates at the left, a bowl or cluster of green fruit on the counter, yellow sunflowers near a sunny window over the sink, and a stovetop with pots or metal cookware to the right.
As she talks to the viewer, a lower-third name \textbf{caption} appears reading “ Elayne Boosler. ” She gestures casually with the sponge, then raises the Fantastik bottle higher so the label faces forward.
She presents the bottle prominently in front of her chest.
It is a white plastic spray cleaner bottle with a teal-and-white trigger top and a colorful label with orange, yellow, and teal bands ; the brand name “ Fantastik ” is visible on the lower part of the label.
As she holds it toward the viewer, colorful graphic bursts and small streaks briefly radiate around the bottle, emphasizing it.
The bottle fills much of the view, with her yellow sleeve and kitchen background blurred behind it.
The demonstration moves to a white tiled countertop.
Two brownish-orange greasy-looking spots sit on the tile, with small specks scattered around them.
A hand brings the yellow sponge down onto the mess and wipes across the stains.
The sponge moves firmly over the tile, and the greasy patches disappear under it.
After the wiping, the tile looks clean and pale again.
A fingertip then slides across the cleaned tile surface, pressing lightly as if checking for residue.
The finger glides over the smooth tile, visually suggesting that no sticky film remains.
The woman reappears holding the Fantastik bottle at her side.
She looks down briefly at the product, then back toward the viewer, continuing to speak.
Her expressions shift from matter-of-fact to animated and slightly playful ; she raises the yellow sponge as she gestures.
The bottle remains visible beside her shoulder, its white body and teal trigger contrasting with her bright yellow top.
As she continues, her face fills more of the scene : her curly hair frames her face, her earrings swing slightly, and she speaks directly forward with expressive eyes and small head tilts.
The commercial ends with a clean product display on the tiled kitchen counter.
The Fantastik spray bottle stands upright on the right, label facing outward.
On the left, large black on-screen text reads, line by line : “ No Grease.
No Film.
New Fantastik. ” The softly lit kitchen background remains out of focus behind the product, keeping attention on the bottle and the written claim.

% matched lemmas: caption
\end{textsample}
