\begin{textsample}{NEG Dim 2 – 1970 – Score 1.00 – 1970/tv\_com\_1970\_53.txt}  \label{ex:f2_neg_026}
A blonde adult woman sits in a soft, bright domestic setting, leaning forward on white bedding or a cushioned white surface.
She has long, feathered 1970s-style hair with full bangs, light eye makeup, and a calm, direct expression as she faces the viewer.
She wears a silky, pale green satin blouse with loose sleeves and a delicate necklace.
Behind her is a tall window with white curtains, showing leafy greenery outside ; flowers and plants add to the airy, garden-like atmosphere.
In front of her, near the lower left of the scene, stands a plain white rectangular bottle with a dark cap and no visible label.
A large cluster of pale flowers fills the right foreground, slightly out of focus.
She rests her cheek in one hand while speaking, then glances down and reaches toward the plain bottle.
She slides it closer and lifts it upright beside her face, holding it so the unmarked front is clearly visible.
The bottle is simple and opaque-looking, with rounded corners and a dark brown or black cap.
She continues addressing the viewer while keeping the bottle near her, visually emphasizing that it has no label.
After setting the bottle back down, she becomes more animated with her hands.
She lowers her hand from her face, folds her arms lightly on the white surface, and leans in.
Her expression remains composed and earnest.
As she continues, she gestures toward herself, touching her upper chest and collarbone area with one hand, then lets her fingers move through the ends of her hair.
Her long blonde hair falls over her shoulders and across the front of her blouse, catching the soft light.
She then demonstrates the qualities of her hair by lifting a section from the side.
She draws the hair outward and upward, letting it fan out in a pale, silky sheet.
The hair appears light, smooth, and full, with the ends moving loosely as she shakes and releases it.
She smiles more broadly, briefly laughs or beams, and brushes her hair back from her face.
The plain white bottle remains standing near her left hand in the foreground.
Near the end of her on-camera appearance, she reaches for the bottle again.
Smiling, she holds it with one hand and uses the other to grasp the cap, beginning to twist or open it.
The visual focus shifts away from her face to a close view of an open palm held over the white surface.
The hand is cupped and ready to receive the product.
The bottle ’s mouth appears above the palm, tilted downward.
A thick, translucent golden liquid begins to pour from the bottle in a slow stream.
It lands in the center of the palm and forms a glossy oval pool.
The stream continues steadily, building up a rounded, honey-colored dollop.
The liquid looks smooth and rich, reflecting light as it spreads slightly but keeps a thick shape.
Finally, two labeled product bottles stand side by side on a reflective light-colored surface.
Both are rectangular with rounded corners and dark caps.
Their labels feature a smiling portrait of Farrah Fawcett with blonde hair, and the visible text identifies one as Farrah Fawcett Shampoo and the other as Farrah Fawcett Creme Rinse Conditioner.
The bottles sit against the same soft, bright background, with flowers still visible at the right, ending on a clear product display.

% matched lemmas: 
\end{textsample}
