\begin{textsample}{NEG Dim 2 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_102.txt}  \label{ex:f2_neg_069}
Against a plain black studio background, a white chicken fills the center of the image, its wings thrown wide and blurred from rapid flapping.
Its feathers are ruffled and spread out as it drops downward toward a small dark portable CD player beneath it.
The player sits alone on the black surface, with a rounded rectangular shape, a small display area on the front edge, and control buttons along the sides.
The chicken continues descending, body tilted forward and head pointed down, its orange beak and pale feathers visible amid the motion blur.
As it lands, its wings beat hard on either side, creating a messy, feathery cloud around its body.
The bird ’s orange feet come down onto the top of the CD player, using it like a tiny platform.
The Magnavox name is faintly visible on the player as the chicken ’s feet and body partially cover it.
The bird steadies itself while still flapping.
Its wings stretch out horizontally, then begin folding in.
The chicken crouches low over the player, head down, feathers puffed into a rounded mound.
Its orange feet grip the top surface, toes splayed across the device near the front controls.
The dark background keeps all attention on the white bird and the small electronic player beneath it.
Gradually, the chicken settles.
Its wings tuck closer to its sides, and it stands more upright on the portable CD player.
The bird lifts its head slightly and turns to one side, looking off to the right, while remaining balanced on the device.
The visual joke is that the player remains in place under the significant jolt of the chicken ’s landing.
The commercial then changes to a clean white promotional screen.
Large black text reads “ Free ” at the top, with a thin red line beneath it, followed by “ CD Case. ” Below the words is a picture of a small black zippered CD carrying case with a wrist strap.
Under the case, smaller text reads, “ Up to a \$20 value, ” followed by fine print : “ Offer ends March 31, 1996.
While supplies last. ”

% matched lemmas: 
\end{textsample}
