\begin{textsample}{NEG Dim 2 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_56.txt}  \label{ex:f2_neg_066}
A plain white refrigerator stands alone in the center of a sparse studio-like room.
The floor is a gray-and-white checkerboard pattern, and the background is a smooth pale gray wall with soft light centered behind the appliance.
The refrigerator has a top freezer section, a larger lower door, a vertical handle on the right, and a small brand badge near the upper right of the freezer door.
The view moves in close to the refrigerator ’s upper edge.
From behind the white appliance surface, the top of a man ’s head rises into view.
He is a large Black man with close-cropped dark hair and a mustache, wearing an all-white athletic outfit.
As more of him appears, he leans over the refrigerator edge with both arms forward.
His right wrist is wrapped in a thick white athletic wristband, and a ring is visible on one hand.
He looks down with a focused, slightly amused expression while moving his hands along the white surface in front of him, as if working on or cleaning part of the refrigerator just below the visible edge.
He then lowers his head and shoulders back down until only the top of his hair is visible, and then disappears.
The refrigerator is again seen standing by itself in the same empty room.
A moment later, the man peeks out from behind the right side of the appliance.
Only part of his face and shoulder are visible at first, pressed close to the refrigerator ’s side.
He smiles broadly, looking toward the open space to his right, then ducks back behind it.
The full room comes back into view.
The refrigerator remains centered, and the man emerges from behind its right side.
He is dressed entirely in white football-style gear : a loose white jersey, white football pants, white socks, white high-top athletic shoes, and white wristbands.
His build is very large and powerful.
He steps beside the refrigerator, smiling, then places his hands on the side and handle area.
He grips the refrigerator and begins to tip it toward himself.
The appliance leans diagonally, its bottom edge lifting off the floor on one side.
He braces it against his body, arms wrapped around the side, and hoists it up with apparent ease.
Still smiling, he walks left across the checkerboard floor while carrying the full-size refrigerator at a slant in front of him.
The refrigerator ’s bottom hovers above the floor as he continues stepping sideways and forward, his white shoes crossing the patterned tiles.
As he carries the refrigerator off toward the left edge of the room, large dark lettering fades in on the wall behind him.
The CP\&L logo appears, followed by the slogan “ Where Listening Generates Powerful Ideas, ” and beneath it the phone number “ 1-800-THE-FRIDGE. ” The man and refrigerator continue moving partly out of view on the left, leaving the CP\&L message and phone number clearly centered against the pale wall.

% matched lemmas: 
\end{textsample}
