\begin{textsample}{NEG Dim 2 – 1970 – Score -1.00 – 1970/tv\_com\_1970\_69.txt}  \label{ex:f2_neg_006}
The commercial opens with a close-up of a blonde woman in a dark, studio-like setting.
She is dressed in a reddish-brown top and appears carefully made up, with earrings visible.
Bright round lights line the right side of the frame, suggesting a backstage, dressing-room, or performance environment.
She lifts one hand toward her hair or ear.
The next shot shows the same woman from the side, smiling or speaking while looking downward.
Her short, styled blonde hair and earrings are visible, and she wears a loose brown/orange garment with a dark beaded necklace.
The background remains dark with soft floral shapes behind her.
A title card follows.
Against a pale, warm-toned background, large red serif text reads “ MEMORY YARN. ” Small copyright text appears at the lower left, including “ {\EmojiFont ©} 1978 Leggs Products. ” The commercial then cuts to a close shot of a woman ’s legs.
One leg is extended horizontally, with a hand pointing toward or touching the shin/calf area.
The person is wearing open-toed heeled sandals and sheer hosiery.
The surrounding background is dark, keeping attention on the leg.
Next, an egg-shaped L’eggs package is shown standing upright.
The blue “ L’eggs ” logo is printed on the upper half.
Through a vertical opening or cutout, a pair of legs in sandals is visible inside or behind the package, visually linking the product to legs/hosiery.
The final frame shows the egg-shaped L’eggs package centered against a dark background with a light floor or surface beneath it.
Below the package, black text reads : “ Nothing beats a \textbf{great} pair of L’eggs. ” A “ Classic Commercial Archives ” watermark appears in the lower-left corner throughout the frames, with a faint archive watermark across the lower portion of several images.

% matched lemmas: great
\end{textsample}
