\begin{textsample}{NEG Dim 2 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_70.txt}  \label{ex:f2_neg_002}
A black-and-white scene opens on a wall calendar hanging against a plain dark background.
The visible page reads “ 1952, ” “ MAY, ” a very large “ 30, ” and “ FRIDAY, ” establishing the date.
Beneath the calendar, a tabletop arrangement comes into view : a compact portable radio with a glossy dark rounded case and a pale front grille.
The brand name “ RCA Victor ” is visible near the bottom of the radio ’s front.
To the radio ’s right sits a small rectangular RCA battery carton with the RCA circle logo on its face.
A pair of adult hands, seen from the wrists down in suit sleeves, begins handling the radio.
One hand wears a ring.
The hands steady the portable set and turn it so the plain dark back faces forward.
The person ’s fingers feel along the back panel and top edge, then open the rear of the radio.
Inside, the radio ’s components are exposed : a metal chassis across the top with small printed markings, rows of holes, wiring, and compact electrical parts arranged in the lower compartment.
The hands work carefully inside the open radio, moving wires and reaching into the battery compartment.
A rectangular RCA battery package is brought in from the right, its side showing a round RCA logo.
The battery is guided into the lower part of the radio ’s interior while the other hand holds loose leads and positions the connectors.
The battery is slid into place horizontally across the bottom section, with the RCA logo facing outward.
The fingers continue adjusting the wires, pressing them down and tucking them into the space around the battery so the parts sit neatly inside the open case.
After the battery is installed, the radio is turned again so its smooth back faces outward.
To the left of the radio, a retail display of RCA batteries appears on the tabletop.
It includes a box with two upright cylindrical batteries pictured or standing on top, each carrying the RCA logo.
A sign on the display reads “ RCA ” and “ Radio A Battery. ” The radio remains at the right edge while the battery display becomes the focus.
The view then presents a wider \textbf{assortment} of RCA battery packages arranged like a store display.
There are several rectangular cartons and cylindrical battery forms in different sizes, all marked with the RCA logo.
Large boxes are stacked at the back, smaller boxes and open display trays sit in front, and the text “ RADIO A B BATTERY ” is visible on a large carton.
Other packaging shows RCA logos and product labels for radio batteries, suggesting a variety of sizes for different portable radio models.
The final close-up isolates two products : a large rectangular box on the left and a cylindrical battery on the right.
Both carry bold RCA circle logos.
The box reads “ RADIO B BATTERY ” and includes the line “ RADIO-ENGINEERED FOR EXTRA LISTENING HOURS. ” Below that, smaller text reads “ No.
VS 016 • 67½ VOLTS. ” The cylindrical battery beside it is labeled “ RADIO A BATTERY, ” also with the RCA logo prominently centered.
The commercial ends visually on this clear product display, emphasizing the branded RCA radio batteries and their packaging.

% matched lemmas: assortment
\end{textsample}
