\begin{textsample}{NEG Dim 2 – 1950 – Score 1.00 – 1950/tv\_com\_1950\_114.txt}  \label{ex:f2_neg_005}
The commercial is in black and white and begins in a staged jewelry-shop setting.
A clean-cut adult man with dark hair stands facing forward, dressed formally in a dark suit jacket, white shirt, bow tie, and pocket square.
He smiles as he speaks.
To his left is a display counter filled with small watch or jewelry items, arranged in rows with little signs or cards.
Behind him are shelves holding boxes and display pieces, and a leafy plant sits near the counter, giving the set a neat retail-showroom feel.
The presenter remains beside the display counter, addressing the viewer directly.
He shifts his posture slightly and gestures with one hand toward the merchandise.
After a few moments he reaches to the counter and lifts a small open presentation case.
He brings it up to chest height and holds it with both hands, angling it forward so the contents face the viewer.
The view changes to a close look at the open case.
Inside is a satin-lined watch box with the word “ BULOVA ” printed on the inner cushion, and “ BULOVA ” also appears across the front edge of the case.
Resting inside is a delicate ladies ’ wristwatch.
The watch has a small bright face and a narrow metal bracelet.
A hand reaches down from above, pinches the watch carefully by the bracelet, and lifts it out of the box.
The watch is then held suspended in front of a plain background.
It dangles from the fingers, with its small face catching the light.
Another hand comes up behind it, palm and fingers forming a backdrop so the watch can be seen more clearly.
The watch is positioned upright against the hand.
Its face is small and light-toned, framed by an ornate, decorative case.
The bracelet is narrow and segmented, with small metal sections above and below the face.
A closer view shows the watch held against the fingers.
The face has dark hour markers and dark hands, with a rounded or oval decorative case around it.
A fingertip points to the lower part of the bracelet, drawing attention to the band.
The hands turn the watch slightly from side to side, showing the profile and the decorative side pieces where the bracelet meets the case.
The bracelet is then demonstrated in the hands.
Each end of the band is held between fingers and gently pulled outward, stretching the bracelet lengthwise.
The metal links separate and flex, showing it as an expansion bracelet.
The watch face remains in the center while the band extends on both sides, then is relaxed and brought back toward its original shape.
The hands rotate it back to a front-facing position, again presenting the small ornate face and slim bracelet straight up and down.
Text appears over the watch image : “ BULOVA ” in bold capital letters, with “ Miss America ” below in a flowing script.
The watch remains centered in front of the hand as the product name overlays the image.
The visual then becomes a clean product display on a dark background : the watch is enlarged and laid horizontally across the screen, bracelet stretching left and right, with the dial in the center.
Beneath it, the text reads “ BULOVA ” and “ Miss America, ” the brand in block capitals and the model name in cursive script.
The large watch display continues, emphasizing the polished case, the bright face, and the narrow bracelet links.
The face is square-ish or rounded with small dot markers and dark hands, surrounded by a decorative, jewel-like border.
The bracelet sections on both sides appear slim and reflective.
The product name stays clearly visible below the watch.
The presenter reappears behind the product image as the watch and “ BULOVA Miss America ” lettering remain superimposed over him for a moment.
He is back in the jewelry-shop set, still in his suit and bow tie, holding the small watch near his chest as he continues addressing the viewer.
A new overlay presents the watch and price.
On the left, a hand holds the watch vertically between fingers, close and prominent.
On the right, large text reads “ BULOVA, ” “ Miss America, ” “ only, ” and “ \$35 75, ” with the “ 75 ” set smaller and raised like cents.
The watch face is bright and centered in the fingers, while the price and name fill the right side of the screen.
The presenter is faintly visible behind the overlay in some moments, but the product and price dominate the image.
The overlay fades back to the shop setting.
The presenter stands beside the counter again, then looks down and reaches toward the display.
He picks up the open Bulova presentation case once more.
Holding it with both hands, he brings it up and turns it toward the viewer, smiling.
The open box shows the satin lining and the “ BULOVA ” name inside, with the watch nestled at the bottom of the case.
He keeps the case raised at chest level, angled outward as if offering one final look.
His expression remains pleasant and confident.
The shelves and display counter stay in the background, reinforcing the jewelry-store setting.
Near the end, he glances down at the box with a satisfied smile, still holding it carefully in both hands.
The image gradually darkens until the screen fades to black.

% matched lemmas: 
\end{textsample}
