\begin{textsample}{NEG Dim 2 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_107.txt}  \label{ex:f2_neg_064}
The commercial unfolds as a fast-paced travel and adventure montage.
It opens with tilted, close-up shots of people in an active situation.
A young person in a gray-and-blue top is seen from above or at an angle, looking upward and extending a hand.
The next shots show a man ’s face in close-up, also looking upward with an intense or excited expression.
A black-gloved hand reaches down against a bright sky, while another bare hand reaches up toward it ; the hands come very close, though the sampled frames do not clearly show a grasp.
The scene then cuts to a large white cruise ship moving through blue water under a bright sky.
This is followed by an aerial view of a coastline with green vegetation, sandy beach, and blue ocean.
Inside what appears to be a helicopter or small aircraft, a man points out through a window toward the \textbf{sea} below.
The view cuts to a sailboat seen from above on deep blue water.
A rapid sequence of water and outdoor activities follows : a person is seen against a bright sky ; then there are close-up \textbf{splashing} shots of a person in water.
Another shot shows blue-green water from above or underwater.
A small personal watercraft or jet ski moves across churning water with riders visible, followed by a distant, blurred silhouette of a rider on water against a bright horizon.
The montage shifts to more adventure imagery.
One shot shows people on or near a climbing/rope structure against a bright blue sky.
Then a person wearing an orange top, helmet, and backpack moves along a forest trail, likely on a bicycle or similar outdoor activity ; this is followed by close-up shots of helmeted people in the forest, their faces filling the frame as green foliage passes behind them.
A helicopter is shown flying low over the ocean near a sandy beach and surf.
Another shot shows a curved fishing rod silhouetted against a pale sky with clouds.
The final adventure sequence shows a climber on a steep, tan, rock-like wall or cliff.
The climber, wearing a harness or gear, moves across the textured surface in several consecutive shots, with a blue sky and architectural or cliff edges visible around the wall.
Near the end, the commercial returns to a wide, scenic shot of a large cruise ship on calm water at sunset or sunrise, with warm golden light and hills in the background.
On-screen branding appears : “ royalcaribbean.com, ” the Royal Caribbean International logo/name, and the tagline “ Get out there. ” The final sampled frame is black, indicating a fade-out or end screen.

% matched lemmas: sea, splash
\end{textsample}
