\begin{textsample}{NEG Dim 2 – 1950 – Score 1.00 – 1950/tv\_com\_1950\_34.txt}  \label{ex:f2_neg_008}
Against a shimmering curtain backdrop, a young adult woman in smart daytime dress appears in black and white.
She wears a broad, feathery or fur-trimmed hat, a tailored coat, and layered pearl necklaces.
Holding a small hand mirror in one hand with light-colored gloves draped over it, she uses a round powder puff on her cheek and chin.
She studies her reflection with a composed, pleased expression, then lowers the puff and smiles slightly, as if satisfied with her made-up appearance.
A male presenter in a dark suit, white shirt, and tie joins the scene beside her.
Behind them hangs an oversized, flat display shaped like the Deep Magic bottle, with the words “ deep magic ” visible on it.
The woman remains to the side with her mirror and gloves, while the presenter faces forward as the main speaker.
In a closer view, he stands beside the large bottle display and raises a small cosmetic item in his hand, using it as a prop while he talks about the product.
The bottle display remains prominent at his shoulder, its pale pear-shaped form contrasting with the dark curtain.
The scene changes to another woman seated or standing at a dressing table, seen through or beside an ornate, \textbf{scrolling} mirror frame.
She is a young adult with dark, curled hair and wears a light, soft-looking blouse or robe with a ruffled collar.
Holding a folded white cleansing cloth or pad, she wipes her face methodically.
She passes it over one cheek, across the nose, up over the forehead, around the eyes, and down along the chin and jaw.
Her expression is calm and pleasant, and as she continues wiping, her face appears clean and fresh.
The decorative mirror frame curves along both sides of the image, giving the setting the feel of a bedroom or vanity area.
A hand then holds a close-up of the product bottle.
It is a light-colored, tapered bottle with a narrow cap and a rounded, pear-like body.
The label reads “ deep magic, ” with smaller text below indicating it is a facial cleansing lotion, and the product name is centered clearly on the front.
The presenter returns, again in front of the curtain with the large Deep Magic bottle display beside him.
He leans slightly forward as if emphasizing his point, then brings up a special sales package.
He holds the package at chest height and points to it with his other hand.
The package contains two small Deep Magic bottles standing side by side in a cardboard carrier.
As he continues indicating the offer, the package is shown more clearly : a large sign across the top reads “ Special 89¢, ” and the two bottles beneath it match the same tapered Deep Magic shape.
The final view centers on the two-bottle special pack, with the bold “ Special 89¢ ” price above the bottles and additional small savings text along the bottom.

% matched lemmas: scroll
\end{textsample}
