\begin{textsample}{NEG Dim 2 – 1950 – Score 1.00 – 1950/tv\_com\_1950\_30.txt}  \label{ex:f2_neg_009}
In black and white, a middle-aged man with a receding hairline, a small mustache, and a neat suit and tie stands in a dark studio beside a large poster-style display.
The display looks like an oversized newspaper advertisement.
Across the top, bold lettering reads, “ NEW LAXATIVE ADVANCE, ” with a second line, “ For Fast Relief of Irregularity. ” The main dark panel of the display features the large words “ NEW SERUTAN PLUS. ” On the left side are a drawing of a capsule or pill form and an open bottle filled with capsules, labeled “ Serutan Plus. ” Beneath the product name, smaller text reads, “ with soothing medication for more comfortable action, ” and the lower portion contains dense fine print like an ad or product information box.
The presenter faces forward, standing to the right of the display.
He gestures toward the poster with one hand, then points specifically at the large “ NEW SERUTAN PLUS ” lettering.
As the product name fills more of the view, his hand remains visible at the right edge, indicating the words and drawing attention to the product name, the capsule image, and the bottle illustration.
The display remains the main visual focus, with the black background making the white lettering and product graphics stand out sharply.
The man then appears closer against a dark background, holding an actual small Serutan Plus bottle upright in one hand near his chest.
The bottle has a light cap and a dark label with the product name visible in block lettering.
With his other hand, he forms a precise “ OK ” or pinching gesture, as if showing or emphasizing a small capsule between his fingers.
He looks directly forward while speaking, then glances down toward the bottle.
His expression is controlled and earnest, and he uses small, careful hand motions rather than broad gestures.
He raises the bottle slightly, turns his attention to its label, and points at or taps the bottle with a finger, visually reinforcing the product identification.
The wider studio arrangement returns, with the large Serutan Plus display on the left and the presenter on the right.
He now holds the bottle near his chest, keeping it visible while addressing the viewer.
He stands upright in his suit, occasionally lifting a finger as if making a key point, then bringing both hands around the bottle in a presenting gesture.
The oversized display remains unchanged : “ NEW LAXATIVE ADVANCE, ” “ For Fast Relief of Irregularity, ” “ NEW SERUTAN PLUS, ” the capsule graphic, the bottle illustration, and the smaller line about soothing medication are all visible.
The commercial ends on a clean product graphic rather than the presenter.
On the left are two Serutan Plus packages : a rectangular carton and a glass bottle or jar, both labeled “ SERUTAN PLUS. ” Across the top, large raised-looking letters read “ NEW LAXATIVE ADVANCE. ” To the right, a framed rectangular panel first reads “ FAST RELIEF. ” Along the bottom, a bold dark banner carries the product name “ SERUTAN PLUS ” in large white letters.
The right-hand panel then changes from “ FAST RELIEF ” to “ GENTLE RELIEF, ” while the carton, bottle, top headline, and bottom Serutan Plus banner remain fixed in place.

% matched lemmas: 
\end{textsample}
