\begin{textsample}{NEG Dim 2 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_6.txt}  \label{ex:f2_neg_030}
The commercial is in black and white and appears to move through several \textbf{distinct} visual segments. 1. **Opening frame** : The clip begins on a very dark, nearly black image with no clearly visible objects or people. 2. **Early scene** : The next sampled frame is blurred and low to the ground.
A light-colored object or garment is visible near the upper center-left, with darker vertical shapes nearby.
The setting and action are unclear from this frame alone. 3. **Text screen** : A dark background appears with the word **“impossible? ” ** in white lowercase letters, positioned toward the right-center of the frame.
No other clear imagery is visible. 4. **Woman eating** : The commercial cuts to a close-up of a young woman seated indoors.
She has short, \textbf{curled} light hair and is looking downward toward a fork held near her mouth.
She appears to be tasting or about to taste food.
The background includes domestic-looking details such as vertical blinds or shutters. 5. **Food close-up** : A plate or shallow bowl of food is shown on a table setting.
The dish contains small mixed pieces, possibly a prepared meal.
A fork lies to the left, and other tableware is visible around the plate. 6. **Product display** : The final frame shows three cans arranged side by side on a display surface.
The cans are labeled **“GOOD MEASURE”** with a circular **“300”** marking near the top.
The visible varieties are **“NOODLES \& CHICKEN, ” “ BEEF STEW,”** and **“CHILI CON CARNE.”** Beneath the cans, text reads **“EDWARD DALTON CO.”** with smaller company text below that is partly difficult to read.

% matched lemmas: curl, distinct
\end{textsample}
