\begin{textsample}{NEG Dim 2 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_107.txt}  \label{ex:f2_neg_049}
The commercial begins with a dark/black frame, with no discernible visual content.
Around 12 seconds, the image cuts to a close view of printed product-label or packaging text.
The words “ POLYSORBATE 80 ” are clearly visible and are emphasized by a red oval/circle drawn around them.
Other surrounding text is partially visible but blurred or cut off, including fragments such as “ CHOLESTEROL ” and “ ADVICE OF A PHYSICIAN. ” A faint image of a person ’s face appears behind or under the text, suggesting a superimposed/dissolve effect.
The next shot shows a bottle of Wesson oil, labeled “ NO CHOLESTEROL ” and “ wesson, ” with “ PURE VEGETABLE OIL ” visible on the label.
The bottle is presented large in the frame, while golden fried or cooked food appears in front of it.
The image has a soft, bright, slightly overexposed look.
The sequence then dissolves into a plate of food.
A round plate is visible with several items, including a yellow ear or piece of corn and pieces of fried or cooked food.
The bottle image still appears faintly superimposed during the transition, creating a layered effect between product and meal.
Next, the commercial shows another layered dissolve : the Wesson bottle appears on the left while a woman ’s face appears behind or beside it.
Food remains faintly visible in the foreground, including what looks like a slice or piece of food being held or placed near a dish.
The visuals overlap, making some details indistinct.
The final frame resolves into a clear product-and-person shot.
A smiling blonde woman holds a glass bottle of Wesson Pure Vegetable Oil close to her face.
The label reads “ NO CHOLESTEROL, ” “ wesson, ” and “ PURE VEGETABLE OIL. ” She is facing the camera and smiling directly, with the bottle prominently displayed in the foreground.
The background is bright and softly lit.

% matched lemmas: 
\end{textsample}
