\begin{textsample}{POS Dim 5 – 2010 – Score 14.00 – 2010/tv\_com\_2010\_66.txt}  \label{ex:f5_pos_005}
The commercial opens on a static product display in a bright kitchen-like setting.
A “ NINJA COFFEE BAR ” coffee machine is centered on a counter, surrounded by a glass carafe and several cups of coffee or layered coffee drinks.
Large on-screen text reads “ NINJA COFFEE BAR, ” with smaller retailer information including “ KOHL ’S ” and “ Walmart. ” The screen then cuts briefly to black.
The next scene is in an airport terminal.
An orange promotional booth prominently displays the text “ FREE FLIGHT with 25,000* MILES. ” A woman with a shoulder bag stands at the counter \textbf{looking} down at paperwork, while a \textbf{uniformed} \textbf{staff} \textbf{member} behind the counter holds yellow caps.
The airport background includes waiting passengers, signage, and terminal architecture.
A closer view shows the same woman at the counter holding a clipboard and pen.
Yellow caps sit on the counter, and the orange “ FREE FLIGHT ” sign is visible behind her.
She \textbf{looks} toward someone off-frame.
A \textbf{man} in a dark \textbf{suit} approaches her at the counter, holding or \textbf{gesturing} with one of the yellow caps.
Behind him are \textbf{other} travelers, including a \textbf{man} in a chef ’s white \textbf{uniform} and hat, a \textbf{uniformed} airport or airline worker, and \textbf{other} people standing in line.
A wider shot shows the promotional counter with the orange “ FREE FLIGHT 25,000 MILES ” branding.
The \textbf{suited} \textbf{man} stands beside the woman, \textbf{addressing} the group visually.
Overhead airport signs point toward gates, ground transportation, and baggage claim.
Several travelers wait nearby, including the chef and a \textbf{man} holding papers.
The scene cuts to a laptop screen.
The screen shows large red text reading “ NO 25,000 MILE SEATS, ” beside an image resembling an airplane interior or seat map.
Hands are on the keyboard, and part of a person wearing headphones is visible in the foreground.
Another airport \textbf{seating} area appears.
A \textbf{man} wearing headphones sits with a laptop open in front of him.
The \textbf{suited} \textbf{man} leans in from behind his seat, \textbf{looking} at the laptop area. \textbf{Other} passengers and luggage are visible in the terminal background.
The setting changes to a newsstand or magazine \textbf{shop}.
The \textbf{suited} \textbf{man} stands near shelves filled with magazines.
He holds up a small card.
Several magazine covers and displays are visible around him, including many repeated cover images.
The \textbf{suited} \textbf{man} then walks through the airport terminal with \textbf{other} travelers behind him.
A wall directory and overhead signs for “ Baggage Claim ” and terminal \textbf{directions} are visible.
Small legal/disclaimer text appears along the bottom of the frame.
The next scene is inside an airplane cabin.
The \textbf{suited} \textbf{man} is seated among passengers and holds up a small clear plastic cup or container.
Around him, \textbf{other} passengers sit in rows : one woman \textbf{looks} down at something in her hands, a chef in white stands or leans in the aisle holding food, and another \textbf{man} in a light \textbf{shirt} holds a cup.
A close-up shows a boarding pass and a blue Capital One “ VENTURE ” card placed on top of it.
The boarding pass includes visible text such as “ FLY, ” “ www.capitalone.com, ” “ LEE M CARDHOLDER, ” and stamp-like graphics reading “ DOUBLE MILES ” and “ EVERY PURCHASE. ” The final scenes take place in an airplane cockpit.
The \textbf{suited} \textbf{man} sits in the left foreground wearing a \textbf{seatbelt}, while a \textbf{uniformed} pilot sits to the right at the controls.
On-screen branding appears : “ Capital One, ” the website “ capitalone.com, ” and the visible text “ what ’s in your wallet? ” In the last frame, the \textbf{suited} \textbf{man} has his eyes closed or partly closed, while the pilot \textbf{looks} toward him and raises a hand.

% matched lemmas: address, direction, gesture, look, man, member, other, seatbelt, seating, shirt, shop, staff, suit, uniform
\end{textsample}
