\begin{textsample}{POS Dim 5 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_22.txt}  \label{ex:f5_pos_013}
The commercial opens in a \textbf{stark} black-and-white studio space.
A casually dressed adult man with medium-length dark hair and facial hair sits facing forward in a large cushioned armchair placed on a round braided rug.
He wears a plaid robe or loose shirt, light pants, and sneakers, with his feet stretched out in front of him and his hands resting on the chair arms.
The background is otherwise empty and bright.
A small black television set appears alone against the same white background.
Its screen first shows static, then changes to a Soloflex image : the bold word “ SOLOFLEX ” above a simple drawing of the exercise machine.
A thick hand-drawn black arrow points toward the TV from the left.
The toll-free \textbf{number} “ 1-800-762-FREE ” appears in large white lettering on a black rectangular \textbf{bar} across the TV screen, then the TV fades away so the \textbf{number} remains by itself on the white background, with another black arrow pointing down toward it.
The scene changes to a close-up of a smiling female-presenting telephone operator in a headset, shown in a vintage switchboard setting.
She has styled dark hair, wears jewelry including rings, and holds one hand near her ear while the headset microphone curves toward her mouth.
Beside her, rows of switchboard plugs and jacks fill the right side of the image.
She looks engaged and pleasant, as if taking the call.
On the white background, printed Soloflex materials are displayed : a brochure or manual with a drawing of a muscular torso, and a dark videocassette or video case with a photograph of a muscular chest and the word “ SOLOFLEX ” at the top.
A black arrow points up toward these materials.
The toll-free \textbf{number} “ 1-800-762-FREE ” appears again by itself, this time with an arrow pointing in from the right.
A delivery worker in a cap and \textbf{uniform} pushes a very large cardboard shipping box on a hand truck.
The box is tilted diagonally and nearly as tall as the worker.
It is printed with “ SOLOFLEX ” and shipping markings including “ THIS SIDE UP, ” “ LAY FLAT, ” and “ DO NOT PLACE ON END. ” The worker grips the hand truck handle and smiles toward the viewer as the oversized package dominates the scene.
The Soloflex machine itself is then shown assembled on the white studio floor.
It has a vertical upright post, a curved support frame, a flat padded bench, a horizontal \textbf{bar}, and a base labeled “ SOLOFLEX. ” The design is compact and minimal, with dark metal parts standing out against the pale background.
The phone \textbf{number} reappears once more, centered on a black \textbf{bar} with an arrow pointing toward it.
A \textbf{shirtless}, athletic adult man in light shorts begins demonstrating exercises on the machine.
In a close view, he stands beside the vertical post and grips a horizontal \textbf{bar} with both hands at hip level, performing a curl-like movement as the \textbf{bar} rises toward his waist.
A drawn arrow points toward the machine ’s upright column.
His posture is controlled, and his gaze is directed downward toward the \textbf{bar}.
The exercise sequence continues with the same man lying on an angled bench, knees bent and feet braced against the machine.
With his hands near his head, he curls his upper body upward in a sit-up or abdominal crunch.
The machine ’s curved frame and upright post are visible to the side, and a black arrow points toward his bent legs and the movement area.
He then appears front-facing with a padded \textbf{bar} across the back of his shoulders, squatting on the machine platform.
His knees are bent, feet planted, and he rises through the squat with a \textbf{focused} expression.
A high-contrast silhouette follows : the man ’s body is shown in black profile against a white background, with his legs bent and supported near the machine ’s upright post.
He curls his torso upward toward his knees, emphasizing an abdominal movement.
The vertical post with a line of adjustment \textbf{holes} appears at the left, and a drawn arrow points down toward his torso and knees.
The silhouette makes the body position and movement stand out clearly.
In a low, close view from beside the bench, the \textbf{shirtless} man lies on his back and grips a \textbf{bar} above his chest for a press.
His hands hold the \textbf{bar} wide apart ; his arms bend and extend as the \textbf{bar} moves over his chest and toward his face.
The machine ’s metal frame surrounds him, and a black arrow points toward his chest and the pressing motion.
His muscles are highlighted by the black-and-white lighting.
Another silhouette exercise is shown in profile.
The man holds a handle or \textbf{bar} close to his chin with one fist while a long resistance arm angles back toward the machine on the right.
He leans back and lowers his upper body, then pulls against the resistance, the fist staying near his face as the arm and shoulder engage.
A black arrow points from the right toward the working position.
The phone \textbf{number} “ 1-800-762-FREE ” returns again on the plain white background, with an arrow pointing up toward it.
A round wall clock appears, black-rimmed with large \textbf{numbers} and hands \textbf{clustered} around 12, suggesting a short amount of time.
A hand-drawn arrow points toward the clock.
The visual shifts to a \textbf{flipping} desk calendar.
A page marked “ MONDAY 13 ” is visible in bold type, surrounded by blurred duplicate calendar pages as if time is passing quickly.
A hand turns the page, and the calendar changes to “ WEDNESDAY 15. ” The Wednesday page remains centered for several moments, then another hand turn reveals “ FRIDAY 17. ” The pages are large, with bold black \textbf{numbers} and weekday names on white paper, held on metal rings at the top.
The phone \textbf{number} appears again with an arrow pointing down to it.
A shaggy, light-colored dog sits alone on the white background, facing forward with an alert, friendly expression.
Its mouth is slightly open, and its ears hang down.
A black arrow points toward the dog ’s head, visually matching the spoken reference to how the dog looks.
A close-up of a \textbf{shirtless} torso and loose jeans follows.
The waist of the jeans appears too large, with extra space around the abdomen.
A hand pulls a belt strap across the front, showing multiple belt \textbf{holes} as it tightens the pants.
A black arrow points toward the slimmer waist area and the looseness of the jeans.
The phone \textbf{number} returns again, centered on the white background with an arrow pointing upward at it.
The athletic man reappears from the chest up, \textbf{shirtless} and sweaty, facing forward.
At first the phone \textbf{number} briefly overlays his chest, then disappears.
He throws his head back with his mouth wide open, fists clenched near his sides and chest, as if exulting after a workout.
His hair is damp and pushed back, his eyes close or squint with effort, and sweat glistens down the center of his chest.
He continues pumping his arms and holding the triumphant open-mouthed expression while a black arrow at the left points toward him.
The phone \textbf{number} “ 1-800-762-FREE ” appears once more on a black rectangular \textbf{bar} with a downward arrow above it.
The final product image returns : the Soloflex machine stands alone on the white background, with the large bold word “ SOLOFLEX ” above it and the base also labeled “ SOLOFLEX. ” The commercial ends on the phone \textbf{number} again, now surrounded by many hand-drawn black arrows from every direction, all pointing inward toward “ 1-800-762-FREE. ”

% matched lemmas: bar, cluster, flip, focused, hole, number, shirtless, stark, uniform
\end{textsample}
