\begin{textsample}{POS Dim 5 – 2020 – Score 13.00 – 2020/tv\_com\_2020\_48.txt}  \label{ex:f5_pos_034}
The commercial begins at an outdoor racquet-sport venue in bright daylight.
Several people stand near a court-side counter or bar area.
A young \textbf{man} in an orange athletic \textbf{shirt} holds dark gear, while a young woman in a burgundy-red tennis-style outfit and sunglasses stands beside him. \textbf{Other} people and umbrellas are visible in the background near fenced courts.
The next shot is a close-up of beer being poured into a tall, tilted glass.
The glass is branded “ Michelob ULTRA, ” with pale golden beer and foam forming inside.
The scene returns to the outdoor venue.
A middle-aged blonde woman and a middle-aged \textbf{man} in navy athletic jackets lean over a \textbf{table} or counter, \textbf{looking} toward someone off-camera.
Two glasses of beer are blurred in the foreground.
The pair appear \textbf{amused} and \textbf{attentive}, with the \textbf{man} slightly behind the woman.
Subsequent close-ups show them continuing to \textbf{look} off to the side, smiling or \textbf{reacting}.
The \textbf{man} and woman then appear walking near fenced courts.
The \textbf{man}, still in a navy track jacket, smiles broadly while moving forward.
The blonde woman stands farther back, holding a paddle and \textbf{watching}.
The action shifts onto a sunny outdoor court.
The young woman in the burgundy-red outfit prepares to play, holding a paddle and a yellow ball.
In a wider view, she stands with the young \textbf{man} in the orange athletic \textbf{shirt}, both holding paddles and facing the court. \textbf{Other} players are visible in the background.
The young woman then \textbf{turns} and walks near the net, her hair moving as she \textbf{looks} across the court.
The blonde woman in the white sleeveless sweater over a dark long-sleeve top appears in motion on the court, holding a paddle.
She \textbf{looks} upward and swings or moves as if tracking the ball.
Her \textbf{expression} is focused and energetic.
A cut returns to the young pair at the bar/counter area.
The young woman \textbf{looks} tired or unimpressed, leaning forward slightly, while the young \textbf{man} stands beside her in the orange \textbf{shirt}, holding his hands near his chest.
The middle-aged \textbf{man} then appears on a court in a white T-shirt, \textbf{turning} his body and extending an arm as if making or following a shot.
The setting remains outdoors, with court fencing and distant buildings visible.
The commercial then moves to a different outdoor location near the coast at sunset or golden hour.
From a distance, two people are seen on a grassy rise under a large tree.
Another shot, framed as if viewed through binoculars, shows two people seated on sand near a cooler filled with cans or bottles.
A wide aerial view shows a curved coastal court or recreation area beside the ocean, with long shadows and the sun low over the water.
A closer shot shows a \textbf{man} and a woman by the ocean holding or carrying a cooler full of colorful cans or bottles.
The woman wears a white cap and sleeveless white top ; the \textbf{man} wears a white T-shirt.
They \textbf{look} toward someone off-frame.
The action returns to racquet-sport play.
The middle-aged \textbf{man} now wears a sleeveless gray athletic top and holds a paddle overhead, preparing to hit.
A young woman with long hair in a white top and patterned skirt or shorts also swings a paddle on an outdoor court.
Another group appears wearing matching light-blue \textbf{shirts}.
A Black \textbf{man} in a blue \textbf{shirt} smiles and \textbf{gestures} with arms extended while holding a paddle.
The \textbf{shirt} has visible white text including “ PRO vs PRO, ” though the smaller text is not fully legible.
A wide shot shows him and a female teammate positioned on a court, both ready to play.
The woman in the blue \textbf{shirt} is then shown running or \textbf{turning} near the net.
The commercial shifts to a nighttime or indoor-stadium-like court with spectators.
The middle-aged \textbf{man} in the gray sleeveless top makes an intense swinging motion.
A \textbf{man} in a teal \textbf{shirt} and backward cap \textbf{looks} upward, with a large green wall behind him showing “ Michelob ULTRA ” branding.
Another shot shows the court surface and boundary line, suggesting a ball has landed near the line, though the ball is not clearly visible in that frame.
The middle-aged \textbf{man} then raises both arms in celebration while holding his paddle, with a blurred crowd cheering or \textbf{reacting} behind him.
The final scene takes place indoors in a sleek, dimly lit room resembling a lounge or retail display space.
Illuminated refrigerators line the sides, and shelves or product displays appear in the background.
A large silver trophy sits on a pedestal behind the two main \textbf{older} players.
The \textbf{man} stands holding a glass of beer ; the blonde woman sits in front of him, smiling and also holding a beer.
Small legal/disclaimer text appears along the bottom but is too small to read fully in the sampled frame.
The final frame overlays the product branding prominently in the center : “ Michelob ULTRA ” with the red vertical mark, and below it the text “ SUPERIOR LIGHT BEER. ” The \textbf{man} raises his glass slightly while the woman smiles below the logo.
The trophy and product displays remain visible in the background.

% matched lemmas: amused, attentive, expression, gesture, look, man, old, other, react, shirt, table, turn, watch
\end{textsample}
