\begin{textsample}{POS Dim 5 – 2010 – Score 13.00 – 2010/tv\_com\_2010\_40.txt}  \label{ex:f5_pos_010}
The commercial unfolds in a bright, modern living-room setting with \textbf{neutral} colors, large windows, sheer curtains, a cream sofa, glass/white furniture, and wood-framed doorways. 1. **Opening view** : The first frame is soft-focused and slightly blurred, showing an interior living space.
A pale sofa is visible in the foreground, with a doorway or open passage leading to another room in the background. 2. **Man on sofa ; woman entering foreground** : A middle-aged \textbf{man} in a light gray \textbf{shirt} and light trousers sits on a cream sofa.
He \textbf{turns} to \textbf{look} toward someone in the foreground.
A woman in white clothing is partially visible close to the camera, walking across the room or standing in front of him.
The setting remains domestic and well-lit. 3. **Woman holding a small blue item** : The woman is shown in profile, standing near tall curtains.
She wears a white blouse or light jacket and holds a small blue object or package in both hands.
She appears to be \textbf{looking} toward something off-screen to the right. 4. **Man and woman together with product box** : The \textbf{man} now stands beside the woman.
She holds a rectangular white box with visible branding.
The text “ 1800 CONTACTS ” is readable on the box.
Both \textbf{look} forward, slightly \textbf{serious} or \textbf{attentive}. 5. **Couple standing near sofa and windows** : The pair stand together in the living room.
The \textbf{man} \textbf{gestures} with one hand while the woman holds the box and a dark clipboard-like object or folder.
She faces forward, and he stands close beside her, suggesting interaction or shared attention toward something off-screen. 6. **Close-up of couple with box** : The \textbf{man} and woman are in a tighter shot.
The woman ’s hand rests on or near the \textbf{man} ’s shoulder, and the product box is held in front of them.
The visible label again reads “ 1800 CONTACTS. ” Their \textbf{expressions} appear \textbf{concerned}, earnest, or emotionally engaged. 7. **Man covering his face ; woman close beside him** : The \textbf{man} bends his head and covers part of his face with his hand.
The woman is close to him, partly out of frame, still holding the white “ 1800 CONTACTS ” box.
The posture suggests distress, embarrassment, or strong emotion, though the exact reason is not visually clear. 8. **Shift reveals another \textbf{man} in background** : As the couple move or the camera framing changes, another \textbf{man} becomes visible seated in the background.
He wears a gray \textbf{suit} with a light \textbf{shirt} and \textbf{tie}.
The first \textbf{man} remains partly in the foreground with his hand near his face, while the product box is still visible at the edge of the frame. 9. **Suited \textbf{man} with product display** : The final frame centers on the \textbf{suited} \textbf{man} seated on the sofa.
A small round \textbf{table} in front of him holds an open box labeled “ 1800 CONTACTS, ” with contact-lens-related packaging visible inside.
He faces the camera directly, composed and formal, while the living-room background remains visible behind him.

% matched lemmas: attentive, concerned, expression, gesture, look, man, neutral, serious, shirt, suit, table, tie, turn
\end{textsample}
