\begin{textsample}{POS Dim 5 – 2010 – Score 11.00 – 2010/tv\_com\_2010\_39.txt}  \label{ex:f5_pos_018}
The commercial opens with a static product shot : a yellow Old El Paso “ Hard ’ n Soft Taco Kit ” box on a tabletop, with tomatoes, a lime, and a small dish nearby.
The background is softly blurred and appears to show people in a warm, kitchen-like or dining setting.
The text “ oldelpaso.com.au ” is visible near the bottom of the product shot.
It then cuts abruptly to a washed-out, cinematic shot of a lone figure standing on top of a rocky cliff or outcrop.
The person is small in the frame, silhouetted against a pale sky.
Next, a woman in a green dress appears in a rocky or cave-like environment.
She is smiling and \textbf{looking} toward something off-frame.
A vertical pinkish light or glow is visible along the right edge of the frame.
The sequence then shows a shirtless \textbf{bearded} \textbf{man} in dark swim briefs standing upright against a plain blue-gray background, possibly sky or water.
He raises one arm straight upward, as if signaling or posing.
The commercial shifts to a dense jungle setting.
An \textbf{older} gray-haired, \textbf{bearded} \textbf{man} in a light \textbf{suit} jacket and open-collared \textbf{shirt} walks through thick vegetation.
Behind him are people with painted faces and tribal-style accessories.
The lighting is dramatic, with strong shafts of light and shadows through leaves.
A bright flare or burst of light floods the jungle frame in red and white tones, partially obscuring the \textbf{older} \textbf{man}.
The next shots show him continuing through the foliage, framed by large leaves and bamboo-like plants, with another painted person partly visible behind him.
A close-up follows of a person with red face paint, earrings, and a beaded necklace.
The person is shown in profile or three-quarter view, mouth open, reaching upward or holding onto something just outside the frame.
The setting changes to a medical or clinical environment.
A \textbf{bearded} \textbf{man} lies back while people in light-colored medical clothing gather around him.
One woman with a stethoscope smiles while \textbf{looking} toward a small white animal, possibly a dog, visible through or beyond a glass \textbf{partition}.
In a wider shot, several medical \textbf{staff} or attendants stand around the reclining \textbf{bearded} \textbf{man}, smiling or laughing.
Overhead medical lighting is visible.
The next scene shows three monkeys in a misty outdoor setting, possibly hot springs or water.
They have distinctive red or pale faces and wet-looking fur.
One appears to hold something close to its mouth, while the \textbf{others} \textbf{look} around.
The final part moves to a dark bar or lounge.
The \textbf{older} gray-haired, \textbf{bearded} \textbf{man} sits at a \textbf{table} with two women and another person partially seen at the left edge.
On the \textbf{table} are tall glasses of beer with foam, green beer bottles, and small items including a red ashtray.
The group appears to be conversing or \textbf{reacting} to one another.
Small white text appears along the bottom, but it is too small to read clearly in the frame.
A close-up then centers on a green Dos Equis beer bottle on a coaster, with a tall glass of beer beside it and the red ashtray in the background.
The bottle label is visible, showing the Dos Equis branding with two red X marks.
The commercial ends with a portrait-style shot of the \textbf{older} \textbf{bearded} \textbf{man} against a dark background.
To his left is the Dos Equis logo and text reading “ CERVEZA XX DOS EQUIS, ” with the slogan “ STAY THIRSTY, my friends ” below it.
Additional small text appears near the bottom, including a responsible drinking message, though it is partially difficult to read.

% matched lemmas: bearded, look, man, old, other, partition, react, shirt, staff, suit, table
\end{textsample}
