\begin{textsample}{POS Dim 5 – 1960 – Score 8.00 – 1960/tv\_com\_1960\_4.txt}  \label{ex:f5_pos_060}
The commercial is presented in warm reddish/orange-tinted vintage footage, with a “ Nostalgic X’er ” watermark visible at the lower right in most frames. 1. **Opening street scene:** The commercial begins outside a row of public telephone booths marked “ TELEPHONE. ” A \textbf{man} in a dark \textbf{suit} and hat stands with his back to the camera, facing one of the booths. \textbf{Older} cars are parked in the foreground on both sides of the frame. 2. **Close-up, unclear movement:** The image cuts to a very close, partially obscured shot of fabric or clothing moving past the camera.
The details are indistinct, but the reddish lighting continues. 3. **Audience or seated group:** A dimly lit shot shows several people seated in rows, likely in an auditorium, theater, or similar public space.
Their faces are mostly in shadow, with bright rim lighting around heads and shoulders. 4. **Close-up of interior objects:** A close-up shows part of an interior setting with a chair-like structure or angled support and a small block-like base.
The exact location and object are unclear from the sampled frame. 5. **Train or bus interior:** A woman in a light-colored hat and \textbf{coat} sits in a cushioned seat beside another passenger.
She appears relaxed or drowsy, leaning back.
A window behind her glows with bright exterior light, suggesting travel. 6. **Bathroom or domestic interior:** A striped towel hangs on a rack near a wall or door.
The shot is static and domestic-looking, possibly a bathroom or wash area. 7. **Street/parking scene:** The commercial returns to an outdoor urban setting.
A \textbf{man} stands between parked cars, one dark car on the left and a pale car on the right.
He appears to be moving or \textbf{gesturing} near the cars. 8. **Obscured transition:** A dark figure or object passes very close in front of the camera, blocking much of the view.
The pale car remains partially visible on the right. 9. **People entering through doorway:** A woman in a red or dark \textbf{coat} with a light \textbf{collar} stands or steps through a doorway, facing forward.
Behind her are \textbf{other} people, including a \textbf{man} in a hat.
Another person is partly visible at the right edge, \textbf{turned} away. 10. **Product close-up:** A close-up of a bottle or container label appears.
The label prominently reads “ Sucaryl, ” with small icons beneath the name that resemble food or drink items. 11. **Product beside cup:** A tall, tapered bottle labeled “ Sucar … ” stands on the left beside a cup or mug filled with a dark liquid.
A hand at the right holds a small item or utensil near the cup, suggesting preparation or sweetening, though the exact action is not fully visible. 12. **Final product/title frame:** The bottle remains on the left against a plain warm background.
Large text appears on the right reading “ Sucaryl, ” with smaller text underneath that reads “ SWEETENER. ” The bottom of a cup or saucer is partly visible near the lower edge.

% matched lemmas: coat, collar, gesture, man, old, other, suit, turn
\end{textsample}
