\begin{textsample}{POS Dim 5 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_76.txt}  \label{ex:f5_pos_036}
A clean white background fills the screen, with black borders at the sides.
Centered on it is the word “ SONY ” in large, deep red capital letters.
The letters grow larger until only part of the word is visible, then the view moves into the red “ O, ” which fills the screen like a thick red ring.
The ring breaks down into an arrangement of red dots on white.
The dots vary in size and form a compact, stepped block, like a stylized pattern or digital symbol.
A white grid appears over the dots, then the background changes to a cool blue city scene with dark building silhouettes.
The red dots disappear, leaving a \textbf{glowing} white square grid hovering in front of the dusky urban skyline.
The grid brightens and begins to take on depth, \textbf{transforming} from a flat square into a luminous three-dimensional cube.
The cube \textbf{floats} in midair among the shadowy skyscrapers, its edges and internal divisions outlined in bright blue-white light.
It rotates and tilts, sometimes appearing as a flat diamond shape, sometimes as a full cube with multiple gridded faces visible.
A sweeping, curved band of light, at moments red and later green or blue-green, arcs around it like an orbiting ribbon.
The band passes in front of and behind the \textbf{glowing} cube, making the cube seem \textbf{suspended} in a stylized, futuristic space above the city.
The cube continues to rotate and glow more intensely.
Its white grid lines flare against the deep blue background, while dark building shapes remain behind it.
The cube grows larger until its corner and gridded faces dominate the view.
The square divisions stretch across the sides, creating the impression of a precise engineering diagram or a wireframe structure.
As it comes closer, the top edge becomes a bright horizontal band, and the cube begins to feel less like a simple block and more like an object being examined from inside and out.
The gridded cube then changes into a more open wireframe form.
Its faces separate and slide apart, leaving \textbf{glowing} outlines of rectangular panels and boxes against a dark blue-black background.
The shapes look like parts of a television cabinet or screen housing being constructed in space.
Rectangular frames rotate and align ; one large box-like outline sits forward, with smaller rectangular forms moving toward it.
The lines are bright electric blue-white, with a halo of light around them.
Pieces appear to assemble around a central rectangular opening, suggesting the body of a television set forming from individual panels.
More components move into position.
A larger rectangular frame stands upright, with a hollow center like a screen.
Smaller block-like wireframe parts approach from the side and below, then align with the main body.
The structure becomes brighter and more solid-looking as the \textbf{glowing} outlines overlap.
The shape resolves into a boxy television-like form, with a prominent front opening and a base or lower support.
The interior recedes into nested \textbf{glowing} rectangles, as if looking through the front of the set into its depth.
The glow intensifies until the screen area becomes a rounded bright white square, nearly filling the view.
Below the bright square, a row of vertical black-and-white \textbf{bars} appears along the bottom edge, like a striped platform or graphic base.
The brilliant white screen fades into a real television set : a black Sony Trinitron-style CRT television sits centered on a low stand.
Its screen shows the earlier blue city scene with dark buildings and a pale sky, connecting the abstract \textbf{glowing} imagery to the television display.
Beneath the set is a rectangular stand or component shelf in beige and dark tones, and the black-and-white vertical stripes remain in the foreground as a bold graphic element.
The surrounding space is dark, making the television and its screen the focus.
The commercial ends with a graphic brand display.
Against a black background, the word “ SONY ” appears again, now in large metallic, silver-white capital letters with dark shading inside the strokes.
Behind the letters, broad beams and fan-like ribbons of \textbf{color} \textbf{radiate} and overlap : blue, green, red, yellow, white, and orange.
The \textbf{colored} light shapes shift behind the word, forming a prism-like burst.
As the sequence progresses, the letters remain prominent while the \textbf{colored} beams slide and fan outward, and the visible portion of the word narrows until a large “ S ” dominates the center, still backed by the vivid rainbow-like light rays.

% matched lemmas: bar, color, float, glowing, radiate, suspend, transform
\end{textsample}
