\begin{textsample}{POS Dim 5 – 2010 – Score 17.00 – 2010/tv\_com\_2010\_14.txt}  \label{ex:f5_pos_004}
The commercial takes place in a very bright, futuristic cafeteria or office dining area with white furniture, glass or translucent blue wall panels, and a luminous grid-like ceiling.
Many people wear office-style clothing and ID badges ; several badges and the background show Intel branding.
At the beginning, three \textbf{men} sit at a white cafeteria \textbf{table} eating and drinking from translucent blue cups.
One \textbf{man} in a lavender \textbf{shirt} and \textbf{tie}, wearing glasses, sits between a \textbf{man} in a gray \textbf{shirt} and a \textbf{man} in a light blue lab \textbf{coat}.
Plates with sandwiches, \textbf{chips}, fruit, and cups are visible on the \textbf{table}. \textbf{Other} workers sit and move in the background.
The camera then focuses on the \textbf{man} in the lavender \textbf{shirt}.
He holds a blue cup and raises his \textbf{other} hand slightly, \textbf{looking} off to the side with a startled or \textbf{uncertain} \textbf{expression}.
Behind him, people continue eating at \textbf{tables}.
Next, the \textbf{man} in the gray \textbf{shirt} is shown in closer view holding a sandwich.
A woman standing behind him carries a white tray with a white cup.
She wears an Intel ID badge.
The \textbf{man} \textbf{looks} upward or to the side, as if \textbf{reacting} to someone nearby.
The scene \textbf{widens} again to show the gray-shirted \textbf{man} and the lavender-shirted \textbf{man} at the \textbf{table}.
A small white robot with a rounded body, black face screen, and glowing blue circular “ eyes ” is visible behind or beside them.
The robot ’s face is glossy and reflective.
The \textbf{men} appear to be \textbf{looking} around and \textbf{reacting} to the robot ’s presence.
A cut shows the \textbf{man} in the light blue lab \textbf{coat} seated at the same \textbf{table}.
He also wears an Intel badge.
A vending machine or illuminated cabinet is visible in the background, along with people at another \textbf{table}.
He \textbf{looks} toward the \textbf{others}, with a \textbf{neutral} or slightly \textbf{concerned} \textbf{expression}.
The camera returns to the gray-shirted \textbf{man} and lavender-shirted \textbf{man}.
The lavender-shirted \textbf{man} smiles broadly while holding his cup ; the robot remains behind them, its blue eyes visible.
The woman with the tray stands nearby.
A close-up then centers on the robot ’s face.
Its black, reflective face panel shows bright blue eye-like lights and reflections of the cafeteria scene, including people at the \textbf{table}.
The robot ’s design is rounded, white, and glossy, with a compact body.
The next shot shows the robot more fully.
It appears to have small arms and a tray or platform in front of it holding food, including what \textbf{looks} like strips of bacon or similar items, and a blue cup on the \textbf{table} in front.
People around it continue eating.
The robot faces forward between \textbf{diners}.
The robot is then shown lower between the seated people while the \textbf{man} in the lavender \textbf{shirt} \textbf{turns} away laughing or \textbf{speaking} with an open-mouthed smile.
The gray-shirted \textbf{man} \textbf{looks} down at his food.
The woman with the tray remains behind them.
A later shot shows the robot from behind or side as it moves away across the white floor.
Its body has rounded white panels and a glowing blue element on its torso.
Nearby, people sit in white chairs and walk through the cafeteria.
The scene returns to the \textbf{table} with the three \textbf{men} and the woman holding the tray.
The lavender-shirted \textbf{man} holds his cup, the gray-shirted \textbf{man} \textbf{looks} down at his sandwich, and the \textbf{man} in the blue lab \textbf{coat} \textbf{looks} forward.
The \textbf{table} remains covered with plates, cups, and food.
The final portion shifts to a blue screen or blue-tinted transition.
The last frame shows the Intel logo centered over a faint, blue-tinted background of people in a cafeteria or office setting.
Beneath the logo, readable text says : “ Sponsors of Tomorrow. ”

% matched lemmas: chip, coat, concerned, diner, expression, look, man, neutral, other, react, shirt, speak, table, tie, turn, uncertain, widen
\end{textsample}
