\begin{textsample}{POS Dim 5 – 1980 – Score 10.00 – 1980/tv\_com\_1980\_72.txt}  \label{ex:f5_pos_066}
The commercial opens with a very dark, low-contrast shot.
A person is seen from behind or in silhouette in an interior space, but the setting and details are difficult to make out.
The scene then cuts to a brighter office-like interior with warm-toned walls and horizontal blinds.
A woman with short dark curly hair, wearing a light-colored blazer and a white blouse or scarf, leans forward beside a desk or \textbf{partition}.
A framed picture/poster is visible on the wall behind her.
She appears to be \textbf{looking} toward someone off-camera.
The next shot shows an \textbf{older} \textbf{bald} \textbf{man} wearing large glasses, a dark \textbf{suit}, white \textbf{shirt}, and \textbf{tie}.
He is framed in close-up against a light wall with framed items behind him.
The commercial cuts back to the woman in close-up, still leaning forward and \textbf{looking} \textbf{attentive}.
A following shot shows the \textbf{older} \textbf{man} moving or \textbf{turning} near a doorway or \textbf{partition}, partly seen from behind/side.
The setting still appears to be an office.
The focus then shifts to a small portable computer on a desk.
It has a compact keyboard, a wide display area above the keys, and a Radio Shack-style product label on or near it ; some of the small label text is not fully readable in the frame.
A hand reaches toward or steadies the device.
Office objects surround it, including papers, folders, and a small potted plant.
A later close-up shows hands typing on the compact computer ’s keyboard.
The display screen is visible above the keys, though the screen content is not legible in the sampled frame.
A pair of glasses or a dark cable-like object lies nearby on the desk.
The commercial then presents the portable computer against a dark background like a product display.
Large white text appears below it : “ From \$799. ” Under that, a higher price, apparently “ \$1,099. ”, is shown crossed out.
Near the end, the layout changes to a black background with an inset image of the \textbf{older} \textbf{man} seated at a desk, holding and reading papers.
Office equipment, including a monitor or computer terminal, is visible behind him.
Large on-screen text appears below the inset image : “ RadioShack ” in red, followed by “ Model 100 now on sale ” in white.
The final frame holds the same end-card arrangement : the \textbf{older} \textbf{man} in the inset office scene above, with the text “ RadioShack Model 100 now on sale ” below.

% matched lemmas: attentive, bald, look, man, old, partition, shirt, suit, tie, turn
\end{textsample}
