\begin{textsample}{POS Dim 5 – 1960 – Score 13.00 – 1960/tv\_com\_1960\_57.txt}  \label{ex:f5_pos_053}
The commercial opens with a very dark or black frame ; no visual content is discernible.
It then cuts to a tight close-up of three adult \textbf{men} in \textbf{suits} leaning in toward one another.
The \textbf{man} in the center wears a tan/brown jacket and \textbf{looks} forward with a \textbf{serious} \textbf{expression}, while the two \textbf{men} on either side face inward toward him.
The framing is close and crowded, emphasizing their faces.
The next shots focus on a foot wearing a dark, likely black, sock.
The socked foot is extended horizontally, and another person ’s hands and trousered leg are visible nearby.
The setting appears to be a bright white studio space with a reflective glass surface or \textbf{table}.
A close-up follows of one \textbf{man} in a dark \textbf{suit}, white \textbf{shirt}, and \textbf{tie}.
He rests his fingers against his mouth or chin, appearing to study something off-screen with a thoughtful or \textbf{concerned} \textbf{expression}.
The camera returns to the socked foot.
A \textbf{man} in a \textbf{tan} \textbf{suit} reaches toward or holds the lower leg/ankle area near the sock.
The foot rests on or just above a glass tabletop, which reflects the foot and hands.
The tan-suited \textbf{man} ’s red \textbf{tie} is visible.
Another close-up shows a different \textbf{man} in a dark \textbf{suit} wearing dark-rimmed glasses.
He faces left, appearing to \textbf{speak} or \textbf{react}, though no audio is available.
His \textbf{expression} is \textbf{attentive} and somewhat animated.
The camera briefly moves very close past the \textbf{man} with glasses, with part of his face and eyeglasses filling the foreground while another \textbf{man} bends or leans behind him.
The image is partially obscured by the extreme proximity.
A low-angle shot then shows the black-socked foot looming large across the upper part of the frame, with the tan-suited \textbf{man} seen below \textbf{looking} upward.
The white studio background remains plain and minimal.
A wide overhead or high-angle shot reveals the full arrangement : a glass \textbf{table} in the center, black modern chairs on both sides, and several \textbf{men} gathered around it.
One \textbf{man} in a \textbf{tan} \textbf{suit} stands on or at the center of the glass \textbf{table}, while two \textbf{men} in dark \textbf{suits} sit on either side.
A dark object, possibly a shoe, lies on the floor to the right.
The space is stark white with a rectangular rug or platform beneath the \textbf{table} and chairs.
In the final frame, the tan-suited \textbf{man} stands with his arms spread outward above the seated \textbf{men}, facing the camera.
Large white text appears over the scene.
The visible text reads : “ Stand-Up Socks!
By Hanes Plus 4 ” and below it “ Of Ban-Lon Caprolan nylon by Allied Chemical, ” though some wording is slightly blurred.
The visual emphasis throughout is on the dark socked foot and the \textbf{men} examining or \textbf{reacting} to it in a minimalist studio setting.

% matched lemmas: attentive, concerned, expression, look, man, react, serious, shirt, speak, suit, table, tan, tie
\end{textsample}
