\begin{textsample}{POS Dim 5 – 2000 – Score 10.00 – 2000/tv\_com\_2000\_4.txt}  \label{ex:f5_pos_028}
The commercial begins on a nearly black frame with a small red heart-shaped channel/logo watermark in the lower-right corner.
A graphic image then appears showing a stylized beer label or sign.
The visible text includes “ ROLLING ROCK ” and “ Extra Pale, ” with a horse-head emblem.
The image has a striped, high-contrast, slightly distorted \textbf{look}, as if seen through scan lines or a graphic transition.
The scene changes to a dimly lit bar or pool hall.
A young adult \textbf{man} with light hair, wearing a pale short-sleeved \textbf{shirt} over a white T-shirt, \textbf{looks} upward toward someone standing close to him.
Warm string lights and blurred bar activity are visible in the background.
A wider view shows a pool \textbf{table} in the foreground with billiard balls spread across the green felt.
Several young adults are gathered around the \textbf{table}.
A woman in an orange sleeveless top stands to the left with a pool cue.
Near the center, the light-haired \textbf{man} stands beside a blonde woman in a black strapless top and light skirt. \textbf{Other} patrons are visible around the bar and pool area.
The \textbf{man} is then shown from behind as he approaches or stands close to the blonde woman.
Her face is partly visible beyond his shoulder.
Another shot shows three people near the pool \textbf{table} : the woman in the orange top holding a cue on the left, the blonde woman in the black top in the center with her back partly \textbf{turned}, and the light-haired \textbf{man} on the right holding green beer bottles.
The group appears to be interacting casually in the bar environment.
A wider shot from across a \textbf{table} shows the same pool hall scene.
The \textbf{man} and blonde woman stand near the pool \textbf{table} while \textbf{other} people sit or stand around them.
Green bottles are visible on a nearby \textbf{table} in the foreground.
The setting includes warm lighting, dark wood tones, and bar/pool-room décor.
A closer shot frames the \textbf{man} and blonde woman facing one another near the pool \textbf{table}.
He holds a green bottle, and she holds a small object in one hand, possibly related to the pool game, though it is not clearly identifiable.
Their facial \textbf{expressions} appear \textbf{attentive} or conversational.
The next shot is a close-up of hands and torsos around drinks.
The light-haired \textbf{man} ’s arm moves near two green bottles.
A woman in a reddish or pink top is in the background.
The bottles have white labels, but the label text is not fully readable in this frame.
The \textbf{man} is then shown frontally, holding two green bottles with white labels.
He \textbf{looks} downward at them.
Small white copyright text appears across the lower portion of the frame ; it is partially legible and includes “ {\EmojiFont ©} 2000 … Brewing Co., Latrobe, PA. ” A cutaway shows three young adult \textbf{men} seated at a \textbf{table}, smiling and \textbf{looking} toward the action off-camera.
They have green beer bottles in front of them, and one \textbf{gestures} with his hand.
The same small white copyright line remains near the bottom.
The light-haired \textbf{man} appears again in a medium close-up, facing forward with a \textbf{neutral} or slightly resigned \textbf{expression}.
A green bottle is partly visible at the bottom edge.
The bar background remains softly lit and out of focus, with the copyright text still faintly visible near the bottom.
The commercial then transitions back to a green-toned branded graphic.
A horse-head emblem appears above large white text reading “ KEEP ON ROCKIN ’. ” The background \textbf{looks} like glass or liquid texture, matching the beer branding style.
The final frame is a close-up of a green glass beer bottle covered with condensation.
The label is clearly visible and reads “ ROLLING ROCK ” and “ Extra Pale, ” with the horse-head emblem and decorative label details.
The red heart-shaped watermark remains at the lower-right corner.

% matched lemmas: attentive, expression, gesture, look, man, neutral, other, shirt, table, turn
\end{textsample}
