\begin{textsample}{POS Dim 5 – 1970 – Score 7.00 – 1970/tv\_com\_1970\_87.txt}  \label{ex:f5_pos_082}
The commercial begins in a dimly lit indoor basketball \textbf{arena}, with the polished wooden court reflecting bright overhead lights.
Several adult male basketball \textbf{players} crowd together low to the floor.
A muscular Black \textbf{player} in a white sleeveless \textbf{uniform} is crouched in a dribbling stance, moving the basketball close to the ground while defenders in green \textbf{jerseys} and shorts close in around him.
The \textbf{players} ’ legs, socks, and sneakers dominate the view : the white-uniformed \textbf{player} wears white high-top sneakers and white socks with red and dark stripes near the top, while the defenders wear darker sneakers and green-and-white socks.
The white-uniformed \textbf{player} keeps the ball low and shifts his weight from side to side.
His \textbf{jersey} front clearly reads “ PRO-Keds, ” making the shirt itself part of the product imagery.
He looks focused, leaning forward with bent knees and strong arms, while green-uniformed defenders reach and step in around him.
The back of his \textbf{jersey} shows the \textbf{number} 10, with a name above it that appears to read “ WHITE. ” One defender in green, with the \textbf{number} 12 on his back, stays close to him ; another, \textbf{number} 44, moves into the lane ahead.
Hands reach in, bodies brush together, and the white-uniformed \textbf{player} works through the pressure with the ball.
The action concentrates on his feet as he dribbles and cuts.
His white Pro-Keds sneakers slide, pivot, and push off the glossy court near a red painted area.
The ball bounces beside his ankles, blurred by motion, while the shoes grip and turn.
The \textbf{player} ’s feet plant, roll, and spring, suggesting quick changes of direction.
The defenders ’ legs pass in and out of view, but the white sneakers remain the visual focus, repeatedly shown under strain as he accelerates and maneuvers.
The \textbf{player} drives into a crowd of defenders.
Green \textbf{jerseys} with large black \textbf{numbers} fill the foreground and sides, while his white “ PRO-Keds ” \textbf{jersey} \textbf{flashes} between them.
Arms lift and reach ; the defenders appear to challenge his path.
The white-uniformed \textbf{player} rises through the \textbf{cluster}, still framed as the central figure, his body angled upward as if beginning a jump toward the basket.
The commercial then shifts into a more stylized product display.
A single white high-top sneaker is isolated against a dark background and a glossy red court surface.
The shoe lifts from the floor, toe first, with bright vertical reflections glowing beneath it.
The laces and smooth white upper are visible, and the sole has a darker section near the bottom.
The foot continues upward until the sneaker appears \textbf{suspended} in the air.
Both feet are then shown together, white high-tops hanging above bright light flares against a black background, emphasizing the shoes while the rest of the body is mostly out of view.
A basketball hoop appears next, seen against darkness with a bright light shining behind it.
The white net hangs below the metal rim.
The \textbf{player} ’s white sneakers and striped socks descend around the rim and net in a stylized dunking sequence.
The net stretches and twists as his legs and body pass near it, and the \textbf{number} 10 on the back of his white \textbf{jersey} is briefly visible behind the rim.
The net billows and tangles around the motion, then a basketball drops through the hoop.
The ball pushes the white net downward, then falls out of view, leaving the net swinging and settling beneath the rim.
The focus returns to the shoes landing.
Against the glossy red court, the white sneakers descend slowly from above.
First the toes hover just above the floor, then the front edges touch down lightly.
The shoes continue to lower, rolling from the toes toward the soles.
The white uppers, laces, grey-white socks, and a dark stripe-like detail near the sole are clearly visible.
The landing is gentle and controlled : the toes make contact, the soles compress slightly, and both shoes come to rest flat on the court, reinforcing the visual idea of a soft return to the floor after a jump.
The commercial ends on a black background with a large “ PRO-Keds ” logo in bold blue letters outlined in white, with a red block behind the beginning of the word.
Beneath the logo is a small white sneaker graphic.
Below that, in large white text, the slogan reads : “ When we let you down, we let you down easy. ”

% matched lemmas: arena, cluster, flash, jersey, number, player, suspend, uniform
\end{textsample}
