\begin{textsample}{POS Dim 5 – 2020 – Score 10.00 – 2020/tv\_com\_2020\_77.txt}  \label{ex:f5_pos_039}
The commercial begins in a stylized desert/western landscape.
Wide shots show sandy ground with scrubby bushes, mesas, and a bright blue sky with scattered clouds.
A rider on a white horse moves through the scene, dressed in cowboy-style clothing with a wide-brimmed hat.
The sequence then cuts closer to the rider : a woman in a white western \textbf{shirt}, brown cowboy hat, yellow neck scarf, and leather/fringe accents sits on the white horse.
A black bird, resembling a crow or raven, is visible on the ground nearby.
The bird is then shown in close-up standing on the sand, \textbf{looking} upward.
A subsequent close-up shows a small object partly buried in the sand, like a ring or cap, with the visible text “ price ” on it ; the black bird ’s beak or head is near the object.
The rider is next shown in medium close-up holding an acoustic guitar while seated on the horse.
Her western outfit remains prominent : brown hat, yellow scarf, white \textbf{shirt}, and guitar across her body.
A small prairie-dog-like animal wearing a yellow bandana appears perched near her shoulder in a close shot, visually matching the yellow scarf worn by the rider.
The setting then abruptly changes from the desert to the inside of a modern pharmacy or clinic-like retail space.
Shelves filled with bottles and boxes line the room.
A \textbf{man} in a cap stands browsing products.
In the background, the white horse and rider are visible entering or present inside the pharmacy area, creating a contrast between western imagery and the contemporary store environment.
A close shot shows an \textbf{older} \textbf{man} with glasses and a \textbf{mustache} \textbf{looking} toward the rider from behind shelves stocked with medical or health products.
Some product labels are visible but not fully central ; the pharmacy context is visually clear.
The rider appears again indoors, smiling and holding up a bright yellow smartphone.
The phone screen displays the word “ GoodRx ” in dark text.
The scene then focuses on \textbf{other} pharmacy customers and \textbf{staff}.
A woman with a large orange tote bag walks to the counter. \textbf{Other} people wait nearby, including a \textbf{man} with a \textbf{beard} and a sling on one arm and several pharmacy \textbf{employees} in white \textbf{coats}.
The rider remains mounted on the white horse inside the pharmacy, waiting behind queue stanchions.
Store shelving and a pharmacy counter are visible, with “ www.goodrx.com ” faintly readable on signage above the counter area.
The rider is shown seated on the horse at the counter, facing a pharmacy worker or customer off-frame.
The prairie-dog-like animal with the yellow bandana reappears in a close-up beside the rider ’s shoulder.
The commercial then cuts to a receipt or label printer on a pharmacy counter.
Initially, the device has two red indicator lights and a strip of paper feeding out.
After a cut back to the pharmacy counter area, the printer is shown again with two green indicator lights while paper continues to feed out, suggesting a successful or improved transaction visually, though no audio or dialogue is available to confirm this.
Near the end, the rider sits on the white horse beside the woman with the orange tote bag, who appears to be smiling while \textbf{looking} downward, possibly at a phone or receipt.
The rider holds the yellow phone and \textbf{looks} pleased.
The final sequence shifts to a solid bright yellow background.
A small figure briefly rises at the bottom edge, then the screen resolves into a clean end card.
Large black text reads “ GoodRx. ” Beneath it, smaller text reads “ Save time and money on prescriptions. ” A white rounded button appears below with the words “ CHECK GOODRX. ”

% matched lemmas: beard, coat, employee, look, man, mustache, old, other, shirt, staff
\end{textsample}
