\begin{textsample}{POS Dim 5 – 2010 – Score 9.00 – 2010/tv\_com\_2010\_51.txt}  \label{ex:f5_pos_046}
A woman stands facing forward in a warm, wood-toned room, framed by shelves holding decorative objects.
She appears to be presenting at a table covered with food items : a cake stand with small treats, a bowl of red fruit, green leafy vegetables, eggs in blue holders, carrots, and a covered silver dish.
She wears a buttoned purple blouse with a tied waist and holds a small round object in one hand, looking directly ahead with a surprised or emphatic expression.
The scene moves to a bright, busy airport terminal.
A young woman with light skin, long brown hair and straight bangs walks through the concourse while holding a dark smartphone to her ear.
She wears a pale pink trench coat over a white shirt with a red collar detail, black trousers, and carries a shoulder bag.
Around her, travelers with backpacks and rolling luggage move between blue queue barriers, while \textbf{uniformed} airline staff stand in the background.
She looks upward with concern, as if checking information above her.
A flight information board fills the view.
Rows of flight \textbf{numbers} appear on the left, gate \textbf{numbers} on the right, and status words in the middle.
Some rows first read “ ON TIME ” in green, while others read “ DELAYED ” in red ; then more rows change to red “ DELAYED, ” creating a screen full of delays.
Back in the terminal, the woman lowers her gaze, looking frustrated or resigned.
Nearby, a \textbf{cluster} of travelers crowd around a round charging station.
Several people stand close together, each focused on a phone, with charging cables plugged into a central column.
Suitcases sit at their feet, and the available outlets appear occupied.
The woman in the pink coat stands off to the side holding her phone, watching the \textbf{crowded} charging area.
Fine-print legal text appears along the bottom of the screen.
She looks down at her own phone.
A close view of the screen shows the battery settings page with “ BATTERY ” at the top and a large circular indicator reading “ 72 \%. ” The top status \textbf{bar} shows “ 4G ” and the time “ 3:45 PM. ” The words “ Estimated battery life ” and a “ BATTERY USAGE ” button are visible.
The woman ’s expression softens ; white text appears over her in the airport reading “ All day battery. ” She smiles, lifts the phone back to her ear, and continues walking through the terminal, no longer needing the \textbf{crowded} charging station.
A Samsung phone is then shown lying horizontally on a white surface in a blue case or cover, with its screen glowing in a blue-to-orange gradient and app icons along one side.
A hand reaches to the right edge and pulls out the slim yellow S Pen.
The setting changes to a very bright, modern white room with tall windows and a long table.
The phone sits propped up on the table in the foreground, facing a group at the far end.
Two women stand together first, smiling toward the phone, then a larger mixed group of adults gathers behind them, posing closely like for a group photo.
The group fills the view, smiling at the phone.
They include people of different appearances and styles : a woman with short dark hair in a rust-colored top, a red-haired woman in a light blue blouse, a bearded man in a black shirt, people wearing glasses, and others standing shoulder to shoulder.
A hand holds the yellow S Pen, with a small dark button visible near the end, suggesting it is being used as a remote.
The phone ’s screen displays the group photo, and large white text across it reads “ S Pen with remote control. ” The commercial shifts to a spacious design studio or office with glass walls, large windows, white tables, desk lamps, and many small toy-like figures arranged around the workspace.
Two men work at a table : one, a Black man with short curly hair and a beard wearing a light shirt, leans in with a Samsung phone ; another man nearby helps position a small white figurine.
The figurine resembles a rabbit-like \textbf{character} with long white ears, a white body, and a shiny reflective silver head.
The bearded man holds the phone horizontally and frames the figurine on the camera screen.
On the phone display, the white rabbit figure stands centered on a round platform, while a hand adjusts something beside it.
The camera interface is visible, including a small count \textbf{number} on the right.
The phone captures many variations : the view becomes a grid of photos showing the same rabbit figure in different angles and positions, with rows and rows of thumbnails multiplying across the screen.
The bearded man leans over the device with \textbf{intense} focus, while another light-skinned man in a blue-gray shirt comes in close behind him, also looking at the screen.
Their expressions are concentrated and slightly \textbf{anxious}, as if checking whether they have enough images.
In a wider view, the tabletop is crowded with colorful small figures in the foreground, while the two men sit or kneel at the table.
One of them turns his head back toward the camera with a surprised look.
More tiny figures, lamps, and the white rabbit model are visible around the studio.
A close view of the phone shows a gallery packed with dense rows of image thumbnails.
A finger swipes through the \textbf{huge} collection.
White text over the phone reads “ 1 terabyte ready. ” The gallery continues scrolling, suggesting a very large \textbf{number} of stored photos.
In a wider, dimmer view of the studio, the two men move around the workspace among tables and lamps, and the text expands to read “ 1 terabyte ready with expandable memory. ” Fine-print legal text remains along the bottom.
The final product display appears on a solid bright blue background.
A blue Samsung Galaxy Note9 is shown from the back, with its rear camera area and “ Samsung ” branding faintly visible.
The yellow S Pen lies diagonally across the phone, its button facing outward.
Large white text at the bottom reads, “ The new super powerful Note, ” with small Samsung copyright text in the lower corner.

% matched lemmas: anxious, bar, character, cluster, crowded, huge, intense, number, uniform
\end{textsample}
