\begin{textsample}{POS Dim 5 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_38.txt}  \label{ex:f5_pos_015}
In bright outdoor light on a sports field, teenage boys play a rough flag-football-style \textbf{game} in front of empty metal bleachers and trees.
A brown-haired teen in a white \textbf{jersey} with blue stripes and the large \textbf{number} 21 reaches up and catches the \textbf{football} while other boys in purple and white \textbf{jerseys} crowd around him.
He runs with the ball, but a boy in a purple \textbf{jersey}, \textbf{number} 85, closes in.
The play becomes a blur of motion as the boy in white is taken down, sliding onto the green grass.
Only legs, shoes, and the edge of his white \textbf{uniform} are visible as he lands on the turf.
The scene shifts to a locker room with gray lockers, hanging lights, and several teenage boys changing clothes in the background.
From the \textbf{viewpoint} of an open laundry bin or chute, a \textbf{shirtless} teen with wet, tousled hair stands in front holding a bundled white garment.
He grins and tosses clothing forward into the opening.
Other boys in athletic shorts move around behind him.
The white \textbf{jersey} with blue stripes and the \textbf{number} 21 appears among the clothes being handled, suggesting it is the shirt from the field.
Back outside, the same teen in the white \textbf{number} 21 \textbf{jersey} presses the fabric up over his nose and face.
In close view, he holds the shirt against his face as if smelling or wiping with it.
His dark hair falls over his forehead, and the white fabric covers most of his face.
The \textbf{jersey} is no longer crisp ; it looks worn and dirty, with smudges and grass-colored stains.
Back in the locker room, another \textbf{shirtless} teenage boy with curly hair brings a bulky pile of clothes toward the same open laundry bin.
He pushes the bundle forward, and the \textbf{number} 21 \textbf{jersey} lies prominently at the front, its blue \textbf{number} visible amid the white fabric.
The boy looks down at the shirt as it rests near the opening, while other teammates move in the background among the lockers.
The \textbf{game} continues outdoors.
The \textbf{number} 21 \textbf{player} reaches up alongside another boy in a white \textbf{jersey} \textbf{numbered} 61 as both stretch for the \textbf{football}.
Arms are extended high, and other \textbf{players} watch from nearby.
The ball passes through the group, and the \textbf{number} 21 \textbf{player} turns afterward, smiling.
His \textbf{jersey} front is visibly stained and dingy, with patches of dirt around the chest and \textbf{number}.
Indoors again, a teenage boy wearing a maroon overshirt over a white T-shirt stands by a red duffel bag.
He holds the dirty white \textbf{number} 21 \textbf{jersey}, folds or bunches it, and places it into the bright red bag.
In close view, the \textbf{jersey} lands inside the open duffel ; hands press it down and zip or close the bag around it.
In a laundry area at home, a woman with shoulder-length brown hair, wearing a dark plaid shirt tucked into jeans, pulls the \textbf{number} 21 \textbf{jersey} from the red duffel.
A man stands just behind her, watching.
The \textbf{jersey} is held up between them ; the blue \textbf{number} 21 is large on the front, and the white fabric is heavily marked with \textbf{yellow-green} dirt and grass stains, especially around the chest and underarm areas.
The woman examines the fabric closely, pinching and lifting sections, while the man peers over her shoulder with a concerned look.
On a shelf beside them sits an orange box of Tide with Bleach, its large white “ Tide ” logo visible against a sunburst background.
The woman lowers the dirty \textbf{jersey} back toward the laundry and reaches up toward the shelf.
The Tide with Bleach box is then shown close up : an orange package with a bright yellow sunburst pattern, the large white and blue “ Tide ” name, and the words “ with BLEACH ” printed beneath it.
A hand brings in a blue plastic scoop filled with white powder.
The scoop tilts, and the powder pours out in a steady white stream, suggesting detergent being added for the wash.
A demonstration follows on a dark surface.
A white shirt with two red sleeve stripes lies flat, showing pale greenish stains on the body.
Product boxes sit above the shirts : on the left, a red box labeled “ Detergent plus Bleach, ” and on the right, the orange Tide with Bleach box.
A second white shirt with matching red sleeve stripes is placed on the right side for comparison.
The left shirt remains visibly dingy and stained, while the right shirt appears cleaner and whiter under the Tide with Bleach package.
Near the end, the woman and the teenage boy stand together in a softly lit room with white window blinds and greenery visible outside.
She holds up the now-clean white \textbf{number} 21 \textbf{jersey}, and the boy, now in a brown shirt, takes it from her.
The \textbf{jersey} looks bright white, with the blue \textbf{number} and sleeve stripes clear.
He looks down at it, then bends his head to press his face into the fabric as if checking or savoring its freshness.
The woman smiles at him.
The final product image places a box of Tide with Bleach beside a neat stack of folded towels in white and pale pink.
Across the bottom, white on-screen text reads, “ IF IT ’S GOT TO BE CLEAN, IT ’S GOT TO BE TIDE. ”

% matched lemmas: football, game, jersey, number, player, shirtless, uniform, viewpoint, yellow-green
\end{textsample}
