\begin{textsample}{POS Dim 5 – 1990 – Score 7.00 – 1990/tv\_com\_1990\_5.txt}  \label{ex:f5_pos_079}
The commercial opens on a nearly black frame, with no clearly visible content.
It then cuts to a warm, softly lit, crowded \textbf{restaurant} or café scene viewed from above.
Many people are seated at small \textbf{tables}, eating and socializing.
The image has a hazy, glowing \textbf{look}, with busy movement throughout the space.
The next shots focus on food and desserts.
A server or \textbf{diner} is shown carrying plates, including a plate with a bright yellow-centered dessert and red fruit-like toppings.
This is followed by close-up dessert imagery : a layered slice with whipped cream and toppings, then a square chocolate dessert on a white plate topped with whipped cream, nuts, and syrup being poured from above.
The food is presented in close, glossy, appetizing shots.
A woman is then shown seated at a \textbf{table}, smiling or \textbf{speaking}, holding a fork with a bite of dessert near her mouth.
A plate with dessert is visible in front of her.
The background remains blurred and restaurant-like.
The commercial shifts to a close-up of a small rectangular package held between fingers.
The package is a blue-and-white Trident gum pack.
The visible text includes “ Trident ” and “ Original Flavor, ” and in the clearest later frame, “ SUGARLESS GUM ” is also readable.
The product is shown in soft focus with hands holding it near the camera.
A close-up of a \textbf{man} follows.
He appears to be in the same social dining setting, facing someone off-camera or partly visible in the foreground.
His mouth is open, suggesting he may be \textbf{speaking} or \textbf{reacting}, but no audio content can be inferred from the frames.
An overhead \textbf{table} shot then shows several people around a \textbf{table} with plates and cups.
One person appears to be extending or handing something across the \textbf{table}, but the exact object is not clearly visible in that frame.
The final part returns to repeated close-ups of the Trident package.
The pack fills much of the frame, held between fingers, with the branding emphasized.
The last frame clearly shows the package text : “ Trident, ” “ SUGARLESS GUM, ” and “ Original Flavor. ” The background remains softly blurred, maintaining the warm \textbf{restaurant} atmosphere while the product becomes the central visual focus.

% matched lemmas: diner, look, man, react, restaurant, speak, table
\end{textsample}
