\begin{textsample}{POS Dim 5 – 2020 – Score 7.00 – 2020/tv\_com\_2020\_92.txt}  \label{ex:f5_pos_068}
A middle-aged man with short dark hair sits indoors in a modern, softly lit home.
He is dressed in a dark button-up shirt and dark pants, seated cross-legged in a pale gray, high-backed wing chair.
To his right, on a small round wooden side table, stands a white Xfinity Wi-Fi gateway : a smooth, rounded rectangular tower with a small top seam.
Behind him are warm wood tones, sheer curtains, a kitchen counter with stools, and a sink, giving the room a calm, upscale domestic feel.
The man faces forward as if explaining the product, while the gateway is placed clearly beside him.
The scene shifts into a futuristic spacecraft cockpit.
The same man now appears as a space pilot, wearing a bulky gray-and-blue armored flight suit with shoulder plates and a small \textbf{glowing} eyepiece over one eye.
He sits in a command chair surrounded by dark blue metal walls, illuminated instrument panels, switches, and screens.
A young girl, likely his niece from the audio context, sits at another control station to his right.
She has light skin, her hair pulled back, and wears a matching gray-and-blue armored suit.
Bright light flares through the cockpit windows, and both \textbf{characters} appear focused on the ship ’s controls.
Outside, a sleek spacecraft speeds through a dark, blue-toned asteroid field.
The ship has long wings, glowing front lights, and bright engine points.
It passes among \textbf{floating} rocks and debris.
A \textbf{sudden} bright \textbf{flash} blooms into an orange explosion near the ship, filling part of the surrounding space with fire and smoke-like light.
Back inside, the man grins and reaches toward the control panel, seeming tempted by something.
The girl turns with wide eyes, visibly alarmed, as if \textbf{warning} him not to act.
A panel shows a large red button set inside a yellow-and-black hazard-striped square.
The label above it reads “ SUPERSONIC SPEED, ” and beneath it, in smaller lettering, “ DO NOT PUSH. ” After this, the view ahead of the cockpit fills with streaking white lines, as though the ship has jumped to extreme speed.
The two pilots are seen from behind at their stations, facing a brilliant white point of light ahead while blue-white lines stretch past them.
The cockpit instruments glow with charts and readouts.
The man ’s face is then shown front-on in his pilot seat ; his eyes are wide, his mouth open, and his whole expression is tense and frightened as the ship accelerates.
The Xfinity gateway appears again, now placed on a futuristic control console inside the spacecraft rather than in the living room.
It is the same white, rounded rectangular tower, standing upright amid dark controls, knobs, and illuminated panels.
White on-screen text appears to the left of it : “ The fastest Internet. ” Very small fine print runs along the bottom of the image.
The gateway is presented as a calm, clean object against the busy sci-fi cockpit background.
The spacecraft continues \textbf{racing} through a tunnel-like field of blue and white light streaks toward a \textbf{glowing} point ahead.
More white text appears on the left side of the screen in stages : “ The largest Gig-speed network. ” The ship remains centered in the distance, its engines \textbf{glowing}, while long lines of light rush around it.
Fine print remains along the bottom.
Inside the cockpit, the young girl is reclined back in her seat, lit by the harsh blue-white glow from the windows.
Her armored collar frames her face, and she looks upward with an excited, slightly concerned expression.
Nearby panels flicker with warm yellow-orange symbols and diagrams.
The man is then shown again in his pilot chair, still in his gray armor with the eyepiece catching the light.
His face relaxes from panic into a softer, embarrassed look, as if responding to the girl ’s comment about whether he is crying.
The final images return outside to the ship traveling at high speed through the luminous tunnel.
The craft glides past long, parallel streaks of blue-white light, with a bright star-like glow to one side.
As the ship recedes, a large white “ X ” appears in the middle of the rushing light field.
The letters complete into the white “ xfinity ” logo, centered against the dark blue, high-speed streaks, with the bright point of light still glowing to the right.

% matched lemmas: character, flash, floating, glowing, race, sudden, warn
\end{textsample}
