\begin{textsample}{POS Dim 5 – 1970 – Score 12.00 – 1970/tv\_com\_1970\_15.txt}  \label{ex:f5_pos_081}
A dark green sponsor card appears first, with large white text reading “ 800-841-8000 ” and, below it, “ NAVY, IT ’S NOT JUST A JOB, IT ’S AN ADVENTURE. ” Smaller text at the bottom says it is sponsored by the U.S.
Navy.
The scene then changes to a bright playroom where several young children crowd around a white table, excitedly playing with the Weebles Wobble Race toy.
A long-haired blonde girl in a red shirt leans over the track, her mouth open in excitement, while a child in a green striped shirt watches from the left.
Small egg-shaped Weeble racer figures, painted with helmets and \textbf{numbered} white \textbf{jerseys}, sit on a colorful racetrack in front of them.
The full tabletop toy is shown : a white plastic base with four colored \textbf{racing} lanes—green, yellow, orange, and red—leading toward a bold “ FINISH ” label at one end.
A blue upright rail or hurdle crosses part of the track, and a large illustrated backdrop rises behind it, decorated like \textbf{stadium} stands with \textbf{cartoon} spectators, bunting, and small signs \textbf{such} as “ START ” and “ EXIT. ” Four children gather around the \textbf{game}, including the blonde girl, a red-haired boy in a red shirt, a blond child in a light top, and the child in the green striped shirt.
Their faces are animated, mouths open as they watch the \textbf{race}.
Close views show the Weebles in detail.
They are rounded, weighted figures with glossy \textbf{colored} bottoms and helmet-like tops : green \textbf{number} 4, yellow \textbf{number} 3, orange \textbf{number} 2, and red \textbf{number} 1.
Their painted faces and arms make them look like little racers.
They wobble and lean rather than lying flat, bumping into one another on the lanes.
The green \textbf{number} 4 tips far to one side near the edge, then rocks back upright, while the yellow, orange, and red racers jostle together near the blue rail.
The children keep the \textbf{race} going by pressing and moving parts of the toy with their hands.
The blonde girl and the red-haired boy lean close, concentrating on the track.
The racers advance unevenly, rocking from side to side.
At the finish end, the four Weebles \textbf{cluster} together in their lanes beneath the blue rail, with the large “ FINISH ” lettering visible across the front.
The yellow \textbf{number} 3, orange \textbf{number} 2, red \textbf{number} 1, and green \textbf{number} 4 crowd side by side, nudging each other as they wobble.
One sequence focuses on the green \textbf{number} 4 near an “ EXIT ” arch on the backdrop.
The green racer collides with another figure and tumbles off the side of the track onto the white tabletop.
Even after tipping over, it rocks back and forth instead of staying down.
A child ’s hand reaches in and steadies or retrieves it, returning attention to the \textbf{race}.
The red \textbf{number} 1 racer is then shown alone on a red lane, rocking forward.
It sways dramatically from side to side, briefly tilting almost horizontal, then rights itself and continues wobbling.
Another close view shows green \textbf{number} 4 and yellow \textbf{number} 3 pressed shoulder to shoulder in neighboring lanes, their rounded bodies pushing against each other as they rock in place.
A wider view returns to the whole toy on the table.
The children are gathered behind it, watching.
The green \textbf{number} 4 leans sideways near the green lane, while yellow \textbf{number} 3, orange \textbf{number} 2, and red \textbf{number} 1 continue toward the finish.
At the finish end, the racers bunch together, bump, and spill off the track onto the tabletop.
Several figures roll or wobble outside the white plastic base, but they keep rocking upright or nearly upright.
The illustrated grandstand on the toy backdrop fills the view. \textbf{Cartoon} spectators with \textbf{exaggerated} faces cheer, blow horns, and hold their hands to their mouths.
Bright orange balloons \textbf{float} above them, and red, white, and blue bunting decorates the front of the stands, reinforcing the race-day setting.
The children \textbf{celebrate} around the table.
The blonde girl in the red shirt throws both arms straight up, the red-haired boy behind her raises an arm and laughs, and the child in the green striped shirt sits at the left with mouth wide open in excitement.
Another blond child at the right looks down toward the toy.
The playroom background includes blue walls, a white door, a black lamp, and yellow wall shelves.
The commercial ends with a clean product display against a plain light background.
The complete Weebles Wobble Race set is arranged neatly : the colorful racetrack base in front, the illustrated \textbf{stadium} backdrop standing behind it, and four loose Weeble racers lined up along the front.
Large yellow-orange text above the set reads “ Weebles Wobble Race. ”

% matched lemmas: cartoon, celebrate, cluster, color, exaggerated, float, game, jersey, number, race, racing, stadium, such
\end{textsample}
