\begin{textsample}{POS Dim 5 – 2010 – Score 11.00 – 2010/tv\_com\_2010\_10.txt}  \label{ex:f5_pos_019}
The commercial opens in a living room.
A middle-aged \textbf{man} wearing glasses and a light \textbf{plaid} \textbf{shirt} sits on a couch with a compact keyboard resting on his lap.
The room is dimly lit and domestic, with cushions, framed pictures, and furniture in the background.
The sequence then cuts to a brighter dining area.
The same \textbf{man} sits at a \textbf{table} and smiles while holding up a large decorative plate or circular object showing a simple portrait-style drawing of a person in a red jacket. \textbf{Other} decorative plates hang on the wall behind him, and a bowl of green/yellow fruit sits on the \textbf{table}.
Next, the setting changes to a darker office or den.
The \textbf{man} sits in a chair facing a desk and a small screen that shows another person.
He holds a magazine or booklet.
The room contains framed portraits, trophies, a helmet or astronaut-style \textbf{suit} on the right, and \textbf{other} memorabilia, suggesting a hobby or fan-themed space.
The commercial returns to the living-room couch.
The \textbf{man} again has the keyboard on his lap.
He appears \textbf{attentive}, \textbf{looking} forward toward something off-screen.
A rear/side view shows what he is \textbf{watching} : a wall-mounted television displaying an ice hockey game.
The \textbf{man} sits on the couch with his hands raised as if \textbf{reacting} to the game.
A small caption at the lower left reads “ Screen imagery simulated. ” The room includes framed pictures, a tuxedo-like red jacket on display, speakers beside the TV, and a fireplace below it.
The camera cuts back to the \textbf{man} on the couch.
He \textbf{looks} down and \textbf{gestures} toward the keyboard.
A close-up follows of his hands typing on a black keyboard with low-profile keys.
The TV screen is then shown more closely, still displaying the hockey game.
Later, the \textbf{man} appears again on the couch, \textbf{looking} forward.
Another shot of the TV shows an on-screen interface/menu over the video image, with multiple list items and a highlighted row.
The top right includes “ Google TV, ” though most menu text is too small or blurred to read clearly.
A close-up of the \textbf{man} ’s face follows.
He \textbf{looks} pleased or amused, with a slight smile.
The final frames shift to a product display on a solid green background.
White text reads “ Logitech Revue, ” shown beside a black keyboard and a small black set-top box.
In the next product frame, the text reads “ Logitech Revue with Google TV, ” with the Google TV mark next to it.
Small fine print along the bottom states that it requires an HDTV with HDMI in, a cable or satellite set-top box with HDMI out, and high-speed internet access.
The last frame is a white end card with the Logitech logo and the word “ Logitech. ” Below are “ logitech.com, ” a Best Buy logo, and “ amazon.com, ” with the same small requirement text along the bottom.

% matched lemmas: attentive, gesture, look, man, other, plaid, react, shirt, suit, table, watch
\end{textsample}
