\begin{textsample}{POS Dim 5 – 1970 – Score 16.00 – 1970/tv\_com\_1970\_83.txt}  \label{ex:f5_pos_041}
The commercial appears to take place inside a grocery or retail store and unfolds as a sequence involving a store \textbf{employee}, a \textbf{uniformed} officer, shoppers, and packages of Charmin.
At the beginning, the camera shows a close view of a display of rounded \textbf{tan} items arranged in rows, with red produce or decorations behind them.
Several hands reach in from the left and press or handle the items.
One person is wearing a bright blue sleeve.
The scene cuts to a middle-aged \textbf{man} in a white store \textbf{coat} with a black bow \textbf{tie} and glasses.
He \textbf{turns} his head as if \textbf{reacting} to something off-screen.
The next shot shows an \textbf{older} \textbf{man} in a dark \textbf{uniform} and peaked cap, possibly a police officer or guard, \textbf{looking} back toward the camera or toward the store \textbf{employee}.
The store \textbf{employee} is then shown in close-up facing the \textbf{uniformed} \textbf{man} ; his glasses sit low on his nose, and he appears to be \textbf{speaking} or explaining something.
The camera returns briefly to the display where hands continue touching or pressing the rounded items.
Then it cuts back to the store \textbf{employee} and \textbf{uniformed} \textbf{man} in \textbf{conversation}.
A wider shot reveals both \textbf{men} standing in an aisle.
In the background, several women stand near a display.
Behind them is a sign, partially visible, that reads “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” A close-up shows a shopper ’s hands holding a large package of Charmin.
The package features a baby ’s face and the brand name “ Charmin ” in large letters.
The shot then returns to the wider aisle view, with the store \textbf{employee} and \textbf{uniformed} \textbf{man} \textbf{looking} toward the women and the display.
The camera cuts to a close-up of the sign : “ PLEASE DO N’T SQUEEZE THE CHARMIN, ” written in large, hand-lettered black text on a white board.
Below the sign, the tops of Charmin packages are visible.
Two women are then shown standing in front of the Charmin display, each holding a package.
One woman has dark hair and wears a dark polka-dot blouse ; the \textbf{other} has reddish hair and wears a light-colored top.
Both hold Charmin packages with baby images on the front.
Their facial \textbf{expressions} are initially restrained, then later they smile and appear \textbf{amused}.
The \textbf{uniformed} \textbf{man} is shown holding a Charmin package while the store \textbf{employee} stands beside him.
The \textbf{uniformed} \textbf{man} \textbf{looks} down at the package and presses or grips it with both hands, examining it closely.
In a closer shot, he continues holding the package in front of his chest and \textbf{looking} at it with a \textbf{serious} \textbf{expression}.
The background shelves are softly visible.
The two women are shown again smiling in front of the Charmin display.
The \textbf{uniformed} \textbf{man} continues to inspect the package, then \textbf{looks} sideways.
The store \textbf{employee}, now also holding a Charmin package, smiles broadly while the \textbf{uniformed} \textbf{man} stands beside him holding another package.
A close-up of the store \textbf{employee} shows him smiling with his glasses low on his nose.
Near the end, the commercial shows a product display : several rolls or packages of Charmin arranged in a row beneath the same sign reading “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” The visible packages include different color accents and baby images on the front.
The final frame cuts to black.

% matched lemmas: amused, coat, conversation, employee, expression, look, man, old, other, react, serious, speak, tan, tie, turn, uniform
\end{textsample}
