\begin{textsample}{POS Dim 5 – 2020 – Score 16.00 – 2020/tv\_com\_2020\_70.txt}  \label{ex:f5_pos_033}
The commercial opens inside a bright, modern AT\&T retail store.
The space has blue accent walls, light wood display \textbf{tables}, shelves with phones/accessories, blue stools, and a glass entrance with the AT\&T logo above it.
A gray-haired \textbf{man} in a dark jacket and green \textbf{shirt} stands in the store, while a female store \textbf{employee} in a light blue AT\&T \textbf{shirt} stands behind a counter on the right.
White on-screen text at the bottom reads : “ This ad was made safely.
Please wear a mask in our stores. ” The next shot moves closer to the gray-haired \textbf{man} as he faces someone off-camera.
The back of another person ’s head and shoulder is visible in the foreground, suggesting he is \textbf{addressing} another customer or person in the store.
The same safety text remains at the bottom.
The view then cuts to a younger \textbf{man} wearing a brown sweater over a patterned-collar \textbf{shirt}.
He stands near a display \textbf{table} and shelves of phone accessories, \textbf{looking} toward someone off-screen with a somewhat skeptical or questioning \textbf{expression}.
The commercial alternates between the two \textbf{men}.
The gray-haired \textbf{man} is shown from the front with a \textbf{tense}, \textbf{focused} \textbf{expression}.
The younger \textbf{man} is then shown in an extreme close-up of his eyes, appearing to squint or stare intently.
This is followed by an extreme close-up of the gray-haired \textbf{man} ’s face, with furrowed brows and a similarly intense \textbf{look}.
The female AT\&T \textbf{employee} is then shown behind the counter, centered in front of shelves with boxed devices and accessories.
She holds or stands behind a tablet/register and appears to be \textbf{speaking} or \textbf{reacting} to the two \textbf{men}, though no audio is described.
A wider shot shows the two \textbf{men} facing each \textbf{other} across the store, with the \textbf{employee} positioned behind the counter between them in the background.
The scene visually frames them as if they are in a direct exchange or comparison.
The younger \textbf{man} is then shown closer, smiling broadly and \textbf{gesturing} with one hand.
Small white legal/disclaimer text appears along the bottom of the frame but is too small to read clearly in full.
The gray-haired \textbf{man} is shown next, \textbf{turned} slightly to the side and also appearing to \textbf{speak} or respond, with the same small disclaimer text at the bottom.
Another wide shot returns to the two \textbf{men} standing \textbf{opposite} each \textbf{other} in front of the counter.
The \textbf{employee} remains centered behind them, \textbf{watching}.
The final frame transitions to a bright blue promotional end card.
A smartphone image appears on the left.
Large white text is partially visible, including “ FR ” and “ SAMSUNG GA …, ” suggesting a Samsung Galaxy-related offer, but the full headline is cropped/obscured in the sampled frame.
Smaller text reads in part : “ Buy on a qualifying installment plan with … \$75/mo. before discounts \& trade … ” Additional fine print appears at the bottom, too small to fully read.
The AT\&T store scene is faintly visible behind the blue promotional overlay.

% matched lemmas: address, employee, expression, focused, gesture, look, man, opposite, other, react, shirt, speak, table, tense, turn, watch
\end{textsample}
