\begin{textsample}{POS Dim 5 – 1970 – Score 4.00 – 1970/tv\_com\_1970\_95.txt}  \label{ex:f5_pos_090}
A tall Glade aerosol can stands alone against a pale mint-green background.
The can is metallic gold and cream with a matching yellow cap.
The bold black word “ Glade ” is visible on the front, with smaller text below identifying Sunny Lemon air freshener, and lemon imagery decorating the label.
The can begins to reveal an illustrated scene alongside it, as though the label or package is opening into a little world.
A tall, narrow panel appears with a simple \textbf{cartoon} landscape : rolling hills made up of hundreds of round yellow lemons, stylized lemon trees with brown trunks and dotted \textbf{yellow-green} canopies, and a small orange sun partly tucked behind a white cloud.
The product can slips out of sight, leaving the \textbf{cartoon} lemon grove filling the tall panel.
Within this lemon-filled landscape, two small line-drawn \textbf{cartoon} people appear.
One looks like an older man, with a bald head, tufts of white hair, a large rounded nose, and simple greenish clothing.
The other appears to be an older woman, with fluffy white curly hair, a short dress, and a rounded nose.
They move among the lemon hills beneath the trees.
The man approaches the seated woman, and they settle together on the mound of lemons under a large tree.
The man becomes active, standing beside her and stretching a long, narrow tool or ladder-like object up into the lemon tree.
He pulls down an oversized lemon, nearly as large as his head, and cradles it proudly.
The woman watches with a pleased expression.
He sits back down beside her, holding the big lemon between them.
The fruit is then shown cut open, its circular cross-section divided into wedge-shaped segments.
Both \textbf{characters} hold lemon halves or shallow bowls filled with lemon slices, smiling and looking content, as if enjoying the fresh lemon scent around them.
The pair continue interacting playfully in the lemon grove.
The older man sniffs or presents a large lemon, while the woman rises from her seated position and gestures animatedly.
A large butterfly with pale wings, orange spots, and dark outlines \textbf{floats} in from the upper right, much bigger than the two little people.
The woman lifts a long white object upward toward it, and both \textbf{characters} look up.
The butterfly flutters above the lemon tree, then moves away across the open sky.
The man and woman watch it go, then move across the rolling lemon hills as the scene grows smaller again.
The lemon-grove illustration narrows back into the tall panel shape, with the sun, cloud, trees, and yellow hills still visible inside it.
The product can reappears beside the illustrated panel, reconnecting the sunny outdoor \textbf{cartoon} world with the actual Glade Sunny Lemon can.
The panel closes away, returning to the single aerosol can standing by itself on the pale background.
A real hand enters from the right and reaches for the can.
The hand has neatly manicured nails and grips the can around its middle, lifting it slightly.
The setting changes to a real kitchen-like interior with warm wooden cabinets above and a light-colored appliance or wall surface below.
The hand holds the gold Glade can at an angle beneath the cabinets.
Bold black on-screen text appears near the bottom : “ Newest of the Natural Scents from Glade. ” As the hand presses the top, a visible white mist sprays from the can toward the left, spreading into the air under the wooden cabinets.

% matched lemmas: cartoon, character, float, yellow-green
\end{textsample}
