\begin{textsample}{POS Dim 5 – 1990 – Score 11.00 – 1990/tv\_com\_1990\_25.txt}  \label{ex:f5_pos_009}
The commercial opens in \textbf{stark} black and white with two young faces filling the screen side by side.
Both appear \textbf{anxious} and wide-eyed, with only parts of their faces visible at the edges.
Red question marks appear over their foreheads and cheeks, suggesting uncertainty about where a pimple might appear.
A young man ’s face then fills the image ; he has dark, tousled hair and a small pimple centered high on his forehead.
A round magnifying glass swings down over the pimple, and inside the glass appears a tiny bald, bespectacled man ’s head, grinning broadly.
Handwritten text beside him reads “ Hi, ” as if the pimple or acne bacteria is cheerfully announcing itself.
Tiny versions of the same bald, glasses-wearing head appear on a woman ’s cheek and forehead, then on the young man ’s face.
He looks around with \textbf{exaggerated} alarm as more of the little heads pop up across his forehead, cheeks, nose, and chin.
The image then widens to show the young woman and young man together beneath large handwritten words reading “ Acne Bacteria, ” with a green curved underline.
Small text in the lower left reads “ SIMULATED BLACKLIGHT DEMO. ” The lighting shifts to a blue blacklight effect, and both faces are covered with glowing green dots, making the bacteria appear spread across their skin.
A \textbf{sudden} bright graphic fills the screen with \textbf{huge} hot-pink letters \textbf{spelling} “ OXY ” against a white background.
The two young people appear small beneath the giant logo, moving playfully in the open white studio space.
Turquoise handwritten-style lettering reading “ sensitive ” overlays the pink OXY logo, followed by the word “ New ” below it and a small turquoise diamond-shaped product mark.
The style remains high-contrast and graphic, mixing black-and-white people with bright pink, blue, and green product \textbf{colors}.
The young man appears again on the left, smiling and speaking expressively, with handwritten text to his right reading “ VIRTUALLY No Drying. ” The words curve loosely across the white background.
He pulls \textbf{exaggerated} faces and leans partly out of view, as if reacting comically to the claim.
A young woman then appears beside the words “ VIRTUALLY No Irritation. ” She has messy, teased hair with dangling earrings and a concerned, pouty expression.
Bright pink blotches are painted over her forehead and cheeks as visual symbols of irritation, while small text at the bottom says “ SEE PACKAGE FOR DETAILS. ” The two young people stand together under a large handwritten “ GUARANTEED, ” arched across the top with a pale blue underline.
The young man moves toward the young woman and wraps his arms around her in an enthusiastic hug, lifting one leg behind him in a playful pose.
This dissolves into another blacklight-style image of the young man ’s face, now tinted blue with glowing green spots.
Large hands enter from both sides, with index fingers extended like pointers, aiming at the spots on his cheeks and forehead.
As the hands sweep across his face, the green marks fade.
He ends facing forward with a broad, slightly goofy smile, while handwritten names of days of the week appear around him, including “ Sun, ” “ Thur, ” “ Fri, ” and “ Tue, ” suggesting daily use.
A row of bald, glasses-wearing heads, representing the acne bacteria, peek over a curved gray surface like little figures hiding behind a wall.
They grin and look around.
Behind them, a turquoise Oxy Sensitive package rises into view.
As it grows larger, handwritten words \textbf{such} as “ HELP ” and “ NO ” appear around the scene.
The product package dominates the center : it is turquoise with a black diamond panel reading “ sensitive, ” large pink “ OXY ” lettering, blue “ sensitive ” text, and a black strip with yellow “ VANISHING ” visible near the bottom.
The bald heads remain scattered around the lower edge, reacting as the package looms above them.
The young woman returns under the blue blacklight effect, with glowing green spots on her face and the on-screen instruction “ USE ONLY AS DIRECTED ” in the upper left.
She rubs or wipes her cheek and around her mouth with her hand.
As her hand moves away, her face looks clearer and she smiles.
The turquoise product package slides in from the right, partly covering her face, then fills much of the screen before moving aside to reveal the young man again.
He faces forward in black and white, one eye squeezed shut in a wink and his mouth open mid-expression.
Blue \textbf{radiating} lines appear on both sides of his head, adding a graphic emphasis to his reaction.
Two \textbf{floating} bald heads appear on a plain white background : one wears regular black glasses and smiles, while the other wears dark sunglasses and has a small mustache.
Pink-red heart shapes pop around them, implying the bacteria are multiplying or “ breeding. ” A thick red diagonal \textbf{bar} sweeps across them, forming a prohibition symbol.
The completed red circle-and-slash sign surrounds the two heads, with handwritten white text around it reading “ Oxycute ’ em in Advance. ” The heads look trapped inside the “ no ” symbol.
A small turquoise Oxy Sensitive package appears beneath curved handwritten text reading “ Product Shot, ” with “ Invisible Gel ” written below it.
The package tilts slightly on the white background, again showing the turquoise \textbf{color}, black diamond “ sensitive ” panel, pink OXY logo, and the vanishing/invisible gel branding.
Finally, a circular cutout opens in a white surface.
The young man appears inside the circle, then the young woman joins him, smiling and putting an arm around his shoulders.
Large turquoise, three-dimensional-looking text arcs above them reading “ Oxycute ’ em. ” At the bottom, the “ SB SmithKline Beecham ” logo appears, closing the commercial with the couple framed together and the product slogan hovering overhead.

% matched lemmas: anxious, bar, color, exaggerated, floating, huge, radiate, spell, stark, such, sudden
\end{textsample}
