\begin{textsample}{POS Dim 5 – 1970 – Score 10.00 – 1970/tv\_com\_1970\_70.txt}  \label{ex:f5_pos_044}
The commercial begins with a very dark, low-contrast title-like frame showing large block letters that appear to read “ ILGWU ” or similar, though the text is not fully clear.
It then cuts to a close-up of an \textbf{older} \textbf{man} with gray hair, seated indoors.
The image has a yellow-green tint and visible video softness.
Shelving and containers are visible in the background.
The “ Classic Commercial Archives ” watermark appears over the image.
A wider shot shows three \textbf{older} \textbf{men} gathered around a small \textbf{table} or barrel-like surface, with a white curly-haired dog sitting in the foreground.
One \textbf{man} wears a cap and glasses, another appears to be wearing a white \textbf{coat} or \textbf{apron}, and another has gray hair and an apron-like garment.
They seem to be \textbf{looking} at or handling something on the \textbf{table}.
The setting appears to be an interior \textbf{shop} or workroom with shelves and goods behind them.
The next shot is a close-up of two of the \textbf{men}, one in a cap and glasses and the \textbf{other} in glasses with a light-colored \textbf{coat}.
They face forward, as if \textbf{reacting} to or \textbf{watching} something.
A soft dissolve or overlay effect makes parts of the image \textbf{look} doubled.
A close-up then shows hands holding or presenting a pale, rounded mass of food in front of the \textbf{men}.
At the bottom of the frame, white all-capital text appears : “ MEAT BY-PRODUCTS AND MEAT, VEGETABLES, VITAMINS AND MINERALS. ” The \textbf{men} and the dog remain visible behind the food, partially obscured by the close-up and dissolve effect.
The commercial returns to a close-up of the gray-haired \textbf{man} leaning forward.
The ingredient text remains partially visible at the bottom, though it is partly cut off and blurred.
Next, the dog is shown eating from a bowl.
Behind the dog, a box of “ Gaines-burgers ” is displayed prominently.
The box is mainly orange/red with blue and yellow areas, and the brand name “ Gaines-burgers ” is large and easy to read.
A product display follows : three “ Gaines-burgers ” boxes stand behind a bowl filled with chunks of dog food.
The dog is low in the foreground, partly visible near the bowl.
The three boxes are different color variants : yellow, orange/red, and white/blue.
The bowl sits centered in front of them.
The final frame is a clearer product shot : three “ Gaines-burgers ” boxes lined up behind a bowl of food on a reflective surface.
Large white on-screen text at the bottom reads : “ The canned dog food without the can. ” Small text beneath includes “ {\EmojiFont ©}GENERAL FOODS CORP 1977. ”

% matched lemmas: apron, coat, look, man, old, other, react, shop, table, watch
\end{textsample}
