\begin{textsample}{POS Dim 5 – 1970 – Score 10.00 – 1970/tv\_com\_1970\_96.txt}  \label{ex:f5_pos_045}
The commercial opens in an interior kitchen or dining area.
A woman in a floral dress, \textbf{apron}, and white cap is seen from behind or side, facing a darker area where \textbf{other} people are gathered near a \textbf{table} or counter.
The room has hanging lamps and cabinetry, with a somewhat dim, domestic setting.
The scene then cuts to a bright, close-up view of a sink or dishwashing area.
The image is washed out by steam, suds, or glare.
Dishes, pots, and a white curved sink edge are visible.
A pale, stained or soiled surface/object appears among the dishes, but the exact item is unclear.
Next, two women are shown in a kitchen.
The woman in the floral dress and white cap holds up a cylindrical cleanser can, examining or presenting it.
Beside her is a Black woman in a peach blouse with a white \textbf{collar}, \textbf{watching} attentively.
Kitchen cabinets with patterned panels are visible behind them.
The commercial then moves into a comparison-style visual.
A semi-transparent overlay shows the same dishwashing/dirty-surface imagery, with large black text near the bottom.
On the left, the word “ Comet ” is clearly visible.
On the right, the text reads “ \textbf{Other} Leading Cleanser, ” though part of it is cropped or softened by the image quality.
The background continues to show suds, dishes, and a sink area.
A brief transitional frame follows, showing a dark blue/purple field with a vertical bright beam or flare in the center.
The object or scene is unclear and may be a visual transition.
The comparison imagery resumes.
Hands are shown scrubbing or wiping a surface with blue cleaning pads or cloths.
The bottom text remains : “ Comet ” on the left and “ \textbf{Other} Leading Cleanser ” on the right.
The surface appears wet and foamy, with streaks or residue visible.
The hands move across the divided comparison area, suggesting side-by-side cleaning action, though the exact boundary between the two sides is not fully clear.
Later, the image overlays the comparison text and cleaning imagery with the kitchen scene again.
The woman in the floral outfit, the \textbf{man} in a \textbf{shirt}, \textbf{tie}, and \textbf{vest}, and the Black woman in the peach blouse are all visible together, partially obscured by the semi-transparent comparison graphics.
In the final frame, the three people stand close together in the kitchen.
The \textbf{man} in the center holds a cylindrical cleanser can with an orange-toned label facing forward.
The woman in the floral dress stands on the left, \textbf{gesturing} with one hand, while the woman in the peach blouse smiles on the right.
The product can is central in the shot, and the scene is brightly lit compared with the opening.

% matched lemmas: apron, collar, gesture, man, other, shirt, table, tie, vest, watch
\end{textsample}
