\begin{textsample}{POS Dim 5 – 2000 – Score 7.00 – 2000/tv\_com\_2000\_98.txt}  \label{ex:f5_pos_030}
A sunlit sailboat moves across glittering water in warm golden light.
Several young adult women in swimsuits are aboard, their bodies mostly in silhouette against the bright sea and sky.
One woman leans over part of the boat ’s rigging, handling a line or rail ; she wears a turquoise bikini top and white shorts, with long hair falling forward as the sun flares behind her.
The imagery is saturated with yellows and blues, giving the boat, ocean, and women an adventurous, tropical look.
A brief, glossy overlay of blue lettering appears near the water, suggesting the Venus name before the scene returns to the women on the boat.
A close view shows a woman ’s face and shoulders in strong backlight, her long hair blowing across her face.
She wears a bikini top and looks off to the side, relaxed and alert.
The setting then opens to the ocean, where a dolphin leaps out of the water, its body arcing upward with a splash below and clouds above.
Back on the sailboat, a woman sits or kneels on the pointed bow, raising both arms high as if \textbf{celebrating} or balancing, with dark blue water and distant hills behind her.
The commercial moves into underwater imagery.
A dolphin dives beneath the surface, surrounded by bright bubbles and golden light from above.
Two women stand at the pointed ends of the boat and leap into the sea ; one in the foreground springs forward with arms extended, while another is already diving from a farther point.
Underwater, two outstretched hands and forearms cut through deep blue water, leaving trails of bubbles.
A blonde woman swims below the boat with her arms spread wide, looking upward toward the rippling surface and the dark shape of the hull overhead.
The product is introduced visually in this underwater world.
A blue-and-white Gillette Venus disposable razor \textbf{floats} into the foreground, enlarged and crisp against the softer image of the swimmer and ocean behind it.
The white razor head has “ Gillette ” printed on it, and the blue handle carries the Venus name.
Bubbles rise around it.
The razor rotates slowly in space, revealing its curved blue handle, white rounded head, and grip details.
Several views show the product from different angles, including a close-up of the head and blades.
The razor appears \textbf{suspended} in a luminous bubble, emphasizing the rounded head and the three parallel blades set inside a white oval frame.
More underwater beauty images follow.
A swimmer ’s tanned legs glide through the water, \textbf{crossed} and extended, with sunlight making golden, rippling patterns across the skin.
Two dolphins swim near a woman underwater ; they appear as dark, graceful silhouettes against the bright surface, one on each side of her.
She \textbf{floats} between them with one arm extended, creating a dreamlike scene of swimming alongside marine life.
The product is then shown in actual use.
In bright sunlight aboard the boat, a blonde young woman in a pink-and-white striped bikini top and white sunglasses bends one knee and shaves along the top of it with a blue disposable razor.
Her long hair blows across the frame, and she looks down with a small, \textbf{focused} smile.
The razor ’s white head rests against her skin as she guides it over the curve of her knee, visually matching the later product claim about the rounded head hugging curves.
The razor reappears underwater in close-up, its white oval head and three blades prominent against a background of bubbles and blue water.
Behind it, a swimmer ’s silhouette moves faintly near the surface.
The head glints with highlights as it tilts, again showing the rounded shape and blade area.
The underwater scene returns to a woman and dolphins swimming in silhouette, framed by a \textbf{glowing} sunlit patch above them.
Back at the sailboat, two women lounge on the edge of the deck in warm light.
One, wearing the pink striped bikini, sits near the bow with one leg extended and one knee bent, leaning back on an arm.
Another woman in a blue or turquoise top sits farther back near the sail and rigging.
The water beside the boat \textbf{flashes} with reflected sunlight.
A blonde woman swims underwater in a pink-toned swimsuit, her body stretched horizontally as bubbles trail behind her.
She moves smoothly through deep blue water, one hand lifted near her face and the other arm drifting back.
A dolphin dives nearby in a burst of white foam.
Then two women surface through heavy splashes, smiling broadly with arms raised.
One wears a bright blue bikini top, and the other, partly obscured by spray, wears a pink top.
The water droplets fill the foreground, making the scene feel energetic and playful.
For the final product display, several blue razors \textbf{float} upward through a dark, watery background toward a bright star-like light.
The light flares strongly, and the razors rotate into view.
The Venus brand name appears large in glowing blue letters, followed by “ DISPOSABLES ” underneath.
Two product packages stand side by side : a pink package on the left and a blue package on the right, each showing Venus disposable razors inside.
At the bottom, white script text reads, “ Reveal the goddess in you. ”

% matched lemmas: celebrate, cross, flash, float, focused, glowing, suspend
\end{textsample}
