\begin{textsample}{POS Dim 5 – 1990 – Score 22.00 – 1990/tv\_com\_1990\_12.txt}  \label{ex:f5_pos_003}
A \textbf{crowded}, dim interior is washed in green light.
Young adults and older adults sit close together in rows that slope downward, like a theater or auditorium.
A young man with short hair, tinted completely green by the lighting, wears a light jacket over a shirt and forces his way past people in the aisle.
He leans over shoulders, grips another person ’s arm for balance, and pushes forward with an urgent, intent expression.
A young woman with long hair, also green-lit, smiles slightly as she moves through the crowd.
From behind, the green-clad young man runs down the center aisle toward a red-lit stage or screen at the front while gray-suited audience members rise or turn to watch.
The scene cuts into Nintendo 64 \textbf{game} \textbf{footage} from a first-person shooter.
A large weapon fills the lower right of the screen, firing bright green-white \textbf{blasts} at a \textbf{huge} dinosaur-like boss in a dark \textbf{arena}.
At the top, the word “ BOSS ” appears above a \textbf{health} \textbf{bar}.
Energy rings, explosions, smoke, and a towering reptilian creature dominate the action.
A green title card follows, with large \textbf{glowing} white text reading “ TUROK ” and smaller text underneath reading “ DINOSAUR HUNTER. ” More \textbf{game} \textbf{footage} shows a first-person weapon aimed across a rocky or industrial landscape, with small white text along the bottom : “ Call 1-800-771-3772 for Game \textbf{rating} information. ” Enemies and dinosaur-like creatures appear in murky greenish environments, including a close encounter with a lunging open-mouthed creature among thin tree trunks.
Back in live action, a young woman with long braids fills the right side of the image, her face and hair \textbf{glowing} green.
Behind her, a nighttime city street is crowded with people and cars.
A man in a green jacket hurries toward a pale, rigid-looking man in a white short-sleeved shirt and black tie, who stands near a car like a guard or authority figure.
The green man reaches him at close range.
An overhead view then reveals a city \textbf{intersection} at night, with cars parked along the curbs and small groups of people gathered in the crosswalks and street.
More Turok \textbf{footage} follows : a first-person weapon targets small creatures in outdoor terrain, and reddish \textbf{flashes} cover the screen during hits or explosions.
Then the visuals shift to a stage performance in a theater.
Blue-lit performers move in front of a large projection screen.
Big block letters on the screen \textbf{spell} out changing words, including “ RULES, ” and then “ DRESS CODE ‘ BOY ’. ” White text at the bottom reads, “ \textbf{Game} and system sold separately. ” A boy or young teen, his skin and hair painted or lit vivid blue, stands center stage facing forward.
He wears a simple shirt and stares directly ahead, wide-eyed and serious.
Other blue performers crouch or gesture around him while an audience watches from below.
The commercial moves into GoldenEye 007 \textbf{footage}.
In a gray industrial hallway, a first-person gun fires at guards and a vehicle ; explosions bloom orange and white.
A blue textured title screen assembles into \textbf{glowing} white text : “ GOLDENEYE 007. ” Four-player split-screen gameplay appears, dividing the screen into four equal panels.
Each panel shows a first-person view inside a pale gray, tiled industrial \textbf{arena}, with gunfire, muzzle \textbf{flashes}, and explosions occurring in different corners at once.
The overhead city \textbf{intersection} appears again, now with more color-coded groups gathering.
More GoldenEye \textbf{footage} shows a first-person view across a dark outdoor platform toward an armed guard near crates, then an interior with gray walls, stairs, consoles, and \textbf{uniformed} enemies.
Shots are exchanged, and bright muzzle \textbf{flashes} light the scene.
A bright, airy corridor appears in live action, lined with tall white columns and filled with office workers in white shirts and dark trousers walking normally.
A young person in a yellow outfit and yellow helmet rides a skateboard through the corridor, crouched low and weaving between the adults.
The skater wears elbow pads and sneakers, reaches one arm out for balance, and rolls close to passing workers.
A close-up shows the skateboard wheels and the rider ’s foot skimming along the polished floor.
The visuals shift to Star Wars \textbf{game} \textbf{footage}.
In a snowy landscape, a large gray Imperial walker strides across a white battlefield.
A golden title card reads “ STAR WARS SHADOWS of the EMPIRE. ” Gameplay follows a small vehicle speeding through a sandy canyon or city-like desert environment, seen from behind as it passes blocky buildings and open archways.
In live action, the yellow-clad skater is seen from below against a dark night sky and tall building lights, appearing to leap high overhead with arms and legs spread, clothing flaring around the body.
More Star Wars gameplay shows a \textbf{character} in a futuristic white interior using a laser weapon.
On-screen meters include “ Health ” on the left and “ Laser ” on the right.
A gray two-legged walker fires red laser beams, then the \textbf{player} \textbf{character} runs through pale corridors under a large hovering craft.
Later, several bulky white, ape-like creatures crowd a dark corridor, surrounding the \textbf{player} ’s \textbf{viewpoint}.
The palette changes to red.
In a bright white outdoor or studio-like space, many people in white T-shirts and shorts stand in organized rows.
Among them, a few people are painted or lit red and dressed in red clothing.
One red-tinted young man blows a \textbf{huge} pale bubble of gum until it fills the space beside his face.
Another red-painted young man with short spiked hair grins broadly and lunges toward the viewer with manic energy.
Red-clad figures run, dance, and dart between the orderly white-shirted crowd.
From above, the white-shirted people form a grid-like pattern while the red figures cut across it unpredictably.
Extreme-G \textbf{racing} \textbf{footage} appears.
A futuristic motorcycle-like vehicle \textbf{races} along curving, elevated tracks with a heads-up display showing position, time, speed, and meters.
The track \textbf{loops} through purple, green, yellow, and orange sci-fi environments, with \textbf{glowing} tunnels, sweeping banks, and bright explosions.
A red textured title card forms the text “ EXTREME-G, ” glowing in white.
More \textbf{racing} \textbf{footage} shows a rider speeding through colorful ramps, energy effects, and tube-like courses, sometimes in eighth, sixth, or second place according to the visible on-screen position indicator.
A nighttime view looks up at a tall building with many lit windows.
The aerial \textbf{intersection} returns, now filled with clustered groups in green, red, blue, and yellow.
The \textbf{colored} groups are more numerous and begin to form a deliberate shape in the center of the road.
A brief abstract game-like corridor appears with glossy black, purple, red, and teal surfaces.
A small, blocky, brightly \textbf{colored} figure or object moves through the space as explosions glow in the distance.
Then four \textbf{live-action} \textbf{colored} figures lean in from all sides, looking down toward the viewer : green on the left, blue upside down at the top, red on the right, and yellow in the center.
The yellow young person steps closest, smiling directly downward, while the others hover around the edges like a circle of challengers or teammates.
A pale man in a white short-sleeved shirt and black tie stands on the edge of a rooftop at night, legs braced wide, looking outward over the city.
Finally, from high above the \textbf{intersection}, the \textbf{colored} crowd has arranged itself into the recognizable blocky Nintendo 64 “ N ” logo shape, with green, red, blue, and yellow sections packed tightly together in the middle of the streets, surrounded by parked cars and the city grid.

% matched lemmas: arena, bar, blast, character, color, crowded, flash, footage, game, glowing, health, huge, intersection, live-action, loop, player, race, racing, rating, spell, uniform, viewpoint
\end{textsample}
