\begin{textsample}{POS Dim 5 – 1960 – Score 14.00 – 1960/tv\_com\_1960\_8.txt}  \label{ex:f5_pos_052}
The commercial opens in a warmly lit, old-fashioned interior resembling a study or parlor.
A \textbf{uniformed} \textbf{man}, possibly a hotel or domestic \textbf{staff} \textbf{member}, stands in the background, while a dark silhouetted figure occupies the foreground.
The room contains framed pictures, a mantelpiece, and furniture, giving it a formal, period-style atmosphere.
A “ Nostalgic X’er ” watermark appears at the lower right throughout the frames.
The scene then cuts to a close-up of packaged dessert products on a tray.
Several tubs or cups are visible with labels reading “ Cool ’ n Creamy, ” including a chocolate-flavored container in the foreground.
The visible label includes wording such as “ Instant Chocolate Flavored Pudding. ” A hand moves near the foreground container.
Next, the commercial shows two \textbf{men} standing close together in the same interior.
One \textbf{man} wears a dark \textbf{uniform} with light trim and sleeve stripes ; he has a neat, formal appearance.
The \textbf{other} \textbf{man} wears a \textbf{tan} \textbf{suit} with a \textbf{vest}, white \textbf{shirt}, and \textbf{tie}.
The \textbf{uniformed} \textbf{man} \textbf{looks} toward the \textbf{suited} \textbf{man}, while the \textbf{suited} \textbf{man} \textbf{looks} downward or to the side.
A wider shot reveals the \textbf{men} standing at a \textbf{table} or desk covered with serving items.
On the \textbf{table} are a metal tray, dessert containers, bowls, spoons, and \textbf{other} decorative objects.
The \textbf{suited} \textbf{man} appears to handle or present the dessert items while the \textbf{uniformed} \textbf{man} \textbf{watches}.
The commercial cuts to a close-up of dessert in small clear cups.
A spoon is inserted into a chocolate pudding cup in the foreground. \textbf{Other} cups, including a lighter-colored pudding, sit nearby on the tray.
The texture appears creamy and smooth.
The \textbf{men} are then shown again at the \textbf{table}.
The \textbf{suited} \textbf{man} holds or \textbf{gestures} with a spoon over the tray, while the \textbf{uniformed} \textbf{man} \textbf{looks} down toward the desserts.
The setting remains the same formal room with mantelpiece and decorative objects in the background.
A closer shot follows as the \textbf{suited} \textbf{man} moves across the frame in front of the \textbf{uniformed} \textbf{man}.
The \textbf{uniformed} \textbf{man} remains in dark clothing with visible sleeve stripes, \textbf{watching} the action.
The \textbf{suited} \textbf{man} is then shown holding a small dessert cup and spoon.
He raises the spoon toward his mouth and appears to taste the pudding.
The \textbf{uniformed} \textbf{man} is partly visible at the edge of the frame.
The final frame is a product display shot.
A metal tray holds multiple “ Cool ’ n Creamy ” containers and prepared dessert cups, including chocolate and a lighter-colored variety.
Large white text over the product display reads : “ Too good to be pudding. ” The product packaging and prepared puddings are centered as the closing visual emphasis.

% matched lemmas: gesture, look, man, member, other, shirt, staff, suit, table, tan, tie, uniform, vest, watch
\end{textsample}
