\begin{textsample}{POS Dim 5 – 1950 – Score 8.00 – 1950/tv\_com\_1950\_10.txt}  \label{ex:f5_pos_083}
The commercial begins with a black screen.
It then cuts to a black-and-white scene inside what appears to be a pharmacy or \textbf{shop}.
Shelves in the background hold boxed and bottled products.
A woman with dark, styled hair stands in the foreground wearing a light cardigan over a \textbf{collared} top.
Behind her, a \textbf{man} in glasses and a bow \textbf{tie} works near the shelves or counter.
The woman \textbf{looks} downward with a \textbf{serious} or \textbf{concerned} \textbf{expression}.
The next shot is a close-up of an open palm holding two small, round tablets.
The background is a speckled countertop or surface.
The commercial then returns to the \textbf{shop} counter.
The \textbf{man} in glasses and bow \textbf{tie} stands beside the woman, \textbf{looking} down toward the counter or her hand.
The woman also \textbf{looks} down and appears to handle or examine something in her palm.
On the counter are small product containers or bottles.
Later, a close-up product shot shows a hand holding or surrounding several tablets and a medicine package labeled “ VANQUISH. ” The image includes both round and oblong tablets, and a packet or wrapper-like item is visible near the hand.
The final frame is a staged product display on a dark background.
A box labeled “ VANQUISH ” sits next to a small pouch or bottle-like object and two oblong tablets.
Large on-screen text reads : “ Relief so long lasting, most headaches don't come back. ”

% matched lemmas: collar, concerned, expression, look, man, serious, shop, tie
\end{textsample}
