\begin{textsample}{POS Dim 5 – 1960 – Score 11.00 – 1960/tv\_com\_1960\_31.txt}  \label{ex:f5_pos_054}
The commercial is shown in a sepia-toned or black-and-white vintage style, with a “ Nostalgic X’er ” watermark visible in the lower-right corner throughout the sampled frames.
It opens with a dimly lit shot of two human figures seen mostly in silhouette, facing each \textbf{other} near a doorway or windowed interior space.
The background appears domestic, with window frames and interior lighting visible.
The scene then cuts into a brighter interior room.
A close, partially obscured shot shows the back of someone ’s head in the foreground, with a wall picture and household furnishings behind.
The setting becomes clearer in the next frame : a woman with short hair, wearing a dark dress, is near a small \textbf{table} by a window.
A \textbf{man} in a light-colored \textbf{shirt} with a bow \textbf{tie} stands close beside or behind her.
The room appears like a kitchen or dining area, with a large window with blinds, framed pictures, and a small \textbf{table}.
The commercial then alternates between close-ups of the two people.
The \textbf{man} is shown in profile and then from the front, wearing a bow \textbf{tie} and light \textbf{shirt}.
He appears to be smiling or \textbf{speaking} visually, though no audio content can be inferred.
The woman is shown in close-up \textbf{looking} upward or to the side, with a \textbf{serious}, skeptical, or questioning facial \textbf{expression}.
Her face is lit from one side, creating strong shadows.
A later wider shot shows the woman standing more centrally, facing forward, while the \textbf{man} stands behind her to the left.
She appears to \textbf{gesture} or shift her hands while the \textbf{man} remains nearby.
The domestic background remains consistent : window, \textbf{table}, wall décor, and a framed object or mirror on the right side.
The next close-up shows both faces together : the woman on the left with a pursed or exaggerated facial \textbf{expression}, and the \textbf{man} on the right smiling.
They appear to be \textbf{reacting} to each \textbf{other} visually.
Another wider shot shows them facing one another beside the \textbf{table} ; the woman ’s hands are held out slightly, while the \textbf{man} ’s hands are near his waist or stomach.
The exchange remains confined to the same interior room.
The final frame cuts to a product display.
Three Head \& Shoulders packages are arranged on a shelf or counter : a tube on the left, a box in the center, and a bottle on the right.
Large text above them reads “ Really Works. ” The Head \& Shoulders name is visible on the packaging.

% matched lemmas: expression, gesture, look, man, other, react, serious, shirt, speak, table, tie
\end{textsample}
