\begin{textsample}{POS Dim 5 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_85.txt}  \label{ex:f5_pos_070}
The commercial opens with a close-up of a young \textbf{man} in a light-colored \textbf{shirt} standing in front of weathered wooden siding.
He \textbf{looks} \textbf{serious} or intent, with strong shadows across his face.
It then cuts to a wider exterior view of an \textbf{old} wooden house on a street, shaded by trees.
The building has worn clapboard siding, shutters, and a small storefront-like section or doorway.
The sequence returns to the young \textbf{man} in close-up.
His head is tilted back, his eyes are partly closed or closed, and the image has a soft, pinkish light flare across one side.
He appears to be leaning against or near the same weathered wall.
Next, he is shown crouching low beside the house, wearing jeans and a pale \textbf{shirt}, with his hands held near his mouth as if \textbf{watching} or waiting.
A brief overexposed, blurred transition follows, making the action unclear.
The scene then shifts to close-up shots of hands rubbing soap or suds over a glossy surface.
Soon after, white liquid or soap streaks are seen dripping down the side of a light blue car.
A wider shot reveals a vintage light blue car parked beside the \textbf{old} house.
A young woman in a pink top and denim shorts is bent over near the front of the car, apparently washing it.
A clothesline with hanging fabric is visible in the background.
The house ’s worn siding and shutters remain prominent.
After a brief dark transition, there is a close-up of the woman ’s denim shorts from behind, showing back pockets, damp-looking spots, and a brown leather patch at the waistband.
The \textbf{man} is then shown sitting on the ground against the house, legs spread out, in bright light.
He appears startled or caught off guard.
A close-up of the woman follows : she \textbf{turns} her head and \textbf{looks} back over her shoulder, holding a sponge or wash item near her hand.
Her \textbf{expression} appears direct and slightly questioning or knowing.
Near the end, the \textbf{man} stands leaning against the weathered wall with his hands near his pockets, \textbf{looking} off to the side and then smiling.
Large red text “ 501 ” appears over the image, with a red Levi ’s logo at the lower right.
The commercial then cuts to black.

% matched lemmas: expression, look, man, old, serious, shirt, turn, watch
\end{textsample}
