\begin{textsample}{POS Dim 5 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_56.txt}  \label{ex:f5_pos_021}
A packed indoor basketball \textbf{arena} fills the screen.
A large overhead scoreboard reads “ MAKE SOME NOISE … ” with “ HOME 78, ” “ VISITOR 80, ” and just four seconds on the clock.
The stands are crowded, and the atmosphere is tense and expectant.
On the court, \textbf{players} in white \textbf{uniforms} and \textbf{players} in blue “ STATE ” \textbf{uniforms} \textbf{cluster} near the basket.
A white-uniformed defender with “ DENSEN 25 ” on his back faces a blue-uniformed \textbf{player} wearing a dark headband.
Cheerleaders in green-and-white outfits stand behind them holding shiny silver pom-poms.
The play continues with the blue team trying to get off a final shot.
A blue-uniformed \textbf{player} rises and releases the basketball while white-uniformed defenders jump with arms stretched high. \textbf{Players} on both teams watch the ball arc upward.
In the stands, several fans lean forward with open mouths, frozen in suspense : a boy and a woman hold drinks, a heavyset man in a striped shirt stares ahead, a young man in a blue “ STATE 1 ” \textbf{jersey} looks stunned, and a tall man in a bright blue shirt points or gestures toward the court.
The scoreboard later shows no time remaining, with the score still displayed as 78 to 80, while \textbf{players} begin to spread across the court and the crowd remains fixed on the outcome.
The scene then moves away from the \textbf{arena} to a busy public food court or concession area.
A red-haired man in a checked shirt stands among people, holding a cell phone to his ear.
Beside him is a large decorative hot dog cart with the words “ HOT DOGS ” on it.
He looks upward as if following the \textbf{game} somewhere above him.
From behind the same red-haired man, a wall-mounted television is visible high above a counter area.
The television shows the basketball \textbf{game}.
Large green letters on the wall below \textbf{spell} out parts of a menu, including “ DOGS ” and other food items.
More people stand below, looking upward toward the screen.
A higher overhead view reveals a line of customers at a counter, all oriented toward the same general area, suggesting that many people in the food space are watching the end of the \textbf{game} together.
Inside a diner-like food stand, a bald man in a white apron stands near a long row of orange drink machines or dispensers.
A small television mounted above the dispensers shows the \textbf{game}.
Customers at a counter on the left also look toward it.
The aproned worker raises his hands near his face in anticipation, caught between working and watching.
Back in the \textbf{arena}, a young vendor wearing a blue apron and carrying a tray of pink drink cartons watches from the aisle, his face lifted toward the court.
Small white legal text appears along the bottom of the screen during this part, including a coverage disclaimer that is only partly legible.
The commercial briefly shows people gathered outside a storefront at night, looking through large windows at multiple televisions inside.
One man in the group holds a phone to his ear.
The same small disclaimer text continues along the bottom.
A closer view through the glass shows several adults standing outside, faces tilted up toward the screens inside, with city lights reflected in the window.
Back in the \textbf{arena}, a group of young pep-band members in matching blue “ STATE ” shirts sit among red seats with drums, a trombone, and cymbals.
A drummer holds sticks above a drum and watches intently.
The court reappears, with \textbf{players} still gathered under the high \textbf{arena} lights.
Then a close view of the hoop shows the white net hanging from a red rim above the red baseline area, with cheerleaders lined up behind the backboard.
The vendor in the blue apron is shown again, now \textbf{shouting} or cheering, clutching his tray of drinks with one hand and making a fist with the other.
The \textbf{players} and crowd \textbf{erupt}.
A blue-uniformed \textbf{player} wearing a headband throws both arms up, mouth wide open in celebration.
The scene cuts back to the diner, where the aproned worker and customers raise their arms in celebration while the television remains visible above the drink machines.
Near the basket, blue-uniformed cheerleaders duck and move under the hoop as people behind them stand and cheer.
The pep band jumps up, smiling and \textbf{shouting}, with drumsticks, a trombone, and a cymbal raised in the air.
Blue “ STATE ” basketball \textbf{players} gather in a tight celebratory huddle, grinning, \textbf{shouting}, and wrapping arms around one another.
One \textbf{jersey} back reads “ DASHO 22. ” Their faces are sweaty and joyful, with raised fists and wide smiles.
In the stands, the young fan in the “ STATE 1 ” \textbf{jersey} \textbf{celebrates} beside the tall man in the bright blue shirt.
The tall man holds up a small \textbf{flip} phone, angling it outward as if taking a picture or sharing the moment.
The young fan holds up a blue garment or sign with “ STATE 1 ” visible, his mouth open in amazement.
A close-up shows a silver Motorola \textbf{flip} phone held in someone ’s hand over a checkered diner counter.
On the phone ’s small \textbf{color} screen is an image or video of the two \textbf{celebrating} fans in the \textbf{arena}, with the word “ STATE ” visible behind them.
As the phone fills more of the view, the Motorola name appears above the screen, emphasizing the mobile device receiving or displaying the celebration.
The imagery then transitions into a clean white graphic.
A teal antenna icon and rising teal signal \textbf{bars} appear above the word “ ALLOVER ” in thin red capital letters, visually matching the spoken idea of “ more \textbf{bars} in more places. ” The signal \textbf{bars} grow to full height.
The screen changes to a white background with the AT\&T Wireless logo on the left—a teal striped globe above the words “ AT\&T Wireless”—and the red Cingular jack-shaped figure on the right.
Finally, the AT\&T globe mark enlarges and moves across the white field, filling the screen with a glossy teal \textbf{sphere}.

% matched lemmas: arena, bar, celebrate, cluster, color, erupt, flip, game, jersey, player, shout, spell, sphere, uniform
\end{textsample}
