\begin{textsample}{POS Dim 5 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_68.txt}  \label{ex:f5_pos_075}
The commercial begins in a very dark shot.
A human figure or silhouette appears faintly behind what \textbf{looks} like vertical window or door framing, but the details are difficult to make out because the frame is underlit.
It then cuts to a brightly lit exterior setting with tall stone columns and a classical building façade.
A young \textbf{man} with medium-length brown hair is shown close to the columns.
He wears a dark long-sleeved top, loose jeans, dark shoes or boots, and a red \textbf{plaid} \textbf{shirt} or fabric \textbf{tied} around his waist.
In close-up and medium shots, he \textbf{turns} his head and \textbf{gestures} with his hands.
His facial \textbf{expressions} \textbf{look} animated, with his mouth open in several frames, suggesting he is \textbf{speaking} or \textbf{reacting}, though no audio content can be inferred from the images alone.
The camera alternates between close-ups and low-angle or wider shots.
The \textbf{man} is repeatedly framed against the large vertical columns, making him appear small compared with the architecture.
He moves energetically, raising his hands near his face and outward from his body.
Some frames show motion blur or overlapping ghosted images, indicating fast movement or a stylized transition effect.
A wider shot shows him standing on a ledge or step in front of the columned building.
He then crouches down on the ledge and reaches toward the ground or toward something near his feet, though the object is not clearly visible.
After this, another close-up shows him \textbf{looking} off to the side, again with a quick, alert \textbf{expression}.
Later, he is seen in close-up with one hand near his ear or neck area, mouth open, still appearing highly animated.
A close-up follows of a hand holding small rectangular slips of paper or tickets.
The visible writing appears to include the word “ Shhh ” or a similar handwritten/printed word, but the text is blurry and not fully certain.
The scene then shows the young \textbf{man} standing beside a young woman.
She has short brown hair and wears a light-colored top under a darker sleeveless garment, possibly with a black choker necklace.
She faces the camera with an expressive \textbf{look}, while the \textbf{man} \textbf{looks} down at and holds several paper slips or cards.
They stand near the same stone-columned exterior.
Near the end, the \textbf{man} is shown alone again in a full-body wide shot on the ledge in front of the tall columns.
He faces forward, \textbf{gesturing} with both hands raised near shoulder height.
In the final frame, he remains in the same location, centered against the vertical column background, still \textbf{gesturing} animatedly.
No product, brand name, or clear slogan is visible in the sampled frames.

% matched lemmas: expression, gesture, look, man, plaid, react, shirt, speak, tie, turn
\end{textsample}
