\begin{textsample}{POS Dim 5 – 2000 – Score 11.00 – 2000/tv\_com\_2000\_115.txt}  \label{ex:f5_pos_027}
The commercial begins with a fully black screen.
At about 6.4 seconds, the scene cuts to a large indoor room that \textbf{looks} like a meeting or training space.
Multiple adults stand in two lines facing each \textbf{other} at close range.
They wear casual or business-casual clothing, and several appear to have name badges.
In the center foreground, two \textbf{men} stand face-to-face, very close together, creating a \textbf{tense} or competitive visual arrangement. \textbf{Other} pairs stand similarly behind them.
At about 18.8 seconds, the visual focus shifts to a \textbf{man} in a blue-gray \textbf{shirt} with a name badge.
He is centered in the frame and appears to be concentrating on a small stacked block tower in front of him.
A group of people crowds tightly around him from all sides.
Several hold objects near him—one person holds what \textbf{looks} like a megaphone or horn, and \textbf{others} appear to be leaning in, \textbf{watching}, \textbf{gesturing}, or \textbf{reacting}.
The central \textbf{man} ’s \textbf{expression} is \textbf{serious} and focused, while the surrounding people create a visually noisy, pressured environment.
At about 20.4 seconds, there is a close-up of the same or a similar dark-haired \textbf{man} leaning forward.
He holds one hand to his ear as if listening, and his \textbf{other} hand is near a small object or mechanism in the foreground.
His facial \textbf{expression} is intense and concentrated.
The background is blurred, with another person visible farther back, but the setting is not fully clear from the sampled frame.
At about 23.7 seconds, the \textbf{man} in the blue-gray \textbf{shirt} walks behind another \textbf{man} in a dark \textbf{suit} in a modern interior space, possibly a hallway or airport/business facility.
The \textbf{suited} \textbf{man} extends his arm toward a wall or panel, as if pressing a button or operating a control.
The blue-gray-shirted \textbf{man} follows closely behind.
At about 27.4 seconds, the commercial cuts to the exterior of a large airplane.
The plane is white and silver with red, white, and blue striping.
Bright sunlight reflects strongly off the fuselage, partially obscuring the lettering.
The visible letters suggest the beginning of “ American. ” In the final frame at about 29.1 seconds, the side of the airplane is shown more clearly.
Large red text reads “ American ” across the fuselage.
In the upper-left corner, white on-screen text reads “ AA.com. ” A small circular blue logo appears near the lower-right corner of the image.
The sky is visible behind the aircraft, and the shot functions as the closing brand/product image.

% matched lemmas: expression, gesture, look, man, other, react, serious, shirt, suit, tense, watch
\end{textsample}
