\begin{textsample}{POS Dim 5 – 2000 – Score 10.00 – 2000/tv\_com\_2000\_28.txt}  \label{ex:f5_pos_029}
The commercial opens on a nearly black frame, with no clear visual detail visible.
It then cuts to an exterior view of a large Best Buy store.
The building has a dark blue façade and a prominent yellow price-tag-shaped “ BEST BUY ” sign.
A tall yellow sign or inflatable-style marker with black lettering is also visible near the entrance area, though the text is partially blurred.
The scene moves inside the store.
A person in a large blue-and-yellow Best Buy price-tag costume walks or dances on the glossy black-and-white floor.
Nearby shoppers and \textbf{employees} stand around ; one person raises an arm as if cheering or signaling.
The store interior is brightly lit with rows of merchandise and checkout or display areas in the background.
Several quick shots show customers interacting with store \textbf{staff} and products : - A \textbf{man} in a \textbf{suit} and another \textbf{man} stand near a display or device, \textbf{looking} at a screen or equipment. - A close-up of a small screen shows a smiling \textbf{man} ’s face, suggesting a video or camera display. - A wider store shot shows customers and a Best Buy \textbf{employee} in a blue \textbf{shirt} \textbf{talking} near an appliances area ; an “ APPLIANCES ” sign is visible overhead. - Another shot shows a customer \textbf{speaking} with an \textbf{employee} near rows of computer monitors. - Aisles of packaged products are shown from above or at an angle, with shoppers browsing. - A Best Buy \textbf{employee} in a blue \textbf{shirt} assists a woman at a large computer or monitor display. - Another \textbf{employee} and customer interact near a display area marked with large “ DVD ” signage.
The commercial continues with more energetic in-store visuals.
A child or young person sits in or leans over a large yellow-and-black display structure shaped like a Best Buy tag or themed product station. \textbf{Other} shoppers and \textbf{employees} are visible in the background.
Near the checkout or service area, a yellow shopping basket with the Best Buy logo appears in the foreground.
A customer holds or places a red-and-black \textbf{plaid} garment or item near the basket.
A smiling Best Buy \textbf{employee} in a blue \textbf{shirt} stands behind the counter area, interacting with the customer.
The background includes product displays and signage, though much of the smaller text is unclear.
The final sequence returns to the exterior of the Best Buy store.
There is a close-up and then a wider view of the yellow “ BEST BUY ” sign mounted high on the blue building.
Large white on-screen text appears near the bottom right reading “ Now Open. ” In the final frame, the entrance with glass doors is visible below the sign, and small text at the lower left reads “ {\EmojiFont ©} 2000 Best Buy. ”

% matched lemmas: employee, look, man, other, plaid, shirt, speak, staff, suit, talk
\end{textsample}
