\begin{textsample}{POS Dim 5 – 1990 – Score 11.00 – 1990/tv\_com\_1990\_10.txt}  \label{ex:f5_pos_073}
The commercial opens on a black frame, then cuts to a very bright, almost overexposed white setting.
An elderly \textbf{man} with gray hair, wearing a blue jacket, is shown from behind and then from the front as he faces another \textbf{older} \textbf{man} behind a white counter or desk.
The \textbf{man} behind the counter wears a white \textbf{shirt} and \textbf{tie} and has an open book or ledger in front of him.
Beside him is a white mug with bold black text reading : “ Do I \textbf{Look} Like I Care. ” The shots alternate between the \textbf{man} behind the counter and the elderly \textbf{man} in blue, suggesting an exchange, though no dialogue is visible. \textbf{Other} people are visible behind the elderly \textbf{man}, partially out of focus.
The setting remains white and misty, with soft lighting and very little background detail.
The scene then expands to a wide view : a long line of people stretches far into the distance through a white, cloudlike space.
The queue includes people in varied outfits, such as a \textbf{man} in a black \textbf{suit}, people in colorful casual clothing, a person in fencing gear, and \textbf{others} in costumes or \textbf{uniforms}.
The camera cuts closer to the line, showing several people waiting in the misty environment.
A close-up shows feet standing in the foglike floor.
The elderly \textbf{man} in blue \textbf{turns} and \textbf{looks} to the side, as if \textbf{reacting} to the line behind him.
A close-up then shows a \textbf{man} in a green cap and purple \textbf{shirt} holding and eating from a candy bar or snack, though the wrapper details are not fully clear in that frame.
The commercial then cuts to a product card on a white background.
A Snickers bar is centered with the visible brand name “ SNICKERS. ” Beneath it, black text reads : “ Really hungry?
Why wait? ” After the product card, the scene returns to the bright white counter area.
A Black \textbf{man} in a dark \textbf{suit} and an elderly woman in a green dress with a white \textbf{apron} stand in front of a white-uniformed \textbf{older} \textbf{man} behind the counter.
A small object with green coloring sits on the counter between them.
The final frame holds on this white, gate-like counter setting with the three figures facing one another.

% matched lemmas: apron, look, man, old, other, react, shirt, suit, tie, turn, uniform
\end{textsample}
