\begin{textsample}{POS Dim 5 – 1990 – Score 32.00 – 1990/tv\_com\_1990\_75.txt}  \label{ex:f5_pos_002}
A \textbf{stark} white surface with horizontal seams fills the screen.
A thin dark line appears across it, then a shiny compact disc rises into view.
The disc is shown large and centered, its reflective surface \textbf{shimmering} in bright pink, orange, red, and pale green around a clear center \textbf{hole}.
The scene shifts to a futuristic white room with a gridded floor, white paneled walls, and two sculptural red lounge chairs placed symmetrically on either side.
A young man in a white top is seen from behind at the center of the room.
His brown hair \textbf{whips} forward dramatically, as if something powerful is rushing toward him or through him.
When he is no longer in the center, a black rectangular \textbf{game} system or monitor-like object is visible ahead, \textbf{suspended} or displayed inside a vertical column of pale blue light between the two red chairs.
The image changes to video \textbf{game} \textbf{footage} from a science-fiction cockpit view.
A gray, cratered or metallic landscape stretches toward an orange sky.
Instrument panels and small screens line the bottom edge.
Bright purple laser beams fire toward blocky structures, which \textbf{erupt} into large orange and yellow explosions that fill more and more of the screen.
Back in the white room, the young man is now reclined in a red chair, seen from above.
He wears white clothing, his hair stands wildly upward, and he smiles with wide-eyed excitement.
Orange flame-like \textbf{blasts} stream out horizontally from both sides of his head near his ears, \textbf{exaggerating} the idea that the \textbf{game} experience is overwhelming.
Another white surface appears with a horizontal slit, and a second compact disc rises into view.
This one glows mostly blue and green, with a pale highlight at the top.
A different young \textbf{player} appears in a padded-looking white room.
This person is youthful, dressed entirely in white, including a soft white cap, and sits in a bright green chair.
They hold a black wired \textbf{game} \textbf{controller} with both hands, leaning forward and grinning while \textbf{playing}.
A sequence of \textbf{game} images follows.
First, a motorcycle \textbf{racing} \textbf{game} shows riders speeding down a city street between blocky buildings.
A yellow vehicle is ahead, and a \textbf{game} display along the bottom includes labels \textbf{such} as “ Player 1, ” \textbf{numbers}, \textbf{colored} status \textbf{bars}, and the name “ Pearl. ” Then a soccer \textbf{game} appears in a \textbf{stadium}, with \textbf{players} in \textbf{colored} \textbf{uniforms} running across a green field under a blue sky.
Next, a golf \textbf{game} shows a golfer standing by water and grass, with on-screen text including “ Delacruz, ” “ 1st stroke, ” “ 506 yards, ” “ 4 mph, ” “ Hole 18, ” and “ Par 5. ” Another science-fiction \textbf{game} view shows a craft or platform moving through a gray industrial corridor with glowing orange-red elements.
The white padded room returns from a high angle.
The \textbf{player} in white stands near the green chair, still holding the wired \textbf{controller}.
A black console sits on the floor to the left, with the \textbf{controller} cord trailing across the white floor.
In front of the \textbf{player}, a section of the white wall is visibly cracked in a jagged pattern, as if damaged by the intensity of the play.
A third compact disc appears, this time with purple, pink, and blue reflections around its center.
Another young man, also dressed in white, plays with a black wired \textbf{controller} in a clean white space.
He has brown hair parted at the center and looks intensely focused, holding the \textbf{controller} close to the viewer.
Behind him are white shelves or alcoves containing pale disc-like shapes.
More \textbf{game} \textbf{footage} follows.
A \textbf{fighting} \textbf{game} shows two martial-arts \textbf{characters} battling on a red and gold platform in front of large red columns, snowy mountains, and an East Asian-style building. \textbf{Health} \textbf{bars} stretch across the top of the screen, with a \textbf{timer} reading “ 96. ” One fighter kicks toward the other.
A large animated martial artist then appears against a black background : first as a white silhouette, then in full \textbf{color}.
He is muscular, with short brown hair, a torn white gi, red wrist wraps, and a guarded fighting pose.
A monster truck \textbf{game} appears next.
A large truck with oversized tires drives across a rough dirt track under a blue sky, then tips up and \textbf{flips} dramatically.
An American \textbf{football} \textbf{game} follows from an overhead view : small \textbf{players} in red and white \textbf{uniforms} \textbf{cluster} and scatter on a green field near yellow goalposts, with the crowd visible beyond the end \textbf{zone}.
Then a driving \textbf{game} is shown from inside a car, looking over a dashboard and steering wheel onto a curving road bordered by guardrails and rocky hills.
The brown-haired young man in white reappears holding the \textbf{controller}.
His face is comically \textbf{distorted}, with enlarged eyes and an \textbf{exaggerated} mouth, as if the \textbf{game} ’s graphics or intensity have warped him.
Then the \textbf{viewpoint} is low, looking up past his hands and \textbf{controller}.
His head seems to detach and \textbf{float} or fall away from his body, moving upward and then off into the room.
Finally, the lower half of the same \textbf{player} ’s body is seen sitting in a bright yellow chair, still holding the \textbf{controller}.
The black cord lies in a loose curve across the white floor.
His head rolls or slides into the foreground on the carpet, separated from the body, but still animated and smiling.
In the background, his headless body remains seated in the yellow chair with the \textbf{controller}, while his face in the foreground looks out with a dazed, pleased expression.

% matched lemmas: bar, blast, character, cluster, color, controller, distorted, erupt, exaggerate, exaggerated, fight, flip, float, footage, football, game, health, hole, number, player, playing, racing, shimmer, stadium, stark, such, suspend, timer, uniform, viewpoint, whip, zone
\end{textsample}
