\begin{textsample}{POS Dim 5 – 2020 – Score 12.00 – 2020/tv\_com\_2020\_2.txt}  \label{ex:f5_pos_037}
The commercial opens with a tight close-up of a \textbf{bald}, middle-aged \textbf{man} in a black \textbf{suit}, white \textbf{shirt}, and black \textbf{tie} against a plain white background.
His face is expressive, and he appears to be \textbf{addressing} the camera.
The scene then \textbf{widens} to a bright white bathroom.
The same \textbf{man} is kneeling beside an open toilet, wearing bright pink rubber gloves while still dressed in the \textbf{suit}.
Around him are cleaning supplies : a blue bucket filled with cloths and bottles, a blue towel hanging on the bathtub, a toilet paper roll, and a small potted plant on the toilet tank.
He holds a spray bottle and a cleaning cloth or sponge.
The bathroom shot continues, with the \textbf{man} positioned beside the toilet.
A transparent bottle is visible on the left side of the frame, suggesting a product close-up or a split-screen transition, while the \textbf{man} remains on the right beside the toilet.
A split-screen-style visual follows : on the left is a close-up of a dirty or stained surface with a round dial or gauge-like object ; on the right, the \textbf{man} is still in the bathroom near the toilet, wearing the pink gloves and holding cleaning items.
The setting then changes to a different room with a white brick wall.
A \textbf{globe} and a \textbf{table} lamp stand on the left, while a metal safe or cabinet is open on the right and appears filled with many paper items.
A spray bottle sits on top of the cabinet.
The \textbf{man}, still in his \textbf{suit}, leans in from the right side of the frame, \textbf{looking} toward the camera.
Next, the \textbf{man} appears beside a framed portrait of himself.
He holds a spray bottle and a cloth, as if cleaning the glass or frame.
The left edge of the frame shows part of another close-up image, including a hand and wristwatch, suggesting another split-screen or transitional montage.
The commercial returns to the bathroom, where the \textbf{man} is now lying in a bathtub filled with many small paper slips or money-like pieces.
He is still wearing the black \textbf{suit}, with a blue patterned shower cap on his head.
Towels and bathroom shelving are visible nearby.
A product display then appears on a clean white background.
Four cleaning products are lined up : three spray bottles containing blue, pink, and yellow liquids, and a clear pump bottle.
Above them is the word “ BLUELAND ” in large blue lettering, and below it is a dark rectangular button reading “ SHOP NOW. ” Small tablet-like objects or packaging pieces are placed in front of the bottles.
The smaller text on the product labels is not clearly readable.
The final shots return to the bathroom.
The \textbf{man} kneels beside the open toilet again, wearing pink gloves.
He sprays or holds a pink liquid spray bottle and uses a blue cloth near the toilet seat.
In the last frame, he faces the camera while holding the spray bottle in one hand and the blue cloth in the \textbf{other}, with the bucket of cleaning supplies still visible on the floor nearby.

% matched lemmas: address, bald, globe, look, man, other, shirt, suit, table, tie, widen
\end{textsample}
