\begin{textsample}{POS Dim 5 – 2010 – Score 11.00 – 2010/tv\_com\_2010\_94.txt}  \label{ex:f5_pos_043}
A teal-blue title card appears with the white AT\&T globe logo and “ AT\&T ” centered on screen.
Beneath it, smaller white text reads “ att.com/unlimited. ” The scene then shifts into a dark, \textbf{glowing} virtual environment.
Everything has a futuristic, weightless look, with orange, pink, and blue neon lines, \textbf{floating} geometric blocks, and soft haze.
A \textbf{glowing} orange disc, like a small flying puck with circular rings, spins through the space.
An adult man with long dark hair, a full beard, glasses, and a pale pink shirt reaches toward it with one hand.
His body is stretched out horizontally as if \textbf{floating} in zero gravity, and his face is open-mouthed, \textbf{anxious} or surprised.
The disc drifts away from his outstretched palm.
Around him, the \textbf{arena} is filled with luminous orange strips, triangular patterns, and dark metallic surfaces.
The view widens to reveal a large circular goal structure or scoreboard area, with several \textbf{players} \textbf{suspended} in the air around it.
Some appear as ordinary people in casual clothing, while others look like sleek armored \textbf{game} avatars in blue or red suits with \textbf{glowing} accents and helmeted faces.
A digital scoreboard near the top shows a blue “ 02 ” on one side and an orange “ 00 ” on the other.
Small white disclaimer text appears near the bottom in some of these \textbf{arena} views.
The \textbf{players} hover in different directions around circular target-like rings and triangular panels, reinforcing the impression that there is no up or down.
An adult woman with dark hair tied back, wearing a pink or mauve long-sleeved top and dark pants, flies forward through the neon \textbf{arena}.
She is angled horizontally, arms bent as if swimming through the air, with a \textbf{focused}, excited expression.
Behind and around her, armored figures streak past, leaving blue light trails.
She moves among black \textbf{floating} cubes outlined with glowing orange triangles.
The action accelerates as the woman and several armored \textbf{players} chase through the \textbf{arena}.
Blue and orange trails cut across the space, and the \textbf{glowing} disc moves between them.
The man reappears in close view, still \textbf{floating} belly-down with his arms spread wide.
His hair lifts away from his head as if weightless, and his expression shifts between alarm and determination.
The \textbf{arena} ’s \textbf{colors} change more toward blue and magenta.
The woman glides close to a large dark wall or structure edged in pink light, her face tense and concentrated.
She brushes near it and turns her head, while a \textbf{glowing} device or armored \textbf{player} passes close behind her shoulder.
Nearby, two or more armored figures collide or grapple around the orange-glowing disc.
Bright cyan triangular outlines and a honeycomb-like wall pattern fill the background.
A red-armored humanoid \textbf{player} with a smooth reflective helmet \textbf{floats} in the foreground.
Its suit has small orange and blue \textbf{glowing} details and a letter-like marking on the chest.
Other armored \textbf{players} move behind it, one carrying or reaching toward the orange disc.
The scene remains crowded with \textbf{suspended} cubes and triangular neon outlines.
The woman then appears near a black block with bright blue triangular outlines.
She reaches upward and catches or bats the \textbf{glowing} orange disc above her head.
Her mouth is open in a triumphant or excited expression as she stretches one arm high.
A moment later, the disc flies toward the large illuminated goal area.
At the goal, several armored \textbf{players} converge in front of a bright blue, diamond-shaped panel with a faint triangle symbol in the center.
The scoreboard still shows blue “ 02 ” and orange “ 00 ” nearby.
Hands and bodies reach in from different directions as the \textbf{glowing} disc strikes the center.
The screen floods with warm light, suggesting a successful score.
The \textbf{arena} pulls back to a wider view.
Large white letters on an orange-lit board read “ GOAL. ” \textbf{Players} drift and tumble around the scoring area while red-orange light beams spread from the goal.
The woman \textbf{floats} in the middle distance with one arm raised, as if \textbf{celebrating}.
Around her, helmeted avatars and casual-clothed human figures continue to hang weightless among the neon cubes and circular structures.
The bearded man is shown from above beneath a large black pyramid-like block outlined with bright blue triangular lines.
He reaches up with one hand, still looking uneasy as he \textbf{floats} over a platform edged in pink light.
The final views settle on the full futuristic \textbf{arena} : a central platform, many suspended black cubes with \textbf{glowing} blue triangle outlines, pink circular side structures, and scoreboards at the top.
The blue side reads “ 02, ” while the orange side now reads “ 03, ” indicating the orange team has pulled ahead.
The commercial ends visually inside this luminous zero-gravity \textbf{game} world, emphasizing the immersive virtual experience rather than showing the headset itself.

% matched lemmas: anxious, arena, celebrate, color, float, floating, focused, game, glowing, player, suspend
\end{textsample}
