\begin{textsample}{POS Dim 5 – 1980 – Score 11.00 – 1980/tv\_com\_1980\_11.txt}  \label{ex:f5_pos_063}
The commercial begins on a black screen.
It then cuts to a softly lit interior that \textbf{looks} like an office or meeting room, with large windows, blinds, framed wall art, a \textbf{table} lamp, papers, cups, and several adults gathered around a \textbf{table}.
A curly-haired woman in a light blouse stands behind or beside the seated people.
An elderly white-haired woman with glasses and another woman with short hair and dark-framed glasses sit at the \textbf{table}, \textbf{looking} down at papers or objects in front of them.
The next shot moves into a close-up of the short-haired woman with dark-framed glasses.
Her face is partly obscured by someone ’s shoulder in the foreground.
She appears to be \textbf{looking} downward, focused on something off-screen or on the \textbf{table}.
The scene returns to the meeting room.
More people are visible around the \textbf{table}, including a \textbf{man} in glasses in the background and a dark-haired woman on the right.
The curly-haired woman in the light blouse stands and \textbf{gestures} with her hands, as if \textbf{addressing} or demonstrating something to the group.
The seated woman with dark-framed glasses remains focused on the \textbf{table}.
A close-up follows of the elderly white-haired woman with glasses.
She \textbf{looks} sideways past someone in the foreground ; her \textbf{expression} is reserved or \textbf{attentive}.
The commercial then cuts to a product shot : a white bottle or container with a blue cap on a shelf.
The label clearly reads “ SURE, ” with diagonal colored stripes across the front. \textbf{Other} glass or toiletry-like containers are around it, and a white towel is visible at the side.
Back in the meeting-room setting, the curly-haired woman stands behind the seated woman and raises both arms outward while \textbf{gesturing}.
At the far left edge, a hand or arm holds up the same white “ SURE ” container, partly visible.
People around the \textbf{table} continue to \textbf{look} at papers or toward one another.
A close-up shows a \textbf{man} wearing round glasses and a dark jacket.
He \textbf{looks} forward with a \textbf{serious} or evaluative \textbf{expression} ; reflections are visible in his lenses.
Another shot shows the curly-haired woman leaning over a \textbf{partition} or \textbf{table} edge toward \textbf{other} people.
A \textbf{man} with glasses stands or sits nearby, and another person with dark hair is partly visible.
In the background, a sign with the partial letters “ LIDE ” can be seen, but the full word is not visible in the frame.
The setting then shifts to a blurred view of shelving or a cabinet area.
The camera appears to pass by or pan across shelves.
The “ SURE ” bottle is visible again among \textbf{other} bottles and containers, with its white body, blue cap, and diagonal label design.
The final frame shows a group of people standing together in a crowded indoor space.
The curly-haired woman now stands near the center foreground wearing a light pink blouse and smiling slightly.
The elderly woman and a \textbf{man} with glasses are nearby, with more people behind them.
Large white text reading “ SURE ” is overlaid across the lower center of the image.
No \textbf{spoken} words, music, or slogans are visible or inferable from the frames alone.

% matched lemmas: address, attentive, expression, gesture, look, man, other, partition, serious, speak, table
\end{textsample}
