\begin{textsample}{POS Dim 5 – 1970 – Score 14.00 – 1970/tv\_com\_1970\_104.txt}  \label{ex:f5_pos_042}
The commercial begins with a very dark, nearly black frame with only faint blue-purple edges visible.
It then cuts to a softly lit shot inside what appears to be an aircraft cabin or service area.
A person wearing a large headset is shown in profile on the left, silhouetted against a bright window.
Another person ’s face or shoulder is partially visible in soft focus on the right edge.
The image has a hazy, backlit quality.
Next, a blue title card appears with large white serif text reading : “ United ’s Friendship Service. ” The background is dark blue with indistinct shapes behind the lettering.
The scene shifts to an aircraft passenger cabin.
A middle-aged \textbf{male} flight attendant or service \textbf{employee} is seated or leaning beside a seat, putting on or adjusting a headset with both hands.
He wears a light-colored striped \textbf{shirt} and \textbf{tie}.
The \textbf{seating} around him suggests rows of airplane seats.
A wider cabin view follows.
The same \textbf{man} is visible near the aisle or beside a seat, wearing the headset with a microphone positioned near his mouth.
Several passengers are visible in the background, seated in rows.
Reflections or glass-like overlays make the image \textbf{look} layered, as if shot through a \textbf{partition} or window.
The next shot is a close-up of a different \textbf{male} crew \textbf{member} or \textbf{employee}, also wearing a headset with a microphone.
He has a \textbf{mustache} and is smiling slightly.
The background again shows aircraft \textbf{seating} and passengers, though it is soft and partially obscured by reflections.
The commercial then cuts to an \textbf{older} woman passenger with white hair and dark-framed glasses.
She is seated in an airplane seat and appears to be smiling or \textbf{speaking}.
She wears earrings and a dark outfit with a patterned scarf or \textbf{collar}.
The cabin seat back is visible behind her.
Another shot shows a \textbf{man} seated in the cabin, viewed from behind and in profile as he \textbf{turns} his head back over his shoulder.
He appears to be the earlier striped-shirted \textbf{man} or a similarly dressed passenger/employee.
The top of a seat back is visible in the foreground, and the cabin interior is softly lit.
Near the end, a blue title card appears with large white serif text reading : “ United to 113 cities. ” The background is a solid or gradient blue.
The final frame is black.

% matched lemmas: collar, employee, look, male, man, member, mustache, old, partition, seating, shirt, speak, tie, turn
\end{textsample}
