\begin{textsample}{POS Dim 5 – 2020 – Score 10.00 – 2020/tv\_com\_2020\_3.txt}  \label{ex:f5_pos_040}
The commercial opens inside a bright home entryway or mudroom.
An exterior door stands open to a sunny garden outside.
On the left is a built-in storage area with hanging \textbf{coats}, bags, shoes, and small household items.
A woman enters through the open door carrying a large white tote or fabric bag.
She appears hurried or strained, holding the bag close to her body.
The next shot moves into a close-up of the woman.
She is indoors in front of the \textbf{coat} area.
Her face is contorted as if upset, crying, or \textbf{reacting} strongly to something unpleasant.
She clutches the white bag near her chest.
The scene then cuts to a close-up of a \textbf{man} standing nearby in the same entryway.
He has a moustache and wears a short-sleeved polo \textbf{shirt}.
His eyes are closed tightly and his facial \textbf{expression} suggests discomfort or distaste.
The open door and hanging \textbf{coats} remain visible behind him.
A following close-up shows an elderly woman at the doorway area.
She wears a red cardigan and a colorful beaded necklace.
She \textbf{looks} to the side with \textbf{widened} eyes and a \textbf{tense} or \textbf{concerned} \textbf{expression}.
The open glass-paneled door and greenery outside are visible behind her.
A wider shot then shows the group together in the entryway.
The woman stands to the left, covering part of her face with her hand while holding or standing near the bag.
The \textbf{man} stands center holding the large white bag in both hands.
The elderly woman stands behind him, and a young boy in a turquoise \textbf{shirt} stands to the right, \textbf{looking} toward the adults.
The storage area with \textbf{coats}, a scooter, bags, shoes, and the open door remain in view.
The next shot cuts to a close-up of a closet rod with hanging clothes.
A hand places or hangs a white moisture-absorbing product bag on the rod.
The product label is clearly visible : “ DampRid ” in red and blue lettering.
The bag has a white upper portion and a transparent lower chamber.
In the final frame, the DampRid bag hangs among clothing, including a \textbf{tan} knit garment and a denim item.
The lower transparent chamber contains blue liquid or gel-like material.
On-screen text appears to the right of the product in bold white letters : “ Traps excess moisture. ” The shot emphasizes the product hanging in the closet and its stated function.

% matched lemmas: coat, concerned, expression, look, man, react, shirt, tan, tense, widen
\end{textsample}
