\begin{textsample}{POS Dim 5 – 2020 – Score 19.00 – 2020/tv\_com\_2020\_8.txt}  \label{ex:f5_pos_031}
The commercial unfolds as a rapid montage, beginning and ending with a bright living-room setting and cutting between many scenes from different programs. 1. **Opening living-room shot** : A person, later shown more clearly as a Black \textbf{man}, sits on a light-colored sofa in a bright, minimalist room.
He wears a loose white hoodie and pale \textbf{pants}.
The first frame is cropped so his face is mostly out of view ; his hands are held in front of his body as if \textbf{gesturing}. 2. **Restaurant/kitchen setting** : The scene cuts to a professional kitchen or \textbf{restaurant} prep area.
Two people in white \textbf{shirts} and dark \textbf{aprons} stand near a counter under a large overhead light.
Stainless-steel counters and shelves are visible.
At the bottom, the Disney+ and Hulu logos appear with the title **“The Bear.”** 3. **Close-up of a \textbf{man} in the kitchen** : A \textbf{bearded} \textbf{man} in dark clothing is shown in close-up, \textbf{looking} downward or toward someone off-camera.
Part of another person ’s head is visible in the foreground.
The bottom text still shows Disney+ and Hulu with **“The Bear.”** 4. **Two women on a couch** : The montage cuts to a domestic living-room/kitchen space.
An \textbf{older} woman in blue pajamas and glasses sits beside a younger red-haired woman in pink pajamas.
They hold round containers or bowls.
The lower text reads Disney+ and Hulu with **“Freakier Friday.”** 5. **Office/interview room** : A blonde woman in a leopard-print \textbf{coat} sits at a desk or interview \textbf{table} facing someone whose back is visible in the foreground.
Behind her are people in a room with glass \textbf{partitions} and blinds.
Bottom text : Disney+ and Hulu with **“High Potential.”** 6. **Nighttime exterior/low light** : The same blonde woman appears outdoors or in a dark setting, wearing a bright turquoise fuzzy \textbf{coat}.
She \textbf{looks} upward or to the side.
Bottom text remains Disney+ and Hulu with **“High Potential.”** 7. **Man running outdoors** : A \textbf{man} in a white dress \textbf{shirt} and loosened dark \textbf{tie} runs down a suburban street in daylight.
Houses and trees line the background.
Bottom text : Disney+ and Hulu with **“Paradise.”** 8. **Green superhero figure in a kitchen-like environment** : A large green \textbf{male} figure with glasses, wearing a gray \textbf{shirt} and dark robe or cardigan, stands in what \textbf{looks} like an industrial kitchen or storage area.
His hands are raised in front of him.
A woman stands in the background.
Bottom text : Disney+ and Hulu with **“Avengers : Endgame.”** 9. **Classroom or school interior** : A smiling woman with curly hair wears a pale yellow sweatshirt. \textbf{Other} people and window blinds are visible behind her.
Bottom text : Disney+ and Hulu with **“Abbott Elementary.”** 10. **Dark science-fiction-looking close-up** : A woman with short dark hair is shown in a dim, blue-toned environment, \textbf{looking} intently forward.
Bottom text : Disney+ and Hulu with **“Alien : Earth.”** 11. **Woman in white bonnet and red clothing** : A close-up shows a woman wearing a large white bonnet and red garment in a dark, high-contrast setting.
She \textbf{looks} \textbf{serious}.
Bottom text : Disney+ and Hulu with **“The Handmaid ’s Tale.”** 12. **Reality/interview-style couch shot** : A woman with long light-brown hair sits on a pale sofa in a bright white room, \textbf{gesturing} with one hand.
She wears a gray top and a cross necklace.
Bottom text : Disney+ and Hulu with **“The Secret Lives of Mormon Wives.”** 13. **Return to living-room man** : The montage returns to the Black \textbf{man} in the white hoodie on the light sofa.
He is now fully visible from the waist up, \textbf{gesturing} with one arm.
The setting is airy and \textbf{neutral}, with a lamp, pillows, and plants in the background. 14. **Woman eating from a bowl** : A woman in a beige cardigan over a white top sits in a bright interior, holding a bowl or cup and \textbf{looking} downward with a dissatisfied or skeptical \textbf{expression}.
Bottom text : Disney+ and Hulu with **“The Secret Lives of Mormon Wives.”** 15. **Living-room \textbf{man} again** : The \textbf{man} in the white hoodie appears again on the sofa, leaning forward and smiling or \textbf{speaking} silently.
The same bright living-room background is visible. 16. **Streaming-brand transition** : The image cuts to a dark teal/blue gradient screen with a glowing animation forming the **Disney+** logo.
Faint text beneath is partially visible but not fully readable in this frame. 17. **Final end card** : The final frame shows the **Disney+** logo on the left and the **hulu** logo in green on the right against a teal gradient background.
Centered below them is the text : **“All of these and more now streaming.”** Near the bottom appears **“DisneyPlus.com”** with small legal text beneath it.

% matched lemmas: apron, bearded, coat, expression, gesture, look, male, man, neutral, old, other, pant, partition, restaurant, serious, shirt, speak, table, tie
\end{textsample}
