\begin{textsample}{POS Dim 5 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_37.txt}  \label{ex:f5_pos_076}
The commercial opens with a dark, grainy view of a snow-covered mountain peak under heavy clouds.
The image is low-lit and bluish-gray, emphasizing a cold, high-altitude setting.
It then dissolves into an indoor interview-style shot of an \textbf{older}, white-haired \textbf{man} seated in a room.
A lamp and interior furnishings are visible behind him.
The mountain image remains faintly superimposed over his face and body during the transition.
On-screen text identifies him as : “ Walt McConnell Everest Expedition Leader ” The \textbf{man} is shown in several close and medium shots, wearing a \textbf{collared} \textbf{shirt} under a sweater or jacket.
He appears to be \textbf{speaking} or \textbf{gesturing}, though no audio content can be inferred.
The visuals repeatedly layer his face with snowy mountain scenes and expedition imagery, creating a double-exposure effect.
The montage continues with snowy mountain-camp or climbing imagery overlaid on the \textbf{man} ’s profile.
A product package begins to appear in the layered visuals : a blue box labeled “ Alka-Seltzer Plus Cold Medicine. ” The box is shown alongside or superimposed over the \textbf{man} ’s face and background imagery.
A clearer product shot follows : the blue “ Alka-Seltzer Plus Cold Medicine ” box appears large in the frame, with “ Fast Relief ” visible on a red label.
A small line of text at the bottom reads “ Use only as directed. ” The box is layered over a figure in cold-weather climbing gear holding a pole, with a map or snowy expedition background behind it.
The next shots show close-ups of a climber ’s lower legs and boots moving through snow, with a pole visible.
Snow is kicked up around the boots.
The imagery remains blue-toned and cold-looking.
The commercial returns to layered close-ups of the white-haired \textbf{man} ’s face, now combined with snowy climbing scenes and a climber ’s red glove or clothing.
His \textbf{expression} changes slightly between frames, but the sampled images do not show enough to describe a complete action beyond apparent \textbf{talking} or \textbf{reacting}.
Another product overlay appears, again showing the “ Alka-Seltzer Plus Cold Medicine ” box large across a snowy climbing background.
The product is visually \textbf{tied} to the mountaineering imagery through superimposition and dissolves.
The final frame changes to a clean pack shot against a dark blue-purple studio background.
A green box is centered and clearly labeled : “ Alka-Seltzer Plus Night-Time Cold Medicine ” Additional visible text includes “ Fast Relief ” on a red label and a red burst stating “ Contains No Alcohol. ” Small manufacturer or legal text appears at the lower right but is too small to read clearly.

% matched lemmas: collar, expression, gesture, man, old, react, shirt, speak, talk, tie
\end{textsample}
