\begin{textsample}{POS Dim 5 – 2010 – Score 13.00 – 2010/tv\_com\_2010\_43.txt}  \label{ex:f5_pos_011}
The commercial opens in a bright suburban driveway outside a beige house.
A small mint-green Fiat 500 is parked on the driveway.
A \textbf{man} stands to the left near the car, while a young woman in a pink cardigan, light blue \textbf{shirt}, and light \textbf{pants} comes from the house toward the car.
The lawn, porch, windows, and plants make the setting \textbf{look} residential and well kept.
The next shots focus on the \textbf{man} in the driveway area, standing near hedges and smiling broadly, and then on the young woman approaching the mint-green car.
She \textbf{looks} pleased and animated as she reaches the front passenger-side area of the car.
A closer shot shows her smiling at the vehicle, with the house porch behind her.
The scene then cuts sharply to a different location : an urban/industrial street or parking area under or near an overpass.
A black sedan is shown in a parking space, but it is badly stripped : the wheels are missing, the car rests on blocks, and the front bumper/grille area is removed or incomplete.
A \textbf{man} in a gray \textbf{suit} stands nearby, \textbf{looking} toward the damaged car.
The background includes brick and industrial buildings, a stop sign, traffic, and stacked pallets.
Another brief shot shows an \textbf{older} \textbf{man} wearing glasses and a green \textbf{apron} standing in a red-brick doorway, holding a cloth or towel.
He appears to be \textbf{watching} from the doorway near trash bags and dumpsters.
The commercial then returns to the stripped black car and the \textbf{suited} \textbf{man}, who \textbf{gestures} with his hands in apparent frustration or disbelief.
The ad intercuts between the two situations : the suburban driveway with the intact mint-green Fiat and the young woman ’s delighted \textbf{reaction}, and the urban scene with the stripped black sedan and the \textbf{suited} \textbf{man} ’s agitated \textbf{gestures}.
The driveway \textbf{man} is also shown smiling near the mint-green car.
The \textbf{older} apron-wearing \textbf{man} is shown again in the brick doorway, appearing to \textbf{speak} or \textbf{react}, though no audio is available.
As the intercutting continues, the young woman near the Fiat becomes more visibly excited, smiling and then laughing with her mouth open.
The \textbf{suited} \textbf{man} by the stripped car \textbf{gestures} emphatically, raising and moving his hands as he faces the vehicle.
The black sedan remains stationary on blocks throughout these shots, with visible missing wheels and front parts.
Near the end, the setting changes to the entrance of a State Farm office.
A \textbf{man} in the \textbf{plaid} \textbf{shirt} enters or approaches a glass doorway with a red “ StateFarm ” sign visible inside.
In the next exterior shot, the plaid-shirted \textbf{man} and the young woman are outside the glass-fronted office near a ramp and railing.
The red State Farm signage is visible through the windows.
The final frame is a solid red screen with centered white text reading : “ Here to help life go right. ” A small line of fine print appears near the bottom, but it is too small to read clearly in the sampled frame.

% matched lemmas: apron, gesture, look, man, old, pant, plaid, react, reaction, shirt, speak, suit, watch
\end{textsample}
