\begin{textsample}{POS Dim 5 – 1950 – Score 7.00 – 1950/tv\_com\_1950\_107.txt}  \label{ex:f5_pos_089}
The commercial is in black and white and appears to centre on automobile travel. - **Opening frame (0.000s):** A car is shown from a distance driving along a winding road in a mountainous or rocky landscape.
The road curves through steep terrain, with cliffs or dense dark vegetation on both sides.
The vehicle is small in the frame, emphasizing the road and scenery. - **Around 11.9s:** The scene cuts to a close-up of a woman seated inside what appears to be a vehicle.
The background is blurred, with light-colored seat backs visible behind her.
She faces forward but \textbf{looks} slightly to the side, with an animated facial \textbf{expression}.
The image has some motion blur or double exposure, suggesting either movement or a transition effect. - **Around 20.1s:** The commercial cuts to a close-up of a \textbf{man}, also seated inside the vehicle.
He is wearing a \textbf{suit} and \textbf{tie} and faces directly toward the camera.
Seat backs and indistinct figures or interior shapes are visible behind him.
His \textbf{expression} is \textbf{composed}, with a slight smile or confident \textbf{look}. - **Around 26.2s:** The woman appears again in close-up inside the same or similar vehicle interior.
She is framed frontally, with blurred interior elements behind her.
Her \textbf{expression} is more \textbf{tense} or exaggerated in this sampled frame, and there is visible blur/ghosting, possibly from movement or an overlapping transition. - **Final frame (58.0s):** The viewpoint shifts to inside a vehicle \textbf{looking} forward through the windshield.
A road stretches ahead under trees, with a railing or fence visible to the right.
The driver is seen only as a dark silhouette on the left.
Windshield wipers and the dashboard area are visible in the foreground.
The car appears to be moving along a tree-lined road.
Overall, the sampled frames show a sequence moving between exterior road travel, close-ups of passengers or occupants inside a vehicle, and a driver’s-eye/front-windshield view of the road.
No product name, written slogan, or audio information is visible in the provided frames.

% matched lemmas: compose, expression, look, man, suit, tense, tie
\end{textsample}
