\begin{textsample}{POS Dim 5 – 1990 – Score 11.00 – 1990/tv\_com\_1990\_2.txt}  \label{ex:f5_pos_008}
The commercial opens inside the video \textbf{game}, on a dusty tan racecourse in a desert canyon.
Several futuristic hover-motorcycles line up across the track, each with a rider in a helmet and \textbf{racing} suit.
Low stone barriers run along both sides, orange canyon walls rise in the background, and a large overhead electronic sign hangs above the track.
At first the sign reads “ SET ” in bright yellow block letters, then changes to “ GO! ” A white \textbf{race} \textbf{timer} appears in the upper left.
The \textbf{viewpoint} sits just behind a green-and-teal hover bike marked with a large \textbf{number} 2, centered in the lane.
When the \textbf{race} begins, the other racers surge forward, kicking up pale dust clouds and leaving the \textbf{number} 2 bike behind.
Its rear glows red-orange as if powered, but it lags under the “ GO! ” sign while the pack pulls farther ahead.
The scene jumps through different \textbf{game} courses to show the \textbf{racing} variety.
On a narrow wooden plank bridge \textbf{suspended} over a deep rocky ravine, several hover bikes crowd together, including a large blue-and-white bike marked \textbf{number} 7 very close in front.
The planks stretch in a thin line across the gap, with green terrain beyond the canyon.
Then the setting changes to a dramatic, futuristic track at night or twilight.
A rider speeds along a steeply banked wall, with a deep blue and purple sky, dark building-like structures, and a white lattice track or framework curving below.
The bike appears to cling to the side of a twisting tube-like course before the image returns to the original desert starting stretch, where the \textbf{number} 2 bike is still under the \textbf{glowing} “ GO! ” sign.
More \textbf{racing} clips follow.
In a sandy canyon turn, hover bikes slide around a bend and throw up thick splashes of dust or sand ; a small \textbf{rating} icon sits in the lower left.
A close view shows a rider on a yellow-and-red bike marked \textbf{number} 3, wearing a white helmet with red accents.
Another bike sweeps past on the inside of the curve, and a large sandy plume fills the left side of the track as racers disappear around the bend.
The action then moves to a bright blue water course near a \textbf{huge} wall of falling water or spray.
A red-and-yellow bike marked \textbf{number} 1 flies above the water, then lands and skims forward between orange buoys and industrial-looking structures.
Next, the racers are on a snowy mountain track bordered by cliffs and rocks.
Several hover bikes carve through the snow, leaving pale tracks and blue-tinted glow beneath them as they bunch together and \textbf{race} under a sign ahead.
The commercial returns again to the desert starting area with the \textbf{number} 2 bike still sitting beneath the big yellow “ GO! ” sign.
Suddenly the \textbf{game} ’s rider gets off the bike.
He is a computer-animated, male-presenting racer in a tight green \textbf{racing} suit with red-orange shoulder pads and accents.
A small helmet lies on the ground to his right.
He runs straight toward the viewer with an angry, urgent expression, his brows sharply lowered and his mouth set.
As he gets closer, his face fills the screen : pale, angular, low-polygon features, short brown hair, heavy dark eyebrows, and a scowling look.
The edges of a television screen become visible around him, revealing that he is inside the \textbf{game} on an old-fashioned TV.
The real-world setting is a warmly lit living room.
An elderly white woman with short white hair sits in a cushioned chair, holding a gray PlayStation \textbf{controller} with both hands.
She wears a soft white cardigan over a pink blouse or nightdress and looks intently toward the television, her face calm and slightly puzzled.
The TV sits in front of her in a wooden entertainment unit or cabinet, with shelves and small decorative objects around it.
On the TV screen, the animated racer ’s large face is still glaring outward from the \textbf{game} world as if addressing her directly, while she remains seated and continues holding the \textbf{controller}.
The product title then appears on a cloudy, silvery-white background with faint lightning-like streaks.
In the center is a dark oval logo with gold text reading “ Jet Moto 2. ” After the logo, the \textbf{game} image returns briefly to the desert start line : the empty \textbf{number} 2 hover bike sits under the “ GO! ” sign while the green-suited racer stands beside it, with his helmet still on the ground.
He moves near the bike as if urging action.
The commercial ends back in the living room with the elderly woman holding the \textbf{controller} in her lap, looking forward with a faintly annoyed or confused expression.

% matched lemmas: controller, game, glowing, huge, number, race, racing, rating, suspend, timer, viewpoint
\end{textsample}
