\begin{textsample}{POS Dim 5 – 1990 – Score 45.00 – 1990/tv\_com\_1990\_63.txt}  \label{ex:f5_pos_001}
The commercial opens on a dark, \textbf{distorted} computer-style screen filled with flickering white text, like a hacked transmission or a corrupted menu.
Through the static, a list of PlayStation sampler contents is visible, including \textbf{game} names \textbf{such} as Wipeout, NFL GameDay, Warhawk, and Namco ’s Tekken.
The text swims and smears across black, blue, green, and white interference patterns, with rows of small circular icons near the bottom and release-date-like \textbf{numbers} on the right.
The screen repeatedly breaks up into bright white bands and glitchy shapes, as if the signal is unstable.
A cracked, explosive graphic appears, with a burst pattern \textbf{radiating} outward and bold white words \textbf{flashing} across the center.
Large block letters slam into view : “ BEGIN, ” followed by “ TRANSMISSION, ” with a bright orange-white flare behind them.
The imagery has a high-contrast, industrial science-fiction look, full of light streaks, metal textures, and \textbf{sudden} \textbf{flashes}.
The first \textbf{game} \textbf{footage} is from a futuristic flight-combat \textbf{game}.
From inside a cockpit, angular aircraft and targets appear against a blue sky and flat landscape.
A heads-up display surrounds the view with green meters, a small radar-like square in the upper right, gauges at the bottom, and \textbf{numbers} on the left.
The craft fires or flies toward other vehicles, leaving \textbf{colored} trails in the sky.
Briefly, the \textbf{game} title “ WARHAWK ” appears over the cockpit view, mixed with bright, abstract shapes.
In between the \textbf{game} clips, a \textbf{live-action} setup appears : a person in a yellow outfit is strapped into a large circular metal rig, like a gyroscope or simulator \textbf{cage}, inside a dark industrial room lit with warm orange panels.
The person is spun and \textbf{flipped} inside the ring, their body blurring from the movement.
Back in the Warhawk \textbf{footage}, small aircraft streak over a gray surface under a dark blue sky.
Explosions bloom in orange, yellow, and white near the edges of the screen.
The \textbf{player} ’s craft follows twisting \textbf{colored} trails and targets in the distance.
Another scene shows a sandy, orange landscape with towers and \textbf{floating} debris, then a cockpit view of a tower or platform exploding directly ahead.
A bold white word “ DEPLOYED ” appears over a \textbf{fiery} map-like background, and then the \textbf{game} returns to a military platform \textbf{suspended} over clouds at sunset.
The \textbf{player} ’s craft approaches a tall structure ; a \textbf{blast} \textbf{erupts} on the platform, and fire fills the cockpit view.
The \textbf{live-action} simulator returns, with the person in yellow spinning inside the metal ring.
Over this, an American \textbf{football} video-game scoreboard graphic appears with the words “ CRUNCH TIME, ” team labels, a score, and game-clock information.
The \textbf{football} \textbf{game} \textbf{footage} follows : tiny 3D \textbf{players} in red, white, black, and green \textbf{uniforms} move on a \textbf{stadium} field before a packed crowd.
Labels appear over selected \textbf{players}, \textbf{such} as “ Davis, ” “ Martin, ” and “ Smith. ” A quarterback stands in the pocket, \textbf{players} collide and fall, and a runner breaks across midfield.
The NFL \textbf{shield} and the title “ NFL GameDay ” appear large on screen, with a \textbf{ratings} box in the upper right.
The sequence cuts back to gameplay, where a \textbf{player} is tackled on a large midfield logo while other \textbf{players} converge.
The imagery then becomes abstract again, with close-ups of unreadable scrolling text, bright \textbf{yellow-green} panels, circular lens-like objects, and a reversed-looking menu screen showing PlayStation \textbf{controller} symbols.
The spinning simulator reappears, the yellow-clad person tumbling inside the circular frame in front of the warm orange-lit walls.
A \textbf{racing} \textbf{game} begins, visually identifiable as Wipeout-style futuristic anti-gravity \textbf{racing}.
A sleek dark hovercraft speeds along a vivid blue track with ridged, wave-like surfaces.
On-screen graphics show lap and position \textbf{numbers}, a \textbf{timer}, and a \textbf{colored} energy or speed \textbf{bar} along the bottom.
A close-up of a blurred red-and-blue vehicle streaks past, followed by a bright white screen with the word “ FASTER ” \textbf{floating} in the center.
For a moment, the scene jumps to a surreal real-world image of bananas stacked in boxes, \textbf{crossed} by a \textbf{glowing} blue curved streak, then returns to the \textbf{racing} craft speeding along a dark track beside rocky walls.
Another overlay names a craft or team, “ FIRESTAR, ” over a \textbf{fiery} orange tunnel graphic.
More industrial, high-saturation \textbf{live-action} images follow : the simulator rig and surrounding machinery are shown in blue, green, and red tones, with the person still \textbf{suspended} and spinning.
The action shifts into Tekken fighting-game \textbf{footage}.
Two polygonal fighters face off in outdoor \textbf{arenas} with \textbf{health} \textbf{bars} at the top.
In one \textbf{fight}, a small, blonde female-presenting fighter in a black outfit throws or \textbf{flips} a \textbf{huge} bear-like opponent in a grassy setting.
The massive \textbf{character} tumbles head over heels and crashes down while the smaller fighter stands ready.
A “ TEEN ” \textbf{rating} box appears in the lower right.
A quick \textbf{live-action} close-up shows a bald or closely shaved adult man in round, dark \textbf{goggles} and a bright yellow top, his face overexposed by \textbf{intense} light ; his mouth is open as if \textbf{shouting} or reacting.
Tekken continues with a blond male fighter in a blue jacket and white pants \textbf{fighting} in a desert-like \textbf{arena} at sunset.
He grabs and throws another fighter.
A small screen inside the simulator briefly displays the Tekken title with red Japanese \textbf{characters} above the word “ TEKKEN. ” Another Tekken scene shows a fighter being lifted upside down and slammed to the ground on a stone floor, with translucent PlayStation \textbf{controller} button icons—triangle, circle, \textbf{cross}, and others—appearing over the action.
The man in \textbf{goggles} returns in extreme close-up, his round lenses reflecting bright light, his expression \textbf{intense} and \textbf{exaggerated}.
The simulator \textbf{flashes} again in electric \textbf{colors}.
The fighting-game clips keep coming : the blond fighter in the blue jacket stands in the desert \textbf{arena} while an opponent is hurled away, and another bright, inverted-looking Tekken screen shows directional arrows and button prompts over a fighter, suggesting \textbf{controller} inputs.
The man in \textbf{goggles} appears once more, very close to the viewer, his face washed in white and yellow light.
A red-tinted \textbf{racing} \textbf{game} screen appears briefly, almost entirely covered by a red overlay, then the Wipeout-style \textbf{racing} \textbf{footage} returns on a tan, wooden or stone-looking track \textbf{crossing} a mountainous landscape.
The craft speeds forward, with red text at the top and a \textbf{timer} at the bottom.
Tekken appears again in an \textbf{icy} \textbf{arena}, where a \textbf{shirtless} fighter in black pants strikes a silver or armored-looking opponent ; large \textbf{controller} icons sit at the lower left.
Warhawk returns with a gray aircraft flying beside a futuristic structure in space or a dark sky, followed by a bright blocky explosion.
NFL GameDay returns for a moment, with a mass of \textbf{football} \textbf{players} colliding around the line of scrimmage.
The \textbf{goggled} man appears again, now tinted orange and yellow, teeth bared in an \textbf{intense} grin or \textbf{shout}.
Near the end, graphic text elements \textbf{build} the commercial ’s \textbf{warning} visually.
A large black oval shape with a \textbf{glowing} blue “ U ” appears over a pale, blueprint-like background.
Then an enormous dark letter “ R ” fills the screen.
Next, the word “ NOT ” appears in bold black letters over the same \textbf{icy} blue technical background.
Red \textbf{glowing} lowercase “ e”-like letters and shapes pulse over a busy orange, circuit-board-like collage, suggesting the continuation of the phrase heard in the audio context, “ You are not ready. ” The product imagery closes the commercial.
A white Sony PlayStation console and \textbf{controller} appear against an electric green, smoky background.
The \textbf{controller} ’s \textbf{colored} button symbols are visible : green triangle, red circle, blue \textbf{cross}, and pink square.
A dark, dramatic close-up shows the PlayStation console ’s circular disc lid \textbf{glowing} blue-white, with a red beam of light near it.
Then the white PlayStation \textbf{controller} is shown clearly on a black textured surface.
The brand text “ SONY ” is printed across the top center, with the PlayStation logo and the word “ PlayStation ” below it.
The “ SELECT ” and “ START ” buttons are labeled, and the square button is visible at the right edge of the close-up.
After a blurred, fast-moving glimpse of people or figures in a warm-toned space, the commercial ends on an abstract orange-and-black mechanical background with the large white word “ END ” centered on screen.

% matched lemmas: arena, bar, blast, build, cage, character, color, controller, cross, distorted, erupt, exaggerated, fiery, fight, flash, flip, float, floating, footage, football, game, glowing, goggle, health, huge, icy, intense, live-action, number, player, race, racing, radiate, rating, shield, shirtless, shout, stadium, such, sudden, suspend, timer, uniform, warn, yellow-green
\end{textsample}
