\begin{textsample}{POS Dim 5 – 2000 – Score 12.00 – 2000/tv\_com\_2000\_26.txt}  \label{ex:f5_pos_026}
The commercial begins with a black screen.
It then cuts to a black-and-white corporate boardroom.
A long polished conference \textbf{table} dominates the room, with rows of empty executive chairs along both sides.
Three \textbf{men} in dark \textbf{suits} are seated far apart around the \textbf{table}.
The setting is formal, minimal, and high-contrast, with wood-paneled walls and overhead lighting.
The camera moves to closer views of the \textbf{men}.
One \textbf{older} \textbf{man} with light hair sits at the \textbf{table}, seen in profile, while another middle-aged \textbf{man} in a \textbf{suit} sits farther back.
The middle-aged \textbf{man} is then shown in close-up, facing forward with a \textbf{serious} \textbf{expression}.
Another cut shows the \textbf{older} light-haired \textbf{man} seated alone at the \textbf{table}, also \textbf{serious} and formal.
The mood remains \textbf{tense} and restrained.
The middle-aged \textbf{man} is shown again in close-up, now appearing to \textbf{speak} or \textbf{react}, though no audio content is visible.
Shortly after, people begin standing up around the conference room.
More \textbf{men} in \textbf{suits} enter or rise from their seats.
The room becomes crowded with similarly dressed businesspeople.
Several \textbf{men} stand close together, \textbf{looking} in different \textbf{directions}, as if responding to something happening in the room.
The number of \textbf{suited} \textbf{men} increases dramatically.
A wide shot shows many \textbf{men} standing throughout the boardroom, filling the space around the \textbf{table} and chairs.
One \textbf{man} stands prominently in the foreground, while many \textbf{others} are arranged behind him.
The \textbf{older} light-haired \textbf{man} remains seated in one shot, surrounded by standing figures, making him appear isolated or boxed in.
The scene then shifts to an exterior view through large glass windows.
Many \textbf{suited} \textbf{men} are visible inside or behind the glass, pressed together in a dense group.
The commercial cuts to an overhead view of people in \textbf{suits} moving outdoors on a city street or plaza.
Their bodies and shadows form a scattered but coordinated-looking flow.
A higher aerial shot shows a large crowd of dark-suited figures gathered densely at a street corner or intersection among tall city buildings.
The crowd appears compact and massed together, contrasting with the earlier boardroom setting.
The final frame changes visual mode : it shows a medical-style X-ray image of a human chest and lungs.
Over the X-ray, large text reads “ undo tobacco now, ” with “ un ” in red and the rest in black.
Below it is the website “ TobaccoFreeCA.com. ” The final image introduces an explicit anti-tobacco message visually, linking the preceding corporate/crowd imagery to tobacco through the closing text and lung X-ray.

% matched lemmas: direction, expression, look, man, old, other, react, serious, speak, suit, table, tense
\end{textsample}
