\begin{textsample}{POS Dim 5 – 2020 – Score 19.00 – 2020/tv\_com\_2020\_104.txt}  \label{ex:f5_pos_032}
The commercial opens in a large, dim, symmetrical office space with rows of cubicles and desks.
The room has grey-green walls, long fluorescent ceiling lights, rectangular wall lights, desk lamps, and \textbf{older} beige desktop computers.
Many workers sit at separate workstations, creating a highly ordered, bureaucratic-looking environment.
A white-haired \textbf{man} wearing glasses and a dark, high-collared, tailored jacket is then shown at a lectern or raised desk near the front of the office.
He appears to be \textbf{addressing} the room.
Subsequent shots show workers at their desks with vintage computers, keyboards, phones, papers, and glowing dome-shaped lamps.
The overall setting remains controlled and austere.
The white-haired \textbf{man} is shown walking or standing among the cubicles.
He faces different \textbf{directions} and appears to be \textbf{speaking} or issuing instructions, though no audio content is visible.
The camera alternates between medium shots of him and \textbf{reaction} shots of \textbf{employees}.
In one shot, a Black \textbf{male} \textbf{employee} sits at a desk facing a beige computer, \textbf{looking} \textbf{serious} or \textbf{attentive}.
The tone becomes visually more unusual : one \textbf{man} in a grey \textbf{suit} is shown standing up on top of a desk or cubicle surface.
The white-haired \textbf{man} \textbf{looks} upward toward him.
Another \textbf{employee} is also shown standing on a desk in the background.
A \textbf{bald}, \textbf{bearded} \textbf{man} later appears standing on a desk as well.
Several seated workers \textbf{look} on, while \textbf{others} remain at their computers.
The white-haired \textbf{man} ’s \textbf{gestures} grow more emphatic ; in one close shot he raises an arm as if signaling or pointing.
The setting then abruptly changes to a bright café or coffee \textbf{shop} during the day.
People sit at \textbf{tables}, and a person stands near the entrance.
Large windows \textbf{look} out onto a city street, with visible signage on the glass, including “ COFFEE ” and smaller text that is partly unclear.
A barista-like woman in an \textbf{apron} stands behind an espresso machine and \textbf{looks} toward the camera or toward someone off-screen.
The commercial then cuts to a nighttime urban street scene with an ambulance parked with its rear doors open.
A paramedic or emergency worker stands at the back of the ambulance near a stretcher.
A \textbf{bald} \textbf{man} lies on the stretcher, partially reclined, \textbf{looking} upward.
City buildings and lights are visible in the background.
On-screen subtitle text appears in two languages across these ambulance shots : first in Spanish, “ Uso Zoom para traducir. ”, and then in English, “ I use Zoom to translate. ” The subtitles suggest translation visually, but no \textbf{spoken} content is visible in the frames.
A full-screen blue title card appears with the white “ zoom ” logo centered.
After the logo, the commercial returns to the office scene.
The white-haired \textbf{man} is in the foreground, pointing forcefully toward someone or something off-screen.
Behind him, another \textbf{man} remains standing on a desk, while \textbf{other} workers sit at their stations.
The final frame holds on the white-haired \textbf{man} pointing and appearing intense or commanding, with the office environment still visible behind him.

% matched lemmas: address, apron, attentive, bald, bearded, direction, employee, gesture, look, male, man, old, other, reaction, serious, shop, speak, suit, table
\end{textsample}
