\begin{textsample}{POS Dim 5 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_8.txt}  \label{ex:f5_pos_023}
The commercial opens on a black frame, then cuts to a bright, modern reception/lobby area.
The space has a long illuminated front desk, polished floors, white walls, a black staircase or elevator structure at the right, and people moving through with luggage.
A \textbf{man} in a \textbf{suit} walks across the foreground carrying a briefcase, while another \textbf{man} in a tan/olive jacket approaches the reception desk pulling a rolling suitcase.
The scene then moves into a closer exchange at the front desk.
A \textbf{male} receptionist or desk clerk with straight black, chin-length hair, wearing a dark \textbf{suit} and blue \textbf{shirt} with \textbf{tie}, faces someone off-camera.
The next shots show the customer : a curly-haired \textbf{man} in a tan/olive blazer over a blue \textbf{shirt}.
He stands at the counter, leaning forward at times, apparently \textbf{speaking} or \textbf{reacting}.
Behind him, \textbf{other} people and luggage are visible, reinforcing the lobby or hotel-like environment.
The interaction continues through alternating close-ups and medium shots.
The dark-haired clerk remains \textbf{composed} behind the counter, while the curly-haired \textbf{man} appears somewhat anxious or \textbf{concerned}, \textbf{looking} down at papers or items on the counter and then back up at the clerk.
A blonde woman in a pink top appears in the background near the \textbf{seating} area, but she is not the main focus.
The lobby decor includes potted plants with long twisting stems, framed wall art, lamps, and a staircase structure.
After several shots of the front-desk \textbf{conversation}, the commercial cuts abruptly to a bedroom.
A red anthropomorphic M\&M character is lying in bed on a pillow, with white-gloved arms and legs visible.
The red candy character has large eyes, a small mouth, and the white “ m ” logo on its body.
It appears to be lying under or on bedding.
The next shot \textbf{widens} to show a bed from above.
A human \textbf{man} lies on the left side of the bed under a blanket, facing upward, while the red M\&M character lies on the right side under separate bedding.
Two bedside lamps are lit, creating a warm nighttime bedroom atmosphere.
The room has a wooden headboard and dark bedding.
In the final branded frame, the same overhead bedroom shot remains, with white on-screen text across the lower portion : “ m\&m ’s Deep down they ’re all chocolate. ” Beneath it is the website “ www.mms.com, ” with small legal/trademark text along the bottom.
The commercial then cuts to black.

% matched lemmas: compose, concerned, conversation, look, male, man, other, react, seating, shirt, speak, suit, tie, widen
\end{textsample}
