\begin{textsample}{POS Dim 5 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_86.txt}  \label{ex:f5_pos_074}
The commercial opens in a very dark interior with large window or glass-door panels.
Several people appear only as silhouettes, standing or moving in a room with strong backlighting.
The image then dissolves into an office-like setting.
A \textbf{man} in a white dress \textbf{shirt} and \textbf{tie} is seen close to the camera, partly superimposed over the previous glass-walled interior.
The layered transition makes the details hazy, but the setting appears to include desks, windows, and people in business attire.
Next, two \textbf{men} in dress \textbf{shirts} and \textbf{ties} are shown together, again with overlapping dissolves.
One appears \textbf{older} or balding ; another stands beside him.
They seem to be \textbf{looking} downward or at something in front of them, though the object is not clearly visible.
A close-up follows of an \textbf{older} \textbf{bald} \textbf{man} in a \textbf{shirt}, \textbf{tie}, and dark \textbf{vest}.
His face is centered and serious-looking.
The shot remains visually layered with remnants of \textbf{other} office images, making the background indistinct.
The sequence continues with businesspeople in \textbf{shirts} and \textbf{ties}, including a \textbf{man} facing forward and another \textbf{older} \textbf{man} beside him.
The images are still heavily cross-faded, giving a montage effect of office workers in discussion or observation.
Another close-up shows a middle-aged \textbf{man} in a white \textbf{shirt} and striped \textbf{tie}, with pens visible in his \textbf{shirt} pocket.
His \textbf{expression} appears \textbf{concerned} or intent.
A side view of another \textbf{man} overlaps the frame.
The montage then includes an image of a large airplane seen from the front, superimposed over the office scene.
The aircraft appears centered with wings extended, while the office worker remains faintly visible beneath the overlay.
The scene cuts to an exterior street view in daylight.
A building entrance has a sign reading “ SAN MARCOS HOTEL. ” A white delivery van with a red and orange/purple marking is parked at the curb.
A person in light clothing walks toward or into the hotel entrance carrying a package or parcel.
Palm trees and street fixtures are visible outside.
The next interior shot shows a dim conference or meeting room.
Several seated figures are visible in silhouette against horizontal window blinds.
A tilted rectangular “ Federal Express ” logo graphic appears over the scene, as if displayed or superimposed in front of the people.
The commercial ends on a full-screen graphic : a tilted “ FEDERAL EXPRESS ” logo on a textured brown/gold background.
Beneath it, large white text reads : “ OUR MOST IMPORTANT PACKAGE IS YOURS. ”

% matched lemmas: bald, concerned, expression, look, man, old, other, shirt, tie, vest
\end{textsample}
