\begin{textsample}{POS Dim 5 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_26.txt}  \label{ex:f5_pos_012}
A \textbf{stark}, gray, futuristic chamber appears, with smooth metal or concrete walls, circular porthole-like openings, and a cone-shaped fixture jutting from one wall.
In the middle of the room, a lone adult man stands near a short cylindrical pedestal.
He is light-skinned, with long brown hair tied back, light stubble, and a tense, guarded expression.
He wears a loose blue-gray overshirt over a dark T-shirt, giving him a rough, non-uniform look against the rigid, institutional surroundings.
His hands are shown close up.
A metal band or cuff is visible around one wrist, and his fingers work at a dark strap or restraint near his body.
He grips and pulls at a small metal piece as if loosening or freeing himself.
The imagery then shifts to a large, round, \textbf{glowing} white disk set into the wall.
The light is \textbf{intense} and almost featureless, surrounded by darkness.
The man stands in silhouette in front of it, his head and shoulders black against the bright circle, before the view is overwhelmed by white glare.
His face appears again, lit harshly from the side.
His hair is pulled back but loose strands move around his face.
He looks downward and then to the side, squinting and bracing himself against the brightness.
The room keeps \textbf{flashing} between the blinding white light and the mechanical wall fixtures.
The \textbf{huge} circular lamp dominates the left side of the space, while the man remains by the pedestal on the right, slightly hunched, as if under pressure from the light.
On the wall, dark circular panels and recessed rings echo the shape of the lamp.
One fixture resembles a black cone projecting straight out from a round opening.
Another looks like a dark, rounded dome set into a circular frame.
The man stands in profile near the pedestal, the giant white circle glowing behind him through a haze.
Small wall markings or numerals are visible near the light, including \textbf{characters} that resemble “ 021, ” and later large industrial-style \textbf{numbers}, including “ 26 ” and “ 27, ” appear across a dark wall surface.
These markings reinforce the chamber ’s \textbf{numbered}, controlled atmosphere.
The man ’s posture remains tense.
He looks off to one side, then turns, as if tracking something in the room or resisting instructions.
In silhouette, he raises a hand toward the side of his head or ear, partially \textbf{shielding} himself.
Brief, blurred glimpses of his face show him grimacing and narrowing his eyes ; his eyes are shown extremely close, strained and searching under the glare.
The white light swells again until it fills almost everything.
When the man reappears, his face is clearer and more determined.
He is still in the same loose shirt, standing against the gray wall and circular port behind him.
He glances down, then turns his head sharply.
Another pale circular shape fills the view, followed by another wash of white.
His wrist and hand return in close detail.
A smooth metal band is still around his wrist, and his hand moves quickly in the dark.
He reaches toward an object and grasps what appears to be a pair of sunglasses : a compact, futuristic-looking frame with dark lenses and pale metallic parts.
The product is handled as something he has retrieved for himself rather than something handed to him.
Backlit by the enormous lamp, the man bends forward over the pedestal, almost swallowed by the glow.
He raises his hands to his face and begins putting the sunglasses on.
His body is a dark outline, shoulders rounded and head bowed, while the circular light burns behind him like a white sun.
He holds the glasses in place, then gradually straightens.
As he lifts his head, the light remains directly behind him, creating a halo around his silhouette.
He stands more upright and still, no longer \textbf{shielding} his eyes with his hands.
A bright white \textbf{flash} gives way to a detailed side profile of his face wearing the sunglasses.
The Oakley-style eyewear is bold and sculptural : a silver or light gray wraparound frame with dark, rounded lenses.
The frame has distinctive side panels around the eyes, including small circular \textbf{holes} near the lower edge, giving it a mechanical, protective look.
The dark lenses cover his eyes completely, cutting the glare.
His expression is calm and firm now, with his lips slightly parted in one moment and his jaw set.
The product is shown close against his skin and hair, emphasizing the shape of the frame, the dark lens surface, and the way it \textbf{shields} his eyes.
The commercial ends with the man again as a black silhouette, standing squarely before the large \textbf{glowing} circle.
His shoulders are relaxed compared with earlier, and he faces the light directly.
The chamber remains hazy and gray around him, but the sunglasses have changed his relationship to the glare : instead of recoiling or \textbf{shielding} himself, he stands still in front of it.

% matched lemmas: character, flash, glowing, hole, huge, intense, number, shield, stark
\end{textsample}
