\begin{textsample}{POS Dim 5 – 1960 – Score 10.00 – 1960/tv\_com\_1960\_115.txt}  \label{ex:f5_pos_056}
The commercial shows a middle-aged \textbf{man} and a blue two-door car in a sunny suburban outdoor setting, presented through a sequence of shots focusing alternately on the \textbf{man} and the vehicle. 1. **Opening shot:** A \textbf{man} in a light-colored sweater over a \textbf{collared} \textbf{shirt} stands beside a blue car, near the driver-side area.
The car door appears open or partly open, and the \textbf{man} is \textbf{turned} toward the camera.
The background is shaded with trees and outdoor objects. 2. **Man with car behind him:** The scene changes to a clearer view of the \textbf{man} standing in front of the blue car.
The car is parked outdoors, with trees, a driveway, and suburban houses or structures visible in the background.
The \textbf{man} faces the camera with a \textbf{composed} \textbf{expression}. 3. **Interior/side detail of the car:** The camera cuts to a close angled view through the side window area of the blue car.
The steering wheel, dashboard, and front \textbf{seating} are visible.
The car has a sleek hardtop profile and glossy paint. 4. **Rear-side exterior view:** The car is shown from the rear quarter, emphasizing its long body, rear fender, wheel, and tail section.
It is parked on a driveway or paved area, with trees and a residential-looking background. 5. **Full side profile:** A wider side view shows the entire blue two-door car parked parallel to the camera.
The long roofline, large rear quarter panel, and whitewall tires are visible.
A yard, sidewalk or driveway edge, and suburban structures appear behind it. 6. **Man in front of the car again:** The \textbf{man} reappears in a medium close shot, standing with the car behind him.
He faces the camera directly, smiling slightly.
The background remains the same suburban outdoor setting with trees and houses. 7. **Rear view with model plate:** The camera cuts to a straight rear view of the car.
The rear lights and wide trunk are visible.
A license plate reads **“IMPALA.”** The car is parked on a driveway with a garage or house structure in the background. 8. **Man gesturing:** The \textbf{man} appears again in front of the car.
He smiles and raises or moves his hands in front of him, as if demonstrating or emphasizing something.
The car remains parked behind him. 9. **Final shot with branding:** The last frame shows the \textbf{man} seated inside the blue car, leaning toward or \textbf{looking} out from the driver-side window area.
A large **Chevrolet** logo graphic appears over the upper left portion of the frame.
The car ’s interior upholstery is visible, and the \textbf{man} \textbf{looks} outward with a \textbf{serious} or \textbf{attentive} \textbf{expression}.

% matched lemmas: attentive, collar, compose, expression, look, man, seating, serious, shirt, turn
\end{textsample}
