\begin{textsample}{POS Dim 5 – 1960 – Score 5.00 – 1960/tv\_com\_1960\_57.txt}  \label{ex:f5_pos_057}
In a \textbf{stark} white studio space, three adult men in business suits sit around a small rectangular glass table set on a pale rectangular rug.
The chairs have thin metal frames and dark seats and backs.
Loose papers or fabric samples lie on the glass tabletop.
The men lean inward over the table, \textbf{clustered} closely as if in a serious conference.
One man wears a tan suit with a red tie and sits at the far side ; the other two wear darker suits, one of them later seen with black-framed glasses.
Their posture is intent and argumentative, with heads bent over the tabletop and hands reaching toward the papers or sock samples.
The three men draw closer until their faces nearly fill the view : the man in the tan suit is centered, with short neatly combed hair, flanked tightly by the two men in dark suits.
All three are middle-aged, clean-shaven, and dressed like office professionals.
Their expressions are exaggeratedly serious.
The man in tan looks from one man to the other, then becomes animated, narrowing his eyes, opening his mouth wide, and gesturing sharply as if making a forceful point.
One of the men in a dark suit leans away while the man in tan continues, his face tense and emphatic, eventually raising a finger as though \textbf{warning} or correcting the others.
A black socked foot and lower leg suddenly become the focus, placed upright on the glass tabletop.
The sock is dark, smooth, and long, reaching high up the calf.
The tan-suited man sits behind it, partly visible through and above the glass.
Hands from the men in dark sleeves hover around the sock, one hand spread open beside the calf as if measuring or indicating its height.
The glass table reflects the foot and leg clearly, doubling the shape of the black sock on the shiny surface.
One man points toward the sock ’s lower calf area, while another steadies or presents the leg from the side, making the over-the-calf length visually explicit.
The comparison shifts to another leg extended across the tabletop.
This foot and lower leg are covered in a light tan or beige sock, with the trouser leg pulled up to expose the sock ending much lower, around the lower calf or just above the ankle.
Several hands gather near the top edge of the sock, pinching and smoothing the cuff to show where it stops.
The black over-the-calf sock remains nearby in the background, creating a direct side-by-side contrast between the taller dark sock and the shorter tan sock.
The men ’s hands point repeatedly at the ankle area and the cuff line, emphasizing the shorter length.
One of the men in a dark suit, with neatly combed reddish hair, is shown in close-up resting his fingers against his mouth in a thinking pose.
He looks off to the side, then downward, appearing to consider the argument.
The focus returns to the feet on the table.
A dark burgundy socked foot slides in from the right, placed alongside the other socked feet.
Hands smooth and hold the burgundy sock near the ankle and cuff, presenting it as another option.
The burgundy sock has a dressy, polished look, and the men handle it carefully, as if drawing attention to its styling.
Papers or white fabric briefly slide beneath or near the feet as the comparison becomes \textbf{crowded} and busy.
The man with black horn-rimmed glasses, wearing a dark suit and tie, now appears in close-up.
He faces another man whose back is partly visible in the foreground.
The bespectacled man speaks with a concentrated, almost lecturing expression, his eyebrows raised behind the thick frames.
He leans forward and continues, mouth opening and closing through several emphatic expressions, as though laying out his own position in the debate.
The tan-suited man reappears from a low \textbf{viewpoint} among the feet and legs.
A dark socked foot crosses high in the foreground, while the tan-suited man looks down and gestures toward the lower legs around him.
The composition makes the socks loom large, with the men ’s faces and pointing hands peering in from above.
The tan-suited man ’s hands indicate different sock areas between two tan-colored socked feet in the foreground.
Other men ’s hands enter from both sides, pointing and gesturing toward the socks from several directions at once.
The debate becomes visually chaotic : fingers point, arms reach in, and faces crowd around the socks, all focused downward on the competing lengths and styles.
The scene widens again to the white studio set.
The tan-suited man is now standing on top of the glass table, rising above the two seated men.
One of the dark-suited men sits to the left, leaning in and looking up ; the bespectacled man sits to the right.
A dark shoe lies on the floor near the right chair, reinforcing that the men are showing socks rather than shoes.
The tan-suited man stands upright in his suit and tie, arms slightly out, as if presenting the conclusion of the debate.
The two seated men look up toward him and the socks, their bodies still angled toward the table.
Large bold white lettering appears over the lower half of the image, partially covering the table and men.
The visible text reads : “ Stand-Up Socks!
By Hanes Plus 4 ; Of Ban-Lon Caprolan nylon by Allied Chemical. ” Behind the text, the tan-suited man remains standing on the glass table with his arms opened outward, while the seated men stay on either side, still looking up and gesturing around him.

% matched lemmas: cluster, crowded, stark, viewpoint, warn
\end{textsample}
