\begin{textsample}{POS Dim 5 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_15.txt}  \label{ex:f5_pos_077}
The commercial begins with a nearly black frame, with no clear visible content.
It then cuts to a warm, orange-lit room that \textbf{looks} like a casual den or attic lounge.
Two \textbf{men} are seated facing forward, apparently \textbf{watching} something off-screen.
The \textbf{man} on the left wears a blue \textbf{shirt} over a white long-sleeve layer and a dark cap ; he is holding a drink container.
The \textbf{man} on the right wears an orange \textbf{shirt} and light \textbf{pants}.
A golden retriever lies on a green leather chair between them.
The room contains sports or poster-like wall decorations, windows, shelves, and scattered items on a low \textbf{table}.
A close-up shows the golden retriever resting its head on the arm of the green chair, \textbf{looking} calm or sleepy.
The scene returns to the two \textbf{men} and the dog ; both \textbf{men} appear engaged with what they are \textbf{watching}.
The commercial then cuts to a televised American football game.
Players in black \textbf{uniforms} face players in white \textbf{uniforms} with orange helmets at the line of scrimmage.
A later shot shows the golden retriever walking on the football field itself.
The sequence alternates between the room and the game footage, suggesting the \textbf{men} are \textbf{watching} the dog appear in the game.
One shot shows a television screen with a close-up of the \textbf{man} in the blue \textbf{shirt}, framed inside the TV set.
On the football field, the dog is seen near the line of scrimmage and then running across the grass.
A \textbf{man} in a blue \textbf{shirt} appears among the football players, holding or moving with a football while players in \textbf{uniforms} surround him.
The dog runs alongside or near the action.
Several shots emphasize motion : the dog sprinting in profile, the dog ’s paws striking the turf, and the dog weaving low between players ’ legs.
There is a stylized upward shot of the dog ’s head against a bright blue sky with clouds, followed by more close-ups of running paws and field-level action.
The dog moves rapidly among the players.
A product shot appears : a cold brown beer bottle with a white-and-blue “ Lite ” label in the foreground, with \textbf{other} blurred bottles behind it.
Small copyright text at the bottom reads “ {\EmojiFont ©}1995 Miller Brewing Co.
Milwaukee WI. ” The football sequence continues.
In the stadium background, banners and signs with “ Lite ” branding are visible.
The dog runs downfield while players in black \textbf{uniforms} pursue.
A large “ Lite ” sign is shown behind a helmeted player.
Another shot shows the \textbf{man} in the blue \textbf{shirt} among \textbf{uniformed} players, smiling and \textbf{gesturing} with a raised hand/fist as players crowd around him.
The dog is then shown lying on the grass with a football against its mouth or front paws, as if it has caught or secured the ball.
The commercial cuts back to the room, where the two seated \textbf{men} raise their hands and appear to celebrate with a high-five.
The field action continues with a close-up of the dog ’s paws placed on top of an upright football on the turf.
In the background, the \textbf{man} in the blue \textbf{shirt} approaches.
A later wide shot shows the dog sitting beside the football near the goalpost area, with the \textbf{man} in blue nearby and football players lined up in the foreground.
The final shots return to the room.
The two \textbf{men} sit in their chairs, holding or positioned near long white rods or poles in the foreground ; their exact function is unclear from the frames.
A blue rectangular graphic appears at the bottom with the visible text “ Lite is good. ” and a circular Lite logo.
The \textbf{man} on the left raises both arms in celebration, while the \textbf{man} on the right \textbf{looks} downward toward his hands or the object in front of him.
The “ Lite is good. ” graphic remains on screen through the final frame.

% matched lemmas: gesture, look, man, other, pant, shirt, table, uniform, watch
\end{textsample}
