\begin{textsample}{POS Dim 5 – 1990 – Score 13.00 – 1990/tv\_com\_1990\_67.txt}  \label{ex:f5_pos_072}
The commercial appears to take place in a brightly lit lighting or lamp showroom, with many \textbf{table} lamps, chandeliers, vanity bulbs, and ceiling fixtures visible throughout.
At the start, the scene is dark and seen in a wide shot.
The showroom is crowded with lamps and hanging lights.
As the image brightens, two young \textbf{men} are shown near a wall of round vanity bulbs.
One is a young Black \textbf{man} in a red \textbf{shirt} and patterned overshirt ; the \textbf{other}, seen shortly after, is a young white \textbf{man} with reddish hair wearing a red \textbf{shirt} under a dark/plaid jacket.
They \textbf{look} closely at the illuminated display.
An \textbf{older} woman is seated in the background near the window, and a neon sign is visible behind her, though the lettering is not fully clear.
The two young \textbf{men} stand together beside a mirror or illuminated display.
Their attention seems directed upward or toward something off-screen.
A cut shows a ceiling panel or opening with exposed material and wiring, lit with blue-white light, suggesting some kind of electrical or fixture problem.
Another shot shows a \textbf{bearded} \textbf{man} in a flamboyant outfit : he wears a patterned jacket, a large colorful hat, and yellow slatted sunglasses.
He appears among the lighting displays and handles long white tube-like lights.
The scene then shifts to a \textbf{man} in a light-colored \textbf{shop} \textbf{coat} or work \textbf{coat} standing on a ladder beneath a hanging chandelier/ceiling fixture.
He appears to be working on or near the fixture.
Close-up shots show a tool or cable near the fixture area.
Suddenly there are bright flashes and sparks around him.
The \textbf{man} ’s body jerks and twists near a ceiling fan or chandelier, and the lighting becomes very intense and overexposed.
The ceiling fan blades are visible, and the \textbf{man} appears to be caught up in the movement or electrical disturbance.
Sparks continue to spray outward.
The \textbf{bearded} costumed \textbf{man} is shown again, now close to camera, holding white tube-like lights and \textbf{gesturing} toward the viewer.
The commercial cuts rapidly between him, the worker, the spinning ceiling fan, and sprays of sparks.
The \textbf{older} woman seated near the neon-lit window \textbf{reacts} with her mouth open and a startled \textbf{expression}.
The ceiling fan continues to spin amid flashes ; one shot shows the worker hanging or being pulled downward from the fan area while sparks scatter around him.
Several frames become almost completely washed out by white light.
The young \textbf{men} and the costumed \textbf{man} appear together in a \textbf{reaction} shot, all \textbf{looking} toward the bright disturbance.
Their faces are strongly overexposed by the flashes, and the young Black \textbf{man} appears to be smiling or laughing in one frame, while the reddish-haired young \textbf{man} \textbf{looks} open-mouthed.
The \textbf{bearded} \textbf{man} stands behind them in the same bright, chaotic lighting.
Near the end, the worker is shown on the floor, apparently fallen from the ladder or fixture area.
He is surrounded by blue glowing cables or tubing and scattered objects.
The lighting is still very bright.
In another shot, he sits or reclines on the floor holding something, with tools or fixture parts around him.
The final shots return to the \textbf{bearded} costumed \textbf{man}.
He faces the camera directly, wearing the colorful hat and yellow slatted sunglasses, and holds up two red-and-yellow packaged items or bottles, one in each hand.
The product labels are partially visible but not clearly readable in the sampled frames.
He presents the items prominently in front of the lighting displays as the commercial ends.

% matched lemmas: bearded, coat, expression, gesture, look, man, old, other, react, reaction, shirt, shop, table
\end{textsample}
