\begin{textsample}{POS Dim 5 – 1950 – Score 8.00 – 1950/tv\_com\_1950\_19.txt}  \label{ex:f5_pos_084}
The commercial appears in low-resolution black-and-white/green-tinted footage with a dark border around the image. - **Opening frame:** The first frame is very dark and indistinct.
Only vague shapes are visible, and no clear setting or people can be identified. - **Kitchen with two children:** The scene cuts to two young girls standing side by side in what appears to be a kitchen.
The girl on the left has dark hair and wears a patterned dress with a large light-colored \textbf{collar}.
The girl on the right has pigtails and wears a light sailor-style top.
Behind them are kitchen cabinets and a counter ; a white duck- or goose-shaped object is visible in the background.
The girl on the right faces forward with her mouth open as if speaking, while the girl on the left \textbf{looks} toward her. - **Adult woman near a window/display:** The next shot shows an adult woman in profile, indoors, near a window or glass display.
She has styled dark hair and wears a patterned-collar garment.
She raises one finger near her lips or face.
Through or beyond the glass, blurred street or shop-window details are visible, including shapes resembling cars or signage, but the background is not clear. - **Return to the children:** The commercial cuts back to the two girls in the kitchen.
They now face more toward the camera.
The girl on the left appears to be \textbf{speaking} or \textbf{reacting} ; the girl on the right \textbf{looks} forward with a more \textbf{serious} or \textbf{attentive} \textbf{expression}. - **Close-up of the girl in sailor top:** A close-up focuses on the girl with pigtails.
Her face fills most of the frame, and her sailor-style \textbf{collar} is visible.
She \textbf{looks} slightly sideways and downward, with her mouth open as if mid-speech or \textbf{reacting}.
A hand or utensil may be near the lower left edge, but it is not clear enough to identify confidently. - **Blurry kitchen/product close-up:** The next image is very soft and abstract.
It appears to show a close-up of reflective glass or liquid/container surfaces, possibly in a kitchen or food-preparation context, but the objects are too blurred to identify precisely. - **Final product display:** The last frame shows a lineup of Campbell ’s soup cans on a counter or shelf.
A hand holds a can labeled **“Campbell ’s Vegetable Soup”** in the center foreground. \textbf{Other} visible cans include **“Bean with Bacon Soup”** on the left and **“Turkey Noodle Soup”** on the right.
A taller can or container in the background appears to read **“Minestrone Soup,”** though it is partly obscured.
The final image functions as a product display, with the Campbell ’s branding prominently visible.

% matched lemmas: attentive, collar, expression, look, other, react, serious, speak
\end{textsample}
