\begin{textsample}{POS Dim 5 – 2010 – Score 14.00 – 2010/tv\_com\_2010\_64.txt}  \label{ex:f5_pos_007}
The commercial begins on a black screen.
It then cuts to a bright daytime exterior of a large white suburban house with a front porch, manicured lawn, shrubs, a driveway, and parked cars nearby.
A \textbf{man} is standing at or near the front door.
The scene moves to the doorway.
Inside the house, a Black \textbf{man} wearing a gray “ SAINTS ” T-shirt stands just inside the open door.
Behind him are interior stairs, framed pictures, and a glass door.
Facing him from outside is a white \textbf{man} seen mostly from behind, wearing a dark gray zip-up top with a New Orleans Saints fleur-de-lis logo.
The two appear to be having a \textbf{conversation} at the threshold.
The camera alternates between the two \textbf{men}.
From the porch side, the white \textbf{man} is shown \textbf{gesturing} with his hands while \textbf{speaking} visually ; the neighborhood street and parked cars are visible behind him.
The homeowner ’s \textbf{expressions} shift from \textbf{attentive} to \textbf{surprised} or \textbf{uncertain}.
The visitor remains upbeat and expressive, at one point raising a finger as if making a point.
The visitor then holds up a smartphone toward the homeowner.
The phone screen shows a delivery-related app interface with a simple map or route graphic and colored elements, though the small text is not clearly readable.
Very small white disclaimer-style text appears near the bottom of the frame, but it is too small to read clearly.
A wider exterior shot shows the two \textbf{men} still at the front door from outside the house.
The visitor stands on the porch near decorative railings, while the homeowner remains partly inside.
The camera then cuts to the street : a \textbf{bald} \textbf{man} wearing a brown, padded-looking \textbf{vest} over a gray \textbf{shirt} walks near a gray car parked by the curb or driveway area.
The two \textbf{men} at the door \textbf{turn} their attention outward, \textbf{looking} toward him.
The \textbf{bald} \textbf{man} is shown more clearly standing near the car, \textbf{looking} toward the house.
He appears to be the focus of the two \textbf{men} ’s attention, though his role is not explicitly explained visually in the sampled frames.
The scene cuts back to the porch.
The visitor glances sideways toward the street, then back toward the homeowner.
The homeowner ’s face appears \textbf{serious} or skeptical as he \textbf{looks} at the visitor.
The commercial ends on a clean white background with the FedEx logo centered in purple and orange.
Beneath it is the URL “ fedex.com/delivery. ” The final frame holds the same FedEx end card.

% matched lemmas: attentive, bald, conversation, expression, gesture, look, man, serious, shirt, speak, surprised, turn, uncertain, vest
\end{textsample}
