\begin{textsample}{POS Dim 5 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_2.txt}  \label{ex:f5_pos_048}
The commercial begins on a nearly black screen, with archive watermarks visible.
It then cuts to close-up shots of pizza.
The camera shows the surface of a pizza in warm, saturated color : browned crust, melted cheese, red sauce, and mixed toppings.
One close-up shows rounded reddish slices and crumbled meat-like toppings ; another shows melted cheese stretching around green pepper strips and \textbf{other} toppings.
The scene shifts to people eating pizza in what appears to be a crowded, warmly lit \textbf{restaurant} or social dining setting.
A young woman with long reddish-brown hair is shown in close-up biting into a slice of pizza.
Another young woman, holding a slice, \textbf{turns} her head to the side while seated among \textbf{others}.
A close-up of hands follows : several people reach toward a pizza on a plate or tray, pulling or taking slices.
More individual \textbf{reaction} and eating shots follow.
A young \textbf{man} with curly hair \textbf{looks} forward with a pleased or \textbf{amused} \textbf{expression}.
Two people are then shown side by side, each holding a slice and biting into it ; the pizza toppings and crust are visible.
Another young woman in a light top lifts a slice to her mouth and bites into it.
A young \textbf{man} with curly hair smiles while holding food near the bottom edge of the frame.
The next shots continue the eating sequence.
A young \textbf{man} in a light-colored sweater holds a slice close to his mouth and takes a bite.
In the following shot, he appears to \textbf{react} positively, smiling with his hand raised ; a strand of melted cheese or topping appears near his fingers.
The commercial ends on a white title card.
At the top is a small trapezoid-shaped image containing a smiling woman and food imagery.
Large centered text reads : “ New SuperStyle. ” Beneath it, small text reads : “ {\EmojiFont ©} Pizza Hut Inc., 1978. ” Archive watermarks remain visible on the image.

% matched lemmas: amused, expression, look, man, other, react, reaction, restaurant, turn
\end{textsample}
