\begin{textsample}{POS Dim 5 – 1960 – Score 5.00 – 1960/tv\_com\_1960\_84.txt}  \label{ex:f5_pos_059}
A glamorous young blonde woman is surrounded by reporters in a dark, \textbf{crowded} public setting, like an arrival outside a theater or event.
She wears a pale, fluffy fur wrap or coat around her shoulders, with curled 1960s-style hair, heavy winged eyeliner, pearl earrings, and lipstick.
She smiles broadly over her shoulder while several microphones are thrust toward her from below and from the sides.
On the left, a boxy press camera with a \textbf{flash} attachment is visible ; on the right, the backs and profiles of men in suits crowd close to her.
She turns her head from left to right, smiling and posing as if answering questions, then faces forward more directly while microphones hover inches from her mouth.
As the questioning continues, she alternates between playful smiles and more composed expressions.
Her face fills the center of the scene, framed by the pale fur collar.
Reporters ’ hands and microphones keep moving in and out of the foreground : a black handheld microphone from the left, a tall silver microphone rising in front of her, and other dark shapes from the crowd.
She laughs, tilts her head, lowers her gaze shyly, then looks back up at the man in front of her.
At moments her face is partly blocked by the heads of the reporters pressing in, reinforcing the feeling of a celebrity press scrum.
When the subject turns to “ cheesecake, ” clarified by the transcript as the hosiery product, her expression becomes bright and animated.
She leans toward the microphones and speaks with an exaggeratedly pleased look, smiling widely and showing her teeth.
The pale fur collar nearly fills the lower part of the image, with only her face, hair, and the \textbf{cluster} of microphones clearly visible.
She looks from one interviewer to another, sometimes glancing sideways with raised brows, sometimes closing her eyes briefly as if savoring what she is describing.
Her manner remains theatrical and coy, with little smiles, head tilts, and careful facial poses.
The scene then cuts from her face to a close view of her lap and upper legs.
She is seated, wearing a light cream top, a pale beige skirt, and long pale gloves.
Her gloved hand lifts the hem of the skirt slightly to reveal the top of a sheer nylon stocking on her thigh.
The stocking is a warm beige tone and very fine, blending closely with her skin.
The top edge has a decorative, slightly scalloped or fluted band, which she pinches and points to with her gloved fingers.
The surrounding fabric is soft and pale, matching the elegant, creamy \textbf{color} palette of her clothing and fur.
The view widens enough to show both of her legs \textbf{crossed} while she sits on or beside striped luggage.
A suitcase with vertical dark stripes is directly behind and beneath her legs, and a handbag with short handles sits to the left in the background.
Her legs are extended diagonally downward, slim and smooth in the sheer stockings.
She keeps one knee raised over the other, then runs her gloved hand slowly along the stockinged thigh and down toward the knee, as if demonstrating the fit and smoothness.
The skirt drapes softly over her lap, and the fur wrap remains visible at her side.
A man ’s shoulder or head appears as a dark shape at the right edge, suggesting the reporters are still close by while she displays the stockings.
Her gloved hand continues to stroke and smooth the stocking along the front of her leg, moving from the upper thigh down over the knee and toward the shin.
The nylon catches the light subtly, giving the leg a soft sheen.
She rests her hand near the knee, then slides it lower and back again, showing that the stocking lies flat without obvious wrinkles.
The luggage, handbag, pale skirt, and fur create a luxurious travel-or-arrival setting around the product demonstration.
After the leg demonstration, the image returns to her face.
She is again surrounded by the dark silhouettes of reporters and microphones.
Her expression becomes more serious and precise for a moment, as if emphasizing an important point.
The silver microphone stands just below her mouth, and another microphone comes from the left.
She looks straight ahead, then slightly down, then to the side, speaking with controlled, glamorous composure.
Her pearl earring and curled hair are visible against the pale fur at her shoulder.
She blinks slowly, raises her eyebrows, and shapes her lips carefully as she continues.
Near the end, the crowd partially blocks her face, with dark shoulders and heads passing across the foreground.
She gives a small, knowing smile, then her expression settles into a poised, almost satisfied look.
A brief bright, soft blur washes across the image, followed by abstract out-of-focus lights.
The lights appear as glowing white circles against a dark background, gradually resolving into rows of bulbs and streaks of colored lines.
The final image becomes a product display.
A black rectangular package or sign is decorated with many thin vertical colored streaks, like festive neon lines.
Across it, the word “ CHEESECAKE ” appears in large white capital letters.
Beneath and to the right is the Cameo branding : a large stylized white “ C ” with the word “ Cameo ” beside it and smaller text reading “ stockings. ” The package remains centered against a blue-toned background, clearly identifying the product as Cheesecake by Cameo stockings.

% matched lemmas: cluster, color, cross, crowded, flash
\end{textsample}
