\begin{textsample}{POS Dim 5 – 2010 – Score 7.00 – 2010/tv\_com\_2010\_11.txt}  \label{ex:f5_pos_049}
A young adult man with light skin and short brown hair sits at a desk in a large open-plan office, facing a black Toshiba laptop.
The white “ TOSHIBA ” logo is centered on the back of the screen, filling the foreground.
He wears a white dress shirt and looks serious and focused, his eyes fixed on the laptop.
Around him are rows of desks, office chairs, coworkers, papers, file holders, and long strips of fluorescent ceiling lights stretching far into the background.
A woman in business clothes walks behind him through the office while he remains still and intent on his work.
The setting shifts to a dimly lit apartment.
The same man, still in his white shirt and black tie, comes in through a door near a small kitchen.
A dark coat hangs on wall hooks beside him, and warm table lamps glow in the living area.
He carries a dark shoulder bag and moves past a compact kitchen with black cabinets, a sink, dishes, mugs, and under-cabinet lighting.
In the wider living room view, another young adult man with dark hair and light skin lounges on a gray sofa, wearing a dark long-sleeved shirt and jeans.
He sits slouched with one arm spread along the back of the couch, facing a television that is out of view at the bottom edge.
The man in office clothes walks behind the sofa toward the living area, still carrying his laptop or bag, while the roommate remains relaxed and passive on the couch.
A wall covered with photographs and pinned images appears near a lit table lamp.
The display includes many snapshots arranged around a corkboard : outdoor action pictures, people in odd or playful scenes, and small photo prints tacked up in an informal collage.
The man in the white shirt moves into this area, leaning down as if setting up or reaching for something below the pictures.
The view moves closer to several pinned images.
One large photo shows a child-sized \textbf{football} \textbf{player} in a red \textbf{jersey} and white helmet holding a \textbf{football} in a grassy field, with a giraffe standing in the background.
Another photo, in black and white, shows a person surrounded by dolphins or dolphin-like shapes.
A third photo below shows a man outdoors, mouth open in an \textbf{exaggerated} expression, with one arm raised.
The images look deliberately humorous or surreal, suggesting edited or staged digital-photo projects.
A black Toshiba laptop sits open on a table.
Its screen shows a video or image of a basketball hoop from below, with a ball and hands reaching upward toward the rim.
The Toshiba logo is visible below the screen, and a white mug sits to the right of the laptop.
The man ’s hands are near the keyboard, suggesting he is using the computer to work with images or video.
Later, in the apartment living room, the man in the white shirt laughs while seated behind the open Toshiba laptop.
The black laptop lid again faces outward with the white Toshiba logo.
Behind him, the roommate stands holding a bowl and spoon, watching with a neutral or slightly puzzled expression.
The room has exposed brick, warm lamps, and casual home furnishings, giving it a relaxed loft-like feel.
The man then wears large over-ear headphones and leans close to a microphone mounted on a stand.
He holds a black electric guitar across his lap, with the Toshiba laptop open directly in front of him.
His face is intent and concentrated as he looks over the laptop screen, using it as part of a home recording or editing setup.
A large television across the room shows an American \textbf{football} \textbf{game} on a bright green field, with \textbf{players} in purple and white \textbf{uniforms} running near yard-line markings.
The \textbf{football} \textbf{footage} continues on the television while the man sits in the foreground wearing headphones.
Below the TV, the Toshiba laptop is open on a low table and displays video-editing software.
The laptop screen shows the same \textbf{football} \textbf{footage} in a preview window, with multiple editing tracks and controls underneath, including vertical audio-level meters.
Nearby on the table are loose items \textbf{such} as a magazine or papers and small electronic accessories, reinforcing the home media workspace.
Back at the laptop, the man continues wearing headphones, holding the guitar and leaning toward the microphone.
His brow is furrowed and his mouth is shaped as if speaking or singing, while he watches the Toshiba screen.
The roommate sits on the sofa nearby, arms stretched along the back, looking toward him with a restrained, unimpressed expression.
In the final visible moment, both men are seen together in the living room : the roommate remains seated on the couch, while the man in the shirt and tie sits in front of the Toshiba laptop with the guitar, headphones, and microphone.
A pizza box and magazines lie on the table, and the kitchen glows in the background, making the scene feel like an after-work apartment setup where the laptop has become the center of creative projects at home.

% matched lemmas: exaggerated, footage, football, game, jersey, player, such, uniform
\end{textsample}
