\begin{textsample}{POS Dim 5 – 2000 – Score 12.00 – 2000/tv\_com\_2000\_116.txt}  \label{ex:f5_pos_024}
The commercial opens in a pale blue clinical-looking office or examination room.
A younger \textbf{man} sits in a chair across a desk from an \textbf{older} \textbf{man} in a white \textbf{shirt} and \textbf{tie}.
The room contains medical-looking furniture, an examination \textbf{table}, cabinets, framed certificates, and wall-mounted images that resemble X-rays.
The camera cuts closer to the younger \textbf{man}, seated facing forward at the desk.
A glass of water sits in front of him.
He \textbf{looks} \textbf{serious} and still.
The view then cuts to the \textbf{older} \textbf{man} behind the desk, with papers, a pen, and office items spread out in front of him.
He appears to be \textbf{addressing} the younger \textbf{man}, though no speech is visually indicated.
The camera returns to a tighter close-up of the younger \textbf{man}, whose \textbf{expression} \textbf{looks} \textbf{tense} or \textbf{uncertain}.
The setting then shifts abruptly to a blue-tinted car interior.
The same younger \textbf{man} is now seated in the driver ’s seat, smiling broadly.
A quick close-up shows a printed page or document with a Mercedes-Benz logo at the top and a structured layout of text and boxes, though most of the text is not readable.
A sequence of driving and lifestyle images follows.
A silver Mercedes-Benz sedan is shown driving through a city street lined with tall buildings.
The \textbf{man} is seen again inside the car, hands on the steering wheel, \textbf{looking} relaxed and pleased.
Another low-angle city shot shows the car passing along a curb while pedestrians walk on the sidewalk.
A distant skyline appears across water under a clear sky.
The montage continues with leisure and travel imagery : people near water, a person stepping or jumping from a dock, and a shot involving the Golden Gate Bridge with the car and driver visible in the foreground.
The silver sedan is shown parked beside a waterfront while the \textbf{man}, in a \textbf{suit}, stands on top of the car roof holding something to his face, possibly binoculars or a camera, though the object is not fully clear.
The car then drives across a large steel bridge.
The visuals shift again to a beach or coastal setting.
The same \textbf{man} appears bare-shouldered, smiling while moving along a shoreline.
A wider shot shows dunes, grasses, and the ocean.
The silver Mercedes sedan is then shown driving on an open road or bridge under a bright blue sky.
Near the end, the \textbf{man} appears again inside the car, now bare-shouldered, \textbf{looking} forward with a calmer \textbf{expression}.
The commercial ends on a black title card with the Mercedes-Benz three-pointed star logo, the text “ Mercedes-Benz, ” and the large line “ The C-Class starts at \$29,950. ” A website \textbf{address} appears at the top, and small legal fine print runs along the bottom, but most of the fine print is too small to read clearly.

% matched lemmas: address, expression, look, man, old, serious, shirt, suit, table, tense, tie, uncertain
\end{textsample}
