\begin{textsample}{POS Dim 5 – 1960 – Score 16.00 – 1960/tv\_com\_1960\_9.txt}  \label{ex:f5_pos_051}
The commercial takes place inside a small grocery or general store, with shelves, product displays, and signs visible throughout.
A white “ Nostalgic X’er ” watermark appears at the lower right of the frames.
At the beginning, a middle-aged \textbf{male} store \textbf{employee} in a white \textbf{coat} and black bow \textbf{tie} peers around a store shelf or display.
He wears glasses low on his nose and \textbf{looks} toward something off-screen.
The setting includes stocked shelves and boxed goods.
The scene then cuts to a tall \textbf{man} dressed in a Western/cowboy style : a wide-brimmed hat, \textbf{vest}, red \textbf{shirt}, neckerchief, and belt.
He stands in the store near display cases and product shelves.
The store interior has warm lighting and a cluttered retail layout.
Next, two women are shown holding large packages of Charmin toilet tissue.
One is a blonde woman in a \textbf{tan} \textbf{coat} with a scarf ; the \textbf{other} has dark hair and wears a pink cardigan over a black-and-white striped top.
Behind them is a prominent hand-lettered sign reading “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” Stacks of Charmin packages are arranged behind them as a display.
Both women appear to be examining or holding the packages closely.
The cowboy-dressed \textbf{man} is then shown standing beside the store \textbf{employee} in the white \textbf{coat}.
The \textbf{employee} \textbf{looks} up at him, while the cowboy faces forward.
A pink price or promotional sign is visible above and behind them, though the smaller text is not fully legible.
The two women reappear with Charmin packages in their arms.
Their \textbf{expressions} suggest surprise or concern as they \textbf{look} toward something off-screen.
The Charmin display and the “ PLEASE DO N’T SQUEEZE THE CHARMIN ” sign remain visible behind them.
The cowboy is then shown in front of the store \textbf{employee}, who is partly hidden behind him.
The cowboy faces forward with a \textbf{serious} or \textbf{attentive} \textbf{expression}, while the \textbf{employee} peeks from behind his shoulder.
A closer shot of the two women follows.
Both \textbf{look} startled, with the dark-haired woman raising her hands slightly in a defensive or \textbf{surprised} \textbf{gesture}.
The Charmin display remains in the background.
The commercial then cuts to a close-up of a Charmin package held in two hands.
The package shows a baby ’s face and the large brand name “ Charmin. ” Visible text includes “ Discover Squeezably softness ” near the upper left.
The package is centered prominently, with the holder ’s pink cardigan visible behind it.
The cowboy is shown smiling while holding or standing near a Charmin package.
The background is softly focused store shelving and lighting.
He is then shown beside the store \textbf{employee} again, with the \textbf{employee} \textbf{looking} upward toward him.
The cowboy holds a Charmin package at chest level.
Store shelves and packaged goods fill the background.
A wider shot shows the cowboy and the store \textbf{employee} standing in front of a large Charmin display.
The sign behind them clearly reads “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” The blonde woman walks away or \textbf{turns} away at the right side of the frame.
The cowboy and the two women are then grouped together in another aisle or section of the store.
The cowboy stands in the center foreground, with the blonde woman partly behind him on one side and the dark-haired woman on the \textbf{other}.
They face forward, and store shelves are visible behind them.
Near the end, the store \textbf{employee} is shown frontally holding a Charmin package in both hands.
He stands in front of a large stacked Charmin display.
A sign behind him now reads “ DO N’T SQUEEZE THE CHARMIN. ” He raises or holds the package high enough to cover part of his face, with his eyes and glasses visible above it.
In the final frame, the \textbf{employee} continues holding the Charmin package in front of him, \textbf{looking} over it through his lowered glasses.
The Charmin display and the large “ DO N’T SQUEEZE THE CHARMIN ” sign fill the background.
The product branding and baby image on the packages are clearly visible.

% matched lemmas: attentive, coat, employee, expression, gesture, look, male, man, other, serious, shirt, surprised, tan, tie, turn, vest
\end{textsample}
