\begin{textsample}{POS Dim 5 – 1980 – Score 6.00 – 1980/tv\_com\_1980\_81.txt}  \label{ex:f5_pos_038}
In a bright outdoor amusement-park setting, a blonde adult woman in a fitted, short-sleeved pink dress walks through a plaza.
White on-screen text at the bottom identifies her as “ Barbara Eden. ” Around her are families, children, balloons in yellow, blue, orange, and pink, a large fountain, \textbf{uniformed} performers, and a costumed \textbf{character}.
She smiles as she strides confidently in pink heels, her skirt moving lightly as she walks.
The setting feels festive and public, with colorful attractions and people \textbf{crossing} behind her.
As she continues through the park, the view lingers on her lower body and legs as she walks past a red vehicle or ride with large yellow wheels.
Her pink dress sways around her knees, and her smooth, tan legs and heels are emphasized.
She then approaches an amusement ride or tram area where children are climbing aboard and adults stand nearby.
She pauses beside a vertical metal pole at the ride entrance, smiling and gesturing toward herself, including a hand near her waist and stomach as if demonstrating fit or control.
A closer view shows her holding up a small, pale blue, egg-shaped package.
The label on it reads “ control top, ” with the Legg ’s branding visible in small print.
She presents the package beside her face, looking directly forward with a poised smile.
Behind her is a white railing and leafy trees, giving the product a clean, bright backdrop.
She keeps the package raised for several moments, then lowers it out of sight.
Still in the ride area, she leans on a white barrier and then rises, placing her hands at her waist and hips to show the smooth line of the dress over her midsection.
She turns to the side, then steps to a tall metal pole and holds it with one hand.
She pivots gracefully around it, stretching one leg back and arching slightly, showing that she can move freely while wearing the fitted dress and pantyhose.
She walks away from the ride into the open plaza, smiling back over her shoulder.
The action shifts to a balloon stand, where a man stands beside a \textbf{cluster} of colorful balloons.
Barbara reaches up high and takes hold of strings near the top of the bunch.
She extends one arm upward and the other outward, balancing on one leg in a dancer-like pose, her pink skirt flaring gently.
The balloons fill the left side of the scene with bright \textbf{color} while benches and parkgoers sit or stroll in the background.
She then crouches beside a low water area or animal enclosure and reaches down to feed a small dark animal at the edge, possibly a goat or similar park animal.
Her knees bend easily as she lowers herself, and she keeps one hand near her skirt while offering food with the other.
Next, she moves to a bench near flower beds and sits down.
A little girl in a white top and pale blue skirt approaches holding an ice cream cone.
Barbara smiles, raises her hands playfully, and accepts or compares ice cream with the child, showing relaxed movement while seated.
Later, she appears on a carousel among painted horses.
She climbs onto a white carousel horse with colorful tack, the pink dress showing a side slit as she sits sidesaddle.
A \textbf{uniformed} carousel attendant stands nearby.
Barbara lifts both arms wide in a joyful, open pose while the carousel lights glow warmly overhead.
She remains balanced and animated on the horse, one leg extended and \textbf{crossed} gracefully as the horse and surrounding carousel decorations fill the scene.
The \textbf{live-action} scene narrows into a graphic transition : the carousel image is framed by diagonal shapes, then an egg-shaped form appears against a dark red background.
The egg glows and sparkles with blue and white light, suggesting the familiar Legg ’s egg package.
It resolves into the pale blue “ control top ” package centered on the red background.
Beneath it, white text appears : “ Nothing beats a great pair of Leggs. ”

% matched lemmas: character, cluster, color, cross, live-action, uniform
\end{textsample}
