\begin{textsample}{POS Dim 5 – 2000 – Score 14.00 – 2000/tv\_com\_2000\_81.txt}  \label{ex:f5_pos_022}
The commercial opens on a dark office door or wall with a small sign reading “ MEDICAL GROUP. ” A white “ VIAGRA ( sildenafil citrate ) tablets ” graphic appears in the lower right.
A \textbf{man} in a gray \textbf{suit}, carrying a shoulder bag, enters through a doorway into a bright, modern hallway.
The setting appears medical or office-like, with glass walls, pale blue-green lighting, and clean, clinical interiors.
In the next shot, he is seen in a close, crowded interior space with \textbf{other} \textbf{suited} \textbf{men} behind him ; he \textbf{looks} upward or ahead with a \textbf{serious}, \textbf{attentive} \textbf{expression}.
The scene shifts to a bright office viewed through glass.
A woman sits at a desk in the distance.
She is then shown closer : she has short curly hair and wears a teal or greenish blouse/jacket.
She \textbf{looks} toward someone off-camera, appearing engaged in \textbf{conversation}.
The \textbf{suited} \textbf{man} is then shown in close-up, facing her \textbf{direction}, still in the same cool-toned office environment.
A partial view of the office desk follows, with items such as a phone, lamp, and papers visible ; the foreground is partly blocked by a dark silhouette.
The \textbf{suited} \textbf{man} then walks down a bright hallway from behind. \textbf{Other} staff-like figures stand or move in the corridor, including a woman holding papers and a \textbf{man} in a \textbf{shirt} and \textbf{tie} holding a folder or clipboard.
The \textbf{suited} \textbf{man} stops near the \textbf{man} with glasses and a \textbf{tie}.
They face each \textbf{other} in the hallway and appear to \textbf{speak}.
The \textbf{suited} \textbf{man} ’s face is shown animatedly, and the \textbf{man} with glasses \textbf{gestures} while holding or referring to documents.
The \textbf{suited} \textbf{man} is later seated in an office chair near a desk, while the \textbf{man} with glasses stands in the foreground.
The interaction continues through alternating close-ups : the \textbf{man} with glasses \textbf{speaks} or \textbf{gestures} ; the \textbf{suited} \textbf{man} \textbf{looks} down, then back up, appearing to listen and respond.
A wider hallway shot shows the \textbf{suited} \textbf{man} framed from behind or from an office doorway, with several people gathered in the corridor.
In the next shot, the \textbf{suited} \textbf{man} stands among a small group, including the curly-haired woman, a shorter-haired woman holding papers, and the \textbf{man} with glasses.
The “ VIAGRA ( sildenafil citrate ) tablets ” graphic again appears in the lower right.
The group faces inward as if in discussion, while the \textbf{suited} \textbf{man} \textbf{looks} forward with a \textbf{composed} \textbf{expression}.
The commercial then cuts to a computer or web page display.
The page includes the word “ VIAGRA ” and appears to show a website-like layout with images and panels.
A following shot shows the \textbf{man} with glasses walking away down a corridor.
On-screen text at the bottom reads : “ America Online Keyword : VIAGRA. ” The final sequence moves outdoors or to a parking/traffic scene.
The \textbf{suited} \textbf{man} is seen among cars, viewed from behind or at a distance.
Large centered white product text reads “ VIAGRA ( sildenafil citrate ) tablets, ” with a Pfizer logo in the upper right.
At the bottom, the text first reads “ Ask your doctor. ” In the last frame, the bottom text reads : “ Ask your doctor.
See the difference. ”

% matched lemmas: attentive, compose, conversation, direction, expression, gesture, look, man, other, serious, shirt, speak, suit, tie
\end{textsample}
