\begin{textsample}{POS Dim 5 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_7.txt}  \label{ex:f5_pos_047}
The commercial opens on a nearly black frame with archival watermarks visible.
It then cuts to a dimly lit, upscale \textbf{restaurant} or dining room.
Several round \textbf{tables} are covered with white tablecloths, set with plates, glasses, and small \textbf{table} items.
In the foreground, a woman in a light-colored outfit and a \textbf{man} in a dark \textbf{suit} sit facing each \textbf{other} at a round \textbf{table}.
The background contains \textbf{other} \textbf{diners}, warm lights, and dark furnishings, creating an intimate evening \textbf{restaurant} atmosphere.
The scene moves closer to the seated couple.
The woman is seen from the front/side with wine glasses and \textbf{table} settings in front of her.
The \textbf{man} sits \textbf{opposite}, partly visible, holding or \textbf{looking} at a menu.
The image uses a soft, overlapping dissolve effect, so \textbf{restaurant} details and figures briefly appear superimposed.
A wider view follows : the woman remains seated at the \textbf{table} while the \textbf{man} continues to \textbf{look} at a menu.
A waiter in a black tuxedo stands beside them, holding a bottle near the \textbf{table} as if presenting or preparing to serve it.
The \textbf{restaurant} remains warmly lit, with chandeliers or small lights in the background and \textbf{other} \textbf{tables} visible behind them.
The focus shifts to a close-up of a green glass bottle with a cream-colored label and a neck seal.
A hand holds the bottle near the top.
The label is partially readable but blurred ; it appears to be the same brand shown clearly later.
The shot is warmly lit, with the \textbf{restaurant} imagery faintly layered in the background.
Next, the bottle is tilted above a wine glass.
A pale liquid is poured into the glass.
The close-up emphasizes the glass, the stream of liquid, and the bottle neck, with soft golden highlights and blurred background shapes.
The image then dissolves to a close-up of a \textbf{man} in a \textbf{suit}, likely the \textbf{male} \textbf{diner}, seen through or behind the glass and reflections.
He appears to be \textbf{looking} downward or toward the \textbf{table}.
A waiter ’s dark sleeve and hand are visible at the side, suggesting continued \textbf{table} service.
The layered visual effect makes some details indistinct.
The final frame is a product shot against a dark background : a green bottle stands upright on a lit surface.
Large white text reads “ Fazi-Battaglia, ” with smaller text beneath reading “ imported from Italy. ” The bottle and brand name are centered, presenting the product clearly.
A “ Classic Commercial Archives ” watermark and a larger archive watermark remain visible over the footage.

% matched lemmas: diner, look, male, man, opposite, other, restaurant, suit, table
\end{textsample}
