\begin{textsample}{POS Dim 5 – 1980 – Score 9.00 – 1980/tv\_com\_1980\_53.txt}  \label{ex:f5_pos_069}
The commercial begins on a black screen.
A wide exterior shot then shows a Texaco gas station across a divided roadway or service area, with a large overhead sign reading “ TEXACO ” and the Texaco star logo.
In the foreground are fuel pumps labeled “ ZX, ” and a white car is parked at the pumps.
The setting appears open and roadside, with low hills or desert-like terrain in the distance.
The view moves closer to the white car.
A \textbf{man} is visible in the driver ’s seat with the door open.
A blue shopping-cart-like object or basket is near the car.
Another close-up shows a dark-haired \textbf{man} in a light-colored \textbf{shirt} seated in the car, \textbf{looking} outward through the open door/window area.
The camera cuts back to a wide shot of the Texaco station across the road.
The same or similar \textbf{man} in a white \textbf{shirt} is now outside the white car in the foreground, facing toward the distant station.
A middle-aged, balding \textbf{man} in a patterned blue \textbf{shirt} is shown beside a pump marked “ ZX. ” He appears to be attending to a car or fuel pump.
Behind him, a large red “ Z ” graphic is visible on the station wall.
He leans near the pump and car, then later stands upright and \textbf{looks} off to the side with a \textbf{serious} or curious \textbf{expression}.
A high, symmetrical shot shows a long divided highway or roadway stretching into the distance.
A \textbf{man} in a light \textbf{shirt} walks near the central divider, emphasizing the separation between the foreground service area and the Texaco station across the road.
Back at the pumps, the \textbf{man} in the white \textbf{shirt} reaches toward a pump panel/nozzle area.
The pump island includes Texaco branding and multiple black hoses.
The balding \textbf{man} is shown again in close-up holding or standing near a fuel nozzle, \textbf{looking} alertly toward something off-screen.
Another wide roadway shot shows the \textbf{man} in the white \textbf{shirt} standing at the central divider while a long fuel hose extends from the right side of the frame toward him.
The hose crosses or reaches across the open paved area.
The scene returns to the white car and pumps.
The \textbf{man} in the white \textbf{shirt} is crouched or bent near the rear side of the white car, handling a fuel nozzle and hose.
The balding \textbf{man} stands nearby among the pumps.
A close-up of the balding \textbf{man} follows, with the nozzle visible near him ; he leans forward slightly, as if \textbf{watching} or \textbf{reacting} to the activity.
Inside the station building, the \textbf{man} in the white \textbf{shirt} appears at a service window or counter.
A blond \textbf{employee} wearing a striped \textbf{shirt} sits behind the counter, surrounded by shelves and equipment.
The two face each \textbf{other} through the window area.
A black title card appears with the Texaco star logo and the word “ TEXACO ” beneath it.
Large white text at the bottom reads : “ EXPECT MORE. ” The commercial then returns briefly to the exterior station view.
In the foreground, the balding \textbf{man} is near a “ ZX ” pump beside the white car, with the Texaco station still visible across the roadway.
In the next shot, he walks away from the pump area toward the Texaco station across the road, carrying or guiding something not fully clear from the sampled frame.
The scene ends on black.

% matched lemmas: employee, expression, look, man, other, react, serious, shirt, watch
\end{textsample}
