\begin{textsample}{POS Dim 5 – 1960 – Score 11.00 – 1960/tv\_com\_1960\_44.txt}  \label{ex:f5_pos_055}
The commercial is presented in a sepia-toned or black-and-white nostalgic style, with a persistent “ Nostalgic X’er ” watermark at the lower right.
It opens in a dim interior that \textbf{looks} like an \textbf{old} \textbf{shop}, café, or soda-fountain setting.
A long counter runs into the foreground with a row of stools beside it.
Shelves and a doorway or window are visible in the background, creating an old-fashioned retail atmosphere.
The scene cuts closer to a young boy seated or standing at the counter.
He wears a cap and \textbf{looks} toward the camera or toward someone off-camera.
Behind him are shelves or display areas filled with items, though details are indistinct.
A close-up then shows a young girl with curled hair.
She \textbf{looks} directly forward and smiles slightly.
The framing is tight on her face, emphasizing her \textbf{expression}.
The commercial then cuts between close-ups of different children : a blond boy smiling, another boy with curly hair \textbf{looking} forward with his mouth open, and later two boys side by side, one in a patterned \textbf{shirt} and another wearing a small hat.
The children appear \textbf{attentive} and engaged, often \textbf{looking} toward someone or something off-screen.
An elderly \textbf{man} appears behind the counter.
He has thinning hair, wears glasses, and is dressed in a \textbf{shirt} with a bow \textbf{tie} and dark \textbf{vest} or \textbf{apron}.
Behind him are shelves with glassware or jars.
He \textbf{looks} upward and smiles in some shots, and in another shot he \textbf{looks} down as if preparing or handling something below the counter.
There is a brief close-up of a hand manipulating or holding a dark object near a counter or machine, but the exact object is unclear from the sampled frame.
Several shots use dissolves or superimposed imagery : one frame overlays the boy ’s face with the \textbf{older} \textbf{man} and the \textbf{shop} background, and another overlays the \textbf{older} \textbf{man} ’s face with a circular or elongated object near his mouth area, though the details are not clear.
Near the end, a blond boy smiles in close-up, followed by the elderly \textbf{man} smiling or \textbf{reacting} animatedly.
The final frame shows a product package in close-up.
The box has a window revealing dark rounded items inside.
Visible text includes “ 4 PACK, ” “ NEW, ” and the product name “ Jolli-lolli. ” A brand name or logo appears at the upper left but is not fully clear in the frame.

% matched lemmas: apron, attentive, expression, look, man, old, react, shirt, shop, tie, vest
\end{textsample}
