\begin{textsample}{POS Dim 3 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_25.txt}  \label{ex:f3_pos_018}
The commercial opens very dark, with only vague shapes visible.
It then shifts into a high-contrast black-and-white montage of \textbf{human} faces and graphic overlays.
Two overlapping faces fill the frame, with several red question marks placed around their eyes and cheeks.
The style is \textbf{layered} and collage-like, with faces partially transparent and superimposed.
A circular magnifying-glass-like graphic appears over a face.
Inside it is a smiling bald cartoonish/miniature head with glasses, and handwritten text such as “ Hi ” appears nearby.
The \textbf{imagery} then cuts to a young man ’s face in close-up, eyes wide open, with a round spot or lens centered on his nose and small red acne/bacteria-like icons on the face.
The same male face remains as a background while large handwritten text reading “ Acne Bacteria ” appears across his forehead area, underlined with a green stroke.
Small red circular symbols are scattered over the image.
At the lower left, small text appears to read “ SIMULATED BLACKLIGHT DEMO, ” though it is partly blurred.
The commercial then introduces product-related typography.
A large pink “ OXY ” logo and blue “ sensitive ” text \textbf{dominate} the frame, \textbf{layered} over a grayscale male face on the left.
Handwritten phrases include “ Virtually, ” “ No Drying, ” and “ New. ” Small \textbf{human} \textbf{silhouettes} stand in front of the large text, including a figure with raised arms.
Next, a woman ’s face fills the right side of the frame in black and white, with pink marks on her cheek.
Curved handwritten text reads “ Virtually No Irritation ” and “ No Drying. ” On the left, a smaller figure or image of a man appears in an exaggerated pose.
Small text at the bottom says “ SEE PACKAGE FOR DETAILS. ” The word “ GUARANTEED ” then appears large across the top, while the woman ’s face remains on the right and small walking figures appear near the center.
Another shot shows a male face in close-up with large hands framing his eyes and cheek.
Blue and green \textbf{glowing} spots appear over the face, and the word “ GUARANTEED ” is written above.
A small couple-like \textbf{silhouette} stands in front of the face.
The montage returns to the wide-eyed male face.
Around him are handwritten day labels or partial words such as “ Wed, ” “ Sun, ” “ Mon, ” and “ Fri, ” along with small acne-like icons arranged across the face area, suggesting a time sequence visually.
A product package then appears large in the center : a teal-and-black “ OXY sensitive ” package with “ VANISHING ” visible near the bottom.
It is superimposed over the black-and-white face montage and other graphic \textbf{elements}.
The next frames show the male face again with two small smiling bald heads wearing glasses and sunglasses \textbf{layered} over it, surrounded by red heart \textbf{graphics}.
Text in the upper left reads “ USE ONLY AS DIRECTED. ” The background then turns pink, isolating the two floating cartoon heads and hearts.
A red prohibition symbol appears over the two heads, with handwritten text above that appears to say “ Product Shot, ” and white text inside or near the circle reading “ In Advance. ” The meaning is \textbf{stylized} and partially unclear, but the visual resembles a “ no ” symbol over the heads.
A final product shot shows the “ OXY sensitive ” package again on a plain light background.
Handwritten text reads “ Product Shot, ” “ Invisible Gel, ” and “ NEW ” on both sides.
The package is tilted slightly, with the teal-and-black design and pink “ OXY ” branding prominent.
The commercial ends with a black-and-white image of a smiling young woman with her arm around a young man.
Large blue \textbf{stylized} lettering arches above them, appearing to read “ OXYCUTE ’ em ” or similar, though the exact wording is \textbf{stylized} and not fully clear.
At the bottom right is the “ SB SmithKline Beecham ” logo.

% matched lemmas: dominate, element, glowing, graphics, human, imagery, layer, silhouette, stylize
\end{textsample}
