\begin{textsample}{POS Dim 3 – 1970 – Score 11.00 – 1970/tv\_com\_1970\_120.txt}  \label{ex:f3_pos_031}
A city skyline fills the screen in daylight.
Several office towers stand against a pale blue sky : a tall, dark, almost black \textbf{rectangular} building on the left, a striped high-rise on the right, and lower white and gray buildings in the foreground.
The view emphasizes a dense downtown business district, with modern corporate buildings clustered together.
The skyline gradually gives way to a dramatic upward view of a glass office tower.
Its reflective windows and dark vertical supports stretch high into a bright sky, making the building look tall and imposing.
Sunlight glints off the glass.
The image then blends into the inside of a busy office, where several adults work at desks under fluorescent ceiling lights.
The room has a practical 1970s office look : pale walls, desks arranged in rows, papers, chairs, and office equipment.
On the right, a woman-presenting worker with dark hair, wearing a bright yellow long-sleeved top, sits at a desk and uses a white telephone \textbf{console}.
She holds a white \textbf{handset} to her ear while her other hand rests near the buttons.
Other workers sit or stand in the background, including a person in a striped shirt near shelves or equipment and another person in a patterned shirt at a nearby desk.
The view moves closer to the telephone \textbf{console} on the woman ’s desk.
It is a compact white PBX-style \textbf{unit} with a \textbf{slanted} front panel.
The upper \textbf{section} has rows of small \textbf{horizontal} label strips or indicator lights, and the lower \textbf{section} has multiple push buttons.
A white coiled cord runs from the \textbf{handset} to the \textbf{console}.
The woman ’s hand reaches across the panel, pressing or selecting buttons, suggesting she is routing or managing calls.
The equipment is shown as small enough to sit on a regular desk rather than requiring a large switchboard.
The office equipment image blends back into upward-looking city architecture.
Tall buildings rise on either side, their window grids receding toward a bright patch of sky.
The view continues among the high-rises, reinforcing the urban business setting.
This then dissolves into another office interior, brighter and more open, with a reception or administrative area.
A large counter or desk sits in the foreground with telephone \textbf{consoles} placed on it.
Behind it, people work at desks in a larger room.
The space is tidy and professional, with ceiling panels, office chairs, and a doorway leading to a darker hall.
The focus shifts left to a darker reception desk area.
A seated adult with dark hair and a gray jacket \textbf{operates} another compact PBX \textbf{console} placed on the desk.
A framed picture hangs on the wall behind them, and a doorway opens into a back area where another worker is visible at a desk.
The operator ’s hands move over the \textbf{slanted} control panel.
They lift a \textbf{handset} from its cradle, then the \textbf{handset} and coiled cord move out of the way as the \textbf{console} remains prominently displayed.
The \textbf{unit} again appears compact, with rows of labeled indicators and a cluster of buttons on its angled face.
It sits neatly on the desk beside stacked papers or trays, taking up relatively little surface space.
The \textbf{console} image overlays with another view of a tall glass-and-grid office building.
The building façade fills the view, its many square windows forming a repeating pattern.
Reflections of nearby structures and sky shimmer across the glass.
The perspective moves along the building face, showing mirrored blue panes and dark structural lines, then widens slightly to include neighboring high-rises.
The visual connection between office buildings and telephone equipment continues through these overlapping images.
The scene changes to a private office or conference-like workspace.
A woman-presenting adult with short dark hair, wearing a dark blazer over a light blouse, sits at a wooden desk.
A cream-colored PBX telephone \textbf{console} is on the desk in front of her, angled toward her hand.
Behind her, a person in a plaid shirt stands near shelves or a cabinet, and to the right a man-presenting adult in a suit sits with papers in his lap, watching or working.
The woman reaches toward the \textbf{console}, lifts the \textbf{handset}, and brings it to her ear.
The \textbf{console} has a long dark top panel with several white \textbf{horizontal} label strips and a \textbf{central} cluster of square buttons, plus a coiled cord connected to the \textbf{handset}.
The view moves in closer to the desk as her hand \textbf{operates} the \textbf{central} buttons on the \textbf{console}.
Papers and office items lie nearby, and the suited man remains partly visible in the background, holding documents.
Her fingers press different buttons, visually \textbf{demonstrating} call handling or line selection.
The close-up emphasizes the controls : rows of white line labels, small switches or buttons, and the compact wedge-shaped white \textbf{casing}.
The telephone \textbf{console} then blends into another city-building view.
A mid-rise office building with a grid of windows appears against a pale sky.
As the city scene settles, large white text appears centered over the buildings : “ We hear you. ” The words are bold, rounded, and easy to read, with a period at the end.
Beneath the phrase is the Bell logo : a white bell symbol inside a white \textbf{circle}.
The background returns to the original downtown skyline with the dark tower on the left, lighter high-rises on the right, and white buildings in the foreground.
The slogan and Bell logo remain centered over the city as the commercial ends.

% matched lemmas: casing, central, circle, console, demonstrate, handset, horizontal, operate, rectangular, section, slant, unit
\end{textsample}
