\begin{textsample}{POS Dim 3 – 1950 – Score 18.00 – 1950/tv\_com\_1950\_74.txt}  \label{ex:f3_pos_004}
The commercial is in black and white.
It opens on a \textbf{plain} studio background with a neatly dressed adult man standing behind two television sets.
He has dark, combed hair and wears a light-colored suit jacket, dress shirt, and dark tie.
His hands rest on the tops of the sets as he faces forward like a \textbf{demonstrator}.
To his left is a larger television cabinet with a broad, rounded \textbf{rectangular} screen and controls beneath it.
To his right is a darker, older-looking set with a much smaller screen area and \textbf{speaker} grilles on either side.
The larger set begins showing a close-up of a young woman ’s face in profile.
She has dark, smooth hair and appears to be smiling or speaking, her head and shoulders filling much of the big rounded screen.
The smaller set beside the man has a noticeably smaller blank screen, and a tiny floating image of the same woman ’s head appears on the wall behind it, emphasizing the difference in viewing \textbf{size}.
The man leans slightly toward the larger television and gestures over its screen.
He then lifts a rounded \textbf{rectangular} panel or screen-shaped image upward from the large television.
The panel contains the woman ’s close-up, now separated from the TV cabinet like a visual comparison card.
He holds it by the top edge, raising it beside his own head.
The woman ’s face on the panel is nearly as large as the man ’s, making the comparison very direct.
The big television cabinet below is now blank, while the small image remains off to the side in the background.
The scene dissolves into a single RCA Victor television set placed in a home-like setting.
The set stands on slim legs and has a large rounded screen with the same woman ’s smiling profile displayed.
Large white \textbf{price} lettering appears over the lower part of the set : “ \$199.95. ” Beneath it, smaller text reads, “ SLIGHTLY HIGHER IN FAR WEST AND SOUTH. ” The \textbf{price} text then disappears, leaving the television centered with the woman ’s close-up still on the screen.
More of the living room becomes visible around the set.
The television sits against the back wall, beneath three framed pictures.
To the left are a sofa, curtains, a side table, a floor lamp, and an \textbf{upholstered} chair.
In the foreground is a coffee table with magazines or papers and a dark floral \textbf{arrangement}.
To the right are another chair, a small table or \textbf{console}, and a pair of matching lamps.
The television remains the \textbf{central} object in the room.
The woman ’s image \textbf{fades} away, leaving the screen blank, and the set stands quietly as part of the furnished living space.
Near the end, large translucent lettering begins to appear over the living room wall, then becomes a bold RCA Victor brand graphic.
The room \textbf{fades} behind it.
The final image is the RCA Victor logo on a \textbf{plain} background : large capital letters spelling “ RCA \textbf{VICTOR}, ” with the familiar dog sitting beside a \textbf{phonograph} \textbf{horn}, listening into it.
Below, in \textbf{quotation} marks, the text reads “ HIS \textbf{MASTER} ’S \textbf{VOICE}. ”

% matched lemmas: arrangement, central, console, demonstrator, fade, horn, master, phonograph, plain, price, quotation, rectangular, size, speaker, upholster, victor, voice
\end{textsample}
