\begin{textsample}{POS Dim 3 – 1980 – Score 9.00 – 1980/tv\_com\_1980\_68.txt}  \label{ex:f3_pos_035}
The commercial opens with a dark, low-contrast shot of a man seated behind a desk or table.
He appears to be wearing a dark jacket with a light shirt, possibly formal clothing.
Behind him are vertically striped curtains.
On the desk there are indistinct objects, including papers or fabric to the right and a dark rectangular object to the left.
The image then shifts to a television or monitor screen.
The screen shows \textbf{layered}, semi-transparent \textbf{imagery} : a face or figure, colored shapes, and faint text or \textbf{graphics}.
The surrounding frame of the television is visible, suggesting the viewer is looking at an image displayed on a set rather than directly at a scene.
Another monitor image follows, now mostly monochrome.
It shows a \textbf{silhouetted} scene with figures or objects moving across a horizontal landscape-like background.
Faint greenish text or display \textbf{graphics} are superimposed over the picture, but the words are not clearly readable.
The commercial cuts to an \textbf{extreme} close-up of a circular speaker cone or similar audio component.
The round diaphragm and central dust cap are prominent, with light reflecting off the surface.
Next, a television/monitor displays a stage-like image with dark figures against a gray background.
Across the screen, a bold horizontal black strip carries the large white word “ MITSUBISHI. ” The brand name \textbf{dominates} the frame.
The following shot returns to \textbf{layered}, \textbf{reflective} \textbf{imagery}.
A person or figure appears partially visible through or overlaid with glass-like panels and window frames.
The scene is \textbf{difficult} to parse because of reflections and superimposition, but it suggests a display \textbf{environment} with screens and shiny surfaces.
Later, the frame shows a home-electronics arrangement : a large speaker on the left, a television/monitor in the center, and a dark stereo or component stack on the right.
The center screen displays a man wearing dark sunglasses and a suit, turned partly toward the camera.
The image on the screen overlaps visually with reflections or a translucent blue-tinted overlay.
A similar setup remains visible in the next shot, slightly wider or shifted.
The man in sunglasses is still shown on the central screen.
The surrounding room includes a brick or tiled wall pattern and objects in the foreground, possibly a remote control or equipment on a surface.
The left speaker and right-side audio components remain visible.
The commercial ends on a close-up of a television screen showing a black-and-white \textbf{extreme} close-up of a mouth with a thick mustache above the upper lip.
The television frame is visible, and the “ Mitsubishi ” name or logo appears below the screen.

% matched lemmas: difficult, dominate, environment, extreme, graphics, imagery, layer, reflective, silhouette
\end{textsample}
