\begin{textsample}{POS Dim 3 – 1950 – Score 6.00 – 1950/tv\_com\_1950\_99.txt}  \label{ex:f3_pos_084}
The commercial is in grainy black-and-white and centers on a light-colored, two-door convertible car with the top down, whitewall tires, chrome trim, and a prominent front bumper/grille. - It begins with a nearly black frame, with no distinct objects visible. - The first clear image shows the convertible in a clean side profile, centered against a pale, studio-like background.
The car is shown as an isolated product image. - The image then shifts through a hazy or dissolving visual \textbf{effect}, with the car still visible in side profile but partly obscured by cloudy, circular blur. - A front three-quarter \textbf{studio} view follows, emphasizing the car ’s rounded front end, headlights, chrome bumper, windshield, and whitewall front tire. - A very close, low-contrast detail shot appears next, showing a horizontal line or trim area on a smooth surface, likely part of the car body, though the exact feature is unclear because of blur and overexposure. - The commercial then moves to outdoor driving-related shots.
A close side view shows the open cabin, windshield frame, front seat area, and folded convertible top at the rear, with trees or foliage in the background. - A wider outdoor shot shows the car parked or moving slowly with at least two occupants inside.
The vehicle is viewed from the front-left side, with the top down. - Several closer shots show the occupants through the windshield and over the hood.
Reflections and glare make faces and details indistinct.
In one frame there appears to be faint text or a graphic near the bottom, but it is not readable. - A side close-up shows two people seated in the car, viewed through the open side and windshield frame.
Their exact identities, expressions, and actions are unclear, though they appear to be riding in the convertible. - Another exterior shot shows the car on a road or driveway bordered by darker trees or shrubbery, angled as if traveling or turning toward the camera. - The commercial returns to close product-detail \textbf{imagery}, including an \textbf{overexposed} close-up of the car ’s side door and lower body trim. - The final frame returns to a clean studio-style side profile of the convertible, centered against a pale background, again emphasizing the full length of the car, its open top, side trim, and whitewall tires.
Overall, the visuals \textbf{alternate} between \textbf{polished} \textbf{studio} product shots of the convertible and outdoor lifestyle/driving shots with occupants, using dissolves, close-ups, and frontal/side angles to highlight the car ’s exterior styling and open-top design.

% matched lemmas: alternate, effect, imagery, overexpose, polished, studio
\end{textsample}
