\begin{textsample}{POS Dim 3 – 2000 – Score 8.00 – 2000/tv\_com\_2000\_26.txt}  \label{ex:f3_pos_029}
The commercial begins with a black screen.
It then cuts to a black-and-white corporate boardroom.
A long \textbf{polished} conference table \textbf{dominates} the room, with rows of empty executive chairs along both sides.
Three men in dark suits are seated far apart around the table.
The setting is formal, minimal, and high-contrast, with wood-paneled walls and overhead \textbf{lighting}.
The camera moves to closer views of the men.
One older man with light hair sits at the table, seen in profile, while another middle-aged man in a suit sits farther back.
The middle-aged man is then shown in close-up, facing forward with a serious expression.
Another cut shows the older light-haired man seated alone at the table, also serious and formal.
The mood remains tense and restrained.
The middle-aged man is shown again in close-up, now appearing to speak or react, though no audio content is visible.
Shortly after, people begin standing up around the conference room.
More men in suits enter or rise from their seats.
The room \textbf{becomes} \textbf{crowded} with similarly dressed businesspeople.
Several men stand close together, looking in different directions, as if responding to something happening in the room.
The number of suited men increases dramatically.
A wide shot shows many men standing throughout the boardroom, filling the space around the table and chairs.
One man stands prominently in the foreground, while many others are arranged behind him.
The older light-haired man remains seated in one shot, surrounded by standing figures, making him appear isolated or boxed in.
The scene then shifts to an exterior view through large glass windows.
Many suited men are visible inside or behind the glass, pressed together in a dense group.
The commercial cuts to an overhead view of people in suits moving outdoors on a city street or plaza.
Their bodies and \textbf{shadows} form a \textbf{scattered} but coordinated-looking flow.
A higher aerial shot shows a large \textbf{crowd} of dark-suited figures gathered densely at a street corner or intersection among tall city buildings.
The \textbf{crowd} appears compact and massed together, contrasting with the earlier boardroom setting.
The final frame changes visual mode : it shows a medical-style X-ray image of a \textbf{human} chest and lungs.
Over the X-ray, large text reads “ undo tobacco now, ” with “ un ” in red and the rest in black.
Below it is the website “ TobaccoFreeCA.com. ” The final image introduces an explicit anti-tobacco message visually, linking the preceding corporate/crowd \textbf{imagery} to tobacco through the closing text and lung X-ray.

% matched lemmas: become, crowd, dominate, human, imagery, lighting, polished, scattered, shadow
\end{textsample}
