\begin{textsample}{POS Dim 3 – 1950 – Score 12.00 – 1950/tv\_com\_1950\_24.txt}  \label{ex:f3_pos_014}
The commercial is in black and white and opens in a neat 1950s living room.
A sofa sits on the left with two women seated on it, a coffee table in front of them covered with magazines or photo albums and cups.
Behind them are paneled walls, a table lamp, shelves filled with books, and decorative objects including a small horse figurine and a bust.
A compact slide projector rests on a small table to the right of the sofa.
It is a \textbf{boxy} machine with a \textbf{slanted} top, front controls, and a round projection lens on its right side.
A tall, dark-haired man in a suit leans casually near the sofa, looking toward the women.
Another suited man stands at the shelves with his back turned, then turns and comes toward the projector holding slide materials.
The women smile and look on as the men gather around the projector.
The man who came from the shelves handles small slide mounts, and the taller man leans in to examine them.
In a closer view against the bookcase background, the two men compare different slide \textbf{sizes}.
One man holds up a small square slide mount, inspecting it by eye, while the other removes a larger square slide or slide packet from a small box.
They hold the different formats side by side, making the \textbf{size} difference visible.
The older-looking man with a \textbf{pocket} square raises a larger slide mount as if explaining it, while the taller man looks at the box in his hands.
The product name then appears over the men and dissolves into a clean display of the projector alone.
Large script text across the lower part reads “ Anscomatic, ” followed by smaller text underneath : “ the A+ slide projector. ” The projector is shown on a \textbf{plain} surface, its lid and top assembly open so the slide-loading area and controls are visible.
Its round lens \textbf{protrudes} from the right side, and a power cord trails away to the left.
The demonstration moves closer to the machine.
Bold on-screen text appears, including “ Fully-Automatic, ” and then the clearer phrase “ Takes 2¼ x 2¼ slides, too! ” A hand holds a larger square slide mount above the open top and places it into the projector ’s slide area.
The hand then moves down toward the controls, showing how the slide is handled and advanced.
The projector ’s open channel, switches, and mechanical parts are visible as the large slide sits upright in the top slot.
A projection screen fills the scene next.
On it is a sharp family snapshot : three young boys sitting outdoors with a dog between them.
The screen is bordered by darkness around the room.
The \textbf{projected} image changes to another child ’s picture, and a suited man stands to the right of the screen holding a small \textbf{wired} remote control near his chest.
As he \textbf{operates} it, the images on the screen change : a picture briefly appears in a \textbf{horizontal} strip, then a full portrait of a young boy fills the screen, followed by another child image.
The man watches the screen and smiles, \textbf{demonstrating} that he can control the slide changes while standing away from the projector.
The room lights then come back up, revealing the living room again.
The guests are seated together on the sofa : the two women and a suited man sit close, smiling and looking toward the presenter.
The presenter stands beside the small table with the projector on it, holding the \textbf{wired} remote.
The lit table lamp glows behind the sofa, and the group appears pleased and engaged at the end of the slide show.
One seated man raises a hand or small control toward the standing presenter as they all react to the demonstration.
The projector returns on a \textbf{plain} surface for the closing product display.
Large white text at the bottom reads, “ Only \$11.95 Down. ” The product remains centered, showing its sloped top, front buttons, and side lens.
The image then blends into a circular camera-lens graphic.
Around the ring are lens markings including “ ANSCO ” and “ f:2, ” with smaller technical lettering around the inner rim.
Inside the lens \textbf{circle}, different Ansco products appear one after another : a box labeled “ Anscochrome ” with the word “ ANSCOCHROME ” below it, then a box labeled “ Ansco ” with the on-screen words “ All-Weather Pan, ” then a simple front view of a camera with the word “ CAMERAS. ” Finally, the Anscomatic projector appears inside the same lens \textbf{circle} with the word “ ANSCOMATIC ” beneath it, tying the projector to the broader Ansco camera and film line.

% matched lemmas: boxy, circle, demonstrate, horizontal, operate, plain, pocket, project, protrude, size, slant, wire
\end{textsample}
