\begin{textsample}{POS Dim 3 – 1960 – Score 27.00 – 1960/tv\_com\_1960\_94.txt}  \label{ex:f3_pos_021}
A wooden Zenith stereo \textbf{console} is seen from above against a \textbf{plain} blue studio background.
Its top is open, revealing a black \textbf{vinyl} \textbf{record} on the \textbf{turntable} at the right, a \textbf{radio} or amplifier control panel at the left with a \textbf{horizontal} \textbf{dial} and round \textbf{knobs} below it, and a large wood \textbf{speaker} \textbf{section} on the far right.
The cabinet is long and low, with warm wood grain and short \textbf{tapered} legs.
As the view comes closer, the \textbf{record} fills more of the image.
It has a red center label, and the tonearm rests near the right side of the \textbf{turntable}.
The Zenith name is visible on the metal \textbf{turntable} base.
A man ’s hand and wrist, the sleeve of a dark suit jacket visible, reaches in from the right.
He grips the end of the tonearm and moves it over the spinning black \textbf{record}.
From above, the hand deliberately places the \textbf{cartridge} near the middle of the \textbf{record}, then shifts it around rather freely, \textbf{demonstrating} contact with the \textbf{record} surface.
The red label on the \textbf{record} is readable enough to show it is a Columbia \textbf{record}.
The tonearm itself is light-colored, with a \textbf{rectangular} \textbf{cartridge} at the end and a slim arm extending back to its pivot.
Closer side views show the tonearm and \textbf{cartridge} just above or on the glossy \textbf{record} surface.
The hand holds the \textbf{cartridge} between thumb and fingers, lowering it and lifting it again.
A tall metal center spindle rises from the middle of the \textbf{turntable}, and another \textbf{horizontal} support arm is visible in the background.
The \textbf{demonstrator} presses the \textbf{cartridge} down lightly with a fingertip, then slides it across the \textbf{record} surface and over the red label area.
The action looks intentionally rough for a \textbf{record} player demonstration : the \textbf{cartridge} is dropped, dragged, lifted, and set down again, while the \textbf{record} ’s shiny grooves reflect light.
No face or full person appears, only the hand performing the demonstration.
The close-up continues with the \textbf{cartridge} moving from the black grooved area toward the red label, then back across the \textbf{record}.
The hand repeatedly lifts the tonearm a small distance above the \textbf{record} and lets it return, emphasizing that the needle pressure is very light.
The \textbf{cartridge} rests on the spinning disc without any visible gouging or tearing.
The surrounding \textbf{turntable} parts are metallic gray and cream-colored, with vertical posts and the \textbf{central} spindle framing the action.
The image then shifts to a more technical-looking close-up of the tonearm over the \textbf{turntable}, now with the \textbf{record} surface appearing darker and more diagram-like.
A small shiny coin-like weight is placed by the hand on the end of a narrow balance or lever near the stylus area.
White on-screen text appears near the upper right : “ ONLY 1/14th OUNCE. ” The small weight sits at the far end of the light-colored lever while the \textbf{cartridge} and tonearm hover nearby, visually illustrating the tiny amount of pressure being discussed.
The hand \textbf{withdraws}, leaving the weight and tonearm \textbf{arrangement} in view.
This demonstration image blends into a product display of a full wooden \textbf{console} stereo.
Large white text reading “ ZENITH STEREO ” appears above and behind the cabinet.
The \textbf{console} is centered on a blue, misty studio background.
It has a long \textbf{rectangular} body, pale \textbf{speaker} grilles at both ends, and carved or arched wood paneling across the middle.
The cabinet stands on slim legs and is presented like fine furniture rather than just electronics.
The \textbf{console} changes to another cabinet style.
The background becomes warmer and pinkish, and the new stereo is more modern and \textbf{boxy}, with a long, low profile on angled legs.
Its front has vertical slats at both ends and lighter vertical panels through the center.
The cabinet is shown straight on, isolated against the \textbf{plain} studio backdrop.
A small, \textbf{simplified} electronic component then appears in the center of the cabinet, as if revealed from inside it.
The cabinet \textbf{fades} away, leaving the component \textbf{enlarged} : a metal amplifier chassis with cylindrical silver parts, black \textbf{rectangular} blocks, and a blue-gray base.
White text appears above the amplifier : “ ZENITH SOLID STATE 240W AMPLIFIER. ” The amplifier sits alone on the warm studio background, angled slightly so its front and side are visible.
It has a \textbf{sturdy} metal base, a few front openings and controls, several shiny cylindrical capacitors rising vertically, and black components lined up behind them.
Later the text changes to “ 240 WATTS PEAK MUSIC POWER, ” with a smaller line of technical output text at the bottom.
The amplifier remains prominent, cleanly lit, and mechanical-looking, contrasting with the earlier furniture cabinets.
The amplifier image \textbf{fades} into a furnished room setting.
A \textbf{mid-century} wooden Zenith \textbf{console} sits against a textured blue wall.
It is long and low, with vertical slatted \textbf{sections} and a \textbf{central} wood panel, supported by angled legs.
A decorative shallow bowl rests on top.
To the right is a light yellow \textbf{upholstered} armchair with wooden legs, and behind it a tall potted plant resembling bamboo.
A framed wall decoration hangs above the \textbf{console}.
The floor has an irregular stone-pattern design.
A large white, italicized “ ZENITH ” logo appears across the upper part of the scene.
The same large Zenith logo remains as the setting changes to another room.
A more traditional wood \textbf{console} stands against patterned wallpaper.
It has pale \textbf{speaker} grilles at each end and curved raised wood panels in the center.
A dark wooden chair with a light seat sits to the left, and an ornate wall \textbf{clock} hangs above and to the right.
The stereo has a polished furniture look, with the electronics hidden inside the cabinet.
Finally, another room display appears with a different Zenith \textbf{console}.
This cabinet is warmer reddish wood, with decorative curved legs, pale \textbf{speaker} grilles at both ends, and double doors or panels in the center.
A vase of flowers sits on top at the left, a framed picture hangs above, and a light-colored chair stands to the right near heavy curtains.
The large Zenith logo stays over the upper portion of the image, reinforcing the brand while the visuals show the stereo offered in several furniture cabinet styles.

% matched lemmas: arrangement, boxy, cartridge, central, clock, console, demonstrate, demonstrator, dial, enlarge, fade, horizontal, knob, mid-century, plain, radio, record, rectangular, section, simplify, speaker, sturdy, taper, turntable, upholster, vinyl, withdraw
\end{textsample}
