\begin{textsample}{POS Dim 3 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_6.txt}  \label{ex:f3_pos_040}
The commercial begins in what appears to be a \textbf{studio} or backstage setting.
A woman in a purple outfit stands near television or \textbf{stage} equipment, including a large camera or light on a stand and other production gear.
On-screen text identifies her as “ Martha Raye ” and “ denture wearer. ” The \textbf{lighting} is \textbf{dim} and theatrical, with equipment and walls visible around her.
The next frame cuts to a close-up of a product box being held in someone ’s hand.
The box is teal/green-blue and prominently labeled “ Extra Strength Polident ” with the words “ Denture Cleanser ” underneath.
The brand name “ Polident ” appears in large yellow \textbf{letters}.
A small circular label on the front also reads “ Polident. ” The background is blurred, emphasizing the product package.
The following frame shows the same woman more clearly in a brightly lit dressing-room or backstage \textbf{environment}.
She has light blue-gray hair, wears a lavender/purple top, and holds the Polident box up near her face.
She is smiling.
The background includes vertical mirror lights, giving the setting a performance or makeup-room look.
The image has a soft, slightly overlaid or transitional appearance.
In the final frame, the woman remains in the dressing-room setting, holding the Polident box beside her face and looking toward the camera.
She wears jewelry, including a necklace, and the purple outfit is still visible.
On-screen text at the bottom reads : “ Polident green gets tough stains clean. ” The product box is clearly visible in her hand, and the \textbf{illuminated} mirror bulbs and backstage decor remain in the background.

% matched lemmas: dim, environment, illuminate, letter, lighting, stage, studio
\end{textsample}
