\begin{textsample}{POS Dim 3 – 2020 – Score 14.00 – 2020/tv\_com\_2020\_108.txt}  \label{ex:f3_pos_053}
The commercial opens in near-total darkness.
A single small figure stands or crouches far away under a narrow blue-white spotlight, surrounded by black space.
The setting has a theatrical, studio-like feel.
The camera then shows a speed skater in a white outfit under a bright blue spotlight on an ice-like surface.
The athlete bends low in a skating stance, one arm extended, with a long \textbf{shadow} visible on the \textbf{illuminated} patch beneath them.
The visual style quickly shifts into a digital/neon \textbf{environment} : the skater appears against a blue and green background with a gridded floor, wearing bright yellow skates.
A white wireframe sphere and cross-sectional lines then appear around the skater, suggesting motion analysis or design modeling.
The same skater is shown in close-up and side views, moving low across a blue-lit icy surface with particles or snow-like specks in the \textbf{air}.
Multiple ghosted images of the skater appear in sequence, indicating speed and \textbf{repeated} motion.
Thin white rectangular overlays and small tracking boxes appear on screen.
Onscreen text identifies the athlete as “ ERIN JACKSON ” and “ TEAM USA SPEED SKATING. ” The commercial cuts to real competition \textbf{footage} of a speed skater on an indoor rink, skating around a turn.
The athlete wears a dark racing suit and white lower-leg coverings.
This contrasts with the \textbf{stylized} \textbf{studio} shots.
The next sequence focuses on a skier.
In a dark, blue-lit \textbf{studio} \textbf{environment}, a skier in a pale/white outfit with red skis is captured midair.
The skier is shown both in full-body action and in close-up details of skis, bindings, boots, and body position.
White and yellow technical rectangles and line overlays appear across the image, again giving the \textbf{impression} of digital tracking or design analysis.
The skier is also shown in outdoor snow-park \textbf{footage}, jumping over a white terrain feature.
This is followed by highly \textbf{stylized} color treatments : one image appears in hot orange/yellow/red \textbf{tones}, and another in stark black-and-white with blue crosshair lines over the skier.
The commercial then briefly shows a snowboarder on a snowy course.
The athlete wears a red helmet and red/white top, rides a snowboard, and then appears seated or sliding on the snow with one arm raised.
The competition course markings and pale blue lines are visible.
The visuals return to close-up \textbf{studio} shots of winter-sport equipment and body mechanics.
A red boot, ski binding, and mechanical-looking lower-limb or support components are shown in \textbf{extreme} close-up, surrounded by blue \textbf{lighting} and snow-like particles.
More rectangular tracking overlays appear across these details.
Some shots are partially obscured by motion blur and tight \textbf{framing}, so the exact equipment configuration is not fully clear, but the emphasis is on the connection between athlete, boot, ski, and mechanical parts.
A dark, close-up portrait of a bearded man appears briefly, lit in blue and mostly in \textbf{shadow}.
The skier is then shown again in midair with digital rectangular overlays, followed by a close-up of a red ski boot clipped into a ski.
The commercial returns to the speed skater in the blue-lit \textbf{studio}, moving directly toward the camera in a low racing posture, with snow-like particles behind.
It then cuts back to competition \textbf{footage} : a speed skater in a dark suit on an indoor rink passes boards showing Toyota branding.
Another shot shows an athlete holding a U.S. flag overhead while on the ice.
Near the end, there is a very blurred close-up of red, white, and blue-toned motion, possibly an athlete or equipment moving quickly through snow or spray ; the image is too unclear to identify precisely.
The final title card appears on a dark background.
Centered text reads : “ Stadiums ” “ Skyscrapers ” “ Racetracks ” “ Make Superheroes ” The first three words appear \textbf{dimmer} or crossed/faded compared with “ Make Superheroes, ” which is brighter.
Below is “ autodesk.com. ” The last frame shows the Autodesk logo and wordmark, alongside two U.S. flag-themed emblems above the Olympic rings and Paralympic symbol, all on a black background.

% matched lemmas: air, dim, environment, extreme, footage, framing, illuminate, impression, lighting, repeated, shadow, studio, stylize, tone
\end{textsample}
