\begin{textsample}{POS Dim 3 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_93.txt}  \label{ex:f3_pos_009}
The commercial opens in a simple black-and-white cartoon bedroom.
A drawn man in pajamas sits slumped on a bed, one leg bent, looking tired and uncomfortable.
He holds a folding fan above his head and waves it at himself.
Wavy lines around the bed, lamp, and furniture suggest heavy heat.
The room has a bedside table with a lamp on the left and a bedpost on the right, giving the scene a stuffy nighttime feeling.
The cartoon image gives way to a live domestic room.
An adult woman presenter with light, curled 1950s-style hair stands beside a window-mounted Westinghouse room air conditioner.
She wears a light long-sleeved blouse with the sleeves pushed up and a dark high-waisted skirt.
Behind her are curtains and venetian blinds, with a glimpse of foliage outside the window.
A small framed picture hangs on the wall to the left.
The air conditioner sits below the window, its front facing outward into the room.
It is a wide, \textbf{rectangular} \textbf{unit} with three separate front grille \textbf{sections}.
Long, narrow paper ribbons are attached to the grilles, hanging down and fluttering to show the air movement.
As the woman stands to the left of the \textbf{unit}, large \textbf{handwritten-style} words appear across the front of the scene : “ COOLS IN SUMMER. ” The words fill much of the right side, \textbf{overlapping} the air conditioner and window.
Then the message changes to “ FRESHENS THE AIR, ” again in large white script.
A third message follows : “ WARMS IN WINTER. ” The woman remains beside the appliance, facing forward, then turns toward it as if preparing to \textbf{demonstrate} its \textbf{features}.
She places a hand on the top of the air conditioner and lifts or opens an upper panel.
The top \textbf{section} rises, revealing a control area along the upper front edge.
A closer view shows her hand \textbf{operating} the control panel : a row of small buttons or levers set into a long \textbf{horizontal} strip.
She points to and presses one of the controls, illustrating that the \textbf{unit} can be \textbf{adjusted} with a simple push.
The view returns to the full front of the air conditioner.
The upper panel is open, and the three front grille \textbf{sections} are clearly visible below, each with ribbons hanging and moving in the airflow.
The woman reaches across the open top and draws up a large filter assembly from inside the \textbf{unit}.
The filter rises vertically behind the front \textbf{casing}.
It has a distinctive honeycomb or circular-cell pattern, divided into \textbf{rectangular} \textbf{sections}, making it look like a grid of many round openings.
She holds it up so the entire filter surface is visible above the air conditioner, then begins guiding it back down into place.
After displaying the filter, she lowers it back inside the \textbf{unit} and closes the top panel.
Her hand smooths the lid shut across the top.
The front grilles continue to blow the hanging ribbons outward and downward.
The ribbons flutter steadily rather than whipping sharply, reinforcing the demonstration of controlled airflow.
The woman then \textbf{demonstrates} the adjustable grilles.
Her hand enters from the left and \textbf{grasps} the left grille \textbf{section}.
She turns or pivots it, changing the direction of the slats.
The ribbons attached to that \textbf{section} shift as the grille is angled.
She \textbf{adjusts} it again, showing that the air outlet can be directed.
The three grille \textbf{sections} remain separated by vertical decorative dividers, and the paper ribbons on all \textbf{sections} continue moving in the air stream.
The scene changes to a full-screen sign with ornamental flourishes.
The text reads, “ Certified Dealer ” at the top, “ for Westinghouse ” in the middle, and “ ROOM AIR CONDITIONERS ” in large block letters across the lower portion.
The sign is framed by decorative white scrollwork against a dark background.
The air conditioner appears again front and center, still installed below the window.
The ribbons continue to flutter from the three grille openings.
Large white handwritten text \textbf{fades} in over the \textbf{unit} : “ AS LITTLE AS \$3.25 A WEEK. ” The \textbf{price} is written prominently across the center, partially covering the grilles and ribbons.
For the final message, the air conditioner remains in view with the ribbons moving.
White script appears across the upper part of the image : “ You can be SURE … ” Then more words are added : “ if it ’s, ” followed by the large Westinghouse name across the lower center.
The final composition layers the slogan over the front of the appliance, ending with the Westinghouse brand name dominant over the still-running air conditioner.

% matched lemmas: adjust, casing, demonstrate, fade, feature, grasp, handwritten-style, horizontal, operate, overlap, price, rectangular, section, unit
\end{textsample}
