\begin{textsample}{POS Dim 3 – 1960 – Score 22.00 – 1960/tv\_com\_1960\_95.txt}  \label{ex:f3_pos_023}
The commercial opens on an old-fashioned \textbf{phonograph} : a dark \textbf{record} spins on a wooden \textbf{turntable} cabinet with a curved metal tone arm and a hand crank on the side.
A hand reaches in and lowers the needle toward the \textbf{record}.
The scene widens to reveal a woman dressed in turn-of-the-century style, wearing a high-necked pale dress and an enormous feathered hat.
She stands beside a large \textbf{gramophone} \textbf{horn} on a small wooden stand, with an ornate hanging lamp above.
She lifts her hand from the machine, then poses with one finger lightly under her chin, smiling faintly as if listening.
As she moves out of view, the large flared \textbf{gramophone} \textbf{horn} fills the center of the image.
The circular mouth of the \textbf{horn} visually gives way to the round reels of a modern tape recorder.
A clear plastic reel spins in the center of a sleek \textbf{rectangular} \textbf{unit}.
The view widens to show a built-in reel-to-reel tape deck with two large reels, a \textbf{central} control panel with round \textbf{knobs} and push-button controls, and a light-colored face set into a long, slim cabinet.
A blonde woman in a pale sleeveless dress stands to the left of the equipment, hands loosely together, looking relaxed and pleased.
Behind her, the long stereo \textbf{unit} stretches across the wall, with the tape deck in the middle and additional panels extending to either side.
The tape recorder is then shown more directly.
Two reels turn on the front of the \textbf{unit}, tape running across the lower center between them.
Above the machine, large \textbf{printed} text reads “ WOLLENSAK 5300. ” A hand reaches in and \textbf{operates} the \textbf{central} controls, pressing or turning one of the round controls near the top.
The product face is clean and \textbf{symmetrical}, with the left and right reels in clear circular covers, small buttons along the lower left, and a \textbf{central} control area between them.
The view moves along the larger stereo furniture system.
To the right of the tape recorder is a tuner \textbf{section} with a \textbf{horizontal} \textbf{radio} \textbf{dial} display and three round \textbf{knobs} beneath it.
Further right is an open shelf holding a row of slim \textbf{rectangular} tape boxes or tape \textbf{cartridges}, arranged upright like books.
The cabinet has a long walnut-wood appearance, with light-colored \textbf{speaker} or panel \textbf{sections} at the ends and darker wood \textbf{sections} in the middle, giving it the look of wall-mounted furniture rather than a standalone machine.
The blonde woman appears again in front of the long wall-mounted \textbf{unit}, gently swaying or stepping as her light dress moves around her legs.
She turns and poses near the stereo, presenting it as part of a modern room.
A potted plant with long, narrow leaves stands nearby.
She places one hand lightly near the walnut cabinet, drawing attention to its slim \textbf{horizontal} shape.
As she moves away, the furniture remains centered on the wall, framed by plants on both sides, including a feathery dried \textbf{arrangement} on the right.
The long \textbf{unit} appears closed in places, with smooth walnut doors and pale \textbf{speaker} panels, emphasizing its furniture-like design.
The front of the large Wollensak \textbf{unit} reappears with its tape reels visible again, now set into the cabinet, with a textured \textbf{speaker} panel to one side.
The reels continue to turn inside the \textbf{rectangular} wooden surround, the controls and tape path clearly visible.
The final \textbf{section} introduces a more compact reel-to-reel recorder on a simple table.
A brunette woman in a sleeveless red dress sits or kneels beside it, seen from the side and back at first.
She reaches both arms outward to swing open the detachable \textbf{speaker} panels on either side of the recorder.
The left \textbf{speaker} panel opens like a \textbf{hinged} door, revealing a fabric-covered \textbf{speaker} surface ; the right side is also opened outward, framing the \textbf{central} tape recorder.
The compact \textbf{unit} has two spinning reels, a small \textbf{central} control panel, and a \textbf{boxy} wooden \textbf{case}.
After opening the \textbf{speakers}, the woman settles beside the table, facing the recorder with a soft smile and a calm, listening posture.
The compact system sits on the tabletop with both \textbf{speakers} spread out to the sides.
Above it hang two simple cylindrical pendant lamps.
A cushion or low ottoman rests in the foreground, and the overall room is spare and modern, with the recorder presented as something that can sit neatly on a shelf-like table while filling the space visually with its opened \textbf{speaker} wings.

% matched lemmas: arrangement, boxy, cartridge, case, central, dial, gramophone, hinge, horizontal, horn, knob, operate, phonograph, printed, radio, record, rectangular, section, speaker, symmetrical, turntable, unit
\end{textsample}
