\begin{textsample}{POS Dim 3 – 2020 – Score 11.00 – 2020/tv\_com\_2020\_92.txt}  \label{ex:f3_pos_055}
The commercial begins in a modern interior space.
A man dressed in dark clothing sits in a large high-backed armchair, facing forward as if addressing the viewer.
The room appears softly lit, with light-colored curtains, a kitchen or bar area in the background, stools, a floor lamp, and a small side table holding a white cylindrical device.
The scene then shifts abruptly to a \textbf{futuristic} spacecraft or control-room \textbf{environment}.
A man in a blue and gray suit is seated among \textbf{illuminated} panels and screens.
The camera angle is close and slightly tilted, with reflections or transparent overlays making the cockpit appear \textbf{layered} and high-tech.
Next, the \textbf{imagery} \textbf{becomes} more abstract and speed-oriented.
A tunnel-like digital or sci-fi \textbf{environment} fills the frame, with bright linear streaks radiating toward a central light source.
On the left side, large white text reads : “ The \textbf{fastest} Internet. ” Very small fine print appears near the bottom, but it is not legible in the sampled frame.
The commercial returns briefly to the spacecraft interior.
A close-up shows a person in a \textbf{futuristic} suit facing forward, with another suited person visible in the background.
The image includes reflections and translucent interface-like overlays, reinforcing the \textbf{impression} of a high-tech vehicle or control cabin.
The final sequence moves into a fast-motion visual tunnel.
Bright blue-white light streaks rush past, suggesting rapid movement through space or a data-like corridor.
A \textbf{glowing} light source appears ahead.
A large white \textbf{stylized} “ X ” then appears centered over the moving streaks.
In the final frame, the brand name “ xfinity ” appears in white lowercase \textbf{letters} at the center, with the same luminous speed-line background and bright light on the right side.

% matched lemmas: become, environment, fast, futuristic, glowing, illuminate, imagery, impression, layer, letter, stylize
\end{textsample}
