\begin{textsample}{POS Dim 3 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_70.txt}  \label{ex:f3_pos_008}
A black-and-white scene opens on a wall calendar hanging against a \textbf{plain} dark background.
The visible page reads “ 1952, ” “ MAY, ” a very large “ 30, ” and “ FRIDAY, ” establishing the date.
Beneath the calendar, a tabletop \textbf{arrangement} comes into view : a compact portable \textbf{radio} with a glossy dark rounded \textbf{case} and a pale front grille.
The brand name “ RCA Victor ” is visible near the bottom of the \textbf{radio} ’s front.
To the \textbf{radio} ’s right sits a small \textbf{rectangular} RCA battery carton with the RCA \textbf{circle} logo on its face.
A pair of adult hands, seen from the wrists down in suit sleeves, begins handling the \textbf{radio}.
One hand wears a ring.
The hands steady the portable set and turn it so the \textbf{plain} dark back faces forward.
The person ’s fingers feel along the back panel and top edge, then open the rear of the \textbf{radio}.
Inside, the \textbf{radio} ’s components are exposed : a metal chassis across the top with small \textbf{printed} markings, rows of holes, wiring, and compact electrical parts arranged in the lower compartment.
The hands work carefully inside the open \textbf{radio}, moving \textbf{wires} and reaching into the battery compartment.
A \textbf{rectangular} RCA battery package is brought in from the right, its side showing a round RCA logo.
The battery is guided into the lower part of the \textbf{radio} ’s interior while the other hand holds loose leads and positions the connectors.
The battery is slid into place horizontally across the bottom \textbf{section}, with the RCA logo facing outward.
The fingers continue \textbf{adjusting} the \textbf{wires}, pressing them down and tucking them into the space around the battery so the parts sit neatly inside the open \textbf{case}.
After the battery is installed, the \textbf{radio} is turned again so its smooth back faces outward.
To the left of the \textbf{radio}, a retail display of RCA batteries appears on the tabletop.
It includes a box with two upright cylindrical batteries pictured or standing on top, each carrying the RCA logo.
A sign on the display reads “ RCA ” and “ Radio A Battery. ” The \textbf{radio} remains at the right edge while the battery display becomes the focus.
The view then presents a wider assortment of RCA battery packages arranged like a store display.
There are several \textbf{rectangular} cartons and cylindrical battery forms in different \textbf{sizes}, all marked with the RCA logo.
Large boxes are stacked at the back, smaller boxes and open display trays sit in front, and the text “ RADIO A B BATTERY ” is visible on a large carton.
Other packaging shows RCA logos and product labels for \textbf{radio} batteries, suggesting a variety of \textbf{sizes} for different portable \textbf{radio} \textbf{models}.
The final close-up isolates two products : a large \textbf{rectangular} box on the left and a cylindrical battery on the right.
Both carry bold RCA \textbf{circle} logos.
The box reads “ RADIO B BATTERY ” and includes the line “ RADIO-ENGINEERED FOR EXTRA LISTENING HOURS. ” Below that, smaller text reads “ No.
VS 016 • 67½ VOLTS. ” The cylindrical battery beside it is labeled “ RADIO A BATTERY, ” also with the RCA logo prominently centered.
The commercial ends visually on this clear product display, emphasizing the branded RCA \textbf{radio} batteries and their packaging.

% matched lemmas: adjust, arrangement, case, circle, model, plain, printed, radio, rectangular, section, size, wire
\end{textsample}
