\begin{textsample}{POS Dim 3 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_13.txt}  \label{ex:f3_pos_019}
The commercial begins with an overhead view of a street or parking area.
Several cars are visible from above : a dark car at the lower left and orange/red cars parked along the curb and right side.
A red/orange vehicle moves or is shown positioned between the others.
In the next frames, the view remains high and angled down toward the street ; the red/orange car \textbf{becomes} central, and a bright yellow rectangular placard or sign is visible on its roof or upper surface.
The image is washed in bright light in some frames, making details slightly unclear.
The sequence then shifts into a \textbf{stylized} or electronic-looking image of the same red/orange car from above.
The colors \textbf{become} distorted and high-contrast, with overlay \textbf{graphics} and time-like numbers along the bottom, resembling a recorded or game-screen interface.
After this, the commercial cuts rapidly into video-game \textbf{imagery}.
One frame shows a side-scrolling game-like scene with pale blue water or sky \textbf{tones} and bright yellow/orange shapes, possibly an explosion or projectile.
Another screen shows a vertical, underwater-looking \textbf{game} area with sea-colored backgrounds, rings or circular objects, and small dark shapes, with game-status numbers along the bottom.
The montage continues with more gameplay screens.
One dark blue-toned underwater or aquatic scene shows a large red “ 10 ” overlaid in the center, with additional interface numbers and icons around the edges.
Immediately after, a colorful green checkerboard-like \textbf{game} field appears with blue spherical objects, and a large red word “ \textbf{GAMES} ” fills the center of the screen.
Later frames show more distinct \textbf{game} \textbf{footage} : a blue water or sky background with a curved vine or rope and small cartoon-like characters, with score/life indicators in the corners.
Another frame shows a board-game-like grid with a large purple cartoon character overlaid in the center.
This is followed by a busy promotional collage with comic-style \textbf{imagery} and large red text reading “ \textbf{COOL} NEW, ” with additional smaller text beneath that is mostly too blurred to read clearly.
Near the end, the screen changes to a red background with a flat yellow/orange \textbf{silhouette} of a cartoon figure holding a horn or megaphone-like object.
Fine-print copyright/legal text appears along the bottom, including references to Looney Tunes and Warner Bros., though much of it is small and \textbf{difficult} to read.
The final frame keeps the red background and yellow/orange cartoon \textbf{silhouette}.
Large white ordering text appears in the center : “ To order call InterMedia 247-2183 Only \$11.95/month. ” Small white fine print fills the lower portion, mentioning restrictions, fees, service requirements, and copyright/trademark notices, including Sega-related references, though the full small text is not completely legible.

% matched lemmas: become, cool, difficult, footage, game, graphics, imagery, silhouette, stylize, tone
\end{textsample}
