\begin{textsample}{POS Dim 3 – 1950 – Score 6.00 – 1950/tv\_com\_1950\_83.txt}  \label{ex:f3_pos_083}
The commercial begins with a black screen.
It then cuts to a sepia-toned \textbf{studio} scene.
A blonde woman in a glamorous strapless dark dress, with a light shawl draped around her arms, stands near a vertical piece of \textbf{stage} equipment or \textbf{lighting} rig.
The background is hazy and softly lit, giving the scene a theatrical or dreamlike look.
She faces forward and appears posed for the camera.
The next sampled shot shows the same woman more prominently.
A large, smiling close-up of her face is superimposed or \textbf{layered} over a smaller full-body view behind her, creating a double-exposure \textbf{effect}.
She is still in the same formal outfit, with curled hair and jewelry visible.
The commercial then shifts to a montage of automobiles and travel scenery.
A light-colored mid-century car drives along a rural road bordered by open fields and trees.
This is followed by a closer side-front view of a similar light-colored car with chrome detailing and whitewall tires driving past a line of trees.
The next shots emphasize roads and landscapes : an empty paved road stretches downhill through a wide countryside ; a high view looks over a body of water and shoreline with masts or vertical poles visible at the right ; another view shows a road or bridge crossing through a valley ; and a road runs through a dramatic rocky mountain or canyon landscape.
A later shot shows a dark convertible-style mid-century car approaching on an open road, with flat countryside or fields around it.
Another vehicle may be visible behind it, though details are limited.
The commercial then returns to the \textbf{studio} performer.
In a close-up, the blonde woman faces the camera, smiling broadly, still wearing the dark strapless dress, shawl, and necklace against the soft, \textbf{glowing} background.
In the final sampled frame, she raises her hand to her mouth in a kiss-like gesture, looking upward and toward the camera.
No visible text appears in the sampled frames.

% matched lemmas: effect, glowing, layer, lighting, stage, studio
\end{textsample}
