\begin{textsample}{POS Dim 3 – 2020 – Score 9.00 – 2020/tv\_com\_2020\_51.txt}  \label{ex:f3_pos_057}
The commercial begins with a close-up of a white tube of **Gold Bond Ultimate Crepe Corrector Age Defense**.
The packaging uses purple and \textbf{gold} \textbf{accents}, with “ NEW ” visible near the top.
It then cuts to a warm outdoor scene at sunset : a blond adult wearing a large backpack looks back while moving through a dry, open landscape.
The light is soft and golden.
Next, an adult with tattoos lies on a bed with two young children.
They are smiling and laughing together in a bright, domestic setting with white bedding.
The sequence shifts to a fitness setting.
A woman with a high ponytail, wearing a black athletic top, holds a dumbbell and appears to be exercising or strength training.
The background suggests an indoor gym or \textbf{studio}.
A close-up follows of two adults sitting closely together.
One person looks ahead while the other leans in smiling ; the scene is softly lit and intimate.
The ad then shows an \textbf{extreme} close-up of a hand touching or stroking light-toned skin near the neck or upper shoulder area.
Blonde hair is visible at the edge of the frame, emphasizing skin texture and touch.
Another lifestyle image appears : an adult with very short light hair and a young child lie on green grass, smiling and embracing.
The camera looks down from above.
A close-up of skin and a hand appears with large pale-yellow text overlaid reading **“JUST.”** The background is sunlit and warm.
The product returns in a centered shot : a tube of **Gold Bond Ultimate Crepe Corrector Age Defense** stands in the foreground, while a blurred figure or body part appears in the background.
The commercial then shows a product lineup on a dark teal surface : multiple Gold Bond products are arranged together, including tubes and a pump bottle.
The packaging is primarily white with purple and \textbf{gold} branding.
The \textbf{lighting} \textbf{dims}, and the product lineup \textbf{becomes} mostly \textbf{silhouetted} against the teal background.
Large \textbf{gold} \textbf{letters} begin to slide or appear over the products.
The final frame shows the products darkened behind a bold, all-caps \textbf{gold} message : **“CHAMPION YOUR SKIN.”** The word “ SKIN ” appears slightly motion-blurred or still resolving in the sampled frame.

% matched lemmas: accent, become, dim, extreme, gold, letter, lighting, silhouette, studio
\end{textsample}
