\begin{textsample}{POS Dim 3 – 1990 – Score 13.00 – 1990/tv\_com\_1990\_2.txt}  \label{ex:f3_pos_010}
The commercial begins on a black screen with the PlayStation logo centered : the multicolored PlayStation symbol above the word “ PlayStation. ” It then cuts to video \textbf{game} \textbf{footage}.
A group of \textbf{futuristic} racing craft or hover bikes are lined up on a desert-like track.
A large overhead digital sign reads “ SET, ” and the camera is positioned behind one racer with a large number “ 2 ” on the back of the vehicle.
The \textbf{game} \textbf{environment} has orange-brown canyon walls and a bright sky.
The next gameplay shot shows racers moving along a narrow bridge made of wooden planks suspended over a \textbf{deep} canyon or ravine, with grassy terrain on either side.
The race HUD timer is visible in the upper-left corner.
The \textbf{game} returns to the desert starting area, now with the overhead sign reading “ GO! ” in large yellow \textbf{letters}.
A single racer with the number “ 2 ” accelerates forward beneath the sign.
Subsequent gameplay shots show multiple hover-bike racers speeding through different \textbf{environments} : a sandy canyon, a close-up of a racer leaning into a turn, a water course with floating markers, and a snowy mountain or cliffside track.
An ESRB-style rating icon appears in the lower-left corner during several gameplay shots, though the small text is not fully legible in the frames.
After more \textbf{footage} of the “ GO! ” start screen, the commercial cuts to live action.
An elderly white woman with white hair is seated indoors in a \textbf{dim}, warm room.
She wears a light cardigan over a pink blouse and holds a PlayStation controller.
She appears focused, looking toward the television while manipulating the controller.
In a wider shot, the TV screen in front of her shows a man ’s face from the \textbf{game} or a game-related screen.
The room includes furniture and decorative objects in the background, but details are soft and partially \textbf{shadowed}.
The commercial then \textbf{switches} to a product-title graphic.
A dark \textbf{oval} logo with the text “ Jet Moto 2 ” appears centered.
The background \textbf{alternates} rapidly between a pale, cloudy or electric-looking white-gray field with lightning-like streaks and a nearly black background.
The same “ Jet Moto 2 ” logo remains centered through these \textbf{flashes}.
The ad then briefly returns to gameplay at the desert start area.
The overhead sign still reads “ GO! ” A \textbf{human} \textbf{game} character or rider stands beside the number “ 2 ” craft, and a helmet or small object lies on the track nearby.
Finally, it cuts back to the elderly woman in the chair.
She still holds the controller and looks forward with a serious, concentrated expression.
The last frame is very dark and shows only a few small turquoise glowing marks or shapes ; the surrounding content is unclear.

% matched lemmas: alternate, deep, dim, environment, flash, footage, futuristic, game, human, letter, oval, shadow, switch
\end{textsample}
