\begin{textsample}{POS Dim 3 – 1990 – Score 5.00 – 1990/tv\_com\_1990\_35.txt}  \label{ex:f3_pos_059}
A dim, spacious bedroom comes into view, lit mostly by daylight from tall bay windows.
Outside the windows are neighbouring apartment buildings and trees.
The room has an old fireplace and mirror on the left, a cushioned armchair and small tables near the windows, a low black object and loose papers on the carpet, and a wooden bed on the right piled with white bedding.
A shirtless adult man lies in the bed under the sheets, apparently waking in a disordered morning setting.
Beside the bed, a glass-topped tray table holds a black round alarm \textbf{clock}, a white cup, and small grooming or bedside items.
The man ’s arm reaches from the bed toward the table, fumbling among the objects near the \textbf{clock}.
He then pushes himself upright, bare-chested, with tousled dark hair and a sleepy, slightly dazed expression.
Still wrapped in white bedding or loose pale sleepwear, he leans forward and rises from the bed.
Near the floor, his bare foot steps down among scattered papers and dark footwear or a bag, emphasizing the messy, rushed morning feel.
The scene moves into a bathroom or dressing area with shelves of bottles and grooming items in the background.
The same shirtless man faces forward as if looking into a mirror.
He has dark, thick, wavy hair, light eyes, and visible stubble along his jaw, chin, and upper lip.
He studies his face, then rubs his cheek and jaw with one hand, feeling the roughness.
In his other hand he holds a compact Braun electric shaver : a grey and black \textbf{rectangular} device with a perforated grip, a broad foil shaving head, and adjustable trimming parts.
He brings the shaver up to his cheek and jawline.
With one hand he stretches the skin below his chin while the other guides the shaver along the side of his face.
Close views show the device pressed neatly against the cheek, its head aligned with the curve near the sideburn and jaw.
The shaver is shown in different working positions : a narrow \textbf{projecting} trimmer-like \textbf{section} is used along the cheek and sideburn area, then the broader foil head is held under the chin as the man tilts his head back to expose the underside of his jaw.
His mouth tightens slightly as he shaves around the chin.
He then works around the upper lip.
The shaver is held horizontally beneath his nose while he trims along the moustache area.
His lips purse and shift to stretch the skin, and he carefully moves the device from one side of the upper lip to the other.
A close view of the shaver in his hand shows his thumb sliding a small switch on the top \textbf{section}, \textbf{adjusting} the head.
The Braun name is visible on the perforated body of the device.
After the adjustment, he tilts his chin up again and runs the shaver beneath the jaw and along the neck.
The man continues \textbf{demonstrating} the adjustable head near the lower face and then near the ear.
He raises the shaver beside his temple and sideburn, trimming close to the ear while looking forward with a more alert, controlled expression.
The device remains compact in his hand, with its dark sides and silver-grey perforated front clearly visible.
After shaving, he faces forward, clean-shaven and more composed.
He rubs his cheek and chin with his hand, checking the smooth result.
His expression softens into a small, satisfied smile, replacing the earlier sleepy look.
The commercial ends with a polished product display on a glass shelf.
Two Braun shavers rest among reflective glass and a pale towel-like fabric.
One shaver lies in the foreground with its grey perforated body and dark head facing diagonally across the shelf ; another stands partly behind it.
White on-screen text appears at the bottom : “ BRAUN ” with the line “ Designed to perform better. ”

% matched lemmas: adjust, clock, demonstrate, project, rectangular, section
\end{textsample}
