\begin{textsample}{POS Dim 3 – 2010 – Score 3.00 – 2010/tv\_com\_2010\_19.txt}  \label{ex:f3_pos_087}
A bottle of Vitaminwater Triple X stands alone on a glossy white platform against a soft gray background.
The drink inside is a vivid pink-red, with a clear cap and a black-and-white label reading “ vitaminwater ” and “ xxx. ” Tiny beads of condensation dot the bottle, making it look cold.
Around it, miniature, toy-like health-gag objects begin appearing : a small upside-down figure in red and black drops from above, and a gray, capsule-like chamber sits on the tabletop to the right of the bottle, suggesting an exaggerated wellness device.
The bottle remains steady on the left as the scene shifts into another odd visual joke.
A green block of holey cheese, with little \textbf{human} limbs sticking out of it, tumbles across the tabletop near the bottle and rolls away.
From behind the bottle, a small \textbf{human} figure steps out.
He is dressed casually in a black jacket or hoodie with red accents, blue jeans, and white sneakers.
Instead of a normal head, he has a large stylized basketball-hoop-and-crown headpiece : a dark \textbf{rectangular} “ face ” like a backboard, a yellow net hanging across the front, and an ornate black crown shape around the top and sides.
He walks forward confidently beside the much larger Vitaminwater bottle.
A dark basketball suddenly passes very close across the front of the scene, briefly filling the view and partially hiding the bottle and the hoop-headed figure.
When it clears, the figure stands near the bottle while small product-related graphics and miniature props appear around the label, including a round magnifying-glass-like display with tiny check marks and label details, as if calling attention to the drink ’s contents.
The Vitaminwater bottle remains the largest object on the left, bright pink against the clean white-and-gray setting.
A black hanging banner with a gold border descends on the right.
At first only “ LONG ” is visible, then the full message appears in large pale letters : “ LONG LIVE THE KING. ” The hoop-headed figure stands centered beneath it, holding a basketball.
Two tiny silver-suited figures enter from either side, dressed like little futuristic technicians or astronauts, with helmets, black boots, red chest bands, and hose-like cords trailing behind them.
They point nozzle-like devices toward the \textbf{central} figure.
A pale pink mist begins to billow around the hoop-headed figure, growing thick enough to partly obscure him and soften the background.
The silver-suited attendants keep aiming their devices as the vapor surrounds him.
Then he breaks forward out of the cloud, carrying the basketball and running toward the viewer and off to the right, passing large in the foreground.
The attendants remain small on either side, and the “ LONG LIVE THE KING ” banner hangs behind the pink haze.
As the figure exits, the mist \textbf{fades}, leaving the Vitaminwater Triple X bottle still standing on the left and the “ LONG LIVE THE KING ” banner on the right.
Finally, large on-screen text appears beside the bottle : “ kingjameswater, ” with “ king ” in bright pink and the rest in darker lettering.
A faint line of small legal text runs along the bottom, too small to read clearly.

% matched lemmas: central, fade, human, rectangular
\end{textsample}
