\begin{textsample}{POS Dim 3 – 2010 – Score 16.00 – 2010/tv\_com\_2010\_68.txt}  \label{ex:f3_pos_071}
The commercial begins in a bright, minimalist ballet \textbf{studio}.
A young adult woman with dark hair tied up in a bun stands near the right side of the room, wearing a dark sports bra/crop top, dark briefs, and ballet pointe shoes.
The \textbf{studio} has white walls, large windows, a radiator, and ballet barres along the wall.
She is framed at first from a distance, standing poised with one leg crossed and her hands near her abdomen.
The camera then moves into close-up views of her lower legs and feet.
She rises and balances on pointe, with the pale pointe shoes pressing into the floor.
Several shots emphasize the strain and precision of the feet, ankles, calves, and legs.
One \textbf{extreme} close-up shows the tips of the pointe shoes contacting the floor.
Another shot from behind shows her upper back and shoulders as she raises her arms overhead, revealing a small Under Armour logo on the back of her top.
The sequence continues in the same bright \textbf{studio}.
She walks or glides forward on pointe, with a full-body shot showing her centered in the room.
A close-up of her face shows a focused, calm expression as she looks slightly downward or ahead.
The \textbf{lighting} is soft and natural, coming from the windows.
The setting then shifts into a much darker performance space.
The transition includes a very dark frame where details are unclear.
The dancer appears under warm, golden \textbf{stage} \textbf{lighting}.
Her face is shown in close-up with \textbf{stronger} contrast and \textbf{shadows}, and she appears serious and composed.
Bright vertical \textbf{stage} lights and lens \textbf{flares} appear behind her.
The next part shows her dancing on a large \textbf{stage} or performance platform.
The \textbf{stage} has tall rectangular panels, vertical rows of warm yellow lights, and \textbf{cooler} blue-white light from above or the side.
In wide shots, she appears small against the large \textbf{architectural} \textbf{stage} set.
She performs ballet movements : extending one leg high to the side while balancing, turning with arms outstretched, lifting her arms overhead, and moving across the \textbf{glossy} dark floor.
Close-ups \textbf{alternate} with wide shots, emphasizing both the physical detail of her body and the scale of the \textbf{stage}.
Several shots focus on \textbf{dynamic} movement : her arms sweep through the \textbf{air}, her torso twists, and her feet \textbf{land} or push off from pointe.
One shot shows her in a full split leap suspended in the \textbf{air}, arms raised, legs extended horizontally in opposite directions.
The \textbf{lighting} \textbf{alternates} between \textbf{cool} blue-white and warm \textbf{gold}, with frequent lens \textbf{flares} and backlighting that partially \textbf{silhouette} her body.
Near the end, she is shown from behind and in profile under golden light, then in a close-up facing forward.
In this final close-up, she looks directly ahead with a slight, controlled smile or composed expression.
Her face is evenly lit against a \textbf{cool}, neutral background.
The commercial concludes with a black background and a white Under Armour logo.
The words “ UNDER ARMOUR ” appear beneath the logo.
In the final frame, additional white text appears : “ I WILL WHAT I WANT, ” with the website “ iwillwhatiwant.com ” shown smaller at the bottom.

% matched lemmas: air, alternate, architectural, cool, dynamic, extreme, flare, glossy, gold, land, lighting, shadow, silhouette, stage, strong, studio
\end{textsample}
