\begin{textsample}{POS Dim 3 – 1950 – Score 28.00 – 1950/tv\_com\_1950\_68.txt}  \label{ex:f3_pos_002}
The commercial is in black and white, with a \textbf{plain} studio backdrop and strong shadows.
It begins with a dark-haired young woman standing high on a tall stepladder or platform \textbf{ladder}.
She wears a light blouse or dress with a striped skirt and holds a \textbf{boxy} portable \textbf{radio} across her arms at chest height.
From farther back, the \textbf{ladder} is shown as very tall and narrow, with the woman perched near the top against an otherwise empty background.
She raises her arms and releases the \textbf{radios}.
Two portable sets tumble down past the \textbf{ladder}, one dark and one lighter, while loose pieces and fragments fly around them as they fall.
The scene changes to a tabletop covered with the aftermath : at the left is a broken-open \textbf{radio} chassis, exposing a round \textbf{speaker}, tubes, wiring, and loose parts.
At the right sits a more intact \textbf{rectangular} portable \textbf{radio} with a \textbf{ribbed} front grille and a large round side \textbf{knob}.
A man ’s hand in a suit sleeve reaches into the broken-looking \textbf{mechanism}, handles small parts and \textbf{wires}, then moves to the intact set.
He \textbf{grasps} the intact \textbf{radio} by its top handle and lifts it from the tabletop, bringing it forward as the broken parts remain scattered behind.
A light-skinned, middle-aged male presenter in a dark suit, white shirt, patterned tie, and \textbf{pocket} square holds the RCA Victor portable \textbf{radio} in front of his chest.
The \textbf{radio} is compact and \textbf{rectangular}, with rounded corners, a large \textbf{horizontal} grille across the front, a small circular RCA emblem above the grille, a flat handle on top, and round controls \textbf{protruding} at the sides.
He faces forward and presents it squarely, one hand on the handle and the other supporting it from below.
He then looks down at the set and turns it slightly, indicating the side controls or \textbf{case} area with his hand as he continues to \textbf{demonstrate} it.
The product is then displayed alone on a low surface.
The intact \textbf{radio} stands upright in the center, while broken debris from the earlier smashed set lies to its left.
The \textbf{radio} ’s front grille and top handle are clearly visible, and the \textbf{case} looks unmarked.
Handwritten-style text appears above it reading “ non breakable, ” while large bold lettering below reads “ IMPACT \textbf{case}, ” with “ \textbf{case} ” in a script style.
The display returns to the \textbf{radio} with the broken pieces beside it, then bold white block letters appear along the bottom : “ 5-YEAR GUARANTEE. ” The presenter reappears, now holding the \textbf{radio} again and looking down at it.
He turns the set slightly and touches the side, then lowers it toward a tabletop.
In a close view, only his hands and the \textbf{radio} are visible.
He grips the \textbf{radio} at both sides, lifts it a short distance, and repeatedly brings it down against the flat surface, as if \textbf{demonstrating} that the \textbf{case} withstands impact.
The front grille stays aligned, the corners remain intact, and no visible pieces break off.
After one demonstration, bold white capital letters appear above the \textbf{radio} : “ NO CHIPPING. ” The hands repeat the handling and impact demonstration ; then the words “ NO CRACKING ” appear above the set.
After another repetition, the words change to “ NO BREAKING. ” Each time, the same compact \textbf{rectangular} \textbf{radio} remains whole, with its grille, handle, emblem, and side \textbf{knobs} still in place.
The display shifts to a dark, softly lit product showcase.
Several RCA Victor portable \textbf{radios} pass across a \textbf{slanted} platform or rotating display, each shown at a dramatic angle.
One \textbf{model} has a darker front panel and a prominent round side \textbf{knob}.
Another lighter \textbf{model} shows a circular \textbf{dial} centered on its face.
The familiar \textbf{rectangular} grille-front \textbf{model} appears again, followed by additional \textbf{horizontal} portable sets with long front grilles and top-mounted controls.
The \textbf{radios} \textbf{overlap} and slide past one another visually, emphasizing a range of portable designs.
At the end, a large “ RCA \textbf{VICTOR} ” wordmark fills the background.
In front of it, the RCA circular logo appears near the left, and the classic RCA Victor dog sits beside a \textbf{gramophone}, facing the \textbf{horn} as if listening.
Along the bottom, the slogan “ HIS \textbf{MASTER} ’S \textbf{VOICE} ” appears in \textbf{quotation} marks.

% matched lemmas: boxy, case, demonstrate, dial, gramophone, grasp, horizontal, horn, knob, ladder, master, mechanism, model, overlap, plain, pocket, protrude, quotation, radio, rectangular, rib, slant, speaker, victor, voice, wire
\end{textsample}
