\begin{textsample}{POS Dim 3 – 2010 – Score 3.00 – 2010/tv\_com\_2010\_71.txt}  \label{ex:f3_pos_088}
The commercial opens on a clean white title card with the Farmers Insurance logo centered : a blue, red, and white emblem above the words “ FARMERS INSURANCE. ” Smaller text underneath lists “ home, ” “ auto, ” “ life, ” and “ business, ” and “ farmers.com ” appears near the bottom.
The scene then changes to a \textbf{plain} white studio background.
A middle-aged, light-skinned man with short gray hair stands facing forward in a casual taupe button-up shirt.
His face is covered in white shaving cream around his mouth, cheeks, and chin, and he is holding a black razor against one cheek as if shaving.
A small black “ trivago ” logo sits at the lower right of the screen.
While still shaving, he hunches slightly and appears to be doing something else at his waist with his other hand.
A long brown object, likely a shoehorn or similar dressing aid, sticks out near his hip, adding to the sense that he is trying to get ready while shaving.
He looks downward and fumbles around his belt or trouser area, still holding the razor in one hand and the brown object in the other.
His posture is awkward and rushed, with his shoulders bent forward and his attention split between his face and his clothes.
He then straightens up, still with shaving cream on his face, and faces the viewer as if explaining something.
From the right side of the screen, a white cup on a saucer appears at about chest height.
The man gestures with one hand, then takes or presents the cup and saucer in front of him, still unshaven.
He dips downward out of sight, leaving the white background briefly empty except for the small “ trivago ” logo in the lower right.
He rises back into view transformed into a more polished version of himself : now clean-shaven, wearing a dark suit jacket, white dress shirt, dark tie, and a white \textbf{pocket} square.
He faces forward against the same minimalist white background, looking composed and professional.
A larger multicolored “ trivago ” logo appears behind him toward the upper right.
Beside and behind him, a hotel comparison graphic slides into view.
It shows a photo of a tidy hotel room with a bed, bedside lamp, curtains, and a desk area.
Below the photo is the hotel name “ Finsbury Red Hotel, ” a row of yellow star symbols, and a bright green rating box marked “ 89. ” The man shifts slightly to the left so the hotel search panel is clearly visible over his right shoulder.
A vertical list of booking-site \textbf{prices} appears beneath the hotel image, including visible \textbf{prices} such as “ \$154, ” “ \$169, ” “ \$182, ” and “ \$260. ” He turns toward the graphic and gestures with one hand, indicating the hotel photo, the rating, and the \textbf{price} list.
At one point he holds his fingers in a small “ OK ” or pinching gesture near the hotel image, as if highlighting a precise comparison or choice.
The layout looks like an online hotel-search result, with the Trivago logo at the top, the room photo, rating, hotel name, and multiple \textbf{prices} stacked below.
As he finishes pointing, the comparison panel \textbf{fades} into the background until only the presenter remains centered against the \textbf{plain} white studio backdrop.
He faces forward calmly in his suit, maintaining a slight, confident smile as the visual focus returns entirely to him.

% matched lemmas: fade, plain, pocket, price
\end{textsample}
