\begin{textsample}{POS Dim 3 – 1980 – Score 9.00 – 1980/tv\_com\_1980\_98.txt}  \label{ex:f3_pos_034}
The commercial opens on a nighttime street scene with a brightly lit storefront.
The shop façade has large windows, neon-like trim, and \textbf{illuminated} signs in the windows that appear to show the Kit Kat logo.
The pavement in front looks wet and \textbf{reflective}.
A person stands outside near the entrance, facing the door.
The image then dissolves into a close-up of a young blond man.
His face is overlaid with the \textbf{glowing} storefront lights and window signage, creating a \textbf{layered}, dreamy visual \textbf{effect}.
The colors are saturated, with reds, greens, and yellows bleeding into each other.
Next, the sequence cuts/dissolves to a blond woman in a pale or white collared top, seen in front of the same \textbf{illuminated} shopfront.
The shop windows and Kit Kat signs remain visible behind or superimposed over her.
She looks forward with a calm, slightly expectant expression.
A man then appears framed in the open doorway of the shop.
He is wearing a jacket over a light shirt, and the doorway is outlined by bright lights.
The shot is frontal, with him standing between the open doors.
The blond woman appears again in close-up.
She smiles and looks slightly upward or to the side, with warm, colorful reflections and lights surrounding her face.
The \textbf{imagery} then shifts to close-ups of the product.
A red Kit Kat wrapper is shown, partly blurred and superimposed over other \textbf{imagery}.
The white “ Kit Kat ” logo is visible on the red wrapper, though the image is soft and \textbf{layered}.
The blond man returns in profile or three-quarter view, with a large translucent Kit Kat wrapper overlaid across the frame.
The montage continues with a clearer view of a Kit Kat bar/package near a person ’s face and hand.
A hand appears to hold or present a piece of chocolate or a small portion of the bar, but the exact action is somewhat obscured by the double exposure and soft focus.
Another product shot follows, again with the red Kit Kat wrapper prominent in the foreground and faces/hands faintly visible behind it.
The editing uses dissolves and overlapping images rather than a straightforward continuous action.
A darker, backlit shot shows a woman with long hair in profile or near-profile.
She appears to bring something small toward her mouth, possibly a piece of chocolate, but the details are partially obscured by \textbf{shadow} and \textbf{strong} colored \textbf{lighting}.
The \textbf{illuminated} shop sign remains in the background.
Near the end, there is another soft, \textbf{layered} image of figures and the storefront, with the product \textbf{imagery} fading through the scene.
The final frame is a clean product end card on a light background.
A red Kit Kat package is centered near the top.
Beneath it, black text reads : “ The taste you can fall in love with. ” Small fine print and a small logo appear at the lower left, but they are too small to read clearly in the sampled frame.

% matched lemmas: effect, glowing, illuminate, imagery, layer, lighting, reflective, shadow, strong
\end{textsample}
