\begin{textsample}{POS Dim 3 – 1960 – Score 22.00 – 1960/tv\_com\_1960\_97.txt}  \label{ex:f3_pos_024}
A studio scene opens on a male-presenting adult performer with a white-painted, mask-like face and a calm, serious expression.
He stands against a \textbf{plain} blue-gray background, dressed like a stylized juggler or clown : a tall yellow cone hat, a pale gray long coat, a large yellow bow tie, yellow trousers, and oversized patch \textbf{pockets} decorated in gray and yellow patterns.
One \textbf{pocket} has a grid design, another has diagonal stripes, and another has large yellow dots.
He juggles several small \textbf{rectangular} transistor \textbf{radios}, tossing them in smooth arcs above his hands and even above his hat.
The \textbf{radios} are different colors, including white, yellow, brown, and dark-toned \textbf{models}, with circular \textbf{dials} and small \textbf{speaker} faces visible as they turn.
The image moves in tight to one of his coat \textbf{pockets}, the gray-and-yellow grid \textbf{pocket}.
A small white \textbf{radio} drops neatly into it, leaving only the top edge and part of a black circular \textbf{dial} peeking out.
The \textbf{pocket} bulges slightly around the \textbf{radio}.
After a pause, the view shifts across the front of his coat to another patch \textbf{pocket}, this one gray with bold yellow diagonal stripes.
Another small \textbf{radio} slides into this \textbf{pocket}, again sticking out just enough to show its top and \textbf{dial} area.
Attention then goes to the dotted \textbf{pocket} on the performer ’s chest, gray with large yellow \textbf{circles}.
A white RCA Victor portable \textbf{radio} rises into view from inside this \textbf{pocket}, its round tuning \textbf{dial} prominent near the top.
Large white on-screen lettering reading “ RCA \textbf{VICTOR} ” appears across the lower part of the image.
A hand reaches in, grips the \textbf{radio} by the \textbf{dial} area, and pulls it out.
As it emerges, the \textbf{radio} ’s front is shown clearly : a \textbf{rectangular} white \textbf{case}, a large \textbf{ribbed} \textbf{speaker} grille across the lower half, a circular tuning \textbf{dial} near the top, and small controls on the side.
The hand sets the \textbf{radio} upright on a smooth white rounded surface, propping it with a small fold-out stand so it leans back slightly.
The hand rests on the circular \textbf{dial} as if \textbf{demonstrating} or \textbf{adjusting} it.
The demonstration changes to batteries.
Two hands appear against the same \textbf{plain} studio background, tossing small red-and-black cylindrical batteries.
A soft yellow cone hat, matching the performer ’s hat, is held open like a basket.
Batteries drop into the hat one after another.
After several have gone in, a hand reaches down inside the hat and rummages around.
It pulls out a small handful of three red RCA-branded batteries, their round RCA logos visible on the labels, and holds them together in the palm.
The RCA Victor \textbf{radio} is then shown held horizontally in both hands, with its front facing outward.
The white \textbf{case} has the circular tuning \textbf{dial} on the right side, a round \textbf{speaker} grille in the middle, a small red button or indicator to the left, and an open battery compartment on the side.
The \textbf{demonstrator} brings the red RCA batteries to the open compartment and loads them in.
As this happens, large bold white text appears over the \textbf{radio} reading “ 4 times longer, ” with a pale blue-green shadow that makes the words stand out.
The hands continue placing or \textbf{adjusting} the batteries at the side of the \textbf{radio} while the “ 4 times longer ” text remains over the product.
The performer reappears, again juggling the portable \textbf{radios} in front of the \textbf{plain} blue-gray background.
His face remains composed and focused as the \textbf{radios} rotate through the air over his hands and hat.
The scene then shifts to a low view of a flat studio surface.
Several non-RCA \textbf{radios} or \textbf{radio} parts hit the floor and break apart.
Yellow and white \textbf{casing} pieces, \textbf{wires}, and internal components scatter.
A dark \textbf{radio} falls and bursts open, exposing its inside parts.
In contrast, a white RCA Victor \textbf{radio} drops onto the same surface.
It bounces and flips, but remains in one piece.
It rotates through the air, lands on a corner, and settles intact, leaning diagonally with its \textbf{speaker} grille and circular \textbf{dial} still visible.
Large white lettering appears around it : “ non-breakable ” at the top and “ IMPAC \textbf{case} ” at the bottom, presenting the \textbf{case} as durable.
The juggler returns once more, still in his pale gray coat with yellow accents, tossing the small \textbf{radios} in a steady pattern.
He catches and releases them with open hands, the \textbf{radios} flashing their \textbf{dials} and colored \textbf{cases} as they turn.
The product lineup appears on a blue-gray surface.
First, one pale mint or light green RCA Victor portable \textbf{radio} rests at the upper left, lying at a slight angle with its circular tuning \textbf{dial} on top and \textbf{speaker} grille visible.
A copper-brown version slides or appears at the lower right, similarly shaped with a round \textbf{dial} and front grille.
A white version then joins at the lower left.
The three \textbf{radios} form a loose triangular \textbf{arrangement}, showing the \textbf{model} in three different colors.
The commercial ends on the RCA Victor brand mark against a blue background.
Large white text reads “ RCA \textbf{VICTOR}. ” Beneath it are the round red RCA logo and the familiar “ His Master ’s Voice ” image : a white dog sitting and listening to a \textbf{horn} \textbf{gramophone}.
The words “ HIS \textbf{MASTER} ’S \textbf{VOICE} ” appear in \textbf{quotation} marks below the image.

% matched lemmas: adjust, arrangement, case, circle, demonstrate, demonstrator, dial, gramophone, horn, master, model, plain, pocket, quotation, radio, rectangular, rib, speaker, victor, voice, wire
\end{textsample}
