\begin{textsample}{POS Dim 3 – 1950 – Score 35.00 – 1950/tv\_com\_1950\_73.txt}  \label{ex:f3_pos_001}
The commercial begins in black and white with a large RCA emblem centered against a dark, starry-looking background.
The letters “ RCA ” sit inside a \textbf{circle}, with a small lightning-bolt-like mark beneath them.
A cartoon alarm \textbf{clock} appears next.
It is an old-fashioned round \textbf{clock} with two bells on top, little legs, and animated arms.
Its face has large numerals and exaggerated hands, and it behaves like a noisy, bothersome character.
It rocks and dances around, its bell cap bouncing, its arms flailing, and its \textbf{clock} face changing into a grimacing, toothy expression.
A pale \textbf{human} hand reaches in from the right and presses down on the top of the \textbf{clock}, squashing it low and flattening its animated face into a strained frown.
When the hand lifts away, the \textbf{clock} pops back upright.
The cartoon image then gives way to a darker bedroom setting, with the alarm \textbf{clock} briefly still visible in a spotlight-like \textbf{circle} before the scene changes fully to a real room.
In the bedroom, an adult woman lies in bed beside a nightstand.
She has dark, wavy hair and is under light-colored sheets, with a padded, tufted headboard behind her.
On the nightstand sits the RCA Victor \textbf{clock} \textbf{radio} : a \textbf{rectangular}, light-colored \textbf{unit} with a round \textbf{clock} \textbf{dial} on the left, a \textbf{speaker} grille in the middle, and a circular tuning \textbf{dial} on the right.
A table lamp with a broad shade stands behind it.
The woman is shown asleep, turned toward the \textbf{clock} \textbf{radio}.
She begins to stir gently, opens her eyes, and smiles faintly.
She raises herself slightly, then relaxes back into the pillow, appearing comfortable rather than startled.
A large transparent \textbf{clock} face is \textbf{superimposed} over the bedroom scene, its numerals and hands filling much of the screen while the woman remains visible beneath it.
As the \textbf{clock} graphic remains over the bed, the woman continues lying down.
Later, she wakes more abruptly, lifting her head and opening her mouth as if responding to a later alarm signal.
The visual emphasis is on the passage of time and the \textbf{clock} \textbf{radio} ’s timed waking \textbf{function}.
The product is then shown in close-up on the nightstand.
A hand \textbf{adjusts} the circular \textbf{clock} \textbf{dial} on the front left side.
Around the \textbf{dial} are large printed numbers, and small \textbf{protruding} tabs or indicators sit near the \textbf{dial} ’s edge.
The hand turns or sets the \textbf{clock} \textbf{mechanism}, then moves away, leaving the \textbf{clock} \textbf{radio} ’s front clearly visible : \textbf{clock} on the left, \textbf{horizontal} \textbf{speaker} grille on the right side of that earlier \textbf{model} view, and clean, simple 1950s styling.
The commercial next presents another close view of the \textbf{clock} \textbf{radio} ’s control panel, now centered against a \textbf{plain} background.
The face is darker, with two round controls : a small \textbf{clock} or timing \textbf{dial} on the left and a larger \textbf{radio} tuning \textbf{dial} on the right.
The RCA Victor name is printed on the lower right of the panel.
The layout is \textbf{plain} and \textbf{symmetrical}, emphasizing the functional \textbf{dials} and the brand mark.
The \textbf{radio} is turned around to show its back panel.
A hand rests on top and then points to different \textbf{features} on the back.
The rear is a dark \textbf{rectangular} panel with a \textbf{printed} instruction or information label in the center, a round opening or socket on the right, and smaller sockets or switches on the lower left.
The hand points first toward the \textbf{central} label, then down toward the lower-left connections.
A cord is brought in and plugged into one of the back-panel outlets.
The hand steadies the \textbf{radio} while \textbf{inserting} the plug, then \textbf{withdraws}.
As the plugged-in cord trails away from the back of the \textbf{radio}, a tall metal coffee maker appears to the left on the same surface.
It has a cylindrical body, a handle, and a lid, with its cord looping across to the \textbf{clock} \textbf{radio}.
The \textbf{arrangement} shows the coffee maker connected through the \textbf{radio} ’s built-in outlet, with the \textbf{radio} acting as the timer or controller for the appliance.
The scene returns to the bedroom at night.
The lamp on the nightstand is lit, the \textbf{clock} \textbf{radio} sits beside it, and the woman lies asleep on her pillow.
The bed, tufted headboard, and soft bedding fill the right side of the scene, while the \textbf{radio} and lamp are on the left.
The woman ’s face is calm, her eyes closed.
In a closer view, the \textbf{radio} remains beside her, its \textbf{dials} and \textbf{central} grille visible.
Then the room darkens : the lamp goes out, leaving the \textbf{radio} and the sleeping woman in dimmer light.
The visual suggests the device has turned off the bedside lamp automatically while she sleeps.
The \textbf{clock} \textbf{radio} is then isolated against a \textbf{plain} dark background, shown as a clean product display.
It is light-colored, \textbf{rectangular}, with the round \textbf{clock} on the left, a \textbf{central} vertical grille of close \textbf{horizontal} slats, and the \textbf{radio} tuning \textbf{dial} on the right.
Two small \textbf{knobs} sit beneath the grille.
The RCA Victor name is printed near the lower right corner.
A stylized profile of a \textbf{human} head appears over the \textbf{speaker} grille, like a graphic emblem \textbf{associated} with sound or tone, centered between the two \textbf{dials}.
A large \textbf{price} graphic appears over the product : “ \$39.95 ” in bold, raised-looking white lettering.
Beneath it, smaller capital letters read, “ SLIGHTLY HIGHER IN FAR WEST AND SOUTH. ” The \textbf{price} text sits across the face of the \textbf{clock} \textbf{radio}, partially covering the \textbf{central} grille and \textbf{dials}.
After the \textbf{price} \textbf{fades}, the \textbf{radio} remains centered while the view broadens to reveal other RCA Victor \textbf{radios} arranged around it on shelves or display stands.
The \textbf{clock} \textbf{radio} stays in the middle.
Above left is a light-colored portable-style \textbf{radio} with a handle and a large circular \textbf{dial}.
Above right is a squarer \textbf{radio} with a large grille front and a handle-like frame.
Below and around the \textbf{central} \textbf{clock} \textbf{radio} are additional table and portable \textbf{models}, including darker \textbf{rectangular} \textbf{units} and lighter \textbf{radios} with rounded \textbf{dials} or grille fronts.
The display becomes a wall of different RCA Victor \textbf{radio} styles, with the \textbf{featured} \textbf{clock} \textbf{radio} at the center.
The final image overlays the brand identity over the display.
Large words “ RCA Victor ” appear across the upper center.
Below them is the familiar RCA Victor dog, seated and leaning toward the \textbf{horn} of an old \textbf{gramophone}.
Under the dog and \textbf{gramophone}, the slogan “ HIS \textbf{MASTER} ’S \textbf{VOICE} ” appears in \textbf{quotation} marks.
The closing visual holds on this brand mark, with the dog, \textbf{gramophone}, and large RCA Victor lettering dominating the screen.

% matched lemmas: adjust, arrangement, associate, central, circle, clock, dial, fade, feature, featured, function, gramophone, horizontal, horn, human, insert, knob, master, mechanism, model, plain, price, printed, protrude, quotation, radio, rectangular, speaker, superimpose, symmetrical, unit, voice, withdraw
\end{textsample}
