\begin{textsample}{POS Dim 3 – 1990 – Score 14.00 – 1990/tv\_com\_1990\_75.txt}  \label{ex:f3_pos_005}
The commercial begins with a very dark, nearly black image, with only faint horizontal \textbf{bands} visible.
It then cuts to a bright, \textbf{futuristic} white room seen from behind a young man.
The room has \textbf{glowing} tiled floor panels, pale gridded walls, and two \textbf{vivid} red lounge chairs positioned symmetrically on the left and right.
The young man, wearing white, faces toward the far wall.
A small dark screen or console area appears at the center of the room, with a cable trailing across the floor.
The camera moves into a close-up of the young man ’s face as he looks directly toward the viewer/camera while gripping a black \textbf{game} controller.
His expression is \textbf{intense} and engaged, suggesting he is actively playing.
The controller cable is visible.
The commercial then rapidly cuts through several video \textbf{game} scenes shown full-frame or as if on a screen : - A motorcycle or racing \textbf{game} in an urban street setting, with on-screen HUD \textbf{elements} and a rider leaning into the road. - A golf \textbf{game} showing a golfer near water and green terrain, with text overlays such as distance, stroke, and wind/speed indicators. - A side-view platform/action \textbf{game} in a stone-walled \textbf{environment}, with a character hanging or moving in a water-filled vertical opening while another colorful character stands above. - A fighting \textbf{game} scene with two fighters in a \textbf{stylized} arena with bright red \textbf{architectural} \textbf{elements} and health bars at the top. - A dark, high-contrast blue-and-red image of a bulky humanoid or creature-like figure, followed by a white \textbf{silhouette} version of the same figure, then back to the colored version. - An off-road racing scene with a small vehicle/buggy driving over rough terrain. - A very dark scene with \textbf{scattered} bright white shapes or figures ; the details are \textbf{difficult} to identify from the sampled frame.
Between the \textbf{game} clips, the white room reappears.
In one wide shot, the young man is seated in the room with the controller cable on the floor, and the wall behind him appears cracked or broken, as if impacted.
Later, he is shown again from the front, still holding the controller, focused on playing.
Another shot looks upward from a low angle : his face and hands with the controller are seen above, with the cable hanging across the frame.
A following shot shows him seated in a yellow-and-white chair, holding the controller with the cable trailing across the white floor.
The final product shots appear on a black background.
A Panasonic-branded product display comes into view with a dark \textbf{game} console, a controller, discs, and a small rectangular item.
Large \textbf{stylized} white lettering forms the word “ REAL, ” with small red, green, and blue colored squares between \textbf{letters}.
The last frame clearly reads “ Panasonic REAL ” above and beside the displayed console and accessories.

% matched lemmas: architectural, band, difficult, element, environment, futuristic, game, glowing, intense, letter, scattered, silhouette, stylize, vivid
\end{textsample}
