\begin{textsample}{POS Dim 3 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_30.txt}  \label{ex:f3_pos_013}
The commercial opens on a brightly lit \textbf{studio} set designed like a \textbf{stylized} dance or performance space.
The set contains round platforms, large colored circles, red cone-shaped props, hanging \textbf{reflective} disco balls, and many people standing or dancing around the space.
At the center, a woman in a long orange-red outfit stands on a white circular platform, visually positioned as the main performer.
The next shots move closer to this central woman.
She has large curly hair with orange fabric or ribbons in it and holds a handheld microphone.
She wears an orange dress with pink/orange flowing sleeve \textbf{accents} and bracelets.
She raises one hand while facing forward, as if addressing or performing to the surrounding \textbf{crowd}.
The background remains theatrical, with bright red triangular forms and \textbf{reflective} curtains.
The commercial cuts to other people in the set : two dancers or audience members with large hairstyles and 1980s-style clothing move and gesture, one holding light-colored fabric or gloves.
Another close-up shows a blonde woman with heavy eye makeup looking upward or toward the \textbf{stage} while people dance behind her.
These shots present the \textbf{crowd} as fashionable, expressive, and visually engaged with the performance.
The main performer is then shown again full-length on the circular platform, framed by foreground \textbf{silhouettes} of other people.
She continues holding the microphone and gesturing.
Close-ups show her looking down at her hand or outward, with the microphone centered in front of her.
The editing \textbf{alternates} between her and reaction/dance shots, maintaining the \textbf{impression} of a live \textbf{staged} performance.
Midway through, a group shot shows dancers in front of large hanging spheres and geometric props.
Bold white all-capital text appears across the lower/middle part of the frame : “ IF YOU ’RE NOT LISTENING TO A KENWOOD, ” The same text continues over a close-up of the main performer holding the microphone.
The font is thick, sans-serif, white, and highly legible against the darker, colorful background.
A brief blurred motion shot follows, showing a dancer moving quickly across a shiny, dotted backdrop.
Then the main performer is seen again at a distance, with the \textbf{crowd} in the foreground and large circular wall \textbf{graphics} behind her.
Another white all-capital text overlay appears : “ THERE MIGHT AS WELL BE NO MUSIC AT ALL. ” A final close-up of the performer shows her face and microphone prominently, with her mouth open and eyes directed upward or forward.
The commercial then cuts to a black background with the brand name “ KENWOOD ” centered in white lettering ; the “ W ” includes a small red triangular \textbf{accent}.
In the next frame, a smaller white tagline appears beneath it : “ DO THE MUSIC JUSTICE. ” The last sampled frame shows an abstract, fast-moving blur of colored diagonal streaks.
Its exact relation to the preceding logo screen is unclear from the sampled frames alone.

% matched lemmas: accent, alternate, crowd, graphics, impression, reflective, silhouette, stage, studio, stylize
\end{textsample}
