\begin{textsample}{POS Dim 3 – 2000 – Score 4.00 – 2000/tv\_com\_2000\_59.txt}  \label{ex:f3_pos_067}
A black screen is filled by the words “ INITIALIZE SEQUENCE ” in large, bold, red block letters with a white outline and a faint glow, suggesting a computer start-up theme.
The words remain centered while the glow behind them pulses between dark and grey.
The Computer Renaissance logo appears over a hand-drawn, old-world style illustration of a Renaissance man in profile, holding what looks like a small keypad or calculator.
The logo is a long \textbf{rectangular} banner, yellow on the left and purple on the right, with “ Computer ” in large black letters and “ RENAISSANCE ” printed smaller beneath it.
A large metallic grey word, partly visible as “ solution, ” sweeps across the drawing, matching the spoken emphasis on solutions.
The setting changes to the inside of a computer retail store.
Fluorescent ceiling lights run down a narrow \textbf{showroom}.
Along the right side, several beige CRT monitors, towers, keyboards, and mice sit on a long white display counter.
A bright blue computer tower stands closest to the foreground.
On the left, stacks of yellow-and-white product boxes form display islands, with more shelves and computer accessories covering the back wall.
White text begins appearing over the lower left of the store scene, listing computer specifications, starting with “ Celeron 500 MHz ” and then “ 8.4 GB HD. ” A stylized computer package begins to move through the store as if animated : a grey desktop tower, CRT monitor, keyboard, mouse, \textbf{speakers}, and boxed accessories separate from the display area and float forward.
The pieces tilt and rotate in midair, passing over the stacks of Lexmark-branded boxes.
The CRT monitor hangs at an angle, the tower and keyboard swing around it, and smaller components cluster nearby.
As the parts drift, more white specification text layers over the left side of the picture : “ 64 MB RAM, ” “ 17 ” Monitor, ” “ Keyboard \& Mouse, ” “ CD-ROM/Sound Card, ” “ \textbf{Speakers}, ” “ Windows 98 2nd Edition, ” and “ MS Works. ” The floating computer components settle into a neat product \textbf{arrangement} in the foreground.
A beige tower stands on the left, flanked by a small grey \textbf{speaker}.
In the center, a beige CRT monitor faces forward with a black screen, a white keyboard directly in front of it, and a white mouse to the right.
On the far right, another grey \textbf{speaker} stands beside a colorful “ CD-ROM ” software or hardware box.
Behind and beneath the display are stacked Lexmark boxes, including boxes marked “ 1100, ” while the store shelves in the background are packed with hanging accessories, boxed products, and additional desktop systems.
The translucent white \textbf{feature} list continues to overlay the scene, partially covering the products as the package is shown.
The store background briefly clears to reveal more shelves and counters : printers, small electronics, boxed accessories, and another monitor on a shelf to the right.
Then three boxed items float prominently against a softly blurred store background.
On the left is a yellow box labeled “ LinkScan, ” showing a small flat scanner-like device.
In the middle is a blue “ Lexmark ImageWave ” box with a large photo of a smiling person.
On the right is a yellow-and-white Lexmark printer box labeled “ 1100, ” visually matching the spoken offer of a printer or scanner choice.
Large promotional text fills the center over the store interior : “ FREE ” appears in big red letters, with “ Internet Access ” below in large yellow letters.
Small text underneath says “ See Store for Details. ” The background remains the computer store, slightly out of focus, with rows of equipment and boxed displays visible.
The full computer package returns against the blurred store background : tower on the left, monitor and keyboard in the center, \textbf{speakers} on both sides, mouse at the keyboard ’s right edge, and the CD-ROM box on the right.
Above it, yellow text reads, “ Includes 1 Year Warranty. ” The commercial ends on a blue graphic screen with the Computer Renaissance logo at the top.
Beneath it, white text reads “ 250 Stores Nationwide. ” Large yellow text gives the location, “ Across From Columbia Center, ” followed by the phone number “ 783-2499. ” At the bottom, a website address appears : “ www.crkennewick.com. ” A dark green map-like shape sits behind the text as a subtle background graphic.

% matched lemmas: arrangement, feature, rectangular, showroom, speaker
\end{textsample}
