\begin{textsample}{POS Dim 3 – 1960 – Score 6.00 – 1960/tv\_com\_1960\_17.txt}  \label{ex:f3_pos_050}
The commercial is presented in black-and-white, with dark borders around the image and a visible “ Nostalgic X’er ” watermark in the lower-right corner throughout the sampled frames.
At the beginning, the screen is almost entirely black, with little visible detail apart from the watermark.
The next sequence shows an outdoor wooded setting.
A \textbf{human} figure, apparently a man, is seen in \textbf{silhouette} among trees.
He appears to be running or jogging through the forest.
The camera faces him from the front or front-left at times, while \textbf{strong} sunlight shines through the trees behind and beside him, creating glare and lens \textbf{flare}.
The runner ’s body is mostly dark against the bright background, making facial features and clothing unclear.
As the sequence continues, the runner remains framed among tall trees and foliage.
The sunlight \textbf{becomes} very bright, briefly washing out much of the image.
The figure is still visible as a dark outline, moving forward with bent arms in a running posture.
A clearer side view follows : the man appears shirtless and is running through the woods from left to right.
His arms are bent, and his body is shown in profile against a background of tree trunks and undergrowth.
The image remains high-contrast and somewhat grainy.
Later, product text appears over the forest-running scene.
A large word, “ VIGRAN, ” is centered across the image, with “ SQUIBB VITAMINS ” underneath.
A simple line graphic or outline runs horizontally around the text.
The \textbf{silhouetted} runner remains visible behind the typography.
The text then appears larger over a closer view of the runner ’s upper body. “ VIGRAN ” is prominently centered, with “ SQUIBB VITAMINS ” below it.
The man ’s face remains mostly \textbf{shadowed} and indistinct because of the bright backlighting.
The final frame cuts to a studio-style product shot : a dark glass bottle with a light-colored cap stands centered against a plain, softly lit background.
The label reads “ VIGRAN SQUIBB, ” with smaller text below that appears to include “ MULTI-VITAMINS, ” though the smaller wording is not fully sharp.
A geometric design is visible on the lower part of the label.

% matched lemmas: become, flare, human, shadow, silhouette, strong
\end{textsample}
