\begin{textsample}{POS Dim 3 – 1960 – Score 12.00 – 1960/tv\_com\_1960\_100.txt}  \label{ex:f3_pos_028}
In black and white, a middle-aged, light-haired man in a dark business suit sits at an office desk, holding a black telephone \textbf{handset} to his ear.
He faces slightly toward the viewer, with a calm, expectant expression.
A second telephone base sits on the desk at the left edge, and behind him are vertical curtains and a small framed picture on the wall, giving the setting a formal office feel.
The scene shifts to another office desk, where a younger dark-haired man in a suit and tie holds a black telephone \textbf{handset} to his ear.
On the desk to his left is a large desktop calculating machine : a light-coloured base with a dark upper housing, a \textbf{slanted} keyboard area, and a roll or strip of paper emerging at the top.
Papers, a pencil, a small ashtray-like dish, and a pen holder sit around him.
While speaking on the phone, he gestures with his free hand, points off to the side, then looks down at his wristwatch as if pressed for time.
He reaches for a pencil and paper, settles his hand on the sheet, and appears to take down figures while listening.
The first, light-haired man reappears at his desk, still on the telephone.
He pulls a sheet of paper toward himself, lifts and straightens it, and studies it while speaking.
His brow tightens in concentration as he reads from the document, then he looks more satisfied, keeping the \textbf{handset} close to his ear.
Back at the younger man ’s desk, the calculator becomes the focus.
He keeps the telephone at his ear with one hand and reaches across with the other toward the machine.
A close view shows his hand rapidly \textbf{operating} the calculator ’s controls.
The keyboard has a cluster of small round white number keys, larger dark \textbf{function} keys, and a grey \textbf{rectangular} key ; his fingers press and move across them quickly.
The machine ’s dark upper \textbf{section} rises behind the keys, and a paper tape is visible near the top.
After entering the figures, he reaches to the top area of the machine, where the paper strip sits, as though checking the \textbf{printed} result.
The younger man remains on the phone, his left hand resting on the top of the calculator near the paper roll.
He looks toward the machine and then back ahead, composed and confident, as if reporting the answer.
He \textbf{withdraws} his hand from the calculator and sits upright, with the papers and pencil still in front of him.
The older man then appears again, smiling into the phone, his expression turning from businesslike to impressed and pleased.
The younger man continues at his desk with the calculator beside him.
He smiles slightly while holding the \textbf{handset}, then the view tightens to his face.
He is clean-shaven, with neatly combed dark hair, wearing a dark suit, white shirt, and patterned tie.
He speaks into the receiver with a relaxed, assured expression.
A ring is visible on the hand holding the phone.
He smiles more broadly, then lowers the \textbf{handset} out of view, as though ending the call.
Now without the phone at his ear, he looks forward and addresses the viewer directly.
His expression is friendly and confident, and the \textbf{plain} office wall behind him keeps attention on his face.
As he continues, the image of the calculator gradually appears over him in a soft \textbf{overlap}, then replaces him completely.
The final view presents the Underwood Olivetti calculator alone on a \textbf{plain}, light surface against a simple light background.
The machine is angled slightly so its front keyboard is clearly visible.
It has a \textbf{sturdy} light-coloured lower body, a dark rounded top cover, a \textbf{slanted} control panel filled with white circular number keys and darker surrounding keys, and a paper tape \textbf{protruding} from the rear top.
The product remains centered and still, shown as the main object, with no large readable text on screen.

% matched lemmas: function, handset, operate, overlap, plain, printed, protrude, rectangular, section, slant, sturdy, withdraw
\end{textsample}
