\begin{textsample}{POS Dim 3 – 1980 – Score 9.00 – 1980/tv\_com\_1980\_17.txt}  \label{ex:f3_pos_036}
The commercial opens on a dark/black frame, then cuts into a highly \textbf{stylized} beauty montage.
A close-up of a blonde woman appears against a pale blue sky-like background with soft pink clouds.
She wears a dark navy cap with a small decorative pin and matching dark clothing.
Her makeup is prominent, especially her eye makeup and \textbf{glossy} lips, and she looks directly toward the camera.
The next shots show lipsticks in shiny \textbf{silver} tubes, grouped in threes, filmed in close-up against the same blue-sky/cloud backdrop.
The lipstick shades shown are mainly warm browns, beiges, and soft pinks.
The camera \textbf{alternates} between these product close-ups and close-ups of women ’s faces.
A second woman appears in close-up wearing a yellow-green cap with a small star-like pin.
She has long, curled brown hair, pale eyes, dramatic eye makeup, and \textbf{glossy} brownish lipstick.
Another woman follows in close-up wearing an orange-brown cap, also with \textbf{strong} eye makeup and \textbf{glossy} lips.
The models are framed frontally, with direct or near-direct gazes.
The montage continues with \textbf{repeated} close-ups of lipstick bullets in \textbf{reflective} metal casings.
Some are brown-toned ; others are pink or beige.
The lipsticks are arranged in sets of three and shot from slightly different angles, sometimes tilted diagonally across the frame.
The background remains a soft, artificial sky with clouds.
The blonde woman in the navy cap returns in a frontal close-up.
Immediately afterward, the screen cuts to a graphic brand card : a blue background with a large white logo reading “ L’ERIN, ” topped by a rainbow/arched emblem.
A product lineup then appears on a \textbf{reflective} black surface in front of the same cloud backdrop.
Visible items include a compact, a white cylindrical product labeled “ L’ERIN, ” a tall boxed product with text that appears to include “ FROSTED LIP COLOR, ” an opened lipstick in a \textbf{silver} tube, and a small bottle that resembles nail color or cosmetic liquid.
The items are arranged upright like a display.
Another shot shows a larger array of many lipsticks in \textbf{silver} tubes, arranged in rows at different heights.
The shades vary across pink, beige, brown, and mauve \textbf{tones}.
A close-up then shows one of the women applying lipstick to her lower lip.
Only her face and the lipstick tube are visible, with the lipstick touching the lip area.
This is followed by a single lipstick bullet in close-up, isolated against the blue/cloud background, emphasizing its \textbf{glossy} pink-beige surface.
The “ L’ERIN ” logo card appears again, identical or very similar to the earlier blue-and-white graphic.
Near the end, three women are shown together in profile or three-quarter profile, standing side by side and facing toward the left.
They wear coordinated caps and outfits in different colors : yellow-green, navy, and orange-brown.
Their styling is \textbf{polished} and uniform-like, with the small decorative cap pins repeated.
The final shots focus on the woman in the orange-brown cap.
She turns or is framed from a partial side view into a more frontal close-up, looking toward the camera.
The last frame places her face on the left side of the screen with the white “ L’ERIN COSMETICS ” logo overlaid on the lower right.
The background remains pale blue, and her \textbf{glossy} brown lipstick and eye makeup are emphasized.

% matched lemmas: alternate, glossy, polished, reflective, repeated, silver, strong, stylize, tone
\end{textsample}
