\begin{textsample}{POS Dim 3 – 1960 – Score 27.00 – 1960/tv\_com\_1960\_106.txt}  \label{ex:f3_pos_022}
The commercial opens on a rocky ocean shoreline.
Churning water and pale foam fill the view, washing over dark rocks in a greenish, \textbf{faded} color palette typical of old film.
The sea surface glitters and shifts, then the image moves across wide stretches of surf, with waves rolling toward a rugged coast and breaking into spray around black, jagged rocks.
The ocean scene gives way to a modern interior with large, \textbf{slanted} floor-to-ceiling windows overlooking the same restless sea.
Inside, in front of the windows, stands a \textbf{mid-century} wooden stereo cabinet.
It is a long \textbf{rectangular} \textbf{console} on short \textbf{tapered} legs, with lighter wood panels on each side and a darker \textbf{central} \textbf{section} of narrow vertical slats, suggesting \textbf{speaker} grille or cabinet doors.
Chairs and small furnishings sit to either side, making the space feel like a stylish living room or \textbf{showroom} with an ocean view.
The cabinet is then presented more directly against the windows, centered on a low platform.
The sea continues to fill the background beyond the glass.
As the product is introduced in the audio as RCA Victor Total Sound Stereo, the cabinet remains the visual focus : polished wood, clean lines, and a balanced, \textbf{symmetrical} front.
A close view reveals the top of the stereo opened to its controls.
A black \textbf{record} lies on the \textbf{turntable} in the center, with the tone arm resting over it.
On both sides are \textbf{rectangular} control panels with round \textbf{knobs} and \textbf{dials} arranged neatly, showing the cabinet as both furniture and audio equipment.
Another close-up isolates one control area : metallic circular \textbf{knobs} sit in a vertical row beside a long, slim control strip.
A separate view shows a \textbf{radio} tuner panel with a vertical frequency scale, three round \textbf{knobs} to the side, and the edge of the \textbf{record} player nearby, matching the audio \textbf{references} to the \textbf{record} changer and AM-FM \textbf{radio}.
The commercial returns briefly to the cabinet in the ocean-view room, then cuts back to the coast.
Waves slide along a sandy shoreline, then crash hard against cliffs and rock faces.
Foam explodes upward and spreads across the rocks, sometimes filling almost the entire image with pale spray.
Wider views show tall, rugged rock formations rising from the surf as water surges around them, emphasizing the scale and force of the sea.
The ocean image gradually blends into a studio display of several RCA Victor stereo cabinets.
The products are arranged on curved, tiered platforms in a softly lit \textbf{showroom} setting.
Multiple wooden cabinet styles are visible : a \textbf{central} \textbf{rectangular} \textbf{console} with vertical grille slats, a lower cabinet to the left, a more ornate cabinet to the right with shaped panels and legs, and additional cabinet fronts or \textbf{models} elevated behind them.
The display suggests a range of furniture styles, from simple modern panels to more traditional decorative fronts, all in warm wood tones.
A small matching \textbf{rectangular} \textbf{unit} stands near the center-right, possibly a \textbf{speaker} or accessory.
Near the end, the product display \textbf{fades} behind a large circular RCA Victor emblem.
Inside the \textbf{circle} is a line drawing of the famous dog listening to a \textbf{gramophone}, the “ His Master ’s Voice ” image : the dog stands beside the \textbf{horn} of the \textbf{phonograph}, facing it attentively.
The background darkens so the emblem stands out.
Finally, the closing graphic forms around a circular record-like design.
The letters “ RCA ” appear large in the center of a red \textbf{circle}, with a lightning-bolt-like mark beneath.
Below, white text reads, “ The Most Trusted Name in Sound, ” matching the closing slogan in the audio.

% matched lemmas: central, circle, console, dial, fade, gramophone, horn, knob, mid-century, model, phonograph, radio, record, rectangular, reference, section, showroom, slant, speaker, symmetrical, taper, turntable, unit
\end{textsample}
