\begin{textsample}{POS Dim 3 – 1960 – Score 17.00 – 1960/tv\_com\_1960\_96.txt}  \label{ex:f3_pos_025}
A mother stands in a warmly lit home interior that looks like a kitchen or dining area, with shelves, wall decorations, and hanging household items behind her.
She has neatly styled dark hair swept back in a 1960s shape and wears a dark collared dress or blouse.
Holding something small near her waist, possibly a cloth or dish, she looks down and then turns her face toward someone off to the side, her expression attentive and questioning.
The view shifts to a young blond boy, about elementary-school age, wearing a dark red top.
He first looks downward, then raises his eyes and smiles slightly, as if answering.
The setting behind him is softer and more living-room-like.
A wider view reveals the family gathered around a low table : the blond boy sits on the right, a young girl with bangs and a short-sleeved dark dress kneels or stands on the left, and an adult man, likely their father, sits behind them in glasses and a dark cardigan over a light shirt.
Everyone is grouped around a small portable \textbf{record} player on the table.
The product has a white \textbf{rectangular} base, a red or dark lid \textbf{section} opened to one side, and a small black \textbf{record} already on the \textbf{turntable}.
The adults and children look relaxed and pleased, with the children closest to the player.
The \textbf{phonograph} is then shown more clearly from above.
Its compact white base holds a black \textbf{vinyl} \textbf{record} with a pale center label, and the red lid or \textbf{speaker} \textbf{section} sits open to the left.
The tone arm rests to one side, and the whole \textbf{unit} is small enough to fit comfortably on the tabletop.
Another view shows the player from the side with the family blurred behind it, emphasizing its low, portable shape and simple controls.
The scene changes outdoors to a park-like picnic setting.
A wooden picnic table with a white cloth stands on grass, with bare trees and water in the background.
The same family appears to be gathered around it : the girl stands at the left side of the table, the adult man sits beyond the table, and the blond boy in the red top sits with his back partly turned on the bench.
Food and picnic items are spread on the table, and the Swingster \textbf{phonograph} is set up among them, visually \textbf{demonstrating} that it can be taken outside.
Close views show a child ’s hands \textbf{operating} the portable player on the picnic table.
The white base has a red \textbf{turntable} platter, and the tone arm is lifted out of the way.
A hand holds a small black 45 rpm \textbf{record} by its edge, moves it over the platter, and places it onto the center spindle.
The \textbf{record} settles flat on the red platter.
Then both hands \textbf{adjust} the tone arm and its guide, positioning it over the \textbf{record} so the stylus can be set down.
The \textbf{mechanism} is shown as simple and hands-on, with the player ’s parts large and visible.
An even closer view shows the tone arm over the spinning \textbf{record} area.
The \textbf{cartridge} or head of the arm has the word “ swingster ” printed on it.
A thin guide \textbf{wire} or lift guide crosses above the \textbf{record}, leading toward a small \textbf{ribbed} control piece near the edge, illustrating how the arm is aligned and lowered.
The final product display shows the Kenner Swingster package on a \textbf{plain} light background.
The box is upright and \textbf{features} a large red “ swingster ” name with the Kenner brand above it.
The front illustration shows children using the portable \textbf{phonograph}.
Across the bottom of the screen, visible text reads “ BATTERIES AND \textbf{RECORDS} NOT INCLUDED. ”

% matched lemmas: adjust, cartridge, demonstrate, feature, mechanism, operate, phonograph, plain, record, rectangular, rib, section, speaker, turntable, unit, vinyl, wire
\end{textsample}
