\begin{textsample}{POS Dim 3 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_70.txt}  \label{ex:f3_pos_020}
The commercial begins with a very dark, low-contrast close-up of a person ’s face.
The individual appears to be facing the camera, but the image is too \textbf{dim} to identify facial features, age, expression, or setting clearly.
After this, the visuals shift into a bright, \textbf{stylized} sequence \textbf{dominated} by purple, blue, and green color \textbf{effects}.
A young woman ’s face appears in close-up, partially obscured by a superimposed product package.
The package branding is visible as “ PROPA pH, ” suggesting the product line is being introduced through \textbf{layered} dissolves and color overlays.
The next frame shows two white bottles side by side, both labeled “ PROPA pH. ” The labels read “ astringent cleanser, ” and smaller text below appears to mention acne-related skin care, though not all of it is fully legible.
The shot is still heavily \textbf{stylized} with purple and blue \textbf{lighting} and a soft, overlapping transition \textbf{effect}.
A small line of text appears near the bottom, but it is too blurred to read with confidence.
The commercial then returns to the young woman, now smiling and facing the camera.
Her face is again \textbf{layered} with product \textbf{imagery}, including a large “ PROPA pH ” package in the foreground.
The background remains saturated with purple \textbf{tones}, giving the scene a \textbf{glossy}, cosmetic-advertising style.
The final frame is a clear pack shot on a purple textured background.
Three products are arranged upright : a rectangular carton on the left, a tall bottle in the center, and a rounded bottle on the right.
All display the “ PROPA pH ” branding.
The left package appears to read “ pimple/acne mask, ” the center bottle reads “ astringent cleanser, ” and the right bottle reads “ foaming face wash. ” Large promotional text appears above and beside the products : “ THE PROPA WAY TO CLEAR UP YOUR SKIN. ” The product lineup is centered and brightly lit, functioning as the closing brand/product display.

% matched lemmas: dim, dominate, effect, glossy, imagery, layer, lighting, stylize, tone
\end{textsample}
