\begin{textsample}{POS Dim 3 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_72.txt}  \label{ex:f3_pos_047}
A warmly lit office appears, with mustard-yellow walls, venetian-blind shadows, framed artwork, and a desk holding early-1980s office equipment : a printer and a beige CRT computer terminal.
In the foreground, a light-skinned adult woman with short, curly dark hair sits or leans forward at her desk with her back partly to view.
She wears a pale gray blazer over a white blouse with a soft scarf-like bow at the neck.
In the doorway across the room stands an older light-skinned man, balding with hair at the sides, wearing large glasses, a dark suit, tie, and \textbf{pocket} square.
He faces into the office as if addressing her, then steps slightly inward and turns his head toward the computer equipment beside him.
The woman is then seen from the front, smiling up toward the older man.
Her expression is polite and attentive at first, and she leans forward beside a wooden desk partition.
Behind her, striped light from blinds falls across the wall, and a framed picture hangs to her left.
As the exchange continues, her smile softens into a more uncertain, dutiful look.
The older man appears in close view, his large glasses prominent, his face serious.
He turns his head aside, then leaves through the doorway.
The door or wall edge fills the view as he passes out, briefly obscuring him.
Attention moves to the portable computer.
A pair of hands places a compact white Radio Shack Model 100 Portable Computer into an open brown briefcase on a desktop.
The machine is \textbf{rectangular}, with a full black keyboard on the lower half, a long narrow display screen above it, and small control panels on the right.
Around it are office items : a small potted cactus, stacked binders or folders, a black notebook, a pen, and a desk nameplate that appears to identify Fletcher.
The hands settle the computer neatly into the briefcase, then the briefcase lid begins to close over it, emphasizing that the computer can be packed up and carried.
The woman is then shown away from the office, sitting in the back seat of a car or taxi beside a window.
She now wears a beige trench coat and holds the Model 100 on a small wooden surface in front of her.
City scenery outside the car window passes by in soft blur.
She looks down, positions the computer in front of her, and begins using it, resting one hand near the keyboard and the other near the side of the machine.
Her posture is focused and businesslike, using the computer as a traveling workstation.
The setting changes again to a home-like room with warm wood tones.
A sofa sits in the background, with a side table holding a cream-colored telephone.
A coffee table is cluttered with papers, a cup, and small objects.
The same dark-haired person, likely Fletcher, sits forward over the Model 100 on the coffee table, typing and working intently.
The room includes a lamp and dark furniture in the background, giving the sense of a comfortable living room being used as an office.
A close view shows hands typing rapidly on the Model 100 ’s black keys.
The long display screen shows faint lines of text, though the words are not readable.
A pair of eyeglasses and papers lie above the computer on the table.
The hands continue working across the keyboard, \textbf{demonstrating} it as a word processor or general work machine.
Then an arm wearing a wristwatch reaches past the computer toward telephone equipment.
Beside the computer are cords, a black acoustic coupler-like device, and a cream push-button telephone.
A white \textbf{handset} is lifted and placed into the black cradle, with cords running between the phone equipment and the workspace, visually suggesting the portable computer connecting through the telephone line.
Back in the office, the older man returns through the doorway.
He is now without his suit jacket, wearing a dark vest over his dress shirt and tie, and carrying papers.
He steps into the office where the printer and CRT terminal sit on the table against the yellow wall.
Papers are scattered on the desk, and a red-orange object or garment rests in the foreground.
Fletcher herself is not clearly visible here, making the office feel momentarily unattended as he looks in.
The product is then displayed alone on a dark background.
The Model 100 sits angled upward with a pen beside it, its white body, black keyboard, and long display clearly visible.
Large white on-screen text reads “ From \$799. ” Beneath it, a higher \textbf{price}, “ \$1,099, ” is shown crossed out, reinforcing the sale \textbf{price}.
Finally, a black background holds a \textbf{rectangular} picture of the older man seated in the office, reading a sheet of paper beside the printer and CRT computer.
Large red text below reads “ Radio Shack, ” and white text underneath says “ Model 100 now on sale. ”

% matched lemmas: demonstrate, handset, pocket, price, rectangular
\end{textsample}
