\begin{textsample}{POS Dim 3 – 1970 – Score 12.00 – 1970/tv\_com\_1970\_76.txt}  \label{ex:f3_pos_061}
The commercial begins with a black screen.
It then cuts into a highly \textbf{stylized}, colorful scene with theatrical \textbf{lighting} in pink, red, blue, and purple \textbf{tones}.
The \textbf{imagery} appears to feature dolls, puppets, mannequins, or human-like figures rather than clearly identifiable live actors.
One early close-up shows a face-like figure with large round goggles or glasses, curly hair or textured material around the sides of the head, and decorative markings on the face.
The \textbf{lighting} is saturated and dreamlike.
A second figure appears with a pale green-blue face, long hair or hanging strands, and a prominent dark star shape over one eye.
The background contains \textbf{glowing} bulbs and \textbf{reflective} objects, suggesting a \textbf{staged} display or fantasy shop-window-like \textbf{environment}.
The next shots show more of this crowded, decorative setting.
Figures or mannequins appear posed among hanging lights, shiny metallic surfaces, ribbons, and props.
One shot shows a figure raising an arm near round hanging lights, with bright red sparkling reflections to the right.
The space is dense with objects and has a theatrical, fashion-display quality.
A product-like display appears : a small open case or box is shown among bright props and \textbf{reflective} materials.
The contents are not fully clear from the frame, but the scene suggests watches or jewelry are being displayed.
The \textbf{lighting} continues to be \textbf{vivid} and neon-like.
Another shot shows a curly-haired figure leaning toward or working near a shiny mechanical-looking fixture.
The figure is lit in pink and red.
Nearby are colorful props and possibly small decorative flowers or watch-display \textbf{elements}.
The figure ’s activity is not fully clear from the sampled frame.
A later shot shows another human-like figure in profile, holding or interacting with a large object against a dark, red-lit background.
The object is not clearly identifiable in the frame.
The commercial then cuts to a close-up of a wristwatch or pendant-like watch with a round face.
It is shown against a blue background, with a decorative top piece and a chain or strap visible below.
The watch face is centered and brightly lit.
This is followed by a clearer close-up of a wristwatch with a round white dial, dark hour markers, and a metallic case.
The watch is attached to a dark strap and fills most of the frame.
The scene returns to the theatrical setting with the curly-haired figure beside the shiny fixture.
The figure ’s head is tilted upward, and arms appear extended toward nearby props.
The \textbf{lighting} remains pink-red.
Another figure appears in blue and purple light, partially obscured by foreground objects and bright reflections.
A watch or circular object may be present near the center, but the image is \textbf{layered} and not fully clear.
A wide shot shows a cluttered, colorful arrangement of fabrics, props, dolls or mannequins, hanging lamps, and display objects.
The setting resembles an elaborate fantasy display filled with soft pink fabrics and \textbf{scattered} decorative items.
A small watch-like object is visible near the lower center, though details are limited.
The final shots present a graphic title card on a dark background.
The text reads : “ TIMEX FASHION WATCHES 9⁹⁵–19⁹⁵ ” The lettering is bright blue and white with a pink ornamental border.
The last frame holds this graphic cleanly against black.

% matched lemmas: element, environment, glowing, imagery, layer, lighting, reflective, scattered, stage, stylize, tone, vivid
\end{textsample}
