\begin{textsample}{POS Dim 3 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_112.txt}  \label{ex:f3_pos_015}
The commercial begins on a nearly black screen with only a small “ 90 ’s commercials ” watermark visible at the lower right.
A dimly lit \textbf{pair} of doors then opens inward, letting a narrow vertical beam of bright light into a dark interior.
The setting shifts to a blue-lit, smoky, industrial-looking space with \textbf{strong} backlighting and spotlights.
A large mechanical or armored figure appears centered in the frame, moving or being revealed in the \textbf{haze}.
The next shot shows a close-up of a metallic tube or nozzle-like device aimed toward the camera, attached to a larger orange-and-gray apparatus.
The \textbf{lighting} remains dramatic and \textbf{futuristic}.
This is followed by a \textbf{dim} kitchen or countertop scene : cabinets, a counter surface, and a small appliance are visible, with a thin orange light entering from the left side of the frame.
The commercial then cuts to a \textbf{stylized} targeting display over an insect-like form.
The image appears colorized or x-ray-like, with a \textbf{glowing} rectangular targeting frame and crosshair lines.
Text along the bottom reads : “ REFUND LIMITED CALL ORKIN FOR DETAILS. ” The targeting display \textbf{alternates} between dark and bright/negative color versions.
The words “ TARGET TERMINATED ” appear across the upper part of the targeting frame, and then “ GUARANTEED ” appears in large \textbf{letters} below it.
These overlays repeat across several quick cuts while the insect-like body remains behind the graphic.
A later shot returns to the \textbf{futuristic} setting.
A person or armored figure faces the camera, wearing a bulky suit or protective equipment with a red diamond-shaped “ ORKIN ” logo visible on the chest area.
The figure holds or points a device toward the viewer ; a bright circular light or lens is visible on it.
The final product/service frame shows a smiling man in an Orkin-style uniform : white cap, white shirt, black tie, and a red diamond Orkin logo on the shirt and cap.
He stands against a smoky blue background.
Large white text across the bottom reads : “ 1 800 800 ORKIN, ” and a red diamond “ ORKIN ” logo appears to the right of him.
The commercial then fades back to a very dark screen with the small lower-right watermark still present.

% matched lemmas: alternate, dim, futuristic, glowing, haze, letter, lighting, pair, strong, stylize
\end{textsample}
