\begin{textsample}{POS Dim 3 – 1970 – Score 10.00 – 1970/tv\_com\_1970\_113.txt}  \label{ex:f3_pos_032}
The commercial opens on a television screen filled with a simple electronic game.
Against a dark reddish background, a bright dotted line runs vertically down the center like a net, with small \textbf{rectangular} paddles on either side and a tiny square “ ball ” near the play area.
The image shifts into a more colorful game display : large score numbers appear near the top, reading as “ 15 ” on the left and “ 11 ” on the right, while rows of small square blocks in cyan, green, white, and pink form a grid across the lower part of the screen.
The glowing edges of the TV picture curve slightly, emphasizing that this is being seen on an old-style tube television.
The scene then moves into an electronics or television shop.
Shelves of \textbf{boxy} CRT televisions line the walls in the background, many stacked in wood-toned display \textbf{units}.
A boy with straight, light-brown hair, wearing a light-colored shirt, sits at a counter in front of a large television on the right.
Beside and slightly behind him stands an adult man with short dark hair, wearing a tan sweater over a collared shirt.
The man leans in attentively, watching the boy and the TV screen.
The boy ’s hands are on a dark control panel below the television, using a round \textbf{knob} or \textbf{dial} to play.
In the background, another adult in a light shirt faces away, looking at or \textbf{adjusting} a different television.
As the boy continues at the controls, the adult man looks toward someone in front of them.
A pair of hands enters from the foreground holding up a woodgrain video game \textbf{unit} for them to see.
This \textbf{unit} has a sloped top, two large black round \textbf{knobs}, a \textbf{central} \textbf{rectangular} panel, and a pattern of white curved stripes on the front.
The man faces forward as if responding to the offer, while the boy glances toward the \textbf{unit} but remains close to the TV.
The offered \textbf{console} is held between the viewer and the pair, partially blocking the lower half of the scene.
The adult man gestures back toward the television and the control area, appearing to point out the game they are already using.
The offered woodgrain \textbf{unit} is lowered out of view, and the boy returns his attention to the screen and the controls.
The television screen itself is mostly a bright blue-green field with a simple vertical line and small game shapes, consistent with the electronic Pong-style play seen earlier.
A second alternative \textbf{unit} is then presented from the foreground.
This one is longer and flatter, with a black \textbf{central} panel, reddish-orange ends, round control \textbf{knobs}, and small \textbf{rectangular} switches or labels in the middle.
It is held close to the camera, again partially covering the boy and the counter.
The adult man continues facing forward and talking, while the boy remains seated beside him.
The man ’s expression is focused and explanatory ; he occasionally raises his hand, palm up, as though comparing choices or listing \textbf{features}.
The foreground \textbf{unit} is eventually lowered, returning the view to the boy, the man, the TV, and the built-in controls at the counter.
The boy keeps one hand on the control \textbf{knob} while the adult man leans near the screen and gestures with both hands.
He points toward the TV, then toward the control panel, visually tying the \textbf{console} to the game on the screen.
The boy watches him and then looks back to the television.
The man ’s gestures become more animated : he opens his hands, counts or indicates multiple options with his fingers, and looks between the boy, the controls, and the unseen person in front.
The shop setting remains busy but orderly, with rows of televisions behind them and warm overhead lighting.
The boy continues playing, turning the \textbf{knob} on the right side of the control area.
The adult man smiles broadly for a moment, then leans down and reaches toward the controls himself, as if eager to join in or \textbf{demonstrate}.
He and the boy both face the TV, their bodies angled toward the game.
The man then turns his head to the side, looking off toward the shelves or someone nearby, while the boy keeps his hand on the controller.
The commercial ends with a clean product display.
A large CRT television sits on a \textbf{plain} surface with the Atari Super Pong \textbf{console} positioned directly in front of it.
The \textbf{console} has two prominent round control \textbf{knobs}, one on each side, and a \textbf{central} panel with switches or markings.
A cord runs from the \textbf{unit} toward the right.
On the TV screen is a simple Pong-style game : a vertical dotted center line, small paddles on the left and right, and a dark playing field with a faint blue-green glow.
Above the television, large bold white text reads, “ IT ’S A REAL ATARI. ”

% matched lemmas: adjust, boxy, central, console, demonstrate, dial, feature, knob, plain, rectangular, unit
\end{textsample}
