\begin{textsample}{POS Dim 3 – 1960 – Score 17.00 – 1960/tv\_com\_1960\_105.txt}  \label{ex:f3_pos_026}
The commercial opens in black and white, first with a very dark image and then with fast, slightly blurred glimpses of children outdoors.
A young girl with a short dark bob, wearing a light top and a patterned or plaid skirt, appears in a backyard near a fence and the roofline of a house.
She lifts one arm high and dances energetically, her body bending and turning as if moving to a beat.
A young boy in shorts and a patterned shirt runs and dances across a patio area, arms bent and lifted, passing outdoor furniture.
The backyard has a domestic feel, with a wooden fence, garden plants, a watering can, and a picnic table visible at different moments.
The children move around the yard with \textbf{records}.
One boy runs forward holding a small \textbf{vinyl} \textbf{record} up in one hand, the round disc clearly visible against the sky.
Another child near the house carries something flat, likely a \textbf{record} or sleeve, while moving toward the patio.
The scene settles around a picnic table in the backyard.
Several children gather there, including a blond boy in a striped shirt, the dark-haired girl in the plaid skirt, and at least one younger boy.
They place a \textbf{boxy} portable \textbf{phonograph} on the table.
It has a \textbf{hinged} lid, a \textbf{rectangular} body, a flat \textbf{turntable} area inside, and a small round control or \textbf{knob} on the front.
A closer view shows the \textbf{phonograph} open on the table with a small black 45 rpm \textbf{record} lying on the \textbf{turntable}.
The blond boy in the striped shirt stands nearest it and handles the machine while the other children crowd around to watch.
A hand lifts the lid, revealing the \textbf{record} inside ; then the lid is lowered over the \textbf{record}.
The design is shown as simple and enclosed : instead of a visible tone arm being placed on the \textbf{record}, the child just closes the lid.
The lid has a broad, sloped top with an opening or window-like recess, and the front of the machine has a prominent pale round \textbf{knob}.
The children ’s hands rest on the table edges as they watch the \textbf{record} player work.
The group reacts with interest.
The dark-haired girl in the plaid skirt stands close beside the blond boy, leaning in.
Another boy at the left holds a \textbf{record}, and a child across the table watches over the lid.
The \textbf{phonograph} is opened again to show the black \textbf{record} with its light center label, then closed once more, visually emphasizing the “ close and play ” action.
A close view of the product shows the \textbf{record} spinning area, the \textbf{hinged} lid moving down, and a small control on the right side.
The hand presses or \textbf{adjusts} the front control while the lid is shut.
The setting changes to a bedroom.
Two young girls are on a bed with a \textbf{plain} wall behind them and a framed picture above.
One girl, with long dark hair, sits near the headboard ; the other, with a short dark bob and a plaid dress, sits on the bed facing the \textbf{phonograph}.
The \textbf{boxy} \textbf{record} player rests between them on the bedspread.
The younger girl leans forward over the machine, smiling and using it herself, while the older girl watches from the side.
A close view of the younger girl ’s face shows her smiling broadly, looking down toward the \textbf{phonograph} with delight.
The product is then shown alone again, open with a black 45 \textbf{record} on the \textbf{turntable}.
A hand \textbf{demonstrates} the lid : it swings down over the \textbf{record}, covering it almost completely.
The same hand opens the lid again, revealing the \textbf{record}, then lowers it once more.
The motion is slow and clear, making the \textbf{mechanism} easy to understand visually : open lid, \textbf{record} visible ; closed lid, \textbf{record} covered and the front control accessible.
The \textbf{phonograph} sits on a tabletop near patterned curtains and a modern-looking lamp.
Next, several children walk through a living room carrying the closed \textbf{phonograph}.
A girl in a plaid jumper or skirt leads, holding the \textbf{rectangular} player in both arms at chest height.
Behind her, a blond boy in a striped shirt and other children follow in a line.
The room has a wide fireplace or dark wall \textbf{feature} in the background, curtains on the left, and \textbf{upholstered} furniture on the right.
The children appear to be taking the portable \textbf{phonograph} from one room to another.
The scene changes again to a children ’s party.
Four children sit or stand around a low table in front of a sofa, wearing paper party hats and surrounded by party decorations, balloons, streamers, and several loose 45 rpm \textbf{records} spread across the tabletop.
The Close ’ N Play \textbf{phonograph} sits in the center with its lid closed.
One child blows a party \textbf{horn} or noisemaker, stretching a long paper tube outward.
Another child holds a balloon to their mouth.
The girl with the short bob and dark dress stands near the \textbf{phonograph}, smiling and moving happily.
Close views show children ’s faces as they blow party \textbf{horns}, cheeks puffed, eyes focused forward.
The \textbf{phonograph} remains \textbf{central} on the table, with \textbf{records} laid out around it as party props.
A product package appears against a \textbf{plain} background.
The box shows a picture of the \textbf{phonograph} and children using it.
Large readable text on the package says “ Kenner CLOSE ’ N PLAY \textbf{PHONOGRAPH}, ” with smaller wording including “ CLOSE LID \textbf{RECORD} PLAYS. ” Bold text at the bottom of the screen reads “ BATTERIES NOT INCLUDED. ” A visible watermark, “ STARRPHOTO@BARFOOT.COM, ” appears along the bottom during this later portion.
The commercial ends with simple line animation on a white background.
A cartoon bird with a long neck, round body, big eyes, little feather tufts, and a large dark beak stands at the right.
The bird grabs or pulls at a black circular shape, which grows into a huge dark \textbf{circle} that nearly fills the screen before popping away into scribbly lettering.
The lettering resolves into a bold Kenner sign : “ IT ’S Kenner IT ’S FUN! ” with “ Kenner ” written in a script style and the other words in thick block letters.
The cartoon bird stands beside the slogan.
After a brief dark transition, a different animated-looking scene appears : a huge blocky robot or giant figure towers in a futuristic setting with curved walls and a tall tower-like structure, while a small boy stands at its feet.
Another image shows the boy at a doorway or control panel marked “ TOOLS, ” reaching toward a round handle or button on a large curved surface.

% matched lemmas: adjust, boxy, central, circle, demonstrate, feature, hinge, horn, knob, mechanism, phonograph, plain, record, rectangular, turntable, upholster, vinyl
\end{textsample}
