\begin{textsample}{POS Dim 3 – 1960 – Score 9.00 – 1960/tv\_com\_1960\_2.txt}  \label{ex:f3_pos_045}
The commercial is presented in a sepia/brown-toned, high-contrast style with black side borders.
A white “ Nostalgic X’er ” watermark appears at the lower right throughout the sampled frames.
At the beginning, the image is an \textbf{extreme} close-up of a mechanical object, likely part of a typewriter mechanism.
The view is abstract and partially blurred, with shiny metal surfaces and cylindrical components seen at an angle.
The next shots move into close macro views of a typewriter ’s internal parts.
A rounded, metallic, golf-ball-like typing \textbf{element} appears, covered with raised \textbf{letters} and symbols.
The camera shows it from different angles, very close up, emphasizing the engraved or raised characters on its surface.
The \textbf{lighting} creates bright reflections on the \textbf{polished} metal.
The sequence then \textbf{becomes} more kinetic and blurred.
The spherical typing \textbf{element} and surrounding mechanical arms or linkages appear to move rapidly.
Several frames show streaked motion and partial glimpses of \textbf{letters}, curved metal rings, and small mechanical parts.
The action is \textbf{difficult} to resolve in detail because of motion blur, but the visuals suggest the typing mechanism rotating, shifting, or striking.
Some shots show fragments of characters on the ball, including partial letterforms, but most are not clearly readable.
Later, the commercial cuts to a clearer medium close-up of a typewriter mechanism from the side.
The spherical typing \textbf{element} is visible next to other components inside the machine.
This is followed by a display-like shot of multiple spherical typing \textbf{elements} grouped together on a light surface.
They are shiny and patterned with raised characters, shown as interchangeable-looking metal balls.
The commercial then returns to a close-up of the typing area.
A dark central shape and surrounding mechanical parts appear in front of the type ball, with the shot still highly \textbf{stylized} and partially blurred.
Near the end, the frame shows a sheet of paper in a typewriter with typed text visible.
The text is only partly legible.
The top line includes something like “ The ‘ Selectric ’ Typewri …, ” and another line includes “ system and dual stroke …, ” while a lower line includes fragments such as “...
Waste ) in correcti … ”.
The typing \textbf{element} and typewriter parts are visible below the paper.
The final shots reveal the full typewriter on a dark background.
A \textbf{pair} of hands types on the keyboard.
A sheet of paper is inserted upright in the carriage area, and a cylindrical knob is visible on the right side.
The camera remains at a three-quarter angle, showing the compact body of the typewriter, the keyboard, the paper, and the typist ’s hands continuing to press keys.

% matched lemmas: become, difficult, element, extreme, letter, lighting, pair, polished, stylize
\end{textsample}
