\begin{textsample}{POS Dim 3 – 1950 – Score 16.00 – 1950/tv\_com\_1950\_50.txt}  \label{ex:f3_pos_006}
The commercial begins in black and white with two adults pressed close together against a \textbf{plain} studio background.
A clean-cut man in a suit leans toward a light-haired woman as if sharing a secret.
He holds a sheet of paper up beside his face, partly shielding his mouth.
The woman, dressed in a light jacket or suit with a pearl necklace, looks forward with a composed but alert expression, then turns her eyes toward him.
As he continues holding the paper like a privacy screen, she reacts with widening eyes and a more animated expression, suggesting surprise or excitement.
The woman suddenly moves off to the right, clutching a large textured handbag or purse.
She rushes toward another man, who stands in a suit, tie, dark brimmed hat, and thick-rimmed glasses.
She lifts the handbag up beside her mouth, using it almost like a megaphone or shield, and leans very close to his ear as if whispering the secret to him.
He faces forward stiffly, wearing a serious, slightly startled expression, while she looks up at him from the side.
After a moment, he turns away from her and becomes the \textbf{central} figure.
The bespectacled man in the hat stands in front of a dark doorway or sign area where the faint words “ RCA Victor ” are visible behind him.
He faces the viewer in his suit, striped tie, \textbf{pocket} square, and glasses, then turns to his right and steps into a showroom-like display area.
The space is staged like a neat retail or studio display, with a smooth wall in the background and television sets arranged on low platforms.
Large white lettering on the wall reads “ SPRING ” on the left, separated by a vertical line from “ trade-in special ” on the right.
Several RCA Victor television sets are displayed across the room.
On the left, a table \textbf{model} sits on a low surface near a decorative urn or lamp.
A dark hanging lamp is suspended above.
In the center is another compact table television with rounded screen corners, and below it a small flower \textbf{arrangement} or decorative plant sits on the floor.
On the right stands a larger television set in a taller cabinet, beside a small white animal figurine that resembles a deer or dog.
The man walks across the foreground with his back to the viewer, gesturing toward the display as the “ SPRING trade-in special ” lettering remains prominent above the products.
The focus moves to a single table \textbf{model} television placed on a tabletop.
It has a \textbf{boxy} cabinet, a large rounded \textbf{rectangular} screen, and a light-colored front panel framed by darker sides.
A decorative urn remains to the left of it.
Large bold white \textbf{price} text appears over the television screen : “ \$199.95. ” Smaller script-style text reads “ nationally advertised \textbf{price}, ” and large lower text reads “ less big trade-in, ” indicating a trade-in deduction from that advertised \textbf{price}.
Another table television is then shown alone, angled slightly so its side depth is visible.
It has a rounded screen set into a light front panel, with the RCA Victor name faintly visible near the lower edge.
Bold text overlays it : “ \$229.95, ” again with “ nationally advertised \textbf{price} ” across the middle and “ less big trade-in ” across the bottom.
The same \textbf{price} and trade-in wording then appears over a larger deluxe console-style television in a darker cabinet raised on short legs, emphasizing that the trade-in offer applies to the larger \textbf{model} as well.
The man in the hat reappears in the \textbf{showroom}, now near the front left of the display.
Behind him, the “ SPRING trade-in special ” wall text and the televisions are visible again.
He smiles and gestures with his hand, then lifts or tips his dark hat in an energetic motion.
He ducks down and moves out of the way, leaving the product display unobstructed : three television sets arranged across the room, the hanging lamp, the decorative urn, the small \textbf{central} flowers, and the white animal figurine on the right.
The final image is a brand card.
On a \textbf{plain} dark background, large text reads “ RCA \textbf{VICTOR}, ” with additional lines above and below : “ FIRST IN BLACK AND WHITE TELEVISION ” and “ FIRST IN COMPATIBLE COLOR TELEVISION. ” At the lower left is an RCA \textbf{circle} logo.
To the right, the RCA Victor dog mascot sits beside an old-fashioned \textbf{gramophone} \textbf{horn}, listening toward it.
Beneath the dog and \textbf{gramophone} appears the phrase “ HIS \textbf{MASTER} ’S \textbf{VOICE}. ”

% matched lemmas: arrangement, boxy, central, circle, gramophone, horn, master, model, plain, pocket, price, rectangular, showroom, victor, voice
\end{textsample}
