\begin{textsample}{POS Dim 3 – 2000 – Score 5.00 – 2000/tv\_com\_2000\_64.txt}  \label{ex:f3_pos_065}
An adult man with light skin, short dark hair, and a clean-shaven face appears in a staged indoor setting, seated or standing in front of a pale beige \textbf{upholstered} surface.
He wears a bright red button-up shirt with a black \textbf{rectangular} “ RESOLVE ” patch on the chest, giving him the look of a product \textbf{demonstrator}.
He holds a bottle of Resolve Dual Power carpet cleaner upright in both hands, angled so the label faces forward.
The bottle has a white cap, a red-orange upper label area, and a white lower body with blue graphics and the word “ RESOLVE ” prominently across the front.
He looks to the side and then forward while presenting the product.
The scene moves to a light gray carpet sample laid over a patterned rug or floor.
Only a person ’s lower leg and black shoe are visible near the edge.
A hand tips a dark bottle over the carpet, pouring a thin stream of dark red-brown liquid onto the pale surface.
The liquid forms a long, uneven stain with splattered spots around it.
Another hand then brings in a small white container with a narrow spout and drips more dark liquid onto a separate area, creating additional brown stains on the carpet.
The carpet now has several visible marks : a reddish streak, scattered dark droplets, and separate brown blotches.
The Resolve bottle is shown close up in a hand.
The front label is clearly visible, with “ RESOLVE ” across the top and “ DUAL POWER ” on the lower portion.
A finger points to the lower label area, drawing attention to the product ’s dual-power \textbf{feature}.
The bottle is then turned upside down, and a clear liquid streams from its white dispensing top.
Back on the stained gray carpet, the upside-down bottle pours cleaner over and around the dark marks.
White foamy liquid spreads across the carpet, covering the reddish and brown stains in irregular patches.
As more cleaner is applied, the stained areas become increasingly obscured by foam and wetness.
The carpet surface looks mottled with white cleaner, pale damp areas, and \textbf{fading} remnants of the stains.
Small on-screen text near the bottom reads, “ Time elapsed 5 minutes. ” A hand presses a folded white cloth firmly onto the treated carpet and wipes or blots along the edge of the carpet sample.
The cloth moves across the damp area, then lifts away.
The previously stained \textbf{section} now appears pale and clean, with only faint damp patches or foam residue visible rather than the earlier red and brown marks.
A black shoe remains visible near the top edge, emphasizing the carpet as a floor demonstration.
The commercial ends with a product display : the Resolve Dual Power bottle stands on the left against a textured gray background.
To the right, large red text reads, “ Better than the other leading brands. ” Beneath it is the bold “ RESOLVE ” logo in white letters with a dark outline.

% matched lemmas: demonstrator, fade, feature, rectangular, section, upholster
\end{textsample}
