\begin{textsample}{POS Dim 3 – 1950 – Score 19.00 – 1950/tv\_com\_1950\_117.txt}  \label{ex:f3_pos_003}
In black and white, the commercial begins in darkness with the front of a large, glossy automobile approaching or standing in a dim outdoor setting.
Its two round headlights shine brightly on either side of a tall, formal grille, with reflections glinting across the hood and chrome trim.
The car has the dignified look of a limousine.
A white-gloved hand in a dark sleeve reaches for the door handle, and the person opening it wears a dark uniform with decorative cords or braid, suggesting a chauffeur or formal attendant.
From beside the car, the attendant removes a \textbf{rectangular}, polished-looking presentation box.
The box has a dark vertical panel on the front with a shield-like crest near the top, making it look like a ceremonial gift.
The setting shifts to an elegant interior that resembles a palace or grand residence.
A large chandelier hangs at the left, with candle-shaped lights and dangling glass ornaments.
A suit of armor stands against the wall near a column, and the floor is laid out in large square tiles.
A man in a light-colored formal uniform carries the presentation box through the hall.
He approaches a richly furnished study or office where an older, light-haired man in a dark suit sits at a desk in a high-backed ornate chair.
A table lamp glows behind the desk, and papers and desk objects lie in front of him.
The uniformed man sets the gift box on the desk, facing the seated man, who leans forward with interest.
The box is opened in front of him.
Its top and front panels lift away, and inside is a portable \textbf{radio}.
The uniformed man holds the open packaging steady while the seated man rises slightly from his chair and reaches toward the \textbf{radio}.
The product is a Zenith Trans-Oceanic \textbf{radio}, a compact, suitcase-like \textbf{rectangular} set with a carrying handle on top.
It has a dark front, shiny metal trim, a row of small tuning marks across the upper front, and a large round control \textbf{knob}.
Hands lift the \textbf{radio} out of the box and place it on the desk for a closer look.
A close view shows the \textbf{radio} centered on the desk.
A hand rests on the handle at the top while another hand opens the front cover.
As the cover drops down, it reveals the \textbf{radio} ’s lighter \textbf{speaker} grille panel, \textbf{horizontal} tuning scales across the upper \textbf{section}, several small \textbf{knobs} on the left, and a large circular tuning \textbf{dial} on the lower right.
The hands \textbf{adjust} the controls, turning a \textbf{knob} and moving over the tuning area, \textbf{demonstrating} how the portable \textbf{radio} opens and \textbf{operates}.
The scene briefly returns to an overhead view of the desk, where the older man sits with the \textbf{radio} in front of him.
The \textbf{radio} is then shown more prominently on its own, open and gleaming, with the Zenith name visible on the upper right of the front panel.
Its handle stands upright, and the open front cover forms a base beneath it.
The commercial then introduces smaller Zenith \textbf{radios}.
A hand places a tiny pocket-sized transistor \textbf{radio} on a checkerboard or chessboard surface.
The little \textbf{radio} stands upright among blurred chess pieces in the background.
It has vertical grille bars on the front, a small display area near the top, and the word “ ZENITH ” clearly printed across its face.
After the hand \textbf{withdraws}, the small \textbf{radio} remains centered, emphasizing how compact it is.
Several Zenith \textbf{radios} are displayed together on a shelf or tabletop.
They vary in \textbf{size} and shape : some are \textbf{rectangular} table \textbf{models} with broad \textbf{speaker} grilles, some have circular \textbf{dials}, and others are slim portable sets.
White on-screen text appears near the bottom reading “ FM/AM \textbf{RADIOS}. ” The display changes to another group of larger household sets, including table \textbf{radios} and \textbf{clock} \textbf{radios} with \textbf{clock} faces and \textbf{rectangular} cabinets.
The bottom text changes to “ TABLE AND \textbf{CLOCK} \textbf{RADIOS}. ” Another \textbf{arrangement} follows, showing portable \textbf{radios} of different \textbf{sizes}, including small transistor sets with wrist straps, medium portables with handles, and a larger portable with an extended antenna.
The bottom text reads “ SOLID STATE PORTABLES. ” The display grows into a broad collection of many Zenith \textbf{radios} arranged in rows and at different heights, filling the scene from foreground to background.
There are \textbf{boxy} \textbf{radios} with large round \textbf{dials}, slim \textbf{rectangular} \textbf{models}, handle-top portables, and \textbf{clock} \textbf{radios}, all presented together like a \textbf{showroom} lineup.
Over this array, a large stylized “ ZENITH ” logo appears in bold white lettering with a lightning-like slash through the initial Z.
Beneath it, cursive-style text \textbf{fades} in : “ The quality goes in before the name goes on. ” The final image settles on a smaller grouping of Zenith \textbf{radios} : a large Trans-Oceanic-style portable behind, a tiny \textbf{pocket} \textbf{radio} in front, and another portable \textbf{radio} at the right with a circular \textbf{dial} and raised antenna.
The big Zenith logo remains above them, with the slogan underneath.
An ornate picture-frame border appears around the whole display, as if the \textbf{radios} and logo are being presented as a framed gift or treasured object.

% matched lemmas: adjust, arrangement, boxy, clock, demonstrate, dial, fade, horizontal, knob, model, operate, pocket, radio, rectangular, section, showroom, size, speaker, withdraw
\end{textsample}
