\begin{textsample}{POS Dim 3 – 1990 – Score 5.00 – 1990/tv\_com\_1990\_107.txt}  \label{ex:f3_pos_058}
A red brick factory wall fills the screen, with a large rounded sign reading “ Nice’n Soft ” in pale letters outlined in dark blue.
Below the sign is a wide industrial window.
Through the glass, a busy factory floor is visible, with white-clad workers moving around large machinery.
As the view settles lower on the window, the interior becomes clearer : adults in white lab coats or coveralls, some wearing bright blue caps, work among steel beams, pipes, stairs, hanging lamps, and oversized rolls of white paper.
Inside, the factory has a clean but exaggerated industrial look, with blue metal supports, high windows, and mist or steam drifting around the machines.
A huge roll of bathroom tissue sits on a spindle in the foreground, nearly as tall as the workers.
Several workers in white uniforms gather around \textbf{consoles} and equipment, while others carry materials or push carts.
The scene is arranged like a busy production line, with people monitoring \textbf{dials}, handling paper, and moving from station to station.
At a large pale-blue machine labeled “ FLUFFING, ” a heavyset adult worker in white coveralls and a blue cap stands beside panels with round gauges and small windows.
White vapor pours from openings near the lower left side of the machine.
The worker holds up a small white wad, as if inspecting or presenting something soft, then brings it toward his face.
Other workers are partly visible around and behind the machine, reinforcing the sense of a bustling, comic factory operation.
A darker, older-looking machine appears next, surrounded by haze.
It has large metal wheels and rollers, with industrial lamps hanging above and stacked paper or rolls in the background.
The equipment looks more mechanical and old-fashioned than the earlier blue machine, with belts, wheels, and a slightly grimy, steamy atmosphere.
The action returns to the brighter production area.
A worker in white coveralls and a blue cap walks across the foreground carrying a long dark bar or pipe over one shoulder.
Behind him, several adults in white lab coats stand at a waist-high control table, watching and working.
To the left is a giant white paper roll, and to the right is a large pale-blue machine face covered with round gauges.
The workers at the table appear focused and orderly, like inspectors or technicians.
A \textbf{section} labeled “ PERFUMING ” appears, with the word printed in bold black letters on a white sign above a row of colored round containers or bulbs.
Beneath them are glass laboratory flasks and tubes, suggesting a perfume or scent station.
The display looks more like a laboratory bench than a normal factory machine, with liquids and glassware arranged in front.
Another area of the factory shows a playful testing setup.
On the left, a worker in a white coat writes on a clipboard beside large decorative gears and a tall vertical gauge with numbers running upward.
A red pointer sticks out from the gauge.
On the right, a sign over a station reads “ SOFTNESS CHECK-OUT. ” Several lab-coated adults stand together there, some holding blue clipboards and writing.
A large white roll or column of paper is positioned near them.
In the foreground, a worker in white coveralls and a blue cap pushes a low cart or table loaded with flat white material across the scene, passing in front of the testing area while the inspectors continue taking notes.
The softness-testing group is then seen more closely.
Four adults in white lab coats cluster around a vertical test column with alternating white \textbf{sections} and reddish-orange rounded \textbf{sections}.
Two male-presenting inspectors on the left bend over clipboards, writing intently.
A woman with short red hair stands near the center-right, also holding a blue clipboard, while a taller male-presenting inspector on the far right reads or writes on his own blue clipboard.
Their attention is directed toward the column and their notes, as if carefully measuring or judging the softness of the paper.
The factory mood shifts to a dimmer, older corner with a bulky, antique-looking machine covered in dust and cobwebs.
A heavyset worker in white coveralls and a blue cap leans into the machine, bracing himself as he \textbf{operates} it.
Large dark wheels and belts surround him.
Loose strips of paper and debris are scattered around the base.
Steam or dust bursts from the machinery, filling the air with white clouds.
The worker ’s face is partly obscured by the machine and haze ; he appears to be wrestling with the equipment rather than smoothly running it.
In a closer view of the old \textbf{mechanism}, white vapor blasts around small metal parts and paper fragments.
The machine looks rough and unreliable, with cobwebs stretched across its upper areas and scraps caught around the openings.
The worker appears behind the wheels and pipes, lifting one hand as if \textbf{adjusting} or pulling something.
His face, seen through the machinery, is strained and intent as he looks upward and works the equipment.
A wider view shows the old machine sitting alone in a shadowy part of the factory, under hanging lamps and high windows.
The worker stands near it with a bundle or wad of white material, while the surrounding floor and machinery look dusty and worn compared with the brighter, cleaner production line shown earlier.
The commercial ends with the packaged product displayed prominently in front of a softly lit factory-machine background.
The package contains bathroom tissue rolls wrapped in a blue label with a pink wave near the top and large white bubble letters reading “ Nice’n Soft. ” Small text on the lower left of the package reads “ Unscented Bathroom Tissue. ” Along the bottom of the screen, a slogan appears in white decorative lettering : “ It ’s Nothing But Soft. ” The package remains centered and still, with the industrial background blurred behind it, keeping attention on the brand name and the bathroom tissue rolls.

% matched lemmas: adjust, console, dial, mechanism, operate, section
\end{textsample}
