\begin{textsample}{POS Dim 3 – 1950 – Score 13.00 – 1950/tv\_com\_1950\_3.txt}  \label{ex:f3_pos_011}
The commercial opens in a carefully arranged, black-and-white home interior with no people present.
A bright, smooth floor fills much of the foreground, laid out in large irregular geometric \textbf{sections} with dark dividing lines.
To the left is a striped sofa with rounded arms, pillows, a small side table, and a shaded lamp.
Plants stand near a \textbf{central} wall.
Through a large rounded archway in the background is a dining area with a round table, several chairs, striped wall treatment, potted plants, and a large globe-shaped hanging light.
The emphasis remains on the clean, light-coloured floor stretching between the living and dining spaces.
The setting changes to another room, like a home office or den.
A glossy patterned floor dominates the lower half of the scene, reflecting the table and chair legs.
The floor has a bold star-like or crisscross design made from contrasting light and dark strips.
Against the back wall are built-in shelves with books and decorative objects.
In front of them is a small writing table or desk with thin metal legs, a chair, papers or accessories on top, and a large old-fashioned telephone or office machine sitting to one side.
A small round side table and an \textbf{upholstered} chair appear to the right as the room widens into view.
Another home interior appears, this time a living room with a fireplace.
A plaid sofa sits on the left, an \textbf{upholstered} chair on the right, and a small glass-topped table stands between them.
The fireplace opening is dark, with small decorative objects on the hearth and mantel.
The floor is highly polished, with large square panels bordered by dark strips, forming a grid.
Reflections from the furniture and light shimmer on the surface, again drawing attention to the floor ’s shine and pattern.
The scene then changes to a bright kitchen or breakfast nook.
White cabinets line the left side, a door with frosted or patterned glass is on the right, and a small writing desk or counter with a white chair sits in the centre back.
A vase of flowers rests on the desk, with a leafy potted plant beside it.
The floor is a checkerboard of light and dark square tiles.
Bold white capital letters appear across the lower part of the screen : “ KENTILE EASY CLEAN \textbf{VINYL}. ” The view settles lower on the checkerboard floor, and more text appears near the bottom : “ \$33.95 FOR 8X10 AREA. ” The \textbf{price} remains over the floor while the chair, plant, desk, and glass door stay in the background.
A woman is then shown kneeling on the floor during installation.
She appears to be a young adult, with curled, mid-length hair, wearing a practical button-front top with rolled sleeves and light trousers or work clothes.
Beside her is an open can of adhesive.
She uses a brush to spread dark adhesive over an existing floor surface, working close to the base of a cabinet or wall.
Dark marbled \textbf{vinyl} tiles are already being placed in a row beside her.
She dips the brush into the can, then smooths adhesive onto the floor in broad strokes.
In a close view, the woman smiles as she holds a dark marbled tile in her hands and cuts it with scissors.
The tile bends slightly as she trims it, showing it is thin enough to cut by hand.
The scissors make a neat cut through the \textbf{vinyl}, and a narrow piece separates from the larger square.
She then returns to the floor and presses tile pieces into place along the edge of a cabinet or wall, using her hands to smooth and align them.
A \textbf{rectangular} tile is fitted into a corner area, and she \textbf{adjusts} it carefully so it sits flush with the surrounding tiles.
A graphic demonstration follows : a stack or layered \textbf{arrangement} of dark marbled \textbf{vinyl} squares is shown against a \textbf{plain} background.
Over it, the word “ \textbf{VINYL} ” repeats vertically in large white letters across the screen, visually stressing that the material is \textbf{vinyl} throughout.
The layered tiles \textbf{overlap} like thin sheets, with their marbled pattern visible on the exposed surfaces.
The kitchen checkerboard floor returns with a dark greasy spill spread across one light square tile.
At the bottom of the screen, bold white text reads “ GREASEPROOF. ” A mop or squeegee enters from the right and pushes through the spill.
As it passes over the tile, it clears away the dark mess, leaving the light square visibly clean behind it.
The tool continues across the tile, gathering the spill into a smaller area and \textbf{demonstrating} that the surface wipes clean.
The woman now stands in the kitchen wearing a neat \textbf{mid-century} dress with a fitted waist and full skirt, dark low heels, and styled hair.
She mops the checkerboard floor near the white chair and flower-filled desk.
The floor looks clean and glossy.
She finishes mopping, lifts the mop upright, and steps toward the glass door on the right, carrying the mop with an easy, tidy posture.
She exits out of view, leaving the spotless checkerboard kitchen visible.
The kitchen \textbf{fades} into a close view of an open telephone directory or classified pages lying on a surface, with a pencil across the page and a rotary telephone behind it.
Listings and advertisements are visible ; one \textbf{section} includes flooring-related text and “ KENTILE ” in an ad.
Over the open directory, a boxed logo appears in large block letters : “ KENTILE FLOORS. ” The logo sits centred over the \textbf{printed} pages.
Finally, the commercial returns to a close view of the checkerboard \textbf{vinyl} floor.
The dark tiles have a marbled streaked texture, and the light tiles are \textbf{plain} and bright.
Across the centre, in a flowing script, the words “ Easy Clean \textbf{Vinyl} ” appear, ending on the product name over the clean tiled surface.

% matched lemmas: adjust, arrangement, central, demonstrate, fade, mid-century, overlap, plain, price, printed, rectangular, section, upholster, vinyl
\end{textsample}
