\begin{textsample}{POS Dim 3 – 2010 – Score 9.00 – 2010/tv\_com\_2010\_25.txt}  \label{ex:f3_pos_079}
The commercial begins on a completely black screen.
After several seconds, the image fades into a very dark, industrial-looking interior, resembling a large warehouse or hangar.
The space is mostly in \textbf{shadow}.
Overhead rectangular skylights or ceiling lights are faintly visible, forming a grid-like pattern near the top center.
The side walls have tall panel-like structures or windows, but details are obscured by low \textbf{lighting}.
The floor appears \textbf{glossy} or \textbf{reflective}, though most of it remains dark.
The next frame reveals a large \textbf{illuminated} “ verizon ” wordmark centered in the same industrial space.
The \textbf{letters} are bright white, set in lowercase, with a red checkmark to the right of the word.
The \textbf{glossy} floor reflects the white \textbf{letters} and the red checkmark, creating a mirror-like \textbf{effect} below the logo.
The background remains a \textbf{dim} warehouse interior with overhead light panels and dark structural \textbf{elements}.
The scene then returns to a darker view of the same interior without the visible logo.
The space is again mostly \textbf{shadowed}, with only the ceiling lights and faint outlines of the walls and central structure visible.
Later, the “ verizon ” logo appears again in the same setting, now large and centered.
The white lettering and red checkmark stand out strongly against the dark industrial background.
The \textbf{reflective} floor again shows elongated reflections of the logo.
The commercial ends by cutting back to black, with the final sampled frames showing a blank black screen.

% matched lemmas: dim, effect, element, glossy, illuminate, letter, lighting, reflective, shadow
\end{textsample}
