\begin{textsample}{POS Dim 3 – 1990 – Score 5.00 – 1990/tv\_com\_1990\_52.txt}  \label{ex:f3_pos_056}
A \textbf{plain} light background appears with the words “ Constructive Behavior. ” centered in dark blue type.
The title then gives way to a warmly lit indoor play area, seen through a doorway.
In the room, a young blond child with light skin, wearing a light blue shirt and a toy tool belt around the waist, stands at a child-sized workbench.
Sunlight falls in bright patches across the scene.
On the right side of the bench is a bright red Fisher-Price workshop \textbf{unit} with a pegboard-like back, yellow side pieces, and attached pretend tools.
The child faces the bench, looking down with concentration while handling a small piece on the tabletop.
The view moves closer to the child ’s face and hands as the child reaches up toward the red workshop.
The child ’s expression is serious and focused, eyes following the toy \textbf{mechanism}.
A close view of the workshop ’s drill attachment shows a yellow cylinder labeled “ DRILL, ” with \textbf{printed} measuring numbers on it.
A yellow drill bit points downward toward a flat yellow board on the work surface.
The child ’s small hand turns a gray side \textbf{knob}, and the drill bit lowers into the board ’s hole area, \textbf{demonstrating} the pretend drilling action.
The red support structure and the yellow work surface fill most of the view, with the child ’s hand working the control from the side.
The scene widens again to show the child beside the full red Fisher-Price workshop.
White text along the bottom reads, “ TOOL BELT NOT INCLUDED. ” The child stands with one hand near the belt and lifts a yellow accessory up beside the face, as if pretending to use or inspect it.
The red pegboard \textbf{unit} behind the child displays the Fisher-Price name at the top, with small toy tools and parts arranged across it.
A close view then focuses on the tabletop saw area of the workshop.
A gray work surface has ruler markings and a small circular saw blade rising through a slot, with the word “ SAW ” visible on the blade guard or label.
The child ’s hand pushes a long yellow plastic board across the surface toward and past the blade, \textbf{demonstrating} a pretend sawing motion.
The board slides steadily from right to left, while another yellow block sits farther back on the bench.
Near the end, the child ’s face fills the scene in warm light, looking downward at a small yellow plastic piece held in both hands.
Large white “ Fisher-Price ” text appears across the lower part of the screen.
The child brings the piece closer, studies it, then begins to smile subtly, still focused on the toy.
The final images hold on the child ’s pleased expression and hands working with the yellow piece, with the Fisher-Price name remaining visible at the bottom.

% matched lemmas: demonstrate, knob, mechanism, plain, printed, unit
\end{textsample}
