\begin{textsample}{POS Dim 3 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_71.txt}  \label{ex:f3_pos_048}
A metallic, futuristic armored figure fills the opening moments.
Only the side of its helmet is visible at first : a smooth gray-silver headpiece with a narrow, black, visor-like eye slit and molded ridges across the forehead.
Tubes or cables run from the back of the helmet and shoulders.
The background is a hazy, artificial sci-fi space washed in pink and red light, with drifting smoke and jagged rock-like shapes.
A small Nintendo logo appears near the lower left in some early views.
The armored figure turns and emerges more fully through the fog.
Its suit is bulky and robotic-looking, with segmented shoulder plates, a chest plate, and \textbf{ribbed} metal-like arms.
It raises one hand near its helmet, then brings the arm forward as if aiming.
The setting remains surreal and staged, with white smoke rolling around the figure ’s body and sharp, gray, craggy forms rising behind it against a bright pink sky.
A blue beam shoots from the figure ’s extended hand or weapon toward the right, cutting across the smoky scene.
The blast clears to reveal a young light-skinned man, likely a teenager or young adult, with thick brown hair.
He wears a light blue denim jacket over a vivid hot-pink or red high-neck shirt.
He holds a gray Nintendo Game Boy in one hand and looks down at it with a surprised, pleased expression, then smiles.
The Game Boy is shown close up : a \textbf{rectangular} off-white handheld with a dark gray screen border, the word “ Nintendo ” appearing at the top of the screen, and the \textbf{printed} text “ Nintendo GAME BOY ” below the display.
The young man continues holding the Game Boy near his chest, looking at it with interest and excitement.
A close view shows a black plug being pushed into a port on the side or bottom edge of the Game Boy, \textbf{demonstrating} an accessory connection.
Another close view shows a small black earbud placed at the side of the armored helmet, with a thin cord running down, visually reinforcing the portable stereo \textbf{feature} mentioned in the transcript.
A hand \textbf{inserts} a gray game \textbf{cartridge} into the top/back slot of the Game Boy.
The \textbf{cartridge} label is colorful and reads “ TETRIS ” in large purple letters.
Fingers press it firmly into place until only the upper part of the Tetris label is visible above the \textbf{cartridge} slot.
The young man now plays the Game Boy with both hands, looking down and smiling.
The armored figure looms nearby in the same pink, smoky fantasy landscape, also holding a Game Boy in both hands as if playing along.
A close view of the Game Boy screen shows Tetris in progress : black-and-white blocks stack in a narrow playfield, with score panels on the right reading “ LEVEL 3, ” “ HIGH 3, ” and “ LINES 25. ” The blocks shift and clear ; later the lines count has dropped to “ 21, ” and a small preview box shows the next Tetris piece.
The young man faces the armored opponent with a confident expression.
A small earbud is visible in his ear, and the Game Boy is raised just below his chin.
The armored figure, still helmeted and expressionless behind the narrow black visor, grips its own Game Boy and appears absorbed in the game.
In a wider view, the two stand across from each other amid the fog and jagged set pieces, each looking down at a handheld \textbf{unit}.
A thin cable trails between them, suggesting the head-to-head link connection.
A close view shows a black connector being plugged into a \textbf{rectangular} port on the side of the Game Boy.
The young man smiles broadly while holding the connected device.
He then lifts one hand and points outward with a playful, triumphant gesture.
A bright blue beam appears from his pointing hand or from the direction of his gesture, streaking across the pink background toward the armored figure.
The armored opponent is struck and becomes outlined in glowing blue, arms spread as if jolted or blasted backward.
The figure rapidly shrinks into a small blue shape in the distance and disappears into a wash of pink-white light and fog.
The commercial ends with a product display.
A Game Boy retail box stands upright beside the handheld \textbf{unit}.
The box has large vertical “ GAME BOY ” text on the left and artwork of the device with colorful light streaks.
In front of it lies a Tetris \textbf{cartridge}, and beside the Game Boy are small earphones and cables.
The final images shift to a bright, colorful Nintendo logo centered against radiating neon streaks in red, pink, blue, green, and yellow, ending in a glowing burst around the logo.

% matched lemmas: cartridge, demonstrate, feature, insert, printed, rectangular, rib, unit
\end{textsample}
