\begin{textsample}{POS Dim 3 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_110.txt}  \label{ex:f3_pos_039}
The commercial begins on a nearly black frame, with little visible detail.
It then cuts to a modern, upscale interior with large glass panels.
A woman in a swimsuit reclines on a white lounge chair, wearing large round sunglasses.
She appears relaxed, lying back with her hands behind her head.
A sculptural object stands to the left, and the setting has a \textbf{polished}, minimalist look.
A dark, close-up profile of a man follows, mostly in \textbf{silhouette}.
The \textbf{lighting} obscures his facial details.
The next shot shows several red Coke cans lined up in a refrigerator or bar area, with the white “ Coke ” \textbf{lettering} clearly visible.
A hand reaches near the cans, and glassware is visible in front.
The scene widens again to show the same spacious room from a distance.
The reclining woman is seen beyond tall window panels, with blue-toned light outside or behind the glass.
A large sculptural form is \textbf{silhouetted} in the foreground.
A man is then shown in a medium close-up, standing indoors near flowers.
He has light-colored hair and wears an open-collar shirt.
He looks upward or across the room.
The woman is shown in close-up : she wears \textbf{reflective} sunglasses, earrings, and a blue/green swimsuit or top.
She touches her lips with her fingers, appearing composed and observant.
A close-up shows a hand opening a red Coke can.
Condensation droplets are visible on the can surface.
The woman then adjusts or lifts her sunglasses slightly, looking forward.
A hand holds a red Coke can near someone ’s mouth ; the person is partly obscured in \textbf{shadow}.
The can fills much of the frame, with the “ Coke ” logo prominent.
The man appears again in close-up, smiling slightly in low light.
The can is then shown being crushed or squeezed, with dark liquid and foam \textbf{bursting} or spilling out from the opened top.
This is followed by a shot of the woman from behind or side-on, seated on the lounge chair with her hair backlit against the blue window light.
The next shot shows a vase of white flowers on a \textbf{polished} surface.
Liquid splashes across or past the surface near the vase.
A small dog with shaggy white and gray fur is then shown on a sofa or cushioned area, wearing a collar with a tag, looking alert.
A wide view of the room shows a grand piano at right, a stool in front of it, and a large open space with decorative objects.
The lounge area and sculpture are visible in the background.
A close-up of sheet music on the piano follows ; a long thin object or stream crosses in front of it, but its exact source is unclear from the sampled frame.
Another close-up shows a hand holding a red Coke can on its side, with the open end visible and drops or liquid coming out.
Glassware is then shown on a bar or tray : a hand places or holds a tall glass near an ice bucket or bowl of ice.
A \textbf{pair} of sunglasses sits among the glassware.
Another shot shows a long dark line or cord-like shape stretching diagonally across a pale wall or ceiling area ; its function is unclear from the frames.
The woman is shown reclining again, head tilted back against the lounge chair, with blue-toned light behind her.
A close-up then shows a glass being filled with dark carbonated liquid.
The liquid foams heavily as it enters the glass.
The woman drinks from the foamy glass.
Her face is in close-up, with the glass at her lips and foam at the top.
The final frame presents a product shot against a dark background : a red Coke can stands beside a tall glass filled with dark cola and a thick pale foam head.
The white “ Coke ” lettering on the can is clearly visible.

% matched lemmas: burst, letter, lighting, pair, polished, reflective, shadow, silhouette
\end{textsample}
