\begin{textsample}{POS Dim 3 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_75.txt}  \label{ex:f3_pos_046}
The commercial begins in darkness, then a soft, misty white studio space appears.
In the center is a cream-colored Apple Macintosh computer : a compact, upright all-in-one machine with a small dark screen at the top, a narrow floppy disk slot below it, a separate low keyboard in front, and a small \textbf{rectangular} mouse off to the right, attached by a thin cord.
The computer is presented alone, cleanly lit, with no people visible.
The Macintosh slowly shifts from an ordinary exterior view into a cutaway, as if the \textbf{casing} has opened to reveal what is inside.
The keyboard and mouse remain nearby while the computer ’s side and back seem to peel away or become transparent.
Inside, the machine becomes a colorful, miniature mechanical landscape.
Curving red, yellow, blue, and black \textbf{wires} loop across the interior like thick vines or roads.
Pale molded plastic parts, round components, brackets, and circuit-board structures fill the space.
The view moves deeper through this interior, passing under and around arched cables and small electronic parts, with green and gold light giving everything a dreamlike, futuristic glow.
The inner workings are shown in close detail.
Thick orange and yellow cables sweep across the foreground, partially blocking and then revealing pale support pieces, dark connectors, and patterned circuit-board walls behind them.
The shapes are not just \textbf{plain} hardware ; they are arranged almost like a tiny city or factory inside the computer, with upright black pieces, rounded housings, slots, and pathways layered at different depths.
The parts remain still, but the movement through them makes the interior feel large and complex.
The view then glides over a flat green circuit board.
Rows of tiny white dots and solder points form neat lines along both sides, while small yellow and orange components sit like markers along a \textbf{central} path.
A large \textbf{rectangular} chip-like piece appears ahead, followed by additional black \textbf{rectangular} components with many evenly spaced metal pins underneath, standing like bridges or gates across the board.
The circuit board surface is marked with fine \textbf{printed} lines and small white labels, though most of the tiny lettering is too indistinct to read.
A round speaker-like part appears near the top of the image : a circular frame with a \textbf{central} cone and curved supports, mounted above the green board.
Around it are small red and gold components and white \textbf{printed} circuit markings.
The circular piece fills more of the view, then dissolves back into a broader look at the board, where many black chips, silver pins, and small upright parts are spread across the surface.
The green board is dense with components, arranged in rows and clusters.
The passage continues between tall, comb-like rows of metal pins and colored \textbf{wires}.
Red, blue, purple, green, and orange cables run lengthwise, framing rows of gold and silver contacts.
The parts are shown in close-up, with the metallic pins forming repeating vertical patterns.
The interior remains abstract and magnified, emphasizing the complexity of the electronics rather than showing a person using them.
Near the end of this internal journey, a pale cylindrical connector or shaft appears, set between rounded plastic housings.
It points toward the right, glowing softly in the warm green-yellow light.
This mechanical detail fills the screen, then the imagery dissolves back out to the complete Macintosh in the white studio setting.
The cream computer, keyboard, and mouse are again visible as a simple desktop setup, with the mouse placed to the right and its cord trailing back toward the machine.
The screen of the Macintosh briefly shows a simple graphic shape, faint and gray, resembling a folded envelope or \textbf{slanted} icon.
The computer then \textbf{fades} away from view, leaving the mouse isolated against the soft white background.
The mouse is cream-colored, rounded \textbf{rectangular}, with a single dark \textbf{rectangular} button on top and three small dark slits near one end.
A light-skinned adult hand enters, gently taking hold of the mouse.
The fingers wrap around it, and then the image cuts closer to a single fingertip poised above the mouse button.
In extreme close view, the fingertip presses the one \textbf{rectangular} button downward.
As the finger rests on the button, the word “ Macintosh ” appears over the image in large white serif lettering, centered on the screen.
The background darkens behind the text until only the clean white “ Macintosh ” name remains on a dark field.

% matched lemmas: casing, central, fade, plain, printed, rectangular, slant, wire
\end{textsample}
