\begin{textsample}{POS Dim 3 – 2000 – Score 4.00 – 2000/tv\_com\_2000\_93.txt}  \label{ex:f3_pos_069}
A brightly coloured macaw perches on a bamboo railing outside a tropical-looking house.
The bird has a vivid red-orange chest, dark blue wings, greenish feathers around the head and back, and a large curved beak.
Behind it are pale shutters, potted plants, palm leaves, blue sky, and a glimpse of ocean, giving the balcony a warm island atmosphere.
A loose white sheet of paper rests beside the bird on the railing, as if the macaw is reading or presenting a letter.
The view widens to show the balcony raised above dense greenery, with bamboo railings and stairs surrounded by palms and tropical plants.
The white paper product then comes to life : a roll of toilet paper appears on the bamboo rail and begins to unroll, its loose end trailing behind like a long ribbon.
It travels through the leafy deck area and onto a wooden walkway, winding between plants as the strip of paper curls and lifts slightly off the boards.
The macaw remains perched on the railing, looking downward with its head tilted, as if watching the roll ’s progress.
The roll continues across sunlit wooden planks.
Close up, the white toilet paper shows a fine, \textbf{ribbed}, wavy texture.
Black \textbf{handwritten-style} words appear along the unrolled strip.
As the roll moves, the visible writing reads in parts : “ I ’m new Cottonelle toilet paper with Aloe and E. ” The product name and “ Aloe and E ” are written directly on the toilet paper, turning the unrolling strip into a moving letter.
The roll keeps gliding over the deck among large green leaves, the paper ribbon trailing behind it.
More handwritten words appear : “ I ’ve got a silky, gentle touch you can actually feel. ” The roll passes close to a person ’s bare toes on the wooden floor.
Only the feet and a bit of pink fabric are visible ; the toenails are painted pink.
The strip of toilet paper slides gently across the tops of the toes, visually \textbf{demonstrating} softness through contact with skin.
The roll itself remains bright white, thick, and cylindrical, with the hollow cardboard center visible.
After the toe demonstration, the roll continues along the planks near broad leaves and small stones.
A small green frog appears beside the unrolled strip, sitting near the words “ nature calls. ” The handwritten message now reads in part, “ So the next time nature calls, ” as the frog rests near the paper in the tropical garden setting.
A close view emphasizes the toilet paper ’s texture, filling the image with the white roll ’s surface.
The wavy, raised-looking lines run vertically along the paper, suggesting softness and cushioning.
The scene then shifts to a polished wooden tabletop or deck surface.
The roll sits near a bowl of fruit in the background, with bananas, grapes, and other colourful fruit visible.
The paper strip stretches across the wood like a letter, with handwritten words reading, “ I ’ll make you cheerier, with a gentle touch … ” An open notebook or writing pad and a black pen lie to the right, reinforcing the idea of a written note.
As the roll advances, more of the message becomes visible : “ with a gentle touch on your posterior. ” A pair of tan woven slippers rests nearby on the wooden surface, adding to the relaxed, natural, spa-like setting.
The roll remains the active object, moving along and revealing the written message on its own paper.
At the end, the product is displayed clearly.
On the left sits a \textbf{plain} white roll of toilet paper with a short strip trailing out across the polished wood.
On the right is a green Cottonelle package with a large white-and-blue “ Cottonelle ” logo and the words “ Aloe \& E ” in lighter lettering near the bottom.
A small aloe graphic appears on the package.
Behind the products is a bamboo lattice with leafy plants and blue sky beyond it, keeping the tropical, natural theme consistent.
The final \textbf{arrangement} presents the loose roll beside the branded Cottonelle Aloe \& E package.

% matched lemmas: arrangement, demonstrate, handwritten-style, plain, rib
\end{textsample}
