\begin{textsample}{POS Dim 3 – 1980 – Score 11.00 – 1980/tv\_com\_1980\_36.txt}  \label{ex:f3_pos_042}
A black audio cassette rests inside a clear plastic cassette \textbf{case} on a \textbf{plain} grey surface.
The cassette label includes “ SONY ” and “ UCX-S 90. ” A hand enters from the left, steadies the \textbf{case}, and opens the transparent lid.
The cassette is slid downward and lifted out, leaving the \textbf{hinged} plastic \textbf{case} empty and open, with its two small internal pegs visible against the grey background.
The empty \textbf{case} remains centered.
Instead of simply staying empty, it begins to be filled with electronics.
A hand places a pale green circuit board into the upper right portion of the \textbf{case}, its tiny black chips, silver contacts, and \textbf{printed} pathways visible.
A smaller green circuit board is set into the lower left.
Another compact mechanical part is brought in by both hands and fitted over the boards ; it has small metal brackets and dark components, like the inner workings of a tape player.
The hands press the pieces into place carefully, as if assembling a miniature device inside the cassette \textbf{case}.
The view shifts closer to a silver metal \textbf{mechanism} with two large circular reel areas and small black spindles.
A hand slides another small green circuit board into the side of this metal plate.
The parts line up tightly, emphasizing how compact the assembly is.
The partly built device then appears inside a \textbf{rectangular} silver housing.
The word “ STEREO ” is printed near the top right, and small control buttons or \textbf{knobs} sit along the upper edge.
The original black cassette, still marked “ UCX-S 90, ” lies above the device on the grey surface, acting as a \textbf{size} comparison.
Hands now add the front portion of the player.
A silver faceplate with two round reel-window shapes is guided into place over the exposed \textbf{mechanism}.
The fingers \textbf{adjust} it on both sides, pressing it down so the two circular areas align.
A dark smoked plastic cover is then lifted from below and swung up across the front.
As it closes, the finished \textbf{unit} is revealed : a compact silver Sony Walkman with a black oval window showing the two circular reel shapes beneath.
Across the top front, “ SONY ” appears on the left and “ WALKMAN ” in red on the right, with a thin red line near the top edge.
The assembled player sits neatly on the grey surface, with the cassette still lying above it.
A white earphone cord is draped across the Walkman, looping diagonally over the front window and across the brand name area.
Large white on-screen lettering \textbf{fades} in over the product : “ SONY, ” with the smaller slogan beneath it, “ THE ONE AND ONLY. ” The Walkman remains visible behind the bold text, partly covered by the crossing earphone cord.
The final scene shows a freestanding in-store display on a dark surface.
It is a tall white sign held upright by dark side supports, with a picture of the Walkman near the lower middle and a pair of white earphones lying in front to the left.
Large blue text at the top reads : “ Listen to the new Sony Super Walkman.
You might win to the tune of \$25,000. ” Small fine print appears along the bottom of the screen, including “ No Purchase Necessary, ” entry-card information, and an offer expiration date, though some of the smaller wording is difficult to read.

% matched lemmas: adjust, case, fade, hinge, knob, mechanism, plain, printed, rectangular, size, unit
\end{textsample}
