\begin{textsample}{POS Dim 8 – 2020 – Score 8.00 – 2020/tv\_com\_2020\_84.txt}  \label{ex:f8_pos_004}
The commercial opens in a \textbf{snowy} forest setting.
A woman and a man walk together hand in hand through deep \textbf{snow}, surrounded by snow-covered evergreen trees.
Both are dressed in winter clothing : the woman wears a pale blue coat, grey knit hat, and scarf ; the man wears a dark coat over a grey sweater.
They look at each other warmly.
The camera cuts closer to the man ’s face as he smiles at the woman.
The scene then shifts to a wide view of an open \textbf{snowy} path between trees.
A small dark shape appears in the \textbf{snow} at a distance.
In the next shot, it is revealed to be a black, white, and brown puppy running through the \textbf{snow} toward the camera, kicking up powder as it moves.
The woman and man react happily.
The woman holds the puppy in her arms while the man stands beside her smiling.
In a closer shot, the puppy rests against the woman, and she looks up toward the man.
The man looks down at her with a pleased expression.
Another shot shows the couple standing together with the puppy ; the man stands behind the woman with his hands around her arms, and the puppy is cradled in front.
The mood then shifts to action imagery.
A black GMC pickup truck drives forcefully through deep \textbf{snow} in the same kind of wooded winter landscape. \textbf{Snow} bursts outward around the front of the truck.
Several close-up shots show the side of the truck and its wheel moving through \textbf{snow}, with chunks and powder flying across the frame.
The truck ’s front grille and vertical light elements are visible through the spray.
A later front-facing shot shows the black GMC truck emerging more clearly, centered on the \textbf{snowy} track, with evergreen trees behind it.
Small fine-print text appears along the bottom, but it is too small to read clearly in the sampled frames.
The commercial cuts back to the couple and puppy.
The woman, still holding the puppy, and the man look off-screen with surprised or impressed expressions, apparently toward the \textbf{arriving} vehicle.
A wider shot reveals the black GMC pickup parked in the \textbf{snow} near them.
The man stands beside the front of the truck, while the woman stands farther left holding the puppy.
Large bold white text appears in the upper left : “ GIFT LIKE A PRO, ” with a red vertical accent line beside it.
The \textbf{snowy} forest continues as the background.
The next sequence presents offer graphics.
A red GMC Sierra pickup is shown parked on a \textbf{snowy} landscape with mountains or forested hills in the background.
Large text reads : “ GMC, ” “ 2026 GMC SIERRA 1500, ” “ MICHIGAN RESIDENTS, ” and “ \$1,000 \textbf{LEASE} CASH. ” Fine-print legal text appears along the bottom but is mostly too small to read clearly.
Another promotional frame shows the same red pickup, with large text at the top : “ GMC HOLIDAY EVENT. ” Additional text reads : “ 2026 GMC SIERRA 1500 ELEVATION CREW CAB 4x4, ” “ WITH TURBOMAX ENGINE, ” and a large price offer : “ \$169 PER \textbf{MONTH} FOR 24 \textbf{MONTHS}. ” More smaller qualifying text and extensive \textbf{fine} \textbf{print} fill the lower portion of the screen, but much of it is not legible at this resolution.
The commercial ends on a black background with the red “ GMC ” logo centered.
Beneath it, smaller white text reads : “ WE ARE PROFESSIONAL GRADE. ”

% matched lemmas: arrive, fine, lease, month, print, snow, snowy
\end{textsample}
