\begin{textsample}{POS Dim 8 – 2000 – Score 7.00 – 2000/tv\_com\_2000\_58.txt}  \label{ex:f8_pos_012}
A glossy red circular button sits alone on a pale grey surface, like a large control button set into a smooth panel.
It changes into a shiny blue button with a silver rim and a yellow triangular play symbol in the centre, set against a vivid blue background with faint watery streaks and floating digital shapes.
The yellow play triangle grows until it fills the view, becoming a bright gateway into an abstract orange and gold space filled with glowing rings, bubbles, and streaks of light.
Within this warm, glowing environment, a small computer-window image appears, then gives way to close, warmly lit faces.
A smiling young woman with short dark hair looks directly forward, while a man with facial hair leans in behind her, nuzzling close at her shoulder.
Both appear relaxed and happy.
A little blond girl then fills the screen, smiling directly outward in bright sunlight, her hair falling across her forehead and her light patterned top visible at the edges.
The \textbf{mood} turns more energetic as a young man with dark hair, black rectangular glasses, a bright blue shirt, tie, and dark trousers poses outside a striking yellow building.
He carries a dark shoulder bag and makes playful, animated gestures, lifting one knee and pointing as if dancing or celebrating in front of the building ’s large round yellow architectural feature.
Inside what appears to be a small aircraft, a woman in a blue skydiving \textbf{suit} and yellow goggles sits in front of a blond instructor wearing dark sunglasses.
The instructor gives a thumbs-up from behind her, and she smiles broadly.
A blue graphic streak sweeps along the bottom with the white text “ push FASTER. ” A handheld or small screen is then shown displaying the same skydiving scene, as if the action is being watched or shared through a digital device.
The orange digital background returns with a floating web browser-style page.
The page has a purple bar across the top with Telocity branding at the upper right and a section labelled “ e-mail. ” On the right side of the message, large readable text says, “ Hey kids, See what I did!
Love, Grammy. ” On the left, a photo shows the woman skydiving with her instructor, arms spread in freefall against a blue sky, visually matching the earlier plane scene.
Another web page floats in the same glowing orange space.
It is a green travel page with Telocity branding at the top right.
A left column reads “ Kato Falls, ” and the main area shows moving scenic imagery of rushing water, rocks, and green foliage.
The page includes a “ Travel ” heading and a “ Locator ” area, suggesting destination browsing.
The travel imagery then becomes full-screen : a woman in outdoor clothes with a backpack stands in a lush, rocky forest gorge before a tall waterfall.
She stretches both arms outward and lifts her face toward the falling water, surrounded by deep greens and cool blue light.
The young man with black glasses reappears in a \textbf{city} \textbf{street} lined with tall buildings.
He smiles broadly into the foreground.
A blue streak crosses the lower part of the image, and large white text appears : “ push COOLER. ” The exaggerated close view makes his grin and glasses prominent, with skyscraper \textbf{facades} rising behind him.
Back in the orange digital space, a shopping page spins into view.
It has a purple-blue layout with Telocity branding at the top right, a section labelled “ Shop, ” and a product category that reads “ scooters. ” In the centre, a small scooter is displayed inside a large orange circular frame.
On the right, bold white text says “ BUY NOW, ” next to a round orange button.
The scooter image enlarges and rotates slightly within the page, with navigation arrows visible near the bottom.
The commercial then shows the scooter in real life : a low, close view of a yellow kick scooter rolling along a \textbf{city} \textbf{street} beside parked cars.
A person ’s black shoe rests on the scooter deck as the front wheel moves past the camera.
The same young man in the blue shirt, dark \textbf{vest}, and black glasses appears riding or moving forward, smiling as he passes through a softly blurred urban background.
A quick series of joyful lifestyle images follows.
A young boy smiles in cool blue light, his face close and bright against a dark background.
A young woman in a red top smiles outdoors beneath a vivid blue sky, her hair blown back.
At a beach at sunset, several \textbf{people} run across wet sand toward the water ; a yellow-and-white surfboard lies in the foreground, and the sky glows pink, orange, and purple.
A Black woman laughs with her head tilted back, lit in deep blue tones against a dark, leafy background.
A man in a white T-shirt and sunglasses appears suspended midair against a deep blue sky, arms spread wide beside a curved yellow surface, suggesting an extreme-sport or airborne moment.
The visuals shift to a bright orange offer screen.
Large white text appears : “ FREE Activation. ” Fine print along the bottom is small but partially readable, mentioning limited service availability, monthly service fees and shipping, and a limited-time offer with details on the web site.
The offer expands to read “ FREE Activation ” and “ No Annual Contract ” in large white lettering over the orange glow.
A blue and yellow swoosh sweeps across the offer screen, revealing the website address “ www.telocity.com. ” The commercial ends on a glossy blue background with soft circular ripples and bubbles.
The white Telocity logo appears in the centre, accented by a yellow swoosh around the final letters.
A yellow line streaks beneath the logo as the brand mark remains prominent on the blue field.

% matched lemmas: city, facade, mood, people, street, suit, vest
\end{textsample}
