\begin{textsample}{POS Dim 8 – 1980 – Score 6.00 – 1980/tv\_com\_1980\_68.txt}  \label{ex:f8_pos_048}
It opens in black and white with a middle-aged man in formal evening wear standing behind a low rail or podium in front of heavy stage curtains.
He has a dark tuxedo jacket, white shirt, bow tie, and a neat mustache, and he faces forward with an exaggerated, genial expression.
A seated woman in pale clothing is partly visible at the right edge beside him.
Across the bottom of the image, white capital letters read, “ IN STEREO WHERE AVAILABLE. ” The scene abruptly shifts to an extreme close view of a woman ’s face in color.
She appears light-skinned with blonde hair, her head tilted back, eyes wide, and mouth opened very wide in a terrified scream-like expression.
Her face fills almost the entire screen.
This is followed by a black-and-white horror-film image displayed within the frame of a Mitsubishi television : a woman with dramatic makeup and streaked hair, resembling a classic movie monster bride, looks upward with her mouth open and eyes wide.
The television then shows a brightly colored opera or theatrical performer.
The performer wears elaborate stage makeup, a large ornate gold headdress with dangling decorations, and a blue robe over a jeweled costume, posed against a warm gold background.
The imagery switches again inside the television to black-and-white \textbf{western} scenes : several riders on horseback move across a dusty landscape, their silhouettes dark against a pale sky and low hills.
One rider lifts a bugle or horn to his mouth while riding, and the horses and riders pass across the screen in quick succession.
A bright, indistinct burst of light fills the television image, followed by a science-fiction-looking image in blue : a spacecraft or large curved structure occupies the right side while a white-blue plume or beam shoots horizontally from it.
A Mitsubishi nameplate fills the screen next.
The familiar three-diamond logo appears at the left, followed by bold white block letters spelling “ MITSUBISHI ” on a dark rectangular strip mounted against a plain gray surface.
The logo remains visible for several moments.
The commercial continues with more examples of dramatic screen images.
A television picture shows a pale room with a jagged hole smashed through a wall near the floor ; broken plaster or debris is scattered below it.
A small table stands to the right with objects on top and a lower shelf.
Then a black-and-white close-up shows a square-headed Frankenstein-like monster with a flat forehead, heavy eyelids, and bolts at the neck, looking sideways with a faint, grim smile.
A color image follows of an orange, shaggy puppet drummer with a huge open mouth and wild hair, seated behind a drum kit, arms lifted and blurred as if pounding the drums.
This dissolves into a black-and-white scene of a large vehicle, like a truck or bus, crashing through glass doors or a windowed \textbf{entrance}, with bright shards and reflections around it.
The product itself is then shown in a home \textbf{entertainment} cabinet.
On the left is a television set built into a dark rectangular unit, and on the right is a vertical stack of audio and video components with buttons, displays, slots, and panels.
The television screen first shows a basketball game on a court, then changes to dancers lined up in a stage or film musical.
The image moves into a black-and-white musical number on the TV : several performers in light costumes dance together in a busy stage setting, with a central dancer stepping forward while others move in formation around him.
A closer view isolates the stacked Mitsubishi components.
Three dark, sleek units sit one above another, each with a mix of metallic panels and black display areas.
The top component has a large round control knob on the right.
The middle unit has a long front panel with many small buttons and a small \textbf{illuminated} display.
The lower unit includes cassette-like openings or compartments and another large knob at the right.
The arrangement emphasizes a full audio-video system rather than just a television.
The Mitsubishi logo returns, again as white lettering and the three-diamond mark on a gray surface.
Then the full home theater setup appears in a modern living room.
A large floor speaker stands on the left, with visible circular drivers of different sizes.
The television is centered, and the component stack is to its right within the same dark \textbf{entertainment} console.
The TV screen shows a close-up of feet in dress shoes, with a bright orange glow near the floor.
Then the TV fills the view with a color movie image of a dark-haired man in a \textbf{suit}, seen from the side against a pale background, looking toward someone whose silhouette is only partly visible.
The room is shown wider.
It has a stylish, loft-like interior with white brick walls, a large angled window or glass structure on the left, and a spiral staircase curving upward on the right.
A vase with a tall plant sits on top of the \textbf{entertainment} unit.
Cushions or soft furnishings lie on the floor in the foreground, and a patterned throw or rug is spread at the lower right.
The Mitsubishi system anchors the center of the room : speaker on the left, television in the middle, equipment stack beside it, and a tall dark speaker or cabinet on the right.
On the television, the images continue changing rapidly through different movie scenes, including a distant landscape, a fast-moving roadway or \textbf{city} \textbf{street}, railway tracks, cloudy or smoky imagery, and a yellow vehicle seen from above or at an angle.
A light-haired adult woman stands near the right wall by the staircase, wearing a light top and darker lower clothing, watching from the side.
The final television image is a black-and-white extreme close-up of a man ’s mouth and thick mustache.
Only the lower nose, mustache, and lips fill the TV screen, with the Mitsubishi television frame visible around the picture.

% matched lemmas: city, entertainment, entrance, illuminate, street, suit, western
\end{textsample}
