\begin{textsample}{POS Dim 8 – 1960 – Score 5.00 – 1960/tv\_com\_1960\_108.txt}  \label{ex:f8_pos_086}
In black and white, the commercial begins on a plain studio floor against a bare backdrop.
A small group of adults sits very close together on stools, arranged as if they are passengers in a car.
At first they are seen from the side, lined up tightly.
One man wears a dark \textbf{suit}, a woman wears a light dress and hat, and another person in clown makeup holds a large steering wheel prop as if pretending to drive.
Other faces crowd behind them, suggesting a full carload squeezed into a very small space.
They sit upright and stiff, knees close together, with little room between bodies.
The group is then seen from the front.
The man in the dark \textbf{suit} sits on the left with his hands folded, the woman sits in the middle, and the clown driver sits on the right gripping the steering wheel.
Two more faces peer from behind them.
A pale square appears around the group and visually closes in, making the already tight cluster seem even more confined.
As it shrinks, the \textbf{people} bunch closer together ; heads lean inward, shoulders press together, and the clown driver ’s steering wheel is crowded into the group.
The cramped group dissolves into the front windshield of a compact car, where several clowns are packed inside.
Round balloons float above the roof, and long curled streamers hang in the background.
Through the windshield, painted clown faces, hats, ruffled collars, and polka-dotted costumes fill the interior from side to side.
The car ’s front grille and twin headlights are visible, and the clowns look comically crowded behind the glass.
The view widens to a studio decorated like a festive showroom or circus party, with hanging streamers covering the backdrop and clusters of balloons at both sides.
A light-colored Studebaker Lark sedan sits center stage.
Clowns stand near the car \textbf{holding} balloons, while more clowns are visible inside.
The car ’s shape is boxy and compact, with a prominent chrome grille, bright trim, whitewall tires, and large windows.
Inside the car, a clown in profile sits by a window wearing a tall, soft, decorated hat with tassels and a flower-like \textbf{ornament}.
His face is painted white with dark eyebrows, a round nose, and an exaggerated mouth.
There is visible space above his hat and around his head, emphasizing headroom.
He turns slightly, his expression alert and pleased rather than squeezed.
A series of interior views then focuses on the clown ’s polka-dotted costume spread across the seat and down toward the floor.
The loose white fabric with dark spots drapes over his lap and legs.
The view travels along the bench seat area toward his feet, where oversized clown shoes rest on the flat floor.
The shoes have rounded toes and contrasting panels.
The seat cushion, door hardware, and the lower interior panels appear close around the legs, but the composition shows lengthwise space for the costume and feet.
The car is shown from the side with both side doors open, revealing a wide doorway and the bench seats inside.
A clown sits in the front, and another reclines or lounges in the rear seat area, his polka-dotted costume stretched along the cushion.
The open doors expose a broad \textbf{entrance} and a low, unobstructed step-in area.
A close view shows an oversized clown shoe stepping across the door opening onto the carpeted floor.
The foot moves in and out over the threshold without lifting over a high sill.
The door frame and lower trim are visible along the edge, and the carpet lies nearly level with the \textbf{entrance}.
The shoe shifts forward and back, demonstrating the flat, easy step into the car.
Loose white feathers are scattered on the dark carpeted floor.
A large soft brush or broom sweeps across the flat floor, pushing the feathers toward the door opening.
The bristles move briskly from side to side, gathering the debris without catching on ridges or raised floor sections.
The interior upholstery is then shown in detail.
The bench seat has broad, smooth cushions with parallel stitched pleats running across the seat and vertically up the backrest.
The fabric or vinyl has a soft sheen in the black-and-white image, and the stitching creates evenly spaced channels.
The clown ’s polka-dotted costume enters the edge of the view as he sits against the upholstered backrest.
A clown seated comfortably inside holds an open glossy magazine or \textbf{brochure} across his lap with both gloved hands.
He wears white gloves and a loose polka-dotted costume with ruffled cuffs.
The magazine pages reflect light and show a printed image, though the details are not fully readable.
His posture is relaxed, with the reading material resting easily in front of him, suggesting there is room to sit and handle it.
A close view of another clown ’s face fills the screen.
He wears a soft cap or beret, a ruffled collar, and full white clown makeup with arched painted eyebrows, a round nose, and a large outlined mouth.
His eyes open wide and his mouth opens into an exaggerated expression of delighted surprise.
The car returns to the decorated studio floor beneath the streamers.
Different Lark models are displayed one after another.
A light-colored car is shown with balloons tied near the front, its chrome grille and whitewall tires bright against the plain stage.
Another model is seen from the side, with a long roofline and rear side windows.
A convertible appears in profile with the top down, balloons rising from inside.
A station wagon is shown from the rear with its tailgate open ; balloons and a clown ’s legs protrude playfully from the cargo opening, reinforcing the roomy, festive presentation.
The final image places the Lark in the background beneath hanging streamers, then large white lettering appears over it.
The on-screen text reads “ THE LARK ” in big italic letters, with a small bird-like arrow shape near the word, and beneath it, “ BY STUDEBAKER. ” The car fades behind the lettering until the title remains centered on a plain background.

% matched lemmas: brochure, entrance, holding, ornament, people, suit
\end{textsample}
