\begin{textsample}{POS Dim 8 – 2000 – Score 9.00 – 2000/tv\_com\_2000\_41.txt}  \label{ex:f8_pos_007}
At night on a wet \textbf{city} \textbf{street}, a corner \textbf{storefront} glows with green and red neon and a sign with Chinese characters.
Pedestrians move along the sidewalk under the \textbf{awnings} while the slick pavement reflects the lights.
In the foreground, a round manhole sits open in the \textbf{street}.
A light-skinned, male-presenting worker in a yellow hard hat and dark work jacket rises up through the manhole, holding a \textbf{mobile} phone to his ear.
He wears dark-framed glasses and a rectangular name patch on his chest.
Only his upper body is visible above \textbf{street} level as he looks forward, listens, and speaks into the phone, then settles into a small, satisfied smile while \textbf{people} continue \textbf{walking} behind him.
The same bespectacled man appears next in a swampy wooded area, now wearing gray chest waders over a dark shirt.
He holds the phone to his ear with one hand while trudging through shallow water among tree trunks and exposed roots.
He lifts his knees high to step through the mud and water, then reaches out with his free hand to steady himself against a narrow tree trunk.
He pauses there, standing knee-deep in the wet ground, still listening and talking on the phone, surrounded by muted greens and browns of the marsh.
The scene changes to a bright office corridor lined with gray cubicles.
A professional-looking woman in a tan skirt \textbf{suit} \textbf{walks} down the aisle toward the front, carrying a stack of \textbf{folders} and a black briefcase.
As she passes out of the way, the same man is revealed seated in an office chair in the middle of the aisle, still wearing his dark work jacket and glasses, phone pressed to his ear.
A small line of white legal text runs along the bottom of the image, too small to read clearly here.
Behind him, office workers stand and talk near a bright window, and an older beige computer monitor sits in one cubicle.
The man sits upright, calm and focused, then slowly turns and rolls the chair sideways while continuing his call.
He is then seen outdoors in warm sunlight beside tall reeds or cane plants, with muddy water and a large dark piece of equipment or vehicle in the background.
In close view, he holds a silver-and-black \textbf{mobile} phone to his ear and looks slightly off to the side through his black glasses.
The golden light catches his face and the plants around him.
He remains intent on the call, his expression neutral and testing, then begins to move out of the reeds.
In a dry desert setting, he steps into view in front of reddish rock formations, a Joshua tree, and a small outdoor campsite or \textbf{activity} area with \textbf{people} and gear in the background.
The sky is clear blue.
He wears the dark Verizon-style work jacket with a rectangular patch and continues holding the phone to his ear.
He \textbf{walks} a few paces, facing forward, speaking and listening, while the desert rocks fill the background.
The environment shifts to a cold, dark, wintry-looking place.
The man is bundled in a heavy black parka with a large fur-trimmed hood pulled around his face.
His black-framed glasses are still visible, and a rectangular patch is sewn on the front of the coat.
A phone or headset rests at his ear, partly hidden by the hood and glove.
He looks straight ahead, then glances slightly upward and to the side, appearing alert and still engaged in the same phone test despite the extreme cold suggested by the heavy clothing and dim, icy-looking background.
A long, open road or bridge appears at sunset, lined on the right by a repeating row of tall utility poles that recede into the distance.
The man is now a small figure \textbf{walking} away down the road, silhouetted against orange light near the horizon and darker clouds above.
Over this scene, the Verizon Wireless logo fades in large across the center : white lowercase “ verizon ” with the red checkmark accent above it and the word “ wireless ” in smaller white letters to the right.
The background darkens slightly behind the logo while the distant figure continues to stand or \textbf{walk} along the road.
After the logo, the man appears on a \textbf{city} sidewalk outside a \textbf{storefront}.
He is in the left foreground, still on his phone, facing a smiling young woman with long dark hair who wears a red top with white stripes on the sleeves and holds a snowboard or skateboard-like board against her hip.
Another young woman in a green top stands behind them near the doorway, watching.
On the right, a bald man crouches or sits low, also holding a phone to his ear.
Yellow flyers or stickers are posted in vertical rows on the doorframe and window area.
The main man gestures with his free hand while talking, then steps closer to the smiling woman, turning partly away so the back of his dark jacket is visible, with white Verizon Wireless lettering across it.

% matched lemmas: activity, awning, city, folder, mobile, people, storefront, street, suit, walk
\end{textsample}
