\begin{textsample}{POS Dim 8 – 1980 – Score 10.00 – 1980/tv\_com\_1980\_50.txt}  \label{ex:f8_pos_041}
The commercial opens inside a Best Western hotel lobby at the front desk.
A middle-aged man with curly dark hair and a full beard stands on the guest side of a light wood reception counter, facing the viewer.
He wears a bright blue windbreaker over a teal sweater and light shirt, and he has a friendly, animated smile.
Across the counter, a blonde woman in a dark blue uniform appears to be the desk clerk ; she smiles at him and then looks down to work with papers or a register.
Behind them, a large \textbf{illuminated} Best Western sign with the crown logo hangs on the wall, and a row of round wall clocks suggests different time zones.
A vase of pink flowers sits on the counter, adding color to the lobby.
Other hotel guests and staff move in the background, including men in \textbf{suits} and a blonde woman with luggage.
The bearded spokesperson remains near the desk, leaning slightly on the counter and addressing the viewer directly.
He clasps his hands, fidgets with a small object or folded paper, and gestures as he talks.
His expressions shift between earnest, amused, and broadly smiling.
The clerk continues looking down at paperwork, while the background guests pass through the lobby and converse.
The Best Western sign remains visible behind the counter, reinforcing the hotel setting.
He then moves away from the front desk into a warmly lit indoor area with leafy green plants in front of windows or glass panels. \textbf{People} are visible behind the plants in a lounge-like space, and vertical strings of small lights create a festive glow.
A couple briefly crosses close in front of him, partly blocking him, before he reappears standing in front of the greenery.
He holds a folded paper or \textbf{brochure} in one hand and continues speaking directly to the viewer.
His blue jacket and teal sweater stand out against the dark green plants and warm amber background.
He gestures with open hands as if explaining options, then settles into a centered stance, smiling and nodding.
The scene changes to a nighttime hotel \textbf{entrance} or driveway.
At the left is an ornate horse-drawn carriage with large wooden wheels and a polished, old-fashioned body ; its door is open.
A group of costumed celebrity impersonators steps away from the carriage.
Small white on-screen text near the bottom reads “ Celebrity impersonators. ” In the group, a woman dressed as a queen wears a tiara, a pale formal \textbf{gown}, a white fur-like wrap, and carries a small gold handbag.
Beside and behind her is a tall man in a black ceremonial military-style uniform decorated with gold braid and medals, wearing white gloves.
Other costumed \textbf{attendants} include a figure in a red uniform with a hat and additional older men in formal or period-looking attire.
They \textbf{walk} together toward the hotel \textbf{entrance}, passing potted tropical plants and a doorman or \textbf{suited} staff member near the doorway.
The bearded spokesperson appears again at the right side of the hotel \textbf{entrance}, still in his blue windbreaker and holding folded papers.
He turns toward the costumed group and points or gestures back at them with a raised thumb, as if referring to them while continuing his joke.
The queen impersonator and the uniformed man stand in the background near the \textbf{entrance}, while \textbf{suited} men linger nearby.
The hotel façade has a lit \textbf{awning} or trim above the doorway, giving the \textbf{entrance} a bright, polished nighttime look.
The spokesperson looks between the viewer and the costumed group, smiling with a slightly mischievous expression.
At the end, large white numbers appear across the lower part of the screen : “ 1-800-528-1234. ” A Best Western logo box appears on the lower right, showing the crown above the words “ Best Western, ” with smaller text below indicating independent worldwide lodging.
The spokesperson turns his head toward the costumed queen and her entourage as they remain gathered by the \textbf{entrance}, while the phone number and logo stay prominently on screen.

% matched lemmas: attendant, awning, brochure, entrance, gown, illuminate, people, suit, walk
\end{textsample}
