\begin{textsample}{POS Dim 8 – 1970 – Score 5.00 – 1970/tv\_com\_1970\_68.txt}  \label{ex:f8_pos_039}
A large, light-colored suburban house with tall windows, a front stoop, and a green lawn appears on a quiet residential \textbf{street}.
A white station wagon is parked in the driveway, its rear angled toward the house.
Near the sidewalk, a small child ’s tricycle rests on the grass, and a folded stroller or carriage stands near the front steps, suggesting a home prepared for children and family.
A person stands near the open front doorway as if \textbf{waiting} or \textbf{welcoming} someone.
At the car, a Black woman sits inside holding a newborn wrapped in a soft white blanket.
The car door is open, framing her in the dark interior.
She wears a pale pink or lavender blouse or dress and smiles warmly as someone approaches from outside.
Another Black woman, older or middle-aged, with a rounded Afro hairstyle and a peach-toned blouse, leans into the open car door to look at the baby.
The mother turns her face toward her, smiling, then looks down at the bundled infant in her arms.
The two women share the moment closely, their attention centered on the small white-wrapped baby.
Outside the house, the woman with the Afro bends over the baby, now held near the doorway or front steps.
Behind her stands a Black man with glasses, a mustache, a white shirt, tie, and suspenders.
He beams broadly over her shoulder.
The woman leans down and kisses or nuzzles the infant through the blanket.
More relatives gather in around them, including a young woman at the side and a smiling man in a light \textbf{suit}.
Their faces crowd around the baby, each looking down with delighted expressions.
The setting shifts to an outdoor family gathering.
A table is filled with picnic-style food : ears of corn, grapes, fruit, bowls of vegetables or beans, and other dishes.
Dark glass Pepsi bottles with visible Pepsi labels are placed among the food, including several bottles grouped together.
Hands set the bottles down as part of the spread, making the Pepsi part of the family celebration.
In the leafy yard, a young Black man or older boy in a patterned shirt turns his head and looks back, then smiles slightly.
An older Black man in a light \textbf{suit}, dark bow tie, and pale \textbf{brimmed} hat looks on with a thoughtful, pleased expression.
He lifts his hand to the \textbf{brim} and removes the hat, revealing short gray hair, as if respectfully greeting the baby or the family.
The mother, now outdoors under trees, carries the baby wrapped in white.
A smiling Black man in a light \textbf{suit} and tie stands close behind her, likely the father.
They approach the older man.
The mother ’s face is bright and emotional as she presents the infant.
The older man leans in, smiling tenderly, while the father places a hand around him or on his shoulder.
The older man bends close to the baby ’s blanket, appearing to kiss or affectionately greet the infant.
The family forms a tight circle around the newborn, with hands on shoulders and faces turned inward.
The baby ’s face fills the scene : a very small Black infant with dark hair, lying against white fabric.
The baby ’s mouth opens in a wide smile or laugh, eyes partly closed, one tiny hand near the chin.
The infant ’s expression is animated and happy.
The older man, the mother, and the father look down at the baby and laugh together.
The older man ’s face breaks into a broad grin, his gray hair and bow tie visible, while the younger adults lean in from both sides, smiling at him and the child.
On a blanket or low seating in the yard, the mother sits with a little Black girl wearing large round glasses and a light dress with a bow in her hair.
The father sits beside them, smiling.
The mother holds a small soft baby item, possibly a bootie or little piece of clothing, and laughs as she shows it to the child.
The girl reacts with delight, her mouth open in laughter.
A middle-aged Black man nearby grins broadly ; a Pepsi bottle stands upright behind him with its label visible, linking the product to the cheerful gathering.
The mother and little girl continue playing with the small baby items.
The girl lifts one near her face while the mother holds another in her hand, both smiling.
The father, still beside them in a light shirt and tie, watches with a broad grin.
Their posture is relaxed and casual, seated close together under the shade of trees.
A Black woman with short, curly hair drinks directly from a glass Pepsi bottle.
The Pepsi label is clearly visible near the neck of the bottle as she tilts it to her lips.
Her eyes are closed or relaxed, and she takes a long sip, with other family members softly out of focus behind her.
Elsewhere in the yard, a young Black boy sits holding the newborn in his lap, carefully supporting the white-wrapped baby.
To his left is the bespectacled man with suspenders, smiling and leaning in ; to his right is the older man in the pale hat and light clothing, also leaning toward the child and baby.
The boy looks from one adult to the other, then down at the infant, as if proud and slightly amazed to be trusted with the baby.
Another group sits with an open photo album or large book across their laps.
A Black woman in a white sleeveless dress sits between two children.
The girl on one side, wearing glasses, laughs with her mouth wide open ; the child on the other side leans back laughing.
The woman raises a hand playfully, then smiles down at the book.
Behind them, a man in light clothing sits back holding the baby or a white bundle, completing the feeling of a large family gathering spread across the yard.
The mother bends over a baby lying on a white-covered surface, possibly a blanket or bassinet, with a young child seated nearby watching.
She smiles down at the infant and gently reaches toward the baby, while the child, holding a small object, observes with curiosity.
The scene is soft and intimate, surrounded by greenery and flowers.
Near the end, the young man or older boy in the patterned shirt drinks from a glass Pepsi bottle.
He tilts the bottle high, the Pepsi label facing outward, while the woman with the Afro stands behind him smiling.
The dark soda is visible through the glass as he drinks.
Finally, the parents stand together outdoors beneath the trees.
The Black man in a light shirt and tie holds the mother around the waist, and she has both arms around his shoulders.
They lean close, smiling, then kiss.
Other family members and Pepsi bottles or crates are visible in the background, suggesting the celebration continues around them.
White on-screen text appears across the lower center reading, “ Have a Pepsi day. ”

% matched lemmas: brim, street, suit, wait, welcome
\end{textsample}
