\begin{textsample}{POS Dim 8 – 1950 – Score 2.00 – 1950/tv\_com\_1950\_29.txt}  \label{ex:f8_pos_081}
The commercial is shown in black and white and appears to move from a social scene to a product display.
At the beginning, several adults are gathered indoors in what looks like a party or dance setting.
The room is dimly lit, with a \textbf{staircase} visible on the left and darker wall or curtain areas in the background.
Three women are prominent : one on the right wears a light-colored, full-skirted formal dress ; the woman in the center wears a light top with a dark skirt ; another woman stands toward the left near other figures.
Their body positions suggest movement or dancing, but the exact action is not fully clear from the single frame.
By the final frame, the setting has changed or the camera has moved to a closer shot.
A smiling woman is shown from about the waist up, facing the camera.
She wears a light satin-like sleeveless dress and a necklace, with styled curled hair.
She holds up a rectangular product box beside her face, presenting it toward the viewer.
The box has \textbf{printed} text on it, but the brand or full wording is not clearly legible in the sampled frame.
Behind her are interior details including a \textbf{staircase} railing, a wall lamp, and what appears to be part of a dressing-table or mirror area with round bulbs on the left.
A partial face or figure is visible at the far right edge of the frame, but it is cut off and unclear.

% matched lemmas: print, staircase
\end{textsample}
