\begin{textsample}{POS Dim 8 – 1980 – Score 2.00 – 1980/tv\_com\_1980\_25.txt}  \label{ex:f8_pos_056}
The commercial begins with a black frame, with no visible objects or people.
By around 9.4 seconds, the scene has changed to an indoor counter or workbench setting.
In the foreground, a large white plastic jug of drain cleaner is prominently displayed.
The label reads “ Liquid Plumr ” and also includes “ Drain Opener ” ; there is additional smaller text near the top that appears to say “ Clears fast, ” though the exact wording is somewhat blurred.
The bottle has a red cap and red/blue label graphics.
Behind the product are three men seated or leaning at the counter.
They are wearing \textbf{matching} plaid shirts or jackets and light-colored caps.
Each appears to be holding a black telephone receiver to his ear, suggesting they are taking calls.
Their facial expressions appear animated or attentive, but \textbf{fine} details are limited by image quality.
The background includes signage with partially readable text, including “ DISCOUNT ” and “ PLUM …, ” likely related to plumbing, though the full sign is not clearly visible.
The lighting is colorful and somewhat theatrical, with pinkish and bluish tones.
Near 28 seconds, the shot changes or tightens to a clearer product-focused view.
The jug of Liquid Plumr dominates the left side of the frame on the counter.
The people are no longer visible.
The background remains an indoor shop-like setting, out of focus, with the same partially visible signage and a bluish light beam or reflection across the back.
Small objects lie on the counter around the bottle, but they are indistinct.
The final frame is essentially the same product shot : the Liquid Plumr bottle remains centered-left and prominent, with the blurred store/workshop background behind it.
No additional visible action occurs in the sampled frames.

% matched lemmas: fine, match
\end{textsample}
