\begin{textsample}{POS Dim 8 – 1990 – Score 8.00 – 1990/tv\_com\_1990\_89.txt}  \label{ex:f8_pos_062}
A young blonde woman in a white top and dark skirt moves through a dim, sunlit interior with large windowpanes behind her.
Warm light cuts across her clothing and hair as she lifts or adjusts a dark bag and heads toward a doorway.
She passes behind an old-fashioned metal elevator or security gate with crisscrossing vertical bars, her figure broken into strips by the lattice.
In the warm, shadowy space, faces are seen through the bars, close and partially blurred, giving the moment an intimate, fleeting feel.
A black Sony camcorder appears resting on a surface, propped on a small support with its strap draped underneath.
The front lens is prominent, and the white “ SONY ” name is visible on the upper part of the device.
The blonde woman looks down toward it with a soft smile that grows into a broad, delighted grin, her face warmly lit from below and her loose hair glowing around her cheeks.
A young man with short light hair, wearing a dark sweater, \textbf{waits} near a glass door in a bright lobby.
He leans casually with one arm raised against the doorframe and smiles with a dimpled expression.
The blonde woman, now in a dark jacket over her outfit and carrying a bag, approaches him.
He holds the door open as she \textbf{walks} through, and sunlight spills across the floor and glass behind them.
Outside, the blonde woman is seen in bright glare and reflections, now holding the compact camcorder up to her eye.
The black body and lens fill part of the view, and the “ SONY ” lettering appears large across the side or strap as she records.
Her silhouette and hair are backlit, making her profile and the camcorder stand out against a pale, hazy background.
The setting shifts to a busy \textbf{city} sidewalk in daylight. \textbf{People} in casual 1990s clothing pass along \textbf{storefront} windows, and a red convertible is parked along the curb in the foreground.
A man in a black hat and dark clothes stands near the \textbf{storefront} while several pedestrians move past him.
The \textbf{atmosphere} is public and social, with \textbf{people} gathering and flowing in different directions.
At an outdoor café, several young adults sit and stand around small tables.
A woman with long, curly dark hair in a bright red top laughs openly at the table.
Behind and beside her, the blonde woman and other \textbf{friends} are visible in the sunlight.
A blond young man in a dark sweater stands outside the café area holding the Sony camcorder in one hand, presenting it casually to the group.
The camcorder is small enough to rest in his palm, with its lens barrel and rectangular body clearly visible.
Another young man in a black \textbf{leather} jacket raises the camcorder to his eye and records, holding it close to his face with both hands.
The blond woman and the blond man then stand together, his arm around her shoulders.
They smile at each other and toward the person filming, appearing relaxed and affectionate in the bright outdoor light.
A close view of the camcorder pressed to someone ’s eye shows the “ SONY ” name in white on the black casing.
The round eyepiece sits against the user ’s face, and the lens projects forward below it.
The person squints slightly while filming, emphasizing the camcorder as a handheld, personal device.
The blond man then turns with the camcorder in one hand and gestures broadly with both arms, as if calling \textbf{friends} together.
Around the café tables, \textbf{people} look toward him.
A seated dark-haired woman watches from behind a small table with cups, while more \textbf{friends} gather nearby.
The blonde woman stands close to a bearded man in denim, and a curly-haired woman in a red top joins them ; they cluster shoulder to shoulder, smiling and leaning in for the camcorder.
Another young couple, a short-haired man in layered casual clothes and the curly-haired woman, smile side by side as they look toward the person recording.
The final image changes to a blue-toned evening or nighttime setting.
In the distance, a couple stands together against the backdrop of a large apartment building.
The man raises the small camcorder high in one hand while holding the woman close.
Large translucent text reading “ Handycam. ” stretches across the center of the image.
Then the couple fills the view : the blonde woman nestles against the blond man ’s shoulder, both wrapped close together in dim blue light.
Their expressions are calm and affectionate ; their eyes close briefly, then open as they look toward the viewer, ending with a quiet, intimate portrait of the two of them.

% matched lemmas: atmosphere, city, friend, leather, people, storefront, wait, walk
\end{textsample}
