\begin{textsample}{POS Dim 8 – 1970 – Score 6.00 – 1970/tv\_com\_1970\_5.txt}  \label{ex:f8_pos_036}
The commercial opens in grainy black-and-white with a close view of a formally dressed man seated inside a car.
He appears middle-aged to older, with a serious expression, wearing a dark \textbf{suit}, white shirt, tie, and thick dark eyeglasses.
His hands carefully hold a small object and a jeweler ’s tool in front of him.
White on-screen text at the bottom reads “ Actual demonstration. ” The view moves closer to his fingertips as he handles a rough, pale stone-like piece, consistent with the transcript ’s reference to a Cartier diamond.
His fingers turn it delicately beside a darker clamp or \textbf{holding} tool, emphasizing precision and risk.
The black-and-white sequence then shows a large, dark, full-size Mercury sedan driving along a \textbf{city} \textbf{street}, its long hood, chrome grille, and broad body reflecting light as it rolls smoothly around a bend.
The scene changes to color.
A clean-cut adult man in a dark \textbf{suit} and striped tie stands beside a dark blue 1978 Mercury Monarch parked on a wet-looking urban \textbf{street}.
He rests his hands on the roof near the windshield and faces forward as if addressing the viewer.
Behind him are \textbf{storefront} windows and large pale \textbf{awnings} ; a few men in \textbf{suits} stand nearby, watching.
The Monarch is a four-door sedan with a light-colored vinyl roof, chrome trim, whitewall tires, and a squared-off front end.
As the full car is shown in profile, large white text appears near the bottom : “ 1978 MERCURY MONARCH. ” The car ’s front end is then featured closely : a tall, bright chrome grille, rectangular headlights, chrome bumper, and hood \textbf{ornament}.
The dark blue paint gleams as the car moves forward.
The view tracks along the front corner, fender, and spinning wheel, showing the whitewall tire and chrome hubcap.
The Monarch is next seen driving on a sunlit road lined with trees.
A split view presents the car approaching in the upper portion while the lower portion shows the roadway surface rushing by, visually stressing the uneven road mentioned in the transcript.
Inside the moving car, the older jeweler is now seated in the back seat.
He wears a \textbf{suit} and dark tie, with large black-framed glasses.
He raises a jeweler ’s loupe or magnifier to one eye, leaning forward in concentration.
Outside, the Monarch continues down the tree-lined \textbf{street}, seen head-on through the windshield with the driver and back-seat passenger visible.
The front grille fills the center, steady and upright as the car travels.
A divided image then shows the demonstration happening inside the car while the wheel and road remain visible below.
The text “ Actual demonstration ” appears again at the bottom.
In the upper portion, the jeweler ’s hands hold a small diamond and a tool near the rear door panel ; below, the car ’s wheel rolls along the road.
The jeweler steadies the stone in a small dark holder, then raises a broad, flat metal blade or striking tool over it.
His movements are careful and controlled.
In a wider interior view, he sits at a small work surface or board laid across the back seat.
Several tools lie on the board beside a dark upright holder.
He brings the tool down, then smiles broadly, suggesting the cut has succeeded.
The driver, a younger adult man in a dark \textbf{suit}, is shown from the front seat in profile, then glancing back over his shoulder toward the jeweler.
The jeweler is shown in close-up holding the small stone between his fingers and the tool, smiling with visible relief and satisfaction.
His black glasses dominate his face, and his expression changes from focused concentration to a pleased grin.
The Monarch continues driving smoothly along the road, its dark blue side passing across the screen in a blur of chrome trim, whitewall tires, and reflections.
It returns to the \textbf{city} setting, parked outside the same \textbf{storefront} area with the \textbf{suited} presenter standing beside it.
Large white pricing text appears over the lower part of the image : “ UNDER \$4800, ” followed by smaller text reading “ Sticker price as shown.
Destination charges, title, taxes extra. ” The car remains angled toward the viewer, displaying its boxy front, chrome grille, light roof, and polished body.
Near the end, the older jeweler appears seated inside the car, seen through an open window or dark interior frame, smiling and speaking toward someone outside.
The final image is a black background with a circular emblem at the top containing Mercury and Lincoln branding.
Large white text reads “ MERCURY MONARCH. ” Beneath it appears “ LINCOLN-MERCURY DIVISION, ” and a Ford 75th anniversary-style emblem is shown at the lower right.

% matched lemmas: awning, city, holding, ornament, storefront, street, suit
\end{textsample}
