\begin{textsample}{POS Dim 8 – 1990 – Score 2.00 – 1990/tv\_com\_1990\_4.txt}  \label{ex:f8_pos_069}
The commercial opens on an almost completely dark, indistinct frame.
It then cuts to a close product shot : an orange plastic bottle labeled “ V8 Splash ” stands beside what appears to be a stereo or boombox.
A hand is visible near the equipment, but the action is unclear because the image is soft and partially obscured.
The \textbf{ad} moves into a fast, stylized montage.
A young woman is shown in a bright interior room, possibly a bedroom or dressing room, with white curtains and scattered objects in the background.
She is standing and moving energetically while holding or swinging a large orange/red piece of fabric.
The camera angle is tilted, and the image has a hazy, soft-focus quality.
The following shots layer multiple images over one another : the orange V8 Splash bottle, the woman dancing or posing, and room details overlap through double exposure.
The bottle appears large in the foreground in some shots, while the woman remains visible behind or beside it.
The montage uses saturated colors, motion blur, and translucent overlays.
The woman continues dancing and changing poses.
She appears in different outfits or under different color overlays, including dark shorts, a red/orange garment, and later a patterned or animal-print top.
She is repeatedly shown smiling or looking toward the camera, though her face is often blurred by the visual effects.
The product bottle appears repeatedly in the same layered space.
Around the middle of the commercial, graphic text appears over the montage.
On the left, readable text says “ 100 \% VITAMIN A. ” Horizontal colored bars appear across the frame, suggesting a comparison or nutritional graphic.
Other small text appears along the bottom, but it is too blurred to read clearly.
A bottle or package appears on the right, but its label is not fully legible.
The montage continues with more overlapping shots of people moving in the room.
At least one woman in a green dress or top appears, and another figure in orange/red clothing is visible.
The product bottle remains a recurring foreground element, often enlarged and semi-transparent over the dancing figures.
Near the end, the imagery becomes more direct.
A woman with very long, bright orange hair stands near a \textbf{staircase}, smiling at the camera while holding a bottle of V8 Splash.
This shot is clearer than much of the montage and places the product visibly in her hand.
The final frames show a product packshot : a large bottle labeled “ New V8 Splash Tropical Blend ” surrounded by fruit, including visible lime slices, kiwi, pineapple, and other tropical-looking fruit.
White handwritten-style text across the bottom reads : “ KEEP THE PEACE.
DO N’T TELL THE KIDS. ”

% matched lemmas: ad, staircase
\end{textsample}
