\begin{textsample}{POS Dim 8 – 2020 – Score 3.00 – 2020/tv\_com\_2020\_34.txt}  \label{ex:f8_pos_013}
The commercial is an animated sequence featuring blue bear characters and Charmin toilet paper branding.
At the start, the scene is set in a bright domestic kitchen or utility-room environment.
Two blue-and-white cartoon bears stand near a wooden table or counter.
One bear is on the left, partly turned toward the other.
The other stands closer to the table, beside a large visible pack of Charmin \textbf{Ultra} Soft.
The pack is dark blue with the Charmin logo and “ \textbf{Ultra} Soft ” text, and appears to indicate a “ Mega ” size.
The room includes shelves, cabinets, framed wall art, a window with blinds, and various household items on the table, including \textbf{bags} and small produce-like objects.
The next scene shifts to a product-comparison style display on a blue gradient background.
Two stacks of toilet paper sheets are shown side by side.
Each stack is labeled “ 200 Sheets ” near the bottom.
The left stack is visibly shorter and has a label above it reading “ Leading Bargain Brand, ” while the right stack is taller and has a label with the Charmin \textbf{Ultra} Soft branding.
A strip of toilet paper extends upward from each stack.
Fine-print disclaimer text appears along the bottom but is too small to read clearly in full.
The commercial then cuts to a close-up of a blue bear against a dark, soft-focus background with glowing light spots.
The bear is smiling with relaxed eyes and holds a white roll of toilet paper in one arm while pressing or rubbing tissue against its cheek with the other paw, visually emphasizing softness and comfort.
A following frame shows the same bear-like close-up, but the image is blurred, suggesting a transition or motion effect.
The bear remains in a similar pose with a roll of toilet paper, but details are less clear due to the blur.
The final portion moves to a clean light-blue branded end screen.
A large Charmin logo appears in the center with a white ribbon-like shape extending from it, resembling a strip of toilet paper.
A small P\&G logo is visible in the upper-right corner.
A blue bear enters or stands on the left side of the frame.
In the last frame, the bear stands fully visible on the left holding or interacting with a small piece of tissue near its face.
The central logo now includes the readable phrase “ enjoy the go ” on the white \textbf{ribbon} beneath the Charmin name.
The P\&G logo remains in the top-right corner.
The overall visual ending is a static brand/tagline display with the animated bear posed beside it.

% matched lemmas: bag, ribbon, ultra
\end{textsample}
