\begin{textsample}{POS Dim 8 – 1960 – Score 4.00 – 1960/tv\_com\_1960\_65.txt}  \label{ex:f8_pos_090}
The commercial is in black and white.
It begins outside in a dense \textbf{city} setting.
A young adult woman with shoulder-length, softly curled hair steps out from a building \textbf{entrance} onto an exterior stair or stoop.
She wears a light-colored coat and carries a dark handbag or bundle close to her body.
Tall office-like buildings rise in the background, and a dark metal railing cuts diagonally across the foreground as she descends toward the \textbf{street}.
She appears next on a subway platform beside a train.
A large sign with the number “ 57 ” hangs behind her.
Still in her light coat, with a dark handbag hanging from her arm, she stands among other commuters, including a woman in a hat close behind her.
She faces the train windows, then raises a hand as if steadying herself or preparing to board.
Inside the subway car, she is surrounded by standing passengers in coats and hats.
Overhead hand straps hang in rows above them.
She holds a folded newspaper up in front of her and reads with a calm, concentrated expression while commuters face different directions around her.
The setting changes to an office or workplace refreshment area.
The same woman is now seated at a desk, no longer in her coat, wearing a neat dress.
File cabinets line the background, and another woman sits behind her working with papers.
In the foreground, hands from men in dark \textbf{suits} pass a tray of pastries and a small cup across the desk.
A large shiny cylindrical coffee urn stands to the right.
The seated woman looks down at the food and drink being offered, then looks up toward the person serving her.
Her expression softens into a polite smile.
Papers, pencils in a holder, and office equipment sit on the desk, giving the space a busy, professional look.
She then returns to a residential building.
From above, a small entry hall is visible with a bold black-and-white checkerboard floor, paneled doors, and a stair railing.
The woman comes up the stairs carrying a potted plant or bouquet with tall stems and leaves, her dark handbag tucked at her side.
She moves along the hallway toward an apartment door marked “ 4, ” while a neighboring door marked “ 6 ” is visible nearby.
A wall lamp casts a bright cone of light beside the door.
She stops at apartment 4, holding the plant against her chest as she works at the door, then enters.
Inside a compact kitchen, a paper bag of flour stands prominently on the counter beside a clear glass mixing bowl.
The package is readable : “ Gold Medal ” in a round logo and “ ENRICHED FLOUR ” printed below.
Around it are small kitchen appliances and containers, including what looks like a toaster or small countertop appliance and a coffee pot or kettle.
The woman, now wearing an apron over her dress, moves through the tight space.
Utensils and pans hang on the wall, and cabinets and counters are close together, emphasizing the smallness of the kitchen.
She reaches up and around the stove area, then uses a lit match near the burners or oven.
In a wider view of the narrow kitchen, pans hang neatly on a wall rack, and she bends low with the match, lighting or checking a low oven.
The flame glows clearly in her hand as she crouches in front of the appliance.
After attending to the oven, she returns to the counter where the Gold Medal flour bag remains in clear view beside the glass bowl.
She opens the flour bag and dips in a metal measuring cup.
Holding the filled cup above the bag, she levels the flour with a straight utensil, likely a knife, scraping the top smooth.
The flour looks fine and soft, heaped cleanly in the cup.
A close view shows the cup filled to the \textbf{brim} with white flour against the Gold Medal bag behind it.
She tips the cup into a glass bowl, pouring the flour directly in.
No sifter is visible ; the flour goes straight from cup to bowl.
From above, the work surface is arranged with baking tools : a hand mixer with beaters, bowls, a measuring cup, and small dishes.
The woman cracks or adds ingredients into a mixing bowl and then begins using the electric hand mixer.
In a closer view, the white mixer ’s twin beaters churn batter inside a glass bowl.
Another glass bowl filled with flour sits to the side, and a small measuring cup or glass stands nearby.
She reaches into the flour bowl with a measuring scoop, adds flour to the mixing bowl, and continues mixing.
The batter clings to the sides of the glass bowl while the beaters spin through it.
As she works, her hand moves between the flour bowl and the mixer bowl.
She scoops, adds, and tests the texture with her fingertips.
At one point her fingers dip into the flour, then lift with a light dusting of white on them.
The close views emphasize the flour, the glass bowls, and her hands as she bakes carefully and confidently in the small kitchen.
The final scene presents the finished baking.
The woman smiles gently behind a tray of desserts.
On the tray are neatly arranged cakes : a sliced piece on a small plate and a larger frosted cake with a cut section showing pale cake layers separated by a dark filling.
The frosting on the larger cake is glossy and spread in soft swirls over the top and sides.
A small cup sits near the sliced piece.
The woman ’s face remains just behind the tray, pleased and serene, as the view centers more and more on the cake ’s cut face and thick frosting.
A pale, translucent stream or ribbon-like overlay appears over the cake, visually suggesting a white, floury or creamy “ touch ” descending onto the finished dessert.
The cake remains the focus : light interior layers, dark filling line, and shiny frosting surrounding it, with the woman ’s lower face and soft smile partly visible in the background.

% matched lemmas: brim, city, entrance, street, suit
\end{textsample}
