\begin{textsample}{POS Dim 8 – 1960 – Score 2.00 – 1960/tv\_com\_1960\_65.txt}  \label{ex:f8_pos_074}
The commercial is in black and white and unfolds as a short narrative moving from travel/work scenes into a home kitchen and baking sequence.
At the beginning, the image is dark and indistinct, followed by a black frame.
The first clear scene shows a woman in a light coat standing on what appears to be a train or subway platform beside a train.
A sign with the number “ 57 ” is visible overhead.
She appears to be waiting or preparing to board.
The next shots move closer to her : she is seen near a train doorway or window, then inside a crowded train car.
She stands or sits among other passengers, with overhead hand straps visible.
Her expression is calm and composed.
After this, she is shown in an indoor workplace-like setting, seated at a desk or table with papers around her while other people move nearby.
The setting then shifts to a domestic interior.
A \textbf{stair} railing and a black-and-white checkered floor are shown, suggesting a home kitchen area.
The camera then cuts to a kitchen counter where a \textbf{bag} labeled “ Gold Medal ” and “ ENRICHED FLOUR ” stands beside a glass mixing bowl.
Appliances and containers are visible in the background.
A person, likely the same woman, enters the kitchen workspace.
Her hands and arms move quickly around the counter.
She reaches above the counter, handles kitchen items, and works in front of wall-mounted utensils and cabinets.
The Gold Medal flour \textbf{bag} remains prominently visible on the counter beside the glass bowl.
The following shots focus on baking preparation.
The woman reaches into or near the flour \textbf{bag}, and a metal measuring cup filled with flour is shown in close-up in front of the flour package.
From an overhead view, the counter contains bowls, utensils, a hand mixer, and ingredients.
A hand mixer is then used in a glass bowl, while another bowl with flour or a dry mixture sits nearby.
A bottle or jar and measuring items are visible on the counter.
The sequence continues with close-ups of mixing and adding ingredients.
The camera emphasizes the glass bowls, the mixer beaters, and the flour mixture.
The final shot shows a finished or nearly finished cake on a plate or stand being covered or frosted with a light-colored icing or topping.
The cake appears round, with thick frosting spread over the top and sides.

% matched lemmas: bag, stair
\end{textsample}
