\begin{textsample}{POS Dim 8 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_48.txt}  \label{ex:f8_pos_045}
The commercial opens on a graphic layout with a blue-and-gray vertically striped background.
At the upper left is a small white airplane symbol followed by large white text reading “ Meissner ’s, ” with “ Travel Service ” underneath.
Around the logo are overlapping, postcard-like vacation photos : a beach scene with several \textbf{people} sitting near the water, a formal table set with flowers, and a small outdoor image of \textbf{people} \textbf{walking} through green scenery with mountains in the distance.
The same Meissner ’s Travel Service logo remains in place while the travel photos change and overlap in a collage.
A pool or seaside image shows \textbf{people} relaxing in water.
Another photo shows two figures in silhouette, seated close together under a shaded structure against a bright yellow background, suggesting a romantic or leisure setting.
A smaller image at the lower right shows a person climbing or pulling themselves up on a rope or sail-like surface over blue water.
More vacation images slide into the collage.
A wide photo on the left shows a person riding a horse along a beach or shoreline, with pale sand and water behind them.
At the upper right, the silhouetted couple remains visible in a warm-toned scene, and below it a sunset or harbor image shows sailboats and masts reflected near the water.
The overall look is like a travel \textbf{brochure} spread, with multiple destinations and \textbf{activities} presented as photographic snapshots.
The collage continues with different leisure scenes.
A large tilted photo at the upper right shows a smiling woman in a swimsuit riding or holding onto a water-skiing or water-sport device, surrounded by spray or pale blue water.
A long photo across the left shows a low, dark silhouette of beach or shoreline at sunset.
A smaller photo at the lower right shows two \textbf{people} standing close together on a beach in front of an orange-gold sunset, their bodies mostly in silhouette.
The commercial then switches to a blue background with a centered photograph of a \textbf{storefront}.
The \textbf{storefront} sign reads “ MEISSNER TRAVEL AGENCY, ” with other shop signage visible above and around it.
Beneath the photo, large white all-capital text reads “ DOWNTOWN KITCHENER, ” and below that, “ 157 KING \textbf{STREET} W. ” The image presents the travel agency as a physical street-level office with a glass \textbf{entrance} and display windows.
A second blue-background location card appears with another \textbf{storefront} photograph.
The sign above the glass-fronted shop reads “ MEISSNER TRAVEL. ” Below the photo, large white text reads “ WESTMOUNT PLACE, ” with “ WATERLOO ” beneath it.
The office interior is faintly visible through the windows, with posters and displays near the \textbf{entrance}.
The final location card shows a Meissner Travel \textbf{storefront} inside a mall.
The red-orange sign above the glass doors reads “ MEISSNER TRAVEL. ” The office appears brightly lit inside, with travel posters and display materials visible through the windows.
Beneath the photo, large white text reads “ CONESTOGA MALL, ” with “ WATERLOO ” below, completing the visual listing of the travel service ’s locations.

% matched lemmas: activity, brochure, entrance, people, storefront, street, walk
\end{textsample}
