\begin{textsample}{POS Dim 8 – 2020 – Score 5.00 – 2020/tv\_com\_2020\_59.txt}  \label{ex:f8_pos_009}
The commercial opens with two women in a softly lit, mint-green bathroom-like setting.
Both wear white sleeveless tops.
A large white “ GARNIER ” wordmark with a green leaf-like “ G ” circle overlays the center of the frame.
One woman holds a small green cosmetic bottle near her face while the other looks toward her.
The next shots keep the same two women in close-up.
They smile and gesture toward the camera while handling the green bottle.
They then apply product to their faces with their fingertips, touching areas around the cheek and under-eye area.
A small green circular “ G ” logo appears in the upper-right corner.
The \textbf{ad} then cuts to a minimalist product presentation : a small green-and-white pump bottle is centered against a white, soft, fabric-like or fluid background.
This transitions to a clearer product display on a pale mint surface : a green bottle and a \textbf{matching} box labeled “ Garnier green labs ” and “ Serum \textbf{Cream}. ” A pineapple slice is partly visible at the left edge, suggesting an ingredient association.
A woman with curly hair then holds the green pump bottle close to the camera, making the product the focal point while her face remains behind it.
The following close-up shows a hand pressing the white pump and dispensing \textbf{cream} into an open palm.
The commercial presents three ingredient/product variants in graphic product shots.
One shows the green bottle against a yellow pineapple background with readable text : “ vitamin c + pineapple extract. ” Another shows a red watermelon background with “ hyaluronic acid + watermelon extract. ” A third shows green leaves with “ niacinamide b3 + cannabis sativa seed oil. ” The product bottle remains centered in each composition, with the ingredient text placed around it.
The next shots return to people applying the product.
A woman rubs \textbf{cream} onto her cheek while on-screen text at left reads “ CLEAN, ” followed by “ NO mineral oil, ” “ NO parabens, ” and “ NO dyes. ” Another close-up shows a woman applying product below both eyes ; the left-side text reads “ VEGAN FORMULA ” and “ NO animal-derived ingredients. ” The setting shifts outdoors.
Several close-ups show different women near green metal \textbf{stair} railings and an exterior building structure.
One woman rests her head near a green rail ; another, wearing a yellow top, touches her neck while seated or leaning near \textbf{stairs}.
A third woman smiles upward in a bright outdoor shot.
The green circular “ G ” logo remains in the upper-right corner.
The women then appear together in pairs and as a group on an exterior \textbf{staircase} with green railings and a building façade behind them.
They pose, lean on the railing, and move down the \textbf{stairs}.
Their clothing includes sleeveless tops, shorts or skirts, and casual summer-like outfits.
Near the end, the \textbf{ad} returns to a clean product lineup : multiple green-and-white boxes and a central green pump bottle arranged on a pale mint surface.
The visible product family includes variants such as “ Canna-B, ” “ Hyalu-Melon, ” and “ Pinea-C, ” though some smaller label text is not fully legible.
The final shots show four women standing together outdoors in front of large green leaves and the metal \textbf{staircase}.
A large green circular “ G ” logo overlays the center in one frame, and the final frame shows the group posing with a white “ GARNIER ” wordmark across the lower center.

% matched lemmas: ad, cream, match, stair, staircase
\end{textsample}
