\begin{textsample}{POS Dim 8 – 1960 – Score 6.00 – 1960/tv\_com\_1960\_4.txt}  \label{ex:f8_pos_084}
The commercial opens in a reddish, softly tinted \textbf{street} scene lined with old-fashioned telephone booths.
The word “ TELEPHONE ” appears above each booth.
Parked cars fill the foreground, their rounded roofs and windshields framing a heavyset, middle-aged man in a dark \textbf{suit} and \textbf{brimmed} hat as he \textbf{walks} toward the center booth.
He pauses with his back partly to us, then turns slightly sideways near the booth door.
He raises a large dark briefcase or \textbf{folder} up in front of him as if trying to manage it in the tight space, his body close to the booth \textbf{entrance}.
A passerby in a lighter jacket briefly crosses in front, partially blocking the view.
The scene changes to a tight domestic or public seating area with padded, tufted chair backs on both sides.
A woman in a fitted dress is seen mostly from the waist and hips as she tries to move through a narrow gap between the upholstered chairs.
The chairs have pale, buttoned cushions with rows of dark nailhead trim.
Her skirt brushes close to both sides, emphasizing how little room there is as she squeezes through.
Inside a car, the focus is on a large-bodied person in the driver ’s seat.
The steering wheel sits close to the person ’s abdomen, leaving very little space between belly and wheel.
The person ’s hands are near the wheel, and the dashboard and front seat frame the cramped interior.
Another vehicle interior follows : a woman in a pale hat and light coat sits upright, while a larger figure passes very close in the foreground, blocking part of her and pressing through the tight aisle or seating area.
She turns her face downward and to the side, looking uncomfortable or crowded as the other body moves past the back of her seat.
A bathroom appears next.
A striped towel hangs on a rack beside a shower or glass door.
The door slides open, revealing a shirtless, heavyset man wrapped in a towel around his waist.
Only his torso and hips are shown at first.
He stands very close to the shower doorframe, his abdomen nearly touching the edge, again making the space look narrow.
The towel sits low around his waist, and the reddish lighting highlights the curve of his stomach as he shifts within the doorway.
At a dining table, a woman in a short-sleeved dress sits on a white folding chair.
The view centers on her side and lap as she leans toward the tabletop.
Her hips fill the small chair, and the thin folding legs and back supports are visible around her.
She reaches toward the table with one hand, where dishes and glassware are partly visible.
As she adjusts herself and leans forward, the chair looks undersized beneath her.
In a narrow aisle lined with shelves full of books, two adults are squeezed back-to-back.
A blonde, middle-aged woman in a light \textbf{suit} stands on the left, and a heavyset man in a dark \textbf{suit} stands on the right, facing the bookshelves.
Their backs press together in the cramped passage.
The woman glances over her shoulder with a strained, annoyed expression, while the man looks toward the books with a faint, \textbf{awkward} smile.
They both shift slightly, but neither has much room to move.
Back outside among parked cars, a heavyset man in a dark \textbf{suit} is wedged between two vehicles : a darker car on the left and a pale car on the right.
He raises a large rectangular briefcase above his head, then lowers it awkwardly as he tries to get himself into the narrow space by the car door.
His shoulders and torso press close to the pale car ’s side.
He bends and twists, struggling to fit himself and the briefcase into the car.
Eventually the dark car door stands open, then closes, leaving only the vehicles in view.
An elevator doorway appears crowded with \textbf{people}.
A short, balding, middle-aged man in a dark \textbf{suit} and narrow tie stands at the front, facing outward.
Behind him are several passengers packed closely together : a woman in a red coat with a pale collar, a man in a light trench coat, another man in a hat, and other partially visible faces.
The balding man lowers his head and steps or shuffles forward slightly, but the group remains tightly pressed together behind him.
He looks ahead with a resigned, neutral expression while the others watch or look around.
The sliding elevator door begins to close from the right, narrowing the opening until the crowded group is almost completely hidden.
The visual focus then shifts to the product demonstration.
A white teacup filled with a dark hot drink sits on a saucer, with a small spoon resting beside it.
Above the cup, a pointed white dispenser tip hovers over the surface, suggesting drops of sweetener being added.
A hand then brings in a tall, clear, tapered bottle and sets it beside the cup.
The bottle has a red lower section, a pale oval label, and a long white pointed cap.
The label reads “ Sucaryl, ” with small icons underneath that resemble food and drink items, such as a cup, fruit, and a tall glass.
A hand in a jacket sleeve steadies the Sucaryl bottle next to the cup, then points toward the label and the cup, drawing attention between the sweetener and the drink.
The view moves closer to the label so the word “ Sucaryl ” fills most of the image.
A finger points near the bottle as the view travels upward along the container ’s shape, from its wider body to its narrow neck and long, thin, pointed white cap.
The finger reaches the tip and presses or taps near it, emphasizing the sharp, slender point.
Finally, the bottle stands upright on the left beside the cup on the right.
The Sucaryl label remains visible, and the cup of dark drink sits on its saucer with the spoon nearby.
A hand reaches to the cup, touches the handle, and gently lifts it from the saucer, leaving the tall, pointed Sucaryl bottle standing prominently beside it.

% matched lemmas: awkward, brim, entrance, folder, people, street, suit, walk
\end{textsample}
