\begin{textsample}{POS Dim 8 – 2010 – Score 6.00 – 2010/tv\_com\_2010\_118.txt}  \label{ex:f8_pos_032}
The commercial begins inside a house, with a low-angle view from a \textbf{staircase}.
A person, visible only from the waist down, carries or drags a full white plastic trash \textbf{bag} with red drawstrings down carpeted \textbf{stairs}.
Household décor such as framed pictures, a thermostat, and furniture are visible in the background.
The next shot cuts to an outdoor hot tub or spa area.
A person ’s feet in flip-flops stand near the edge while the same type of full white drawstring \textbf{bag} is positioned beside the water.
Small white \textbf{fine} \textbf{print} appears along the bottom of the frame, but it is difficult to read fully ; it appears to reference data and dates.
The \textbf{bag} is then shown being pulled along a hallway or indoor floor.
The camera remains low, focused on the \textbf{bag} and the red drawstring as it moves across the floor.
The lower part of a person ’s leg is visible at the side.
The sequence continues with closer shots of a person ’s hand gripping the red drawstrings.
One shot is outdoors near what looks like a porch or deck railing, with soft background blur.
Another shot shows the \textbf{bag} being held indoors next to a person wearing blue plaid pajama pants.
The \textbf{bag} is then carried outside through a garden or yard area \textbf{decorated} with colorful balloons and a table in the background, suggesting a party or gathering setting.
The camera again focuses on the lower body of the person and the full white \textbf{bag} hanging from the red drawstrings.
A later shot shows a garage with a blue vehicle parked inside and shelves full of household items.
On the right edge, part of a person wearing a pink striped shirt is visible holding a red drawstring, with a trash bin or container partly visible at the bottom foreground.
The commercial then transitions to a bright yellow product display.
A box of Glad trash \textbf{bags} appears against a yellow background.
The packaging shows the red “ GLAD ” logo and an image of a white drawstring trash \textbf{bag} sitting in a bin.
The product text visible on the box includes “ Tall Kitchen ” and “ Drawstring \textbf{Bags}. ” In the final product frame, large red text appears beneath the box : “ Strength that saves. ” The commercial ends on a black screen.

% matched lemmas: bag, decorate, fine, print, stair, staircase
\end{textsample}
