\begin{textsample}{POS Dim 8 – 2000 – Score 10.00 – 2000/tv\_com\_2000\_43.txt}  \label{ex:f8_pos_006}
A dark, blue-toned \textbf{city} appears before dawn, with the Manhattan \textbf{skyline} in the distance and a suspension bridge stretching toward it.
The bridge walkway is empty except for a small white chicken moving along the center line, an odd, quiet figure against the wet, gloomy \textbf{city}.
The \textbf{streets} also look slick with rain, reflecting building lights and the heavy clouds overhead.
In the \textbf{city}, chickens and roosters begin appearing in places where \textbf{people} or traffic would normally be.
At an empty intersection, several brown chickens stand and move across broad white crosswalk lines beneath tall buildings, including a pointed, triangular-topped tower in the background.
On a narrow cobblestone \textbf{street} lined with old buildings and hanging signs, two chickens stand at the left edge, looking down the deserted road.
A close view of a rooster follows : it has golden-brown feathers, a red comb and wattles, and its beak opens wide as if crowing, the blurred \textbf{city} canyon behind it glowing pale blue.
More birds gather on urban objects.
Three chickens stand on the roof of a yellow taxi, balanced around the taxi sign and license plate area ; one white rooster is centered and upright, with brown chickens on either side.
In a brighter, neon-lit commercial \textbf{street} resembling Times Square, several brown chickens rush across the wet roadway, their bodies low and legs extended mid-stride.
Reflections from signs and streetlights streak across the pavement as the birds cross from both sides.
Back on the bridge, a tall white rooster runs directly toward the viewer along the walkway ’s greenish center stripe, with darker chickens following behind near the railings.
The bridge cables and metal latticework frame the birds as they advance under the same moody blue sky.
The scene then moves underground or beside a train : a row of chickens crowds along a narrow platform next to glossy train doors.
A white rooster hurries past in the foreground, its tail feathers fanned out, while brown chickens peck and jostle near the door openings.
At a subway \textbf{entrance} on a \textbf{city} sidewalk, roosters and hens move around the stairwell railings.
A black station sign reads “ West St Station, ” with route numbers that appear to include “ 1 ” and “ 2. ” The birds cluster at the top of the stairs and pass in front of the sign, their red combs and pale feathers catching the cool light from below.
The scale suddenly expands.
A huge crowd of chickens fills a financial district \textbf{street} and the steps of a grand columned building.
Thousands of birds pack the plaza and roadway, surrounding a statue on a pedestal in front of the building.
Close views show roosters and hens pressed together in the foreground, their feathers ranging from white to tan to deep brown, with tall skyscrapers leaning over them.
Some birds stand on ledges and stone barriers, looking outward like sentries.
Others crowd the steps beneath the massive columns, their heads \textbf{bobbing} and beaks open as if answering the earlier crowing.
Daylight begins to break between tall buildings.
A narrow slice of sun appears at the edge of a high-rise, growing brighter and sending lens-like flares across the \textbf{street} canyon.
The light washes the previously blue, nocturnal \textbf{city} with a warmer glow.
The roosters remain gathered on stone ledges and in the plaza below, many with open beaks and raised heads.
One white rooster stands high on a rounded dark surface in front of the classical building, overlooking the enormous flock spread across the \textbf{street} below.
Three brown chickens perch on metal railings, facing different directions while the crowd of birds continues to fill the background.
From above, the flock becomes a dense, shifting mass in the \textbf{streets}, like a moving pattern of small dark and pale shapes.
A wider \textbf{city} view shows the birds spilling down an avenue away from the columned building, occupying the road between tall office blocks while a few vehicles sit off to the sides.
The \textbf{city} appears to be waking up, but the chickens have taken over the \textbf{streets}.
The commercial then shifts from the rooster-filled \textbf{city} to broader urban scenes.
A high, almost map-like view looks straight down on blocks of buildings and \textbf{streets}, with sunlight striking rooftops and \textbf{facades}.
The perspective pulls away into a larger grid of the \textbf{city}.
On the ground, a sidewalk and \textbf{street} are littered with scattered boxes, bags, and debris near a white service or sanitation truck.
Loose papers and trash blow across the pavement, suggesting the \textbf{city} is busy and unsettled.
Another \textbf{street} scene shows tall buildings framing an avenue where a dark utility truck moves through a gray, misty intersection.
A white \textbf{city} bus crosses in front of a dramatic burst of water or steam erupting from the \textbf{street}.
Orange-and-white traffic barrels and barriers sit near the disturbance, and mist spreads across the road.
From a low angle, the bus looms large as it drives past, headlights glowing, while debris and dark fragments swirl behind it in the bright, backlit haze between the buildings.
The view then rises far above the \textbf{city}.
Lower Manhattan appears as a compact cluster of skyscrapers surrounded by water, softened by morning haze.
The \textbf{city} recedes until it becomes small within a broad expanse of blue-gray \textbf{atmosphere}.
The image continues outward to the curve of the Earth from space.
Clouds, \textbf{ocean}, and landmasses are visible beneath a dark sky dotted with faint stars.
Sunlight grows at the edge of the planet, brightening into a strong glow that spills over the horizon.
The final image becomes a clean, pale background with a blurred blue-and-green “ ca ” mark emerging.
A thin black circle appears to the left of the letters, overlapping the blue “ c ” as the logo sharpens.
Beneath it, gray text reads “ Computer Associates. ” The ending is simple and uncluttered, identifying the company after the sweeping sequence of citywide roosters, morning light, urban \textbf{activity}, and the Earth from space.

% matched lemmas: activity, atmosphere, bob, city, entrance, facade, ocean, people, skyline, street
\end{textsample}
