\begin{textsample}{POS Dim 8 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_53.txt}  \label{ex:f8_pos_080}
The commercial is in black and white and appears to take place in a mountainous, wooded outdoor area.
It begins with a very dark frame in which little is visually distinguishable.
The next shot is framed as if seen through binoculars : a campsite or picnic area is visible, with a folding table, a cooler or box, and a striped umbrella or tent-like structure.
A bear-like animal is near the table, apparently investigating the area.
The view then cuts to a close-up of a man wearing a broad-brimmed hat and uniform-like clothing, looking through binoculars.
He lowers or adjusts the binoculars.
In a wider outdoor shot, the same man stands beside a white car, with other vehicles or equipment behind him.
He appears to move toward the car.
Several close shots show the car interior, including dark upholstered seats.
The man, still wearing the hat and uniform-like jacket with a badge-like emblem, gets into the vehicle.
A side view shows the white car parked on a dusty mountain road with hills and trees in the background.
A close-up focuses on one of the car ’s wheels.
The car then begins moving along rough, unpaved roads, kicking up dust.
The commercial then alternates between exterior driving shots and interior shots of the driver.
The car travels along winding dirt roads on hillsides, past pine trees and open mountain views.
Dust trails behind it.
Interior shots show the man holding the steering wheel and concentrating on the road.
There are moments of strong sunlight and lens flare through the windshield, briefly washing out parts of the image.
The car continues through wooded areas, seen from the front and side, moving quickly on dusty roads.
It passes through forested terrain with tall trees and uneven ground.
The driver remains focused, with both exterior and interior shots emphasizing motion, dust, and rough-road driving.
Near the end, the car \textbf{arrives} back near a campsite or picnic area.
A wide shot shows the car approaching through trees.
Another shot shows a bear near trash cans or containers beside a structure or campsite area.
The final exterior shots show the white car parked or slowing near the picnic site, with the man standing beside or near the car and equipment in the foreground.
The last frame shows a scenic mountain background with large white text overlaid : “ American Motors quality built in not added on ”

% matched lemmas: arrive
\end{textsample}
