\begin{textsample}{POS Dim 8 – 2010 – Score 7.00 – 2010/tv\_com\_2010\_47.txt}  \label{ex:f8_pos_027}
A wooden table is covered with Taco Bell food in close view : a folded taco or breakfast taco sits to the left, a long wrapped burrito or rolled item lies to the right, and small piles of cheesy, diced toppings and sauce are scattered across paper wrappers and plates.
In the softly blurred background, several \textbf{people} stand around what looks like a casual indoor gathering or kitchen.
Over the food, a white Taco Bell logo appears with the words “ Wake Up ” and “ Live Más. ” A hand reaches in near the right side as if someone is picking up or preparing to eat the food.
The scene then changes to a dark, aged-looking surface, like the cover of a \textbf{leather} book or wooden plaque.
A gold emblem with \textbf{wings} and circular linework reads “ Innovators Club, ” with “ Five Years Out ” below it.
In white text at the lower left, a profile appears : “ Serena S, ” “ Industrial Designer, ” and “ Member Since 2009. ” The styling suggests an exclusive, old-fashioned club record or membership introduction.
The setting shifts into a warm, dimly lit formal room with a vintage \textbf{atmosphere}.
Several \textbf{people} stand together in evening clothes, gathered as if at a private club reception.
On the left, an older white man with long gray hair and a dark formal coat faces the group.
Beside him stands a tall, slim white man in an old-fashioned dark \textbf{suit} with a high-collared white shirt.
A young woman with long dark hair, wearing a sleeveless black dress, stands near the center, facing a young man in a black \textbf{suit} or tuxedo.
To the right, another man in a tuxedo and bow tie watches the exchange.
In the foreground, a seated bald man in formalwear is partly visible, and a small shaded lamp glows on a table between the central figures, adding to the club-like, historical \textbf{mood}.
As the group continues interacting, the tall man smiles and leans slightly toward the woman, while the young man in the \textbf{suit} turns toward her as if introducing her or presenting her to the others.
The woman smiles modestly, looking between the men around her.
The older gray-haired man on the left observes with a reserved expression.
The gathering remains close and conversational, with everyone standing shoulder to shoulder in the warmly lit room, visually suggesting that Serena is being \textbf{welcomed} into this “ Innovators Club ” among notable, old-fashioned figures.

% matched lemmas: atmosphere, leather, mood, people, suit, welcome, wing
\end{textsample}
