\begin{textsample}{POS Dim 8 – 2020 – Score 3.00 – 2020/tv\_com\_2020\_79.txt}  \label{ex:f8_pos_016}
The commercial begins inside a clothing or department-store setting.
A woman with shoulder-length reddish hair stands in the foreground, facing toward the camera.
She wears a green-and-white striped sweater over a white collared shirt, with a crossbody strap visible across her chest.
Behind her are racks and shelves of folded or hanging clothing in a softly lit retail environment.
The scene then cuts abruptly to a bright magenta/pink graphic background.
The background contains semi-transparent rectangular shapes and faint repeated “ DEALS ” text along the right side.
Small fine-print text appears near the bottom, but it is too small to read clearly in the sampled frame.
Next, the commercial displays a promotional collage on the same magenta background.
Large bold white text in the center reads “ SAVE UP TO 50 \%. ” Around the text are product images in white-bordered boxes, including folded clothes, boots, ornaments or \textbf{holiday} decorations, a handbag, knitwear, clothing sets, a scarf or blanket, baskets, and other apparel/accessory items.
The layout becomes more densely filled over the next frames, with additional product images appearing or sliding into view around the central “ SAVE UP TO 50 \% ” message.
Fine-print legal text remains along the bottom but is mostly unreadable at this resolution.
The graphic then transitions to a new promotion.
Large bold white text reading “ CLEARANCE ” appears across the magenta background.
The word is positioned prominently, first toward the lower/right area and then more fully across the left side as the framing changes.
The background continues to use abstract rectangles, diagonal dark red shadow shapes, and faint repeated “ DEALS ” text.
In the final frame, the clearance message is expanded : large white text reads “ CLEARANCE ” at the upper left, with “ SAVE UP TO 85 \% ” centered below it in very large bold numerals.
Smaller text beneath reads “ AFTER AN EXTRA 50 \% OFF. ” Additional \textbf{fine} \textbf{print} appears at the bottom but is too small to read clearly.
The overall visual style is a bright, high-contrast retail sale graphic emphasizing discount percentages and clearance deals.

% matched lemmas: fine, holiday, print
\end{textsample}
