\begin{textsample}{POS Dim 8 – 1960 – Score 4.00 – 1960/tv\_com\_1960\_27.txt}  \label{ex:f8_pos_089}
The commercial is in black and white and begins in a bright, tidy home kitchen.
A middle-aged woman with short dark hair stands at a kitchen counter in a dark dress, a light apron tied at her waist, and a necklace.
She is busy preparing food, stirring or mixing something in a large pot or bowl on the counter.
Around her are domestic kitchen items : a pepper grinder, utensils, dishes, and shelves with plates and glassware.
A tall refrigerator stands on the right side of the room.
A middle-aged man in a light sweater and dark trousers \textbf{walks} in behind her, then turns toward the refrigerator.
While the woman continues working, he opens the refrigerator door and reaches inside.
He takes out a dark glass Coca-Cola bottle and brings it back toward the counter, where a small glass sits nearby.
A young woman, likely a teenager or young adult, enters from the right.
She wears a light blouse tucked into a full plaid skirt.
She moves casually into the kitchen and stands near the counter and refrigerator area, joining the \textbf{conversation} with the man in the sweater while the woman at the counter keeps preparing food.
The young woman briefly holds or stands beside a Coca-Cola bottle on the counter, and the older woman glances over from her work.
The family members are clustered around the kitchen island and refrigerator, suggesting a busy household getting ready for guests or a meal.
A closer view inside the refrigerator shows several Coca-Cola bottles standing upright on a shelf, their white script logos visible against the dark glass.
The man in the light sweater reaches in and handles one of the bottles, then the refrigerator door closes.
Back in the wider kitchen view, the woman continues working at the counter.
Another man enters from the back doorway, older than the young woman but younger-looking than the parents, wearing a darker buttoned shirt.
He carries a small plate or bowl and steps up to the counter.
The man in the light sweater sets a glass down and handles a Coca-Cola bottle nearby.
The newcomer takes a bottle and drinks from it while still holding his plate, standing between the woman at the counter and the man in the sweater.
The scene becomes more crowded, with \textbf{people} moving around the kitchen as food and bottles accumulate on the counter.
The older woman then goes to the refrigerator herself.
She opens the tall door and leans in to look at the shelves.
Inside are several Coca-Cola bottles lined up on an upper shelf, along with other food containers and refrigerator items.
She points toward the bottles as if counting them or checking the supply.
The dark-shirted man stands just to her left, watching.
She turns back from the open refrigerator with a concerned, questioning expression and gestures toward him.
He responds with a broad arm gesture, spreading his arms as if indicating there is more somewhere else.
Her expression softens.
She steps closer to him and affectionately straightens or pats the front of his shirt near the collar, then rests her hands lightly on his shoulders.
Behind them, the refrigerator remains open, with the row of Coca-Cola bottles still visible on the shelf.
The scene shifts to a dining room where a group of \textbf{people} sit closely around a round or oval table.
The table is crowded with serving dishes, plates, glasses, and Coca-Cola bottles.
The older woman sits among the guests, facing forward, while several men and women sit around her.
Curtains, a window, and home furnishings in the background give the room a warm domestic \textbf{atmosphere}.
Everyone appears settled in for a shared meal, with bottles and glasses placed within easy reach.
A young woman with shoulder-length hair smiles at the table, holding a glass, while a young man beside her sits with a bottle or glass in hand.
Both appear relaxed and cheerful.
Another view at the table shows the older woman beside the dark-shirted man.
A large piece of meat or a loaf sits on the table near a Coca-Cola bottle with the logo visible.
The man pours Coca-Cola from a bottle into a glass, then both he and the woman lift their glasses and drink.
More bottles and filled glasses are visible among the dishes, visually tying the meal to the soft drink being served.
The final moments return to the kitchen refrigerator.
The older woman stands beside the open refrigerator, smiling directly outward while holding a Coca-Cola bottle in one hand.
Behind her, the refrigerator is now well stocked with many Coca-Cola bottles lined up in neat rows on the shelves.
She turns slightly and gestures toward the supply, presenting the bottles.
The view moves closer to the refrigerator shelf : dark glass Coca-Cola bottles fill the space, their white script labels clearly visible across the front.
Below the bottles, a row of eggs sits on a lower shelf.
A hand reaches in and adjusts or takes hold of one bottle among the lineup, emphasizing the abundance.
The commercial ends with the refrigerator shelf dominated by multiple Coca-Cola bottles, arranged side by side and ready to serve.

% matched lemmas: atmosphere, conversation, people, walk
\end{textsample}
