\begin{textsample}{POS Dim 8 – 2010 – Score 9.00 – 2010/tv\_com\_2010\_42.txt}  \label{ex:f8_pos_031}
The commercial opens with a sequence of individual men in different locations, many shown eating or holding food, before ending with a product display.
At the start, a man stands outdoors on a city street or residential block with \textbf{stairs} and buildings behind him.
He looks down while holding a small rectangular food container.
The scene then cuts to a man in what appears to be a workshop or garage.
He wears a work shirt and holds a wrapped item close to his face, as if about to eat or smell it.
Next, an older man indoors stands in front of windows with blinds and takes a bite from a folded food item.
Another man in an office-like interior, wearing glasses and a light button-down shirt, eats while holding a small container with more food.
The commercial then shows a bald man in a suit and a bright bow tie standing in a formal interior with a \textbf{staircase} behind him.
He faces the camera.
The next shot moves outdoors to a lawn in front of a large house.
A man in a gray work shirt stands near a white \textbf{utility} truck.
On-screen text identifies him as “ Ronald McDonald ” and gives the location “ Bossier City, LA. ” A living-room scene follows, showing a teenage boy and an older man seated in armchairs.
Both face forward.
The same lower-right text style identifies “ Ronald McDonald ” with the location “ Dubuque, IA. ” A close-up then focuses on the teenage boy seated against patterned upholstery, with the same “ Ronald McDonald / Dubuque, IA ” text still visible.
The commercial cuts to a man outdoors near a barn-like building and a green tractor.
He holds food in one hand.
Lower-right text reads “ Ronald McDonald ” and “ Worcester, MA. ” In a following closer shot, he looks down and handles the food item.
The man in the gray work shirt from the lawn scene reappears holding a Taco Bell-style food box.
The \textbf{utility} truck and house remain in the background, and the lower-right text again reads “ Ronald McDonald / Bossier City, LA. ” A different man, wearing a black sweatshirt, stands outside in front of a storefront window with cursive lettering partly visible behind him.
He holds a small food box.
Lower-right text reads “ Ronald McDonald / Chicago, IL. ” The bald man in the suit and bow tie reappears indoors by the \textbf{staircase}, now holding food with both hands.
The lower-right text identifies him as “ Ronald McDonald / Kane, PA. ” Several more men appear in quick succession, each facing the camera in different outdoor settings.
One older bald man is labeled “ Ronald McDonald / Plaucheville, LA. ” Another man stands in front of a modern-looking building façade and is labeled “ Ronald McDonald / Whispering Pines, NC. ” Another man in a black T-shirt holds a small piece of food outdoors, with lower-right text reading “ Ronald McDonald / Hyattsville, MD. ” The commercial then cuts to a large group shot in a plain studio-like room.
Many men of varying ages stand and sit together, all facing the camera.
Small disclaimer text appears along the bottom ; it is partially legible and \textbf{states} that the Ronald McDonalds shown are not affiliated with McDonald ’s Corporation and were individually selected as paid endorsers of Taco Bell breakfast, though the full text is small and difficult to read completely.
The final section shifts to a close-up tabletop product display in a bright kitchen or counter setting.
Several breakfast items are arranged on wrappers and trays : folded tacos or burrito-like items filled with eggs and other ingredients, round bite-sized pastries or doughnut-hole-like items, a drink cup, a black cup labeled “ COFFEE, ” a \textbf{bag}, and packaging with Taco Bell branding.
Small \textbf{fine} \textbf{print} along the bottom \textbf{mentions} participation/locations and that \textbf{hours} may vary, though it is partly difficult to read.
The last frame adds a large central white graphic over the food display.
It shows the Taco Bell logo and the text “ TACO BELL, ” “ OPEN 7AM, ” and “ OR EARLIER. ” The breakfast food and coffee remain visible behind and around the graphic.

% matched lemmas: bag, fine, hour, mention, print, stair, staircase, state, utility
\end{textsample}
