\begin{textsample}{POS Dim 8 – 2020 – Score 5.00 – 2020/tv\_com\_2020\_82.txt}  \label{ex:f8_pos_058}
A bright T-Mobile magenta screen fills the view, with the white square T-Mobile “ T ” logo centered.
The logo then appears over a sunlit desert road, where a magenta streak sweeps across the image before clearing to reveal a long, cracked two-lane road stretching through scrubby desert toward low hills and a blue sky.
Far in the distance, a pickup truck crests the rise and drives toward the viewer.
The silver pickup approaches head-on, centered on the road, its headlights glowing.
Dry brush and sandy shoulders line both sides, and the late-day light casts long shadows across the pavement.
A small magenta T-Mobile-colored plate or accent is visible on the truck ’s front.
Inside the truck, a middle-aged white man with a close-cropped beard and mustache drives.
He wears a black baseball cap pulled low, a green-and-blue plaid button-up shirt, and dark bracelets on his wrist.
He sits upright behind the wheel, one arm extended to steer, glancing toward the side as if addressing someone just outside the viewer ’s perspective.
Through the window behind him, the desert landscape passes by, including a Joshua tree and pale sand under a clear sky.
His expression is direct and conversational, with a slight squint from the bright light.
The truck pulls off near a roadside area in the desert.
In profile, the front half of the silver pickup rolls into view on dusty ground beside a tall roadside sign structure.
The background shows open desert, distant mountains, and a few scattered signs.
Under the truck, a pair of brown boots steps down onto the dirt, the man climbing out from the driver ’s side.
The wider view reveals the truck parked at left beside a tall sign.
At the top is a large pink T-Mobile “ T ” logo, mounted above an oval sign that reads “ Best Network. ” The sign stands in the middle of the desert roadside, with mountains behind it and the sky still bright.
The man is now outside the truck, small in the scene near the vehicle.
He then stands facing forward on the roadside, with the desert and road behind him.
He is still wearing the black cap and plaid shirt, and his face is lit warmly by the sun.
Small white legal text appears along the bottom of the screen, including the readable claim “ T-Mobile : Best Mobile Network in the U.S. ” followed by finer print that is too small to fully make out.
He smiles more broadly as he continues addressing the viewer.
The setting changes to the front of a low, retro roadside building in the desert.
The building has a pale mint-green façade, double glass doors in the center, windows with blinds, star decorations near the roofline, and a vertical neon-style sign on the right side.
Across the roof, large pink \textbf{illuminated} letters spell, “ It ’s better over here. ” The same man \textbf{walks} from left to right in front of the building, now holding a phone in one hand and looking down at it as if checking or using it while he \textbf{walks}.
As he continues past the \textbf{entrance}, the full \textbf{storefront} becomes more visible.
To the right is a service-window or diner-like section with a red trim band, vending or menu-style signs, a green trash can, and desert hills beyond.
The pink roof sign remains prominent above him, glowing against the evening sky : “ It ’s better over here. ” The view widens to show the building set beside a highway running into the desert, with Joshua trees, parked vehicles, low mountains, and a warm sunset gradient in the sky.
The man appears small below the sign as he pauses near the front of the building.
The commercial ends on a solid T-Mobile magenta screen.

% matched lemmas: entrance, illuminate, storefront, walk
\end{textsample}
