\begin{textsample}{POS Dim 3 – 1950 – Score 6.00 – 1950/tv\_com\_1950\_97.txt}  \label{ex:f3_pos_008}
If you feel like this, instead of feeling like this, put yourself in a driverized cab of a new Ford economy truck.
This cab is new all the way.
A push-button handle opens an all-steel safety door that 's nearly a full yard wide.
This new gooseneck hinge lets the door swing open extra wide for easy entrance.
When you step inside, you slide onto a \textbf{seat} that is wide enough for three \textbf{men}.
Ford makes the only truck \textbf{seat} that gives you such comfort features as the new non-sag springs, the exclusive \textbf{seat} shock snubber, and a backrest that is independently adjustable.
And in the Ford driverized deluxe cab, you 'll find 16 custom extras like this foam \textbf{rubber} cushion available at slight additional cost.
Check this new driverized truck cab for visibility unlimited.
Sweep your eyes across this big one-piece curved windshield.
Even the rear window is over four feet wide.
All in all, this new Ford driverized cab has over 2,100 square inches of glass area for safer driving.
Notice how \textbf{deep} these side windows are. \textbf{Man}, what comfort.
Before you buy any truck, stop in at your Ford \textbf{dealers} and take a 15-second sit-down test.
See the world 's \textbf{most} comfortable truck cab.
It 's new, it 's driverized, and only Ford has it.
See the Ford E-Class.
Economy trucks, sold.

% matched lemmas: dealer, deep, man, most, rubber, seat
\end{textsample}
