\begin{textsample}{POS Dim 2 – 2020 – Score 22.00 – 2020/tv\_com\_2020\_113.txt}  \label{ex:f2_pos_045}
The commercial begins at \textbf{night} on a wet suburban street lined with houses decorated in warm white holiday lights.
A large white Toyota pickup faces forward in the road or driveway, its bright headlights glowing against the dark, reflective \textbf{pavement}. \textbf{Snow} or slush borders the curb, and the house in the background has lit windows and Christmas decorations.
At the left edge, only part of a person is visible, standing close to the \textbf{vehicle} ’s \textbf{path} in a light sweater and dark pants.
As the \textbf{truck} ’s headlights shine toward them, the scene has a secretive, after-dark holiday feel.
The setting changes to daytime in a residential driveway.
The open rear hatch of a \textbf{vehicle} frames a young boy leaning into the cargo area.
He has medium-length brown hair and wears a green hoodie.
Inside the back are household items, including a red fabric \textbf{bundle} and a gray-and-black round item that looks like a portable seat, tub, or carrier.
The boy reaches in quickly, then turns and pulls items out.
Outside the \textbf{vehicle}, he \textbf{hurries} beside a gray \textbf{sedan} with its \textbf{trunk} open.
A young woman, likely a teenager or young adult, with long dark hair, a cream-colored fleece jacket, red top, blue jeans, and brown \textbf{boots}, steps in to help.
She steadies him with one hand as he moves aside, and the open \textbf{trunk} reveals a red, white, and black \textbf{bundle} with white handles placed inside.
A middle-aged man walks out of the house carrying golf gear.
He wears a white visor, a light zip-up top, a dark quilted vest, gray pants, and black sneakers.
A brown leather golf bag hangs over his shoulder, with clubs and other items tucked in.
The house behind him has a red tile roof, pale stucco walls, and holiday decorations, including a large candy-cane ornament near the entry.
He checks his wrist as if looking at a watch, then pauses with a mildly suspicious or puzzled expression, looking toward the driveway.
The young woman and the boy face him, smiling and waving as though sending him off.
The man then loads the bulky golf bag into the open cargo area of a blue Toyota SUV parked beside the gray \textbf{sedan}.
The SUV ’s rear hatch is raised, and the man leans in to \textbf{push} the bag into place while the two younger family members stand nearby watching.
Another holiday errand unfolds in a public shopping area or town street.
A man in a dark puffer vest and long-sleeved shirt walks away from the viewer with a small red gift box \textbf{hidden} behind his back.
The box is wrapped with a wide white ribbon and bow.
He approaches a silver Toyota \textbf{sedan} parked near a large \textbf{outdoor} Christmas \textbf{tree} decorated with red and gold ornaments.
The street is wet and festive, with storefronts, wreaths, and people in the background.
He opens the driver ’s door and gets in.
Inside the car, he lowers the small wrapped gift near the center console, trying to conceal it.
He then looks up and turns with a surprised expression.
Across the cabin, a woman seated in the front passenger seat smiles knowingly at him, suggesting she has caught him trying to \textbf{hide} the present.
The scene shifts back to a home at \textbf{night}, warmly lit from inside.
In a garage or entryway, figures move near an open red \textbf{vehicle} with holiday decorations visible beyond.
A young Black boy in light-colored pajamas with a green pattern stands on an indoor landing behind a metal stair railing.
He grips the \textbf{rail} with both hands and watches what is happening below.
A dartboard, framed picture, and stored household items hang on the wall behind him.
His face is alert and curious, as if he has discovered the adults ’ holiday preparations.
The final holiday reveal takes place outside a snow-covered house.
The same boy now sits in a small red ride-on toy car styled like a Toyota, with a large white bow on the hood.
He wears his patterned pajamas under a dark jacket, and he holds the little \textbf{steering} wheel while looking upward with wide, amazed eyes.
Behind him, family members stand near a full-size red Toyota SUV parked by the garage.
They wear cozy \textbf{winter} or pajama-like clothing, and the garage door is decorated with a wreath and garland.
Snow covers the driveway, shrubs, and roofline.
Fine-print legal text appears along the bottom, noting that the ride-on toy is a third-party product and not a Toyota-manufactured \textbf{vehicle}.
The view widens to show the entire snow-covered home glowing with warm holiday lights.
Large white text appears across the center of the scene : “ Let ’s make joy the holiday mission. ” The boy \textbf{drives} the small red toy car across the \textbf{snowy} driveway while the red Toyota SUV remains parked near the garage and the family watches.
A red square with the white Toyota \textbf{emblem} appears over the house, followed by the black word “ TOYOTA. ” The \textbf{snowy} home fades into a clean white background, leaving the Toyota logo centered on screen.

% matched lemmas: boot, bundle, drive, emblem, hide, hurry, night, outdoor, path, pavement, push, rail, sedan, snow, snowy, steering, tree, truck, trunk, vehicle, winter
\end{textsample}
