\begin{textsample}{POS Dim 2 – 1990 – Score 24.00 – 1990/tv\_com\_1990\_31.txt}  \label{ex:f2_pos_032}
A wide desert canyon opens the commercial, filled with warm golden light.
Red and orange \textbf{rock} \textbf{formations} rise on both sides, with a \textbf{shadowed} valley stretching between them and \textbf{hazy} \textbf{mountains} in the distance.
Against an orange sunset \textbf{sky}, a lone \textbf{silhouetted} figure wearing a large feathered headdress moves along a ridge, holding one arm forward as if carrying or examining something.
The scene shifts to a bird gliding over pale orange desert \textbf{rock}, its dark body and \textbf{shadow} crossing the \textbf{sunlit} \textbf{ground}.
A green lizard then appears on a \textbf{rough} dark \textbf{rock}, its long tail \textbf{trailing} behind it.
It climbs and pauses, alert, with its head lifted against a soft, sandy-colored background.
As the lizard remains perched, the desert landscape \textbf{blends} into \textbf{towering} red \textbf{rock} columns, where \textbf{mountain} bikers begin to appear on a sloped \textbf{trail}.
Several adult cyclists ride through the red-rock terrain.
One rider in a bright orange top leads, with others following behind near the base of tall, weathered sandstone walls.
The riders wear helmets and lean forward over their handlebars as they travel across the uneven, \textbf{dusty} surface.
Close-ups show \textbf{bicycle} wheels and frames bouncing over \textbf{rocks} and dirt, tires kicking up dust as the bikes angle down steep slopes.
A rider crouches low over the handlebars, legs bent and tense, moving through the \textbf{sunlit} \textbf{haze}.
From above, two cyclists are seen on layered sandstone ledges, one in orange near the center and another farther back.
The \textbf{reddish} \textbf{rock} shelves form natural steps and drop-offs, emphasizing the rugged desert setting.
The image \textbf{blends} into a tabletop or cloth surface printed like a map.
A white Jolly Rancher candy package lies among \textbf{outdoor} items : orange cord or sunglasses, a small compass or round lens, and square translucent candies in orange, yellow, green, and red.
The package has a blue stripe and large multicolored letters spelling “ JOLLY RANCHER, ” with the wrapper partly opened at one end.
A close-up of a person ’s mouth follows in warm orange light.
Lips part, and a small square red candy is brought toward the mouth by fingers.
A young boy ’s face appears next, softly lit, looking intently at a red square candy held up near his eyes.
His expression is calm and focused as he studies it.
The imagery returns briefly to a \textbf{bicycle} wheel in close-up, the hub at the center with many spokes radiating outward in a circular pattern.
Then the green lizard reappears on the \textbf{rock}, now holding a bright orange square candy in its mouth.
It grips the candy at the edge, then the candy disappears as the lizard ’s mouth closes, leaving the lizard perched alertly on the \textbf{stone}.
Back on the desert floor, \textbf{rocks} and dust shift across a sandy surface, suggesting loose rubble being disturbed.
The cyclists reappear riding hard through the red dirt.
A woman-presenting adult cyclist in a dark purple cycling outfit, black helmet, and sunglasses rides beside or behind the orange-shirted rider.
She leans forward with gloved hands on the handlebars.
The orange-shirted rider wears a helmet, tan shorts, and bright gloves.
Their bodies are low and athletic as they climb and descend through \textbf{rough} terrain.
Fast close views show a bike wheel cutting \textbf{past} the red \textbf{rock} and then the woman rider navigating loose \textbf{stones}.
Her bike tilts over the rocky \textbf{ground}, her legs and tires surrounded by dust and scattering gravel.
Another close view shows a wheel and rider \textbf{splashing} through shallow water or a wet rocky patch, droplets spraying upward in golden light.
The woman rider ’s face is shown close, partly shaded by a glossy dark helmet and sunglasses, her mouth slightly open as she looks ahead.
The orange-shirted rider is shown close as well, bent over the bars against a dark background, helmeted and concentrating.
A wider view shows a single cyclist riding straight along a rocky \textbf{path} filled with rounded \textbf{stones}, the long \textbf{shadow} of the bike stretching behind.
The scene \textbf{blends} again with a Jolly Rancher package, this time positioned beneath or near a dark \textbf{bicycle} part, as a hand reaches in and pulls at the candy wrapper.
In a playful, surreal moment, a small rider-like figure seems to burst or leap out from the area near the package, then a red-clad cyclist-shaped figure sails through blue \textbf{sky} with one arm raised, as if launched into the open air.
A bike wheel lands back on the \textbf{dusty} slope, \textbf{throwing} up a cloud of red dust.
Two young people appear in warm close-up, smiling and leaning close together.
A blonde young woman smiles with her eyes lowered, while a young man beside her smiles toward her, his face partly in \textbf{shadow}.
Their expressions are relaxed and pleased.
The tabletop returns, showing two Jolly Rancher packages placed side by side on the map-like cloth, with several unwrapped square candies in front of them.
A gloved hand sets the wrappers down.
Nearby are a small round magnifying lens or compass and another black circular object.
The candy squares are glossy and jewel-like, in red, orange, yellow, green, and dark purple-brown tones.
The cyclists ride together again across the desert, the orange-shirted rider in front and the purple-clad rider behind, moving slowly along a \textbf{reddish} dirt \textbf{path} with sparse desert shrubs.
Then the scale becomes fantastical : two tiny cyclists are \textbf{silhouetted} on top of a huge red cherry with a long curved stem.
The giant cherry sits in the desert landscape, with red \textbf{rock} cliffs and blue \textbf{sky} behind it.
The product package rests below in the foreground, labeled “ JOLLY RANCHER. ” The giant fruit changes from a cherry to a large yellow lemon, then to a cluster of purple grapes with green \textbf{leaves}, then to a bright green apple, and then to a triangular slice of watermelon with black seeds.
Each fruit towers above the Jolly Rancher package, set against the same \textbf{sunlit} canyon backdrop.
Finally, a huge glossy red square candy appears floating or standing above the package, its rounded edges and translucent shine making it look like an enlarged Jolly Rancher piece.
Small text in the upper right reads “ Natural and Artificial Flavors. ” The commercial ends with the \textbf{silhouetted} headdress-wearing figure again on the orange horizon, now standing beside a \textbf{bicycle}, one knee lifted near the frame, holding a small object in one hand against the sunset \textbf{sky}.

% matched lemmas: bicycle, blend, dusty, formation, ground, haze, hazy, leaf, mountain, outdoor, past, path, reddish, rock, rough, shadow, silhouette, sky, splash, stone, sunlit, throw, towering, trail
\end{textsample}
