\begin{textsample}{POS Dim 2 – 1980 – Score 10.00 – 1980/tv\_com\_1980\_63.txt}  \label{ex:f2_pos_052}
The commercial is presented in a 4:3 format with black borders at the sides.
It unfolds as a product demonstration and retail end-card. 1. **Opening title/graphic** The first frame is very dark and low-contrast.
A large cursive-style word or logo appears near the top, but it is not clearly legible from the sampled frame.
A lighter rectangular area \textbf{sits} below it, possibly part of a title card or product graphic, but the details are unclear. 2. **Lamp in a \textbf{home} interior** The scene cuts to a lit table lamp with a warm beige shade.
A leafy houseplant is visible on the left against a pale wall.
The lamp is centered and glowing, suggesting a \textbf{domestic} setting and drawing attention to household lighting. 3. **Product box introduced** A product box is shown standing on a \textbf{wooden} tabletop.
The packaging reads **“The Clapper”** in large yellow/orange lettering, with the phrases **“CLAP IT ON! ” ** and **“CLAP IT OFF! ” ** around the name.
The front of the box includes images of hands clapping and smaller demonstration pictures. 4. **Closer view of the packaging** The camera moves closer to the box.
More text becomes visible : **“SOUND ACTIVATED ON/OFF SWITCH FOR APPLIANCES.”** The product is visually presented as a \textbf{device} that controls appliances through sound.
The background remains softly blurred, with chairs or furniture behind the table. 5. **Extreme close-up of product name and claims** The box fills most of the frame.
The large brand name **“The Clapper”** dominates the upper portion.
The slogans **“CLAP IT ON! ” ** and **“CLAP IT OFF! ” ** are clearly printed near the logo.
The text **“SOUND ACTIVATED ON/OFF SWITCH FOR APPLIANCES.”** is also visible on the right side of the package front. 6. **Darkened doorway or hallway** The commercial cuts to a dim interior \textbf{space}.
A doorway with glass panels is visible, with faint outdoor light or reflection through the glass.
A human figure may be present in the darkness near the door, but the details are indistinct.
The scene visually suggests a nighttime or low-light household situation. 7. **Electrical wall outlet** A close-up shows a standard two-socket electrical outlet mounted on a wood-paneled wall.
The outlet plate appears dark or black.
This shot visually \textbf{connects} the product to electrical appliances or household power. 8. **Elderly woman shown close-up** A close-up shows an elderly woman with short white hair.
She is smiling slightly and looking forward.
She wears earrings and a patterned cardigan over a blouse with a bow or tie at the neck.
The background is bright and plain. 9. **White wall-mounted device** A white rectangular \textbf{device} is shown mounted on a wood-paneled wall.
It has vertical grille-like ridges and small switches or controls near the bottom.
This appears to be the product unit or a related sound-activated switch \textbf{device}, though the sampled frame does not show it being handled or installed. 10. **Elderly woman in bed** The elderly woman is now lying in bed under light-colored bedding.
She is smiling, with her head resting on pillows.
A decorative \textbf{wooden} headboard is visible behind her.
The scene presents her as using the product from bed or in a bedroom setting, though no action is visible in this frame. 11. **Bedroom wide shot with lamp and television** A wider bedroom shot shows the elderly woman in bed.
A lit bedside lamp is on near the head of the bed, and a small television with a blue \textbf{screen} \textbf{sits} to the left.
Bedding covers much of the foreground.
Curtains and a \textbf{plant} or bedside arrangement are visible in the background.
The visual arrangement emphasizes \textbf{multiple} household appliances near the bed. 12. **Final product and retailer end-card** The final frame is a black background with \textbf{multiple} graphic elements.
On the left is an image of the product packaging.
To the right is the large logo **“The Clapper”** with the phrases **“CLAP IT ON! ” ** and **“CLAP IT OFF! ” ** nearby.
Additional retailer or promotional logos appear below, including **“Snyder”**, **“CONCEPTS SUPER BUY”**, **“RED OWL.”**, and partially visible text at the bottom reading **“Elliot ’s Ace Hardware”**.
The end-card functions as a product identification and retail availability \textbf{screen}.

% matched lemmas: connect, device, domestic, home, multiple, plant, screen, sit, space, wooden
\end{textsample}
