\begin{textsample}{POS Dim 2 – 2000 – Score 8.00 – 2000/tv\_com\_2000\_12.txt}  \label{ex:f2_pos_040}
The commercial begins on a black \textbf{screen}.
It then cuts to a dimly lit tabletop or kitchen-counter setting viewed from above.
A bowl \textbf{sits} on a placemat under a large orange hanging lamp or lampshade.
The bowl is filled with Reese ’s candy packages and loose candy pieces.
Other objects, \textbf{such} as a mug, papers or a notebook, and small containers, are visible around the table in the shadows.
The camera moves to a lower, closer view of the bowl.
Several orange Reese ’s packages are visible sticking out of the bowl, surrounded by \textbf{many} small round candies in Reese ’s colors.
The background remains dark and kitchen-like, with counters and appliances or cabinets out of focus.
Next, the scene becomes more dynamic.
Pieces of candy and wrapped items appear to rise or swirl out of the bowl into the air.
A Reese ’s package is suspended among a stream of small candies, creating the impression of the candy being animated or flying through the \textbf{room}.
The bowl remains at the lower left of the frame, while the background shows a dark interior with blue-toned windows or cabinets.
A product display follows. \textbf{Multiple} Reese ’s products are arranged together on a blue textured surface.
Visible packages include Reese ’s Pieces, ReeseSticks, Reese ’s Bites, Reese ’s Peanut Butter Cups Miniatures, NutRageous, and a Reese ’s 2 Peanut Butter Cups bar.
At the bottom of the \textbf{screen}, small white promotional text appears.
It reads : “ Free tickets by mail with proofs of purchase from 3 bags or 12 candy bars.
Requests must be received by 8/1/02.
Allow 6 to 8 weeks for \textbf{delivery}.
Up to 6 tickets per household.
See complete details at in-store displays. ” The commercial then returns to a moving candy sequence.
A stream of small round candies and wrapped pieces travels across a dim interior \textbf{space}, as if flying through the air in a curved path.
The background is blurred and appears to be an indoor kitchen or \textbf{room}.
The final shot is a simple brand \textbf{screen} : the Reese ’s logo in yellow script with dark shadowing, centered on an orange gradient background.
The same logo remains on \textbf{screen} through the last frame.

% matched lemmas: delivery, many, multiple, room, screen, sit, space, such
\end{textsample}
