\begin{textsample}{POS Dim 2 – 1980 – Score 15.00 – 1980/tv\_com\_1980\_85.txt}  \label{ex:f2_pos_066}
A young light-skinned man fills the opening view, standing against \textbf{rough}, weather-beaten wooden siding with peeling white paint.
He appears to be in his twenties, with thick dark hair \textbf{brushed} up, \textbf{heavy} eyebrows, and a faint \textbf{shadow} of facial hair.
He wears a loose white button-up shirt over a white undershirt.
His expression is serious and slightly strained, his brow furrowed as he looks ahead, almost directly outward.
The setting opens up to reveal an old clapboard house on a quiet street.
The house has worn shutters, a small awning, peeling paint, and a large \textbf{tree} casting shade across the front.
A fire hydrant stands near the curb, and the whole place has a faded, sun-bleached, slightly rundown look.
Back against the peeling wall, the young man tilts his head upward with his eyes closed and lips parted, as if bracing himself or lost in thought.
A young light-skinned woman appears briefly from above or close by, leaning forward in a pink shirt.
She has light brown or blonde hair pulled back loosely and smiles down with a teasing, interested look.
The man is then seen crouched low beside the old house, wearing pale blue jeans and dark shoes.
He \textbf{balances} on his heels with his elbows near his knees and his hands clasped near his mouth, watching intently toward the street or driveway.
A soft \textbf{haze} or wash of light \textbf{passes} across him, then clears, leaving him still crouched by the weathered siding.
The woman ’s hands and forearms take over the action as she washes a pale blue car.
Her sleeves are pink, matching her shirt.
Soap and water stream over the glossy metal as she presses a foamy sponge or cloth across the surface.
Suds run in bright white \textbf{trails} down the curved \textbf{bodywork}.
The motion is practical and energetic : both hands \textbf{push} and wipe, spreading foam over the car.
The man stands again against the old house, now shown from farther back.
His white shirt hangs loose over his jeans, and he looks down, then forward.
He shifts his weight, one hand near his pocket, and then folds his arms across his chest as if cold or self-conscious.
Behind him are louvered shutters and cracked, flaking boards.
He leans into the wall and looks off to the side, thoughtful and guarded.
Soap drips down the car ’s side in close detail, running over the pale blue panel above a dark wheel arch and a \textbf{whitewall} tire.
The car is then seen in full : a vintage pale blue \textbf{sedan} parked alongside the same old building.
The young woman bends over the front fender, washing it, with a bucket on the \textbf{ground} beside her.
Laundry hangs on a line in the background, adding to the lived-in, domestic street setting.
The man ’s face returns in close view against the peeling wood.
He is calmer now, looking forward with a closed mouth and a restrained, almost stoic expression.
The focus then shifts to the woman ’s jeans from behind as she bends at the car.
Her pink shirt rides slightly above the waistband, revealing the back of faded blue denim jeans with stitched back pockets, \textbf{belt} loops, and a tan leather-like patch at the waistband.
The jeans look worn and casual, with darker damp marks from washing.
The man is suddenly down on the \textbf{ground} against the house, legs spread out in front of him in his pale jeans and dark shoes.
He props himself with one arm stretched to the side, looking toward the woman with his mouth open as if reacting.
One leg lifts slightly, then settles, giving him a flustered, off-balance look.
The woman turns her head over her shoulder, holding a sponge near her chest.
Her expression starts alert and questioning, then softens into a small smile.
She looks toward the man, her pink shirt bright against the faded wall behind her.
The man is back upright, leaning casually against the wall.
His posture loosens, one hand near his front pocket, and he looks upward and to the side with a faint smile.
Large red numbers “ 501 ” appear over the scene, spanning much of the image in front of him.
In the lower right, a small red Levi ’s logo with white lettering appears.
The final image keeps him leaning against the weathered house in his white shirt and blue jeans, smiling slightly behind the bold “ 501 ” branding.

% matched lemmas: balance, belt, bodywork, brush, ground, haze, heavy, pass, push, rough, sedan, shadow, trail, tree, whitewall
\end{textsample}
