\begin{textsample}{POS Dim 2 – 1970 – Score 12.00 – 1970/tv\_com\_1970\_19.txt}  \label{ex:f2_pos_079}
An animated \textbf{winter} scene opens in a \textbf{heavy} snowstorm.
Against a pale blue \textbf{sky} and soft yellow-white snowbanks, a tiny yellow open car or buggy moves through deep \textbf{snow}.
Large white snowflakes drift across the whole picture.
The \textbf{vehicle} has a rounded yellow front, a simple upright windshield and rail-like sides.
A small cartoon driver sits inside, \textbf{bundled} in pale clothing with a blue cap or nightcap.
Blue “ Z ” symbols appear near him, suggesting drowsiness or sleep, while the car \textbf{pushes} along through the \textbf{snow}.
As the yellow \textbf{vehicle} comes nearer, its tires become the focus.
Beneath the rounded body, the black tires are drawn like living creatures.
Each tire has big white eyes and an open mouth filled with triangular white teeth, as if the tires are biting into the \textbf{snow}.
The rear of the \textbf{vehicle} bounces and churns through the drifts while the tire-creatures clamp down and pull forward. \textbf{Snow} piles around the tires, and the animated mouths alternately open and close, giving the impression that the tires are chewing their way through the \textbf{winter} road.
The car continues across \textbf{rolling} snowbanks.
The driver remains seated behind the windshield, holding on as the \textbf{vehicle} rides over uneven \textbf{snow}.
From behind, the two rear tires look like paired gray monsters tucked under the yellow fenders, their eyes peering out and their toothy mouths digging into the surface.
Sometimes one tire-face appears wider and darker, sometimes the other, as they take turns biting and gripping.
The yellow body \textbf{rocks} above them, with \textbf{snow} collecting along its edges and the windshield.
The view tightens on the tires and their tread.
The black rubber surfaces fill the picture, showing deep, chunky grooves.
The tread pattern is exaggerated into rows of jagged, tooth-like shapes along the edges, with a darker central strip between them.
Snowflakes \textbf{pass} in front of the close-up while the grooves and raised bars are shown as if they are cutting into \textbf{snow}.
The tire tread appears thick, deep, and aggressive, with zigzag channels and protruding blocks that visually match the “ teeth ” idea.
The yellow \textbf{vehicle} then climbs a steeper \textbf{snowy} hill.
The rear tires dominate the lower part of the \textbf{vehicle}, their \textbf{heavy} black tread rotating through packed \textbf{snow}.
The driver, still \textbf{bundled} in pale clothing with a blue cap, leans with the car as it tilts upward. \textbf{Snow} sprays and bunches under the tire-creatures as they pull the \textbf{vehicle} up and over the rise.
The landscape remains stylized and simple : smooth drifts, a blue \textbf{sky}, falling flakes, and faint triangular evergreen shapes in the background.
After cresting the hill, the yellow \textbf{vehicle} descends into a flatter \textbf{snowy} area.
A dark blue car appears ahead and to the right, partly buried in \textbf{snow}.
Its roof and hood are covered by a thick white layer, and only parts of its dark body, wheels, and windows remain visible.
The yellow \textbf{vehicle} approaches the buried car from the left, its bright headlight-like yellow front facing toward it.
The tire-creatures continue to work underneath, leaving curved tracks behind in the \textbf{snow}.
The yellow car rides up alongside and slightly above the snow-covered dark car, continuing through the deep drift rather than getting stuck.
The dark car remains low and partly submerged, while the yellow \textbf{vehicle} ’s large animated tires keep turning and biting.
The yellow body \textbf{passes} over the uneven \textbf{snow} near the other car, then moves beyond it, leaving the stuck-looking car behind on the left.
The contrast is clear visually : the dark car sits buried and passive, while the yellow \textbf{vehicle} stays mobile, its tire-creatures actively chewing and pulling through the \textbf{snow}.
The \textbf{vehicle} moves away from the dark car and returns to the center of the \textbf{snowy} scene.
The tire faces are shown again from the rear and then closer from below the yellow fender.
Their eyes glance outward beneath the car, and their white triangular teeth remain prominent.
The black treads rotate through the \textbf{snow}, with clumps and flakes surrounding them.
The yellow car body fills much of the upper picture, while the gray tire-creatures and their mouths fill the lower part.
Near the end, the car slows on a snowbank.
The two anthropomorphic tires sit side by side under the rear fender, their eyes half-lidded and calmer, as if resting after the work of biting through the \textbf{snow}.
Blue “ Z ” marks appear again in the \textbf{snowy} blue background, reinforcing the sleepy visual theme from the opening.
The driver remains tucked behind the windshield, partly covered by pale clothing or a blanket-like shape.
The final product card appears on a light background.
At first, an inset picture shows the animated yellow \textbf{vehicle} with the two tired-looking tire faces in the \textbf{snow}, and large \textbf{red-orange} script text below reads “ Firestone. ” Under it, smaller text reads “ Town \& Country Snow Biters. ” The last image replaces the cartoon inset with a product view of two real black tires side by side, showing their deep tread.
Beneath the tire picture, the large \textbf{red-orange} “ Firestone ” name remains, followed by “ Town \& Country Snow Biters ” and the slogan in capital letters : “ PUT TEETH IN \textbf{WINTER} DRIVING. ”

% matched lemmas: bundle, heavy, pass, push, red-orange, rock, roll, sky, snow, snowy, vehicle, winter
\end{textsample}
