\begin{textsample}{POS Dim 2 – 2010 – Score 32.00 – 2010/tv\_com\_2010\_95.txt}  \label{ex:f2_pos_051}
The commercial opens over a \textbf{broad} \textbf{rural} landscape of \textbf{rolling} green hills, fields, and distant \textbf{mountains} under a bright, \textbf{hazy} \textbf{sky}.
A narrow pale road winds through the hills like a ribbon, with a tiny dark \textbf{vehicle} visible far below on the road.
The setting feels open and pastoral, with no buildings or people close by.
The view shifts to an empty \textbf{paved} road stretching forward between metal guardrails, with tree-covered hills and blue-green \textbf{mountains} in the distance.
Small white safety text appears along the bottom, reading like a standard closed-course warning.
A glossy red car then appears in close detail : its dark alloy wheel spins rapidly, with a red brake caliper visible behind the spokes and the Alfa Romeo \textbf{emblem} at the wheel ’s centre.
The car ’s red \textbf{bodywork} fills the upper left of the image, reflecting light as it moves.
The red \textbf{sedan} is seen from farther away on a curving \textbf{mountain} road bordered by silver guardrails and a tall \textbf{stone} retaining wall.
Beyond the road are orderly rows of \textbf{trees} or crops on a hillside, suggesting an Italian countryside or vineyard-like landscape.
A \textbf{brief} dark passage follows, with bright \textbf{outdoor} light flashing at the edge of the image, as if the car is moving through or \textbf{past} a shaded structure.
The red front wheel and fender reappear in a dimmer area, the tire \textbf{rolling} across a bright patch of \textbf{pavement}.
A calm landscape \textbf{shot} shows a line of tall, narrow cypress-like \textbf{trees} standing evenly along a ridge, with \textbf{hazy} \textbf{mountains} behind them.
The commercial then presents the car ’s front as an object of focus : the glossy red hood and the distinctive Alfa Romeo triangular grille dominate the image.
The circular Alfa Romeo \textbf{badge} sits prominently at the centre above a black diamond-pattern grille.
Reflections of tall dark \textbf{trees} ripple across the curved red hood, emphasizing its sculpted shape.
More close views highlight the front lower bumper.
The red body surrounds black mesh air intakes and a low black splitter beneath the grille.
The car is moving, and the \textbf{pavement} slides by below the front edge.
The red paint is bright and polished, while the black grille and trim create a strong contrast.
The \textbf{shot} moves along the front corner toward the spinning front wheel, again showing the performance styling and dark wheel design.
The setting returns to a descending \textbf{mountain} road with a \textbf{stone} wall on the right and a guardrail on the left.
The asphalt curves through \textbf{dry} golden hillsides dotted with shrubs.
Inside the car, a close view shows a driver ’s hand near the \textbf{steering} wheel and paddle controls.
The image is soft and partially blurred, but a wrist with a watch and a hand moving close to the wheel are visible, suggesting active control of the \textbf{vehicle}.
The red Alfa Romeo then comes toward the viewer on a \textbf{sunlit} \textbf{mountain} bend.
Its narrow headlights are on, and the triangular grille is centred between them.
The low \textbf{sun} shines from the right side, creating bright \textbf{glare} and lens-like circles of light across the scene.
The car ’s nose appears planted and wide as it follows the curve beside the \textbf{stone} retaining wall.
A close detail of the rear \textbf{underside} follows, showing two round exhaust pipes set into a dark diffuser beneath the red bumper.
Sunlight flickers through blurred \textbf{trees}, creating abstract flashes of bright white and green.
From high above, the road appears as a series of sweeping curves and hairpins cut through grassy hills.
The red car is a small but vivid shape tracing the bends.
It then appears from the side, larger and clearer, rounding a curve on the \textbf{mountain} road.
Its profile shows a four-door sports \textbf{sedan} shape with a long hood, smooth roofline, dark wheels, and tinted windows.
The car hugs the inside of the curve, with the guardrail and rocky hillside behind it.
A frontal view shows the red Giulia driving along a shaded road bordered by \textbf{trees}.
Its headlights form sharp white slits, and the Alfa grille remains visible in the centre.
As it approaches, the image becomes washed in warm golden light until the car is nearly swallowed by brightness.
The side of the red \textbf{sedan} then \textbf{rushes} \textbf{past}, showing the rear door, rear wheel, and sculpted rear quarter panel.
Sun \textbf{glare} blooms over the \textbf{trunk} and back window while the rear wheel spins.
Inside the car again, two hands hold the black \textbf{steering} wheel.
A silver paddle shifter is visible behind the right side of the wheel, and a digital instrument display glows in the background.
The driver ’s hands appear steady and engaged, with fingers wrapped around the wheel as the car continues through the road.
The red car \textbf{passes} through a \textbf{mountain} valley in bright \textbf{sun}, with dark \textbf{mountain} slopes on both sides and the \textbf{sun} low ahead.
The car ’s side glints as it moves across the landscape.
A small triangular \textbf{badge} is visible on the front fender, and the roofline and side windows are \textbf{silhouetted} against the light.
The view shifts behind the car as it \textbf{drives} away along a curving road bordered by a \textbf{stone} wall on the right and a guardrail on the left.
Red taillights glow in the rear, and the \textbf{sedan} leans into the bend while the \textbf{sun} casts long \textbf{shadows} and circular flares across the road.
The final close-up focuses on the rear left side of the car.
The red taillight forms a bright, angular shape, and the \textbf{chrome} “ GIULIA ” nameplate is clearly visible on the \textbf{trunk} lid.
Part of the Alfa Romeo round \textbf{badge} and a partial license plate appear at the left edge.
The glossy red rear panel, dark rear spoiler-like trim, side mirror, and green \textbf{trees} in the background frame the product name as the car continues moving forward.

% matched lemmas: badge, bodywork, brief, broad, chrome, drive, dry, emblem, glare, hazy, mountain, outdoor, pass, past, paved, pavement, roll, rural, rush, sedan, shadow, shot, silhouette, sky, steering, stone, sun, sunlit, tree, trunk, underside, vehicle
\end{textsample}
