\begin{textsample}{POS Dim 2 – 1970 – Score 15.00 – 1970/tv\_com\_1970\_63.txt}  \label{ex:f2_pos_074}
A broadcast graphic appears first on a dark background, with large white words reading “ GOOD MORNING AMERICA, ” the ABC logo below, and smaller text advertising “ 7am Weekdays. ” The commercial then moves to a dark, studio-like setting where a black-and-yellow BMX-style \textbf{bicycle} fills the view.
Only the torso and legs of a child or young teen are visible behind it, wearing a red striped shirt and blue jeans, hands on the yellow handlebar grips.
The bike has a black frame, yellow handlebar and frame pads, thick tires, and bright yellow mag-style wheels.
A plaid-sleeved adult hand reaches in from the right and points around the front of the bike, drawing attention to the head tube, fork, and bracing near the frame.
Close views linger on the bike ’s construction : a yellow pad with raised “ Huffy ” lettering, a black triangular support near the front frame area, a white head-tube label with the Huffy mark, and yellow lettering along the black frame.
The scene opens outdoors in a bright desert landscape with rocky mesas and scrub \textbf{brush}.
A brown van with orange side panels is parked on a dirt pull-off, its doors open.
Two children with \textbf{bicycles} stand beside it while an adult man in a plaid shirt and jeans is nearby.
One child, with light shoulder-length hair, wears a white shirt with red sleeves, jeans, and white sneakers, straddling or mounting the black-and-yellow bike.
Another child in a red striped shirt and light blue jeans stands with a similar bike, also black with yellow wheels and pads.
The children \textbf{push} off and begin riding away from the van onto a wide dirt road.
The two children ride side by side along the \textbf{dusty} road through the open desert.
The child in the white-and-red shirt rides on the left, leaning forward over the yellow handlebar pad ; the child in the red striped shirt rides on the right, also bent forward and pedaling hard.
Their bikes ’ yellow wheels stand out against the pale road.
A close view of one rider ’s foot shows a white sneaker pressing the pedal through a full rotation, the long crank and chain area visible as the rear wheel turns.
The black frame carries yellow graphics, including the product name along the diagonal tube.
The riders continue \textbf{past} red \textbf{rock} \textbf{formations} and low desert plants, moving quickly across the uneven \textbf{ground}.
From the front, the child in the white-and-red shirt rides directly toward the viewer down the dirt road, hair blown back, hands gripping the bars, body crouched in an active riding posture.
The wide yellow handlebar pad sits prominently in front of the rider ’s chest, and the rocky canyon scenery stretches behind under a clear blue \textbf{sky}.
Back near the van, the adult man sits high on the roof.
He has dark hair, a mustache, and wears a red-brown plaid shirt with blue jeans.
He lifts a pair of binoculars to his eyes and looks out across the desert, as if following the children ’s ride from a distance.
A wide landscape view shows a \textbf{broad} valley dotted with shrubs and framed by layered \textbf{mountains} and mesas.
The children reappear riding on a \textbf{rougher} dirt \textbf{trail}, approaching from the distance and coming over ruts and bumps.
One bike ’s front wheel lifts briefly as it hits uneven \textbf{ground}, then both riders steer through the \textbf{dusty} track.
They lean their bodies into the turns, tires kicking up small \textbf{trails} of dust.
Close views emphasize the yellow wheels \textbf{rolling} over the rugged surface and the riders ’ feet working the pedals.
The child in the white-and-red shirt rides back toward the van along the dirt road, seen from behind, while the adult remains seated on top of the van watching.
The desert cliffs and boulders surround the road.
From a higher angle near the van roof, both children ride side by side down the road below, their long \textbf{shadows} stretching across the dirt as they move away through the canyon-like setting.
The \textbf{bicycle} is then presented alone against a plain light gray studio background.
Large yellow block letters above it read “ PRO THUNDER 4. ” The bike is shown in profile : a black frame, yellow top pad and handlebar pad, yellow grips, black saddle, black tires, and yellow mag-style wheels.
The closing graphic shifts to a stylized animation.
An orange-yellow simplified figure rides a \textbf{bicycle} across a glossy black surface under a blue gradient \textbf{sky}, with a red reflection of the bike beneath.
Small sparkling dots \textbf{trail} behind the rider.
White text along the bottom reads “ WHEEL STYLE MAY VARY. ” Finally, the Huffy brand message appears in white above the horizon : “ Building the bikes America likes. ” Beneath it, the large word “ HUFFY ” is displayed, while the wheel-style notice remains along the bottom.

% matched lemmas: bicycle, broad, brush, dusty, formation, ground, mountain, past, push, rock, roll, rough, shadow, sky, trail
\end{textsample}
