\begin{textsample}{POS Dim 2 – 2000 – Score 31.00 – 2000/tv\_com\_2000\_119.txt}  \label{ex:f2_pos_021}
A \textbf{mountain} road curves toward a large \textbf{stone} tunnel entrance built into a rocky hillside.
The tunnel mouth is dark, with a line of lights receding inside, and a white road edge line runs along the foreground.
Small white text near the bottom reads, “ Professional riders on closed \textbf{course}. ” A gold touring motorcycle flashes \textbf{past} the tunnel entrance in a blur, emphasizing speed, then the view cuts to the yellow double center lines of the road \textbf{rushing} by.
The motorcycle appears on an open \textbf{mountain} curve, leaning smoothly through a bend on a \textbf{paved} \textbf{two-lane} road.
Its front lights glow brightly, and the rider, wearing a dark full-face helmet and riding gear, is tucked behind a clear windshield.
Misty \textbf{blue-gray} \textbf{mountains} rise in the background, with the road ’s double yellow lines sweeping in an S-shape across the \textbf{pavement}.
The same small safety text remains along the bottom.
A black Honda Gold Wing touring motorcycle then travels through a \textbf{sunlit}, scrubby landscape.
The rider wears a black helmet and dark jacket, sitting upright behind the large front fairing and windshield.
The bike ’s \textbf{broad} \textbf{bodywork}, side cases, and rear \textbf{trunk} make it look substantial and built for travel.
Low \textbf{brush} and warm-toned hills blur \textbf{past} around the road.
The scene opens wider on a straight \textbf{highway} leading toward dramatic snowcapped \textbf{mountains}.
Two touring motorcycles ride along the road : a yellow Gold Wing close to the right side of the image and a darker motorcycle farther ahead in the left lane.
Both riders wear helmets, and the yellow bike ’s large front fairing, mirrors, and headlight cluster are prominent.
The snow-covered peaks stretch across the horizon under a pale blue \textbf{sky}.
A side view shows a black Gold Wing 1800 carrying two helmeted riders.
The driver, in a dark leather jacket, blue jeans, gloves, and \textbf{boots}, sits upright with both hands on the handlebars.
The passenger, also wearing a helmet, dark jacket, blue jeans, and \textbf{boots}, sits relaxed on the raised rear seat with a padded backrest and large rear storage \textbf{trunk} behind them.
The motorcycle ’s \textbf{chrome} engine covers, footboards, windshield, and wide saddlebag area are clearly visible.
At the upper left, white text reads “ Gold Wing 1800. ” A \textbf{few} moments later, bold white text appears along the bottom : “ ‘ Motorcycle of the \textbf{Year} ’, ” with smaller attribution text beneath it to Motorcyclist and Rider magazines.
The bike continues steadily \textbf{past} a forested \textbf{mountain} backdrop.
The commercial returns to a single black Gold Wing on a narrow \textbf{rural} road bordered by golden \textbf{grass}.
From above and ahead, the rider approaches along the winding \textbf{pavement}, the motorcycle centered in the lane.
The rider leans the bike gently into the curve, and the front headlights and amber side lights are visible.
Tall \textbf{grasses} and \textbf{fence} posts line the roadside, giving the setting a quiet countryside feel.
From behind, a black touring motorcycle leans through another \textbf{broad} \textbf{mountain} curve.
Its red rear lights and large rear \textbf{trunk} are visible as it arcs along the double yellow lines.
The rider ’s dark helmet and jacket form a compact \textbf{silhouette} above the bike ’s wide rear storage cases. \textbf{Blue-gray} \textbf{mountain} ridges and scattered evergreens fill the distance.
An orange Gold Wing rides through a desert canyon road.
Red and tan \textbf{rock} walls rise close beside the \textbf{pavement}, with a natural arch-like opening visible in the \textbf{rock} face behind the motorcycle.
The rider wears a black helmet and dark riding clothes, seated upright behind the tall clear windshield.
The orange fairing, matching saddlebags, rear \textbf{trunk}, \textbf{chrome} engine area, and bright headlight cluster stand out against the warm \textbf{rock}.
A large gold wing \textbf{emblem} and the word “ GOLDWING ” appear over a curving \textbf{mountain} road, with “ Test Ride ” in bold white text beneath.
Fine-print legal text fills the lower portion of the screen, including a visible note that the test ride program is good through 4-1-2002 and that dealers may deny participation at their discretion.
Behind the graphics, a motorcycle rounds the bend toward the viewer and then \textbf{passes} by, partially blurred by motion, while evergreen \textbf{trees} and a pale \textbf{sky} frame the road.
A black Gold Wing approaches head-on through a red-rock canyon under a clear blue \textbf{sky}.
The rider is centered behind the windshield, and the \textbf{twin} headlights glow.
White fine print remains along the bottom.
The text “ honda.com ” appears in white above the legal copy as the motorcycle continues along the road between \textbf{reddish} \textbf{rock} \textbf{formations} and a sloping canyon wall.
The setting shifts back to golden fields.
A black Gold Wing moves away along a narrow \textbf{paved} country road, partly screened by tall green \textbf{grasses} in the foreground.
Large white text appears at the upper left : “ 2.9 \% APR. ” Fine print along the bottom explains that the 2.9 \% APR financing applies to new Gold Wings and includes additional qualification and Honda Finance details.
The motorcycle continues farther down the road, becoming smaller as the landscape opens into a \textbf{broad} valley of yellow fields, \textbf{fence} posts, and distant red and gray \textbf{rock} cliffs.
In the final view, the lone motorcycle rides away along the center of the winding road through the expansive golden valley.
The large “ 2.9 \% APR ” offer fades, while the fine print remains at the bottom.
A red Honda wing-shaped graphic appears above the road, followed by the white slogan “ PERFORMANCE FIRST. ” The motorcycle continues toward the distant cliffs and open \textbf{sky}, visually ending on the idea of a long scenic journey.

% matched lemmas: blue-gray, bodywork, boot, broad, brush, chrome, course, emblem, fence, few, formation, grass, highway, mountain, pass, past, paved, pavement, reddish, rock, rural, rush, silhouette, sky, stone, sunlit, tree, trunk, twin, two-lane, year
\end{textsample}
