\begin{textsample}{POS Dim 2 – 1950 – Score 10.00 – 1950/tv\_com\_1950\_107.txt}  \label{ex:f2_pos_090}
In black and white, a streamlined Greyhound bus travels along a winding \textbf{mountain} road bordered by steep \textbf{rock} walls, scrubby \textbf{brush}, and distant hills.
It comes around a bend from the left side of the road, growing larger as it approaches.
The bus has a rounded 1950s front, large windows, a raised rear section, and bright trim that catches the light.
As it \textbf{passes} through the rocky landscape, huge dark letters appear over the scene reading “ BUS 509, ” making the bus seem like the subject of a mystery.
Inside the bus, three passengers sit side by side in cushioned seats with high, light-colored headrests.
On the left, a middle-aged man in a dark business suit and tie looks down at a notepad or papers in his lap and writes with a pen, appearing focused and businesslike.
In the middle, a middle-aged woman with neatly styled dark hair wears a dark dress or suit, earrings, and a pearl necklace.
She sits upright, smiling pleasantly.
On the right, an older man with light hair or a balding head wears a suit and tie ; he leans back with his eyes closed, relaxed as if napping.
Other passengers are dimly visible behind them.
The view moves closer to each passenger.
The businessman is shown from the front, seated squarely with other passengers blurred behind him.
He looks down, then raises a pen toward his mouth and face as if pausing to think while working.
His expression is calm and satisfied, and he keeps the pen near his lips before lowering his gaze again.
The woman is shown in close-up, smiling warmly and turning her eyes slightly to the side as if speaking to someone nearby.
Her pearl necklace stands out against her dark clothing, and her posture remains poised and comfortable.
The older man is shown in close-up leaning back in his seat.
His eyelids droop, then close fully ; his head tilts gently to one side and then settles back, emphasizing how at ease he is.
The exterior mountain-road view returns, again showing the bus rounding the bend and gliding \textbf{past} rocky cliffs and open hills.
A close view of the side of the bus follows, showing the Greyhound running-dog \textbf{emblem} stretched across a smooth panel.
The dog is drawn in profile, long and lean, mid-stride, with its legs extended as if racing.
The bus then appears on a \textbf{broader} tree-lined road, approaching from the distance beneath dark leafy \textbf{branches}.
It comes closer on the open roadway, its rounded front and bright windshield visible, then \textbf{passes} by, filling much of the view before moving out of sight.
Near the end, the perspective is from inside the front of the bus, looking through the windshield.
The driver is a dark \textbf{silhouette} on the left beside the \textbf{steering} wheel, while the road ahead leads toward large overpass structures and other cars.
A vertical windshield support or wiper hangs near the center.
Across the lower part of the image, large white italic capital letters appear : “ IT ’S SUCH A COMFORT TO TAKE THE BUS. ” The text remains over the forward road view as the bus continues smoothly toward the overpasses.

% matched lemmas: branch, broad, brush, emblem, mountain, pass, past, rock, silhouette, steering
\end{textsample}
