\begin{textsample}{POS Dim 2 – 1990 – Score 18.00 – 1990/tv\_com\_1990\_92.txt}  \label{ex:f2_pos_038}
A quiet golf \textbf{course} appears first : \textbf{broad} green fairways, a pond in the foreground reflecting the \textbf{sky}, and \textbf{trees} scattered across the landscape.
The light is warm and low, with pale clouds glowing near the horizon, giving the \textbf{course} a calm, early-morning or late-day feeling.
The golf imagery \textbf{blends} into a close view of a hand placing a white golf ball on a white tee in short green \textbf{grass}.
The ball has small dark lettering on it, and a white golf shoe is blurred in the background.
A gloved hand then grips the dark handle of a golf club, the other bare hand settling into position around it.
The glove is white with a small yellow patch near the wrist.
A tanned, older male golfer with light gray-blond hair is seen in \textbf{tight} close-up, leaning down and squinting with concentration.
The ball sits upright on the tee beside the metal face of a club.
The golfer completes his grip and swings ; seen from above and then from a wider view, he wears a turquoise and light-striped golf shirt, dark trousers, and white shoes.
He follows through with the club high over his shoulder on a manicured tee box under a bright blue \textbf{sky}, with \textbf{trees} and \textbf{rolling} green hills behind him.
The scene shifts from golf to a dark Lincoln \textbf{sedan} moving along a tree-lined road.
At first, only parts of the front end are glimpsed through leafy \textbf{branches} and \textbf{tree} \textbf{trunks} : the rectangular headlights, amber turn signal, \textbf{chrome} trim, and the tall vertical-bar grille with the Lincoln hood ornament above it.
The car glides along a \textbf{paved} road bordered by dense green vegetation.
Sunlight flashes through the \textbf{trees}, and reflections ripple across the glossy black hood.
The road curves gently under a canopy of large \textbf{trees}.
The Lincoln Town Car then approaches head-on, centered on the road.
Its \textbf{broad}, formal front is clearly visible : a large chrome-framed grille, rectangular headlights, amber lamps at the inner sides, white side mirrors, and a long dark hood.
White on-screen text appears along the bottom : “ 17 City 23 Hwy.
EPA Estimates. ” The car continues toward the viewer, filling more of the image, with the fuel-economy text remaining at the bottom.
A close view follows of the Lincoln branding on the car ’s body.
The \textbf{chrome} letters spelling “ LINCOLN ” stand out against the dark glossy paint, catching bright highlights.
The surface reflects light and \textbf{shadow}, emphasizing the polished finish.
The car is then shown in side profile \textbf{driving} across a green park-like setting, still glossy black with \textbf{chrome} trim along the doors and around the windows.
Large white promotional text overlays the lower half of the image : “ NOW GET \$1,000 CASH BACK ON ’ 92 LINCOLN TOWN CAR. ” Beneath it, smaller fine print runs across the bottom, including wording about cash back from Lincoln-Mercury, taking new retail delivery from dealer stock by 12/31/91, and seeing the dealer for details.
The \textbf{sedan} continues smoothly from left to right \textbf{past} lawns, \textbf{trees}, and flowering shrubs.
Inside the car, the view moves through the rear passenger area.
The interior is dark, with black leather upholstery and softly gleaming surfaces.
A wide rear seat cushion with stitched panels fills the lower portion, while the back of the front seat and its rounded headrest appear in the foreground.
Across the far side are a dark door panel, a \textbf{chrome} door handle, controls, and a band of warm woodgrain trim.
The cabin looks spacious and subdued, with soft light falling across the leather seat cushions and headrests.
The exterior returns to the Town Car in motion along the wooded road.
Seen from the side, then from the rear quarter, the long black \textbf{sedan} \textbf{passes} between tall \textbf{tree} \textbf{trunks} and green undergrowth.
Its \textbf{chrome} wheel trim, rectangular side windows, and long body line remain visible as it moves away.
In the final view, the rear of the car recedes into the \textbf{trees}, with a wide red taillight strip and \textbf{chrome} bumper briefly visible before the \textbf{vehicle} disappears farther down the winding, shaded road.

% matched lemmas: blend, branch, broad, chrome, course, drive, grass, pass, past, paved, roll, sedan, shadow, sky, tight, tree, trunk, vehicle
\end{textsample}
