\begin{textsample}{POS Dim 2 – 1960 – Score 5.00 – 1960/tv\_com\_1960\_94.txt}  \label{ex:f2_pos_067}
The sampled frames show the commercial moving from a technical slate to close-ups of a record player and then to a final product display. 1. **Opening frame (0.000s)** The \textbf{screen} is black with white overlaid text reading **“Not For Broadcast”** near the upper left/center area.
A white timecode appears near the bottom : **“01:00:00:00.”** No product or scene is visible yet. 2. **Record player close-up (7.113s)** The scene cuts to a close-up of a turntable.
A black vinyl record with a red center label is spinning or positioned on the platter.
A hand is holding or guiding the tonearm/cartridge assembly toward the record.
The tonearm mechanism and spindle are visible.
The background appears to be a wood-toned surface.
The “ Not For Broadcast ” watermark and timecode remain overlaid. 3. **Tonearm on/near the record (14.663s)** A closer side view shows the tonearm and cartridge positioned at the edge of or on the record.
The record ’s black surface and red label are still visible.
The spindle and parts of the turntable mechanism are in view.
The hand is no longer visible.
The same “ Not For Broadcast ” watermark and timecode remain on \textbf{screen}. 4. **Final product shot (59.041s)** The scene changes to a \textbf{room} setting with a \textbf{wooden} console cabinet centered in the frame.
The cabinet has speaker panels on the left and right and \textbf{wooden} doors in the middle, suggesting a \textbf{home} audio or stereo console.
A vase of flowers \textbf{sits} on top, and a framed landscape picture hangs behind it.
Large white stylized text **“ZENITH”** appears above the console.
At the bottom, a slogan is visible : **“The quality goes in before the name goes on”** though part of it is overlapped by the timecode.
To the right of the console is a chair, with curtains behind it.
The “ Not For Broadcast ” watermark and timecode remain visible.

% matched lemmas: home, room, screen, sit, wooden
\end{textsample}
