\begin{textsample}{POS Dim 2 – 1980 – Score 23.00 – 1980/tv\_com\_1980\_41.txt}  \label{ex:f2_pos_061}
A bright \textbf{outdoor} scene opens on a huge mound of cut logs under a blue \textbf{sky} with a \textbf{few} white clouds.
The logs are piled unevenly in every direction, their bark \textbf{rough} and their pale cut ends visible.
A curly-haired adult man, male-presenting, wearing a red plaid shirt and light blue jeans, stands among the logs with his feet braced for \textbf{balance}.
He grips a long-handled tool like an axe or pick and works it into the wood, then raises it above his shoulder as if preparing another strike.
The setting feels like a logging yard or a staged rugged test area, with the log pile rising like a small hill.
The view widens to reveal a dark Ford pickup \textbf{truck} waiting on the flat, \textbf{dusty} \textbf{ground} beside the log pile.
The man walks near the \textbf{truck} carrying the long-handled tool.
The pickup has a squared 1980s shape, a \textbf{chrome} grille, rectangular headlights, an empty open bed, and lighter trim along the lower body.
The foreground is filled with the jumbled logs, while the \textbf{truck} sits just beyond them, positioned to climb onto the pile.
The \textbf{truck} begins \textbf{driving} up over the logs.
A side view shows it angled uphill, its front wheels climbing from one log to another while the bed remains empty.
Large white on-screen numbers appear in the upper right : “ 25 EST.
HWY ” above “ 18 EPA EST.
MPG. ” Across the bottom, small white fine print reads that the \textbf{truck} has an optional 4-speed transmission, that the figures are for comparison, that mileage may differ depending on speed, distance, and weather, that actual \textbf{highway} mileage may be lower, and that a V-8 is required in California.
As the \textbf{truck} continues upward, its body \textbf{rocks} and tilts over the uneven surface, with the wheels dropping into gaps and then rising over rounded logs.
From the front, the Ford ’s \textbf{chrome} grille and blue oval \textbf{badge} are prominent as it crawls over the pile.
The front end is high, and the left and right wheels sit at different levels on the logs, showing the \textbf{truck} flexing over the obstacle.
The \textbf{dusty}, open landscape and low hills stretch behind it.
The mileage numbers and fine print remain on screen while the pickup advances, the tires gripping the \textbf{rough}, shifting-looking surface.
A much wider view emphasizes the scale of the challenge : the \textbf{truck} is now a small dark shape partway up an enormous slope of logs.
The foreground is dominated by thick \textbf{trunks} stacked chaotically, some split and pale at the ends, others dark with bark.
The \textbf{truck} continues slowly along the crest of the pile under the bright \textbf{sky}.
The focus moves closer to the front of the \textbf{truck} as it comes toward the viewer over the logs.
A male-presenting adult driver is visible through the windshield, seated upright and \textbf{steering}.
The front suspension and \textbf{underside} can be seen between the wheels ; brightly colored components beneath the \textbf{truck} stand out against the brown logs.
As the \textbf{truck} \textbf{rolls} forward, one front wheel rises while the other drops, and the body leans, then begins to level out as the wheels find new footing.
A \textbf{tighter} front view centers on the grille and the lower front end.
The logs \textbf{pass} beneath the bumper, and the undercarriage remains visible between the front tires.
The wheels move independently over the uneven obstacles, with one tire lower in a gap and the other higher on a log.
The \textbf{truck} continues carefully forward without stopping.
A close side view shows the front wheel and fender.
The \textbf{badge} on the side reads “ F-150, ” and the \textbf{truck} ’s dark paint is accented by a red stripe and silver lower trim.
The tire climbs over a log, compresses slightly as it bears weight, then rises and clears the rounded wood.
Cut log ends and smaller chunks fill the foreground, showing how irregular the surface is.
Another angle places a tall, charred-looking or dark-barked log diagonally across the foreground like a large beam, partially blocking the view.
Behind it, the Ford pickup keeps moving left to right across the pile.
The \textbf{truck} ’s front wheel climbs onto a long log, the body tilts upward, and then the rear follows.
The driver remains visible through the side window as the empty bed \textbf{passes} behind the large foreground log.
The \textbf{truck} reaches the top of the log mound.
It stands nearly level on the crest, with the man from the opening scene beside it holding his long-handled tool upright.
He faces the \textbf{truck} and the surrounding pile, standing as if presenting the completed climb.
The \textbf{truck} ’s front grille faces slightly toward the viewer, and the open bed extends to the left.
The scene gradually appears wider, making both the \textbf{truck} and the man look small against the \textbf{broad}, heap-like \textbf{mountain} of logs beneath them.
The commercial then changes to a bold graphic on a blue gradient background.
A black, rock-textured \textbf{silhouette} of the United States fills the center, with large white block letters across it reading “ AMERICA ’S \textbf{TRUCK}. ” A shield-shaped \textbf{emblem} slides in beside it, also dark with a light border, carrying the words “ Built Ford Tough ” in white.
The final image is the Ford blue oval logo on a black background, with “ FORD DIVISION ” written below in white capital letters.

% matched lemmas: badge, balance, broad, chrome, drive, dusty, emblem, few, ground, highway, mountain, outdoor, pass, rock, roll, rough, silhouette, sky, steering, tight, truck, trunk, underside
\end{textsample}
