\begin{textsample}{POS Dim 2 – 1960 – Score 30.00 – 1960/tv\_com\_1960\_68.txt}  \label{ex:f2_pos_004}
A rugged Jeep \textbf{vehicle} is first seen in \textbf{tight} detail by its front wheel.
The large, knobby tire \textbf{rolls} slowly over uneven \textbf{ground}, pressing across \textbf{rocks}, dirt, and low \textbf{brush}.
Thin \textbf{branches} and \textbf{tree} \textbf{trunks} \textbf{pass} in front of the wheel as the \textbf{vehicle} \textbf{pushes} through a wooded area.
The \textbf{bodywork} above the wheel is high off the \textbf{ground}, and the tire ’s deep tread is prominent as it climbs over \textbf{stones} and ruts.
The view widens to reveal a Jeep station wagon-style \textbf{vehicle} moving across a rocky hillside among pine \textbf{trees}.
A long canoe is strapped lengthwise to the roof, extending beyond the front of the \textbf{vehicle}.
The driver, an adult man in a patterned shirt, rests one arm out the open window while guiding the \textbf{vehicle} uphill.
The wagon ’s front wheel bumps over loose \textbf{rocks} and scrub plants, then the whole \textbf{vehicle} continues steadily through the \textbf{rough} terrain.
It \textbf{passes} between \textbf{trees}, with the rear of the canoe visible above the roof, and gradually moves away into the forest.
A different open-top Jeep appears on a narrow dirt road through slender \textbf{trees}.
Two adult men ride in it : one \textbf{drives} from the front seat, and another sits in the rear, wearing a light-colored cap.
The \textbf{spare} tire is mounted on the back.
The Jeep travels away along the forest track, then climbs onto a slanted \textbf{bank} at the edge of the road.
Its body leans sharply to one side as one side rides higher on the slope, showing the \textbf{vehicle} ’s ability to handle uneven \textbf{ground}.
It then appears in a scenic \textbf{outdoor} spot near a creek, surrounded by large rounded boulders, pine \textbf{trees}, and distant \textbf{mountains}.
The commercial returns to the station wagon-type Jeep.
Its front tire again works over \textbf{rocks} and \textbf{dry} \textbf{brush}, with a “ 4 wheel \textbf{drive} ” \textbf{badge} visible near the front side panel.
The \textbf{vehicle} ’s side windows show passengers inside, while the driver keeps an arm out the window.
The wagon crawls over scattered \textbf{stones} and continues uphill through the \textbf{trees}, its rear gradually receding into the wooded slope.
The rear cargo area of the Jeep wagon is then shown with the back opened wide.
It is packed with \textbf{outdoor} gear : folded chairs or cots stacked near the bottom, luggage and bags, a fishing net or racket-shaped frame, a \textbf{spare} tire along one side, and blankets or soft \textbf{bundles} piled toward the back.
Large white block letters appear across the lower part of the cargo opening reading “ 95 CUBIC FT. ” An open Jeep \textbf{drives} across a \textbf{broad}, pale field bordered by tall pine \textbf{trees}.
It approaches from the distance, bouncing lightly over the \textbf{ground} and leaving a \textbf{dusty} \textbf{trail} behind it.
Large white words appear at the upper left, then expand across the top : “ COSTS LESS TO OPERATE. ” The Jeep \textbf{passes} left to right beneath the text.
Two adult men are visible inside, one driving and another beside or behind him ; both wear \textbf{outdoor} clothing, and the open windshield and simple, boxy body of the Jeep are clearly visible.
The setting changes to a \textbf{vehicle} sales lot.
Several older cars and \textbf{trucks} are parked in a row, and a large sign above them reads “ \textbf{TRUCKS}. ” A small price sign reading “ 285 ” is posted in the window of one \textbf{vehicle}.
In the center is a Jeep with its distinctive vertical grille and round headlights.
Two adult men in suits and hats stand in front of it, facing each other and the Jeep as if discussing the \textbf{vehicle}.
One man gestures toward the Jeep ’s front while the other stands near the driver ’s side.
Other \textbf{trucks} flank the Jeep on both sides, creating the appearance of a dealership display.
The words “ HUNTING \& FISHING ” appear in large white capital letters across the top of the scene.
The dealership view gives way to a forest \textbf{path} under the same text.
An open Jeep \textbf{drives} forward through dense \textbf{trees} and uneven \textbf{ground}, its front end rising and dipping as it crosses ruts.
Dust kicks up around the tires.
Another Jeep station wagon with a canoe on its roof emerges behind it from the left side of the wooded \textbf{trail}.
The open Jeep moves across the foreground and exits to the right, while the wagon follows, turning through the \textbf{trees} and over a \textbf{rough} patch in the \textbf{path}.
Both \textbf{vehicles} are presented as part of the same \textbf{outdoor} travel scene.
After a \textbf{brief} dark transition, a circular spotlight-like view reveals a full lineup of Jeep \textbf{vehicles} arranged on a \textbf{paved} lot.
The circle widens to show multiple models in neat rows : open Jeeps, station wagons, pickup-style \textbf{trucks}, a flatbed or cab-over \textbf{truck}, and other boxy utility \textbf{vehicles}.
The \textbf{vehicles} are spaced evenly, viewed from above, emphasizing the variety of the lineup.
An open Jeep then climbs a steep, rocky mountainside.
The slope rises diagonally across the picture, with scrubby plants and loose \textbf{stones} covering the \textbf{ground}. \textbf{Mountains} stretch in the background.
The Jeep powers upward from left to right, \textbf{throwing} dust behind its rear wheels as it angles toward the top of the hill.
It continues climbing until it disappears off the upper right edge, leaving a drifting dust cloud over the slope.
The commercial ends on a close view of a printed telephone directory page under the heading “ 1874 \textbf{TRUCKS}. ” The page is filled with dealer listings and columns of small text.
The view settles on a boxed listing titled “ WILLYS SALES AND SERVICE, ” with the Jeep logo prominently printed beside it.
The readable lines include “ Universal ‘ JEEP, ’ ” “ ‘ JEEP ’ Station Wagon, ” “ ‘ JEEP ’ Trucks, ” “ The Jeep family of 4-wheel-drive \textbf{vehicles}, ” and “ WHERE TO BUY THEM — DEALERS. ”

% matched lemmas: badge, bank, bodywork, branch, brief, broad, brush, bundle, drive, dry, dusty, ground, mountain, outdoor, pass, path, paved, push, rock, roll, rough, spare, stone, throw, tight, trail, tree, truck, trunk, vehicle
\end{textsample}
