\begin{textsample}{POS Dim 2 – 1960 – Score 24.00 – 1960/tv\_com\_1960\_50.txt}  \label{ex:f2_pos_005}
At the beginning, the view is very \textbf{tight} on a dark horse in motion.
Only parts of the animal are visible at first : slim legs, hooves, and the lower body \textbf{passing} across a pale, \textbf{dusty} \textbf{ground}.
The hooves strike and lift in quick rhythm, kicking up soft clouds of dust.
The images are warm and \textbf{reddish}, with strong dark \textbf{shadows}, so the horse often appears almost as a \textbf{silhouette} against the light sand.
The setting opens out to a \textbf{dry}, open landscape.
A dark horse stands and then runs along a flat sandy \textbf{path} at the base of a \textbf{rough}, rocky hillside.
Sparse desert shrubs dot the \textbf{ground}, and the background is made up of pale cliffs and scrub.
The horse moves from left to right, its head forward, mane and tail \textbf{trailing}, with dust rising behind its hind legs.
As it \textbf{gathers} speed, all four legs repeatedly lift clear of the \textbf{ground}, giving the impression of a free-running mustang in a desert canyon.
The horse is then seen in a more graphic, shadowy profile, its body dark against a pale background.
Its mane flares upward and backward, and its tail streams out as it gallops.
The sequence returns to very close views of the legs and hooves, again emphasizing the pounding movement and dust.
The horse continues racing across the desert floor, dark and muscular against the pale \textbf{rocks}.
A circular stamp-like graphic appears over the running horse.
Inside the circle, bold capital letters read “ ON-THE-SPOT LOAN. ” The circle has small tick marks around its edge, like a seal or clock face.
The horse is still visible behind the lettering for a moment, then the commercial cuts to the same circular “ ON-THE-SPOT LOAN ” mark by itself on a pale paper background.
The paper is revealed to be part of a \textbf{bank} check or loan document lying diagonally on a dark burgundy surface.
On the left is a detachable-looking section with a dotted vertical line and the circular “ ON-THE-SPOT LOAN ” \textbf{emblem}.
On the right, large printed text at the top reads “ Chemical New York. ” Smaller form lines, numbers, and handwriting appear across the check, including a signature area, though most of the details are too small or blurred to read clearly.
The check remains centered as a clean, flat product image, presenting the loan visually as an official \textbf{bank} document.
The scene changes to a red 1960s Ford Mustang \textbf{driving} through a bright, arid landscape.
At first the rear-left side of the car fills much of the view.
The car has squared-off rear lights, \textbf{chrome} trim, and a license plate that appears to read “ 1967. ” It moves away along a pale road bordered by sand and low desert scrub.
Through the rear window, a driver is faintly visible, but details of the person are indistinct.
The Mustang continues farther down the road, shrinking into the open desert.
The surroundings are flat and \textbf{sunlit}, with low \textbf{bushes} scattered on both sides and a \textbf{hazy} horizon in the distance.
The car ’s red body stands out against the cream-colored sand and muted \textbf{sky}.
Later it is seen from the front at an angle, \textbf{driving} toward and \textbf{past} the viewer ’s side of the road.
The Mustang \textbf{emblem} is visible in the center of the front grille, and the same “ 1967 ” plate is mounted below.
The driver remains only a dark figure behind the windshield.
The commercial ends on a large \textbf{outdoor} sign for the \textbf{bank}, set against dark foliage with a bright \textbf{glare} of sunlight near the top.
The sign reads “ Chemical New York ” in large white serif letters.
Beneath it, smaller text reads “ CHEMICAL BANK NEW YORK TRUST COMPANY. ”

% matched lemmas: bank, bush, chrome, drive, dry, dusty, emblem, gather, glare, ground, hazy, outdoor, pass, past, path, reddish, rock, rough, shadow, silhouette, sky, sunlit, tight, trail
\end{textsample}
