\begin{textsample}{POS Dim 2 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_82.txt}  \label{ex:f2_pos_089}
The commercial opens in black and white with a large high-top canvas sneaker standing alone on a flat, painted-looking \textbf{outdoor} \textbf{ground} beneath a cloudy \textbf{sky}.
The shoe is shown in profile, toe pointing right.
It has a dark canvas upper, a thick light rubber sole, a rounded white rubber toe cap, white laces, and a circular ankle patch reading “ U.S.
Keds. ” From the top of the shoe, an animated clown-like mascot pops up.
He has a round, cheerful face with a big dark nose, a tiny top hat, a ruffled collar, oversized gloves, and a loose white costume decorated with large spots.
Across his chest, the name “ Kedso ” is visible.
He holds a small umbrella and raises his arms broadly, grinning and gesturing like a performer greeting an audience.
Kedso continues to perform from inside the giant shoe, tipping or lifting his tiny hat, holding the umbrella upright, and waving his gloved hands.
His expressions change from open-mouthed delight to a pleased smile.
He leans forward, spreads his arms, and then springs upward out of the shoe, leaving the top of the sneaker visible below him against the cloudy background.
The scene shifts to a textured \textbf{ground} with bold white words on the right : “ IF YOU WANT SHOES. ” Kedso dances on the left side of the words, using his umbrella like a cane or baton.
He hops, kicks one leg high, and \textbf{balances} on one foot, his oversized shoe soles flashing as he moves.
The text changes to “ WITH LOTS OF PEP, ” still in large block letters on the right, while Kedso keeps stepping and kicking beside it.
A close view of the sneaker ’s ankle patch follows, showing the round “ U.S.
Keds ” logo stitched onto the dark canvas near the laces.
More lyric-style text appears beside Kedso : “ FOR BOUNCE AND ZOOM. ” He continues a jaunty dance, lifting one knee and swinging the umbrella overhead.
The words then change to “ IN EVERY STEP, ” while he points the umbrella toward the lettering and steps in place.
The round “ U.S.
Keds ” patch appears again in close view, and the circle briefly transforms into a smiling cartoon boy ’s face with closed, happy eyes and a wide grin, visually linking the logo with children.
Kedso then appears on a baseball field.
He stands near home plate holding a bat over his shoulder, his spotted outfit and tiny hat still prominent.
He swings at a baseball, lifts one leg dramatically, and twists his whole body through the motion.
The bat sweeps across the scene, and he bounces and spins with exaggerated cartoon energy.
He crouches low, then rockets forward across the field, leaving motion \textbf{trails} behind him.
The field stretches into the distance with a cloudy \textbf{sky}, dark \textbf{tree} shapes, and a small sign or scoreboard-like structure at the far left.
A baseball sails high through the \textbf{sky}, grows very large as it comes toward view, and then the scene returns to the field, where Kedso walks along with a baseball glove tucked behind him and one foot lifted in a jaunty stride.
A baseball floats against a plain background, and the image changes into a circular “ U.S.
Keds ” logo.
The circle then changes again into the smiling cartoon boy ’s face, and back once more to “ U.S.
Keds. ” Kedso appears leaning casually against a barrel on a \textbf{rough} \textbf{outdoor} \textbf{ground}.
The barrel has dark bands around it, and Kedso rests one arm on it with a satisfied smile, his chest again marked “ Kedso. ” Live-action footage follows.
Two boys walk together across a \textbf{broad} open field in daylight.
The older boy, on the left, appears to be a teenager wearing a light short-sleeved shirt, cuffed trousers, and sneakers.
The younger boy, on the right, wears a striped short-sleeved shirt, shorts, socks, and sneakers.
They walk side by side across \textbf{dry} \textbf{ground} with \textbf{trees}, utility poles, distant cars, and low hills in the background.
They slow and stop, looking down toward something ahead of them.
Kedso is now standing on top of the small barrel in the field, at the boys ’ feet.
The live-action boys \textbf{pass} close by, their sneakers prominent as they step around him.
They crouch down to his level, smiling and leaning in with curiosity.
Kedso gestures animatedly with both hands and his umbrella, addressing them from the barrel top.
The older boy squats on the left, the younger boy squats on the right, both focused on the little mascot.
Kedso hops and waves, while the boys remain crouched and attentive.
A close animated view of Kedso follows.
He holds the umbrella in one hand, points upward with the other, then brings a hand to his forehead as if shading his eyes or calling attention to something.
His face shifts from thoughtful to confident as he looks off to the side.
A white high-top Keds shoe is shown from the heel and side.
Near the heel, the slogan “ The Shoe of Champions ” is printed in script, and below it is a rectangular label reading “ u.s.
Keds. ” A large white arrow graphic points directly at the label, emphasizing where to look.
The view tightens on the same heel area so that “ The Shoe of Champions ” and the “ u.s.
Keds ” label fill the screen.
The product is then displayed as a clean white high-top sneaker lying on a plain surface under dramatic lighting.
It has metal eyelets, a white rubber sole, a rounded toe, and loose laces spilling forward.
The shoe is opened up to reveal its interior : the tongue is pulled back, the upper lies partly collapsed, and the insole becomes visible.
Inside the shoe, printed markings identify comfort features.
A closer view shows the text “ CUSHIONED INSOLE ” and “ SHOCK-PROOF ARCH CUSHION, ” with curved stripe-like graphics marking the arch support area.
The live-action boys reappear standing outdoors against a bright \textbf{sky} with clouds.
Both are smiling and wearing plain light T-shirts with pinned ribbons or \textbf{badges} that read “ CHAMP. ” Each boy raises a Keds sneaker above his head like a trophy.
The older boy on the left holds up a dark high-top shoe with a light sole and visible round ankle patch ; the younger boy on the right raises another dark sneaker with a light sole.
They hold the shoes high, grinning proudly.
The commercial ends with the animated Kedso standing beside a large circular “ US RUBBER ” logo.
The logo is dark with big white letters “ US ” and the word “ RUBBER ” beneath.
Kedso faces it and tips his tiny top hat upward with one gloved hand while resting the other hand against his chest, smiling in a final showman-like pose.

% matched lemmas: badge, balance, broad, dry, ground, outdoor, pass, rough, sky, trail, tree
\end{textsample}
