\begin{textsample}{POS Dim 2 – 1960 – Score 36.00 – 1960/tv\_com\_1960\_80.txt}  \label{ex:f2_pos_001}
In black and white, the commercial opens tightly on the rear of a fire \textbf{truck}, where a large rectangular warning sign reads “ KEEP BACK 500 FEET ” in bold white block letters.
The view shifts to pieces of firefighting gear : tall rubber \textbf{boots} standing on the \textbf{pavement} as someone steps into them and pulls at the tops, then helmets and tools hanging from the side of a fire engine.
A firefighter climbs onto the \textbf{truck} ’s side step near metal valves, hoses, and equipment.
The same “ KEEP BACK 500 FEET ” sign appears again, followed by \textbf{silhouetted} firefighters beneath an overhead structure as a long ladder rises diagonally across the scene.
The fire \textbf{truck} moves through city streets with its ladder stacked along the side and equipment packed onto running boards.
As it \textbf{drives}, the view settles on one of its large tires, where the word “ Firestone ” is clearly visible on the sidewall.
The montage broadens to other kinds of \textbf{vehicles} and wheels.
A flatbed \textbf{truck} carries rows of \textbf{heavy} rectangular \textbf{bundles} or crates, \textbf{secured} between upright stakes.
In a \textbf{rural} field, a tractor pulls farm equipment through \textbf{rough} soil, its large rear tire \textbf{rolling} over stubble and dirt.
A long station wagon \textbf{drives} along a road beside a body of water, with several passengers visible through the side windows.
A large industrial \textbf{truck} with a long elevated framework travels over sandy, rutted \textbf{ground}, suggesting \textbf{heavy} \textbf{outdoor} work.
A young child rides a small tricycle or toy bike along a sidewalk while an adult woman, wearing a skirt and light top, runs alongside and steadies it with her hands ; she stretches one leg back as she keeps \textbf{pace}, helping the child move forward.
A low open car, possibly a small sports car, \textbf{drives} away down a tree-lined road, framed by dark foliage on both sides.
The sequence continues with wheels in more demanding settings.
A jet airliner comes in low over a runway, its landing gear down ; the \textbf{underside} of the plane and its clustered wheels fill the scene as they approach the \textbf{pavement}.
The side of the aircraft carries the partly visible words “ FLY EASTERN. ” A person \textbf{pushes} a lawn mower through tall \textbf{grass} near garden plants, with the mower ’s small wheels \textbf{rolling} over the lawn.
A bulldozer or earthmover \textbf{pushes} a \textbf{broad} wall of dirt forward with a wide front blade, the soil spilling and crumbling in front of it.
In a marshy or \textbf{muddy} \textbf{outdoor} area, a rugged \textbf{vehicle} with oversized tires \textbf{drives} through shallow water, reeds and \textbf{trees} around it.
A small golf \textbf{cart} with two seated adults moves away along a smooth \textbf{path} bordered by dense hedges.
Then a very large cylindrical load, resembling industrial or oil-field equipment, is hauled on a multi-wheeled trailer through a street scene with utility poles and other \textbf{vehicles} in the background.
A close view follows the wheels of a \textbf{bicycle} as a rider pedals along a \textbf{paved} surface.
The thin tires spin rapidly, with the rider ’s shoes pressing the pedals in a steady cycle.
Next, on a wet road in the rain, a car tows a large white cabin boat on a trailer.
Water glistens on the \textbf{pavement}, reflections shimmer beneath the tires, and other cars sit or \textbf{pass} nearby.
The boat ’s hull dominates the scene as the trailer \textbf{rolls} by, emphasizing the many small wheels underneath.
A \textbf{brief} close-up shows a car tire turning beside a rounded fender.
A child then rides in a small pull wagon on a sidewalk.
The wagon ’s side panel is clearly labeled “ Firestone CRUISER, ” with the Firestone name in a lighter inset panel and “ CRUISER ” in bold letters to the right.
The child, seen from the torso down, sits inside with one arm resting over the wagon ’s side and one leg bent, while the wagon ’s \textbf{whitewall} wheels \textbf{roll} smoothly.
The Firestone name fills the screen in a close view on the wagon side.
The final action \textbf{shots} return to roads and \textbf{heavy} traction.
A full-size car \textbf{drives} through rain on a slick urban road, its front grille and headlights approaching low to the wet curb before it \textbf{passes} close by, \textbf{throwing} spray from the tires.
Then a rugged \textbf{vehicle} pulls a boat or boat-like trailer through a \textbf{dusty}, \textbf{rough} surface ; dust billows around the wheels and partly \textbf{obscures} the \textbf{bodywork} as the tire churns through the \textbf{ground}.
The dust thickens until the image becomes \textbf{hazy}.
Out of the \textbf{haze} emerges the Firestone brand graphic : a pale outline map of the United States above the large script word “ Firestone, ” displayed as the closing visual \textbf{emblem}.

% matched lemmas: bicycle, bodywork, boot, brief, broad, bundle, cart, drive, dusty, emblem, grass, ground, haze, hazy, heavy, muddy, obscure, outdoor, pace, pass, path, paved, pavement, push, roll, rough, rural, secure, shot, silhouette, throw, tree, truck, underside, vehicle, whitewall
\end{textsample}
