\begin{textsample}{POS Dim 2 – 1960 – Score 32.00 – 1960/tv\_com\_1960\_54.txt}  \label{ex:f2_pos_002}
The commercial opens in stark black and white with an extreme close view of a shiny circular metal fitting on the car, possibly a dashboard control or ignition area.
A small ridged, key-like piece sits beside the \textbf{chrome} ring and appears to move into place, catching bright highlights against dark reflections.
The imagery is \textbf{tight} and mechanical, emphasizing polished metal surfaces and the act of starting or engaging the car.
The view then jumps to the front of a light-colored AMC Rebel.
Its face fills the scene : a long dark rectangular grille, round headlights set in dark surrounds, a bright \textbf{chrome} bumper, and small spaced letters across the front edge of the hood.
The car is outdoors near \textbf{bushes} and open countryside.
The front end glides \textbf{past} from one side to the other, lingering on the grille and paired headlights before the image gives way to \textbf{rough} \textbf{outdoor} textures, like scrubby \textbf{grass} or \textbf{brush}.
A light-colored convertible Rebel then appears head-on on a \textbf{paved} road bordered by low walls or curbs.
An adult woman \textbf{drives}, visible above the windshield.
She has dark hair pulled back neatly, and her posture is upright and composed as she faces forward.
The car moves toward and then \textbf{past} the viewer, its \textbf{broad} flat hood, rectangular grille, and four round headlights prominent.
This is followed by a graphic background of dark clouds crossed by jagged white lightning-like lines.
Large bold block letters appear in the center reading “ THE NOW CARS, ” first in white over the stormy background, then in black on a plain light background.
The Rebel returns in a side \textbf{silhouette}.
The convertible top is down, and the woman driver is seen in profile as a dark outline against a bright \textbf{sky}.
Her hair is \textbf{gathered} at the back of her head, and the windshield frame and open cabin form clean angular lines around her.
Huge white block letters reading “ REBEL ” rise across the lower half of the picture, partially covering the car ’s side.
As the car moves \textbf{past} \textbf{trees}, the driver ’s \textbf{silhouette} alternates between bright \textbf{sky} and dark foliage, while the word “ REBEL ” remains large and bold in front.
The car is next shown cruising along a tree-lined road in a leafy, suburban or park-like setting.
The light-colored convertible moves smoothly from left to right, its long body and open top clearly visible between \textbf{tree} \textbf{trunks} and dense foliage.
The surroundings are shaded, with bright patches of \textbf{sky} and road contrasting with dark \textbf{branches}.
A close view of a small side \textbf{emblem} follows : a dark rectangular \textbf{badge} above a V-shaped \textbf{chrome} ornament on the car ’s body, suggesting engine or trim identification.
The \textbf{emblem} is mounted on the smooth light body panel, near a thin horizontal crease line.
The Rebel continues along the road, now seen from the front three-quarter angle.
The adult woman remains alone at the wheel, looking ahead through the open windshield.
The car ’s low, squared front, \textbf{chrome} bumper, and paired headlights are repeatedly emphasized as it \textbf{drives} through alternating \textbf{shadow} and light.
From inside the car, the dashboard is shown behind the driver.
The woman ’s hands hold the \textbf{steering} wheel ; the dashboard has a \textbf{broad} rectangular instrument panel, round knobs, and a simple horizontal layout.
The windshield wipers rest at the base of the windshield, and the hood stretches out ahead.
The view moves across the dashboard toward the passenger side, showing the wide front bench area and open cabin.
A white picket \textbf{fence} appears, first as a close blur of pointed \textbf{fence} tops, then as two open gate panels framing a driveway or \textbf{path}.
Beyond the gate is an open rural-looking area with \textbf{trees} and low horizon.
The Rebel enters from the left beyond the gate, partly \textbf{obscured} by dust or road \textbf{haze}, and \textbf{drives} away into the distance.
The white \textbf{fence} panels stand on both sides like a gateway, their pointed tops bright against the darker \textbf{ground} and \textbf{trees}.
A quick close-up shows the script “ Rebel ” \textbf{badge} on the side of the car, mounted on a light body panel near a vertical door seam.
The front of the car is then shown again in motion, traveling along a road.
The imagery studies the grille from left to right : \textbf{twin} round headlights, the dark central grille, hood lettering spaced above it, the small Rebel \textbf{badge} in the grille, and the \textbf{chrome} bumper below.
The car then appears far out in an open landscape under a \textbf{heavy}, cloudy \textbf{sky}.
It approaches across a low horizon, the convertible body bright against dark \textbf{ground}, then sweeps \textbf{past}.
A tall metal windmill stands alone in the field, its circular blade wheel and tail \textbf{silhouetted} against the overcast \textbf{sky}.
The windmill is shown closer and closer until its radial blades fill the image like a spinning pattern of dark and light spokes.
This circular pattern gives way to an overhead view of the open convertible interior.
The woman driver sits in the front seat, wearing a dark top and long earrings, her face in profile and her expression calm and focused.
She grips the steering wheel with both hands and looks forward.
The light-colored upholstery is visible around her : a \textbf{broad} front bench seat and a rear bench behind it, both with stitched, padded sections.
The view settles on the seats, showing the spacious cabin.
The rear bench has multiple seating positions, with rectangular seat-belt buckles or latch points visible on the cushions ; the front bench has thick padded bolsters and a central backrest area.
The open-top layout makes the two rows of seats easy to see from above.
The Rebel is again shown traveling on a long \textbf{paved} road bordered by dark \textbf{trees} or fencing.
It \textbf{passes} from the side and then appears from a front three-quarter angle, top down, with the woman still \textbf{driving}.
The car holds a steady lane, its white body contrasting with the dark roadside.
A close interior view focuses on the \textbf{steering} wheel and column.
The driver ’s hands hold the wheel, and the column and hub are clearly visible, with the dashboard controls nearby.
The \textbf{shot} emphasizes the \textbf{steering} assembly and its sturdy central column before returning to the moving car outside.
The car speeds \textbf{past} from the front and side, then continues away down an open road.
Its rear end is visible with squared tail lamps, a straight \textbf{trunk} line, and a \textbf{chrome} rear bumper.
The convertible top remains folded down behind the rear seat.
The car grows smaller as it travels along the road into open countryside.
The storm-cloud graphic with jagged white lightning returns, followed by more fast, abstract close views of dark horizontal \textbf{rails} or structural beams, as if the car is moving through or across a bridge-like structure.
Large white block letters spelling “ REBEL ” fill the center of the image over these dark metal lines.
The word is massive and bold, occupying most of the picture.
The final sequence shows the light-colored convertible driving through a bridge or elevated roadway with \textbf{heavy} vertical and diagonal metal supports crossing in the foreground.
The car is seen from above and at a distance, moving along the lane beneath the dark framework.
In the lower left, large white text appears : “ THE 1967 AMERICAN MOTORS. ” The car continues through the repeating beams and railings, partially \textbf{hidden} at times by the structure.
Near the end, an enormous white word “ NOW ” appears across the center, covering most of the view while the car and bridge structure remain faintly visible behind it.
The commercial closes with this oversized “ NOW ” dominating the image.

% matched lemmas: badge, branch, broad, brush, bush, chrome, drive, emblem, fence, gather, grass, ground, haze, heavy, hide, obscure, outdoor, pass, past, path, paved, rail, rough, shadow, shot, silhouette, sky, steering, tight, tree, trunk, twin
\end{textsample}
