\begin{textsample}{POS Dim 2 – 1960 – Score 21.00 – 1960/tv\_com\_1960\_75.txt}  \label{ex:f2_pos_008}
In black and white, the commercial opens at a sports-car paddock under a bright, cloudy \textbf{sky}.
Low, open racing cars are parked on \textbf{pavement}.
At the left, a light-coloured roadster has its hood raised and a racing number on the door.
To the right, a darker, low open car is being readied.
A young adult man in a light racing outfit leans over the dark car, while two women stand nearby ; one appears seated or leaning inside the open cockpit, and another, a blonde woman in light pants and a darker top, \textbf{pushes} or steadies the car from the rear side.
The scene has the look of a race staging area, with other cars and thin poles or masts in the background.
The dark open racing car \textbf{rolls} forward toward the foreground.
Its front grille is oval and pale, the wheels are exposed, and a \textbf{roll} bar rises behind the seats.
The man in the light racing clothes moves beside it, and the blonde woman continues to \textbf{push} from the right side.
Large racing numbers and letters are visible on the car ’s body as it \textbf{passes} close.
The attention then moves to the car ’s shiny dark \textbf{bodywork} near the small windshield.
A pack of Camel cigarettes lies on the car, close to the windshield and \textbf{steering} wheel.
The pack is light-coloured with the word “ CAMEL ” and the camel illustration visible on its top and side.
A hand reaches in, picks up the pack, and lifts it away.
The young man in the white racing outfit stands beside the car with the blonde woman nearby.
He opens the cigarette pack and handles a cigarette while she also holds a cigarette or small item in her hands.
They stand at the edge of the track or paddock, with flat open \textbf{ground} and fencing behind them.
He looks down at the pack, then toward the woman, and offers or exchanges something with her.
Both now have cigarettes at their mouths.
He puts one between his lips, brings his hands to his chest as if tucking the pack or another item into his jacket, and smiles slightly while the woman looks down at what she is holding.
A closer view shows the man ’s face and upper body.
He has dark, neatly combed hair and wears a white racing jacket over a dark collar.
A cigarette rests between his lips.
Bold white capital letters appear across the lower part of the image : “ EVERY INCH A REAL SMOKE. ” He cups a lighter or match in both hands and lights the cigarette.
After lighting it, he lowers his hands, takes a drag, and looks ahead with a calm, focused expression.
The image transitions into the track itself.
A long \textbf{shadow} falls across the \textbf{paved} road, then the open racing \textbf{course} stretches into the distance, bordered by \textbf{grass}, low fencing, \textbf{trees}, and a small raised observation booth on the right.
A light-coloured sports car speeds away down the centre of the road.
Other cars \textbf{rush} \textbf{past}, some blurred from their speed, including darker open racers and light roadsters.
The race cars spread across the track in a loose pack as they head toward a bend.
A dark open car with a helmeted driver races along a wooded section.
The driver wears a white helmet and dark goggles.
The car \textbf{passes} near a light-coloured roadster, sometimes drawing alongside it.
A close view of the driver ’s face fills the image : he is framed by the \textbf{roll} bar and windshield, hands on the \textbf{steering} wheel, eyes \textbf{hidden} behind large goggles, expression steady and concentrated.
On-screen text in bold white capitals identifies him as “ BOB SHARP. ” Other race cars appear behind him, moving in and out of the background as he \textbf{drives}.
More racing action follows.
From a low roadside angle, cars streak by, leaving dust or road spray behind.
The \textbf{paved} track curves through open \textbf{grass} and \textbf{trees}.
The surface looks damp in places, with puddles reflecting the \textbf{sky} and \textbf{passing} cars.
Inside the car, the \textbf{steering} wheel and dashboard are shown close-up : the wheel has metal spokes with circular holes, and round gauges sit behind it.
A gloved hand holds the wheel ; another close view shows a gloved hand working a gear lever beneath the dashboard.
The driver shifts decisively, then returns to the race.
Cars sweep around a \textbf{broad} curve.
A light roadster flashes \textbf{past} first, then the dark open car follows, its front grille and exposed wheels prominent as it comes toward the viewer and turns through the bend.
From behind and alongside, the dark car appears among several competitors, including light-coloured roadsters on both sides.
The group moves tightly on the wet-looking road.
From \textbf{ground} level beside a puddle, cars \textbf{pass} one after another, their shapes reflected briefly in the water before they disappear, leaving a misty \textbf{trail} across the track.
The race sequence gives way to the dark number 33 car parked on \textbf{grass} near a chain-link \textbf{fence}.
The driver sits in the cockpit, still wearing his white helmet and goggles.
The large number “ 33 ” is painted prominently on the hood.
A light-coloured roadster \textbf{passes} in the background beyond the \textbf{fence}.
Two women approach from the left : the blonde woman in light pants and a sweater with a \textbf{broad} light stripe near the neckline, and a dark-haired woman in a light top and plaid skirt.
They lean in toward the car as if greeting or checking on him.
The driver removes his helmet, revealing the same dark-haired young man, and lowers his goggles around his neck.
He rubs or wipes his face with one hand, then looks down into the cockpit and reaches for something.
The women stand beside the car, watching him.
He brings out a cigarette pack or cigarette, settles back in the seat, and places a cigarette at his mouth.
A closer view shows his face from the side, goggles hanging at his chest, his white racing suit open at the neck.
A hand from the left, belonging to one of the women, comes in to help light the cigarette.
He cups the flame with both hands and leans forward to light it.
The Camel pack is then shown clearly on the dark car surface : the word “ CAMEL ” appears in large letters above the camel illustration, with smaller package text below including “ Turkish \& Domestic Blend Cigarettes. ” The pack ’s light wrapper contrasts against the glossy dark body of the car.
Back on the driver, he finishes lighting the cigarette and takes a drag.
The assisting hand withdraws.
He holds the cigarette between his fingers, smoke visible near his mouth, and looks upward toward the women with a relaxed, pleased expression.
Bold white capital letters again appear across the lower image : “ EVERY INCH A REAL SMOKE. ” He smiles and glances up and to the side, the goggles still resting at his collar.
The final image returns to the long straight track with \textbf{trees} in the distance and the observation booth on the right.
Large white block letters spelling “ CAMEL ” appear across the bottom of the screen.
Race cars continue to speed down the road above the lettering.
A large Camel cigarette pack graphic then appears centered over the roadway, growing prominent in the middle of the image.
The pack shows the camel illustration and the word “ CAMEL ” at the top, with smaller text beneath, while the large “ CAMEL ” brand name remains across the bottom.

% matched lemmas: bodywork, broad, course, drive, fence, grass, ground, hide, pass, past, paved, pavement, push, roll, rush, shadow, sky, steering, trail, tree
\end{textsample}
