\begin{textsample}{POS Dim 2 – 2020 – Score 28.00 – 2020/tv\_com\_2020\_83.txt}  \label{ex:f2_pos_043}
The commercial opens on a bright, sunny suburban scene.
A large red-brick, two-story house with white trim sits behind a neatly clipped hedge and \textbf{broad} green lawn.
Bare \textbf{winter} \textbf{trees} and neighboring homes surround it, and the low \textbf{sun} creates \textbf{glare} and long \textbf{shadows} across the \textbf{grass}, giving the scene a crisp holiday-season feeling even though the lawn is still green.
The view shifts to a glossy black Jeep SUV traveling along a \textbf{paved} road bordered by woods.
It is seen from the side, moving smoothly \textbf{past} a guardrail with dense green \textbf{trees} in the background.
Sunlight flashes across its hood and roof \textbf{rails}, and the dark paint reflects the roadside scenery as it \textbf{drives}.
A holiday sales graphic appears over an overhead view of a \textbf{snowy} park.
A tall \textbf{outdoor} Christmas \textbf{tree}, dusted with \textbf{snow} and topped with a red star, stands near winding \textbf{paths} where small pedestrians are visible.
Centered over the \textbf{tree} is a red gift-bow graphic and bold white text inside a red outlined box reading “ WRAP UP THE \textbf{YEAR}, ” with “ SALES EVENT ” beneath it and the Jeep logo below.
Snow covers the \textbf{ground} and garden areas around the \textbf{paths}.
A white Jeep SUV then \textbf{drives} through a \textbf{snowy} landscape lined with evergreen \textbf{trees} decorated in warm white holiday lights.
The \textbf{vehicle} approaches from the right side of the \textbf{snowy} road, its front grille and headlights prominent.
The white body contrasts with the dark green \textbf{trees} and the soft blue-white \textbf{snow}, while the tires leave tracks in the packed \textbf{snow}.
The focus changes to a red Jeep Wrangler plowing through deep \textbf{snow}.
It faces forward at a slight angle, with round headlights, a black seven-slot grille, black bumper, and \textbf{snow} scattered across its hood.
Powdery \textbf{snow} sprays high around the front wheels and along both sides, suggesting forceful movement through difficult terrain.
Large white text at the bottom reads “ JEEP WRANGLER ” and “ MOST CAPABLE WRANGLER EVER, ” with a fine-print disclaimer running along the lower edge.
Inside a Jeep Grand Cherokee, the dashboard is shown straight on from the front seats.
The \textbf{steering} wheel with the Jeep \textbf{badge} is on the left, and a large central touchscreen displays a map.
The interior has dark surfaces with warm wood-toned trim stretching across the dash, along with climate controls below the screen.
White text across the bottom reads “ JEEP GRAND CHEROKEE ” and “ MOST LUXURIOUS \textbf{VEHICLE} IN ITS CLASS, ” again with small disclaimer text beneath.
A close view of the outside of a dark \textbf{vehicle} follows, showing the “ Grand Cherokee ” \textbf{badge} mounted on the side panel.
The glossy paint reflects a rocky roadside and mountain-like landscape, with the lettering catching light as the \textbf{vehicle} moves.
The red Wrangler returns, now \textbf{driving} on a \textbf{dusty}, rocky \textbf{trail} cut into a hillside.
It moves along the uneven dirt road beside a slope of loose \textbf{stones} and scrubby plants.
Dust rises behind and around the tires.
White on-screen text identifies “ JEEP BRAND ” and says “ MOST AWARDED SUV BRAND EVER, ” with fine print along the bottom.
The Wrangler ’s rugged front, round headlights, black fenders, and red body remain prominent as it continues along the \textbf{trail}.
The same award text stays on screen as the scene changes to a distant view of a white SUV traveling along a narrow road through a \textbf{snowy} forest.
Snow blankets the hillsides and the \textbf{ground} on both sides of the road, while dark evergreen \textbf{trees} fill the background.
Tall \textbf{trees} \textbf{pass} in the foreground, partially \textbf{obscuring} the \textbf{vehicle} at moments as it moves steadily along the \textbf{winter} road.
The commercial then shows a nighttime town scene from above.
Streets and buildings are decorated with bright holiday lights, and a large illuminated Christmas \textbf{tree} glows near the center of the town.
Over this festive aerial view, large white text reads “ NO MONTHLY PAYMENTS FOR 90 DAYS, ” with smaller text underneath, “ ON MOST JEEP BRAND MODELS. ” At the bottom is an “ America 250 ” logo, with dense legal fine print spanning the lower edge.
A red Jeep Wrangler \textbf{drives} away on a \textbf{snowy} forest road, its rear-mounted \textbf{spare} tire visible. \textbf{Snow} sprays from the tires as it follows the curving road between \textbf{banks} of \textbf{snow} and dark evergreen \textbf{trees}.
A large white “ Jeep ” logo appears centered over the \textbf{vehicle}, with the slogan “ THERE ’S ONLY ONE ” beneath it.
The “ America 250 ” mark and small disclaimer text remain along the bottom.
The final image is a static dealer-offer screen.
A white 2025 Jeep Grand Cherokee Laredo 4x4 is parked in front of a gray civic-looking backdrop with a large green statue behind it, suggesting Detroit.
On the left, bold white text advertises a lease offer : “ \$280/mo. ” and “ \$280 due at signing, ” with “ \$0 down payment ” below, for qualified current FCA US employee lessees on select dealer-stock models.
A small “ Wrap Up the \textbf{Year} ” sales event logo appears near the lower left.
Along the bottom are Jeep and dealer contact details, including “ JEEP.COM ” and a phone number for lease details.
On the lower right, large branding reads “ METRO DETROIT | Jeep. ”

% matched lemmas: badge, bank, broad, drive, dusty, glare, grass, ground, obscure, outdoor, pass, past, path, paved, rail, shadow, snow, snowy, spare, steering, stone, sun, trail, tree, vehicle, winter, year
\end{textsample}
