\begin{textsample}{POS Dim 2 – 1960 – Score 12.00 – 1960/tv\_com\_1960\_83.txt}  \label{ex:f2_pos_019}
The commercial begins in black and white with a \textbf{tight} view of the Polaroid Big Swinger instant camera held in someone ’s hands.
It is a boxy, two-tone camera with a square, gridded front panel, a round dark lens in the middle, a small viewfinder assembly on top, and the words “ BIG SWINGER ” visible along the lower front.
A hand steadies the side of the camera and then begins manipulating it.
The camera is turned and opened so its back and inner compartment are visible.
A small metal ring or tab is pulled, a hinged section swings open, and a dark rectangular film compartment is exposed.
The hands place or adjust a flat dark panel inside, then close the camera back.
On the rear of the camera there is a rectangular instruction label filled with small printed lines, though the wording is too small to read clearly.
The setting shifts outdoors into very bright sunlight.
The first glimpses are high-contrast \textbf{silhouettes} and soft \textbf{glare}, with faces and horse shapes partly washed out by the \textbf{sun}.
Young adult riders come into view on horseback, moving through an open, rural-looking area with \textbf{trees} in the background.
There are several riders, both men and women, wearing casual 1960s riding clothes rather than formal equestrian gear.
Dust rises around the horses ’ legs as they move along a \textbf{path} or field.
A young woman with long dark hair held back by a wide headband rides near the front.
She wears a light, close-fitting sweater and pants, smiles often, and holds the reins in front of her.
A boxy Big Swinger camera hangs or rests near her lap by its strap.
Beside and behind her are young men on horses, one in a light ribbed turtleneck-style sweater with a dark stripe at the collar and cuffs, another in a light open jacket or shirt over a darker top.
Their horses include dark and light-colored mounts, with bridles and reins visible.
The riders look relaxed and playful, smiling as they ride toward the viewer under open \textbf{sky}.
The camera is shown bouncing lightly against a rider ’s thigh while the horse moves, emphasizing that it is being carried along during the ride.
The young woman with the headband appears again from a low angle, smiling with the wind moving her hair.
A young man on horseback grins broadly, his hair ruffled, while the horse ’s head fills part of the foreground.
Another woman rider appears behind a horse ’s head, smiling as the horse tosses its mane.
One young man in the light sweater lifts the Big Swinger to his face while seated on his horse.
He holds the camera with both hands, brings the viewfinder to his eye, and aims it across the group.
The horse ’s head is close beside him, its mane and bridle visible.
After using the camera, he lowers it and laughs.
Another smiling young man in a white sweater playfully holds the camera out toward the viewer, tilting the front so the round lens and square face are prominent.
The woman with the headband rides \textbf{past} again, smiling.
Then her hands are shown working with a fresh instant photograph.
She holds a pale rectangular print in one hand and a darker backing or negative sheet in the other, peeling the two apart.
A large white-bordered black-and-white photograph is then displayed.
In the picture, the headbanded woman is captured riding in the open field, smiling over her shoulder, with her hair blown back and the landscape stretching behind her.
A thumb holds the lower corner of the print, making its large size clear.
The young man in the light sweater looks off to the side and gestures, as if calling someone ’s attention.
The woman with the headband reacts with a wide open-mouthed expression, smiling or laughing while clutching the reins and the camera against her chest.
The man smiles back.
She then raises the Big Swinger to her own face, holding it with both hands and aiming it while her hair blows sideways in the wind.
After taking the picture, she lowers the camera and pulls a long sheet or developing strip from it, then peels apart another instant print.
The riders continue moving together through the field.
The headbanded woman rides at one side, and a young man on a dark horse rides near the center, with another rider behind them.
The scene remains bright and outdoorsy, with \textbf{trees}, open \textbf{sky}, and dust in the background.
Another finished white-bordered photograph is held up : it shows a smiling young man on horseback, turned toward the camera with a horse and a large \textbf{tree} behind him.
The print is held close enough that the image fills most of the view.
The young woman with the headband is shown again holding the camera near her waist as she rides.
She smiles and points forward, appearing to direct attention toward another subject.
A young man in the open light jacket laughs on horseback while holding the Big Swinger.
A blonde young woman in a dark turtleneck and a dark cap rides nearby, smiling broadly over her shoulder.
Her light hair is \textbf{gathered} back, and the cap sits low and jaunty on her head.
The man in the light jacket turns toward her, then raises the Big Swinger to his eye, holding the reins and camera strap while aiming at her from horseback.
The blonde woman in the dark cap smiles and poses as she rides, one hand on the reins.
She looks lively and amused, with the horse ’s ears and mane entering the foreground.
The man continues aiming the camera at her.
Afterward, his hands are shown peeling apart another instant photograph against the front of his clothing.
He separates a pale print from a dark backing sheet.
The completed print is held up : a white-bordered black-and-white photo of the blonde woman on horseback, smiling back toward the camera in the open field with \textbf{trees} behind her.
The man in the light jacket laughs and looks toward the other riders, holding the camera and its strap while mounted.
The blonde woman, still in her dark cap and turtleneck, holds the Big Swinger herself and laughs with her mouth open, appearing delighted.
The camera ’s rectangular body is visible in her hands as she rides beside her horse ’s head.
Near the end, the camera is again shown in close detail while being carried on horseback.
A hand with a ring grips the top and side of the camera ; the striped front panel and round lens face outward, and the long rectangular body extends down toward the rider ’s lap.
The open field and \textbf{fences} blur behind it.
The product remains the visual focus as the riders continue moving.
The final scene shows the group riding away from the viewer down a \textbf{dusty} \textbf{path} lined with \textbf{trees}.
Several horses and riders recede into the distance, their backs visible as dust hangs low over the \textbf{ground}.
A large translucent image of the Big Swinger camera briefly overlays the riding scene, tying the product to the action.
Then bold white on-screen text appears over the riders and dust : “ The Big Swinger ” in large letters, with “ 24⁹⁵ ” beneath it.
Smaller text below reads “ suggested list price. ” The riders continue into the background behind the large price and product name.

% matched lemmas: dusty, fence, gather, glare, ground, past, path, silhouette, sky, sun, tight, tree
\end{textsample}
