\begin{textsample}{POS Dim 2 – 2000 – Score 30.00 – 2000/tv\_com\_2000\_25.txt}  \label{ex:f2_pos_022}
A very young boy in a red-and-gray striped T-shirt and a dark baseball cap worn backward beams with his mouth open, leaning forward excitedly beside a smiling blonde woman in a light shirt.
They are outdoors near a house or patio, with potted greenery and white trim behind them.
The woman crouches close to him and raises one hand in a cheerful wave, while the boy looks ahead with delighted anticipation.
A large red toy motorcycle fills the lawn, styled like a cruiser with black handlebars, a black seat, chrome-colored pipes, round headlights, and flame decals on the body.
An adult man in a black shirt and light pants moves in from the side, hands out as if guiding or steadying.
The little boy in the striped shirt runs up and climbs onto the motorcycle, lifting one leg over the seat while the man stays close behind.
The boy settles onto the seat, grips the handlebars, and smiles as the man crouches behind him, supervising and helping him get started.
The blonde woman from the opening appears in the background, laughing and watching as the boy leans forward over the handlebars and the red motorcycle begins to \textbf{roll} across the green lawn.
The scene opens out to \textbf{rolling} grassy hills under a bright blue \textbf{sky} with large white clouds.
Two boys ride in a white toy pickup \textbf{truck} with blue striping and a Chevrolet-style bowtie on the grille.
One boy has very light blond hair and wears an orange shirt ; another boy in a red shirt sits beside him.
The toy \textbf{truck} ’s oversized black tires and shiny silver-colored wheels dominate the view as it moves through \textbf{grass}.
A small copyright notice appears near the bottom in some of these \textbf{shots}.
The \textbf{truck} rides over uneven \textbf{ground}, its high stance and chunky wheels making it look like a miniature off-road \textbf{vehicle}.
Another ride-on appears from the front : a black-and-yellow jeep-like \textbf{vehicle} with a bright red \textbf{roll} bar, yellow \textbf{steering} wheel, big round yellow lights, and a pretend engine blower on the hood.
Two boys sit inside, laughing.
The boy on the passenger side wears a blue-and-white striped shirt and round toy goggles \textbf{pushed} up on his forehead ; the driver wears a blue jacket over a red shirt.
They bounce along a lawn, grinning, with the striped-shirt boy clutching the side and the driver holding the \textbf{steering} wheel.
The view moves close to their faces as they laugh and lean with the \textbf{vehicle} ’s motion.
Several white toy pickup \textbf{trucks} then \textbf{drive} across tall \textbf{grass} on a hillside, each carrying children.
The \textbf{vehicles} look like small Chevrolet pickups with \textbf{broad} grilles and chunky tires.
A group of children ride in \textbf{formation}, some in red, yellow, and blue shirts, with the \textbf{trucks} staggered across the hill.
In front, one \textbf{truck} carries the blond boy in orange and another child in red ; another \textbf{truck} to the side carries a girl and a boy.
The children look forward and to one another with excited expressions as the \textbf{trucks} \textbf{roll} through the \textbf{grass}.
A red Jeep-style ride-on comes forward across a lawn.
A girl in a bright yellow sleeveless dress sits on the passenger side and waves a white \textbf{flag} on a pole out to the side.
Beside her, a boy in a blue sports-style shirt \textbf{drives}, smiling and looking ahead.
The red Jeep has a gray windshield frame, a vertical grille, and decorative flame-like decals on the hood.
As it \textbf{passes}, the girl turns toward the viewer, still holding the \textbf{flag} proudly, while the boy keeps both hands near the \textbf{steering} wheel.
A pair of pink Jeep-style ride-ons with purple wheels follows, carrying several children.
In the front pink Jeep, two girls wave with arms raised ; behind them, another pink Jeep carries more children, including a blond child wearing sunglasses.
The \textbf{vehicles} have gray windshield frames, blue circular headlights, and bright toy-like colors.
The children smile broadly, some waving as if in a parade, while the Jeeps \textbf{roll} along a green lawn with shrubs and flowering plants in the background.
A silver toy pickup \textbf{truck} \textbf{drives} through a park-like area with \textbf{trees}.
Two boys ride inside ; a blond boy in a red shirt is visible in front, while another child in a blue cap sits behind him.
The silver \textbf{truck} has blue side graphics, a small black \textbf{spare} tire at the back, and large black tires.
It moves through tall \textbf{grass}, with the children looking around and smiling.
Then an adult man in a light shirt and shorts stands near the red motorcycle ride-on on a grassy hill with water visible in the distance.
A boy in a red shirt sits on the motorcycle while the man bends down to help with the handlebars.
Small white on-screen text at the bottom reads, “ Adult supervision required. ” The man then lifts the boy up in his arms, raising him high against a bright \textbf{sky}, and the boy smiles down at him while the same supervision text remains visible.
In a wooded green setting, a small child rides the red motorcycle, dressed in a black leather-like jacket, blue jeans, dark sunglasses, and black \textbf{boots}, giving the child a playful “ biker ” look.
Other children on similar red motorcycles appear behind.
The red cruiser-style toy has chrome-colored side panels and pipes, a black storage box at the rear, and round headlights.
The child looks over to the side while \textbf{rolling} along the \textbf{grass} under leafy \textbf{trees}.
A younger boy in a blue shirt then appears inside a yellow-and-red framed ride-on, gripping a red \textbf{steering} wheel.
He smiles tightly, almost scrunching his face with excitement, surrounded by the bright yellow roll-cage bars.
More pink Jeeps \textbf{drive} along a garden \textbf{path}.
Two girls ride in the front : one with dark curly hair in a red top raises both hands high, while a blonde girl in sunglasses and a light vest sits at the wheel and smiles.
The pink Jeep ’s blue headlights and silver grille face forward as they \textbf{pass} lush \textbf{bushes} and flowers.
A closer view of a pink Jeep shows the front wheel \textbf{rolling} over a \textbf{paved} \textbf{path}, with the white “ Jeep ” logo visible on the side.
A silver Chevrolet-style toy \textbf{truck} then approaches from the front, its hood and grille filling the view, followed by a yellow Jeep seen from behind with a red bumper and “ Jeep ” written on the back as it \textbf{drives} away on \textbf{pavement} under a bright \textbf{sky}.
A boy in a light shirt rides the red motorcycle on a vivid green lawn.
He leans forward dramatically and wraps his arms around the front headlight cluster, hugging the red body and round headlights as if pretending to be a racer tucked low over the handlebars.
The \textbf{vehicle} is stationary or moving slowly, and his face is partly \textbf{hidden} by the motorcycle ’s front as he clutches it.
Another group of girls in pink Jeeps \textbf{passes} through a \textbf{sunlit} garden lawn, smiling and waving ; one blond girl in sunglasses \textbf{drives} while other girls ride alongside and behind.
A purple-and-yellow dune buggy-style ride-on speeds across a lawn.
It has a yellow \textbf{roll} cage, yellow wheels, red springs at the rear, and a rounded yellow front bumper.
A boy in a red shirt sits inside, mouth open in excitement, as the buggy turns slightly and the large rear tire and yellow cage sweep through view.
Then the white pickup \textbf{truck} returns, \textbf{driving} through a \textbf{muddy} puddle.
The front tire drops into water and mud, \textbf{throwing} up a \textbf{splash} around the wheel.
White on-screen text along the bottom reads, “ Batteries are covered by a six month warranty. ” The \textbf{truck} ’s black tires churn through the wet patch, \textbf{splashing} \textbf{muddy} water as the blue side step and side graphics \textbf{pass} by.
A large circular warranty seal appears over the image, then fills the view on the side of a silver \textbf{vehicle}.
It is a purple and gold \textbf{badge} with a big number “ 1 ” in the center and a ribbon across it reading “ BUMPER TO BUMPER. ” Around the circle, the visible text reads “ ONE \textbf{YEAR} ” and “ WARRANTY. ” The smaller white line of text at the bottom about batteries being covered by a six-month warranty remains visible beneath the \textbf{badge}.
Near a flower bed, an adult woman wearing a broad-brimmed garden hat kneels on the \textbf{grass} with two young girls hugging her.
One blonde girl in sunglasses, an orange top, and a light green skirt climbs onto the woman ’s back, while another girl with long hair leans in from the side.
A pink Jeep with purple wheels is parked behind them on the lawn.
The woman smiles and \textbf{gathers} the children close in a playful embrace among low white flowers and garden greenery.
At the end, an adult man in a bright blue shirt and jeans stands with his back to the viewer, leaning on a white wooden gate in a rural-looking yard.
Beyond the gate are green fields, \textbf{trees}, and \textbf{rolling} hills.
To the left, a small white ride-on utility \textbf{cart} or pickup \textbf{drives} away carrying children, including a child in a blue shirt and another with light hair.
The man remains by the gate watching as the children ride off across the \textbf{grass}, visually echoing the idea of an adult looking on while the kids enjoy the toy \textbf{vehicles}.

% matched lemmas: badge, boot, broad, bush, cart, drive, flag, formation, gather, grass, ground, hide, muddy, pass, path, paved, pavement, push, roll, shot, sky, spare, splash, steering, sunlit, throw, tree, truck, vehicle, year
\end{textsample}
