\begin{textsample}{POS Dim 2 – 1960 – Score 4.00 – 1960/tv\_com\_1960\_95.txt}  \label{ex:f2_pos_069}
The sampled frames show a chronological progression of audio playback/recording \textbf{devices} and associated \textbf{domestic} scenes. 1. **Opening frame (0.000s):** A close-up shows an old-style gramophone or phonograph on a \textbf{wooden} cabinet.
A black disc record is on the turntable, and a curved tonearm/horn mechanism is visible on the right.
The image has archival film wear and overlaid markings, including “ MY, ” “ 160-172, ” and a timecode. 2. **Early scene change (2.726s):** The setting shifts to a period-style interior.
A woman in historical dress, with a large hat or bonnet, stands beside a gramophone with a large flared horn.
She appears to be operating or adjusting the machine with one hand.
A decorative hanging lamp is visible above. 3. **Later scene change (20.610s):** The frame cuts to a front-facing close-up of a reel-to-reel tape recorder.
Two large reels are visible behind circular covers, with control knobs and a central panel between them.
The \textbf{device} fills most of the frame, emphasizing the technology. 4. **Final frame (52.043s):** The scene changes to a more \textbf{modern} \textbf{domestic} interior.
A woman \textbf{sits} on the floor beside a low table or console holding a compact reel-to-reel tape recorder, flanked by two speaker-like panels or cabinet sections.
She is seated calmly, looking toward the \textbf{device}.
Two cylindrical pendant lights hang above, and the overall setting appears minimalist and contemporary compared with the earlier scenes.
Across the sampled frames, the commercial visually moves from older phonograph/gramophone technology to reel-to-reel tape equipment, pairing the \textbf{devices} with period-styled and then more \textbf{modern} \textbf{domestic} environments.
No dialogue, slogans, or audio content is visible in the frames.

% matched lemmas: device, domestic, modern, sit, wooden
\end{textsample}
