\begin{textsample}{POS Dim 2 – 1950 – Score 18.00 – 1950/tv\_com\_1950\_69.txt}  \label{ex:f2_pos_081}
A black-and-white Ford crest fills the screen, with the word “ FORD ” in large block letters at the top of a shield-shaped \textbf{emblem}.
As the \textbf{emblem} fades, it remains superimposed over the front side of a parked 1957 Ford Fairlane.
The car sits in a driveway beside a mid-century suburban house with brickwork, large windows, shrubs, and flower beds.
The Fairlane is a two-tone hardtop with a light roof and light rear side panel, darker body sides, \textbf{chrome} trim, \textbf{whitewall} tires, and shiny hubcaps.
A man in a dark suit and dress shoes walks alongside the car carrying two hard-sided suitcases, one in each hand.
Only his lower body and hands are seen at first.
He \textbf{passes} the front wheel and continues toward the rear of the car.
The side of the Ford fills the view, showing its long, smooth body line, \textbf{chrome} door handle, and the distinctive sweeping two-tone panel that curves toward the rear fins.
At the \textbf{trunk}, a close view shows the rear lock and trim.
The word “ FAIRLANE ” is visible on the \textbf{trunk} ornament beneath a round lock.
The man ’s hand holds a key, inserts it into the lock, and turns it.
The \textbf{trunk} lid lifts open.
Inside, the \textbf{trunk} is spacious, with a patterned floor mat and a full-size \textbf{spare} tire standing upright at the back.
A California license plate reading “ MRT 031 ” is mounted on the lowered rear panel.
The man places a large suitcase into the \textbf{trunk}, sliding it flat inside, then adds a second suitcase on top of it.
The luggage fits beneath the raised \textbf{trunk} lid, beside the \textbf{spare} tire.
With the luggage stowed, the scene returns to the car ’s side.
The suited man walks forward along the driver ’s side toward the door.
He reaches for the \textbf{chrome} handle, pulls it, and the door opens outward.
The interior is visible through the open door : a \textbf{broad} front seat, the \textbf{steering} wheel, and the dashboard.
He bends and slides into the driver ’s seat, then begins pulling the door closed behind him.
Inside the car, attention shifts to the controls.
A \textbf{chrome} switch panel is set into quilted door trim ; a finger presses one of several small switches.
The window beside it is seen with blurred \textbf{bushes} outside, suggesting the glass is being operated.
Another close view shows the side of the front seat, where the man ’s hand reaches down to a small control near the seat base, indicating an adjustment to the powered seat.
His suit sleeve and shirt cuff are visible as he works the control.
The rear of the Fairlane appears, highlighting the round taillight set into the tail fin, the \textbf{broad} \textbf{chrome} bumper, and the clean, symmetrical rear styling.
The car backs away from the house along the driveway, growing smaller as it moves into the open space.
The suburban setting remains visible : a low-roofed house to the right, flower beds beneath the windows, and \textbf{trees} in the background.
The viewpoint moves to inside the car, looking forward through the windshield over the dashboard.
A quiet residential street stretches ahead with lawns, \textbf{trees}, and houses.
A boy rides a \textbf{bicycle} near the curb ahead of the car.
The Ford then appears from behind on the street, its white roof, rear fins, round taillights, and \textbf{whitewall} tires clearly visible as it \textbf{drives} \textbf{past} neat houses and landscaped yards.
A close view shows the boy ’s face as he moves along outdoors.
He appears to be a preteen or young teenage boy with light skin, dark wavy hair combed back, and a jacket over a collared shirt.
He looks toward the \textbf{passing} car with a slight smile, then purses his lips as if whistling or reacting with interest, before smiling again.
The background behind him is blurred foliage and sidewalk, reinforcing that he is moving.
Inside the Ford again, a dashboard clock is shown in close detail, with a rectangular face and large numbers around it.
Then the radio fills the view.
Its horizontal dial is marked with numbers from about 5.5 through 16, with a row of \textbf{push} buttons beneath.
A finger presses one of the preset buttons.
The radio dial then dissolves into a view of an open road, visually linking the dashboard controls to the \textbf{driving} scene.
A smooth, empty \textbf{highway} curves gently through a wooded area. \textbf{Trees} line both sides, and the pale road surface sweeps to the right.
The car itself is not visible in this part ; the view suggests traveling forward along a quiet, open road.
The Ford appears again from the side on a \textbf{rural} \textbf{highway}.
The camera stays close to the front fender and door area as the car moves, showing the \textbf{chrome} side trim, \textbf{whitewall} front tire, and the “ Fairlane ” script along the front side panel.
Fields, low hills, and distant \textbf{trees} slide by in the background.
The driver, still in a dark suit, is visible through the open side window with his hands near the \textbf{steering} wheel.
As the view moves rearward along the car, the sweeping two-tone side panel and white roof stand out, followed by the rear quarter, tail fin, round taillight, and \textbf{chrome} bumper.
The Fairlane continues cruising along a straight open \textbf{highway}.
From behind and slightly to the side, its rear styling is prominent : \textbf{twin} round taillights, \textbf{broad} bumper, central \textbf{trunk} ornament, and wide rear window.
The car remains steady in its lane, with open countryside, scattered \textbf{trees}, and low \textbf{mountains} in the distance.
Near the end, the Ford is seen head-on \textbf{driving} along a road through a wide landscape.
Its front grille spans the width of the car, with round headlights set high at each side and \textbf{chrome} bumper guards below.
The road and distant hills frame the car.
The Ford crest then appears over the center of the grille and enlarges until it dominates the screen, again showing the bold “ FORD ” name at the top of the shield.

% matched lemmas: bicycle, broad, bush, chrome, drive, emblem, highway, mountain, pass, past, push, rural, spare, steering, tree, trunk, twin, whitewall
\end{textsample}
