\begin{textsample}{POS Dim 2 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_78.txt}  \label{ex:f2_pos_054}
The commercial begins with a static promotional end-card style image.
A display of audio-related products and packaging appears against a dark background.
Readable text includes “ Technics ” in large red letters and “ The science of sound ” beneath it.
Smaller white text above mentions an offer period and participating Technics dealers, but much of it is difficult to read clearly.
The scene then cuts abruptly to animation.
Three cartoon characters stand side by side against a simple pastel background.
The central figure resembles a sailor in a white cap and dark shirt ; a woman stands to his left, and a large bearded man in a yellow shirt stands to his right.
All three are shown full-body and appear to be smiling or posing.
The next frame shows a red-to-white gradient \textbf{screen} with faint, partially obscured shapes or lettering.
The content is not clear enough to identify with certainty.
The commercial then shifts to close-ups of handheld electronic game \textbf{devices}.
A white folding \textbf{device} is held in two hands.
It has two small \textbf{screens}, one in the upper half and one in the lower half, with simple black-and-white game graphics.
Control buttons are visible on the right and left sides.
The game imagery appears to involve small cartoon-like figures and obstacles.
A similar close-up follows, now of an orange folding handheld game.
It also has two \textbf{screens} and side controls.
The \textbf{screens} show a simple platform or obstacle-style game layout, with small figures and horizontal/vertical structures.
The next shot widens to a \textbf{domestic} living-room setting.
A handheld game unit \textbf{sits} on a white table in the foreground.
An adult or older person in a light yellow shirt stands beside the table, with one hand lowered toward the \textbf{device}.
In the background, several children \textbf{sit} on a \textbf{couch}, watching or reacting.
The \textbf{room} contains \textbf{home} furnishings and wall decorations, but details are somewhat soft due to the image quality.
The commercial then cuts to an extreme close-up of a handheld game \textbf{screen}.
The \textbf{device} frame includes readable text \textbf{such} as “ SNOOPY TENNIS ” at the top and “ WIDE \textbf{SCREEN} ” near the bottom.
The \textbf{screen} shows a simple black-and-white tennis-like game scene with small cartoon characters, including a dog-like figure on one side and another character near the opposite side.
Fingers hold the \textbf{device} at the edges.
The final sampled frame shows another handheld game \textbf{device} opened like a book, with two side-by-side \textbf{screens}.
The lower front area prominently displays the “ Nintendo ” name and a large “ Toys ‘ R ’ Us ” logo.
The two \textbf{screens} show simple game layouts with ladders, platforms, and small figures.
Hands hold the \textbf{device} at both sides, with a thumb near the right-side control area.

% matched lemmas: couch, device, domestic, home, room, screen, sit, such
\end{textsample}
