\begin{textsample}{POS Dim 2 – 1980 – Score 15.00 – 1980/tv\_com\_1980\_38.txt}  \label{ex:f2_pos_065}
A small child dressed like a firefighter trots along a sidewalk in front of a white picket \textbf{fence}.
The child wears a shiny red fire helmet, a \textbf{red-and-white} striped shirt, red pants with dark suspenders, and black \textbf{boots}.
A spotted Dalmatian dog moves ahead, pulling or leading a red wooden wagon with white \textbf{rails} and black wheels.
Inside the wagon sit several Dalmatian puppies, their black-and-white heads peeking over the sides.
The child holds the wagon handle and \textbf{hurries} happily after the dog as the little wagon \textbf{rolls} along beside a green lawn and flower beds.
The scene shifts to a leafy garden where a large, playful dragon costume fills the view.
The dragon has a round gray head with a big eye, shaggy orange and yellow fringe, and a long green body with orange triangular spikes along its back.
Pink blossoms blur in the foreground, giving the garden a soft, magical look.
A young child in a bright green one-piece outfit runs beside the dragon ’s green tail, reaching out with both hands as if chasing or trying to catch it.
The child follows the dragon \textbf{past} a \textbf{stone} garden lantern and across the \textbf{grass}.
Next, at a decorated birthday party, a smiling blonde woman in a white blouse carries a white frosted birthday cake on a plate toward a blonde little girl in a white dress with pink ribbons in her hair.
Behind them are white lattice panels, balloons, streamers, flowers, and large block letters spelling part of “ BIRTHDAY. ” The girl beams up at the cake, then leans forward toward several pink candles.
The woman holds the cake steady and watches warmly as the girl blows at the candles ; the child ’s cheeks puff slightly and the candle flames flicker and disappear.
A white wall or \textbf{fence} then appears with a large Clorox 2 logo centered on it : bold black “ CLOROX ” over a black “ 2, ” inside a \textbf{red-orange} diamond outline.
Flowers line the base of the wall.
The firefighter child and Dalmatian dog briefly run \textbf{past} the logo, linking the earlier \textbf{outdoor} play scene to the product name.
The commercial moves into a product demonstration on a dark blue studio background.
A blue box labeled “ CLOROX 2 ” and “ Color Safe Bleach ” is tipped downward by a hand, and white powder pours from the box.
The powder then streams into a clear glass vessel marked with the Clorox 2 diamond logo.
Water and powder mix inside the glass.
Close-up views follow of laundry fabrics moving through water : a bright white garment floats among colorful yellow and red cloths, with bubbles and ripples around them.
The white fabric stays visibly clean and bright while the colored fabrics remain vivid in the same wash.
In a home laundry room, a blonde adult woman in a sleeveless coral top and blue jeans stands beside a washer and a folding table.
A box of Clorox 2 sits prominently on the table near neatly folded colored clothes and a white laundry basket full of bright garments.
The woman lifts a white child ’s dress or top, shakes it open, and holds it up with both hands to inspect it.
The garment looks crisp and bright against the blue-toned laundry room, with an arched window and shelves in the background.
The scene changes to a \textbf{sunlit} field of flowers near a pond.
A young Black girl with a large ponytail tied with a purple bow runs through tall pink and purple blossoms.
She wears a purple dress with white puff sleeves and a white collar, and she smiles while reaching toward a small butterfly fluttering in front of her.
The \textbf{grass} and flowers sway around her as she moves lightly through the meadow.
Back at the birthday party, the blonde woman and the blonde little girl lean close together over the decorated cake.
Both smile broadly ; the girl nestles against the woman ’s cheek, and they share an affectionate hug among the balloons and pink party decorations.
The final \textbf{outdoor} celebration \textbf{gathers} many children on a grassy lawn bordered by a white picket \textbf{fence} and flower beds.
The firefighter child runs with another smaller child in a matching red firefighter-style hat and red pants.
Other children follow, including the girl in the purple dress, a blonde girl in a white dress, a girl in a purple top and pink skirt, and a child in a yellow shirt and shorts.
They carry or run beneath bright balloons and long, rainbow-colored streamers or kite tails.
A Dalmatian dog runs across the foreground.
The Clorox 2 diamond logo is visible again on the white wall in the background as the children \textbf{rush} \textbf{past}, laughing and playing.
The commercial ends with a product display against a blue \textbf{sky} with white clouds : a large Clorox 2 powder box stands beside a blue handled jug labeled “ LIQUID CLOROX 2, ” both using the same bold black lettering and \textbf{red-orange} diamond logo.

% matched lemmas: boot, fence, gather, grass, hurry, outdoor, past, rail, red-and-white, red-orange, roll, rush, sky, stone, sunlit
\end{textsample}
