\begin{textsample}{POS Dim 2 – 1990 – Score 18.00 – 1990/tv\_com\_1990\_2.txt}  \label{ex:f2_pos_037}
The commercial opens inside the video game, on a \textbf{dusty} tan racecourse in a desert canyon.
Several futuristic hover-motorcycles line up across the track, each with a rider in a helmet and racing suit.
Low \textbf{stone} barriers run along both sides, orange canyon walls rise in the background, and a large overhead electronic sign hangs above the track.
At first the sign reads “ SET ” in bright yellow block letters, then changes to “ GO! ” A white race timer appears in the upper left.
The viewpoint sits just behind a green-and-teal hover bike marked with a large number 2, centered in the lane.
When the race begins, the other racers surge forward, kicking up pale dust clouds and leaving the number 2 bike behind.
Its rear glows \textbf{red-orange} as if powered, but it lags under the “ GO! ” sign while the pack pulls farther ahead.
The scene jumps through different game \textbf{courses} to show the racing variety.
On a narrow wooden plank bridge suspended over a deep rocky ravine, several hover bikes crowd together, including a large blue-and-white bike marked number 7 very close in front.
The planks stretch in a thin line across the gap, with green terrain beyond the canyon.
Then the setting changes to a dramatic, futuristic track at \textbf{night} or twilight.
A rider speeds along a steeply \textbf{banked} wall, with a deep blue and purple \textbf{sky}, dark building-like structures, and a white lattice track or framework curving below.
The bike appears to cling to the side of a twisting tube-like \textbf{course} before the image returns to the original desert starting stretch, where the number 2 bike is still under the glowing “ GO! ” sign.
More racing clips follow.
In a sandy canyon turn, hover bikes slide around a bend and \textbf{throw} up thick \textbf{splashes} of dust or sand ; a small rating icon sits in the lower left.
A close view shows a rider on a yellow-and-red bike marked number 3, wearing a white helmet with red accents.
Another bike sweeps \textbf{past} on the inside of the curve, and a large sandy plume fills the left side of the track as racers disappear around the bend.
The action then moves to a bright blue water \textbf{course} near a huge wall of falling water or spray.
A red-and-yellow bike marked number 1 flies above the water, then lands and skims forward between orange buoys and industrial-looking structures.
Next, the racers are on a \textbf{snowy} \textbf{mountain} track bordered by cliffs and \textbf{rocks}.
Several hover bikes carve through the \textbf{snow}, leaving pale tracks and blue-tinted glow beneath them as they bunch together and race under a sign ahead.
The commercial returns again to the desert starting area with the number 2 bike still sitting beneath the big yellow “ GO! ” sign.
Suddenly the game ’s rider gets off the bike.
He is a computer-animated, male-presenting racer in a \textbf{tight} green racing suit with \textbf{red-orange} shoulder pads and accents.
A small helmet lies on the \textbf{ground} to his right.
He runs straight toward the viewer with an angry, urgent expression, his brows sharply lowered and his mouth set.
As he gets closer, his face fills the screen : pale, angular, low-polygon features, short brown hair, \textbf{heavy} dark eyebrows, and a scowling look.
The edges of a television screen become visible around him, revealing that he is inside the game on an old-fashioned TV.
The real-world setting is a warmly lit living room.
An elderly white woman with short white hair sits in a cushioned chair, holding a gray PlayStation controller with both hands.
She wears a soft white cardigan over a pink blouse or nightdress and looks intently toward the television, her face calm and slightly puzzled.
The TV sits in front of her in a wooden entertainment unit or cabinet, with shelves and small decorative objects around it.
On the TV screen, the animated racer ’s large face is still \textbf{glaring} outward from the game world as if addressing her directly, while she remains seated and continues holding the controller.
The product title then appears on a cloudy, silvery-white background with faint lightning-like streaks.
In the center is a dark oval logo with gold text reading “ Jet Moto 2. ” After the logo, the game image returns briefly to the desert start line : the empty number 2 hover bike sits under the “ GO! ” sign while the green-suited racer stands beside it, with his helmet still on the \textbf{ground}.
He moves near the bike as if urging action.
The commercial ends back in the living room with the elderly woman holding the controller in her lap, looking forward with a faintly annoyed or confused expression.

% matched lemmas: bank, course, dusty, glare, ground, heavy, mountain, night, past, red-orange, rock, sky, snow, snowy, splash, stone, throw, tight
\end{textsample}
