\begin{textsample}{POS Dim 2 – 2000 – Score 18.00 – 2000/tv\_com\_2000\_109.txt}  \label{ex:f2_pos_029}
A \textbf{sunlit} desert canyon opens the commercial.
Tall sandstone cliffs frame a wide, \textbf{dusty} valley, with low scrub and uneven tracks across the \textbf{ground}.
Bright light pours through the canyon, making the distant \textbf{rock} walls \textbf{hazy}.
A small dark \textbf{vehicle} is barely visible far off, and dust hangs over the road as if it has just \textbf{driven} through.
A black Honda SUV appears head-on on the desert floor, its \textbf{chrome} Honda \textbf{badge} centered in the grille.
The \textbf{vehicle} sits against pale \textbf{rock} cliffs and a bright \textbf{sky}.
A wider view reveals the SUV in profile beside a massive rounded sandstone \textbf{formation}.
It is towing a small open trailer loaded with off-road motorcycles or dirt bikes, suggesting an \textbf{outdoor} riding trip in the desert.
Inside the \textbf{vehicle}, the focus moves to the dark leather-trimmed seating.
A close view of a front seat headrest shows a distinctive oval opening near the top, with stitching visible along the leather.
Through the side window, the rocky desert and a rider or bike-like shape can be glimpsed outside.
Small white on-screen text along the bottom reads, “ Leather-trimmed interior available on EX model only. ” The cabin is then shown from behind the front seats : a black \textbf{steering} wheel with a Honda \textbf{emblem}, a center dashboard with controls, a \textbf{broad} center armrest, and dark leather seats.
The windshield looks out onto the same rocky canyon landscape.
The interior is shown again from the front, looking back through the cabin.
Multiple rows of seats are visible, including the second and third rows, with matching dark headrests and a spacious, squared-off interior.
Outside the rear window, the desert and the towed trailer are visible.
Then the left-side door opens and \textbf{muddy} passengers begin climbing in.
A younger boy, his face and hair splattered with mud, gets into the rear area.
An adult man with short dark hair, also \textbf{muddy} and wearing a light-colored, dirt-stained shirt, leans in on the driver ’s side and settles behind the \textbf{steering} wheel.
A second older boy or teenager, with longer dark hair and a gray shirt covered in mud, climbs into the front passenger seat.
The adult driver smiles and reaches across the cabin while the children settle into place.
The younger boy sits behind the front seats, looking tired and \textbf{muddy}, his face heavily spattered.
The older boy in the front passenger seat leans back with a pleased, relaxed expression despite being covered in mud from his neck down across his shirt.
The adult driver glances toward him with a smile, and the three occupants share a light, comfortable moment inside the \textbf{vehicle}.
Their \textbf{muddy} clothing and faces contrast with the clean, dark leather interior around them.
A close view of the center console shows a built-in navigation screen.
A \textbf{muddy} finger presses one of the buttons beside the display.
The screen shows a simple map-like graphic, and the right-side buttons include labels such as “ MENU, ” “ MAP/GUIDE, ” “ A/C, ” “ CANCEL, ” and “ VOICE. ” Small white text at the bottom reads, “ Available on select EX models. ” Mud smears on the glossy black control panel as the button is pressed.
The black Honda Pilot is then shown outside again, towing the open trailer loaded with several dirt bikes across the desert floor.
The SUV ’s side windows are dark, and its silver wheels stand out against the \textbf{dusty} \textbf{ground}.
White text along the bottom reads, “ Shown with available towing package. ” Behind it, layered tan cliffs stretch across the background.
The final scene places the SUV and trailer in \textbf{silhouette} on a desert road at sunset.
The \textbf{sky} is dramatic, with dark clouds edged by bright light, and a flat-topped butte stands in the distance.
The \textbf{vehicle} \textbf{drives} away, kicking up dust behind the trailer.
Large white on-screen text reads, “ The new Pilot, ” with the blue Honda logo and “ HONDA ” beneath it.
In the lower left corner, small text reads “ honda.com. ”

% matched lemmas: badge, broad, chrome, drive, dusty, emblem, formation, ground, hazy, muddy, outdoor, rock, silhouette, sky, steering, sunlit, vehicle
\end{textsample}
