\begin{textsample}{POS Dim 2 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_106.txt}  \label{ex:f2_pos_088}
A dark black-and-white screen gives way to a staged miniature airfield under a painted \textbf{sky} filled with large clouds.
Three toy helicopters sit on a flat runway with low \textbf{mountains} and a lattice tower in the background.
Each helicopter is long and rounded, with a clear bulb-like cockpit at the front, wheels underneath, and large rotor blades on top.
The rotors blur as if spinning, and the helicopters appear to taxi forward.
One on the right moves closest, its nose and spinning front rotor dominating the scene while the others remain farther back.
The toy is then shown as if flying against a cloudy \textbf{sky}.
It is a long twin-rotor helicopter with a rounded transparent cockpit, small round windows along the side, wheels below, and printed markings including “ WHIRLYBIRD ” and “ RESCUE CORPS ” on its body.
The rotor blades spin so fast they become pale sweeping arcs.
The helicopter is angled upward, giving the impression of climbing through the clouds, with its side details, landing wheels, and tail markings clearly visible.
The action shifts to the \textbf{underside} and rear portion of the helicopter in the cloudy \textbf{sky}.
A thin line hangs down from beneath it, suggesting a chain or cable with a small hook.
The helicopter ’s side has military-style triangular insignia and small window decals.
The toy hovers above a miniature battlefield landscape, where a tank is attached to a sling made of several thin straps.
The tank, light-colored and blocky with a turret and barrel, is lifted up out of a \textbf{rough} crater.
Around it are tiny toy soldiers, small \textbf{vehicles}, and uneven terrain made to look like \textbf{rocks}, dirt, and battlefield debris.
As the tank rises, it clears the hole and moves upward toward the top of the scene.
After the tank is lifted away, the battlefield below erupts into a bright white burst that fills much of the screen, followed by drifting smoke over the crater and the toy soldiers below.
The tiny soldiers remain positioned around the rugged \textbf{ground}, some standing near small artillery pieces and \textbf{vehicles} while smoke clouds partially \textbf{obscure} the set.
Two children then appear behind the miniature terrain, playing with the helicopter.
Both wear light-colored toy soldier helmets and dark jackets.
The child on the left kneels behind the helicopter and holds it level with both hands, guiding it over the edge of a raised play area.
The child on the right lies on their stomach with elbows down and chin resting in both hands, smiling broadly as they watch the dangling hook and small load below the helicopter.
The helicopter ’s rotors are still shown spinning, and a thin line hangs from its \textbf{underside} with a small object at the end.
A close view of the helicopter ’s side shows a rectangular cargo door outlined on the body, with a small dark window or latch panel.
The door opens downward like a ramp, revealing a cargo compartment inside.
Tiny soldier figures stand in the open hold, posed as if ready for action.
They wear dark uniforms and helmets and hold small rifles.
The compartment is then shown holding a small cannon, its long barrel angled upward and its wheels visible inside the open bay.
The miniature battlefield returns, now spread out with many included accessories : a tank on the right, a jeep or \textbf{truck} near the center, a larger \textbf{vehicle} with a mounted cannon on the left, a small helicopter or aircraft shape near the upper left, and clusters of tiny soldiers standing in \textbf{formation} or aiming weapons.
Smoke and bright flashes appear in different parts of the battlefield, creating the look of explosions around the \textbf{vehicles} and troops.
The terrain is uneven, with rocky hills, trenches, and scattered light and dark patches suggesting dirt and battlefield damage.
The tank rescue is repeated from above : the light-colored tank hangs in the sling over the crater, rises, and disappears upward while tiny soldiers and equipment remain below.
Another large white flash fills the upper area, then fades into smoky \textbf{haze} over the same battlefield set.
The children reappear behind the play area.
The child on the left now smiles directly forward while holding the helicopter proudly at chest height.
The child on the right, still in a helmet, grins and leans close to the toy, hands near their face, watching it with excitement.
The helicopter stretches across both children, its long body and top rotor spanning the space between them.
The toy helicopter is shown again against the cloudy \textbf{sky}, angled in flight with its rotors spinning.
Large white price text “ 9.98 ” appears over the lower middle of the image.
Then bold white text “ PLAY INDOORS ” appears at the top, with “ 9.98 ” centered below the helicopter.
A smaller line of text along the bottom begins “ Not a Flying … ” but the final words are partly \textbf{obscured} and difficult to read.
The helicopter remains in the background, its rotors blurred in motion, while the price and indoor-play message stay prominently on screen.

% matched lemmas: formation, ground, haze, mountain, obscure, rock, rough, sky, truck, underside, vehicle
\end{textsample}
