\begin{textsample}{POS Dim 2 – 2010 – Score 15.00 – 2010/tv\_com\_2010\_36.txt}  \label{ex:f2_pos_023}
The sequence begins with a static product-style shot of two Tide PODS containers against a light blue background.
One white-and-blue container is labeled “ Tide PODS free \& gentle, ” with a small “ NEW ” \textbf{tag}, and an orange/purple Tide PODS container \textbf{sits} behind it.
Small \textbf{safety} \textbf{icons} and a fine-print \textbf{safety} warning are visible near the bottom, including wording about keeping detergent away from children.
The scene then cuts to a bright \textbf{home} interior, likely a kitchen or \textbf{living} area.
A young girl with light brown hair, wearing a pink cardigan, smiles toward the camera while holding up a light-colored shoe.
A Care.com watermark appears at the lower right.
Next, the same girl is shown holding and blowing into a brass trumpet or cornet.
She looks toward the camera while seated or standing in the same bright \textbf{domestic} setting, with a window and small objects in the background.
The Care.com watermark remains.
A close-up follows of the girl smiling directly at the camera.
She now wears a purple top and a colorful bead necklace.
The background is softly lit and child-oriented, with plush toys or soft furnishings visible but out of focus.
The next close-up returns to the girl in the pink cardigan.
Her head is tilted upward and she looks down toward the camera, giving a playful expression.
The \textbf{home} background remains softly blurred, and the Care.com watermark is still present.
The commercial then introduces an adult woman speaking directly to camera.
She stands in front of a cool-toned, softly blurred background with an image-like panel behind her.
On-screen text identifies her as “ Sheila Marcelo, ” “ Founder \& CEO, ” and “ Mother of two. ” She wears a purple cardigan and smiles.
The Care.com watermark appears at the lower left.
The visual focus shifts to a \textbf{computer} \textbf{interface} for Care.com.
The Care.com logo appears at the top with the tagline “ There for you. ” Large rectangular buttons or category selections are visible, including “ Full-time nanny, ” “ Part-time sitter, ” and “ Post a job now. ” The \textbf{screen} is shown at an angle, emphasizing the website \textbf{interface}.
A subsequent website \textbf{screen} shows a list of caregiver profiles.
The Care.com logo appears at the top, along with a line indicating a large number of babysitters near the user.
Profile names are visible, including “ Madison L., ” “ Sarah R., ” and “ Chloe S., ” each with a photo thumbnail, star \textbf{ratings}, and brief caregiving details.
Another website profile \textbf{page} is shown for “ Brianna P., ” labeled “ Part-time sitter. ” Her portrait appears on the left.
Green check-mark bullet points list tasks or services \textbf{such} as “ Transportation, ” “ After school activities, ” “ Groceries, ” and “ Appointments. ” Green \textbf{rating} or verification-style boxes appear to the right, including “ Background Check ” and “ Driving Record. ” The sequence then shows a hand holding a \textbf{smartphone}.
On the \textbf{phone} \textbf{screen} is a Care.com-branded payment \textbf{interface} with the caregiver ’s photo and a large green button labeled “ Pay Now. ” Papers and a pink item lie blurred on a table in the background.
The commercial returns to the young girl in the bright \textbf{home} setting, again playing the brass instrument.
She holds it up to her mouth, with the bell of the instrument prominent in the foreground.
The Care.com watermark appears at the lower right.
The final frames use a clean blue-white gradient background with the Care.com logo centered.
The tagline “ There for you ” appears beneath the logo.
One frame reads “ Join Today. ” The last frame changes the text to “ Find the perfect, ” followed by a blank line, and small category labels along the bottom : “ Babysitters, ” “ Nannies, ” “ Senior Care, ” “ Pet Care, ” and “ and More! ”

% matched lemmas: computer, domestic, home, icon, interface, living, page, phone, rating, safety, screen, sit, smartphone, such, tag
\end{textsample}
