\begin{textsample}{POS Dim 2 – 1960 – Score 16.00 – 1960/tv\_com\_1960\_51.txt}  \label{ex:f2_pos_013}
The commercial is in black and white and begins outdoors in a \textbf{rural} orchard.
A medium-sized dog with dark-and-light markings bounds toward the viewer across a grassy lane, mouth open and ears lifted as it runs.
Behind the dog, a light-skinned, middle-aged to older man walks at an easy \textbf{pace} between rows of orchard \textbf{trees}.
He wears a light cap, a short-sleeved shirt, and light trousers, with his arms relaxed at his sides.
The \textbf{trees} form dark leafy walls on both sides of the open \textbf{path}, giving the scene a quiet farm setting.
The view changes to the same man much closer, seen from below against a pale \textbf{sky}, with \textbf{leaves} along one edge of the image.
He wears a baseball-style cap and a patterned short-sleeved shirt with repeating circular designs.
He faces forward as if talking, and one hand is raised beside his face, palm turned inward ; a ring is visible on one finger.
His expression is calm and thoughtful.
A title then identifies him on screen as “ WALTER HORST ” and “ SHIPPENSBURG, PA. ” A second title appears beneath his portrait : “ A CASE HISTORY FROM MONY, ” with smaller text reading “ MUTUAL OF NEW YORK. ” He is then seen in front of dense fruit-laden \textbf{branches}, likely apple \textbf{trees}.
Fruit hangs all around him among dark \textbf{leaves}.
He rests one side of his face against his hand, looking forward with a reflective expression, while his patterned shirt and cap remain visible.
The imagery briefly overlaps with another \textbf{outdoor} view of him walking through \textbf{rough} \textbf{grass} and \textbf{brush} near a \textbf{broad}, open field.
He moves through the farm landscape, then appears from behind walking along a pale dirt road bordered by orchard \textbf{trees}.
Far ahead, a low barn or storage building sits at the end of the road, its open dark doorway visible.
The scene shifts to farm machinery.
The man leans over a large circular \textbf{steering} wheel, likely on a tractor or similar piece of equipment.
A vertical support post rises behind him, and he bends forward with his cap pulled low, concentrating on something below the wheel or at the controls.
The image then layers into a more contemplative side view of him standing outdoors, head lowered, cap brim shading his face.
He appears still and thoughtful for several moments, the background soft and leafy.
His expression brightens as he turns and smiles.
The images briefly overlap with a busy area of stacked produce crates or boxes.
Several people are visible from behind or above, including at least one smaller person lifting or holding a rectangular box near the stacked crates, suggesting work around harvested fruit.
This \textbf{blends} back into the orchard, where the man leans on a \textbf{rail} or wooden support among heavily fruited \textbf{branches}.
His cap is off or \textbf{pushed} aside ; a light-colored cap or cloth hangs near his head on the right.
He rubs or scratches the side of his head with one hand and looks upward with a modest smile, surrounded closely by fruit and leaves.
Near the end, he sits indoors or in a shaded storage area in a chair, relaxed with one leg crossed.
Behind him are stacked wooden crates with large printed lettering, including “ GREAT A. \& P.
TEA CO.
INC. ” and “ MARTINSBURG, W.
VA. ” He wears the same cap and patterned shirt and holds a sheet of paper in both hands, reading it.
The farm-storage setting feels practical and workmanlike, with crates forming the backdrop.
The final image is a clean white title card.
Large bold text reads “ MONY, ” with a dollar sign inside the letter “ O, ” and underneath it says “ MUTUAL OF NEW YORK. ” Below that, the card reads : “ …FOR ‘ INSURED INCOME PLANNING SERVICE ’ ” and, in smaller print, “ THE MUTUAL LIFE INSURANCE COMPANY OF NEW YORK, N.Y. ”

% matched lemmas: blend, branch, broad, brush, grass, leaf, outdoor, pace, path, push, rail, rough, rural, sky, steering, tree
\end{textsample}
