\begin{textsample}{POS Dim 2 – 2020 – Score 17.00 – 2020/tv\_com\_2020\_74.txt}  \label{ex:f2_pos_048}
A bright blue Hyundai Tucson \textbf{drives} along a smooth \textbf{highway} bordered by \textbf{dry}, rolling hills under a clear blue \textbf{sky}.
The SUV is shown from the front at first, with the Hyundai \textbf{badge} centered in a \textbf{chrome} grille and daytime running lights glowing.
Small white legal text runs along the bottom edge of the image.
Inside the \textbf{vehicle}, an adult man with short dark hair and a trimmed beard sits in the driver ’s seat, wearing a pale blue button-down shirt and a seat \textbf{belt}.
He looks ahead with a calm, focused expression while holding the \textbf{steering} wheel.
In one hand he also holds a small brown carton filled with thin French fries.
He reaches into the carton, pulls out a fry, and brings it toward his mouth while continuing to \textbf{drive}.
Outside, the blue Tucson is traveling very close beside a large tractor-trailer.
The semi ’s long gray tarp-covered trailer fills the lane next to the SUV, making the Tucson look small beside its tall side panels and large wheels.
The two \textbf{vehicles} move parallel to each other on the \textbf{highway}.
Back inside the car, the driver is seen in profile.
The semi ’s gray trailer wall fills the side window, emphasizing how near it is.
The man holds the fry carton up near the \textbf{steering} wheel and eats while \textbf{driving}.
A moment later he looks down toward his shirt as if something has gone wrong with the food.
A blonde adult woman appears outside the passenger-side area, visible through the window and windshield, wearing a navy blazer over a white shirt, light blue jeans, and light-colored shoes.
She leans in close to the \textbf{vehicle} from the narrow space between the Tucson and the \textbf{truck}, looking toward the driver with an animated, concerned expression.
As the man lowers one hand toward his lap, fries spill from the carton near the \textbf{steering} wheel, and his attention is drawn down toward the mess.
The woman is then visible outside between the blue Tucson and the massive semi-truck.
She stands in the slim gap beside the SUV ’s front door and mirror, with the Tucson ’s bright front end on one side and the semi ’s huge wheels and gray trailer on the other.
She walks forward in that \textbf{tight} space, gesturing with her hands as if explaining or warning.
Her hair moves in the wind, and she keeps her body close to the Tucson as the \textbf{truck} looms beside her.
The road and open hills remain in the background, while a line of small legal text stays along the bottom of the screen.
The view widens to show the full situation : the blue Tucson on the left, the semi-truck on the right, and the blonde woman walking between them in the lane.
The SUV ’s \textbf{chrome} grille and headlights face forward, and the semi ’s large polished wheels and dark cab dominate the other side.
She continues forward, centered between the two \textbf{vehicles}, illustrating how narrow the space is.
A low view near the road shows the danger more directly.
On the left, the semi ’s large tires \textbf{roll} close by ; on the right, the blue Tucson ’s side panel and front wheel move alongside them.
White lane markings slide \textbf{past} beneath the \textbf{vehicles}, and the SUV appears to drift near the line before moving away from the \textbf{truck} ’s tires.
The spacing between the Tucson and the semi becomes the focus, with both sets of wheels \textbf{rushing} along the \textbf{pavement} only a short distance apart.
Inside the SUV again, the driver now grips the steering wheel with both hands.
His face looks more alert and serious.
A small \textbf{reddish} stain is visible on the front of his light blue shirt, suggesting the food accident has left a mark.
He looks to the side toward the \textbf{truck}, then back ahead, while reflections of \textbf{sky} and passing \textbf{vehicles} ripple across the windshield.
The Tucson continues down the \textbf{highway}, now shown from the side and rear as it travels smoothly along the road with the hills behind it.
The semi-truck moves out of the foreground, leaving the blue SUV clearly visible.
White on-screen text appears above the \textbf{vehicle} : “ Highest Ranked Compact SUV in Initial Quality ” followed by “ — J.D.
Power, ” with a J.D.
Power award icon beside it.
Small fine print appears along the bottom.
The commercial then changes to a clean white studio-style background.
A blue 2021 Hyundai Tucson is displayed in profile, slowly repositioning from a side view toward a front three-quarter view.
Large black offer text fills the upper half of the screen : “ 2021 Hyundai TUCSON, ” then “ \$0 ” for “ Due at lease signing, ” “ \$0 ” for “ First month ’s payment, ” and “ \$0 ” for “ Security deposit. ” To the right, another large figure reads “ or up to \$3,500 total savings. ” Smaller text below mentions “ \$189 per month for 36 months, ” and dense legal fine print spans the bottom.
Finally, the screen becomes a white end card with the blue Hyundai logo and the word “ HYUNDAI ” centered.
Beneath it, text reads “ Southeast Michigan Hyundai Dealers, ” followed by a list of dealer names and locations, including Elder Hyundai in Macomb, Feldman Hyundai of New Hudson, Fox Ann Arbor Hyundai, Glassman Hyundai in Southfield, LaFontaine Hyundai in Dearborn, Ralph Thayer Hyundai in Livonia, and Suburban Hyundai in Troy.
Near the bottom, the website “ BuyHyundai.com ” appears, along with America ’s Best Warranty information in small print.

% matched lemmas: badge, belt, chrome, drive, dry, highway, past, pavement, reddish, roll, rush, sky, steering, tight, truck, vehicle
\end{textsample}
