\begin{textsample}{POS Dim 2 – 1960 – Score 18.00 – 1960/tv\_com\_1960\_60.txt}  \label{ex:f2_pos_011}
The commercial opens on an abstract, close view of a polished aircraft surface against a pale, clouded \textbf{sky}.
A long silver form, likely part of a wing or tail assembly, angles diagonally across the screen, catching soft light as clouds drift in the background.
The aircraft structure gradually slides out of view until the image becomes mostly bright \textbf{sky} and \textbf{haze}.
The scene shifts to a busy airport apron crowded with large jetliners.
The view is \textbf{tight} among the aircraft : rounded engine nacelles, landing gear, wings, and fuselage sections overlap so closely that the planes seem packed nose to tail.
A large circular jet engine dominates the center, with dark turbine openings visible inside.
Nearby, \textbf{heavy} black wheels and struts sit beneath white and metallic aircraft bodies.
One white fuselage bears the number “ 602 ” in dark lettering.
The visual emphasis is on the size and density of the fleet, with multiple Eastern-style white aircraft and blue striping visible in the same space.
More parked planes fill the airfield.
Rear fuselage sections and tall tails appear in layers, some with bold blue diagonal stripes.
Ground-service equipment and low airport \textbf{vehicles} sit beneath the wings and around the planes, stacked and parked in the foreground.
The aircraft are mostly white with blue accents, and several rear-mounted engines are visible.
One rear engine housing carries the word “ Whisperjet ” in dark letters, identifying a quieter jet service or aircraft type.
The apron looks \textbf{hazy} and \textbf{sunlit}, with a muted 1960s film color palette and a pale \textbf{sky} over the runway area.
A closer view isolates the side of a tail and fuselage, showing a \textbf{broad} blue diagonal stripe crossing a white aircraft surface.
The cloudy \textbf{sky} fills the open background.
A small protruding fixture and thin cable or line appear on the adjacent aircraft surface, reinforcing the close, mechanical detail of the planes.
The commercial then presents a larger, more frontal view of an Eastern jet parked on the tarmac.
Its rounded white nose fills the right side, with a dark blue band running across the cockpit area and around the front of the fuselage.
The cockpit windows sit like dark rectangles above the blue band.
Behind it, other jets and their engines line up across the apron, with tails and wings layered in the distance.
The word “ Eastern ” is partially visible on the forward fuselage near the top.
A low runway-side view follows, looking beneath a \textbf{passing} aircraft.
Large jet engines hang under the wing, their circular openings dark against the bright runway beyond.
The aircraft ’s landing gear, with thick black tires, moves across the scene close to the \textbf{ground}. \textbf{Grass} borders the runway in the foreground, and low airport buildings and a \textbf{tree} line sit far behind.
The \textbf{underside} of the plane glides \textbf{past}, showing wheels, struts, engine pods, and the smooth belly of the fuselage as it \textbf{rolls} along or just over the runway surface.
Another close-up returns to the rear section of an aircraft, with the word “ Whisperjet ” clearly printed in black on a white engine or tail-mounted nacelle.
A deep blue stripe cuts diagonally across the tail area.
As the view shifts along the aircraft ’s side, the “ Whisperjet ” lettering moves out of frame while the blue-striped tail and \textbf{underside} details remain prominent.
Through gaps between the aircraft structures, another Eastern jet is visible on the \textbf{ground} in the distance.
A smaller jet appears airborne or climbing in the background, seen beyond and between the tails of parked aircraft.
It moves across the pale \textbf{sky} above the airport, its dark \textbf{underside} and swept tail \textbf{silhouetted} slightly against the \textbf{haze}.
Tall airport light poles stand below it, and the tops of parked jets \textbf{pass} through the foreground, creating a layered view of activity in the air and on the \textbf{ground} at the same time.
The nose of a blue-and-white Eastern aircraft then \textbf{passes} close across the screen.
The cockpit windows and rounded front move by first, followed by the smooth white fuselage with a wide blue lower band.
A circular Eastern logo appears on the side : a dark round \textbf{emblem} with a white stylized mark inside.
Small passenger windows line the lower portion of the fuselage as the plane continues \textbf{past}.
The final sequence is from an extremely low position on the runway, centered on a yellow line stretching into the distance.
At first, the space is dark and enclosed by the \textbf{underside} of an aircraft, with bright \textbf{sky} visible ahead.
Massive landing-gear wheels loom on either side of the yellow line, \textbf{silhouetted} against the runway and \textbf{sky}.
As the plane moves away, the \textbf{twin} wheels and gear struts recede, and the \textbf{underside} of the fuselage extends overhead like a dark, curved ceiling.
Gradually more of the aircraft becomes visible from behind : the belly, the landing gear, the wings spreading left and right, and engine pods hanging under each wing.
The aircraft continues straight down the runway, perfectly aligned with the yellow center line, becoming smaller against the wide open airfield and cloudy \textbf{sky}.
At the end, the plane is seen from the rear at a distance, centered on the runway with its wings level and engines evenly spaced.
Over the lower part of the image, the Eastern Airlines branding appears in white : a circular logo at the left and the word “ EASTERN ” in bold capital letters beside it.

% matched lemmas: broad, emblem, grass, ground, haze, hazy, heavy, pass, past, roll, silhouette, sky, sunlit, tight, tree, twin, underside, vehicle
\end{textsample}
