\begin{textsample}{POS Dim 2 – 2010 – Score 13.00 – 2010/tv\_com\_2010\_5.txt}  \label{ex:f2_pos_060}
A wide, icy \textbf{mountain} range fills the screen under a pale blue \textbf{sky}, with jagged white peaks stretching into the distance.
On one \textbf{snowy} slope, an adult skier in \textbf{winter} gear appears : a turquoise jacket with dark sleeves, beige pants, black gloves, ski poles, a dark helmet or hood, and reflective goggles.
The skier moves downhill across open \textbf{snow}, small against the vast alpine landscape, then launches off a crest.
High above the \textbf{mountains}, the skier twists into an aerial flip, skis and poles sweeping upward as the body rotates against the \textbf{sky}.
A close view briefly shows the skier ’s face partly \textbf{hidden} by a black helmet and large blue-purple mirrored goggles, the mouth set in concentration as \textbf{snow} and \textbf{sky} blur behind.
The setting changes to an indoor ice track.
The ice is glossy and pale, bordered by dark walls and rows of bright overhead lights that curve away into the distance.
A speed skater ’s blade carves along the ice at close range, then several adult skaters in \textbf{tight} racing suits appear.
They wear black suits with red shoulders or panels, white-and-black caps, and dark wraparound goggles.
They lean forward in deep, aerodynamic positions, one arm often tucked behind the back while the other swings low near the ice.
The group moves in a staggered line around the bend, knees bent sharply, skates crossing over as they \textbf{push} through the turn.
Close views isolate faces under caps and goggles, showing focused, compressed expressions and taut posture.
The skaters \textbf{pass} close together, their red-and-black uniforms streaking across the shiny surface.
One athlete drops extremely low, almost horizontal, with a hand skimming the ice, while another continues upright ahead ; the prone figure slides along the ice before the image shifts away.
An adult athlete then stands facing forward in a narrow, dim passage or tunnel, both hands raised to adjust a glossy black helmet.
The outfit has red sleeves with white stripes and a gray torso panel, suggesting \textbf{winter} racing gear.
The background is patterned with gray, graffiti-like or mural-like shapes, giving the space a hard, urban feel.
The athlete ’s face is mostly \textbf{shadowed} by the helmet.
Outside, a bright, snow-covered city appears.
Tall modern buildings with glass, white façades, and geometric patterns rise around an empty street or plaza.
A black convertible-style car is parked beside a curb, its long dark body contrasting with the pale \textbf{snow}.
The helmeted athlete in the red-sleeved suit walks \textbf{past} the car.
From inside or near the car, the athlete is seen moving toward a low black sled resting on the \textbf{snow}.
The sled is narrow and flat with raised handles or supports, like a skeleton sled.
The athlete steps beside it and lowers onto it headfirst, chest down, arms bent at the front, legs stretched straight behind with red lower legs visible.
The skeleton sled now travels along an icy track that winds through an urban structure.
The track has high white walls, blue guardrails, and overhead concrete beams, with city buildings visible beyond.
The sled \textbf{rushes} through sweeping curves, hugging the wall.
At times the athlete is a small dark shape banking along the far side of the track ; then the front of the sled fills the image, rounded and glossy black, with the athlete ’s red-striped legs tucked along either side.
The sled ’s nose points straight ahead as it skims close to the ice, the white walls reflecting across its curved surface.
The action returns briefly to speed skating.
A skater in the red-and-black suit leans forward, face partly hidden by dark goggles and a white-black cap, \textbf{driving} one arm back and the other forward in a powerful stride.
The posture remains low and urgent, with the ice and dark rink background streaking behind.
The skier reappears high in a cold blue \textbf{sky}, still in the turquoise jacket and beige pants, rotating through another aerial move with skis extended upward.
The figure moves out of view, leaving mostly \textbf{sky}, then a close-up returns to the skier ’s helmeted head and mirrored goggles.
The face is partly visible at the edge of the screen, focused and calm against the pale blue background.
White branding appears over the \textbf{mountain} \textbf{sky} : the bold word “ VISA ” on the left, separated by a thin vertical line from the Olympic rings on the right.
Beneath it, smaller white text reads “ worldwide sponsor. ” The background settles on a wide view of \textbf{snowy} \textbf{mountain} peaks.
Blue and gold rectangular bands slide in behind the logo, echoing Visa ’s brand colours, and the small text changes to “ everywhere you want to be. ” The final image holds the Visa wordmark, the Olympic rings, and the slogan over the panoramic white \textbf{mountain} range.

% matched lemmas: drive, hide, mountain, pass, past, push, rush, shadow, sky, snow, snowy, tight, winter
\end{textsample}
