\begin{textsample}{POS Dim 2 – 1990 – Score 30.00 – 1990/tv\_com\_1990\_91.txt}  \label{ex:f2_pos_031}
The commercial opens in warm, \textbf{hazy} light, looking \textbf{past} a dark vertical obstruction as if from behind a doorway or pillar.
Beyond it, a black four-door \textbf{sedan} is parked on a \textbf{broad} \textbf{paved} plaza lined with \textbf{trees}.
A man in dark clothing approaches the car from the right, carrying or holding a dark jacket or bag.
As more of the scene becomes visible, the car ’s low front end, rectangular headlights, glossy black paint, and silver wheels come into view.
Behind it are pale buildings, bare-branched \textbf{trees}, and a large dark fountain or sculpture, giving the setting a formal urban-park feel.
The man reaches the driver ’s side.
He stands beside the front door, then opens it and leans in.
He appears to be an adult man with short dark hair, wearing a dark jacket and trousers.
The view shifts inside the car, where the interior is tan or beige, with a rounded \textbf{steering} wheel, a dark dashboard, and a center console.
The man lowers himself into the driver ’s seat, bending forward as he settles in.
He reaches toward the console and \textbf{steering} area, then pulls a seat \textbf{belt} across his body.
The tan seat and door trim contrast with his dark clothing.
He handles the dark item he brought with him, moving it across his lap or in front of him as he prepares to \textbf{drive}.
The setting changes to a winding road bordered by rocky hillsides and \textbf{dry} vegetation.
The road curves away into \textbf{shadow}, its double yellow center lines glowing in golden light.
The black Infiniti appears around the bend with its headlights on, moving toward the viewer through an orange sunset \textbf{haze}.
From the front, the car ’s rounded hood, wide dark grille, Infiniti \textbf{emblem}, and bright amber headlights dominate the image.
Dust or mist hangs low around the road as the \textbf{sedan} advances, the driver only a dark \textbf{silhouette} behind the windshield.
The car is then seen in profile, moving through a landscape washed in deep golds and oranges. \textbf{Dry} \textbf{grasses} and shrubs blur across the foreground, partly \textbf{hiding} the lower half of the car.
Bright \textbf{sun} \textbf{glare} flashes along the roofline and windshield, and the black body is outlined by a thin rim of light.
The \textbf{sedan} glides \textbf{past} from left to right, its compact four-door shape clear against the glowing background.
Inside, the focus turns to the empty cabin.
Beige leather seats fill the view : the front passenger seat in the foreground with a \textbf{broad} padded headrest, and a rear bench behind it with three seating positions and vertical seat \textbf{belts} at the sides.
The upholstery is plush, with stitched panels and \textbf{gathered} detailing near the upper backrests.
Warm sunlight and \textbf{shadow} move across the seats, emphasizing the roomy, open-looking interior.
No passengers are visible ; the \textbf{shot} lingers on the spacious rear seat and the light-colored cabin materials.
The commercial returns to fast-moving exterior views of the road and rocky hillside, rendered as streaks of gold and brown.
The Infiniti \textbf{passes} again in side view through the \textbf{sunlit} scrub, its headlights flaring and the roofline catching a bright highlight.
As it continues, the rear half of the car crosses the screen, leaving a glowing \textbf{trail} of dust and warm light behind it.
From the rear, the black \textbf{sedan} \textbf{drives} away into an orange-lit \textbf{haze}.
Red taillights glow on both sides, the Infiniti \textbf{emblem} sits centered on the \textbf{trunk}, and a “ G20 ” \textbf{badge} is visible on the right side of the rear.
Dust rises around the tires and softens the outline of the car as it recedes.
Inside again, the driver is shown in \textbf{silhouette} from the passenger side.
He sits upright with both hands near the \textbf{steering} wheel, facing the road ahead.
The dashboard and center stack are visible to his right, with rectangular vents and controls.
Through the windshield and side windows, rocky slopes and \textbf{sunlit} roadside \textbf{brush} \textbf{pass} by, bathing the interior in warm amber light.
The view briefly looks upward through tall \textbf{trees}, with the \textbf{sun} blazing through \textbf{branches} and \textbf{leaves}.
The bright white-gold \textbf{sun} is partially blocked by \textbf{trunks} and foliage, creating a shimmering, \textbf{outdoor} sense of speed and openness.
The black Infiniti then approaches head-on along a \textbf{dusty}, \textbf{sunlit} road.
Its headlights glow yellow, and a bright highlight runs along the top edge of the hood and roof.
Dust clouds billow out from both sides behind the front wheels, while the surrounding background is dark and wooded.
The car moves steadily forward, centered and assertive against the golden road surface.
At the end, large on-screen text appears over the darkened image of the car : “ G20 ” in big white letters, with the price “ \$21,485 ” below.
Smaller fine print underneath reads that the price is M.S.R.P., fully equipped including destination charges, and that title, taxes, and license fees are not included.

% matched lemmas: badge, belt, branch, broad, brush, drive, dry, dusty, emblem, gather, glare, grass, haze, hazy, hide, leaf, outdoor, pass, past, paved, sedan, shadow, shot, silhouette, steering, sun, sunlit, trail, tree, trunk
\end{textsample}
