\begin{textsample}{POS Dim 2 – 1990 – Score 19.00 – 1990/tv\_com\_1990\_79.txt}  \label{ex:f2_pos_036}
A straight \textbf{two-lane} \textbf{highway} stretches through a desert landscape lined with tall cacti and scrub.
The \textbf{sky} is dark and dramatic, with \textbf{heavy} clouds opening to a bright patch of light near the horizon.
Far down the road, a tiny \textbf{vehicle} approaches along the center of the empty \textbf{pavement}.
A close view shows a male-presenting \textbf{highway} patrol officer in a wide-brimmed tan hat and mirrored aviator sunglasses.
He has a serious, alert expression and faces another uniformed person whose back and hat brim are visible in the foreground.
Reflected in the officer ’s sunglasses are the road and desert surroundings.
The approaching \textbf{vehicle} becomes a low, dark car seen from far ahead, wavering in heat \textbf{haze} as it grows larger.
Its front end is \textbf{broad} and dark, and then pairs of round headlights glow near the \textbf{ground}.
The officer ’s face fills the view again, his mirrored lenses now reflecting another uniformed patrolman standing outside in the desert.
The scene shifts to two \textbf{highway} patrol officers beside a white patrol car with a red-and-blue light bar on the roof.
Both wear tan uniforms, brimmed hats, \textbf{belts}, and dark shoes.
One stands with hands near his hips, watching the road ; the other stands near the car.
The patrol car has blue striping and large highway-patrol markings.
Small white text appears at the bottom : “ Performance based on regular use. ” A hand holds a bright red STP bottle and tilts it downward into the filler opening of a white \textbf{vehicle}.
The bottle is labeled with the white STP oval logo and large white words “ GAS TREATMENT, ” seen upside down as it is poured.
The long red neck of the bottle is inserted into the car ’s opening, suggesting the product is being added to the fuel system.
The same small disclaimer remains along the bottom.
The image \textbf{blends} to the rear of a dark, wide-bodied car \textbf{driving} along the desert road at dusk.
Its round rear lights glow red against a purple-pink \textbf{sky}, with cactus \textbf{silhouettes} and low \textbf{mountains} around it.
The car comes closer from behind, centered in the lane, its \textbf{broad} rear end and dark roofline filling more of the view.
In daylight again, the dark car speeds \textbf{past} in the foreground, briefly \textbf{obscuring} the two officers and their patrol car.
Once it \textbf{passes}, the officers are visible beside the white cruiser ; one bends or reaches near the side of the car while the other stands upright, ready and watching.
Close details of the patrol car ’s lettering flash by, including large yellow letters from “ \textbf{HIGHWAY} ” and the red-and-blue light bar.
The white \textbf{highway} patrol car then moves along the road, shown from the side with its blue stripe, star-shaped \textbf{badge} \textbf{emblem} on the door, roof light bar, side mirror, and driver visible through the window.
It continues \textbf{past} scrubby desert vegetation.
Finally, the patrol car turns onto the \textbf{highway} or pulls away sharply, kicking up a pale cloud of dust behind its rear wheels.
Dark \textbf{mountains}, tall cacti, and the fading \textbf{sky} frame the road as the cruiser heads off into the desert.

% matched lemmas: badge, belt, blend, broad, drive, emblem, ground, haze, heavy, highway, mountain, obscure, pass, past, pavement, silhouette, sky, two-lane, vehicle
\end{textsample}
