\begin{textsample}{POS Dim 2 – 1990 – Score 22.00 – 1990/tv\_com\_1990\_80.txt}  \label{ex:f2_pos_034}
A warm, \textbf{reddish} view of a roadway opens the commercial.
The road surface fills most of the image, with painted lane lines and a small roadside sign near the lower edge.
A car ’s lights streak \textbf{past} in a blur, suggesting speed.
The image then \textbf{blends} into the inside of an automotive factory, where large metal car body panels and robotic welding equipment fill the space.
Mechanical arms move close to the bare silver car structure, and bright white-orange sparks burst outward as welding begins.
A middle-aged man in a blue work shirt and a tan cap with a Toyota-style patch is seen close up.
He has glasses, a gray beard and mustache, and a focused expression as he looks downward toward equipment just out of view.
His gloved hands work with a dark handheld tool beside an engine or mechanical assembly.
Another worker ’s gloved hand steadies a gray metal frame while a vertical welding tool touches it ; sparks scatter across the surface.
The commercial cuts between manufacturing and road imagery.
A silver or light-colored car \textbf{rushes} along a \textbf{highway} or test road, blurred by speed.
Back in the plant, a blonde woman wearing a light-colored cap and dark safety glasses stands behind foreground machinery.
She faces forward with a calm, concentrated expression as moving parts and warm orange factory lighting \textbf{pass} in front of her.
More welding follows : a tool presses against a silver car body panel, producing an intense flare of light and a shower of sparks.
A man in a white hard hat with a clear face shield and a light blue protective apron stands at a workstation in the factory.
He looks downward while working near a hanging chain and metal apparatus ; sparks fall nearby.
Another road \textbf{shot} shows a car sweeping \textbf{past} very close, its headlights and grille stretched by motion.
Two workers in red shirts and hard hats stand beside equipment ; one, wearing striped head protection and safety glasses, holds a long tool or hose and laughs while turning toward the other worker, who wears a sleeveless red shirt and a hard hat.
A rapid view down a factory aisle leads to a finished dark red Toyota Camry from the rear.
The \textbf{trunk} lid carries the Toyota \textbf{emblem} and large “ CAMRY ” lettering across a dark panel.
A man in a dark shirt and light pants bends beside the rear bumper, closely inspecting or adjusting the car ’s back corner.
A close-up follows from under or inside the rear body area, where a worker in safety glasses peers upward through hanging cables and dark structural parts, inspecting the \textbf{underside} with a serious, careful expression.
A car body sits in a spray or wash booth under bright overhead lights.
Dense blue-white mist pours over it from above and around the sides, \textbf{obscuring} the outline of the \textbf{vehicle}.
The front of a light-colored car gradually appears through the mist, its headlamp and side mirror visible as spray billows along the passenger side.
The scene shifts to an industrial area glowing \textbf{red-orange}, where a worker is seen as a dark \textbf{silhouette} moving through a corridor of bright light panels.
Assembly and inspection continue.
A car with its hood raised sits on the factory floor, with papers or check sheets clipped above the open hood.
A woman in a worn red hard hat, safety glasses, and a blue work shirt works beside an orange tool or fixture, looking down with concentration.
Another person in the blurred background also works at the line.
In a wider factory aisle, a person rides away on a small three-wheeled \textbf{cart} or \textbf{bicycle}, wearing a loose light-blue coat that flares out behind them ; they lift a cap in one hand as they move down the polished aisle.
A close-up returns to the dark red Toyota ’s rear corner.
A worker wearing white gloves runs a hand along the glossy paint near the taillight and \textbf{trunk} seam, inspecting the finish.
The “ TOYOTA ” \textbf{badge} is visible on the \textbf{trunk} as the worker leans in closely, eyes following the contour of the body panel.
Outside, on a \textbf{banked} test track under a pale blue \textbf{sky}, dark and light-colored \textbf{sedans} speed \textbf{past} along the curved \textbf{pavement}.
The imagery overlaps with a circular close-up of a wheel or metal rim, inside which orange sparks spray dramatically, linking the road testing with factory work.
Then a large group of Toyota plant employees walks toward the viewer outdoors.
They are a diverse mix of men and women, mostly adults, wearing work shirts, khaki pants, hard hats, caps, safety glasses, gloves, and some uniforms.
Several smile ; one woman carries a clipboard.
Two cars \textbf{drive} around an orange cone on a wet test surface, their reflections visible on the shiny \textbf{pavement}.
The group of employees appears again closer up, smiling and walking forward.
A dark red Camry then glides across the wet, reflective surface near orange traffic cones, with the group standing in the background watching.
The car comes to rest in profile, centered in front of the assembled workers.
Large white text “ CAMRY ” appears on the wet floor beneath the car.
The crowd stands behind it in rows, many in hard hats and factory uniforms.
As the final image holds, the workers raise their arms and cheer visually, some lifting hats.
More white text appears near the bottom : “ WE JUST COULD N’T LEAVE WELL ENOUGH ALONE. ” In the upper right, the Toyota logo appears with the slogan “ I love what you do for me ” and “ TOYOTA. ” The dark red Camry remains centered between two orange cones, its side reflected on the polished surface while the employees celebrate behind it.

% matched lemmas: badge, bank, bicycle, blend, cart, drive, emblem, highway, obscure, pass, past, pavement, red-orange, reddish, rush, sedan, shot, silhouette, sky, trunk, underside, vehicle
\end{textsample}
