\begin{textsample}{POS Dim 2 – 1980 – Score 14.00 – 1980/tv\_com\_1980\_59.txt}  \label{ex:f2_pos_070}
A silver station wagon is parked in a leafy \textbf{outdoor} area, likely a park or roadside under large \textbf{trees}.
Its rear hatch is raised high, exposing a roomy cargo area.
An older woman with short light-blond or gray hair, wearing a pale pink sweater and matching pants with white shoes, stands at the open back.
She is loading a flat crate or tray filled with many pale green round items into the rear.
The cargo space already holds more of the same green items and a soft bag with red, white, and blue sections.
She \textbf{pushes} the load farther in, then looks up toward someone off-screen as if responding to the conversation about the car ’s space.
She reaches overhead with both hands and pulls the hatch down, closing the rear of the wagon.
With the wagon now closed, the woman walks along the side of the silver car beneath dappled \textbf{tree} shade.
The car ’s long roofline, large side windows, black trim, and practical wagon shape are clearly visible.
She reaches the front door, opens it, and begins to get inside.
The front grille is visible with a small \textbf{badge} at the center ; the car is presented as a clean, everyday family-style \textbf{vehicle} with generous cargo room.
The scene changes to the interior of a car with tan upholstery and a \textbf{sporty}, well-equipped cabin.
A dark-haired adult man, probably in his thirties, sits in the driver ’s seat wearing a dark jacket and a seat \textbf{belt}.
Tan bucket seats, a center console, gear shift area, and overhead roof glass or sunroof panels are visible.
He holds the steering wheel with one hand while turning his head toward the passenger side, speaking with an alert, friendly expression.
As greenery blurs through the windows behind him, he alternates between looking toward the person beside him and looking forward at the road.
His expression softens into a smile, suggesting reassurance as the conversation shifts from the brand name to the car ’s performance.
A red two-door sports coupe appears on a wide, curving road bordered by green hills and \textbf{sunlit} slopes.
It \textbf{drives} toward the viewer with a low, angular front end, black grille area, dark headlight surrounds, and amber running lights.
The hood has a raised vent or scoop detail, emphasizing the car ’s performance look.
As it comes closer, the red nose fills the view, then the car sweeps \textbf{past}, revealing its side profile : a compact, aerodynamic coupe with dark-tinted glass, black side mirrors, and silver wheels.
The road and hillside slide by in warm daylight.
Back inside a car, the same dark-haired male driver is seen from the front, framed by the steering wheel at the bottom.
He wears a dark jacket over a light shirt, and his seat \textbf{belt} crosses his chest.
He smiles broadly while driving, hands near the wheel, with \textbf{sunlit} greenery visible through the windshield and side windows.
The silver station wagon is then shown in motion on an open road at dusk or late afternoon.
It \textbf{passes} from a side view into a rear view, its boxy wagon shape and large rear window clear against a pale \textbf{sky}.
The taillights and amber lights glow as it travels away along the lane, with \textbf{trees} and low landscape on either side.
The red sports coupe returns on the hillside road, now seen from a wider angle as it travels along the curve.
It leans visually with the road ’s angle, its red body catching the warm light while the green hillside rises behind it.
The car continues smoothly along the \textbf{pavement}, reinforcing the contrast between the practical wagon and the \textbf{sporty} coupe.
The commercial ends on a black background with a bold red “ NISSAN ” wordmark across the center.
White, streak-like lettering sweeps across the foreground, partially \textbf{obscuring} the logo and creating a sense of motion.

% matched lemmas: badge, belt, drive, obscure, outdoor, pass, past, pavement, push, sky, sporty, sunlit, tree, vehicle
\end{textsample}
