\begin{textsample}{POS Dim 2 – 2020 – Score 12.00 – 2020/tv\_com\_2020\_70.txt}  \label{ex:f2_pos_017}
The commercial opens inside a bright, \textbf{modern} AT\&T retail \textbf{store}.
The \textbf{space} has blue accent walls, light wood display tables, \textbf{shelves} with phones/accessories, blue stools, and a glass entrance with the AT\&T logo above it.
A gray-haired man in a dark jacket and green shirt stands in the \textbf{store}, while a female \textbf{store} employee in a light blue AT\&T shirt stands behind a counter on the right.
White on-screen text at the bottom reads : “ This ad was made safely.
Please wear a \textbf{mask} in our \textbf{stores}. ” The next shot moves closer to the gray-haired man as he faces someone off-camera.
The back of another person ’s head and shoulder is visible in the foreground, suggesting he is addressing another \textbf{customer} or person in the \textbf{store}.
The same \textbf{safety} text remains at the bottom.
The view then cuts to a younger man wearing a brown \textbf{sweater} over a patterned-collar shirt.
He stands near a display table and \textbf{shelves} of \textbf{phone} accessories, looking toward someone off-screen with a somewhat skeptical or questioning expression.
The commercial alternates between the two men.
The gray-haired man is shown from the front with a tense, focused expression.
The younger man is then shown in an extreme close-up of his eyes, appearing to squint or stare intently.
This is followed by an extreme close-up of the gray-haired man ’s face, with furrowed brows and a similarly intense look.
The female AT\&T employee is then shown behind the counter, centered in front of \textbf{shelves} with boxed \textbf{devices} and accessories.
She holds or stands behind a tablet/register and appears to be speaking or reacting to the two men, though no audio is described.
A wider shot shows the two men facing each other across the \textbf{store}, with the employee positioned behind the counter between them in the background.
The scene visually frames them as if they are in a direct exchange or comparison.
The younger man is then shown closer, smiling broadly and gesturing with one hand.
Small white legal/disclaimer text appears along the bottom of the frame but is too small to read clearly in full.
The gray-haired man is shown next, turned slightly to the side and also appearing to speak or respond, with the same small \textbf{disclaimer} text at the bottom.
Another wide shot returns to the two men standing opposite each other in front of the counter.
The employee remains centered behind them, watching.
The final frame transitions to a bright blue promotional end card.
A \textbf{smartphone} image appears on the left.
Large white text is partially visible, including “ FR ” and “ SAMSUNG GA …, ” suggesting a Samsung Galaxy-related offer, but the full headline is cropped/obscured in the sampled frame.
Smaller text reads in part : “ Buy on a qualifying installment plan with … \$75/mo. before discounts \& trade … ” Additional fine print appears at the bottom, too small to fully read.
The AT\&T \textbf{store} scene is faintly visible behind the blue promotional overlay.

% matched lemmas: customer, device, disclaimer, mask, modern, phone, safety, shelf, smartphone, space, store, sweater
\end{textsample}
