\begin{textsample}{POS Dim 2 – 2020 – Score 13.00 – 2020/tv\_com\_2020\_84.txt}  \label{ex:f2_pos_050}
A couple stands hand in hand in a bright, \textbf{snowy} evergreen forest.
The woman, a young adult with long blonde hair, wears a pale blue \textbf{winter} coat, gray knit hat, gray scarf, dark pants, and \textbf{boots}.
The man, a young adult with short dark hair and light facial hair, wears a dark navy coat over a gray sweater.
They face each other warmly against a background of snow-laden pine \textbf{trees}.
In a closer view, the man smiles at the woman, then raises his fingers to his mouth as if making a sharp call or whistle.
Far across the \textbf{snow}, a small dark shape appears between the \textbf{trees}, then resolves into a fluffy black, white, and tan puppy bounding through deep powder.
The puppy, wearing a collar with a round tag, charges toward them with its ears flopping and \textbf{snow} spraying around its chest and paws.
The woman receives the puppy in her arms, laughing and hugging it close as it stretches its front paws up toward her face.
The man stands beside her, smiling with a pleased, slightly proud expression, and rests a hand near her shoulder.
The puppy nestles against the woman ’s coat while she turns toward the man and speaks to him, cradling the dog between them.
The mood shifts as the woman looks off to the side with a knowing expression.
She holds the puppy in one arm and brings her other hand toward her mouth, as though preparing to call out or reveal something of her own.
The man also looks in the same direction, his face changing from contentment to curious surprise.
A black GMC Sierra pickup bursts forward through the \textbf{snowy} landscape between tall pines, \textbf{driving} straight through deep \textbf{snow} and \textbf{throwing} up wide curtains of white powder on both sides.
Its front grille is large and chrome-accented, with a red GMC \textbf{badge} in the center and bright C-shaped daytime running lights framing the headlights.
A small safety disclaimer appears along the bottom during these \textbf{driving} images, including language such as “ Professional driver.
Closed \textbf{course}.
Do not attempt.
Prior model shown. ” Close views show the \textbf{truck} ’s front wheel and fender cutting through \textbf{snow}, the tire spinning over packed powder while chunks of \textbf{snow} fly across the screen.
The \textbf{truck} settles into view from the front, imposing and glossy black against the blue-white \textbf{winter} background.
Back with the couple, the woman holds the puppy and smiles softly while the man stares ahead, impressed.
He turns toward her, and she gives him a satisfied, playful look, as if this \textbf{truck} is her surprise for him.
The scene widens to show the black GMC Sierra parked on the \textbf{snowy} \textbf{ground} near the couple.
Snow-covered \textbf{trees} fill the background, and a lamppost stands to the left.
The man walks toward the \textbf{truck} ’s front grille and bends near it, while the woman remains a short distance away holding the puppy.
Large white block text appears in the upper left beside a red vertical line : “ GIFT LIKE A PRO. ” The commercial then changes to promotional offer graphics.
A red GMC Sierra 1500 is displayed on a \textbf{snowy} open landscape with \textbf{mountains} and forest behind it.
Large text at the upper left reads “ GMC ” and “ 2026 GMC SIERRA 1500, ” followed by “ MICHIGAN RESIDENTS ” and a bold “ \$1,000 ” with “ LEASE CASH ” beneath it.
The final offer screen keeps the red Sierra on the right and shows large text on the left : “ GMC HOLIDAY EVENT, ” “ 2026 GMC SIERRA, ” “ 1500 ELEVATION \textbf{CREW} CAB 4x4, ” and “ WITH TURBOMAX ENGINE. ” A prominent price reads “ \$169 ” per month for 24 months, with “ \$3,759 due at signing after all offers ” shown below, followed by smaller eligibility and lease details in fine print across the bottom.

% matched lemmas: badge, boot, course, crew, drive, ground, mountain, snow, snowy, throw, tree, truck, winter
\end{textsample}
