\begin{textsample}{POS Dim 2 – 2000 – Score 12.00 – 2000/tv\_com\_2000\_52.txt}  \label{ex:f2_pos_033}
The commercial opens on a nearly black frame, then cuts to the exterior of a house at night.
A lit upstairs window shows a silhouetted figure inside.
The house façade is illuminated with cool blue-purple lighting.
A wider exterior shot follows : the house \textbf{sits} on a residential street with trees, a glowing porch light, and a dark car passing in the foreground.
The scene moves inside the house.
A shadowy figure is seen on or near a stair landing/railing, suggesting movement through the house at night.
The next shot shows a young blonde woman in a bathroom, wearing a pink or rose-colored top, brushing her teeth in front of a mirror under bright bathroom lights.
The focus then shifts to a \textbf{computer} \textbf{screen} viewed over someone ’s shoulder.
A word-processing or messaging window is open, and visible typed text reads something like “ When can I see y ” or “ When can I see y … ” ; the full line is cut off or unclear.
A young dark-haired man is then shown seated at a \textbf{computer} in a dim \textbf{room}, looking at the \textbf{screen} with a serious or attentive expression.
After a brief dark transition, the blonde woman appears in close-up with a toothbrush in her mouth, smiling.
She is later shown from a low angle at a bathroom sink or counter, reaching forward with both arms, possibly operating a camera or computer-related \textbf{device}.
Another close-up shows her smiling brightly, resting her face on her hand.
The man ’s \textbf{computer} \textbf{screen} appears again, showing a \textbf{desktop} with \textbf{multiple} windows.
One window contains a small image or video area.
The woman is shown again smiling, partly obscured by a dark foreground shape, as if seen through or around a \textbf{monitor}.
A close-up of a \textbf{computer} \textbf{interface} follows, with toolbar \textbf{icons} and a pale window ; the woman ’s smiling face is faintly superimposed or reflected over the \textbf{interface}.
The man is then shown smiling at his \textbf{computer}.
The commercial emphasizes internet browsing/searching visually.
A close-up of a web \textbf{page} or search \textbf{interface} shows large text including “ Internet ” and “ Enter the … ” with “ Search ” visible.
Another layered shot combines the search text with an image of two people lying on pillows or a bed-like surface ; the word “ Angel ” is visible, though the full text is unclear.
A close-up of \textbf{interface} \textbf{icons} shows a magnifying glass labeled “ Search ” and another label beginning “ Favorit … ” likely “ Favorites, ” with a cursor arrow pointing near the search area.
The man ’s \textbf{monitor} then shows an image of two people with angel wings or wing-like shapes behind them, lying side by side.
A close-up of a hand on a mouse follows, suggesting clicking or navigating.
The man is shown again at his desk, looking downward toward the \textbf{computer}.
A split or layered \textbf{screen} effect shows the blonde woman on the left and typed words on the right.
The visible text reads “ I like … ” and then more clearly “ I like this. ” The phrase is later overlaid with the man ’s face, creating a montage of text and faces.
The blonde woman is then shown seated or leaning forward at a \textbf{computer} desk in a bedroom-like \textbf{room} ; a bed and lamp are visible behind her.
She extends her hands toward the camera, holding a small object that is unclear in the sampled frame.
A mostly white \textbf{computer} \textbf{screen} appears, with only a small image area visible near the upper left.
The woman then appears in close-up covering part of her face with her hand, smiling or laughing.
The final frame is a dark end card with the AT\&T globe logo above the text “ AT\&T. ” Beneath it, readable text includes “ 1-800-WORLDNET ” and “ www.att.com/worldnet. ”

% matched lemmas: computer, desktop, device, icon, interface, monitor, multiple, page, room, screen, sit
\end{textsample}
