\begin{textsample}{POS Dim 2 – 1970 – Score 18.00 – 1970/tv\_com\_1970\_41.txt}  \label{ex:f2_pos_073}
At the very start, a small television-style graphic appears against a dark background.
At the top is the CBS eye symbol followed by the word “ SUNDAY ” in large white letters.
Below it is a close-up of a blond man ’s face inside a rectangular picture, with promotional text underneath that includes “ CBS SUNDAY \textbf{NIGHT} MOVIES ” and a start time, though some of the smaller wording is hard to read.
The commercial then shifts outdoors to a bright, \textbf{sunlit} setting with tall \textbf{dry} \textbf{grasses} and a soft, \textbf{hazy} background.
A young adult man and woman stand close together, dressed for cool weather.
The man, on the left, has light brown wavy hair and wears a brown leather-like jacket over layered shirts or a sweater.
The woman, on the right, has short dark curly hair and wears a light beige jacket with a high white turtleneck underneath.
They face slightly toward each other at first, then turn their attention forward, as if looking at something approaching.
The man ’s expression is attentive and expectant ; the woman looks up and across with a curious, pleased expression.
As they continue looking forward, the man ’s arm rests around or behind the woman ’s shoulders, and she leans in close beside him.
A \textbf{red-orange} Toyota sports coupe appears in the distance, coming straight toward the viewer along a flat road in open country.
The front of the car rises into view, framed by pale \textbf{sky} and muted fields.
As it approaches, its low, squared front end becomes clear : two round headlights on each side, a black grille across the center, amber lights low in the bumper, and a dark windshield with a driver faintly visible inside.
The car continues forward until the Toyota name on the grille area is visible.
The car is then seen in profile, traveling left to right along a \textbf{rural} roadway.
It is a compact two-door coupe with a long hood, a sloping rear roofline, shiny wheel covers, and \textbf{chrome} trim along the side.
The body color reads as orange-red, glowing warmly in the sunlight.
The background is a soft blur of fields, roadside fencing, and autumn-toned vegetation, emphasizing the car ’s movement through open space.
Next, the coupe \textbf{drives} through a residential street.
It \textbf{passes} a white house with dark shutters, a porch, a white picket \textbf{fence}, and a large leafless \textbf{tree} beside the road.
The car moves close by, showing the front corner, windshield, side windows, door, and rear quarter panel in quick succession.
Reflections of \textbf{trees} and \textbf{sky} ripple across its glossy paint and glass as it \textbf{passes}.
The interior is shown empty, emphasizing seating.
There are two front bucket seats and a rear bench, all upholstered in dark material with horizontal stitched panels.
The front seats have substantial headrests, and a center console runs between them.
The rear seating area is visible behind, suggesting room for two additional passengers.
A close view of the dashboard follows.
On the left is a \textbf{sporty} \textbf{steering} wheel with metal spokes.
Across the dash are multiple round gauges and rectangular control panels, with a radio and ventilation controls on the right.
A manual gearshift rises from the center area, its knob marked on top, and keys hang from the ignition.
The arrangement presents the cockpit as driver-focused, with many instruments clustered in front of the wheel and along the center dash.
The \textbf{red-orange} Toyota then returns outside, \textbf{driving} head-on through the same residential-looking area with the white \textbf{fence} behind it.
The front grille, paired round headlights, and hood reflections are prominent as it approaches and \textbf{passes}.
After that, the car is seen from the side and rear along a country road bordered by wooden fencing and open fields.
It travels away along the \textbf{pavement}, its rear window, \textbf{trunk} lid, rectangular taillights, and \textbf{chrome} rear bumper visible.
The road curves gently through flat farmland under a pale \textbf{sky}.
The front of the car fills the view again in a grassy or open roadside setting.
The Toyota \textbf{badge} area on the black grille is shown very close.
The word “ TOYOTA ” appears in white capital letters beside the round headlamp cluster, growing larger until the brand name dominates the image next to a gleaming headlight.
The couple reappears standing behind the roofline of the car, still outdoors.
Both now look pleased.
The woman smiles broadly, and the man, still in his brown jacket, gestures forward with one raised index finger while speaking or addressing the viewer.
The car ’s upper side and window edge run across the lower foreground, with the couple visible above it.
The view widens to reveal the car parked on a gravel or dirt area near a modern, angular building set on a grassy slope.
The \textbf{red-orange} coupe is shown from the rear side with its \textbf{trunk} lid open.
The man and woman stand near the open \textbf{trunk}, moving around the back of the car as if preparing to load or unload belongings.
The woman appears beside the \textbf{trunk} holding or reaching for a dark soft bag.
Tall \textbf{dry} \textbf{grasses} and the building ’s large windows form the background.
At the end, the parked Toyota remains angled toward the left with the \textbf{trunk} open and the couple beside it.
Large white capital letters spelling “ TOYOTA ” appear across the bottom of the screen, with a smaller line of text beneath that is only partly legible.
The final image holds on the car, the open \textbf{trunk}, the couple, and the modern building behind them.

% matched lemmas: badge, chrome, drive, dry, fence, grass, hazy, night, pass, pavement, red-orange, rural, sky, sporty, steering, sunlit, tree, trunk
\end{textsample}
