\begin{textsample}{POS Dim 2 – 1960 – Score 22.00 – 1960/tv\_com\_1960\_53.txt}  \label{ex:f2_pos_007}
In black and white, the commercial opens on a high \textbf{mountain} landscape with ridges and distant hills stretching across the horizon.
A man in a light-colored cowboy hat and light jacket stands at an overlook, holding binoculars to his eyes.
He appears to be an adult man, clean-shaven, with dark hair under the hat.
His jacket has a badge-like \textbf{emblem} on the chest, giving him the look of a ranger or \textbf{outdoor} patrolman.
He scans the distant campsite below.
Through the rounded binocular view, a small camp area appears : a pitched tent, a folding table, boxes or coolers, and a dark bear moving among the camping gear.
The bear is large and rounded, bending over the table and supplies as if rummaging through them.
The man lowers the binoculars, squints into the sunlight, smiles knowingly, and turns away as if deciding to act.
He walks across a \textbf{dusty} \textbf{mountain} turnout toward a light-colored Rambler Rebel with a dark roof, parked beside the overlook.
Another \textbf{vehicle}, a utility wagon or \textbf{truck} with gear on it, sits farther back.
The Rebel is a long, low, two-door car with clean straight sides, \textbf{chrome} trim, round wheels with \textbf{whitewall} tires, and a squared-off rear.
The man opens the driver ’s door and climbs in.
Inside, the car has dark, striped bench seats and a large \textbf{steering} wheel.
He settles behind the wheel, leaning forward with purpose.
The car starts off from the gravel turnout.
A close view of the rear wheel shows the tire turning and biting into loose dirt and \textbf{stones}.
The Rebel pulls away, kicking up dust, then descends a \textbf{rough} \textbf{mountain} road near a small lookout building.
It bounces and leans slightly over uneven \textbf{ground}, yet remains steady as it comes down the slope.
Wider views show the car moving along a winding, exposed dirt road high above valleys and hills, with scattered \textbf{trees} and guard posts marking the road edge.
Inside the car, the man \textbf{drives} with both focus and control.
He wears his cowboy hat low and keeps one hand near the steering wheel while the other reaches toward the gear selector or transmission controls.
His face is calm and intent, and he glances between the road and the controls.
The visible action matches the transcript ’s references to power and “ Shift-Command, ” as the car is shown being \textbf{driven} hard on the \textbf{mountain} roads rather than simply displayed.
The Rebel continues along forested dirt roads, \textbf{throwing} up a thick plume of dust behind it.
It approaches from the distance, then \textbf{passes} close to the viewer, its front grille and paired headlights prominent.
The landscape shifts between open \textbf{mountain} views and shaded pine woods.
Sunlight flashes through the windows and across the driver ’s face as he steers through the \textbf{trees}.
The road surface is \textbf{rough} and \textbf{dusty}, but the car moves quickly and smoothly, sometimes seen from the front emerging through dust clouds, sometimes from behind as it speeds away along a narrow track lined with pines.
Meanwhile, the campsite is shown in disarray.
The bear has pulled down or collapsed the tent, and camping equipment is scattered around : folding chairs, boxes, fabric, and containers lie tipped over on the \textbf{ground}.
The bear noses among the supplies and later \textbf{pushes} at a metal trash can, knocking it over.
The campsite is in a wooded area, with tall \textbf{tree} \textbf{trunks} and strong patches of sunlight and \textbf{shadow}.
The Rebel arrives near the camp.
The man gets out and stands on the raised \textbf{ground} near the car, facing the bear and the wrecked camp.
He raises his arms wide, gesturing in a shooing motion.
The bear remains low in the foreground near the collapsed tent and scattered gear, while the car sits behind the man, its light body bright against the darker \textbf{trees}.
The man steps forward with his arms spread, continuing to wave the animal away.
The scene suggests he has reached the campsite in time to confront the nuisance animal, with the Rebel parked close by as the means that got him there.
The setting then changes from rugged \textbf{mountain} roads to a \textbf{paved} \textbf{highway} bridge.
The light-colored Rambler Rebel with its dark roof \textbf{drives} along a smooth elevated roadway bordered by guardrails.
The car is seen in profile and from behind, traveling at speed across a long bridge high above a valley.
Below and beyond the bridge are \textbf{rolling} hills, fields, and distant \textbf{mountains}.
As the view widens, the bridge ’s tall supports and arched structure become visible, emphasizing the height and openness of the landscape while the car appears small but steady on the roadway.
At the end, large white text appears over the wide valley and bridge view : “ American Motors. ” The car continues as a tiny shape on the bridge beneath the words.
A final line of text is added below, forming the closing message : “ American Motors ” and, underneath it, “ quality built in not added on. ”

% matched lemmas: chrome, drive, dusty, emblem, ground, highway, mountain, outdoor, pass, paved, push, roll, rough, shadow, steering, stone, throw, tree, truck, trunk, vehicle, whitewall
\end{textsample}
