\begin{textsample}{POS Dim 2 – 2000 – Score 22.00 – 2000/tv\_com\_2000\_45.txt}  \label{ex:f2_pos_025}
A glossy red sports car fills the screen in extreme close detail against a dark background.
Its side window and rear quarter panel are visible, with red seats inside and a white rectangular reflection or paper-like shape catching the light through the glass.
A large red door panel or upward-opening body section rises above the cabin, emphasizing the car ’s sculpted, exotic shape.
The view glides across the car ’s red \textbf{bodywork}, showing the curved roofline, black glass, vents, and smooth reflections on the paint.
The game title appears over racing imagery : bold, slanted white letters spell “ MIDNIGHT CLUB II, ” with large white Asian characters above and to the left.
Behind the text, a teal-green car body fills the right side, while a blurred \textbf{night} street and another orange car sit to the left, suggesting speed and city racing.
The title remains centered across the shiny car surface for several moments.
The red sports car returns in a close side view, now focused on the front wheel, fender, and door.
The silver multi-spoke rim sits under a rounded wheel arch, and a small \textbf{chrome} side vent or intake glints near the lower body.
The red paint is highly polished, reflecting soft light as the car ’s contours dominate the image.
The perspective shifts inside a moving car, looking out through dark window pillars at a nighttime city.
Bright yellow-lit building windows streak \textbf{past}.
An orange sports car races alongside outside the passenger window, visible in pieces as it \textbf{passes} behind the dark interior frame and side mirror.
It drops back into the distance on an elevated road lined with barriers and surrounded by tall buildings.
A metallic Rockstar-style \textbf{emblem} appears on a yellow surface : a rounded square \textbf{badge} with a gold “ R ” and a star at the lower right, rendered like a chrome-and-gold logo.
The \textbf{badge} recedes slightly, centered on the yellow background.
Headlights flare in the darkness as cars approach head-on.
Then the city opens into a wide skyline view : tall modern buildings, elevated \textbf{highways}, and a bright horizon.
The scene darkens rapidly into \textbf{night}, and white and red light \textbf{trails} curve along the roads between the buildings, giving the impression of traffic and high speed through an urban downtown.
A purple classic muscle car with bright round headlights fills the foreground from a low angle.
The front bumper is \textbf{chrome}, the front wheel has a shiny deep-dish rim, and yellow flame graphics lick back along the purple side panel.
The car looks \textbf{heavy} and customized, with an aggressive stance.
From inside another car, a green-and-white racing car slides sideways across a narrow nighttime street in front of a metal \textbf{fence} and \textbf{stone} buildings.
Its headlights \textbf{throw} a bright beam through tire smoke.
The green lower body and white upper body are visible as it drifts, wheels angled, smoke curling around the car and across the \textbf{pavement}.
Two cars are then seen from behind, side by side, their red taillights glowing through smoky air as they accelerate down a city street.
The left car is yellow or orange ; the right car is darker red.
Both appear to be racing away into the \textbf{night}.
A motorcycle appears briefly, front wheel lifted high in a wheelie.
Its headlight shines toward the viewer, and the rider is mostly a dark \textbf{silhouette} in black gear, leaning back as the bike rears up near parked cars on a dim street.
A silver or gray sports car charges forward at \textbf{night} with icy blue headlights.
Its hood has dark vents and a central stripe or raised line, and the windshield reflects orange vertical lights from buildings overhead.
The car ’s front end dominates the scene as it speeds along empty streets.
On a cobblestone street at \textbf{night}, a car crests or scrapes along the uneven road, \textbf{throwing} orange sparks from underneath.
The headlights \textbf{glare} brightly, and the car flashes \textbf{past} from left to right, leaving sparks scattered over the \textbf{stones}.
Another set of headlights follows from the distance up the same street.
Police imagery follows : a dark police car or patrol \textbf{vehicle} approaches with bright headlights and a red-and-blue light bar on top.
The image becomes blurred with blue and red flashes, then shifts to a dark aerial view where a purple-white searchlight beam cuts down through the \textbf{night}.
A car drifts beneath tall bridge supports or street structures, leaving a plume of smoke as the searchlight illuminates the road.
A high, exterior view looks through a grid of vertical building bars or window frames at cars racing along a multi-level ramp or elevated roadway inside an urban structure.
Headlights flare behind the bars, and a light blue car and an orange car appear close together.
The view pulls wider to show them exiting toward a city intersection below, where another car with headlights crosses the street.
On a foggy street, headlights glow through \textbf{haze} near old buildings and lampposts.
A red sports car sweeps across the foreground from right to left, its rear lights and curved body blurred by speed.
Light streaks and smoke make the \textbf{passing} cars hard-edged and ghostly, as if they are sliding through mist.
A dark purple sports car follows in close detail.
Bright headlights shine from the front, then the view tracks along the side : large black wheels, low \textbf{bodywork}, and a raised rear wing.
Smoke clings around the tires and lower panels as the car glides \textbf{past} on a \textbf{paved} road.
An orange sports car is shown from behind and low to the \textbf{ground}, racing down a city street between tall buildings.
Its right taillight glows red, its rear wing rises high, and the body reflects the \textbf{blue-gray} street and building lights.
White lane lines stretch ahead.
A small ESRB rating icon appears at the lower left, showing a large “ T ” for Teen.
The car continues forward through the city canyon as neon and window reflections slide across its paint.
A purple muscle car with flame decals returns, sliding around a corner near a building with bright turquoise horizontal neon bands.
Smoke billows heavily from the rear tires.
The car has a black hood or roof, \textbf{chrome} trim, and a prominent engine blower protruding through the hood.
The “ T ” rating icon remains at the lower left as the car moves across the scene and exits, leaving a cloud of smoke behind.
The action shifts to a rain-slicked, neon-lit city intersection.
Dark cars streak across the wet road, their \textbf{silhouettes} cutting in front of bright white signs and traffic lights.
Reflections shimmer on the \textbf{pavement}.
Headlights approach in a cluster, growing brighter and more blurred among colorful billboards.
A large blue sign with the word “ club ” is visible in the background as smoke or spray washes across the street.
Large white title letters begin to \textbf{rush} forward over the racing scene.
The background remains a bright, wet nighttime avenue with billboards and headlights, while the slanted metallic letters assemble across the center.
The final title locks into place : white Asian characters above the bold italic words “ MIDNIGHT CLUB II. ” The ESRB “ T ” for Teen rating icon sits at the lower left, and the title remains over the blurred neon city backdrop.

% matched lemmas: badge, blue-gray, bodywork, chrome, emblem, fence, glare, ground, haze, heavy, highway, night, pass, past, paved, pavement, rush, silhouette, stone, throw, trail, vehicle
\end{textsample}
