\begin{textsample}{POS Dim 2 – 2020 – Score 35.00 – 2020/tv\_com\_2020\_78.txt}  \label{ex:f2_pos_041}
A winding road cuts through dark, \textbf{rolling} countryside under a cloudy dawn \textbf{sky}.
A large gold Chevrolet bowtie \textbf{emblem} appears over the road, then becomes a bright white outline framing the same landscape.
A blue Chevrolet pickup comes toward the viewer on a \textbf{two-lane} bridge or raised road, headlights and vertical running lights glowing against the dim \textbf{sky}.
Its \textbf{broad} grille and bowtie \textbf{badge} fill the view as it \textbf{drives} steadily forward.
The scene shifts to a sunny, tree-lined neighborhood street.
A light-colored Chevy pickup \textbf{drives} along the asphalt beneath leafy \textbf{branches}, \textbf{passing} lawns and houses.
Inside, a bearded adult man in a white baseball cap \textbf{drives} with a calm, focused expression, while a passenger sits beside him in \textbf{shadow}.
From behind, the same pickup continues down the residential street, where a yellow school bus is parked off to the left and houses sit back among the \textbf{trees}.
A black Chevrolet \textbf{truck} travels along a \textbf{rural} road towing a large trailer, with \textbf{dry} \textbf{grass} and \textbf{trees} blurring \textbf{past} in the background.
Inside another \textbf{vehicle}, a blonde adult woman wearing a wide white cowboy hat and a \textbf{dusty} rose button-up shirt \textbf{drives} with her seat \textbf{belt} on.
Sunlight falls across her face as she looks ahead with a slight smile.
The black \textbf{truck} arrives on a \textbf{dusty} gravel area surrounded by pine \textbf{trees} and rustic buildings.
A small tower-like structure stands to the left, a low wooden building to the right, and utility trailers are parked nearby.
Dust rises behind the \textbf{vehicle} as people walk across the \textbf{grounds}.
Inside the back seat, several adult men laugh and settle in.
A bald Black man in a white shirt sits on the left with a seat \textbf{belt} across his chest ; beside him, a light-skinned man in a beige hoodie holds a drink or small item and smiles ; another man climbs in through the open door.
Through the windshield, the driver and passengers are visible together in the front and rear rows, suggesting a group heading out as a team.
Under a covered walkway in warm low sunlight, several people with backpacks move quickly away from the curb, as if arriving somewhere and \textbf{hurrying} inside.
A woman driver, seen from inside her \textbf{vehicle}, holds the \textbf{steering} wheel and looks out with a gentle smile.
She wears a dark T-shirt, and the \textbf{vehicle} ’s dashboard screen and \textbf{steering} wheel are visible beside her.
A red Chevrolet pickup then \textbf{drives} through a city setting, its headlights bright against tall downtown buildings.
The \textbf{truck} \textbf{passes} close by, showing its red body and modern front lighting.
At \textbf{night}, a rodeo arena appears : a rider in a cowboy hat races a dark horse around a barrel, kicking up dust, while spectators sit behind a \textbf{rail} \textbf{fence} under arena lights.
In daylight again, people work around a large fallen \textbf{tree} or thick \textbf{branches}.
A man in a backward white cap and dark shirt leans over the \textbf{rough} bark, helping move debris ; another person is partly visible to the left.
Moments later, he clasps hands with a bald man in a friendly, firm grip, both leaning toward each other as if celebrating the work or helping each other up.
A forest \textbf{trail} follows, with \textbf{mountain} bikers riding through dappled sunlight between tall \textbf{trees}.
One rider in a light top \textbf{passes} closest, followed by another farther back on the dirt \textbf{path}.
Small fine print appears near the bottom during the action, indicating a professional-driver or closed-course disclaimer.
A Chevrolet pickup then powers through dust off-road, seen close on its front corner with the bowtie \textbf{badge}, headlight, and vertical running light visible.
Inside, a man in a dark baseball cap laughs broadly while driving, one hand on the wheel.
The rear of a blue Chevrolet Silverado fills the view as it \textbf{drives} along a sunny \textbf{two-lane} road.
The tailgate shows the Chevrolet bowtie in the center, Silverado badging on the left, and “ 4x4 ” on the right ; a Texas license plate is visible below.
The \textbf{truck} continues away down the \textbf{highway} between \textbf{dry} roadside \textbf{brush} and open \textbf{sky}.
The final section becomes a clean promotional layout.
On the right, a silver 2026 Chevrolet Silverado \textbf{drives} along a road bordered by \textbf{snow} or pale \textbf{winter} fields under a gray \textbf{sky}.
On the left, a dark vertical panel contains large white offer text.
The most prominent words read “ START THE \textbf{YEAR} IN \textbf{DRIVE}, ” followed by “ 2026 CHEVY SILVERADO 1500 \textbf{CREW} CAB WITH TURBOMAX ENGINE OR SELECT 2026 SILVERADO 1500 \textbf{CREW} CAB MODELS, ” “ 1.9 \% APR, ” and “ \$6,144 TOTAL VALUE, ” with additional fine print below.
At the bottom right, the gold Chevrolet bowtie appears beside the word “ CHEVROLET. ”

% matched lemmas: badge, belt, branch, broad, brush, crew, drive, dry, dusty, emblem, fence, grass, ground, highway, hurry, mountain, night, pass, past, path, rail, roll, rough, rural, shadow, sky, snow, steering, trail, tree, truck, two-lane, vehicle, winter, year
\end{textsample}
