\begin{textsample}{POS Dim 2 – 1980 – Score 19.00 – 1980/tv\_com\_1980\_43.txt}  \label{ex:f2_pos_063}
A red Toyota Celica \textbf{drives} on a \textbf{sunlit} race track in an open, \textbf{dry} landscape.
White on-screen text at the bottom reads “ WILLOW SPRINGS RACE TRACK. ” The car is first seen head-on, low and wide, with a dark grille, black bumper trim, and a sloping windshield.
It approaches a pit area bordered by a black-and-white checkered wall.
Behind the wall stands a large racing transporter with red, orange, and yellow striping and large lettering that reads “ ALL AMERICAN RACERS PIT \textbf{CREW}. ” Several pit \textbf{crew} members, mostly men in white short-sleeved shirts, dark trousers, and some red caps, lean over the wall and watch the Celica come in.
The red Celica \textbf{rolls} alongside the pit \textbf{crew} and stops in front of the transporter, shown in profile as a compact \textbf{sporty} fastback with silver alloy wheels, black side trim, and a rear hatch.
The \textbf{crew} immediately springs into action.
Men in white shirts \textbf{rush} around the front of the car with tools and equipment.
One carries a red jack stand ; another moves a wooden-handled floor jack.
The checkered pit wall and the “ All American Racers Pit Crew ” lettering fill the background, giving the scene the look of a professional race stop.
A red fire extinguisher and hoses sit near the wall.
Under the car, a low view shows the floor jack being \textbf{rolled} into place on its small wheels beneath the chassis.
The Celica is lifted, and a front wheel is removed.
A close look at the exposed brake assembly shows a shiny ventilated disc with slots and a large caliper beside it, the wheel studs protruding from the hub.
In the background, a \textbf{crew} member crouches by another wheel while jack stands support the car.
The emphasis is on the mechanical parts being inspected in the pit.
The Celica then appears back out on the track from the rear.
Its hatchback tail, rectangular red taillights, and black center panel are visible, with “ TOYOTA ” on the license-plate area, “ GT-S ” on one side, and “ TOYOTA CELICA ” badging on the other.
Sun flare glints around the back of the car as it \textbf{drives} along the straightaway.
Another \textbf{underside} view shows a \textbf{crew} member ’s hands near suspension or drivetrain components, inspecting parts beneath the raised car.
The car continues through the open race \textbf{course}, seen from behind as it leans slightly over a rolling section of \textbf{pavement}, with brown hills and desert terrain stretching around the track.
In the pit, a \textbf{crew} member in a white shirt holds and examines a small engine-related part near the open hood.
The hood is raised, and the engine bay is shown clearly : black hoses and wiring, metallic covers, a white fluid reservoir, and other engine components arranged tightly under the windshield cowl.
A hand points into the bay as if checking or demonstrating the engine layout.
The Celica is then shown moving again in a low side view, emphasizing the front wheel spinning and the red front fender, headlamp, black bumper, and long sloped hood.
The car ’s red body and black trim stand out against the pale \textbf{sky} and track surface.
It speeds away across the wide \textbf{pavement}, becoming smaller against the flat, \textbf{sunlit} landscape and low hills.
Back in the pit, the red Celica is raised again while a \textbf{crew} member crouches at the rear wheel area, working close to the tire.
Tools and hoses lie on the \textbf{ground}, and jack stands are visible under the car.
Another hand presses down on or wipes across the red hood near the headlamp, with the pit \textbf{crew} trailer in the background.
Inside the Celica, the focus shifts to the driver and interior.
The driver is a middle-aged white man in a white racing suit with Toyota patches, orange racing gloves, and a black helmet ; “ GURNEY ” is visible on the helmet in later views, matching the transcript ’s identification of Dan Gurney.
He reclines deeply in the gray, ribbed seat with a seat \textbf{belt} crossing his chest.
His head is tipped back, his mouth open, and he appears extremely relaxed, almost as if dozing.
A \textbf{crew} member ’s hand at the left wipes or pats the gray upholstery with a white cloth, as though inspecting the interior comfort.
Outside the open window, pit \textbf{crew} members stand by the checkered wall.
Several \textbf{crew} members lean into the open side window, peering at the relaxed driver with curious, surprised expressions.
One man rests his hand on the window edge ; others bend forward to look inside.
The driver stirs, lifts an orange-gloved hand, and sits up toward the \textbf{steering} wheel.
His expression becomes alert and amused as he turns toward the \textbf{crew}.
The men outside react with open mouths and animated faces, as if impressed or startled by what he says or does.
The Celica ’s wheels spin again as it pulls away from the pit area, the red side panels sweeping \textbf{past} close to the \textbf{ground}.
The car \textbf{passes} in front of the “ All American Racers Pit Crew ” trailer while the \textbf{crew} members step back and watch it go.
Inside the moving car, the driver is shown from the chest up, still wearing the black helmet and white Toyota racing suit, seat-belted and holding the wheel.
He looks toward the viewer and speaks with a slight smile, the pale \textbf{sky} visible through the side window behind him.
The final scene returns to the pit area.
The red Toyota Celica is parked at an angle in front of the large “ ALL AMERICAN RACERS PIT \textbf{CREW} ” trailer and checkered wall.
The driver stands to the left of the car in his white racing suit and black helmet, leaning casually with one leg crossed, while the pit \textbf{crew} \textbf{gathers} around the car.
Several \textbf{crew} members raise their arms and caps in celebration.
Large white text appears across the bottom reading “ TOYOTA, ” with the red Celica centered above it as the \textbf{crew} continues cheering around the \textbf{vehicle}.

% matched lemmas: belt, course, crew, drive, dry, gather, ground, pass, past, pavement, roll, rush, sky, sporty, steering, sunlit, underside, vehicle
\end{textsample}
