\begin{textsample}{POS Dim 2 – 2010 – Score 15.00 – 2010/tv\_com\_2010\_17.txt}  \label{ex:f2_pos_053}
Two hooded figures stand close together in a dim, worn-looking interior, facing a bright window.
One wears a deep red hooded sweatshirt, the other a pale gray or white hood under a black jacket.
The room has patterned wallpaper and an old, urban-apartment feel.
Bright daylight pours in from outside, briefly flaring across the scene.
The figure in the red sweatshirt turns out to be an oversized, humanlike hamster.
With pale paws, it pulls the red hood down and reveals a large tan hamster head with rounded ears, glossy dark eyes, whiskers, and a small pink nose.
The sweatshirt has bold white script across the chest reading “ Hamstar, ” and the hamster wears thick gold chains.
Behind it, another hamster wears a white hoodie under a black leather jacket, with the hood and a black cap partly shading its face.
Outside, a group of similarly human-sized hamsters \textbf{gathers} on a city sidewalk in front of an older brick apartment building.
They are dressed in urban streetwear : the red “ Hamstar ” hoodie, the white hoodie with black leather jacket and yellow shoes, a green tracksuit with white stripes and large round headphones around the neck, and other oversized hoodies and jackets.
A large old-style boombox sits on a \textbf{stone} post near the entrance.
The hamsters stand on the stoop and curb, gesturing and moving as if dancing or greeting each other.
The city setting is dense and slightly gritty, with brick façades, metal railings, and narrow sidewalks.
A city skyline appears, with tall buildings in the distance and a sign on a nearby structure reading “ H\&H. ” The urban theme continues with a street sign high between tall buildings : one sign reads “ HAMSTERDAM AV, ” and below it a “ ONE WAY ” sign points to the right.
Back at street level, one hamster in the green tracksuit embraces the hamster in the white hoodie and black leather jacket beside a brick wall.
The green-suited hamster ’s round headphones hang prominently at the chest.
Soon the lime-green Kia Soul appears parked at the curb in front of the apartment buildings.
Its boxy shape, rounded front, Kia \textbf{badge}, and shiny wheels are visible.
Several hamsters dance and pose around it, with the red-hoodie hamster near the front passenger side and the white-hoodie hamster moving by the driver ’s side.
Small legal text appears along the bottom of the image while the \textbf{vehicle} is displayed.
The commercial starts visually comparing the Kia with absurd hamster-sized alternatives.
A giant silver toaster, about the size of a small \textbf{vehicle}, \textbf{rolls} down the street with two hamsters sitting on top of it.
Its black lever and slots are visible, making it unmistakably a toaster.
In the foreground, the white-hoodie hamster in the black leather jacket gestures toward it, then points emphatically, as if dismissing that option.
The same hamster then stands beside the Kia ’s front grille and \textbf{badge}, dancing with both paws raised, drawing attention back to the real car.
The toaster continues down the street \textbf{past} brownstone-style buildings and a red fire hydrant, while other hamsters stand on sidewalks watching.
The toaster glides like a \textbf{vehicle}, with its polished metal sides reflecting light.
In another city lot, the red “ Hamstar ” hamster stands beside the boombox, while the green Kia Soul sits behind.
The white-hoodie hamster dances on a piece of flattened cardboard on the \textbf{ground}, using it like a dance mat.
A drummer hamster appears outside a theater entrance, wearing an olive-green parka, a dark knit cap, and a chain necklace.
It sits at a drum kit and raises drumsticks over a snare and cymbal.
Behind it, a theater marquee with rows of lights includes readable text such as “ Moochie Mania.com presents ” and “ Moochie \& the Woodchucks, ” with a “ Sat 8pm ” listing beneath.
Other hamsters move in the background near the theater.
The Kia Soul is then shown driving through a city street from behind and alongside, its lime-green paint standing out against beige and gray buildings.
The rear Kia \textbf{badge}, vertical taillights, roof \textbf{rails}, and square hatchback shape are clear.
Inside the car, three hamsters ride in the front and back seats.
The red “ Hamstar ” hamster \textbf{drives} with both paws on the \textbf{steering} wheel, looking forward.
The white-hoodie hamster sits in the front passenger seat wearing a seatbelt, and the green tracksuit hamster sits in the back.
Through the rear window, the giant toaster can be seen following along the road in the distance.
As the Kia \textbf{drives} \textbf{past}, another oversized hamster alternative appears : a huge metal exercise wheel on a stand, like the kind used in small animal cages.
A hamster runs inside the wheel on the sidewalk while the Kia \textbf{passes} smoothly beside it.
Other hamsters stand along the street watching.
The contrast is visual and comic : the real compact crossover cruises down the road while the hamster wheel and toaster look awkward and impractical.
At a car wash, the white-hoodie hamster leans casually against the front corner of the green Kia, one paw resting near the headlight.
A sign above the building reads “ CAR WASH ” with a star graphic.
The hamster gestures outward, and the view shifts across the car wash area to another makeshift transportation option : several hamsters are inside a large cardboard box shaped like a car.
The box has cut-out windows, drawn-on circular headlights, a red arrow, and pink flame graphics along the side.
Their furry legs stick out underneath as they shuffle the cardboard “ car ” forward by foot.
Two hamsters in red clothing stand near the car wash building watching.
Inside the Kia, the dashboard and center console are shown.
The audio controls and climate dials fill the center, and a small red display glows on the stereo.
A hamster paw holds a smartphone or music player near the passenger side ; the screen shows album art and text, though the details are small.
Fine print appears along the bottom while this device and the car ’s interior controls are shown.
The cardboard box car later travels down a city street behind or near other odd appliances, including a large washing machine-like \textbf{vehicle}.
The cardboard car wobbles badly, tips onto one side, and collapses into a crumpled heap on the \textbf{pavement}.
Hamsters inside are partially visible through the cut-out openings as the box folds down.
A subway entrance sign nearby reads “ 45 Stree Station ” with additional text including “ Downtown to South Ferry. ” Other hamsters on the sidewalk look on.
Back at the car wash, two hamsters in pale pink skirts dance facing each other in front of the \textbf{red-and-white} building.
Elsewhere in a wide city lot, the green Kia Soul sits on the left while the white-hoodie hamster dances beside it.
On the right, the giant toaster stands with hamsters perched on top and a black electrical cord \textbf{trailing} along the \textbf{ground}, making it look even less like a practical \textbf{vehicle}.
The Kia continues \textbf{driving} through \textbf{sunlit} city streets.
The front grille, rounded headlights, lower black bumper, and spinning wheels are emphasized as it moves forward.
In the background, the toaster-like contraptions and other hamster figures blur \textbf{past} on the road and sidewalks, while the Kia remains the polished, functional \textbf{vehicle}.
From the side window, the white-hoodie hamster in the front passenger seat bobs and moves both paws as if dancing, still buckled in.
The red “ Hamstar ” hamster \textbf{drives} beside them, focused ahead, with the green exterior door frame visible at the edge.
The commercial ends on a clean white information screen.
On the left is the Kia oval logo above the words “ KIA MOTORS ” and the slogan “ The Power to Surprise. ” On the right, large text reads “ 2010 KIA SOUL. ” Beneath it, pricing information reads “ \$149 / Month, ” “ 36 Month Lease, ” “ \$2,299 Due at Signing, ” and “ SOUL + A/T. ” Near the lower left is a small award graphic with the quoted text “ TOP SAFETY PICK, ” followed by dense fine print across the bottom.

% matched lemmas: badge, drive, gather, ground, pass, past, pavement, rail, red-and-white, roll, steering, stone, sunlit, trail, vehicle
\end{textsample}
