\begin{textsample}{POS Dim 2 – 2010 – Score 15.00 – 2010/tv\_com\_2010\_98.txt}  \label{ex:f2_pos_055}
A \textbf{sunlit} roadside scene opens in a \textbf{dry}, hilly landscape.
A small metal vent or pipe with a dangling chain sticks up near the edge of a simple corrugated building, with pale blue \textbf{sky} and \textbf{dusty} hills beyond.
Beside the building, power lines stretch across the view and an orange, older-looking hatchback \textbf{drives} along a flat road in front of scrubby hills and patches of green \textbf{grass}.
A close view of the orange car ’s rear shows a cream bumper sticker reading “ PLANET HUGGER, ” with a small drawing of the Earth being hugged by hands ; just below it, a dark exhaust pipe protrudes from the bumper.
Inside the car, a light-skinned adult man with short brown hair, a moustache and beard, wearing a red-and-blue plaid shirt under a tan vest and a seatbelt, sits at the wheel with a calm, slightly serious expression.
A traffic signal is green.
From the side, he waits in the orange car, looking ahead, then reaches his right arm down toward the console or gear area as if preparing to \textbf{drive}.
On a \textbf{broad} suburban road with low \textbf{mountains} in the distance, his orange car is stopped beside a newer orange compact car with bright blue-accented headlights.
In the newer car, another light-skinned adult man with dark hair and a thick moustache sits behind the wheel wearing a burgundy top and a seatbelt, while a shaggy tan dog with a red collar sits upright in the front passenger seat.
The dog pants happily with its tongue out and looks toward the other driver ; the moustached driver glances over, then smiles.
The plaid-shirted driver in the older orange car returns the look with a faint, uncertain smile.
Seen through the windshield of the newer car, the dog sits alert on the left side of the view and the driver gestures with one hand near the \textbf{steering} wheel, as though casually acknowledging the other car.
The dog ’s face fills the view for a moment, cheerful and relaxed, before the plaid-shirted driver turns his head to look out his side window with a more intent expression.
A close view of the newer orange car ’s rear quarter panel flashes by in warm sunlight, suggesting it is moving off quickly.
Back on the road, the newer orange car has pulled ahead while the older orange car remains behind.
The moustached driver in the newer car looks forward, composed, then briefly closes his eyes as if satisfied.
A woman with shoulder-length hair, wearing a teal blouse, dark pants, and ankle \textbf{boots}, stands in a parking lot beside a white electric car plugged into a tall charging station with green panels ; another identical charging station stands beside it.
The orange car \textbf{passes} along the road in the background while the charging cable \textbf{trails} from the station to the white car.
The scene broadens to a winding \textbf{two-lane} road through green fields and low hills, with \textbf{mountains} and a distant cluster of white buildings or towers on the horizon.
The orange car travels ahead along the road, and more cars join the traffic behind and beside it : a black \textbf{vehicle}, then a dark blue one, a white car, and another \textbf{reddish} \textbf{vehicle}, all moving through the sunny landscape.
The first part ends on this image of multiple cars sharing the open road.
The screen then becomes plain white, and a new indoor setting appears : a dim, upscale restaurant with a round white table crowded with small plates, desserts, coffee cups, water glasses, wine glasses, and orange-colored drinks.
From behind, a light-skinned adult man with reddish-brown hair and a full beard, wearing a salmon-pink short-sleeve button-up shirt, sits at the table among friends.
A server in a white sleeve reaches in and places a bill folder or tray near him.
He looks down and smiles awkwardly, then tilts his head with a bashful expression.
Across the table, a bald Black adult man in a black polo shirt smiles and extends a dark blue credit card toward the center of the table.
A close view shows the card in detail : it is dark blue with a silver chip, the word “ REWARDS ” on the right, and the name “ BRAD KAYAL ” printed near the lower left.
The card is set down onto a black bill folder over a receipt.
The red-bearded man ’s eyes are shown very close, narrowed and focused, as if he is thinking hard about the card.
Around the table, the bald man gestures animatedly with both hands while speaking ; beside him, a light-skinned man in glasses and a dark jacket leans in, smiling and looking down toward the table.
The bald man then holds up a smartphone toward the group.
On the phone screen, the green “ nerdwallet ” logo is clearly visible above the words “ BEST REWARDS CARDS, ” with an image of the same style of blue rewards card, a five-star rating, and a green “ APPLY NOW ” button.
The red-bearded man stares ahead wide-eyed, surprised or caught off guard, while another hand holding the phone is partly visible in the foreground.
A wider view of the table shows him seated next to a light-skinned woman with dark hair wearing a striped sweater ; she looks toward the conversation while the others sit around the table with the phone and bill folder between them.
The commercial ends on clean graphic imagery : a green credit card floats against a pale mint background with small green shapes moving around it, then the card appears centered on a white background with simple radiating line accents.
Tiny grey legal text sits along the bottom, too small to read clearly.
A solid green rectangular button-like shape appears underneath the card, completing the final branded credit-card visual.

% matched lemmas: boot, broad, drive, dry, dusty, grass, mountain, pass, reddish, sky, steering, sunlit, trail, two-lane, vehicle
\end{textsample}
