\begin{textsample}{POS Dim 2 – 2020 – Score 13.00 – 2020/tv\_com\_2020\_1.txt}  \label{ex:f2_pos_014}
The commercial begins on a black frame, then cuts to a close-up of a white-and-blue \textbf{flag} waving against a bright blue sky.
The \textbf{flag} carries a stylized wordmark that appears to read something like “ SABITZ, ” though the folds make the lettering partly unclear.
It then cuts to a sunny beach scene.
A shirtless young man with curly dark hair stands in shallow water or at the shoreline, wearing red-and-white vertically striped swim trunks.
His skin appears noticeably sunburned.
Behind him are a sandy beach, rows of blue umbrellas, palm trees, and a tall white lighthouse.
Next, the setting shifts to a tree-lined path or resort road.
A woman in bright pink/red clothing \textbf{sits} in a small open vehicle or cart, facing forward.
Other people stand in the background.
A green roadside sign with white writing is visible, but the text is too small/unclear to read.
The commercial then cuts indoors to a rustic, wood-paneled \textbf{room} with ski equipment.
Several people are present ; two people in the foreground wear winter/ski clothing and stand near skis and gear.
Large windows show mountains or a snowy-looking outdoor landscape in the distance.
The scene changes to a bright \textbf{modern} resort with a turquoise swimming pool, white balconies, palm trees, and lounge chairs.
A shirtless middle-aged man in patterned swim shorts stands on an upper walkway or balcony, looking outward with his hands on his hips.
A closer shot follows, showing his shorts and legs near a glass railing, then another closer shot of his upper body and face on the same balcony.
The commercial cuts to a bedroom.
A young man and a woman lie side by side under bedding in a large tufted bed.
They look toward each other in the overhead shot.
A wider view follows from the doorway, showing the bed centered between bedside lamps, with curtains and a small table or tray area to one side.
Next, two people are shown relaxing separately in square \textbf{wooden} hot-tub-like tubs on an outdoor terrace overlooking the ocean.
Only their heads and upper shoulders are visible above the tub edges.
Large potted \textbf{plants} frame the scene.
The setting then moves to a poolside area.
An older woman reclines on a turquoise-striped chaise lounge beside a large pool.
She wears oversized white sunglasses, a head covering, earrings, and a light-colored cover-up.
A person in white clothing walks in the background near the pool.
A closer shot shows the woman smiling and turning slightly while seated on the lounge.
The commercial cuts back briefly to the wood-paneled ski \textbf{room}.
The two people in ski clothing stand in front of racks of skis and look forward.
It then returns to the beach.
The sunburned young man is shown in close-up, lifting or adjusting green-tinted sunglasses on his face.
The lighthouse and blue beach umbrellas are visible behind him.
Another close-up returns to the older woman at the poolside lounge.
She is shown in profile/three-quarter view, still wearing the white sunglasses, with the pool and a person in white in the background.
The final sequence takes place on a golf course with \textbf{many} palm trees, bright green grass, sand traps, and a golf cart.
A wide shot shows two golfers on the course.
A closer shot shows a man wearing a light-colored patterned \textbf{sweater} vest, cap, and blue trousers holding a \textbf{smartphone} up in one hand, with another golfer behind him.
A close-up of the \textbf{smartphone} \textbf{screen} follows.
The \textbf{phone} displays a travel-booking-style \textbf{interface} with a dark \textbf{header} that appears to say “ ORBITZ ” or a similar wordmark.
Below it are rows of listings with small thumbnail images and prices or text, though most details are too small to read.
A finger interacts with the \textbf{screen}.
The golfer is then shown near a flagstick on the green.
A blue-and-white \textbf{flag} with the same stylized logo/wordmark waves in the wind.
The man stands beside it, and the golf course with palm trees stretches behind him.
The final shot returns to a close-up of the waving blue-and-white branded \textbf{flag} against the sky, with the lettering again partly obscured by motion and folds.

% matched lemmas: flag, header, interface, many, modern, phone, plant, room, screen, sit, smartphone, sweater, wooden
\end{textsample}
