\begin{textsample}{POS Dim 2 – 1960 – Score 22.00 – 1960/tv\_com\_1960\_109.txt}  \label{ex:f2_pos_006}
The commercial opens in black and white with a close view of a large parrot or macaw nestled among dense tropical \textbf{leaves}.
Its curved beak, pale facial markings, and long body are partly \textbf{hidden} by glossy foliage.
The bird turns and shifts slightly as leaves fill the foreground, creating the feeling of a thick jungle.
A small open jeep appears on a narrow \textbf{path} through the same \textbf{heavy} vegetation.
Four adult men in safari-style clothing ride in it.
They wear light pith helmets, short-sleeved shirts, shorts, \textbf{belts}, and high socks or \textbf{boots}.
The jeep is light-coloured, with a flat hood, round headlights, an upright windshield, and a vertical slatted front grille.
It moves slowly along the jungle track while \textbf{leaves} and \textbf{branches} crowd in from both sides.
The men sit close together, looking around and leaning forward as if watching the \textbf{path}.
A closer view shows two mustached men in the front seats.
The driver, wearing a pith helmet and safari shirt, holds the \textbf{steering} wheel and looks uneasy or impatient.
Another man sits beside or just behind him, also mustached, peering around with widened eyes.
The driver props his cheek on his hand, then glances from side to side.
The man behind him looks off to the left, then begins to move out of the jeep.
The driver turns his head sharply, then folds his arms over the wheel as if resigned or exasperated.
The group then leaves the \textbf{vehicle} on the jungle road.
The jeep remains in the middle of the \textbf{path} while the men walk around it.
One man stays near the \textbf{steering} wheel, while others take positions around the front and sides.
They begin moving the jeep by hand, lifting and guiding it rather than simply \textbf{driving}.
The front of the \textbf{vehicle} rises slightly as the men, still dressed like explorers, trudge forward through the uneven \textbf{ground}.
Their arms swing with effort, and one man in front walks ahead as if leading the way.
The jungle opens into a \textbf{broader} \textbf{outdoor} landscape with \textbf{mountains} in the distance and water or marshland in the foreground.
The jeep is now near the edge of the water.
The men stand around it with expedition gear : one holds a long pole or rifle-like object, another raises binoculars or a spyglass to his eyes, and others climb onto or stand beside the jeep.
They scan the horizon and prepare to continue.
The scene looks staged like an exaggerated expedition, with leafy \textbf{branches} framing the top and sides.
The journey continues across water.
The jeep sits on a makeshift raft or low floating platform surrounded by rippling water.
One explorer at the front bends down and \textbf{pushes} with a long pole.
Another stands tall near the middle, holding a long telescope or spyglass to his eye and looking outward.
A man at the back holds an oar, and another sits in the jeep area.
As they float, the men shift positions and wave hats or paddles, still wearing their pith helmets and safari outfits.
The setting changes to rolling sand dunes under a wide \textbf{sky}.
The same open jeep is being carried or \textbf{pushed} across the sand by the explorers.
Two men move in front and others follow behind, all trudging over the dunes while the jeep sits raised between them.
The image emphasizes the absurd effort of transporting the \textbf{vehicle} through harsh terrain.
The expedition then reappears in an ordinary suburban neighbourhood.
The safari-dressed men are still moving the jeep by hand along a \textbf{paved} street. \textbf{Bushes}, sidewalks, lawns, a white picket \textbf{fence}, and parked mid-century cars line the road.
The jeep ’s windshield is upright, and one man \textbf{pushes} from behind while two others walk in front or alongside it.
The contrast is comic : they look like explorers marching through a quiet residential area.
Ahead, an American service station comes into view.
The men guide the jeep toward the pumps.
The station has a large building with bold block letters spelling “ AMERICAN ” across the front, and another sign over a service area reads “ ATLAS. ” Tall modern light poles stand over the forecourt, and several gas pumps are arranged near the curb.
Parked cars sit near the station building.
The explorers \textbf{gather} around the jeep in front of the pumps, having apparently gone through jungle, water, desert, and suburb to arrive there.
A close view of a gas pump shows the product clearly.
The pump carries the “ AMERICAN ” name at the top, with “ AMOCO ” visible on the front.
A large sign on the lower panel reads, “ The only one!
CERTIFIED LEAD-FREE. ” Fuel hoses hang from the side of the pump.
In the closing images, the parrot or macaw returns, now perched high on the curved top of a large roadside American Oil Company sign.
The sign is an oval \textbf{emblem} with a stylized flame or torch at the top and the word “ AMERICAN ” in large capital letters across the middle.
The bird flutters its wings, sidesteps along the top edge, and settles near the flame \textbf{emblem}.
The sign is shown from different angles as it stands above \textbf{trees} against the \textbf{sky}.
At the end, small on-screen text beneath the sign reads “ AMERICAN OIL COMPANY. ”

% matched lemmas: belt, boot, branch, broad, bush, drive, emblem, fence, gather, ground, heavy, hide, leaf, mountain, outdoor, path, paved, push, sky, steering, tree, vehicle
\end{textsample}
