\begin{textsample}{POS Dim 2 – 1960 – Score 18.00 – 1960/tv\_com\_1960\_114.txt}  \label{ex:f2_pos_010}
A light-colored 1960s \textbf{sedan} sits in deep \textbf{snow} on a bright, open hillside, with small evergreen \textbf{trees} scattered around it.
Snow covers the \textbf{ground} and lies along the car ’s windows and roofline.
Inside, a blonde woman, dressed for \textbf{winter} in a textured coat, dark gloves, and a head covering or hood, sits at the \textbf{steering} wheel.
She faces forward, then glances upward and ahead with a worried, attentive expression as she works the controls.
In the back seat, two young children \textbf{bundled} in \textbf{winter} hats and coats lean toward the side window.
Snow is piled along the outside window ledge, and the children smile and appear to play or look out through the glass, more amused than alarmed.
A close view of one of the car ’s wheels shows the tire sunk into soft \textbf{snow}.
The wheel turns but remains buried, churning in place. \textbf{Snow} bunches up around the tire and fills the wheel well, making the car look trapped.
The children are shown again at the \textbf{snowy} window, smiling, while the woman is visible behind them in the front seat.
Outside, a tow \textbf{truck} stands behind the \textbf{sedan} on the \textbf{snowy} incline, with a worker near it, suggesting the car has been deliberately stuck or positioned for a demonstration.
The focus shifts to a tire being installed.
A person in a light work jacket and dark gloves crouches beside the car, holding a new tire with a bold, \textbf{heavy} tread pattern.
The tire has wide, deep cleats around its surface and a \textbf{whitewall} sidewall near the rim.
The worker aligns it against the car ’s wheel hub and presses it into place.
The cleated tread is shown prominently as the hands adjust the tire under the fender, emphasizing its rugged, chunky design.
With the new tire on the car, the wheel sits again in deep \textbf{snow}.
At first it is half-buried, surrounded by loose \textbf{snow}.
Then the tire begins to turn.
Instead of simply spinning in place, it bites into the packed ruts. \textbf{Snow} sprays and crumbles behind and beneath it as the wheel gains purchase.
The car starts moving forward through the same \textbf{snowy} \textbf{path}, leaving churned tracks behind.
From above, the \textbf{sedan} pulls away from the tow \textbf{truck} and travels along the rutted \textbf{snow} lane, \textbf{passing} between low shrubs and small evergreens.
The tow \textbf{truck} remains behind while the car continues on under its own power.
Several close views then demonstrate the tire ’s action in \textbf{snow}.
The tire \textbf{rolls} through soft drifts, its \textbf{whitewall} rim bright against the dark rubber and the pale \textbf{snow}.
As the tread digs down, \textbf{snow} is \textbf{pushed} aside in ridges and \textbf{thrown} out from under the wheel.
Bold black on-screen words appear over the \textbf{snow} : “ DEEP CLEATED, ” followed by “ SURE FOOTED. ” A separate graphic-like view shows a dark tire track pattern pressed into a pale surface, with repeating zigzag and block-shaped marks.
The words “ BITING ACTION ” appear beneath the tread pattern.
The tire is then shown \textbf{rolling} again through \textbf{snow}, and the words “ SELF-CLEANING TREADS ” appear along the lower part of the image as \textbf{snow} is flung away from the grooves rather than packing into them.
The \textbf{sedan} now \textbf{drives} steadily along the crest of a \textbf{snowy} rise against a plain \textbf{winter} \textbf{sky}.
The car moves across the top of the snowbank with the driver visible through the side window, and the two children can be glimpsed inside.
Small snow-covered evergreens \textbf{pass} in the foreground as the car continues smoothly over uneven, piled \textbf{snow}.
The wheels remain partly hidden by drifts, but the car keeps moving without stopping, crossing the \textbf{snowy} landscape from one side of the scene to the other until it disappears beyond the edge of the snowbank.
The commercial ends on a large Gulf sign mounted on a pole against a simple \textbf{sky} background.
The round sign has a thick circular border and a horizontal band across the middle with the word “ Gulf ” in large dark letters.
The sign turns slowly, briefly showing its narrow side and then rotating back so the Gulf name faces forward again.

% matched lemmas: bundle, drive, ground, heavy, pass, path, push, roll, sedan, sky, snow, snowy, steering, throw, tree, truck, whitewall, winter
\end{textsample}
