\begin{textsample}{POS Dim 2 – 1960 – Score 15.00 – 1960/tv\_com\_1960\_110.txt}  \label{ex:f2_pos_016}
A dark, misty nighttime scene begins with a bright, \textbf{hazy} light in \textbf{heavy} \textbf{glare}.
As the image clears, the side of a car appears low to the \textbf{ground} on a wet, \textbf{rough} roadside.
One wheel is visibly flat, the tire collapsed and spread against the \textbf{pavement} under the wheel well.
Water and gravel glisten around it.
A hand holding a small flashlight moves close to the tire and hubcap, sweeping the light across the flattened rubber and the puddled \textbf{ground}, emphasizing that the car is stranded.
A young adult woman with light hair, wearing a light-colored coat or dress and heels, stands near the car in the darkness.
The car ’s lights flare behind her through mist or road spray.
Large white block letters appear on the left : “ WHEN THERE ’S NO MAN AROUND. ” The woman looks small against the dark roadside and the bright headlights, holding a handbag as she moves away from the car across the wet, uneven \textbf{ground}.
Her legs and \textbf{shadow} are shown against the shiny \textbf{pavement}, then she is seen in \textbf{silhouette} approaching a large dark telephone booth or public phone structure.
Inside the lit phone booth, the woman holds a telephone receiver close to her face.
Her short, light hair is rimmed by the booth ’s light, and her expression appears tense or worried as she speaks into the phone.
The rotary telephone is shown close up, with the circular dial and letter-number groupings around it.
A hand lifts the receiver from its cradle.
The woman ’s face is then shown beside the receiver, partly reflected in the booth glass.
The phrase “ WHEN THERE ’S NO MAN AROUND ” appears again in bold white letters beside her.
As the view widens, the word “ TELEPHONE ” is visible above the booth, and she remains inside, framed by the booth windows, still using the phone.
The image of the phone booth becomes surrounded by concentric circular shapes, visually turning the booth into the center of a car wheel.
The scene resolves into a close view of a car ’s \textbf{whitewall} tire and shiny hubcap.
Bold white text appears below the wheel : “ GOODYEAR SHOULD BE. ” The wheel is shown in motion, \textbf{rolling} along a wet road surface.
The tire demonstration follows in close detail.
The words “ GOODYEAR DOUBLE EAGLE ” appear over a tire pressing down near jagged debris on the \textbf{ground}.
The debris looks like sharp broken pieces, possibly glass or metal, lying on wet gravel.
The tire is shown large and \textbf{heavy}, its tread and sidewall filling the image as it \textbf{passes} over or near the sharp pieces.
More bold text appears : “ CARRIES ITS OWN \textbf{SPARE} INSIDE. ” A cutaway-style view of the tire reveals an inner tire-like structure inside the outer tire.
The words “ LIFEGUARD SAFETY \textbf{SPARE} ” appear across the tire, followed by “ A TIRE IN A TIRE, ” making the internal \textbf{spare} visually explicit.
The tire \textbf{rolls} over the jagged objects, the outer tire moving while the inner structure remains visibly part of the design.
The woman is then seen inside a car at \textbf{night}, no longer stranded.
Her face is softly lit from the side, with blurred city or road lights outside the window behind her.
She looks calm and relieved, then smiles.
Outside, a light-colored car \textbf{drives} along a dark road, its body and \textbf{whitewall} tires visible as it \textbf{passes}.
The road is lit by headlights and scattered points of light in the distance.
Large, elegant white letters appear over the nighttime road : first “ GO, ” then “ GO GO, ” and then the “ GOODYEAR ” name with the winged-foot logo.
The car continues along the road.
The words “ NEW DOUBLE EAGLE ” appear in bold block letters while the \textbf{underside} and front wheel area of the moving car are shown.
A close view of a tire tread follows, centered vertically, with the tread pattern running toward the viewer.
The final product image shows the tire upright with the Goodyear logo at the top and the words “ WITH LIFEGUARD SAFETY \textbf{SPARE} ” printed boldly across the lower part, presenting the Double Eagle tire and its built-in safety \textbf{spare} as the closing visual.

% matched lemmas: drive, glare, ground, hazy, heavy, night, pass, pavement, roll, rough, shadow, silhouette, spare, underside, whitewall
\end{textsample}
