\begin{textsample}{POS Dim 2 – 1990 – Score 20.00 – 1990/tv\_com\_1990\_81.txt}  \label{ex:f2_pos_035}
The commercial opens with the whole screen filled by warm orange and brown streaks, soft and indistinct, like sunlight stretched across a surface in motion.
No clear objects are visible at first ; the image is abstract, with vertical bands of amber, rust, and \textbf{shadow} shifting gradually.
The colours deepen and lighten in waves until the texture begins to feel less like a flat surface and more like motion through a \textbf{sunlit} landscape.
The scene resolves into a low, close view of a road.
A champagne-silver \textbf{sedan} enters along the left side of the image, only its lower side and front wheel visible at first.
It \textbf{drives} along a narrow \textbf{paved} road through dense \textbf{trees}.
The late-day light is golden-orange, and the \textbf{tree} \textbf{branches} cast long, moving \textbf{shadows} across the \textbf{pavement}.
The car ’s paint reflects the warm surroundings, picking up copper and gold tones as it moves.
The view stays close to the left side of the \textbf{vehicle} : the rounded front fender, wheel, side mirror, and smooth door panels \textbf{pass} beside the road while the wooded lane stretches ahead, curving gently through the forest.
The road is empty, with tall \textbf{trunks} and leafy \textbf{branches} forming a tunnel of green and amber light.
The focus shifts inside the car.
The cabin is shown in a warm \textbf{reddish} glow, with beige leather upholstery in the foreground and a dark dashboard across the front.
The center console contains rows of buttons and controls for the audio and climate systems, with wood trim lower down.
The passenger-side glove compartment and rectangular air vents are visible, and the interior looks clean, uncluttered, and spacious.
The materials are smooth and softly lit, emphasizing leather, dark plastic, and polished wood accents.
A driver ’s hands appear on the \textbf{steering} wheel.
Only the hands and forearms are visible ; the person wears a patterned, textured knit sweater in dark purples and browns.
One hand grips the wheel near the upper left side, then both hands settle firmly on either side.
The \textbf{steering} wheel is dark leather with the Lexus “ L ” \textbf{emblem} embossed in the centre.
Behind it, analog gauges with white markings sit in a curved instrument cluster.
To the right, the dashboard controls remain visible, arranged in neat horizontal rows.
The driver ’s posture is implied by the steady hands, but the driver ’s face and body are not shown.
The interior view fades into a close exterior reflection on the car ’s glossy side.
Dark \textbf{silhouettes} of \textbf{tree} \textbf{branches} and a low orange \textbf{sun} ripple across the paint and window glass.
The black side mirror and chrome-like window trim frame the reflection.
As the view moves along the side of the \textbf{sedan}, the front door handle, rear door seam, rear door handle, and tinted side windows come into view.
The body colour appears champagne or light silver, but the sunset makes it glow orange.
The car ’s side panels are smooth and gently rounded, with a narrow protective strip running along the lower doors.
The \textbf{vehicle} is then seen from the rear three-quarter angle, \textbf{driving} away on the same quiet road.
Its red tail lamps stretch horizontally across the rear corners, and a Lexus \textbf{badge} is centered on the \textbf{trunk}.
The license plate is visible but not readable.
The \textbf{sedan} rides low and level, its rear window darkened, its wheels turning as it moves through the warm light.
Dust or road \textbf{haze} appears faintly near the tires. \textbf{Trees} and shrubs line the roadside, and the background remains natural and calm, with no pedestrians or other \textbf{vehicles} visible.
As the car continues away, the image \textbf{blends} into a new view of the road from ahead.
The \textbf{sedan} appears in the distance at the top of a slight rise, facing forward.
It crests the hill and comes toward the viewer, centered between low, \textbf{dry} golden embankments with dark evergreen \textbf{trees} behind them.
The front of the Lexus is now fully visible : a wide, smooth hood ; a small central Lexus \textbf{emblem} ; narrow, clear headlamp clusters on either side ; and a clean, understated front bumper.
The windshield appears dark, so no occupants are visible.
The car advances slowly toward the foreground, still bathed in sunset tones, presenting the Lexus ES 300 as a refined four-door \textbf{sedan} moving through a quiet, scenic road.

% matched lemmas: badge, blend, branch, drive, dry, emblem, haze, pass, paved, pavement, reddish, sedan, shadow, silhouette, steering, sun, sunlit, tree, trunk, vehicle
\end{textsample}
