\begin{textsample}{POS Dim 2 – 1960 – Score 12.00 – 1960/tv\_com\_1960\_17.txt}  \label{ex:f2_pos_020}
In black-and-white footage, an adult man with a masculine presentation runs along a narrow wooded \textbf{path}.
He wears light-colored exercise clothes, including a short-sleeved top and long pants, and his arms pump steadily at his sides.
The \textbf{path} curves through dense \textbf{trees} and \textbf{brush}, with \textbf{branches} arching overhead like a tunnel.
Bright daylight filters through the \textbf{leaves}, creating a high-contrast scene where the runner is often partly \textbf{silhouetted} against the pale \textbf{sky}.
He continues running toward the viewer through the forest, keeping a steady \textbf{pace}.
As he moves, the background remains filled with tall \textbf{trunks}, tangled \textbf{branches}, and patches of \textbf{sunlit} foliage.
His face is difficult to see in the front-facing views because of the strong backlight, but his posture is upright and purposeful, with his head slightly raised as he runs.
The view shifts to his side as he runs from left to right through the same wooded setting.
His short dark hair and side profile become clearer.
He appears focused and active, breathing through the exertion of the run, with one arm bent forward and the other swinging back.
Over the lower center of the image, large white capital letters appear : “ VIGRAN. ” Beneath it, in smaller white capitals, the text reads “ SQUIBB VITAMINS. ” The runner remains visible behind and above the words as he keeps moving through the \textbf{trees}.
The product name stays on screen while the man continues jogging in profile.
At moments, a bright jagged white line appears across the lower part of the picture, running horizontally near the “ VIGRAN ” text, like a simplified energy or pulse line.
The forest background blurs with his motion, while the bold product lettering remains steady and prominent in the foreground.
The image returns to a darker, front-facing \textbf{silhouette} of the runner among the \textbf{trees}, still with “ VIGRAN ” and “ SQUIBB VITAMINS ” centered near the bottom.
Sunlight flares through the \textbf{branches} to one side, making the runner ’s body mostly a dark outline.
He keeps running without stopping, shoulders rising and falling and arms continuing their rhythm.
Near the end, the runner ’s \textbf{shadowed} upper body fills more of the screen behind the product name.
Then a bottle of Vigran Squibb multivitamins appears in the foreground, centered in front of the forest background.
It is a dark glass bottle with a light-colored cap and a rectangular light label.
The label reads “ VIGRAN ” at the top and “ Squibb ” beneath it, with smaller text indicating multivitamins and a geometric Squibb mark near the lower part of the label.
The runner fades from prominence, leaving the bottle clearly displayed by itself against the softly blurred \textbf{outdoor} background.

% matched lemmas: branch, brush, leaf, outdoor, pace, path, shadow, silhouette, sky, sunlit, tree, trunk
\end{textsample}
