\begin{textsample}{POS Dim 2 – 1950 – Score 8.00 – 1950/tv\_com\_1950\_3.txt}  \label{ex:f2_pos_071}
The commercial is shown in black and white and appears to focus on \textbf{domestic} interiors and flooring.
At the start, the frame shows a clean, \textbf{modern} \textbf{home} interior.
On the left is a striped upholstered \textbf{sofa} or daybed with cushions, next to a small table and several houseplants.
In the background/right area is a dining or \textbf{sitting} \textbf{space} with a round table, several chairs, a bench or low seating, more \textbf{plants}, and a hanging globe-shaped light.
The floor is light-colored with visible geometric seams or tile-like outlines, emphasizing the floor surface across the \textbf{room}.
Later, the scene changes to a kitchen or utility-room setting.
A woman in a dress and heels is cleaning the floor with a mop.
She is bent slightly forward, holding the mop handle, and appears to be working near a white basket filled with flowers.
The \textbf{room} has light-colored cabinetry on the left, a checkered floor pattern in dark and light squares, \textbf{plants}, and large glass doors or windows in the background.
The visual emphasis is again on the floor and its clean appearance.
At the end, the camera shows a close-up of a checkered floor surface.
Over the floor, large promotional text appears : “ KENTILE ” at the top, “ Easy Clean Vinyl ” in a cursive style across the middle, and “ FLOORS ” at the bottom.
The final image clearly identifies the advertised product as Kentile easy-clean vinyl floors.

% matched lemmas: domestic, home, modern, plant, room, sit, sofa, space
\end{textsample}
