\begin{textsample}{POS Dim 2 – 2010 – Score 10.00 – 2010/tv\_com\_2010\_20.txt}  \label{ex:f2_pos_028}
The commercial begins on a black frame.
It then cuts to a \textbf{domestic} living-room setting.
A young boy stands in the foreground, facing the camera, wearing a \textbf{grey} striped T-shirt.
Behind him, two older children or teenagers \textbf{sit} on a \textbf{couch} ; one appears to be holding a handheld game \textbf{device}.
A kitchen area is visible in the background with an adult figure moving or standing there.
On-screen text identifies the boy as “ Dan Sweeney ” and labels him “ Frustrated Brother. ” An ESRB-style \textbf{rating} \textbf{icon} appears at the lower left.
The camera moves closer to Dan ’s face.
The background siblings remain blurred, emphasizing Dan as the speaker/subject.
His expression appears serious or concerned.
The scene cuts to a barbershop or hair salon.
A young boy \textbf{sits} in a barber chair wearing a light blue haircut cape while a woman trims or clips his hair.
He is holding a handheld gaming \textbf{device} in both hands.
The window behind him has decorative red lettering, and blinds cover the glass.
On-screen text identifies him as “ Marcus Rivers ” and labels him “ Sibling Conflict Advisor. ” The commercial cuts back to Dan in the \textbf{living} \textbf{room}, again in close-up.
He appears to be talking directly toward the camera.
The \textbf{couch} and the two older children remain out of focus in the background.
It returns to the barbershop in a wider shot.
Marcus \textbf{sits} reclined in the barber chair, still holding the handheld \textbf{device}, while the woman stands behind him working on his hair.
The shop interior includes barber chairs, a tiled floor, a trash can near the door, and a large front window looking out onto the street.
A close-up follows of Marcus holding the handheld \textbf{device} up toward the camera, partially obscuring his face as he gestures with it.
His expression appears confident or animated.
The commercial cuts back to the \textbf{living} \textbf{room}.
Dan is shown from the waist up, still facing the camera.
The two older children are behind him on the \textbf{couch}, one looking down at a handheld \textbf{device} and the other reclining.
The barbershop returns in a medium shot.
Marcus looks upward toward the camera while holding the \textbf{device}, as the woman continues cutting his hair behind him.
A shallow-focus shot in the \textbf{living} \textbf{room} places the older girl on the \textbf{couch} in clearer focus while Dan is blurred in the foreground.
The girl reclines with a neutral or slightly pleased expression.
The older boy beside her looks down at a handheld \textbf{device}.
The live-action scenes transition to a white graphic \textbf{screen}.
Large black text appears reading : “ STEP YOUR UP. ” The word “ UP. ” includes a small trademark symbol.
Faint, oversized \textbf{grey} text appears behind it, partially blurred.
Another graphic shot shows a blurred handheld gaming \textbf{device} near the top of the frame, with faint large background text and the phrase “ STEP YOUR ” visible lower down as the motion or focus shifts.
The final brand \textbf{screen} shows three logos centered on a white background : the PlayStation logo, the “ PSP ” logo with “ PlayStation Portable ” underneath, and a purple circular logo at the right.
The last frame cuts to a dark \textbf{screen} with a bright bluish-white lens-flare-like light and small light spots, suggesting an end transition or fade-out.

% matched lemmas: couch, device, domestic, grey, icon, live, rating, room, screen, sit
\end{textsample}
