\begin{textsample}{POS Dim 2 – 1950 – Score 18.00 – 1950/tv\_com\_1950\_99.txt}  \label{ex:f2_pos_083}
The commercial begins in near darkness, then opens into a soft, dreamlike black-and-white \textbf{sky} filled with pale clouds.
A light-colored 1950 Ford convertible appears in clean side profile, top down, suspended level in the middle of the cloudy space as if floating in midair.
No driver or passengers are visible.
The car ’s long, smooth body, rounded fenders, \textbf{whitewall} tires, \textbf{chrome} bumpers, and dark folded convertible top behind the seats stand out against the misty background.
For several moments the Ford remains centered and steady among drifting cloud shapes, emphasizing the impression that it is gliding or floating rather than \textbf{driving} on a road.
The view moves close to the front left side of the car, filling the image with the rounded front fender, headlight area, bumper edge, and front wheel.
The body panel becomes semi-transparent, revealing the engine inside the front compartment.
Dark mechanical parts appear beneath the pale exterior : a compact engine block, \textbf{belts}, hoses, and a round air cleaner sitting high on top.
The engine is shown as if seen through the \textbf{bodywork}, then the transparent overlay fades and the fender returns to a smooth, solid surface.
The Ford is then presented again in a bright studio-like space with a cloudy background, now from the front three-quarter angle.
Its rounded hood, circular headlights, \textbf{broad} \textbf{chrome} grille, central ornament, bumper guards, and \textbf{whitewall} front tire are shown prominently.
The image lingers on the car ’s polished front and side details, then \textbf{passes} along the body toward the rear, showing the straight side trim, door area, rear wheel, curved rear quarter panel, tail light, \textbf{trunk} shape, and shiny rear bumper.
The setting shifts from the floating display to a real \textbf{outdoor} road.
The convertible, top down, \textbf{drives} away along a \textbf{paved}, tree-lined roadway.
The rear of the car is most visible at first, with the \textbf{trunk}, rear bumper, \textbf{whitewall} tires, and dark interior contrasted against deep \textbf{shadows} from \textbf{trees}.
The car travels smoothly along a gently curving road, growing smaller as it moves forward.
A closer side view of the open cabin follows : the windshield and front bench seat are visible, and then two adults appear seated in front.
The driver is a clean-cut adult man with short dark hair, wearing a light suit jacket and tie.
Beside him is an adult woman with light, styled hair, wearing a pale blouse or dress.
Both sit upright in the open convertible, relaxed and smiling, with the woman turned toward the man as if conversing.
The car is then seen from outside in a wider view, moving slowly \textbf{past} shrubs and \textbf{trees}.
Its long, pale side, \textbf{whitewall} wheels, and dark folded top behind the rear seat are visible as the couple rides together.
The focus turns to the occupants and interior.
From the front, over the hood and windshield, the man and woman sit side by side with generous space between them on the bench seat.
The man holds the \textbf{steering} wheel and smiles toward the woman ; she looks back at him with a cheerful expression.
From behind the front seats, the open cabin is shown while the car travels along a \textbf{broad} road or parkway, with an overpass or bridge visible ahead and \textbf{trees} lining the sides.
The two seatbacks fill the lower foreground, the \textbf{steering} wheel is on the left side, and the simple dashboard stretches across the front.
A rearview mirror hangs at the center of the windshield.
The woman, seated on the right, turns toward the driver and gestures lightly with one hand near the dashboard, while the driver glances toward her and then back toward the road.
The car appears roomy and open, with the \textbf{sky} above and the roadway ahead visible through the windshield.
More views show the couple in the convertible from the side and from slightly above.
The woman ’s light hair catches the \textbf{sun}, and she smiles while facing the driver.
The man remains composed at the wheel, wearing his suit and tie, and returns her smile.
The dark folded convertible top forms a low mound behind them.
The car glides along a \textbf{sunlit} road bordered by \textbf{bushes} and \textbf{trees}.
Seen from above the windshield, the long hood stretches forward, with the couple framed by the open top and the windshield posts.
Their posture remains relaxed and social, suggesting an easy pleasure \textbf{drive}.
The Ford then approaches from the front on a tree-lined road.
Its rounded front end and \textbf{chrome} trim dominate the view : circular headlights, wide grille, central \textbf{chrome} ornament, bumper, and \textbf{whitewall} tires all catch the light.
The two occupants are visible behind the windshield as the car comes closer.
It \textbf{passes} by, bringing the front fender and spinning \textbf{whitewall} wheel close to view, then the side trim and door sweep across the image.
The body appears smooth and light-colored, with a narrow horizontal \textbf{chrome} strip running along the side.
The commercial returns to the stylized cloud setting.
The convertible reappears in full side profile, again without visible occupants, top down with the dark folded roof behind the cabin.
It hangs level against the pale, misty background, its front bumper, \textbf{whitewall} wheels, long side panel, door handle, and rear quarter clearly outlined.
The car remains centered and still, surrounded by soft, shifting clouds, closing on the same floating, “ out of this world ” visual idea introduced at the beginning.

% matched lemmas: belt, bodywork, broad, bush, chrome, drive, outdoor, pass, past, paved, shadow, sky, steering, sun, sunlit, tree, trunk, whitewall
\end{textsample}
