\begin{textsample}{POS Dim 2 – 2000 – Score 20.00 – 2000/tv\_com\_2000\_120.txt}  \label{ex:f2_pos_027}
The commercial begins in a bright, stylized suburban neighborhood.
A silver \textbf{sedan} \textbf{drives} straight toward the viewer along a dark, freshly marked road, centered over double white lines.
On both sides are neat sidewalks, lawns, small houses, mailboxes, and vivid \textbf{red-orange} \textbf{trees}, with snow-capped \textbf{mountains} rising in the distance under a blue-green \textbf{sky}.
The scene has a polished, miniature-model look, with saturated colors and very clean lines.
The view pulls back to show the silver car continuing down the middle of the quiet residential street.
Other \textbf{vehicles} appear nearby : a dark SUV on the left side of the road and a red sports car on the right.
The setting remains orderly and scenic, with rows of houses, bright autumn \textbf{trees}, and \textbf{mountains} beyond the neighborhood.
Inside the silver car, a light-skinned adult man \textbf{drives}.
He appears to be in his thirties or forties, with short dark hair, wearing a dark long-sleeved top.
He sits upright in the driver ’s seat, both hands on the \textbf{steering} wheel, looking forward with a calm, focused expression.
The car interior is dark, with a \textbf{broad} dashboard and empty passenger seat visible.
Back outside, the silver \textbf{sedan} is seen from behind as it continues away down the center of the road.
The residential area gives way to a dramatic \textbf{mountain} route.
A \textbf{snowy} rocky peak fills the foreground, and beyond it a curving road hugs a steep cliff.
Tall gray \textbf{rock} walls, evergreen \textbf{trees}, pink-orange foliage, and a waterfall create a fantasy \textbf{mountain} landscape.
The road runs along a high viaduct with \textbf{stone} arches, and small cars trace the curve around the mountainside.
The cars then travel beneath a dense canopy of brilliant red, pink, and orange \textbf{trees}.
The silver \textbf{sedan} remains in the center, flanked by a dark SUV on the left and a red coupe on the right.
Fallen \textbf{leaves} speckle the road as the three \textbf{vehicles} \textbf{drive} close together.
In the red car ’s side mirror, the silver \textbf{sedan} and the dark SUV are reflected behind it, framed by the mirror ’s black border and the red \textbf{bodywork} of the car.
The route opens onto a high cliff road with sweeping \textbf{mountain} views.
Cars wind along a narrow elevated roadway wrapped around a massive gray \textbf{rock} face, with a deep valley and more autumn-colored \textbf{trees} below.
A close view of the red sports car ’s front end shows its low bumper and headlights as it \textbf{rolls} over the dark road.
The \textbf{vehicles} approach a tunnel entrance built into the \textbf{mountain}, where three arched openings sit beneath digital overhead signs.
The signs display mileage numbers : “ 15000, ” “ 7500, ” and “ 5000, ” each above a separate tunnel lane.
Above another three-arch tunnel, three giant Mobil oil bottles stand like roadside monuments.
From left to right, the bottles have different cap and label colors : a red-capped Mobil bottle labeled with “ 5000, ” a blue-capped Mobil bottle labeled with “ 7500, ” and a larger bottle with a gold cap and a black-and-gold Mobil label associated with extended performance.
The silver \textbf{sedan}, the dark SUV, and the red coupe \textbf{drive} toward and beneath these oversized product bottles, which are mounted against the rocky \textbf{mountain} backdrop and framed by bright autumn \textbf{trees}.
A side view shows the \textbf{vehicles} moving along the \textbf{highway}, with the grille of the dark SUV large in the foreground and the silver \textbf{sedan} and red coupe \textbf{passing} alongside.
The landscape stays vivid and artificial-looking, with guardrails, pink \textbf{trees}, blue \textbf{sky}, and distant \textbf{mountains}.
A large roadside billboard appears next.
On it, a shiny metallic engine assembly is displayed against a graphic background of bold pink and pale blue shapes.
The engine parts slide across the billboard image, showing pistons and cylindrical components in reflective \textbf{chrome}, visually suggesting internal engine parts being protected.
The road continues \textbf{past} modern roadside structures built into cliffs, with the billboard standing high on a pole beside the elevated \textbf{highway}.
The scenery then shifts to a lake surrounded by \textbf{mountains} and colorful \textbf{trees}.
A huge red-capped Mobil bottle stands on the far shore like a statue, while cars continue along a road behind it.
As the view widens, three oversized Mobil oil bottles are arranged across the landscape : the blue-capped “ 7500 ” bottle on the left, the red-capped “ 5000 ” bottle in the center background, and the gold-capped extended-performance bottle on the right, set on rocky outcrops around the water.
A white speedboat or watercraft cuts across the lake, leaving a pale wake.
Cars \textbf{pass} along the road in the foreground as the bottles remain prominent against the \textbf{mountain} scenery.
From high above, the entire route is revealed as a sprawling, looping road system winding through forests, \textbf{mountains}, waterfalls, a blue lake, and small clusters of houses.
The road curves repeatedly like a long test track, with multiple lanes and sweeping bends, emphasizing distance and endurance across varied terrain.
The final product display appears on a clean white background.
Three Mobil oil bottles stand together : a red-capped Mobil 5000 bottle on the left, a larger gold-capped Mobil 1 extended-performance-style bottle in the center, and a blue-capped Mobil 7500 bottle on the right.
Beneath them is small text reading “ Official Lubricant of ” followed by the NASCAR logo.
The commercial ends on a simple white screen with the Mobil logo in large teal letters and a red “ o, ” and the website “ mobiloil.com ” centered below.

% matched lemmas: bodywork, broad, chrome, drive, highway, leaf, mountain, pass, past, red-orange, rock, roll, sedan, sky, snowy, steering, stone, tree, vehicle
\end{textsample}
