\begin{textsample}{POS Dim 2 – 1970 – Score 7.00 – 1970/tv\_com\_1970\_39.txt}  \label{ex:f2_pos_082}
The commercial sequence begins with a product display outdoors on grass : several yellow boxes of **Milk-Bone Dog Biscuits** are lined up, each with a \textbf{dog} image on the front. \textbf{Dogs} are visible behind or near the boxes.
Large white on-screen text at the bottom reads **“Better Teeth Cleaner…”** though the rest is partly obscured/unclear.
A “ Classic Commercial Archives ” watermark appears at the lower left.
The scene then cuts to an indoor office or break-room setting.
A gray-haired man in a dark suit and tie stands beside a countertop \textbf{coffee} machine labeled or styled like a **Mr.
Coffee** unit.
He holds a white cup to his mouth as if drinking.
Other people \textbf{sit} or move in the background at tables, and large windows with curtains and \textbf{plants} are visible.
Later, the same man is shown in the same office-like \textbf{space} holding up a large newspaper, flyer, or printed sheet while standing near the \textbf{coffee} maker.
A white cup is visible near his hand, and the \textbf{coffee} machine remains on the counter to his side.
Background figures and office furniture are still visible, but details are soft and partly obscured by motion or dissolve effects.
The final frame shifts to a studio-style product display against a yellow background.
The suited man stands at the left with a **Mr.
Coffee** machine in front of him.
Several Mr.
Coffee products are arranged across a table, including \textbf{multiple} \textbf{coffee} makers and packaging or display placards.
Large white text above reads **“The MR. \textbf{COFFEE} \$5.00 Rebate.”** Smaller text at the bottom reads **“See \textbf{stores} for details.
Offer ends Nov. 30, 1978.”** The archive watermark remains visible near the lower left.

% matched lemmas: coffee, dog, multiple, plant, sit, space, store
\end{textsample}
