\begin{textsample}{POS Dim 2 – 2010 – Score 10.00 – 2010/tv\_com\_2010\_84.txt}  \label{ex:f2_pos_026}
The commercial begins in a bright, formal banquet or hotel dining \textbf{room}.
Two servers in black vests, white shirts, and bow ties are preparing tables set with white tablecloths, plates, folded napkins, and chairs.
A female server in the foreground holds a small brightly colored packet or candy-like item, while a male server works at a nearby table.
The camera then focuses on the male server from the side as he looks downward, still in the same dining-room setting.
The scene abruptly cuts to a different interior : a warmly lit \textbf{living} \textbf{room} with striped wallpaper, framed wall art, curtains, furniture, and a colorful bouquet of flowers in the foreground.
A small jet-like object is then shown flying through this \textbf{domestic} \textbf{room}, passing near \textbf{plants} and furniture.
A wider shot reveals a \textbf{living} \textbf{room} with a glass \textbf{coffee} table, \textbf{sofa}, armchair, and various decorative objects.
The male server appears to be seated in the \textbf{room}, still wearing his waiter uniform.
The commercial cuts to a close-up of a pilot-like figure wearing a red helmet and a gray oxygen \textbf{mask} inside what appears to be a cockpit.
The helmet has decorative markings, and tubes and straps are visible.
Another shot shows the \textbf{living} \textbf{room} from a tilted angle, with the small jet-like object positioned low in the \textbf{room}, suggesting rapid movement through the \textbf{space}.
A close-up follows of the male server ’s face as he \textbf{sits} in a green chair.
He is holding a small pink cube-shaped item near his mouth.
A small red-and-white object appears at the right edge of the frame, pointing toward him, though its exact nature is unclear from the frames.
The pilot figure is shown again, turning or looking to the side while still wearing the helmet and \textbf{mask}.
The next shots show a shaggy, light-colored \textbf{dog} inside the \textbf{room}.
The \textbf{dog} appears animated or excited, with its mouth open ; in one shot it is seen from above, and in another it \textbf{sits} upright near furniture, facing upward.
The scene then cuts back to the original banquet hall.
The male server looks off to the side with a concerned or startled expression.
A wider shot shows both servers again in the formal dining \textbf{room} : the female server is in the foreground, slightly out of focus at first, while the male server is behind her.
Both appear serious or uneasy.
The final frame is a product shot on a bright yellow background.
A red candy wrapper is centered with the word “ Starburst ” clearly visible in large lettering.
Small fine print appears along the bottom, but it is too small to read clearly in the sampled frame.

% matched lemmas: coffee, dog, domestic, live, mask, plant, room, sit, sofa, space
\end{textsample}
