\begin{textsample}{POS Dim 2 – 1960 – Score 15.00 – 1960/tv\_com\_1960\_33.txt}  \label{ex:f2_pos_015}
A small workboat moves across a harbor toward the viewer, leaving a wake on the pale, pink-tinted water.
As it approaches, large cream-colored block letters appear diagonally over the water and boat, reading “ DODGE REBELLION OPERATION ’ 67. ” The letters are bold and \textbf{shadowed}, like a stamped announcement.
The scene shifts to a drawbridge seen from below against a bright \textbf{sky}.
A blonde adult woman, slim and dressed in a dark \textbf{reddish} fitted outfit with a high neck, stands high above on the bridge walkway.
She moves along the railing, then plants herself at the center where the two halves of the bridge meet.
From below, she grips the railings on either side, legs braced wide over the seam.
A striped \textbf{red-and-white} warning barrier with round signal lights is shown, reinforcing the bridge setting.
The two bridge halves begin to separate, opening into a widening gap beneath her.
She stretches her arms outward, holding the railings as the bridge opens, her stance dramatic and precarious.
In a closer view, her light blonde hair frames her face, and she looks forward with an intent expression.
Then, from a distant overhead-looking view, she appears tiny between the two raised bridge sections and drops down through the opening, arms lifted.
At the waterfront, a sailboat with a large white sail sits near a dock while people are seated low in the boat.
Beyond it, a white 1967 Dodge Polara is visible on a pier or ramp, positioned above the water near marina structures.
The car then appears on a long dock road beside the harbor, with boats and moorings in the background.
Large cream block text fills the center of the picture over the marina scene : “ ’ 67 Dodge Polara. ” The Polara is shown in motion along a palm-lined waterfront road.
It is a long, white, two-door hardtop with a \textbf{broad} \textbf{chrome} front grille, paired round headlights on each side, \textbf{whitewall} tires, and shiny \textbf{chrome} trim.
A driver, an adult man in a light shirt or jacket, is visible through the side window, seated upright at the wheel.
Palm \textbf{trees} and boats \textbf{pass} behind the car, and the harbor stretches across the background.
The front of the car is emphasized : its grille spans the width of the nose, the headlights gleam, and sunlight flashes off the \textbf{chrome} bumper and hood.
The front license plate area shows “ 1967. ” The car continues along the waterfront in side profile, its long roofline and extended rear deck clearly visible.
The background includes palm \textbf{trunks}, a calm bay, and ships or boats in the distance.
The view moves to the rear of the car, highlighting the wide red taillights set into the back corners, a \textbf{chrome} bumper, and a rear license plate marked “ 1967. ” The rear deck has clean, angular lines, and the letters across the back are visible but small.
The car ’s back end remains the focus as it glides beside the water.
A close view shows the scripted “ Polara ” \textbf{badge} on the car ’s white body, beside a round \textbf{emblem}.
The scene then reveals the pale interior through the open side : light-colored bench seats with vertical ribbed upholstery, seat \textbf{belts} lying across the cushions, and a matching door panel with simple rectangular handles and trim.
The upholstery appears plush and neatly stitched.
The view continues inside to the front cabin, showing the \textbf{steering} wheel, dashboard, instrument cluster, and the driver ’s hands holding the wheel.
The dashboard has \textbf{chrome} and dark panels, with circular gauges and horizontal trim, giving the interior a polished, spacious look.
The exterior returns to the car ’s front quarter.
The white Polara sits or moves slowly under palm \textbf{trees}, its quad headlights and \textbf{chrome} grille filling the scene.
The front wheel and \textbf{whitewall} tire are shown closer, with the \textbf{chrome} hubcap reflecting light as the wheel turns.
The bright reflections make the hubcap sparkle.
The car then appears again in full side profile near a marina crowded with sailboat masts, moving smoothly across the waterfront road.
Palm fronds cast \textbf{shadows} across the car and \textbf{pavement} as it \textbf{passes} beneath \textbf{trees}.
The earlier drawbridge image reappears faintly, with the woman still falling between the separated bridge halves.
The scene resolves into a tall, cylindrical platform or open-topped podium outdoors.
A vintage-style microphone on a stand stands to the left of the podium.
The woman drops into the open top, disappears for a moment, then pops back up from inside.
Her blonde hair is tousled, and she now leans over the rim with her forearms crossed on top.
She smiles broadly, animated and playful, looking toward the viewer and toward the nearby microphone.
She gestures with one hand, then rests both arms on the rim, grinning.
As the final moments continue, she points outward toward the viewer, then glances aside, still leaning comfortably from the podium beside the standing microphone, with the warm \textbf{sky} and distant landscape behind her.

% matched lemmas: badge, belt, broad, chrome, emblem, pass, pavement, red-and-white, reddish, shadow, sky, steering, tree, trunk, whitewall
\end{textsample}
