\begin{textsample}{POS Dim 2 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_43.txt}  \label{ex:f2_pos_087}
The commercial is in black and white.
It opens outdoors on a grassy playing field where several school-age children are \textbf{gathered} around a low net, playing a ball game that looks like volleyball.
The net stretches horizontally across the lower part of the scene, with children on both sides looking upward and reaching as a light-colored ball arcs above them.
The children wear casual short-sleeved shirts and play clothes.
They shift positions under the ball, some with arms lifted, others watching and waiting.
A \textbf{few} boys move closer to the net, tracking the ball as it sails back and forth.
The view moves closer to two boys on the field.
One blond boy in front looks up with his hands raised, ready to catch or hit the ball, while another boy just behind him also follows the ball.
They stand on open \textbf{grass} with no buildings visible, emphasizing the \textbf{outdoor} play.
The boys ’ faces are intent and active ; they raise their arms as the ball comes down, then lower them as it \textbf{passes} out of reach.
The scene changes to a classroom.
Several children sit at individual wooden desks arranged in rows.
Chalkboards fill the wall behind them, covered with arithmetic problems and children ’s names written in chalk.
The children are school-age, dressed neatly in 1950s classroom clothing : collared shirts, patterned blouses, dresses, and a boy in a shirt and tie.
Some children sit alertly, while others glance toward the front of the room as if listening to a teacher.
In the middle front area, a dark-haired girl with braids sits at her desk wearing a dark dress with a bright white collar.
She looks tired and unengaged compared with the others.
Her head rests against one hand, her elbow on the desk, and her posture is slumped.
A closed book lies on her desk beside papers.
Around her, other children begin raising their hands.
A boy in the back row lifts his arm high with an eager expression, and another boy at the left also raises his hand.
The girl with braids remains low over her paper, slow and subdued, while the classroom activity continues around her.
The girl tries to write.
She holds a pencil and moves it across the paper, but her movements appear sluggish.
She keeps one hand at the side of her head, then lowers her gaze to the desk.
Her face looks serious and weary, with little expression.
Behind her, the boy who had raised his hand lowers it and watches ahead.
The chalkboard arithmetic remains visible in the background, including columns of numbers and addition marks.
The girl ’s face is then seen more closely.
She looks down at her desk, then gradually lifts her eyes upward.
Her expression softens from tired concentration to a faint, hopeful smile.
Large white lettering appears over her face and the classroom background : “ IT ’S TIME TO CALL FOR JUVENAL. ” The words “ IT ’S TIME TO CALL FOR ” are in bold, slanted script-like capitals, while “ JUVENAL ” is much larger, in \textbf{heavy} block capitals across the bottom.
A product display appears : a rectangular carton stands on the left and a dark glass bottle stands on the right, both placed on a smooth tabletop.
The carton reads “ JUVENAL ” at the top and “ LIQUID VITAMINS and IRON ” beneath it, with “ NUTRITIONAL SUPPLEMENT ” printed lower down.
A circular seal is visible on the front of the package.
The bottle label also reads “ JUVENAL ” and “ NUTRITIONAL SUPPLEMENT. ” The packaging is arranged neatly side by side, lit from above so that the bottle has glossy highlights.
The product image fades into a close view of the same dark-haired girl with braids, now standing or sitting upright in front of a background patterned by strong horizontal \textbf{shadows} from window blinds.
She smiles brightly.
An adult woman ’s hand enters from the right holding a spoon with a dark liquid on it ; the hand also holds the product bottle close by.
The girl opens her mouth willingly as the spoon approaches.
The spoon is placed in her mouth, and she takes the liquid.
The adult hand withdraws the spoon, and the girl looks upward with a pleased expression, then smiles, appearing satisfied rather than reluctant.
Back in the classroom, the mood is livelier.
A young girl in a light sleeveless dress sits at a front desk, smiling broadly and raising her hand high above her head.
Other children behind her also raise hands.
The chalkboard with arithmetic problems remains in the background.
The girl leans forward eagerly, arm stretched upward, eyes bright, as if she knows the answer.
A boy seated behind her smiles and raises his hand too, while another boy watches from the side.
The girl in the light dress keeps her hand raised, then waves it slightly with excitement.
She begins to rise from her desk, \textbf{pushing} herself up with one hand on the desktop.
Her dress has a full skirt that flares as she stands.
She faces toward the unseen front of the classroom, smiling and animated.
Other children look toward her or toward the teacher ’s direction, and one boy at the right turns his head to watch her.
She stands beside her desk, hands resting near her papers, appearing confident and energetic.
The scene changes to a medical or school health room.
A nurse in a white uniform, white cap, and heels stands beside a tall physician ’s scale with a height-measuring rod.
Strong striped \textbf{shadows} from window blinds fall across the wall.
Several children line up on the left beside an adult man, possibly a parent or school staff member.
A boy stands on or near the scale while the nurse adjusts the measuring apparatus.
The children wait in a loose line, watching.
The children move quickly and energetically around the scale.
A boy steps down and darts \textbf{past} the nurse, while the girl in the light dress \textbf{hurries} forward from the line.
She climbs onto the scale platform, facing the nurse with an eager smile.
The nurse looks down at the scale and holds the measuring rod, calmly guiding the process.
Behind them, other children and the adult man wait near a small table or \textbf{cart} with bottles and supplies.
The girl stands on the scale with her hands at her sides, looking up at the nurse.
She appears cheerful and healthy, her posture upright and lively.
Another child runs \textbf{past} in the foreground, momentarily blurring across the right side, while the nurse continues attending to the scale.
The setting remains orderly, with the blinds, wall chart, and medical equipment reinforcing the health-office atmosphere.
The product packaging then appears again, large in the foreground over the health-room scene : the Juvenal carton on the left and the bottle on the right.
As the background fades away, the final image settles on the product alone on the tabletop.
The carton clearly displays “ JUVENAL, ” “ LIQUID VITAMINS and IRON, ” and “ NUTRITIONAL SUPPLEMENT, ” with the dark bottle beside it carrying the matching Juvenal label.
The commercial ends with this clean product display, the carton and bottle standing side by side under bright studio lighting.

% matched lemmas: cart, few, gather, grass, heavy, hurry, outdoor, pass, past, push, shadow
\end{textsample}
