\begin{textsample}{POS Dim 2 – 2020 – Score 21.00 – 2020/tv\_com\_2020\_82.txt}  \label{ex:f2_pos_046}
A bright T-Mobile magenta screen fills the view, with the white square T-Mobile “ T ” logo centered.
The logo then appears over a \textbf{sunlit} desert road, where a magenta streak sweeps across the image before clearing to reveal a long, cracked \textbf{two-lane} road stretching through scrubby desert toward low hills and a blue \textbf{sky}.
Far in the distance, a pickup \textbf{truck} crests the rise and \textbf{drives} toward the viewer.
The silver pickup approaches head-on, centered on the road, its headlights glowing. \textbf{Dry} \textbf{brush} and sandy shoulders line both sides, and the late-day light casts long \textbf{shadows} across the \textbf{pavement}.
A small magenta T-Mobile-colored plate or accent is visible on the \textbf{truck} ’s front.
Inside the \textbf{truck}, a middle-aged white man with a close-cropped beard and mustache \textbf{drives}.
He wears a black baseball cap pulled low, a green-and-blue plaid button-up shirt, and dark bracelets on his wrist.
He sits upright behind the wheel, one arm extended to steer, glancing toward the side as if addressing someone just outside the viewer ’s perspective.
Through the window behind him, the desert landscape \textbf{passes} by, including a Joshua \textbf{tree} and pale sand under a clear \textbf{sky}.
His expression is direct and conversational, with a slight squint from the bright light.
The \textbf{truck} pulls off near a roadside area in the desert.
In profile, the front half of the silver pickup \textbf{rolls} into view on \textbf{dusty} \textbf{ground} beside a tall roadside sign structure.
The background shows open desert, distant \textbf{mountains}, and a \textbf{few} scattered signs.
Under the \textbf{truck}, a pair of brown \textbf{boots} steps down onto the dirt, the man climbing out from the driver ’s side.
The wider view reveals the \textbf{truck} parked at left beside a tall sign.
At the top is a large pink T-Mobile “ T ” logo, mounted above an oval sign that reads “ Best Network. ” The sign stands in the middle of the desert roadside, with \textbf{mountains} behind it and the \textbf{sky} still bright.
The man is now outside the \textbf{truck}, small in the scene near the \textbf{vehicle}.
He then stands facing forward on the roadside, with the desert and road behind him.
He is still wearing the black cap and plaid shirt, and his face is lit warmly by the \textbf{sun}.
Small white legal text appears along the bottom of the screen, including the readable claim “ T-Mobile : Best Mobile Network in the U.S. ” followed by finer print that is too small to fully make out.
He smiles more broadly as he continues addressing the viewer.
The setting changes to the front of a low, retro roadside building in the desert.
The building has a pale mint-green façade, double glass doors in the center, windows with blinds, star decorations near the roofline, and a vertical neon-style sign on the right side.
Across the roof, large pink illuminated letters spell, “ It ’s better over here. ” The same man walks from left to right in front of the building, now holding a phone in one hand and looking down at it as if checking or using it while he walks.
As he continues \textbf{past} the entrance, the full storefront becomes more visible.
To the right is a service-window or diner-like section with a red trim band, vending or menu-style signs, a green trash can, and desert hills beyond.
The pink roof sign remains prominent above him, glowing against the evening \textbf{sky} : “ It ’s better over here. ” The view widens to show the building set beside a \textbf{highway} running into the desert, with Joshua \textbf{trees}, parked \textbf{vehicles}, low \textbf{mountains}, and a warm sunset gradient in the \textbf{sky}.
The man appears small below the sign as he pauses near the front of the building.
The commercial ends on a solid T-Mobile magenta screen.

% matched lemmas: boot, brush, drive, dry, dusty, few, ground, highway, mountain, pass, past, pavement, roll, shadow, sky, sun, sunlit, tree, truck, two-lane, vehicle
\end{textsample}
