\begin{textsample}{POS Dim 2 – 2020 – Score 27.00 – 2020/tv\_com\_2020\_107.txt}  \label{ex:f2_pos_044}
A young adult woman identified by on-screen text as Madison Chock, U.S.
Olympian in figure skating, stands on an indoor ice rink under dim, dramatic lighting.
She has long dark hair pulled back, red lipstick, and a serious, focused expression.
She wears a sleeveless, pale beige skating dress with sparkling beaded details.
Behind her, the rink boards are softly out of focus, with a large red “ HONDA ” sign visible.
The scene shifts inside a rally car.
Dai Yoshihara, identified by on-screen text as a rally car driver, sits strapped in behind the wheel, wearing a black Honda-branded racing helmet and white racing gloves.
Only his eyes and upper face are visible through the helmet opening.
He raises both gloved hands to adjust the helmet and visor, then lowers them, staring forward with concentration from inside the car ’s roll-cage interior.
Another athlete appears in a dark, enclosed sporting environment.
Kaysha Love, identified as a U.S.
Olympian in bobsled, wears a glossy black helmet with a clear visor and a fitted blue racing suit with red and white accents, including a “ USA ” patch on the chest.
She leans forward over the front of a bobsled, eyes fixed ahead through the visor.
A snowboarder identified as Brenna Huckaby, U.S.
Paralympian in para snowboarding, stands in a \textbf{snowy} \textbf{mountain} setting.
She wears a white \textbf{winter} jacket with a red Honda “ H ” logo, dark pants, a helmet, and ski goggles.
Snow-covered \textbf{trees} fill the background.
She begins descending a slope on a snowboard, body low and balanced, orange bindings visible at her feet.
Red \textbf{course} gates and white barriers marked “ HONDA ” line the run.
She carves through the \textbf{snow}, kicking up powder as the board edges sharply across the slope.
A bobsled races along a curving ice track.
The sled is blurred from speed as it hugs the high white wall of the track, with metal railings along the edge.
This connects back to Kaysha Love, whose face fills the view again inside her helmet, eyes intense behind the visor.
The setting changes to a high-tech lab or design studio.
A young adult woman with long hair, glasses, and a white lab coat stands behind a transparent digital display.
A \textbf{red-and-white} Honda \textbf{badge} is pinned to her coat.
She reaches forward with one hand as if touching a floating control.
Blue holographic graphics surround her : a glowing outline of a car, circular interface icons, and panels of technical text.
One visible panel reads “ PRELUDE HYBRID. ” A \textbf{vehicle} chassis sits on a table, and a translucent blue hologram grows over it, forming the shape of a sleek car body.
That digital outline then \textbf{blends} into a real blue Honda coupe \textbf{driving} on a \textbf{two-lane} road through open countryside, with \textbf{mountains} in the distance.
The car approaches from the front, then is seen from behind as it continues along the winding road, its smooth rear light bar and low, \textbf{sporty} shape visible.
Back on the ice rink, Madison Chock now skates with a male partner identified by on-screen text as Evan Bates, U.S.
Olympian in figure skating.
He wears black, while she wears the flowing beige dress seen earlier.
They glide together across the lit ice, holding hands and moving in unison.
Under bright rink lights, he supports her through turns and lifts ; her hair and dress fringe \textbf{trail} with the motion.
Close views of their skates show black and white \textbf{boots} cutting into the ice, sending fine sprays of ice crystals outward.
From above, their linked bodies trace graceful circular \textbf{paths} as they spin together.
A white, red, and black Honda race car appears on a \textbf{dusty} dirt \textbf{course}, sliding through a wide turn and \textbf{throwing} up a cloud of dust.
It transitions to an open-wheel race car on a \textbf{paved} track, red and black accents visible as it speeds around a \textbf{banked} curve.
Large white capital letters begin appearing over the action.
First, over the figure skaters, the word “ THIS ” is centered near the top.
As the skaters glide hand in hand, the word remains above them.
Over a white Honda racing \textbf{vehicle} \textbf{driving} through \textbf{sunlit} dust, the text expands to “ THIS IS. ” Then over the bobsled \textbf{rushing} along the ice wall, it becomes “ THIS IS THE. ” Over the blue Honda coupe driving through \textbf{mountain} scenery, it reads “ THIS IS THE POWER. ” As the snowboarder carves through a \textbf{snowy} forest, the words add “ OF. ” Finally, over the blue Honda on the road, the full phrase fills the center in stacked white letters : “ THIS IS THE POWER OF DREAMS. ” The phrase stays centered while the imagery becomes a collage of vertical panels.
On the left, the figure skaters celebrate, with an American \textbf{flag} held behind them.
In the middle, the blue Honda continues \textbf{driving} on a road.
On the right, Brenna Huckaby appears in her white Honda jacket and helmet against the \textbf{snowy} \textbf{trees}.
Additional panels slide into view showing athletes in racing suits celebrating and a bobsledder speeding down an icy track, all arranged around the central white text “ THIS IS THE POWER OF DREAMS. ” The commercial ends on a clean white background with animated Honda \textbf{vehicles} and athletes moving horizontally across the screen.
A red SUV, a red \textbf{sedan}, a blue race car, cyclists, skaters, and other small \textbf{vehicle} \textbf{silhouettes} streak across in red and blue bands, forming parallel lines like stylized stripes.
In the center, the red “ HONDA ” wordmark appears in bold capital letters.
The moving red and blue lines continue \textbf{past} it, then fade, leaving the Honda name centered on the bright white field.

% matched lemmas: badge, bank, blend, boot, course, drive, dusty, flag, mountain, past, path, paved, red-and-white, rush, sedan, silhouette, snow, snowy, sporty, sunlit, throw, trail, tree, two-lane, vehicle, winter
\end{textsample}
