\begin{textsample}{POS Dim 2 – 1970 – Score 6.00 – 1970/tv\_com\_1970\_47.txt}  \label{ex:f2_pos_084}
The commercial begins with a close-up of a red Christmas-tree ornament hanging among dark green branches.
White script on the ornament is partially legible and appears to say “ Happy Holidays ” and “ Pepsi-Cola, ” though the text is somewhat blurred.
The next scene shows a woman seated in a dark upholstered reclining chair in a furnished \textbf{room}.
She is wearing a light-colored pantsuit or matching outfit and has her legs extended, suggesting the chair is reclined or has a footrest.
Behind her are other \textbf{home} furnishings, including a plaid-patterned chair or cushion and a dark patterned wall or backdrop.
The commercial then cuts to a furniture product display.
A low rectangular \textbf{coffee} table with a glass or inset top is shown in the foreground.
Behind it, the background is divided into two display panels : on the left is a small side table or end table, and on the right is a \textbf{wooden} cabinet or pedestal-style table.
The furniture is arranged on a tiled floor.
The following shot widens to a showroom-like set with \textbf{multiple} pieces of furniture on different platform levels.
The same woman stands near the center among \textbf{coffee} tables, end tables, lamps, and chairs.
The set includes warm-toned flooring, raised platforms, and several staged living-room arrangements.
In the final frame, the woman remains standing in the furniture display area while large promotional text overlays the image.
A prominent “ Sears ” logo appears in the upper right, with small copyright text beneath it.
Large sale prices are displayed across the bottom, including “ Sale 99.88 ” and another price ending in “ 109.88. ” A line of text at the bottom reads “ At most Sears larger \textbf{stores}. ” A “ Classic Commercial Archives ” watermark is visible in the lower-left corner, with a faint archive watermark across the lower part of the image.

% matched lemmas: coffee, home, multiple, room, store, wooden
\end{textsample}
