\begin{textsample}{POS Dim 2 – 1970 – Score 14.00 – 1970/tv\_com\_1970\_5.txt}  \label{ex:f2_pos_075}
The commercial opens in grainy black-and-white with a close view of a formally dressed man seated inside a car.
He appears middle-aged to older, with a serious expression, wearing a dark suit, white shirt, tie, and thick dark eyeglasses.
His hands carefully hold a small object and a jeweler ’s tool in front of him.
White on-screen text at the bottom reads “ Actual demonstration. ” The view moves closer to his fingertips as he handles a \textbf{rough}, pale stone-like piece, consistent with the transcript ’s reference to a Cartier diamond.
His fingers turn it delicately beside a darker clamp or holding tool, emphasizing precision and risk.
The black-and-white sequence then shows a large, dark, full-size Mercury \textbf{sedan} \textbf{driving} along a city street, its long hood, \textbf{chrome} grille, and \textbf{broad} body reflecting light as it \textbf{rolls} smoothly around a bend.
The scene changes to color.
A clean-cut adult man in a dark suit and striped tie stands beside a dark blue 1978 Mercury Monarch parked on a wet-looking urban street.
He rests his hands on the roof near the windshield and faces forward as if addressing the viewer.
Behind him are storefront windows and large pale awnings ; a \textbf{few} men in suits stand nearby, watching.
The Monarch is a four-door \textbf{sedan} with a light-colored vinyl roof, \textbf{chrome} trim, \textbf{whitewall} tires, and a squared-off front end.
As the full car is shown in profile, large white text appears near the bottom : “ 1978 MERCURY MONARCH. ” The car ’s front end is then featured closely : a tall, bright \textbf{chrome} grille, rectangular headlights, \textbf{chrome} bumper, and hood ornament.
The dark blue paint gleams as the car moves forward.
The view tracks along the front corner, fender, and spinning wheel, showing the \textbf{whitewall} tire and \textbf{chrome} hubcap.
The Monarch is next seen driving on a \textbf{sunlit} road lined with \textbf{trees}.
A split view presents the car approaching in the upper portion while the lower portion shows the roadway surface \textbf{rushing} by, visually stressing the uneven road mentioned in the transcript.
Inside the moving car, the older jeweler is now seated in the back seat.
He wears a suit and dark tie, with large black-framed glasses.
He raises a jeweler ’s loupe or magnifier to one eye, leaning forward in concentration.
Outside, the Monarch continues down the tree-lined street, seen head-on through the windshield with the driver and back-seat passenger visible.
The front grille fills the center, steady and upright as the car travels.
A divided image then shows the demonstration happening inside the car while the wheel and road remain visible below.
The text “ Actual demonstration ” appears again at the bottom.
In the upper portion, the jeweler ’s hands hold a small diamond and a tool near the rear door panel ; below, the car ’s wheel \textbf{rolls} along the road.
The jeweler steadies the \textbf{stone} in a small dark holder, then raises a \textbf{broad}, flat metal blade or striking tool over it.
His movements are careful and controlled.
In a wider interior view, he sits at a small work surface or board laid across the back seat.
Several tools lie on the board beside a dark upright holder.
He brings the tool down, then smiles broadly, suggesting the cut has succeeded.
The driver, a younger adult man in a dark suit, is shown from the front seat in profile, then glancing back over his shoulder toward the jeweler.
The jeweler is shown in close-up holding the small \textbf{stone} between his fingers and the tool, smiling with visible relief and satisfaction.
His black glasses dominate his face, and his expression changes from focused concentration to a pleased grin.
The Monarch continues \textbf{driving} smoothly along the road, its dark blue side \textbf{passing} across the screen in a blur of \textbf{chrome} trim, \textbf{whitewall} tires, and reflections.
It returns to the city setting, parked outside the same storefront area with the suited presenter standing beside it.
Large white pricing text appears over the lower part of the image : “ UNDER \$4800, ” followed by smaller text reading “ Sticker price as shown.
Destination charges, title, taxes extra. ” The car remains angled toward the viewer, displaying its boxy front, \textbf{chrome} grille, light roof, and polished body.
Near the end, the older jeweler appears seated inside the car, seen through an open window or dark interior frame, smiling and speaking toward someone outside.
The final image is a black background with a circular \textbf{emblem} at the top containing Mercury and Lincoln branding.
Large white text reads “ MERCURY MONARCH. ” Beneath it appears “ LINCOLN-MERCURY DIVISION, ” and a Ford 75th anniversary-style \textbf{emblem} is shown at the lower right.

% matched lemmas: broad, chrome, drive, emblem, few, pass, roll, rough, rush, sedan, stone, sunlit, tree, whitewall
\end{textsample}
