\begin{textsample}{POS Dim 2 – 1990 – Score 17.00 – 1990/tv\_com\_1990\_98.txt}  \label{ex:f2_pos_039}
A pink and lavender \textbf{sky} stretches over a restless ocean at sunrise or sunset.
Low waves \textbf{roll} toward a rocky shoreline in the foreground, and far out near the horizon a long, dark ship sits in profile, its small white structure visible toward one end.
As the view continues along the coast, tall dark \textbf{rocks} rise at the right edge, and the ship remains a slim \textbf{silhouette} against the glowing orange-pink band of \textbf{sky}.
In the foreground, a large sea lion or seal appears on the \textbf{rocks}, its body dark against the light, head lifted upward as if calling toward the open water.
It raises a flipper, with the ship still distant beyond the surf.
The scene shifts to a bright green marsh or pond, where several ducks float and \textbf{splash} among tall reeds.
Their bodies are warm brown and cream, with pale heads and darker bills.
One duck stands partly upright in the shallow water, wings spread wide, beating them and \textbf{throwing} droplets into the air while the others bob nearby.
Out in blue water, sea otters float on their backs.
Their dark wet bodies lie low in the ripples, with lighter, whiskered faces turned upward.
One otter lifts its head and paws ; another drifts close beside it, the two appearing relaxed and buoyant as they paddle gently at the surface.
A dolphin bursts vertically out of the sea, grey body shining, water streaming down from its sides.
It rises higher above the green-blue waves, arcing slightly, then begins to descend, leaving a burst of white spray below.
On \textbf{sunlit} coastal \textbf{rocks}, two sea lions sit upright with the ocean behind them, their long necks extended and flippers braced on the \textbf{stone}.
A close view returns to a group of sea otters clustered together in calm water.
Their pale faces and dark fur fill the view ; one otter raises a dark paw beside its head, while others press close, whiskers and wet fur catching the light.
An orca breaches from the open ocean, its black-and-white body \textbf{rolling} sideways above the blue water.
The white \textbf{underside} and black dorsal fin are clearly visible as it turns, then crashes back down, \textbf{throwing} up a huge plume of white spray that spreads across the surface.
Two tall white birds, likely cranes, stand in shallow water near reeds with low hills in the distance.
Their white wings flare open, showing dark tips, as they step and lift their legs in a dance-like motion.
The water is calm and blue, with the birds reflected faintly beneath them.
Two dolphins surface close together in bright blue water.
Their smooth grey heads rise side by side, \textbf{splashing} as they \textbf{push} forward.
One opens its mouth slightly while the other glides \textbf{past}, their bodies partly submerged and surrounded by white foam.
A large flock of ducks covers a lake, many of them beating their wings and taking off at once.
The water churns with \textbf{splashes} as birds lift from the surface, while others remain scattered in the background.
Back on the rocky coast, three sea lions are \textbf{silhouetted} against a pale \textbf{sky} and ocean.
One large sea lion stands tall at the left, another sits on a central \textbf{rock} with a flipper extended, and a smaller one perches on a separate \textbf{rock} at the right, all facing outward as if alert to the sea.
On a \textbf{snowy}, icy landscape, black-and-white penguins waddle and slide.
Some stand upright with white bellies and dark heads ; others lie low on their stomachs, \textbf{pushing} themselves forward with flipper-like wings.
They move in different directions across the uneven white surface.
A dense flock of pink flamingos fills the \textbf{sky}, flying low with long necks stretched forward and long legs \textbf{trailing} behind.
Their wings beat rapidly, showing dark black feathers at the tips among the vivid pink bodies.
A crowded group of tan and brown sea lions or seals \textbf{gathers} on wet \textbf{rocks}, their heads tilted upward.
Their whiskered faces overlap in a \textbf{tight} cluster, with droplets and spray visible around them, suggesting a noisy, active shoreline gathering.
Three dolphins leap together from a \textbf{sunlit} ocean.
The \textbf{sun} glows off to the left, making the water sparkle pink and gold.
Each dolphin rises nearly vertical from a column of spray, suspended above the waves with curved bodies and fins visible.
They hang in the air for a moment at different heights before beginning to fall back toward the sea.
The final view returns to a \textbf{broad} coastal sunset.
The \textbf{sky} is deep orange, the \textbf{sun} low above the horizon, and many sea lions appear as dark \textbf{silhouettes} scattered across layered \textbf{rocks} along the shore.
Some sit upright with heads raised ; others recline lower on the \textbf{rocks}.
Over this sunset scene, the white DuPont oval logo appears at center, followed by the slogan in white script beneath it : “ Better things for better living. ”

% matched lemmas: broad, gather, past, push, rock, roll, silhouette, sky, snowy, splash, stone, sun, sunlit, throw, tight, trail, underside
\end{textsample}
