\begin{textsample}{POS Dim 2 – 1960 – Score 18.00 – 1960/tv\_com\_1960\_56.txt}  \label{ex:f2_pos_009}
On a bright beach, four boys run along the wet sand at the edge of the surf, seen mostly as dark \textbf{silhouettes} against the glittering ocean.
A shaggy dark dog trots beside them on the left.
The water behind them is full of white breaking waves, and the low \textbf{sun} makes the sea shine so strongly that the children ’s bodies read as playful outlines.
A huge striped beach ball, several feet across, floats above and ahead of them.
As they run from left to right, the boys look upward and reach toward the ball, while the dog keeps \textbf{pace} close to the waterline.
The beach ball drops lower as the group catches up to it.
The boys cluster around it, still in \textbf{silhouette}, with one child stretching both arms up and another stepping in front of the ball as if to catch or bat it away.
The dog stays near their legs, occasionally pausing or bounding forward.
The oversized ball, divided into \textbf{broad} colored panels, becomes the focus of their play as they move along the shore.
The image then \textbf{blends} into a closer, brighter view of the boys running toward the viewer on the beach.
Their faces and clothing become visible.
One light-skinned boy in an orange-gold short-sleeved knit shirt and pale blue shorts smiles broadly as he runs at the right.
Behind him is a light-skinned boy in a gray-blue long-sleeved knit shirt and dark shorts.
Another boy, Black, wears a pale yellow short-sleeved knit shirt with dark shorts and runs smiling near the front.
The enormous striped beach ball \textbf{passes} close in front of them, so large that its pastel orange, green, pink, yellow, and dark panels fill much of the view and briefly \textbf{hide} the children.
The ball \textbf{rolls} or floats \textbf{past} the foreground, and the boys appear around it, laughing and reaching.
Their hair blows as they run in the bright, washed-out sunlight.
The Black boy in the pale yellow shirt moves forward with an open smile, while the boy in the orange shirt runs beside him.
A taller light-skinned boy in an olive or brownish long-sleeved shirt and white shorts joins the group, raising his arms as the ball bounces above them.
The dog is visible again at their feet as the children \textbf{gather} beneath the ball.
The boys jump together, stretching their arms high toward the oversized beach ball.
The gray-blue-shirted boy leaps with both hands up ; the taller boy in the olive shirt reaches overhead ; the boy in yellow jumps from the side ; and the boy in orange stands close by, looking up.
The shaggy dog remains low at the left, partly \textbf{hidden} by the children ’s legs.
The ball lifts out of their reach, and for a moment the children ’s hands remain raised toward the bright \textbf{sky} and foamy ocean behind them.
The ball fills the view again, drifting across a pale, \textbf{sunlit} background.
Its panels turn \textbf{past} : dark blue or black, yellow, red, pink, and orange.
Through the soft, overlapping imagery, the boys continue moving behind it.
Then the view returns to the boys from behind, running after the ball toward the bright horizon.
The orange-shirted boy is centered with his back to the viewer, arms pumping, while the gray-blue-shirted boy runs to his right.
The huge ball hovers above and ahead of them.
A closer side view follows the Black boy in the pale yellow shirt as he reaches both hands toward the large ball.
He leans forward, concentrating on it, his fingers spread as if to \textbf{push} or tap it.
The ball ’s pale green and orange panels are visible at the right edge.
He extends his arms fully, then moves alongside it, his yellow knit shirt catching the \textbf{sun}.
The action remains energetic and playful, with the ball repeatedly crossing in front of the children and briefly \textbf{obscuring} them.
The boys reappear in a loose group, still running on the beach.
The orange-shirted boy smiles directly ahead, arms out for \textbf{balance}, while the gray-blue-shirted boy turns his body as if changing direction.
The Black boy in yellow is partly visible at the left, and the taller boy in the olive shirt and white shorts \textbf{passes} close in front.
The children weave around one another, each looking toward the moving ball or toward the play around them.
The ball \textbf{passes} overhead again, and the children ’s \textbf{silhouettes} and \textbf{shadows} become softer and more abstract in the bright light.
The view returns to the backlit shoreline : the ocean is again a sparkling silver backdrop, and the boys and dog are dark outlines near the surf.
One boy jumps with both arms extended straight up as the giant ball descends above him.
The others stand or run nearby, watching its \textbf{path}.
The dog sits or pauses near the center-left, looking up or toward the children.
The jumping boy reaches high and appears to tap or toss the ball upward.
The large striped ball rises and drifts left to right above the group.
The children spread out along the sand, some with arms lifted, others running to get into position.
Their figures remain mostly \textbf{silhouetted}, with the white waves \textbf{rolling} behind them.
Bold black text appears over the beach scene while the boys continue to move beneath it.
The on-screen words read : “ Just made for boys : Donmoor shirts.
Of Ban-Lon Caprolan nylon by Allied Chemical. ” The text is centered in the upper and middle part of the image, large and \textbf{heavy}, standing out against the pale ocean.
Behind and below the lettering, the \textbf{silhouetted} boys and the shaggy dog keep playing near the surf as the oversized striped beach ball \textbf{passes} across the words and then drops back toward the children.
The final moments hold on the beach tableau : boys in motion, dog at the shoreline, waves behind them, and the product message overlaid above.

% matched lemmas: balance, blend, broad, gather, heavy, hide, obscure, pace, pass, past, path, push, roll, shadow, silhouette, sky, sun, sunlit
\end{textsample}
