\begin{textsample}{POS Dim 2 – 2020 – Score 33.00 – 2020/tv\_com\_2020\_75.txt}  \label{ex:f2_pos_042}
A red compact SUV travels along a winding \textbf{two-lane} \textbf{mountain} road, seen small against a \textbf{broad} landscape of dark evergreen forest and layered blue-green \textbf{mountains}.
The road curves through the \textbf{trees}, with pale sunlight breaking over the ridge and a \textbf{hazy} glow across the valley.
The setting shifts deeper into the \textbf{mountains} : steep forested slopes frame a road beneath a dramatic peak partly wrapped in low cloud.
The red SUV then appears close up, its wheels spinning fast over \textbf{rough} \textbf{ground}.
Mud, gravel, and dust kick up around the tires as it leaves smooth \textbf{pavement} for a rocky dirt track.
The rear and side of the \textbf{vehicle} flash \textbf{past}, showing its glossy red paint, dark tinted windows, silver trim, and athletic, rounded body shape.
Fine-print legal text appears very small along the bottom during these \textbf{driving} scenes.
From a wider view, the SUV climbs a dirt \textbf{path} through open green mountainside, \textbf{trailing} a plume of pale dust behind it.
The \textbf{vehicle} continues up the slope through a mix of forest \textbf{shadow} and bright open \textbf{grass}.
Its rear quarter is visible, with the back window and taillights partly \textbf{obscured} by dust clouds rising from the road.
The scene opens to a sweeping aerial-like view of a high \textbf{mountain} valley : green ridges, scattered \textbf{rocks}, winding tracks, and \textbf{towering} cliffs under clouds.
The red SUV is then shown from the front and side as it charges along a narrow forest road, headlights lit, dust streaming behind it.
A \textbf{brief} close-up introduces a wild owl perched in the forest.
Its face fills the view, with mottled gray-and-brown feathers, pointed ear tufts, and intense golden eyes looking straight ahead.
The SUV \textbf{splashes} through a wet, \textbf{muddy} stretch, sending water and mud outward in a \textbf{heavy} spray.
The red hood and front lights \textbf{push} through the \textbf{splash}, then the rear \textbf{badge} comes into focus under streaks of water and foam : \textbf{chrome} letters spell “ Sportage ” across the red tailgate.
The SUV keeps plowing through water and \textbf{brush}, the front grille and headlights partly \textbf{hidden} by white spray.
It emerges back onto rocky \textbf{mountain} terrain, \textbf{driving} across a \textbf{rough} hillside dotted with \textbf{stones}, shrubs, and boulders.
From farther away, the red \textbf{vehicle} moves left to right along a \textbf{dusty} track, leaving a long beige \textbf{trail} behind it.
Closer again, the front end tilts on uneven \textbf{ground}, showing the black Kia grille, bright headlamps, silver lower bumper trim, and large alloy wheels biting into the dirt.
Several close views highlight the wheels and drivetrain details.
A Kia logo is visible at the center of a black-and-silver alloy wheel as it rotates through dust.
On the red front fender, a small \textbf{chrome} “ AWD ” \textbf{badge} is shown beside the wheel arch, identifying the all-wheel-drive feature.
The SUV then \textbf{drives} across a rocky ridge under a bright \textbf{sky}, with distant blue \textbf{mountains} in the background and dust \textbf{rolling} up from the rear tires.
The front of the \textbf{vehicle} approaches steadily, its headlights on and grille centered, before the view drops to the spinning wheel grinding over gravel and \textbf{throwing} up dust.
Inside the SUV, an adult driver is seen from behind at the wheel.
The driver has short dark hair and wears a dark jacket.
Both hands are near the steering wheel while the \textbf{vehicle} faces a mountainous view through the windshield.
A dashboard screen glows in the center console, and the rearview mirror hangs above.
Windshield wipers sweep across the glass as the road and \textbf{mountains} remain visible ahead.
The commercial ends with the red Kia Sportage parked on a rocky grassy overlook among tall evergreen \textbf{trees}, \textbf{mountains} layered in the distance beneath a partly cloudy \textbf{sky}.
The SUV is shown in profile and three-quarter front view, clean and glossy after the action, standing still on the ridge.
Large white on-screen text across the lower center reads, “ 10-YEAR / 100,000-MILE WARRANTY, ” with a thin line of much smaller legal text beneath it.

% matched lemmas: badge, brief, broad, brush, chrome, drive, dusty, grass, ground, hazy, heavy, hide, mountain, muddy, obscure, past, path, pavement, push, rock, roll, rough, shadow, sky, splash, stone, throw, towering, trail, tree, two-lane, vehicle
\end{textsample}
