\begin{textsample}{POS Dim 2 – 2010 – Score 13.00 – 2010/tv\_com\_2010\_8.txt}  \label{ex:f2_pos_024}
The commercial unfolds as a montage centered on bare feet, outdoor leisure, \textbf{home} activities, and then a prescription toenail product. 1. **Beach opening** : The first frame shows an overhead view of a sandy beach with waves at the top edge.
Several colorful beach umbrellas and towels are arranged on the sand, and a person walks near the waterline. 2. **Feet in sand** : The view cuts to a low close-up of bare feet beside a pink towel on the beach.
The feet press into the sand while other beachgoers ’ legs are visible in the background near the shoreline. 3. **Home \textbf{couch} scene** : The setting shifts indoors to a bright \textbf{living} \textbf{room}.
A man \textbf{sits} barefoot on a brown leather \textbf{sofa}, reading or looking at something in his hands.
A white bulldog lies on the \textbf{couch} beside him.
A \textbf{coffee} table and open kitchen/dining area are visible. 4. **Close-up with dog** : A closer shot shows the \textbf{dog} resting on the \textbf{sofa} next to the man ’s bare foot and rolled-up jeans. 5. **Poolside lounging** : The scene changes to a point-of-view-like shot of bare feet resting on a white lounge chair near a swimming pool.
Brick paving and pool water are visible. 6. **Garden/lawn scene** : A green garden hose lies coiled on grass.
A rake or garden tool and part of a person ’s foot/leg appear nearby, suggesting outdoor yard activity. 7. **Yoga mats / exercise setting** : A close-up shows bare feet stepping or standing on colored exercise mats.
Other feet and mats are blurred in the background. 8. **White transition** : The \textbf{screen} becomes very bright and mostly white, acting as a visual transition. 9. **Feet on white background with product text** : Bare feet appear against a clean white background.
Small on-screen text near the bottom reads that prescription KERYDIN / tavaborole is FDA-approved, with a Kerydin logo at the lower right. 10. **Toenail close-up** : A close-up of toes shows one large toenail with the words “ TOENAIL FUNGUS ” written on it.
Fine print appears along the bottom, including directions about KERYDIN drops and duration of use, with the Kerydin logo at lower right. 11. **Overhead beach towels** : The commercial returns to a beach-like overhead composition.
Several people lie on striped towels arranged in a circular/radial pattern on sand, with their feet pointing toward the center.
Fine-print \textbf{safety} text and the Kerydin logo remain along the bottom. 12. **Yoga class upper-body view** : A man and woman in a yoga/exercise class raise their arms overhead.
The orange studio wall and other participants are partially visible.
Bottom fine print lists possible side effects \textbf{such} as skin peeling, ingrown toenail, redness, itching, and swelling. 13. **Yoga class feet** : A low shot shows a row of bare feet on green and blue mats during the class.
The same style of bottom white band with \textbf{safety} text and Kerydin branding is visible. 14. **Barefoot walking outdoors** : People walk barefoot across a lawn or garden path near a house and flowerbed.
Bottom text includes “ Individual results may vary, ” with the Kerydin logo on the right. 15. **Seated yoga pose** : In the exercise studio, a man and woman \textbf{sit} cross-legged on mats.
The man lifts one hand toward the side of his head while the woman \textbf{sits} upright.
Bottom text includes “ See our ad in People, ” and the Kerydin logo remains at lower right. 16. **Feet in bed** : A close-up shows bare feet under or between white sheets on a bed, with soft white fabric surrounding them. 17. **Final product shot** : The final frame shows a small bottle and applicator/dropper cap beside large text reading “ Kerydin ( TAVABOROLE ) TOPICAL SOLUTION, 5 \%. ” Additional text at the bottom gives a website and \textbf{phone} number : “ Visit www.TOETUCKER.com or call 1-844-KERYDIN for product \textbf{information}. ”

% matched lemmas: coffee, couch, dog, home, information, living, phone, room, safety, screen, sit, sofa, such
\end{textsample}
