\begin{textsample}{POS Dim 2 – 2010 – Score 14.00 – 2010/tv\_com\_2010\_78.txt}  \label{ex:f2_pos_057}
The commercial begins with a separate-looking food image : two purple takeout cartons filled with loaded curly fries sit on a dark tabletop against a black background with soft purple lights.
The cartons carry the Jack logo, with labels for “ Triple Cheese \& Bacon Curly Fries ” and “ Chili Cheese Curly Fries, ” and glowing text reads “ Jack late \textbf{night}. ” The imagery then shifts to a silver or white Volkswagen \textbf{sedan} moving through a leafy, tree-lined road.
The car is shown in glossy, high-contrast glimpses : its side profile \textbf{passes} beneath dark \textbf{branches}, then its front corner moves close to a \textbf{tree} \textbf{trunk} along the roadside.
Inside the car, the view focuses on sleek black trim near the \textbf{steering} wheel and dashboard, then on dark, textured seat upholstery with neat stitching and a visible seatbelt buckle.
The car ’s pale hood reflects the \textbf{trees} overhead as it travels forward.
A darker car appears ahead on the same road, seen from behind, with the Volkswagen following at a distance.
Small, fine-print legal text runs along the bottom of several of these \textbf{driving} images.
The scene briefly shows a metallic-looking grille or layered car structure, then the front of the silver Volkswagen beside a dark car behind it, suggesting surrounding traffic.
The Volkswagen ’s left front light and amber side marker are prominent in the foreground while the darker car sits back in the lane.
A close view of the driver-side mirror follows.
In the mirror ’s glass, a small icon shaped like two cars appears, first pale and then glowing amber, visually indicating the blind spot monitor mentioned in the audio context.
The mirror surface reflects blurred greenery and the side of a \textbf{passing} \textbf{vehicle}.
The car ’s exterior is then shown in polished close-ups : the side mirror housing, the roofline, a rectangular sunroof, and smooth silver body panels reflecting \textbf{trees} and \textbf{sky}.
A small “ IIHS Top Safety Pick+ ” \textbf{badge} appears near the upper left during some of these car-detail \textbf{shots}, with tiny explanatory text beneath it.
The silver car ’s front headlight fills the view next.
A bright circular lamp glows within a black housing, surrounded by a row of small rectangular light elements.
The headlight and grille details look sharp and premium, with the silver \textbf{bodywork} curving around them.
The setting changes to a stadium parking lot at sunset or early evening.
A silver Volkswagen Jetta \textbf{drives} or \textbf{rolls} into a tailgating area outside a large stadium with purple banners and \textbf{flags}.
People in purple-and-yellow football jerseys stand around tents, coolers, folding chairs, and parked RVs.
The Jetta stops in a marked parking space among the tailgaters.
A young woman with long brown hair, wearing a purple football jersey with a large yellow “ 35, ” stands beside the Jetta near the driver-side door.
In a close view of the side window, a nearby fan ’s purple jersey is reflected in the glass, and the woman ’s hand rests near the top of the door frame.
The car ’s silver paint, dark-tinted windows, and clean \textbf{sedan} profile are clearly visible.
The stadium lot becomes busier in a wider view.
The Jetta sits centered in the parking space, with the large stadium curving behind it and groups of fans milling around.
The brown-haired woman in the number 35 jersey stands at the car ’s side, while other fans move in the background near tents and \textbf{vehicles}.
A young man with curly dark hair, wearing a purple jersey with a large yellow “ 5, ” faces toward the women while holding a plate of food at chest height.
Other fans in purple jerseys stand behind him, including one with the number 27 visible from the back.
He appears to be talking to the women by the car.
Two young women stand beside the Jetta.
One has bright red hair, a purple zip-up hoodie, and a yellow top ; she smiles broadly.
The other is the brown-haired woman in the purple number 35 jersey ; she glances toward the red-haired woman, then looks ahead with a small, confident smile.
After the exchange, the brown-haired woman turns and walks away to the right, leaving the red-haired woman smiling beside the car.
A wide view shows the full tailgate scene again : the silver Jetta parked in front of the stadium, surrounded by fans, tents in green and purple, \textbf{flags}, RVs, and coolers.
The car remains the visual centerpiece in the busy parking-lot environment.
The background fades to a clean white screen with faint centered text reading “ Introducing lots of new. ” Then the Jetta appears again in the stadium parking lot in a polished product display.
Large text at upper left reads “ The new Jetta. ” Next to it is the “ 2014 IIHS Top Safety Pick+ ” \textbf{badge} with small supporting safety-rating text.
The silver \textbf{sedan} is shown from the front three-quarter side, parked neatly with its Volkswagen \textbf{badge} centered on the grille and its alloy wheels visible.
The commercial ends on a plain white screen with bold black text : “ Isn't it time for German engineering? ”

% matched lemmas: badge, bodywork, branch, drive, flag, night, pass, roll, sedan, shot, sky, steering, tree, trunk, vehicle
\end{textsample}
