\begin{textsample}{POS Dim 2 – 1950 – Score 7.00 – 1950/tv\_com\_1950\_52.txt}  \label{ex:f2_pos_072}
The commercial begins with a nearly black frame, with no clearly visible objects or people.
It then cuts to a black-and-white \textbf{domestic} interior, resembling a \textbf{living} \textbf{room} or study.
A woman stands near a desk or side table, holding a box-shaped object in front of her body.
The \textbf{room} contains a table lamp, shelving with books or objects, a chair or \textbf{sofa}, and other household furnishings.
The image is somewhat soft, so fine details of the object she is holding are not fully clear.
Next, there is a close-up of hands operating a small mechanical \textbf{device}.
The \textbf{device} appears box-like and has a slot or opening where a rectangular item is being inserted or adjusted.
A hand presses or guides part of the mechanism.
The exact product function is not fully clear from the frame alone, but the shot emphasizes the handling of the \textbf{device} and its moving parts.
The scene then shifts back to a darker \textbf{room} where a television \textbf{screen} or projected image is visible.
On the \textbf{screen}, a man and a child are shown together.
In the foreground or to the side, a person \textbf{sits} near a table or lamp, watching or facing the \textbf{screen}.
The surrounding \textbf{room} is dim, making the \textbf{screen} the brightest and most prominent element.
The final frame shows a product pack on a plain studio background.
The box is clearly branded “ Kodak, ” with the name printed large on the front and again on the top.
A checkerboard-like strip runs along the lower edge of the packaging.
The commercial visually ends by foregrounding the Kodak-branded product.

% matched lemmas: device, domestic, live, room, screen, sit, sofa
\end{textsample}
