\begin{textsample}{POS Dim 2 – 1960 – Score 31.00 – 1960/tv\_com\_1960\_112.txt}  \label{ex:f2_pos_003}
A large 1960s station wagon appears head-on in a \textbf{reddish}, \textbf{dusty} \textbf{haze}, its wide grille and stacked headlights \textbf{pushing} through mud or swirling dust.
As it advances, the long body comes into view : a two-tone wagon with a pale roof and upper panels, darker sides, \textbf{chrome} trim, roof \textbf{rails}, and \textbf{whitewall} tires.
The car moves \textbf{past} in profile through a rugged, open landscape of scrub, dirt, and pale \textbf{rock} \textbf{formations}, then comes to a stop beside \textbf{bushes} and \textbf{trees}.
An elderly man with long white hair and a full white beard appears near the rear of the wagon.
He has a sturdy, outdoorsy look, wearing a dark long-sleeved shirt tucked into brown trousers with a \textbf{belt}.
He climbs up the uneven \textbf{ground} beside the car and moves to the open rear cargo area.
He glances upward, then leans into the back.
The tailgate is open, revealing the wagon ’s long cargo space with the rear seats folded flat.
Several wooden planks or boards lie lengthwise inside, making the interior look like a small loading platform.
The man adjusts the boards with both hands, arranging them across the flat floor.
The playful “ Noah ’s Ark ” idea becomes visible as animals begin to appear.
Close to the man ’s waist, two small spotted big-cat cubs, likely young leopards or similar cats, move together across the rear area.
They sniff and step around one another while the man stays nearby, watching and guiding them.
He smiles faintly, looking pleased and busy.
From inside the wagon, the rear opening frames him outside as one cub climbs in, then another follows, their paws landing on the cargo floor.
The man ’s hands hover close, as if encouraging them to enter.
A white, woolly animal lies or crouches on the wooden ramp area near the rear, its pale fleece filling the foreground.
The man bends over it and pats or smooths its coat with both hands, gently urging it along.
The view then moves to a tortoise on the wooden boards, its rounded shell and thick legs visible as it inches forward.
The man continues working around the tailgate, looking down into the cargo area with a patient, caretaker-like expression.
Inside the wagon, several animals are now visible in the back, including woolly, goat-like or sheep-like forms with horns and shaggy coats packed under the roof.
A wider view shows the full wagon parked beside a sloping \textbf{rock} face, with animals \textbf{gathered} around it.
On the rocky hillside above are several camels and smaller animals ; nearer the car are larger animals, including what appears to be an elephant and other dark, bulky shapes.
The elderly man stands at the right side of the car near a ramp or tailgate platform, dwarfed by the station wagon and the animals around it.
He then reaches up and handles a large long-necked bird or birdlike animal, grasping it around the body and neck as he guides it upward.
The animal ’s long neck bends and sways while he lifts and steadies it, his face partly \textbf{hidden} behind the animal as he works.
More animals crowd the ramp.
Two striped tigers move across the wooden boards near the rear of the wagon, one darker and one lighter in tone, their long bodies filling the space as they step carefully \textbf{past} the man.
Their striped flanks \textbf{pass} close together, tails low, while a large elephant stands in the background on the \textbf{rocks}.
The man remains behind them, visible between their bodies, calm and watchful as they board.
At the side of the wagon, the man stands beside a rear side window.
His white-bearded face is reflected in the glass.
An animal ’s head or neck \textbf{passes} between him and the car, briefly \textbf{brushing} close to the window, and he looks at it with a small, amused smile.
A large pale animal then crosses very close in front of him, its body filling the view and momentarily \textbf{obscuring} his face.
When the animal \textbf{passes}, the man looks upward again, as if checking the next creature in line.
A camel approaches from the right, \textbf{towering} above the man and the car.
The man stands below it, one arm raised, gesturing for it to move forward.
Its long neck and legs dominate the scene as it steps toward the ramp.
The man ’s face appears beneath the animal ’s body as it \textbf{passes} overhead, then a large hoofed foot lands on the wooden boards.
The boards flex visually under the weight, emphasizing the \textbf{heavy} load being taken into or over the wagon ’s rear area.
The man looks serious and focused, continuing to guide the boarding process.
With the animals loaded, the man moves to the back of the station wagon and swings the large tailgate closed.
From a low angle, he \textbf{pushes} the pale rear door upward and then presses it firmly into place with both hands, patting and smoothing the outside as if making sure everything is \textbf{secure}.
He smiles as he finishes, then steps away from the rear.
Inside the front of the car, the driver ’s area is crowded with animals.
A young big cat sits near the \textbf{steering} wheel and dashboard, its paws up on the seat or console, while another animal ’s head is partly visible beside it.
The dashboard has a large round steering wheel and circular gauges.
The elderly man leans in from the driver ’s side, bending around the animals to get into position.
He settles behind the wheel, reaching forward with one hand, while the animals shift in the passenger area beside him.
Outside the windshield, the rocky hillside is visible, making the car still feel parked in the same wild, \textbf{outdoor} setting.
The commercial then returns to exterior views of the station wagon.
The front grille and stacked headlamps are shown prominently, then the long side of the car \textbf{passes} by, highlighting the length of the body, the \textbf{chrome} trim, the large side panels, and the \textbf{whitewall} tires.
The wagon moves through a wooded area, partly \textbf{hidden} by \textbf{branches} and \textbf{leaves} in the foreground.
Animals remain around it, including bulky \textbf{silhouettes} near the car, while the \textbf{vehicle} continues away through \textbf{rough} \textbf{ground} and \textbf{trees}.
Finally, the wagon is seen from behind \textbf{driving} along a narrow, wooded \textbf{path}, receding into the distance under overhanging \textbf{branches}.
Large white block letters appear across the lower part of the screen reading “ THE 1967 AMERICAN MOTORS. ” The car continues away behind the text, its pale rear and long roofline still visible as it disappears deeper into the sepia-toned woods.

% matched lemmas: belt, branch, brush, bush, chrome, drive, dusty, formation, gather, ground, haze, heavy, hide, leaf, obscure, outdoor, pass, past, path, push, rail, reddish, rock, rough, secure, silhouette, steering, towering, tree, vehicle, whitewall
\end{textsample}
