\begin{textsample}{POS Dim 2 – 1970 – Score 12.00 – 1970/tv\_com\_1970\_108.txt}  \label{ex:f2_pos_080}
The commercial begins outside a small-town storefront in warm daylight.
A dark, open-top Jeep with a soft black roof is parked along the curb in front of shop windows and signs.
In the driver ’s seat sits a male-presenting, middle-aged man wearing a dark cap, glasses, a plaid shirt, and a light-colored vest.
He holds a CB radio microphone up near his mouth while seated behind the \textbf{steering} wheel, looking forward and slightly down as if speaking into the radio.
The Jeep ’s windshield, side supports, and open door area frame him, and the \textbf{vehicle} has a rugged, outdoorsy look.
The scene changes to the Jeep from behind.
Through the rear window, the driver is seen from the back, still at the wheel.
Across the lower back of his light vest is visible lettering that reads “ MIDLAND CB ” with “ CONVOY BUDDY ” beneath it, matching the product and slogan.
A long antenna-like rod is visible inside or near the rear window.
The Jeep pulls away onto a road, its rear \textbf{spare} tire centered on the back door and a red fuel can mounted on the left rear.
Dust or exhaust rises behind it as it \textbf{drives} off into a sunny \textbf{rural} area with bare \textbf{trees} and low hills in the distance.
Inside the \textbf{vehicle}, a black Midland CB radio is mounted under the dashboard.
It has a rectangular face with a small display area, rows of knobs, and a large circular control on the right.
A hand reaches in and adjusts the knobs, demonstrating the radio as an active, usable piece of equipment.
The setting shifts to a stream or shallow river.
A male-presenting fisherman, middle-aged to older, stands knee-deep in rippling water.
He wears a gray bucket-style hat, a plaid shirt, a light fishing vest, waders, and a small pack or gear bag on his back.
He holds a fishing rod in one hand, but instead of casting, he brings a small radio microphone close to his mouth with the other hand.
A coiled cord runs from the microphone to a portable radio unit hanging from his shoulder or \textbf{belt}.
He stands among reflective water and natural greenery, looking as though he is calling for help or communicating while fishing.
The Jeep is then seen driving along a dirt or \textbf{rural} road through wooded hills.
It approaches and \textbf{passes} by, showing its front lights, open sides, soft top, large tires, and rear-mounted \textbf{spare} tire.
The driver is visible through the windshield and side opening.
He continues \textbf{driving} with one hand on the \textbf{steering} wheel, focused on the road.
A closer view through the windshield shows the driver ’s face.
He is still wearing his dark cap and glasses, with his light vest over a patterned shirt.
He grips the \textbf{steering} wheel and looks ahead, then slightly to the side, as if responding to the radio communication.
Back at the stream, the portable CB unit is shown close against the fisherman ’s side.
It is a dark rectangular device hanging from straps, with a coiled cord leading to the hand microphone.
The fisherman lifts the microphone toward his mouth.
His face is now clearer : he has a moustache, weathered features, and a friendly, intent expression under the brim of his hat.
He speaks into the microphone while standing in dappled sunlight near the water.
Inside the Jeep again, the driver holds the microphone near his mouth while \textbf{driving}.
Outside the windows, \textbf{trees} and roadside scenery blur \textbf{past}.
He keeps one hand near the wheel and appears to answer the fisherman through the CB.
The mounted Midland radio is shown again under the dashboard, its knobs and display clearly visible.
A hand adjusts or reaches near it, and a blue gearshift knob sits below, emphasizing the radio ’s placement in the \textbf{vehicle}.
The Jeep then travels along a narrow wooded road beside a \textbf{fence} or bridge railing.
The soft top and side windows reflect \textbf{trees} as it moves \textbf{past}.
The rear \textbf{spare} tire and red fuel can remain prominent on the back as the \textbf{vehicle} continues toward the fishing area.
The fisherman appears again in the water, now smiling broadly.
He raises one arm high in greeting or thanks while holding his fishing rod across his chest.
Behind him, the water sparkles.
A wide view reveals the Jeep stopped or moving slowly on a small wooden bridge above the stream, with the fisherman below in the water raising his arm toward it. \textbf{Trees} and \textbf{brush} surround the bridge, creating a secluded \textbf{outdoor} fishing spot.
The final image keeps the Jeep on the bridge and the fisherman below, then large bold on-screen text fills the lower portion of the picture : “ MIDLAND CB ” above “ CONVOY BUDDY. ” Smaller text beneath reads “ Midland International Corporation. ” The visual closes by linking the Jeep driver, the fisherman, and the Midland CB radio as connected companions through the product.

% matched lemmas: belt, brush, drive, fence, outdoor, pass, past, rural, spare, steering, tree, vehicle
\end{textsample}
