\begin{textsample}{NEG Dim 8 – 1950 – Score -2.00 – 1950/tv\_com\_1950\_58.txt}  \label{ex:f8_neg_029}
The commercial opens in a black-and-white domestic laundry or utility room.
A woman stands on the left near a washing machine or laundry counter, wearing a short-sleeved dress with a light patterned apron tied at the waist.
A man stands on the right at a workbench or counter, wearing a dark long-sleeved shirt with the sleeves rolled and light trousers.
Behind them are stairs, wall panels, and shelves or tools, giving the room a practical basement-laundry feel.
The man is bent slightly over the counter, handling a white cloth or handkerchief.
The woman notices what he is doing and walks toward him.
As she approaches, he looks down at the cloth in his hands.
She points at it, and they both focus on it.
The cloth is unfolded between them and appears badly marked with dark \textbf{smears} and stains across much of its surface.
The woman takes hold of one side and inspects it closely while the man, smiling a little, holds the other side and watches her reaction.
She spreads the stained handkerchief wider so the dirty areas are clearly visible.
The image shifts to a presenter in a plain studio setting.
He is a neatly dressed adult man in a light suit jacket, white shirt, and dark tie.
He holds a large rectangular box of detergent angled toward the viewer.
The package has the brand name “ Dash ” printed in very large vertical letters on the front.
He turns and tilts the box so the name is easy to see, then holds it upright beside his chest.
The background is simple and softly lit, with a few laboratory-like glass containers partly visible behind him, reinforcing that a test or \textbf{demonstration} is about to take place.
The \textbf{demonstration} area shows two clear glass jars side by side on a platform, each with a vertical stirring rod descending from an overhead frame.
Each jar contains water.
A small label near the left jar identifies it as “ LOW SUDSER A, ” while a label near the right jar reads “ DASH. ” A Dash box stands prominently to the right of the jars, with the large “ Dash ” name facing forward.
Another box or sign marked “ LOW SUDSER A ” sits to the left.
A hand holds the Dash package near the right jar, then sets it down at the side.
Spoons are brought in from both sides.
A spoonful of detergent is added to the left jar, and another spoonful is added to the right jar.
As the \textbf{powders} fall in, the water in both jars begins to turn cloudy and foamy at the bottom.
In front of the jars, on a flat white tray, a long strip of cloth is laid out.
A dark oily-looking streak is poured or spread across it, forming a heavy stain through the middle.
Hands enter from both sides and divide or handle the cloth into two pieces.
One stained cloth piece is lifted toward the left jar, and a matching piece is lifted toward the right jar.
Each piece is pushed down into its jar, one into the low-sudser solution and one into the Dash solution.
The stirring rods move in the jars, agitating the water and cloth.
Foam rises in both, but it remains relatively low, swirling around the cloth rather than overflowing.
The two jars churn side by side, with the left labeled “ LOW SUDSER A ” and the right labeled “ DASH, ” while the Dash box remains visible on the right.
As the agitation continues, the water in the right jar gradually becomes noticeably darker than the water in the left jar.
A hand points at and gestures near the right jar, drawing attention to the murkier water around the Dash-washed cloth.
The cloth pieces tumble and fold under the rods.
The right jar ’s liquid looks more gray and dirty, while the left jar stays lighter by comparison.
Both jars still have a layer of white suds near the surface, but the difference in the water beneath becomes clearer.
Hands then reach into both jars at the same time and pull out the two cloth pieces.
The left-hand cloth is lifted from the low-sudser jar, and the right-hand cloth is lifted from the Dash jar.
Water drips back into the jars as the pieces are \textbf{squeezed} and opened.
The left piece still shows visible dark streaks and smudges.
The right piece, held beside it, appears much whiter and cleaner.
The two cloths are stretched out side by side in front of the jars for comparison : the left piece remains dingy and stained, while the right piece looks clean and bright.
The Dash box is still visible at the right edge of the display.
The scene returns to the laundry room.
The man and woman stand at a counter beneath a window with curtains.
Outside the window, dark leafy shapes are visible.
On the counter are neat stacks of folded white towels and other white laundry, with a Dash box placed upright in the center so the large brand name faces forward.
The woman, still in her dress and patterned apron, stands on the right, holding or presenting a white piece of laundry.
The man stands on the left, leaning one hand near the counter and looking at her and the laundry.
He reaches toward the cloth, takes it, and unfolds or examines it in his hands.
His expression softens into a pleased smile as he looks down at the clean fabric, then back toward the woman.
The final display focuses on the counter filled with clean white laundry.
Several folded towels are stacked in a tall pile on the left, more folded and draped white cloths lie across the foreground, and the Dash detergent box stands upright near the center-right.
The large “ Dash ” name on the package is clearly visible.
Over the clean laundry, bold on-screen text appears : “ Dash Gets clothes cleaner. ” The words are large, bright, and placed across the lower left and bottom of the image, with “ Dash ” especially prominent.

% matched lemmas: demonstration, powder, smear, squeeze
\end{textsample}
