\begin{textsample}{NEG Dim 8 – 1980 – Score -8.00 – 1980/tv\_com\_1980\_22.txt}  \label{ex:f8_neg_051}
A close view of a white electric stovetop shows a hand pressing a tan rectangular piece, like a block of sandpaper, flat against the enamel surface.
Black \textbf{coil} burners sit to either side, and chrome control knobs are visible along the back edge.
The hand rubs the tan block back and forth over the stovetop, suggesting an exaggerated, harsh way to clean it.
The view widens to a home kitchen.
A middle-aged man with light skin, short dark hair, and a beige button-down shirt stands at the stove.
A large brass- or copper-colored pot sits on the right side of the stovetop.
The man holds the tan cleaning block in one hand and looks down at the stove, then toward the viewer, as if presenting the \textbf{example}.
The kitchen behind him has dark wood cabinets, a built-in oven, a sink area, and bright daylight coming from a window.
A teal \textbf{cylindrical} can labeled in large white letters “ SCOURING \textbf{POWDER} ” stands upright on the stovetop between the black \textbf{coil} burners.
A crumpled white cloth or paper towel lies beside it.
The can is presented alone in the center of the stove surface, making it the focus.
The man appears again from the chest up in the kitchen, facing forward.
He then raises a white plastic bottle with a dark oval label and yellow lettering reading “ Soft Scrub, ” holding it near his shoulder so the label faces outward.
The \textbf{demonstration} moves back to the stovetop.
Small white text at the top reads “ USE ONLY AS DIRECTED. ” The white stove surface around one burner is \textbf{smeared} with yellowish-brown spills and stains.
The copper-colored pot remains on the left.
The man holds a lavender rectangular sponge in one hand and the Soft Scrub bottle in the other.
He tilts the bottle downward and \textbf{squeezes} a line of thick white cleanser onto the sponge.
He sets the bottle upright nearby with the Soft Scrub label still visible, then presses the lavender sponge onto the stained white enamel.
With his other hand he scrubs in short strokes around the burner area, moving the sponge across the brownish spill marks.
The white cleanser spreads into a pale film as he works.
The pot stays at the left edge of the stove, its side marked with cooking stains, while the black \textbf{coil} burner sits just behind the cleaning area.
The scrubbing continues across the front-right area of the stovetop.
The sponge moves back and forth, then side to side, covering the stained patch.
The Soft Scrub bottle stands in the background to the right, label facing forward, while the man ’s hand keeps the sponge flat against the surface.
As he wipes, the area looks cleaner and whiter, with fewer visible stains.
He lifts the sponge slightly and moves it toward the pot, then sets it aside near the pot handle.
With his free hand, he rubs a fingertip across the cleaned white surface, tracing along the edge of the wiped area as if checking for leftover grit or residue.
The man returns in a medium view, facing the viewer in the kitchen.
He holds up a small pinch or speck between his fingers near his face, using the gesture to illustrate what has been removed or what is not left behind.
The final product display returns to the stovetop.
The teal “ SCOURING \textbf{POWDER} ” can stands on the left, with the pot on the right in the background.
Large white on-screen text appears over the stove : “ Cleans like a scouring \textbf{powder}, but doesn't \textbf{scratch} like one. ” A hand slides the white Soft Scrub bottle into the foreground, placing it in front of the scouring \textbf{powder} can.
The bottle remains standing on the left side of the screen, label facing forward, while the slogan fills the right side over the stovetop.

% matched lemmas: coil, cylindrical, demonstration, example, powder, scratch, smear, squeeze
\end{textsample}
