\begin{textsample}{NEG Dim 8 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_72.txt}  \label{ex:f8_neg_010}
The commercial appears in a mid-20th-century black-and-white/monochrome style, with visible film grain and some image wear.
At the start, the frame shows a simple cartoon-style television set against a plain light background.
The TV cabinet is drawn in perspective, with a screen on the front.
Inside the screen is an anthropomorphic face with wide eyes, raised eyebrows, and a downturned mouth, giving the television a worried or unhappy expression.
The set has small circular controls and a rectangular panel below the screen.
A “ tvdays.com ” watermark appears at the lower right.
By around 16 seconds, the commercial cuts to a text-heavy promotional graphic.
Large white \textbf{capital} letters read : “ MORE RCA PICTURE TUBES NOW IN USE ”.
Below, smaller text reads : “ …than any other make! ” The background is dark and mottled, with a simplified outline drawing of a picture tube or television tube behind the text.
The RCA logo appears near the lower right area of the central graphic, and the “ tvdays.com ” watermark remains at bottom right.
At the final sampled frame, the commercial displays the RCA logo prominently in the center : the letters “ RCA ” inside a circular outline, with a lightning-bolt-like underline or emblem beneath the letters.
The background is dark with scattered bright specks resembling stars, sparks, or a glittering field.
The “ tvdays.com ” watermark is still visible in the lower right corner.
Overall, the visuals move from a cartoon personified television set to a factual claim about RCA picture tubes, and then to a closing brand-logo image emphasizing RCA.

% matched lemmas: capital
\end{textsample}
