\begin{textsample}{NEG Dim 8 – 2010 – Score -4.00 – 2010/tv\_com\_2010\_108.txt}  \label{ex:f8_neg_071}
The commercial opens in a public outdoor \textbf{demonstration} area, set up in front of a bright blue OxiClean backdrop covered with repeating white-and-blue OxiClean logos.
A middle-aged man with short dark hair stands behind a clear rectangular tank on a white table.
He wears a bright blue button-down shirt with a small OxiClean logo on the chest and khaki pants.
To his right sits a large blue-and-yellow OxiClean tub on a white pedestal.
Several young girls and women stand to his left, watching with curious smiles.
The man gestures toward the tank, then leans in and pours a scoop of white \textbf{powder} into dark reddish-brown liquid inside the clear container.
In a close view of the tank, the white \textbf{powder} spreads through the liquid in cloudy plumes.
The water is initially stained deep red and orange, but thick white clouds bloom outward and downward, pushing through the discoloration.
As the mixture churns, the dark colour fades in large patches, revealing lighter areas and glimpses of coloured items at the bottom of the tank.
Within a few moments, most of the liquid has turned milky white, with only a band of orange-brown colour lingering near the top and right side.
The man then stands upright again, smiling broadly with his arms slightly out, while the onlookers beside him smile at the result.
The scene changes to an adult woman with long brown hair and medium-toned skin standing at a table in front of the same OxiClean logo backdrop.
She wears a light pink patterned shirt and holds up a light blue shirt.
A large dark stain, roughly shaped like a spill, covers the lower front area of the shirt.
A white plastic wash basin sits in front of her on the table.
She lowers the stained shirt into the basin and works it with both hands in sudsy water.
Her hands press, rub, and agitate the fabric ; foam gathers around the shirt as she kneads it underwater.
She then lifts the blue shirt out of the basin.
It is wet and covered in patches of white suds, but the large dark stain is no longer visible.
She holds it up by the shoulders and smiles with a wide, surprised expression.
Next, a fair-skinned woman with red hair tied up in a bun stands in front of the OxiClean backdrop wearing a white shirt with black horizontal stripes.
She holds a small white plush teddy bear.
The bear has a reddish-purple stain on one lower leg or paw area.
In a close view, the stained paw is held over a clear tray containing liquid.
A white nozzle or applicator is \textbf{aimed} at the stained plush, and liquid is applied directly to the reddish patch.
The stain begins to bleed out into the liquid below, creating a dark puddle beneath the bear ’s paw while the plush fibres look progressively lighter.
The woman then looks down at the bear and smiles, appearing pleased and surprised as she holds it close.
Another adult woman, fair-skinned with shoulder-length blonde hair, appears at a table in front of the same blue OxiClean backdrop.
She wears a cream-coloured top and stands over a pale wash basin.
She handles a strip of lace or delicate fabric, dipping and rubbing part of it in sudsy water.
A close view shows the lace lifted vertically : the upper portion remains dingy beige and brown, while the lower portion is bright white and foamy, creating a clear before-and-after contrast along the same piece of fabric.
Her hand, covered in suds, supports the cleaned section near the basin.
She looks down at the lace, then raises her face with an impressed expression.
The commercial then moves to a bright, clean laundry-room setting.
A blue OxiClean Versatile Stain Remover tub with a yellow lid sits on a glossy white counter.
Behind it are a washing machine, shelves, and neatly folded towels.
A glowing blue-white graphic burst appears to the left of the tub, resolving into large playful blue-and-white text that reads, “ Gets The \textbf{Tough} Stains Out! ” The OxiClean tub remains on the right, with its bold “ OxiClean ” logo visible on the front and a yellow “ 65 ” marking on the package.
The final product display shows a white laundry counter with folded colourful towels stacked on the left and a white laundry basket filled with clothes on the right.
In the center stands a dark blue pouch labeled “ OxiClean Laundry Paks High Def, ” with a small “ 47 paks ” marking near the top.
A hand places a large dark blue OxiClean liquid laundry detergent bottle beside it.
The bottle has a built-in handle and a silver cap, with the OxiClean logo and “ High Def ” labeling on the front.
The hand withdraws, leaving the pouch and bottle standing side by side as the final clean, bright product image.

% matched lemmas: aim, demonstration, powder, tough
\end{textsample}
