\begin{textsample}{NEG Dim 8 – 2000 – Score -2.00 – 2000/tv\_com\_2000\_56.txt}  \label{ex:f8_neg_077}
The commercial opens on a nearly black frame, then cuts to a large basketball arena scoreboard.
The scoreboard reads “ MAKE SOME NOISE, ” with “ HOME ” and “ VISITOR, ” and shows a very close score : Home 78, Visitor 80, with 00:04 remaining in the half or game display.
The stands around the scoreboard are filled with spectators.
The action moves to a college-style basketball game in progress.
A wide view shows players in white uniforms and dark/blue uniforms near the basket, with cheerleaders and spectators along the baseline.
A closer shot shows two players facing each other ; one white jersey has the name “ DENSEN ” and number 25 visible.
Cheerleaders with silver pom-poms stand behind them.
Another court-level shot shows players spaced around the key as one player appears to be preparing to shoot or pass.
The commercial then cuts to spectators in the stands.
A group of fans, including children and adults, lean forward and react intensely.
A white \textbf{barrier} in front of them has sports-style graphics, including a large letter “ H ” on the right.
The image briefly breaks into horizontal bands, as if the video signal or screen image is disrupted or split.
The basketball game returns in a wide arena shot, showing players running upcourt and a crowd in the background.
The scene then shifts away from the arena to an indoor concourse or food-court-like area.
A man with reddish hair stands among pedestrians and holds a mobile phone to his ear.
To his left is a large hot-dog-shaped display or stand with the word “ HOT DOGS ” visible.
The same man is then shown from behind, still on the phone, looking up at a wall-mounted television screen showing the basketball game.
Large green letters on the wall below the screen include “ DOGS, ” suggesting a food-service location.
An overhead shot shows people lined up or milling around a counter area below.
Inside a concession stand, a \textbf{worker} in a white apron and cap stands near a \textbf{row} of machines, some with orange/red containers.
A television is visible above the equipment.
The \textbf{worker} raises a hand as if reacting to the game.
Another shot shows a young employee wearing an apron carrying a tray with several paper cups or cartons ; small white legal-style text appears along the bottom of the frame but is too small and blurred to read clearly.
A nighttime exterior shot shows people gathered outside a storefront with many televisions displayed in the window.
A red car is parked at the curb.
The televisions appear to be showing the same basketball game, and small unreadable legal text remains at the bottom of the frame.
The commercial cuts back to the arena.
A student pep band or drum section wearing blue “ STATE ” shirts is shown in the stands.
Several people hold drumsticks and percussion instruments.
The basketball game resumes : a player in a dark/blue uniform takes a free throw or set shot.
A close shot of the rim shows the ball dropping through the net.
The concession \textbf{worker} with the tray is shown reacting enthusiastically.
Fans and cheerleaders in the arena also react, with one dark-uniformed player cupping his hands near his face as if shouting.
Another rim shot shows a player or person in blue near the basket falling or sliding under the hoop after the play, while cheerleaders stand along the baseline.
The pep band celebrates, raising sticks and instruments.
Players in dark/blue uniforms gather together and celebrate, smiling and reaching toward each other.
Near the end, a close-up shows a hand holding an open flip phone.
On the phone ’s small screen, a video image of people appears, suggesting live or recorded video on the device.
Some small text appears at the lower left of the frame, but it is not legible in the sampled image.
The final frame shows an abstract green/turquoise circular or spherical logo-like shape on a white background, without readable text in the sampled frame.

% matched lemmas: barrier, row, worker
\end{textsample}
