\begin{textsample}{NEG Dim 8 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_22.txt}  \label{ex:f8_neg_011}
The commercial begins with an almost entirely dark/black frame, with no clearly visible objects or people.
At about 0.7 seconds, the scene changes to a black-and-white cartoon image.
A stylized chicken or hen is shown sitting on a nest or straw-like ground.
Behind it is a fence or wire-mesh pattern, suggesting a barnyard or poultry enclosure.
The chicken faces slightly to the right with its beak open, but no audio or dialogue can be inferred from the frames.
Much later, around 31.9 seconds, the commercial cuts to a product display.
Multiple identical rectangular tins or boxes are stacked in \textbf{rows} on a store-style display shelf.
The labels repeatedly show the brand/name “ BAKER ’S ” and large text that appears to read “ 4-in-1. ” The product packaging is arranged to fill most of the frame, emphasizing repetition and availability.
In the next two frames, the camera or framing moves closer/lower toward the display.
The same \textbf{rows} of “ BAKER ’S 4-in-1 ” packages remain visible, while the lower part of the display becomes more prominent.
A larger promotional panel or package sits at the bottom front ; it includes a product image and text, though not all wording is fully legible.
A small hanging or standing tag/card is also visible near the bottom right of the display.
The final frame shows a clearer end-card style product shot.
On the left is a large tin labeled “ BAKER ’S 4-in-1, ” with additional listed uses visible on the label : “ ICING, ” “ FROSTING, ” “ FUDGE, ” and “ SAUCE. ” To the right is a cup and saucer.
Large bold superimposed text across the image reads : “ DOUBLE YOUR MONEY BACK. ” The composition presents the product next to serving ware and highlights the money-back offer visually.

% matched lemmas: row
\end{textsample}
