\begin{textsample}{NEG Dim 8 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_70.txt}  \label{ex:f8_neg_030}
The commercial is in black and white and unfolds as an outdoor scene followed by close-up product imagery. 1. **Opening outdoor scene** : The first frame shows a man and a woman standing outside on a grassy area.
There are large rectangular structures in the background, possibly numbered or marked buildings/booths.
The woman stands in the foreground facing the man ; the man is turned partly away, with one arm raised near his back or shoulder. 2. **Product and props on a surface** : The scene cuts to a close-up of a dark tabletop or \textbf{bench}.
Several cylindrical objects, possibly cans or tubes, are arranged beside a cigarette pack.
A man ’s head is visible behind or just beyond the table edge.
The cigarette pack appears to be **Chesterfield**, though some smaller text is not fully legible. 3. **Man and woman conversing visually** : The next shot shows a man and woman facing each other outdoors.
The man is on the left and appears to hold something in one hand.
The woman is on the right, smiling.
Behind them are the same kind of tall rectangular structures, one marked with the number **4**. 4. **Close-up of clothing/pocket area** : The camera cuts to a close-up of a light-colored jacket or coat.
The frame focuses on the torso area, including a pocket seam or opening.
No face is visible. 5. **Cigarette pack used playfully with the woman ’s hair** : A close-up shows the woman smiling broadly in profile.
A hand holds or places a cigarette pack and several cigarettes near or in her hair, as if arranging them like hair accessories.
The pack again appears to be Chesterfield.
The woman ’s expression is cheerful. 6. **Cigarette being smoked** : The commercial then cuts to an extreme close-up of a person ’s mouth holding a cigarette.
A hand is near the cigarette, and smoke is visible rising from the lit end.
The face is only partially shown, mainly the nose, lips, fingers, and cigarette. 7. **Product claim overlay** : A layered shot shows a hand holding a cigarette pack and cigarette, with the word **“smoother”** displayed in large white lowercase letters across the image.
The background remains smoky and soft-focused. 8. **Final product display** : The final frame shows a large cigarette pack labeled **“Chesterfield KING Cigarettes”** on the right.
On the left, large script text reads **“They Satisfy.”** The cigarette pack has cigarettes protruding from the top, emphasizing the product packaging as the closing visual.

% matched lemmas: bench
\end{textsample}
