\begin{textsample}{NEG Dim 8 – 1970 – Score -1.00 – 1970/tv\_com\_1970\_83.txt}  \label{ex:f8_neg_045}
The commercial appears to take place inside a grocery or retail store and unfolds as a sequence involving a store employee, a uniformed officer, shoppers, and packages of Charmin.
At the beginning, the camera shows a close view of a display of rounded tan items arranged in \textbf{rows}, with red produce or decorations behind them.
Several hands reach in from the left and press or handle the items.
One person is wearing a bright blue sleeve.
The scene cuts to a middle-aged man in a white store coat with a black bow tie and glasses.
He turns his head as if reacting to something off-screen.
The next shot shows an older man in a dark uniform and peaked cap, possibly a police officer or guard, looking back toward the camera or toward the store employee.
The store employee is then shown in close-up facing the uniformed man ; his glasses sit low on his nose, and he appears to be speaking or explaining something.
The camera returns briefly to the display where hands continue touching or pressing the rounded items.
Then it cuts back to the store employee and uniformed man in conversation.
A wider shot reveals both men standing in an aisle.
In the background, several women stand near a display.
Behind them is a sign, partially visible, that reads “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” A close-up shows a shopper ’s hands holding a large package of Charmin.
The package features a baby ’s face and the brand name “ Charmin ” in large letters.
The shot then returns to the wider aisle view, with the store employee and uniformed man looking toward the women and the display.
The camera cuts to a close-up of the sign : “ PLEASE DO N’T SQUEEZE THE CHARMIN, ” written in large, hand-lettered black text on a white board.
Below the sign, the tops of Charmin packages are visible.
Two women are then shown standing in front of the Charmin display, each holding a package.
One woman has dark hair and wears a dark polka-dot blouse ; the other has reddish hair and wears a light-colored top.
Both hold Charmin packages with baby images on the front.
Their facial expressions are initially restrained, then later they smile and appear amused.
The uniformed man is shown holding a Charmin package while the store employee stands beside him.
The uniformed man looks down at the package and presses or grips it with both hands, examining it closely.
In a closer shot, he continues holding the package in front of his chest and looking at it with a serious expression.
The background shelves are softly visible.
The two women are shown again smiling in front of the Charmin display.
The uniformed man continues to inspect the package, then looks sideways.
The store employee, now also holding a Charmin package, smiles broadly while the uniformed man stands beside him holding another package.
A close-up of the store employee shows him smiling with his glasses low on his nose.
Near the end, the commercial shows a product display : several rolls or packages of Charmin arranged in a \textbf{row} beneath the same sign reading “ PLEASE DO N’T SQUEEZE THE CHARMIN. ” The visible packages include different color accents and baby images on the front.
The final frame cuts to black.

% matched lemmas: row
\end{textsample}
