\begin{textsample}{NEG Dim 8 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_62.txt}  \label{ex:f8_neg_046}
The commercial opens on a clean white screen with the “ medifacts ” logo in turquoise and dark blue.
A pale turquoise silhouette of a human figure stands behind the wordmark, and the smaller words “ HEALTHCARE INFORMATION ” appear underneath.
A blonde, light-skinned woman presenter appears in front of fully stocked store shelves filled with Microban 24 products.
She wears a black blazer over a white shirt with a small “ medifacts ” logo near the lower edge of the jacket.
To her left are rows of tall yellow and green bottles with purple labels, arranged in neat display trays.
A central yellow display panel shows Microban 24 \textbf{packaging} and the promise of killing bacteria for 24 hours.
The presenter faces forward, gesturing with open hands and then bringing her hands together as she speaks.
The scene shifts to a close view of a hand sliding along a silver stair railing in a bright home interior.
Red, stylized germ shapes appear on the railing where the hand has touched it.
The word “ \textbf{Dramatization} ” is visible in small text near the bottom, and a small “ medifacts ” watermark sits at the lower right.
The red germ icons multiply along the rail as the hand moves.
The imagery expands into a four-part domestic montage showing common household surfaces being touched.
In one section, a person in a purple long-sleeved top grasps a shiny metal door handle, leaving red germ shapes on and around it.
In another, hands use a bathroom sink faucet, where red germs appear on the faucet handle.
A third section shows a blue backpack with white dots being handled near wall hooks, with red germs collecting on the hook area and bag handle.
The fourth shows the stair railing again, now with red germs scattered along it as someone passes by.
The overall impression is of germs being transferred to frequently touched surfaces around the home.
A single Microban 24 sanitizing spray can then stands centered on a white surface, with shelves of matching products blurred behind it.
The can is yellow with a purple label and an orange cap.
The label reads “ Microban 24 Hour ” and “ Sanitizing Spray. ” In a bright living room, a dark-haired woman in a purple long-sleeved top sprays a white tabletop.
She stands on the left side of the table, leaning slightly forward with the can in her hand.
Red germ shapes cover the tabletop in the foreground.
In the background, a young boy sits at a low play table near a gray sofa, surrounded by toys and colorful household items.
A turquoise text bar appears across the lower part of the screen reading, “ Spray on and allow to dry, ” with small fine print below.
The commercial continues with a split view : on the left, the woman sprays the tabletop ; on the right, a close-up hand sprays a Microban 24 can toward a silver door handle.
Red germ shapes cluster around the handle.
The turquoise instruction bar remains, and then changes to “ Kills 99.9 \% of viruses and bacteria initially. ” As the product is sprayed, the red germ shapes near the handle fade and thin out.
Back at the tabletop, the woman continues spraying from the left edge of the screen.
The red germ shapes spread across the white surface but begin to disappear where the spray passes.
The child remains softly visible in the background at his play table.
A turquoise text box near the upper right repeats, “ Kills 99.9 \% of viruses and bacteria initially. ” Fine print runs along the bottom, including a note that the image is a \textbf{dramatization} and that the product ’s 24-hour protection is for bacteria on non-porous, non-food-contact surfaces.
The text changes to “ Kills 99.9 \% of the virus that causes COVID-19*. ” The tabletop becomes clean and white as the remaining red germ shapes vanish.
The woman lowers the spray can slightly, still standing beside the table, while the boy continues playing in the blurred background.
A blue scientific-style comparison graphic appears.
The left panel is labeled “ UNTREATED HARD SURFACE ” and shows a dark handprint on a blue background.
The right panel has a Microban 24 Hour shield icon and a mostly clean blue surface.
A circular marker between the panels reads “ 0 HOURS. ” A turquoise bar and fine print run along the bottom.
The graphic then advances to “ 13 HOURS. ” On the untreated left side, the handprint glows with green and yellow bacterial-looking growth, while the treated right side remains mostly clean under the Microban shield.
A turquoise banner reads, “ \textbf{Protect} your home against bacteria for 24 hours. ” The presenter returns in the store aisle, now holding a yellow Microban 24 sanitizing spray can upright with both hands, presenting it toward the viewer.
The shelves beside and behind her are packed with matching Microban 24 bottles and cans, and a yellow display panel again highlights the 24-hour message.
The commercial ends on a softly blurred home background with the young boy at a table.
Over the blur, the “ medifacts ” logo appears in turquoise and dark blue, followed by the website “ mymedifacts.com ” centered across the screen.

% matched lemmas: dramatization, packaging, protect
\end{textsample}
