\begin{textsample}{NEG Dim 8 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_101.txt}  \label{ex:f8_neg_054}
A young blonde girl, about early elementary-school age, skates alone on an indoor ice rink.
Her hair is in two high pigtails with curled ends, and she wears a pale lavender figure-skating dress with long sleeves, a short pleated skirt, white trim down the front and back, white socks, and white skates.
The rink boards and glass panels line the background, with a dark seating area beyond.
She glides with one arm extended, turns her head over her shoulder, then spins and skates forward across the ice.
She looks focused and pleased as she moves, her skirt flaring slightly with each turn.
She continues across the rink, then stretches into a graceful balance : her body leans forward, one leg planted on the ice and the other lifted straight behind her.
One arm reaches forward while the other reaches back toward her raised skate, creating a long, steady skating pose.
As she holds the pose, a table scene appears : the same girl sits rink-side in front of a plate with a white-bread sandwich, a glass of milk, and a wrapped loaf of Wonder White bread.
The loaf package is white with Wonder ’s red, yellow, and blue dot pattern, and large visible words including “ WONDER ” and “ WHITE. ” At the table, she faces forward, speaking while holding the sandwich upright with both hands.
The glass of milk stands to her left, the Wonder White loaf sits to her right, and the ice rink remains softly visible behind her, with other skaters passing in the distance as blurred figures.
She tilts her head, looks upward as if answering someone, then looks back toward the front.
She smiles, lowers her gaze to the sandwich, lifts it, and takes a large bite.
The sandwich appears thick and soft, with white slices and a pale filling visible at the edge.
An adult woman then appears against a warm, wood-toned background, holding a loaf of Wonder White bread at chest height so the package faces outward.
She has short, dark, softly styled hair and wears a blue jacket over a cream turtleneck.
A patterned scarf or pocket square with Wonder-like colored dots is tucked near her shoulder.
She smiles directly forward while presenting the bread, then lowers the loaf out of view and continues speaking to the viewer.
A nutrition comparison graphic appears on a wood background.
At the top, white text reads “ \% U.S.
RDA PER 2 OZ.
SERVING. ” Two bread shapes sit side by side : on the left, a brown \textbf{speckled} slice labeled “ WHOLE WHEAT, ” and on the right, white slices labeled “ WONDER. ” Large black numbers are printed over the bread shapes.
For “ PROTEIN ” and “ \textbf{IRON}, ” both sides show “ 8 ” and “ 8. ” The graphic changes to show more nutrients : “ RIBO-FLAVIN ” shows “ 4 ” for whole wheat and “ 8 ” for Wonder, and “ THIA-MINE ” shows “ 10 ” for whole wheat and “ 15 ” for Wonder.
The bold numbers dominate the bread shapes, making the comparison very prominent.
Back on the ice, the young girl skates with a tall adult skater or coach.
The adult wears a reddish-brown skating outfit with a white front panel and dark skates, and holds one of the girl ’s hands.
The girl extends one leg behind her in another skating balance while the adult raises one arm high overhead and leans slightly, guiding her in a partnered glide.
They move together across the rink, connected by their hands, with the girl low and outstretched and the adult upright and supportive.
The scene changes to the adult woman seated closely beside the girl, now together at the rink.
The woman, still in her blue jacket and cream turtleneck, looks forward while the child eats the white-bread sandwich.
The woman ’s arm is around or close behind the girl in a protective, affectionate posture.
The child chews, holding the sandwich with both hands.
The commercial ends with a product display : a loaf of Wonder White bread lies prominently on a smooth dark surface, angled so both the side and top of the package are visible.
The white wrapper is covered with Wonder ’s colorful dot pattern and large red and black “ WONDER ” and “ WHITE ” lettering.
In the upper left is a small inset image of the woman and child together.
To the right, large white capital letters read : “ GOOD NUTRITION DOES N’T HAVE TO BE WHOLE WHEAT. ”

% matched lemmas: iron, speckle
\end{textsample}
