\begin{textsample}{NEG Dim 8 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_13.txt}  \label{ex:f8_neg_067}
The commercial opens in a courtroom setting styled around airline fees.
A judge in a black robe sits behind a high wooden \textbf{bench}, with a gavel and papers in front of her.
An American flag stands behind the \textbf{bench}, and a uniformed court/security officer sits to the judge ’s side.
A wall sign reads “ FEE COURT, ” and the judge ’s \textbf{bench} has a nameplate that is partially legible.
The scene cuts to a wider view of a jury-like panel seated behind a wooden rail.
A large wall sign reads “ THE AIRLINE FEE COURT. ” The panel is made up of people dressed like airline or airport personnel : some wear reflective safety vests, \textbf{headsets}, pilot-style uniforms, or service uniforms.
A yellow-and-red sign on the front of the rail reads “ SOUTHWEST AIR … ” with the final letters partly obscured by framing.
The camera returns to the judge in close-up.
She looks down toward papers on the \textbf{bench} and then forward, appearing attentive and serious.
The wood-paneled courtroom, leather judge ’s chair, gavel, and American flag remain visible.
A wider courtroom shot shows two men standing before the judge.
One is an older bald man in a dark business suit and tie.
Beside him is a younger man wearing a red zip-up hoodie over a dark shirt.
The uniformed officer remains seated behind them near the \textbf{bench}.
The younger man appears to be addressing the court in later shots, gesturing with one hand while facing toward the judge and the older man.
Close-ups alternate between the younger man in the red hoodie, the older suited man, and the judge.
The younger man ’s expressions shift from neutral to animated as he looks to the side and gestures.
The older man appears more reserved ; in one shot he looks upward, and in another he looks down toward the desk or documents in front of him.
The judge watches with a composed, evaluative expression.
The commercial also cuts to reactions from the jury-like panel.
Several airline/airport-uniformed people are shown seated together.
A man in a reflective vest with “ SWA ” on it, a man in a purple polo shirt with a small airplane logo, a pilot or uniformed airline \textbf{worker}, and other personnel are visible.
Some look toward the courtroom action, and their facial expressions vary from attentive to amused or surprised.
Another close-up shows two women in airline-style uniforms reacting while seated among the panel.
Near the end, the courtroom scene cuts abruptly to a bright yellow full-screen graphic.
There is a brief blurred motion effect against the yellow background, then a final brand card appears.
In the center is a stylized red, blue, and yellow airplane graphic above the text “ SOUTHWEST.COM. ” At the bottom right, small text reads : “ Fare difference may apply. ”

% matched lemmas: bench, headset, worker
\end{textsample}
