\begin{textsample}{NEG Dim 8 – 2010 – Score -7.00 – 2010/tv\_com\_2010\_52.txt}  \label{ex:f8_neg_061}
The commercial opens on a black screen with the white word “ SAMSUNG ” centered.
A small URL appears near the bottom, apparently “ samsung.com/note9. ” It then cuts to a bright outdoor pedestrian walkway lined with trees and campus-like buildings.
A person in a business suit wears a large round white \textbf{mascot} head with blue eyes, a red smile, a small nose, and a pointed orange cone-shaped hat.
The figure holds a long wrapped sandwich upright in one hand while walking toward the camera.
The suit is blue with a white shirt and red tie.
A close-up product shot follows : two long sandwiches sit on dark trays against a dark background.
One appears to contain deli meat and green vegetables ; the other has visible bacon-like strips, cheese, onions, and sauce.
The next shots return to the \textbf{mascot} character on the leafy walkway, still holding the sandwich and facing the camera.
The \textbf{mascot} then appears seated in a red convertible car, viewed through the windshield, still holding the sandwich.
The next street scene shows a storefront façade with a large window display and a person outside carrying or handling several colorful balloons and a cardboard box as a blue car passes in the foreground.
A man in a bright blue suit is shown standing or jumping on top of a car roof in an urban street setting, arms spread wide.
The scene then cuts to the \textbf{mascot} leaving a storefront with teal-painted trim.
Window signs are visible : one says “ ALTERATIONS ” and “ STAIN REMOVAL, ” with “ WEDDING \textbf{GOWNS} ” near the bottom ; another large diamond-shaped sign reads “ cleaners. ” Back in the tree-filled outdoor area, a man in a blue sweater holds a long wrapped sandwich in one hand and looks down at a smartphone in the other.
In a wider shot, the same man stands on a grassy area while, at the right edge, a football player in a red-and-white uniform appears mid-action, bent forward as if running or lunging toward him.
Other pedestrians and \textbf{benches} are visible in the background.
The \textbf{mascot} is next shown seated at a small outdoor café table.
A tablet or phone on a stand sits on the table, along with small potted plants.
The \textbf{mascot} holds the sandwich while looking downward toward the table.
The setting includes a sidewalk, parked cars, and people in the background.
A close-up shows a large black portable stereo/boombox placed outdoors, with speakers and control panels visible.
The following wider shot reveals a construction-site street scene with cones, \textbf{barriers}, caution signs, \textbf{workers} in orange safety vests and \textbf{hard} hats, and equipment.
The \textbf{mascot} stands in front holding the sandwich while \textbf{workers} move around behind him.
The commercial then cuts to a product end-card.
Against a dark smoky background, two long sandwiches are displayed on trays.
Large red text reads “ PANNIDOS, ” with “ New ” above it in smaller white script.
Small labels identify the sandwiches : one label reads “ Deli Trio, ” and the other appears to read “ Turkey, Bacon \& Cheddar. ” Fine-print legal or descriptive text appears along the bottom but is too small to read clearly.
The final frame returns to the construction-site scene.
Overlaid graphics appear : a red “ Jack ” logo with “ in the box ” beneath it, and the DoorDash logo/text to the right.
Between/near them is the message “ GET ’ EM DELIVERED ” with an arrow-like delivery icon.
The \textbf{mascot} walks across the left side of the frame while construction \textbf{workers} and equipment remain visible in the background.

% matched lemmas: barrier, bench, gown, hard, mascot, worker
\end{textsample}
