\begin{textsample}{NEG Dim 8 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_4.txt}  \label{ex:f8_neg_056}
A brief product image appears first that does not match the Benadryl \textbf{packaging} : two Rolaids antacid tablet rolls lie on a pale tiled surface, with a bright orange “ SODIUM FREE ” label on one package and large black words below reading “ 100 \% RELIEF. ” The image quickly darkens.
The scene then shifts to a murky, greenish outdoor-looking landscape.
Huge stone letters spelling “ ALLERGY ” stand across the background like weathered monuments.
The ground is rough and uneven, with dark vegetation and drifting mist.
A gray cat moves across the lower part of the scene from right to left, its head low and ears visible, passing in front of the massive letters.
As the cat leaves the bottom edge, the fog thickens and rolls across the foreground, partly hiding the word “ ALLERGY ” and making the setting look damp, hazy, and threatening.
The view moves closer into the stone word, focusing on the first letter, a giant rough-textured “ A. ” The letter is cracked and weathered, standing on rocky ground.
Inside the triangular opening of the “ A, ” a bright blue light appears, contrasting sharply with the dark green-gray surroundings.
The opening grows larger in view, revealing a clear, bright blue landscape beyond it, like calm water or ice under a pale sky.
The dark, rocky allergy scene frames this bright opening until the blue scene fills the screen.
In the bright blue setting, flat icy or watery shapes stretch toward the horizon.
A Benadryl box appears in the lower right area and then becomes more central and larger.
The package is a cream-colored rectangular box with a bold red “ Benadryl ” name across the front and a red horizontal band beneath it ; “ NOW! ” is visible near the top left of the package.
The box stands upright against the clean blue background, reflected slightly on the glossy surface below.
Small white on-screen text appears along the bottom : “ Use as directed for upper respiratory allergy and \textbf{cold} symptoms. ” Large magenta lettering then appears behind and partly around the Benadryl box, reading “ NOW! available without prescription, ” with the oversized “ NOW! ” especially prominent.
The Benadryl package remains in front, centered against the blue watery or icy backdrop, while the caution text continues along the bottom.
Finally, the product display expands to show several Benadryl forms together : a cream-colored Benadryl box on the left with the red band, a small white bottle in the center with a Benadryl label and cap, a second Benadryl box on the right with a blue band, and a smaller package standing behind them.
The products are arranged on the same bright blue surface with pale ice-like shapes in the background.
Large dark text at the bottom reads, “ From Parke-Davis. ”

% matched lemmas: cold, packaging
\end{textsample}
