\begin{textsample}{NEG Dim 8 – 1950 – Score -3.00 – 1950/tv\_com\_1950\_44.txt}  \label{ex:f8_neg_025}
A small, rounded white Stopette bottle is held at the bottom of a dark, plain background.
A finger \textbf{squeezes} the soft-looking bottle, and a narrow, pale mist shoots straight upward from the open top.
The bottle label is faint but reads “ Stopette ” with “ spray deodorant ” beneath it.
Large block letters then appear above and behind the bottle, building into the question “ WHAT ’S YOUR LINE? ” with the Stopette bottle still centered below the words.
A woman appears in a tidy domestic kitchen, facing forward as if speaking directly to the viewer.
She is a young adult to middle-aged white woman with short, curled 1950s hair.
She wears a dark dress with a wide, light-colored ruffled neckline that frames her shoulders and chest.
Behind her are kitchen cabinets, a chair, and household surfaces, placing her in a home setting.
Her expression is alert and confident, and she remains mostly still, occasionally shifting her head and shoulders as she talks.
The image blends into a more dressed-up version of the same woman in a dining or living room setting.
She now wears a dark, square-necked dress with a necklace and earrings, and she sits upright near a high-backed chair.
A curtain is visible at the left, and a framed picture hangs on the wall.
She smiles, appearing prepared for a more formal part of the day.
The scene then shifts again to her in a lighter, softer garment, like a robe or house dress, standing near a mirror or medicine cabinet.
A cabinet door opens to reveal shelves holding toiletries.
On a lower shelf, the rounded Stopette bottle sits among taller glass bottles and other containers.
The Stopette bottle is \textbf{squat} and oval, with a short cap and a label on its front.
A woman ’s hand reaches in from the right, passes the taller bottles, grasps the Stopette bottle, and lifts it out.
She holds it close to the cabinet opening, turning it so the front label faces outward.
Back in front of a mirror, the woman holds the small Stopette bottle beside her face, presenting it.
She is now in a light-colored robe with delicate trim at the sleeves or shoulders.
She demonstrates the bottle with both hands, looking between the product and the viewer.
Her fingers curl around the soft oval body, showing that it can be \textbf{squeezed}.
She brings a larger, bright bottle shape forward for emphasis, filling the foreground with the rounded Stopette form.
The commercial returns to the dark \textbf{demonstration} background.
The Stopette bottle is held upright at the bottom center, and the top points upward.
A fine mist rises from it again.
Handwritten-style white lettering appears above the spray : first the word “ Poof! ” Then more script appears across the middle : “ there goes perspiration. ” The bottle remains below the words, reinforcing the action of the spray.
A close view shows the bottle near a tiled bathroom wall and a white sink with shiny chrome faucets.
The woman ’s hands hold the bottle over the sink.
Her nails are darkly polished, and one hand steadies the bottle while the other places or adjusts the cap at the top.
The Stopette label is visible on the front as she handles it.
She twists or presses around the cap area, demonstrating the top and the clean handling of the container.
Then the bottle slips from her hands and drops into the white porcelain sink.
It lands on its side in the basin near the drain and chrome faucet, remaining intact.
In a wider bathroom view, the woman reaches into the sink and picks it up.
She stands beside the sink in her light garment, then raises the bottle near her face and examines it.
Her expression softens into a satisfied smile, suggesting the bottle has not broken or spilled.
A package display fills the view.
A large Stopette box shows a glamorous illustrated woman applying deodorant under one arm.
Readable text on the package includes “ NEW Stopette SPRAY DEODORANT ” and “ \textbf{SQUEEZE} THE BOTTLE IT SPRAYS! ” with a price that appears to read “ \$1.25. ” The box sits among other Stopette display cartons and rows of the rounded bottles, as if on a drugstore or cosmetics counter.
Multiple cardboard displays show the Stopette script logo and product image, with bottles arranged in front.
The scene changes to a tabletop product arrangement.
A decorative round cosmetic jar or container sits in the center on a wooden surface, while Stopette bottles appear around it.
The bottles are pale, rounded, and capped, with some labels readable as “ Stopette. ” They seem to multiply and arrange themselves on either side of the central jar, building into a neat display.
The Stopette bottles gradually surround and outnumber the central old-fashioned-looking container, ending in a semicircle of bottles around it.
The display settles into a front-facing product lineup.
Several Stopette bottles stand in the foreground, with one larger bottle raised behind them at the center.
The central bottle becomes the focus, its label clearly reading “ Stopette spray deodorant. ” The background bottles blur slightly, while the large central bottle remains bright and prominent.
The final image returns to the dark background with the small Stopette bottle held at the bottom center.
A finger \textbf{squeezes} it, sending a narrow mist upward.
The handwritten word “ Poof! ” appears above the spray, followed by the beginning of the phrase “ there goes perspiration ” in large white script across the dark space, while the Stopette bottle stays visible below.

% matched lemmas: demonstration, squat, squeeze
\end{textsample}
