\begin{textsample}{NEG Dim 8 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_34.txt}  \label{ex:f8_neg_040}
The commercial begins with a very dark, nearly black frame.
No clear objects, people, or setting are visible at this point.
After several seconds, the image changes to a layered or cross-faded scene.
A football field with players is visible, including one player in a red jersey with the number 97 on the right side.
Over this field scene, there appears to be a translucent architectural interior with a long arched corridor or hallway, creating a superimposed visual effect.
The image is soft and hazy, suggesting a transition or montage rather than a single clear location.
The next frame shows a closer view of a football player wearing a red jersey with the number 97.
He appears to be standing on a field and holding a football helmet at his side.
His face is tilted upward, and his expression appears strained or emotional, though the exact emotion is not fully clear.
Other figures in red sports clothing are faintly visible behind him, and the image still has a soft, overlaid quality.
Later, the commercial cuts to a close-up background of a person ’s face, partially obscured and out of focus.
Over this image, a prominent graphic appears across the center : a black rectangular \textbf{banner} with large text reading “ 1-800-COLLECT. ” Beneath it, smaller text reads : “ America ’s Inexpensive Way To Call Someone Collect. ” At the bottom, very small text reads : “ Use it every time you make a long distance collect call. ” The background person appears to be holding something near their face, possibly a telephone receiver, but the frame is soft and partly covered by the text, so this is not completely clear.
The final frame presents a clean white background with the same central branding and message.
A black rectangular \textbf{banner} contains “ 1-800-COLLECT ” in large lettering.
Below it is the line : “ America ’s Inexpensive Way To Call Someone Collect. ” At the bottom, smaller text reads : “ Use it every time you make a long distance collect call. ” No people or setting are visible in this final frame.

% matched lemmas: banner
\end{textsample}
