\begin{textsample}{NEG Dim 8 – 2020 – Score -7.00 – 2020/tv\_com\_2020\_50.txt}  \label{ex:f8_neg_042}
A softly lit living room appears mostly in black and white, with sheer curtains glowing behind a stationary exercise bike.
A person exercises on the bike, leaning forward over the handlebars in a strained posture.
A sofa with a throw blanket sits to the left, and tables and shelving are visible around the room.
Across the lower foreground, a large, brightly colored “ ICYHOT ” logo stands out against the grayscale scene, with “ ICY ” in blue and “ HOT ” shifting from yellow to orange-red ; its colors reflect on the shiny floor.
The view moves closer to the rider, an adult woman with her hair pulled back, wearing a dark athletic tank top.
The bike ’s handlebars partly frame her face.
She looks down and appears tired or uncomfortable, with a tense expression, as if the \textbf{workout} or pain is wearing on her.
The scene changes to a product \textbf{demonstration} against a dark, plain background.
From behind, a person in a black tank top exposes the upper back and shoulders.
A hand holds an Icy Hot product bottle near the left shoulder and applies it to the shoulder area.
Blue animated rings appear on the skin where the product is being applied, visually suggesting relief spreading outward.
Small text near the bottom reads “ \textbf{Dramatization} ” on the left and “ Use as directed ” on the right.
Large white text appears over the back : “ \textbf{POWERFUL} RELIEF. ” The \textbf{demonstration} continues, with the blue rings pulsing over the shoulder.
The screen then splits vertically.
On the left, the same shoulder application remains visible ; on the right, a hand holds a can labeled “ Icy Hot Dry Spray ” over a bent limb, spraying a fine mist toward the skin.
Blue rings also appear on the sprayed area.
The on-screen text builds to read “ \textbf{POWERFUL} RELIEF \textbf{MUSCLES} + JOINTS, ” emphasizing both the shoulder \textbf{muscle} area on the left and the joint-area application on the right.
The small “ \textbf{Dramatization} ” and “ Use as \textbf{directed} ” notices remain near the bottom.
The final view is a black background with the Icy Hot logo at the top.
Beneath it, large text reads “ HAS A NEW LOOK, ” with “ NEW ” in a red rounded shape.
Two Icy Hot lidocaine patch packages are shown side by side : an older-looking yellow and gray package on the left and a cleaner white-and-blue package on the right.
A blue arrow points from the left package to the right package, indicating the updated \textbf{packaging} design.
Small text at the bottom again says, “ Use as directed. ”

% matched lemmas: demonstration, directed, dramatization, muscle, packaging, powerful, workout
\end{textsample}
