\begin{textsample}{NEG Dim 8 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_87.txt}  \label{ex:f8_neg_078}
The commercial opens on a nearly black screen, with a small red heart-shaped watermark/logo visible in the lower-right corner.
It then cuts to a bright, softly lit interior with sheer white curtains and a polished wooden floor.
A light-skinned woman with shoulder-length reddish-brown hair sits on a \textbf{bench}, wearing a pale/light gray or white sleeveless dress.
She is barefoot, leaning forward with one elbow on her knee and one hand near her hair or face.
The setting looks minimal and airy, with cushions on the floor in the background.
The camera moves to a closer view of her bare legs as she sits on the \textbf{bench}.
Her feet are extended toward the reflective wooden floor, and the floor reflection emphasizes the smoothness and shine of the scene.
The background remains bright with white curtains and soft furnishings.
A close-up follows of the woman ’s shoulder and upper arm area, partly framing her face at the edge of the shot.
The focus is on her skin, with the same pale curtain background.
The product is then shown : two upright tubes of Jergens “ natural glow ” “ daily moisturizer ” placed side by side against the white curtain backdrop.
The tubes are beige/tan with teal Jergens logos, and they appear to represent two shade or formula variations, though the smaller text is not fully readable.
Next, there is a close-up of the woman ’s bare shoulder and upper back as a hand touches or smooths over the upper arm/shoulder area.
Small white disclaimer text appears in the upper-right corner ; “ results may vary ” is legible, while the rest is difficult to read clearly.
The woman is then shown standing near the white curtains, still wearing the light sleeveless dress.
She looks downward with a calm expression, one hand near or touching the curtain or wall.
Her hair is styled smooth and side-parted, and the lighting remains soft and bright.
The image briefly becomes an abstract bright curtain background with no person or product visible, maintaining the white, luminous visual style.
The final frame shows the Jergens logo centered over the pale curtain background, with the text “ GLOWING SKIN IS IN ” underneath.
The small red heart-shaped watermark/logo remains in the lower-right corner.

% matched lemmas: bench
\end{textsample}
