\begin{textsample}{NEG Dim 8 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_16.txt}  \label{ex:f8_neg_066}
The commercial takes place in an automotive service/tire shop. - **Opening frame:** A man in a gray long-sleeve shirt, jeans, and a dark baseball cap stands in the foreground near stacks of tires.
Behind him, a service \textbf{worker} in a blue-and-white uniform is bent over a tire near a vehicle with its hood open.
The shop interior contains tire racks, equipment, and hanging lights.
A sign in the background includes tire brand names such as **Goodyear** and **Continental Tire**. - **Next shot:** The camera moves closer to the man in the cap.
He stands in front of tall stacked tires and service equipment, appearing to address the viewer.
A monitor and more workshop machinery are visible behind him. - **Mid-sequence:** The man stands beside a large horizontal stack of tires, gesturing with one hand.
In the background are more tire racks and a service bay with vehicles.
A sign above the tires shows the logos/text **Ford**, **Lincoln**, and **Mercury**. - **Graphic/product shot:** The scene cuts to a clean graphic-like display of \textbf{rows} of tires filling the lower half of the frame.
Above them are tire brand logos, including **Goodyear**, **Continental Tire**, **Hankook**, **Yokohama**, and **Pirelli**.
At the bottom, large orange text reads **“LOW PRICE TIRE”**. - **Service equipment shot:** The man leans on or rests his arm near a tire mounted on a red tire-service machine.
He appears to be inspecting or thinking while looking at the tire.
A black lower-third \textbf{banner} appears with dealership/service branding : **Ford**, **Lincoln**, **Mercury**, and the word **“SERVICE”**.
A plate-like marking on the machine reads **“TCX 575”** along with a Ford logo. - **Final frame:** The man stands beside service machinery and tires, facing the viewer with one hand raised in a pointing or emphatic gesture and the other hand on his hip.
The lower-third \textbf{banner} remains visible with **Ford**, **Lincoln**, **Mercury**, and **SERVICE**.
The automotive shop setting, tire stacks, and open vehicle hood remain visible in the background.

% matched lemmas: banner, row, worker
\end{textsample}
