\begin{textsample}{NEG Dim 8 – 1970 – Score -1.00 – 1970/tv\_com\_1970\_4.txt}  \label{ex:f8_neg_049}
The commercial opens with a dark, green-tinted map-like image showing the northeastern United States or a similar region.
Pale lines trace coastlines and routes, with many small bright dots scattered across the map.
A “ Classic Commercial Archives ” watermark appears at lower left, with a faint larger archive watermark across the lower portion.
The scene then shifts to an operations/control-room setting.
A man sits at a console on the right, facing equipment and displays.
Behind him is a large wall board with \textbf{rows} of text ; some visible words include “ PITTS … ” and other partially legible place or chart-related labels.
A rectangular display or screen appears on the left, with a dark silhouette-like figure or graphic on it.
The image uses a double-exposure or overlay effect, blending the operator, console, and wall board.
Next, two men in white coats are shown close-up in a technical environment.
One man extends an arm toward a vertical panel or screen, apparently pointing or placing something on it.
The other man looks on.
Behind them are clusters of small lights or a patterned illuminated panel, suggesting monitoring or laboratory equipment.
The commercial cuts back to the control-room view.
A man at the console is seen in profile from behind/right, with a telephone receiver near his head.
The same large wall board and display screen are visible in the background, again with layered reflections or superimposed imagery.
A close-up follows of a hand operating a keyboard or switch panel.
The fingers press down on \textbf{rows} of dark rectangular keys or toggles arranged in parallel lines.
The shot emphasizes manual input into the equipment.
This is followed by a more abstract, layered image : \textbf{rows} of keys or equipment are overlaid with glowing blue and white alphanumeric readouts, numbers, and dotted lines.
The exact data is not fully readable, but the visual suggests computerized or electronic information processing.
Near the end, a middle-aged or older man in a suit and tie stands facing the camera in the same control-room environment.
Behind him is the large board with partially visible text, including “ PITTS … ” and “ CHART …, ” along with other obscured words.
The image still contains superimposed lines and reflections, giving the scene a technical, data-driven look.
The final frame fades to a dark green/black screen with the archive watermark still visible.

% matched lemmas: row
\end{textsample}
