\begin{textsample}{NEG Dim 8 – 2000 – Score -3.00 – 2000/tv\_com\_2000\_74.txt}  \label{ex:f8_neg_084}
A white carpet sample is held upright in a clamp against a green wall.
A woman ’s hand steadies the left edge, and a pinkish circular stain appears near the center.
Black on-screen text labels it “ Red Wine. ” The woman, seen partly from behind, has dark hair and wears a black top ; only her profile and arm are visible at first.
The view widens to reveal a staged testing area that resembles an indoor range or lab, with green walls, metal posts, overhead strip lighting, and carpet samples hanging from clamps.
The dark-haired woman in black stands behind a table at the center.
She wears clear safety glasses and large black ear protectors.
To the right, a blonde woman in a white outfit stands with her arms crossed, also wearing safety glasses and ear protectors, watching calmly.
A blue \textbf{aerosol} can sits on the table near the dark-haired woman.
The dark-haired woman extends her arm straight out and sprays the blue \textbf{aerosol} can toward the stained carpet, holding it like a tool \textbf{aimed} at a target.
A pale stream sprays from the nozzle across the space toward the hanging carpet sample.
The can ’s label is partly visible and includes large white lettering for a spot cleaner.
Her expression is serious and focused.
The carpet sample is shown again hanging in the clamp ; the stain area looks muted but still faintly marked.
The blonde woman then steps forward in the same testing area, wearing a white blouse and light trousers.
She reaches out with both hands and presents a different product close to the viewer : Woolite Oxy Deep 2X.
The package looks like two silver \textbf{aerosol} cylinders joined side by side in a red-and-blue holder, with a red cap and a handle-like blue piece.
The label is bold, with “ Woolite ” above large white “ OXY DEEP ” text and “ 2X ” near the bottom.
She holds it steadily, almost like a double-barreled device, with a confident, slight smile.
A comparison appears on the green wall : two white carpet samples hang side by side from black clamps.
Beneath the left sample is the “ OXY DEEP 2X ” logo, and beneath the right sample is the text “ A Leading Competitor. ” A small circular timer graphic between them reads “ 6 sec. ” The left carpet sample appears cleaner, while the right sample shows a small pale spot or residue.
Later, the two hanging samples rotate sideways, revealing their backs.
When they face front again, the left sample associated with Oxy Deep looks clean through the material, while the right sample associated with the competitor shows a darker stain bleeding through from behind.
A circular time graphic remains between the labels.
The product is then displayed on a tabletop against a green background.
On the left, large blue “ Woolite ” text appears, with the tagline underneath : “ \textbf{Tough} love for your carpet. ” To the right stands the Woolite Oxy Deep 2X package, the two silver canisters joined in the red-and-blue holder, label facing forward.
Finally, the blonde woman in white stands in the testing area holding the Woolite Oxy Deep product.
She wears her protective earmuffs and glasses, looks forward with a composed, satisfied expression, and flips or turns the product in her hand before bringing it up toward the viewer, presenting it confidently as the closing image.

% matched lemmas: aerosol, aim, tough
\end{textsample}
