\begin{textsample}{NEG Dim 8 – 1950 – Score -3.00 – 1950/tv\_com\_1950\_63.txt}  \label{ex:f8_neg_024}
At first, only a person ’s torso and hands are visible against a dark, plain background.
The person wears a light short-sleeved blouse with a collar and dark piping along the seams.
In both hands, they hold a soft metal tube horizontally, label facing outward.
The large printed words on the tube read “ LISTERINE, ” with “ TOOTH PASTE ” below.
The cap end is on the left, and the fingers work around that end as if opening or readying the tube.
The view widens to reveal an older girl or young woman, likely a teenager, standing at a bathroom sink.
She has light-colored curled hair and wears the same neat light blouse.
She smiles down at the toothpaste tube while handling it.
A younger girl steps into view beside her, wearing a light, frilly or ruffled top and holding a toothbrush.
The older girl positions the Listerine tube over the younger girl ’s brush, appearing to \textbf{squeeze} toothpaste onto it.
A small blond boy in darker clothing appears on the other side, watching with interest.
The setting is a tidy bathroom or washroom, with a tiled wall and a sink in front.
Several faucets and bathroom items sit along the sink edge.
The younger girl smiles as she receives the toothpaste.
She holds her toothbrush up in front of her, then begins brushing.
The boy also has a toothbrush and starts brushing at the left, lower in the scene.
The older girl stands on the right, smiling and supervising, then raises her own toothbrush to her mouth.
All three children brush together at the sink.
Their expressions are cheerful and cooperative, and their mouths begin to show visible white foam from the toothpaste.
The boy is then seen alone in a closer view.
He is a young blond child with neatly combed hair, wearing a dark sweater or jacket over a light collared shirt.
He brushes the front of his teeth with a toothbrush held in one hand.
White toothpaste foam is visible across his teeth and lips.
He glances to the side and smiles slightly while continuing the brushing motion.
Large white lettering begins to appear over the brushing scene.
The word grows across the lower part of the image, spelling “ LUSTERFOAM ” in bold, all-capital letters.
Behind the text, the younger girl is shown brushing her teeth.
She has dark hair parted in the middle and tied into side pigtails, and she wears a light patterned blouse.
She smiles broadly as she brushes, with foam visible around her teeth.
The word “ LUSTERFOAM ” remains large across the bottom of the screen, partly covering her blouse and toothbrush hand while her face remains visible above it.
The older girl appears next in a separate view, brushing her teeth.
Her light hair is styled in soft curls and pinned back, and she wears the same light collared blouse.
She turns slightly to one side, smiling as she brushes, then faces more forward.
White foam is visible at her mouth, and her expression remains bright and pleasant.
The commercial then shifts to a product display.
A rectangular box of Listerine Tooth Paste sits on a tabletop, label facing outward.
The \textbf{packaging} is bold and graphic in black and white.
The front reads “ LISTERINE TOOTH PASTE, ” repeated in two horizontal bands, suggesting a two-tube pack.
A large diagonal price panel on the right says “ ONLY 59¢, ” with smaller text indicating “ 90¢ \textbf{value} ” and “ Two 45¢ Tubes. ” A Listerine toothpaste tube slides or is placed in front of the box, label facing outward, then a second tube appears beneath it, so two tubes are visible stacked one above the other in front of the carton.
The box alone is shown again, centered on the tabletop, with the “ ONLY 59¢ ” price panel prominent on the right side and “ LISTERINE TOOTH PASTE ” across the front.
The package remains steady for several moments, making the price and two-tube offer the main visual focus.
Finally, the pack sits on a counter in front of a person wearing a light coat or smock, visible from the chest down, with both hands resting near the counter edges.
The box remains centered, label facing the viewer.
On the right side of the counter, a vertical display holds additional Listerine packages with the same “ 59¢ ” price marking ; more stacked packages are partly visible on the left.
A customer ’s hand reaches in from the left, fingers curling around the front Listerine pack.
The hand pulls the box toward the left, as if taking it from the counter to buy.
The scene ends with the product pack being lifted or slid away while the coated figure ’s hands stay near the counter and the store displays remain at the sides.

% matched lemmas: packaging, squeeze, value
\end{textsample}
