\begin{textsample}{NEG Dim 8 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_49.txt}  \label{ex:f8_neg_009}
The commercial is presented in black and white and appears to move from an animated or graphic opening into a live-action studio presentation.
At the start, the frame shows a simple illustrated/animated composition.
Near the upper part of the image there is a small cartoon-like figure or \textbf{mascot} associated with a long, dark, diagonal object that resembles a pen or pen tip.
On the lower right, large block lettering is partly visible ; it appears to read “ NEW, ” though the image is somewhat blurred.
The background is plain and light, giving the opening a graphic, advertisement-card appearance.
By the next sampled frame, the scene has changed to live action.
A formally dressed man stands in front of heavy curtains.
He wears a dark suit or tuxedo jacket, a light shirt, a bow tie, and a boutonniere.
He holds a small slender object in one hand, likely a pen, though the frame is not sharp enough to confirm every detail.
To his right is a framed display board or sign.
Only part of the sign is visible, showing cursive letters beginning with “ wi … ” and larger block letters beginning “ PAP … ”.
In the final frame, the man remains beside the display board, now more fully visible.
The board contains the written message : “ without a PAPER MATE pen. ” The words “ without a ” are in cursive script, “ PAPER MATE ” is in large block \textbf{capitals}, and “ pen ” appears in smaller cursive writing.
A small cartoon \textbf{mascot} or figure is also printed near the lower part of the board.
The man gestures toward the camera while still holding the small object, maintaining the demonstrative pose of a presenter.

% matched lemmas: capital, mascot
\end{textsample}
