\begin{textsample}{NEG Dim 8 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_117.txt}  \label{ex:f8_neg_019}
The commercial is in black and white and appears to move through several distinct visual scenes before ending on a branded product display.
At the beginning, the screen is almost entirely dark, with no clearly identifiable objects visible.
Around 5.8 seconds, the image cuts to a very bright circular light or illuminated round object in close-up.
It dominates the center of the frame and produces glare against a dark, reflective background.
As the sequence continues, the bright circle shifts toward the right edge of the frame, revealing more dark metallic or glossy surfaces behind it.
The exact object is unclear from the sampled frames, but it resembles a strong lamp, headlight, or illuminated circular fixture.
At about 18 seconds, the scene changes to a close-up of a rectangular electronic device or appliance.
It has a dark front panel, a \textbf{row} of small markings or buttons, and a large round knob near the lower left.
A hand reaches in from above and appears to adjust or touch controls on the top of the device.
The device sits among other small objects on a table or counter.
At about 25 seconds, the camera shows an overhead view of a room or office setting.
A person sits at a desk, viewed from above and behind.
The desk contains papers, a lamp with a round shade, and small objects that may include office equipment.
Another standing figure or the shadow of a figure is visible near the top of the frame, but details are indistinct.
At about 49 seconds, the commercial cuts to a display of multiple electronic products arranged closely together.
These are box-shaped devices with dials, knobs, speaker grilles, and front panels, resembling radios or similar home electronics.
The shot emphasizes variety and quantity, with several devices overlapping in the frame.
The final sequence, beginning around 56.6 seconds, presents a staged branded display.
A large stylized “ ZENITH ” logo appears prominently across the upper portion.
Beneath it is readable text : “ The quality goes in before the name goes on. ” Several Zenith-branded-looking appliances or radio-like devices are arranged on a platform below the text.
As the shot progresses, the camera appears to pull back or the framing widens, revealing that the display is enclosed within an ornate decorative frame with bright, reflective trim.
By the final frame, the full framed display is visible : the large Zenith logo at top, the slogan centered underneath, and the products arranged along the bottom platform.

% matched lemmas: row
\end{textsample}
