\begin{textsample}{NEG Dim 8 – 1950 – Score -3.00 – 1950/tv\_com\_1950\_92.txt}  \label{ex:f8_neg_022}
In black and white, the commercial opens on an extreme close view of a woman ’s hand, fingers held in a gentle pinch.
Her nails are neatly shaped and polished.
Between her thumb and forefinger, a small glossy bead of liquid stretches downward into a teardrop shape, hanging for a moment against a soft, blurred background.
Large bold white lettering then appears over a smoky, cloudy background : “ DISHES GO FROM GREASE TO SHINE. ” A second line is added below : “ IN HALF THE TIME. ” The Joy bottle rises into view behind the words and then stands alone, centered.
It is a \textbf{squat}, clear-looking bottle with a dark cap, rounded shoulders, and a ribbed lower body.
The front label is light with the word “ Joy ” in large dark, playful letters.
An adult woman is then shown from the chest down holding the Joy bottle in both hands.
She wears a light-colored, short-sleeved domestic blouse or house dress with a soft bow or tie at the neckline.
She unscrews the dark cap, removes it, and tips the bottle sideways.
The label “ Joy ” remains visible as she appears to pour or measure the liquid using the cap or bottle opening.
The scene moves to a kitchen sink crowded with dirty dishes.
Large plates with visible dark streaks and greasy \textbf{smears} lean against each other.
A hand works at one plate under the faucet area, rubbing across its surface.
The sink quickly fills with thick, white suds that spread over the dishes.
The foam rises high, covering much of the basin and partially hiding the plates.
A hand reaches through the suds, scrubbing and moving dishes beneath the bubbles.
One round plate is lifted from the sudsy water.
Its surface still shows dark greasy marks at first, then it is turned and worked in the foam.
The woman ’s hand continues washing with vigorous circular motions.
As the plate is handled and rinsed, the dark streaks disappear.
Water runs from the faucet over the plate while the surrounding suds mound around the sink.
The plate is tilted so water sheets off it, leaving it looking clear and bright.
The woman appears in the kitchen, now visible from the waist up.
She is an adult woman with short, dark, curled hair and a light-colored blouse or dress.
She smiles faintly while looking down at the clean dish in her hands.
Behind her is a patterned kitchen wall with repeating small motifs, and part of a sink or counter is visible.
She lifts and presents a large clean plate, its pale surface smooth and shiny.
A dish rack filled with clean dishes appears : several plates stand upright in a row, with a glass and round pieces of tableware arranged in the wire rack.
Thin drawn sparkle lines radiate around the dishes to suggest shine.
Bold white text appears along the bottom : “ FROM GREASE TO SHINE, ” followed by “ IN HALF THE TIME. ” The Joy bottle then appears over the rack, and the word “ JOY ” is emphasized in large letters beneath it before the bottle stands alone again against a simple studio backdrop.
The bottle is shown centered on a counter in front of a plaid or grid-patterned background.
It gradually appears smaller and shifts to the left side of the scene, leaving open space on the right.
A large box labeled “ Soap Powder ” appears on the right.
Then a second box slides in beside it, so two tall rectangular soap \textbf{powder} boxes stand next to the smaller Joy bottle.
The comparison is arranged clearly : Joy on the left, two “ Soap Powder ” boxes on the right.
The imagery returns to the close view of the woman ’s hand.
Her thumb and forefinger again hold a small glossy amount of liquid, which stretches into a smooth teardrop hanging below her fingers.
The droplet elongates and gleams against the blurred background.
The final portion becomes graphic and animated-looking.
Huge dark letters spell “ JOY ” across a pale background filled with floating outlined bubbles.
The word fills most of the screen.
Then the bubbles multiply and overlap the letters.
A burst-like splash graphic opens in the center, revealing the phrase “ Joy in a bottle. ” More words appear until the full message reads : “ Joy in a bottle beats anything in a box! ” The background remains filled with drifting bubble outlines.
At the end, the Joy bottle appears again in front of the slogan, with a soap \textbf{powder} box behind it, reinforcing the final comparison between the bottle and boxed \textbf{powders}.

% matched lemmas: powder, smear, squat
\end{textsample}
