\begin{textsample}{NEG Dim 8 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_89.txt}  \label{ex:f8_neg_013}
The commercial is in black and white and unfolds through a series of showroom, office, and car-detail shots.
It opens on a black frame.
The first visible scene shows a desk or worktable covered with papers and advertising boards.
A man ’s hands are handling a large printed sign or layout.
Several signs emphasize cost, with visible words such as “ LOW, ” “ LOWEST, ” “ COST, ” and “ ALL the FEATURES. ” The setting appears like an office or design/planning area, with shelves or books in the background.
The scene then changes to a man standing near a large wall-mounted notice board.
Several papers are pinned to the board.
The man is partly transparent or blurred in the transition, suggesting a dissolve or superimposed effect.
He appears to be moving past the board or turning away from it.
A stylized transition follows : the image is framed by dark vertical borders, like looking through a narrow aperture or filmstrip.
Through this, a white 1950s Chevrolet-style car is seen in a showroom-like space.
The commercial then presents glamour shots of the car.
A close frontal view highlights the large chrome grille, bumper, headlights, hood ornament, and decorative front-end styling.
Another close-up moves along the front fender and hood area, showing chrome trim, side vents, the headlight housing, and the glossy body surface.
Next, the interior is shown with the driver ’s door open.
The camera looks into a spacious cabin with a large light-colored steering wheel, dashboard, front \textbf{bench} seat, and rear seating area.
The door panel and chrome-framed window are visible.
A man wearing a hat is then seen seated inside the car, viewed from outside through the side window.
He appears to be in the driver ’s position.
Another shot returns to the open-door interior view, showing the man seated at the wheel with his upper body partly visible.
Another dark, narrow-framed transition appears, again resembling a view through a slot or filmstrip.
The car is then shown in motion or staged against a cloudy backdrop.
A side view shows two men inside the car : the driver in a hat and another man seated behind or beside him.
The car ’s side windows, door handle, rear side panel, and curved roofline are clearly visible.
The image briefly returns to the narrow, dark-framed transitional view, showing the car from a distance in the showroom-like setting.
The final frame shows a wide view of a dealership or showroom display.
Large wall text reads “ ‘ 57 CHEVROLET. ” Several cars are arranged indoors on a glossy floor.
A man stands near the central car, facing it or the wall.
Chairs, small tables, and printed materials are visible in the foreground, reinforcing the showroom setting.

% matched lemmas: bench
\end{textsample}
