\begin{textsample}{NEG Dim 8 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_2.txt}  \label{ex:f8_neg_008}
The commercial opens in a warm, sepia-toned close view of the inside of an IBM electric typewriter.
A sheet of white paper is held around the dark \textbf{cylindrical} platen, with faint typed words already visible near the top.
In the foreground, the machine ’s metal rails, rollers, and typing mechanism run diagonally across the picture.
The small square IBM badge appears on the light-colored body of the typewriter.
The printing mechanism moves rapidly along the line, a shiny, rounded metal element flickering near the paper as new characters are struck.
The surrounding studio background is mostly black, making the pale typewriter body and white paper stand out.
The view widens to show more of the IBM Selectric Typewriter : a cream or light beige machine with a broad curved front, a keyboard at the lower left, a large round knob on the right side, and a sheet of paper rising from the carriage.
A pair of adult hands, light-skinned, rests over the keys and types.
The fingers are the only human presence ; the person ’s face and body are not shown.
As the typing continues, attention shifts to the Selectric ’s distinctive printing element : a shiny, golf-ball-shaped metal sphere covered with rows of raised letters, numbers, and punctuation marks.
It has a small loop-like handle or latch on top.
The element is shown by itself and then mounted in the typewriter, where it spins and tilts with quick, precise movements.
In enlarged views, its polished surface catches bright highlights while the raised characters blur as it turns.
At moments the motion is slowed enough to make the action clearer : the sphere rotates to bring a chosen character into position, tilts forward, and strikes toward the paper, then pulls back and repositions for the next character.
Behind it, typed text becomes legible in fragments, including the beginning of a line reading, “ The ‘ Selectric ’... ” followed by partial words such as “ system ” and “ dual stroke, ” though some words are cut off by the machinery.
The \textbf{demonstration} then emphasizes changing the printing element.
A light-skinned hand reaches in from above and grips the small loop on top of the metal sphere.
The fingers lift it away from the typewriter mechanism.
The scene changes to a white tabletop or display surface holding several identical-looking Selectric elements arranged in a cluster.
Each is a rounded metal ball with raised characters around the sides and a dark cap on top ; some caps show white IBM lettering and small type-style markings that are partly visible but not fully readable.
A hand selects one element from among the group, pinching it by the top loop, and lifts it out.
Back inside the typewriter, the chosen element is placed onto its central mount.
The hand presses and settles it into position, using the top loop to secure it.
Once installed, the machine resumes typing.
The paper now shows several typed lines, including partial text beginning “ The ‘ Selectric ’ Typewri... ” and another line below in a visibly different, more slanted type style that begins, “ You can change type sty... ” The metal element moves back and forth in front of the paper as it prints the new line.
The commercial ends by returning to the full typewriter in the dark studio setting, with the white sheet in the carriage and the same pair of hands typing steadily on the keyboard.

% matched lemmas: cylindrical, demonstration
\end{textsample}
