\begin{textsample}{NEG Dim 8 – 2000 – Score -2.00 – 2000/tv\_com\_2000\_105.txt}  \label{ex:f8_neg_073}
The commercial begins with a close, low frontal view of a dark Dodge Ram pickup driving on a road through an open landscape.
The truck ’s chrome grille dominates the frame.
Small white disclaimer text appears along the bottom, including wording about vehicles being shown with optional features and securing cargo.
It cuts to a close-up of the truck ’s front wheel rolling along the road, then to a wider shot of the pickup driving on a curving mountain or canyon road bordered by rock walls and a guardrail.
The imagery emphasizes motion, chrome details, and rugged scenery.
A man is then shown beside a dark truck with “ Ram 1500 ” visible on the door.
He stands close to the driver-side area, partly facing the camera.
The next shot is a close-up of the side of the truck, showing a badge reading “ 5.7 liter HEMI magnum, ” with the wheel and fender beneath it.
The setting changes to an urban/industrial-looking location with older stone or concrete buildings.
A silver/gray Dodge Ram is parked in a courtyard-like space.
A man in a yellow jacket stands beside it and then appears in a closer angled shot walking near the front of the truck.
The commercial then shifts to a worksite.
A man wearing a white \textbf{hard} hat leans against or stands beside a light-colored pickup.
A wider view shows him with the truck in an industrial yard with large structures, conveyors, or machinery in the background.
Next, a red Dodge Ram pickup is shown near a barn or farm building, with green hills and trees nearby.
A woman stands at the front side of the red truck.
A close-up follows of her face and upper body, with the red truck visible behind her.
Small promotional text appears at the bottom, but it is only partly legible in the sampled frames.
The man in the yellow jacket appears again beside the gray truck in front of a large weathered building.
Large painted lettering on the wall includes “ STEEL FABRIC … ” and other partially obscured words.
The woman at the farm setting is then shown loading what appears to be a saddle or equestrian gear into the open bed of the red pickup.
The truck bed and tailgate area are visible.
Back at the industrial site, the light-colored pickup is shown with a large cylindrical or coiled object in its bed.
The hard-hat \textbf{worker} stands at the side of the truck and then moves toward or opens the driver-side door.
A graphic screen follows with a red-and-white “ Dodge Spring Event ” label at the top and large bold lettering in the background ; the visible letters include “ JOIN. ” The final shots return to the gray Dodge Ram and the man in the yellow jacket in the urban/industrial courtyard.
The camera shows the truck from a high angle and then a closer front-side angle, with the man standing near the front fender and facing toward the camera.

% matched lemmas: hard, worker
\end{textsample}
