\begin{textsample}{POS Dim 8 – 1950 – Score 6.00 – 1950/tv\_com\_1950\_41.txt}  \label{ex:f8_pos_001}
Now, here 's a question I have for you ladies.
What will they think of next?
Here 's Evelyn Patrick to tell you about a combination they did think of next.
Snow Peach and Futurama.
Yes, girls, for color that puts a new light on your lips that is pure allure, you 'll want Revlon 's shade of Snow Peach lipstick.
And, of course, you 'll want it in a glamorous Futurama like this.
The engraved white enamel case is just perfect for any fashion and bound to give you that feeling of elegance every woman wants.
With Futurama within easy \textbf{reach}, you 're at your best.
But the marvelous part about this stunning Futurama is it looks expensive, but it 's not.
And remember, with Futurama, you 're getting a permanent case because all you need ever \textbf{buy} again is a Revlon refill that clicks in and out as easily as this.
That means a saving of 35 \textbf{cents} on every single lipstick you \textbf{buy}.
So, girls, when you say...... the light, bright shade that 's bound to give you a look of \textbf{summer} brilliance, say, Snow Peach in a Futurama.
That 's right, girls.
Give yourself a \textbf{gift} of a Snow Peach in a Futurama \textbf{tomorrow}.
And, folks, remember, Futurama is the perfect \textbf{gift} for graduations, bridesmaids, birthdays, an anniversary, really nearly anything.
Thank you.
Try it.

% matched lemmas: buy, cent, gift, reach, summer, tomorrow
\end{textsample}
