\begin{textsample}{NEG Dim 1 – 2000 – Score 1.00 – 2000/tv\_com\_2000\_74.txt}  \label{ex:f1_neg_088}
The commercial appears to be set in a controlled test or demonstration environment with suspended carpet samples and people wearing protective headphones.
At the start, the image is dark and close-up.
A hand or arm is seen near a surface, possibly adjusting or placing something, but the exact action is unclear because the frame is dim.
The scene then cuts to a brighter laboratory-like space.
A carpet sample or panel hangs from an overhead rig.
A dark-haired woman in black stands behind or near the hanging sample, while a blonde woman in white stands to the side with her arms crossed.
Both appear to be in a testing area with metal frames and overhead lighting.
Next, the dark-haired woman, wearing protective earmuffs and glasses, holds up a blue aerosol can labeled partly with “ SPOT CLEAN. ” She sprays a beige carpet panel.
A visible spray mist comes from the can toward the carpet surface.
A close-up shows a hanging beige carpet swatch with a visible dark stain or mark in the center.
The texture of the carpet is clearly shown.
The blonde woman in white, also wearing protective earmuffs, then reaches upward toward a hanging carpet sample and presses or rubs it with both hands, as if applying or working something into the surface.
A comparison shot follows : two carpet samples hang side by side against a green background.
On-screen text and graphics identify the left side as “ OXY DEEP 2x ” and the right side as “ A Leading Competitor. ” A circular timer-like graphic appears between them, showing “ 6 sec. ” The right sample still has a visible mark, while the left sample appears less marked in the sampled frame.
The dark-haired woman is then shown close-up, removing or adjusting her protective glasses.
Her facial expression looks skeptical or concerned, with pursed lips and raised brows.
Another comparison shot of the two hanging carpet samples appears.
The same labels are visible : “ OXY DEEP 2x ” on the left and “ A Leading Competitor ” on the right.
The timer-like circle now shows “ 5 sec. ” The right sample still appears to have a visible stain area ; the left appears comparatively cleaner in the sampled image.
The commercial then cuts to a product pack shot.
On the left, large blue text reads “ Woolite, ” with the tagline “ Tough love for your carpet ” underneath.
On the right is a packaged product labeled “ Woolite OXY DEEP 2x, ” shown in a red-and-blue container with a handle.
In the final shots, the blonde woman in white walks forward in the same test environment, wearing headphones.
She then holds up a small colorful object or product-related item toward the camera ; the exact object is not fully clear from the sampled frame.

% matched lemmas: 
\end{textsample}
