\begin{textsample}{NEG Dim 1 – 2020 – Score 3.00 – 2020/tv\_com\_2020\_10.txt}  \label{ex:f1_neg_089}
In a simple hand-drawn park with pale grass, low bushes, and a tree trunk in the background, two cartoon dogs face each other.
On the left is a small cream-colored poodle with fluffy ears, a blue bow on its head, and a little heart-shaped tag at its neck.
On the right is a larger pale gray dog with floppy ears, a big rounded nose, a pink collar, and a yellow tag.
The poodle stands calmly with eyes half closed, while the gray dog approaches eagerly.
The gray dog becomes very animated, bouncing up into the air and then rolling onto its back in front of the poodle as if trying to impress or play.
The poodle remains composed, lifting a paw daintily and watching him.
The gray dog lowers into a play bow, front legs down and rear up, while the poodle looks on with a reserved expression.
A tall, slim man appears nearby in the park beside a tree.
He has short dark hair and wears a blue shirt, light trousers, and brown shoes.
Several red leashes hang from his hand and arm.
He stands looking toward the dogs, apparently calling for the gray dog.
Back with the dogs, the poodle steps away with a fluffy puff-like cloud behind it, while the gray dog stands alert, nose raised.
The poodle then lowers its head and body slightly, and the gray dog sits nearby, scratching or shifting uncertainly.
A moment later the gray dog sits facing the poodle and holds a small Red Bull can in one paw.
The can is blue and silver with the red-and-yellow bull logo visible.
He lifts it to his mouth as if drinking from it, while the poodle stands opposite him.
After that, the gray dog becomes more lively.
He leans forward, then starts trotting away from the poodle across the open grass.
He moves with a brisk, eager gait, ears flopping and tail raised.
He heads toward the man with the leashes, who is standing beside the tree.
The gray dog reaches him and presses up close, nuzzling at his hand.
The man bends slightly and attaches or gathers the leash at the dog ’s collar.
Once leashed, the gray dog immediately \textbf{surges} around the man ’s legs and the tree.
The man holds the red leash, but the dog pulls hard, circling the trunk and darting from one side to the other.
The leash stretches taut as the dog runs.
The man tries to keep hold of the loops, but the dog ’s path winds the leash around him.
The gray dog races in repeated circles, shown with sketchy motion lines around his body, until the red leash wraps several times around the man ’s waist and the tree trunk.
The man ends up pinned upright against the tree, his torso bound in multiple red loops.
The gray dog finally pauses beside the tied-up man, still attached by the leash.
He sits for a moment with a satisfied, relaxed expression.
Then he rises onto his hind legs like a person and takes hold of the leash near his collar, tugging it with his front paws.
Standing upright, he pulls and works at the leash until he can walk away from the man.
The man remains bound to the tree at the edge of the scene, while the gray dog steps off on two legs with a jaunty, self-assured posture.
The gray dog returns to the poodle, still walking upright.
The poodle reappears from the left and watches him approach.
She first stands, then sits neatly with her front paws lifted in a poised, almost impressed pose.
The gray dog stands tall in front of her, chest forward, eyes closed in a pleased expression, and gestures with one paw as if resuming their date.
The poodle looks up at him with a small smile, and he leans closer, mouth open as if speaking.
The commercial ends on a clean white background with a single open Red Bull can centered on screen.
The can is blue and silver with water droplets, the Red Bull logo, and the pull tab visible on top.
Beneath it, black text reads : “ Red Bull gives you wiiings. ”

% matched lemmas: surge
\end{textsample}
