\begin{textsample}{NEG Dim 1 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_64.txt}  \label{ex:f1_neg_057}
The commercial opens with very dark imagery.
In the first two sampled frames, only \textbf{vague} shapes and faint colored text or graphics are visible ; the details are mostly unclear because the scene is underlit.
At around 2.6 seconds, the ad cuts to a close-up of a sandwich being assembled or displayed.
Red, sauce-covered meatballs sit inside a split bread roll, with pale cheese visible underneath.
Small white on-screen text at the bottom reads : “ For a \textbf{limited} time on 6"subs. ” The next frame shows a Subway employee in a red uniform and red cap, smiling toward the camera while holding a tray of long bread rolls.
Behind her are bakery racks filled with additional rolls.
The same small text remains at the bottom : “ For a \textbf{limited} time on 6"subs. ” The commercial then moves into close-up food preparation shots.
A large pot or pan of \textbf{thick} red tomato sauce is being stirred with a wooden spoon.
This is followed by a close-up of a tomato being sliced, with red slices lying on a cutting surface.
Another close-up shows a green bell pepper on a cutting board, with a blurred hand or knife motion above it.
The next image returns to the sandwich : a close-up of meatballs in red sauce inside a bread roll, with melted or folded pale cheese beneath.
The sandwich fills most of the frame and is presented as the main product.
Around 8.9 seconds, the scene cuts to a single wrapped or paper-covered round object on a dark tabletop or counter, lit from above.
Its identity is not fully clear from the frame alone.
The final frame is a full product and price graphic.
On the right is the meatball sub, shown partly wrapped in white paper, with red sauce and meatballs visible inside the bread.
Large colorful text on the left reads : “ THE SUBWAY MEATBALL SUB ” and “ JUST 96¢ FOR A \textbf{LIMITED} TIME. ” The Subway logo appears near the bottom right.
Small fine print along the bottom reads that the offer is at \textbf{participating} stores and mentions beverage purchase requirements, with additional regional price limitations.

% matched lemmas: limited, participate, thick, vague
\end{textsample}
