\begin{textsample}{NEG Dim 1 – 1950 – Score -3.00 – 1950/tv\_com\_1950\_29.txt}  \label{ex:f1_neg_010}
In black and white, the commercial begins in a backstage dressing-room-like space.
A stair rail and plain walls are visible in the background, and a \textbf{vanity} table with round light bulbs around a mirror stands to the left.
Several young adult women are gathered there.
Most wear light short-sleeved tops with dark \textbf{high-waisted} pants or skirts, giving the scene a rehearsal or dressing-room feel.
At the center is a young adult woman presented as the demonstrator : she wears a light, sleeveless, full-skirted ruffled gown and a short \textbf{pearl} necklace, with her hair set in neat, soft curls around her face.
She smiles and turns among the other women as they approach her, all appearing attentive and friendly.
The woman in the gown walks toward the lighted \textbf{vanity} table on the left, with the others following or standing nearby.
The tabletop holds small \textbf{grooming} items and a rectangular product box.
She reaches down and picks up the box, then turns back to face the group.
The others gather around her in a loose semicircle, watching.
She holds the box at chest height with both hands, presenting it clearly.
The package reads “ Richard Hudnut Quick Home Permanent, ” with “ Lanolized ” on a darker band near the bottom.
She keeps the front of the box facing outward while speaking, smiling confidently.
The package is then shown larger against a dark background, held in a woman ’s hands at the right side of the image.
Large bold white words appear to the left : “ NEW PENETRATING INGREDIENT. ” The box still reads “ RICHARD HUDNUT Quick HOME PERMANENT, ” with “ LANOLIZED ” below.
Soon the words change to another bold message : “ PREVENTS WEAK SURFACE WAVES, ” placed to the left of the same product box.
The demonstrator ’s face and dressing-room background briefly overlap with this product image as the commercial returns to her.
A visual hair demonstration follows.
A dark lock of hair hangs vertically against a plain light background.
It has broad waves, but the surface looks loose and uneven.
A hand enters from the right and presses or pinches the hair near the middle, drawing attention to the wave pattern.
The fingers slide and lift sections of the hair, showing that the wave seems shallow and limp near the surface.
The hand then moves away as the hair \textbf{sways} slightly to the left, leaving the impression of a soft but weakly held wave.
A second dark hair sample appears, again held against a plain background.
This time the wave pattern looks more regular and stronger, with a smooth S-shaped curve.
A hand lifts a section from the right side, revealing fine, repeated ripples through the inner layers of the hair, not just along the outside.
The fingers separate and support the lock so the deeper wave pattern is visible across the thickness of the hair.
When the hand releases and smooths the section back, the wave remains rounded and full, with a more natural, lasting-looking shape.
The scene returns to the demonstrator in the dressing room.
She faces forward in her light gown and \textbf{pearls}, framed by the \textbf{vanity} lights on the left and the stair rail in the background.
She smiles as she continues presenting the product.
A close view then features another young adult woman with light blonde hair.
She wears a sleeveless dress and a \textbf{pearl} necklace.
Her hair is styled in soft, sculpted waves around the sides and back, with a smooth rolled shape at the nape and gentle curls near the temples.
She turns her head from side profile toward the front, showing the hairstyle from different angles.
As she faces forward, she smiles warmly, displaying the finished curled look.
The group reappears around the \textbf{vanity}.
The demonstrator stands in the middle, holding the Quick Home Permanent box again.
The blonde woman stands to the left near the lighted mirror, while two other women, including a dark-haired woman in a light top, stand to the right.
They look toward the demonstrator and the package.
The demonstrator raises the box, keeps the label facing outward, and gestures toward it as she talks.
Her expression remains bright and assured.
Near the end, she brings the package closer to her chest and points at the front label with one finger, emphasizing the name “ Quick. ” The final images keep the product box clearly visible beside her smiling face, with the dressing-room lights glowing along the left edge.

% matched lemmas: groom, high-waisted, pearl, sway, vanity
\end{textsample}
