\begin{textsample}{NEG Dim 1 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_29.txt}  \label{ex:f1_neg_027}
The commercial begins with a very dark, indistinct frame.
No clear objects, people, or setting can be identified at the start.
A soft, layered visual transition follows.
Multiple images appear superimposed : a person in a yellow top is visible, and a man in a shirt and tie appears faintly over the scene.
The imagery is hazy and partly transparent, making the exact setting and actions unclear.
The overlapping visuals suggest a montage or dissolve effect rather than a single stable shot.
The next sampled frame shows a child or young person wearing a yellow shirt, holding a blue spray bottle with a white spray nozzle.
The person is turned partly toward the camera and appears to be smiling.
The background remains soft and indistinct, and the image still has a translucent, dreamlike quality.
The commercial then cuts to a clear close-up of a product label.
The text reads “ CLOROX Prewash ” in large blue letters.
Beneath it, smaller text reads “ LAUNDRY SOIL AND STAIN REMOVER. ” The label uses a white central field with red, orange, and blue geometric bands around it.
Later, the same “ CLOROX Prewash ” label remains on screen, now with another image faintly superimposed over it.
A person ’s face or figure is visible behind or through the product label, but the overlay makes the details unclear.
The label text is still readable, emphasizing the product name and purpose.
The final frame shows a smiling blonde woman wearing large eyeglasses and a purple uniform-style top with a light collar.
She holds up a blue Clorox Prewash spray bottle next to her face, presenting it toward the viewer.
A red-and-orange patch or logo-like design is visible on her sleeve.
The background is dark and plain, keeping visual focus on the woman and the product.

% matched lemmas: 
\end{textsample}
