\begin{textsample}{NEG Dim 1 – 1950 – Score -6.00 – 1950/tv\_com\_1950\_104.txt}  \label{ex:f1_neg_002}
The commercial is in black and white.
It begins indoors in a plain dressing-room-like space.
Two young adult women stand close together, both dressed for swimming or changing.
One, on the right, wears a dark \textbf{strapless} one-piece swimsuit with a structured \textbf{bodice}, light piping down the front seams, gathered fabric across the bust, and three pale buttons in a vertical line.
The other, on the left, appears wrapped in a towel or light cover-up.
They smile and look down at a pale undergarment-like swimsuit component the woman in the dark suit is holding.
The towel-wrapped woman points to it and touches it, while the woman in the dark suit unfolds it, turns it in her hands, and holds it open to show its \textbf{high-waisted}, panty-shaped construction.
The focus is on the garment ’s built-in support : the woman stretches it across the front of her own suit, lifts the waistband, and displays the roomy, structured lower section as if demonstrating how it fits inside or under the swimsuit.
The scene moves outdoors to a sunny poolside or beach-club terrace with cabana doors, \textbf{louvered} shutters, lounge chairs, towels, and a woven beach basket.
Several young women in fitted swimsuits gather near the cabanas.
They suddenly spring into motion, leaving chairs and bags behind as they run across the terrace.
One woman in a dark \textbf{strapless} suit leads, while others in lighter suits follow.
Another woman emerges from a doorway and joins them, hurrying after the group.
The women descend an outdoor staircase bordered by smooth white walls and a metal handrail.
They come down in a line, smiling and lively, each wearing a different one-piece swimsuit.
At the bottom, they move into a wide paved courtyard.
In the background are curved white walls, stairs, and a large building with steep roofs and turret-like shapes, giving the setting a club or resort feel.
Three of the women join hands and walk forward together across the open space, arms spread slightly for balance and display.
At the pool area, two women stand high on or beside a diving platform.
One is on the end of a diving board in a dark \textbf{strapless} one-piece with a row of pale buttons down the front ; another stands behind her in a lighter suit, shading her eyes with one hand.
Beneath the board hangs a sign that reads “ POOL CLOSED. ” The woman on the board smiles broadly and waves as if greeting the others, then turns away from the board with the other woman, both looking down and stepping back rather than diving.
The commercial then presents the swimsuits more like a fashion display.
A woman in a light-colored suit is shown from shoulder to thigh, standing with one hand on her hip.
Her suit has a smooth \textbf{bodice} and noticeably shirred, gathered fabric around the hips, creating a soft, ruched band across the lower body.
She shifts her stance slightly to show the shaping at the waist and hips.
Another model in a fitted \textbf{strapless} suit walks toward the viewer ; her suit has a diagonal panel of gathered or ribbed texture running across the front from the upper torso down toward the hip, emphasizing the body-hugging construction.
Two women sit at a small outdoor table on a stone-patterned terrace near the water.
A square board game with letter tiles and racks is laid out between them, resembling Scrabble.
One woman wears the dark structured \textbf{strapless} suit with pale piping and decorative trim across the top ; the other wears a lighter swimsuit and sits in a slatted chair.
They lean toward the board, smiling and concentrating on the game.
The woman in the dark suit then appears standing alone, smiling directly forward as she puts on a very large, pale, floppy straw sunhat with a rippled brim that frames her head like a halo.
She adjusts the brim with both hands, turns slightly to the side, and receives or picks up dark sunglasses.
She brings the sunglasses up and puts them on beneath the wide brim.
Nearby, on the terrace, one woman reclines in a folding lounge chair wearing a dark swimsuit, while another stands beside her in a light, \textbf{strapless}, skirted swimsuit and the large sunhat.
The standing woman hands the seated woman the sunglasses or gestures toward them, and they exchange smiles.
The view tightens to the standing woman ’s side, focusing on a striking vertical strip of white crisscross lacing running down the side of her suit from the upper torso toward the hip.
The seated woman ’s bracelet-covered hand reaches up and traces the lacing, pointing out the decorative feature.
The standing woman holds still, then turns slowly so the side detail, the back curve of the suit, and the skirted lower edge can be seen.
The lacing remains the visual emphasis, contrasting brightly against the darker tone of the suit fabric.
A blonde young woman then poses against a bright sky in a \textbf{strapless} swimsuit with a sculpted, “ winged ” or folded-looking bra front.
She smiles broadly, looking off to one side and then forward.
Her short curled hair is neatly styled, and her posture is upright and poised, with one hand at her hip.
As the view lowers, the suit ’s lower half appears like a short romper or skirted swimsuit, with soft pleats or flap-like panels over the hips.
She slips her hand into a side pocket or pocket-like opening, showing the playful, \textbf{tailored} detail while standing near a rocky waterfront with water and a distant \textbf{shoreline} behind her.
Finally, four women line up on a narrow seawall above rocks and water.
The blonde in the skirted romper-style swimsuit leads, smiling and balancing with both arms extended out to the sides.
Behind her, three other women follow in single file, also barefoot in fitted swimsuits, arms stretched wide like tightrope walkers.
One wears the dark suit with vertical piping and buttons ; the others wear lighter suits.
They move carefully along the seawall with the waterfront and rocks below them, ending the commercial with the group posed in a cheerful, summery line, displaying the variety of Surf Togs swimsuit styles.

% matched lemmas: bodice, high-waisted, louvered, shoreline, strapless, tailored
\end{textsample}
