\begin{textsample}{NEG Dim 1 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_11.txt}  \label{ex:f1_neg_046}
A bright, crowded workroom or classroom-like office is filled with people seated around a table covered in papers, folders, cups, and saucers.
Large paned windows glow behind them, with posters and shelves on the walls.
Kathy, a young adult woman with curly brown shoulder-length hair, stands near the table in a light blouse tucked into a grey skirt with a wide dark belt.
She wears a short necklace and looks active and intent, as if trying to keep the discussion moving.
Around her sit several adults : an older woman with white hair and glasses, a younger woman with short reddish hair and large dark glasses, a dark-haired man in a suit and tie, and a dark-haired woman in a dark top.
They read papers, write, and pass documents while Kathy gestures with one hand, then leans forward over the table to reach for something.
As Kathy stretches across the seated group, her raised arm and blouse move very close to the face of the short-haired woman in glasses.
In a tight view, the seated woman ’s face is partly hidden by her glasses as Kathy ’s sleeve and underarm area fill the foreground.
The seated woman ’s expression changes from concentration to discomfort and suspicion ; her brow tightens, her eyes shift upward, and she seems to register something unpleasant even though Kathy ’s blouse itself appears dry and unstained.
The image emphasizes that nothing visible is wrong with the fabric, yet the nearby person reacts.
The product appears on a bathroom or medicine-cabinet shelf.
A white plastic roll-on \textbf{deodorant} bottle with a dark blue cap stands upright among toiletries.
Its label reads “ SURE ” in dark letters, crossed by diagonal yellow-orange and blue stripes.
A white towel is visible at the edge of the shelf, and glass containers and \textbf{grooming} items sit nearby.
Back in the busy room, Kathy stands behind the seated people and suddenly lifts both hands toward her head.
She looks worried and flustered, fingers pressing into her hair as if the pressure of the situation is getting to her.
The people around the table continue reading and handling papers, while a dark-haired woman at the right glances sideways.
Kathy gathers her hair up with both hands, raising her elbows and exposing the underarm area of her light blouse.
Her posture suggests anxiety or self-consciousness.
A close view of the suited man with round glasses follows ; he looks past Kathy ’s raised arm with a serious, wary expression, his eyes moving as if noticing her presence too closely.
The scene returns to the meeting table from another angle.
Kathy stands behind the seated group holding or looking down toward a sheet of paper, her body still tense but more still.
The older white-haired woman and the short-haired woman with glasses remain seated with documents, while the suited man bends over his work.
The atmosphere remains crowded and pressured, with papers in constant use and people close together.
The setting then shifts to a softer, more private bathroom or bedroom area.
Kathy ’s face appears in a dreamy, close view, eyes closed, one hand near her hair as if \textbf{waking} or preparing for the day.
The background is dim and domestic, with a lamp-like wall fixture and mirrored surfaces.
The view moves across a bathroom mirror area to the medicine cabinet shelf, where the Sure Roll-On bottle stands among cotton swabs in a clear container, a small bottle of nail polish, a round makeup container, and a tall glass perfume bottle with amber liquid.
A hand reaches in from the right, grips the blue cap and upper part of the white Sure bottle, and lifts it from the shelf.
The “ SURE ” label is clearly visible as the product is taken away.
Finally, Kathy appears in a public hallway or lobby filled with people moving behind her.
She now wears a pale pink blouse tucked into a dark skirt, looking neater and more confident.
She walks closely beside a middle-aged man in a suit and glasses, while the older white-haired woman with glasses walks on the other side holding a dark folder.
Kathy glances toward the man, then smiles gently and faces forward.
Large white capital letters spelling “ SURE ” appear across the lower center of the screen as she continues through the crowd, visually linking her more assured appearance with the \textbf{deodorant}.

% matched lemmas: deodorant, groom, wake
\end{textsample}
