\begin{textsample}{NEG Dim 1 – 1990 – Score -2.00 – 1990/tv\_com\_1990\_46.txt}  \label{ex:f1_neg_052}
The commercial begins very dark, with only a faint rectangular sign visible.
The sign appears to show a pizza offer, but the details are hard to read in the first frame.
The image then brightens to a stage-like setup.
A large projection screen or hanging sign fills the background.
It clearly reads : - “ 2 PIZZAS ” - “ \$5.99 ” In front of the sign, centered low in the frame, is a small performer or character with a dark head covering or hair and a bright face.
The costume or prop in front of them is yellow with dark spots, resembling a pizza slice or pizza-themed outfit.
Along the bottom of the image, small white disclaimer text reads : “ \textbf{Limited} time offer in \textbf{participating} stores.
Pricing may vary. ” This same composition remains for several frames with little visible change : the large price sign stays centered, the small pizza-themed figure remains in front, and the disclaimer stays at the bottom.
The commercial then cuts to a close-up of a man styled like an Elvis impersonator : he has large dark hair, dark sunglasses, a white decorated jacket with red/orange details, and visible jewelry.
The lighting is dramatic, with a bright flare or spotlight near his face and a round light visible in the background.
The final frame returns to the large offer sign reading “ 2 PIZZAS \$5.99. ” In front of it, at the lower right, there is a small animated Little Caesars-style character holding up a pizza-like object.
Across the bottom, large branding text reads “ Little Caesars Pizza!
Pizza! ” with the Little Caesars logo at the left.
Smaller text beneath says “ \$8.99 in Alaska \& Hawaii. ”

% matched lemmas: limited, participate
\end{textsample}
