\begin{textsample}{NEG Dim 1 – 1960 – Score -5.00 – 1960/tv\_com\_1960\_36.txt}  \label{ex:f1_neg_023}
The commercial begins in black and white with a San Francisco landmark : a large rooftop sign spelling “ SAN FRANCISCO ” stretches across the top of a building, with a tall clock tower rising at the left.
The view then shifts to the product itself, a soft metal tube of Groom \& Clean lying diagonally across a wet, rippling surface.
Water flows around and beneath it, making the tube look freshly washed.
The label is large and bold : “ \textbf{GROOM} \& CLEAN, ” with smaller wording visible near the bottom reading “ hair \textbf{grooming} — without grease. ” A small illustration of a man ’s \textbf{groomed} head appears near one end of the tube.
A fast sequence of San Francisco \textbf{sights} follows.
A cable car travels down a city street between tall buildings and parked cars, with people riding on the outside platform.
Coit Tower is shown from below, rising high above trees against a pale sky.
A dark, shadowy interior or covered space appears briefly, with palm-like shapes and bright window openings in the background, before the scene opens onto a young woman with long loose hair.
She is outdoors by the water, smiling broadly and clutching a hanging fishing net or rope net with both hands.
Her costume is shimmering and scale-like, suggesting a mermaid.
Behind her, the bay and city waterfront are visible in soft focus.
She leans around the net, grinning and gesturing playfully toward the viewer, then pulls back to reveal more of her body : she has a fitted, \textbf{glittering} mermaid tail that curves down into the water.
She swings from the net above the bay, waving one arm while her tail splashes and flicks at the surface, with boats, piers, and the San Francisco skyline behind her.
The action returns to the city.
A cable car is seen from a low angle as people board ; a man in a dark suit helps or steadies others at the entrance.
The side of the cable car passes close by, and a small “ Pepsi ” sign or advertisement is visible on the car ’s side.
Two young adults, a man in a suit and a woman in a light top, ride together and smile as they look out.
They appear cheerful and windblown, leaning near a vertical pole on the car.
A large street sign or billboard then fills the view with the words “ \textbf{GROOM} \& CLEAN ” in huge block letters.
Beneath it, smaller text reads “ clear cleansing hair \textbf{grooming} — without grease, ” and “ SAN FRANCISCO ” is visible below the sign.
The young couple continues smiling on the moving cable car, looking off to the side as if reacting to the city around them.
The imagery becomes bright and hazy, with the man and woman partly silhouetted against buildings and sunlight.
Then a young man appears in a convertible, seen from the side inside the car.
He has short, neatly combed dark hair and wears a patterned shirt.
He turns his head and smiles while riding through the city.
The view widens to show a light-colored convertible carrying several young adults.
The driver sits at the front, with other passengers seated behind, all moving through streets lined with apartment buildings.
The car rolls along in the sunshine, the passengers ’ hair and clothing stirred by the open air.
A close-up shows a man \textbf{grooming} his hair.
His head is tilted down, and a hand draws a comb through the front and side of his dark hair.
The hair looks wet or glossy but orderly, with comb lines visible as the teeth pass through.
The comb moves steadily from the front hairline toward the side, shaping the hair into a smooth natural wave.
The close-up emphasizes the hair ’s texture : controlled, shiny, and clean-looking rather than heavy.
The setting shifts to the Golden Gate Bridge and rocky \textbf{shoreline}.
A young woman in the same mermaid-like costume sits on large dark rocks beside churning water.
The bridge towers and cables stretch behind her, and waves break white against the rocks in the foreground.
She holds a tube or small product container near her chest as if presenting or discussing it.
Large white on-screen words appear beside her : “ water active. ” She smiles and looks toward the viewer while the bridge structure frames the background.
The product demonstration begins in close-up.
A hand holds the Groom \& Clean tube and squeezes a dark, glossy ribbon of hair dressing into an open palm.
The “ water active ” words remain on screen.
The product sits on the skin like a small curved strip of gel.
The hand then moves into water.
As the palm swishes through the surface, the gel mixes with the water, creating ripples, bubbles, and a foamy-looking swirl.
The product appears to disperse and wash away rather than stay greasy.
After several passes through the water, the palm is shown open and clean, with the “ water active ” text still visible beside it.
The \textbf{grooming} demonstration continues with another close-up of the man ’s head.
Hands and a comb work through his damp-looking hair, smoothing it down and guiding it into shape.
Bold white words appear over the hair : “ cleans away dirt dandruff. ” The comb moves along the side and top of the head while fingers press and separate the hair near the temple.
The words remain centered over the dark hair as the combing continues, visually linking the wet-combing action with cleansing.
The commercial returns to the convertible by the water.
A young man with neatly \textbf{groomed} dark hair sits close beside a young woman wearing a light headscarf tied around her hair.
They smile and relax together, with water shimmering behind them.
The man ’s hair remains smooth and controlled despite the outdoor setting.
The woman turns her face slightly upward and away, smiling calmly as the car or boat-like setting moves near the bay.
A \textbf{sailboat} appears on the water with the Golden Gate Bridge in the background.
Its large \textbf{sail} has bold curved panels and numbers near the top.
The boat moves across choppy water, leaning slightly with the wind.
The scene then shifts to two young adults standing on a rocky slope near a large round mechanical or nautical object at the left edge, possibly part of boating equipment.
The woman wears a light outfit and moves rhythmically, facing a man in a light shirt and dark trousers.
They gesture and dance casually together, smiling and turning toward each other in the open air.
The man is then shown in close profile against a bright sky, smiling as he turns his head.
His short hair stays neatly in place, shaped close to the head.
The mermaid figure returns, swinging again from the hanging net over the bay.
She reclines in the net with her \textbf{glittering} tail trailing through the water, then raises herself, laughs, and flicks the tail so it splashes.
In a wider silhouette, she hangs high above the water with the Golden Gate Bridge off to the left, her body and tail forming a curved shape inside the net.
She swings back and forth, then leans toward the camera, smiling and waving one arm.
Her long hair falls around her face, and the city waterfront blurs behind her.
The commercial ends by returning to the product tube.
Groom \& Clean lies diagonally across the wet, flowing surface again, with water moving beneath it.
The brand name “ \textbf{GROOM} \& CLEAN ” dominates the label, and the smaller phrase “ hair \textbf{grooming} — without grease ” is visible near the bottom, reinforcing the product ’s clean, water-soluble presentation.

% matched lemmas: glitter, groom, sail, sailboat, shoreline, sight
\end{textsample}
