\begin{textsample}{NEG Dim 1 – 2020 – Score 1.00 – 2020/tv\_com\_2020\_103.txt}  \label{ex:f1_neg_067}
The commercial unfolds in a bright, tidy home interior. 1. **Opening living-room scene:** An adult man stands behind a blue sofa, holding and folding a gray \textbf{blanket} or piece of fabric.
The room has framed wall \textbf{art}, plants, shelves, and a staircase in the background. 2. **Child entering with toy:** A young girl wearing denim overalls, a striped shirt, and a backpack is shown near a glass door and coat area.
She is holding or dragging a gray stuffed rabbit toy by one ear.
The room contains children ’s items, toys, and bags. 3. **Close-up of toy near shoes:** The stuffed rabbit is dragged along the floor beside the girl ’s sneakers.
The toy appears to be in contact with the floor. 4. **Girl holding the stuffed rabbit:** The girl lifts the stuffed rabbit close to her face and chest.
She looks upward, as if addressing someone off-frame. 5. **Man reacting:** A close-up shows the man looking concerned or alert.
He faces toward the girl ’s direction. 6. **Girl in the room:** The girl stands near a coat rack with hanging jackets and bags.
She smiles while holding the stuffed rabbit.
The bright interior and children ’s objects remain visible. 7. **Object flying through living room:** In the living room, a gray fabric item or toy is airborne above the sofa.
The man is partly crouched or moving quickly, as if reacting to it. 8. **Man moving quickly across the room:** The man runs or leaps near the sofa while a gray item moves through the air.
The girl ’s arm is visible at the right edge.
Small on-screen text near the bottom reads : “ Use as directed. ” 9. **Stuffed rabbit and laundry basket:** A close-up shows the gray stuffed rabbit moving toward or into a white laundry basket.
Inside the basket is clothing and a bottle labeled Lysol Laundry Sanitizer.
The text “ Use as directed. ” remains visible at the bottom. 10. **Product on laundry-room surface:** A hand places a white bottle with a blue cap labeled Lysol Laundry Sanitizer on a laundry-room counter.
A yellow bottle is visible behind it. 11. **Stuffed rabbit in washing machine:** The stuffed rabbit is visible inside the front window of a washing machine among light-colored laundry.
A hand is near the washing-machine door.
The bottom text again reads : “ Use as directed. ” 12. **Product being used:** The man stands at the washing machine with the detergent drawer open.
The Lysol Laundry Sanitizer bottle is on the counter, and he holds a blue cap, suggesting product is being added.
The yellow bottle remains in the background.
The bottom text reads : “ Use as directed. ” 13. **Girl receiving or seeing the stuffed rabbit again:** The stuffed rabbit is shown close to the camera, blurred in motion, with the girl smiling behind it on the sofa.
The living-room staircase and wall \textbf{art} are visible in the background.
The bottom text “ Use as directed. ” is still present. 14. **Product packshot and offer text:** Two Lysol Laundry Sanitizer bottles are displayed on a clean surface : a larger bottle and a smaller “ new trial \textbf{size} ” bottle.
Large white text on the right reads : “ TRY FOR UNDER \$5. ” A small red label above the smaller bottle reads : “ NEW TRIAL \textbf{SIZE}. ” 15. **Final product display:** The final frame remains on the two Lysol Laundry Sanitizer bottles with the same large text : “ TRY FOR UNDER \$5 ” and the red “ NEW TRIAL \textbf{SIZE} ” label.

% matched lemmas: art, blanket, size
\end{textsample}
