\begin{textsample}{NEG Dim 1 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_94.txt}  \label{ex:f1_neg_050}
The sampled frames show the commercial moving from a technical slate to close-ups of a \textbf{record} player and then to a final product display. 1. **Opening frame (0.000s)** The screen is black with white overlaid text reading **“Not For Broadcast”** near the upper left/center area.
A white timecode appears near the bottom : **“01:00:00:00.”** No product or scene is visible yet. 2. **Record player close-up (7.113s)** The scene cuts to a close-up of a turntable.
A black vinyl \textbf{record} with a red center label is spinning or positioned on the platter.
A hand is holding or guiding the tonearm/cartridge assembly toward the \textbf{record}.
The tonearm mechanism and spindle are visible.
The background appears to be a wood-toned surface.
The “ Not For Broadcast ” watermark and timecode remain overlaid. 3. **Tonearm on/near the \textbf{record} (14.663s)** A closer side view shows the tonearm and cartridge positioned at the edge of or on the \textbf{record}.
The \textbf{record} ’s black surface and red label are still visible.
The spindle and parts of the turntable mechanism are in view.
The hand is no longer visible.
The same “ Not For Broadcast ” watermark and timecode remain on screen. 4. **Final product shot (59.041s)** The scene changes to a room setting with a wooden console cabinet centered in the frame.
The cabinet has speaker panels on the left and right and wooden doors in the middle, suggesting a home audio or stereo console.
A vase of flowers sits on top, and a framed landscape picture hangs behind it.
Large white stylized text **“ZENITH”** appears above the console.
At the bottom, a slogan is visible : **“The quality goes in before the name goes on”** though part of it is overlapped by the timecode.
To the right of the console is a chair, with curtains behind it.
The “ Not For Broadcast ” watermark and timecode remain visible.

% matched lemmas: record
\end{textsample}
