\begin{textsample}{NEG Dim 1 – 1970 – Score 1.00 – 1970/tv\_com\_1970\_119.txt}  \label{ex:f1_neg_037}
The commercial appears in a soft, slightly blurred, 1970s-style image with dark borders around the frame.
It unfolds through quick dissolves and superimposed imagery. 1. **Opening shot** : A dark-haired man is shown in a busy indoor setting.
The background is crowded and indistinct, with shapes suggesting people or displays.
He looks downward, holding something small near his chest or face, but the object is not clear. 2. **Instant-photo image** : The scene changes to what looks like a printed instant photograph.
Two people are visible inside a white photo border : an older woman wearing glasses on the left and a younger person with dark hair on the right.
They appear close together, smiling or posing. 3. **Layered portrait imagery** : A dissolve overlays another image of a woman and child or young person.
The figures are partially transparent due to the transition.
A small camera-like object or dark rectangular item appears near the center, but details are unclear. 4. **Group of photographers** : The image shifts to a crowd of people facing forward, many holding cameras up to their faces.
Several camera flashes or reflective camera fronts are visible.
The group fills the frame, suggesting many people taking photographs at once. 5. **Man with camera** : Through another dissolve, a smiling man appears in the foreground, holding a camera close to his face.
Other figures and cameras remain faintly visible behind him because of the overlapping transition. 6. **Product/price title card** : A graphic title card appears on a dark blue/purple background with large white text.
It reads : “ \$66* Pronto!
A Polaroid Land camera ” Beneath that, in smaller text, it reads : “ *Suggested list price. ” 7. **Fade to black** : The screen cuts or fades to black. 8. **Black end frame** : The commercial remains black through the final sampled frame.

% matched lemmas: 
\end{textsample}
