\begin{textsample}{NEG Dim 1 – 1950 – Score -2.00 – 1950/tv\_com\_1950\_20.txt}  \label{ex:f1_neg_016}
In black and white, a smiling young blonde woman appears inside a circular medallion, posed like a beauty portrait with bare shoulders and curled 1950s hair.
The circle is set against a plain light background.
As the view widens, the medallion is revealed as part of a large rectangular bar of soap with rounded corners.
The word “ CAMAY ” is carved in large capital letters across the front of the bar, and the woman ’s profile portrait sits above it.
The soap rests on glossy, dark, satin-like fabric that catches the light in soft folds.
The scene changes to a stylized, theatrical space with tall, dark, pillar-like shapes standing in a row.
They resemble oversized ornamental columns or chess-piece forms, and they cast heavy shadows across a pale floor and background.
A slim young woman in a long dress moves among them almost entirely in silhouette.
She passes behind one column, then reappears between two of them, her body and face still mostly hidden in darkness.
She pauses, turns slightly, and continues forward through the dim space.
The columns dominate the foreground, making her look small and partially obscured.
Gradually she steps away from the heavy shadows.
Her features become clearer : she is a young blonde woman with short curled hair, wearing an elegant light-colored satin evening gown with an off-the-shoulder neckline and long sleeves.
A single strand necklace rests at her collarbone.
As she comes into brighter light, she smiles warmly, first looking downward and then toward the viewer.
The shadowy column remains off to one side while the background becomes softer and lighter, with faint leafy shadow patterns behind her.
She tilts her head and smiles with a poised, glamorous expression.
Her appearance then blends into a bridal image.
A translucent veil appears over and behind her hair, and her gown changes to a high-necked white bridal dress with a delicate lace collar and a row of small buttons down the front.
The veil frames her face and falls over both shoulders.
She faces forward with the same composed smile, presented as a radiant bride.
The commercial then shifts to a different young woman with short dark hair, wearing a sleeveless light slip or undergarment against a plain bright background.
She holds a mound of white \textbf{lather} in one cupped hand and touches her cheek with the other, smiling slightly and looking upward.
She brings the \textbf{lather} to her face and begins washing.
Foam appears on her cheeks and around her mouth as she gently rubs in circular strokes.
She uses one hand, then both hands, spreading the creamy \textbf{lather} over each cheek and along her chin.
Her expression stays pleasant and relaxed as she massages the soap across her face.
A closer, more high-contrast view follows, with the same or a similar woman reclining or tilting her head back while washing.
Her face is partly covered with \textbf{suds}, especially around the mouth, chin, and cheeks.
Both hands move over her face and neck area, smoothing and lifting the \textbf{lather}.
Bright light falls across her face, making the foam stand out sharply against the darker background.
As her hands rise, water or misty brightness passes over the image, and the face becomes increasingly obscured by soft, swirling light and \textbf{suds}.
The image resolves into a round mirror or circular frame.
Inside it is a young dark-haired woman in a light blouse or jacket, wearing small earrings and a necklace.
She is seated in what appears to be a social setting.
A man in a suit is partly visible to her right, facing her.
In front of them are glasses, possibly stemmed drinking glasses, and her hand rests near one of them.
She looks toward the man, her expression softening into a smile.
As they face each other, she appears pleased and attentive, while he looks back at her from the side.
The final product display shows Camay packaging laid on draped satin fabric.
A wrapped bar stands prominently in the center-right, with a circular profile silhouette emblem near the top and the large word “ CAMAY ” printed across the front.
Along the bottom band, the package reads, “ THE SOAP OF BEAUTIFUL WOMEN. ” To the left is an unwrapped pale bar of soap, also with faint Camay lettering on it.
Behind and beside the package are decorative clusters of small round beads or flowers, adding a luxurious display.
The arrangement remains steady, with the Camay box and unwrapped soap clearly presented as the closing image.

% matched lemmas: lather, suds
\end{textsample}
