\begin{textsample}{NEG Dim 1 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_14.txt}  \label{ex:f1_neg_030}
The commercial is in black and white.
It opens on an outdoor terrace beside a calm body of water, with café-style white metal chairs and small round tables.
Several adults sit at the tables with glasses and small items in front of them.
In the background, the water reflects light, and a \textbf{shoreline} or landscaping is visible.
A man in a dark suit, white shirt, and tie sits alone at a round table near the water.
He appears to be a young to middle-aged adult with short dark hair and a clean-shaven face.
He holds a \textbf{cigarette} in one hand, with an ashtray and a small glass on the table.
His posture is relaxed, leaning back in the chair, and he looks off to the side as if listening to someone nearby.
The view settles more closely on this suited man, identified by the audio context as Dave.
He keeps the \textbf{cigarette} near his mouth, glancing around thoughtfully.
He shifts his attention from the table to the side, then toward the viewer, with a faint, knowing expression.
The patio remains softly lit behind him, with the water filling most of the background and a flower arrangement partly visible beside him.
As Dave seems to begin considering his answer, his image fades into the face of a young woman.
She has short, curled hair, bare shoulders, and a light halter-style dress or top.
She wears dangling earrings and smiles broadly, turning her face slightly as if enjoying attention.
Behind her are bright, soft shapes that look like fountains or decorative lights, giving the scene a glamorous evening atmosphere.
Her image dissolves into another young woman outdoors.
This woman has long light-colored hair and is wrapped in a coat or shawl around her shoulders.
She stands on a walkway near a low wall, with leafy branches hanging overhead and trees or shrubs in the background.
She looks back over her shoulder toward the viewer with a gentle smile, then turns inward shyly, lowering her face and drawing the coat closer around her.
The setting changes to night, where a blonde young woman sits in a light-colored convertible.
She is positioned behind the open side of the car and lifts one arm high to wave.
City lights and a large column-like structure blur in the background.
She smiles while waving, then the car moves away, carrying her out of view.
Another young woman appears leaning against a large tree trunk.
She has long hair with bangs and wears a horizontally striped top.
A park-style lamp is visible behind her.
She rests close to the tree, looking out with a playful, slightly coy expression.
She lifts her hand to brush her hair back from her face, then keeps her hand near her temple while gazing forward.
The scene then shifts to an equestrian setting.
A young woman in riding clothes sits on a light-colored horse in front of a white fence and stable buildings with dark roofs.
She wears a dark riding helmet, a \textbf{tailored} jacket, and light riding pants.
Holding the reins, she smiles as the horse moves slowly past the fence, her posture upright and composed.
Next, a short-haired young woman is seen in profile in what looks like a social or restaurant setting.
She has a smooth bob haircut and wears a sleeveless top.
Other people appear blurred behind her.
She leans forward toward someone just outside the picture, her lips moving as if speaking, her expression soft and engaged.
Dave reappears at the café table, now facing forward more directly.
He still wears his dark suit and holds the \textbf{cigarette}.
His expression is amused and confident, as though he has just finished naming the women he was thinking of.
He gestures lightly with his hand, palm upward, then points or extends his fingers toward the viewer while leaning forward.
Dave ’s image fades into a large product bottle that fills the center of the screen.
The bottle is light-colored, with a rounded rectangular body and a narrowing neck.
On the front is a detailed drawing of a sailing ship.
Beneath it, the label reads “ Old Spice ” in script, with “ After Shave Lotion ” printed below.
The background becomes dark and plain, isolating the product.
The bottle remains centered as more of its upper neck and small stopper-like cap become visible, ending with the Old Spice aftershave bottle presented clearly against the dark background.

% matched lemmas: cigarette, shoreline, tailored
\end{textsample}
