\begin{textsample}{NEG Dim 1 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_10.txt}  \label{ex:f1_neg_048}
A sunny outdoor dog show is taking place on a grassy field bordered by white rail fencing.
Hay bales and white posts linked by blue rope mark off areas, and round blue number signs identify spaces for competitors.
An adult woman with wavy brown hair walks briskly through the show ring with a large black dog on a leash.
She wears a bright pink sweater over a white collared shirt with a dark bow at the neck, a dark skirt, and a yellow armband marked “ 34. ” She smiles as she moves through the busy scene.
Around her, other handlers stand with dogs of different sizes, including a child with a light-coloured dog and adults holding or \textbf{grooming} their animals.
People occasionally pass close in the foreground, briefly obscuring her as she continues forward.
The woman approaches a middle-aged man in a light grey suit and tie near a table covered with a blue cloth.
Behind him, a large sign reads in part “ Annual Dog Show. ” He is shown in profile and then closer, looking serious and speaking or reacting while the dog show continues behind him.
The woman turns back toward the activity, smiling broadly.
She faces forward, then lifts a black rectangular box of Irish Spring soap beside her face.
The package is dark with green-and-white branding and a shamrock emblem, and the words “ Irish Spring ” are visible on the front.
She holds it steady at shoulder height as dogs and handlers move in soft focus behind her.
A young red-haired boy with pale skin and curly hair appears nearby, wearing a light yellow sweater over a plaid-collared shirt.
He looks up toward the woman with an attentive, slightly surprised expression.
The woman steps beside him, smiling, and puts an arm around him.
Together they face forward, cheek to cheek, both smiling.
She continues holding the Irish Spring box up near them so the label is visible.
The product demonstration moves to a close view of a bar of soap held in someone ’s hands against the background of a checked jacket.
The soap is a pale greenish-white bar with darker green stripes running through it.
A small knife blade points to and traces along the stripe area, emphasizing the layered interior.
Large white on-screen text appears over the soap reading “ 2 \textbf{Deodorants}. ” The same “ 2 \textbf{Deodorants} ” text remains as a man showers in a lush, dark green outdoor-looking setting.
He is bare-chested, covered with white \textbf{lather}, and water pours diagonally over him from above.
He smiles and washes his chest and shoulders, then raises a white bar of soap in his hand near the falling water, showing it clearly while remaining soapy and wet.
The washing imagery continues with the woman under a stream of water in a similar leafy, natural-looking shower setting.
Her hair is pinned up loosely, and her shoulders and arms are covered with \textbf{lather}.
She rubs the soap across her shoulder and upper arm, turns toward the viewer, smiles, and continues washing as water cascades beside her.
She appears fresh and relaxed, then tilts her face upward into the water.
Back at the dog show, the woman is now dressed differently, in a soft taupe or beige robe-like top with a wide white ruffled collar.
Her hair is styled in loose waves.
She holds the Irish Spring box beside her face again, with the logo facing forward.
People and dogs move in the blurred background.
A man in a blue turtleneck sweater steps in beside her, holding a black-and-white puppy.
She turns toward him and smiles ; he smiles back, and they pose closely together.
The puppy rests in his arms, its white face and black ears visible as it looks downward and then forward.
The woman keeps the soap package raised near her shoulder while the two adults smile warmly at each other and toward the viewer.
The final image places their dog-show portrait inside a smaller rectangular picture on a solid green background.
Beneath and to the right is a black Irish Spring product logo panel with a shamrock and the words “ Legendary Green Irish Spring ” and “ The Double \textbf{Deodorant} Soap. ” Large white text appears on the left, building to read “ Fresh and Clean as a Whistle, ” while the couple and puppy remain pictured above the brand panel.

% matched lemmas: deodorant, groom, lather
\end{textsample}
