\begin{textsample}{NEG Dim 1 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_88.txt}  \label{ex:f1_neg_058}
A balding, middle-aged man in a light blue dress shirt and patterned tie hurries up to an outdoor ATM set into a brick wall.
Above the machine are the Mastercard overlapping red-and-yellow circles and a blue “ CIRRUS ” sign.
He turns toward a younger man with thick curly hair, wearing a dark leather jacket over a green shirt.
The younger man stands beside the ATM holding a small stack of dollar bills, while the balding man holds up a small greenish card as if asking for help.
Pedestrians pass between them.
The curly-haired man looks down at the card, then out to the side with a doubtful, uncertain expression, still clutching his cash.
Both men end up looking off in the same direction, as if trying to figure out where to go.
On another sidewalk, near an ATM mounted in a wall, two adults lean toward an elderly woman seated low beside a parked car.
One person in a red patterned top points firmly into the distance, while another person in a beige vest leans in close and points as well.
The elderly woman looks up at them as they appear to give complicated directions.
The balding man is then seated in a car with the top down, holding up the same greenish card near his face.
He smiles hopefully toward someone outside the car.
A young woman with short dark hair, a bright pink hair scrunchie, hoop earrings, and a blue jacket faces him while holding a large brown paper grocery bag with a baguette sticking out.
A passerby briefly blocks the view.
The woman smiles at first, then looks more concerned and uncertain, hugging the bag to her chest and gesturing with one hand as if she does not know the answer.
The man studies the card, flips it slightly in his fingers, and looks back up, still waiting for help.
He next sits on the hood of a red car beside a cyclist in a white helmet, purple cycling shirt, black gloves, and cycling gear.
Behind them is a roadside diner with large roof letters spelling part of “ DINER. ” The balding man holds folded papers or maps in his lap, while the cyclist grips the handlebars and points off to the side, apparently adding another set of directions.
The man looks away in the direction indicated.
A wide outdoor view shows a pale green metal truss bridge spanning calm water, with trees behind it.
A small red car drives across the bridge, emphasizing that the search has taken him well away from the city streets.
Back on a sunny sidewalk, the balding man bends forward beside a small elderly woman wearing a straw hat, large eyeglasses, a patterned blouse, and a vest.
She gestures emphatically with one finger raised, then points outward and downward, giving a long, detailed explanation.
The man listens with a serious, slightly weary expression, leaning in close at her height.
She adjusts her glasses, waves her hand, and continues pointing, while pedestrians move in soft focus behind them along a tree-lined street.
The focus shifts to the product in use.
A hand holds a gray Mastercard card close to an ATM card slot.
The card clearly shows the blue “ MasterCard ” name and the red-and-yellow Mastercard circles.
The hand slides the card into the horizontal slot.
The card goes partway in, with the logo still visible, then disappears deeper into the machine.
Another ATM is shown with the Mastercard and CIRRUS logos below its screen and keypad.
A hand retrieves a stack of cash from the cash dispenser, then moves to press buttons on the keypad.
At the ATM, the balding man now stands beside a young woman with shoulder-length brown hair wearing a peach-colored blouse.
They are outside a light-colored building with a small domed tower visible against a bright blue sky.
The man holds up the greenish card near his chest while the woman holds cash.
They look at each other, then she looks upward and points confidently into the distance, as if indicating a much simpler solution or location.
The man watches her, appearing relieved but still slightly bemused.
The image blends back to the elderly woman and the balding man on the sidewalk.
White text appears along the lower part of the screen reading “ MASTER THE MOMENT, ” and the Mastercard overlapping red-and-yellow circles logo appears at the lower right with the “ MasterCard ” name.
The elderly woman continues talking and gesturing with one raised finger, while the man leans beside her and eventually dips his head downward, as if \textbf{exhausted} by all the complicated directions.

% matched lemmas: exhaust
\end{textsample}
