\begin{textsample}{NEG Dim 1 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_11.txt}  \label{ex:f1_neg_015}
The commercial begins with a black frame.
It then cuts to a softly lit child ’s bedroom.
A dark-haired adult figure is seen from behind near a wall with childlike decorations.
The room has a warm pink/beige color tone.
A young girl with dark hair and bangs is shown lying in bed under white bedding.
An adult woman stands beside the bed holding toys, including a doll and a black-and-white stuffed figure.
The bedroom contains a decorative headboard, framed pictures on the wall, hanging garments, and a bedside lamp.
A close-up shows a blonde adult woman in a patterned top, with dark-framed glasses resting on top of her head.
She smiles while looking downward, apparently toward a child off-screen.
The girl is then shown in close-up in bed holding a doll.
She also holds a small container or jar with a dark cap near her face, though the label is not readable in this frame.
Another shot shows the blonde woman in the patterned top turning toward a child lying in bed in the background.
The child appears propped on a pillow.
The sequence then shows a blonde adult woman in a dark green top sitting close to the young girl in bed.
She smiles warmly and touches or adjusts the girl ’s \textbf{blanket} or clothing near the shoulder/chest area.
The girl looks back at her.
A side-profile close-up of the blonde woman in the patterned top follows ; she faces to the right, looking downward or off-screen.
The woman in the green top is then shown facing the camera in the bedroom, with hanging clothes and a framed picture behind her.
She smiles slightly.
A close-up shows the girl holding her doll while an adult hand touches or applies something to the upper chest/neck area of the girl ’s nightgown.
The product itself is not clearly visible in this frame.
A wider shot shows the woman in the green top seated beside the girl ’s bed.
The woman ’s hand is placed on the girl ’s upper chest area, and both appear calm and affectionate.
The girl remains tucked under white bedding.
The next shot isolates a lit bedside table lamp with a pale lampshade, creating a warm nighttime bedroom atmosphere.
The final frame is a product shot : a jar labeled “ Vicks VapoRub ” sits on a tabletop, with a lamp blurred in the background.
Visible label text includes “ Vicks VapoRub, ” “ Vaporizing Ointment, ” and “ RELIEVES DISTRESS OF COLDS. ” Large white text to the right reads : “ most comforting \textbf{thing} you can do for a cold. ”

% matched lemmas: blanket, thing
\end{textsample}
