\begin{textsample}{NEG Dim 1 – 1960 – Score -4.00 – 1960/tv\_com\_1960\_70.txt}  \label{ex:f1_neg_024}
In black and white, the commercial opens outdoors on a wide grassy shooting range beside open water.
A small range building marked with the number “ 4 ” stands to the left.
An adult woman with short, styled, light-colored hair watches as an adult man, wearing a light shooting jacket with dark shoulder and side patches, raises a long shotgun and aims out across the range.
He fires upward at small dark clay targets crossing the sky, then lowers the gun and looks out toward the field.
The woman stands nearby in a light jacket over a skirt, observing him with an approving smile.
After the shot, he turns toward her, holding the shotgun upright, and they move closer together.
They smile and talk face to face on the grass with the water and distant \textbf{shoreline} behind them.
He gestures with one hand while holding the gun in the other, then they both glance down toward something off-screen.
A wooden bench or table appears with several shotgun shells lying on it, along with a white pack of Chesterfield King \textbf{cigarettes}.
The pack is open at the top, with \textbf{cigarettes} visible inside.
Part of the shotgun rests nearby, its stock leaning against the bench.
A hand reaches in and picks up the \textbf{cigarette} pack.
Back with the couple, the man presents the open Chesterfield King pack to the woman.
In a close view, the pack fills the hand ; the visible label reads “ Chesterfield, ” “ KING, ” and “ \textbf{CIGARETTES}, ” with \textbf{cigarettes} protruding from the top.
Another hand pulls one \textbf{cigarette} out.
The woman, smiling in profile, accepts the \textbf{cigarette}.
She lifts it to her lips while the man brings a lighter toward the tip.
The \textbf{cigarette} is lit, and she holds it between her fingers, her expression pleased and relaxed.
The imagery then focuses closely on smoking.
First, the woman ’s mouth is seen in extreme profile as a soft stream of smoke leaves her lips.
The man ’s face appears next in profile against the distant water ; he looks content, smiles broadly, and raises a \textbf{cigarette} to his mouth.
He holds it between his fingers and takes a puff.
A close-up of the man ’s \textbf{cigarette} at his lips becomes a visual demonstration.
A bright white arrow appears above the \textbf{cigarette}, pointing from the burning end toward his mouth, illustrating the path the smoke travels along the length of the \textbf{cigarette}.
Wisps of smoke curl around the \textbf{cigarette}.
The word “ air-softened ” appears in bold white lowercase letters over the smoky background, hovering above the \textbf{cigarette}.
The \textbf{cigarette} remains horizontal, held between fingers, while smoke drifts around the word.
The on-screen word changes to “ milder, ” still floating above the \textbf{cigarette} and smoke.
The same kind of close-up demonstration is repeated with the woman ’s \textbf{cigarette}.
Her face is shown in side profile, lips at the filter end, with her manicured fingers holding the \textbf{cigarette}.
A bright white arrow travels along the \textbf{cigarette} from the burning end toward her mouth, again emphasizing the length of the smoke path.
Smoke gathers and curls around the \textbf{cigarette}.
The word “ air-softened ” reappears in large white letters behind the \textbf{cigarette}, partly veiled by smoke.
The smoke grows denser, briefly clouding the word and the \textbf{cigarette} before clearing enough to reveal them again.
The word then changes to “ cooler, ” centered above the \textbf{cigarette}, and later to “ smoother, ” again in clean white lowercase letters over the smoky background.
A hand then holds up the Chesterfield King pack with a \textbf{cigarette} resting above it.
The pack front is clearly visible : “ Chesterfield, ” “ KING, ” and “ \textbf{CIGARETTES} ” are printed on the front, with the pack opened at the top and \textbf{cigarettes} sticking out.
The background gradually widens to reveal the shooting range again.
The man is seated or crouched at the right foreground, holding the pack and \textbf{cigarette}, while the woman stands in the distance at the left, aiming or posing with the shotgun near the range area.
The \textbf{shoreline} and scattered rocks lie beyond her.
The scene shifts back to the couple walking together across the grass near the water.
The man carries the shotgun at his side or over his shoulder, still in his shooting jacket.
The woman walks beside him in her light jacket and skirt, holding a \textbf{cigarette}.
They smile and look at each other as they stroll, with a small \textbf{sailboat} and low \textbf{shoreline} visible in the distance.
The image then shrinks into a graphic shape resembling the outline of a \textbf{cigarette} pack on the right side of a dark background.
Large handwritten-style white script appears on the left reading “ They \textbf{Satisfy}. ” The small scene of the couple is replaced by a large illustration of the Chesterfield King \textbf{cigarette} pack on the right, open at the top with \textbf{cigarettes} protruding.
The final image holds on the slogan “ They \textbf{Satisfy} ” beside the pack labeled “ Chesterfield KING \textbf{CIGARETTES}. ”

% matched lemmas: cigarette, sailboat, satisfy, shoreline
\end{textsample}
