\begin{textsample}{NEG Dim 1 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_12.txt}  \label{ex:f1_neg_029}
The commercial begins with a black screen.
A scene then shows a young girl outdoors, riding or sitting on a bicycle on a tree-lined path.
She faces the camera with her hands on the handlebars.
The background is green and sunlit, with added sparkling/star-like visual effects around her.
The next shot switches to a product-style graphic : a tube of Colgate toothpaste appears on a pale background.
The tube is labeled “ Winter Fresh Gel ” and “ Colgate. ” A dark, curved gel-like line trails from the tube, forming part of a large cursive letter.
The commercial cuts to two boys standing outdoors near a house or porch area.
One boy wears a yellow shirt and looks toward the camera with his mouth open ; the other wears a plaid shirt and looks downward.
Sparkling visual effects are again visible around them.
A close-up product demonstration follows.
A tube labeled “ Winter Fresh Gel ” is squeezed over a toothbrush, dispensing a pale gel or paste onto the bristles.
Behind it, a red Colgate box is visible, with text including “ Colgate ” and “ MFP Fluoride. ” The graphic sequence returns : a Colgate Winter Fresh Gel tube is shown on a pale background, leaving a dark gel trail that forms cursive letters, now resembling “ ge. ” The tube is positioned near the top right, and the gel line curves below it.
The next scene shows an adult man leaning over a bathroom sink with two young girls, one on each side.
The girls are brushing their \textbf{teeth} and smiling.
The man looks toward the camera.
Bathroom fixtures, including two faucets and a central drain or knob, are visible.
Sparkling effects overlay the scene.
Small on-screen text appears near the bottom, but it is too small and blurry to read clearly.
The commercial then shows a close-up of two stacked red Colgate product boxes against a dark background.
Large labels on the boxes read “ Great Regular Flavor ” on the upper box and “ Winter Fresh Gel ” on the lower box.
A final product display shows two Colgate boxes stacked against a dark background.
The upper box is labeled “ Great Regular Flavor, ” and the lower box is labeled “ Winter Fresh Gel. ” Large white text underneath reads : “ The cavity-fighting gel with the Winterfresh taste. ” After that product display, the sequence cuts back outdoors to a young child in a yellow jacket or top, standing near a tree in a grassy area.
The child looks toward the camera, with sunlight and sparkling visual effects in the background.

% matched lemmas: tooth
\end{textsample}
