\begin{textsample}{NEG Dim 1 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_41.txt}  \label{ex:f1_neg_043}
The commercial begins in a brightly lit domestic kitchen.
A woman stands at a stove or counter area, leaning forward with one arm extended toward something on the wall or upper counter.
The setting includes patterned curtains, wall decorations, a dining table, chairs, and kitchen cabinets.
The image is low-resolution and color-shifted, with a “ Nostalgic X’er ” watermark visible near the lower right.
The scene then changes to a bathroom or dressing area.
A woman with long dark hair stands near a sink or vanity while a man in a suit stands beside and slightly behind her.
He appears to be holding up or examining a section of her hair while looking at it.
The woman looks downward or toward her hair.
The background includes a window with curtains, bathroom fixtures, and framed wall \textbf{art}.
Next, the commercial cuts to a product-focused composition.
A bottle of Prell shampoo is shown prominently in the foreground, with the label “ Prell ” clearly visible.
Behind and around it are bathroom-related objects, including faucets and grooming items.
The frame has a soft, superimposed or layered look, as if product imagery is being combined with a bathroom scene.
The following shot shows a person leaning over a bathtub or basin, washing or tending to another person ’s hair.
The Prell bottle remains visually emphasized through superimposition or placement in the upper/central area of the image.
Bathroom fixtures and a tub edge are visible.
The action suggests hair washing, though the exact details are partly obscured by the low image quality and layered visual effect.
Later, the scene cuts to a close-up of a smiling couple.
A man and a woman face each other closely, both smiling.
The woman has long hair and appears to be wearing glasses.
The man ’s hand is near her hair or face, suggesting affectionate \textbf{attention} to her hair.
The background includes patterned décor and a circular wall object.
The final frame is a static product end-card.
A large bottle of Prell shampoo is shown on the left against a plain light background.
To the right, handwritten-style text reads : “ Close your eyes.
Touch your hair. ” The Prell label is clearly visible on the bottle.
The watermark remains in the lower right.

% matched lemmas: art, attention
\end{textsample}
