\begin{textsample}{NEG Dim 1 – 2000 – Score 1.00 – 2000/tv\_com\_2000\_92.txt}  \label{ex:f1_neg_084}
The commercial begins with an almost completely dark frame.
A small red square watermark or channel bug is visible in the lower-right corner.
It then cuts to a blue-and-white abstract animation.
A bright white curved shape fills most of the frame against a dark blue background, with a turquoise radial burst or starburst pattern in the center.
The animation moves into large, blurred blue lettering, suggesting a rapid graphic transition.
Next, oversized white numerals with a dark blue outline fill the screen, resolving into “ 20. ” Immediately after, the full promotional graphic appears : the text “ Oral-B Vitality ” is shown above a large “ \$20, ” with an image of an electric toothbrush standing upright on the left.
A small white cord or charger is visible near the toothbrush.
The overall color scheme is blue, white, and light cyan, with a burst graphic behind the price.
The commercial then shifts to a split-screen demonstration-style image.
On the left, a yellow background is labeled “ regular manual, ” with stylized \textbf{teeth} along the bottom.
On the right, a blue background shows the “ Oral-B Vitality ” branding above a toothbrush head positioned against cartoon-like \textbf{teeth}.
A vertical line divides the two sides.
Some very small text appears near the bottom left but is not clearly readable in the frame.
After the product demonstration, the ad cuts to a close-up of a smiling person with light skin and light-colored eyes.
Only part of the face is visible, with one side cropped by the frame.
The person appears to be raising an arm near their hair and is wearing a blue top.
Their \textbf{teeth} are prominently visible in a smile.
The imagery then returns to abstract blue animation : a white leaf- or teardrop-shaped form with a bright radial burst inside appears against a dark blue background.
The final frame shows the “ Oral-B Vitality ” logo centered on a light blue background, with a bright starburst or splash effect behind the word “ Vitality. ” Faint silhouettes or outlines of toothbrush handles appear in the background.
The small red watermark remains in the lower-right corner.

% matched lemmas: tooth
\end{textsample}
