\begin{textsample}{NEG Dim 1 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_24.txt}  \label{ex:f1_neg_060}
The commercial opens with an extreme close-up of a fly- or mosquito-like insect.
Its compound eyes, antennae, legs, and blurred wings fill the frame under purple-blue lighting.
It cuts to a living room : a teenage boy sits centered on a couch, facing a television in the foreground.
He appears focused upward toward the screen.
Around him are pillows, a plaid \textbf{blanket}, papers, and snack packaging.
The room is dimly lit with a cool, \textbf{bluish} cast.
The ad then returns to macro insect imagery : the insect ’s face is shown head-on, with its long proboscis extending toward the camera.
A later side view shows the insect standing on a textured, hairy surface that appears to be skin, with its proboscis positioned against it.
The sequence briefly switches to video-game footage.
One shot shows a fighting-game-style scene with large statue-like figures in the background and an on-screen rating box marked “ MA-13. ” Another set of shots shows a basketball video game : a player jumps near the hoop, defenders stand below, and a crowd fills the background.
A rating box marked “ GA ” appears, and small text at the bottom indicates that Sega Genesis game screens are being shown.
The insect close-ups continue.
One shot shows the insect from the side with a swollen reddish-orange abdomen while it remains on the hairy skin surface, lit dramatically from behind in purple light.
The boy is then shown in a tight close-up from above.
A small insect is visibly on the center of his forehead while his eyes roll upward toward it.
Immediately after, a white cylindrical object with a crossword- or grid-like design and red handwritten letters moves down in front of his face, partly obscuring him.
The commercial cuts to a white background where the word “ SEGA ” appears in \textbf{thick}, dark red, liquid-like lettering with splatters around it.
The letters fill the frame and then settle into a clearer full wordmark.
The final sampled frame returns to the insect on the hairy skin surface.
It appears sprawled or distorted against the surface, still lit with the same purple-toned, high-contrast macro style.

% matched lemmas: blanket, bluish, thick
\end{textsample}
