\begin{textsample}{NEG Dim 1 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_6.txt}  \label{ex:f1_neg_049}
A silver-haired older woman identified by on-screen text as “ Martha Raye denture wearer ” walks onto a studio set.
She has a bright, broad smile and wears a loose lavender tunic over white pants, with a white necklace or trim at the neckline.
Around her are visible television-production objects : a large blue studio camera on a pedestal stands to her right, overhead lights hang above, and a wooden director ’s chair to her left has her name printed on the back.
She moves toward the viewer, smiling and gesturing with one hand as if addressing the audience directly.
She pauses near the large camera, still smiling, then gestures toward it with a playful, confident expression.
The setting then shifts to a dressing-room \textbf{vanity} area.
She stands beside a wide mirror bordered with round glowing bulbs.
Her reflection appears in the mirror on the left, while the real figure stands on the right.
The counter is cluttered with dressing-room items, including boxes, small containers, and a vase of red flowers.
She turns toward the viewer, smiles, and picks up a small teal-green box from the \textbf{vanity}.
Holding the box beside her face, she presents it clearly.
A close view shows the package : a teal box with large yellow lettering reading “ Polident, ” smaller text reading “ Extra Strength ” and “ Denture Cleanser, ” and a white circular tablet graphic surrounded by bubbles.
Her fingers grip the sides of the box, and the lavender of her outfit is blurred behind it.
She then appears again in the dressing room, smiling while holding the Polident box up near her cheek.
The commercial moves into a product demonstration.
A hand holds a set of dentures against a dark background.
The teeth and gum line are visibly marked with heavy \textbf{brownish} stains, especially along and between the teeth.
The stained dentures are lowered into a clear cylindrical glass.
White lettering on the glass reads “ Extra Strength Polident. ” The dentures sit at the bottom in liquid.
A hand drops a tablet into the glass, and white-blue foam begins to bloom and swirl around the dentures.
The liquid becomes cloudy and effervescent, filling much of the glass with cleaning action.
White on-screen text appears near the bottom : “ 15 minutes later. ” A hand reaches into the glass and lifts out the dentures, now appearing bright white.
In a close view, two hands hold the cleaned denture sections apart, showing smooth white surfaces and clean spaces between the teeth, with the earlier brown staining no longer visible.
The “ 15 minutes later ” text remains at the bottom during this reveal.
The scene returns to the dressing room.
Martha Raye stands in front of the lit \textbf{vanity} mirror, smiling broadly in her lavender outfit, with the flowers and dressing-table objects still behind her.
She speaks toward the viewer, then raises the teal Polident box beside her face again.
White on-screen text appears across the lower part of the image : “ Polident green gets tough stains clean. ” She holds the product steady near her cheek, alternating between a knowing look and a big smile, keeping the package label visible as the commercial ends.

% matched lemmas: brownish, vanity
\end{textsample}
