\begin{textsample}{NEG Dim 1 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_40.txt}  \label{ex:f1_neg_065}
A hand moves through a colourful produce display, reaching among glossy orange bell peppers beside a dense pile of red peppers.
One orange pepper is lifted away and dropped into a metal wire shopping cart.
The scene shifts to trays of green okra, where the same hand presses down and gathers a handful from the pile.
Dark shellfish, likely mussels or clams, sit on crushed ice, their wet shells \textbf{gleaming} in the light.
A red Visa Debit card is held between fingers with pale manicured nails.
The card fills the view against a dark background with blurred vegetables behind it.
Large white text reads “ VISA DEBIT, ” with a Visa logo in the lower right corner of the card and small card numbers across the front.
More produce appears laid out on a black checkout belt : red, orange, yellow, and green peppers, dark green chiles, small orange peppers, and okra arranged in neat groups.
The red Visa Debit card appears again over the produce, then moves out of view, visually linking the groceries with payment by card.
At home, a brown paper grocery bag is set down on a dark counter.
Nearby are keys, folded papers, and a bowl holding dark round produce, possibly avocados.
Cooking preparation begins with a close view of a fresh okra slice, its \textbf{star-shaped} cross-section showing pale seeds inside.
A knife chops okra on a wooden cutting board, leaving small green pieces to one side.
In a sink, hands rinse shellfish in a metal colander under a steady stream of water, shaking and turning the colander so the shells tumble and wash.
Warm, low-lit cooking details follow.
A red pepper or similar ingredient is pressed into a simmering, glossy mixture.
A hand rubs a block of pale cheese across a metal grater, and thin strands fall through the holes inside the grater.
The food preparation feels quick and coordinated, with ingredients moving from market to counter to cooking.
The finished meal is presented in a large, shallow, brown ceramic serving dish filled with seafood : dark mussel shells, pale clam shells, pieces of red and green vegetables, and herbs.
Behind it, several adults sit around a warmly lit table, their faces softly out of focus.
The setting appears to be an evening dinner gathering, with candlelight and small glowing lights in the background.
A smiling man ’s face appears briefly, then another adult man with short dark hair and trimmed facial hair smiles with his eyes partly closed, reacting as if enjoying the moment.
A woman in a patterned sleeveless dress carries a rectangular platter to the table.
Another man in a light blue button-down shirt sits nearby as a large cooked fish or long grilled dish is set in front of him ; hands reach toward it as people serve themselves.
Small tea lights in round holders glow on the table.
A woman ’s hand holds a small dark cup or glass while she speaks or laughs, her face visible in profile, smiling.
Another man in a light blue shirt smiles across the table, with a red drink in a glass near him.
A woman with dark hair and a sleeveless patterned top laughs warmly beside another guest in the foreground.
The view turns to decorative lights at night.
Golden points of light form the word “ go. ” against a dark background, with the two letters and period made from soft glowing circles.
The scene widens to an outdoor covered patio or terrace where the dinner party continues at a table under a roof, surrounded by candles and plants.
A large red Visa Debit card graphic appears prominently to the right of the diners, with “ VISA DEBIT ” and the Visa logo visible.
At the bottom of the image, small white text reads “ visa.com/go. ” The final image keeps the softly lit patio in the background while large white text appears across the foreground : “ more people go with VISA, ” with “ VISA ” in bold, oversized letters and the Visa colour accent beside it.

% matched lemmas: gleam, star-shaped
\end{textsample}
