\begin{textsample}{NEG Dim 3 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_86.txt}  \label{ex:f3_neg_082}
The commercial is in black and white.
It opens outdoors on a sunny lawn, where several young children sit around a small party table covered with a checkered tablecloth.
They wear light-colored party clothes and paper hats, and the table is crowded with plates, cups, bottles, napkins, and party food.
The children face one another around the table, leaning in and reaching for food, creating a lively, busy birthday-party scene.
The view moves in close to the tabletop.
A large platter piled with hot dogs sits near the top of the table, with cups, plates, a jar or pitcher, and scattered utensils around it.
Children ’s arms reach in from different sides to take food.
One cup tips over onto the checkered cloth, leaving a dark spill.
The table looks increasingly messy, with plates partly filled, napkins and crumbs spread around, and the overturned cup lying on its side.
A close view of a small boy follows.
He sits at the table on the lawn wearing a light shirt and a soft paper party cap with a streamer sticking out behind him.
He holds food near his mouth, bites into it, and then looks down at his shirt.
He lifts one arm across his chest and rubs at the front of his light shirt, as if noticing a stain or smear from the food.
His posture is hunched slightly forward over the table, focused on the mess on his clothing.
The scene then shifts to children playing on the grass.
One child lies on the ground while two boys in light shirts and party hats drag the child by the arms across the lawn.
Another child stands nearby, and two girls in light, frilly party dresses run in from the side.
The girls ’ full skirts bounce as they move, and the group dashes away across the grass.
The children ’s light clothing contrasts with the darker lawn, emphasizing how easily the outdoor play could dirty their clothes.
The setting changes to a \textbf{bright} domestic laundry or kitchen area.
A smiling middle-aged woman with short, styled dark hair stands beside a top-loading washing machine.
She wears a sleeveless light-colored house dress or blouse-and-skirt outfit with a fitted waist.
Around her are a laundry counter, a glass measuring cup, folded fabrics, and shelves or windows in the background with leafy plants.
She holds a bundle of children ’s soiled light-colored clothing, then places the garments down into the open washing machine.
She looks toward the viewer as she works, presenting the laundry as something she is about to handle.
She turns to her left and reaches for a large box of Oxydol detergent.
She brings it forward and holds it against her torso so the front label faces outward.
The package has a bold circular design with the large word “ Oxydol ” across the front.
She smiles while displaying it, then sets the box near the washer and reaches for a small cup.
Holding the Oxydol box in one hand and the cup in the other, she pours detergent from the box into the cup.
The white powder streams down visibly, filling the cup before she tips it toward the washing machine.
A new display appears with freshly washed clothing hanging on a line in front of a paneled wall.
The garments are all light and crisp-looking : a little dress with a belt on the left, a short-sleeved shirt in the center, and long \textbf{pants} or overalls on the right.
A folded cloth lies across a counter in the foreground.
The woman enters beside the hanging clothes with the Oxydol box placed prominently at the lower left.
She gestures toward the clean garments and touches the little dress and shirt as if showing their brightness.
Script text appears along the bottom reading “ detergent-clean. ” The woman lifts the short-sleeved shirt from the line and holds it out in both hands, smiling.
The shirt looks very pale and clean against the darker paneled background.
The on-screen script changes to “ bleach-white, ” positioned across the lower part of the picture.
She continues holding the shirt open, then lowers it onto the counter in front of her, smoothing and folding the fabric while the Oxydol box remains upright at her left.
She gestures toward the package and then the picture cuts closer to the box.
The label fills much of the view.
Across the top of the package, readable text says “ BLEACHES AS IT WASHES. ” The large brand name “ Oxydol ” dominates the center, and smaller text near the bottom reads “ COLOR-SAFE OXYGEN BLEACH. ” The box sits among the clean laundry, linking the product directly with the white garments around it.
Back at the laundry display, the woman stands between the Oxydol box and the hanging clothes.
She gestures to the box with one hand and to the clean garments with the other, then reaches to the counter and picks up the short-sleeved shirt again.
Holding it by the shoulders, she presents it squarely toward the viewer.
The shirt has a small collar and short sleeves, and it appears smooth and \textbf{bright}.
Script text appears along the bottom reading “ removes stains. ” She smiles broadly while keeping the shirt lifted.
She then lowers the shirt and picks up another light garment from the counter, shaking it open and smoothing it between her hands.
She handles the fabric carefully, showing its clean surface and soft folds.
After laying it down, she turns back toward the hanging little dress and touches it, drawing attention to its neat shape and \textbf{bright} appearance.
The Oxydol box stays in the foreground on the left, its brand name still clearly visible, while the long white garment hangs on the right.
Near the end, the woman faces forward again with the clean laundry arranged around her : the boxed Oxydol in front at her left, the little dress hanging behind it, a long white garment hanging to her right, and folded fabrics on the counter.
She rests a hand on or near the product box and continues speaking to the viewer, smiling in a confident, pleasant manner.
The final visual impression is of an orderly laundry area filled with clean, white clothes, with the Oxydol package displayed as the central product.

% matched lemmas: bright, pant
\end{textsample}
