\begin{textsample}{NEG Dim 3 – 2020 – Score -4.00 – 2020/tv\_com\_2020\_57.txt}  \label{ex:f3_neg_025}
A warm yellow screen opens with the magenta “ Aspercreme ” logo centered over a soft, hazy background.
Behind the logo, faint silhouettes suggest outdoor activity, but the brand name dominates the view.
The logo grows large and fills the screen, then the yellow overlay gives way to a \textbf{bright}, leafy outdoor setting.
In a sunlit wooded area, an adult man with medium-dark skin, short dark hair, and a trimmed goatee bends forward smiling as he plays with a brown-and-white dog wearing a dark collar.
He is dressed in a gray long-sleeve \textbf{athletic} quarter-zip top and dark \textbf{pants}.
The dog stands close to him in the foreground, and he reaches down with both hands, petting and engaging with it.
The man ’s expression is cheerful and affectionate as he leans over the dog.
After playing, the man stands upright among the trees and places one hand over his opposite shoulder.
His eyes close briefly and his smile tightens, suggesting shoulder discomfort after the activity.
The green, softly lit outdoor background remains behind him.
The view shifts to a close-up of bare shoulder and upper back skin.
A hand holds a small yellow Aspercreme bottle with teal-green bands and a white roll-on applicator, pressing it against the shoulder area.
The applicator is rolled along the skin as the product is applied.
A magenta “ Aspercreme ” wordmark appears over the shoulder area as a graphic overlay, with tiny white text near the bottom reading “ Use as directed. ” A small Aspercreme logo also appears in the lower right corner.
The imagery then changes to a stylized red-and-orange interior view resembling layered muscle fibers or flowing tissue.
The Aspercreme wordmark sits on the left while \textbf{bright} white text builds on the right.
First, “ WORKS ” appears with a small clock-like icon and a yellow motion streak, then it becomes “ WORKS FAST. ” A second line appears beneath it : “ LASTS, ” also paired with a small circular check-style icon.
The red muscle-like background gradually warms toward \textbf{orange} and yellow while the small “ Use as directed ” text remains at the bottom.
The commercial ends on a product display against the same \textbf{golden} yellow background.
Three yellow Aspercreme Lidocaine packages stand side by side : a low rectangular box on the left, a taller patch package in the center with an image of a person ’s shoulder or back, and a taller package on the right showing a roll-on style applicator.
Large text beneath the products reads “ Aspercreme WORKS, ” with “ Aspercreme ” in magenta and “ WORKS ” in white.
Small “ Use as directed ” text remains near the bottom.

% matched lemmas: athletic, bright, golden, orange, pant
\end{textsample}
