\begin{textsample}{NEG Dim 3 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_90.txt}  \label{ex:f3_neg_053}
The commercial begins with a nearly black frame ; no discernible objects or setting are visible.
The next visible scene shows a bright domestic window from inside a \textbf{house}.
Light-colored curtains frame the window, and foliage hangs down near the top.
Through the glass, an outdoor residential view is visible, including trees and a \textbf{house} across the way.
The scene suggests a clean, sunlit home interior.
The commercial then cuts to a close-up of a hand wiping a smooth, light-colored countertop or tabletop with a white cloth.
The person wears a long-sleeved brown or rust-colored \textbf{knit} top.
The surface appears glossy, and the action is focused on cleaning or polishing.
A wider kitchen scene follows.
Two women stand at a kitchen counter.
One woman, wearing a patterned blouse and red trousers, stands on the left, leaning slightly toward the counter.
The other woman, wearing the brown \textbf{knit} top, stands on the right and continues wiping the countertop with a white cloth.
She holds a small bottle or container in her other hand.
Kitchen cabinets and appliances are visible in the background.
A saucepan sits on the counter, and other household items are nearby.
The next shot shows the woman in the patterned blouse standing beside a refrigerator or tall kitchen appliance.
She holds a small bottle or container in one hand and wipes the vertical surface with a cloth in the other hand.
The kitchen cabinetry remains visible behind her.
The emphasis is again on applying or wiping a cleaning product on a household surface.
The final shot is a product display on a kitchen counter.
Two containers stand in the foreground : one appears to be a bottle and the other a taller carton or canister.
Both are labeled “ Jubilee Kitchen, ” with “ Johnson Wax ” visible on the taller package.
The taller package also includes the words “ cleans, ” “ shines, ” and “ protects. ” In the background, slightly out of focus, a woman continues working in the kitchen near the refrigerator.
The final composition foregrounds the product while keeping the domestic cleaning context visible behind it.

% matched lemmas: house, knit
\end{textsample}
