\begin{textsample}{NEG Dim 3 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_87.txt}  \label{ex:f3_neg_079}
A hand-drawn attic appears in cool blue tones, with an arched window centered at the back, bare wooden floorboards, heavy cobwebs in the corners, a large old trunk on the right, and stored household objects on the left.
In a pool of light on the floor, a tiny group of cartoon mosquitoes gathers around a small upright sheet of paper.
The view moves closer to the insects.
A green, long-nosed mosquito with whisker-like hairs, a black cape, a striped shirt, and red shorts stands like an instructor beside a tall paper diagram of a simple human figure.
Facing him are several smaller mosquito recruits ; one hovers with white wings while others stand in a row.
The caped mosquito points with a stick at the drawn human body, indicating target areas on the diagram.
The recruits watch attentively, their pointed noses aimed toward the chart.
After the lesson, the paper chart rolls upward out of sight, leaving the instructor facing the group.
A square hatch opens in the floor, releasing a \textbf{bright} yellow beam of light from below.
The instructor pulls the hatch up and gestures dramatically toward the opening, as if sending one of the recruits on a mission.
He leans over the hatch, then climbs partly into the lighted opening.
A sudden change shows an animated white aerosol can with a blue cap and human-like arms.
The can ’s label reads “ Raid Flying Insect KILLER ” on a black shield.
The can has an angry face near the top and appears to be confronting the insects.
Its nozzle releases a strong white spray cloud.
The spray shoots through a ceiling opening and into the attic hatch area, where the caped mosquito is still beside the beam of light.
A white cloud fills the opening.
One winged mosquito emerges near the instructor, then hovers unsteadily in the blue room.
Beneath it, a small puff of white vapor curls upward and transforms into a fluffy wreath shape with a bow.
The instructor, now smiling, admires the wreath, reaches toward it, and then pulls it around himself like a decorative garland.
The wreath surrounds his head and body in soft white curls, almost like a large perfumed collar.
A small spray or atomizer-like object with a sparkling, flower-shaped tip appears at the side of the wreath.
The caped mosquito sniffs and smiles broadly, seeming pleased by the scent.
The white wreath swells until it nearly engulfs him, leaving only parts of his face and cape visible.
Then an \textbf{orange} starburst fills the center of the white cloud, with tiny insect shapes silhouetted inside it, and the image washes into a \textbf{bright} pale transition.
The commercial shifts from cartoon to live action inside a warmly lit home.
A hand and forearm in a beige sleeve holds a can of Raid Flying Insect Killer at the right side of the picture.
The can is white with a blue cap and the same black shield label with large yellow “ Raid ” lettering.
The hand presses the top, sending a broad white mist leftward across the room.
In the softly blurred background are domestic furnishings : a table with flowers, chairs, a lamp with a stained-glass-like shade, and darker furniture or a fireplace area.
As the spray continues, bold white on-screen text appears near the bottom : “ PATENTED CLEAN-SMELLING FORMULA. ” The mist spreads in a thick cone from the nozzle across the room while the product remains clearly visible in the hand.
Finally, the can is brought forward and set upright on a reflective tabletop.
In close view, the label reads “ Raid Flying Insect KILLER, ” with the blue cap on top and smaller product details below.
The warm household background stays softly out of focus behind the can, while faint Johnson Wax branding appears near the lower right.

% matched lemmas: bright, orange
\end{textsample}
