\begin{textsample}{NEG Dim 3 – 2000 – Score 1.00 – 2000/tv\_com\_2000\_1.txt}  \label{ex:f3_neg_077}
The commercial begins on an almost completely dark/black frame with only a small colorful on-screen logo or watermark visible in the upper-left corner.
It then cuts to an outdoor backyard/patio setting in bright daylight.
A bald, baby-faced person is shown in close-up, seated in a chair and wearing a pale green/gray oversized shirt.
They hold a small green object or container up to their mouth.
Behind them are a wooden fence, rooftops, trees, and a blue sky.
The view widens to show two bald, baby-faced people seated side by side in outdoor chairs.
The person on the left wears a dark top and holds a small pink object or container ; one hand is raised toward the other person.
The person on the right wears the pale green/gray shirt and holds a green object or container.
Both are positioned in front of the same fence and suburban backyard background.
The commercial cuts back to a closer shot of the person on the right.
They face forward with a neutral or serious expression, still seated outdoors, with the fence and sky behind them.
A wider shot follows again with both seated figures.
The left figure turns toward the right figure, while the right figure faces forward and continues holding the green item.
The patio chairs and backyard environment remain visible.
The setting then changes to a product display on a light blue gradient background.
Four small bottle-shaped candy containers are lined up.
Their labels are partly blurred but appear to include the words “ Candy Juice ” and “ Bottle Pop. ” The bottles have different colors, including pink/purple, yellow, blue, and green.
The final frame shows a clearer product packshot : four colorful bottle-shaped containers with cap-like tops in pink, yellow-green, blue, and green.
Large curved text above them reads “ Candy Juice. ” The product labels on the bottles are visible but somewhat soft/blurred.
The overall image has black side borders and a small logo/watermark remains in the upper-left corner.

% matched lemmas: 
\end{textsample}
