\begin{textsample}{NEG Dim 3 – 1970 – Score -3.00 – 1970/tv\_com\_1970\_52.txt}  \label{ex:f3_neg_061}
A brief opening image shows a steep city street sloping down toward water, with a cable car or bus on the left and large white lettering across the center reading “ HERSHEY ’S, ” with smaller text below.
The commercial then moves into a brightly lit carnival or fairground midway.
The space is crowded and colorful, filled with glowing booth lights, pastel balloons, and big clouds of pink and white cotton candy.
A young blonde woman with shoulder-length, full 1970s-style hair walks beside a young man.
She wears a vivid red-pink zip-front top, matching high-waisted \textbf{pants}, and a dark choker at her neck.
He wears a shiny blue satin jacket with white sleeve stripes over a red shirt and dark \textbf{pants}.
They move down the aisle between food and game booths while other fairgoers stand around eating cotton candy and talking.
As they walk, the woman gestures with one hand as if making a point, her expression mildly doubtful or unimpressed.
The man looks over at her, listening, then glances around the busy midway.
Behind them, people hold large fluffy cotton candy sticks, and a booth sign with pink neon-like writing partly reads “ Sugar … ” in the background.
The couple slows near the booth.
The woman looks off to the side, then toward the man, still seeming skeptical.
A hand from off to the right brings in a dark glass soda bottle with a pale label ; from the audio context and the visible Dr Pepper-style bottle design, this is Sugar Free Dr Pepper.
The woman turns toward it with a guarded expression, then accepts or is offered the bottle.
She raises the bottle to her lips and takes a drink.
Her face changes as she tastes it : first concentrated, then surprised.
She lowers the bottle and looks straight ahead with widened eyes, as if startled by the flavor.
Her mouth opens in an exaggerated “ wow ” expression, and she leans forward slightly with delighted surprise.
The man reappears close beside her, and the two are framed among the crowd, cotton candy, and balloons.
Their excitement grows ; they look animated, and the woman lifts her arms as if the taste has energized her.
The couple begins dancing in the carnival aisle.
The woman bounces and swings her arms, smiling broadly, while the man joins in beside her, grinning and moving his arms in rhythmic gestures.
Other fairgoers behind them watch and smile, some still holding cotton candy.
The \textbf{bright} midway remains packed with pink, \textbf{orange}, blue, and white balloons overhead.
The pair dance through the crowd, moving from the booth area toward a carousel.
White and gray carousel horses with red saddle blankets appear on either side of them.
The woman now holds the soda bottle in one hand as she dances, stepping between the horses ; the man follows closely behind, still moving with her.
They continue dancing around the carousel horses.
The woman leads with playful, confident steps, sometimes turning her head toward the man and sometimes facing forward.
He stays just behind her or at her side, smiling and copying her movements.
The fairground lights glow in rows above them, and the setting looks like a staged carnival, full of saturated color and lively background action.
The woman passes a white carousel horse on her left and a gray horse on her right, then moves out into a wider area.
She keeps the bottle visible in her hand as she dances, making the product part of her movement rather than simply holding it still.
The scene opens into an area near a booth marked with a large sign reading “ SIDE SHOW. ” The sign sits above an entrance with glass or reflective panels, and a balloon vendor or attendant stands nearby holding a bunch of pastel balloons.
The blonde woman and the man face each other and dance in front of the side show entrance, stepping back and forth with bent knees and swinging arms.
She turns and moves toward a low platform or bench to the left of the entrance, climbing or stepping up with one leg in a theatrical pose.
The man stands just behind her, watching and staying in rhythm.
A large poster with figures is mounted on the left side of the side show area.
The woman dances across the platform area with energetic, showy movements, stretching her arms outward and lifting her knees.
The man joins her, standing behind or beside her as they perform together.
To the right, the balloon vendor and other spectators remain near the side show entrance, watching.
The carnival background is packed with warm bulbs, signs, and painted panels.
On the far left, a large illuminated product display begins to come into view : a dark sign bordered by lights, with a glowing outline of a Dr Pepper bottle and big white lettering.
The couple moves in front of the large sign.
The sign ’s main visible message reads, “ It tastes fattening, ” and lower lines complete the slogan as “ but it ’s not, ” matching the audio context.
A stylized bottle graphic, outlined in blue and green light, is angled across the black background, with a Dr Pepper-style circular logo on it.
The woman and man dance beneath and beside this sign, using broad arm sweeps and side steps.
The woman, still in her red-pink outfit, stands slightly in front ; the man in the shiny blue jacket moves just behind her.
The product display dominates the final view, visually connecting the dark soda bottle and the slogan : Sugar Free Dr Pepper is presented as tasting rich or indulgent while being sugar-free and low-calorie.

% matched lemmas: bright, orange, pant
\end{textsample}
