\begin{textsample}{NEG Dim 3 – 2020 – Score -4.00 – 2020/tv\_com\_2020\_45.txt}  \label{ex:f3_neg_022}
Outside a modern glass-fronted building, a person rides up on a white sport motorcycle.
They wear a white full-face helmet, a black leather jacket, \textbf{bright} \textbf{mint-green} \textbf{pants}, and black boots.
A small black TRESemmé logo appears near the bottom of the picture.
The rider stops, leans forward over the bike, then lifts off the helmet.
As the helmet comes away, shoulder-length blonde hair swings free and whips across the person ’s face in the sunlight.
Large white on-screen text reads “ 0 \% PARABENS. ” The blonde rider is then seen indoors in a sleek office meeting room.
Now dressed in a \textbf{mint-green} suit over a black top, they stand at the head of a conference table with both hands planted firmly on the tabletop, facing forward with a steady, confident expression.
Other people are seated at the table edges, partly visible, watching.
The same white text, “ 0 \% PARABENS, ” remains, and a second line appears beneath it : “ 100 \% FIERCE. ” The scene changes to a \textbf{bright} white dance studio with tall windows, glossy floors, wall-mounted barres, and sunlight stretching in long shapes across the floor.
A dancer in pale clothing moves through the open space.
White text reads “ 0 \% SULFATES. ” In a closer view, the dancer, a young adult with dark hair pulled back, raises both hands near her face and moves expressively in a soft cream-colored top.
The text expands to “ 0 \% SULFATES ” and “ 100 \% PASSIONATE. ” Next, under deep purple and blue stage lighting, a performer with voluminous dark curly hair moves dramatically in silhouette.
One arm lifts overhead as their hair and body arc through the light.
The white text now reads “ 0 \% DYES ” and “ 100 \% BOSS. ” A close view shows a black bag sitting open, with a TRESemmé Pro Pure can inside.
The can is labeled “ DRY SHAMPOO, ” with a turquoise accent and the word “ CLEAN ” visible near the bottom.
A hand with keys hovers over the bag, then lowers toward it.
Beside the bag, the white motorcycle is visible, and its side mirror reflects the blonde rider ’s face against a blue sky.
In the mirror, she touches and smooths her blonde hair, checking her look.
On a dressing table, the same TRESemmé Pro Pure Dry Shampoo can stands upright among beauty items : small bottles, a spray bottle, a round mirror, and soft vanity lights.
A hand reaches in and touches the top of the can.
The setting shifts wider to a warmly lit dressing-room vanity.
A performer with a large halo of curly dark hair sits or stands before the mirror, stretching one arm over her head while surrounded by bulbs, cosmetics, flowers, and glowing decorative lights.
The commercial ends with a neat product lineup on a dark counter against a black tiled wall.
Multiple TRESemmé Pro Pure bottles and cans stand side by side in white, pale blue, green, and lavender label variations, with black caps.
A small plant sits to the left, and hair tools and a brush are arranged to the right, framing the collection as the final visual focus.

% matched lemmas: bright, mint-green, pant
\end{textsample}
