\begin{textsample}{NEG Dim 3 – 2010 – Score -4.00 – 2010/tv\_com\_2010\_96.txt}  \label{ex:f3_neg_002}
A woman with shoulder-length dark brown hair stands indoors against a softly blurred garage or home-workspace background.
She appears to be an adult, wearing a sleeveless floral blouse with ruffled shoulders and a small necklace.
She faces forward, first with a closed-mouth smile, then breaking into a broad laugh.
Behind her, indistinct shapes suggest a bicycle, wall art, shelves, and household storage.
The view opens to show her full body standing in the doorway of a garage framed by green ivy.
She wears gray \textbf{pants} with the floral blouse and raises one hand in a casual wave.
The garage interior is \textbf{bright} and tidy, with a bicycle on the left, storage shelves along the back, and bins or equipment on the right.
White lowercase text appears across the middle : “ noom stories. ” The scene changes to a backyard pool area.
A young adult woman with long dark hair dyed reddish-purple at the ends stands beside the pool, facing forward.
She wears glasses, a purple sleeveless crop top, and dark patterned shorts.
Behind her are two red circular woven patio chairs, a small black side table, dense green hedges, and the blue edge of the swimming pool on the right.
The white “ noom ” logo sits in the upper-right corner.
Small lower text identifies her as a Noom user.
She gestures outward with both hands, then lets her arms rest at her sides, her expression shifting from \textbf{matter-of-fact} to more relaxed.
The woman from the garage returns, now standing centered in the ivy-framed garage opening.
Small white text near her reads “ Katelyn ” and “ Noom User. ” She clasps her hands in front of her and speaks toward the viewer.
A closer view follows, with the “ noom ” logo in the upper-right corner ; her floral blouse and necklace are clearer, and she gestures lightly near her chest while maintaining direct eye contact.
Back by the pool, the woman in purple smiles in the sunny garden setting, still positioned between the red chairs and the pool.
Then a man appears in a \textbf{bright} white kitchen.
He is an adult with dark hair and a full beard, wearing a navy \textbf{short-sleeve} henley shirt.
He stands near a kitchen island, holding a white towel or cloth in one hand.
The background includes white cabinets, a refrigerator covered with family photos or small notes, a window, a fruit bowl with \textbf{oranges}, and a phone lying on the counter.
On-screen text identifies him as “ Mike ” and “ Noom User, ” with the “ noom ” logo in the upper-right corner.
A blonde woman named “ Sarah, ” identified by small white text as a Noom user, sits in a softly lit bedroom.
She has long straight hair and wears a pale floral off-the-shoulder blouse.
Behind her is a white tufted headboard, pillows, and \textbf{bright} sheer curtains glowing with daylight.
She speaks while seated, looking forward, then the view widens to show the whole bedroom : pale blue walls with sloped ceilings, a bed centered under the window, bedside tables, a dresser on the left, a decorative stand with a hat and scarf, wicker baskets on the right, and a light rug on a wooden floor.
Sarah stands at the foot of the bed, leaning back on her hands for a moment, then turns and walks a few steps beside the bed before facing forward again with a smile.
Mike reappears in the white kitchen, first shown from the waist up and then closer.
The refrigerator photos and notes are visible behind him, and the “ noom ” logo remains in the upper-right.
He looks straight ahead as if giving his testimonial.
The poolside woman returns, standing still and smiling gently in the garden, with the red patio chairs behind her and the pool edge on the right.
A closer view shows her from the waist up against a leafy green background ; she glances slightly downward with a small, satisfied smile.
The “ noom ” logo stays in the upper-right, and faint fine print runs along the bottom.
The final visible image is a flat coral-red graphic screen.
It has minimal white dotted elements : a short dotted horizontal line on the left, another on the right, and a small vertical row of white dots near the top, suggesting a simple app-style or brand graphic transition.

% matched lemmas: bright, matter-of-fact, orange, pant, short-sleeve
\end{textsample}
