\begin{textsample}{NEG Dim 3 – 2020 – Score -2.00 – 2020/tv\_com\_2020\_93.txt}  \label{ex:f3_neg_049}
The commercial opens on a \textbf{solid} red screen with the Target bullseye logo centered in white and red.
It then cuts to a doorway scene : a large Target \textbf{shopping} bag with red handles and a red-and-white bullseye pattern sits on the floor just inside or near an open door.
The bag is filled with packaged items, including what look like household or grocery products.
A person ’s legs and shoes are partly visible behind it, but the person ’s upper body is not shown.
Small fine-print text appears along the bottom, but it is too small to read clearly.
Next, a tablet is shown in someone ’s hands.
On the tablet screen is a Target webpage or app interface with a large “ order pickup ” graphic and a red button beneath it.
The Target branding appears in the interface, including the red header and logo.
The scene then widens to a living room.
An adult man and a young girl sit together on a couch, looking at the tablet.
Both appear relaxed and smiling.
The background includes a gray sofa, pillows, and warm-toned decor.
The commercial cuts to an in-store or pickup-counter setting with a red Target-branded wall behind the counter.
A Target employee wearing a red top and a face mask stands behind the counter with a Target bullseye-patterned \textbf{shopping} bag.
A man and a young girl, both also wearing face masks, stand on the customer side.
Large white on-screen text reads “ free order pickup. ” The background wall includes oversized “ order pickup ” branding.
The next scene shows the open trunk of a vehicle.
A Target employee with long red hair, wearing a red top, places or adjustss two large red-and-white bullseye Target bags in the trunk.
The bags are filled with groceries or household items.
White on-screen text reads “ free drive up. ” A brief interior car shot follows.
A child wearing an orange \textbf{knit} beanie and a seatbelt sits in the back seat, seen from the side/back, looking toward the window.
The lighting suggests evening or a dimly lit setting.
Small fine-print text appears at the bottom but is not readable in the frame.
The screen then turns \textbf{solid} red.
Near the end, a red screen displays a circular icon showing a car with a Target bag or pickup symbol, with the words “ drive up ” in white below it.
The final frames show a graphic transition or zoom into the Target bullseye : a large white circle fills much of the red screen, then resolves into the red-and-white Target bullseye logo centered on a red background.

% matched lemmas: knit, shopping, solid
\end{textsample}
