\begin{textsample}{NEG Dim 3 – 2020 – Score -4.00 – 2020/tv\_com\_2020\_88.txt}  \label{ex:f3_neg_027}
A glossy blue Cadillac SUV stands in a vast, sunlit desert, its front grille and Cadillac crest prominent against the flat \textbf{golden} ground and distant low mountains.
A person in a neutral tan suit walks toward the vehicle across the open sand.
From above, the SUV appears small in the empty landscape, with large white capital letters stretching across the scene : “ ENTER ORDINARY. ” The driver ’s door of the blue SUV opens.
A slim adult with short dark hair and sunglasses steps out, now wearing a loose, pale blue suit with wide trousers.
Behind them, another adult in a dramatic \textbf{bright} red, ruffled dress appears at the open door.
White text overlays the desert scene : “ EXIT EXTRAORDINARY. ” The person in the blue suit strikes playful dance poses beside the car, while the person in red follows, the dress billowing like a cloud of fabric.
The blue-suited dancer runs, bends, and launches into an exaggerated leap across the sand ; the red-dressed dancer remains near the SUV, swirling and lifting the red fabric.
In a wider view, the two dancers and the blue Cadillac sit tiny within the enormous desert.
The setting shifts to a \textbf{bright} ocean platform surrounded by deep blue water.
A red Cadillac SUV is parked on the pale concrete surface.
A woman in a cream-colored, flowing outfit dances barefoot beside it, her curly hair moving as she extends her arms and turns.
She approaches the vehicle door, seen partly from inside the dark interior looking outward toward the sea.
As the door opens, a different woman emerges from the red SUV wearing a vivid pink, strapless, ruffled gown.
Her hair is pulled into a high \textbf{bun}, and she raises her arms in graceful, ballet-like gestures against the clear sky.
She continues dancing beside the red SUV, with the ocean horizon stretching behind her.
A wide overhead view reveals the car and dancer on a small, geometric platform floating alone in the water.
The pink-dressed dancer stands to the left of the red Cadillac SUV and performs precise hand and arm movements, lifting her arms above her head, then framing her face and chest.
The red vehicle remains parked to her right, its black grille, Cadillac crest, and vertical light design clearly visible.
In closer views, she turns her head and poses with one hand under her chin, her pink eye makeup and jewelry visible, while the red SUV fills the background.
The scene changes again to a rooftop or elevated urban lot with a city skyline and mountains in the distance.
An \textbf{orange} Cadillac sedan is parked behind a woman in a cream blazer.
She repeats a poised hand gesture near her chin, then moves out of view, leaving the \textbf{orange} car centered against the city backdrop.
The image flips upside down for a stylized moment : two adults in light-colored outfits stand beside the \textbf{orange} sedan with its doors open.
The car ’s \textbf{orange} body and dark roof glass dominate as the view passes closely over it.
Large white capital letters appear across the \textbf{orange} car scene : “ BE VIBRANT. ” Two people are at the open doors.
On the left, a long-haired adult in a \textbf{bright} pink suit steps out from the driver ’s side, hair blown across their face.
On the right, a woman in a vivid green outfit leans from the rear door with one arm extended in a dance pose.
The city remains far below in the background.
The message changes to “ BE CONFIDENT ” in the same large white lettering.
A dancer in green, with long dark hair and pink sleeves visible, stands near the front of the \textbf{orange} Cadillac holding two open white fans raised high, while the car ’s grille and crest occupy the right side of the image.
The commercial ends on a still promotional layout at sunset.
A white Cadillac sedan is parked on an elevated roadway or overlook with mountains and a warm orange-purple sky behind it.
On the left are the Cadillac crest and the words “ MOVE UP. ” On the right, large lease text identifies a “ 2023 CT5 Premium Luxury AWD ” and shows “ \$499 per month ” for “ 39 ” months, with “ \$3,969 due at signing ” visible below.
Dense fine print runs along the bottom of the screen.

% matched lemmas: bright, bun, golden, orange
\end{textsample}
