\begin{textsample}{NEG Dim 3 – 2000 – Score -3.00 – 2000/tv\_com\_2000\_91.txt}  \label{ex:f3_neg_037}
A blonde adult woman stands alone against a \textbf{bright} white studio background.
She wears a blue zip-front sweater over a gray shirt, cropped white \textbf{pants}, and is barefoot.
At first she looks unwell and uncomfortable : her arms are folded tightly, one hand presses against her temple, and her brow is furrowed.
She shifts to holding her throat with a pained expression, then hugs herself as if chilled.
In close-up, her eyes narrow and close, her mouth opens wide, and she covers her mouth as she appears to cough or sneeze, bending forward with discomfort.
She then holds a clear drinking glass filled with water in one hand and a white round tablet in the other.
Small white text at the lower right reads, “ use as directed. ” Looking serious and focused, she drops the tablet into the glass.
The tablet begins to fizz at the bottom, sending bubbles upward through the water.
She lowers the glass to the white floor beside her bare feet, releases it, and steps back.
Now seen full length, she stands centered in the white space.
Her posture changes from hunched and sickly to more active and ready.
She raises both arms outward and upward and jumps straight into the air.
The image changes into a playful visual metaphor : her feet descend toward the rim of an enormous glass of vigorously bubbling water.
She plunges down into it, creating a rush of foam and effervescence.
Inside the bubbling water, her body is surrounded by white foam and streams of tiny bubbles.
Her blue sweater and pale \textbf{pants} are visible through the froth as she sinks or floats upright.
Her hair fans dramatically upward in the water, and her expression begins to relax.
Fine print appears along the bottom : “ Day Cold does not contain an antihistamine. ” As the bubbles swirl behind her, she faces forward calmly ; her eyes open, and her mouth settles into a slight smile.
The overall image suggests she is being immersed in the fizzing medicine, with bubbles reaching around her whole body.
A teal product box appears over the watery background, then fills the center on a clean white background.
The package reads “ Alka-Seltzer Plus ” in large yellow-green lettering, with “ Cold ” below and an \textbf{orange} graphic labeled “ Orange Zest. ” Smaller text on the front lists cold-symptom relief, including nasal congestion, runny nose, cough, headache, sore throat, and sinus pain and pressure.
The same fine print remains at the bottom : “ Day Cold does not contain an antihistamine. ” The woman reappears underwater, now looking refreshed.
Bubbles continue to stream all around her as her hair floats upward in a reddish-blonde plume.
She smiles more clearly, facing forward with a relaxed, relieved expression.
Her blue sweater is speckled with bubbles, and the water behind her churns like a \textbf{bright}, foamy backdrop.
She then tips her head upward as if rising toward the surface, passing through a dense layer of bubbles.
From above, the back of her wet blonde head briefly breaks through a rippling surface.
Back in the white studio space, she springs upward and lands lightly, now energetic and playful.
She appears dry again, with her blue sweater and white \textbf{pants} neat, and she moves with a loose, dance-like bounce.
Her facial expression is cheerful and relieved, a contrast to the earlier grimacing and shivering.
A large Alka-Seltzer Plus Cold box stands on the white floor to her left as she walks near it.
Big blue capital letters appear across the top of the screen : “ LIQUIDATES YOUR BIG COLD. ” She gestures beside the box, then the scene widens into a product lineup.
From left to right are the Alka-Seltzer Plus Cold Orange Zest box and three brown liquid medicine bottles with white caps and colored labels : a green-labeled “ Night Cold, ” a blue-labeled “ Day Cold, ” and a purple-labeled “ Cold \& Cough. ” The slogan “ LIQUIDATES YOUR BIG COLD. ” remains large across the top.
Near the end, small text appears at the bottom left, “ alkaseltzerplus.com, ” and a small Bayer cross logo appears at the bottom right.

% matched lemmas: bright, orange, pant
\end{textsample}
