\begin{textsample}{NEG Dim 3 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_107.txt}  \label{ex:f3_neg_060}
A blonde adult woman, identified by on-screen text as “ FLORENCE HENDERSON, ” stands in a \textbf{bright}, softly lit kitchen-like setting with pale curtains behind her.
She faces forward and holds up a clear bottle of Wesson oil beside her face, gripping the neck with one hand and supporting the bottom with the other.
The bottle contains pale \textbf{golden} oil and has a blue-and-green label reading “ NO CHOLESTEROL, ” “ wesson, ” and “ PURE VEGETABLE OIL. ” She looks directly outward as if addressing the viewer, then glances down at the bottle and smiles.
The view changes to an extreme close look at a Crisco Oil label.
Large red letters spell “ Crisco OIL ” on a white background, with “ NO CHOLESTEROL ” above and a yellow band at the top that includes the words “ Fried Chicken and Salads. ” A yellow burst near the lower right reads “ New, ” with smaller words partly visible below it.
The label area shifts across the package to a side or back panel where dense ingredient and product text appears.
The most readable line includes “ MADE FROM VEGETABLE OIL ” and “ POLYSORBATE 80, ” visually supporting the comparison mentioned in the spoken context.
The woman returns in close view against the same pale, \textbf{bright} background.
She smiles, looks down and to the side, then lifts the Wesson bottle back into view.
She presents it upright beside her face, again showing the label clearly : “ NO CHOLESTEROL, ” “ wesson, ” “ PURE VEGETABLE OIL. ” Her expression is warm and confident, and she holds the bottle steady as if showing it off.
A serving scene follows : the Wesson bottle stands in the background on a white surface, label facing forward, while a white plate piled with golden-brown fried chicken sits in front.
Metal tongs enter from the right holding a piece of chicken, lowering it onto the plate.
The chicken pieces have a rough, craggy, crisp-looking coating.
The tongs settle the piece among the others, then move away, leaving the Wesson bottle prominently visible behind the food.
The woman appears again briefly in close-up, looking straight ahead.
Her expression shifts from attentive to a \textbf{bright} smile, maintaining the same neat appearance : short feathered blonde hair, light sweater over a pale collared blouse, and small earrings.
The scene changes to a child in a home living room, sitting on the floor near a wooden television set.
The child, seen mostly from behind and the side, has straight brown hair and wears a white shirt with yellow sleeves, blue jeans, and white high-top sneakers.
The child sits with knees bent and hands clasped, watching the glowing television screen.
The TV image is indistinct, bluish, and framed by a wooden cabinet.
A plate of fried chicken fills the view next, set on a table with woven placemats nearby.
Several hands reach in from different sides at once.
One hand takes a large piece from the right side of the plate ; another reaches from the left toward a drumstick ; a smaller hand reaches from the top.
The pieces shift as they are picked up, leaving gaps in the pile.
At the dining table, a young boy with brown hair and large dark-framed glasses sits facing forward.
He wears the same yellow-and-white shirt seen earlier.
An adult hand holds a plate heaped with fried chicken in front of him from the right, and he eagerly lifts a drumstick in his left hand.
On the table in front of him are a glass of milk and another glass with an orange-colored drink.
He opens his mouth wide, brings the drumstick to his mouth, and bites into the crisp coating.
He continues chewing, holding the chicken with both hands, his eyes partly lowered behind the oversized glasses.
The woman returns for the final product presentation, holding the Wesson bottle upright beside her face in the same \textbf{bright} kitchen setting.
The label remains clear and central : “ NO CHOLESTEROL, ” “ wesson, ” “ PURE VEGETABLE OIL. ” She looks at the bottle, then back outward, smiling broadly.
The commercial ends with her still smiling warmly while the Wesson bottle is displayed prominently in the foreground.

% matched lemmas: bright, golden
\end{textsample}
