\begin{textsample}{NEG Dim 3 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_112.txt}  \label{ex:f3_neg_056}
A chilled green glass beer bottle stands on the left beside a tall, narrow beer glass on the right.
Both are set on a dark tabletop against a softly lit grey background.
The bottle is covered with beads of condensation, and at first its front label is turned mostly away, so the bottle appears as a glossy green shape with only a dark, partial label area visible.
The glass is filled with \textbf{golden} amber beer and topped with a thick, smooth white foam head that rises slightly above the rim.
The beer glows warmly, with bubbles and highlights visible through the glass.
The bottle and filled glass remain side by side, evenly spaced, like a simple studio product display.
The amber beer stays steady in the glass, and the foam cap remains rounded and dense.
A hand enters from above and grips the neck of the bottle with thumb and fingers.
The hand begins to rotate the bottle, turning it so that the label faces forward.
As it turns, more of the white and green label comes into view.
The bottle is now presented front-on.
Its oval label is clearly visible, with the Heineken name across the center and surrounding label text including “ Imported Beer. ” The green bottle still looks cold and wet with condensation.
A smaller neck label is also visible near the top.
The glass of beer remains to the right, upright on its stem, with the \textbf{bright} \textbf{golden} liquid and white foam head forming a clean contrast against the darker background.
Near the end, another hand reaches in from the right and wraps around the stem of the beer glass.
The hand lifts the glass slightly from the tabletop while the Heineken bottle remains standing to the left with its label facing forward.
The final image holds the bottle and the lifted glass together, emphasizing the chilled bottle, the branded label, and the freshly poured beer.

% matched lemmas: bright, golden
\end{textsample}
