\begin{textsample}{NEG Dim 3 – 2020 – Score -2.00 – 2020/tv\_com\_2020\_16.txt}  \label{ex:f3_neg_048}
The commercial opens in a bright living room with a beige sofa, pillows, houseplants, shelves, and large windows.
A small shaggy black-and-white dog sits upright on the sofa near a TV remote, while a person is visible outside the window handling a garden sprayer or container.
The next shots focus on the dog lounging on the sofa.
A smartphone is propped against a cushion near the dog, showing a dog on a green-screen interface.
The dog then appears lying back among pillows, holding or looking at a phone.
The dog looks toward a television.
On the TV screen is an advertisement-like image for a green product labeled “ Spruce, ” with large visible text : “ SAFE FOR USE AROUND PEOPLE, PETS \& BEES. ” The product image shows a green container with a spray wand.
The dog becomes active on the sofa, then the scene cuts to a wooden coffee table with a set of keys and a paw-shaped keychain.
In the background, the dog jumps or runs off the sofa, suggesting movement toward leaving.
A close-up follows of a car ignition area with keys being inserted or handled.
Outside, the rear of a white vintage-style convertible is shown with a license plate reading “ 1H8WDZ. ” The car is then seen in motion with the dog riding in it, wearing goggles.
A green Spruce product container is visible in the car near the windshield.
The setting shifts to a garden-center or home-improvement store aisle.
A woman stands in front of a bright green Spruce display \textbf{stocked} with multiple bottles and containers.
The dog sits facing the display beside her.
Back outdoors at a \textbf{house}, a man uses a green Spruce container with a spray wand on a patio or garden area while the dog stands nearby on the \textbf{lawn}.
A close-up comparison shot shows two small plants growing in soil, with green labels above them ; the visible text is partially cut off, showing “ UNTREAT … ” on the left and “ TRE … ” on the right.
The man then crouches beside the dog in the yard and pets it.
A Spruce container is placed beside them.
A later shot shows a dark pickup truck driving with several dogs visible through the open windows and a large Spruce product display standing in the truck bed.
The final frame is a graphic product card on a green and yellow background.
Large text reads : “ PET FRIENDLY.
WEED DEADLY. ” A Spruce Weed \& Grass Killer container is shown prominently, with a spray wand attached.
Additional visible text says : “ SAFE FOR USE AROUND PEOPLE, PETS \& BEES, ” with a small note : “ *When used as directed. ”

% matched lemmas: house, lawn, stock
\end{textsample}
