\begin{textsample}{NEG Dim 3 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_100.txt}  \label{ex:f3_neg_067}
The commercial begins with a very dark frame ; no clear objects or people are visible.
It then cuts to a brightly lit backstage or dressing-room setting.
A young woman dressed like a ballerina, wearing a white tutu and hair ornament, sits at a vanity/table.
Around her are theatrical dressing-room elements, including a lit mirror, flowers, costumes or garments in the background, and breakfast items on the table.
A red box of **Kellogg ’s Frosted Mini-Wheats** is prominently placed beside a bowl, a plate with food, a mug, and a white pitcher.
The next shot is a product display on a red tabletop.
The **Kellogg ’s Frosted Mini-Wheats** box is centered and clearly readable.
Around it are a glass of milk, a glass of orange-colored juice, a white pitcher, a bowl containing cereal pieces, and a plate with stacked toast or waffles topped with a pat of butter.
Small copyright text appears at the bottom right, but it is only partly legible.
The camera then cuts closer to the bowl of cereal.
Several rectangular shredded-wheat pieces are visible in the bowl, with a frosted or pale coating on one side.
The shot emphasizes the cereal texture and shape.
The setting changes to a room with East Asian/Japanese-style visual elements : grid-like wall panels, red circular wall decorations, low table surfaces, and a wall hanging with vertical writing.
A young man sits at a low table wearing a white robe or jacket with a circular patch.
A red **Frosted Mini-Wheats** box is on the table beside him, along with a small bottle, dishes, and a bowl.
A close-up follows of a single Frosted Mini-Wheats cereal piece resting on a metal spoon.
The background is blurred, showing part of the man ’s white garment and dark inner clothing.
The camera returns to the young man.
He smiles while holding the spoon toward the camera, with the cereal box visible at his side.
The bowl and tableware remain in front of him.
In the final frame, he is still smiling, holding the spoon in one hand while raising or waving a brown, blurred object with the other hand near the camera.
The red **Kellogg ’s Frosted Mini-Wheats** box remains visible in the foreground.
The exact nature of the raised object is unclear from the sampled frame.

% matched lemmas: 
\end{textsample}
