\begin{textsample}{NEG Dim 3 – 1990 – Score -2.00 – 1990/tv\_com\_1990\_1.txt}  \label{ex:f3_neg_081}
The commercial opens on a very dark, indistinct outdoor image ; details are not clearly visible.
It then cuts to a warmly lit scene with an older man and a young blonde woman close together.
The man wears a light-colored brimmed hat and outdoor-style clothing.
The woman leans in toward him, and the moment appears affectionate or playful.
The setting looks rustic or outdoors-adjacent, with wood and greenery in the background.
The next shots show the young blonde woman outdoors in daylight, smiling and walking through a leafy, wooded area.
She wears a brown jacket over a light shirt.
A close-up follows inside a vehicle : she smiles and looks toward someone beside her, with bright foliage visible through the window.
A close-up shows a hand touching or resting near a seat or interior surface, possibly inside the car.
The image is tight and somewhat unclear, but it emphasizes the vehicle interior and a person ’s hand.
The older man is then shown driving.
He wears the same light brimmed hat, a light jacket, and a seat belt.
He looks toward the passenger side while seated behind the steering wheel.
An exterior shot shows a white four-door sedan parked in front of a log cabin or rustic wooden \textbf{house} surrounded by trees.
The car is shown in profile, emphasizing its side view and compact sedan shape.
Back inside the car, the older man holds up a small round metallic object, possibly a fishing-related item or container, while smiling.
The steering wheel and seat belt are visible.
The scene then cuts to the white sedan driving along a wooded road, seen from the front through trees and dappled sunlight.
Inside the moving car, the older man and the young woman are shown together wearing seat belts.
He raises an arm near the roof area, and she turns toward him.
A closer shot of the woman shows her smiling slightly and looking sideways toward him.
The car continues driving through a forested road, shown from the front and side with trees passing in the foreground.
The man is again shown inside holding metallic cylindrical objects or containers.
The woman \textbf{responds} with a smiling expression from the passenger seat.
A close-up shows one of the metallic containers being tipped over a cup or small holder in the car ’s center console area.
The exact contents are not visible.
Near the end, the commercial shifts to promotional overlays.
A front view of the white sedan driving appears with large white text at the top : “ Up To \$1,400 Cash Back ” “ \$800 Cash Back plus \$600 Bonus for Import Owners ” Small legal text appears at the bottom : “ You must take retail delivery from dealer \textbf{stock}.
See your participating dealer for qualification details. ” The same promotional text continues over additional shots : a close-up of a hand inside the car, a rear view of the white sedan driving away on a wooded road, and a close-up of the smiling young woman inside the vehicle.
The final frame presents a static product-and-brand image.
A white sedan is parked in profile beside a lake with mountains and forest in the background.
Large text at the top reads : “ GET TO KNOW Geo ” At the bottom, text reads : “ AT YOUR CHEVROLET-GEO DEALER ’S ” The visual emphasis throughout is on a white Geo sedan, outdoor leisure imagery, a friendly interaction between an older male driver and a young female passenger, and a cash-back sales offer.

% matched lemmas: house, respond, stock
\end{textsample}
