\begin{textsample}{NEG Dim 3 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_94.txt}  \label{ex:f3_neg_029}
The commercial opens in a \textbf{bright}, toy-like miniature neighborhood.
From above, a gray road curves in a loop through green lawns, tiny trees, colorful little houses, and soft cottony clouds around the edges.
A small red delivery vehicle moves along the road.
The whole world looks like a handcrafted model, with saturated colors and neat, playful shapes.
The red vehicle passes a PetSmart storefront with the large “ PETSMART ” sign on the building.
In the open-top vehicle sits a small, shaggy white dog with gray-tan patches on its ears and around one eye.
The dog sits upright like the driver or passenger, mouth slightly open as if \textbf{panting}.
Behind it are red delivery bags branded with PetSmart and DoorDash.
The vehicle itself is also labeled with PetSmart and DoorDash marks, making it look like a tiny branded delivery car.
It rolls past stylized houses, rounded shrubs, and puffy clouds in the painted-blue sky.
A closer view focuses on the vehicle ’s black tires and red side panel as it passes in front of a house with a \textbf{bright} blue front door.
As the car moves away, a red delivery bag is left standing neatly on the doorstep between two round potted shrubs.
The bag has white text and logos reading “ PETSMART ” and “ DOORDASH. ” It sits upright like a completed doorstep delivery.
The scene then glides past greenery into another miniature yard.
A yellow camper-shaped pet home with a teal door sits behind a white picket fence.
The camper has playful details, including rounded windows and cat-like pointed shapes along the top, giving it a whimsical pet-house look.
A red PetSmart/DoorDash delivery bag waits on the grass to the right of the doorway.
In front are pet toys and yard props : a small red lounge chair, balls, a rope-like toy, and pink flamingo lawn ornaments near trimmed hedges.
The shaggy white dog pops out of the teal doorway and bounds down the little steps toward the lawn.
It moves toward the toys and the red bag, head low for a moment as if inspecting what has arrived.
The view passes through more bushes into an indoor pet space that still looks like part of the same miniature world.
The room has warm cream walls, arched openings, small wall decorations, and a patterned rug.
On the left is a gray, multi-level cat-tree or pet play structure with ramps and platforms.
Near the center is a large green reptile or tortoise-like pet resting among stones, leafy shapes, and scattered food pellets.
On the right, another red PetSmart/DoorDash delivery bag stands beside the pet area.
Around it are pet supplies and greenery, suggesting the delivery includes items for different kinds of animals, not only dogs.
The room looks cozy and staged like a tiny pet apartment.
The greenery gives way to a glass-walled aquarium-like home.
Inside, a \textbf{bright} \textbf{orange} fish swims in a room filled with fanciful miniature furniture : a black grand piano, a small white chair, pink gravel covering the floor, a chandelier-like decoration overhead, and a tall green aquatic plant on the right.
A red delivery bag sits outside the glass structure on the right side, again marked for PetSmart and DoorDash.
The fish floats in the center of this underwater living room, while the bag waits just outside, continuing the playful idea that many kinds of pets can receive supplies.
The shaggy white dog returns in the red open-top delivery car, now seen closer at neighborhood level.
It sits upright in the vehicle, framed by simple modern houses and rounded green hills in the background.
The dog ’s fur is fluffy and cream-white, with darker patches on its floppy ears.
Its mouth is open, \textbf{tongue} visible, and it looks alert and cheerful.
The small windshield is in front of it, and the car ’s side still shows PetSmart and DoorDash branding.
As the car continues, the dog faces forward, then slightly to the side, remaining the active guide through the miniature pet neighborhood.
The setting changes into a real home interior.
A small white-and-gray dog, matching the one from the miniature scenes, looks up from a low angle.
An adult man with short dark hair, a trimmed beard, and a friendly expression stands above the dog.
He wears a red, white, and dark plaid overshirt open over a pale blue T-shirt, with casual \textbf{pants}.
Behind him is a warm living room with beige walls, leafy green houseplants, a wall shelf with small decorative items, and a soft, homey light.
He holds up a large red PetSmart/DoorDash delivery bag in one hand, showing it to the dog.
A wider view reveals the room more fully.
The dog lies or sits on a red-and-white pet bed shaped like the same little delivery car, placed on a patterned rug.
The man bends down beside it and sets the red bag on the floor.
Behind them are framed pictures arranged in a grid on the wall, including pet-themed images, plus a light-colored armchair, a side table with a lamp, and more plants.
The man reaches toward the dog with a gentle, affectionate gesture, petting or greeting it as the dog looks up from its car-shaped bed.
The commercial ends on a clean graphic background in pale blue with soft abstract shapes.
On the left is the “ PETSMART ” logo with the tagline “ Anything for Pets. ” A vertical line separates it from the red DoorDash logo and the word “ DOORDASH ” on the right.
The little red delivery car drives across the bottom of the screen with the shaggy white dog seated inside and red delivery bags stacked behind it.
As the car passes in front of the logos, black text appears underneath : “ Get more from your neighborhood. ” The dog continues riding toward the right edge as the PetSmart and DoorDash logos remain centered.

% matched lemmas: bright, orange, pant, tongue
\end{textsample}
