\begin{textsample}{NEG Dim 3 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_111.txt}  \label{ex:f3_neg_055}
The commercial opens on a green graphic from a different-looking ad : a small inset picture of a smiling couple outdoors appears above large white words reading “ Fresh and Clean as a Whistle, ” beside a black Irish Spring soap logo panel.
It then moves to the McDonald ’s scene outside a glass-fronted restaurant with the white “ McDonald ’s ” sign high above the windows.
A crowd of customers and onlookers gathers on the patio, some standing, some sitting on the ground, several holding white McDonald ’s bags.
Across the bottom, bold white text reads “ JUMP TO IT, ” with a red McDonald ’s logo box at the lower right.
In front of the restaurant, a group of young performers in coordinated red, white, and yellow \textbf{athletic} clothing gathers around a jump rope.
Their outfits use McDonald ’s colors : red tracksuits or sweaters, white panels, yellow leg warmers, white sneakers, and yellow headbands or hats.
Two rope turners stand at opposite sides, moving the rope in long arcs, while a young woman in the center steps forward to jump.
She wears red \textbf{pants}, a white-and-red striped top with yellow bands, yellow leg warmers, and white shoes.
The crowd watches from behind the performers, framed by the restaurant ’s reflective windows and brick walls.
The routine becomes more acrobatic.
A young woman wearing a yellow cap with a red pom-pom climbs onto another performer ’s shoulders, then drops down into the rope area.
She and another performer in a white McDonald’s-logo vest and red \textbf{pants} begin a lively partner routine, stepping close together, hopping in place, and matching each other ’s footwork.
Their faces show concentration and enjoyment as they look at each other and the moving rope.
One performer wears large red earmuffs ; the other ’s yellow cap bounces as they move.
A close-up briefly shows a Chicken McNugget being pulled apart by two hands.
The \textbf{golden} breading cracks open to reveal white chicken inside, with visible steam rising against a dark background.
The scene returns to the outdoor performance, where the same two performers jump together.
One lifts or supports the other through a flip : the performer in the yellow cap bends backward across the partner ’s body, legs swinging up and over in a controlled tumble while a rope turner at the side keeps an arm raised.
Spectators behind them smile and lean forward to watch.
The two performers land and face each other again, laughing and clapping hands.
The McDonald ’s logo is visible on the back of one white vest, along with small printed words beneath it.
Another young man in a red jacket and white \textbf{pants} steps into the routine.
He faces the performer in the yellow cap, lifting his knees in rhythm while they mirror each other ’s small hops and quick foot movements.
The performer in earmuffs stands nearby, clapping along.
The action cuts to another close-up of the product : a \textbf{golden} Chicken McNugget is dipped into a small white plastic cup of sauce.
The nugget goes down into the glossy sauce and rises coated ; thick sauce stretches and drips back into the cup in a slow ribbon.
Back outside, the performers continue jumping and leaning through the rope, with one man bent forward as if becoming part of the obstacle or stunt while another guides the movement behind him.
A product display appears on a tabletop : stacked McDonald ’s Chicken McNuggets boxes, including brown boxes with “ Chicken McNuggets ” printed on the sides and large numerals such as “ 20, ” plus a light-colored clamshell box on top.
Hands reach in from different sides and quickly take the packages away, leaving the tabletop almost empty.
The performers continue beside the restaurant windows.
The young woman in the yellow cap and the young man in the red jacket face each other closely, gesturing with their hands as if playfully talking or counting beats.
Then they resume bouncing footwork together, clapping palms and hopping in place.
Another close-up again shows a Chicken McNugget being pulled open, the white interior steaming between the two \textbf{golden} halves.
Near the end, the wider group returns to the center of the patio.
Several performers tumble and slide into low poses while the crowd forms a semicircle around them.
Large white on-screen text appears across the bottom : “ IT ’S A GOOD TIME FOR THE GREAT TASTE, ” with the red McDonald ’s arches logo at the lower right.
Behind the dancers, a large yellow arch sign is visible near the restaurant entrance.
The performers finish on the ground in a playful pile or seated cluster, smiling.
The final close view centers on the young woman in the yellow cap reclining comfortably among the other performers.
She smiles directly forward, her red-and-white McDonald’s-colored top visible, while friends in red \textbf{athletic} jackets grin behind and beside her.
She lifts one hand in a small approving gesture, ending the scene with a cheerful, relaxed expression.

% matched lemmas: athletic, golden, pant
\end{textsample}
