\begin{textsample}{NEG Dim 3 – 2000 – Score 1.00 – 2000/tv\_com\_2000\_19.txt}  \label{ex:f3_neg_078}
The commercial begins with a nearly black frame, with no discernible visual content.
It then cuts to the interior of a moving vehicle, seen from the front through the windshield.
Three people are visible : a blonde woman wearing a blue shirt and seatbelt on the left, a young man in a red hoodie seated between/behind the front occupants, and an older man in a tan jacket driving on the right.
The background through the windows is bright and green, suggesting a rural or open landscape.
The next sequence alternates between close-ups of the occupants inside the vehicle.
The young man in the red hoodie is shown looking to the side and then forward, appearing to speak or react.
The blonde woman is shown in profile and then facing forward with a slight smile or restrained expression.
The driver is shown holding the steering wheel and looking ahead.
These shots suggest an exchange among the passengers, but no dialogue is visible or inferable from the frames alone.
A close-up then shows a foot pressing or moving on a vehicle pedal in the footwell.
The exact pedal is unclear from the sampled frames, but the motion implies a driving action.
The scene cuts to exterior shots of the vehicle : a tan, wood-paneled SUV or station wagon driving along a sunny rural road.
Mountains, green fields, and white fences are visible in the background.
The vehicle is shown from the front, from a distant side view, and in closer side tracking shots, emphasizing its movement through the countryside.
The commercial then cuts to a product-style shot : a bowl filled with small square, ridged cereal pieces.
Milk is being poured into the bowl from the upper left of the frame.
Near the end, the young man in the red hoodie appears outside beside a white fence in a green rural pasture landscape.
He is carrying luggage, including a large brown bag or suitcase and another bag slung over his shoulder.
A black-and-white cow is visible behind the fence.
Large white on-screen text reads “ Golden Grahams ” beside him.
In the final frame, the young man is still near the fence with his luggage, appearing to move along or step near the roadside.
The rural pasture and cow remain in the background.
Large white text across the field reads : “ GO GET YOUR OWN. ”

% matched lemmas: 
\end{textsample}
