\begin{textsample}{NEG Dim 3 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_92.txt}  \label{ex:f3_neg_051}
The commercial is in black and white and unfolds outdoors, mostly on a \textbf{lawn} near a suburban \textbf{house}.
A pink “ @FromFilm ” watermark appears near the bottom center of all sampled frames. 1. **Opening frame** : The first frame is very dark and low-contrast.
Only vague shapes are visible, including what may be a person or object in the foreground, but the scene cannot be identified clearly from the frame. 2. **Interviewer and woman outside a house** : The scene cuts to a bright outdoor setting.
A middle-aged man in a dark suit, white shirt, tie, and glasses stands on the left, holding a handheld microphone toward a young woman on the right.
She wears a light-colored patterned blouse and has shoulder-length styled hair.
Behind them is a single-story \textbf{house} with a \textbf{lawn}. 3. **Close-up of the young woman** : The camera cuts to a tight close-up of the same woman ’s face.
She looks forward, slightly squinting in the outdoor light, as if answering or addressing someone.
The background is blurred. 4. **Product shown by the man** : The man now faces the camera, still outdoors in front of the \textbf{house}.
He holds up a rectangular product box with both hands.
The box text is clearly visible : “ COLD POWER ” and below it “ LAUNDRY \textbf{DETERGENT}. ” He also holds a microphone vertically at his side. 5. **Return to woman and interviewer** : The man is seen from behind/side on the left, facing the woman.
The woman smiles while looking at him.
The \textbf{lawn} and \textbf{house} remain in the background. 6. **Another angle with a sign in foreground** : The man stands facing the woman, who is seen from behind.
He holds the microphone toward her.
In the lower right foreground there is a sign or decorative object with partial readable text : “ THE R.
LANDS … ” The rest is cut off or obscured.
The background appears wooded or leafy. 7. **Close-up of a different woman** : A new woman appears in close-up.
She has dark, short styled hair and faces the camera directly.
The background is softly focused foliage or outdoor scenery. 8. **Close-up of another woman** : The commercial cuts to a different woman in close-up, with short curled hair.
She faces the camera.
A small dark spot or mark is visible near her forehead area.
The background is out of focus. 9. **Close-up of the original young woman** : The first young woman in the patterned blouse reappears in close-up, facing forward.
Her expression is more neutral or serious than in the earlier smiling shot.
The background remains an outdoor residential setting. 10. **Man with product again** : The man reappears in a medium shot on the \textbf{lawn}, holding the “ COLD POWER LAUNDRY \textbf{DETERGENT} ” box in front of his chest.
The \textbf{house} is visible behind him.
On the right edge of the frame, part of a large light-colored object is visible, but it is only partially shown and cannot be identified with certainty. 11. **Final product-and-text frame** : The same shot continues with the man holding the \textbf{detergent} box.
Large white on-screen text appears to his right reading : “ Proved by women like you. ” The product box remains visible on the left side of the text, with the man behind it.

% matched lemmas: detergent, house, lawn
\end{textsample}
