\begin{textsample}{NEG Dim 3 – 1950 – Score 1.00 – 1950/tv\_com\_1950\_26.txt}  \label{ex:f3_neg_003}
The commercial is in black and white and appears to move through a domestic, bedroom/laundry-related setting before ending with a product display. 1. **Opening frame** : The clip begins on a very dark, nearly black frame.
No clear objects or people are visible. 2. **Close-up of a woman** : A blonde woman is shown in close-up, facing slightly upward and to the side.
She wears a patterned dress with a white collar and earrings.
Behind her are curtained windows, giving the scene a home interior appearance. 3. **Bedroom scene with clothing or fabric** : The same blonde woman stands in a bedroom-like room, holding up a light-colored garment or piece of fabric, possibly a dress or robe.
Two other women sit in the foreground on or near a bed, turned toward her.
The room includes floral wallpaper, a window with curtains, a dressing table or dresser, and a mirror. 4. **Two women inspecting fabric** : The scene cuts closer to two seated women.
One woman in a light dress smiles while another woman holds or points to a folded white cloth or garment.
They appear to be examining the fabric together.
A framed picture and vase or flowers are visible in the background. 5. **Blonde woman holding fabric** : The blonde woman is shown again, standing near a dresser and mirror.
She looks downward with a slight smile while holding a large white cloth or garment.
A door and framed wall picture are visible behind her. 6. **Product being poured** : A close-up shows hands pouring flakes or powder from a box labeled **“IVORY SNOW”** into a glass or container.
The box dominates the frame, and the product name is clearly visible in large lettering. 7. **Final product display** : The commercial ends with a pack shot of the **Ivory Snow** box standing in a mound of white, snow-like material.
Text on the screen reads **“99 44/100 \% PURE”** and **“WITH BEAUTY GLOW.”** The background is dark, making the white mound and product package stand out clearly.

% matched lemmas: 
\end{textsample}
