\begin{textsample}{NEG Dim 3 – 1970 – Score -3.00 – 1970/tv\_com\_1970\_10.txt}  \label{ex:f3_neg_062}
An outdoor scene opens on a small airboat in a sunny marsh or river setting.
Two adults in light-colored outdoor clothing and caps sit on the boat, one higher at the controls behind a large circular fan cage and another seated lower in front.
The boat speeds across calm greenish water, throwing wide white sprays to both sides and leaving ripples behind.
Trees and low vegetation line the far bank, and the airboat cuts across the water from the distance toward the side of the scene, partly disappearing behind its own cloud of spray before continuing on.
The scene changes to an empty running track with rows of hurdles set up in several lanes.
Stadium bleachers rise along the left side, and the track stretches into the distance.
Two athletes rush through the foreground in a blur, leaping over the nearest hurdles.
One wears a light outfit with blue accents, and another wears a yellow top with shorts.
They pass so quickly that their bodies smear across the image, leaving the hurdles and long lanes visible again.
A Big Mac appears alone against a dark studio background on a glossy surface.
It is a tall, layered hamburger with a sesame-seed top \textbf{bun}, two beef patties, a middle \textbf{bun} layer, melted yellow cheese, shredded lettuce, sauce, and other toppings peeking from between the \textbf{buns}.
The view moves into very close detail, filling the screen with the browned patty, creamy sauce, lettuce, and sesame-speckled bread.
The setting shifts to a dim nightclub or dance floor with reddish and pink lighting.
Adults in 1970s-style dress clothes dance in groups and couples.
A man in a pale suit stands near the center with a woman in a light dress ; other dancers in \textbf{bright} dresses and dark outfits sway and raise their arms around them.
Small mirrored disco balls hang overhead, and a red “ EXIT ” sign glows in the background.
The crowd keeps moving, with arms lifting, bodies turning, and people crossing in front of one another in the low, colorful light.
Back on the dark product display, the sandwich is built up layer by layer.
A sesame-seed \textbf{bun} half sits on the reflective surface, then lettuce and sauce are visible under a slice of pale yellow cheese.
A browned beef patty appears on top, sprinkled with small chopped onions.
Another \textbf{bun} layer is added, followed by more filling and a second patty with onions.
Finally, the rounded sesame-seed top \textbf{bun} completes the Big Mac.
The finished sandwich stands tall and neat, with the two patties separated by the center \textbf{bun} and the toppings visible around the edges.
The view again moves very close to the top portion, emphasizing the sesame seeds, browned meat, sauce, and lettuce.
Inside a McDonald ’s dining area, a middle-aged to older Black man with a bald head, hair at the sides, and a mustache sits facing forward.
He wears a red sweater or jacket with a white collar.
He holds a Big Mac in both hands at chest height.
Behind him, other customers and restaurant activity are softly out of focus ; people pass by carrying trays, and a seated person is visible to the side.
The man lifts pinched fingers toward his mouth as if tasting a loose sesame seed, then smiles warmly while still holding the sandwich.
He looks pleased and playful, glancing forward as he brings the Big Mac closer.
He lowers his face toward it and takes a bite, holding the sandwich carefully with both hands.
The image of the man eating is then framed inside a gold-bordered rectangle on a black background.
Beneath the inset, the McDonald ’s \textbf{golden} arches appear, with small “ McDonald ’s ” lettering and large white words reading “ Big Mac. ” The inset changes briefly to the running track with hurdles, still above the same McDonald ’s and “ Big Mac ” branding.
It then changes again to a centered picture of the Big Mac on the dark background.
At the bottom, the McDonald ’s arches and large “ Big Mac ” text remain prominent, with a small copyright line below.

% matched lemmas: bright, bun, golden
\end{textsample}
