\begin{textsample}{NEG Dim 3 – 2000 – Score -3.00 – 2000/tv\_com\_2000\_107.txt}  \label{ex:f3_neg_033}
A young woman with dark hair, wearing a grey and blue \textbf{athletic} top, black shorts, and a climbing harness, clings to a pale grey artificial rock wall.
Dark safety ropes run diagonally across the view.
She looks tense and uncertain, her body pressed close to the wall, one arm reaching outward as if searching for help or the next hold.
A young man with short dark hair and light stubble, wearing a navy shirt with \textbf{orange} panels, appears nearby on the same wall.
He looks up toward her with an encouraging smile, one hand braced on the wall and the other reaching toward her.
Their hands meet in close-up against a \textbf{bright} blue sky : his gloved hand reaches down, her bare hand reaches up, and they clasp fingers.
The wider view reveals the full climbing setup, with both of them roped into a tall grey climbing wall dotted with colorful handholds.
An instructor or crew member in blue stands to the side with climbing gear, while the man crouches low on the wall and stretches toward the woman, who is higher and to his left.
The scene opens out to a large white Royal Caribbean cruise ship moving through deep blue water under a \textbf{bright} sky.
Its rounded bow and rows of windows dominate the view as it advances across the ocean.
The vacation montage then expands beyond the ship : a small white helicopter flies over lush green cliffs and a sandy coastline, with turquoise water and surf below.
Inside the helicopter, passengers lean toward the windows.
A smiling woman looks out over the landscape, and another passenger points down toward the sea through the window.
A white sailboat glides over dark blue water, its large triangular sail filled, with several people gathered on deck.
The activity shifts to swimming in vivid turquoise water under a \textbf{bright} sky.
A woman in sunglasses laughs while holding or playing with a child at the water ’s surface, and a man swims behind them.
Another swimmer splashes dramatically, legs rising into the air before the water fills the view in flashes of blue and white.
Two personal watercraft race across sunlit water, throwing up spray.
In a closer view, two people wearing yellow life vests ride together on a white and blue jet ski, skimming across the sea.
Another rider farther away raises both arms high in triumph as the craft speeds forward, leaving a foamy wake behind.
A volleyball game appears under a blue sky with white clouds.
Players jump at a net ; one in a red-orange shirt reaches up as the ball hovers near the top of the net.
The action then moves into a dense green forest.
A rocky trail runs through shaded trees and thick foliage.
Helmeted riders or adventurers move through the wooded terrain.
Close-ups show several adults in helmets, their faces sweaty and alert, looking upward or ahead with focused, excited expressions.
The helicopter returns, now with a man in a red shirt inside holding onto a ceiling handle and smiling as the coastline stretches outside the windows.
Outside, the white helicopter flies low over \textbf{bright} blue surf and a \textbf{golden} beach, with green land beyond.
On the water, a sport-fishing boat pushes through choppy waves, fishing rods angled upward from the deck.
Spray rises around the blue and white boat.
A close view of a fishing rod shows it bending sharply against the sky, suggesting a strong pull on the line.
Two adults on the boat, one woman in an \textbf{orange} top and dark cap and one man in a patterned shirt, smile and hold fishing rods while looking upward and outward.
The rock wall returns in a much wider outdoor view.
A climber in a harness moves across a tan, pockmarked artificial climbing surface, secured by ropes.
The wall curves upward against the blue sky, with many molded holds scattered across it.
The climber stretches from hold to hold, legs spread for balance.
A group of four adults stands chest-deep in water inside a dark rocky cavern or shaded pool.
Light filters down from above.
They smile and look upward, relaxed and delighted.
One man has his arm around a woman in an \textbf{orange} swimsuit, while two other shirtless men stand beside them, all gathered close together in the water.
The final images return to the cruise ship at \textbf{golden} sunset.
The large white ship sails through calm water near dark, hilly land, its windows glowing warm in the low light.
Over the ship, Royal Caribbean branding appears : a blue rectangular logo with the white crown-and-anchor emblem and the words “ Royal Caribbean International. ” The website “ royalcaribbean.com ” appears in white near the lower left, and the slogan “ Get out there ” appears near the bottom beside the logo as the ship continues across the shimmering sunlit water.

% matched lemmas: athletic, bright, golden, orange
\end{textsample}
