\begin{textsample}{NEG Dim 3 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_106.txt}  \label{ex:f3_neg_084}
The commercial opens on a nearly black frame, with only a faint television-style watermark visible in the lower-right corner.
It then cuts to a bright, white kitchen.
Two people are moving around a central island or counter ; one wears a red top.
The kitchen has a large window with warm-colored panes or curtains, a stovetop on the island, and household objects on surrounding counters.
The motion is blurred, suggesting quick activity in the kitchen.
A close-up follows of a woman holding a white trigger-spray bottle labeled “ Direct. ” The label is blue with a large white “ Direct ” name and a red/yellow arrow-like logo.
She is shown in warm sunlight near a window, holding the bottle upright.
The ad then shows a close view of a countertop or stovetop area.
A hand aims the spray trigger toward a small yellowish stain or spill near the edge of a stove.
The stain appears greasy or food-like, but its exact substance is not identifiable from the frame.
Another shot shows the bottle being held near a stovetop and pan, reinforcing the kitchen-cleaning setting.
A close-up isolates a yellow spill or smear on a light surface, with some surrounding clear liquid or droplets.
This is followed by an extreme close-up of the product label.
The visible text includes “ Direct, ” “ Multi-Purpose Cleaner, ” and a claim on the label reading “ Cuts Tough Grease and Grime! ” The Lysol name appears at the bottom of the label.
The setting then changes to another kitchen scene, darker and more warmly lit, with a large window in the background.
Two people lean over a countertop ; one holds the Direct spray bottle.
There are seasonal-looking objects such as pumpkins or orange decorations on or near the counter.
Small copyright text reading “ {\EmojiFont ©} 1992 L\&F Products ” appears at the bottom left.
The commercial then returns to product-focused shots : a blurred close-up of the Direct bottle moving past the camera, followed by a stable product shot of the white trigger-spray bottle standing on a counter in front of a bright window with plants or colored objects in the background.
Near the end, the product line expands visually.
A white Direct spray bottle appears alongside a larger blue refill pouch or container.
The final frame presents both items clearly against a plain light background : the white trigger-spray bottle on the left and a blue “ Direct ” refill package on the right.
The refill package prominently displays the word “ Refill, ” the Direct branding, and “ Multi-Purpose Cleaner. ”

% matched lemmas: 
\end{textsample}
