\begin{textsample}{NEG Dim 7 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_54.txt}  \label{ex:f7_neg_016}
A bright game-like candy selection screen appears on a \textbf{red} fruit-patterned background.
At the top left is the Push Pop Gummy Roll logo, and across the top in large yellow-orange letters is the instruction “ SELECT SWEET GUMMY CANDY. ” Four round Push Pop Gummy Roll dispensers are arranged in a grid : \textbf{blue}, pink, \textbf{red}, and turquoise, each with a \textbf{yellow} frame and a small flavor badge on the front.
A white hand-shaped cursor moves between them, and each choice it touches glows with a white outline, as if being selected.
The scene changes to a colorful cartoon park or game world with \textbf{green} grass, rounded trees, clouds, and distant candy-like buildings.
Two children stand in the middle, outlined with a bright white glow.
On the left is a light-skinned blonde girl, about preteen age, wearing a coral-red long-sleeved top and dark pants.
On the right is a medium-brown-skinned boy of similar age, with tall curly black hair, wearing a black-and-blue color-block sweatshirt and tan pants.
They each hold up a Push Pop Gummy Roll dispenser as the word “ READY... ” appears in large orange letters near the bottom.
Fruit graphics, including grapes and a strawberry slice, appear on glowing display panels beside them.
A close view shows hands holding the turquoise Push Pop Gummy Roll dispenser against the grassy game-world background.
The dispenser is rounded and palm-sized, with a \textbf{yellow} top and \textbf{yellow} front frame, a \textbf{blue} fruit badge on the side, and a roll of \textbf{blue} gummy candy inside.
Along the bottom, bold white words and arrows read “ PULL, ” “ PRESS, ” and “ PUSH. ” A glowing bunch of \textbf{blue} grapes floats to the right over a lit circular platform.
The hand lifts or pulls a \textbf{yellow} tab at the top, matching the highlighted “ PULL ” instruction.
The display then emphasizes “ PRESS, ” and the \textbf{yellow} top is pushed down.
Next, the “ PUSH ” arrow lights up as a \textbf{blue} strip of gummy candy slides out from the side of the dispenser, stretching toward the glowing grape icon.
The product sits on the grass with the \textbf{blue} gummy strip extended, while the word “ PERFECT! ” pops up in large orange letters at the bottom.
The dispenser rotates slightly, showing the \textbf{yellow} top, turquoise body, and front label as the strip waves out.
A hand then holds the dispenser steady with the \textbf{blue} gummy strip protruding.
Another hand grips the end of the strip.
Large orange words appear at the bottom : first “ \textbf{TEAR}, ” then “ \textbf{TEAR} IT OFF. ” The second hand pulls away a bite-sized piece, and small \textbf{yellow} star graphics burst around the dispenser to show the action is completed.
Back in the cartoon park, the two children eat pieces of the gummy strip.
The girl holds a turquoise dispenser in one hand and brings a piece to her mouth with the other.
The boy holds a yellow-and-turquoise dispenser near his waist and lifts a piece to his open mouth.
Both chew and react with pleased expressions.
Big orange text reading “ YUMMY GUMMY ” fills the lower center of the screen, surrounded by glowing \textbf{yellow} stars.
The children glance toward each other, then forward, still holding the candy.
The turquoise Push Pop Gummy Roll dispenser appears alone on a \textbf{blue} background patterned with faint \textbf{blue} fruit silhouettes.
The product spins to show its rounded roll shape, \textbf{yellow} top, front label, and the \textbf{blue} gummy strip extending from one side.
The word “ PERFECT! ” remains in bold orange letters along the bottom.
The final product display appears on a pink background decorated with soft fruit illustrations such as strawberries, watermelon slices, and berry shapes.
Multiple Push Pop Gummy Roll packages in bright colors—blue, \textbf{red}, turquoise, and pink—fan out beneath the green-and-yellow Push Pop Gummy Roll logo. \textbf{Yellow} star graphics sparkle around the packages.
At the bottom, large white text gives the website : “ PUSHPOPGUMMYROLL.COM. ”

% matched lemmas: blue, green, red, tear, yellow
\end{textsample}
