\begin{textsample}{NEG Dim 7 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_26.txt}  \label{ex:f7_neg_005}
The commercial opens in a large industrial indoor space resembling a hangar or vehicle display hall, with high arched \textbf{ceiling} beams, bright \textbf{overhead} lights, and multiple Chevrolet vehicles arranged on the floor and on elevated platforms.
A blue Chevrolet Camaro is foregrounded from the rear/side, with a red pickup and another car visible nearby.
Several adults stand around the vehicles as if examining or discussing them.
The scene cuts to a white sedan parked side-on in the same large space.
A red pickup and a dark vehicle sit behind it.
Several adults stand around the sedan, looking at it.
A white title card appears with centered black text : “ Real people.
Not actors. ” The commercial \textbf{then} shows a rapid sequence of people interacting with different Chevrolet vehicles : - Inside a car, two women sit in the front seats.
One blonde woman in a gray top smiles while looking toward the other person. - A man in a light blue shirt sits in the driver ’s seat of a vehicle, smiling with one hand on the steering wheel.
The vehicle interior is dark with leather-looking seats. - A group of young adults stands beside a red pickup truck marked “ 4x4 ” on the rear side panel. - The same group looks into the open bed of the red pickup, leaning or standing near the tailgate area. - A woman in a red sleeveless top sits inside a red vehicle, with a man in a dark hat in the driver ’s area and another person standing outside the open door. - From the back seat of another vehicle, two people are visible in the front seats.
The dashboard screen shows colorful app-like icons, and a person in the front passenger seat points toward the screen. - A close-up through a window shows a man seated inside a vehicle, smiling. - Inside a larger vehicle, a woman in a red sleeveless top, a woman in a blue top, and a man in a dark hat sit in different seats, appearing to talk and look around the cabin. - A blue Chevrolet SUV is shown from the front with multiple doors open.
People stand around it, including an older man near the driver-side door. - Two women sit or climb into a vehicle interior ; one wears a blue top and looks downward while the woman in red moves toward the front seat. - A white Chevrolet sedan is shown with doors open and several people standing around it. - More people gather near a vehicle under the structure ’s staircase or upper platform area, leaning in to inspect something. - A red pickup is shown from the rear with several people standing behind it as the tailgate area is open or being examined. - A woman in a green top gestures while speaking with two men beside the front of a blue Camaro. - A man in a white shirt and glasses walks in the same industrial space, with a woman behind him.
The commercial \textbf{then} presents individual vehicle shots with model names in white text near the lower part of the frame : - A white sedan is shown at a front three-quarter angle with the label “ MALIBU. ” - A blue coupe is shown at a front three-quarter angle with the label “ CAMARO. ” - A red pickup truck is shown at a front three-quarter angle with the label “ SILVERADO. ” The setting \textbf{then} changes to a more graphic sales-offer layout.
A black Chevrolet Cruze is displayed on a stylized brown/bronze background.
Large yellow pricing text reads “ \$179 ” with “ PER MONTH ” beneath it.
Other visible text includes “ ULTRA-LOW MILEAGE LEASE EXAMPLE, ” “ 24 MONTHS, ” “ \$2,609, ” and “ 2017 CHEVY CRUZE LT, ” along with smaller fine print and Chevrolet branding.
Near the end, a close-up graphic of the Chevrolet bowtie logo appears, followed by a final white end card.
The final card shows the gold Chevrolet bowtie logo above the text “ CHEVY DRIVES THE MOTOR CITY, ” with “ DRIVES ” emphasized in red.
Below it reads “ METRO DETROIT CHEVY DEALERS, ” and at the bottom : “ ChevyDealer.com. ”

% matched lemmas: ceiling, overhead, then
\end{textsample}
