\begin{textsample}{NEG Dim 7 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_51.txt}  \label{ex:f7_neg_026}
The commercial begins with a close-up of a white tube of **Gold Bond Ultimate Crepe Corrector Age Defense**.
The packaging uses purple and gold accents, with “ NEW ” visible near the top.
It \textbf{then} cuts to a warm outdoor scene at sunset : a blond adult wearing a large backpack looks back while moving through a dry, open landscape.
The light is soft and golden.
Next, an adult with tattoos lies on a bed with two young children.
They are smiling and laughing together in a bright, domestic setting with white bedding.
The sequence shifts to a fitness setting.
A woman with a high ponytail, wearing a black \textbf{athletic} top, holds a dumbbell and appears to be \textbf{exercising} or strength training.
The background suggests an indoor \textbf{gym} or studio.
A close-up follows of two adults sitting closely together.
One person looks ahead while the other leans in smiling ; the scene is softly lit and intimate.
The ad \textbf{then} shows an extreme close-up of a hand touching or stroking light-toned skin near the neck or upper shoulder area.
Blonde hair is visible at the edge of the frame, emphasizing skin texture and touch.
Another lifestyle image appears : an adult with very short light hair and a young child lie on green grass, smiling and embracing.
The camera looks down from above.
A close-up of skin and a hand appears with large pale-yellow text overlaid reading **“JUST.”** The background is sunlit and warm.
The product returns in a centered shot : a tube of **Gold Bond Ultimate Crepe Corrector Age Defense** stands in the foreground, while a blurred figure or body part appears in the background.
The commercial \textbf{then} shows a product lineup on a dark teal surface : multiple Gold Bond products are arranged together, including tubes and a pump bottle.
The packaging is primarily white with purple and gold branding.
The lighting dims, and the product lineup becomes mostly silhouetted against the teal background.
Large gold letters begin to slide or appear over the products.
The final frame shows the products darkened behind a bold, all-caps gold message : **“CHAMPION YOUR SKIN.”** The word “ SKIN ” appears slightly motion-blurred or still resolving in the sampled frame.

% matched lemmas: athletic, exercise, gym, then
\end{textsample}
