\begin{textsample}{NEG Dim 7 – 1980 – Score -6.00 – 1980/tv\_com\_1980\_116.txt}  \label{ex:f7_neg_051}
A sunny rural yard appears, with rolling \textbf{green} fields and a winding country road in the background.
In the foreground, a \textbf{red} pickup truck is parked beside stacks of lumber, sawhorses, and boards, suggesting a home construction or renovation project.
Two children run in from around the truck carrying a long wooden \textbf{plank} together.
One child, with light hair and a plaid shirt, leads at the front ; the other, with a dark bowl haircut, a light shirt, and dark overalls, follows behind holding the same board.
A shaggy white-and-brown dog \textbf{trots} after them.
The children look energetic and excited as they hurry across the grass with the \textbf{plank}.
The scene shifts to the unfinished wooden structure attached to a house.
Open wall framing, exposed studs, a ladder, and diagonal support boards fill the background.
An adult woman with curly blonde hair, wearing a \textbf{red} plaid overshirt over a \textbf{yellow} top and jeans, steps into an open doorway holding a \textbf{yellow} box of Cheerios.
The children approach from below, still near the work area.
She lowers the box onto a board or ledge in front of them, placing it where both children can see it.
The Cheerios box is \textbf{yellow}, with large black “ Cheerios ” lettering and a bowl of cereal pictured on the front.
The woman crouches in the doorway, smiling warmly and gesturing with one hand as the children look up toward her and the cereal.
The dog is partly visible nearby, moving through the worksite area.
A bowl of ring-shaped cereal is shown being poured into a clear glass bowl on a breakfast table.
The cereal falls in a stream from above, piling into the bowl.
Around it are breakfast items : a glass of orange juice, a glass of milk, and, off to the side, toast and fruit.
White on-screen text at the bottom reads, “ Kids ’ Number 1 cereal. ” The cereal pieces tumble and bounce as the bowl fills.
Back at the construction area, the two children lean over a horizontal board with the Cheerios box placed between them.
The adult woman smiles from the doorway behind them.
The shaggy dog is visible to the left, and an adult man in denim passes behind the children inside the unfinished structure.
Both children face forward with open-mouthed, delighted expressions, hands braced on the board as if reacting enthusiastically to the cereal.
The adult man, with short brown hair and a denim jacket over a shirt, is then seen close up inside the framed structure.
He holds a bowl of Cheerios with fruit on top and lifts a spoonful to his mouth.
The adult woman ’s curly hair and \textbf{red} shirt are partly visible at the left edge as she stands near him.
He takes a bite, chews, and looks pleased, holding the bowl close to his chest.
A close view of the Cheerios box highlights the package design.
The upper \textbf{blue} banner reads “ OAT TASTE, ” and a \textbf{red} circle on the \textbf{yellow} box reads, “ ONLY 1 GRAM OF SUGAR PER SERVING. ” The box is angled so the large “ Cheerios ” lettering is partly cut off, but the low-sugar claim is clear.
A light-haired boy in a plaid shirt eats from a bowl beside the Cheerios box.
He raises a spoonful to his mouth, eats, and smiles as he chews.
The \textbf{yellow} box remains visible on the left, with the same \textbf{red} circle about one gram of sugar per serving.
The adult woman appears outdoors in front of the \textbf{green} yard, holding a glass bowl of Cheerios and a spoon.
Her curly blonde hair frames her face, and she smiles directly forward while speaking.
She lifts the spoon slightly as if presenting or commenting on the cereal, then continues holding the bowl close to her body.
A wider view shows the whole family gathered around the work area in the yard.
The unfinished wooden addition stands behind them, attached to a house.
The adult man stands or leans at the left, near the two children, who sit on or near the lumber and hold their bowls.
The dark-haired child in overalls sits in the middle, while the light-haired child in plaid eats beside the man.
The woman sits to the right on a long board, holding her bowl and spoon.
The shaggy dog sits in the foreground near the lumber. \textbf{Everyone} appears relaxed and cheerful, eating Cheerios amid the construction materials.
The product is then displayed prominently outdoors : a large \textbf{yellow} Cheerios box stands on a table with breakfast items around it.
The front of the box reads “ General Mills ” at the top, a \textbf{blue} diagonal banner says “ IMPROVED TOASTED OAT TASTE, ” and the large black brand name “ Cheerios ” dominates the center.
Beneath it, smaller text reads “ TOASTED OAT CEREAL, ” with a pictured bowl full of Cheerios and strawberries.
A \textbf{red} circle on the upper right again reads “ ONLY 1 GRAM OF SUGAR PER SERVING. ” Nearby are a bowl of Cheerios, strawberries, milk, orange juice, and toast, arranged like a breakfast setting against the \textbf{green} yard background.
A plain beige title card fills the screen with large black text reading “ Cheerios, ” and below it, smaller black text reads “ low in sugar. ” The adult woman returns, again holding the glass bowl of Cheerios in front of the unfinished wooden structure.
She smiles and speaks while holding the spoon above the bowl.
Her \textbf{red} plaid overshirt and \textbf{yellow} top are clearly visible.
She then pinches or picks up a piece of cereal with her fingers and brings it to her mouth, eating it with a satisfied expression.
The final title card shows large black “ Cheerios ” text on a beige background.
Smaller black words appear underneath and expand into the phrase “ number one! ” so the full message reads “ Cheerios number one! ” As the words remain on screen, a \textbf{red} wheelbarrow rolls in from the right edge carrying the shaggy dog and a child in overalls, adding a playful family-yard image beside the bold product message.

% matched lemmas: blue, everyone, green, plank, red, trot, yellow
\end{textsample}
