\begin{textsample}{NEG Dim 7 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_50.txt}  \label{ex:f7_neg_049}
A bright \textbf{yellow} screen first displays a box of Glad ForceFlex \textbf{trash} bags, with visible text including “ Tear Resistant, ” “ Less Plastic, ” and the slogan “ Small change.
Big difference. ” The scene then cuts to the open rear of a large cargo plane high above the clouds.
The plane ’s ramp is lowered, exposing the cavernous interior, and a black-and-white bull with a rider moves toward the opening.
Inside the aircraft, a cowboy rides the bull out onto the ramp and into open sky.
He is an adult man with a rugged beard and mustache, wearing a black cowboy hat, plaid shirt, brown vest, \textbf{red} neckerchief, tan pants, and rodeo-style gear.
The bull bucks as they leave the plane, its tail whipping and legs kicking while the cowboy raises one arm for balance.
Far below them are scattered clouds and a faint landscape.
A wider view shows the plane continuing across the sky while the tiny shape of the rider and bull falls away beneath it.
As they tumble through the bright \textbf{blue} sky, the cowboy stays seated on the saddle.
Close views show him bracing himself, holding his hat, and looking strained but determined.
Sunlight flares around him.
In a close-up at his waist, a \textbf{yellow} Butterfinger bar is tucked into his belt or holster area, its \textbf{blue} “ Butterfinger ” lettering visible on the wrapper.
He reaches down, pulls the candy bar free, and holds it up while still riding the bull in midair.
The cowboy brings the Butterfinger to his mouth and takes a bite.
The wrapper is peeled back, revealing the chocolate-covered bar.
Crumbs and bits of filling show around his mouth as he chews, still balanced on the airborne bull.
He looks focused and pleased, holding the candy close while the sky and clouds rush behind him.
A second person appears falling through the sky behind him : a light-skinned woman with windblown blonde hair, glasses, a pale blouse, \textbf{blue} pants, and a harness or parachute pack.
She is spread out in a freefall posture, arms extended, and then points toward the cowboy with one finger, as if scolding him.
The cowboy glances aside while holding the Butterfinger near his mouth, then opens wide and takes another bite anyway.
From a distance, the cowboy and bull continue floating and bucking in the sky while the woman remains behind them, arms outstretched.
The cowboy lifts one arm upward, and a large \textbf{yellow} parachute-like canopy unfurls behind him and the bull.
The canopy catches the air and pulls them rapidly off toward the left, leaving the woman alone against the clouds.
The commercial ends on a solid Butterfinger-yellow background with large \textbf{blue} block letters appearing first as “ BOLDER, ” then expanding to “ BOLDER THAN BOLD. ” Finally, a close-up fills the screen with a Butterfinger candy bar : the \textbf{yellow} wrapper is pulled back on both sides, the \textbf{blue} Butterfinger lettering partly visible, and the smooth chocolate-covered center exposed.

% matched lemmas: blue, red, trash, yellow
\end{textsample}
