\begin{textsample}{NEG Dim 7 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_102.txt}  \label{ex:f7_neg_063}
The commercial opens with a static title/logo card.
It shows the Bell System bell emblem inside a circle, with the words “ BELL SYSTEM ” on the bell and “ Southwestern Bell ” printed below.
After a brief dark/blank greenish frame, the sequence cuts to an office-related close-up : trays or drawers filled with many paper cards or forms arranged in rows.
The image has a green-tinted, archival-film look with black borders at the sides.
The next shot shows a young woman in close-up holding a corded telephone handset to her ear.
She has glasses, long hair pulled back, and is smiling while looking slightly off-camera.
The focus is on her face and the telephone receiver.
The commercial \textbf{then} cuts to an \textbf{overhead} view of a desk.
A hand is writing or marking on a rectangular paper form or chart.
A coiled telephone cord runs along the left side of the frame.
Several pencils or pens and a round desk item, possibly a cup or holder, are visible near the top right.
The framing suggests the person is taking notes or filling out paperwork while using the phone, though no audio or spoken content is visible.
The close-up of the same woman on the telephone returns.
She is still smiling and holding the handset, maintaining the impression of a pleasant telephone interaction.
Another \textbf{overhead} desk shot follows.
The paper form remains on the desk, with writing instruments placed nearby.
The hand is no longer clearly active in this sampled frame, and the telephone cord is still visible along the left edge.
The scene \textbf{then} widens to show the woman seated at an office desk.
She holds the telephone handset to her ear, with the phone base on the desk in front of her.
She smiles toward the camera.
The desk contains office items, including papers and writing tools.
In the background, another woman is working at a desk or cabinet.
Wall charts or posted sheets with rows of numbers and letters are visible behind them, along with filing cabinets or office furniture.
The setting appears to be a workplace or telephone-service office.
The final frame is another closing title card.
It shows the text “ Southwestern Bell ” centered on a plain background, with a small Bell System emblem underneath.

% matched lemmas: overhead, then
\end{textsample}
