\begin{textsample}{NEG Dim 7 – 2000 – Score -5.00 – 2000/tv\_com\_2000\_28.txt}  \label{ex:f7_neg_024}
A large Best Buy store fills the opening view, with a deep \textbf{blue} exterior wall and the familiar \textbf{yellow} price-tag-shaped “ BEST BUY ” sign mounted high above glass entrance doors.
In front of the building, a person in a giant Best Buy tag costume bounces and waves.
The costume is shaped like an oversized \textbf{yellow} price tag with thick black lettering, \textbf{blue} sides, white cartoon gloves, \textbf{yellow} sleeves, dark legs, and light-colored shoes. \textbf{Shoppers} move around the entrance with carts ; one person pushes a \textbf{blue} \textbf{shopping} cart near the doors while the mascot gestures toward the store as if welcoming people inside.
The scene moves into the bright retail floor.
The tag mascot is seen up close, so close that the \textbf{yellow} “ BEST BUY ” lettering fills most of the view.
Around it are tall shelves, product displays, and customers under rows of fluorescent ceiling lights.
As the mascot turns, its \textbf{blue} back and thick padded sides become visible.
The store appears large and busy, with wide aisles, glossy black-and-white flooring, and departments arranged in long rows.
The mascot moves through the store like an enthusiastic host, passing shelves of electronics and music while \textbf{shoppers} browse.
In a wide aisle, the mascot dances down the center of the black-and-white floor.
On the right, several adults stand near displays ; one man in dark clothing raises an arm, and others watch or clap.
The mascot spins from showing its plain \textbf{yellow} back to showing the “ BEST BUY ” tag front again, arms spread wide with white-gloved hands open.
Its legs step wide apart in a jaunty, exaggerated dance while customers on both sides continue \textbf{shopping} or react with smiles.
A product demonstration follows at a camcorder display.
Two Black adult men, one in a dark suit and one in a \textbf{green} shirt, look at a small handheld video camera.
A young woman employee in a \textbf{blue} Best Buy shirt smiles as she helps.
The camcorder ’s flip-out screen and a nearby small monitor show a black-and-white image of the two men grinning at close range, demonstrating that the camera is recording or playing back their faces.
The employee holds or presents the camcorder while the men examine it, and the monitor beside them gives a clear view of the captured image.
In the appliance department, white washing machines or dryers are lined up beneath a visible sign reading “ APPLIANCES. ” A male employee in a \textbf{blue} polo shirt and khaki pants stands with a couple : a man in a dark shirt and gray pants and a woman in a tan outfit carrying a shoulder bag.
The employee opens or lifts part of a front-loading appliance door, showing the couple the machine ’s interior.
They stand close together, facing the product and the employee, in a typical sales consultation.
At a computer counter, a woman employee in a \textbf{blue} shirt speaks with a man in a dark dress shirt and patterned tie.
Several desktop computers and monitors sit on the counter behind them, with \textbf{yellow} Best Buy price cards visible on some screens.
The man gestures toward one of the computers while the employee leans comfortably on the counter, both focused on the display.
The view shifts to long aisles of music or media.
Rows of shelves hold CDs or similar packaged items, and \textbf{blue} signs above sections read “ ROCK \& POP. ” A young adult man in a gray sweater browses the shelves, holding a case and looking down as he checks the selection.
The aisle stretches far into the store, with multiple identical \textbf{blue} category signs and other \textbf{shoppers} partly visible between rows.
A small Best Buy tag sign is mounted at the end of one display.
In another electronics area, a Black male employee in a \textbf{blue} Best Buy polo talks with a woman in a loose \textbf{green} sweater near a large white appliance or electronics unit.
He gestures with one hand while she rests her hand on the counter or product surface, listening.
Behind them, more employees and customers examine rows of microwaves or similar boxed white appliances, and several overhead signs glow above the department.
At a black DVD display, large white letters spelling “ DVD ” appear above a built-in screen.
A man in a light gray shirt and a blonde woman in a dark jacket stand close to the display, discussing it.
The man holds a disc or small item in his hand while the woman leans in to look.
The screen shows a view of the store, including a glimpse of the blue-shirted staff and the Best Buy tag mascot.
As they watch, the \textbf{yellow} tag mascot appears in the display area, creating a playful visual connection between the product demonstration and the store mascot.
A bold yellow-and-black car audio display appears next.
The foreground is dominated by the glossy hood or body of a bright \textbf{yellow} vehicle with black racing stripes.
In the background, the Best Buy tag mascot stands upright near the display while customers and employees talk along a wall of car audio components.
A man leans into the open vehicle area, smiling and reaching forward as if testing or exploring the car stereo setup.
The mascot remains nearby, its \textbf{yellow} tag front visible behind him.
A young woman wearing large over-ear headphones smiles brightly while holding a CD jewel case against one side of her head.
She has dark hair pulled back with a headband, \textbf{red} lipstick, and a casual light-colored top.
She presses the headphones with both hands, tilting her head and smiling as if enjoying what she is sampling.
Store shelves blur behind her, suggesting she is in the music department.
Another couple examines a satellite or home entertainment display.
A middle-aged man in a \textbf{red} plaid shirt and jeans stands beside a woman in a light sweater.
They face a large white satellite dish mounted on a display.
The man gestures with one hand toward the equipment while the woman looks on.
A partial sign nearby reads “ NEED, ” though the rest is obscured.
A \textbf{yellow} Best Buy \textbf{shopping} basket then passes very close in the foreground, briefly blocking most of the view with its perforated plastic sides.
At the checkout or service counter, a Black female employee in a \textbf{blue} Best Buy shirt smiles while holding a small handheld scanner or device.
A male customer in a lavender shirt stands beside a \textbf{yellow} Best Buy \textbf{shopping} basket and looks down at an item or receipt in his hands.
The counter area has black-and-yellow signage and product displays behind them.
The employee and customer appear relaxed and friendly as they complete the transaction.
From above, a large circular \textbf{yellow} floor area is visible like a bright spotlight or central store feature.
Several \textbf{shoppers} and employees move around it, and the Best Buy tag mascot stands or moves along the left edge of the circle.
People cross the \textbf{yellow} area in different directions, some carrying items or baskets, while the mascot ’s \textbf{blue} side and \textbf{yellow} tag face are visible from overhead.
The scene emphasizes the busy store environment, with the mascot weaving among customers.
The commercial ends back outside the store.
The \textbf{yellow} “ BEST BUY ” sign is mounted high on the \textbf{blue} facade above the glass entrance.
Large white on-screen text appears at the lower right reading “ Now Open. ” The glass doors and windows below reflect the store entrance area, and a small copyright notice, “ {\EmojiFont ©} 2000 Best Buy, ” appears near the lower left.
The final image holds on the storefront, the big tag logo, and the “ Now Open ” message.

% matched lemmas: blue, green, red, shopper, shopping, yellow
\end{textsample}
