\begin{textsample}{NEG Dim 7 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_111.txt}  \label{ex:f7_neg_048}
Two upright kitchen sponges stand on a glossy white counter like little racers : a \textbf{blue} sponge on the left and a \textbf{yellow} sponge on the right.
Stacks of white plates sit in the background, and the surface reflects the sponges.
As the scene opens up, a translucent \textbf{blue} bottle of Dawn dish soap appears beside the \textbf{blue} sponge, while a tall \textbf{yellow} bottle labeled “ Dish Liquid ” stands beside the \textbf{yellow} sponge.
The \textbf{yellow} bottle has a \textbf{blue} label with \textbf{red} “ DISH LIQUID ” lettering and a lemon image.
The kitchen setting becomes clearer : a deep white sink filled with blue-tinted water stretches across the foreground, with bits and spots of greasy residue floating on the surface, dark \textbf{blue} tile along the back wall, stacks of dishes on both sides, and a tall silver faucet to the right.
The sponges wiggle and bend as if preparing for a race.
The \textbf{blue} sponge is paired with the Dawn bottle on the left ; the \textbf{yellow} sponge is paired with the generic-looking dish liquid on the right.
Both face the water-filled sink, with their reflections visible in the glossy counter and water below.
The sink looks almost like a miniature swimming pool, with scattered yellow-brown grease spots on and under the water ’s surface.
A more controlled demonstration follows.
Two light-skinned hands hold small rectangular pieces of sponge over two long, narrow grey lanes on a white surface.
The \textbf{blue} sponge piece is placed on the left lane in front of the Dawn bottle, and the \textbf{yellow} sponge piece is placed on the right lane in front of the \textbf{yellow} “ Dish Liquid ” bottle.
Both lanes show streaks and patches of orange-brown grease.
Very small white fine print appears along the bottom, describing test conditions, though it is difficult to read fully.
The hands lower the sponges onto the greasy lanes, then lift away, leaving the two sponge pieces upright at the start of their tracks.
The scene shifts back to the sink.
The \textbf{blue} and \textbf{yellow} sponges leap into the \textbf{blue} water, causing splashes and ripples.
The bottles remain standing on the counter behind them, Dawn on the left and the \textbf{yellow} dish liquid on the right.
Water sprays up around the sponges as they tumble and skim across the surface.
The \textbf{yellow} sponge floats and flops near the back and side, while the \textbf{blue} sponge moves more vigorously through the water, churning up foam and splashes.
Seen from the side at water level, both sponges ride low in the water, their porous surfaces dripping.
The \textbf{blue} sponge surfaces near the Dawn bottle, then dips and surges forward again.
The \textbf{yellow} sponge bobs nearby but appears less forceful.
Underwater, the sponges are visible as soft rectangular shapes moving through \textbf{blue} water with trails of bubbles.
The \textbf{blue} sponge dives and rolls, while the \textbf{yellow} sponge hangs farther away, smaller and lower in the scene.
Above the surface, the \textbf{blue} sponge repeatedly breaks through the water, standing up on an edge, then plunging back down with splashes.
The race-like action continues in the sink.
The \textbf{blue} sponge cuts across the water, leaving ripples and bursts of foam behind it.
The \textbf{yellow} sponge appears off to the side and behind.
The Dawn bottle stands close at the left edge of the counter, and the \textbf{yellow} dish liquid bottle is farther back.
The \textbf{blue} sponge rises dramatically near the edge of the sink, upright like a fin, dripping water as it slows near the Dawn bottle, while the \textbf{yellow} sponge floats lower in the background.
The comparison resolves into a product display.
On a bright white counter, the \textbf{blue} Dawn bottle and the \textbf{yellow} “ Dish Liquid ” bottle stand side by side.
A very tall stack of clean white plates stands to the left of Dawn, while a noticeably shorter stack of plates sits to the right of the \textbf{yellow} dish liquid, visually suggesting Dawn cleaned more dishes.
Small white on-screen text near the bottom reads, “ Per drop, while suds last. ” The bottles are centered between the plate stacks in a clean, sunlit kitchen.
The final display shows four Dawn bottles lined up on the counter in different colors : \textbf{yellow}, \textbf{blue}, orange, and \textbf{green}, each with a white cap and the Dawn logo on the front.
A large \textbf{blue} sponge slides across the foreground from left to right like a wipe, covering and revealing parts of the bottles as it passes.
It clears to a mostly white end screen with dark teal text reading “ visit dawn-dish.com ” and the Dawn logo below.
A \textbf{green} Dawn bottle remains partly visible at the far right edge beside the kitchen sink in the background.

% matched lemmas: blue, green, red, yellow
\end{textsample}
