\begin{textsample}{NEG Dim 7 – 1980 – Score -5.00 – 1980/tv\_com\_1980\_9.txt}  \label{ex:f7_neg_053}
A winter outdoor scene opens on a rural metal mailbox in front of a light-colored house, with bare tree branches overhead and patches of snow on the ground.
White on-screen text at the bottom reads “ WINTER HARBOR, MAINE. ” A person wearing a dark coat sleeve and brown leather glove reaches in from the right, pulls open the rounded mailbox door, and reveals a bright \textbf{blue} box of Alka-Seltzer Plus Cold Medicine inside among envelopes.
The gloved hand grasps the box and brings it forward.
In closer views, the package fills much of the picture : it is a \textbf{blue} rectangular carton with \textbf{yellow} and white lettering reading “ Alka-Seltzer Plus Cold Medicine, ” a \textbf{red} banner on the front, and a white fizzy tablet or bubbling graphic near the lower right.
The action continues at another mailbox, a dark one with the name “ PINKHAM ” visible on its side, where the same kind of \textbf{blue} cold medicine box is shown sitting inside with mail, suggesting the product is being delivered or sampled around town.
The scene changes to local residents speaking outdoors in winter clothing.
A woman identified by white text as “ BETTY HANSCOM ” stands near a large pale house.
She appears to be an adult woman with long dark hair, wearing a fluffy white \textbf{knit} hat and a \textbf{blue} winter jacket, facing forward as if answering a question.
Then an adult man identified as “ DALE TORREY ” appears outside by a dark wooden building and exterior steps.
He has a short beard, wears a black \textbf{knit} cap and a dark puffy jacket, and looks toward the viewer while speaking.
A group of townspeople then stands together by a harbor or waterfront, with water, shoreline buildings, and houses in the background.
They are bundled in winter coats, scarves, gloves, and \textbf{knit} hats, and many hold the same \textbf{blue} Alka-Seltzer Plus Cold Medicine boxes upright at chest level so the front labels face outward.
The group includes adults of varied ages and appearances : a woman in a white hat and brown coat with a light scarf, a person in a red-orange \textbf{knit} cap and \textbf{navy} puffer jacket, a man in a tan coat and dark cap, a woman in a salmon-colored coat with a \textbf{red} cap and \textbf{blue} scarf, a bearded man in a black hat and dark jacket, and others in \textbf{blue}, orange, and patterned winter outerwear.
As more people come into view, the line looks like a broad cross-section of the town, all standing close together and calmly presenting the product.
Small white text appears along the bottom : “ READ AND FOLLOW LABEL DIRECTIONS. ” The commercial then focuses on an older man outdoors in a working waterfront setting, with stacked lobster traps or wooden fishing gear behind him.
He wears a tan cap, a \textbf{green} coat, and a scarf, and he looks slightly downward and then forward while speaking.
The final image becomes a product display against a dark background : a \textbf{blue} Alka-Seltzer Plus Cold Medicine box stands on a white tabletop beside a clear glass filled with water and a cloud of fizzing white bubbles.
Two small \textbf{blue} packets lie in front of the glass.
Large bold white text appears above the display reading “ FOR TOUGH WINTER COLDS. ”

% matched lemmas: blue, green, knit, navy, red, yellow
\end{textsample}
