\begin{textsample}{NEG Dim 7 – 1960 – Score 2.00 – 1960/tv\_com\_1960\_59.txt}  \label{ex:f7_neg_080}
A young blonde flight attendant in a bright orange United uniform and matching pillbox-style cap fills the screen.
She wears white gloves and holds a pale balloon close to her mouth, inflating it.
As she lowers it, a round white button pinned to her orange uniform comes into view with decorative \textbf{blue} lettering that reads “ Come fly with me... ” She smiles broadly, her bobbed hair visible beneath the cap, then the image shifts to other United staff and travel scenes.
A uniformed man in a dark suit and cap stands beside large route maps or planning charts, pointing across them as if discussing destinations.
Outside near a United aircraft tail, a male ground crew member in a light \textbf{blue} shirt, cap, and large ear protectors raises both hands in guiding gestures, with “ UNITED ” visible on the plane behind him.
The “ Come fly with me... ” button appears again, now on a white uniform, followed by another smiling female attendant in a white cap and dark-and-white uniform.
She faces slightly to the side, smiling and appearing to sing or speak, with the round campaign button pinned prominently on her chest.
A \textbf{red} version of the button with white lettering is shown on another dark uniform.
The setting then opens to travel imagery : the Statue of Liberty is seen from above with New York Harbor behind it ; a flight attendant stands framed in the open doorway of a United airplane holding a white balloon ; and a close-up shows the orange-uniformed attendant smiling warmly.
A large circular sign with the “ Come fly with me... ” script hangs in an airport-like interior.
Then two water skiers skim across a lake, leaning back on tow ropes with spray rising around their skis.
The travel montage continues through a variety of vacation scenes.
A dark-haired man in a suit appears indoors, followed by passengers seated inside an airplane, including a young woman by a window and a man behind her.
Two people ride horses along a grassy ridge with \textbf{blue} mountains in the distance.
A man in white tennis clothes swings a racket on an outdoor court bordered by glass and dark fencing.
A blonde woman in a \textbf{yellow} top and white skirt swings a golf club while a man stands nearby watching among trees and palms.
Inside an airplane galley, a young female flight attendant with short dark hair and a United scarf pours or serves from a silver coffee pot, then brings a tray with cups to seated passengers, including an older man who smiles and reaches toward it.
Outdoors again, an older couple walks between rocky cliffs ; another couple sits back-to-back in a small \textbf{blue} boat on calm water ; and a lone kayaker in dark clothing paddles through churning whitewater rapids.
The Golden Gate Bridge stretches across \textbf{blue} water in another destination view.
Families and leisure travel appear as well.
In an airplane cabin, a man in glasses sits by the window holding a cup, while a child nearby holds an orange “ Come fly with me... ” balloon ; another passenger leans over to point out the window.
A family rides in an open-top car, with children in the back holding \textbf{red}, \textbf{blue}, and white balloons.
A castle-like entrance, resembling a theme-park castle, stands against a bright \textbf{blue} sky as an old-fashioned car passes in front.
In another interior, a family group is silhouetted near tall columns, then the Lincoln Memorial statue is seen from below, seated high on its pedestal.
Throughout these scenes, round buttons and balloons repeat the “ Come fly with me... ” lettering, tying the travelers and United staff together visually.
The final portion returns to United employees and slogan graphics.
A white button with \textbf{blue} script reading “ Come fly with me... ” fills the screen, then dissolves into a smiling female attendant in a white cap.
A young man in a dark suit stands beside \textbf{red} and \textbf{blue} balloons and reaches toward them.
A male United employee in a light \textbf{blue} shirt and cap, wearing a tie and a round button, smiles in a modern terminal-like space.
Three female flight attendants walk together down a bright corridor, each in a neat 1960s uniform and cap, carrying balloons in \textbf{red}, \textbf{blue}, and white ; one wears white with dark trim, one wears dark with white trim, and one wears orange with white trim.
Large words then appear one at a time across soft, colorful backgrounds : “ Come, ” then a stylized “ fly, ” then “ with, ” then “ me... ” The phrase resolves into the United slogan “ fly the friendly skies of United ” in large white decorative lettering.
Behind the final slogan, a United jet climbs through a \textbf{blue} sky, angled upward, with its wing and engines visible as the aircraft continues into the clouds.

% matched lemmas: blue, red, yellow
\end{textsample}
