\begin{textsample}{NEG Dim 7 – 2020 – Score -4.00 – 2020/tv\_com\_2020\_49.txt}  \label{ex:f7_neg_007}
A sunny \textbf{green} park fills the opening view, with bright grass, leafy trees, and a path in the background.
From the left, a hand lifts a small \textbf{red} candy cup into the foreground.
The cup has a \textbf{yellow} lid and a bold black-and-yellow “ Juicy Drop ” logo on the front, with the product name “ Gummy Dip ’ N Stix ” and an image of a gummy stick being dipped.
The \textbf{yellow} lid flips open, revealing pinkish-red gummy sticks arranged upright around the rim and a round center well filled with \textbf{red} gel.
The opened lid stays hinged behind the cup like a little dish-shaped flap, while the hand holds the package steady against the park background.
A second hand reaches in from above and begins using the candy.
The visuals repeat the action in three side-by-side panels : a long \textbf{red} gummy stick is held vertically, dipped into the \textbf{red} center gel, lifted out, and dipped again.
Each panel shows a slightly different moment of the same dipping motion, emphasizing the gummy stick going down into the sour gel and coming back up.
The setting changes to an indoor study area.
A \textbf{blue} version of the Juicy Drop Gummy Dip ’ N Stix cup is held in front of a desk with stacked books, a \textbf{blue} desk lamp, pencils, and a pale wall.
Its \textbf{yellow} lid is open, and turquoise-blue gummy sticks circle a matching \textbf{blue} center gel.
Again, the action appears in three vertical panels : a hand dips a \textbf{blue} gummy stick into the center well, lifts it, and dips it from different angles.
The hand holding the cup remains steady at the bottom while the other hand controls the candy stick.
The scene then shifts to a skate park.
A purple version of the candy cup is held near the edge of a concrete bowl, with a skateboard visible in the background.
The \textbf{yellow} lid is open, and \textbf{red} gummy sticks sit around a purple-toned center well.
A hand dips a \textbf{red} gummy stick straight down into the gel.
A young boy, likely a preteen, appears wearing a black skate helmet with a chin strap and a gray long-sleeve shirt.
He brings the \textbf{red} gummy stick to his mouth, eats it, and looks forward with a satisfied, calm expression.
Behind him, other \textbf{kids} and bikes are visible around the skate park, with hills and trees in the distance.
The commercial ends on a bright \textbf{yellow} product display.
On the left, large text reads “ NEW JUICY DROP GUMMY DIP ’ N STIX, ” with smaller text underneath : “ CHEWY STICKS AND SOUR GEL ” and “ JUICYDROP.COM. ” To the right are several product cups in different colors, including \textbf{red}, purple, \textbf{blue}, and pink, with one \textbf{red} cup open and a \textbf{red} gummy stick standing upright in the center gel.
At the top right, a small label reads “ New at DOLLAR GENERAL. ”

% matched lemmas: blue, green, kid, red, yellow
\end{textsample}
