\begin{textsample}{NEG Dim 7 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_31.txt}  \label{ex:f7_neg_020}
The commercial opens from inside a vehicle looking out through a windshield with several thin, pale cracks spreading across the glass.
Beyond the damaged windshield, two adult men stand outdoors in a sunny suburban driveway or yard, with \textbf{green} trees behind them.
The man on the left has short light-brown hair and a trimmed beard, and wears a beige sweater.
The man on the right has neatly combed dark hair and wears a brown jacket over a dark \textbf{blue} button-up shirt.
Both lean forward toward the cracked glass, studying the damage with concerned, sympathetic expressions.
A large white “ Safelite ” logo appears centered over the cracked windshield, with tiny text near the bottom reading “ Simulated. ” The dark-haired man is then seen closer, standing in front of a house and lawn.
He looks down as if considering an option, then raises his gaze with a small smile.
A hand holds up a smartphone showing the Safelite website.
The screen has the \textbf{red} Safelite name at the top, a photo of a \textbf{red} Safelite van, and large text reading, “ Get it fixed any way you want, ” with a \textbf{blue} button below that says, “ Let ’s get started. ” A finger taps the phone screen.
A bright \textbf{red} Safelite van drives through a city street lined with modern buildings and trees.
The back doors carry large white lettering : “ Get it fixed any way you want, ” with “ safelite.com ” below.
The van is then seen from the side with a huge white “ Safelite ” logo along the panel and smaller text near the front reading “ Mobile Glass Shop. ” Inside, a smiling male technician in a black uniform shirt with \textbf{red} side panels drives the van.
The scene shifts to a barbershop.
The two men sit inside in barber chairs, visible through the storefront window, with a barber standing behind the dark-haired man.
Outside, a \textbf{red} Safelite van is parked at the curb, and a Safelite technician works on the windshield of a dark vehicle in the foreground.
He wears a black-and-red Safelite uniform, \textbf{blue} gloves, and safety glasses, and handles a small windshield repair device attached to the glass.
Fine print along the bottom notes that mobile service may not be available in all locations.
Next, the same technician works in a more open outdoor setting near water and trees, smiling as he steadies repair equipment on a vehicle windshield with the \textbf{red} Safelite van parked beside him.
The two men appear nearby holding fishing rods ; the bearded man wears a greenish long-sleeve shirt, and the dark-haired man wears a \textbf{blue} jacket.
A gray vehicle and the \textbf{red} Safelite van sit behind them, making the service look as if it is happening while they fish.
The commercial then moves to a home driveway.
A gray SUV is parked facing forward, surrounded by calibration equipment : black tripods, horizontal bars, and a rectangular target board mounted in front of the windshield.
A Safelite technician stands to one side adjusting the setup.
The driveway is bordered by a house, garage, hedges, and a wooden fence, under a clear \textbf{blue} sky.
The dark-haired man now stands casually in the foreground wearing a \textbf{navy} robe or cardigan over a white shirt, holding a light-colored mug.
He raises the mug and takes a sip while the technician continues working in the background.
The bearded man appears on the other side of a wooden fence, visible from the shoulders up, looking over toward him as if reacting to the home-service setup.
A close view of the technician ’s tablet shows the Safelite name on the \textbf{red} case and a \textbf{green} check mark on the screen.
The words update to “ Recalibration Complete, ” confirming the vehicle ’s safety-feature calibration has finished.
The technician then stands smiling in front of a \textbf{red} Safelite van and waves.
The two men are next on a \textbf{green} golf course, each holding a golf club.
The bearded man wears a dark long-sleeve top and light pants, while the dark-haired man wears a \textbf{blue} sweater and light pants.
Both smile toward someone off to the side, with a \textbf{red} flag and scattered golf balls on the grass behind them.
The commercial ends with a \textbf{red} Safelite van driving down a quiet residential street at dusk, trees and houses on both sides and a pinkish sky overhead.
Large white branding fills the center of the screen : “ Safelite. ” Beneath it, the tagline reads, “ Your glass.
Your way. ” A smaller line below says, “ Schedule at safelite.com, ” while the van continues away down the road.

% matched lemmas: blue, green, navy, red
\end{textsample}
