\begin{textsample}{NEG Dim 7 – 1950 – Score 2.00 – 1950/tv\_com\_1950\_28.txt}  \label{ex:f7_neg_079}
The commercial is shown in black and white and the sampled frames suggest a shift from a dark introductory scene to a domestic product-use scene and \textbf{then} to a product/title card. 1. **Opening frame, 0.000s** The image is very dark and soft-focused.
A human figure appears close to the camera, possibly lying down or leaning over, with a head and shoulder area visible.
The surrounding shapes suggest bedding or fabric, but the details are unclear due to the low contrast and blur.
No readable text is visible. 2. **Middle frame, 33.990s** The scene changes to a bright domestic interior, likely a kitchen or laundry/work area.
A young boy stands at a counter in front of a patterned tile wall.
He is shown in profile, wearing a short-sleeved striped shirt.
On the counter are several small objects, including a plate or shallow dish and dark rectangular or cylindrical items.
The boy appears to be reaching toward or handling one of the objects on the counter. 3. **Final frame, 57.048s** The commercial ends on a graphic/product display.
Large text on the left reads **“BLUE MAGIC”**, with a lower line that appears to read **“WHITING CLEANER”** or similar, though it is partly blurred.
On the right is a tilted product box with the clearly visible brand name **“cheer”** in large letters.
A stream or splash-like white graphic extends downward from the package, emphasizing the cleaning/whitening effect visually.

% matched lemmas: then
\end{textsample}
