\begin{textsample}{NEG Dim 7 – 1970 – Score -2.00 – 1970/tv\_com\_1970\_84.txt}  \label{ex:f7_neg_070}
A woman stands in a home kitchen beside an open oven.
She appears middle-aged, with short dark hair, and wears a teal-blue dress or blouse under a pale \textbf{blue} patterned apron, plus bright turquoise rubber gloves.
The oven door is open to her right, showing a dark interior ; a small \textbf{yellow} sponge and a cloth lie near the oven.
The kitchen has patterned wallpaper, a wooden stool on the left, and a window behind her looking out toward a white picket fence and houses with \textbf{red} roofs.
She stands with hands on hips, then leans back and lifts her gloved hands in a weary, exasperated gesture, as if reacting to the messy oven.
Behind her, faces begin appearing at the kitchen window.
Three younger adult women lean in from outside, smiling and animated.
Each holds up a bright \textbf{green} aerosol can of Mr.
Muscle Oven Cleaner.
One has short reddish hair and a beige top, another has lighter hair and a pink jacket, and another has brown hair with a light blouse and darker vest.
They crowd together in the window frame, presenting the cans toward the woman inside.
The woman in the apron turns toward them, surprised and doubtful at first, then gestures back and forth between them and the oven.
The women outside keep the cans raised, their labels facing forward, while the woman inside softens into a smile and opens her hands in a “ why not? ” kind of gesture.
The picture then fills with a close view of the product label on a vivid \textbf{green} background.
Large \textbf{red} letters outlined in black read “ Mr.
Muscle, ” with “ Oven Cleaner ” underneath in black.
A \textbf{yellow} burst at the top says “ NEW. ” As the label is shown lower down, a round badge becomes visible.
It reads “ Fast \textbf{Daytime} ” with “ Cleans in minutes ” beneath it, and below that, in a black section, “ Easy Overnight ” and “ Self-Scours. ” The packaging emphasizes that the same oven cleaner is for both quick \textbf{daytime} cleaning and overnight use.
A demonstration follows inside an oven.
The pale oven surface is marked with dark baked-on stains, and small white on-screen text at the top reads “ Minutes later. ” A turquoise-gloved hand uses a \textbf{yellow} sponge or cloth to wipe across a brown spot.
White text on the oven surface labels the stain “ cheese. ” As the hand moves steadily across it, the dirty patch disappears under the wipe, leaving a cleaner pale area behind.
Another close view shows the gloved hand wiping along a grimy oven ledge or side area labeled “ fat. ” The \textbf{yellow} sponge moves along the strip, clearing away dark grease marks and revealing a cleaner surface.
A third stained area on the oven floor is labeled “ pie, ” again with “ Minutes later ” above ; the gloved hand wipes over the brown patch, and the stain gives way to a smooth, clean-looking section.
The woman in the apron returns in close-up, now holding the bright \textbf{green} Mr.
Muscle can upright beside her face.
The other women remain partly visible behind her at the window, clustered in the background.
She points with one gloved finger to the round label on the can, drawing attention to the “ Fast \textbf{Daytime} ” and “ Easy Overnight ” claims.
Her expression shifts from confident explanation to a broad, pleased smile as she presents the product directly forward, ending with the can clearly displayed in the foreground.

% matched lemmas: blue, daytime, green, red, yellow
\end{textsample}
