\begin{textsample}{NEG Dim 7 – 2010 – Score -5.00 – 2010/tv\_com\_2010\_118.txt}  \label{ex:f7_neg_043}
A person is shown from the waist down inside a home, wearing dark trousers, black shoes, and a light \textbf{blue} shirt.
On a carpeted staircase, they pull a large, overstuffed white \textbf{trash} bag by its \textbf{red} drawstring.
The bag is stretched into a heavy teardrop shape and bumps awkwardly down the steps, sagging and dragging over the carpet as the person steps carefully around it.
The scene shifts outdoors to the edge of a hot tub.
A person ’s feet in flip-flops stand on the rim beside rippling water, with a \textbf{blue} plastic cup nearby.
The same kind of white \textbf{trash} bag is pulled along the hot tub edge by its \textbf{red} drawstring.
Small white fine print appears along the bottom of the screen, giving data-source information.
The bag ’s top bunches tightly as it is dragged, suggesting strain on the thin \textbf{red} ties.
Back inside, another close view follows a white \textbf{trash} bag being dragged low along a floor near white cabinets and a dark piece of furniture.
The \textbf{red} drawstring is taut above the bag.
In a nursery-like room, with a white crib in the background and a \textbf{blue} blanket or towel draped over it, a hand grips the \textbf{red} drawstring.
The string stretches upward while the bag ’s gathered top pulls tight, then the \textbf{red} tie appears to slip or pull loose from the bag.
A person wearing \textbf{blue} plaid pajama pants stands near a doorway with the heavy white bag at their feet.
They hold the \textbf{red} drawstring in one hand, but the bag remains slumped on the floor, its top crumpled, as if the handle has failed and separated from the weight of the \textbf{trash}.
Outside at what looks like a backyard party, colorful balloons in \textbf{yellow}, pink, and \textbf{green} decorate a garden path, and a table with a pale pink tablecloth sits in the background.
A person in dark pants carries another full white \textbf{trash} bag by its long \textbf{red} drawstrings.
The bag swings low, then drops down out of their grip, landing near their leg while the loose \textbf{red} ties dangle above it.
The hand lowers toward the fallen bag, emphasizing that the drawstrings have not held the load.
The comparison changes to a garage setting.
A person on the right, visible from the torso down in a pink striped shirt, holds a white \textbf{trash} bag by a \textbf{red} drawstring.
Behind them, an open garage contains a \textbf{blue} SUV and shelves filled with storage boxes and household items.
In the foreground is a large gray outdoor \textbf{trash} bin.
This bag has a bold \textbf{red} “ GLAD ” logo printed on its side.
It hangs full and rounded but intact as the person lifts it over the bin.
The bag is lowered smoothly into the \textbf{trash} bin, and the person ’s hand releases the \textbf{red} drawstring without the bag \textbf{tearing} or dropping unexpectedly.
The commercial ends on a bright \textbf{yellow} product display.
A box of Glad Tall Kitchen Drawstring Bags floats against the \textbf{yellow} background, showing the \textbf{red} “ GLAD ” logo and an image of a white drawstring \textbf{trash} bag in a \textbf{trash} can.
Below the box, large \textbf{red} text reads, “ Strength that saves. ”

% matched lemmas: blue, green, red, tear, trash, yellow
\end{textsample}
