\begin{textsample}{NEG Dim 7 – 1990 – Score -5.00 – 1990/tv\_com\_1990\_51.txt}  \label{ex:f7_neg_032}
At night, a large two-story house sits behind a wide snow-covered front yard.
Warm \textbf{yellow} light glows from several windows, and a Christmas tree covered in orange-gold lights stands near the walkway on the right.
In the lower part of the snowy yard, a bundled adult in a dark hat, dark pants, gloves, and a deep \textbf{red} winter coat walks across the snow with a medium-sized brown dog \textbf{trotting} close by.
A small Hallmark crown-and-script logo appears near the bottom right over the scene.
The adult moves farther into the yard, then is seen closer, slightly hunched forward with arms out for balance, as if slipping or playfully sliding on the icy snow.
The house lights blur warmly behind them.
They spread both arms wide and plant their feet apart in the snow while the dog watches nearby.
Then the adult drops onto their back in the snow, lying flat with arms stretched out and legs extended.
They sweep their arms and legs outward and inward, making a snow angel.
The \textbf{red} coat stands out vividly against the blue-white snow, and the person ’s face is relaxed and playful as they look upward.
The image shifts indoors to a tabletop covered with a lace cloth.
A shiny silver picture frame holds a photo of two girls or young women close together, one with an arm around the other ; they appear to be smiling or laughing in a casual snapshot.
In front of the frame lies a white greeting card with a \textbf{red} envelope underneath.
As the view settles on the card, handwritten-style text across the top becomes readable : “ you ’re a Special Friend. ” Below the words is a small bordered winter illustration with evergreen trees, snow, and tiny figures in a snowy landscape.
More greeting cards are spread across the lace-covered table.
A \textbf{green} card partly visible reads “ What Is a Husband? ” with smaller text beneath that appears to describe it as a loving definition for wives.
Beside it is an ornate purple and multicolored card with a \textbf{red} center panel and elegant white script reading, “ With Thoughts of You, Grandmother. ” To the right, a smaller purple card says “ For My Teacher ” above a cheerful \textbf{yellow} cat-like cartoon face.
A bright \textbf{blue} envelope or card lies partly over the grandmother card, and a pink glass object and other small decorative items sit around the arrangement.
The display gives the impression of a selection of cards for different important people.
The scene returns outside to the snowy front yard.
The adult now stands near the freshly made snow angel, with the brown dog beside them.
The lit Christmas tree and the warmly lit house remain in the background.
Large white on-screen text fades in over the snow : “ There ’s no place like Hallmark. ” The image then blends into the tabletop again, where a Hallmark \textbf{shopping} bag lies prominently among the cards.
The bag has a \textbf{red} band at the top, a crown above the \textbf{red} Hallmark script logo, and pale starburst patterns across it.
The same white text, “ There ’s no place like Hallmark, ” remains across the lower part of the screen as the Hallmark bag and surrounding cards fill the final image.

% matched lemmas: blue, green, red, shopping, trot, yellow
\end{textsample}
