\begin{textsample}{NEG Dim 7 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_93.txt}  \label{ex:f7_neg_003}
The commercial opens in a dark, high-contrast setting with \textbf{athletic} imagery.
A male athlete is shown falling or twisting through a space filled with many small white particles, resembling snow, dust, or spray.
The background is almost black, and the body is lit dramatically from the side.
The next shots continue the physical-performance motif.
A close-up shows the top of an athlete ’s head and shoulders as he leans forward, apparently preparing for exertion.
This is followed by a close-up of a foot in a bright yellow running shoe pressing into a starting block, with vapor or smoke billowing behind it.
The imagery suggests speed and launch, though no race is fully shown in the sampled frames.
The commercial \textbf{then} cuts to a blue Lexus car driving at night.
The front of the car is seen with headlights on, moving through a dark, controlled driving environment.
The setting appears to be a track or enclosed road bordered by white or light-colored walls.
Motion blur and streaks of red and white light emphasize speed.
A brief abstract close-up shows a vertical pale surface, possibly a wall or pillar, followed by a nearly black frame where only two narrow headlight-like shapes and a low horizontal line are visible.
The car is \textbf{then} shown in close-up at wheel level, with mist, smoke, or tire spray around the tire area.
The blue car continues around the track at night.
Wide shots show it moving along a curved roadway under bright \textbf{overhead} lights.
Small white disclaimer text appears near the bottom in some driving shots ; it is partially readable as a professional-driver/closed-course \textbf{warning}, but not all of the text is clear in the frames.
The camera shifts between exterior angles : rear three-quarter views, side tracking shots, and close-ups of the car ’s body and wheels.
The blue car is shown cornering with illuminated red tail lights.
A silver or gray Lexus sedan \textbf{then} appears in side view, also driving along the same night track environment.
The styling details include sharp headlights, a prominent front grille, and angular tail light shapes.
One shot moves inside the car, showing the driver ’s viewpoint through the windshield on the track.
The dashboard, steering wheel, central screen, and control panel are visible, but the driver is mostly in shadow.
More small legal/disclaimer text appears along the bottom and is difficult to read fully.
The commercial \textbf{then} presents three Lexus IS vehicles parked side by side in a studio-like dark space under a spotlight : a blue car on the left, a white car in the center, and a gray car on the right.
Text beneath them identifies the models and horsepower.
The visible labels appear to read : “ IS 200t ” with “ 241 HP, ” “ IS 350 ” with “ 306 HP, ” and “ IS 300 AWD ” with “ 255 HP. ” A sales-offer screen follows with a gray Lexus IS shown in profile/front three-quarter view against a black background.
Large white text above the car advertises lease offers.
The readable portions include “ THE 2016 IS 200t LEASE ” with “ \$349 / 36 ” and “ \$1,999, ” and “ THE 2016 IS 300 AWD LEASE ” with “ \$369 / 36 ” and “ \$1,999. ” Fine-print legal text appears along the bottom but is too small to read clearly in the sampled frame.
The commercial ends on a black background with the Lexus emblem and the word “ LEXUS ” in white.
In the final frame, the tagline appears below as “ THE PURSUIT OF PE … ” ; the remaining letters are partially cut off or not fully legible in the sampled frame.
A hashtag “ \#LexusIS ” appears near the bottom.

% matched lemmas: athletic, overhead, then, warning
\end{textsample}
