\begin{textsample}{NEG Dim 7 – 1980 – Score -4.00 – 1980/tv\_com\_1980\_29.txt}  \label{ex:f7_neg_056}
The commercial begins in a dim, gray studio-like setting.
A little girl, preschool age, with dark hair in pigtails tied with pale bows, stands facing forward in a pale pink dress with puffed sleeves.
A bright orange stain is smeared down the front of her dress, centered on her chest.
She looks down at the mess, then raises a white cloth or small towel onto the top of her head, her expression subdued and slightly sheepish.
The stained dress is then shown by itself, clean and neatly hanging from a light \textbf{blue} plastic hanger.
The pink puff sleeves, lace-trimmed collar, and waist detail are visible, but the orange stain is gone.
A hand steadies the hanger briefly, then withdraws, leaving the spotless dress centered against the soft gray background.
A blonde adult woman appears, wearing a \textbf{green} sweater over a white collar.
She holds a large \textbf{blue} spray bottle upright in both hands, close to her chest, with the white spray nozzle at the top.
The label on the bottle shows the Clorox Prewash branding in \textbf{blue} letters with orange and \textbf{red} chevron stripes.
She looks directly forward with an alert, pleased expression.
On her sleeve is a red-and-orange chevron patch, visually echoing the idea of “ stripes. ” A man in business clothing appears next.
He wears a dark suit jacket, a pale \textbf{blue} dress shirt, and a dark patterned tie.
Looking down, he opens his jacket and touches the front of his shirt near the chest pocket, where a small dark ink-like spot is visible.
The shirt is then seen laid flat on a white surface while two hands smooth the fabric around the button placket and pocket area, as if preparing it for stain treatment or showing the fabric surface.
Another adult woman, with short curly brown hair, appears in a \textbf{yellow} sweater over a collared shirt.
She holds the same \textbf{blue} Clorox Prewash spray bottle angled across her body, then turns it so the label faces outward.
She smiles warmly.
A red-and-orange chevron patch is also visible on her sleeve.
The product label fills the view.
It reads “ CLOROX Prewash ” in large \textbf{blue} letters, with smaller text below : “ LAUNDRY SOIL AND STAIN REMOVER. ” The white central label is bordered by bold orange and \textbf{red} angled stripes, set into the \textbf{blue} plastic bottle.
A demonstration follows on a small light \textbf{blue} garment, likely a child ’s overall or jumper, with shoulder straps and round buttons.
A dark brown stain sits on the front bib area.
The white nozzle of the \textbf{blue} Clorox Prewash bottle is held close to the stain, aimed at it.
After treatment, the stain is represented visually by many small purple squares and fragments that seem to burst apart and scatter across the fabric.
The pieces spread outward and thin away until the front of the garment appears clean again, with the bib, buttons, seams, and straps clearly visible and no dark stain remaining.
The \textbf{blue} bottle returns in a large product view, its curved side and front label dominating the screen.
The label again reads “ CLOROX Prewash ” and “ LAUNDRY SOIL AND STAIN REMOVER, ” framed by the orange and \textbf{red} chevrons.
The bottle remains the central object, bright \textbf{blue} against a darker background.
Near the end, a young red-haired boy stands facing forward in a \textbf{yellow} T-shirt with horizontal \textbf{red}, \textbf{blue}, and white stripes.
A dark brown stain marks the left side of his chest.
At first he looks neutral, then he smiles.
Finally, a blonde adult woman with glasses, wearing a purple sweater over a white collared shirt, holds the \textbf{blue} Clorox Prewash bottle close to her shoulder.
She smiles with a satisfied expression.
A red-and-orange chevron patch is visible on her sleeve, matching the stripe motif used throughout the commercial.

% matched lemmas: blue, green, red, yellow
\end{textsample}
