\begin{textsample}{NEG Dim 7 – 1990 – Score -2.00 – 1990/tv\_com\_1990\_16.txt}  \label{ex:f7_neg_041}
The commercial opens on a black screen.
It \textbf{then} cuts to a close-up product-demonstration image : a white absorbent pad-like item shown against a mostly black background.
The center area is brightened with a pale yellow-white glow, and the surrounding material appears light pinkish/white.
At the bottom, small white text reads : “ VS.
LEADING REGULAR SIZED THICK NON-WINGED MAXIS. ” A dark rounded shape is visible along the right edge.
The next scene shows a young woman with long blonde/light brown hair in a softly lit bedroom or dorm-like room.
She is smiling and looking directly toward the camera.
She wears a cream-colored knit turtleneck sweater.
In the background there is a bicycle on the left, light curtains, a bed on the right, wooden flooring, and other room furnishings.
The ad briefly returns to the close-up demonstration image of the absorbent pad-like product, again emphasizing the bright central area.
It \textbf{then} cuts back to the young woman in closer view.
She continues facing the camera with a pleasant, conversational expression.
The background is softly blurred, with pale furnishings and possibly a bed or dresser behind her.
A wider shot follows : the woman sits cross-legged on a patterned rug on the wooden floor.
She wears blue \textbf{jeans} and black high-top sneakers with white laces and soles.
The room remains bright and airy, with the bicycle visible on the left and a bed on the right.
Another close-up of the woman appears.
She is slightly angled, smiling or speaking toward the camera.
At the bottom of the frame, the same small comparison text appears again : “ VS.
LEADING REGULAR SIZED THICK NON-WINGED MAXIS. ” The final shots are product-title graphics on a turquoise background.
A dark green label at the top left reads “ NEW. ” Near the top center is a circular logo with teal and pink shapes.
Large text reads “ always with CHANNELS, ” and a dark horizontal band below reads “ MAXI with WINGS. ” In the last frame, an additional line appears at the bottom : “ Cleaner.
Drier.
Protects Better. ”

% matched lemmas: jean, then
\end{textsample}
