\begin{textsample}{NEG Dim 7 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_15.txt}  \label{ex:f7_neg_018}
A young woman with long dark curly hair sits on a \textbf{blue} couch in a bright living room with \textbf{blue} walls, large wooden-framed windows, sheer white curtains, a potted plant, a lamp, and a pale \textbf{green} chair in the background.
She wears a \textbf{blue} sweater over a light collared shirt and light-colored pants.
Two dogs are close to her : a black-and-white dog in front of her and a golden retriever behind her on the couch.
She holds a \textbf{blue} dog \textbf{leash} or toy in one hand and reaches out with the other to pet the black-and-white dog ’s head.
Tiny white particles float through the air around them, suggesting dust, pollen, or pet dander.
A small Claritin-D logo sits at the upper right of the screen.
The black-and-white dog fills the view, panting happily with its mouth open and tongue visible while the woman ’s hand strokes its cheek and the top of its head.
The dog ’s fur is speckled black and white, and its eyes look up toward her.
The floating particles remain visible around the dog ’s face.
Back on the couch, the woman leans close to the dog, then turns her head away and brings her arm up toward her face, as if reacting to allergy symptoms.
The dog looks up at her with its mouth open, while the golden retriever remains behind her.
A blue-and-green Claritin-D box is then held up by a hand against the softly blurred room.
The package reads “ Non-Drowsy Claritin-D 12 Hour, ” with “ Indoor \& Outdoor Allergies ” and “ Allergy + Congestion ” on the front.
Small white fine print appears along the bottom of the screen, including “ Use as directed ” and a list of symptoms such as runny or itchy nose, sneezing, itchy or watery eyes, itchy throat, sinus pressure or congestion, and nasal congestion.
The woman moves through the sunlit room near tall windows, still surrounded by drifting white particles.
At first her expression looks uncomfortable and tense, with her mouth slightly open and her brow drawn.
As she stands in the light, the space brightens.
Sunbeams stream through the curtains behind her, and the particles become less prominent.
Her face relaxes ; she lifts her chin slightly and begins to smile, appearing more comfortable.
The \textbf{blue} walls, hanging plant, framed wall art, and bright window remain behind her, giving the room a cleaner, clearer look.
The scene returns to the couch, now with the woman cuddling the golden retriever.
She bends down and kisses the dog ’s head, then smiles while holding its face gently in both hands.
The golden retriever lies calmly with its mouth open and tongue out, looking content.
On the left side of the screen, large bold text reads “ FAST POWERFUL RELIEF, ” with “ POWERFUL ” highlighted in \textbf{yellow} ; smaller text underneath says it “ Starts working in as little as 30 minutes. ” The woman presses her cheek against the dog ’s head and grins broadly, continuing to hug and scratch the dog affectionately.
The commercial ends on a product display : a Claritin-D box standing in a vivid \textbf{green} field under a bright \textbf{blue} sky with a shining sun.
The package shown is “ Claritin-D 24 Hour, ” labeled for “ Indoor \& Outdoor Allergies ” and “ Allergy + Congestion, ” with “ Relief ” and “ 10 extended release tablets ” visible on the front. “ Use as directed ” appears near the bottom, and a Bayer logo is shown at the lower right.

% matched lemmas: blue, green, leash, yellow
\end{textsample}
