\begin{textsample}{NEG Dim 7 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_24.txt}  \label{ex:f7_neg_014}
The commercial begins with an upward-looking city view between tall buildings.
In the blue sky, white skywriting reads “ MARRY ME JENNY. ” It cuts to a young woman standing outdoors on a city sidewalk.
She looks upward and smiles, apparently reacting to what is in the sky.
She has long wavy hair and wears a dark jacket over a striped top.
The next shot shows a car ’s digital dashboard display.
The speed reads 15 mph, with a graphic of a car and an alert-style icon.
Other visible indicators include “ READY, ” gear indicators, fuel/energy information, and an odometer reading.
This suggests the view is from inside a vehicle.
A street scene follows outside a brick building with outdoor seating.
The same woman stands near a crosswalk while a red car approaches from the right.
Small disclaimer text appears along the bottom, stating that the “ TSS Pre-Collision System with Pedestrian Detection ” is not a substitute for safe and attentive driving and \textbf{referring} viewers to the owner ’s manual.
The woman is \textbf{then} shown closer, seen through or over the vehicle interior, standing in front of the car ’s path.
A screen-like view appears, showing the street scene with the woman and the red car.
Large text on the display reads “ Pedestrian Detection. ” The red car is visible near the crosswalk, and the same safety disclaimer remains at the bottom.
The commercial \textbf{then} shifts to a different driving situation.
Inside a car, a man drives while a woman in the passenger seat looks down at a phone or device.
The landscape outside is open and mountainous, with warm light.
The man holds the steering wheel and looks ahead.
An exterior shot shows a blue Toyota Prius traveling on a two-lane road through a wide, open landscape.
Bottom text states that “ Lane Departure Alert with Steering Assist ” is not a substitute for safe and attentive driving and again \textbf{refers} to the owner ’s manual.
The digital dashboard is shown again : the speed reads 40 mph, and a lane graphic appears in the center display, indicating lane-position assistance.
The driver and passenger are \textbf{then} shown again from inside the car.
Close-up exterior shots show the rear of the blue Prius, including the Toyota emblem, the “ Prius ” badge, and the distinctive vertical taillights.
A wider rear view shows the Prius driving along the road with another vehicle approaching in the opposite lane.
The scene \textbf{then} changes abruptly to the interior of an aircraft.
Several people wearing helmets, goggles, and jumpsuits are gathered near an open door, suggesting skydiving preparation.
One person in a black suit with a cream-colored helmet stands near the door, while others in blue gear sit or crouch nearby.
The open door reveals a view of land far below.
The people appear to be adjusting themselves, holding equipment, or preparing to jump.
A title overlay appears over the aircraft scene : “ The 2017 PRIUS ” with smaller text underneath reading “ Toyota Safety Sense{\EmojiFont ™} Standard. ” The aircraft doorway and skydivers remain visible behind the text.
The image \textbf{then} transitions into a rotating collage or globe of rectangular video panels.
The panels show earlier scenes from the commercial, including the skywriting “ MARRY ME JENNY, ” the driver and passenger in the Prius, road/lane imagery, the skydiving scene, and parts of the car.
The collage continues rotating and pulling back against a white background.
The final frame is a white end card with the Toyota logo on the left, the red word “ TOYOTA ” beneath it, and the slogan “ Let ’s Go Places ” on the right.
A small URL at the bottom reads “ toyota.com/prius. ”

% matched lemmas: refer, then
\end{textsample}
