\begin{textsample}{NEG Dim 7 – 2000 – Score -3.00 – 2000/tv\_com\_2000\_34.txt}  \label{ex:f7_neg_027}
A young man in a dark suit jacket and light shirt walks up the path of a tidy suburban house with a white picket fence and gate.
Behind him, across the street, a \textbf{red} car is parked in front of single-story homes.
Inside the house, two children peer out through a white-paned window with sheer curtains : first a dark-haired boy, then an older girl leaning in beside him.
They look excited and intent as they watch the young man approach.
A close view of his hand shows him carrying a small brown \textbf{shopping} bag filled with white tissue paper.
The bag is printed with the white “ JARED ” logo, identifying it as from Jared The Galleria of Jewelry.
The scene moves through the home as family members react.
In a warm, traditional kitchen with wooden cabinets, a white stove, a sink under a curtained window, and fruit on the counter, an elderly woman in glasses and a cardigan stands beside a middle-aged woman in a pink button-down shirt.
They pause together, smiling and looking toward the commotion.
In another room, a middle-aged man in a \textbf{blue} shirt sits with a phone to his ear while the same woman in pink leans through a doorway behind him, clearly sharing the news.
Outside at the front door, the young man stands close to a dark \textbf{blue} door marked with the house number “ 244, ” reaching toward the doorbell or handle.
The door opens, and the young man faces a whole welcoming cluster of people packed into the entryway.
An elderly woman, a boy, a middle-aged man, the woman in pink, and a young red-haired woman all smile at him.
The red-haired young woman, wearing a light \textbf{blue} button-down shirt, steps forward from the group.
She beams, moves past the others, and comes out through the doorway toward him.
The young man, still in his dark jacket, follows her inside, looking slightly \textbf{nervous} but pleased as the family watches closely from just inside the door.
A jewelry store interior appears, bright and spacious, with glass display cases arranged throughout the room.
Sales associates in dark suits help customers at the counters, while other \textbf{shoppers} browse.
In the foreground, a suited male associate smiles and presents items to a blonde woman leaning over a case ; other customers and staff move among illuminated displays in the background.
The store feels open and polished, with jewelry cases lining the walls and center of the room.
Gold jewelry is then displayed against a black background : curved necklaces, bracelets, chains, and textured pieces arranged neatly so their yellow-gold shine stands out.
Some pieces are smooth and modern, others braided or beaded.
Small on-screen text near the upper right reads “ speak gold, ” alongside a circular gold-themed logo.
Back at the home, the young couple sit side by side on a \textbf{blue} sofa in a living room.
The red-haired young woman sits on the left, watching with an expectant smile.
The young man sits on the right with the brown Jared bag in his lap, pulling out a small white jewelry box from the tissue paper.
Behind them are dining chairs, framed art, and a staircase.
He turns toward her with the box in hand, smiling, and she looks down shyly as he prepares to give it to her.
The Jared bag remains visible on the sofa or beside him, its white rope handles and logo facing outward.
A close view shows his hands opening the white jewelry box.
Inside, resting on a white cushion, is a gold bracelet or bangle with a smooth, gleaming surface.
The inside of the lid has the Jared name printed faintly.
The young woman takes the box and looks at it, then suddenly leans across the sofa to hug him.
He wraps an arm around her as she embraces him tightly, the open jewelry box still in her hand.
While they hug, several family members sit together on the staircase in the background, watching with delighted expressions.
The elderly woman, the woman in pink, the boy, and the middle-aged man crowd together on the steps, smiling at the couple ’s private moment from a not-so-private distance.
A close view of the young woman over the young man ’s shoulder shows her smiling broadly, holding the open white jewelry box near his back so the bracelet is still visible.
The commercial ends outside a Jared store.
The storefront has a large dark entrance tower with bright white signage reading “ JARED ” and, beneath it, “ The Galleria Of Jewelry. ” Cars are parked in front, and a couple walks toward the entrance.
Large white text at the lower right reads “ jared.com. ”

% matched lemmas: blue, nervous, red, shopper, shopping
\end{textsample}
