\begin{textsample}{NEG Dim 7 – 1970 – Score -2.00 – 1970/tv\_com\_1970\_15.txt}  \label{ex:f7_neg_067}
A dark \textbf{green} sponsor card appears first, with large white text reading “ 800-841-8000 ” and, below it, “ \textbf{NAVY}, IT ’S NOT JUST A JOB, IT ’S AN ADVENTURE. ” Smaller text at the bottom says it is sponsored by the U.S.
Navy.
The scene then changes to a bright playroom where several young children crowd around a white table, excitedly playing with the Weebles Wobble Race toy.
A long-haired blonde girl in a \textbf{red} shirt leans over the track, her mouth open in excitement, while a child in a \textbf{green} striped shirt watches from the left.
Small egg-shaped Weeble racer figures, painted with helmets and numbered white jerseys, sit on a colorful racetrack in front of them.
The full tabletop toy is shown : a white plastic base with four colored racing lanes—green, \textbf{yellow}, orange, and red—leading toward a bold “ FINISH ” label at one end.
A \textbf{blue} upright rail or hurdle crosses part of the track, and a large illustrated backdrop rises behind it, decorated like stadium stands with cartoon spectators, bunting, and small signs such as “ START ” and “ EXIT. ” Four children gather around the game, including the blonde girl, a red-haired boy in a \textbf{red} shirt, a blond child in a light top, and the child in the \textbf{green} striped shirt.
Their faces are animated, mouths open as they watch the race.
Close views show the Weebles in detail.
They are rounded, weighted figures with glossy colored bottoms and helmet-like tops : \textbf{green} number 4, \textbf{yellow} number 3, orange number 2, and \textbf{red} number 1.
Their painted faces and arms make them look like little racers.
They wobble and lean rather than lying flat, bumping into one another on the lanes.
The \textbf{green} number 4 tips far to one side near the edge, then rocks back upright, while the \textbf{yellow}, orange, and \textbf{red} racers jostle together near the \textbf{blue} rail.
The children keep the race going by pressing and moving parts of the toy with their hands.
The blonde girl and the red-haired boy lean close, concentrating on the track.
The racers advance unevenly, rocking from side to side.
At the finish end, the four Weebles cluster together in their lanes beneath the \textbf{blue} rail, with the large “ FINISH ” lettering visible across the front.
The \textbf{yellow} number 3, orange number 2, \textbf{red} number 1, and \textbf{green} number 4 crowd side by side, nudging each other as they wobble.
One sequence focuses on the \textbf{green} number 4 near an “ EXIT ” arch on the backdrop.
The \textbf{green} racer collides with another figure and tumbles off the side of the track onto the white tabletop.
Even after tipping over, it rocks back and forth instead of staying down.
A child ’s hand reaches in and steadies or retrieves it, returning attention to the race.
The \textbf{red} number 1 racer is then shown alone on a \textbf{red} lane, rocking forward.
It sways dramatically from side to side, briefly tilting almost horizontal, then rights itself and continues wobbling.
Another close view shows \textbf{green} number 4 and \textbf{yellow} number 3 pressed shoulder to shoulder in neighboring lanes, their rounded bodies pushing against each other as they rock in place.
A wider view returns to the whole toy on the table.
The children are gathered behind it, watching.
The \textbf{green} number 4 leans sideways near the \textbf{green} lane, while \textbf{yellow} number 3, orange number 2, and \textbf{red} number 1 continue toward the finish.
At the finish end, the racers bunch together, bump, and spill off the track onto the tabletop.
Several figures roll or wobble outside the white plastic base, but they keep rocking upright or nearly upright.
The illustrated grandstand on the toy backdrop fills the view.
Cartoon spectators with exaggerated faces cheer, blow horns, and hold their hands to their mouths.
Bright orange balloons float above them, and \textbf{red}, white, and \textbf{blue} bunting decorates the front of the stands, reinforcing the race-day setting.
The children celebrate around the table.
The blonde girl in the \textbf{red} shirt throws both arms straight up, the red-haired boy behind her raises an arm and laughs, and the child in the \textbf{green} striped shirt sits at the left with mouth wide open in excitement.
Another blond child at the right looks down toward the toy.
The playroom background includes \textbf{blue} walls, a white door, a black lamp, and \textbf{yellow} wall shelves.
The commercial ends with a clean product display against a plain light background.
The complete Weebles Wobble Race set is arranged neatly : the colorful racetrack base in front, the illustrated stadium backdrop standing behind it, and four loose Weeble racers lined up along the front.
Large yellow-orange text above the set reads “ Weebles Wobble Race. ”

% matched lemmas: blue, green, navy, red, yellow
\end{textsample}
