\begin{textsample}{NEG Dim 7 – 2020 – Score -3.00 – 2020/tv\_com\_2020\_47.txt}  \label{ex:f7_neg_029}
The commercial uses a subway/train setting and fast lateral motion blur as a recurring visual motif. - It opens on a blurred silver subway train exterior moving horizontally across the frame.
A wide pale-lavender horizontal band runs across the middle.
The train windows and an American flag decal are briefly visible, but most details are softened by motion blur. - As the train continues sliding past, the lavender band becomes a branding area.
The text “ MAYBELLINE NEW YORK ” appears centered in black on the lavender strip. - Product imagery is introduced over the moving train background : two brow-product components are shown horizontally, one near the top and one near the bottom.
The central text reads “ EXPRESS BROW DUO, ” with “ MAYBELLINE ” visible on the product labeling.
The product appears as a two-ended brow cosmetic item, though the exact applicator details are only partly visible in the sampled frames. - The scene cuts inside a subway car.
A young woman with a shaved or closely cropped head stands or sits near the blue bench seating.
She wears a bright neon-yellow hooded sweatshirt under a darker jacket and holds a bag.
Other passengers are partially visible : a person in dark clothing on the left and a red-haired woman on the right holding a large dark bag.
The subway interior has metal poles, blue seats, white walls, and purple advertising panels. - The camera moves closer to the woman with the neon hood as she sits against the subway wall, looking downward or to the side.
The shot is slightly dynamic, with the subway window behind her. - A blonde woman in a beige trench-style coat appears inside the subway car.
She holds an \textbf{overhead} rail with one arm and faces the camera.
Large on-screen text at the lower left reads “ FULLER-LOOKING BROWS ” in white, with a lavender block behind part of the text.
The camera moves in closer to her face, emphasizing her eyebrows. - A hand holds the brow product horizontally against a blurred subway background.
On-screen text reads “ JUST TWO STEPS ” at the lower left.
A close-up \textbf{then} shows the pointed cosmetic tip of the product, with the same “ JUST TWO STEPS ” text remaining visible. - The blonde woman is shown applying the product to her eyebrow while looking into a small handheld mirror.
On-screen text reads “ STEP 1 DEFINE, ” with a number “ 1 ” in a circle.
A close-up follows of the product tip tracing along the outer edge of her eyebrow, visually demonstrating the defining step. - The next product close-up shows another end or component of the item, thicker and darker, with on-screen text “ STEP 2 FILL ” and a number “ 2. ” The background remains a blurred subway interior. - The woman with the neon-yellow hood is \textbf{then} shown reflected or partially seen through glass, applying product to her eyebrow.
The “ STEP 2 FILL ” text remains at the upper left.
A closer shot shows her using the applicator on her brow while her eyes are closed or lowered.
Her face is lit softly, and the brow \textbf{application} is the visual focus. - She \textbf{then} faces the camera in a clean close-up, showing the finished look.
The left edge of the frame contains only a partial fragment of text, not enough to read fully. - The commercial returns to fast-moving subway/train imagery with lavender horizontal bands and motion blur. - The product packshot reappears over the blurred train background, again showing the two-ended “ EXPRESS BROW ” product and the lavender strip. - The final frames return to the branding treatment : “ MAYBELLINE ” and \textbf{then} “ MAYBELLINE NEW YORK ” appear centered in black on a pale-lavender horizontal band, with the moving subway/train background blurred behind it.

% matched lemmas: application, overhead, then
\end{textsample}
