\begin{textsample}{NEG Dim 7 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_54.txt}  \label{ex:f7_neg_066}
The commercial is presented in high-contrast black-and-white and uses rapid cuts, motion blur, stark silhouettes, and large bold typography.
It begins on a black frame, \textbf{then} cuts to an extreme close-up of a shiny circular car detail or mechanical feature.
The exact part is difficult to identify from the sampled frame, but it appears metallic and reflective.
This is followed by a rear/front road shot of a light-colored car moving along a roadway, \textbf{then} a very blurred close pass of a dark car surface or wheel area, suggesting speed.
A title card appears with large block capital letters reading “ THE NOW CARS. ” The words are stacked vertically in white against a dark, smoky or cloudy background.
A white outline shape appears to the left, though its precise meaning is unclear.
The title is repeated in a cleaner form : first faintly over a bright background, \textbf{then} in solid black letters on a plain light background.
The commercial \textbf{then} shows a convertible in profile as a dark silhouette against a bright sky.
A driver or passenger is visible in silhouette, seated low inside the open car.
The image emphasizes the roofless body line and windshield frame.
A large block word “ REBEL ” appears across the lower part of the frame while the convertible passes behind it, identifying the car model visually.
Wider exterior shots follow : a light-colored convertible drives along a tree-lined road, seen from the side and \textbf{then} from a front three-quarter angle.
The car has a long, rectangular front grille and rectangular headlamp area, and the convertible top is down.
The middle section becomes more abstract and kinetic.
There are blurred close-ups of car surfaces or road textures, a dark near-black shot that may be a wheel or shadowed body detail, and several bright white flash-like transitions.
A small car is \textbf{then} shown far in the distance on a flat horizon under a cloudy sky.
This is followed by a dramatic shot of a windmill or rotating radial structure, seen as alternating black and white blades around a circular center.
A close-up shows a woman inside the car in profile, looking forward.
She has dark hair and a long light-colored earring ; her face is strongly lit from the front/side while the car interior remains dark.
The next shots return to the convertible driving on the road : first a front three-quarter view with the driver visible behind the windshield, \textbf{then} a rear three-quarter view as the car moves away along a road bordered by trees.
More bright white transitions appear.
The convertible is \textbf{then} shown in side silhouette again, moving past a bright background with trees behind it.
Later, the car appears in a darker setting with structural beams or bridge-like supports passing across the frame, creating a pattern of vertical and diagonal lines over the vehicle.
The commercial ends with very large bold white capital letters reading “ NOW ” over the moving background of the car/structural setting.
The word fills most of the frame and remains dominant through the final sampled frames.

% matched lemmas: then
\end{textsample}
