\begin{textsample}{NEG Dim 7 – 2000 – Score -4.00 – 2000/tv\_com\_2000\_119.txt}  \label{ex:f7_neg_031}
The commercial opens in a very dark tunnel-like space, where a row of rectangular \textbf{ceiling} lights recedes into the distance.
It \textbf{then} cuts to the outside of a stone-arched road tunnel.
The camera is low near the roadway, looking toward the tunnel entrance.
A road with a shoulder line leads into the dark tunnel, and small white text appears near the bottom reading, “ \textbf{Professional} riders on closed course. ” A close-up follows of double yellow center lines on a road, still with the same “ \textbf{Professional} riders on closed course ” disclaimer at the bottom.
The next shot shows a large touring motorcycle leaning through a curving mountain road.
The motorcycle ’s headlights are on, and hazy mountain silhouettes fill the background.
The same disclaimer remains visible near the bottom.
The sequence continues with multiple riding shots in different landscapes.
One shot shows a dark touring motorcycle traveling through a dry, scrubby area with blurred vegetation in the foreground and background.
Another shows a motorcycle approaching on a paved mountain road, with bright snow-covered peaks in the distance.
The bike is centered in the lane and moving toward the camera.
A side view \textbf{then} shows a motorcycle carrying two riders.
Both wear helmets and dark jackets ; the driver wears light blue \textbf{jeans}.
The motorcycle has a windshield and a large rear seat/backrest.
The road runs through a mountainous or forested area.
A distant \textbf{overhead} or high-angle shot shows a single motorcycle riding along a wide, pale road bordered by yellow-green fields or vegetation.
The bike casts a shadow behind it.
Another shot features an orange touring motorcycle on a two-lane road through red rock canyon terrain.
The rider wears a dark helmet and clothing.
The motorcycle has a windshield, large side cases, and rounded orange storage compartments.
A promotional title card appears over a road scene.
A metallic wing-like emblem is centered above large text reading “ GOLDWING, ” with “ Test Ride ” below it.
Fine-print legal/disclaimer text runs along the bottom, but most of it is too small and blurred to read clearly.
The background remains a curving open road with trees and hills in the distance.
The commercial \textbf{then} returns to action footage : a dark touring motorcycle rides toward the camera on a desert road bordered by red rock formations.
White fine-print text remains overlaid at the bottom.
The final frame shows a wide scenic landscape : a narrow road runs through bright yellow fields toward distant cliffs and mesas.
A lone motorcycle rides away from the camera down the center of the road.
Over the landscape is a red wing-like logo and large white text reading “ PERFORMANCE FIRST. ” Smaller dealership/contact text appears along the bottom, but it is partly blurred and not fully legible.

% matched lemmas: ceiling, jean, overhead, professional, then
\end{textsample}
