\begin{textsample}{NEG Dim 7 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_78.txt}  \label{ex:f7_neg_013}
The sampled sequence begins with a staged product shot unrelated in appearance to the later car imagery : two open takeout-style food cartons sit on a dark tabletop against a black background with purple bokeh lights.
The cartons carry the “ Jack ” branding, and a purple sign reads “ Jack late night. ” Circular labels near the cartons identify curly-fry products.
Very small fine print appears along the bottom but is not legible at this resolution.
The image \textbf{then} cuts to black.
After the black frame, the commercial shifts to a fast, glossy montage centered on a silver sedan.
The car is first seen moving or positioned outdoors among trees, with strong sunlight and lens flare.
Quick close-ups follow : the side of the car, a steering wheel and dashboard area, and dark leather-like seat upholstery with stitching.
Fine-print disclaimer text appears along the bottom in several of these frames, but most of it is too small to read.
The montage continues with exterior details of the vehicle : reflections of trees and sky on a smooth silver body panel or roof, a dark car ahead on a road, and an instrument-cluster display.
The dashboard display shows a compass and driving information, including “ 3:49, ” “ BEAR TRAP RD, ” “ 72{\EmojiFont °}F, ” and numerical trip/mileage information, while analog gauges \textbf{flank} the screen.
The setting \textbf{then} includes a roadway or bridge-like structure, followed by a front/side view of a white or silver Volkswagen sedan in traffic, with another dark vehicle behind it.
More close-up shots emphasize the car ’s exterior surfaces : a side mirror with dark reflective glass, a smooth body panel, and a roofline or upper body seam.
A small badge-like graphic appears in the upper-left corner during several of these shots, but the text is not clearly readable in the frames.
The camera \textbf{then} presents a stylized top or high-angle view of the car ’s rear/roof area, followed by close-ups of the front headlight assembly.
The headlight is illuminated, and the surrounding design includes a row of small rectangular lights or reflective elements around the lamp.
The scene changes to a social outdoor setting near a large stadium.
People in purple sports jerseys move around the car.
Some jerseys show large yellow or white numbers, including “ 5, ” “ 27, ” “ 32, ” and “ 26. ” The silver sedan is parked among tailgating-style elements such as tents, coolers, and recreational vehicles.
The stadium curves through the background, and vertical purple banners or flags are visible.
Several medium shots show individuals near the car : a young man in a purple jersey with a large yellow “ 5 ” holding a tray, and two young women standing near the vehicle, one with red hair in a purple jacket and yellow top, and another in a purple jersey with the number “ 32. ” Their expressions appear cheerful or pleased.
No dialogue is visible or inferable from the frames.
A wider shot shows the silver sedan parked in the lot with groups of people around it, tents and flags in the background, and the stadium dominating the scene.
The car is positioned prominently in the foreground.
Near the end, a clean product shot shows the silver sedan in three-quarter front view in the same stadium/tailgate setting.
Large on-screen text at upper left reads “ The new Jetta. ” A small badge-like graphic appears below it, with additional small text that is not fully legible.
Fine print runs along the bottom.
The final frames switch to a plain white background with centered black text reading : “ Isn't it time for German engineering? ” The same text remains on screen through the last sampled frame.

% matched lemmas: flank, then
\end{textsample}
