\begin{textsample}{NEG Dim 7 – 2000 – Score -8.00 – 2000/tv\_com\_2000\_11.txt}  \label{ex:f7_neg_021}
On a busy city sidewalk outside a modern glass-fronted building, a young woman with shoulder-length brown hair stands at an outdoor flower stall.
She wears a pale yellow-green dress under a black cardigan and smiles as she looks over bright bunches of pink and \textbf{red} flowers.
On the display table beside her are a black handbag and a \textbf{yellow} Post Honey-Comb cereal box partly tucked into a white \textbf{shopping} bag.
A young man in a black \textbf{knit} cap, \textbf{red} plaid shirt, dark gloves, and loose dark pants rushes in from behind her.
He grabs the black handbag and the Honey-Comb box and bolts down the sidewalk.
The woman ’s expression changes to alarm ; she turns, leans forward, and points after him.
The thief sprints past benches outside the building, clutching the bright \textbf{yellow} cereal box against his chest.
Several \textbf{kids} sit nearby.
One blond boy, about early teen age, wears a red-and-black padded vest, elbow pads, wrist guards, and skater clothes, with a skateboard beside him.
He looks up sharply, eyes widening in surprise.
His face fills the view as he reacts with exaggerated amazement, then an animated \textbf{green} thought bubble appears above him, filled with giant golden Honey-Comb cereal pieces glistening with honey.
He pulls on a \textbf{yellow} helmet decorated with dark spots and flame-like markings, as if inspired into action.
The boy is suddenly represented as a small, wild-looking, furry cartoon character : yellow-orange shaggy fur, huge round eyes, a long pink nose and cheeks, black gloves, protective pads, and the same \textbf{yellow} helmet.
He rides a skateboard down the sidewalk near parked bicycles and a flight of building steps.
Arms out for balance, he gains speed, pops off the board, and leaps high, grinning broadly before landing back down in a chaotic slide.
The thief, still hugging the Honey-Comb box, runs through a busier \textbf{shopping} area and looks back over his shoulder with a \textbf{nervous} grin.
The furry skater pursues him along the sidewalk past stacks of newspapers.
As the creature rushes through, the piles of papers fly apart, pages flipping and scattering across the pavement.
Nearby dogs on \textbf{leashes} react and lunge ; a large black-and-white dog fills the view as it jumps forward, while a smaller white dog stands beside it.
Traffic passes in front of storefronts with \textbf{red} and \textbf{green} awnings.
Water suddenly erupts in a tall white spray beside the street, and another column of golden cereal-like pieces or debris showers upward near a shop window, adding to the commotion.
The thief pauses and turns his head, startled, then keeps running with the \textbf{yellow} box tight against his side.
The chase continues past a \textbf{green} awning marked “ K MARKET. ” A large white animal figure or costume-like shape tumbles through the scene, and pedestrians in suits and casual clothes turn to watch.
Ahead, two movers in \textbf{blue} coveralls are pushing a large black upright piano on a wheeled dolly along the sidewalk.
The chaos barrels into them : the piano is struck or tipped, its wooden interior and strings exposed.
A burst of dust and splinters fills the air.
The furry skater shoots through the wreckage, then reappears with black-and-white piano keys comically jammed across his mouth like oversized teeth.
He freezes for a beat with wide eyes and raised hands, looking dazed but still eager.
The thief keeps moving, clutching the Honey-Comb box.
He runs past a construction area where orange-and-white striped barriers and steam mark an open manhole.
A construction worker in a \textbf{yellow} hard hat and reflective vest pushes up the round manhole cover from below.
The thief passes over the opening, and the furry skater uses the raised cover like a ramp.
The little creature is launched upward, flying on his skateboard against a backdrop of tall city buildings and \textbf{blue} sky.
He sails between skyscrapers, crouched low over the board, mouth open in excitement.
From above, the thief is seen running along the sidewalk while the woman in the pale dress follows behind him.
He looks upward, still holding the cereal box and black handbag, as pieces of debris streak down around him.
Then the furry skater drops from above and lands on the thief ’s back.
The thief lurches forward, face strained, while the creature clings to him triumphantly, waving its arms and grinning.
The chase ends with the thief bent over under the furry character ’s weight, the Honey-Comb box still visible against his \textbf{red} plaid shirt, and the woman close behind.
The commercial shifts to a product display on a table outdoors.
A large \textbf{yellow} Post Honey-Comb cereal box stands behind a white bowl filled with the cereal ’s round, honeycomb-shaped pieces.
Around it are breakfast items : a glass of orange juice, a clear pitcher of milk, toast on a plate, and sliced fruit including kiwi and melon.
The box front shows the bold \textbf{blue} words “ Honey-Comb. ” At the end, the scene returns to the building steps.
The blond skater boy sits relaxed on the stoop, no longer the furry character, eating Honey-Comb from a \textbf{blue} bowl with a spoon.
He wears his red-and-black skater outfit with pads, and his \textbf{yellow} helmet and skateboard rest nearby ; the skateboard has a flame design.
A Honey-Comb cereal box sits open beside him.
The woman stands over him in her pale dress and black cardigan, palms turned up in a questioning gesture, looking at him expectantly.
He keeps eating, then glances up with a caught-in-the-act expression.

% matched lemmas: blue, green, kid, knit, leash, nervous, red, shopping, yellow
\end{textsample}
