\begin{textsample}{NEG Dim 7 – 1990 – Score -4.00 – 1990/tv\_com\_1990\_59.txt}  \label{ex:f7_neg_035}
A broad \textbf{green} park appears under a canopy of large leafy trees.
Small groups of people walk across the grass in the distance, dressed in light-coloured clothing, giving the scene a calm, leisurely, old-fashioned feel.
The setting shifts closer to two very young children seated side by side in a white pram or carriage on the grass.
Both wear navy-and-white sailor-style outfits with wide white collars and round white sailor hats trimmed in dark piping.
One fair-haired toddler faces slightly toward the camera, cheeks rosy, while the other is seen mostly from behind.
They sit quietly, looking at each other and down into the pram.
The imagery changes abruptly to a muddy rugby match.
Adult players in dark and \textbf{yellow} jerseys rush across a wet, grassy field.
A player in a dark uniform clutches a pale rugby ball against his chest as other players close in around him.
He drops and slides through \textbf{mud}, landing on his side while a player in \textbf{yellow} reaches toward him.
The action is crowded, fast, and physical, with splashes of \textbf{mud} and blurred legs moving around the tackled player.
A quieter river scene follows.
A narrow wooden rowboat floats on calm water beside reeds and an old brick or stone building.
One person, wearing a cap and dark coat, sits toward the back and rows with oars.
Another person in dark clothing sits nearer the front, facing across the boat.
The water reflects warm light, with bare trees and old architecture along the bank.
Children in school uniforms then pour out from the entrance of a grand old brick building.
The building has stone steps, an arched doorway, and two pale stone lion statues on raised walls near the entrance.
The children wear dark blazers, ties, white socks, and straw boater hats.
Several carry cricket bats, and one child near the front runs forward enthusiastically with a cricket bat held high.
More children stream down the steps behind, spreading across the path.
A large United Airlines jet appears above a thick blanket of clouds tinted peach and gold.
The white wide-body airplane has four engines and a red-orange stripe along the fuselage.
As it moves through the sky, its nose and wings are seen first, then more of the side becomes visible.
The word “ UNITED ” is clearly printed in large dark letters on the side, and the United tail emblem appears at the rear.
The aircraft glides over the glowing cloud tops for an extended stretch, filling much of the image against the warm sky.
The plane image gives way to another tranquil waterway.
A broad, still river or pond reflects leafless trees and the tower of an old church or college building.
Near the left bank, a small punt or flat boat rests close to reeds and grass.
The scene is quiet and spacious, with the tall tower rising in the background and its reflection stretching down into the water.
A cottage garden appears next, dense with flowering plants and greenery.
An elderly woman with short white hair stands on a path beside the house, wearing a pale dress.
She holds purple flowers in her hands and faces a window set into a wall covered with climbing plants and blossoms.
The garden is full and colourful, with \textbf{blue}, purple, white, \textbf{yellow}, and \textbf{red} flowers clustered around the doorway and window.
The view then opens to a sweeping coastline at dusk or early evening.
White chalk cliffs run along the edge of the land, with dark shoreline and water on one side and \textbf{green} fields on the other.
Atop a distant headland sits a small structure or monument, silhouetted against a soft purple-pink sky and a muted sea.
The commercial moves to an aerial view of central London.
The clock tower of the Houses of Parliament, commonly known as Big Ben, rises beside the River Thames.
The Parliament buildings stretch along the river with pointed Gothic details and courtyards.
The river shimmers with reflected light, and small boats are visible on the water.
Roads and patches of \textbf{green} surround the landmark.
In the final visible moment, this London view begins to blend with another image, but the Houses of Parliament and the river remain the dominant visual impression.

% matched lemmas: blue, green, mud, red, yellow
\end{textsample}
