\begin{textsample}{NEG Dim 7 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_64.txt}  \label{ex:f7_neg_054}
The commercial begins with a very dark, indistinct frame in which little visual detail is visible.
It \textbf{then} cuts to what appears to be an indoor waiting area or salon-like setting.
Several people are seated or standing.
A young woman in a colorful outfit sits at the left, while a young man with curly hair sits on the right wearing a bright, multicolored jacket.
Between them, a seated man in a suit holds a newspaper up in front of his face, obscuring his head.
A close-up follows of a young blond man ’s face.
He looks straight ahead with a wide-eyed, startled or fixed expression.
The scene shifts to a close-up of a large portable stereo/cassette unit on a counter.
A hand reaches in and presses or points to a control button on the front panel.
Next, there is a close-up of a barber or salon cape with fine vertical stripes, filling most of the frame.
The setting continues to resemble a salon or barber shop.
The blond young man is \textbf{then} shown seated, smiling, wearing the striped salon cape.
An older man with glasses, likely a barber or stylist, stands behind him with his hands near the young man ’s shoulders.
The older man appears animated, leaning into the frame.
A close-up shows electric clippers being used near the young man ’s temple and ear, trimming his hair.
Another close-up shows a small headphone-like device held near an ear.
The visible text on the earpiece reads “ SoundBand ” and “ Panasonic, ” with small control markings also visible.
The young man is \textbf{then} shown wearing the lightweight headset over his head, with one earpiece visible.
He smiles while seated in the barber chair, and the older barber remains close behind him.
The next scene shows a young woman with very curly hair, also wearing a striped salon cape.
She holds a small portable device in her hand near her face ; the device is attached by a cord, apparently connected to the headset or audio unit.
Someone stands behind her working with her hair.
The commercial briefly returns to the seated man in a suit holding a newspaper up in front of his face, still obscuring his features.
A side close-up of the blond young man ’s head follows, showing a freshly cut style around the ear and back of the head.
He turns slightly, and the striped cape is still visible.
The final frame is a black title card with white branding text.
It reads “ Panasonic ” with the line “ just slightly ahead of our time. ” Beneath that is the “ RAMSA ” logo and the words “ Professional Audio Systems. ”

% matched lemmas: then
\end{textsample}
