\begin{textsample}{NEG Dim 7 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_6.txt}  \label{ex:f7_neg_075}
A young woman appears against a warm, reddish, softly lit dance-party background.
She has a short, rounded 1960s-style bob haircut with bangs and wears a \textbf{red} sweater.
She smiles broadly, turns her head from side to side, and moves with quick, playful dance motions.
Blurred figures move behind her, and round orange lights glow in the haze.
As she dances, the cream-colored block letters on her sweater come into view, spelling “ SLOPPY JOE. ” She laughs and gestures toward her mouth as if acting out eating, then turns and bobs her shoulders, keeping an upbeat, animated expression.
A young man in a brown sweater joins her on the dance floor.
They face each other, leaning in and bouncing to the rhythm, with other young adults dancing in the background.
The woman keeps one hand near her waist and the other raised in a playful gesture ; the man mirrors her energy, smiling and moving his hands near his chest and mouth.
They briefly mime eating or tasting with exaggerated open-mouth expressions, then pull back and continue dancing.
The \textbf{red} sweater ’s “ SLOPPY JOE ” lettering remains prominent as she steps and turns among the group.
The scene shifts to a simple product graphic on a pale beige background.
The \textbf{red} script “ Libby ’s ” appears first, followed by large \textbf{red} lettering that resolves into “ SLOPPY JOES, ” with the Libby ’s name above it.
The words are bold and centered, presenting the product name clearly.
A can of Libby ’s Sloppy Joes is then displayed in front of the blurred dance-party background.
The cream-colored can has the \textbf{red} Libby ’s script at the top and large dark lettering reading “ BARBECUE SAUCE AND BEEF, ” with “ SLOPPY JO … ” visible below.
Near the bottom of the label is a picture of a sandwich bun with saucy meat filling.
The can hangs centered and slightly angled, while dancers remain out of focus behind it.
The preparation is shown in close detail.
A hand holds a fluted paper plate with the bottom half of a hamburger bun on it.
A spoon or serving utensil spreads a thick, dark, chunky meat-and-sauce mixture onto the bun.
More of the glossy filling is spooned on, piling up until it covers the bread in a mound.
The sandwich is left open-faced, with the saucy filling visibly textured and abundant.
A young man ’s face fills the scene as he brings the sandwich up with both hands and takes a bite.
His eyes widen, then close, and his face relaxes into a satisfied expression as he chews.
He tilts his head slightly back, smiling with the look of enjoying the taste.
The dancing woman in the \textbf{red} “ SLOPPY JOE ” sweater reappears, laughing and leaning toward someone just off to the side.
She continues the playful dance gestures, raising her arms and bouncing her shoulders.
The image briefly widens to show several young adults dancing together in the hazy \textbf{red} room : the man in the brown sweater, the woman in the \textbf{red} sweater and dark skirt, and other dancers in sweaters and skirts or pants.
They move in loose pairs and small clusters, facing and turning away from one another.
The product varieties are shown through more sweater lettering.
A \textbf{red} sweater fills the view with large cream letters spelling “ BEEF. ” Then another dancer ’s reddish-brown sweater turns to show large cream letters spelling “ PORK. ” The torso-only views make the words the focus, visually matching the transcript context that the product comes in beef or pork.
The young woman turns back toward the viewer in a close view.
Her bobbed hair frames her face, and she looks directly forward with an animated, excited expression.
She smiles, opens her eyes wide, and then glances down.
She lifts a sandwich in one hand and takes a large bite, her mouth open wide around the bun, reinforcing the deliberately messy “ Sloppy Joe ” idea.
The can returns, again centered in front of the softly blurred dancers.
The label remains clearly visible : Libby ’s at the top, “ BARBECUE SAUCE AND BEEF, ” and the large \textbf{red} “ SLOPPY JO … ” text with a sandwich image near the bottom.
The commercial ends on a plain background with a small \textbf{shopping} cart icon and a written slogan beneath it : “ Something good is always cooking at Libby ’s. ”

% matched lemmas: red, shopping
\end{textsample}
