\begin{textsample}{NEG Dim 7 – 1990 – Score -4.00 – 1990/tv\_com\_1990\_48.txt}  \label{ex:f7_neg_038}
A pair of hands loads a small roll of 200-speed Fujicolor film into the open back of a black camera.
The film canister has a white, \textbf{green}, and orange label, and the fingers press it down into place before the camera back is closed.
A young boy, seen from behind in a \textbf{blue} hooded top, raises the camera toward three children standing outdoors in bright daylight.
They face him as if posing for a picture.
One girl wears dark sunglasses and a light floral dress, with a shoulder bag hanging at her side.
Beside her, another child wears a \textbf{blue} top and a loose \textbf{blue} cap, and a blond boy wears a yellow-green cap turned sideways with an orange shirt and a backpack.
They look fashionable and self-assured rather than traditionally dressed for play.
The group shifts into a tighter pose : the girl in sunglasses and the blond boy stand close together, while the child in \textbf{blue} leans in behind them, their colorful hats and clothes filling the scene.
The setting changes to a softly lit bedroom.
A small child with curly hair, wearing a bright pink top, sits on a white bed near a window.
A small stuffed toy lies nearby.
In front of the child is a compact electronic device with a hinged screen and keyboard, like a toy computer or miniature laptop.
The child presses the keys with one finger, then rests their chin on their arm and gazes thoughtfully toward the screen or window, their face half in shadow from the backlight.
Outdoors after rain, children ’s legs move along a wet sidewalk scattered with leaves.
Water splashes around their black shoes and bright socks.
The children wear bold, colorful clothes : one has a patterned orange tunic with pink leggings and carries a shoe in one hand ; another, walking beside her, wears \textbf{blue} shorts and a black, \textbf{red}, and patterned top.
They slow and turn toward each other, smiling.
A closer view shows a Black girl wearing a large patterned head wrap, beaded necklaces, and a richly colored black, orange, and gold outfit.
Another child in a striped, multicolored cap and matching patterned clothing stands beside her.
The girl ’s expression softens into a small smile as she looks forward.
On a grassy soccer field, a blond child in a black athletic top with white stripes crouches in front of a goal net.
A soccer ball blurs past near the child ’s head.
The child moves around the net, at one point appearing partly caught up or playfully tangled in it, then stands beneath the white mesh, looking upward and to the side with a serious, focused expression.
Two children stand together on a beach or sandy area, smiling broadly.
Both wear matching bright \textbf{blue} T-shirts with large white letters reading “ CLEAN PLANET CLUB. ” One child raises a clear bag filled with collected \textbf{trash}, while the other lifts a \textbf{blue} bucket overhead.
They lean shoulder to shoulder, proud and cheerful.
The commercial then shows children on BMX-style bicycles in a wooded outdoor area.
They wear full helmets and colorful racing gear.
Large number plates are fixed to the handlebars ; one clearly reads “ 358, ” and another partially visible plate reads “ 22. ” The riders wait side by side, hands on the handlebars, looking ready to race.
The blond soccer child returns in a close portrait.
A black-and-white soccer ball is held against the side of the child ’s head, just above one shoulder.
The child looks directly ahead, first with a steady, slightly skeptical expression, then with the beginning of a smile.
The final image is a clean product display on a white background : a \textbf{green}, white, and orange box of Fujicolor Super G film marked “ 200. ” On the box, the words “ FUJICOLOR ” and “ SUPER G ” are visible.
Beneath it, black text reads, “ FUJI.
A new way of seeing things. ”

% matched lemmas: blue, green, red, trash
\end{textsample}
