\begin{textsample}{NEG Dim 7 – 1990 – Score -5.00 – 1990/tv\_com\_1990\_75.txt}  \label{ex:f7_neg_033}
A stark white surface with horizontal seams fills the screen.
A thin dark line appears across it, then a shiny compact disc rises into view.
The disc is shown large and centered, its reflective surface shimmering in bright pink, orange, \textbf{red}, and pale \textbf{green} around a clear center hole.
The scene shifts to a futuristic white room with a gridded floor, white paneled walls, and two sculptural \textbf{red} lounge chairs placed symmetrically on either side.
A young man in a white top is seen from behind at the center of the room.
His brown hair whips forward dramatically, as if something powerful is rushing toward him or through him.
When he is no longer in the center, a black rectangular game system or monitor-like object is visible ahead, suspended or displayed inside a vertical column of pale \textbf{blue} light between the two \textbf{red} chairs.
The image changes to video game footage from a science-fiction cockpit view.
A gray, cratered or metallic landscape stretches toward an orange sky.
Instrument panels and small screens line the bottom edge.
Bright purple laser beams fire toward blocky structures, which erupt into large orange and \textbf{yellow} explosions that fill more and more of the screen.
Back in the white room, the young man is now reclined in a \textbf{red} chair, seen from above.
He wears white clothing, his hair stands wildly upward, and he smiles with wide-eyed excitement.
Orange flame-like blasts stream out horizontally from both sides of his head near his ears, exaggerating the idea that the game experience is overwhelming.
Another white surface appears with a horizontal slit, and a second compact disc rises into view.
This one glows mostly \textbf{blue} and \textbf{green}, with a pale highlight at the top.
A different young player appears in a padded-looking white room.
This person is youthful, dressed entirely in white, including a soft white cap, and sits in a bright \textbf{green} chair.
They hold a black wired game controller with both hands, leaning forward and grinning while playing.
A sequence of game images follows.
First, a \textbf{motorcycle} racing game shows riders speeding down a city street between blocky buildings.
A \textbf{yellow} vehicle is ahead, and a game display along the bottom includes labels such as “ Player 1, ” numbers, colored status bars, and the name “ Pearl. ” Then a soccer game appears in a stadium, with players in colored uniforms running across a \textbf{green} field under a \textbf{blue} sky.
Next, a golf game shows a golfer standing by water and grass, with on-screen text including “ Delacruz, ” “ 1st stroke, ” “ 506 yards, ” “ 4 mph, ” “ Hole 18, ” and “ Par 5. ” Another science-fiction game view shows a craft or platform moving through a gray industrial corridor with glowing orange-red elements.
The white padded room returns from a high angle.
The player in white stands near the \textbf{green} chair, still holding the wired controller.
A black console sits on the floor to the left, with the controller cord trailing across the white floor.
In front of the player, a section of the white wall is visibly cracked in a jagged pattern, as if damaged by the intensity of the play.
A third compact disc appears, this time with purple, pink, and \textbf{blue} reflections around its center.
Another young man, also dressed in white, plays with a black wired controller in a clean white space.
He has brown hair parted at the center and looks intensely focused, holding the controller close to the viewer.
Behind him are white shelves or alcoves containing pale disc-like shapes.
More game footage follows.
A fighting game shows two martial-arts characters battling on a \textbf{red} and gold platform in front of large \textbf{red} columns, snowy mountains, and an East Asian-style building.
Health bars stretch across the top of the screen, with a timer reading “ 96. ” One fighter kicks toward the other.
A large animated martial artist then appears against a black background : first as a white silhouette, then in full color.
He is muscular, with short brown hair, a torn white gi, \textbf{red} wrist wraps, and a guarded fighting pose.
A monster truck game appears next.
A large truck with oversized tires drives across a rough dirt track under a \textbf{blue} sky, then tips up and flips dramatically.
An American football game follows from an overhead view : small players in \textbf{red} and white uniforms cluster and scatter on a \textbf{green} field near \textbf{yellow} goalposts, with the crowd visible beyond the end zone.
Then a driving game is shown from inside a car, looking over a dashboard and steering wheel onto a curving road bordered by guardrails and rocky hills.
The brown-haired young man in white reappears holding the controller.
His face is comically distorted, with enlarged eyes and an exaggerated mouth, as if the game ’s graphics or intensity have warped him.
Then the viewpoint is low, looking up past his hands and controller.
His head seems to detach and float or fall away from his body, moving upward and then off into the room.
Finally, the lower half of the same player ’s body is seen sitting in a bright \textbf{yellow} chair, still holding the controller.
The black cord lies in a loose curve across the white floor.
His head rolls or slides into the foreground on the carpet, separated from the body, but still animated and smiling.
In the background, his headless body remains seated in the \textbf{yellow} chair with the controller, while his face in the foreground looks out with a dazed, pleased expression.

% matched lemmas: blue, green, motorcycle, red, yellow
\end{textsample}
