\begin{textsample}{NEG Dim 7 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_95.txt}  \label{ex:f7_neg_008}
The commercial begins with a black product-style screen showing an **Oculus Quest headset and two controllers** floating against a dark background.
Visible text reads **“oculus quest”**, **“from facebook”**, and an **ESRB Teen rating** icon.
It \textbf{then} cuts abruptly to a driving sequence.
A low, forward-facing road shot shows an empty multi-lane roadway or bridge stretching into a rural landscape with guardrails on both sides.
Small white disclaimer text appears at the bottom, but only partly legible ; it appears to \textbf{refer} to \textbf{professional} drivers/closed course.
A close-up follows of a **red car ’s spinning front wheel**, with a red brake caliper visible behind the rim.
The red bodywork fills the left of the frame.
The visuals shift through dark, blurred, high-speed shots : rows of bright lights in a dark setting, \textbf{then} fast-moving blurred views that appear to pass through or near a tunnel or shaded area, with bright daylight and trees flashing by.
The images are highly motion-blurred and the exact environment is unclear.
A calm landscape shot follows : rolling countryside with a row of tall, narrow trees lined up across a ridge, with distant hills or mountains in the background.
The front of a **red Alfa Romeo** is \textbf{then} shown in close-up.
The Alfa Romeo badge is centered on the grille, with glossy reflections across the hood.
The car appears to be stationary or moving slowly in this close frontal composition.
The commercial returns to road imagery : a curving road bordered by hills and vegetation, followed by close, abstract details of the car, including a blurred exterior surface and \textbf{then} a close-up of **dual circular exhaust pipes** at the rear.
Several shots emphasize sunlight filtering through trees.
The camera moves rapidly past trunks and branches, with strong glare and lens flare.
The sun appears low and bright, producing washed-out areas and purple/pink lens artifacts.
A frontal driving shot shows the red Alfa Romeo approaching on a narrow, wooded road.
Its slim headlights are on.
The car drives toward the camera through alternating patches of shade and intense sunlight.
Several frames are heavily overexposed by glare, briefly obscuring the car ’s details.
A side tracking shot \textbf{then} shows the red car moving past the camera, focusing on the side doors, wheel area, and glossy red paint.
Inside the car, there is a brief blurred view of a driver ’s hand on or near the steering wheel.
The driver is not clearly visible, and no identifying details can be confirmed.
The setting widens to a scenic mountain landscape with bright sun, lens flare, and dark mountain silhouettes.
The car is not clearly visible in that wide shot.
Near the end, the camera tracks along the rear side of the red sedan as it drives on a road bordered by greenery.
The final frames show the rear of the car in close-up : red taillights, rear window, trunk surface, Alfa Romeo badge partially visible, and the model name **“GIULIA”** on the trunk.
A partial license plate is visible but not fully readable.

% matched lemmas: professional, refer, then
\end{textsample}
