\begin{textsample}{POS Dim 7 – 1990 – Score 7.00 – 1990/tv\_com\_1990\_116.txt}  \label{ex:f7_pos_058}
The commercial begins with a black screen.
A small “ 90 ’s Commercials ” \textbf{watermark} is visible in the lower right throughout the sampled frames.
The scene then cuts to a bright, white kitchen.
A man in a light blue button-up shirt stands at the counter near a stove and cabinets, holding a stack of dishes or bowls against his chest.
He appears to be moving awkwardly while carrying multiple items.
The next shots show him at the sink and counter area with glass bowls and \textbf{utensils}.
He lowers dishes toward the counter or sink area, and the kitchen background includes white cabinetry, a stove, countertop items, and glass-front storage.
The commercial briefly cuts to a woman seated indoors, likely in a living room or dining area.
She wears a red shirt and faces the camera.
Behind her are warm-toned furnishings, including an orange/red blanket or \textbf{cushion} and a vase of flowers.
She appears to be addressing the viewer, but no spoken \textbf{content} is visually available.
The sequence returns to the man in the kitchen.
He looks down at small items or residue in his hand, then there is a close-up of the woman ’s hands in front of her red shirt.
Her palms and fingers are shown as if demonstrating or comparing something, but the exact \textbf{object} or substance is not clearly visible in the sampled frame.
The man opens or loads a dishwasher.
Several visibly dirty dishes, glassware, \textbf{utensils}, and cookware are arranged in the lower rack.
Some dishes have red/orange food residue.
He places items into the dishwasher, including a clear glass bowl or lid, and adjusts items in the rack.
The shots emphasize the cluttered, food-soiled load.
A close-up shows a green product box being held above the dishwasher ’s detergent cup.
The box has a large red-and-white “ Cascade ” logo.
The dishwasher ’s detergent compartment is visible in the foreground.
The commercial then cuts to a stylized top-down graphic or demonstration image : a circular or octagonal transparent dish-like shape on a blue background, filled with swirling red/orange and white material.
A vertical dark line runs down the center of the image.
The \textbf{purpose} of this graphic is not explicit from the frames alone, but it visually suggests a cleaning or \textbf{dissolving} demonstration.
Later, the man is shown holding a clear glass plate in the kitchen.
The plate appears clean and reflective.
He looks at it while holding it up.
Near the end, there is a product shot on a kitchen counter : a yellow bottle and a green box, both branded “ Cascade. ” The green box is prominently labeled “ Cascade, ” and additional small text is present but not fully legible at this resolution.
The background is softly blurred, with kitchen \textbf{objects} and a bowl of fruit visible.
The commercial ends by \textbf{fading} or cutting back to a black screen with the same lower-right \textbf{watermark}.

% matched lemmas: content, cushion, dissolve, fade, object, purpose, utensil, watermark
\end{textsample}
