\begin{textsample}{POS Dim 7 – 1960 – Score 7.00 – 1960/tv\_com\_1960\_39.txt}  \label{ex:f7_pos_037}
The commercial begins with a nearly black frame.
A small white \textbf{watermark} reading “ Nostalgic X’er ” appears at the lower right.
After about twelve seconds, the image cuts to a close-up of camera equipment laid out on a surface.
A Polaroid-style instant camera and/or related device is visible, along with a boxy accessory or film pack.
Hands are partially visible near the items, suggesting someone is handling or presenting the equipment.
The image \textbf{quality} is \textbf{soft} and somewhat blurred, so small \textbf{printed} details on the \textbf{objects} are not readable.
The next shot shows a living-room setting.
An adult man with gray hair sits on a sofa or chair holding a boxy instant camera facing the viewer.
A young \textbf{boy} sits close beside him, watching.
The background includes domestic décor such as flowers, curtains, furniture, and a lamp, giving the scene a home interior atmosphere.
The man appears to be demonstrating or showing the camera.
Later, the man turns toward the \textbf{boy} while holding a small rectangular instant \textbf{photograph} or card in one hand and a cup or mug in the other.
The camera rests against him or hangs near his chest.
The \textbf{boy} looks at the photograph/card.
Their body language suggests the man is showing the \textbf{boy} the result of using the camera.
In the final frame, large white title text appears over the living-room shot.
The visible text reads : “ Polaroid ’s Pronto!
Flash 400 Land Cameras. ” The man and \textbf{boy} remain seated behind the text, facing each other.
The “ Nostalgic X’er ” \textbf{watermark} remains at the lower right throughout the visible frames.

% matched lemmas: boy, object, photograph, printed, quality, soft, watermark
\end{textsample}
