\begin{textsample}{POS Dim 7 – 2000 – Score 4.00 – 2000/tv\_com\_2000\_93.txt}  \label{ex:f7_pos_070}
The commercial opens on a tropical-looking balcony or veranda.
A brightly colored parrot, with red-orange chest, blue and green wings, and a dark curved beak, is perched on a bamboo-style railing.
The setting includes white shutters, potted plants, palm-like foliage, and a distant blue sea or sky in the background.
The view then shifts wider, showing the balcony attached to a light-colored building, surrounded by dense green tropical plants.
The bamboo railing and raised deck are \textbf{prominent}, with the parrot still near the railing area.
Next, the camera moves through or cuts to more of the outdoor deck environment : bamboo railings, steps, and thick \textbf{leafy} plants.
The perspective emphasizes a lush garden walkway and the wooden/bamboo construction of the veranda.
A later shot shows a narrow wooden walkway bordered by plants leading toward a small seating area.
A chair is visible at the far end.
On the left side of the walkway, a white toilet paper roll is visible among the greenery, visually standing out from the natural surroundings.
The commercial then returns to a close-up of the parrot on the railing.
The \textbf{bird} leans forward slightly, its claws gripping the bamboo rail.
The background again shows shutters, railings, and blue sky.
The final frame is a product shot.
A package labeled “ Cottonelle ” is placed on a wooden surface beside a loose roll of toilet paper with a sheet trailing to the left.
The package is green and white and includes the text “ Aloe \& E. ” Behind it are a lattice screen, leaves, and \textbf{decorative} \textbf{objects}, maintaining the tropical veranda/garden visual theme.

% matched lemmas: bird, decorative, leafy, object, prominent
\end{textsample}
