\begin{textsample}{POS Dim 7 – 1970 – Score 10.00 – 1970/tv\_com\_1970\_43.txt}  \label{ex:f7_pos_004}
The commercial opens with an \textbf{indistinct}, dark close-up : a glossy reflective \textbf{object} appears near the upper left against a reddish-brown background, but the \textbf{object} is not clearly \textbf{identifiable} from the sampled frame.
It then cuts to a bright beach or lakeside setting.
A young girl in a yellow top stands on sand in the foreground.
Behind her are a striped beach umbrella, seated adults, a beach ball, and distant houses or shoreline features.
The image has a \textbf{soft}, slightly \textbf{hazy} look.
The setting shifts to a kitchen.
A smiling woman stands behind a counter holding and opening a jar.
The counter is filled with food items : tomatoes, \textbf{leafy} vegetables, a large bowl of chopped salad ingredients, eggs or peeled potatoes, and long green vegetables.
A refrigerator, cabinets, \textbf{appliances}, and a large plant by a window are visible in the background.
A transition overlays the kitchen woman with a close-up of the food preparation.
The large bowl of chopped salad fills the foreground, and the jar appears nearby.
The imagery suggests a \textbf{dissolve} from the kitchen scene into a close-up of the ingredients.
Next, a close-up shows the bowl being stirred with a wooden \textbf{spoon}.
Cubed pale ingredients and green flecks are visible.
To the right is a jar with a readable label : “ Hellmann ’s Real Mayonnaise. ” Tomatoes sit in the background.
The commercial then moves outdoors to a picnic table by water.
A young girl and a man in a black-and-white striped shirt sit at the table with plates and food in front of them.
The scene is bright and washed with warm light.
A wider view shows several people seated around the picnic table near the shoreline.
A person in a peach or orange top is close to the camera with their back partly blocking the view, while others sit around the table eating or \textbf{serving} food.
The water, low wall, and distant shore remain visible.
A close-up focuses on the young girl at the table.
She holds a fork and appears to be eating or preparing to take a bite from her plate.
The lake or water is visible behind her.
Another close-up shows a smiling woman leaning toward the table, looking downward at the food or someone seated nearby.
The background remains the same outdoor waterfront setting.
A wider shot returns to the picnic group seated around the table.
A large, softly \textbf{superimposed} image of the smiling woman ’s face overlays the scene, creating a double-exposure effect.
The group continues eating or interacting around the picnic table.
The final frame is a product shot.
A jar labeled “ Hellmann ’s Real Mayonnaise ” stands prominently on the picnic table in the right foreground.
Large white text on the left reads “ The BEST. ” In the blurred background, people remain seated at the outdoor table near the water.

% matched lemmas: appliance, dissolve, hazy, identifiable, indistinct, leafy, object, serve, soft, spoon, superimpose
\end{textsample}
