\begin{textsample}{POS Dim 7 – 1980 – Score 6.00 – 1980/tv\_com\_1980\_51.txt}  \label{ex:f7_pos_046}
The commercial opens in near darkness with three soft, out-of-focus colored lights : blue at lower left, red near the center, and green at upper right.
As the image sharpens, each light becomes a bright starburst with long pointed rays.
Behind them are thin, glowing geometric outlines like tall, transparent prisms in blue, red-orange, and green, set against a black \textbf{studio} background.
A burgundy or deep reddish-brown Cadillac gradually comes into view from the right.
At first only the hood, windshield, and roofline are visible beneath the colored starbursts.
The car ’s hood is long and flat, with a small Cadillac crest ornament near the front.
Through the windshield, the front seats and a pale steering wheel can be seen, but no driver or passengers are visible.
The setting is highly stylized rather than realistic : a dark \textbf{studio} with glossy, reflective flooring and colored light spilling across it in green, orange, blue, and purple.
The car is then shown more fully from the front and slightly to one side.
Its squared-off 1980s shape is prominent : a broad rectangular grille, pairs of rectangular headlights, chrome trim, and a \textbf{formal} roofline.
The front bumper and lower lights reflect warmly on the floor.
A dark license plate area at the front carries the Cadillac name in white \textbf{cursive} \textbf{script}.
The right-side front door area is dark and glossy, and the wire-spoke wheel with a whitewall tire catches highlights along the rim.
The view changes to close details of the front corner.
The rectangular headlamp cluster fills the left side of the image, with an amber side \textbf{marker} beside it and the front wheel and fender to the right.
The paint reflects large white bands of light, emphasizing the smooth, polished bodywork.
The chrome wheel cover, whitewall tire, and crisp body lines are shown in close-up, with the dark \textbf{studio} and green reflections behind them.
A layered transition blends the side of the car with the front end, then settles on the front grille and hood from above.
The Cadillac crest ornament sits centered on the hood, while the grille ’s vertical and horizontal bars \textbf{form} a wide, \textbf{formal} rectangle.
The bumper and lower amber lights glow beneath.
The glossy floor below shows patterned reflections, almost like a gridded or \textbf{textured} surface lit in blue and purple.
Another detail view glides along the upper side of the car : the burgundy roof, the chrome trim around the side window, and the dark interior with the top of a seat visible through the glass.
The imagery then returns to the front.
The left headlight pair, the grille, and the hood ornament dominate the scene, with the blue and red starburst lights still shining in the dark background.
The Cadillac \textbf{script} is again visible on the front plate, and a small \textbf{script} badge appears on the grille area, consistent with the DeVille model identification.
The front of the car remains the focus as the \textbf{composition} moves across the grille from left to right.
The hood ornament stands above the center line, catching a green starburst reflection.
The rectangular headlights on both sides, amber corner lamps, chrome bumper, and dark grille are shown in sequence.
The lower amber light glows warmly, and the wheel at the right edge comes back into view, its chrome spokes reflecting the \textbf{studio} lights.
A final angled view shows the front right corner and wheel with the colored starbursts layered over the car ’s glossy body.
The three colored lights—blue low on the left, red near the center, and green high on the right—return as a repeating visual motif around the burgundy Cadillac.
The car remains stationary, presented like an object on display in a dark showroom-like \textbf{studio}.
Near the end, large centered on-screen text appears over the car.
It reads “ CHICAGOLAND ” in bold white \textbf{capital} letters across the top, “ Cadillac ” in a larger white \textbf{cursive} \textbf{script} through the middle, and “ DEALERS ” in bold white \textbf{capital} letters below.
The text sits over the hood and windshield area while the Cadillac remains visible behind it, with the colored starburst lights still shining around the vehicle.

% matched lemmas: capital, composition, cursive, form, formal, marker, script, studio, textured
\end{textsample}
