\begin{textsample}{POS Dim 7 – 1960 – Score 17.00 – 1960/tv\_com\_1960\_48.txt}  \label{ex:f7_pos_021}
The commercial opens in black and white outdoors beside a stretch of water or a shallow shoreline.
A smiling adult man in a light jacket sits on the ground with a young blond boy tucked beside him.
The boy wears a long-sleeved top, shorts, socks, and shoes, and sits with one leg extended.
Both face forward and smile warmly ; the man leans slightly toward the child, one arm close behind him, suggesting they are watching or sharing a moment of play near the water.
A detailed tanker vessel then appears floating on rippling water.
It has a dark hull with white upper structures, thin masts and railings, and the word “ TEXACO ” painted in large letters on the side.
The bow points to the right, and the ship glides steadily across the water, leaving dark reflections beneath it.
The rear superstructure has a small dark funnel marked with a Texaco-style star emblem, while the midsection is lined with pipes, posts, and deck details that make it look like a scaled-down oil tanker rather than a simple toy.
The scene moves indoors to a \textbf{studio} office setting.
A clean-cut adult male \textbf{presenter} sits behind a desk, facing forward.
He has neatly \textbf{combed} dark hair and wears a dark suit, white shirt, striped tie, and pocket square.
Behind him are shelves filled with rows of books or binders, and a framed picture hangs to one side.
On the desk at his left is a small upright display or miniature pump-like sign.
He begins speaking directly to the viewer, hands folded near a small card on the desk, then turns to his right and reaches offscreen.
He lifts the Texaco tanker toy into view with both hands.
The model is long and narrow, with a dark hull, white cabins, small masts, deck railings, and “ TEXACO ” printed along the side.
He holds it horizontally at chest height, turning it slightly so the side and deck details are \textbf{easy} to see.
His expression is \textbf{pleasant} and confident as he presents it, looking between the toy and the viewer.
The tanker appears quite large for a toy, spanning much of the width of his \textbf{torso}.
A closer view focuses on the rear section of the toy.
The \textbf{presenter} ’s fingers point to the white cabin roof and a dark smokestack with a circular Texaco star emblem.
Small rectangular shapes on the roof and rows of tiny window markings are visible.
The deck railings, pipes, and upright posts run along the tanker ’s midsection, emphasizing the model ’s detailed construction.
He then tilts the tanker upward, showing the underside of the hull.
Small round wheels are visible underneath, tucked partly into the dark body so they do not dominate the ship shape.
He gestures under the hull with one hand, \textbf{drawing} \textbf{attention} to these wheels.
After showing the underside, he lowers the tanker onto the desktop and guides it along the surface, demonstrating that it can rest and move on land as well as float in water.
His hand stays on the top of the model as it rolls or slides smoothly across the desk.
The \textbf{presenter} continues speaking with the tanker \textbf{positioned} in front of him.
He \textbf{alternates} between looking at the toy and looking directly forward.
The model sits lengthwise across the lower part of the desk, its masts and white cabin sections rising in front of his suit.
He smiles slightly as he finishes the demonstration and rests one hand on the toy.
A small model gasoline pump appears on the tabletop.
Its front label is clearly marked “ Sky Chief Su-preme, ” with “ GASOLINE ” and “ PETROX ” below, plus the Texaco star emblem.
A hose and nozzle hang along the side.
A suited hand \textbf{enters} from the right and points toward the pump ’s label and upper meter area.
A second miniature pump is brought into view beside it, and the focus shifts to a pump labeled “ Fire Chief ” with “ GASOLINE ” beneath it and the Texaco star symbol on the front.
The hand points between the pumps, visually \textbf{linking} the tanker offer to the two gasoline products named on the miniature pump faces.
The view returns to the \textbf{presenter} in the office.
He looks down briefly, then back up, continuing his explanation.
He raises a plain light-colored rectangular coupon or card beside his face, holding it upright between his fingers.
The card has \textbf{faint} markings, but the \textbf{writing} is not readable in the image.
He keeps it lifted for several moments while \textbf{addressing} the viewer, then lowers it out of sight.
Near the end, the office view widens.
A large Texaco logo is now visible on the wall to the \textbf{presenter} ’s left : a circle enclosing a \textbf{star-like} “ T ” shape with the word “ TEXACO ” across the top.
The toy tanker rests on the desk in front of him.
He turns toward it, adjusts its \textbf{position}, and then lifts it again with both hands.
Holding the tanker centered at chest \textbf{level}, he presents it squarely to the viewer.
The dark hull with “ TEXACO ” printed on the side is prominent, with white cabins at both ends, small masts, railings, and deck details running along the top.
He smiles directly forward, keeping the toy steady in the foreground while the Texaco wall logo remains visible behind him.

% matched lemmas: address, alternate, attention, comb, draw, easy, enter, faint, level, link, pleasant, position, presenter, star-like, studio, torso, writing
\end{textsample}
