\begin{textsample}{POS Dim 7 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_100.txt}  \label{ex:f7_pos_053}
The commercial begins with an almost entirely black frame, with only very \textbf{faint}, \textbf{indistinct} shapes near the bottom ; no clear setting or subject is visible.
It then \textbf{dissolves} into an outdoor scene with strong image overlap.
Two people wearing light-colored caps or brimmed hats appear in the foreground, seen from the side, with green foliage behind them.
The frame looks layered, as if one shot is \textbf{fading} over another ; small figures or \textbf{objects} are faintly visible near the lower center, but the details are \textbf{unclear}.
The next sampled \textbf{moment} is a fast, blurred action shot.
A figure in a yellow or gold top appears to be moving quickly across an outdoor area, partially obscured by a bright vertical \textbf{object} in the foreground.
The motion blur makes the activity difficult to identify.
Later, another \textbf{dissolve} or \textbf{superimposed} image shows a public outdoor setting, possibly a street or plaza, with several people in dark clothing and hats.
A man in the foreground appears to be walking or gesturing.
The background includes a reddish building or architectural façade.
Because of the \textbf{overlapping} images, individual actions are hard to separate.
The sequence then shifts to a garden or yard scene.
A person on the left, wearing a light top and darker lower \textbf{garment}, reaches toward something dark in the center of the frame.
Dense plants and shrubs fill the foreground and background, with part of a house or structure visible behind them.
The central dark shape may be an animal or \textbf{object}, but it is not clear from the frame.
The commercial ends on a close-up of a smiling young girl wearing a straw boater-style hat with a dark band and a visible letter “ R ” on the front.
Other people are partly visible around her in a dark crowd-like setting.
Large white text reading “ UNITED ” appears across the lower part of the frame, with a small logo mark in the lower-left corner.

% matched lemmas: dissolve, fade, faint, garment, indistinct, moment, object, overlapping, superimpose, unclear
\end{textsample}
