\begin{textsample}{POS Dim 7 – 2010 – Score 7.00 – 2010/tv\_com\_2010\_20.txt}  \label{ex:f7_pos_059}
A black PlayStation symbol appears centered on a plain pale background.
The scene then opens in a comfortable living room.
In the foreground, a slim, light-skinned boy with shaggy brown hair and a gray striped T-shirt faces forward as if \textbf{addressing} someone directly.
White on-screen text identifies him as “ Dan Sweeney ” and “ Frustrated Brother. ” An ESRB “ E ” rating icon appears at the lower left.
Behind him, slightly out of focus on a couch, an older dark-haired boy or teen lounges with his legs stretched out, holding and playing a black handheld PSP.
Beside him, a young woman with long dark hair reclines casually on the sofa.
The room looks domestic and lived-in, with a lamp on the right and a kitchen visible in the background.
Dan ’s face fills more of the view as he continues speaking.
His expression is \textbf{earnest} and worried, his mouth slightly open and his eyes fixed forward.
The older boy behind him stays absorbed in the PSP, while the young woman remains relaxed on the couch.
The setting changes to a bright barbershop.
A Black boy or young teen sits in a barber chair wearing a pale blue barber cape, holding a black PSP in both hands.
A woman barber stands behind him, trimming his hair with electric clippers.
She wears a purple top and jewelry, and her \textbf{attention} is on the haircut.
The shop has a large front window with horizontal blinds and red painted lettering, seen backwards from inside.
White text at the lower right identifies the boy as “ Marcus Rivers ” and “ Sibling Conflict Advisor. ” Marcus looks up from the PSP with a knowing, slightly amused expression, then glances back down at the device as the barber continues cutting.
A wider view shows Marcus centered in the barber chair, draped in the blue cape with purple footwear visible near the footrest.
The barbershop floor has a black-and-white check pattern, and the glass door on the right has a “ closed ” sign.
Marcus remains seated and calm, still holding the PSP while the barber works behind him.
Marcus then raises the PSP toward the viewer, bringing the device forward until it dominates the image.
The black Sony PSP has a glossy screen, circular controls on both sides, and the “ PSP ” logo below the display.
On the screen, the game shows a colorful kart-racing scene with bright green \textbf{markers} and race-position numbers in the corner.
A small disclaimer appears near the bottom right : “ Game and System sold separately. ” The game visuals change rapidly : first a car racing along a track, then a workshop-like customization area where a small vehicle changes appearance, including a yellow car.
Another screen shows an overhead track-building view with a curved road and a red circular section.
The display then returns to racing, with small cartoonish drivers in karts competing on different tracks. \textbf{Position} numbers and timers appear in the game interface, and the vehicles move through environments that include sandy or canyon-like terrain, ramps, curves, and colorful track decorations.
Back in the living room, Dan is again in the foreground, still facing forward.
The older boy in the background continues to play the PSP on the couch, focused on the handheld.
The young woman sits beside him, turned slightly toward the room.
Dan appears to be waiting for an answer, his \textbf{posture} upright and attentive.
The barbershop returns.
Marcus sits low in the chair under the pale blue cape, still gripping the PSP.
He tilts his head and looks up with a mischievous, confident look, as if giving advice.
Behind him, the barber ’s hand and a red \textbf{comb} or tool are visible near the left edge.
Through the blinds, a passerby moves outside the window.
Marcus keeps eye contact forward for several moments, eyebrows slightly raised, while the PSP rests in his hands.
The living room appears again, now with the focus on the couch behind Dan.
The older boy on the left is still intent on the PSP, holding it close in both hands.
The young woman next to him is more clearly visible : she has long black hair, a plaid shirt layered over a dark top, and a \textbf{faint}, relaxed smile.
Dan ’s striped shirt and face are blurred in the foreground, making the two people on the couch the center of \textbf{attention}.
A moment later, Dan ’s face comes back into focus.
He looks startled and wide-eyed, lips pressed together, as if he has just understood Marcus ’s suggestion.
The older boy and young woman remain blurred behind him.
The commercial ends with a clean graphic sequence on a pale background.
Large bold black text appears reading “ STEP YOUR UP. ” with the word “ GAME ” in blue sliding or appearing above to complete the \textbf{phrase} “ STEP YOUR GAME UP. ” A small trademark symbol follows “ UP. ” Then a black PSP floats centered on the same pale background.
Its screen shows Marcus seated in a room, wearing a blue jacket over a colorful shirt, as if appearing in a video on the device.
The handheld \textbf{rotates} to show its slim side \textbf{profile}, and gray text below reads “ MARCUSPSP.COM. ” The PSP turns back to face forward, with Marcus visible again on the screen, then \textbf{rotates} once more to show the back and side of the device.
The final screen returns to a plain pale background with three centered logos : the PlayStation symbol, the “ PSP ” wordmark with “ PlayStation Portable ” beneath it, and a purple ModNation Racers-style logo.

% matched lemmas: address, attention, comb, earnest, faint, marker, phrase, position, posture, profile, rotate
\end{textsample}
