\begin{textsample}{POS Dim 7 – 1950 – Score 15.00 – 1950/tv\_com\_1950\_84.txt}  \label{ex:f7_pos_017}
A brightly colored \textbf{studio} set appears against a plain green background.
Across the lower part of the set are fluffy white cloud-like shapes and flat, oversized Chevrolet bowtie silhouettes in pale beige and green.
In the center, a red sign with large white letters reads “ CHEVROLET. ” A small “ Not For Broadcast ” label is visible near the upper left, and a timecode box sits near the lower left.
Two adult \textbf{presenters} \textbf{enter} and stand on the central bowtie-shaped platform.
The man has dark, neatly \textbf{combed} hair and wears a deep red blazer, white shirt, light green tie, tan trousers, and dark shoes.
The woman has short, \textbf{curled} blonde hair and wears a bright magenta blouse with a small brooch, a wide dark full skirt that flares outward, and matching high heels.
She holds or brushes the skirt as it swishes, revealing flashes of pink lining.
They smile and face forward as if \textbf{addressing} the \textbf{audience}, standing side by side on the raised shape amid the cloud-like scenery.
The view \textbf{alternates} between them.
The man is shown closer, looking forward and speaking with a composed, cheerful expression ; the woman stands just to his side at first, smiling toward him.
Then the focus shifts to the woman alone.
She sits or perches slightly, hands near her lap, smiling directly forward in the same green \textbf{studio} space, her dark skirt spread around her.
The two are then seen full-length again on the platform.
They step apart in opposite directions along the set ’s flat geometric shapes, moving like dancers.
The man walks left and the woman walks right, both keeping their balance on the raised pieces.
They turn back toward each other, the woman ’s skirt swinging in a wide circle as she pivots.
From farther back, the whole \textbf{stage} \textbf{composition} is visible : green \textbf{backdrop}, white clouds, bowtie shapes, and the red “ CHEVROLET ” sign below them.
Large white characters reading “ ’ 59 ” appear high above the \textbf{presenters}.
Both of them raise an arm upward toward the number, \textbf{drawing} \textbf{attention} to it.
Almost immediately, the image cuts to a shiny 1959 Chevrolet in a simple \textbf{studio} setting : a pale green car seen from the rear three-quarter angle, with long horizontal lines, prominent tailfins, oval rear lights, chrome trim, whitewall tires, and a glossy floor beneath it.
The car is stationary and displayed like a featured product.
The view returns to the \textbf{presenters} on the Chevrolet set with “ ’ 59 ” still above them, their arms lifted toward the text.
The woman is then shown closer again, seated and smiling broadly, with the white cloud shapes behind her.
The man appears in a similar close view, seated with one knee raised and one arm resting casually, smiling toward the \textbf{audience}.
They continue appearing separately in close views, both \textbf{maintaining} friendly expressions and polished \textbf{stage} \textbf{posture}.
The man rises or leans forward slightly, speaking directly forward.
He gestures subtly with one hand as he stands against the green background, his red blazer and green tie matching the set ’s color scheme.
The woman follows in close view, smiling and facing forward, her dark full skirt filling the lower part of the image.
Both \textbf{presenters} stand again on the red central \textbf{pedestal} above the large “ CHEVROLET ” sign.
The man steps up first, and the woman moves beside him, placing a hand lightly near his shoulder as they stand close together.
They face forward, then glance toward one another.
The woman ’s skirt continues to ripple as she shifts her feet.
They smile together on the \textbf{pedestal}, framed by the green \textbf{backdrop} and cloud shapes.
They then sit on either side of the central platform above the “ CHEVROLET ” sign, the man on the left and the woman on the right.
Another car appears briefly : a pink or rose-colored Chevrolet station wagon or sedan-wagon viewed from the rear three-quarter angle.
It has chrome bumpers, tailfins, whitewall tires, and a rear license plate that reads “ C1959. ” The car sits still in a \textbf{studio} display area with a light floor and neutral background.
The scene returns to the two \textbf{presenters} seated on the Chevrolet set.
The \textbf{presenters} move again across the bowtie shapes.
The man steps along the platform while the woman turns, her skirt lifting outward in a circular flare.
They then lean over a beige part of the set, both smiling toward the \textbf{audience}, their upper bodies resting casually on the flat shape as if it were a counter or railing.
The woman gestures downward and forward, then both begin to rise.
Standing side by side, the man extends one hand outward in a presenting gesture while the woman faces forward, smiling.
They come together closely, his arm around or behind her, and both look out toward the \textbf{audience}.
Large white text appears above them : “ THURS.
OCT. 16. ” The woman lifts a hand near her face in a small wave or flourish beneath the date.
They look at each other briefly, then face forward again, smiling.
The date text disappears, leaving the green \textbf{backdrop}.
The two remain close together, the woman ’s full dark skirt spreading out in a bell shape.
The man gestures with one hand while standing slightly angled toward her, then both stand centered on the red \textbf{pedestal}.
As the view widens, the large white “ ’ 59 ” reappears above them, and the red “ CHEVROLET ” sign is visible below.
They stand upright and still for a moment, framed symmetrically by the clouds and bowtie shapes.
The pair glance at one another under the “ ’ 59, ” then face front again.
The woman extends one arm outward to the side in a \textbf{graceful} presenting pose.
Another brief product display follows : a pale green and white 1959 Chevrolet seen from the rear side, again emphasizing the long body, tailfins, chrome trim, and whitewall tires on a glossy \textbf{studio} floor.
The commercial returns to the \textbf{presenters} on the Chevrolet set, arms opened slightly as if presenting the car and the brand, with “ ’ 59 ” overhead and the large “ CHEVROLET ” sign below.

% matched lemmas: address, alternate, attention, audience, backdrop, comb, composition, curl, draw, enter, graceful, maintain, pedestal, posture, presenter, stage, studio
\end{textsample}
