\begin{textsample}{POS Dim 7 – 1970 – Score 6.00 – 1970/tv\_com\_1970\_8.txt}  \label{ex:f7_pos_039}
A young blonde woman appears against a bright white background, her face softly lit and slightly hazy.
She has long, \textbf{styled} hair swept back from her forehead, blue eye makeup, rosy cheeks, gold shell-like \textbf{earrings}, and a pale scarf tied at the neck under a light gray or beige coat.
She smiles and turns her head, then pivots so her hair swings over her shoulders.
As she moves, the white space reveals mirrored panels around her, multiplying her reflection on both sides.
She poses with one hand in her coat pocket while the pink-and-gray scarf flutters outward, creating a \textbf{flowing} shape across her chest.
Her reflections show her from the side and back, so she appears surrounded by several versions of herself in the same coat.
The focus drops to her footwear.
A black leather boot with a rounded toe, thick high heel, and shiny finish stands on the white floor, reflected repeatedly in the mirrors.
Near the ankle is a small decorative gold buckle or ring detail.
The boot remains still while the mirror images show the heel and side \textbf{profile} from several angles.
Bold white lettering appears beside it : “ SPECIAL PRICE \$30, ” with a smaller comparison price underneath that appears to read about \$39.90.
A second young woman appears in the mirrored white setting.
She has long brown hair and wears a tan cowboy hat with a wide brim.
She smiles playfully at her reflection, raising both index fingers near her face as if pointing or dancing with the mirrored image.
She wears a red vest over a striped or plaid shirt and a full gray skirt.
As she turns, the mirrors create multiple copies of her in the cowboy hat, some facing forward, some turned away.
She moves lightly with her hands near her waist and the skirt swaying, giving the impression of a cheerful, western-inspired outfit.
Her boots are then shown : tall reddish-brown leather boots with black laces up the front, a rounded toe, a sturdy low stacked heel, and a light-colored sole edge.
The white mirrored floor reflects the boots so several pairs seem to stand around her.
The boots fill \textbf{most} of the image, emphasizing the shiny leather, the lacing, and the warm orange-red color.
Large white text appears beside the boot : “ \$30 LEATHER, ” with a smaller comparison price below that again appears to reference \$39.90.
A third young woman appears, a Black woman with a short rounded \textbf{hairstyle}.
She wears gold round \textbf{earrings}, a gray jacket, a white high-neck blouse with a soft \textbf{ruffled} front, a dark skirt, and a light-colored shoulder strap crossing from one shoulder down her side.
She smiles broadly and turns in the mirrored white room, with her reflections visible behind her.
She holds or adjusts the long strap at her side while walking or posing, her body angled first toward the viewer and then in \textbf{profile}.
The reflections show the back of her jacket and skirt, and the strap hanging down.
Her boots are shown in warm tan leather.
They have a squared, rounded toe, a platform-like sole, and a chunky stacked heel.
A decorative seam or zipper line runs down the side, with a small pull or tab detail near the ankle.
The mirrors show multiple angles of the same tan boot.
White text appears beside it : “ \$30, ” and below it, “ LIMITED TIME ONLY. ” The three women then come together in the white \textbf{studio}.
The brunette in the cowboy hat moves in from one side, the blonde in the pale coat stands in the middle, and the Black woman in the gray jacket stands on the other side.
They face one another briefly, smiling, then turn forward as a group.
The blonde stands centered, with the western-styled woman to her left and the woman in the gray jacket to her right.
They pose shoulder to shoulder, smiling and lightly moving their arms as if stepping into place together.
The boots are presented together at the end : the black heeled boot, the tan side-detail boot, and the reddish lace-up boot line up side by side on the white floor.
Above them, the Fayva logo appears in bold white lettering, with the tagline underneath : “ a different kind of shoe store. ” The final image returns to the three women ’s faces close together, all smiling warmly : the cowboy-hatted brunette on the left, the blonde in the center, and the Black woman on the right.

% matched lemmas: earring, flowing, hairstyle, most, profile, ruffle, studio, style
\end{textsample}
