\begin{textsample}{POS Dim 7 – 1950 – Score 13.00 – 1950/tv\_com\_1950\_105.txt}  \label{ex:f7_pos_018}
It begins with a plain purple screen, then shifts to black-and-white vacation imagery.
A broad tropical shoreline stretches across the view, with calm water in the foreground and a line of palm trees and resort buildings in the background.
Small boats move across the shallow water ; several people sit in long canoe-like boats while others swim or stand near the beach.
The scene becomes busier and closer : a crowded resort beach appears, with many vacationers in swimsuits wading, swimming, walking along the sand, and gathering near the water ’s edge.
Tall palms lean over the beach, and large light-colored hotel buildings stand behind the crowd, giving the setting the look of a sunny seaside holiday resort.
Over this beach scene, a large Western Union telegram \textbf{form} appears in the middle of the picture, tilted slightly as if floating in front of the resort.
It \textbf{grows} until it dominates the view.
Across the top it reads “ WESTERN UNION TELEGRAM, ” and in the center, in bold \textbf{capital} letters, “ IT ’S WISE TO WIRE. ” The beach remains visible behind it at first, with swimmers and boats partially obscured by the \textbf{form}.
The wording on the \textbf{form} then changes to a typed message : “ HAVING WONDERFUL VACATION.
WEATHER GREAT BUT CASH RUNNING LOW.
PLEASE WIRE ONE HUNDRED DOLLARS — GRANT. ” The telegram fills \textbf{most} of the image, visually turning the vacation problem into a written request for money.
The setting changes to a simple \textbf{studio} desk.
A middle-aged man with light skin, neatly \textbf{combed} dark hair, and a \textbf{clean-shaven} face sits facing forward.
He wears a light-colored suit jacket, white shirt, dark tie, and a folded pocket square.
His \textbf{posture} is upright and composed, with his forearms resting on a polished dark tabletop.
A small paper lies in front of him.
He looks toward the viewer as if explaining the service.
After a moment, he picks up a rectangular paper or \textbf{form} with both hands and holds it chest-high, angled slightly toward the camera.
The paper has lines of text on it, though the smaller wording is not fully readable at this distance.
He lowers it again, remaining calm and businesslike against a plain, softly lit background.
A large document then fills the view : a “ WESTERN UNION TELEGRAPHIC MONEY ORDER ” \textbf{form} lying on a wooden surface.
The top line clearly names the service, and below it, large text reads “ MONEY-BY-WIRE : ”.
Small boxed messages appear near the top corners, but they are too small to read clearly.
The \textbf{blank} space beneath “ MONEY-BY-WIRE : ” is then filled with bold typed lines : “ ANY AMOUNT, ” “ ANYWHERE, ” and “ ANY TIME OF THE DAY OR NIGHT. ” The \textbf{form} presents the service in a clear, official-looking layout, like a printed financial document.
The view changes to a countertop demonstration beside a prominent rectangular sign on a stand.
The sign reads “ WESTERN UNION ” in large letters, with “ Everywhere ” written below in a \textbf{script} \textbf{style}.
Only the arms and \textbf{torso} of a person behind the counter are visible ; the person wears a light shirt with sleeves rolled up and a dark apron or skirt.
On the counter are a sheet of paper, a small card, and a stack of paper money.
The person ’s hands handle bills and small slips, placing and arranging them next to the Western Union sign.
The stack of money \textbf{grows} as bills are laid down in a neat pile, while the paper \textbf{form} remains nearby on the tabletop.
The actions visually suggest processing a money order or preparing a cash payment.
Another hand, \textbf{entering} from the lower left and wearing a dark suit sleeve with a light cuff, reaches toward the stack of bills.
This hand gathers the money from the counter, then works briefly with a small dark object near the paperwork, as if completing or marking the transaction.
The \textbf{form} is then lifted from the counter and held up.
A close view of the raised document shows the top reading “ WESTERN UNION TELEGRAPHIC MONEY ORDER. ” In large typed lines, the message on the \textbf{form} reads : “ ENJOY YOURSELF — ALL WELL AT HOME.
SEE YOU IN A FEW DAYS. ” At the bottom, it is signed “ DAD. ” The money order is held at an angle by a hand at the lower left, with the dark background making the white paper and typed message stand out clearly.
The image returns to the suited spokesman at the desk.
He sits in the same plain \textbf{studio} setting, with papers resting under his hands on the polished tabletop.
He faces forward, \textbf{maintaining} a steady, professional expression.
As the commercial closes, he remains centered, composed, and attentive, visually reinforcing the Western Union money-by-wire service that has just been shown through the telegram, the money order \textbf{form}, the counter transaction, and the personal message.

% matched lemmas: blank, capital, clean-shaven, comb, enter, form, grow, maintain, most, posture, script, studio, style, torso
\end{textsample}
