\begin{textsample}{POS Dim 7 – 1980 – Score 9.00 – 1980/tv\_com\_1980\_29.txt}  \label{ex:f7_pos_042}
The commercial begins with a very dark, \textbf{indistinct} frame.
No clear \textbf{objects}, people, or setting can be identified at the start.
A \textbf{soft}, layered visual transition follows.
Multiple images appear \textbf{superimposed} : a person in a yellow top is visible, and a man in a shirt and tie appears faintly over the scene.
The imagery is \textbf{hazy} and partly transparent, making the exact setting and actions \textbf{unclear}.
The \textbf{overlapping} visuals suggest a montage or \textbf{dissolve} effect rather than a single stable shot.
The next sampled frame shows a child or young person wearing a yellow shirt, holding a blue spray bottle with a white spray nozzle.
The person is turned partly toward the camera and appears to be smiling.
The background remains \textbf{soft} and \textbf{indistinct}, and the image still has a translucent, dreamlike \textbf{quality}.
The commercial then cuts to a clear close-up of a product label.
The text reads “ CLOROX Prewash ” in large blue letters.
Beneath it, smaller text reads “ LAUNDRY SOIL AND STAIN REMOVER. ” The label uses a white central field with red, orange, and blue geometric bands around it.
Later, the same “ CLOROX Prewash ” label remains on screen, now with another image faintly \textbf{superimposed} over it.
A person ’s face or figure is visible behind or through the product label, but the overlay makes the details \textbf{unclear}.
The label text is still readable, emphasizing the product name and \textbf{purpose}.
The final frame shows a smiling blonde woman wearing large eyeglasses and a purple uniform-style top with a light collar.
She holds up a blue Clorox Prewash spray bottle next to her face, presenting it toward the viewer.
A red-and-orange patch or logo-like design is visible on her sleeve.
The background is dark and plain, keeping visual focus on the woman and the product.

% matched lemmas: dissolve, hazy, indistinct, object, overlapping, purpose, quality, soft, superimpose, unclear
\end{textsample}
