\begin{textsample}{POS Dim 7 – 1970 – Score 11.00 – 1970/tv\_com\_1970\_5.txt}  \label{ex:f7_pos_003}
The commercial opens on a nearly black screen.
A circular “ Classic Commercial Archives ” \textbf{watermark} is visible at the lower left, and a \textbf{faint} archive \textbf{watermark} runs across the lower part of the image.
It then cuts to a very \textbf{soft}, blurry close-up of a pale mechanical-looking or object-like form.
The image is \textbf{indistinct}, and the \textbf{object} cannot be identified with confidence. \textbf{Faint} text appears near the bottom, but it is not legible enough to read fully.
The scene changes to a large dark-colored sedan driving on a residential or tree-lined street.
The car is shown from the front/side as it moves along the road.
The vehicle has a \textbf{prominent} chrome grille and rectangular headlights, suggesting a 1970s luxury sedan.
The background includes trees, sidewalks, and houses or buildings.
A closer exterior shot emphasizes the front of the car : the wide chrome grille, hood ornament, rectangular headlamps, and front bumper fill most of the frame.
The car is either stopped or moving slowly near a curb.
The commercial then moves inside the car.
An older man with glasses, wearing a suit and tie, is seen through or over a partition-like surface, seated in the rear passenger area.
He appears to be handling something near his mouth or hands, but the \textbf{object} is not clearly \textbf{identifiable} in this frame.
The car is shown again from the front, driving toward the camera on a sunny, tree-lined street.
Through the windshield, multiple occupants are visible : a driver in front and at least one passenger in the rear.
The large grille and hood ornament remain visually \textbf{prominent}.
Several shots use \textbf{dissolves} or overlays between the exterior of the moving car and interior views.
One composite image shows the front grille and windshield overlaid with a view of the steering wheel and dashboard area.
Another closer interior shot shows a hand near the steering wheel or controls ; the dashboard and steering wheel are visible, but the exact action is \textbf{unclear}.
A clearer interior shot shows the older man seated in the rear compartment.
He wears dark-framed glasses, a dark suit, white shirt, and tie.
He is holding and manipulating a small dark \textbf{object} or container with both hands on a tray-like surface in front of him.
The nature of the \textbf{object} is \textbf{unclear} from the sampled frames.
The next shot shows the driver in profile.
He is a middle-aged man with a beard or sideburns, wearing a dark suit, looking forward while driving.
The car interior is bright from daylight through the windows.
A close-up returns to the older man in the rear seat.
He holds a small dark item in one hand and a lighter-colored piece or cap in the other.
His face is centered, and he appears focused on the \textbf{object}.
The exact \textbf{object} and \textbf{purpose} remain \textbf{unclear} visually.
The exterior driving shots resume.
The dark sedan travels along a \textbf{broad} road with trees in the background.
One shot shows the car entering from the left/front, then another shows it passing quickly across the frame from left to right, creating motion blur along the body and wheels.
A final interior/exterior \textbf{dissolve} shows the older man ’s face overlaid with the car ’s exterior, continuing the visual association between passenger comfort and the vehicle.
The commercial ends on a black background with a circular emblem at the top containing a sign with the words “ MERCURY ” and “ LINCOLN ” and an animal figure above it.
Large white text across the lower-middle reads “ MERCURY MONARCH. ” Smaller text beneath reads “ LINCOLN-MERCURY DIVISION. ” At the lower right, a Ford oval logo appears with anniversary-style wording that is partially visible but not fully clear.

% matched lemmas: broad, dissolve, faint, identifiable, indistinct, object, prominent, purpose, soft, unclear, watermark
\end{textsample}
