\begin{textsample}{POS Dim 7 – 1970 – Score 8.00 – 1970/tv\_com\_1970\_94.txt}  \label{ex:f7_pos_013}
The commercial \textbf{unfolds} as a sequence of stylized brand-logo images and abstract graphic/product-like close-ups. 1. **Opening frame:** The image is very dark, with only the right edge of a large, cropped white letter visible.
It appears to be part of the “ GTE ” logo, but most of the logo is off-screen or obscured. 2. **Logo reveal with \textbf{object} above:** A centered **GTE** logo appears in large white block letters inside a dark rounded rectangle.
The logo sits on a softly lit surface and casts a dark shadow/reflection downward.
Above it is a small upright rectangular \textbf{object} or card with a circular design on it.
The background has a muted blue-gray/purple gradient and visible horizontal scanlines. 3. **Alternating \textbf{object} above the logo:** The same GTE logo remains centered, but the \textbf{object} above changes to a plain pale rectangular block.
The lighting remains \textbf{soft} and theatrical, with a spotlight-like glow behind the logo. 4. **Repeated alternation:** The frame returns to the version with the small card-like \textbf{object} above the GTE logo.
The card has a darker circular graphic, though its details are not clearly readable. 5. **Plain block again:** The image switches back to the pale rectangular block above the logo.
The logo and its shadow stay in the same position. 6. **Card-like \textbf{object} again:** The small upright card with a circular design appears once more above the GTE logo.
The sequence creates a flickering or alternating visual effect between different \textbf{objects} placed over the brandmark. 7. **Array of circular elements:** The \textbf{object} above the logo changes to a grid of many small round white circles, arranged in rows.
These look like lights, buttons, or dials, though their exact \textbf{function} is \textbf{unclear}.
The GTE logo remains large beneath them. 8. **Close-up of colored grid/buttons:** The commercial cuts to a close-up of a geometric pattern : rectangular colored panels in pink, orange, and brown tones arranged in a grid, with a row of large yellow-orange circular shapes along the bottom.
The image suggests a panel of buttons or illuminated indicators, but the sampled frame does not make the \textbf{object} \textbf{identifiable}. 9. **Small logo on bright background:** A small **GTE** logo appears near the lower center of a pale blue-white background.
Above it is a \textbf{faint}, translucent vertical white shape, but it is \textbf{indistinct} and not clearly \textbf{identifiable}. 10. **Final logo shot:** The commercial ends on a large, centered **GTE** logo in white block letters inside a dark rounded rectangle.
It is dramatically backlit with a warm glow and casts a strong dark shadow/reflection downward.
The surrounding frame is mostly dark, emphasizing the brandmark.

% matched lemmas: faint, function, identifiable, indistinct, object, soft, unclear, unfold
\end{textsample}
