\begin{textsample}{POS Dim 7 – 1950 – Score 31.00 – 1950/tv\_com\_1950\_41.txt}  \label{ex:f7_pos_001}
The commercial opens in black and white on a \textbf{formal} \textbf{studio} set.
A \textbf{clean-shaven} adult man with dark, neatly \textbf{combed} hair stands facing forward in a dark suit, white shirt, and tie.
He holds a small card or papers at chest height as if introducing the segment.
Behind him, a large oval sign reads “ Revlon ” in \textbf{script}, set against a diamond-patterned \textbf{backdrop}.
At the far left edge, part of another suited man is visible, \textbf{cropped} so only one side of his body and face appear.
The \textbf{main} host smiles and speaks directly toward the viewer, occasionally lowering the card and shifting his hands while keeping an upright, presenter-like \textbf{posture}.
The scene changes to a woman \textbf{presenter} standing before a soft, decorative background with leafy or floral arrangements on either side.
She is an adult woman with \textbf{styled}, waved dark hair, \textbf{earrings}, a pendant necklace, and a light-toned sleeveless dress with a shiny embroidered or beaded bodice.
She faces forward, smiling, then speaks with small changes in expression, her shoulders squared and her hands out of view.
The setting looks \textbf{staged} and elegant, with bright lighting on her face and dress and darker, \textbf{textured} tones behind her.
The product is then displayed in a still-life arrangement.
Three upright lipstick cases stand on a sparkling, \textbf{textured} surface, surrounded by rounded fruit-like shapes and decorative foliage.
The cases differ in finish : one is pale and smooth, one darker and shinier with a decorative design, and one pale case has a striking crisscross or diamond pattern.
A gloved hand \textbf{enters} from the right and gently touches the patterned case, steadying it between the fingertips.
The hand tilts and lifts it slightly, showing its slim, tapered, hourglass-like silhouette and the engraved-looking pattern around the outside.
This visible patterned case corresponds to the Futurama case mentioned in the audio \textbf{context}.
The image shifts to a young adult woman seated at a small round table in a \textbf{graceful} domestic or garden-room setting.
She has a short, dark bob \textbf{hairstyle} and wears a large bow or floral headpiece near the top of her head, a light sleeveless dress with a draped \textbf{neckline}, and a long strand of beads.
A pale handbag rests on the tabletop in front of her, and a \textbf{pedestal} dish holding round fruit sits to her left.
Behind her are low stone or \textbf{textured} walls and floral branches, giving the space a refined patio or conservatory feel.
She leans slightly forward, opens or reaches into the handbag, and takes out a lipstick case.
She holds it in both hands, then raises it in her right hand near her face, studying it with a composed, pleased expression.
She turns the small case slowly, looking at it from different angles rather than applying it, as if admiring the object as a stylish accessory.
The demonstration then moves to a close view of gloved hands working with the lipstick system on a plain tabletop.
A patterned Futurama \textbf{base} stands upright with an open lipstick tube inside it, and a matching cap or \textbf{outer} piece stands nearby.
One gloved hand rests behind the product for support while the other points to the central refill section.
The demonstrator grips the \textbf{inner} lipstick refill and lifts it straight up out of the patterned \textbf{base}, leaving the \textbf{base} below and the cap beside it.
The refill is shown suspended above the case, making clear that the lipstick portion separates from the permanent \textbf{outer} case.
The hands then reverse the action.
The refill is lowered back into the patterned \textbf{base}, aligned carefully, and pressed down until it sits securely inside.
The demonstrator ’s finger remains near the joint, emphasizing where the refill \textbf{fits} into the case.
The matching cap or \textbf{outer} sleeve is picked up and brought over the top, enclosing the lipstick to \textbf{form} a complete, neat cylindrical case again.
As the hand finishes closing and holding the patterned case, bold on-screen \textbf{writing} appears across the lower part of the image : “ Save 35¢ on every LIPSTICK. ” The words “ Save 35¢ ” are in large \textbf{flowing} \textbf{script}, while “ LIPSTICK ” is in large block \textbf{capitals}.
The gloved hand continues to hold and angle the closed case above the text so both the product and the saving message are visible together.
The woman \textbf{presenter} reappears against the floral \textbf{studio} background, again facing forward in her elegant dress and jewelry.
She smiles and speaks calmly, standing centered between the decorative branches.
Her expression is \textbf{poised} and confident, with only subtle head and mouth movement as she continues the product message.
Finally, the commercial returns to the male host in the Revlon \textbf{studio}.
The oval “ Revlon ” sign remains behind him on the diamond-patterned wall.
He now holds a lipstick case upright in one hand near his face, using it almost like a \textbf{pointer}.
He raises his index finger alongside it, then gestures lightly with the case as he continues speaking.
His \textbf{posture} remains \textbf{formal} and presenter-like, and he looks directly forward.
The \textbf{closing} moments keep him centered beside the Revlon sign, holding the lipstick case visibly as the featured object.

% matched lemmas: backdrop, base, capital, clean-shaven, closing, comb, context, crop, earring, enter, fit, flowing, form, formal, graceful, hairstyle, inner, main, neckline, outer, pedestal, pointer, poise, posture, presenter, script, stage, studio, style, textured, writing
\end{textsample}
