\begin{textsample}{POS Dim 7 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_26.txt}  \label{ex:f7_pos_007}
The commercial opens with an extreme close-up of a woman ’s face, focused on one eye.
The eye is heavily made up with dark eyeliner/mascara, and only part of the nose and surrounding skin are visible.
The image is \textbf{soft} and slightly blurred, with a vintage broadcast look.
By the next sampled \textbf{moment}, the scene has changed to a bright, soft-focus domestic or bathroom-like setting.
Several women appear together around a central woman.
The central figure seems to be seated or positioned lower, while others stand close beside or behind her, suggesting a grooming, bathing, or beauty-care context.
The details are washed out and not fully clear, but the scene emphasizes femininity, care, and a light pastel atmosphere.
A bottle-shaped product appears near the lower center/left area, though the label is not readable in this frame.
The final frame is a product display.
A tall blue bottle with a white cap is shown prominently on the left.
Its front label shows large dark lettering beginning with “ Sec … ” or similar, but the full product name is not completely clear from the frame.
On the right, white \textbf{script} text reads : “ Made for a woman ’s extra feelings. ” The background remains \textbf{soft} and light-toned, with \textbf{decorative} or bathroom-like \textbf{objects} visible but \textbf{indistinct}.
A \textbf{watermark} reading “ Classic Commercial Archives ” is visible in the lower-left area, and another \textbf{faint} archive \textbf{watermark} appears across the lower center.

% matched lemmas: decorative, faint, indistinct, moment, object, script, soft, watermark
\end{textsample}
