\begin{textsample}{POS Dim 7 – 1960 – Score 7.00 – 1960/tv\_com\_1960\_8.txt}  \label{ex:f7_pos_036}
The commercial opens in a warmly lit, old-fashioned interior resembling a study or parlor.
A uniformed man, possibly a hotel or domestic staff member, stands in the background, while a dark silhouetted figure occupies the foreground.
The room contains framed \textbf{pictures}, a mantelpiece, and furniture, giving it a formal, period-style atmosphere.
A “ Nostalgic X’er ” \textbf{watermark} appears at the lower right throughout the frames.
The scene then cuts to a close-up of packaged dessert products on a tray.
Several tubs or cups are visible with labels reading “ Cool ’ n Creamy, ” including a chocolate-flavored container in the foreground.
The visible label includes wording such as “ Instant Chocolate Flavored Pudding. ” A hand moves near the foreground container.
Next, the commercial shows two men standing close together in the same interior.
One man wears a dark uniform with light trim and sleeve stripes ; he has a neat, formal appearance.
The other man wears a tan suit with a vest, white shirt, and tie.
The uniformed man looks toward the suited man, while the suited man looks downward or to the side.
A wider shot reveals the men standing at a table or desk covered with \textbf{serving} items.
On the table are a metal tray, dessert containers, bowls, \textbf{spoons}, and other \textbf{decorative} \textbf{objects}.
The suited man appears to handle or present the dessert items while the uniformed man watches.
The commercial cuts to a close-up of dessert in small clear cups.
A \textbf{spoon} is inserted into a chocolate pudding cup in the foreground.
Other cups, including a lighter-colored pudding, sit nearby on the tray.
The texture appears creamy and smooth.
The men are then shown again at the table.
The suited man holds or gestures with a \textbf{spoon} over the tray, while the uniformed man looks down toward the desserts.
The setting remains the same formal room with mantelpiece and \textbf{decorative} \textbf{objects} in the background.
A closer shot follows as the suited man moves across the frame in front of the uniformed man.
The uniformed man remains in dark clothing with visible sleeve stripes, watching the action.
The suited man is then shown holding a small dessert cup and \textbf{spoon}.
He raises the \textbf{spoon} toward his mouth and appears to \textbf{taste} the pudding.
The uniformed man is partly visible at the edge of the frame.
The final frame is a product display shot.
A metal tray holds multiple “ Cool ’ n Creamy ” containers and prepared dessert cups, including chocolate and a lighter-colored variety.
Large white text over the product display reads : “ Too good to be pudding. ” The product packaging and prepared puddings are centered as the \textbf{closing} visual emphasis.

% matched lemmas: closing, decorative, object, picture, serve, spoon, taste, watermark
\end{textsample}
