\begin{textsample}{POS Dim 7 – 1960 – Score 13.00 – 1960/tv\_com\_1960\_54.txt}  \label{ex:f7_pos_023}
The commercial opens in stark black and white with an extreme close view of a shiny circular metal fitting on the car, possibly a dashboard control or ignition area.
A small ridged, key-like piece sits beside the chrome ring and appears to move into place, catching bright highlights against dark reflections.
The imagery is tight and mechanical, emphasizing polished metal surfaces and the act of starting or engaging the car.
The view then jumps to the front of a light-colored AMC Rebel.
Its face fills the scene : a long dark rectangular grille, round headlights set in dark surrounds, a bright chrome bumper, and small spaced letters across the front edge of the hood.
The car is outdoors near bushes and open countryside.
The front end glides past from one side to the other, lingering on the grille and paired headlights before the image gives way to rough outdoor textures, like scrubby grass or brush.
A light-colored \textbf{convertible} Rebel then appears head-on on a paved road bordered by low walls or curbs.
An adult woman drives, visible above the windshield.
She has dark hair pulled back neatly, and her \textbf{posture} is upright and composed as she faces forward.
The car moves toward and then past the viewer, its broad flat hood, rectangular grille, and four round headlights prominent.
This is followed by a graphic background of dark clouds crossed by jagged white lightning-like lines.
Large bold block letters appear in the center reading “ THE NOW CARS, ” first in white over the stormy background, then in black on a plain light background.
The Rebel returns in a side silhouette.
The \textbf{convertible} top is down, and the woman driver is seen in \textbf{profile} as a dark outline against a bright sky.
Her hair is gathered at the back of her head, and the windshield frame and open cabin \textbf{form} clean angular lines around her.
Huge white block letters reading “ REBEL ” rise across the lower half of the picture, partially covering the car ’s side.
As the car moves past trees, the driver ’s silhouette \textbf{alternates} between bright sky and dark foliage, while the word “ REBEL ” remains large and bold in front.
The car is next shown cruising along a tree-lined road in a leafy, suburban or park-like setting.
The light-colored \textbf{convertible} moves smoothly from left to right, its long body and open top clearly visible between tree trunks and dense foliage.
The surroundings are shaded, with bright patches of sky and road contrasting with dark branches.
A close view of a small side emblem follows : a dark rectangular badge above a V-shaped chrome ornament on the car ’s body, suggesting engine or trim identification.
The emblem is mounted on the smooth light body panel, near a thin horizontal crease line.
The Rebel continues along the road, now seen from the front three-quarter angle.
The adult woman remains alone at the wheel, looking ahead through the open windshield.
The car ’s low, squared front, chrome bumper, and paired headlights are repeatedly emphasized as it drives through \textbf{alternating} shadow and light.
From inside the car, the dashboard is shown behind the driver.
The woman ’s hands hold the steering wheel ; the dashboard has a broad rectangular instrument panel, round knobs, and a simple horizontal layout.
The windshield wipers rest at the \textbf{base} of the windshield, and the hood stretches out ahead.
The view moves across the dashboard toward the passenger side, showing the wide front bench area and open cabin.
A white picket fence appears, first as a close blur of pointed fence tops, then as two open gate panels framing a driveway or path.
Beyond the gate is an open rural-looking area with trees and low horizon.
The Rebel \textbf{enters} from the left beyond the gate, partly obscured by dust or road haze, and drives away into the distance.
The white fence panels stand on both sides like a gateway, their pointed tops bright against the darker ground and trees.
A quick close-up shows the \textbf{script} “ Rebel ” badge on the side of the car, mounted on a light body panel near a vertical door seam.
The front of the car is then shown again in motion, traveling along a road.
The imagery studies the grille from left to right : twin round headlights, the dark central grille, hood lettering spaced above it, the small Rebel badge in the grille, and the chrome bumper below.
The car then appears far out in an open landscape under a heavy, cloudy sky.
It approaches across a low horizon, the \textbf{convertible} body bright against dark ground, then sweeps past.
A tall metal windmill stands alone in the field, its circular blade wheel and tail silhouetted against the overcast sky.
The windmill is shown closer and closer until its radial blades fill the image like a spinning pattern of dark and light spokes.
This circular pattern gives way to an overhead view of the open \textbf{convertible} interior.
The woman driver sits in the front seat, wearing a dark top and long \textbf{earrings}, her face in \textbf{profile} and her expression calm and focused.
She grips the steering wheel with both hands and looks forward.
The light-colored upholstery is visible around her : a broad front bench seat and a rear bench behind it, both with stitched, padded sections.
The view settles on the seats, showing the spacious cabin.
The rear bench has multiple seating \textbf{positions}, with rectangular seat-belt buckles or latch points visible on the cushions ; the front bench has thick padded bolsters and a central backrest area.
The open-top layout makes the two rows of seats \textbf{easy} to see from above.
The Rebel is again shown traveling on a long paved road bordered by dark trees or fencing.
It passes from the side and then appears from a front three-quarter angle, top down, with the woman still driving.
The car holds a steady lane, its white body contrasting with the dark roadside.
A close interior view focuses on the steering wheel and column.
The driver ’s hands hold the wheel, and the column and hub are clearly visible, with the dashboard controls nearby.
The shot emphasizes the steering assembly and its sturdy central column before returning to the moving car outside.
The car speeds past from the front and side, then continues away down an open road.
Its rear end is visible with squared tail lamps, a straight trunk line, and a chrome rear bumper.
The \textbf{convertible} top remains folded down behind the rear seat.
The car \textbf{grows} smaller as it travels along the road into open countryside.
The storm-cloud graphic with jagged white lightning returns, followed by more fast, abstract close views of dark horizontal rails or structural beams, as if the car is moving through or across a bridge-like structure.
Large white block letters spelling “ REBEL ” fill the center of the image over these dark metal lines.
The word is massive and bold, occupying \textbf{most} of the picture.
The final sequence shows the light-colored \textbf{convertible} driving through a bridge or elevated roadway with heavy vertical and diagonal metal supports crossing in the foreground.
The car is seen from above and at a distance, moving along the lane beneath the dark framework.
In the lower left, large white text appears : “ THE 1967 AMERICAN MOTORS. ” The car continues through the repeating beams and railings, partially hidden at times by the structure.
Near the end, an enormous white word “ NOW ” appears across the center, covering \textbf{most} of the view while the car and bridge structure remain faintly visible behind it.
The commercial closes with this oversized “ NOW ” dominating the image.

% matched lemmas: alternate, base, convertible, earring, easy, enter, form, grow, most, position, posture, profile, script
\end{textsample}
