\begin{textsample}{POS Dim 7 – 1950 – Score 28.00 – 1950/tv\_com\_1950\_49.txt}  \label{ex:f7_pos_002}
The commercial opens in black and white with a playful animated scene.
Two small cartoon pigs, \textbf{drawn} in a simple 1950s \textbf{style}, ride together on a giant Paper Mate pen as if it were a vehicle.
Both have rounded faces, little snouts, floppy ears, and cheerful open-mouthed smiles.
One is slightly larger and wears a bow or cap-like accessory ; the smaller one also has a little cap.
They cling to the pen as it swoops across a pale background decorated with outline \textbf{hearts}.
The pen ’s tip touches the surface below them and writes the word “ NEW ” in large, dark, tall letters.
As the pen moves, the same word appears again and again, sometimes sliding past in the background, making the screen feel filled with repeated “ NEW ” announcements.
The two cartoon pigs continue to bounce and glide on the oversized pen, waving their arms and smiling broadly.
The pen sweeps over the background and comes to rest near a large product title.
Bold lettering appears : “ NEW PAPER MATE, ” with “ Capri ” written underneath in a \textbf{flowing} \textbf{script}.
A large \textbf{drawing} of the pen floats diagonally above and across the words.
The pigs stand to the left of the lettering, still grinning and gesturing toward the product name, while pale \textbf{heart} outlines remain scattered behind them.
The \textbf{animation} then focuses on the pen itself.
The two pigs stand beside a large angled pen, pointing up at it with excited expressions.
The pen is shown long and \textbf{sleek}, with a darker lower barrel and a lighter upper section.
The pigs climb back onto it, and the pen begins to write a long, smooth looping line across the bottom of the screen.
As it travels, the pigs ride along on the barrel, waving their arms and leaning with the motion.
The background remains soft and pale, with \textbf{faint} \textbf{hearts} and \textbf{textured} patches behind them.
The line produced by the pen \textbf{curls} into loops and arcs, showing the pen writing fluidly.
The animated pen and pigs eventually give way to a more realistic product view.
The pen lies diagonally over a large pale heart-shaped background, its dark barrel and lighter upper portion clearly visible.
A live-action adult hand then holds the pen over a light \textbf{writing} surface.
The pen point touches near the lower right, where a bright \textbf{star-like} glint appears at the tip, emphasizing the point.
The hand holds the pen in a normal \textbf{writing} grip, with the fingers wrapped around the barrel.
A bold caption appears along the bottom in all \textbf{capital} letters : “ BUILT-IN SPARE REFILL. ” Over the hand and pen, a bright white graphic highlight slides along the length of the pen, visually \textbf{indicating} the hidden internal refill.
The pen is then handled by two adult hands.
One hand steadies the barrel while the other grips the front cap or point section.
The fingers unscrew and pull the front section away.
The action reveals a slender \textbf{inner} refill section extending from the pen body.
The refill is \textbf{drawn} out from the barrel, long and narrow, with small segmented portions visible along it.
The bottom caption “ BUILT-IN SPARE REFILL ” remains visible during this demonstration.
The hands hold the refill horizontally to display it.
It is a slim rod-like piece with point sections at both ends, suggesting two usable \textbf{writing} tips.
The hands separate or turn the sections to show each end.
A caption appears at the bottom : “ 2 POINTS. ” The demonstrator places the two ends apart so both tips can be seen, one held in each hand.
The text changes to “ 2 INK SUPPLIES, ” while the hands continue to present the refill as two connected ink sources arranged end to end.
The refill is then \textbf{rotated} and handled carefully, with one hand holding a section and the other repositioning it, visually showing how the parts can be reversed.
The demonstrator brings the refill back to the pen body.
One hand holds the pen barrel steady at the right side of the screen, while the other hand guides the slim refill section back toward the opening.
The refill is inserted into the pen barrel, and the fingers twist and press the parts together.
The hands continue tightening and aligning the sections until the pen is reassembled into its normal \textbf{sleek} \textbf{form}.
The finished pen is again held in writing \textbf{position} over the light surface.
The pen writes in \textbf{cursive} on the page.
Large, slanted \textbf{script} appears : “ No need to run out of ink- ”.
Beneath it, the pen begins writing the word “ Ever, ” \textbf{forming} the letters one by one in smooth strokes.
After completing “ Ever, ” the pen \textbf{draws} an \textbf{underline} beneath it, reinforcing the message.
The final handwritten \textbf{phrase} fills the page : “ No need to run out of ink- Ever, ” with “ Ever ” emphasized by the \textbf{underline}.
The \textbf{animation} returns.
The two cartoon pigs reappear riding on the pen, which again writes a looping line across the bottom.
They bounce and wave as the pen glides along, making more loops in the line.
The background keeps the same pale, heart-decorated look.
The animated pair then ride toward a large product display.
The screen fills with a bold “ PAPER MATE ” logo across the top, “ Capri ” in \textbf{script} near the bottom, and a dark heart-shaped price emblem on the right containing “ \$1.95. ” The pen stands vertically near the center, and the pigs pose at the left, smiling and gesturing upward toward the brand name and price.
The commercial then changes to a live-action \textbf{studio} setting.
A middle-aged man with light skin stands before heavy vertical curtains.
He is dressed formally in a dark suit jacket with a white shirt, a light tie or bow-like neckwear, a white pocket square, and a light flower boutonniere on his lapel.
His hair is dark and neatly \textbf{combed} back, with a high forehead.
He holds a small pen or refill between his fingers near his face and looks toward the viewer while speaking.
His expression \textbf{alternates} between \textbf{earnest} and friendly ; he raises and lowers the small object as he talks.
The man turns toward a framed school-style board on an easel or stand to his right.
The board has a dark \textbf{writing} surface and a thick light-colored frame.
In large white \textbf{cursive} lettering, it reads : “ Don't go back to school. ” The man points toward the words with the pen-like object and rests one hand near the frame.
He smiles beside the board, standing slightly to the left of it, so the message is fully visible.
He then flips or \textbf{rotates} the board panel.
The writing surface swings, revealing another side with a new message.
The text now reads : “ without a PAPER MATE pen! ” The words “ without a ” and “ pen! ” are in \textbf{script}, while “ PAPER MATE ” appears in large bold block letters.
A small cartoon pig mascot is printed beneath the text, echoing the animated pigs from earlier.
The \textbf{presenter} stands beside the board, holding the pen or refill and gesturing toward the message, as if \textbf{underlining} the importance of the product.
The man continues speaking while holding the small \textbf{writing} instrument up between thumb and forefinger, occasionally glancing at it and then back toward the viewer.
He shifts closer to the board and handles the frame again, briefly \textbf{rotating} or adjusting it so the earlier “ Don't go back to school ” message appears once more.
He points to the \textbf{cursive} words on the board, then turns the panel back again to the side that reads “ without a PAPER MATE pen! ” The final images keep him beside the board, formally dressed against the curtain \textbf{backdrop}, with the large board message clearly visible and the pen held up in his hand.

% matched lemmas: alternate, animation, backdrop, capital, comb, curl, cursive, draw, drawing, earnest, faint, flowing, form, heart, indicate, inner, phrase, position, presenter, rotate, script, sleek, star-like, studio, style, textured, underline, writing
\end{textsample}
