\begin{textsample}{POS Dim 7 – 1980 – Score 6.00 – 1980/tv\_com\_1980\_118.txt}  \label{ex:f7_pos_045}
The commercial opens on a nearly uniform dark reddish-brown screen with no discernible \textbf{objects} or people visible.
It then cuts to a warmly lit, orange-tinted domestic interior.
A young girl with light brown hair, wearing a light \textbf{blouse} and pinkish \textbf{garment}, smiles while looking down into a small dark bowl.
She holds a \textbf{spoon} and appears to be stirring or scooping a yellowish mixture.
Next, there is a close-up of hands working with a small round baked item or pastry on a surface.
A knife or spatula spreads a glossy dark topping, likely chocolate-colored, over the top.
The scene then shows a red-haired girl or young woman with straight bangs holding a small round food item near her mouth and taking a bite.
She is indoors, with framed \textbf{pictures} and patterned wallpaper visible behind her.
A close-up returns to the younger girl, who looks downward and smiles, suggesting she is watching or preparing food, though the \textbf{object} she is looking at is not visible in this frame.
Another child appears : a blond \textbf{boy} wearing large round glasses.
He holds a small topped food item with both hands and bites into it.
The background remains warm-toned and softly blurred.
The commercial then cuts to a product display on a plain background.
Centered is a small toy-like oven with a front door and control panel.
Around it are accessories : an orange stand-like tool on the left, two small round metal pans, several packet-like items, a paper insert or recipe sheet, and a white electrical cord extending to the right.
On-screen text at the bottom reads : “ Betty Crocker.
Easy-Bake MINI-WAVE OVEN. ” The same product layout remains on screen, now with the “ Kenner ” logo visible in the upper right corner.
The product name text remains at the bottom.
The final frame shows the same product display \textbf{fading} darker, with the \textbf{objects} and text still faintly visible as the image dims.

% matched lemmas: blouse, boy, fade, garment, object, picture, spoon
\end{textsample}
