\begin{textsample}{POS Dim 7 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_24.txt}  \label{ex:f7_pos_006}
The commercial opens with a close-up of a white rectangular label reading “ Gabriel ” in black letters, with a horizontal rainbow stripe underneath.
The label is positioned over a purple, glossy-looking surface, with an orange circular \textbf{object} or shape visible behind it.
Archive \textbf{watermarks} are visible on the image.
It then cuts to an office setting.
A woman sits at a desk behind what appears to be a typewriter or dark office machine.
Behind her are shelves with books or binders, filing trays, windows, a wall calendar, and a coat or \textbf{garment} hanging on a rack.
She faces forward, apparently working.
A \textbf{soft} \textbf{dissolve} follows into a closer view of a woman in a patterned \textbf{blouse} with a white collar, still against an office-like background.
The image is partly double-exposed, suggesting a transition rather than a fully separate static shot.
The scene changes outdoors to a group of young men gathered closely together, looking toward the center and upward.
In the middle is a fuzzy orange-and-white \textbf{object} or figure being held up ; its exact nature is \textbf{unclear} from the frame.
The background is green and \textbf{leafy}, suggesting a park or outdoor area.
Next, the imagery becomes more graphic and \textbf{superimposed}.
A line drawing resembling a side profile of a nose or nasal passage appears over a \textbf{faded} background of the previous scene.
A Vicks-branded inhaler product is also visible on the right, suggesting the commercial is shifting from narrative scenes to product explanation.
The next scene shows two men moving or carrying an upright piano outside near a house and a truck.
A large, semi-transparent Vicks inhaler graphic remains \textbf{superimposed} over the scene.
One man is at the left side of the piano, while another stands near the right side or by the truck.
A closer shot shows a mustached man beside the piano, looking upward with a strained or concerned expression.
The piano ’s keys are visible behind him.
The commercial then cuts to a man indoors, possibly in a workshop or garage-like space, holding a small \textbf{object} to his nose with both hands.
A bare hanging light bulb is visible in the background.
The \textbf{object} appears to be an inhaler, though the exact handling is only partially visible.
Near the end, the product is shown prominently : a Vicks Inhaler tube appears across the frame with the label “ Vicks Inhaler ” and “ with decongestant action. ” Large white text overlays the lower part of the frame : “ IT ’S A BREATHER FOR YOUR NOSE. ” The product image is initially \textbf{superimposed} over the man ’s face.
The final frame presents a clearer product shot on a plain background : the Vicks Inhaler lies horizontally, with the same large white text beneath it reading “ IT ’S A BREATHER FOR YOUR NOSE. ”

% matched lemmas: blouse, dissolve, fade, garment, leafy, object, soft, superimpose, unclear, watermark
\end{textsample}
