\begin{textsample}{POS Dim 7 – 1960 – Score 12.00 – 1960/tv\_com\_1960\_13.txt}  \label{ex:f7_pos_028}
In black and white, the commercial begins inside a home beside a curtained window.
A middle-aged man with short dark hair, wearing a belted robe or loose casual housewear, stands close to the window and pulls the curtain aside.
He leans forward to look out, as if checking the weather or the view beyond the glass.
After peering through the opening, he turns back into the room, one hand raised in a small questioning or surprised gesture.
The scene moves to a domestic ironing area.
A woman with short, \textbf{curled} hair, wearing a light blouse and dark skirt, stands at an ironing board.
An iron rests on the board to her left, and she holds a tall aerosol can in her hand.
She points the can downward toward a garment laid flat on the ironing board, demonstrating its use before ironing.
The product is then presented very prominently.
A hand grips a spray can labeled “ Faultless ” and “ spray-on starch. ” The can fills the left side of the image while a fine spray shoots out to the right.
The spray is represented not just as \textbf{mist} but as a stream of bright little dots, like tiny stars.
As the spray continues, the smiling face of the woman appears behind the \textbf{mist}, visually \textbf{linking} her ironing demonstration with the product.
Another woman appears in the home, younger-looking, with a dark bouffant \textbf{hairstyle} and a light collared blouse.
She is near a refrigerator or tall kitchen appliance and holds a cup and saucer.
She looks toward the ironing area with an attentive, conversational expression.
In a wider view, the dark-haired woman sits at the left with her cup while the first woman stands at the ironing board on the right.
The iron and the Faultless can are visible on the board between them, making the ironing setup central to the scene.
The standing woman continues handling the garment, while the seated woman watches and reacts.
The product demonstration returns to a large view of the can spraying.
Again, the label “ Faultless ” and “ spray-on starch ” is readable on the can, and the spray \textbf{forms} a broad, bright plume of \textbf{star-like} particles.
The \textbf{mist} thickens, and then the imagery changes into a single glowing star shape floating against a dark background.
The star \textbf{grows} into a graphic emblem : a white five-pointed star with a \textbf{capital} “ F ” in the center, surrounded by radiating lines like a starburst.
A tall can of Faultless spray-on starch appears behind this starburst, standing upright as a product display, with the star emblem superimposed across its front.
The commercial then visualizes the starch at the fabric \textbf{level}.
The screen fills with a close, \textbf{textured} surface that looks like woven cloth, softly mottled with tiny bright points.
This suggests the spray settling into or coating the fibers.
Next, the woman is shown at an open closet.
She stands beside a hanging shirt on a hanger, with louvered closet doors and other clothing behind it.
The shirt is light-colored and neatly shaped.
She lifts it by the hanger and smooths the front with her other hand, showing how it hangs.
She then brings forward another light short-sleeved blouse or shirt with a crisp collar.
She turns it outward and arranges it carefully, spreading and straightening the sleeves and front panels to display its neat, freshly pressed appearance.
Her gestures are deliberate and approving, as if showing the garment ’s smoothness and shape after being treated and ironed.
The scene changes back to the man, now dressed for an outing in a short-sleeved plaid sport shirt and light trousers.
He stands in the same domestic setting, with a refrigerator or cabinet behind him.
He looks down at the front of his shirt and touches or smooths it with both hands, as though feeling the crispness and \textbf{fit}.
The woman stands to his left near a picnic basket or hamper.
She watches him while holding a checkered cloth, then lifts the cloth up from the basket, reinforcing the picnic setting introduced visually at the beginning.
As the couple remains in the background, the product image overlays the scene again : the large Faultless spray-on starch can appears at the left, spraying a bright stream of tiny \textbf{star-like} droplets across the picture.
The background with the man and woman fades behind the product demonstration, leaving the can and its spray as the \textbf{main} visual focus.
Finally, the starburst emblem with the central “ F ” returns over the upright can of Faultless spray-on starch, ending with the product centered and framed by the radiating star graphic.

% matched lemmas: capital, curl, fit, form, grow, hairstyle, level, link, main, mist, star-like, textured
\end{textsample}
