\begin{textsample}{POS Dim 7 – 1970 – Score 11.00 – 1970/tv\_com\_1970\_37.txt}  \label{ex:f7_pos_031}
A hand with long, polished nails writes in dark \textbf{cursive} on a white page.
The words already read “ Writing is here! ” and then the page is shown more fully : “ Eye Writing is here! ” written like a personal note, with an exclamation point.
The lettering looks loose and signature-like, introducing the idea of writing as a visual theme.
A young adult woman with long brown hair appears between the open doorway and frame of a small private airplane.
She has sunglasses resting on top of her head and wears a dark blazer over a high white blouse or scarf.
She leans out from the aircraft doorway, smiling and looking around, then steps down onto the sunlit tarmac.
The small plane ’s white fuselage, windows, open door, and partial registration lettering are visible behind her.
She carries travel bags, one dark and one tan, and stands beside the plane as if arriving or departing.
Her makeup is polished, with defined eyes and a warm, confident smile.
The scene shifts to a display of the Maybelline eye pencils.
Several slim, metallic cosmetic pencils and caps lie scattered in a loose ring on a reflective tabletop.
One pencil lies horizontally in the center with gold-toned labeling visible ; other pencils in silver, black, and muted colors surround it at angles.
A hand reaches in and lightly grips the center pencil, sliding it away from the arrangement, leaving the other pencils spread around the open space.
A beauty model with dark, shoulder-length hair faces forward against a plain light background.
Her eye makeup is emphasized : shaded lids, dark lashes, and shaped brows.
She smiles broadly while holding several metallic eye color pencils upright like a small fan beneath her mouth, their capped ends pointing upward.
The pencils are presented as the \textbf{main} object in her hand while her eyes remain the focal point.
A close view shows a woman applying and blending eye color at a mirror.
The round edge of the mirror is visible on the left.
Her head is turned slightly in \textbf{profile}, and her lips are glossy and copper-red.
With one hand near her upper eyelid, she works along the \textbf{outer} corner and crease area, where dark liner and smoky shadow are already visible.
The color is blended across the lid in soft olive, brown, and charcoal tones.
She then uses a fingertip to smooth the color over the eyelid, pressing and sweeping gently near the brow bone and \textbf{outer} corner.
Her face turns more forward, showing both eyes : one side appears heavily shaded and contoured, while the fingertip continues blending the other lid to even out the look.
The finished makeup is shown on a model with full, voluminous dark \textbf{curls} framing her face.
She looks directly ahead with calm, steady eyes.
Her eye makeup is defined but elegant, with softly blended shadow and dark outlining that makes the eyes stand out.
Then a more dramatic look appears : another glamorous close view against a darker background, with heavier smoky shadow, gleaming eyelids, dark lashes, and dangling \textbf{earrings}.
She looks down first, then raises her eyes sideways with a knowing, slightly playful expression, showing a stronger, more theatrical eye \textbf{style}.
The woman from the airport reappears beside a light-colored \textbf{convertible} parked on the tarmac, with several small airplanes visible in the background.
She is still dressed in her dark blazer and white blouse, with sunglasses on her head.
Smiling, she lowers herself into the open car and settles into the driver ’s seat.
She gestures with one hand as if finishing a thought, then turns forward.
Large black on-screen text appears across the side of the car door area : “ Eyes as unique as your signature. ” She glances back toward the viewer with a bright smile while the airplanes remain in the sunlit background.
The final image returns to the writing theme.
Several Maybelline eye pencils are arranged around a cream-colored page, \textbf{forming} a loose border.
A hand uses one of the pencils to finish writing in \textbf{cursive}, “ Eye Color Styler Pencils. ” Beneath the \textbf{cursive} product name, the Maybelline logo appears in a large orange \textbf{script}.
The metallic pencils remain scattered around the page, framing the brand name and product line as the commercial ends.

% matched lemmas: convertible, curl, cursive, earring, form, main, outer, profile, script, style
\end{textsample}
