\begin{textsample}{POS Dim 7 – 1950 – Score 8.00 – 1950/tv\_com\_1950\_87.txt}  \label{ex:f7_pos_026}
The commercial is in black and white and \textbf{unfolds} through a series of scenes connected by cuts and cross-fades. 1. **Opening product image / exterior setting** The first frame shows a large, semi-transparent box labeled **“Kodak FILM”** \textbf{superimposed} over an outdoor view.
Behind it are clouds, a building façade, a path, grass, and trees.
The product package dominates the frame. 2. **Entrance to a building** The scene changes to glass double doors.
A child or young person is visible through the doors, standing or entering from outside.
Reflections and the bright exterior make details hard to see. 3. **School-like exterior with children** A cross-faded view shows a brick building entrance with glass doors.
Two children or young people stand near the doorway, carrying bags or cases.
A bicycle is parked to the right near the wall.
Reflections in the glass and the \textbf{dissolve} make the scene partially layered. 4. **Close view of brick wall and shrubbery** The image moves to a close exterior detail : a brick corner, a window, and \textbf{leafy} bushes.
A blurred figure passes at the left edge, but the person is not clearly visible. 5. **Interior with model railway / toy setup** After a time jump, the commercial cuts to an indoor scene with a tabletop or floor-level model train layout.
A cylindrical water-tower-like structure and track elements are visible.
The image is slightly blurred, suggesting motion or camera movement. 6. **Boy \textbf{photographing} model train scene** A \textbf{boy} appears behind the model layout, holding a small camera up to his face.
Shelves in the background hold \textbf{objects} or toys.
The foreground includes tracks, a train car or platform, and small model accessories.
He appears to be aiming the camera at the miniature scene. 7. **Camera flash** The \textbf{boy} continues holding the camera.
A bright flash fills the frame briefly, then the image returns to the \textbf{boy} with the flash bulb or camera front glowing brightly.
The model train layout remains in the foreground. 8. **Classroom scene** The commercial cuts to a classroom.
A \textbf{boy} stands at the front, smiling, holding a small \textbf{object} in his hands.
Other students are seen from behind, seated and facing him.
A chalkboard with handwritten text is visible in the background, though the writing is only partly legible. 9. **Boy with camera against plain background** A \textbf{boy} in a dark jacket or uniform holds a camera up to his eye, pointing it slightly upward.
The background is plain and uncluttered. 10. **Marching group outdoors** The next shot shows a marching formation outdoors on a field.
Uniformed participants march in rows, and one person carries a flag.
A crowd or line of spectators is visible in the background, with trees behind them. 11. **Close-up of smiling \textbf{boy} with camera** A \textbf{boy} smiles while holding a camera close to his face.
The camera has a \textbf{prominent} round lens or flash attachment.
The sky or a plain bright outdoor background is behind him. 12. **Statue of Liberty** The commercial cuts to a clear shot of the Statue of Liberty from below, with the statue framed against a dark sky. 13. **Boy looking upward with camera** A \textbf{boy} outdoors smiles and looks upward.
A camera hangs or rests near his chest.
Trees and sky are visible behind him. 14. **Final product display** The last frame shows a product display with a camera and film-related packaging arranged on a tray or platform.
Large outlined text reading **“Kodak”** is \textbf{superimposed} prominently across the right and center of the frame.
The display includes a visible camera and Kodak-branded materials, though some smaller \textbf{printed} text is not fully readable.

% matched lemmas: boy, dissolve, leafy, object, photograph, printed, prominent, superimpose, unfold
\end{textsample}
