\begin{textsample}{POS Dim 7 – 1980 – Score 6.00 – 1980/tv\_com\_1980\_52.txt}  \label{ex:f7_pos_047}
A male-presenting store employee stands behind a parts counter in a bright, \textbf{tidy} auto-parts retail setting.
He appears to be an adult with a receding hairline, dark hair at the sides, and a full dark beard.
He wears a white shop coat over a darker shirt, giving him the look of a parts-counter specialist or service employee.
Behind him, a large blue-and-white sign reads “ PARTS TO GO, ” with a small GM square logo beside it.
Shelving and display boards fill the background, including a dark poster on the right that shows a large white plastic jug with GM-style red and blue striping.
At first he is shown from the waist up, holding a small cylindrical container in his right hand.
The container has a blue label with red and white accents, matching the GM Parts colour scheme ; the audio \textbf{context} identifies this as GM engine oil.
He faces forward as if \textbf{addressing} the viewer, then glances down at the container in his hand, presenting it with the label turned outward.
His \textbf{posture} is upright and confident, and he keeps the product raised near shoulder height so it is \textbf{easy} to see.
The view widens to reveal more of the counter and a larger product display.
On the left side of the counter, many blue-and-red cans are stacked in neat columns, \textbf{forming} a tall block of identical GM-branded containers.
On the right side, several white plastic jugs with handles and red-and-blue labels are arranged in rows.
Overhead lamps hang above the counter, and the background remains clean and orderly, like a dealership parts department.
The employee continues holding the small oil container in front of his chest, occasionally lifting it higher as he speaks.
As the commercial continues, he lowers the can and leans forward over the counter.
Additional products begin appearing from both sides, placed by unseen people whose arms extend into view.
A hand from the left slides a large white jug with a handle onto the counter.
A hand from the right places a smaller container near the front.
The employee points down toward the items as they arrive, organizing the display while staying centered behind the counter.
More GM-branded containers are set out in front of him : a large handled jug, a small rectangular blue-and-red package or can, a white bottle with a narrow neck, and clear or dark containers with coloured liquid visible inside.
The exact labels are soft and not fully readable, but they visually match the audio ’s list of automotive fluids and cleaners.
The employee ’s gestures become more demonstrative ; he points from one item to another as if matching each product to a customer ’s need.
Customer hands in blue sleeves continue to slide items into place from the left and right edges of the counter.
The counter display \textbf{grows} into a broad lineup.
On the left, the stacked blue cans remain tall and orderly.
Across the center are several individual products : handled white jugs, smaller bottles, a short blue-and-red container, and transparent containers showing dark and reddish fluids.
On the right, the repeated white jugs \textbf{form} a blocky display, their handles and labels facing forward.
The employee stays behind the products, leaning in and looking toward the viewer, then down at the items, using his hand to \textbf{indicate} each group as if confirming availability.
Near the end, the counter is crowded with GM Parts products spread from left to right.
The employee, still in his white coat, rests forward behind the display and gives a slight smile.
The “ PARTS TO GO ” sign remains clearly visible over his left shoulder, reinforcing the dealership parts-counter setting.
Large on-screen text appears over the lower part of the picture : “ WE GOT IT. ” in bold white letters, with “ At Your GM Dealer. ” below in blue.
The final image presents the employee framed by the full assortment of automotive fluids and cleaners, all arranged as ready-to-buy parts and maintenance products.

% matched lemmas: address, context, easy, form, grow, indicate, posture, tidy
\end{textsample}
