\begin{textsample}{POS Dim 7 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_13.txt}  \label{ex:f7_pos_010}
The commercial begins in a dimly lit interior, apparently a living room or study.
A man sits in a chair, viewed in profile, holding and looking at a sheet of paper or document.
The background includes shelves or furniture, and the lighting is warm and subdued.
A “ Classic Commercial Archives ” \textbf{watermark} appears at the lower left.
The scene then transitions into a close-up of baked goods or a dessert-like item.
During the transition, large product branding is partially visible over the image, including the word “ Nestle ” and references to “ butterscotch, ” though the \textbf{overlapping} \textbf{dissolve} makes some details \textbf{unclear}.
Next, the image crossfades to a close-up of a young child with blond hair and large round eyeglasses.
The child faces forward.
Product imagery or packaging remains faintly \textbf{superimposed} across the frame during the \textbf{dissolve}, making the shot somewhat layered and \textbf{soft}.
The commercial then cuts to a clearer product close-up : a package labeled “ Nestle ” and “ Butterscotch flavored morsels ” is shown in front of baked cookies or bars.
The package is angled across the lower \textbf{half} of the frame, with the baked goods behind it.
The final frame is a composed product shot.
A Nestle Butterscotch flavored morsels package sits in front of a plate or tray of cookies.
Large on-screen text at the upper right reads “ Oatmeal Scotchies. ” The background includes warm kitchen-like \textbf{objects}, possibly a container or \textbf{utensil}, but details are not fully clear.
The archival \textbf{watermark} remains visible near the lower left.

% matched lemmas: dissolve, half, object, overlapping, soft, superimpose, unclear, utensil, watermark
\end{textsample}
