\begin{textsample}{POS Dim 7 – 1970 – Score 9.00 – 1970/tv\_com\_1970\_20.txt}  \label{ex:f7_pos_009}
The commercial opens with a dark, green-tinted close-up of what appears to be a door or doorway.
A curved, dark handle or \textbf{decorative} element is visible in silhouette, with a brighter rectangular area in the background suggesting light from another room or window.
The next shot cuts to a close-up of the lower body/feet area.
A person ’s dark shoe and leg are visible near a shiny horizontal metal bar or threshold.
The surface below looks smooth and reflective, but the exact setting is \textbf{unclear} because of the low image \textbf{quality} and dim lighting.
The third frame shows a pale, softly lit interior doorway or wall panel.
A blonde-haired woman is partially visible near the \textbf{opening}, seen through or beside a vertical doorframe.
The image is somewhat blurred, and her full appearance is not yet clear.
The fourth frame reveals the woman more fully.
She stands in a doorway or on an upper landing behind a balustrade, facing forward.
She has long blonde hair and is wearing a form-fitting, low-cut dress or eveningwear.
The room around her appears \textbf{decorative}, with framed portraits or \textbf{pictures} on the walls and a lamp visible to the left.
The lighting has a \textbf{soft}, glamorous, slightly tinted look.
The final frame changes to a product display against a dark background.
White text reads “ Emeraude by Coty ” on the left.
To the right is a green perfume bottle with a dark cap or spray top.
Beside it are \textbf{decorative} \textbf{objects} or jewelry-like items, including a round pale \textbf{object} and sparkling beads or stones.
A “ Classic Commercial Archives ” \textbf{watermark} is visible on the frames.

% matched lemmas: decorative, object, opening, picture, quality, soft, unclear, watermark
\end{textsample}
