\begin{textsample}{POS Dim 7 – 1950 – Score 15.00 – 1950/tv\_com\_1950\_42.txt}  \label{ex:f7_pos_014}
The commercial is in black and white.
It opens on a clean-cut adult male \textbf{presenter} standing indoors in what looks like a jewelry or gift-shop setting.
He wears a dark suit jacket with a pocket square, a light shirt, and a bow tie.
His short hair is neatly \textbf{combed}, and he smiles directly toward the viewer.
Behind him are shelves holding small display boxes or gift items, with a plant and a counter or table to his left.
As he continues \textbf{addressing} the viewer, he shifts from smiling to a more \textbf{earnest} speaking expression.
He gestures with one hand near his chest, then lowers his hand and glances down toward the counter at his left.
He reaches to the display surface, picks up a small presentation case, and brings it up in front of his \textbf{torso}.
The case is open, with a pale \textbf{inner} lid and a darker \textbf{base}, \textbf{positioned} so the contents face forward.
He supports it with one hand and points toward it with the other, presenting it as the featured gift.
He holds the open case steadily at chest height while speaking.
The shelves remain visible behind him, filled with neatly arranged boxes and small objects.
His \textbf{posture} is upright and \textbf{formal}, and he \textbf{alternates} between looking at the viewer and glancing down at the item in the case, \textbf{drawing} \textbf{attention} to the watch.
The image then shifts into a product display.
Large white text appears on the left reading “ Bulova Senator, ” with “ Shock Resistant ” beneath it.
On the right is a close view of the wristwatch.
The watch has a light-colored, rounded-square face with dark Arabic numerals, a small seconds dial near the bottom of the face, and a shiny metal case.
The band is metallic and reflective.
The watch is shown upright against a dark, polished background.
The same watch remains centered as the feature text changes. “ Bulova Senator ” stays at the left, while the lower text changes first to “ Unbreakable Mainspring, ” then to “ Expansion Band. ” The watch ’s face and case continue to gleam under \textbf{studio} lighting, with the metal band visible below and around it.
The display changes to show the watch laid out horizontally with its expansion band stretched across the image.
The words “ Bulova Senator ” appear large above it.
The band is made of \textbf{linked}, reflective metal sections, emphasizing its flexible, expandable design.
A price then appears below the watch : “ Only \$35.75, ” with the dollar amount large and prominent.
For a moment, the product image and price are superimposed over the \textbf{presenter} and the shop-like background, then the \textbf{presenter} becomes clear again.
He is still holding the small open case near his left side, facing forward.
He continues speaking with a composed expression, then lowers the case out of view.
The ending returns to a closer view of his face and upper \textbf{torso}.
He looks directly at the viewer, wearing the same suit and bow tie, with the shelves softly visible behind him as the commercial concludes.

% matched lemmas: address, alternate, attention, base, comb, draw, earnest, formal, inner, link, position, posture, presenter, studio, torso
\end{textsample}
