\begin{textsample}{POS Dim 7 – 1950 – Score 9.00 – 1950/tv\_com\_1950\_66.txt}  \label{ex:f7_pos_022}
The commercial is shown in black and white and appears to \textbf{unfold} as a presenter-led product demonstration. 1. **Opening shot:** A man in a suit and tie faces the camera directly.
He is indoors, standing or sitting in front of patterned curtains, with a domestic-looking background.
His hands are held together in front of him, suggesting he is addressing the viewer. 2. **Product demonstration shot:** The scene cuts to a close-up of hands handling a packaged food item on a \textbf{flat} surface.
A foil compartment tray is visible, partly removed from or placed beside \textbf{printed} packaging.
The packaging shows a \textbf{picture} of a prepared meal and large “ TV ” lettering.
The setting appears to include a counter or tabletop ; nearby \textbf{objects} are partially visible but not clearly \textbf{identifiable}. 3. **Return to presenter with superimposition:** The man reappears smiling in the same curtained interior.
A transparent overlay or \textbf{dissolve} effect places the outline/image of the product packaging across the frame, partially over his body and the background.
This creates a visual link between the presenter and the product. 4. **Final product pack shot:** The commercial ends on a centered close-up of the product package.
The box prominently displays “ TV ” and an image of a prepared meal.
The words “ TURKEY DINNER ” are visible on the front.
The package is framed against a background that resembles curtains or a display setting.
The final frame \textbf{functions} as a product-identification shot.
No dialogue, music, or voice-over \textbf{content} is visible in the frames.

% matched lemmas: content, dissolve, flat, function, identifiable, object, picture, printed, unfold
\end{textsample}
