\begin{textsample}{POS Dim 7 – 1970 – Score 7.00 – 1970/tv\_com\_1970\_34.txt}  \label{ex:f7_pos_020}
The commercial begins on a very dark, nearly blank screen.
A “ Classic Commercial Archives ” \textbf{watermark} appears in the lower-left corner, and a \textbf{faint} archive \textbf{watermark} is visible across the lower middle.
At around 9.8 seconds, the scene changes to the interior of a car.
Two adult men are seated side by side in the front seats.
The man on the right, with dark curly hair, looks downward toward an \textbf{object} or package held near his chest ; the man on the left also looks down.
The image has a strong greenish overlay or reflection across the lower \textbf{half}, making some details hard to distinguish.
At around 17.7 seconds, the setting changes to an indoor home-like room.
A woman sits on the left, wearing a light-colored \textbf{blouse} or jacket with a small pattern.
A man stands partly visible on the right, shown mainly from the shoulders down.
They appear to be near a table or bed with fabric or clothing in the foreground.
A lit table lamp and window shutters are visible in the background, suggesting a domestic interior.
At around 25.6 seconds, the commercial cuts to a product display.
Several Dial “ Very Dry ” deodorant/antiperspirant products are arranged upright against a dark background : a large cylindrical container on the left, a box or package in the center, and a roll-on-style container on the right.
A pink cap-like \textbf{object} is placed in front.
The “ dial ” logo appears in a large rectangular outline in the upper right.
The products feature \textbf{prominent} pink circular graphics.
The final frame remains on the same product lineup.
The Dial logo is clear in the upper right, and the packaging text “ dial ” and “ VERY DRY ” is visible on the products.
The arrangement is static, with the products centered and highlighted against the dark background.

% matched lemmas: blouse, faint, half, object, prominent, watermark
\end{textsample}
