\begin{textsample}{POS Dim 7 – 1950 – Score 9.00 – 1950/tv\_com\_1950\_18.txt}  \label{ex:f7_pos_025}
The commercial is in black and white and appears to move from a graphic \textbf{opening} to a domestic kitchen scene and then to a product display.
At the start, the frame shows a \textbf{simple} graphic emblem : a large white letter “ Q ” on a plain gray background.
Inside the circular part of the letter is a stylized illustrated face wearing a dark, wide-brimmed hat and a white collar or head covering.
The image is \textbf{flat} and logo-like rather than photographic.
The next sampled \textbf{moment} shifts to a live-action kitchen or countertop scene.
Two people are visible, apparently standing at a counter or work surface.
The person on the left appears to be a woman wearing a head covering or headband and an apron-like \textbf{garment} ; the person on the right appears to be a man in a darker jacket or uniform-style clothing and a cap.
Several round, pale circular \textbf{objects} are \textbf{prominent} in the foreground and midground, possibly plates, bowls, or food items, but their exact nature is \textbf{unclear} from the frame.
The counter contains various kitchen items, including containers, \textbf{utensils}, and what look like product packages or \textbf{printed} materials.
The image is somewhat layered or blurry, making some \textbf{objects} difficult to identify precisely.
The final frame is a clear product shot.
Large text at the top reads “ Aunt Jemima. ” On the left side, stacked words read “ REGULAR, ” “ BUCKWHEAT, ” and “ BUTTERMILK. ” To the right is a box labeled “ Aunt Jemima, ” showing an illustrated portrait of a smiling woman on the package and an image of pancakes or a prepared serving on the front.
A cylindrical container or pitcher-like \textbf{object} stands beside the box, along with a small textured or waffle-patterned \textbf{object} in front.
The arrangement is set on a counter or tabletop, with the product and readable text centered as the concluding visual focus.

% matched lemmas: flat, garment, moment, object, opening, printed, prominent, simple, unclear, utensil
\end{textsample}
