\begin{textsample}{POS Dim 7 – 2010 – Score 8.00 – 2010/tv\_com\_2010\_2.txt}  \label{ex:f7_pos_081}
The commercial opens on a very dark frame where only a \textbf{faint}, \textbf{indistinct} mark or logo-like shape is visible ; the details are not clear.
It then cuts to a close-up of a hand arranging or picking up small shiny pink and red wrapped items on a pale, scalloped plate on a dark tabletop.
The setting looks softly lit, with a patterned wall or curtain in the background.
Next there is a very \textbf{soft}, blurred close-up of a person near a bright window or light source.
The person ’s face or body is not clearly visible, and the image \textbf{functions} more as a warm transitional shot than a clear action.
The scene moves to a café table.
A woman ’s hands open a glossy burgundy clutch or handbag beside a cup of coffee with foam art.
The tabletop has a \textbf{decorative} patterned surface.
In the following close-up, her hand places or retrieves several shiny pink-wrapped pieces into or from a small pouch or compartment near the handbag, with the coffee cup still visible nearby.
The commercial then shows a café interior.
A barista or café worker stands behind an espresso machine.
Behind them is a chalkboard menu with handwritten items such as “ Café Latte, ” “ Mocha, ” “ Ameri …, ” and “ Tea. ” A customer or another woman is visible in the background, partially obscured by the counter area.
The next scene is outdoors.
A pink mailbox with a hand-drawn heart on its side stands in the foreground.
A woman in a coat walks toward it in the background, holding a small item.
A \textbf{faint} copyright line is visible near the bottom of the frame.
A close-up shows the inside of the pink mailbox.
Inside are pink and red items, including what appears to be a small wrapped package with a \textbf{bow}.
The heart drawing is visible on the outside of the mailbox.
The commercial then cuts to a woman indoors, lit by bright light from a window or doorway.
She holds up a small silver or light-colored wrapper/package and looks toward it with a slight smile.
Her dark hair and face are visible, though the shot is partially softened by glare.
Another indoor shot shows the same or a similar dark-haired woman reclining comfortably in a \textbf{cushioned} chair near curtains.
She is smiling while holding a pink wrapper or card and a red bag or gift bag.
Her posture suggests she is relaxed and enjoying the \textbf{contents}, though the exact \textbf{object} in her hand is partly obscured.
The final frame is a product display : three Dove chocolate bars are arranged on a glossy chocolate-like surface.
The front package is pink and labeled “ Dove ” with “ Silk Chocolate ” visible ; the two packages behind it are darker pink/red tones, also branded “ Dove. ” A small URL, “ facebook.com/dovechocolate, ” appears at the bottom.

% matched lemmas: bow, content, cushion, decorative, faint, function, indistinct, object, soft
\end{textsample}
