\begin{textsample}{POS Dim 7 – 2010 – Score 8.00 – 2010/tv\_com\_2010\_81.txt}  \label{ex:f7_pos_052}
A bright, \textbf{formal} garden opens around a rectangular swimming pool.
The water is turquoise, bordered by pale stone paving, with clipped hedges, sculpted round topiary bushes, potted cone-shaped shrubs, benches, and tall trees in the background.
In the foreground, three cream-colored \textbf{pedestal} stands sit in a row on the grass.
Each \textbf{pedestal} holds a small pale-blue pot with a neatly rounded miniature green topiary.
Three young adult women in bikinis walk in from the right, moving across the front of the pool toward the \textbf{pedestals}.
The first has light brown, shoulder-length hair and wears a pale pink bikini.
Behind her is a blonde woman in a pale yellow bikini, with a patterned headband.
The third has long dark hair and wears a bright magenta-purple bikini.
They line up behind the three \textbf{pedestals}, each standing directly behind one potted topiary.
Because of the alignment, each little green bush sits visually in front of the woman ’s bikini area, making the plants function like a playful stand-in for bikini-line hair.
The women look down at the plants in front of them as if preparing to groom them.
The woman in the pale pink bikini begins trimming her small topiary with a pair of silver scissors.
In a closer view, her \textbf{torso} and pale pink bikini bottoms are visible behind the \textbf{pedestal}, while her hand carefully snips at the rounded green plant.
Tiny bits of leaf fall onto the cream \textbf{pedestal} surface.
She cuts around the sides and front of the miniature bush, but the shape remains uneven and leafy.
The focus shifts across the row to the blonde woman in the yellow bikini.
She uses a larger, heavier-looking trimming tool, more like garden clippers, pressing it into the topiary in front of her.
Leaves and small cuttings scatter around the pot and across the \textbf{pedestal}.
Her \textbf{posture} is intent and slightly bent forward as she works.
The bush is trimmed more aggressively, but the process looks clumsy and messy, with loose greenery collecting on the stand.
The view then moves to the woman in the magenta bikini.
Instead of garden tools, she holds a small blue-and-white grooming device, visually matching the Schick Hydro Silk TrimStyle product later shown.
She runs it smoothly over the rounded topiary.
The device has a light turquoise-blue handle with white sections and a small grooming head.
As she passes it over the plant, bits of greenery fall away onto the \textbf{pedestal}, and the bush becomes more controlled and \textbf{tidy}.
Her movements look \textbf{easier} and more precise than the scissors and clippers used by the others.
All three women are seen together again in front of the pool.
The woman in pink continues concentrating on her plant with scissors.
The blonde in yellow leans over her topiary, still working with her larger tool.
The woman in magenta stands more upright, smiling slightly, holding the blue-and-white grooming device up beside her shoulder as if finished and pleased with the result.
The three \textbf{pedestals} remain lined up in front of them, with clipped leaves scattered around the pots.
A large, translucent image of the same blue-and-white grooming tool sweeps in over the garden scene, \textbf{growing} to dominate the view.
The background becomes a close product display over rippling blue pool water.
The tool floats horizontally on the surface, surrounded by small leaves drifting in the water.
Above it appears the Schick logo in a small dark rounded rectangle, followed by the product name in blue lettering : “ HYDRO Silk TrimStyle. ” The word “ Silk ” is written in a more \textbf{flowing} \textbf{script} \textbf{style}, while the other words are in clearer block lettering.
The product \textbf{rotates} and is shown from both ends.
A circular highlight appears around one end, showing a comb-like trimmer attachment.
Then the product turns so the opposite end is emphasized, with another circular highlight around a razor head with a green strip.
The water ripples outward around the floating tool, reinforcing that the device is associated with use around water.
The branding remains centered above : “ Schick HYDRO Silk TrimStyle. ” The final image holds on the product floating in the blue pool water beneath the Schick Hydro Silk TrimStyle logo.
In the lower right, white on-screen text appears : “ FREE YOUR SKIN. ”

% matched lemmas: easy, flowing, formal, grow, pedestal, posture, rotate, script, style, tidy, torso
\end{textsample}
