\begin{textsample}{POS Dim 7 – 1990 – Score 7.00 – 1990/tv\_com\_1990\_55.txt}  \label{ex:f7_pos_057}
The commercial begins with a very dark, \textbf{indistinct} image.
Little visual detail is visible in the first sampled frame, apart from \textbf{faint} shapes and low blue-black lighting.
The next visible scene shows a softly lit interior with a layered or reflective composition.
On the left, there is a close side profile of an adult ’s face, partly in shadow.
In the background, near a bright window, two children or young people appear to be standing or sitting close together.
The image has a \textbf{hazy}, warm, slightly overexposed look, making details \textbf{unclear}.
The commercial then cuts to a product display.
Multiple boxes and bottles of Dimetapp-branded products are arranged together in the foreground.
The packaging uses \textbf{prominent} purple, white, red, yellow, and blue areas.
Several product names are visible, including “ Dimetapp, ” with different variants shown.
Small white text at the bottom right reads “ Use As Directed. ” The background remains softly blurred, with a bright light flare on the right side.
Next, a large “ Dimetapp ” logo appears across the center of the screen, overlaid on a close-up image of a young child ’s face.
A purple rectangular banner beneath the logo contains the text “ DOCTORS RECOMMEND DIMETAPP. ” The child in the background is softly lit and partially obscured by the text overlay.
The final frame shows a close-up of a young \textbf{boy} smiling.
He is turned slightly to the side and appears warmly lit.
He wears a light-colored top with a blue collar and patterned details.
The background is out of focus, with indoor colors and shapes suggesting a home or playroom setting, but specific \textbf{objects} are not clearly \textbf{identifiable}.

% matched lemmas: boy, faint, hazy, identifiable, indistinct, object, prominent, unclear
\end{textsample}
