\begin{textsample}{POS Dim 7 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_89.txt}  \label{ex:f7_pos_043}
The commercial begins with a very dark, low-visibility shot.
A pale \textbf{object} or appliance-like form is faintly visible in the center, but the scene is too underexposed to identify clearly.
It then cuts to a close-up of a white kitchen \textbf{appliance} bearing the label “ PRESTO SaladShooter ” and the words “ SLICER-SHREDDER. ” The product is shown at an angle, with the brand name in orange and the product name in large black lettering.
The shot emphasizes the product ’s exterior label and branding.
Next, the \textbf{appliance} is shown on a kitchen counter.
A hand holds or steadies it, and the cylindrical outlet or chute is visible at the front.
The image appears partly \textbf{superimposed} with other kitchen elements, suggesting a \textbf{dissolve} or layered transition.
In the background, there are containers and countertop items, but they are \textbf{soft} and partially obscured.
The sequence continues with another \textbf{dissolve} : the \textbf{appliance} remains semi-visible while a large bowl or platter of salad appears in the foreground.
The bowl contains assorted vegetables or salad ingredients, with green \textbf{leafy} pieces and other colorful items visible.
The product and prepared food overlap visually, linking the \textbf{appliance} to salad preparation.
A further montage-like shot shows food on a countertop.
There are small piles of shredded or chopped ingredients, and a hand or utensil-like motion appears blurred over the surface.
Other food items, including round items that may be vegetables or baked goods, are visible around the work area, though the \textbf{overlapping} imagery makes details \textbf{unclear}.
The \textbf{appliance} is then shown being used over a yellow bowl filled with lettuce or salad greens.
A hand holds the white device, and the front chute points downward toward the bowl.
A product card or label reading “ SaladShooter ” is visible inside or beside the bowl.
The image suggests the \textbf{appliance} is dispensing sliced or shredded ingredients onto the salad, though the exact food pieces are hard to distinguish because of motion blur and double exposure.
The final shots return to extreme close-ups of the \textbf{appliance} label.
The camera frames the word “ SaladShooter ” diagonally across the screen, with the line “ ELECTRIC • SLICER • SHREDDER ” visible beneath it.
The last frame remains a tight, angled branding shot, emphasizing the product name and \textbf{function} text.

% matched lemmas: appliance, dissolve, function, leafy, object, overlapping, soft, superimpose, unclear
\end{textsample}
