\begin{textsample}{POS Dim 7 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_18.txt}  \label{ex:f7_pos_041}
The commercial opens in a dark, theatrical space filled with floating bubble-like circles and glittering points of light.
A vivid green lipstick rises into view in a shiny gold tube.
Bright green beams sweep diagonally behind it, and a star-shaped sparkle flashes on the rounded tip, making the lipstick look magical and luminous.
A large hot-pink, glowing shape spreads across the background, while the green lipstick remains upright in the foreground.
As the lipstick shifts to the right side of the screen, glossy \textbf{cursive} letters begin appearing across the pink glow.
The word “ Mood ” \textbf{forms} first in large pink-white \textbf{script}, surrounded by starbursts and sparkles.
The green lipstick, still in its gold tube with a clear \textbf{base}, stands beside the lettering like part of the logo.
More \textbf{cursive} \textbf{writing} appears below until the title reads “ Mood Magic, ” then the scene changes to the word “ Lipstick ” in large cream-colored \textbf{script} against the same pink, bubbly, glittering background.
A lip-shaped opening appears over the word “ Lipstick, ” revealing a close view of a young woman ’s face.
She has fair skin, dark hair, large made-up eyes, and softly blushed cheeks.
She holds the green lipstick in its gold tube to her parted lips.
As she applies it, the color visible on her lips becomes glossy pink to deep rose rather than green.
Her expression is calm and focused, and she looks straight ahead while carefully touching the lipstick to her upper and lower lip.
The image \textbf{dissolves} to another glamorous close-up of a young woman with dark hair, hoop \textbf{earrings}, and shiny bright pink lips.
She faces slightly downward and then toward the viewer, smiling and moving her lips as if speaking or singing along with the advertisement.
Her makeup is dramatic, with defined eyes and rosy cheeks.
Over her face, the product name appears again in pale \textbf{cursive} : “ Mood Magic. ” A gold lipstick tube rises in the foreground, with a purple-pink glow and sparkle around it.
The full title “ Mood Magic Lipstick ” becomes visible in large white \textbf{script} on the right, with the green lipstick standing upright on the left against a magenta, sparkling background.
The product title fades over another portrait-like image.
A young woman with short, softly \textbf{curled} dark hair and glossy red-pink lips looks forward with a composed expression.
She wears a light, \textbf{ruffled} collar and a dangling \textbf{earring}.
Behind her is a stylized night-like \textbf{backdrop} : a pink crescent moon at upper left and smooth bands of blue and magenta waves across the lower background.
She holds a steady, elegant pose, her lips emphasized by their saturated shine.
Her face \textbf{dissolves} into another close-up of a young woman in a blue top.
She has dark hair swept back, warm eye makeup, and bright pink glossy lips.
She turns slightly toward the viewer and smiles broadly, showing her teeth.
Her expression becomes playful and cheerful, with her eyes directed toward the camera and her shoulder angled forward.
A final product display appears.
On the left, several Mood Magic lipsticks are arranged on a light surface beside a red rose-like prop.
One lipstick stands upright in a clear faceted holder with a gold \textbf{inner} tube and green lipstick exposed ; two more gold tubes lie diagonally in front, also showing green lipstick tips.
On the right, the large \textbf{cursive} words “ Mood Magic Lipstick ” sit over a purple-pink, bubble-filled background with sparkling highlights.
Small fine print appears along the bottom identifying the company.
The commercial ends on a store availability card.
The background is a close-up of glossy, deep magenta lipstick-like streaks.
Across the top, white \textbf{capital} letters read, “ CREATE YOUR MOOD MAGIC AT : ”.
Below, a large white rounded rectangle contains the Walgreens logo in dark \textbf{cursive}, with the words “ The Shopper ’s Center ” printed to the right.
Along the bottom of the logo are black silhouette figures of a family group holding hands.

% matched lemmas: backdrop, base, capital, curl, cursive, dissolve, earring, form, inner, ruffle, script, writing
\end{textsample}
