\begin{textsample}{POS Dim 7 – 1960 – Score 13.00 – 1960/tv\_com\_1960\_76.txt}  \label{ex:f7_pos_024}
The commercial opens in black and white on an interior wall with a dark wooden door set into it.
The wall is covered in busy patterned wallpaper, arranged in small square panels with floral-looking designs.
The door is closed at first, its surface dark and slightly reflective, with a round knob low on the right side.
A \textbf{clean-shaven} adult man with short dark hair peeks around the door from the left side, smiling slightly as he \textbf{enters}.
He is dressed like a \textbf{presenter} : a light-colored suit jacket, a white shirt, a bold striped tie, and a white pocket square.
In one hand he holds a small oil can or lubricant applicator with a thin spout.
He steps into the room, keeps one hand on the door, and turns toward the hinge side.
He faces the door and wall, with his back partly to the viewer, and raises the small applicator toward the upper hinge area.
He appears to apply lubricant near the top of the door, then bends down toward the lower hinge area, leaning close to the wall and doorframe.
His \textbf{posture} is practical and focused, as if demonstrating where metal parts rub and need oiling.
After working low near the hinge, he straightens up and moves the door, testing it by opening and closing or swinging it at the edge.
He then turns back toward the viewer, still holding the small applicator, and stands beside the now-quiet-looking door as he continues speaking.
As he stands centered against the patterned wall, the image begins to introduce a technical \textbf{drawing} over him.
A black line diagram of a car ’s underside appears, gradually replacing the room.
The \textbf{drawing} shows the vehicle from below, with four wheels, the front suspension and steering components at the left, the chassis frame running diagonally through the center, and the rear axle and differential toward the right.
The \textbf{presenter} fades behind it until the car diagram fills the screen.
The diagram remains on a plain gray background.
Thin white arrows and long white lines repeatedly appear and disappear over the \textbf{drawing}, pointing to many lubrication points. \textbf{Most} of the arrows cluster around the front end of the car, where the suspension and steering linkages are \textbf{drawn} in more detail.
Other arrows point along the underbody and toward the rear axle area.
The \textbf{alternating} plain diagram and arrow-filled diagram visually emphasizes the many separate places under a car that need \textbf{attention}.
No mechanic or \textbf{actual} car is shown here ; the service is represented as an instructional schematic.
The diagram continues while the transcript \textbf{context} refers to regular lubrication, the transmission and differential, wheel bearings, and friction points of the body and chassis.
Visually, these ideas are represented by the repeated bright arrows aimed at joints and mechanical contact points throughout the undercarriage \textbf{drawing}.
Near the end, the \textbf{presenter} ’s figure fades back in behind the diagram.
He stands upright again in the same suit, facing forward, with the patterned wall faintly visible behind him.
The car \textbf{drawing} and arrows gradually \textbf{dissolve} away, leaving him centered for a moment.
A large circular Lion brand sign then appears over the \textbf{presenter} and becomes the final image.
The sign fills the screen against a sky with soft clouds.
Inside the circle, a lion stands or crouches across the top of a platform-like shape.
Beneath it, the word “ LION ” appears in very large, bold \textbf{capital} letters.
The sign has a strong circular border and a small decorative fixture below, like a roadside service-station sign.
The final view holds on this Lion emblem, matching the transcript ’s reference to having the car lubricated regularly “ at the sign of the Lion. ”

% matched lemmas: actual, alternate, attention, capital, clean-shaven, context, dissolve, draw, drawing, enter, most, posture, presenter
\end{textsample}
