\begin{textsample}{POS Dim 7 – 2020 – Score 4.00 – 2020/tv\_com\_2020\_83.txt}  \label{ex:f7_pos_079}
The commercial \textbf{unfolds} as a Jeep vehicle advertisement with seasonal/holiday and sales-event imagery. 1. **Opening exterior setting:** The first frame shows a large brick suburban house with a lawn and trees in daylight.
The foreground is motion-blurred, suggesting the camera or vehicle is moving past the property. 2. **Black SUV in motion:** The scene cuts to a black Jeep SUV driving along a paved road bordered by green grass and trees.
The camera angle is elevated and side-on, showing the vehicle moving through a wooded or park-like area in daylight. 3. **Holiday sales-event graphic:** The commercial shifts to an aerial view of a wintery public space with snow-dusted trees, paths, and pedestrians.
A large decorated Christmas tree stands centrally.
Overlaid text reads : **“WRAP UP THE YEAR SALES EVENT”** with the **Jeep** logo beneath it.
A red \textbf{bow} graphic appears above the text. 4. **Red Jeep Wrangler in snow:** A red Jeep Wrangler drives through snow or icy mist, facing toward the camera at a slight angle.
Snow is visible on the hood and surrounding the vehicle.
Overlaid text reads : **“JEEP WRANGLER”** and **“MOST CAPABLE WRANGLER EVER.”** Small fine print appears at the bottom but is mostly too small to read clearly. 5. **Interior dashboard view:** The next frame shows the interior of a Jeep vehicle, centered on the dashboard and infotainment screen, with the steering wheel visible on the left and wood-toned trim across the dash.
Overlaid text reads : **“JEEP GRAND CHEROKEE”** and **“MOST LUXURIOUS VEHICLE IN ITS CLASS.”** Additional fine print appears at the bottom. 6. **Red Jeep off-road:** A red Jeep drives along a rough dirt or gravel mountain road, kicking up dust.
The vehicle is angled toward the camera, with a rocky slope on the right side of the frame.
Overlaid text reads : **“JEEP BRAND”** and **“MOST AWARDED SUV BRAND EVER.”** Fine print is again present at the bottom. 7. **Nighttime town / financing offer:** The commercial cuts to a nighttime aerial view of a town or downtown area decorated with holiday lights.
A large lit Christmas tree is visible near the center.
Large white text overlays the scene : **“NO MONTHLY PAYMENTS FOR 90 DAYS”** and below it **“ON MOST JEEP BRAND MODELS.”** A graphic near the bottom reads **“AMERICA 250”** with red, white, and blue styling.
Dense fine print spans the bottom of the frame. 8. **Transition overlay:** The same nighttime town view continues, but the large text begins to \textbf{fade} or \textbf{dissolve}, producing a layered transition effect.
The holiday-lit streets and buildings remain visible underneath the fading promotional text and fine print. 9. **Final dealer offer screen:** The ad transitions to a static promotional layout featuring a white **2025 Jeep Grand Cherokee Laredo 4x4** parked in front of a large statue of a muscular figure holding something in one hand.
The background appears urban/industrial and gray-toned.
Large offer text on the left reads : - **“2025 JEEP GRAND CHEROKEE LAREDO 4x4”** - **“LEASE FOR \$280 / MO.”** - **“\$280 DUE AT SIGNING”** - **“\$0 DOWN PAYMENT”** There is also a small **“Wrap Up the Year”** sales-event logo, **“JEEP.COM,”** and a large regional/dealer branding line reading **“METRO DETROIT | Jeep.”** Fine-print legal text fills the lower portion of the frame. 10. **Closing frame:** The final frame remains on the same static offer screen with the white Jeep, the statue, the lease pricing, **“METRO DETROIT | Jeep,”** and dense fine print along the bottom.

% matched lemmas: bow, dissolve, fade, unfold
\end{textsample}
