\begin{textsample}{POS Dim 7 – 1980 – Score 5.00 – 1980/tv\_com\_1980\_87.txt}  \label{ex:f7_pos_049}
The commercial opens in a dark, steamy shower environment, lit so that water and wet skin gleam against a nearly black background.
A bare hand and forearm reach up into a strong stream of water.
The fingers are spread and slightly curved, with the water striking the palm and wrist and bursting outward in bright sprays and droplets.
The stream runs down the arm, tracing the shape of the wrist and forearm.
A chrome-and-black showerhead appears, angled downward, sending out several forceful streams.
Its metal surface is shiny and faceted, with black bands around it ; small lettering on the head identifies spray settings, including “ CENTER SPRAY. ” The product is presented as a substantial bathroom fixture with multiple water outlets.
A light-skinned adult woman with short, dark, slicked-back wet hair is shown showering.
She is bare-shouldered, with only her upper body visible.
Water rushes across her face and shoulder as she leans sideways into the spray.
Her eyes are closed, and her expression is relaxed, almost absorbed in the sensation.
She tilts her head back under the falling water, exposing her neck and jawline while droplets scatter across her face and hair.
The water continues to hit her from above and behind, \textbf{forming} bright streaks and bursts around her head.
She turns so that her face is partly in shadow, then the stream catches the side of her neck and shoulder.
Her \textbf{posture} remains slow and languid, as if enjoying the water pressure.
Her hands then press and slide over her wet shoulder and upper back.
One hand moves across the rounded shoulder while another steadies near the side of her body, suggesting she is massaging herself as the spray hits.
The water beads on her skin and runs in sheets down her arm and back.
Another product close-up follows, showing the same chrome-and-black showerhead pouring out a broad, bright \textbf{flow}.
The woman leans her head to one side, eyes closed, with one hand spread over the back of her shoulder.
Water crosses diagonally over her face, ear, neck, and shoulder.
She rubs along the shoulder and upper back with slow, open-palmed strokes.
A separate close view of her hand shows water streaming along her fingers and down the side of her body, emphasizing the force and texture of the spray.
She bends forward slightly, one hand resting on her shoulder while water sweeps over the back of her neck.
Her wet hair lies close to her head.
She continues to move her hand over her shoulder and collarbone area, then tilts her chin upward into the water, her mouth slightly open and her face partly shadowed.
The lighting keeps the background dark while the water flashes white around her.
More close views show her hands sliding over her \textbf{torso} and side, the skin glossy with water.
The spray splashes strongly against her body, then the view returns to her face from the side.
She raises an arm above or across her head, and water falls over her forehead, nose, and cheeks.
Her eyes remain closed, and her expression stays calm and pleasurable as droplets break across her face.
The water continues to run over the side of her neck and shoulder.
A lock or dark strand of wet hair hangs near her jaw as she turns slightly, and her fingers move near her face and hair.
The spray strikes near her mouth and chin, then splashes down onto her shoulder.
The showerhead is shown again in detail.
A hand reaches up to the fixture and appears to adjust the ring or dial around the head.
The visible setting reads “ CENTER SPRAY, ” and the water changes into many straight, evenly spaced streams pouring downward in a dense curtain.
The hand remains near the side of the head as the water pattern continues.
After more dark, partial views of her wet body, one leg is lifted into the spray.
A hand strokes along the shin and calf while water streams over the leg and foot.
The foot extends forward with toes pointed, and droplets fall from the heel and arch.
The leg is rim-lit against the dark background, with the spray crossing behind it in pale diagonal lines.
The hand glides down toward the ankle and foot, continuing the massage-like motion as water runs off in rivulets.
The woman ’s face returns, bent forward with one hand at the side of her neck and shoulder.
Her eyes are closed or lowered, and she rubs her neck and upper chest while the spray passes across her face and body.
She appears relaxed and focused on the feel of the water.
The showerhead appears once more, held or adjusted by a wet hand.
The same chrome-and-black fixture pours out a full pattern of streams, then shifts to stronger central jets.
The product label on the head includes the Shower Massage branding, and the black band with white lettering remains visible.
Near the end, water runs over a bent leg or arm while a hand rests on the skin, continuing the visual theme of self-massage under the spray.
The woman ’s face appears again in soft, wet close view, eyes closed, with one hand against her shoulder.
The final image overlays a product logo on top of the dark shower scene.
In a rectangular box near the lower center, white text reads “ THE ORIGINAL ” above a large \textbf{script} “ Shower Massage, ” with “ BY TELEDYNE ” underneath.
Behind the logo, the woman ’s wet arm and face remain partially visible in shadow, with water still falling around her.

% matched lemmas: flow, form, posture, script, torso
\end{textsample}
