\begin{textsample}{POS Dim 7 – 1970 – Score 8.00 – 1970/tv\_com\_1970\_18.txt}  \label{ex:f7_pos_012}
The commercial \textbf{unfolds} as a montage of outdoor leisure scenes featuring Ford trucks and vans, with frequent \textbf{soft} \textbf{dissolves} and \textbf{superimposed} images. 1. **Beach scene with people and an open vehicle** The first frame shows a woman standing on a sandy beach near the ocean.
She wears a white T-shirt with a colorful vehicle graphic on the front.
Behind her is an open-top vehicle with people sitting in or on it.
The coastline and water are visible in the background. 2. **Dissolve into a white van** The image transitions by overlaying the beach scene with a white van that has orange and yellow side stripes.
The van is shown in a three-quarter front view.
People and another vehicle are faintly visible through the \textbf{dissolve}, creating a layered effect. 3. **Van in front of a storefront** The white striped van remains visible while another scene appears behind it : a storefront with a sign that appears to include the words “ COUNTRY … ” though the full sign is not fully clear.
A dark pickup or car is parked in front of the building.
The images are partially \textbf{superimposed} during the transition. 4. **Orange Bronco-like vehicle in a desert/mountain setting** The montage cuts/dissolves to an orange two-door off-road vehicle parked on a dirt overlook.
It has a white side stripe and large tires.
Mountains and a bright sky are visible behind it.
A person is faintly visible near the passenger side, but details are \textbf{unclear} due to the \textbf{dissolve}. 5. **Yellow pickup near mountains with people** A yellow pickup truck is parked in a scenic mountainous or coastal area.
A woman with long blonde hair stands near the driver ’s side, and a man stands by the front or side of the truck.
A bicycle or round \textbf{object} is visible near the man.
The setting appears outdoors on dirt or gravel. 6. **Close-up of smiling people overlaid with vehicles** A close-up of a smiling woman appears, with another person ’s head partially visible beside her.
This close-up is layered over the previous truck scene, continuing the \textbf{soft} montage effect.
The people appear happy or playful, but no dialogue is visible. 7. **Vehicle driving along a coastal road or beach area** A small orange vehicle is seen in the distance near a body of water or coastline.
The shot remains heavily overlaid with a large, \textbf{soft} close-up of a face from the previous scene, making details \textbf{hazy}.
The landscape appears open and coastal. 8. **Close-up of a vehicle exterior detail** The frame cuts to a close-up of the rear side of a dark-colored vehicle.
A red rear light and a \textbf{decorative} side panel or trim are visible.
A person ’s arm and torso are partly visible on the left, possibly leaning or working near the vehicle, but the action is not fully clear. 9. **Interior of a van** The view shifts inside a van, looking forward from the rear cargo area.
A person sits in the driver ’s seat, facing slightly back toward the camera.
The interior has light-colored seats and a long open floor/cargo space.
The rear doors appear open, with daylight coming in from outside. 10. **Wide beach lineup with title text** A wide shot shows several Ford trucks and vans arranged on a beach near the ocean.
People stand among the vehicles.
Large colorful text at the top reads **“FREE-WHEELIN’”**.
Large white text near the bottom reads **“FORD TRUCKS”**.
Smaller text below reads : **“Based on 1978 retail deliveries of all Ford Trucks.”** 11. **Similar beach lineup held on screen** The beach lineup remains visible, with multiple vehicles : an orange off-road vehicle at left, a light-colored pickup, a dark pickup in the center rear, the white striped van at right, and a yellow pickup in the foreground right.
People remain standing between the vehicles.
The same “ FREE-WHEELIN ’ FORD TRUCKS ” text and the smaller retail-delivery note remain on screen. 12. **Final brand/title card** The final frame changes to a dark green-tinted background with the vehicle lineup faintly visible behind it.
A Ford logo appears at the top within a square graphic marked **“75th ANNIVERSARY”**.
Large white text reads **“FORD TRUCK”**, with smaller text below reading **“FORD DIVISION.”**

% matched lemmas: decorative, dissolve, hazy, object, soft, superimpose, unclear, unfold
\end{textsample}
