\begin{textsample}{POS Dim 7 – 2020 – Score 5.00 – 2020/tv\_com\_2020\_29.txt}  \label{ex:f7_pos_089}
The commercial opens in a dim \textbf{studio} space with a large glowing round light overhead and other production equipment faintly visible.
A young woman with a \textbf{sleek}, chin-length dark bob stands beneath the light, wearing a soft pink, satin-like draped top that sits off one shoulder.
White on-screen words appear across her body and the dark background : “ Go pro with me, ” with “ pro ” and “ me ” in heavier bold type.
The scene shifts into a smooth pink \textbf{studio} \textbf{backdrop}, where she turns toward the viewer with a slight smile as her straight bob swings outward.
A small “ CLAIROL ” mark sits in the upper-right corner while the same “ Go pro with me ” text remains centered over her.
A rectangular box of Clairol ProFixer Hair Color Remover is then displayed upright on a narrow ledge against the pink background.
The package has a black upper section with “ CLAIROL ” in white, images of dark, red, and blonde hair, and a white label area with the product name “ pro fixer ” and “ hair color remover. ” The box is presented alone, centered and cleanly lit.
Back on the woman, she now looks concerned as she lifts and examines a section of her hair near her face, as if checking a color problem.
White text builds around her : “ my pro-tip for fixing. ” She \textbf{draws} strands across her face, then turns her head so the bob swings, the hair catching the light.
The words change to “ any color mishap? ” with “ color ” bolded.
Her expression softens into a confident smile as she faces forward, her hair smooth and glossy against the pink background.
The focus moves into a close view of reddish-brown hair strands, showing a shiny, even surface.
A product-use demonstration follows.
A white nozzle dispenses a thick white cream in a wavy line along a clean part in dark hair ; the word “ apply ” appears over it.
The screen then divides into three vertical rounded panels : on the left, the cream is applied along the hair part with “ apply ” ; in the center, dark wet-looking hair is shown coated or processing with “ develop ” ; on the right, hands massage and rinse lathered hair with “ wash. ” The three-step process is laid out side by side as a simple visual sequence.
The woman reappears tilted and upside down against the pink background, her smooth bob framing her face.
White text begins with “ resets, ” then expands to “ resets color. ” She \textbf{rotates} into a more upright pose while holding the ProFixer box against her chest.
The full \textbf{phrase} “ resets color like a pro ” appears in bold white lettering across the center.
She leans slightly, looking composed and confident, with the product package clearly visible in her hand.
Near the end, she holds the Clairol ProFixer box beside her face in the pink \textbf{studio}, smiling softly.
The package is angled toward the viewer so the brand name and “ pro fixer ” label are visible.
Large white letters spelling “ CLAIROL ” appear above her.
In the final moment, she puckers her lips playfully toward the product while still holding it near her cheek, and the word “ IT ’S ” appears beneath the large Clairol name, beginning the brand slogan shown on screen.

% matched lemmas: backdrop, draw, phrase, rotate, sleek, studio
\end{textsample}
