\begin{textsample}{POS Dim 7 – 1970 – Score 7.00 – 1970/tv\_com\_1970\_25.txt}  \label{ex:f7_pos_019}
The commercial begins with a stylized, cartoon-like restaurant or diner illustration.
A real woman ’s smiling face appears through a circular cutout in the drawing, making her look like part of a caricatured figure.
The illustrated figure is shown holding a large hamburger in one hand and has a napkin or cloth draped over the other arm. \textbf{Decorative} hanging lamps appear on both sides, reinforcing an old-fashioned diner setting.
The image has a vintage television look, with visible softness and a “ Classic Commercial Archives ” \textbf{watermark}.
The next sampled \textbf{moment} appears to be a \textbf{dissolve} or \textbf{superimposed} transition.
The \textbf{cartoon} figure is still faintly visible, but close-up images of food begin to overlay it.
The visible food includes hamburger-like buns or sandwiches and what appears to be a round pastry or bun in the foreground.
The layering makes the exact items somewhat \textbf{unclear}, but the emphasis shifts visually from the illustrated character to appetizing food close-ups.
The scene then changes to an exterior daytime shot of a Wendy ’s restaurant.
The building is shown from across a road, with trees behind it and cars parked around it.
A large sign on the building reads “ Wendy ’s ” and “ Old Fashioned Hamburgers. ” A separate roadside sign with the Wendy ’s branding stands to the right of the building.
The restaurant has a low, rectangular shape with a drive-up or storefront-style façade.
The final frame holds on essentially the same exterior view of the Wendy ’s location.
The camera remains static, showing the building, signage, road in the foreground, parked cars, and surrounding greenery.
No additional action is clearly visible in the sampled frames.

% matched lemmas: cartoon, decorative, dissolve, moment, superimpose, unclear, watermark
\end{textsample}
