\begin{textsample}{POS Dim 7 – 1950 – Score 17.00 – 1950/tv\_com\_1950\_62.txt}  \label{ex:f7_pos_008}
A black-and-white image opens on a large tabletop radio, filling \textbf{most} of the screen.
Its front is divided into two wide grille sections with horizontal slats, a tuning dial with numbers across the lower middle, and two round knobs near the bottom corners.
Behind and above it are leafy plants or flowers, giving the radio a domestic, decorative setting.
The radio image fades into a \textbf{poised} young adult woman facing forward in an elegant \textbf{studio} interior.
She has carefully set, waved hair, light-toned skin, arched brows, and a polished 1950s look.
She wears a dark, off-the-shoulder dress with a light trim along the \textbf{neckline}, a double strand of pearls, matching \textbf{earrings}, and bracelets.
Draped curtains hang to one side, and an ornate wall sconce or chandelier detail appears on the other, suggesting a \textbf{formal} dressing-room or parlor-like setting.
She speaks directly outward, her expression composed and knowing, then smiles slightly as if offering advice.
She reaches down and lifts a bottle or can of hair product into view.
She presents it beside her face, supporting it with one hand and gesturing toward it with the other.
The container is light-colored with a small spray-style top and a printed label ; the large visible words on the front read “ SATIN-SET, ” with “ Revlon ” written below in \textbf{script}.
She holds it steady so the label faces outward, then continues speaking with the product raised beside her.
Her \textbf{posture} is upright and confident, and the product is treated as the \textbf{main} object of \textbf{attention}.
The scene changes to another young adult woman with light-toned skin and light blonde hair, seated or standing before a background of louvered shutters.
She wears an off-the-shoulder lace-patterned dress, pearl \textbf{earrings}, and a bracelet.
Her hair is \textbf{styled} in soft \textbf{curls}, but at first the \textbf{curls} at the side and back appear loose and drooping.
She turns her head slightly to one side and touches the ends of her hair near her neck, looking concerned and uncertain.
Her eyebrows lift and her mouth tightens into a worried expression as she fingers the limp \textbf{curl}.
Large bold white letters appear to her right reading “ WATER, ” visually identifying the ordinary setting method being contrasted.
She continues to touch the sagging side \textbf{curl} while looking off to the side, her expression suggesting disappointment with how the \textbf{hairstyle} is holding.
Her expression then changes.
She turns more toward the front, relaxes, and smiles as the hair around her face appears neater and more \textbf{formed}.
The \textbf{curls} at the sides and back look fuller, more defined, and springy.
She turns her head from front to side, smiling broadly, as if showing that the \textbf{curls} keep their shape from different angles.
She lifts a hand to the side of her head and lightly pats or fluffs the \textbf{curl} cluster near her ear.
On the left side of the screen, large bold lettering appears in quotation marks : “ ‘ SATIN-SET ’. ” While that text remains, she continues to touch and display the \textbf{curls}, smiling and glancing to the side.
The visual comparison is clear : the earlier “ WATER ” hair looked limp and worrying, while the “ SATIN-SET ” hair looks smooth, arranged, and resilient.
The elegant \textbf{presenter} returns in the \textbf{formal} interior.
She again raises the Satin-Set container beside her, label facing forward.
Across the lower part of the image, large bold white text appears : “ NO LACQUER. ” The product remains in her hand at the left side of her body while she speaks outward.
After the text fades, she lowers the container and gestures with her free hand up toward the back of her own neatly set hair, lightly touching it behind her ear.
Her hair stays smooth and carefully waved as she smiles, then brings her hand down and continues \textbf{addressing} the viewer.
Near the end, the \textbf{presenter} remains centered while a large product image and lettering begin to appear behind and over her.
The final product display takes over : on the left is an enlarged bottle of Revlon Satin-Set, with a cap and a patterned label that prominently reads “ SATIN-SET ” and “ Revlon. ” On the right, bold white lettering reads “ Revlon ‘ SATIN-SET ’ PIN-CURL SPRAY-SET, ” with “ Revlon ” in a \textbf{cursive} \textbf{script} above the block letters.
The background becomes dark and plain, making the bottle and text stand out clearly.
In the final view, the bottle stays on the left while new large white words on the right read : “ SET PIN-CURLS THAT LAST TWICE AS LONG! ”

% matched lemmas: address, attention, curl, cursive, earring, form, formal, hairstyle, main, most, neckline, poise, posture, presenter, script, studio, style
\end{textsample}
