\begin{textsample}{POS Dim 7 – 1960 – Score 11.00 – 1960/tv\_com\_1960\_40.txt}  \label{ex:f7_pos_032}
The commercial opens on a nearly black screen with a small “ Nostalgic X’er ” \textbf{watermark} at the lower right.
A dining-table scene appears.
A man in a suit and a blonde woman in a sleeveless top sit at a round white table.
Plates, cups, and a glass coffee pot or carafe are on the table between them.
The woman rests her head on her hand and looks toward the man, while the man looks down toward his plate.
Large \textbf{superimposed} text then fills the center : “ PROCTOR SILEX. ” The dining scene remains faintly visible behind the bold lettering.
The screen cuts back to a dark background.
Partial gold lettering appears at the right edge, then the text changes to a large centered phrase : “ DOES IT ALL! ” The letters are large, blocky, and gold-toned.
Behind the text, a \textbf{faint} image of hands and a kitchen or \textbf{appliance} scene is visible.
A close-up follows at a sink.
Water pours from a faucet while a hand holds or rinses something under the stream.
The running water splashes into the \textbf{basin}.
The shot is tightly framed, emphasizing the faucet, hand, and water.
The blonde woman then appears in close-up, facing the camera.
She has styled shoulder-length hair and wears earrings.
Her expression is engaged, as if presenting or speaking, but no audio \textbf{content} can be determined from the frames.
The next image is a close-up of a metallic \textbf{object} or \textbf{appliance} part against a dark background.
Its exact \textbf{function} is \textbf{unclear} from the sampled frame.
A wider tabletop or kitchen display appears, with several items visible : a container or bowl of food on the left, a central \textbf{appliance} or \textbf{serving} setup, and other kitchen \textbf{objects} on the right.
The image has some overlay or \textbf{dissolve} effects, making the details partly \textbf{indistinct}.
The woman is then shown standing beside a white shelving unit displaying multiple small kitchen \textbf{appliances}.
Visible items include a toaster, a coffee maker or percolator-style \textbf{appliance}, a blender or similar tall \textbf{appliance}, and additional boxed or countertop \textbf{appliances} on lower shelves.
She gestures toward the top shelf, presenting the products.
The large gold text “ DOES IT ” overlays the woman and \textbf{appliance} display, partially obscuring her and the shelving unit.
A close-up of a coffee-making \textbf{appliance} appears next, with a glass pot, white handle, and central metal parts visible.
The \textbf{appliance} is shown against a dark background.
The final frame presents the product and slogan-style visual layout : a coffee \textbf{appliance} on the left, the brand name “ PROCTOR-SILEX ” across the top, and large gold text on the right reading “ DOES IT ALL! ” The “ Nostalgic X’er ” \textbf{watermark} remains at the lower right.

% matched lemmas: appliance, basin, content, dissolve, faint, function, indistinct, object, serve, superimpose, unclear, watermark
\end{textsample}
