\begin{textsample}{POS Dim 7 – 2020 – Score 7.00 – 2020/tv\_com\_2020\_28.txt}  \label{ex:f7_pos_084}
A young adult woman with long, very straight dark brown hair smiles directly forward against a clean white \textbf{studio} background.
Her arms extend out toward the viewer on both sides, as if she is leaning in playfully or holding the viewpoint close.
Large white branding text sits over her chest and hair : “ GARNIER FRUCTIS, ” with the green Garnier “ G ” circle partly behind the word “ GARNIER. ” Her hair is center-parted, smooth, and glossy, falling evenly on both sides of her face.
The view shifts above her head in the same bright white setting.
Her long brown hair spreads out in a wide, smooth sheet as she turns, making the ends fan outward like a polished curtain.
In the lower left, bold orange text reads, “ \textbf{SLEEK} THAT STAYS UP TO 5 WASHES? ” A small green Garnier “ G ” logo appears in the upper right.
As she continues turning, the hair swings in a single fluid arc, the surface reflecting light in long bands.
The ends lift and ripple, but the \textbf{main} body remains straight and \textbf{sleek}.
Her taupe-brown fitted top and bare feet are briefly visible below the sweep of hair.
She faces forward again, smiling warmly.
Her hair moves across the left side of the screen, still straight and shiny, then settles around her shoulders.
She wears a simple dark choker-like necklace with a metallic shine and a short-sleeved taupe top.
The background stays \textbf{minimal} and white, emphasizing the smoothness and length of her hair.
A white mechanical arm appears in a bright, clinical-looking space with curved white rails and pale green accents.
It resembles a robotic applicator or salon tool, with a small rounded nozzle at the end.
The arm moves toward a small white bottle with a bright green pump.
The bottle label reads “ Garnier Fructis Sleek \& Stay, ” with orange and black text.
The robotic clamp holds and \textbf{rotates} the bottle so the label faces outward.
Large product text appears beside it : “ GARNIER FRUCTIS \textbf{SLEEK} \& STAY SYSTEM, ” with “ \textbf{SLEEK} \& STAY ” in bold orange.
A small circular icon at the lower right says “ HEAT ACTIVATED, ” illustrated with a heat styling tool.
Fine white disclaimer text runs along the bottom, \textbf{indicating} the system includes Sleek \& Shine shampoo, conditioner, and Sleek \& Stay.
The commercial then shows a stylized close-up of a hair strand or hair fiber as a technical demonstration.
A translucent, pale grid-like coating wraps around the dark strand, \textbf{forming} a protective sleeve.
The coating appears to slide along the hair, covering it smoothly from one section to the next.
Bold orange text on the right reads, “ PATENTED WATER-RESISTANT TECHNOLOGY, ” with the small green Garnier logo still in the upper right.
The hair fiber is shown at an exaggerated scale, with the grid emphasizing a sealed, protective layer.
Back in the white \textbf{studio}, the woman smiles while white rods or robotic arms pass behind and beside her head, suggesting a controlled styling or testing environment.
Her straight, center-parted hair lies flat and glossy against her back and shoulders.
From above and behind, the hair is shown as a continuous smooth surface, with a bright highlight running down the crown and length.
Orange text appears at the lower left : “ ULTRA GLASSY \textbf{SLEEK}. ” The small fine-print line remains along the bottom.
The rods continue moving horizontally around her while her hair stays aligned, \textbf{sleek}, and reflective.
She then turns to face slightly sideways, smiling with her long hair hanging evenly on both sides of her face.
Large orange text at the bottom reads, “ STAYS UP TO 5 WASHES. ” As the sequence continues, multiple copies of the same woman appear side by side, each with the same long, straight, glossy hair and taupe top.
The row \textbf{grows} until five versions of her are visible, visually reinforcing the “ up to 5 washes ” claim.
Some faces are neutral or softly posed, while the rightmost version smiles.
The background remains plain white, and the small green Garnier logo stays in the upper right.
The final product display shows several Garnier Fructis items arranged on a glossy white platform in the same white-and-pale-green environment.
A robotic arm is still visible at the left, placing or presenting the white “ Fructis Sleek \& Stay ” serum bottle with its green pump in front.
Around it are tall green bottles and a green pump bottle from the Fructis Sleek \& Shine line, including shampoo and conditioner packaging.
Large text on the right reads, “ GARNIER FRUCTIS \textbf{SLEEK} \& STAY SYSTEM, ” with “ \textbf{SLEEK} \& STAY ” in orange.
The products stand upright together as a complete hair-care system, with bright green packaging, orange label accents, and the white serum bottle centered prominently in the lineup.

% matched lemmas: form, grow, indicate, main, minimal, rotate, sleek, studio
\end{textsample}
