\begin{textsample}{POS Dim 7 – 1950 – Score 15.00 – 1950/tv\_com\_1950\_51.txt}  \label{ex:f7_pos_016}
The commercial is in black and white.
It opens with a smiling young adult woman facing forward against a plain \textbf{studio} \textbf{backdrop}.
She has neatly \textbf{styled}, shoulder-length wavy hair and wears a light checkered dress with a wide, off-the-shoulder collar, along with a short pearl necklace.
Her expression is bright and direct, as if \textbf{addressing} the viewer.
She shifts her gaze and head slightly while speaking, keeping an upright, confident \textbf{posture}.
A large rectangular box of Fab detergent appears by itself on a simple \textbf{studio} surface.
The package is dark with oversized white block letters spelling “ FAB ” across the front.
Beneath the brand name, a dark label with white text reads, “ WASHES CLOTHES CLEANER THAN ANY SOAP. ” Large bold words then appear across the product image : “ WHITEST-WHITE AND CLEANEST-CLEAN. ” The scene changes to an outdoor domestic setting, where white laundry hangs on a clothesline in front of a house.
Large sheets or towels are clipped with clothespins and spread across the line, with a walkway, shrubs, and part of a window visible behind them.
The same bold wording remains over the laundry, and then an additional line appears underneath : “ YOU ’VE EVER SEEN! ” The bright laundry fills \textbf{most} of the background, visually matching the claim about whiteness and cleanliness.
The woman reappears over the laundry image briefly and then returns fully to the plain \textbf{studio} setting.
She turns to the side with an attentive smile, then faces forward again.
She continues speaking with animated facial expressions, sometimes widening her eyes or shaping her mouth emphatically.
The setting expands to reveal a \textbf{staged} laundry demonstration.
The woman stands between two washing machines : on her left is an older-style round wringer washer with an open tub and a wringer attachment above it ; on her right is a rectangular top-loading machine with a flat lid.
She gestures between them, presenting both as suitable places to use the detergent.
She reaches toward the machine on her right, then lifts a large Fab box and holds it at chest height with the front label facing outward.
The view moves in closer to her hands and the box beside the open round washer.
She tilts the Fab package over the tub.
A stream of light-colored powdered detergent pours from the open spout into the washer.
The \textbf{flow} is steady and clearly visible against the darker interior of the tub.
The large “ FAB ” letters and the label “ WASHES CLOTHES CLEANER THAN ANY SOAP ” remain readable on the front of the box as she pours.
After adding the powder, she tips the box upright again.
She stands once more between the two washers, holding the box, and then turns toward the rectangular machine as if to show that Fab can be used there as well.
The scene then broadens into a display of many washing machines arranged across the \textbf{studio} like a showroom.
Several different \textbf{styles} of washers stand in rows : boxy top-loaders, machines with front panels and control areas, and older wringer-style models.
A Fab box is placed prominently on or in front of nearly every machine, each with the brand name facing the viewer.
The woman moves among them, smiling and gesturing from one washer to another, reinforcing that the same detergent is meant for all the machines.
Some appliance badges are visible but too small or indistinct to read clearly ; the repeated Fab boxes are the dominant readable visual element.
She walks through the center of the display, using both hands in \textbf{sweeping} motions to \textbf{indicate} the whole group of washers.
At times she stands behind a central machine with a Fab box on top, then points outward to machines on either side.
The machines are arranged symmetrically, with larger rectangular washers in the back row and smaller or lower machines in front.
The plain \textbf{studio} wall and floor keep \textbf{attention} on the appliances and the product boxes.
Her dress moves slightly as she steps between the machines, and she \textbf{maintains} a poised, demonstrator-like manner.
As the display continues, she settles behind a central front machine.
A Fab box sits directly in front of her on the washer lid, centered in the foreground.
More Fab boxes remain visible on the machines behind her at different heights, creating a repeating pattern of the brand name throughout the scene.
She raises her hands outward, palms slightly up, then lowers them, as if presenting all the machines around her.
Her expression \textbf{alternates} between a broad smile and a more emphatic, persuasive look while she gestures.
She then leans forward and places her hands on the central Fab box.
She lifts it from the machine and brings it up toward her chest, holding it carefully with both hands so the front panel faces outward.
The box fills much of the image : “ FAB ” appears in large raised-looking white letters, and below it the label again reads, “ WASHES CLOTHES CLEANER THAN ANY SOAP. ” Her fingers grip the sides and bottom edges of the package.
Returning to the wider view, she holds the Fab box beside her face and turns it slightly toward the viewer.
Behind her, several washing machines remain lined up, each topped with its own Fab box.
She smiles and continues \textbf{addressing} the viewer, keeping the package prominently displayed.
The commercial \textbf{alternates} between a closer product view and the wider arrangement of machines, but the visual focus remains the same : the box front, the bold Fab name, and the claim printed beneath it.
Near the end, she points directly to the large “ FAB ” letters on the box, then to the printed claim beneath them, \textbf{drawing} \textbf{attention} to the package text.
She holds the box against her shoulder and smiles broadly.
Finally, the view widens again to show her centered among the many washing machines, with Fab boxes placed on all of them.
She extends one arm outward while holding the Fab box in the other hand, presenting the entire group of appliances as the \textbf{closing} image.

% matched lemmas: address, alternate, attention, backdrop, closing, draw, flow, indicate, maintain, most, posture, stage, studio, style, sweeping
\end{textsample}
