\begin{textsample}{POS Dim 7 – 2000 – Score 13.00 – 2000/tv\_com\_2000\_46.txt}  \label{ex:f7_pos_061}
The commercial begins with a nearly black frame, with no discernible \textbf{objects} or people visible.
It then \textbf{fades} into a softly lit domestic interior, apparently seen through glass or with layered reflections.
A young \textbf{boy} in a green shirt sits at a table near a window.
Around him are household \textbf{objects}, including a chair, plants, and a \textbf{decorative} \textbf{object} that resembles shredded paper or a nest-like arrangement.
The imagery has a \textbf{hazy}, double-exposed look, with reflections and \textbf{overlapping} shots.
The \textbf{boy} is shown closer, seated at the table and looking downward as if focused on something in front of him.
A white \textbf{bird}, likely a duck or goose, appears nearby in the same interior setting.
The \textbf{bird} is shown in close-up, its long pale neck and beak \textbf{prominent}.
The \textbf{boy} and the \textbf{bird} are repeatedly juxtaposed through \textbf{soft} crossfades.
A trading card is shown briefly.
It has the “ Pokémon ” logo at the top and an illustration labeled “ Pichu. ” The card is held or positioned next to the white \textbf{bird}, creating a visual association between the animal and the Pokémon card.
The \textbf{boy} ’s face appears in close-up behind or beside the \textbf{bird} during the \textbf{dissolves}, looking calm and attentive.
The sequence continues with the \textbf{boy} ’s face in a bright, soft-focus close-up.
He appears to be watching the \textbf{bird} or something on the table.
The editing remains dreamlike, with \textbf{overlapping} images of the \textbf{boy}, the white \textbf{bird}, bowls, and tabletop \textbf{objects}.
The \textbf{bird} is then shown at a blue feeding bowl, appearing to eat.
Another blue bowl and small \textbf{objects} are visible on the table or surface nearby.
Several shots show the \textbf{bird} opening its beak and moving close to the camera, while the \textbf{boy} ’s face remains partially visible through \textbf{dissolves}.
At \textbf{moments}, more than one white \textbf{bird} seems to appear, though the layered editing makes it \textbf{unclear} whether there are multiple \textbf{birds} or repeated \textbf{superimposed} shots of the same \textbf{bird}.
The \textbf{bird} and the \textbf{boy} appear together near a cluttered indoor area.
In one shot the \textbf{boy}, still in a green shirt, is seen from behind or side-on, with the \textbf{bird} close to him.
The environment includes a window or counter area and \textbf{soft} warm light.
The product is then introduced visually : a yellow Game Boy Color handheld console appears in front of a game package.
The game box shows the “ Pokémon ” logo and appears to be for a Pokémon game.
The product is placed among household or garden-like \textbf{objects}, including flowers and a potted plant.
Small white text appears at the bottom ; it reads, “ Game and Game Boy sold separately. ” The box and handheld are shown in a bright, staged product shot, with the “ GAME \textbf{BOY} ” branding clearly visible vertically on the packaging.
Another product shot shows the Game Boy box alone at a slight angle, still surrounded by flowers and plants.
The same bottom disclaimer text remains visible, though partly softened by the image \textbf{quality}.
Near the end, the \textbf{boy} is shown standing indoors beside the white \textbf{bird}, turning his head back toward the camera.
Curtains and a bright window or light source are visible behind him.
There is small text near the bottom that appears to be a website address, but it is too blurred to read with certainty.
The final frame is a close-up of the white \textbf{bird} facing the camera.
Its pale head, yellowish beak, and dark eyes are clearly visible, while the background is blurred and greenish.
The commercial ends visually with the \textbf{bird} as the central focus.

% matched lemmas: bird, boy, decorative, dissolve, fade, hazy, moment, object, overlapping, prominent, quality, soft, superimpose, unclear
\end{textsample}
