\begin{textsample}{POS Dim 1 – 1950 – Score 18.00 – 1950/tv\_com\_1950\_69.txt}  \label{ex:f1_pos_082}
The commercial is in black and white and presents a Ford automobile through a sequence of emblem shots, \textbf{exterior} details, interior features, and \textbf{driving} scenes.
A visible “ OsbornTramain ” watermark appears in the lower-right corner throughout the sampled frames. 1. **Opening brand emblem** The commercial begins with a centered Ford crest-style emblem against a plain dark background.
The word “ FORD ” appears prominently at the top of the \textbf{badge}. 2. **Exterior \textbf{model} identification** The next shot shows a close-up of the rear or front trim area of a \textbf{car} with a chrome \textbf{badge} reading “ FAIRLANE. ” The surface is glossy, with a circular ornament above the \textbf{badge}. 3. **Side \textbf{view} of parked car** The \textbf{car} is then shown from the side, parked in front of a house.
The frame focuses on the passenger compartment and doors, with the roofline and windows clearly visible. 4. **Door handle close-up** A hand reaches toward and grips a chrome \textbf{exterior} door handle on the \textbf{car}.
The shot emphasizes the handle and the \textbf{car} ’s smooth body panel. 5. **Interior door or trim control** A close-up shows a shiny chrome fixture set into a quilted or tiled-looking interior surface.
It appears to be an interior handle or control panel, though its exact function is not fully clear from the frame. 6. **Window area** A shot from \textbf{inside} or very near the \textbf{car} shows a window frame with blurred foliage \textbf{outside}.
A small dark object or mark is visible near the lower-left area of the window.
The exact action is unclear. 7. **Seat and lower interior area** The camera shows the lower side of a \textbf{car} seat with upholstery, piping, and a round knob or control near the base.
Part of a seated person ’s clothing is visible above the seat cushion, but the person is not fully shown. 8. **Rear \textbf{exterior} detail** The rear of the \textbf{car} is shown in close-up, including a round tail light, chrome bumper, and smooth rear body panel. 9. **Full rear three-quarter view** The \textbf{car} appears parked on a \textbf{residential} \textbf{street}.
Houses, lawns, trees, and a sidewalk are visible in the background.
The \textbf{vehicle} ’s rear fins, round tail lights, chrome bumper, and whitewall tires are visible. 10. **Boy ’s face** A close-up shows a smiling young boy outdoors, facing the camera or looking slightly toward it.
The background is blurred, likely foliage or ground texture. 11. **Dashboard clock** The interior dashboard is shown in close-up, focusing on an analog clock set into a rectangular chrome-trimmed panel.
Numbers such as 10, 2, 4, and 8 are visible around the dial. 12. **Radio controls** Another dashboard close-up shows a radio tuning display with numbered frequencies, including 55, 10, 12, 14, and 16.
Below the display are several push buttons and knobs. 13. **Moving side \textbf{view} on road** The \textbf{car} is shown in motion from a close side \textbf{angle}, focusing on the rear side panel with “ Fairlane ” script visible.
The \textbf{road} and landscape \textbf{pass} by in the background. 14. **Frontal \textbf{driving} shot** The \textbf{car} is shown from the front driving toward the camera on an \textbf{open} \textbf{road}.
The grille, headlights, bumper, and \textbf{hood} line are prominent.
The background includes \textbf{open} land and \textbf{distant} \textbf{hills} or mountains. 15. **Final brand image** The final frame overlays or places the large Ford crest emblem in the center foreground, with the \textbf{car} still visible behind it from the front.
The \textbf{road} and landscape remain in the background, reinforcing the brand identification at the end.

% matched lemmas: angle, badge, car, distant, drive, exterior, hill, hood, inside, model, open, outside, pass, residential, road, street, vehicle, view
\end{textsample}
