\begin{textsample}{POS Dim 1 – 2010 – Score 21.00 – 2010/tv\_com\_2010\_37.txt}  \label{ex:f1_pos_029}
The commercial begins on a completely black frame.
It then cuts to an \textbf{aerial} \textbf{view} of a dense \textbf{city} area.
Tall \textbf{buildings}, \textbf{streets}, and blocks are seen from above.
Bright, semi-transparent colored light trails—green, blue, purple, and white—run across the cityscape, following or overlaying \textbf{roads} and corridors, suggesting streams of movement or data.
The next scene \textbf{moves} to \textbf{street} level in a downtown area with tall office \textbf{buildings} on both sides. \textbf{Cars} and a \textbf{bus} \textbf{travel} along a multi-lane \textbf{street}.
Similar luminous colored streaks appear along the roadway and around \textbf{vehicles}, visually linking the \textbf{street} \textbf{traffic} to the earlier \textbf{aerial} light patterns.
A closer \textbf{urban} transit scene follows.
A woman with dark hair stands beside a \textbf{bus}, looking down at a handheld device.
The front or side of the \textbf{bus} is close to her, and the route/display area shows “ K750 ” in yellow.
Colored light overlays appear across the \textbf{bus} surface and around the device area, \textbf{continuing} the motif of glowing information or energy flows.
The commercial then returns to a very \textbf{wide} \textbf{aerial} \textbf{view}, now showing an expansive grid of land and \textbf{roads} stretching toward the horizon.
Numerous bright, straight light lines in \textbf{different} colors \textbf{run} across the landscape, forming a large-scale network-like pattern.
The next shot is indoors.
A young girl stands beside a light-colored object that resembles a toy or child ’s electronic device with a grid of colorful square buttons.
She appears to be pressing or touching the buttons.
Colored light effects overlay the scene, especially near the object and across the frame.
The setting then shifts to a dark control-room or command-center environment.
Two human figures are silhouetted in front of a very large wall display.
The display shows a colorful, map-like or data-visualization image with flowing lines and layered colors.
Smaller panels or interface elements appear around the main screen, but their details are not readable.
Another \textbf{aerial} \textbf{city} \textbf{view} follows, showing a \textbf{skyline} in the \textbf{distance} and a large \textbf{urban} area in the foreground, including green spaces and fields.
A bright blue-purple horizontal light stream \textbf{passes} across the mid-ground, again connecting the \textbf{city} visually through animated-looking colored bands.
The final frame is a black background with the red “ Exxon ” wordmark large across the screen.
The letters are red, with the distinctive crossed “ X ” forms, and there are faint multicolored light textures \textbf{inside} or behind parts of the text.

% matched lemmas: aerial, building, bus, car, city, continue, different, distance, inside, move, pass, road, run, skyline, street, traffic, travel, urban, vehicle, view, wide
\end{textsample}
