\begin{textsample}{POS Dim 1 – 2010 – Score 20.00 – 2010/tv\_com\_2010\_22.txt}  \label{ex:f1_pos_030}
The commercial begins with a quiet interior \textbf{view} looking out of a window onto \textbf{city} \textbf{buildings}.
On the windowsill are small toys : two robot-like figures and a row of toy \textbf{vehicles} or train \textbf{cars} in red, yellow, and green.
The scene then cuts to an \textbf{urban} \textbf{street} \textbf{viewed} from \textbf{inside} or behind a window frame.
A cyclist \textbf{rides} through an intersection.
On the sidewalk, a person in a white, dress-like outfit stands near a \textbf{building}.
A \textbf{bus} and \textbf{cars} are visible in the background.
Next, a delivery or service \textbf{truck} is parked at the curb in a downtown area.
A person stands at the rear of the \textbf{truck} with the back door \textbf{open}. \textbf{Pedestrians} are on the sidewalk, and tall office \textbf{buildings} surround the \textbf{street}.
The commercial then shifts into a more fantastical \textbf{city} \textbf{view}.
From an elevated perspective over rooftops, large childlike paper drawings appear integrated into the \textbf{urban} landscape.
One drawing resembles a large smiling sun or round-headed figure rising between \textbf{buildings}, and another resembles a \textbf{cloud}.
A paper-like object appears to \textbf{move} across the foreground.
More large drawings appear in the \textbf{city}.
One shot shows a giant sad-faced figure, drawn on what looks like a paper bag or folded paper form, standing beside \textbf{buildings}.
A small cartoon flying saucer with yellow lights is shown in the \textbf{sky}.
Another shot shows a tall purple creature-like drawing with multiple eyes standing among \textbf{city} \textbf{streets} and \textbf{buildings}. \textbf{Cars} and \textbf{pedestrians} remain visible at \textbf{street} level, making the drawings appear oversized in relation to the real \textbf{city}.
The next \textbf{city} shot shows another large paper-like drawing, this one resembling a blue robot or machine, positioned between tall office \textbf{buildings}.
White crumpled-paper or cloud-like forms float in the surrounding air.
The scene then cuts to a rooftop or elevated outdoor plaza.
A man in a dark business suit sits alone on a black metal bench.
He has medium-length hair and a beard, and he wears a shirt and tie.
Behind him is a \textbf{skyline} of tall \textbf{buildings}.
Paper-like floating objects \textbf{continue} to \textbf{pass} in the background, visually linking this scene to the earlier imaginary drawings.
A closer side \textbf{view} shows the man seated on the bench, looking downward or to the side.
The following frontal close-up shows him looking down with a serious or tired expression.
His tie appears loosened or slightly disordered, and the \textbf{urban} \textbf{skyline} remains visible behind him.
The visual style then changes abruptly to a bright, digital, abstract environment.
A blue-toned control-room-like scene appears \textbf{inside} a translucent sphere : multiple screens or monitors are arranged on curved walls, with smaller displays below.
The image pulls back or expands to show this scene contained within a glossy blue bubble.
The final sequence shows several translucent blue spheres floating in a white, graphic space. \textbf{Inside} the spheres are \textbf{different} media or technology-related images, including a handheld device being used by someone ’s hands and other screen-based images.
Rows of small blue dots form sweeping, wave-like or spiral patterns across the background.
In one sphere, a tablet-like screen is touched by a hand.
Some text is visible on device screens, but it is too small and blurred in the sampled frames to read reliably.
The commercial ends on a black frame.

% matched lemmas: building, bus, car, city, cloud, continue, different, inside, move, open, pass, pedestrian, ride, sky, skyline, street, truck, urban, vehicle, view
\end{textsample}
