\begin{textsample}{POS Dim 1 – 1960 – Score 20.00 – 1960/tv\_com\_1960\_75.txt}  \label{ex:f1_pos_051}
The commercial is in black and white and unfolds as a motor-racing themed sequence. 1. **Opening darkness** The first sampled frame is almost entirely dark, with no clearly visible objects or setting. 2. **Abstract close-up of a \textbf{car} surface** A bright, curved shape appears on a glossy surface, likely part of a racing \textbf{car} body or \textbf{hood}.
The shot is close and partially abstract, with strong highlights and reflections. 3. **Men at a waterside or \textbf{open} outdoor \textbf{location} with text overlay** Two men appear in a soft, partially superimposed image.
One man wears a light-colored jacket and seems to be gesturing or holding something near his mouth or chest.
The background looks like \textbf{open} water or a flat outdoor horizon.
Large white capitalized text across the bottom reads : **“EVERY INCH A REAL SMOKE.”** 4. **Empty racetrack view** The scene cuts to a straight stretch of paved racetrack, seen from a central forward-facing \textbf{angle}.
There are grassy areas on both sides, posts or fencing, trees in the \textbf{distance}, and a small raised booth or \textbf{viewing} \textbf{structure} on the right. 5. **Driver close-up** A male \textbf{driver} is shown from the front in an open-top race \textbf{car}.
He wears a white helmet and large protective goggles.
His expression appears focused.
Other racing \textbf{cars} are visible behind him, out of focus. 6. **Low trackside \textbf{view} of cars** A low-angle shot shows \textbf{cars} \textbf{moving} along a track in the \textbf{distance}.
The foreground is \textbf{rough} ground or track edge, with trees behind the \textbf{road}. 7. **Blurred \textbf{road} surface** The camera shows a close or fast-moving \textbf{view} of the \textbf{road} surface and lane markings.
The image is blurred, suggesting speed or motion. 8. **Driver in open-top \textbf{car} with competitors behind** The helmeted \textbf{driver} is again seen from the front in his \textbf{open} racing \textbf{car}.
Several other open-top \textbf{cars} are visible behind him on the track.
The \textbf{car} has a low windshield and exposed front wheels. 9. **Dashboard and steering wheel close-up** A close-up shows the \textbf{car} ’s steering wheel, gauges, and dashboard.
A gloved hand holds the wheel.
The shot emphasizes mechanical controls and \textbf{driving} action. 10. **Foot pedal close-up** A close-up shows a \textbf{driver} ’s shoe pressing or operating a pedal \textbf{inside} the \textbf{car}.
The framing focuses on the foot and lower dashboard area. 11. **Cars rounding a curve** A \textbf{wide} shot shows race \textbf{cars} \textbf{moving} through a bend on the racetrack.
The surrounding area is grassy with trees in the background. 12. **Three \textbf{cars} racing closely** A front-facing shot shows a central open-wheel \textbf{car} leading or centered in the frame, with two other \textbf{cars} close behind or alongside.
The \textbf{cars} are rounding a curve or \textbf{moving} on a wet-looking track surface. 13. **Low shot of a \textbf{wet} track/puddle** The camera is very low near the track surface.
A \textbf{car} \textbf{passes} in the background, and the foreground shows a reflective \textbf{wet} patch or puddle, with splashing or \textbf{road} texture visible. 14. **Driver without helmet, seated in car** The scene cuts to a closer \textbf{view} of a young man seated in or near an \textbf{open} \textbf{car}.
He is no longer wearing the helmet ; goggles hang around his neck.
He looks downward, possibly toward his hands or the \textbf{car} interior.
A \textbf{fence} and \textbf{car} bodywork are visible behind him. 15. **Camel cigarette pack in car** A pack of **Camel** cigarettes is shown lying on a dark surface \textbf{inside} or beside the \textbf{car}.
The pack displays the camel illustration and the word **“CAMEL.”** \textbf{Nearby} are parts of the \textbf{car} interior or equipment. 16. **Superimposed pack and driver** The Camel cigarette pack appears large in the foreground through a dissolve or superimposition over the \textbf{driver} ’s head and upper body.
The pack ’s branding and camel image are prominent. 17. **Final product shot on racetrack background** The final frame shows a large Camel cigarette pack centered over the racetrack background seen earlier.
The pack displays the camel illustration and the word **“CAMEL.”** Large bold white text at the bottom also reads **“CAMEL.”** The track, posts, grassy sides, \textbf{distant} trees, and small elevated booth remain visible behind the product image.

% matched lemmas: angle, car, distance, distant, drive, driver, fence, hood, inside, location, move, nearby, open, pass, road, rough, structure, view, wet, wide
\end{textsample}
