\begin{textsample}{POS Dim 1 – 2000 – Score 22.00 – 2000/tv\_com\_2000\_106.txt}  \label{ex:f1_pos_010}
The commercial \textbf{opens} with a long shot of a dark blue \textbf{car} \textbf{driving} along a \textbf{winding} mountain \textbf{road}.
The \textbf{road} curves sharply through green hillsides and rocky slopes.
The scene cuts to the \textbf{car} interior.
A man is \textbf{driving}, wearing an orange shirt and a seatbelt.
A woman sits in the front passenger seat, also belted, wearing a light pink top.
The \textbf{car} has a sunroof, and both occupants appear serious or attentive.
The \textbf{driver} looks forward, focused on the \textbf{road}.
Exterior shots show the blue \textbf{car} \textbf{moving} along a narrow, curving \textbf{road} bordered by rocky \textbf{hills} and \textbf{open} \textbf{sky}.
The \textbf{car} is filmed from low \textbf{angles} and side \textbf{angles}, emphasizing its motion through bends.
The \textbf{sky} is bright with scattered \textbf{clouds}.
The woman in the passenger seat is shown in close-up.
She looks toward the \textbf{driver} and then toward the side or rear, with a concerned or questioning expression.
The commercial alternates between close-ups of the passengers and dynamic shots of the \textbf{car} on the \textbf{road}.
Several close-ups highlight parts of the \textbf{vehicle} : a front wheel spinning, the \textbf{road} surface and lane markings rushing \textbf{past}, and the rear of the \textbf{car}.
The \textbf{model} \textbf{badge} “ focus ” is visible on the back of the blue \textbf{car}.
Another frontal driving shot shows the Ford emblem centered on the grille.
The \textbf{car} \textbf{continues} along the \textbf{rural} mountain \textbf{road}.
The woman is shown again, now smiling slightly.
The \textbf{driver} then turns his head, looking back or toward the passenger side.
Shortly afterward, the \textbf{car} is seen stopped on the roadside with the \textbf{driver} ’s door \textbf{open}.
The blue \textbf{car} is parked near a bend in the \textbf{road}, with \textbf{hills} and a cloudy \textbf{sky} behind it.
A \textbf{view} through the side window shows the woman seated in the \textbf{driver} ’s seat.
White text appears at the bottom of the frame reading : “ the best small \textbf{car} to \textbf{drive} ” and beneath it “ Automobile Magazine, Feb. 02. ” A darker interior shot follows with the same text still visible.
There is a close-up of an \textbf{exterior} door handle on the blue \textbf{car}.
The woman is then shown \textbf{inside} the \textbf{car}, seated at the wheel and looking outward.
A \textbf{wider} shot shows the man standing beside the \textbf{open} driver’s-side area of the parked \textbf{car}, facing the \textbf{vehicle}, while the mountain \textbf{road} \textbf{continues} behind him.
The next sequence returns to \textbf{moving} \textbf{road} shots.
White promotional text appears over the \textbf{road} and landscape, including “ 100,000-Mile Powertrain Coverage. ” Additional smaller warranty-related text is visible but not fully legible in the sampled frames.
A \textbf{wide} landscape shot shows the \textbf{road} stretching across green \textbf{hills} with the same large “ 100,000-Mile Powertrain Coverage ” text overlaid.
The woman is then shown in profile driving, looking ahead.
Exterior shots show the blue \textbf{car} \textbf{driving} again along the \textbf{open} \textbf{road} under a blue \textbf{sky}.
The final frames show the \textbf{car} \textbf{driving} away on a \textbf{winding} \textbf{road}.
A large Ford oval logo appears near the top center of the screen, and a \textbf{website} appears near the bottom : “ www.fordvehicles.com. ”

% matched lemmas: angle, badge, car, cloud, continue, drive, driver, exterior, hill, inside, model, move, open, past, road, rural, sky, vehicle, view, website, wide, wind
\end{textsample}
