\begin{textsample}{POS Dim 1 – 1970 – Score 5.00 – 1970/tv\_com\_1970\_49.txt}  \label{ex:f1_pos_068}
A young woman sits at a study table in what looks like a library or school study room, surrounded by tall shelves of dark-bound reference books.
She has a neat, shoulder-length blond bob and wears a pale blue, striped \textbf{button-up} shirt.
She is absorbed in an open book held in both hands.
Behind her, a young man in a bright red cardigan over a light shirt approaches with a playful smile.
He leans over her from behind and places both hands over her eyes, fully covering them.
She stays seated, her book still open in front of her, while he bends close beside her face as if playing “ guess who. ” She looks startled and then \textbf{puzzled} when he takes his hands away, lifting her head and glancing upward.
He remains close at her left shoulder, smiling broadly, while she turns toward him with an increasingly serious, questioning expression.
The two stay close together at the table.
The young man, still in the red cardigan, leans in beside her, speaking animatedly and watching her face.
The young woman ’s expression shifts from surprise to concern or mild disapproval.
She turns her head toward him, then away, and talks back while seated upright.
In the foreground to the right is a large light-colored bag or satchel packed with books and papers.
The shelves behind them and a windowed wall to the left reinforce the study-room setting.
As their exchange continues, she looks down toward the bag, then reaches forward into it.
Her arm stretches over the top of the bag, and the young man watches closely from behind her shoulder.
She pulls out a blue, transparent bottle of Signal mouthwash and holds it up prominently.
The bottle has a white diagonal label with large black “ Signal ” lettering and a small colored stripe near the top of the label.
The blue liquid inside makes the bottle glow against the library background.
She turns the bottle so the label faces outward, presenting it clearly, then brings it closer between herself and the young man.
He looks at the bottle with a more attentive, slightly chastened expression.
She holds it near her mouth and cheek while speaking to him, as if explaining or recommending it, and he reaches a hand toward the lower part of the bottle as they continue their close conversation.
The setting changes to a clean bathroom sink.
A clear glass tumbler sits on the white porcelain basin, with white faucet handles and pale tiled walls behind it.
A hand holds the same blue Signal bottle near the glass.
The label is large and readable : “ Signal, ” with smaller words indicating it is mouthwash and gargle.
The bottle is uncapped and tilted toward the tumbler.
Blue mouthwash pours in a steady stream from the bottle ’s neck into the glass, collecting at the bottom.
Large bold white capital letters appear across the lower part of the \textbf{screen} : “ SIGNAL FIGHTS STRONG MOUTH ODORS. ” The pouring continues until a visible pool of blue liquid sits in the glass.
The bottle is then brought upright and placed beside the glass, making the product label the central visual focus.
A hand moves near the glass and bottle, arranging them so the bottle stands in front with the filled tumbler just behind and to the side, while the same bold text remains across the bottom.
The scene then moves to a wood-paneled school or college hallway near a staircase.
A young woman with shoulder-length light brown or blond hair stands facing someone in a red top whose back is partly visible at the left edge.
The young woman wears a plaid shirt under a dark blue vest and carries books and a tan folder or notebook against her chest.
She smiles brightly, looking engaged and friendly.
Behind her, a young man in a pale shirt and a light gray-green \textbf{sweater} vest approaches from the staircase area, smiling.
He steps up behind her and raises both hands.
He playfully covers her eyes from behind, using both hands across her face.
She keeps holding her books to her chest and tilts her head slightly, smiling under his hands.
He leans in close over her shoulder, grinning.
The hallway has dark wooden wall panels and other students moving in the background, giving it a busy school atmosphere.
After a moment, he lifts his hands away.
She turns her face toward him with a delighted smile, and he keeps one arm around her shoulders.
They stand close together, smiling at each other warmly.
She holds her books against her body, and he rests his hand near her cheek or chin as they look into each other ’s eyes, relaxed and affectionate.
As they continue smiling closely, the product \textbf{message} overlays the scene.
Large capital letters appear over them reading “ SIGNAL FIGHTS STRONG MOUTH ODORS, ” and the blue Signal bottle becomes superimposed in front of the couple.
The final image becomes a product display on a plain light background : a blue bottle of Signal mouthwash stands upright in the center, with a small clear glass partly filled with blue liquid on one side and a white cap on the other.
Above the bottle, large bold text reads “ SIGNAL FIGHTS STRONG MOUTH ODORS, ” with “ STRONG MOUTH ODORS ” emphasized in yellow while the rest is white.
Small copyright text appears near the bottom, including “ {\EmojiFont ©} 1977 Lever Brothers. ”

% matched lemmas: button-up, message, puzzle, screen, sweater
\end{textsample}
