\begin{textsample}{POS Dim 1 – 1960 – Score 15.00 – 1960/tv\_com\_1960\_4.txt}  \label{ex:f1_pos_057}
The commercial is presented in warm reddish/orange-tinted vintage footage, with a “ Nostalgic X’er ” watermark visible at the lower right in most frames. 1. **Opening \textbf{street} scene:** The commercial begins \textbf{outside} a row of public telephone booths marked “ TELEPHONE. ” A man in a dark suit and hat stands with his back to the camera, facing one of the booths.
Older \textbf{cars} are parked in the foreground on both sides of the frame. 2. **Close-up, unclear movement:** The image cuts to a very close, partially obscured shot of fabric or clothing \textbf{moving} \textbf{past} the camera.
The details are indistinct, but the reddish lighting \textbf{continues}. 3. **Audience or seated group:** A dimly lit shot shows several people seated in rows, likely in an auditorium, theater, or similar public space.
Their faces are mostly in shadow, with bright rim lighting around heads and shoulders. 4. **Close-up of interior objects:** A close-up shows part of an interior setting with a chair-like \textbf{structure} or \textbf{angled} support and a small block-like base.
The exact \textbf{location} and object are unclear from the sampled frame. 5. **Train or \textbf{bus} interior:** A woman in a light-colored hat and coat sits in a cushioned seat beside another passenger.
She appears relaxed or drowsy, leaning back.
A window behind her glows with bright \textbf{exterior} light, suggesting \textbf{travel}. 6. **Bathroom or domestic interior:** A striped towel hangs on a rack near a wall or door.
The shot is static and domestic-looking, possibly a bathroom or wash area. 7. **Street/parking scene:** The commercial returns to an outdoor \textbf{urban} setting.
A man stands between parked \textbf{cars}, one dark \textbf{car} on the left and a pale \textbf{car} on the right.
He appears to be \textbf{moving} or gesturing near the \textbf{cars}. 8. **Obscured transition:** A dark figure or object \textbf{passes} very close in front of the camera, blocking much of the \textbf{view}.
The pale \textbf{car} remains partially visible on the right. 9. **People entering through doorway:** A woman in a red or dark coat with a light collar stands or steps through a doorway, facing forward.
Behind her are other people, including a man in a hat.
Another person is partly visible at the right edge, turned away. 10. **Product close-up:** A close-up of a bottle or container label appears.
The label prominently reads “ Sucaryl, ” with small icons beneath the name that resemble food or drink items. 11. **Product beside cup:** A tall, tapered bottle labeled “ Sucar … ” stands on the left beside a cup or mug filled with a dark liquid.
A hand at the right holds a small item or utensil near the cup, suggesting preparation or sweetening, though the exact action is not fully visible. 12. **Final product/title frame:** The bottle remains on the left against a plain warm background.
Large text appears on the right reading “ Sucaryl, ” with smaller text underneath that reads “ SWEETENER. ” The bottom of a cup or saucer is partly visible near the lower edge.

% matched lemmas: angle, bus, car, continue, exterior, location, move, outside, pass, past, street, structure, travel, urban, view
\end{textsample}
