\begin{textsample}{POS Dim 1 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_31.txt}  \label{ex:f1_pos_050}
The commercial \textbf{opens} on a \textbf{wide} desert \textbf{canyon} landscape at golden-orange light.
Rocky mesas and \textbf{cliffs} frame a valley, with deep shadows in the foreground and warm sunlight on the \textbf{rock} faces.
A silhouetted human figure then appears in the same \textbf{canyon} setting, shown in profile against the orange \textbf{sky}.
The person wears a large feathered or spiked headdress-like silhouette and seems to be \textbf{moving} or posing with one knee raised and arms bent, as if dancing or performing.
The figure remains dark, so facial features, clothing details, and identity are not visible.
The imagery shifts to a close \textbf{view} of desert ground and \textbf{rocks}, tinted orange.
A small dark shape, possibly an animal or shadow, appears against the sandy surface, but it is unclear.
This is followed by clearer shots of a lizard on rocky terrain.
The lizard is shown close to the ground among stones, with warm desert light and a shallow, hazy background.
The commercial then cuts to action shots involving a bicycle.
A low-angle close-up shows a cyclist \textbf{riding} over \textbf{rough}, rocky ground, kicking up orange dust.
The rider appears to be wearing shorts and possibly a helmet, though details are blurred by motion and the low-resolution image.
The bicycle frame and wheels dominate the foreground.
Another shot shows the cyclist from the front or slightly above, \textbf{riding} along a rocky surface.
A reddish-orange vertical overlay or superimposed image appears at the right side of the frame, creating a layered, stylized effect.
The exact content of the overlay is unclear, but it resembles \textbf{rock} texture or a human form blended into the scene.
The sequence becomes more dynamic and abstract.
A cyclist or airborne figure appears against a blue \textbf{sky} and \textbf{canyon} background, possibly jumping or \textbf{moving} rapidly ; the frame is partially blurred and difficult to interpret.
The next frame is heavily overlaid and motion-blurred, with orange and blue shapes, a bicycle wheel-like curve, and a human form suggested but not clearly separable.
The final frame returns to the silhouetted desert setting.
Against a vivid orange \textbf{sky}, the headdress-like figure stands beside a bicycle.
The person is in profile with one knee raised, echoing the earlier pose, while the bicycle is clearly visible to the right.
The scene ends with both figure and bicycle as dark silhouettes on the horizon.
No readable text, product packaging, or visible slogan appears in the sampled frames.

% matched lemmas: canyon, cliff, move, open, ride, rock, rough, sky, view, wide
\end{textsample}
