\begin{textsample}{POS Dim 1 – 1980 – Score 15.00 – 1980/tv\_com\_1980\_41.txt}  \label{ex:f1_pos_076}
The commercial \textbf{opens} outdoors in a bright, \textbf{open} area with a large pile of cut logs under a blue \textbf{sky}.
A person is standing or climbing among the logs, holding a long-handled tool, possibly an axe or similar implement.
The next shot widens to show the same log-filled setting.
A dark \textbf{pickup} \textbf{truck} is parked on sandy or dusty ground near the pile, while the person with the tool stands beside it.
The \textbf{truck} appears to be a Ford \textbf{pickup}, with a dark body and light trim.
A product demonstration sequence follows.
The \textbf{truck} is shown in profile driving or positioned on top of the logs.
Overlaid text appears on the screen.
Large figures at the upper right read “ 25 EST HWY ” and “ 18 EPA EST MPG. ” Smaller disclaimer text across the bottom includes : “ Optional 4-speed trans.
For comparison.
Your mileage may differ depending on speed, \textbf{distance} and weather.
Actual highway mileage lower.
MPG required in Calif. ” The \textbf{truck} is presented as \textbf{moving} across an uneven bed of logs.
The camera then cuts to a lower, \textbf{wide} \textbf{view} of the log pile, with the \textbf{pickup} near the top.
The \textbf{truck} is small in the frame, emphasizing the \textbf{rough} terrain and the height of the stacked logs.
Several closer shots show the \textbf{truck} negotiating the logs.
From the front, the \textbf{pickup} ’s grille, headlights, and Ford \textbf{badge} are visible as the \textbf{vehicle} \textbf{rides} over uneven logs.
The suspension and front wheels appear raised at \textbf{different} levels due to the irregular surface.
Another close-up focuses on the front end and lower grille as the \textbf{vehicle} \textbf{moves} over the logs.
A side close-up shows a tire rolling over a log ; the \textbf{badge} “ F-150 ” is visible near the front side panel.
Another shot frames a large upright or \textbf{angled} log in the foreground, with the \textbf{pickup} behind it on the log pile.
The \textbf{truck} remains positioned among the logs, reinforcing the rugged obstacle-course setting.
Near the end of the demonstration, the \textbf{truck} is shown parked or paused on top of the log pile.
The person with the tool stands \textbf{nearby} on the logs, next to the \textbf{truck}.
The commercial then transitions to a graphic : a dark, rocky or metallic silhouette of the United States against a blue background.
Large white block lettering across it reads “ AMERICA ’S \textbf{TRUCK}. ” The final brand screen shows the blue Ford oval logo centered on a dark background, with the words “ FORD DIVISION ” underneath.
The screen then cuts to black.

% matched lemmas: angle, badge, different, distance, move, nearby, open, pickup, ride, rough, sky, truck, vehicle, view, wide
\end{textsample}
