\begin{textsample}{POS Dim 1 – 1990 – Score 11.00 – 1990/tv\_com\_1990\_112.txt}  \label{ex:f1_pos_042}
A dark, blue-tinted computer-style display fills the \textbf{screen}, as if seen through a \textbf{robot} ’s targeting \textbf{system}.
A large ant appears magnified against a textured background, its pale legs and golden body segments clearly visible.
The words “ SEARCH MODE ” glow in the upper left, with a thin rectangular targeting border, small corner markers, and stacked indicator bars along the side.
The view changes to a dim kitchen interior still overlaid with the same search \textbf{graphics}.
Cabinets, a countertop, a \textbf{coffee} maker, bottles, and small appliances sit along the right side, while the floor stretches into the foreground.
A glowing orange trail curves across the kitchen floor, dotted with tiny dark specks that suggest a line of ants moving through the room.
A doorway opens into a smoky, backlit space.
A huge, dark humanoid \textbf{robot} silhouette stands in the doorway, broad-shouldered with oversized arms and heavy mechanical legs.
Bright light shines from behind it, creating a dramatic outline.
As it steps forward, small lights on its body and head begin to glow, and a horizontal flare of light crosses its chest and face.
The \textbf{robot} ’s \textbf{bulky} body fills the doorway, framed by the open doors and blue haze.
The \textbf{robot} is then seen from the front in a larger interior space with high windows and beams of \textbf{cool} blue light behind it.
Its upper body has a cockpit-like opening ; inside is the face of an adult man, visible through the machinery.
He appears to be operating or wearing the \textbf{robot} suit.
The front of the suit includes the Orkin name on a chest panel.
Mechanical arms and side panels rise around him, and small lights dot the \textbf{robot} ’s torso.
A close view of a metallic nozzle attached to the \textbf{robot} ’s arm points outward.
The nozzle resembles a small cannon or sprayer, with a round barrel and polished metal tip.
A bright yellow-orange beam projects from it.
The beam is shown sweeping into the kitchen area, aimed along the counter and appliances.
The display returns to a targeting view of an ant, now enlarged and partly translucent with colored internal-looking areas.
A rectangular orange targeting frame and crosshairs lock over the insect.
Small white text along the bottom reads, “ REFUND LIMITED CALL ORKIN FOR DETAILS. ” The targeting words progress to “ TARGET TERMINATED, ” and a large orange “ GUARANTEED ” appears over the ant image, reinforcing the result of the attack.
The \textbf{robot} faces forward again, still surrounded by blue light, with the arm-mounted sprayer extended and the yellow beam shining from it.
Large white text appears across the bottom : “ 1 800 800 ORKIN. ” As the image continues, the \textbf{bulky} \textbf{robot} exterior gives way to the \textbf{real} Orkin Man standing in its place.
He is an adult man in a neat service uniform : a light-colored \textbf{button-up} shirt with a black tie, tan trousers, a dark belt, and a white cap \textbf{bearing} the Orkin logo.
He holds pest-control equipment at his side and stands confidently against the smoky blue background.
The red Orkin logo appears near him, while the large \textbf{phone} number “ 1 800 800 ORKIN ” remains across the bottom.
He finishes facing forward with a slight smile, one hand near his hip, presenting the service directly to the viewer.

% matched lemmas: bear, bulky, button-up, coffee, cool, graphics, phone, real, robot, screen, system
\end{textsample}
