\begin{textsample}{POS Dim 1 – 1950 – Score 12.00 – 1950/tv\_com\_1950\_14.txt}  \label{ex:f1_pos_089}
The commercial begins with a nearly black frame, with no discernible visual content.
It then cuts to a black-and-white line-drawn animated industrial/workshop setting.
A stocky, balding male cartoon figure in a suit or coat \textbf{runs} urgently through a factory-like space.
The background contains machinery, pipes, hanging cables, hooks, windows, tools, wheels, and control panels.
Other simplified figures appear in the background, suggesting a busy workplace.
The main man is drawn with exaggerated motion lines and, at times, multiple arm positions, emphasizing haste.
The man \textbf{continues} \textbf{running} \textbf{past} large \textbf{industrial} machines.
He \textbf{moves} behind and around big mechanical \textbf{structures} with gears, belts, wheels, and panel-like controls.
The camera/view follows him laterally as he exits the factory area and heads toward a doorway.
A small sign is visible near the doorway, but the text is not fully clear in the sampled frames.
The scene changes to an office or administrative corridor.
Doors and wall signs appear, including one door labeled “ Rooms ” or similar, though the smaller text is unclear.
Silhouetted office workers \textbf{move} through the space \textbf{carrying} briefcases and papers.
The main man \textbf{runs} through the corridor, weaving \textbf{past} people.
Some figures are shown as dark silhouettes, while others are lighter background drawings.
Desks, chairs, seated workers, and piles of papers appear along the \textbf{route}.
As the man \textbf{moves} through the office area, he encounters multiple people handling documents.
A woman holds papers near the corridor ; another seated worker appears at a desk.
The man \textbf{continues} forward, still in a \textbf{running} pose.
A door labeled “ PRIVATE ” appears behind him.
A framed wall sign or certificate reading “ INDUSTRY ” is visible on the wall.
He \textbf{passes} another seated figure at a desk who is holding or receiving papers.
The man then \textbf{approaches} and enters a door labeled “ CODE ” or possibly another short word ; the exact text is not fully clear.
His movement remains urgent, with one leg lifted as if rushing through the doorway.
The next sampled shot shows a \textbf{different} office scene : a worried-looking man sits at a desk covered with many papers.
Large piles of documents surround him, including stacks on both sides and papers spilling over the desk.
Words float around his head, representing pressures or concerns.
Some are legible or partly legible, including “ \textbf{CARS}, ” “ 35 YEARS, ” “ PAID BEFORE FIVE, ” “ NOW, ” “ HE SAID, ” “ POSTPONE, ” and “ BOARD, ” while other words/numbers are unclear.
The visual focus is on the man being overwhelmed by paperwork and deadlines.
A close-up follows of a man ’s head drawn in profile.
A rectangular form labeled “ WESTERN UNION ” is placed across or in front of his face/head like an idea or message.
The form contains lines of text, but only “ WESTERN UNION ” is clearly readable.
The following office shot shows a woman seated at a desk on the left, apparently typing or working at a machine, while a man sits back in a chair on the right holding a document.
Between them is a desk or cabinet with a tall stack of papers rising above it.
The scene suggests clerical processing or message handling, but no dialogue or audio is visible.
The commercial ends with a static card showing a large Western Union telegram form.
At the top it reads “ WESTERN UNION ” with “ TELEGRAM ” beneath it.
In the center, \textbf{inside} an oval, large handwritten-style text reads : “ it ’s wise to wire. ” The final frame remains on this end card.

% matched lemmas: approach, car, carry, continue, different, industrial, inside, move, pass, past, route, run, structure
\end{textsample}
