\begin{textsample}{POS Dim 1 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_107.txt}  \label{ex:f1_pos_085}
The commercial is in black and white and appears to centre on automobile \textbf{travel}. - **Opening frame (0.000s):** A \textbf{car} is shown from a \textbf{distance} \textbf{driving} along a \textbf{winding} \textbf{road} in a mountainous or rocky landscape.
The \textbf{road} curves through steep terrain, with \textbf{cliffs} or dense dark vegetation on both sides.
The \textbf{vehicle} is small in the frame, emphasizing the \textbf{road} and scenery. - **Around 11.9s:** The scene cuts to a close-up of a woman seated \textbf{inside} what appears to be a \textbf{vehicle}.
The background is blurred, with light-colored seat backs visible behind her.
She faces forward but looks slightly to the side, with an animated facial expression.
The image has some motion blur or double exposure, suggesting either movement or a transition effect. - **Around 20.1s:** The commercial cuts to a close-up of a man, also seated \textbf{inside} the \textbf{vehicle}.
He is wearing a suit and tie and faces directly toward the camera.
Seat backs and indistinct figures or interior shapes are visible behind him.
His expression is composed, with a slight smile or confident look. - **Around 26.2s:** The woman appears again in close-up \textbf{inside} the same or similar \textbf{vehicle} interior.
She is framed frontally, with blurred interior elements behind her.
Her expression is more tense or exaggerated in this sampled frame, and there is visible blur/ghosting, possibly from movement or an overlapping transition. - **Final frame (58.0s):** The viewpoint shifts to \textbf{inside} a \textbf{vehicle} looking forward through the windshield.
A \textbf{road} stretches ahead under trees, with a railing or \textbf{fence} visible to the right.
The \textbf{driver} is seen only as a dark silhouette on the left.
Windshield wipers and the dashboard area are visible in the foreground.
The \textbf{car} appears to be \textbf{moving} along a tree-lined \textbf{road}.
Overall, the sampled frames show a sequence \textbf{moving} between \textbf{exterior} \textbf{road} \textbf{travel}, close-ups of passengers or occupants \textbf{inside} a \textbf{vehicle}, and a driver’s-eye/front-windshield \textbf{view} of the \textbf{road}.
No product name, written slogan, or audio information is visible in the provided frames.

% matched lemmas: car, cliff, distance, drive, driver, exterior, fence, inside, move, road, travel, vehicle, view, wind
\end{textsample}
