\begin{textsample}{POS Dim 1 – 2010 – Score 27.00 – 2010/tv\_com\_2010\_83.txt}  \label{ex:f1_pos_022}
The sampled commercial begins with a bright, pale-blue product display that appears separate in style from the rest of the sequence.
A large white “ chewy ” wordmark is shown above a blue Chewy.com box filled with pet products.
Two dogs flank the box, and a toy or small pet figure sits among the products.
The background is a simplified living-room setting in the same blue tone.
Very small \textbf{legal} text appears near the bottom but is not fully legible.
The screen then cuts to black for several seconds.
The next section shifts into a \textbf{montage} of historical or archival-looking imagery.
A shirtless male martial artist is shown in a dim outdoor or garden-like setting.
This is followed by a \textbf{wider} shot of the same or similar martial artist \textbf{inside} a traditional-looking room with sliding doors, posed mid-action.
The footage has a cinematic, older-film appearance.
The \textbf{montage} then cuts to a close-up of a hand drawing or painting a long, low architectural \textbf{structure} on paper.
The image is warm-toned and looks like a drafting or design process.
The sequence \textbf{moves} into black-and-white baseball imagery.
A baseball player in a “ Dodgers ” uniform and cap is seen near a dugout or \textbf{fenced} area.
Then there are crowd shots in black and white, with people standing and cheering.
A \textbf{wide} stadium \textbf{view} shows players spread across a baseball field.
Another crowd shot shows spectators reacting enthusiastically.
The \textbf{montage} includes sepia-toned images of an older man in a suit seated at a drafting table in front of a large architectural drawing.
Later, the same or similar older man is shown at a desk in front of a curved architectural \textbf{model} or \textbf{structure}.
These shots emphasize design, planning, and architecture.
The baseball \textbf{montage} \textbf{continues} with a player in a white uniform, visible number “ 42 ” on the back, \textbf{running} across the field.
Large blurred lettering or signage appears behind him.
Several quick side-on shots show the player \textbf{running}, with the background streaking horizontally, creating a sense of speed.
The commercial then changes to a contemporary \textbf{car} sequence.
A red Mazda \textbf{sedan} \textbf{drives} along a curving two-lane \textbf{road} through a green, wooded area.
The camera shows the \textbf{car} \textbf{approaching} from the front, then \textbf{passing} close to the camera from the side, highlighting the red bodywork and streamlined profile.
Small text appears near the bottom in some shots, but it is too small to read clearly.
A close, elevated \textbf{view} of the red \textbf{car} ’s front end appears with a visible on-screen label reading “ SKYACTIV TECHNOLOGY. ” Fine print appears below but is not legible in the sampled frame.
The \textbf{car} is then shown driving in an \textbf{urban} setting, \textbf{passing} \textbf{buildings} and stone walls. \textbf{Inside} the \textbf{car}, a male \textbf{driver} is shown from the front, seated behind the wheel and wearing a seatbelt.
He looks forward with a focused expression.
The \textbf{exterior} red Mazda is then shown from a low front \textbf{angle} on a \textbf{city} \textbf{street}.
The setting shifts to a \textbf{wider} roadway or bridge, with the red \textbf{car} \textbf{driving} against a \textbf{city} \textbf{skyline} in the \textbf{distance}.
A close-up \textbf{inside} the center console shows a hand operating a round control knob surrounded by buttons.
The next frame shows the dashboard infotainment screen.
Visible interface text includes “ aha, ” “ Presets, ” “ \textbf{Nearby}, ” “ TechTalk, ” “ Facebook, ” “ Twitter, ” “ Groove Salad, ” “ The Drive, ” and a time reading “ 5:37. ” A blurred close-up of the \textbf{moving} red \textbf{car} follows, emphasizing motion through streaked red bodywork and wheel movement.
The \textbf{montage} briefly returns to the sepia-toned older man at the drafting desk and then to the black-and-white baseball player in the dugout area, now shown in a closer portrait-like shot, looking toward the camera.
Near the end, the image fades or flashes to a bright white circular light effect.
The final frame shows the Mazda emblem above the blue word “ mazda, ” with the stylized word “ zoom ” beneath it on a diagonal white shape against a dark background.

% matched lemmas: angle, approach, building, car, city, continue, distance, drive, driver, exterior, fence, inside, legal, model, montage, move, nearby, pass, road, run, sedan, skyline, street, structure, urban, view, wide
\end{textsample}
