\begin{textsample}{POS Dim 1 – 2000 – Score 22.00 – 2000/tv\_com\_2000\_119.txt}  \label{ex:f1_pos_011}
The commercial \textbf{opens} in a very dark tunnel-like space, where a row of rectangular ceiling lights recedes into the \textbf{distance}.
It then cuts to the \textbf{outside} of a stone-arched \textbf{road} tunnel.
The camera is low near the roadway, looking toward the tunnel \textbf{entrance}.
A \textbf{road} with a shoulder line leads into the dark tunnel, and small white text appears near the bottom reading, “ Professional riders on closed \textbf{course}. ” A close-up follows of double yellow center lines on a \textbf{road}, still with the same “ Professional riders on closed \textbf{course} ” disclaimer at the bottom.
The next shot shows a large touring motorcycle leaning through a curving mountain \textbf{road}.
The motorcycle ’s headlights are on, and hazy mountain silhouettes fill the background.
The same disclaimer remains visible near the bottom.
The sequence \textbf{continues} with multiple \textbf{riding} shots in \textbf{different} landscapes.
One shot shows a dark touring motorcycle \textbf{traveling} through a dry, scrubby area with blurred vegetation in the foreground and background.
Another shows a motorcycle \textbf{approaching} on a paved mountain \textbf{road}, with bright snow-covered peaks in the \textbf{distance}.
The bike is centered in the lane and \textbf{moving} toward the camera.
A side \textbf{view} then shows a motorcycle \textbf{carrying} two riders.
Both wear helmets and dark jackets ; the \textbf{driver} wears light blue jeans.
The motorcycle has a windshield and a large rear seat/backrest.
The \textbf{road} \textbf{runs} through a mountainous or forested area.
A \textbf{distant} overhead or high-angle shot shows a single motorcycle \textbf{riding} along a \textbf{wide}, pale \textbf{road} bordered by yellow-green fields or vegetation.
The bike casts a shadow behind it.
Another shot features an orange touring motorcycle on a two-lane \textbf{road} through red \textbf{rock} \textbf{canyon} terrain.
The rider wears a dark helmet and clothing.
The motorcycle has a windshield, large side cases, and rounded orange storage compartments.
A promotional title card appears over a \textbf{road} scene.
A metallic wing-like emblem is centered above large text reading “ GOLDWING, ” with “ Test \textbf{Ride} ” below it.
Fine-print legal/disclaimer text \textbf{runs} along the bottom, but most of it is too small and blurred to read clearly.
The background remains a curving \textbf{open} \textbf{road} with trees and \textbf{hills} in the \textbf{distance}.
The commercial then returns to action footage : a dark touring motorcycle \textbf{rides} toward the camera on a desert \textbf{road} bordered by red \textbf{rock} formations.
White fine-print text remains overlaid at the bottom.
The final frame shows a \textbf{wide} scenic landscape : a narrow \textbf{road} \textbf{runs} through bright yellow fields toward \textbf{distant} \textbf{cliffs} and mesas.
A lone motorcycle \textbf{rides} away from the camera down the center of the \textbf{road}.
Over the landscape is a red wing-like logo and large white text reading “ PERFORMANCE FIRST. ” Smaller dealership/contact text appears along the bottom, but it is partly blurred and not fully legible.

% matched lemmas: approach, canyon, carry, cliff, continue, course, different, distance, distant, driver, entrance, hill, move, open, outside, ride, road, rock, run, travel, view, wide
\end{textsample}
