\begin{textsample}{POS Dim 1 – 1950 – Score 17.00 – 1950/tv\_com\_1950\_97.txt}  \label{ex:f1_pos_083}
The commercial is in black and white and unfolds as a sequence about Ford \textbf{trucks} and their features. 1. **Opening** - The first frame is nearly black, with no clearly visible objects or people. 2. **Showroom or garage setting** - A man in a dark suit stands beside a light-colored Ford \textbf{pickup} \textbf{truck} indoors. - He is positioned next to the driver-side door, appearing to handle or demonstrate the door area. - Behind him are wall posters or display charts ; some text is partially visible, including “ ’ 53 Ford ” and “ FOUR, ” though the full wording is not fully clear. - The setting looks like a dealership, showroom, or service/display area. 3. **Close-up of door hardware** - The video cuts to a close-up of a \textbf{truck} door hinge or latch mechanism. - A metal arm or hinge component is shown between the door and the body frame. - This appears to be a mechanical detail shot, likely emphasizing construction or durability, though no claim is visually stated in this frame. 4. **Presenter by \textbf{open} \textbf{truck} door** - The suited man stands facing the camera near the \textbf{truck}, with the driver-side door \textbf{open}. - The \textbf{truck} cab and part of the front fender are visible behind him. - He appears to be presenting or demonstrating the \textbf{vehicle}, but no speech is visually available. 5. **Seat construction close-up** - The scene changes to a close-up of an exposed seat \textbf{structure}. - The upholstery is partly removed or cut away, \textbf{revealing} metal springs and support elements \textbf{inside} the seat. - The shot focuses on the internal spring pattern and frame. 6. **Simplified side-view seat graphic/model** - A plain side-view image of a seat appears against a simple background. - The seat is shown as a solid, simplified form with a backrest and cushion, mounted on a base. - This looks like a diagrammatic or studio product shot rather than a real \textbf{truck} interior. 7. **Cutaway seat view** - The seat is shown again in a three-quarter \textbf{view}, partly upholstered and partly exposed. - Springs and internal support \textbf{structures} are visible in the seat back and cushion. - The image emphasizes the construction of the seat. 8. **Man \textbf{inside} \textbf{truck} cab** - The suited man is now seated \textbf{inside} the \textbf{truck}, seen through the front windshield. - He faces forward and appears to gesture with one hand. - The driver-side door is \textbf{open}, and the windshield, steering wheel area, and cab interior are visible. 9. **Rear/side \textbf{view} through cab window** - The man is seen through the rear or side window of the cab. - He turns or looks toward the camera from \textbf{inside} the \textbf{truck}. - The smooth rear cab panel and rectangular window dominate the frame. 10. **Man seated in \textbf{open} cab doorway** - The man sits \textbf{inside} the \textbf{truck} with the door \textbf{open}, facing outward toward the camera. - The dashboard and steering wheel area are partly visible. - A poster with a drawing of a \textbf{truck} is visible behind the cab, though the text is not fully readable. 11. **Large \textbf{truck} on \textbf{road}, frontal view** - The scene shifts outdoors to a large Ford \textbf{truck} \textbf{driving} on a \textbf{road}. - The camera faces the \textbf{truck} head-on. - Two people are visible through the windshield, one driving and another seated beside them. - The \textbf{truck} has a large cargo body or trailer behind the cab. 12. **Large \textbf{truck} \textbf{driving} along road** - A \textbf{wider} \textbf{exterior} shot shows the \textbf{truck} \textbf{traveling} along a paved \textbf{road}. - The \textbf{truck} is pulling or \textbf{carrying} a long, high-sided cargo body/trailer. - \textbf{Road} markings, roadside fields or \textbf{grass}, and \textbf{distant} trees are visible. - The \textbf{truck} \textbf{moves} forward along the roadway. 13. **Final title card** - The final frame shows large centered text : - “ FORD ” - “ ECONOMY ” - “ \textbf{TRUCKS} ” - “ for ’ 53 ” - The word “ ECONOMY ” is in a more cursive or italic style, while the other words are in bold block lettering. - A faint \textbf{vehicle} image appears behind the text, but it is mostly obscured by the title.

% matched lemmas: carry, distant, drive, exterior, grass, inside, move, open, pickup, reveal, road, structure, travel, truck, vehicle, view, wide
\end{textsample}
