\begin{textsample}{POS Dim 1 – 1990 – Score 9.00 – 1990/tv\_com\_1990\_34.txt}  \label{ex:f1_pos_045}
A college campus appears in warm autumn colours.
Red leaves fill the upper left, and golden foliage surrounds a stone archway.
Beneath the arch, students move through a shadowy entrance.
A young woman with shoulder-length red hair, wearing a light patterned \textbf{sweater} and \textbf{jeans}, walks beside a stocky blond young man in a red varsity jacket with gold sleeves and a large letter on the chest.
Both carry books or folders, suggesting they are students.
As they stroll and talk, the woman gestures with papers in her arms.
A yellow folder slips or falls to the ground near their feet.
The young man notices, bends down, and picks it up while still holding several books against his side.
He straightens, smiling and continuing the conversation with her.
The scene shifts to a long, arched stone corridor with bright windows along the left and a row of bicycles parked on the right.
In the left foreground, a student struggles under a \textbf{bulky} rolled-up white object, possibly bedding or a rug, draped over his shoulders, with bags or fabric hanging around him.
He shuffles along awkwardly near the windows, partly blocking another student in red clothing.
The corridor feels like an old campus building, with repeating arches stretching into the distance and scattered leaves on the floor.
On a football field, the same blond young man appears in full football gear, wearing a red jersey with the large yellow number 97 and shoulder pads that make him look broad and oversized.
He jogs toward the viewer across green turf, holding a football helmet at his side.
Empty stadium seats and goalposts fill the background.
He slows close to the front, looking winded but pleased, as other distant players practice behind him.
Back on a campus walkway covered with fallen leaves, the young man is again in his red-and-gold varsity jacket, carrying a book tucked under one arm.
He walks toward the viewer with a relaxed, upbeat expression.
Other students in similar red jackets walk away in the soft-focus background.
He lifts one arm in a casual wave.
A clean white graphic \textbf{screen} appears.
Across the centre, a black horizontal rectangle contains the bold gold text “ 1-800-COLLECT. ” Below it, large black text reads “ Save up to 44 \%. ” Small \textbf{fine} print at the bottom says, “ Vs. 3 min.
AT\&T \textbf{operator} dialed interstate call. ” The image dissolves into an \textbf{indoor} public \textbf{phone} area, likely on campus.
A dark payphone is mounted on the left.
The blond student in the varsity jacket stands at the \textbf{phone}, surrounded by other people in a busy, softly lit background.
He turns toward the \textbf{phone}, waiting as another student passes close in front of him, then grips the receiver.
He lifts the handset from its cradle and brings it down into his hand, facing the \textbf{phone} with a focused expression.
Holding the receiver, he reaches toward the keypad.
A close-up shows a metal push-button \textbf{phone} keypad with raised square buttons labeled with numbers and letters, such as “ ABC 2, ” “ DEF 3, ” “ GHI 4, ” “ JKL 5, ” “ TUV 8, ” and “ WXY 9. ” A finger presses the buttons one after another, visually demonstrating the process of dialing a number using the lettered keypad.
Back on the student ’s face, he pauses with a slightly uncertain, thoughtful look, as if considering what to say.
He raises the receiver to his ear and cheek.
In close-up, his expression shifts through hesitation and concentration ; his eyes glance down and to the side, and he leans forward into the \textbf{phone}.
He holds the \textbf{gray} handset tightly against his ear with one hand, his red jacket collar and striped cuff visible.
His face softens as he speaks into the receiver, looking a little embarrassed but sincere.
The commercial ends on another white graphic card.
The black rectangle with gold “ 1-800-COLLECT ” appears again at the centre.
Beneath it, black text reads, “ America ’s Inexpensive Way To Call Someone Collect. ” Smaller text along the bottom says, “ Use it every time you make a long distance collect call. ”

% matched lemmas: bulky, fine, gray, indoor, jean, operator, phone, screen, sweater
\end{textsample}
