\begin{textsample}{POS Dim 1 – 2010 – Score 25.00 – 2010/tv\_com\_2010\_98.txt}  \label{ex:f1_pos_024}
The commercial begins in a dry, rural-looking outdoor setting.
A close shot shows a weathered vertical metal fixture or tank with a chain hanging from it, against a bright \textbf{sky} and low rocky \textbf{hills}.
The next shot widens to a roadside or \textbf{industrial} \textbf{building} at the edge of \textbf{open} land, with utility lines, scrubby vegetation, and layered \textbf{hills} in the background.
The scene then cuts to the rear of an orange \textbf{vehicle}.
A bumper sticker reads “ PLANET HUGGER ” and includes a cartoon image of hands hugging a globe.
The exhaust pipe and rear bumper are visible. \textbf{Inside} the orange \textbf{car}, a light-skinned man with short dark hair, a beard and mustache, wearing a plaid shirt and vest, sits behind the wheel with a seatbelt on.
He \textbf{drives} with a neutral, focused expression.
The \textbf{car} is shown from the side in motion.
The man remains at the wheel.
The setting shifts to a \textbf{suburban} \textbf{road} with trees, \textbf{hills}, and \textbf{traffic} lights.
Two orange \textbf{cars} \textbf{approach} side by side on a multi-lane \textbf{road}.
One appears to be the man ’s \textbf{car} ; the other is another orange \textbf{vehicle} with a similar compact shape.
A \textbf{different} light-skinned male \textbf{driver} with a prominent mustache is shown in profile in the other orange \textbf{car}.
A shaggy tan dog wearing a red collar is seated beside him, leaning forward with its mouth \textbf{open}.
The bearded \textbf{driver} in the first \textbf{car} looks across toward the other \textbf{vehicle} and then smiles slightly.
A close-up of the dog shows it looking outward, panting.
The bearded \textbf{driver} then looks toward the side window, appearing curious or attentive.
There is a very close \textbf{exterior} shot of orange \textbf{vehicle} bodywork, followed by another \textbf{wide} shot of the two orange \textbf{cars} on the \textbf{road}, still positioned near each other.
The mustached \textbf{driver} is shown head-on through the windshield, wearing a seatbelt and looking serious or composed.
The setting then briefly changes to an electric-vehicle charging area.
A woman stands near a white \textbf{car} parked beside two charging stations.
She appears to be holding or standing near a charging cable.
After this, an elevated \textbf{road} shot shows an orange \textbf{car} \textbf{driving} through a green, hilly landscape, with another darker \textbf{vehicle} \textbf{passing} in the opposite direction or \textbf{nearby}.
A \textbf{city} \textbf{skyline} is faintly visible in the \textbf{distance}.
At about the middle of the sequence, the image cuts to a blank white screen.
A large white graphic shape then \textbf{reveals} a new scene underneath, functioning like a transition.
Through the shape, a restaurant table is visible.
The second part takes place in a dimly lit restaurant.
A group of adults sit around a round table set with plates, glasses, cups, and drinks.
The bearded man in a salmon or pink short-sleeved button-up shirt is seated with the group.
Other diners include a bald man in a dark shirt, a woman in a striped sweater, and other people partly visible around the table.
The group appears to be eating or finishing a meal.
A closer shot shows the bald man smiling and gesturing across the table.
The bearded man is shown frontally, looking forward with a serious or slightly uncertain expression.
A dark card is then shown close-up ; the word “ REWARDS ” is visible on it.
The card is placed or \textbf{moved} near the table.
Another shot shows the tabletop with glasses, plates, and a small blue or dark card being handled.
A bill folder or receipt holder is shown on the table, with a paper receipt \textbf{inside}.
There is a close-up of the bearded man ’s eyes, suggesting he is watching closely.
The group \textbf{continues} interacting around the table ; the bald man gestures while another man in glasses looks toward him.
The bearded man turns his head to the side, then is shown again facing someone across the table.
A hand in the foreground holds up a dark rectangular object, likely a card, though the exact details are not fully clear.
A \textbf{wider} restaurant shot shows the bearded man seated opposite other diners, including the woman in the striped sweater.
The table remains covered with plates, glasses, cups, and a bill folder or card holder.
The final shots shift to a clean graphic product display.
A green credit-card-like card appears centered on a pale mint background, then on a white background.
The card is green with a chip and abstract leaf-like or geometric patterns.
Beneath it, a small green square or app-like icon appears.
There is small fine print at the bottom, but it is too small to read clearly in the sampled frame.

% matched lemmas: approach, building, car, city, continue, different, distance, drive, driver, exterior, hill, industrial, inside, move, nearby, open, pass, reveal, road, sky, skyline, suburban, traffic, vehicle, wide
\end{textsample}
