\begin{textsample}{POS Dim 1 – 1960 – Score 14.00 – 1960/tv\_com\_1960\_33.txt}  \label{ex:f1_pos_058}
The commercial \textbf{opens} with a long shot over water.
A small boat is \textbf{moving} toward the camera in a harbor or marina setting, with other boats and shoreline \textbf{structures} faintly visible in the background.
The image has a warm, reddish/pink vintage tint.
It then cuts to a silhouetted figure on a high deck or bridge-like \textbf{structure} with a railing.
The person stands above a large curved surface, likely part of a boat or waterfront \textbf{structure}.
The camera \textbf{moves} closer in the next frames, \textbf{revealing} a blonde woman standing behind the railing.
She wears a fitted dark outfit and holds the horizontal rail with both hands.
She faces forward, then appears in a frontal medium shot against a pale \textbf{sky}.
A dissolve overlays the woman and the railing with architectural or deck shapes, producing a layered image.
Another \textbf{angle} shows her from behind or partially turned, still positioned at the railing, with a rounded post or decorative element centered below her.
The commercial then cuts to a close-up of the blonde woman ’s face and upper body.
She appears to be addressing the camera, though no spoken content can be determined from the frames.
Her hair is styled in a shoulder-length, curled 1960s fashion, and she wears a high-neck top.
A superimposed transition follows, blending her close-up with the same railing/ship-deck imagery.
The scene then cuts to a close \textbf{view} of a large white sail or sail-like fabric stretched upward, suggesting a nautical setting.
Next, the commercial shows a \textbf{wide} marina or dock scene.
A long walkway extends across the frame with multiple posts and \textbf{structures}, and a \textbf{car} is visible on or near the pier.
Water surrounds the dock area, with additional boats or marina features in the background.
Large bold text then appears over a marina/palm-tree background.
The text reads “ 1967 DODGE POLARA, ” with the words stacked prominently in the center of the frame.
Palm trees and a dock or waterfront setting are visible behind the lettering.
The next sequence shows close-up \textbf{exterior} shots of a white 1967 Dodge Polara.
One frame focuses on the rear of the \textbf{car}, including the taillight area and a plate or \textbf{badge} reading “ 1967. ” Later, the front of the \textbf{car} is shown at a low \textbf{angle}, emphasizing the grille, dual headlights, chrome bumper, and whitewall tires.
Palm trees are visible behind the \textbf{vehicle}, reinforcing the waterfront or warm-climate setting.
Near the end, the blonde woman appears again, now standing behind or \textbf{inside} a white cylindrical podium or platform.
A vintage-style microphone on a stand is positioned to her left.
She raises both arms above her head in one frame, then lowers herself to lean forward over the top edge of the podium in the final frame.
The background remains outdoors, with a pale \textbf{sky} and \textbf{distant} low \textbf{structures} or landscape.
A “ Nostalgic X’er ” watermark is visible in the lower-right corner throughout the sampled frames.

% matched lemmas: angle, badge, car, distant, exterior, inside, move, open, reveal, sky, structure, vehicle, view, wide
\end{textsample}
