\begin{textsample}{POS Dim 1 – 1960 – Score 18.00 – 1960/tv\_com\_1960\_54.txt}  \label{ex:f1_pos_054}
The commercial is presented in high-contrast black-and-white and uses rapid cuts, motion blur, stark silhouettes, and large bold typography.
It begins on a black frame, then cuts to an extreme close-up of a shiny circular \textbf{car} detail or mechanical feature.
The exact part is difficult to identify from the sampled frame, but it appears metallic and reflective.
This is followed by a rear/front \textbf{road} shot of a light-colored \textbf{car} \textbf{moving} along a roadway, then a very blurred close \textbf{pass} of a dark \textbf{car} surface or wheel area, suggesting speed.
A title card appears with large block capital letters reading “ THE NOW \textbf{CARS}. ” The words are stacked vertically in white against a dark, smoky or cloudy background.
A white outline shape appears to the left, though its precise meaning is unclear.
The title is repeated in a cleaner form : first faintly over a bright background, then in solid black letters on a plain light background.
The commercial then shows a convertible in profile as a dark silhouette against a bright \textbf{sky}.
A \textbf{driver} or passenger is visible in silhouette, seated low \textbf{inside} the \textbf{open} \textbf{car}.
The image emphasizes the roofless body line and windshield frame.
A large block word “ REBEL ” appears across the lower part of the frame while the convertible \textbf{passes} behind it, identifying the \textbf{car} \textbf{model} visually. \textbf{Wider} \textbf{exterior} shots follow : a light-colored convertible \textbf{drives} along a tree-lined \textbf{road}, seen from the side and then from a front three-quarter \textbf{angle}.
The \textbf{car} has a long, rectangular front grille and rectangular headlamp area, and the convertible top is down.
The middle section becomes more abstract and kinetic.
There are blurred close-ups of \textbf{car} surfaces or \textbf{road} textures, a dark near-black shot that may be a wheel or shadowed body detail, and several bright white flash-like transitions.
A small \textbf{car} is then shown far in the \textbf{distance} on a flat horizon under a cloudy \textbf{sky}.
This is followed by a dramatic shot of a windmill or rotating radial \textbf{structure}, seen as alternating black and white blades around a circular center.
A close-up shows a woman \textbf{inside} the \textbf{car} in profile, looking forward.
She has dark hair and a long light-colored earring ; her face is strongly lit from the front/side while the \textbf{car} interior remains dark.
The next shots return to the convertible driving on the \textbf{road} : first a front three-quarter \textbf{view} with the \textbf{driver} visible behind the windshield, then a rear three-quarter \textbf{view} as the \textbf{car} \textbf{moves} away along a \textbf{road} bordered by trees.
More bright white transitions appear.
The convertible is then shown in side silhouette again, \textbf{moving} \textbf{past} a bright background with trees behind it.
Later, the \textbf{car} appears in a darker setting with structural beams or bridge-like supports \textbf{passing} across the frame, creating a pattern of vertical and diagonal lines over the \textbf{vehicle}.
The commercial ends with very large bold white capital letters reading “ NOW ” over the \textbf{moving} background of the car/structural setting.
The word fills most of the frame and remains dominant through the final sampled frames.

% matched lemmas: angle, car, distance, drive, driver, exterior, inside, model, move, open, pass, past, road, sky, structure, vehicle, view, wide
\end{textsample}
