\begin{textsample}{POS Dim 1 – 2020 – Score 21.00 – 2020/tv\_com\_2020\_74.txt}  \label{ex:f1_pos_040}
The commercial \textbf{opens} on a bright outdoor roadway in a dry, hilly landscape.
A blue Hyundai SUV \textbf{drives} along a multi-lane \textbf{road}, shown from the front-left \textbf{angle}.
Small legal/disclaimer text appears along the bottom but is too small to read clearly.
The scene cuts to the interior of the \textbf{vehicle}.
A male \textbf{driver} wearing a seatbelt is shown behind the steering wheel.
He holds a small cardboard container of fries or a similar snack in one hand and reaches into it with the other while looking forward.
The \textbf{exterior} \textbf{view} returns, showing the blue SUV \textbf{traveling} alongside a large semi-trailer \textbf{truck} on the \textbf{road}.
The SUV is positioned near the \textbf{truck} ’s trailer, emphasizing their close side-by-side placement. \textbf{Inside} the SUV again, the \textbf{driver} is seen in profile with both the steering wheel and dashboard visible.
He \textbf{continues} handling the small snack container while \textbf{driving}.
The \textbf{truck} ’s trailer is visible through the side window, indicating the SUV is still adjacent to it.
The next \textbf{exterior} shot shows a woman standing \textbf{outside} between the blue SUV and the large \textbf{truck}.
She is positioned near the SUV ’s driver-side area, close to the \textbf{truck} ’s wheels and trailer.
The blue SUV ’s front grille and headlight are prominent in the foreground.
More fine-print text appears at the bottom.
A \textbf{wider} shot shows the woman standing in the narrow space between the SUV and the semi-truck.
The blue SUV is stopped or \textbf{moving} very slowly beside the \textbf{truck}, with the woman facing toward the \textbf{vehicles}.
The \textbf{road} and \textbf{open} landscape remain visible.
The commercial then cuts to a close-up of the \textbf{vehicle} ’s instrument cluster.
A digital display reads “ Lane Keep Assist ” and shows a small \textbf{car} graphic centered between lane markings.
Other visible information includes “ D, ” “ 289 mi, ” “ 53{\EmojiFont °}F, ” and “ 1138 mi. ” Analog gauges flank the display.
A low, close-up \textbf{exterior} shot shows the wheels of the semi-truck on one side and the blue SUV ’s front wheel and body on the other, with the lane line visible between them.
The \textbf{vehicles} appear very close together.
Back \textbf{inside} the SUV, the male \textbf{driver} is seen through the windshield.
He looks focused and serious, with his seatbelt across his chest.
Reflections on the windshield partially obscure the \textbf{view}.
The SUV is then shown from the side/rear driving along the \textbf{road} next to the semi-truck.
Large on-screen text appears : “ Highest Ranked Compact SUV in Initial Quality ” with “ — J.D.
Power ” below it, alongside a J.D.
Power trophy-style icon.
The blue SUV \textbf{continues} \textbf{moving} through the hilly landscape.
The ad transitions to a clean white studio-style background with a side profile of the blue 2021 Hyundai Tucson.
Large black promotional text appears above it : “ 2021 Hyundai TUCSON ” and “ \$0 \$0 \$0 or up to \$3,500 total savings. ” Smaller text under the zeros reads “ Due at lease signing, ” “ First month ’s payment, ” and “ Security deposit. ” A dense block of fine-print \textbf{legal} text spans the bottom.
The final frames show a white background with the Hyundai logo and wordmark centered.
Text reads “ Southeast Michigan Hyundai Dealers, ” followed by a list of dealer names and \textbf{locations}, including Elder Hyundai, Feldman Hyundai of New Hudson, Fox Ann Arbor Hyundai, Glassman Hyundai, LaFontaine Hyundai, Ralph Thayer Hyundai, and Suburban Hyundai.
The \textbf{website} “ BuyHyundai.com ” appears near the bottom, with additional warranty/legal fine print below.

% matched lemmas: angle, car, continue, drive, driver, exterior, inside, legal, location, move, open, outside, road, travel, truck, vehicle, view, website, wide
\end{textsample}
