\begin{textsample}{POS Dim 1 – 2000 – Score 18.00 – 2000/tv\_com\_2000\_47.txt}  \label{ex:f1_pos_033}
A glowing America Online logo appears on a black background : the white triangular AOL symbol above the words “ AMERICA Online, ” with “ Online ” written in a large cursive script.
Pale streaks of light sweep across it, then the image becomes a bright, abstract white flare against black, like two beams meeting in the middle.
A smiling woman appears in a warm \textbf{indoor} setting, likely at home.
She has short curly hair, wears a blue shirt over a green top, and looks down and to the side with a pleased expression.
The commercial then returns to AOL visuals : a blue \textbf{computer} \textbf{screen} with the white America Online logo, followed by a bright transition into an AOL welcome page.
The page is mostly blue and white, with a large “ Welcome ” heading and sections such as “ New Music ” and “ More Features For You, ” suggesting the AOL \textbf{start} page.
The \textbf{screen} changes to the familiar AOL mail notification.
On a blue background, a small cartoon mailbox \textbf{icon} is shown next to the words “ You ’ve Got Mail. ” A cursor arrow points near the mailbox.
An e-mail-style window follows, tilted slightly on \textbf{screen}.
It reads “ Greetings from … ” and shows a \textbf{message} about new e-mail stationery : “ How do you like my new e-mail stationery?
Pretty \textbf{cool}, huh? ” There are bright \textbf{interface} elements, including a yellow “ Alert ” button and a small smiley \textbf{icon}.
Two older women sit side by side on a sofa in a sunlit living room, with sheer curtains behind them.
Both are laughing.
The woman on the left has short \textbf{gray} hair and wears a dark cardigan ; the woman on the right has short white hair, glasses, and a light beige blouse or jacket with a long necklace.
They lean comfortably forward, relaxed and amused.
Another abstract black-and-white burst leads into a woman seated beside a \textbf{computer}.
She appears to be an adult with reddish-brown hair, wearing a light blue button-down shirt over a white top.
A desktop \textbf{monitor} is visible to her left, showing blue AOL-style windows.
She faces forward as if explaining or reacting to the service.
An instant \textbf{message} window fills the \textbf{screen}.
The title bar reads “ Instant Message From : ChrisAGill. ” In the conversation area, the name “ ChrisAGill ” appears in blue beside the \textbf{message}, “ I ’ve got an extra ticket to the game tonight -- are you free? ” A reply name, “ SamHansen, ” appears in red, and a large bold blue response appears : “ Definitely!
What time! ” Formatting buttons line the bottom of the window.
The visuals move to AOL parental controls.
A white and blue \textbf{screen} shows a simple \textbf{icon} of an adult and child and the heading “ Parental Controls, ” with the phrase “ EMPOWERING PARENTS. ” Under “ Custom Controls, ” bullet points \textbf{list} \textbf{options} including “ block software downloads, ” “ restrict chat rooms, ” “ block e-mail, ” and “ and more … ” A family scene follows : a woman with curly hair leans over a seated young boy at a desktop \textbf{computer} in a child ’s room with bright blue walls and colorful wall decorations.
The boy points at the \textbf{computer} \textbf{screen} while the woman watches closely, appearing to guide or supervise him.
A middle-aged man with \textbf{gray} hair and a mustache appears in a home or office setting, wearing a \textbf{gray} \textbf{button-up} shirt.
Behind him are shelves and framed items.
The image then cuts to a large graphic sign reading “ 24 HOUR \textbf{Customer} Service, ” with the number “ 24 ” in oversized red letters on a dark blue background and the rest in white.
AOL privacy and security pages appear on \textbf{screen}.
One page has a blue header reading “ Privacy Policy, ” with an AOL circle logo on the left and a browser-style bar at the top also labeled “ Privacy Policy. ” Another page is titled “ Online Safety \& Security. ” A highlighted \textbf{list} includes “ Go To : Parental Controls, ” “ Go To : Mail Controls, ” “ Go To : AOL Neighborhood Watch, ” “ AOL Download Sentry, ” “ Change Your Password, ” and “ Web Browser Security. ” Small \textbf{fine} print appears near the bottom of some \textbf{screens}, including a visible \textbf{note} that availability may be limited during peak usage.
The older woman with white hair and glasses reappears on the sofa, now seen closer.
She wears the same light outfit and necklace and looks toward someone just off to her left, speaking or reacting with a friendly, animated expression.
The other older woman is partly visible beside her.
After another abstract light burst, a younger adult woman with shoulder-length dark hair appears in a softly lit home setting.
She wears a pale blue top and smiles warmly, looking toward someone off to the right.
She seems relaxed, seated with her arms near the foreground.
The commercial returns to AOL ’s \textbf{interface}.
A blue America Online panel shows the AOL logo above the “ You ’ve Got Mail ” mailbox \textbf{icon}.
The view moves through a series of AOL feature \textbf{screens} : a “ Buddy List Window ” labeled “ Buddies Online, ” with a \textbf{list} of friends such as “ SamHansen, ” “ ChrisAGill, ” and others, plus buttons along the bottom for actions like locating, instant \textbf{messaging}, sending, and buddy chat.
A bright blue “ AOL search ” page appears with a yellow “ Search ” button and a white search field.
A blue chat \textbf{icon} appears with stylized cartoon figures and the word “ Chat. ” Then a \textbf{menu} of colorful category bars fills the \textbf{screen}, with labels such as “ international, ” “ Personal Finance, ” “ WorkPlace, ” “ Computing, ” “ Research \& Learn, ” and “ entertainment. ” A sports page appears with the large heading “ SPORTS ” in blue and a “ CHOOSE A SPORT ” \textbf{list} including “ AUTO RACING, ” “ BASEBALL, ” “ GOLF, ” and “ HOCKEY. ” More AOL categories flash by : “ AOL News, ” “ Internet, ” “ Influence, ” “ Travel ” with a small airplane graphic, “ Lifestyles, ” “ Shopping, ” and “ Health. ” The visible sequence ends on a stylized AOL symbol again, now glowing intensely against a dark background.
White and blue beams of light radiate outward from the triangular logo, creating a bright, futuristic finish.

% matched lemmas: button-up, computer, cool, customer, fine, gray, icon, indoor, interface, list, menu, message, monitor, note, option, screen, start
\end{textsample}
