\begin{textsample}{POS Dim 1 – 1980 – Score 15.00 – 1980/tv\_com\_1980\_49.txt}  \label{ex:f1_pos_075}
The commercial \textbf{opens} from darkness.
A large passenger aircraft is then shown at \textbf{night} or dusk on a \textbf{wet} airport apron.
The plane has a red stripe and TWA markings.
The ground reflects lights, and a silhouetted ground crew member stands in the foreground, creating a dramatic backlit airport scene.
The sequence cuts to three women in airline-style uniforms walking toward the camera through a bright, curved interior passage.
They are mostly in silhouette at first.
A closer shot follows, showing two uniformed women, one blonde and one brunette, in dark jackets, white shirts, and neckties or scarves.
They appear poised and smiling.
A hand presses keys on a computer or ticketing keyboard.
This is followed by a ticket-counter or operations setting : a middle-aged man in a suit hands over papers or tickets to someone off-camera, while airline staff are visible behind him and electronic display boards hang above.
A close-up shows a smiling young woman in airline uniform, looking toward someone \textbf{nearby}.
The next shot shifts to a large hangar-like opening : the landing gear of an aircraft is visible in silhouette, with a small human figure standing near a wheel against a bright \textbf{exterior} background.
Another close-up shows a Black woman in uniform, looking attentive and composed.
The scene then cuts to the tail section of an aircraft with a visible red TWA tail marking.
A worker or figure walks along the horizontal stabilizer/tailplane.
Another silhouetted figure appears crouched on the aircraft surface with a cable or hose extending upward ; a plane is faintly visible in the \textbf{distant} \textbf{sky} behind.
A more abstract \textbf{aerial} or graphic-looking shot follows, showing a dark triangular shape over a reddish city- or map-like background.
The image is \textbf{brief} and not fully clear.
The commercial then fades or cuts through darkness.
The next section shows headset-wearing operators seated at a row of computer terminals or monitors, suggesting communications or reservation operations.
A man in a pilot ’s cap is then seen in soft focus or through glass, partly obscured by reflections.
A blonde woman in a coat walks forward in a dim interior space, with other people behind her.
The following shot shows a hand holding or \textbf{passing} a small object near a grid-like screen or window, with warm red-orange light behind it.
A close-up of a red surface with partial white “ TW ” lettering appears, likely part of the TWA visual branding. \textbf{Inside} an aircraft cabin, a seated passenger is shown in profile in a \textbf{wide} seat, with another passenger behind her.
A dark foreground silhouette frames the shot.
A close-up then shows a passenger reclining with eyes closed, wearing visible headset or earphone wires.
Two very \textbf{brief}, blurred transition shots follow ; the visual content is indistinct.
A man wearing a cap with a red TWA logo appears in close-up, smiling.
This is followed by close-ups of two uniformed women smiling warmly : first the Black woman seen earlier, then the blonde woman.
A pilot is shown in profile or three-quarter \textbf{view} in a cockpit-like setting, wearing a headset and cap, lit from a bright window.
The next shot is a \textbf{wide} airport-terminal \textbf{view} through large glass windows : a TWA aircraft is parked \textbf{outside}, and silhouettes of people, including a child-sized figure, stand \textbf{inside} the terminal.
A close-up shows an older male pilot in uniform, partly framed by a doorway or partition.
Then a child appears near metal bars or structural elements, with a large wheel-like aircraft component behind ; the child ’s mouth is \textbf{open}, suggesting excitement, though no audio is available.
The final frame shows a stylized image of an airplane flying above \textbf{clouds} against a colorful twilight \textbf{sky}.
Centered on screen is the text : “ LEADING THE WAY.
TWA. ”

% matched lemmas: aerial, brief, cloud, distant, exterior, inside, nearby, night, open, outside, pass, sky, view, wet, wide
\end{textsample}
