\begin{textsample}{POS Dim 1 – 2010 – Score 23.00 – 2010/tv\_com\_2010\_61.txt}  \label{ex:f1_pos_027}
The sampled sequence begins with a bright, product-centered shot that appears visually \textbf{different} from the rest of the clip.
A blue bottle of **Listerine Cool Mint** stands in the center against a light blue background.
Large white text behind it reads **“BRING OUT THE BOLD”**.
Around the bottle are small animated-looking mouth/teeth figures in red and white.
The scene is clean, colorful, and graphic.
The next frame is completely black, suggesting a transition or cut.
After the black frame, the visual style changes to a cinematic, letterboxed \textbf{car} commercial.
A dimly lit interior scene shows a man in silhouette near large windows, with warm evening light coming through.
The setting appears \textbf{urban} or high-rise, but details are partly obscured by the low lighting.
The next shot shows a man in profile walking or standing near a \textbf{building} with a \textbf{city} \textbf{skyline} and sunset-colored \textbf{sky} in the background.
The commercial then cuts to a nighttime \textbf{city} \textbf{street}.
White centered text reads **“INTRODUCING THE ALL-NEW COMPASS”** while a \textbf{vehicle} with headlights \textbf{approaches} or \textbf{passes} through the \textbf{urban} environment.
The same text \textbf{continues} over a daytime shot of a silver SUV driving along a \textbf{winding} \textbf{road} through dry, rocky \textbf{hills}.
The \textbf{vehicle} is shown from the front, \textbf{moving} toward the camera on a two-lane \textbf{road}.
A close-up interior shot follows, showing a male \textbf{driver} in profile \textbf{inside} the \textbf{vehicle}.
He faces forward with a serious or focused expression.
The lighting is warm and soft, suggesting sunset or early evening.
The next shot focuses on the \textbf{vehicle} ’s center console or touchscreen area.
A hand reaches toward the screen.
White text over the image reads **“AWARD-WINNING UCONNECT{\EmojiFont ®} SYSTEM”**.
The screen itself is visible but not fully legible.
The SUV is then shown in an \textbf{exterior} side/front three-quarter \textbf{view} \textbf{driving} on a \textbf{road} through \textbf{open} landscape with mountains or \textbf{hills} in the background.
It is a silver Jeep Compass-style SUV, with the Jeep grille visible.
Small fine-print text appears at the bottom but is too small to read clearly in the frame.
The commercial cuts to a close-up of the interior seating.
White centered text reads **“REFINED LEATHER-TRIMMED INTERIOR”**.
The image shows light-colored upholstery and stitching details, though the shot is partially abstract and close-cropped.
A front close-up of the SUV follows, with the left headlight and grille visible.
Strong sunlight flares from the right side of the frame, creating a golden glow and partially washing out the image.
Another interior technology shot appears, showing a hand interacting with the touchscreen.
White text reads **“MOST TECHNOLOGY IN ITS CLASS”**.
The dashboard and screen are visible, but some details are blurred or obscured by foreground elements and reflections.
The \textbf{vehicle} is then shown again from the front, \textbf{driving} on a \textbf{road} at dusk.
The headlights are on, and the background includes \textbf{open} terrain, utility poles, low mountains, and a cloudy \textbf{sky} with warm sunset tones.
Small fine print appears at the bottom but is not clearly readable.
The final frames switch to a black background with white promotional lease information.
The main text reads : - **“2018 JEEP COMPASS LATITUDE 4x4”** - **“\$169/MO.”** - **“24 MOS.
WITH \$3279 DUE AT SIGNING”** - **“LOW MILEAGE LEASE FOR CURRENT LESSEES OF COMPETITIVE VEHICLES”** - **“TAX, TITLE AND LICENSE EXTRA”** - **“CALL 1-888-925-JEEP FOR LEASE DETAILS”** Below this is the **Jeep** logo and the phrase **“CELEBRATION EVENT”**.
Very small legal/disclaimer text appears at the bottom, but it is not legible in the sampled frames.

% matched lemmas: approach, building, car, city, continue, different, drive, driver, exterior, hill, inside, move, open, pass, road, sky, skyline, street, urban, vehicle, view, wind
\end{textsample}
