\begin{textsample}{POS Dim 1 – 1970 – Score 13.00 – 1970/tv\_com\_1970\_86.txt}  \label{ex:f1_pos_069}
The commercial begins \textbf{inside} what appears to be a restaurant or food-service setting.
A man dressed as a chef, wearing a white chef ’s coat and white paper hat, is holding a telephone receiver to his ear.
Behind him are menu boards or signs, but the text is too blurred to read clearly.
A long bread-like item or sandwich-shaped prop is visible at the right edge of the frame.
The scene then cuts outdoors to a small tan/gold AMC Pacer parked or \textbf{moving} slowly along a \textbf{residential} \textbf{street}.
The \textbf{car} is shown from the front-left side, near a curb, with trees and houses in the background.
The lighting suggests daytime, and the image has a soft, slightly faded look.
Next, the camera shows an \textbf{empty} section of a quiet \textbf{street} or driveway \textbf{entrance} with a signpost and trees.
No people or \textbf{car} are clearly visible in this sampled frame.
The commercial then returns to the chef, now seated outdoors at a table.
He is still wearing his chef outfit and hat.
He faces the camera and appears to be handling something on the table, possibly food or a utensil, though the exact object is not fully clear.
A close-up follows of the chef ’s hands.
He holds a small round object in one hand and uses a tool or utensil in the other hand.
The exact item being prepared is unclear from the frame, but the shot visually emphasizes manual preparation or handling of a small food-like object.
The next shot shows the chef \textbf{inside} a \textbf{car}, seated at the \textbf{driver} ’s seat.
He is wearing the same white chef hat and coat, and he turns his head back toward the camera while holding the steering wheel.
The \textbf{car} interior and side window are visible, with greenery \textbf{outside}.
The scene then cuts to a \textbf{different} man standing in front of a large white-columned \textbf{building}, possibly a mansion or formal residence.
He is dressed in a black tuxedo with a white shirt and bow tie.
He faces slightly toward the camera, standing on or near the front steps.
A \textbf{vehicle} is partly visible off to the side in the background.
The final frame shows the tan/gold AMC Pacer parked outdoors near a large tree.
The chef stands in front of or beside the \textbf{car}.
A very large sandwich or submarine-style prop is positioned across the \textbf{car} ’s roof or foreground, visually spanning much of the \textbf{vehicle}.
Overlaid text reads : “ AMC Pacer ” and below it, “ Backed by the AMC Buyer Protection Plan. ” The AMC logo appears next to the \textbf{model} name.

% matched lemmas: building, car, different, driver, empty, entrance, inside, model, move, outside, residential, street, vehicle
\end{textsample}
