\begin{textsample}{POS Dim 1 – 2010 – Score 17.00 – 2010/tv\_com\_2010\_24.txt}  \label{ex:f1_pos_023}
Against a blue city sky, white skywriting spells “ MARRY ME JENNY ” between tall buildings.
Below, a young adult woman with long wavy \textbf{light-brown} hair looks upward with a broad, delighted smile.
She wears a dark coat over a cream-and-navy striped top and appears to be walking along an \textbf{urban} sidewalk lined with brick buildings, large windows, café tables, planters, and people seated outside.
Still looking up, she moves toward the street, smiling and distracted by the \textbf{message} overhead.
Inside a Toyota Prius, the digital dashboard shows the car traveling at about 15 miles per hour.
A central display switches to a bright red warning box reading “ BRAKE! ” The speed drops, suggesting the car is slowing.
Outside, the red Prius is near the curb in front of the brick café while the woman stands in the street area nearby.
Small white \textbf{legal} text appears along the bottom about the TSS Pre-Collision System with Pedestrian Detection and its limitations.
Seen through the vehicle ’s front window, the woman faces the car and raises one hand, as if acknowledging the driver or reacting to the stop.
The same street moment then appears on a \textbf{smartphone} held horizontally in two hands.
On the \textbf{phone} \textbf{screen}, the red Prius is parked or stopped near the crosswalk with the woman standing in front of it, and large white text over the image reads “ Pedestrian Detection. ” A \textbf{video} progress bar and small playback \textbf{icons} are visible, making it look like this safety-feature demonstration is being watched as a clip.
The setting changes to the inside of a moving Prius on an open road.
A young adult man with dark hair and light facial hair drives, wearing a salmon-colored \textbf{sweatshirt}, while a young adult woman with dark hair sits in the passenger seat holding a \textbf{phone}.
Outside the side windows, low mountains and dry open landscape pass in warm light.
The blue Prius is then seen from outside traveling along a two-lane highway with mountains in the distance.
Small white \textbf{disclaimer} text at the bottom refers to Lane Departure Alert with Steering Assist and \textbf{notes} limitations.
The Prius dashboard appears again, now showing about 40 miles per hour.
In the center display, a lane graphic shows the car between road lines ; one side of the lane marking turns orange, indicating a lane-departure warning.
The driver remains focused ahead with both hands near the steering wheel.
The rear of the blue Prius is shown in detail, with the “ PRIUS ” badge and Toyota emblem visible, along with the distinctive vertical red tail lights.
The car continues along the rural highway, with another vehicle passing in the opposite lane.
The rear view of the Prius then appears on another horizontal \textbf{smartphone} \textbf{screen}, overlaid with large white text reading “ Lane Departure Alert, ” again with a \textbf{video} progress bar at the bottom.
The \textbf{phone} is revealed to be held by a crash-test dummy inside a small aircraft packed with skydivers.
The dummy has a beige molded head with black crash-test markings, black-framed goggles, and a black jumpsuit with red panels, straps, buckles, and a yellow-and-black harness.
Around him, several human skydivers wear blue jumpsuits, helmets in yellow, white, black, and blue, clear protective goggles, and parachute harnesses.
They sit close together in the narrow, metal-walled aircraft cabin.
An open doorway behind them reveals bright \textbf{daylight} and the landscape far below.
The dummy holds the \textbf{phone} out toward the group, as if showing them the Prius safety-feature clips, while gesturing with his other hand.
The nearby skydivers watch and react ; one blond skydiver in a yellow helmet sits facing him, while another person in a white helmet smiles in the background.
A closer view shows a male-presenting skydiver in a yellow helmet and clear goggles leaning toward the dummy, grinning as he talks.
Behind him, another skydiver in a dark helmet and amber-tinted goggles watches.
The dummy continues to face the group, moving his hands in a conversational way, his expression fixed in the neutral molded look of a crash-test mannequin.
The aircraft cabin remains crowded and brightly lit near the open door, with the outside sky and desert-like ground visible beyond.
The dummy then moves to the open doorway of the plane.
He braces one hand above him on the door frame and leans outward, as if preparing to jump, while the skydivers inside watch.
One person holds up a \textbf{phone} to record him.
White on-screen product text appears over the image : “ The 2017 PRIUS ” with “ Toyota Safety Sense{\EmojiFont ™} Standard ” beneath it.
As the dummy bends forward and \textbf{starts} to exit, his black-and-red jumpsuit and harness fill the doorway, with the wide landscape stretching below.
The final images transition into a clean white background where many rectangular picture tiles form a rotating globe-like collage.
The tiles include moments from the commercial : the skywritten “ MARRY ME JENNY, ” the driver and passenger in the Prius, the crash-test dummy in the aircraft, road scenery, a blue Prius on the highway, and silhouettes of people at sunset.
The collage shrinks and slides aside as the Toyota emblem appears.
The closing \textbf{screen} shows the Toyota logo with red “ TOYOTA ” text on the left, a vertical divider, and the black slogan “ Let ’s Go Places ” on the right.
At the bottom, small \textbf{gray} text reads “ toyota.com/prius. ”

% matched lemmas: daylight, disclaimer, gray, icon, legal, light-brown, message, note, phone, screen, smartphone, start, sweatshirt, urban, video
\end{textsample}
