\begin{textsample}{POS Dim 1 – 2000 – Score 19.00 – 2000/tv\_com\_2000\_57.txt}  \label{ex:f1_pos_031}
The commercial opens on a dark, abstract background with bright, misty beams of light sweeping behind the America Online logo.
The AOL symbol, a triangle with a circular center, sits above the words “ AMERICA Online, ” with “ Online ” written in a flowing script.
A blue, glowing wash fills the \textbf{screen} and resolves into a \textbf{computer} \textbf{interface}.
A web-style AOL welcome page is visible, headed “ Welcome to AOL. ” On the left is a teal vertical sidebar with the America Online logo and large \textbf{icon} buttons, including “ You ’ve Got Mail, ” “ You ’ve Got Pictures, ” and “ My Calendar. ” In the center is a prominent purple box labeled “ Special Offer, ” “ NEW VERSION 6.0, ” and “ DOWNLOAD NOW. ” Around it are magazine-like content panels and headlines, including a red lips graphic on the right and smaller article listings below.
The scene shifts to a home \textbf{computer} setup in a brightly colored child ’s room.
A young boy sits at a white desktop \textbf{computer}, facing the \textbf{monitor} and pointing at the \textbf{screen} with one hand while using the keyboard or mouse area with the other.
A woman with dark curly hair leans over beside him, watching closely and smiling.
The walls are painted blue and decorated with playful drawings or cutouts, including fish-like shapes, giving the space a child-friendly feel.
The \textbf{computer} \textbf{screen} shows a colorful AOL-style \textbf{interface} with large rounded \textbf{icons}.
A middle-aged man with short dark hair, a trimmed mustache and goatee, and a light \textbf{gray} \textbf{polo} shirt appears seated indoors, likely in a living room.
He faces forward as if speaking to the viewer, relaxed and engaged, with a softly lit home interior behind him.
A graphic title appears : huge \textbf{gray} “ 6.0 ” numerals fill the black background, with the America Online triangle logo and “ AMERICA Online ” layered across the center.
This bold AOL 6.0 mark recurs throughout the commercial as a visual separator.
A close view of an AOL instant \textbf{message} window appears.
The blue title bar reads “ Send Instant Message. ” In the recipient field is the \textbf{screen} name “ SurfSamSurf. ” In the \textbf{message} box, text reads, “ Check out this new AOL 6.0! ” More text is \textbf{typed} below, forming “ Isn't this \textbf{cool}? ” A row of formatting buttons sits above the \textbf{message} box, including text-style \textbf{icons} and a small yellow smiley-face button.
A drop-down \textbf{menu} of smiley emoticons opens on the right, showing several yellow faces with \textbf{typed} symbols such as “ :- ) ” and “ ; - ) ” ; a cursor points through the \textbf{list} and highlights an expressive face \textbf{option}.
A woman with short dark hair sits at a desk beside a \textbf{computer} in a warmly lit room with bookshelves behind her.
She wears a blue \textbf{button-up} shirt over a white top and faces forward as if giving a testimonial.
At the bottom of the \textbf{screen}, small white \textbf{fine} print reads, “ Availability may be limited especially during peak usage. ” The image changes to a bold customer-service graphic.
Large red numbers “ 24 ” dominate a deep blue background, followed by the words “ HOUR \textbf{Customer} Service ” in red and white.
The same \textbf{fine} print remains along the bottom : “ Availability may be limited especially during peak usage. ” The large \textbf{gray} “ 6.0 ” America Online logo returns on black.
A parental controls \textbf{screen} fills the view.
At the top it reads “ Parental Controls ” with the subtitle “ EMPOWERING PARENTS. ” A simple \textbf{icon} of an adult and child appears at the upper left.
Under “ Custom Controls, ” bullet points \textbf{list} features : “ block software downloads, ” “ restrict chat rooms, ” “ block e-mail, ” and “ and more... ” The \textbf{interface} has a clean white and blue design, suggesting settings parents can adjust.
A smiling adult man and a blonde adult woman stand together in a bright home setting with white shutters behind them.
The woman wears a light blue overshirt ; the man wears a pale \textbf{polo} shirt.
A \textbf{computer} \textbf{monitor} is visible behind the woman, reinforcing the home-computer context.
Then a teenage boy or young man with curly dark hair sits at a \textbf{computer} in a warmly lit room, wearing a plaid shirt over a yellow T-shirt.
He looks toward the \textbf{screen}, then turns slightly toward the viewer with a small smile.
The AOL 6.0 logo appears again on the black background.
A blonde adult woman in a red top appears in a warm \textbf{indoor} setting with plants and wood tones behind her.
She faces forward, smiling gently as if speaking about the service.
This is followed by a close view of an AOL “ Buddy List ” window.
The title bar reads “ Buddy List, ” and a vertical \textbf{list} of \textbf{screen} names appears with small colorful buddy \textbf{icons} beside some names.
Visible names include “ BaileyXJ, ” “ PaigeDoc, ” “ SamHansen, ” “ ChrisAgill, ” “ AlexJWhite, ” “ SurfSamSurf, ” “ TaylorDJay, ” “ SydneyAWeb, ” “ DevinJacks, ” and “ CaseyPeete. ” The \textbf{list} scrolls, with a scrollbar on the right and playful \textbf{icons} such as faces, a fish, and animal-like symbols beside certain names.
A young adult man with short dark hair and a small goatee sits against an exposed brick wall, wearing a light \textbf{gray} \textbf{sweater} over a white shirt.
He faces forward and smiles slightly, as if giving another user comment.
A tilted close view of an AOL welcome page appears again, with a blue header reading “ Welcome ” and text beneath beginning “ Today on A... ” Headlines are partially visible, including “ New Music ” and “ More Features For You, ” with underlined link-style text.
The \textbf{screen} grows brighter and washes into a pale blue-white glow.
The \textbf{gray} “ 6.0 ” America Online logo returns once more on black.
The blonde woman from the parental-controls scene appears again beside a desktop \textbf{computer}.
She is shown first facing forward, then seated at a wooden desk \textbf{typing} on a keyboard.
The room is bright with white shuttered windows behind the \textbf{computer} and potted plants on the desk and windowsill.
The \textbf{computer} \textbf{monitor} displays an AOL \textbf{interface} with blue and white panels.
The commercial ends with a final AOL 6.0 brand graphic on a black background.
The large \textbf{gray} “ 6.0 ” numerals sit behind the America Online logo and script.
White text appears beneath : “ So easy to use, no wonder it ’s \#1, ” followed by the \textbf{phone} number “ 1-800-4-ONLINE. ”

% matched lemmas: button-up, computer, cool, customer, fine, gray, icon, indoor, interface, list, menu, message, monitor, option, phone, polo, screen, sweater, type
\end{textsample}
