\begin{textsample}{POS Dim 1 – 1990 – Score 16.00 – 1990/tv\_com\_1990\_82.txt}  \label{ex:f1_pos_043}
The commercial \textbf{opens} on a nearly black frame, with no discernible objects or action visible.
It then cuts to a \textbf{wide}, elevated shot of an orange-brown grassy hillside.
A white pickup-style \textbf{vehicle} with a dark rear cargo area \textbf{drives} along a narrow \textbf{road} or track beside a \textbf{fence}, towing a small white two-wheeled trailer.
The setting shifts to a dock or port.
A white box \textbf{truck} with large side lettering reading “ DON ’S MARINE SUPPLY ” is parked in front of a large ship or \textbf{industrial} vessel.
Cranes, forklifts, and dock \textbf{structures} are visible around it.
Small white \textbf{legal} text appears along the bottom : “ INCLUDING OCCUPANTS, EQUIPMENT, AND CARGO. ” The commercial cuts back to the orange hillside.
The same white pickup-like \textbf{vehicle} is shown in profile towing the small trailer along the \textbf{fence} line.
A bottom caption reads : “ Not To Exceed GCWR OF 8,600 LBS. ” The dock scene returns in a closer \textbf{view}.
The “ DON ’S MARINE SUPPLY ” \textbf{truck} fills much of the frame, with a forklift at the rear and a worker visible near the forklift.
The \textbf{industrial} ship and dock remain in the background.
Another hillside \textbf{driving} shot follows.
The white \textbf{vehicle} and trailer \textbf{move} along the sloping \textbf{road} through the warm-toned landscape, again shown from the side at a \textbf{distance}.
The next scene shows a gray \textbf{pickup} \textbf{truck} in an \textbf{industrial} marina or dock area.
It is loaded with large marine-related equipment in its bed, including a prominent boat propeller and a metal frame.
Harbor cranes or dock machinery appear in the background, and the \textbf{wet} ground reflects the \textbf{vehicle}.
The setting then changes to a coastal \textbf{road}.
A red \textbf{pickup} \textbf{truck} is seen from a \textbf{distance} \textbf{driving} on a curving \textbf{road} along \textbf{cliffs} and coastline.
The ocean and pale shoreline are visible in the background, with a pink-orange color cast.
In the final frame, the red \textbf{pickup} is shown closer from the front, \textbf{driving} along the coastal \textbf{road} while towing a trailer.
White on-screen text at the bottom reads : “ I love what you do for me, ” followed by the Toyota logo and the word “ TOYOTA. ”

% matched lemmas: cliff, distance, drive, fence, industrial, legal, move, open, pickup, road, structure, truck, vehicle, view, wet, wide
\end{textsample}
