\begin{textsample}{POS Dim 1 – 2020 – Score 24.00 – 2020/tv\_com\_2020\_68.txt}  \label{ex:f1_pos_034}
The commercial \textbf{opens} with a close-up of an **Amazon** logo on a reflective surface, with the black lowercase letters and yellow smile/arrow visible.
It then cuts to a man \textbf{outside} a modern glass \textbf{building}.
He is wearing glasses, a black face mask, a dark zip-up sweater, a lanyard ID \textbf{badge}, and a backpack.
The setting appears \textbf{urban} or corporate, with glass panels and \textbf{building} \textbf{structures} behind him.
A later shot shows the same man outdoors in a leafy green area, now without the mask visible, standing among trees and plants.
The commercial then shifts to logistics and transport imagery.
A large white cargo airplane is shown on an airport tarmac with **“Prime Air”** branding visible on the side.
Ground equipment, stairs, cones, and workers are present around the plane.
A closer shot shows a worker in a high-visibility jacket and helmet servicing or connecting equipment beneath the aircraft.
Next, packages \textbf{move} through an automated conveyor system.
Multiple cardboard boxes with shipping labels \textbf{travel} along metal rollers and curved conveyor belts \textbf{inside} an \textbf{industrial} facility with yellow safety railings and machinery.
The sequence \textbf{continues} with delivery workers handling packages.
One worker wearing a mask and gloves \textbf{passes} or receives a cardboard box at the back of a delivery \textbf{vehicle}.
Another close-up shows the side of a dark \textbf{vehicle} with visible text reading **“100 \% Electric”** and **“Delivering Shipment Zero,”** while a hand appears near a charging or plug-in area. \textbf{Aerial} footage shows a blue Amazon-branded semi-truck \textbf{driving} along a multi-lane highway bordered by trees.
Another shot shows a **Prime Air** plane \textbf{moving} on or near a runway at an airport.
The commercial then shows a large parking or \textbf{vehicle} staging area from above, with rows of vans and \textbf{cars} arranged in a lot near \textbf{industrial} \textbf{buildings}.
This is followed by an indoor facility where a large delivery-van prototype or \textbf{vehicle} \textbf{model} is being worked on.
The \textbf{vehicle} appears orange at first, with people and equipment around it, then in the next shot it appears with a darker blue and orange \textbf{exterior} as people stand \textbf{nearby} in a bright, spacious workshop or design/testing space.
A close-up shows hands typing on a laptop keyboard.
The commercial returns to the man from earlier : first in a close-up of his face wearing glasses and a black mask, then again standing outdoors among greenery, facing the camera.
Near the end, the visuals \textbf{move} to an \textbf{aerial} landscape shot of a \textbf{road} \textbf{running} through a green area, partially obscured by \textbf{clouds} or \textbf{mist}.
The final frame overlays the white Amazon smile/arrow logo across this \textbf{aerial} \textbf{view}.

% matched lemmas: aerial, badge, building, car, cloud, continue, drive, exterior, industrial, inside, mist, model, move, nearby, open, outside, pass, road, run, structure, travel, urban, vehicle, view
\end{textsample}
