\begin{textsample}{POS Dim 1 – 2010 – Score 16.00 – 2010/tv\_com\_2010\_45.txt}  \label{ex:f1_pos_026}
A dark car dashboard fills the view, with illuminated instrument dials and needles.
The visuals move across different gauges : speed markings, temperature or pressure markings, and warning areas.
A red seat-belt warning symbol glows on one display, then a central red dashboard \textbf{screen} shows the word “ BRAKES, ” a large exclamation point, the word “ WARNING, ” and a small car \textbf{icon}.
Another blue dashboard symbol lights up between round gauges.
The sequence ends this opening set with the Pep Boys three-head logo glowing like a dashboard warning light : three stylized male faces outlined in orange, one with round glasses, one with a moustache, and one clean-shaven.
The scene shifts outside a Pep Boys Auto store on a bright day.
The building is large and rectangular, with blue trim, white walls, and a tall red-and-white section near the entrance.
Several cars are parked or moving in front, including a black car in the foreground and a red car crossing the \textbf{lot}.
People walk near the service bays and entrance.
In the foreground, a \textbf{bald} man wearing glasses and a light yellow shirt walks toward a woman in a red top carrying papers or a bag, while the Pep Boys Auto sign is visible on the building behind them.
Inside a service area, a technician in a blue work shirt stands by the open front of a white Jeep-like vehicle.
He holds a black Bosch-branded battery, with the large red word “ BOSCH ” visible on the side, and positions it near the engine compartment.
Yellow bottles of automotive fluid sit on a red work surface nearby.
The Pep Boys logo appears in the lower corner as the technician lowers the battery into place under the raised hood.
A close-up shows a silver wheel hub with lug nuts as a \textbf{worker} uses a red power \textbf{tool} to fasten or loosen them.
The \textbf{tool} is pressed against one lug nut at a time, and the metallic wheel surface fills most of the view.
Another service scene shows a male technician in a blue shirt and dark \textbf{safety} glasses leaning over an open engine bay.
He works with a \textbf{tool} or hose while looking down into the engine.
Behind him, more vehicles are visible inside the shop, including a bright green car with its hood open and another technician working in the background.
The visuals move to brake service.
Hands in blue sleeves hold and position a large silver brake caliper beside a round brake rotor and exposed wheel studs.
The part is guided into place against the rotor, showing the mechanical components up close.
In the retail counter area, a male \textbf{customer} in a dark red shirt leans toward a \textbf{computer} \textbf{monitor} while a Pep Boys \textbf{employee} in a blue \textbf{polo} sits or stands opposite him.
The \textbf{monitor} shows a blue \textbf{screen} with columns or \textbf{menu} bars.
Behind them, several \textbf{employees} in blue shirts help other \textbf{customers} at counters, with product signage and displays lining the store.
The commercial then presents a tire offer with a split layout.
On the left, a \textbf{worker} pushes a cart carrying stacked tires down a narrow aisle between tall racks filled with tires.
On the right, a \textbf{solid} red panel appears with large white text that builds to read “ Buy 3 tires. ” The left side changes to a tire display area where a woman with dark shoulder-length hair, wearing a sleeveless striped top, stands beside a \textbf{bald} Pep Boys \textbf{employee} in a blue \textbf{polo}.
They look down at tires in front of them while the \textbf{employee} gestures, appearing to explain \textbf{options}.
The red panel on the right continues to show “ Buy 3 tires. ” The offer text expands on the red panel to “ Buy 3 tires get the, ” followed by a bold badge-style graphic reading “ 4th TIRE FREE, ” with a tire illustration wrapped around the badge.
On the left, a technician in \textbf{safety} glasses lifts and aligns a mounted wheel on a vehicle raised in a service bay.
He steadies the tire with both hands, then continues working at the wheel area.
The right side remains a red \textbf{promotional} panel reading “ Buy 3 tires get the 4th TIRE FREE. ” The left side briefly becomes a close-up of a tire and shiny wheel rim, the black rubber and reflective metal filling the space while the same offer remains visible on the right.
The ending returns to the dark dashboard imagery.
The red seat-belt warning symbol appears again, followed by the Pep Boys three-face \textbf{icon} glowing in the dashboard display.
The three cartoon heads then appear larger and clearer above the red Pep Boys logo on a red-and-black background.
Final text on the red background includes “ PEPBOYS, ” the word “ DOES, ” and “ For Locations Call : 1-800-PEP-BOYS. ” Small circular automotive warning-style \textbf{icons} sit near the lower left and right edges, reinforcing the dashboard-light theme.

% matched lemmas: bald, computer, customer, employee, icon, lot, menu, monitor, option, polo, promotional, safety, screen, solid, tool, worker
\end{textsample}
