\begin{textsample}{POS Dim 1 – 1950 – Score 11.00 – 1950/tv\_com\_1950\_109.txt}  \label{ex:f1_pos_090}
The commercial begins with a very dark, nearly blank frame with a greenish cast.
A white “ OsbornTramain ” watermark appears at the lower right.
It then cuts to an outdoor setting in daylight.
A vintage two-tone \textbf{sedan} is parked in a lot beside a low modern \textbf{building}.
A man in a light shirt and dark trousers stands near the front/driver-side area of the \textbf{car}, leaning slightly toward it as if inspecting or presenting it.
The \textbf{car} is shown in a full side profile, emphasizing its long body, chrome trim, whitewall tires, and rear fins.
The next shot \textbf{moves} closer to the front-left side of the \textbf{car}.
The man stands beside the \textbf{hood} and front fender, facing the \textbf{vehicle}.
The camera \textbf{angle} highlights the front wheel, chrome bumper, grille area, and the windshield/roofline.
A front-facing \textbf{view} follows.
The man is positioned at the \textbf{car} ’s front-left corner, bending over toward the headlights and grille.
The shot emphasizes the \textbf{car} ’s \textbf{wide} front grille, paired headlights, chrome bumper, and \textbf{hood} ornament.
A curved \textbf{road} or parking-lot marking is visible on the \textbf{pavement} to the right.
The commercial then shifts to the rear of the \textbf{car}.
The \textbf{sedan} is shown from a rear three-quarter \textbf{angle} in front of a \textbf{building} with large windows and a covered area.
The man stands near the right rear corner, close to the tailfin and taillight.
The rear styling, including the large fins, trunk lid, chrome bumper, and license plate, is clearly featured.
A straight-on rear shot follows.
The man now stands near the left rear corner, looking down toward the tailfin or taillight area.
The \textbf{car} ’s rear end fills the frame, with the centered trunk ornament, license plate, tailfins, and bumper visible.
The next sampled frame is very dark, showing only a faint side silhouette of the \textbf{car}.
The upper part of the frame remains lighter, suggesting a transition or fade, but details are difficult to see.
The final frame is a dark red title card with large white text reading : “ YOUR PLYMOUTH!
DEALER. ” The “ OsbornTramain ” watermark remains at the lower right.

% matched lemmas: angle, building, car, hood, move, pavement, road, sedan, vehicle, view, wide
\end{textsample}
