\begin{textsample}{POS Dim 1 – 2020 – Score 14.00 – 2020/tv\_com\_2020\_14.txt}  \label{ex:f1_pos_017}
The commercial opens outdoors in bright \textbf{daylight}, looking up from inside the back of a pickup truck or cargo area.
Two large blue Walmart reusable bags with the yellow spark logo sit in the foreground, one on each side.
The bags are stuffed with groceries and \textbf{coffee} products ; a red Fire Department Coffee bag is visible in the right bag, and a tan bag and blue-capped bottle peek from the left.
Behind the open tailgate stand two adult men.
One is \textbf{bald}, light-skinned, tall and muscular, wearing an olive-green T-shirt that reads “ Fire Dept Coffee. ” He smiles broadly.
Beside him is a light-skinned man with a short reddish \textbf{beard}, wearing a black baseball cap and a black T-shirt with a large Fire Department Coffee “ FDC ” logo.
They lean forward, each reaching for a Walmart bag as if unloading \textbf{supplies}.
The setting widens to a red-brick fire station with open garage bays.
A black pickup truck is parked near the entrance, and a red-and-white fire engine sits inside the bay on the right.
The two men walk toward the station carrying the blue Walmart bags, joined by people in dark fire department-style shirts.
Over the scene, two white logos appear : the Walmart spark on the left and the Fire Department Coffee “ FDC ” emblem on the right.
Inside the firehouse garage, the group walks past a large fire truck with red and yellow striping.
The man in the black FDC shirt is in front, smiling, while the \textbf{bald} man carries a Walmart bag filled with red \textbf{coffee} bags.
Other firefighters or staff in navy shirts walk nearby, also carrying bags.
The atmosphere is casual and cooperative, with \textbf{daylight} spilling in from the open bay doors.
The focus moves to rows of red Fire Department Coffee bags lined up on a shelf.
Through the gap between the bags, the man in the black cap appears, framed by the \textbf{coffee} packages.
He looks forward and speaks, with the red bags close to the viewer on both sides.
The bags are upright, glossy, and branded with the circular FDC logo and the word “ Coffee. ” In a firehouse kitchen or break room, several people unpack the \textbf{coffee} at a long stone countertop.
Dark cabinets, a sink, a dish rack, a metal range hood, shelves stocked with more red \textbf{coffee} bags, mugs, utensils, and kitchen \textbf{supplies} fill the background.
The \textbf{bald} man stands near a blue Walmart bag packed with red Fire Department Coffee bags, holding one bag upright so the logo faces out.
A young man with \textbf{medium} skin, dark curly hair, and a light \textbf{gray} zip-up hoodie over a dark shirt takes a red \textbf{coffee} bag and smiles.
A woman in a dark shirt with a fire department-style emblem helps pass bags along.
Another person in a blue cap moves in the background with a Walmart bag.
Small white \textbf{fine} print appears along the bottom during the kitchen scene, \textbf{stating} that more than two-thirds of Walmart U.S. total product spend in FY2025 was on items suppliers reported were made, grown, or assembled in the United States.
While that text is on \textbf{screen}, the \textbf{coffee} bags are handed from person to person, lifted from Walmart bags, and placed around the counter.
The young man in the \textbf{gray} hoodie brings a red \textbf{coffee} bag close to his face and smells it, smiling as the woman beside him reacts warmly.
Another close view shows hands passing a red bag into the arms of the man in the black FDC shirt, who holds it against his chest.
The kitchen remains busy and friendly.
The \textbf{bald} man gestures toward the \textbf{coffee} in the Walmart bag as if explaining something, then lifts another red bag from the bag and presents it.
The blue Walmart bags, filled with multiple red \textbf{coffee} packages, sit prominently on the counter in the foreground.
The man in the black cap stands at a kitchen counter near dark cabinets and a row of hanging mugs.
He reaches toward the cabinet area, then turns to face forward in his black Fire Department Coffee shirt.
Behind him, the \textbf{bald} man walks by holding a bright blue mug.
The \textbf{bald} man steps into view smiling and extends the mug outward, offering it to someone off to the right.
The blue mug is passed across the kitchen.
A dark-haired, light-skinned man with a thick mustache receives the mug.
He wears a dark fire department-style work shirt with a patch on the chest, and sunglasses hang from the front of his shirt.
A blue Walmart bag sits behind him on the counter.
He holds the blue mug, which has yellow text reading “ Who knew? ” on the side, and looks a little surprised or intrigued.
He raises the mug to his mouth, takes a sip, then lowers it slightly with a thoughtful, impressed expression.
The \textbf{bald} man and the man in the black FDC shirt face the mustached man in the kitchen.
The \textbf{bald} man smiles and gestures toward him as if responding playfully, while the man in the black cap watches from the side.
The mustached man still holds the blue mug near his chest.
The scene returns to the firehouse garage, now seen from inside looking toward the bright open bay doors.
The two Fire Department Coffee men appear as dark silhouettes walking side by side between fire engines parked on the left and right.
They raise their hands and give each other a celebratory high-five as they continue toward the \textbf{daylight} outside.
The commercial ends on a \textbf{solid} Walmart-blue \textbf{screen}.
Large bold white text in the center reads, “ Who knew? ” Fine-print copyright and trademark text appears small along the bottom.

% matched lemmas: bald, beard, coffee, daylight, fine, gray, medium, screen, solid, state, supply
\end{textsample}
