\begin{textsample}{POS Dim 1 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_106.txt}  \label{ex:f1_pos_086}
The commercial is in black and white, with a “ tvdays.com ” watermark visible at the lower right throughout the sampled frames.
It begins on a dark/black screen, then cuts to a very bright, washed-out outdoor scene that appears to show a \textbf{road} or \textbf{open} area with \textbf{distant} \textbf{structures} and \textbf{vehicles}, though details are hard to make out because of the exposure.
A later shot shows large \textbf{clouds} in the \textbf{sky}.
The commercial then \textbf{moves} into a miniature battlefield-style scene.
A toy helicopter or aircraft and small \textbf{model} \textbf{vehicles} are arranged among \textbf{rough} terrain, \textbf{rocks}, and foliage.
A large toy helicopter is shown suspended or positioned over a crater-like area, with miniature soldiers and equipment below.
After a white flash transition, two children appear lying or crouching behind a low edge or platform.
One child holds or operates a toy helicopter with a dangling hook or cable beneath it.
The other child, wearing a light-colored helmet or cap, watches closely with hands near the face.
The helicopter is shown in profile and has printed markings, including a triangular emblem.
The next shots focus on the side of the toy helicopter.
A close-up shows a rectangular hatch or panel on the fuselage, with partial lettering visible to the right reading “ WHIR … ” or similar.
The panel \textbf{opens} downward like a small door or platform. \textbf{Inside}, several small toy soldier figures are \textbf{revealed} standing in the compartment.
Another close-up shows a mechanical-looking arm or gun-like apparatus \textbf{inside} the \textbf{opened} compartment, mounted on a base and \textbf{angled} outward.
The commercial returns to the miniature battlefield.
The scene includes a toy helicopter at the upper left, a tank-like or armored \textbf{vehicle} to the right, another toy \textbf{vehicle} with a mounted weapon at lower left, and small toy soldier figures positioned around the terrain.
Bright flashes and smoke-like effects appear, suggesting staged explosions in the miniature scene.
The explosions intensify, filling much of the frame with white smoke or overexposed light.
The large toy helicopter is again shown positioned above the terrain, apparently being \textbf{moved} or suspended over the miniature battlefield.
Another bright white transition follows.
The children reappear outdoors behind the low platform.
One child smiles while holding or presenting the toy helicopter ; the other child remains beside it, still wearing the light-colored headgear and looking toward the toy.
A crowd-like background or \textbf{distant} figures may be visible behind them, but the details are indistinct.
The final frame is a product-style shot of the toy helicopter against a cloudy \textbf{sky} background.
Large text above it reads “ PLAY INDOORS. ” Beneath the helicopter, the price “ 9.98 ” is displayed.
At the bottom, partially obscured by the watermark, text reads “ Not a Flying … ” with the final word partly covered or unclear.
The helicopter is shown side-on, with its rotors visible and various decals on the fuselage.

% matched lemmas: angle, cloud, distant, inside, model, move, open, reveal, road, rock, rough, sky, structure, vehicle
\end{textsample}
