\begin{textsample}{POS Dim 1 – 1960 – Score 13.00 – 1960/tv\_com\_1960\_80.txt}  \label{ex:f1_pos_060}
The commercial is in black and white and appears to use a sequence of \textbf{industrial}, transportation, and outdoor images before ending on a brand graphic. 1. **Opening frame:** A large rectangular sign fills most of the frame.
In bold block letters it reads : **“KEEP BACK 500 FEET.”** The sign appears mounted on the rear of a \textbf{vehicle} or piece of equipment, though the surrounding object is mostly dark and indistinct. 2. **Cut to footwear/equipment close-up:** The \textbf{view} changes to a close shot of heavy boots or boot-like gear on the ground.
The text **“KEEP BACK 50 FEET”** is visible across the center area, either printed on a sign/object in the scene or \textbf{carried} over visually from the previous shot.
Legs are partially visible at the sides, but the person is not clearly shown. 3. **Return to warning sign imagery:** The **“KEEP BACK 500 FEET”** text appears again, now larger and partially cropped.
A small human figure or worker silhouette is visible near the lower part of the frame, standing beside or beneath the large sign/equipment.
The scale makes the sign or \textbf{vehicle} appear very large. 4. **Automobile scene:** The commercial cuts to a \textbf{car}, likely a station wagon, \textbf{driving} or positioned on a dirt or gravel \textbf{road}.
Trees line the \textbf{road}, and a bright \textbf{open} area behind them may be water or \textbf{sky}.
The \textbf{car} is \textbf{viewed} from the front/side as it turns or \textbf{moves} along the \textbf{road}. 5. **Airplane scene:** The next shot shows the underside of a large aircraft, including a jet engine, wing, and landing gear area.
The aircraft appears to be on the ground at an airport or runway area.
Small \textbf{vehicles} or equipment are visible near the plane, but details are indistinct. 6. **Earthmoving or excavation scene:** A large mass of soil or \textbf{rock} dominates the frame, possibly part of an excavation, construction site, or earthmoving operation.
The terrain is \textbf{rough} and uneven.
A small machine or \textbf{structure} is visible at the right edge, but it is not clear. 7. **Off-road \textbf{vehicle} scene:** A large-wheeled \textbf{vehicle}, possibly a tractor or industrial/farm \textbf{vehicle}, is shown from the rear or front \textbf{moving} through a \textbf{wet}, muddy, or marshy area.
Water or mud appears beneath it, with trees and brush in the background. 8. **Final brand graphic:** The commercial ends with a graphic display.
A white silhouette map of the United States appears above a large stylized wordmark reading **“Firestone.”** The logo sits across a textured surface, likely representing a product or roadway-like background.

% matched lemmas: car, carry, drive, industrial, move, open, road, rock, rough, sky, structure, vehicle, view, wet
\end{textsample}
