\begin{textsample}{POS Dim 1 – 2020 – Score 14.00 – 2020/tv\_com\_2020\_72.txt}  \label{ex:f1_pos_019}
A warm, floor-level view begins on wide brown wood-look planks, their grain and seams catching light across a living room floor.
A pale rug lies along the right edge.
As the view opens up, colorful wooden blocks appear scattered ahead, and a toddler with curly hair, wearing a light plaid shirt, plays among them.
Behind the child sits an adult with glasses and short dark hair, wearing a tan \textbf{sweater}, smiling and watching closely.
The room feels bright and domestic, with French doors in the background, upholstered chairs, a fireplace, pillows, and soft \textbf{daylight}.
White on-screen product text appears near the lower right : “ SMARTCORE Vinyl \textbf{Flooring}, ” with a visible price range from about “ \$2.78 - \$3.99 ” per square foot.
The toddler crawls forward through the blocks, pushing and reaching for red, blue, yellow, and green pieces while the adult remains seated behind, attentive and cheerful.
The child comes very close to the floor-level view, filling the foreground with their face and hands as they crawl over the blocks.
The background shifts past the child to show more of the living room : a white fireplace with a black \textbf{screen}, a beige chair, a knitted round pouf, a floor lamp, and loose blocks spread across the smooth vinyl surface.
A round black robotic vacuum then enters from the right and glides across the wood-look floor, its glossy top reflecting the room as it moves near the base of a chair.
The scene changes to a soft, blue-toned carpet seen from very low down, emphasizing the plush texture.
Ahead is a blanket fort made from draped sheets, with pillows and stuffed toys arranged around the entrance.
A teddy \textbf{bear} sits to the left, and warm string lights glow inside the fort.
White product text appears at the lower right : “ STAINMASTER carpet, ” with pricing shown as “ \textbf{starting} at \$2.28 ” per square foot.
As the view gets closer, a handmade sign over the fort entrance reads “ SCARY STORIES CLUB. ” Inside, children lie or sit on the carpet around an open book or notebook, while a person in red clothing, partly hidden by the hanging sheets, appears to be telling or acting out a story.
The warm lights overhead make the fort feel cozy and secretive.
A large white \textbf{promotional} graphic overlays the center : “ Free Carpet Installation, ” with “ minimum purchase \$499, ” framed by a simple roofline \textbf{icon}.
Fine-print \textbf{disclaimer} text stretches along the bottom.
Inside the fort, the children react animatedly, smiling and laughing with open mouths as the person in red leans in from the right with raised hands, as if playfully startling them.
The open book remains on the carpet in the center.
The “ Free Carpet Installation ” offer stays large and centered, while the STAINMASTER carpet price remains visible at the lower right for part of this section.
The fort fabric and warm lights fill the background as the figures move closer together in the small space.
The \textbf{promotional} overlay changes to “ Book Now ” with smaller text underneath : “ and have yours installed by the holidays. ” Below it is a “ Lowe ’s safe ” badge and the \textbf{website} “ Lowes.com/HolidayInstall, ” with \textbf{fine} print along the bottom.
Behind the text, the scene shows carpet installation in a home.
A large roll of carpet lies horizontally across the foreground.
One masked installer kneels on the floor near the roll, working with \textbf{tools} ; he wears work clothes and a dark vest.
Another installer, also in a dark Lowe ’s vest, stands or climbs on a ladder at the right near a doorway and white cabinetry.
The room is bright with neutral walls, and work \textbf{tools} are visible nearby, reinforcing that this is an in-home installation.
The final images keep the installer on the ladder at the right, seen from a low angle as he works near the doorway.
A large white Lowe ’s logo appears centered over the scene, first as a house-shaped outline around the word “ LOWE ’S, ” then settling into the familiar Lowe ’s house logo.
Small copyright text appears near the bottom as the installer remains in the background, still positioned on the ladder in the \textbf{customer} ’s home.

% matched lemmas: bear, customer, daylight, disclaimer, fine, flooring, icon, promotional, screen, start, sweater, tool, website
\end{textsample}
