\begin{textsample}{POS Dim 1 – 1970 – Score 14.00 – 1970/tv\_com\_1970\_11.txt}  \label{ex:f1_pos_066}
The commercial \textbf{opens} with a dark, low-contrast outdoor shot.
The setting appears to be a \textbf{road} or \textbf{open} landscape, but details are difficult to distinguish because the frame is very dim.
A “ Classic Commercial Archives ” circular logo appears at bottom left, and a semi-transparent “ @ClassicCommercialArchives ” watermark \textbf{runs} across the lower area.
A blue/silver \textbf{sedan} then appears in motion on a \textbf{road}, shown from a front three-quarter \textbf{angle}.
The \textbf{car} is \textbf{driving} near a guardrail, with dark greenery or \textbf{hills} in the background.
The lighting has a cool blue cast, suggesting dusk or stylized color grading.
The next sampled frames show the \textbf{car} from farther away on a \textbf{wet} or reflective \textbf{road} surface.
The image is heavily distorted by analog color noise and interference, but a light-colored \textbf{sedan} is visible, with another \textbf{vehicle} or background shape behind it.
Large text appears near the bottom in one frame, including a visible “ 25 ” followed by unclear characters ; the full wording is not legible due to video distortion.
The commercial then cuts to the \textbf{car} ’s interior.
A \textbf{driver} ’s hand rests near or on the gear selector in the center console area.
The dashboard and control panel are visible in low light, with knobs, switches, and vents.
The shot emphasizes the interior controls and manual operation, though the exact action is unclear from the still frame.
A closer interior shot follows, focused on the dashboard center area.
Rectangular vents or display panels and circular controls are visible.
The image remains dark and somewhat blurry, but the framing highlights the \textbf{vehicle} ’s instrumentation and console design.
The final \textbf{exterior} sequence shows two similar light-colored \textbf{sedans} parked side by side near a shoreline or large body of water at sunset or twilight.
The \textbf{sky} is purple-pink, with dark land or \textbf{hills} in the \textbf{distance}.
Large white promotional text appears above the \textbf{cars}.
One frame shows pricing-style text : “ \textbf{Sedan} \$5495 ” and “ Coupe \$5795, ” with smaller fine print to the right that is mostly unreadable.
The last frame displays the headline text : “ New Mazda 626 ” and beneath it, “ The more you look, the more you like. ” The two \textbf{cars} remain parked in the foreground, \textbf{angled} toward the viewer, with the coastal background behind them.

% matched lemmas: angle, car, distance, drive, driver, exterior, hill, open, road, run, sedan, sky, vehicle, wet
\end{textsample}
