\begin{textsample}{POS Dim 1 – 2000 – Score 22.00 – 2000/tv\_com\_2000\_7.txt}  \label{ex:f1_pos_008}
The commercial begins on a black screen, then cuts to an \textbf{urban} \textbf{street} scene.
A broad white-striped crosswalk dominates the foreground, with \textbf{pedestrians} and storefronts visible in the \textbf{distance}.
The setting shifts upward to a \textbf{brick} apartment \textbf{building} with metal fire escapes.
A woman stands or sits behind the railing on a fire-escape balcony, looking outward.
The next shot shows a young man in a sleeveless green tank top and dark head covering walking along a sidewalk, holding a red soda can and looking upward toward the \textbf{buildings}.
The \textbf{street} environment includes closed metal storefront shutters, awnings, and \textbf{pedestrians} in the background.
A \textbf{wider} sidewalk shot shows storefronts with red panels and white plastic chairs \textbf{outside}.
An older man stands near the \textbf{entrance}, possibly sweeping or holding a long-handled object.
The commercial then cuts to a close-up of another young man behind a chain-link \textbf{fence}, drinking from a red Dr Pepper can ; the Dr Pepper logo is clearly visible on the can.
The sequence \textbf{continues} with fast, shallow-focus \textbf{street} imagery : a blurred passerby crosses the frame, and an ice-cream \textbf{truck} appears.
A vendor \textbf{inside} the \textbf{truck} reaches out to hand an ice-cream cone to a child, with several children gathered below.
The young man in the green tank top is shown again turning his head, as if noticing activity around him.
The vendor smiles in close-up, and a young girl is shown eating a white ice-cream cone.
A close-up then shows a Dr Pepper can standing on a counter or ledge, partially obscured by a \textbf{moving} figure.
The young man in the green tank top appears again walking beneath fire escapes.
The commercial then cuts to an older man seated on a folding chair by a metal shutter, wearing a hat and holding a newspaper ; he smiles toward the camera or someone \textbf{nearby}.
A passerby briefly obscures him.
Another \textbf{street} shot shows an elderly woman with a cane standing near a shopfront, while a \textbf{moving} body in the foreground partially blocks the \textbf{view}.
The next scene shows an older man in a gray polo shirt crouched or bent forward as if playing a \textbf{street} game such as bocce ; a white ball is visible near him.
He gestures forward with his hand.
Other older men stand \textbf{nearby}, one holding a Dr Pepper can.
The commercial \textbf{continues} with blurred \textbf{pedestrians} \textbf{passing} through the frame, emphasizing movement and \textbf{street} activity.
A taxi appears with a smiling \textbf{driver} wearing a dark turban leaning his arm out of the \textbf{open} window.
The \textbf{view} is partly blocked by a passerby \textbf{moving} across the foreground, then the \textbf{driver} is visible again smiling from \textbf{inside} the cab.
Near the end, a woman walks through the \textbf{city} \textbf{carrying} a small child on her shoulders.
The woman drinks from a red Dr Pepper can while the child smiles and holds onto her head.
A small animated globe graphic appears near them.
In the final branded shot, the woman \textbf{continues} drinking with the child above her, and a Dr Pepper logo graphic appears in the upper right with the text “ MAKES THE WORLD TASTE BETTER. ” A \textbf{website} address, “ drpepper.com, ” is visible near the bottom.
The clip then cuts to a dark frame.

% matched lemmas: brick, building, carry, city, continue, distance, driver, entrance, fence, inside, move, nearby, open, outside, pass, pedestrian, street, truck, urban, view, website, wide
\end{textsample}
