\begin{textsample}{POS Dim 1 – 1980 – Score 14.00 – 1980/tv\_com\_1980\_116.txt}  \label{ex:f1_pos_079}
The commercial \textbf{opens} outdoors in a \textbf{rural} or \textbf{suburban} yard.
A dark \textbf{pickup} \textbf{truck} is parked on \textbf{grass} near piles of lumber or construction materials.
In the background are \textbf{open} fields, trees, fencing, and a house or outbuilding.
The scene shifts to the \textbf{exterior} of a house under renovation or construction.
Exposed wooden framing, ladders, boards, and tools are visible.
A person stands in a doorway holding a large yellow cereal box.
A child \textbf{moves} across the foreground, partially blurred.
Next, a close \textbf{view} shows a man partly hidden behind upright boards or framing, as if working on the \textbf{structure}.
He wears a denim jacket and looks through the gap while holding the wood.
A close-up of the cereal box follows.
The visible packaging includes the phrase “ OAT TASTE ” and a circular label reading “ ONLY 1 GRAM OF SUGAR PER SERVING. ” The shot is tightly cropped, so the whole box is not visible.
The commercial then cuts to a close-up of a smiling woman with curly blonde hair.
She is outdoors, holding a glass bowl of cereal and a spoon.
She wears a red plaid shirt over a yellow top.
A \textbf{road} or driveway and lawn are visible behind her.
A \textbf{wider} shot \textbf{reveals} a family-like group gathered in the yard in front of the partially framed house.
The woman sits at a picnic-style table or sawhorse setup eating cereal.
A man stands \textbf{nearby} holding a board or tool, two children sit or stand around the table area, and a large dog is in the foreground.
Construction materials and the unfinished house facade fill the background.
The next shot presents a product display : a large yellow Cheerios cereal box standing on a table with bowls of cereal, a glass of milk, and small baked or fruit-like items \textbf{nearby}.
The box front reads “ Cheerios, ” with a banner across the top reading “ IMPROVED TOASTED OAT TASTE. ” A bowl of ring-shaped cereal is pictured on the box.
A graphic title card appears on a plain yellow background.
Large black text reads “ Cheerios, ” with smaller text underneath : “ low in sugar. ” The woman reappears in close-up, still holding the bowl and spoon.
She is smiling broadly with her mouth \textbf{open}, as if reacting enthusiastically.
The unfinished house framing remains visible behind her.
Another yellow title card follows.
Large black text reads “ Cheerios, ” and smaller text beneath begins to form “ number one! ” In the final frame, the message is fully visible : “ Cheerios number one! ” On the right side, two children are shown in or near a red wheelbarrow, adding a playful construction-yard image beside the large product text.

% matched lemmas: exterior, grass, move, nearby, open, pickup, reveal, road, rural, structure, suburban, truck, view, wide
\end{textsample}
