\begin{textsample}{POS Dim 1 – 1990 – Score 10.00 – 1990/tv\_com\_1990\_76.txt}  \label{ex:f1_pos_049}
The commercial \textbf{opens} on a very dark shot in which the side profile of a \textbf{car} is barely visible.
Most details are obscured by low lighting, but the outline suggests a sedan-like \textbf{vehicle}.
The scene then changes to a brightly lit studio setting with a red four-door \textbf{sedan} positioned three-quarters front-facing toward the viewer.
A man in a dark suit stands to the left of the \textbf{car}, near the front fender and \textbf{hood} area, appearing to gesture toward or present the \textbf{vehicle}.
The background is a neutral, textured gray, giving the scene a showroom or studio demonstration feel.
The \textbf{car} ’s chrome trim, front grille, headlights, and glossy red finish are clearly visible.
Next, the \textbf{view} cuts to the rear of the same or similar red \textbf{sedan} with its trunk \textbf{open}.
A person, visible mainly from the torso down and wearing dark clothing, is placing or lifting a large light-colored suitcase or rectangular bag into the trunk.
The shot emphasizes the \textbf{open} cargo area and the \textbf{vehicle} ’s rear styling, including the tail lights and bumper.
The final frame shows the red \textbf{car} \textbf{driving} away along a curving \textbf{road} in a landscaped \textbf{suburban} or park-like setting with green lawns, trees, shrubs, and a bright blue \textbf{sky}.
Overlaid text appears prominently in the lower half of the frame.
The largest text reads “ BUICK, ” followed by “ The New Symbol For Quality In America. ” A phone number is displayed underneath : “ 1-800-531-1115. ”

% matched lemmas: car, drive, hood, open, road, sedan, sky, suburban, vehicle, view
\end{textsample}
