\begin{textsample}{POS Dim 1 – 1950 – Score 19.00 – 1950/tv\_com\_1950\_60.txt}  \label{ex:f1_pos_081}
The commercial is in black and white and unfolds as a sequence combining animated/cartoon imagery with live-action or realistic \textbf{car} footage. 1. **Opening storefront/signage** The first frame shows a \textbf{building} façade or showroom \textbf{exterior}.
A large sign reads **“DE SOTO PLYMOUTH”** in capital letters.
To the left is a doorway or glass \textbf{entrance}.
The setting appears urban/commercial. 2. **Animated salesman-like figure** The scene cuts to a cartoon man in a dark suit, white shirt, tie, and dark hat.
He has a simple, rounded face and is smiling.
He stands in front of a tiled or paneled background, possibly an interior showroom or stylized dealership setting. 3. **Animated figure with “ 1955 DeSoto ” badge** A \textbf{different} cartoon character appears, dressed formally in a dark tuxedo-like outfit with a bow tie.
He has a round face and a prominent upward-curving nose or horn-like facial feature.
On his chest is a circular \textbf{badge} or rosette reading **“1955 DeSoto.”** He is shown in profile or three-quarter \textbf{view}, gesturing with one arm. 4. **Animated gesturing and movement** The same character \textbf{continues} gesturing theatrically.
His eyes are closed or nearly closed, and one arm is raised upward as if presenting something.
His body posture is exaggerated, consistent with animation.
The \textbf{badge} reading **“1955 DeSoto”** remains visible. 5. **Animated character near an \textbf{approaching} \textbf{car} shape** The character \textbf{moves} across the frame, extending one arm downward and one leg outward.
At the far left edge, a small car-like shape appears entering or positioned near the side of the frame, though it is only partially visible and indistinct. 6. **Text on \textbf{brick} wall** The scene changes to a \textbf{brick} wall with a circular sign or painted emblem in the center.
It reads **“1955 DeSoto.”** The composition is simple, with the text centered against the \textbf{brick} background. 7. **Live-action/realistic side \textbf{view} of car** A full-size automobile is shown in profile on an \textbf{open} \textbf{road} or flat outdoor surface.
The \textbf{car} has a long body, prominent rear fins, whitewall tires, and a two-tone or light-toned \textbf{exterior}.
The background is \textbf{open} and minimal, suggesting a \textbf{road} or test-track-like setting. 8. **Rear three-quarter \textbf{view} of \textbf{car} in motion** The \textbf{car} is now seen from behind at an \textbf{angle}.
The rear fins, trunk area, bumper, and rear license plate area are visible.
The \textbf{car} appears to be \textbf{driving} along a smooth roadway, with the camera positioned behind and slightly to one side. 9. **Stylized \textbf{suburban} houses** The commercial cuts to an animated or model-like \textbf{suburban} \textbf{street} scene.
Several houses with pitched roofs, windows, and simplified trees appear behind a low wall or \textbf{fence}.
The style is graphic and simplified rather than fully realistic. 10. **Close-up of mechanical/industrial equipment** A close-up shows rotating or mechanical components, possibly part of machinery or an automobile-related mechanism.
Circular dials or wheels and rods are visible.
The exact function is unclear from the sampled frame. 11. **Final side \textbf{view} of the car** The last frame returns to the automobile in a side profile on an \textbf{open} \textbf{road}.
The \textbf{car} is \textbf{stationary} or \textbf{moving} very smoothly ; the sampled frame does not make the motion fully clear.
The long body, whitewall tires, and rear fins are again visible against a plain outdoor background.

% matched lemmas: angle, approach, badge, brick, building, car, continue, different, drive, entrance, exterior, fence, move, open, road, stationary, street, suburban, view
\end{textsample}
