\begin{textsample}{POS Dim 1 – 1950 – Score 13.00 – 1950/tv\_com\_1950\_99.txt}  \label{ex:f1_pos_088}
The commercial is in grainy black-and-white and centers on a light-colored, two-door convertible \textbf{car} with the top down, whitewall tires, chrome trim, and a prominent front bumper/grille. - It begins with a nearly black frame, with no distinct objects visible. - The first clear image shows the convertible in a clean side profile, centered against a pale, studio-like background.
The \textbf{car} is shown as an isolated product image. - The image then shifts through a hazy or dissolving visual effect, with the \textbf{car} still visible in side profile but partly obscured by cloudy, circular blur. - A front three-quarter studio \textbf{view} follows, emphasizing the \textbf{car} ’s rounded front end, headlights, chrome bumper, windshield, and whitewall front tire. - A very close, low-contrast detail shot appears next, showing a horizontal line or trim area on a smooth surface, likely part of the \textbf{car} body, though the exact feature is unclear because of blur and overexposure. - The commercial then \textbf{moves} to outdoor driving-related shots.
A close side \textbf{view} shows the \textbf{open} cabin, windshield frame, front seat area, and folded convertible top at the rear, with trees or foliage in the background. - A \textbf{wider} outdoor shot shows the \textbf{car} parked or \textbf{moving} slowly with at least two occupants \textbf{inside}.
The \textbf{vehicle} is \textbf{viewed} from the front-left side, with the top down. - Several closer shots show the occupants through the windshield and over the \textbf{hood}.
Reflections and glare make faces and details indistinct.
In one frame there appears to be faint text or a graphic near the bottom, but it is not readable. - A side close-up shows two people seated in the \textbf{car}, \textbf{viewed} through the \textbf{open} side and windshield frame.
Their exact identities, expressions, and actions are unclear, though they appear to be \textbf{riding} in the convertible. - Another \textbf{exterior} shot shows the \textbf{car} on a \textbf{road} or driveway bordered by darker trees or shrubbery, \textbf{angled} as if \textbf{traveling} or turning toward the camera. - The commercial returns to close product-detail imagery, including an overexposed close-up of the \textbf{car} ’s side door and lower body trim. - The final frame returns to a clean studio-style side profile of the convertible, centered against a pale background, again emphasizing the full length of the \textbf{car}, its \textbf{open} top, side trim, and whitewall tires.
Overall, the visuals alternate between polished studio product shots of the convertible and outdoor lifestyle/driving shots with occupants, using dissolves, close-ups, and frontal/side \textbf{angles} to highlight the \textbf{car} ’s \textbf{exterior} styling and open-top design.

% matched lemmas: angle, car, exterior, hood, inside, move, open, ride, road, travel, vehicle, view, wide
\end{textsample}
