\begin{textsample}{POS Dim 1 – 1990 – Score 17.00 – 1990/tv\_com\_1990\_80.txt}  \label{ex:f1_pos_041}
The commercial begins on a black frame, then cuts into a fast-paced \textbf{industrial} \textbf{montage}.
A middle-aged male worker in a blue work shirt, safety glasses, gloves, and a light-colored cap is shown in close-up, looking upward or to the side while working in a factory-like setting.
The next shots show gloved hands operating tools and machinery around automotive components, including hoses, metal parts, and a \textbf{vehicle} frame or chassis.
The imagery is tightly cropped and emphasizes manual assembly and mechanical work.
The \textbf{montage} briefly shifts to a blurred roadway or track scene with lateral motion, suggesting speed or \textbf{vehicle} movement, though no \textbf{vehicle} is clearly visible in that frame.
It then returns to factory work : a worker in a white hard hat and face protection operates equipment, producing a burst of sparks.
Another close-up shows the front of a dark \textbf{car} with headlights on, followed by motion-blurred shots of \textbf{cars} \textbf{driving} close together or \textbf{passing} by.
The next sequence shows more factory or construction-like activity.
Workers in hard hats and protective clothing operate tools near large machinery.
A dark-colored \textbf{sedan} is then seen from the rear being \textbf{moved} or pushed through a production area by workers on either side.
The camera \textbf{view} becomes highly stylized with strong motion blur as the \textbf{car} advances through a corridor or assembly line.
Further shots show the \textbf{vehicle} undergoing work in an enclosed area.
Sparks fly near the \textbf{car} ’s body, and then the \textbf{car} is shown from the front \textbf{inside} a brightly lit chamber, with water or \textbf{mist} spraying down over it.
A red-lit control-room-like shot follows, showing gauges and a silhouetted seated person behind glass.
The red lighting and illuminated controls create a testing or monitoring atmosphere.
The \textbf{montage} \textbf{continues} with \textbf{views} \textbf{inside} or through the body of a \textbf{car}, then a close-up of a worker in a red hard hat using an orange power tool.
Another shot shows a small \textbf{vehicle} or cart \textbf{moving} away down a long \textbf{industrial} aisle, \textbf{ridden} by a person wearing a light blue coat.
A close-up then shows gloved hands cleaning or polishing the rear side of a dark \textbf{car} near a chrome or reflective trim area.
The setting shifts to outdoor \textbf{vehicle} testing.
A dark \textbf{sedan} \textbf{drives} along a banked test track.
Another shot shows two \textbf{cars} on a \textbf{wet} \textbf{road} surface maneuvering around an orange \textbf{traffic} cone.
A group of workers and staff wearing hard hats, uniforms, and casual work clothes walk toward the camera ; some smile, and one person holds a clipboard.
A dark red \textbf{sedan} is then presented more clearly on a glossy, wet-looking surface, with its reflection visible beneath it.
The \textbf{car} appears in a controlled studio or test environment.
This is followed by a closer shot of a smiling group of workers, including people wearing white hard hats, safety glasses, caps, and work shirts.
Near the end, the dark red \textbf{sedan} \textbf{drives} \textbf{past} orange cones in front of a large assembled group of workers standing across the background.
In the final frame, the \textbf{car} is parked in profile on the reflective floor, with the crowd behind it raising their arms.
Large on-screen text at the bottom reads “ CAMRY, ” with smaller text below : “ WE JUST COULD N’T LEAVE WELL ENOUGH ALONE. ” In the upper right, visible text reads “ I love what you do for me ” next to the Toyota logo and the word “ TOYOTA. ”

% matched lemmas: car, continue, drive, industrial, inside, mist, montage, move, pass, past, ride, road, sedan, traffic, vehicle, view, wet
\end{textsample}
