\begin{textsample}{POS Dim 1 – 2020 – Score 24.00 – 2020/tv\_com\_2020\_68.txt}  \label{ex:f1_pos_003}
The commercial opens on a tight view of the Amazon logo printed in large black lowercase letters on a glossy, reflective surface, with the yellow smile arrow beneath.
Warm lights and horizontal reflections ripple across the surface, suggesting the side of a vehicle or polished wall.
A Black adult man, identified by the commercial context as Henry, walks outdoors beside a modern building with red brick columns, tall green-framed glass windows, and a glass canopy overhead.
He wears rectangular glasses, a black face \textbf{mask}, a dark zip-up \textbf{sweater} over a collared shirt, a lanyard with an ID badge, and \textbf{backpack} straps over both shoulders.
He faces forward as he walks, appearing purposeful, in a \textbf{professional} campus or office setting.
Henry is then seen standing in a leafy outdoor area, no \textbf{mask} visible in this wider view.
He wears the same dark \textbf{sweater} and glasses, with green trees and shrubs filling the background.
He faces slightly off to one side as if speaking to someone just outside view, his posture relaxed and attentive.
The imagery shifts to Amazon logistics operations at an airport.
A large white cargo aircraft marked “ Prime Air ” sits on the tarmac under a clear sky.
Mobile stairs lead up to an open door near the front, and a raised loading platform reaches another open cargo door farther back. \textbf{Workers} in \textbf{high-visibility} vests stand on the stairs and platform.
In the foreground, a small airport vehicle carries orange traffic cones, and a large cargo container on the left \textbf{bears} an Amazon label.
A closer view shows a \textbf{worker} in a neon \textbf{safety} vest and hard hat handling a thick hose connected to an open panel beneath the aircraft, suggesting servicing or fueling activity.
Inside a warehouse or sorting facility, many brown Amazon packages travel along metal roller conveyors.
One conveyor runs straight through the scene while another curves in a semicircle.
The boxes, with shipping labels and Amazon smile marks, move in an orderly stream through bright yellow \textbf{industrial} structures and railings.
Next, masked Amazon \textbf{delivery} \textbf{workers} unload packages from the open side of a \textbf{delivery} vehicle.
One \textbf{worker} in a blue Amazon vest, white face \textbf{mask}, and light gloves crouches at the doorway while holding a \textbf{medium} cardboard box with the Amazon smile on it.
Large green \textbf{delivery} bags are stacked inside the vehicle behind him.
Another uniformed \textbf{worker} stands nearby holding a handheld \textbf{device} or \textbf{phone}, watching the unloading.
A close view of a dark vehicle door shows bold white and blue lettering : “ 100 \% Electric ” above “ Delivering Shipment Zero. ” A person ’s hand at the left holds a charging plug near the vehicle, visually connecting the text to electric \textbf{delivery}.
A small number “ 15 ” sticker is visible near the lettering.
An aerial view follows a blue Amazon semi-trailer truck with a white cab driving along a multi-lane highway bordered by green vegetation.
The trailer carries a large white Amazon smile logo.
The truck moves steadily along the road, with misty or hazy greenery around it.
Back at an airport runway, a white “ Prime Air ” cargo plane lifts off.
Its landing gear is still extended as it rises above the runway, the blue Prime Air lettering large along the fuselage and the Amazon smile visible on the tail.
The plane climbs gradually, moving across a pale sky with airport buildings and treeline low in the background.
A wide aerial view shows a large \textbf{industrial} \textbf{parking} \textbf{lot} and logistics facility.
Rows of vehicles fill the \textbf{lot} : many dark vans lined up in neat rows, smaller cars parked in groups, and yellow vehicles near a white warehouse building.
Streets border the \textbf{site}, with additional cars parked along the curb.
The area looks like an operations hub or fleet yard.
The commercial then moves inside a spacious vehicle design or workshop \textbf{environment} with polished floors, high windows, and bright linear \textbf{ceiling} lights.
A full-size \textbf{delivery} van prototype sits in the center, initially covered in an orange clay-like or matte material.
Several \textbf{workers} move around it, some standing on ladders, others kneeling near the wheels or working along the body.
Design boards or presentation panels line the back wall.
As the sequence progresses, the van ’s appearance changes from orange to a dark blue finished surface with flowing light-colored lines along the roof and sides and an Amazon smile mark on the side. \textbf{Workers} continue inspecting, adjusting, and working around it, with \textbf{tools}, stools, boxes, and equipment scattered nearby.
The final view of the workshop presents the completed dark blue electric-style \textbf{delivery} van standing prominently in the clean, bright space.
A close view shows hands \textbf{typing} on a \textbf{laptop} keyboard.
The person ’s fingers move across the \textbf{keys}, with a softly blurred green outdoor background beyond the \textbf{computer}.
This suggests data or planning work connected to the \textbf{transportation} scenes.
Henry appears again in a close side view wearing his black face \textbf{mask} and glasses.
Only part of his face is visible, with the \textbf{mask} covering his nose and mouth.
His eyes look focused behind the lenses, and greenery remains softly blurred behind him.
He is then shown once more in the leafy outdoor setting without the close \textbf{mask} view dominating, standing comfortably with trees behind him.
He looks engaged and begins to smile slightly, his expression warm and thoughtful as he continues speaking.
The commercial ends on a high aerial view of a road running through green land partly covered by soft white clouds or mist.
A large white Amazon smile logo appears over the landscape, centered across the road and greenery, becoming the final visual emblem.

% matched lemmas: backpack, bear, ceiling, computer, delivery, device, environment, high-visibility, industrial, key, laptop, lot, mask, medium, parking, phone, professional, safety, site, sweater, tool, transportation, type, worker
\end{textsample}
