\begin{textsample}{POS Dim 1 – 1980 – Score 11.00 – 1980/tv\_com\_1980\_54.txt}  \label{ex:f1_pos_080}
The commercial \textbf{opens} from black to an \textbf{exterior} \textbf{view} of a Shell gas station.
A large yellow canopy with the word “ Shell ” is visible above gas pumps.
A white or silver \textbf{car} is parked beside the pumps.
The camera cuts closer to the pump island and the side of the \textbf{car}, showing Shell-branded pumps and fuel hoses.
The next shot \textbf{moves} \textbf{inside} a dark \textbf{car} interior, apparently a large \textbf{vehicle} or limousine.
Four formally dressed people sit in the back : three men in suits/tuxedos and one woman in a dark outfit with a light blouse.
They hold clipboards or pads, suggesting they are observing and evaluating something \textbf{outside}. \textbf{Outside}, a male gas station attendant in a red shirt and tan pants operates the pump.
He is shown reaching to the pump controls, then a close-up shows the \textbf{car} ’s fuel filler area.
He inserts or handles the fuel nozzle at the side of the \textbf{car}.
The attendant \textbf{moves} quickly and theatrically around the \textbf{car}, while the people \textbf{inside} watch and take notes.
A low-angle shot shows the attendant leaning over the front of the \textbf{car} near the \textbf{hood}, with the Shell canopy and lights above him. \textbf{Inside} the \textbf{car}, the formally dressed observers look attentive and \textbf{continue} writing.
Another \textbf{exterior} shot from under the raised \textbf{hood} shows the attendant at the engine area, as if checking something.
A close-up \textbf{inside} the \textbf{car} shows the woman and one of the men looking toward each other.
A \textbf{brief} product display appears : rows of gray plastic bottles with labels featuring Shell-style colors.
The camera \textbf{moves} across the bottles rapidly, making the exact label text unclear.
The scene returns to the observers \textbf{inside} the \textbf{car}, including a close-up of one older man looking out the window. \textbf{Outside}, the attendant raises one arm in an exaggerated pose beside the \textbf{car}.
From \textbf{inside} the \textbf{vehicle}, the woman is seen in profile while the attendant appears through the rear window behind her.
The observers then become more animated.
A close-up shows a blue windshield squeegee or cleaning tool at the \textbf{car} ’s fuel door area, followed by a close-up of a fuel nozzle with liquid dripping from its tip.
Through the window, the attendant stands \textbf{outside} holding up a large rectangular item or sign, performing toward the people in the \textbf{car}.
The judges/observers raise score cards with large black numbers.
One \textbf{exterior} front shot of the \textbf{car} shows a card above the roof reading “ 10 6, ” suggesting overlapping or partially visible score cards.
Back \textbf{inside}, several people lift cards overhead.
Another front shot shows three score cards above the roof, each displaying “ 10. ” In the final frame, the \textbf{car} is seen from the front with large score cards behind or above it ; visible numbers include “ 10, ” “ 10, ” and “ 9. ” A large Shell logo is centered over the grille, and bold white text across the bottom reads : “ The \textbf{Move} Is On. ”

% matched lemmas: brief, car, continue, exterior, hood, inside, move, open, outside, vehicle, view
\end{textsample}
