\begin{textsample}{POS Dim 1 – 1950 – Score 15.00 – 1950/tv\_com\_1950\_87.txt}  \label{ex:f1_pos_084}
The commercial is in black and white and unfolds through a series of scenes connected by cuts and cross-fades. 1. **Opening product image / \textbf{exterior} setting** The first frame shows a large, semi-transparent box labeled **“Kodak FILM”** superimposed over an outdoor \textbf{view}.
Behind it are \textbf{clouds}, a \textbf{building} façade, a path, \textbf{grass}, and trees.
The product package dominates the frame. 2. **Entrance to a building** The scene changes to glass double doors.
A child or young person is visible through the doors, standing or entering from \textbf{outside}.
Reflections and the bright \textbf{exterior} make details hard to see. 3. **School-like \textbf{exterior} with children** A cross-faded \textbf{view} shows a \textbf{brick} \textbf{building} \textbf{entrance} with glass doors.
Two children or young people stand near the doorway, \textbf{carrying} bags or cases.
A bicycle is parked to the right near the wall.
Reflections in the glass and the dissolve make the scene partially layered. 4. **Close \textbf{view} of \textbf{brick} wall and shrubbery** The image \textbf{moves} to a close \textbf{exterior} detail : a \textbf{brick} corner, a window, and leafy bushes.
A blurred figure \textbf{passes} at the left edge, but the person is not clearly visible. 5. **Interior with \textbf{model} railway / toy setup** After a time jump, the commercial cuts to an indoor scene with a tabletop or floor-level \textbf{model} train layout.
A cylindrical water-tower-like \textbf{structure} and track elements are visible.
The image is slightly blurred, suggesting motion or camera movement. 6. **Boy photographing \textbf{model} train scene** A boy appears behind the \textbf{model} layout, holding a small camera up to his face.
Shelves in the background hold objects or toys.
The foreground includes tracks, a train \textbf{car} or platform, and small \textbf{model} accessories.
He appears to be aiming the camera at the miniature scene. 7. **Camera flash** The boy \textbf{continues} holding the camera.
A bright flash fills the frame briefly, then the image returns to the boy with the flash bulb or camera front glowing brightly.
The \textbf{model} train layout remains in the foreground. 8. **Classroom scene** The commercial cuts to a classroom.
A boy stands at the front, smiling, holding a small object in his hands.
Other students are seen from behind, seated and facing him.
A chalkboard with handwritten text is visible in the background, though the writing is only partly legible. 9. **Boy with camera against plain background** A boy in a dark jacket or uniform holds a camera up to his eye, pointing it slightly upward.
The background is plain and uncluttered. 10. **Marching group outdoors** The next shot shows a marching formation outdoors on a field.
Uniformed participants march in rows, and one person \textbf{carries} a flag.
A crowd or line of spectators is visible in the background, with trees behind them. 11. **Close-up of smiling boy with camera** A boy smiles while holding a camera close to his face.
The camera has a prominent round lens or flash attachment.
The \textbf{sky} or a plain bright outdoor background is behind him. 12. **Statue of Liberty** The commercial cuts to a clear shot of the Statue of Liberty from below, with the statue framed against a dark \textbf{sky}. 13. **Boy looking upward with camera** A boy outdoors smiles and looks upward.
A camera hangs or rests near his chest.
Trees and \textbf{sky} are visible behind him. 14. **Final product display** The last frame shows a product display with a camera and film-related packaging arranged on a tray or platform.
Large outlined text reading **“Kodak”** is superimposed prominently across the right and center of the frame.
The display includes a visible camera and Kodak-branded materials, though some smaller printed text is not fully readable.

% matched lemmas: brick, building, car, carry, cloud, continue, entrance, exterior, grass, model, move, outside, pass, sky, structure, view
\end{textsample}
