\begin{textsample}{POS Dim 1 – 2020 – Score 21.00 – 2020/tv\_com\_2020\_83.txt}  \label{ex:f1_pos_039}
The commercial unfolds as a Jeep \textbf{vehicle} advertisement with seasonal/holiday and sales-event imagery. 1. **Opening \textbf{exterior} setting:** The first frame shows a large \textbf{brick} \textbf{suburban} house with a lawn and trees in daylight.
The foreground is motion-blurred, suggesting the camera or \textbf{vehicle} is \textbf{moving} \textbf{past} the property. 2. **Black SUV in motion:** The scene cuts to a black Jeep SUV \textbf{driving} along a paved \textbf{road} bordered by green \textbf{grass} and trees.
The camera \textbf{angle} is elevated and side-on, showing the \textbf{vehicle} \textbf{moving} through a wooded or park-like area in daylight. 3. **Holiday sales-event graphic:** The commercial shifts to an \textbf{aerial} \textbf{view} of a wintery public space with snow-dusted trees, paths, and \textbf{pedestrians}.
A large decorated Christmas tree stands centrally.
Overlaid text reads : **“WRAP UP THE YEAR SALES EVENT”** with the **Jeep** logo beneath it.
A red bow graphic appears above the text. 4. **Red Jeep Wrangler in snow:** A red Jeep Wrangler \textbf{drives} through snow or icy \textbf{mist}, facing toward the camera at a slight \textbf{angle}.
Snow is visible on the \textbf{hood} and surrounding the \textbf{vehicle}.
Overlaid text reads : **“JEEP WRANGLER”** and **“MOST CAPABLE WRANGLER EVER.”** Small fine print appears at the bottom but is mostly too small to read clearly. 5. **Interior dashboard view:** The next frame shows the interior of a Jeep \textbf{vehicle}, centered on the dashboard and infotainment screen, with the steering wheel visible on the left and wood-toned trim across the dash.
Overlaid text reads : **“JEEP GRAND CHEROKEE”** and **“MOST LUXURIOUS \textbf{VEHICLE} IN ITS CLASS.”** Additional fine print appears at the bottom. 6. **Red Jeep off-road:** A red Jeep \textbf{drives} along a \textbf{rough} dirt or gravel mountain \textbf{road}, kicking up dust.
The \textbf{vehicle} is \textbf{angled} toward the camera, with a rocky slope on the right side of the frame.
Overlaid text reads : **“JEEP BRAND”** and **“MOST AWARDED SUV BRAND EVER.”** Fine print is again present at the bottom. 7. **Nighttime town / financing offer:** The commercial cuts to a nighttime \textbf{aerial} \textbf{view} of a town or downtown area decorated with holiday lights.
A large lit Christmas tree is visible near the center.
Large white text overlays the scene : **“NO MONTHLY PAYMENTS FOR 90 DAYS”** and below it **“ON MOST JEEP BRAND MODELS.”** A graphic near the bottom reads **“AMERICA 250”** with red, white, and blue styling.
Dense fine print spans the bottom of the frame. 8. **Transition overlay:** The same nighttime town \textbf{view} \textbf{continues}, but the large text begins to fade or dissolve, producing a layered transition effect.
The holiday-lit \textbf{streets} and \textbf{buildings} remain visible underneath the fading promotional text and fine print. 9. **Final dealer offer screen:** The ad transitions to a static promotional layout featuring a white **2025 Jeep Grand Cherokee Laredo 4x4** parked in front of a large statue of a muscular figure holding something in one hand.
The background appears urban/industrial and gray-toned.
Large offer text on the left reads : - **“2025 JEEP GRAND CHEROKEE LAREDO 4x4”** - **“LEASE FOR \$280 / MO.”** - **“\$280 DUE AT SIGNING”** - **“\$0 DOWN PAYMENT”** There is also a small **“Wrap Up the Year”** sales-event logo, **“JEEP.COM,”** and a large regional/dealer branding line reading **“METRO DETROIT | Jeep.”** Fine-print \textbf{legal} text fills the lower portion of the frame. 10. **Closing frame:** The final frame remains on the same static offer screen with the white Jeep, the statue, the lease pricing, **“METRO DETROIT | Jeep,”** and dense fine print along the bottom.

% matched lemmas: aerial, angle, brick, building, continue, drive, exterior, grass, hood, legal, mist, move, past, pedestrian, road, rough, street, suburban, vehicle, view
\end{textsample}
