\begin{textsample}{POS Dim 1 – 2020 – Score 15.00 – 2020/tv\_com\_2020\_26.txt}  \label{ex:f1_pos_014}
A brightly lit True Value store appears, with wide white aisles, red overhead \textbf{department} signs, and shelves packed with hardware products.
Red signs mark areas such as “ LAWN \& GARDEN, ” “ PAINT, ” “ ELECTRICAL, ” and numbered aisles.
A store associate in a red True Value shirt walks with a woman shopper in a gray-green jacket and \textbf{jeans}, talking with her as they move down the main aisle.
Nearby, a man pushes a red True Value shopping cart, and other shoppers browse in the background.
The associate and the woman slow to a stop near the electrical section, facing each other as if discussing what she needs, while the man with the cart continues away to the right.
In a \textbf{tools} aisle, a \textbf{bald}, \textbf{bearded} man in a plaid overshirt stands beside a True Value \textbf{employee} wearing a red shirt and name \textbf{tag}.
Both are surrounded by shelves filled with red Milwaukee \textbf{tool} packaging and hanging accessories.
The \textbf{customer} holds out a \textbf{smartphone} and shows it to the \textbf{employee}.
The \textbf{employee} looks at the \textbf{phone}, then points down the aisle, guiding him toward the right product.
The image quickly moves along shelves of red Milwaukee boxes, stopping on a large red box labeled “ M18 FUEL, ” with a circular saw pictured on the front.
The \textbf{customer} reaches in with both hands, pulls the box off the shelf, and carries it toward a red shopping cart while the \textbf{employee} watches from behind with a satisfied expression.
The \textbf{customer} continues shopping.
From the front of the red cart, he places a long yellow DeWalt level or \textbf{tool} into the basket.
The \textbf{tools} aisle around him is divided by red brand displays, with Milwaukee \textbf{tools} on one side and yellow-and-black DeWalt products on the other.
He adds more items from other aisles : a red boxed product in a cleaning section, then a small white bottle or container from a shelf lined with household \textbf{supplies}.
He moves through the store with the cart filling up.
In a wider store view, he pushes the cart past a “ DEAL ZONE ” bin and \textbf{department} signs for “ PLUMBING ” and “ ELECTRICAL. ” The red cart is now loaded with the red Milwaukee saw box, the yellow level, and other \textbf{supplies}, with a bag of material resting on the lower rack.
The scene changes to a home garage.
From inside the dim garage, a white overhead garage door rises, revealing the man standing outside in \textbf{daylight}.
He is now dressed in a brown \textbf{sweater}, \textbf{jeans}, and brown shoes.
As the door lifts, a quiet suburban driveway and houses across the street become visible.
He steps into the garage, which has \textbf{tools} hanging neatly on the wooden wall to the left, including long-handled garden \textbf{tools} and a broom.
He then uses a red Milwaukee circular saw to cut through a long wooden board laid across a work surface.
The saw blade spins through the wood, and the man grips the handle firmly, guiding the \textbf{tool} in a controlled line.
A separate home project appears in a bright kitchen.
A yellow-and-black cordless drill drives a screw into a white cabinet or shelf edge while a hand steadies the surface.
The drill bit presses into the hardware, tightening it into place.
The view widens to show a woman with a casual, practical look : she has medium-brown hair tied back, wears glasses, a dark plaid overshirt over a maroon top, and \textbf{jeans}.
She reaches up to a white cabinet handle, checking or adjusting it.
A yellow drill rests on the black countertop near a vase of sunflowers, and the kitchen has white cabinets, large windows, and a pale turquoise tile backsplash.
A man in a white shirt with red sleeves stands beside her, watching and talking with her.
They look at the newly worked-on cabinets and backsplash area, then exchange a pleased glance, appearing to admire the result together.
A blue kettle sits on the stove beneath a stainless range hood, adding to the \textbf{lived-in} kitchen setting.
Outside, the man in the white-and-red shirt uses a yellow pressure washer in a driveway beside a closed white garage door.
The pressure washer unit stands behind him with a coiled hose on its frame.
He holds the spray wand with both hands and directs a strong stream of water downward across the dark wet pavement, cleaning the surface in front of him.
Potted flowers and greenery sit near the edge of the driveway, and sunlight falls across the house exterior.
Inside another room, a paint roller spreads a glossy dark gray-brown paint over a pale wall.
The roller moves upward and across, leaving a rectangular patch of fresh paint.
The woman in the plaid overshirt is now painting the wall herself.
Blue painter ’s tape outlines the window trim, baseboards, and door frame to protect the edges.
A step ladder stands nearby, and paint \textbf{supplies} are on the floor.
She rolls paint steadily upward, extending the newly painted patch, then lowers the roller and continues smoothing the area.
Back in the living room of the \textbf{bald} man ’s home, he measures a wall with a yellow level.
The room has warm wood floors, a patterned rug, a sofa with colorful pillows, a chair, plants, shelves, and a fireplace in the background.
He holds the level against a pale wall and adjusts it carefully, then fastens shelf brackets.
He lifts a wooden shelf board into place on the brackets, aligning it neatly.
The finished shelf holds a white vase, a small candleholder, and a leafy green plant.
Standing back with his hands in his pockets, he looks at the shelf and smiles, clearly pleased with the completed project.
The background softens behind him, and a red oval True Value logo appears large in the center of the \textbf{screen}.
Beneath it, white uppercase text appears : “ YOUR PROJECT.
YOUR WAY. ” The logo and slogan remain centered while the home interior stays blurred behind them.

% matched lemmas: bald, bearded, customer, daylight, department, employee, jean, lived-in, phone, screen, smartphone, supply, sweater, tag, tool
\end{textsample}
