\begin{textsample}{POS Dim 1 – 1990 – Score 14.00 – 1990/tv\_com\_1990\_91.txt}  \label{ex:f1_pos_044}
The commercial \textbf{opens} on a black screen.
At around 7 seconds, the scene cuts to a sunlit, curving two-lane \textbf{road}, bordered by rocky terrain and dark trees.
The image has a warm, golden-orange color cast.
A dark \textbf{sedan} then appears \textbf{driving} toward the camera with its headlights on, \textbf{moving} along what appears to be a \textbf{wet} or reflective \textbf{road} surface.
The background remains strongly backlit and golden.
A very blurred side \textbf{view} follows, showing the dark \textbf{car} \textbf{passing} through a warm-toned landscape ; the motion blur emphasizes speed and movement.
The commercial then cuts to the \textbf{vehicle} ’s interior : tan or beige leather seats are shown from the front area looking toward the rear bench.
The front headrests, rear seats, seat belts, and side windows are visible.
No passengers are clearly visible in this interior shot.
A \textbf{brief} bright white flash transition appears, followed by more fast-moving \textbf{exterior} imagery.
The camera shows blurred roadside or landscape elements, then a side profile of the dark \textbf{sedan} \textbf{moving} from left to right against an orange, sunlit background.
The \textbf{car} ’s headlight is bright, and the body is largely in silhouette due to the strong backlighting.
A rear \textbf{view} of the \textbf{car} follows.
The trunk area and red taillights are visible, along with a central \textbf{badge} that resembles the Infiniti emblem.
The license plate area is present but not legible in the frame.
Another bright white transition occurs.
The commercial then shows rapidly \textbf{moving} shots of trees and sunlight, with the camera \textbf{passing} through or alongside a wooded area.
The sun flares through the trees, producing strong glare and lens flare effects.
Several frames alternate between bright overexposed flashes and blurred \textbf{views} of trees, \textbf{sky}, and golden foliage.
The final frame returns to a black background with centered white/gray text.
Large text reads “ G20. ” Beneath it, the price is shown as “ \$21,485. ” Smaller text below reads : “ M.S.R.P., fully-equipped including destination charges.
Title, taxes and license fees not included. ”

% matched lemmas: badge, brief, car, drive, exterior, move, open, pass, road, sedan, sky, vehicle, view, wet
\end{textsample}
