\begin{textsample}{POS Dim 1 – 2020 – Score 22.00 – 2020/tv\_com\_2020\_7.txt}  \label{ex:f1_pos_038}
The commercial \textbf{opens} in a vertical-phone-video style, with blurred side borders and a small “ ring ” watermark at the lower left. \textbf{Inside} a home, a man sits beside a young girl who is covering her face, while a light-colored puppy is held between them.
The room appears domestic, with a desk and window in the background.
The next close-up shows the same or similar light-colored puppy pressed against the girl ’s chest ; the girl is smiling or emotional as she holds it.
The tone then shifts.
A close-up shows a young girl outdoors wearing a lavender knit hat and a floral fleece jacket.
She looks serious or worried.
The scene cuts to a \textbf{residential} \textbf{street} where an adult man and the girl are putting up or \textbf{carrying} printed missing-dog flyers on a utility pole.
Houses, parked \textbf{cars}, and bare trees are visible, suggesting a neighborhood setting.
A \textbf{montage} follows of people posting missing-dog flyers in \textbf{different} places and conditions.
One man attaches a flyer to a pole on a \textbf{city} \textbf{street} with storefronts behind him.
An older woman posts a flyer in a snowy neighborhood.
Several close-ups show \textbf{different} “ lost dog ” or “ missing ” posters taped to poles : some are in rainy nighttime \textbf{streets}, some in sunny suburbs, some in autumn settings, and some in snowy \textbf{streets}.
The posters show various dog photos and readable headings such as “ LOST DOG, ” “ MISSING, ” and “ I ’M MISSING, ” with partial details like dog names, contact information, and rewards.
One close-up shows a “ LOST DOG ” flyer for a white dog with the line “ PLEASE HELP FIND OUR MILO. ” The rapid sequence emphasizes many separate lost-dog notices in \textbf{different} neighborhoods.
After a \textbf{brief} black frame, a man appears outdoors in a tree-lined \textbf{residential} area, facing the camera and holding up a smartphone.
The phone screen shows a dog-related page with a photo of a white dog.
The small “ ring ” watermark remains at the lower left.
The commercial then cuts to a close-up of hands using a smartphone.
The screen shows a form with a large photo of a white dog at the top and text-entry fields below.
A person types information into the form.
The next \textbf{view} is a clean, white app interface showing fields labeled “ Pet Name ” and “ Description. ” The pet name field reads “ Milo, ” and the description field begins with “ Milo our ye … ” before the frame changes.
A small blue label at the bottom right reads “ Introducing Search Party. ” Another app screen shows “ Sharing Options ” and a large blue button labeled “ START SEARCH PARTY. ” The visuals then illustrate the feature spatially.
A \textbf{suburban} house is shown from above, and a blue cone or beam-like graphic projects from the driveway or front area.
This is followed by a \textbf{wider} \textbf{aerial} \textbf{view} of a neighborhood with multiple blue glowing circles or pulses appearing over many houses, suggesting a network of \textbf{nearby} homes being notified or connected.
The “ Introducing Search Party ” label remains at the bottom right.
The scene returns to a \textbf{residential} walkway leading toward a \textbf{street}.
The \textbf{view} is from a front entry or porch area, with hedges and low walls on either side.
Then a man and a young girl appear \textbf{inside} or at the doorway of a house, looking outward as if responding to something \textbf{outside}.
The girl wears a cardigan over a striped shirt, and the man smiles.
A blurred low-angle shot shows the front steps of a house as movement \textbf{passes} in the foreground ; the details are not fully clear, but it appears to show someone or an animal \textbf{moving} toward the \textbf{entrance}.
The next shot shows a light-colored dog being embraced or petted by the girl and an adult man on a porch.
Their faces suggest happiness.
Another adult man, shown in close-up under the porch roof, smiles while looking downward, possibly toward the dog or the family, though the exact relationship is not visible from the frames.
Near the end, the earlier man from the phone demonstration walks down a quiet, tree-lined \textbf{street} with a dog on a leash.
Fallen leaves are scattered on the \textbf{road}.
The commercial then cuts to an \textbf{exterior} shot of a house roof and upper windows at dusk or late afternoon.
The final frame shows the Ring end card over the house \textbf{exterior}.
Large white text reads “ ring, ” with smaller text underneath : “ Find your dog with Search Party. ” The background remains the roofline of the house with trees and \textbf{sky} above.

% matched lemmas: aerial, brief, car, carry, city, different, entrance, exterior, inside, montage, move, nearby, open, outside, pass, residential, road, sky, street, suburban, view, wide
\end{textsample}
