\begin{textsample}{POS Dim 1 – 1980 – Score 17.00 – 1980/tv\_com\_1980\_45.txt}  \label{ex:f1_pos_072}
The commercial begins with an almost completely dark frame ; no clear objects or setting are visible.
It then cuts to a close-up of a man outdoors.
He has short dark hair and is wearing dark clothing, gloves, and what appears to be a headset or earpiece with a microphone near his mouth.
The background is a blurred, wooded or hilly landscape.
Next, the man is shown seated \textbf{inside} a \textbf{car}.
He is wearing sunglasses, a brown or olive leather jacket, light-colored pants, and gloves.
The \textbf{car} interior is dark, and the steering wheel and dashboard are visible.
Through the \textbf{open} side or window area, greenery and flowers can be seen \textbf{outside}.
A closer interior shot follows from behind/alongside the \textbf{driver}, focusing on his upper body, arm, steering wheel, and dashboard area.
The man appears to be operating controls or preparing to \textbf{drive}, though the exact action is partly obscured by the camera \textbf{angle}.
The commercial then cuts to a close-up of the instrument panel.
A gauge labeled with numbers from about 10 to 60 is visible, with the needle positioned low-to-mid on the scale.
Other dashboard elements are partially visible, but not clearly readable.
The scene shifts to an \textbf{exterior} front \textbf{view} of a red sports \textbf{car} parked in a driveway or near a house.
The \textbf{car} has a low, angular front end with narrow headlight areas and a raised \textbf{hood} section.
The surrounding setting includes a \textbf{building} \textbf{entrance} and landscaping.
A later shot shows the top/front portion of the \textbf{car} emerging over a rise in a \textbf{road}, framed by tall trees and \textbf{distant} \textbf{hills}.
Only the upper part of the \textbf{vehicle} is visible at first, suggesting it is \textbf{driving} along a \textbf{road} in a wooded or \textbf{rural} area.
The final frame shows an overhead or high-angle \textbf{view} of the red \textbf{car} \textbf{driving} on a \textbf{road} beside a rocky or earthen background.
Large red text near the top reads “ PONTIAC ” with the Pontiac arrowhead logo beside it.
At the bottom, a caption reads : “ NOW THE EXCITEMENT REALLY BEGINS. ”

% matched lemmas: angle, building, car, distant, drive, driver, entrance, exterior, hill, hood, inside, open, outside, road, rural, vehicle, view
\end{textsample}
