\begin{textsample}{POS Dim 1 – 1990 – Score 11.00 – 1990/tv\_com\_1990\_86.txt}  \label{ex:f1_pos_047}
The commercial \textbf{opens} in a very dark interior with large window or glass-door panels.
Several people appear only as silhouettes, standing or \textbf{moving} in a room with strong backlighting.
The image then dissolves into an office-like setting.
A man in a white dress shirt and tie is seen close to the camera, partly superimposed over the previous glass-walled interior.
The layered transition makes the details hazy, but the setting appears to include desks, windows, and people in business attire.
Next, two men in dress shirts and ties are shown together, again with overlapping dissolves.
One appears older or balding ; another stands beside him.
They seem to be looking downward or at something in front of them, though the object is not clearly visible.
A close-up follows of an older bald man in a shirt, tie, and dark vest.
His face is centered and serious-looking.
The shot remains visually layered with remnants of other office images, making the background indistinct.
The sequence \textbf{continues} with businesspeople in shirts and ties, including a man facing forward and another older man beside him.
The images are still heavily cross-faded, giving a \textbf{montage} effect of office workers in discussion or observation.
Another close-up shows a middle-aged man in a white shirt and striped tie, with pens visible in his shirt pocket.
His expression appears concerned or intent.
A side \textbf{view} of another man overlaps the frame.
The \textbf{montage} then includes an image of a large airplane seen from the front, superimposed over the office scene.
The aircraft appears centered with wings extended, while the office worker remains faintly visible beneath the overlay.
The scene cuts to an \textbf{exterior} \textbf{street} \textbf{view} in daylight.
A \textbf{building} \textbf{entrance} has a sign reading “ SAN MARCOS HOTEL. ” A white delivery van with a red and orange/purple marking is parked at the curb.
A person in light clothing walks toward or into the hotel \textbf{entrance} \textbf{carrying} a package or parcel.
Palm trees and \textbf{street} fixtures are visible \textbf{outside}.
The next interior shot shows a dim conference or meeting room.
Several seated figures are visible in silhouette against horizontal window blinds.
A tilted rectangular “ Federal Express ” logo graphic appears over the scene, as if displayed or superimposed in front of the people.
The commercial ends on a full-screen graphic : a tilted “ FEDERAL EXPRESS ” logo on a textured brown/gold background.
Beneath it, large white text reads : “ OUR MOST IMPORTANT PACKAGE IS YOURS. ”

% matched lemmas: building, carry, continue, entrance, exterior, montage, move, open, outside, street, view
\end{textsample}
