\begin{textsample}{POS Dim 1 – 1990 – Score 8.00 – 1990/tv\_com\_1990\_109.txt}  \label{ex:f1_pos_048}
A young adult woman with light skin and long, windblown \textbf{light-brown} hair walks along a sunny city sidewalk.
She wears a short-sleeved, horizontally striped top in pale and dark bands.
Parked cars, trees, and glass-fronted buildings pass behind her.
At first she is seen in profile, moving steadily with a neutral expression.
Then she turns her head toward the viewer, her hair lifting in the breeze, and breaks into a friendly smile as she continues walking between the parked cars and leafy background.
A light-skinned adult man appears outdoors against a soft green backdrop of trees.
He wears a pale lavender button-down shirt and faces forward as if answering a question.
His expression is relaxed and agreeable, with a slight smile.
The scene shifts indoors to a bright, softly lit living room.
A middle-aged light-skinned woman with short dark hair sits on a white sofa.
She wears a beige jacket over a light top, pearl-like earrings, and a delicate necklace.
Pale walls, window blinds, a framed picture, and white furnishings give the room a clean, airy look.
Yellow and white on-screen text identifies her as “ ERIN \textbf{GRAY} ” with “ Film \& TV Star ” underneath.
She looks directly ahead, speaking to the viewer.
She then lifts a tall white cylindrical bottle with a white cap and pump top.
The label, printed vertically in dark lettering, reads “ INSTANT WHITE. ” She holds it beside her face and points to it with one finger, smiling as she presents the product.
A light-skinned adult man in a red shirt demonstrates the spray.
He holds the tall white Instant White bottle close to his mouth, tilts his head slightly, opens his mouth, and presses the pump with his index finger.
The bottle ’s label is large and vertical, and the white pump top is aimed toward his teeth.
A graphic comparison follows.
The \textbf{screen} is divided into horizontal panels showing close views of smiling mouths.
The upper panel is labeled “ Before ” in yellow-green text, and the lower panel is labeled “ After ” in white text.
In the “ Before ” images, the teeth appear duller or more yellowed ; in the “ After ” images, the teeth look brighter and whiter.
Additional split panels show different close-ups of mouths from the side and front, reinforcing the before-and-after contrast.
One layout places two narrow horizontal strips of the same mouth on a black background, with the lower strip visibly brighter.
A close-up shows a hand squeezing a thick gel from a white tube into a translucent mouth tray.
Another clear tray lies nearby on a wooden surface.
The gel piles into the tray, making the process look messy and hands-on.
A woman with short, softly curled \textbf{light-brown} hair is then shown placing a tray or small mouthpiece at her teeth.
She pulls it away and smiles, revealing her teeth.
Immediately after, she holds the tall Instant White spray bottle beside her face, smiling broadly.
She wears a light-colored collared shirt and appears to be in an \textbf{indoor} setting with a darker window or reflective background behind her.
She raises the bottle toward her open mouth and uses it as a spray, the pump aimed at her teeth.
A close-up of a smiling mouth fills the \textbf{screen}.
Large text appears over the lower part of the image : first “ Eliminates Coffee Stains, ” then “ Eliminates Other Discoloration. ” The teeth are shown very white, with lips in a warm peach shade, and the words sit across the lower portion of the smile.
Erin Gray returns on the white sofa, still facing forward in the bright living room.
A large white \textbf{phone} number, “ 1-800-941-8200, ” appears across the bottom of the \textbf{screen} in bold, high-contrast digits while she continues speaking.
She maintains a composed, reassuring expression, occasionally smiling and tilting her head slightly.
The product is then displayed against a glossy blue and teal studio-style background.
A full-size white Instant White bottle stands upright on the left.
A glowing yellow-orange streak points toward the display, and a smaller travel-size white bottle appears beside the larger one.
Large yellow text with a red shadow reads “ FREE BONUS! ” near the upper right.
The \textbf{phone} number “ 1-800-941-8200 ” remains large along the bottom.
A man seated in the driver ’s seat of a car is shown using the smaller bottle.
He wears a blue shirt and sits beside the steering wheel with the driver ’s door area visible.
Holding the travel-size spray near his mouth, he tips his head back slightly and sprays upward toward his teeth, suggesting use away from home.
The \textbf{phone} number remains overlaid at the bottom.
The product display returns on the blue background with both bottles upright : the tall full-size bottle on the left and the smaller travel-size bottle beside it.
Large white price text appears on the right : “ Only \$19.95, ” with the “ 95 ” raised like cents.
The bottles ’ white packaging and bold vertical “ INSTANT WHITE ” labels stand out against the \textbf{cool} blue background.
Finally, Erin Gray appears again in close view in the same soft living-room setting.
Any product and price \textbf{graphics} fade away, leaving her face centered.
She smiles warmly, then speaks directly to the viewer with a steady, confident expression.
The commercial ends on her composed face, framed by the pale sofa and softly lit background.

% matched lemmas: cool, graphics, gray, indoor, light-brown, phone, screen
\end{textsample}
