\begin{textsample}{POS Dim 1 – 1960 – Score 20.00 – 1960/tv\_com\_1960\_36.txt}  \label{ex:f1_pos_052}
The commercial is presented in a grainy black-and-white/sepia style with rapid cuts, motion blur, and occasional double exposure.
A small “ Nostalgic X’er ” watermark appears at the lower right throughout the sampled frames.
It \textbf{opens} on an \textbf{exterior} sign with large rooftop letters, partially visible as “ …ANCIS …, ” suggesting an \textbf{urban} \textbf{location}.
The next few shots are blurred transitions through \textbf{city} \textbf{streets}.
A streetcar or cable-car-like \textbf{vehicle} appears briefly, followed by a low-angle \textbf{view} of a tall tower or monument rising above trees.
The sequence then \textbf{moves} through more fast \textbf{urban} imagery : a low-angle shot of a person \textbf{moving} near a large \textbf{building} or \textbf{vehicle}, a \textbf{street} scene with a \textbf{vehicle} or sign showing “ PEPSI, ” and then a group of young adults smiling while walking together in front of a large \textbf{building} \textbf{entrance}.
These shots are intercut with blurred motion frames.
A storefront sign then appears prominently : “ GROOM \& CLEAN. ” In a closer \textbf{view}, the sign reads “ GROOM \& CLEAN, ” with smaller text underneath including “ FOR CLEAN … HAIR GROOMING — WITHOUT GREASE, ” though parts of the smaller line are hard to read.
The word “ SAN FRANCISCO ” is visible below the sign, tying the setting to San Francisco.
The middle portion shows a man in profile with neatly styled dark hair.
This is followed by close-up grooming imagery : hands working through or combing a person ’s hair, and a person seated while hair is being handled.
A convertible \textbf{car} appears with several young adults \textbf{inside} ; the \textbf{car} is shown from the side as it \textbf{moves} or is parked in an \textbf{urban} \textbf{street} setting.
The commercial then shifts to waterfront and leisure imagery.
A person sits on \textbf{rocks} near the Golden Gate Bridge, with water and \textbf{hills} in the background.
A close-up of a foot or lower leg in water appears with bold on-screen text reading “ water active. ” Another close-up shows \textbf{wet} hair being rubbed or washed by hands.
A further hair close-up includes the on-screen text “ cleans away dirt dandruff, ” with the last word partially obscured but mostly legible.
The next shots show a smiling man and woman close together near water, then a sailboat with a large striped sail \textbf{passing} in front of the Golden Gate Bridge.
A man in a light top is shown in profile against a bright \textbf{sky}.
Near the end, a smiling blonde woman poses playfully while holding onto rigging or netting on or near a boat, with \textbf{city} \textbf{buildings} and bridge \textbf{structures} visible in the background.
The final frame is a product shot : a tube labeled “ GROOM \& CLEAN, ” with smaller text below that appears to include “ HAIR GROOMING — WITHOUT GREASE. ” The tube is placed against a textured background with strands of hair visible \textbf{nearby}.

% matched lemmas: building, car, city, entrance, exterior, hill, inside, location, move, nearby, open, pass, rock, sky, street, structure, urban, vehicle, view, wet
\end{textsample}
