\begin{textsample}{POS Dim 1 – 2000 – Score 18.00 – 2000/tv\_com\_2000\_51.txt}  \label{ex:f1_pos_018}
The commercial \textbf{opens} at \textbf{night} in a dark outdoor setting.
A man stands beside or partly on a red \textbf{car}, with metal barriers or rooftop/industrial \textbf{structures} in the foreground.
The lighting is low and blue-toned, with the \textbf{car} ’s front and rounded headlight visible.
The scene cuts to a close-up of a hand holding a Nokia \textbf{mobile} phone.
The phone has a small green backlit screen and an external antenna.
A thumb presses the keypad or navigation buttons.
The man is then shown sitting or leaning on the red \textbf{car} under a bright moon or streetlight, with a dark \textbf{skyline} behind him.
A \textbf{street} scene follows : a corner \textbf{building} at \textbf{night} with \textbf{wet} \textbf{pavement}, a lit streetlamp, neon signage, and a blue sign reading “ BAR. ” A person stands near the \textbf{entrance}.
Back at the rooftop/car \textbf{location}, a close-up shows the man ’s face in profile, lit with cool blue light.
A close-up of a woman follows ; she has dark hair, wears earrings and a necklace, and appears to be smiling slightly while looking toward the man.
The two are then shown together beside the \textbf{car}.
The man holds the phone while the woman stands close to him.
A close-up of the Nokia phone shows the screen with a connection/loading bar and partially readable text beginning with “ Connecting to … ”.
The exact destination or service text is not fully clear.
The thumb \textbf{continues} operating the phone.
The commercial briefly cuts to a very dark shot with small points of light, then returns to the man and woman silhouetted against the \textbf{night} \textbf{sky} and a bright circular light.
Another close-up of the phone shows a short text message or menu item ; the words are partially readable but not fully clear. “ Options ” and “ Clear ” appear at the bottom of the screen.
A cutaway shows several round ceiling lights in a dark interior.
The woman is shown again in close-up, smiling and looking toward the man.
Another phone close-up shows a menu or service screen with a line that appears to include “ Flight Status, ” though some text is blurred.
The thumb selects or scrolls.
The next images show a vintage-looking propeller airplane at \textbf{night}, lit dramatically from below and from the side.
This is followed by a bright, reflective nighttime \textbf{street} or outdoor café scene with large umbrellas and strong highlights on \textbf{wet} surfaces.
A very dark transitional shot appears, then a close-up of pink neon tubing, forming part of a sign or decorative shape.
A \textbf{brief} interior or club-like scene follows, with people standing or dancing in low light under bright flame-like or lamp-like light sources.
The commercial then returns to the woman ’s close-up ; she looks sideways toward the man with a faint smile.
A \textbf{wider} rooftop shot shows the man and woman seated or leaning on the red \textbf{car}, looking out over a brightly lit \textbf{city} \textbf{skyline} at \textbf{night}.
Small white disclaimer text appears along the bottom : “ Service is not available in all \textbf{locations}.
Please check with your service provider. ” The next shot shows a hand holding the Nokia phone up against a blurred city-lights background, with the same disclaimer text along the bottom.
The couple is again shown from behind or in silhouette beside the \textbf{car}, facing the illuminated \textbf{city} \textbf{skyline} under a bright moon or lamp.
The final frame cuts to a clean white product shot : a Nokia phone centered above the large blue “ NOKIA ” logo.
Beneath it are the words “ CONNECTING PEOPLE ” and the \textbf{website} “ nokia.com. ”

% matched lemmas: brief, building, car, city, continue, entrance, location, mobile, night, open, pavement, sky, skyline, street, structure, website, wet, wide
\end{textsample}
