\begin{textsample}{POS Dim 1 – 1980 – Score 7.00 – 1980/tv\_com\_1980\_49.txt}  \label{ex:f1_pos_059}
Three uniformed women appear as dark silhouettes walking toward a bright opening inside a curved, tunnel-like space.
The surroundings are warm-toned and theatrical, with rounded walls and a broad, wing-like \textbf{ceiling} shape overhead.
As they come closer, their outlines suggest tailored skirt suits and confident, upright posture, moving side by side like airline staff approaching passengers.
The view moves in closer to one of the women, now visible as a smiling flight attendant in a dark TWA-style uniform with a white shirt and striped tie.
She has shoulder-length light brown or blonde hair and turns her head toward a colleague beside her, smiling warmly.
Another blonde uniformed woman passes close behind her, also smiling, reinforcing the sense of a polished, welcoming crew.
A close view shows hands rapidly pressing \textbf{keys} on a \textbf{computer} keyboard, suggesting reservations or airline operations work.
The scene then shifts to pilots in a cockpit : first a dim, misty profile of a pilot wearing a headset, then two cockpit crew members in white shirts and headsets seated among instrument panels.
One older male pilot turns back with a broad smile while another crew member sits farther forward.
A blonde flight attendant smiles directly toward someone just off to the side, her dark uniform and white shirt visible against a softly lit background.
Outside, silhouetted ground crew move in a large hangar doorway, each near a large airplane wheel.
The figures are backlit against a pale exterior, making the wheels and \textbf{workers} appear as strong black shapes.
A Black female airline \textbf{employee} in a dark uniform with a red scarf speaks face to face with a \textbf{customer} or colleague whose back is to the viewer.
She smiles with a composed, attentive expression.
This is followed by a view of an airplane wing and tail : a \textbf{worker} stands high on the wing holding equipment or a hose, while the red tail fin behind him shows large white “ TW ” letters.
He adjusts his stance, bends down, and continues working on the aircraft surface.
In another silhouetted view, a \textbf{worker} crouches on the wing with a line stretching upward, while a small airplane passes in the pale sky behind him.
A stylized aerial image shows pyramids in a reddish desert landscape.
A plane ’s dark shadow sweeps across the sand and pyramid shapes, linking TWA flight with distant travel destinations.
The red TWA tail appears again in close view, with the white letters “ TW ” visible before the image blurs into motion.
Inside an office-like operations area, several headset-wearing \textbf{employees} sit in a row at \textbf{computer} terminals.
They face angled \textbf{screens}, speaking into microphones and smiling as they work.
A pilot in a peaked cap is then seen through glass or a reflective partition, his figure softened by reflections.
Behind another glass doorway, several uniformed flight attendants stand together.
Red circular signs with white horizontal bars are fixed to the glass doors, partially obscuring their faces as the doors slide or the figures move behind them.
A captain or uniformed crew member appears briefly from below or beside aircraft structure, looking upward in dim light.
The commercial then moves inside the passenger cabin.
An elderly white woman with short white hair sits in a dark upholstered airline seat wearing a pale \textbf{sweater} over a white turtleneck.
A hand from the left offers her a tray with a white cup.
She looks pleased, accepts the service, and lifts her hands as if responding appreciatively.
Behind her, another passenger sits quietly.
In an airport or cabin-service setting, a blonde woman in a light coat speaks with a dark-haired uniformed staff member.
They face each other closely, suggesting a helpful conversation.
A dramatic image follows of a TWA jet flying past a grid of tall building windows against a vivid orange-red sky, the plane ’s red tail clearly visible as it crosses the glassy \textbf{urban} backdrop.
Back inside the aircraft, a blonde flight attendant in a dark uniform lifts a large tan leather bag into an overhead compartment.
She raises it with both hands and slides it neatly into the storage bin, where other luggage is already stowed.
Nearby, passengers sit in roomy seats.
One woman, dressed in a businesslike outfit with crossed legs, relaxes beside a window with a drink on the armrest.
Another passenger reclines deeply in a seat by the windows, head tilted back, appearing restful.
The elderly woman with white hair appears again, smiling softly while holding a small item in her hands, comfortable in her seat.
The Black female staff member returns in close view, smiling with a red scarf at her collar, with a busy but softly blurred service area behind her.
The headset-wearing \textbf{employees} at terminals appear again, three in a row, all focused on their \textbf{screens} and microphones.
The pilots reappear : one in a dim headset view, then an older cockpit crew member in a white shirt smiling under the cockpit \textbf{ceiling} panels.
Outside the terminal windows, a large TWA aircraft is parked with red striping along its fuselage.
Silhouettes of adults and a child stand inside the terminal looking out at the plane.
The word fragment “ WORLD ” is visible on the aircraft, consistent with Trans World Airlines branding.
A silver-haired captain in a dark uniform and peaked cap stands in a doorway or passage, looking forward with a calm, faint smile.
A small child with light hair then stands by a railing in front of the aircraft, raising one hand in an excited wave.
The child ’s face is bright and animated, framed by the blurred structure of the terminal and airplane behind.
The final image opens to a starry sky above a glowing horizon, with clouds below and a red-tailed airplane entering from the lower left.
Centered across the sky in white capital letters is the on-screen slogan : “ LEADING THE WAY.
TWA. ” The plane continues along the lower left beneath the text, set against the deep blue, red, and gold colors of the horizon.

% matched lemmas: ceiling, computer, customer, employee, key, screen, sweater, urban, worker
\end{textsample}
