\begin{textsample}{POS Dim 1 – 2000 – Score 30.00 – 2000/tv\_com\_2000\_112.txt}  \label{ex:f1_pos_002}
The commercial \textbf{opens} on a very dark, almost unreadable frame.
It then cuts to a close \textbf{view} of a blonde woman in rainy weather holding a dark umbrella above her head.
The color palette is cold and bluish-gray.
She appears to be outdoors near \textbf{buildings}, and the weather looks \textbf{wet} and windy.
A \textbf{brief}, dark, blurry close-up follows, with water or rain visible but the subject unclear.
The scene \textbf{moves} \textbf{inside} a \textbf{car} : the windshield is covered with raindrops, and the wipers are \textbf{moving} across the glass.
A \textbf{driver} ’s hand is visible on the steering wheel.
The dashboard and front interior are shown from the passenger side. \textbf{Outside}, a dark Volvo station wagon/SUV-type \textbf{vehicle} is parked on a \textbf{wet} \textbf{street} beside \textbf{buildings}.
Its headlights and fog lights are on, and the driver-side door is \textbf{open}.
A person with an umbrella appears to be \textbf{getting} into or standing beside the \textbf{car}.
The \textbf{street} surface reflects the lights because it is \textbf{wet}.
The setting then shifts from the town to \textbf{open}, rugged landscapes. \textbf{Aerial} or high-angle shots show \textbf{winding} \textbf{roads} in a dark, stormy environment.
The Volvo \textbf{drives} along a rain-soaked \textbf{road}, throwing up spray.
The surrounding area appears mountainous or coastal, with heavy \textbf{clouds} and \textbf{mist}. \textbf{Inside} the \textbf{car}, the blonde woman is shown in the front passenger seat, while a man \textbf{drives}.
Both are seen in profile or three-quarter \textbf{view} through the dim interior light.
Their expressions appear serious or focused.
No spoken content is visible.
The \textbf{vehicle} \textbf{continues} across \textbf{open} terrain and along coastal \textbf{roads}. \textbf{Wide} shots show it \textbf{moving} through rain and spray near water and rocky shorelines.
The \textbf{car} ’s headlights remain on, and the \textbf{roads} look slick.
The landscape includes \textbf{cliffs}, waves, \textbf{rocks}, and dark \textbf{hills} under storm \textbf{clouds}.
Several shots emphasize the harsh environment : waves crash against dark \textbf{rocks}, sea foam splashes upward, and the \textbf{sky} remains overcast.
The Volvo is shown \textbf{driving} along a narrow coastal \textbf{road} bordered by \textbf{rocks} and water.
One shot shows it \textbf{approaching} from the front on a \textbf{wet} roadway.
A large, web-like or net-like object appears in the \textbf{road} ahead, covered in moisture.
The \textbf{car} \textbf{approaches} it.
Close-up shots \textbf{reveal} the object more clearly : it looks like a large sheet or mass of webbing stretched over something low on the ground, with strands clinging to a wheel-like or rounded form.
The exact object is unclear from the sampled frames.
The occupants are shown again through the windshield.
The woman looks ahead with a tense, concentrated expression ; the male \textbf{driver} is beside her, also focused forward.
Rain and reflections on the glass partially obscure their faces.
The \textbf{car} then appears near a rocky coastal area.
In one shot, the front grille or side of the Volvo is close to the camera while, in the \textbf{distance}, a small human figure stands or walks along the shore or \textbf{road}.
The scale and identity of the figure are unclear.
More shots show waves breaking violently over \textbf{rocks}.
A small dark object or figure appears amid the water in one \textbf{distant} frame, but it is too unclear to identify.
The commercial then cuts to a \textbf{wide} \textbf{view} of a stormy \textbf{sky} over a low horizon and a rocky shoreline.
The final frame displays centered white text over the storm-cloud background : “ VOLVO ” “ CROSS COUNTRY ” “ for life ” At the bottom, the \textbf{website} “ volvocars.com ” appears.

% matched lemmas: aerial, approach, brief, building, car, cliff, cloud, continue, distance, distant, drive, driver, get, hill, inside, mist, move, open, outside, reveal, road, rock, sky, street, vehicle, view, website, wet, wide, wind
\end{textsample}
