\begin{textsample}{POS Dim 1 – 2010 – Score 23.00 – 2010/tv\_com\_2010\_95.txt}  \label{ex:f1_pos_028}
The commercial begins with a black product-style screen showing an **Oculus Quest headset and two controllers** floating against a dark background.
Visible text reads **“oculus quest”**, **“from facebook”**, and an **ESRB Teen rating** icon.
It then cuts abruptly to a \textbf{driving} sequence.
A low, forward-facing \textbf{road} shot shows an \textbf{empty} multi-lane roadway or bridge stretching into a \textbf{rural} landscape with guardrails on both sides.
Small white disclaimer text appears at the bottom, but only partly legible ; it appears to refer to professional drivers/closed \textbf{course}.
A close-up follows of a **red \textbf{car} ’s spinning front wheel**, with a red brake caliper visible behind the rim.
The red bodywork fills the left of the frame.
The visuals shift through dark, blurred, high-speed shots : rows of bright lights in a dark setting, then fast-moving blurred \textbf{views} that appear to \textbf{pass} through or near a tunnel or shaded area, with bright daylight and trees flashing by.
The images are highly motion-blurred and the exact environment is unclear.
A calm landscape shot follows : rolling countryside with a row of tall, narrow trees lined up across a ridge, with \textbf{distant} \textbf{hills} or mountains in the background.
The front of a **red Alfa Romeo** is then shown in close-up.
The Alfa Romeo \textbf{badge} is centered on the grille, with glossy reflections across the \textbf{hood}.
The \textbf{car} appears to be \textbf{stationary} or \textbf{moving} slowly in this close frontal composition.
The commercial returns to \textbf{road} imagery : a curving \textbf{road} bordered by \textbf{hills} and vegetation, followed by close, abstract details of the \textbf{car}, including a blurred \textbf{exterior} surface and then a close-up of **dual circular exhaust pipes** at the rear.
Several shots emphasize sunlight filtering through trees.
The camera \textbf{moves} rapidly \textbf{past} trunks and branches, with strong glare and lens flare.
The sun appears low and bright, producing washed-out areas and purple/pink lens artifacts.
A frontal driving shot shows the red Alfa Romeo \textbf{approaching} on a narrow, wooded \textbf{road}.
Its slim headlights are on.
The \textbf{car} \textbf{drives} toward the camera through alternating patches of shade and intense sunlight.
Several frames are heavily overexposed by glare, briefly obscuring the \textbf{car} ’s details.
A side tracking shot then shows the red \textbf{car} \textbf{moving} \textbf{past} the camera, focusing on the side doors, wheel area, and glossy red paint. \textbf{Inside} the \textbf{car}, there is a \textbf{brief} blurred \textbf{view} of a \textbf{driver} ’s hand on or near the steering wheel.
The \textbf{driver} is not clearly visible, and no identifying details can be confirmed.
The setting widens to a scenic mountain landscape with bright sun, lens flare, and dark mountain silhouettes.
The \textbf{car} is not clearly visible in that \textbf{wide} shot.
Near the end, the camera tracks along the rear side of the red \textbf{sedan} as it \textbf{drives} on a \textbf{road} bordered by greenery.
The final frames show the rear of the \textbf{car} in close-up : red taillights, rear window, trunk surface, Alfa Romeo \textbf{badge} partially visible, and the \textbf{model} name **“GIULIA”** on the trunk.
A partial license plate is visible but not fully readable.

% matched lemmas: approach, badge, brief, car, course, distant, drive, driver, empty, exterior, hill, hood, inside, model, move, pass, past, road, rural, sedan, stationary, view, wide
\end{textsample}
