\begin{textsample}{POS Dim 1 – 2010 – Score 18.00 – 2010/tv\_com\_2010\_22.txt}  \label{ex:f1_pos_021}
The commercial opens inside a high-rise room, looking past a windowsill toward downtown buildings and a street far below.
On the sill sit small toys : two little metal \textbf{robot} figures at the left and a row of toy vehicles in red, yellow, and green.
The city outside is muted and realistic, with stone and brick buildings, while the toys in the foreground give the scene a childhood feel.
As the view shifts outward toward the street canyon, the toys slip out of attention and a large, flat, childlike cutout figure appears outside among the buildings, as if a drawing has come to life at giant scale.
At street level, \textbf{normal} city traffic and pedestrians continue through an intersection.
A cyclist rides across the road, cars and a bus wait or pass in the background, and red traffic lights hang overhead.
Into this ordinary scene drift pastel, paper-like fish shapes, outlined in crayon colors and casting faint shadows on the pavement.
A colorful hand-drawn train, made of boxy cars with crayon wheels and a cloud of cartoon smoke above it, rolls across the intersection from the right.
Its cars are decorated in bright pink, yellow, red, and blue.
Two adult men on the sidewalk pause and watch ; one \textbf{bald} man in dark clothes holds a bag at his side, while another man with a shoulder bag stands nearby.
The animated train continues away down the street as more floating fish glide past the \textbf{real} buildings and traffic.
The \textbf{fantasy} expands around a parked white \textbf{delivery} truck with a red stripe.
A man stands at the truck ’s open back door, and pedestrians walk on a stepped plaza nearby.
From around the truck rise more child-drawn cutouts : puffy white clouds, triangular rockets with colored windows, a blue \textbf{robot}, and a yellow sun.
They lift upward between tall office towers, filling the sky above the city.
The drawings have thick outlines and visible crayon or marker texture, as if made by a young child, but they move through the \textbf{real} \textbf{urban} space like enormous balloons or paper kites.
From above, rooftops and streets appear below while a huge smiling stick-figure person, drawn in red lines on white paper, stretches up between the buildings.
Its round head and long arms are much taller than the surrounding rooftops.
Nearby, a small blue-outlined cloud floats, and a yellow crayon rocket glides across the buildings.
The smiling figure reaches toward the cloud, then leans between the towers, still grinning, surrounded by other drifting paper clouds.
Another city block shows a tall, rectangular, paper-bag-like character standing above a low wall.
It has scribbled brown hair and a sad face, drawn with simple dark lines.
To the right hovers a child-drawn flying saucer with a white dome and yellow-green lights.
Bright yellow zigzag shapes suddenly flare around the sad character like comic-book energy or lightning.
The character ’s expression changes into a smile, and spring-like curls pop up over its head, turning the gloomy figure into a delighted one while the saucer remains in the sky.
A large purple monster-like drawing appears at the end of a street between rows of buildings.
It has a simple triangular body, a square window-like patch on its belly, skinny legs, and three long eye stalks with huge round eyes.
Pedestrians cross in front of it at a crosswalk, and cars line both sides of the street.
The creature ’s eyes and arms shift positions as it bobs along, then it drifts toward the right edge of the street while a \textbf{real} city bus passes behind the pedestrians.
A small crayon cloud floats overhead, reinforcing the mix of everyday downtown life and imaginary drawings.
More paper clouds move between tall glass-and-concrete towers, and a large blue \textbf{robot} drawing peeks from between the buildings.
The \textbf{robot} has a square face, blocky body, and simple blue outlines, with a pale blue scribbled torso.
White cloud cutouts float in the foreground and background, sliding through the vertical corridors formed by the skyscrapers.
The scene settles on a rooftop or elevated outdoor terrace in the middle of the city.
A white adult man, around middle age, sits alone on a black metal bench.
He has shoulder-length light brown hair, a full \textbf{beard}, and wears a dark business suit with a light blue shirt and a loosened patterned tie.
A dark bag rests on the bench beside him, and a takeaway \textbf{coffee} cup sits on the ground in front.
Behind the low concrete wall, downtown buildings fill the background.
One of the paper clouds floats past behind him.
He looks down toward his lap, calm and slightly tired at first, holding a small dark object near his hand.
As he remains seated, his expression softens.
In closer views, his head is bowed, then he raises his eyes a little and begins to smile gently.
Behind the wall, the purple three-eyed creature peeks up, its large round eyes appearing over the edge like a playful surprise, then its eye stalks bob and turn into rounded purple shapes as it passes behind him.
The final imagery changes from the \textbf{real} city into a clean, bright, abstract digital space.
Glossy, translucent blue bubbles float on a white background, surrounded by streams of small blue and white spheres arranged in sweeping spirals, like a flowing \textbf{network}.
Inside the bubbles are glimpses of communication and \textbf{media} : a wall of many \textbf{video} \textbf{screens}, a handheld \textbf{device} showing a \textbf{screen}, hands using a touchscreen \textbf{device}, a digital \textbf{interface} with pictures and \textbf{icons}, and a tablet or e-reader displaying a news-style page with a bold black title area at the top.
Smaller bubbles show additional images, including a tiny airplane silhouette and other \textbf{screens}.
The bubbles drift together in layered clusters, visually linking \textbf{phones}, tablets, \textbf{video}, news, and digital content in one \textbf{connected}, imaginative \textbf{network}.

% matched lemmas: bald, beard, coffee, connected, delivery, device, fantasy, icon, interface, medium, network, normal, phone, real, robot, screen, urban, video
\end{textsample}
