\begin{textsample}{POS Dim 1 – 1970 – Score 15.00 – 1970/tv\_com\_1970\_46.txt}  \label{ex:f1_pos_065}
The commercial unfolds as a fast, soft-focus \textbf{montage} of \textbf{urban} Italian-looking scenes, with frequent dissolves and color bleeding typical of an older video transfer.
A “ Classic Commercial Archives ” watermark appears at lower left, and a larger translucent archive watermark \textbf{runs} across the lower middle in many frames. 1. **Opening darkness** : The clip begins on a nearly black frame with only faint shapes visible and the archive watermarks. 2. **Establishing \textbf{city} view** : The image cuts to a green-blue tinted \textbf{street} scene.
Classical or monumental architecture is visible in the background, along with a tall streetlamp, trees, and parked or \textbf{passing} \textbf{cars}.
The picture is hazy and heavily color-tinted. 3. **Bright transition** : The next sampled moment is overexposed and washed out, as if during a dissolve.
Rooftop or \textbf{building} shapes are barely visible, but details are unclear. 4. **Fuel-station/street scene** : The \textbf{montage} \textbf{moves} to a busy outdoor scene with \textbf{cars} and people.
A small white \textbf{car} is at or near a fuel pump.
Several people stand around ; in the foreground, a man in a light coat or suit and a woman holding something like a booklet or papers appear to be looking down at it together.
Other figures and \textbf{vehicles} fill the background. 5. **City \textbf{street} with restaurants/shops** : Another dissolve \textbf{reveals} a \textbf{street} lined with \textbf{buildings} and storefronts.
A sign reading “ RISTORANTE ” is visible.
Multiple \textbf{cars}, including a white \textbf{car} and a red \textbf{vehicle}, are parked or \textbf{moving} along the \textbf{street}.
The frame has overlapping color trails from the transition. 6. **Restaurant or café \textbf{exterior} with car** : A white hatchback is parked on a narrow \textbf{street} \textbf{outside} a storefront with a decorative sign beginning with “ Le … ” or similar ; the full name is not fully clear.
There are awnings, plants, and a small table or display near the \textbf{entrance}.
A couple of people stand at the right side near the doorway. 7. **People in a dining/social setting** : The image dissolves into a close, layered shot of several men, likely seated at a table or in a café/restaurant setting.
They wear suits or dress shirts.
One older man in front is prominent, but the overlapping dissolve makes the exact activity unclear.
The scene suggests conversation or dining, though no audio or specific dialogue is visible. 8. **Public fountain/plaza** : The \textbf{montage} shifts to a broad plaza with a large sculptural fountain in front of ornate historic architecture. \textbf{Pedestrians} stand and walk around the fountain.
The setting looks like a European \textbf{city} square. 9. **Final product shot and text** : The final frame shows a white compact hatchback parked in front of the same fountain and historic \textbf{buildings}.
Large text appears over the scene : a blue **FIAT** logo at the top, followed by **“STRADA.
ANOTHER ITALIAN WORK OF ART.”** A price, **“\$4,303*”**, is shown prominently, with smaller fine print beneath it that is not fully legible in the frame.
The \textbf{car} is presented in profile as the central product image.

% matched lemmas: building, car, city, entrance, exterior, montage, move, outside, pass, pedestrian, reveal, run, street, urban, vehicle
\end{textsample}
