\begin{textsample}{POS Dim 1 – 2020 – Score 15.00 – 2020/tv\_com\_2020\_12.txt}  \label{ex:f1_pos_016}
An unfinished construction room appears, with raw \textbf{gray} walls, a dusty floor, exposed openings, and bright work lights on stands.
In the middle, a male-presenting construction \textbf{worker} stands in a blue hard hat, clear \textbf{safety} glasses, a yellow reflective vest over a \textbf{gray} hoodie, \textbf{jeans}, and work boots.
In front of him is a Bosch measuring \textbf{tool} mounted on a white tripod.
On the left wall, a rectangular opening or projected image shows another \textbf{worker} in a reflective vest raising an arm as if marking or checking a surface.
On the right, another \textbf{worker} in a hard hat and reflective vest kneels near materials and equipment.
The central \textbf{worker} looks down and steps toward the tripod-mounted \textbf{tool}.
A close view shows his hands fitting or adjusting a battery and controls on a gray-and-blue Bosch Professional laser \textbf{device} with red buttons and Bosch branding.
Small green indicator lights turn on.
The setting shifts into a darker, more dramatic version of the same construction space, with haze in the air and bright green laser lines running perfectly horizontal and vertical across the walls.
A dark-haired man with light-to-medium skin, stubble, and an athletic build stands in front of the laser, now dressed like a boxer in a shiny dark blue satin robe, white tank top, and large blue boxing gloves with white cuffs.
The green laser lines cut across the room behind him, one horizontal line passing around waist height and one vertical line rising near the tripod.
He faces forward and begins moving like a fighter, raising his gloves and bouncing in place.
As he turns away, the back of his robe reads “ THE LEVELER ” in large white letters.
An older male-presenting construction \textbf{worker} in a white hard hat, \textbf{safety} glasses, yellow reflective vest, plaid shirt, and green jacket appears in the dim construction area, holding a megaphone to his mouth as if calling instructions.
The boxer continues moving through the space between glowing green laser lines.
Another \textbf{worker}, wearing a blue hard hat, \textbf{safety} glasses, a yellow vest with orange stripes, and a tan jacket, stands near scaffolding and holds a metal drywall mud pan and a trowel.
He gestures with the trowel as if coaching or pointing out work to be done.
Throughout these scenes, the green laser grid remains visible across walls, poles, and openings, making the unfinished room look like a boxing ring marked out by light.
The boxer shadowboxes with focused intensity, his gloves up near his face.
Small white \textbf{legal} text appears along the bottom of several scenes, \textbf{stating} that range varies by product category and model, directing viewers to boschtools.com for specifications, and \textbf{noting} that \textbf{tools} shown are suitable for \textbf{indoor} use only. \textbf{Workers} in \textbf{high-visibility} vests stand behind him near wall openings and panels, watching or assisting.
The older man in the white hard hat moves in close like a cornerman, gently holding the boxer back and raising a hand in a calming gesture while the boxer lifts his gloves over his head.
The boxer then sits or crouches low, still wearing the robe and gloves, as the older \textbf{worker} leans in from the left and hands him a small black Bosch measuring \textbf{device}.
The \textbf{worker} in the blue hard hat leans in from the right, presenting a small strip of red-orange construction \textbf{supplies} or fasteners.
Green laser lines continue to run across the background.
The boxer stands again and holds the compact black measuring \textbf{device} up beside his face.
He looks at it, then turns toward a wall opening framed with metal and unfinished drywall.
A close view shows the handheld \textbf{device} pressed near the edge of the opening.
Its \textbf{screen} first reads “ 0.000 ft, ” then a red laser beam projects from it and the display changes to “ 6.000 ft. ” The boxer holds the \textbf{tool} steady against the wall while the \textbf{worker} in the blue hard hat stands nearby, looking on and gesturing toward the opening, as if helping mark or confirm the measurement.
The boxing \textbf{fantasy} continues.
The boxer faces a \textbf{worker} in a blue hard hat and \textbf{safety} glasses who is holding a large \textbf{gray} plastic container or bucket like a punching pad.
The boxer throws punches at it.
In a close view, the \textbf{worker} ’s mouth is open in an excited reaction as he braces behind the container.
The boxer lands a hit ; the container ’s lid flies off, and a burst of white spray or debris erupts dramatically into the air.
The \textbf{worker} raises one hand as if signaling or reacting, while the boxer follows through in a wide stance.
The green laser line remains visible across the back wall and along the equipment.
Near the end, the scene opens up to a product display.
On the left, a worktable holds several Bosch measuring \textbf{tools}, including rectangular laser \textbf{devices} and a handheld distance measurer, with Bosch red-and-black branding visible.
A tripod-mounted laser stands near the center, projecting bright green horizontal and vertical lines across the room.
The boxer, still in his blue robe and gloves, moves and punches on the right side of the room.
Bold white on-screen text appears beside the product display : “ THE MORE YOU BOSCH, ” followed by the longer line, “ THE MORE YOU BOSCH, THE MORE YOU FEEL LIKE A BOSCH. ” The final image is a clean white \textbf{screen} with the Bosch circular emblem and red “ BOSCH ” wordmark centered, and “ boschtools.com ” written below.

% matched lemmas: device, fantasy, gray, high-visibility, indoor, jean, legal, note, safety, screen, state, supply, tool, worker
\end{textsample}
