\begin{textsample}{POS Dim 1 – 1980 – Score 15.00 – 1980/tv\_com\_1980\_43.txt}  \label{ex:f1_pos_077}
The commercial \textbf{opens} with a low frontal \textbf{view} of a red Toyota coupe \textbf{driving} on a race track.
White on-screen text reads “ WILLOW SPRINGS RACE TRACK. ” The setting appears \textbf{open} and desert-like, with bright \textbf{sky} and a paved track.
The next shots establish a pit area beside a black-and-white checkered wall.
A large transporter or trailer in the background \textbf{carries} the text “ ALL AMERICAN RACERS ” and “ PIT CREW. ” Several crew members in white shirts, some wearing red caps, stand along the pit wall as the red \textbf{car} \textbf{approaches} and stops beside them.
The \textbf{car} is shown in side profile in front of the trailer.
Crew members \textbf{move} around it.
One crew member with a red cap leans near the rear of the \textbf{car}, while another stands with equipment.
A jack and other tools are visible near the checkered wall.
Close, quick shots show a crew member working near the \textbf{car}, a low \textbf{view} under the \textbf{car} with wheels and a jack or rolling tool, and a close-up of a wheel area being handled.
The commercial then cuts to the red Toyota from the rear as it \textbf{drives} away on the track.
The rear \textbf{badge} area clearly shows “ TOYOTA. ” This \textbf{driving} shot is followed by another close-up underneath the \textbf{car}, where a mechanic ’s hands work around mechanical components.
The editing alternates between pit-service imagery and track-driving imagery.
A sequence of track shots shows the red \textbf{car} speeding through a curve.
Some frames are blurred by motion, emphasizing rapid movement.
The \textbf{car} is seen from the rear and then from close low \textbf{angles} near the front wheel and side panel.
The landscape remains \textbf{open}, with \textbf{hills} or low mountains in the \textbf{distance} and strong sunlight.
Back in the pit area, a man in a white crew shirt holds a small handheld device near his face ; its exact function is unclear from the frames.
More close-ups show the front wheel area, the \textbf{hood} being raised or lowered, and the engine bay.
Another shot shows the interior : a helmeted \textbf{driver} in a white racing suit sits strapped into the \textbf{driver} ’s seat with a seat belt, while a crew member reaches into the \textbf{car} holding a cloth or paper.
The \textbf{car} is again shown near the pit wall, with crew members pushing or guiding it in the pit lane.
A close-up \textbf{inside} the \textbf{car} shows the helmeted \textbf{driver} from the chest up, wearing a white racing suit with visible Toyota-related patches and a dark helmet, looking forward while holding the steering wheel.
Near the end, the red Toyota is parked in front of the “ ALL AMERICAN RACERS ” trailer.
The \textbf{driver} stands beside the \textbf{car} wearing a helmet and racing suit, while several crew members gather around.
In the final frame, the crew members raise their arms in a celebratory pose around the \textbf{car}.
Large white text at the bottom of the screen reads “ TOYOTA. ”

% matched lemmas: angle, approach, badge, car, carry, distance, drive, driver, hill, hood, inside, move, open, sky, view
\end{textsample}
