\begin{textsample}{POS Dim 1 – 2020 – Score 23.00 – 2020/tv\_com\_2020\_88.txt}  \label{ex:f1_pos_035}
The commercial \textbf{opens} on a nearly black frame, with only a small faint shape visible at the left edge.
A blue Cadillac SUV is then shown in a \textbf{wide}, \textbf{open} desert landscape under a bright blue \textbf{sky}.
A person in a light-colored suit walks toward the \textbf{vehicle} from the left foreground.
The next shot pulls far back to an \textbf{aerial} \textbf{view} : the SUV and small human figures appear isolated in the vast sandy terrain.
Large white uppercase text stretches across the frame : “ ENTER ORDINARY. ” A closer shot shows the blue SUV from the front.
A person stands by the \textbf{open} driver-side door, partly \textbf{inside} or leaning against the \textbf{vehicle}.
The setting remains the \textbf{empty} desert.
The commercial then widens again to show the \textbf{car} and several figures in the \textbf{distance}.
One person in a bright red outfit stands out against the sand.
In the following closer shot, a person in a pale blue outfit \textbf{runs} or \textbf{moves} energetically near the blue SUV, while the red-clad figure performs a dramatic movement or dance gesture \textbf{nearby}.
The imagery shifts abruptly to a rotated or tilted shot : a red Cadillac appears at an unusual \textbf{angle}, with a person in a light beige outfit beside it.
The horizon and \textbf{vehicle} orientation make the shot look visually disorienting.
The setting appears to have changed from desert to a coastal or waterside environment.
A close shot from \textbf{inside} or near a \textbf{car} window shows a woman standing \textbf{outside}, with ocean water behind her.
She has short curly hair and wears a light cream outfit.
She reaches toward the \textbf{car} or window area.
A \textbf{brief} reflective/glare-filled shot follows, showing bright light and part of a \textbf{vehicle} surface or window, but the details are unclear.
The next \textbf{wide} shot \textbf{reveals} a red Cadillac positioned on a floating or platform-like surface surrounded by ocean.
A dancer in red is also on the platform.
The sea fills the background.
The dancer performs expressive arm movements beside the red \textbf{car}.
A closer shot shows a woman in a pink, textured or feather-like dress dancing in front of the red SUV, with the ocean and \textbf{sky} behind her.
The commercial then cuts to an \textbf{urban} rooftop or elevated concrete setting.
A woman in a cream outfit stands in front of an orange/red Cadillac, with a \textbf{city} \textbf{skyline} and mountains in the background.
She poses with one hand near her face.
Another shot is upside down : two people in light outfits stand beside the orange \textbf{car}, with the \textbf{city} \textbf{skyline} also inverted.
This \textbf{continues} the commercial ’s stylized, gravity-defying visual motif.
The scene then shows two women dancing beside the orange Cadillac on the rooftop.
One wears a pink outfit and the other a teal/green outfit.
Large white uppercase text overlays the image : “ BE VIBRANT. ” The following shot features the orange \textbf{car} ’s front grille and a person in a flowing green garment posing or dancing beside it.
Large white uppercase text reads : “ BE CONFIDENT. ” A black screen follows with centered white uppercase text : “ BE ICONIC. ” The commercial then transitions to a product-and-offer end card.
A white Cadillac \textbf{sedan} is parked in a rooftop or elevated \textbf{urban} setting at sunset, with mountains and a \textbf{city} \textbf{skyline} in the background.
The Cadillac logo appears at upper left, with the words “ \textbf{MOVE} UP ” below it.
At upper right, small white promotional text identifies the \textbf{vehicle} as a “ 2023 CT5 PREMIUM LUXURY AWD. ” Large pricing text reads “ \$499 PER MONTH ” and “ 39, ” indicating a 39-month offer.
Smaller fine print appears across the bottom but is too small to fully read in the sampled frames.
The final sampled frame fades to black.

% matched lemmas: aerial, angle, brief, car, city, continue, distance, empty, inside, move, nearby, open, outside, reveal, run, sedan, sky, skyline, urban, vehicle, view, wide
\end{textsample}
