\begin{textsample}{POS Dim 1 – 2020 – Score 23.00 – 2020/tv\_com\_2020\_96.txt}  \label{ex:f1_pos_037}
The commercial \textbf{opens} at \textbf{night} on a \textbf{wet} \textbf{urban} \textbf{street}.
The \textbf{pavement} reflects streetlights and neon-like lights from low \textbf{buildings}.
A dark \textbf{vehicle} is visible near the curb, and a person is seen \textbf{moving} across or along the \textbf{street}.
Small on-screen text at the bottom reads “ European \textbf{model} shown. ” The scene cuts closer to a dark blue/black BMW SUV parked beside a red \textbf{brick} \textbf{building} with barred windows and a vertical red light.
The \textbf{street} and sidewalk are damp.
Two people are visible as silhouettes : one stands near the front/driver-side area of the \textbf{vehicle}, while another \textbf{approaches} from the right side.
An overhead \textbf{view} then shows the BMW SUV leaving or \textbf{driving} along a narrow \textbf{wet} \textbf{street} beside the same \textbf{brick} \textbf{building}.
A small storefront or \textbf{entrance} with bright signage and colored rounded fixtures is visible on the corner.
The \textbf{vehicle} ’s headlights cast reflections on the \textbf{road} surface.
The “ European \textbf{model} shown ” disclaimer remains at the bottom. \textbf{Inside} the \textbf{vehicle}, there is a close-up profile of a male \textbf{driver} in dim lighting.
He has a beard and appears to be smiling slightly while looking ahead or toward the side.
The cabin background is dark and out of focus.
The \textbf{vehicle} is then shown driving through a tunnel or underpass.
The camera faces the front of the BMW as its headlights shine brightly, with white lane markings and tunnel walls \textbf{passing} by.
A small disclaimer appears at the bottom : “ All lights shown may not be available on all \textbf{models}. ” A closer moving shot focuses on the front end of the BMW, including the illuminated headlights and the kidney grille with the BMW \textbf{badge}.
The tunnel setting \textbf{continues}, and the same lighting disclaimer remains visible.
The next shot shows the rear of the BMW \textbf{inside} the tunnel.
The red taillights are lit, and the license plate reads “ TRM205. ” The BMW \textbf{badge} is centered above the plate, with \textbf{model} badging partially visible on the rear.
The commercial then transitions to a static end card over the nighttime \textbf{street} background.
Large white text advertises : “ Lease a 2022 BMW X3 xDrive30i ” and “ \$529 per month for 36 months, ” with additional smaller lease terms including an amount due at signing and an end date. “ BMWUSA.com ” appears on the left, along with a line directing viewers to “ BMWUSA.com/X3xDriveLeaseOffers ” for full details.
On the right side are the BMW logo and the “ alexa ” logo.
Fine-print \textbf{legal} text appears along the bottom but is very small.
The final sampled frame is a black screen.

% matched lemmas: approach, badge, brick, building, continue, drive, driver, entrance, inside, legal, model, move, night, open, pass, pavement, road, street, urban, vehicle, view, wet
\end{textsample}
