\begin{textsample}{POS Dim 1 – 2000 – Score 17.00 – 2000/tv\_com\_2000\_107.txt}  \label{ex:f1_pos_020}
The commercial unfolds as a fast-paced \textbf{travel} and adventure \textbf{montage}.
It \textbf{opens} with tilted, close-up shots of people in an active situation.
A young person in a gray-and-blue top is seen from above or at an \textbf{angle}, looking upward and extending a hand.
The next shots show a man ’s face in close-up, also looking upward with an intense or excited expression.
A black-gloved hand reaches down against a bright \textbf{sky}, while another bare hand reaches up toward it ; the hands come very close, though the sampled frames do not clearly show a grasp.
The scene then cuts to a large white cruise ship \textbf{moving} through blue water under a bright \textbf{sky}.
This is followed by an \textbf{aerial} \textbf{view} of a coastline with green vegetation, sandy beach, and blue ocean. \textbf{Inside} what appears to be a helicopter or small aircraft, a man points out through a window toward the sea below.
The \textbf{view} cuts to a sailboat seen from above on deep blue water.
A rapid sequence of water and outdoor activities follows : a person is seen against a bright \textbf{sky} ; then there are close-up splashing shots of a person in water.
Another shot shows blue-green water from above or underwater.
A small personal watercraft or jet ski \textbf{moves} across churning water with riders visible, followed by a \textbf{distant}, blurred silhouette of a rider on water against a bright horizon.
The \textbf{montage} shifts to more adventure imagery.
One shot shows people on or near a climbing/rope \textbf{structure} against a bright blue \textbf{sky}.
Then a person wearing an orange top, helmet, and backpack \textbf{moves} along a forest trail, likely on a bicycle or similar outdoor activity ; this is followed by close-up shots of helmeted people in the forest, their faces filling the frame as green foliage \textbf{passes} behind them.
A helicopter is shown flying low over the ocean near a sandy beach and surf.
Another shot shows a curved fishing rod silhouetted against a pale \textbf{sky} with \textbf{clouds}.
The final adventure sequence shows a climber on a steep, tan, rock-like wall or \textbf{cliff}.
The climber, wearing a harness or gear, \textbf{moves} across the textured surface in several consecutive shots, with a blue \textbf{sky} and architectural or \textbf{cliff} edges visible around the wall.
Near the end, the commercial returns to a \textbf{wide}, scenic shot of a large cruise ship on calm water at sunset or sunrise, with warm golden light and \textbf{hills} in the background.
On-screen branding appears : “ royalcaribbean.com, ” the Royal Caribbean International logo/name, and the tagline “ \textbf{Get} out there. ” The final sampled frame is black, indicating a fade-out or end screen.

% matched lemmas: aerial, angle, cliff, cloud, distant, get, hill, inside, montage, move, open, pass, sky, structure, travel, view, wide
\end{textsample}
