\begin{textsample}{POS Dim 1 – 1980 – Score 8.00 – 1980/tv\_com\_1980\_66.txt}  \label{ex:f1_pos_055}
The commercial opens in a bright, busy office made up of \textbf{gray} cubicles, desks, filing cabinets, framed prints, plants, and large windows along the far wall.
Several office \textbf{workers} move in the background.
In one cubicle, a woman with short dark hair, wearing a pale \textbf{sweater} and a patterned scarf, sits at a desk covered with papers, a \textbf{pencil} cup, an open book, and a \textbf{computer}.
She raises one arm high above the cubicle wall as if signaling to someone nearby.
As the scene shifts across the partitions, a young man in a striped dress shirt and dark tie is visible in a neighboring cubicle, seated at a cluttered desk with papers, an open book, and photographs pinned to the wall.
He reaches upward toward the top of the partition.
A hand lifts a small electronic \textbf{device} above the cubicle wall.
It is a compact gray-and-black rectangle, about the size of a large calculator, with a narrow display \textbf{screen} at the top, a miniature keyboard below, and a column of rounded buttons on the right side.
The man sits below with one arm still stretched up, looking toward the \textbf{device}, while his desk remains piled with work materials.
He appears to be involved in passing or reclaiming the \textbf{device} across the office partition.
Back at the woman ’s desk, she holds the \textbf{device} in both hands and smiles down at it.
Her cubicle has a \textbf{computer} \textbf{monitor} to her left, a desk lamp, a \textbf{pencil} holder, an open notebook, and personal items on the walls, including a small stuffed animal or toy figure and pinned pictures.
She looks comfortable and amused as she uses the \textbf{device}.
A close view of the product shows the label “ Spell-Checker ” above the display.
The \textbf{screen} first reads “ READY... ” while a \textbf{pencil} tip points near the display and \textbf{keys}.
Small white on-screen text at the bottom reads “ BATTERIES NOT INCLUDED. ” Fingers press the tiny black letter \textbf{keys}, and the display shows an entered approximation of a word, beginning with letters like “ AQ ” and then “ AQUIR, ” suggesting a phonetic or misspelled entry.
The \textbf{device} then shows “ SEARCHING. ” Another view shows the full unit in a hand, with the Texas Instruments logo and name printed on the right side.
A thumb presses one of the side buttons, illustrating the special function \textbf{keys}.
The display then shows spelling results such as “ ACQUIRABLE ” and later “ ACQUIRED, ” with small indicator text beneath the word.
The young man reappears, leaning around the edge of a cubicle partition into the aisle.
He has dark, full hair, a striped shirt, and a loose dark tie, and he looks toward the woman with a playful, expectant expression.
The woman turns toward him while holding the spell checker close to her chest, smiling.
He steps into her cubicle area and stands beside her desk, leaning forward with one hand on the desktop and gesturing with the other.
She remains seated, still holding the \textbf{device}, and looks down at it as if checking another word while he watches closely over her shoulder.
The \textbf{device} is then placed on a light wood desktop beside an open notebook with handwritten lines.
A small glass paperweight sits nearby.
The Texas Instruments Spell-Checker rests flat on the desk, its \textbf{screen} and keyboard clearly visible, with the “ Spell-Checker ” label on the left and “ Texas Instruments ” branding on the right.
A hand adjusts it, then withdraws, leaving the product centered as the focus of the scene.
Another hand reaches in from the left as if about to take it.
At the end, the woman and the young man are together at her desk.
She is seated, smiling broadly, while he leans over the desktop with both hands down, grinning.
The spell checker lies between them near the notebook and paperweight, presented as the object they have been sharing and using.

% matched lemmas: computer, device, gray, key, monitor, pencil, screen, sweater, worker
\end{textsample}
