\begin{textsample}{POS Dim 1 – 1970 – Score 18.00 – 1970/tv\_com\_1970\_4.txt}  \label{ex:f1_pos_061}
At first, the \textbf{screen} is filled with a dark green map of the northeastern and eastern United States.
Thin pale lines outline \textbf{state} borders, coastlines, and routes, while many small light dots are scattered across the map like cities or switching points in a communications \textbf{network}.
The map gradually reveals more of the country, including the Great Lakes, the Atlantic coast, and the Southeast.
An older, light-skinned man with \textbf{gray} hair appears in front of the huge wall map.
He wears a light \textbf{gray} suit, white shirt, and dark tie, presenting himself as a business or technical executive.
White on-screen text identifies him as “ Ian Ross, Executive V.P., Bell Labs. ” He stands upright in a large \textbf{professional} operations room, with the glowing map stretching across the entire back wall.
In front of him are long, curved control-room desks and consoles.
Several \textbf{workers} sit at these stations, partly seen from behind or in profile, with papers, telephones, and equipment spread before them.
As the view widens, the operations center becomes clearer.
The room is dim, lit mainly by the large wall displays and warm desk lights.
To the left is a large blank white board or projection \textbf{screen}.
Along the far left wall are tall vertical panels filled with many narrow illuminated strips or labels, suggesting status boards.
The gray-suited executive stands near the center, while \textbf{operators} at the curved desks read papers and work at consoles.
One person in the foreground leans over a desk ; another, wearing a light shirt, is seated to the right and appears to be writing or checking documents.
A \textbf{worker} carrying papers crosses through the foreground, briefly blocking part of the view, while the executive remains visible near the white board and map.
A close view of one of the tall status boards shows large yellow and white lettering on a dark background.
City names and routing labels are visible, including “ PITTSBURGH, ” “ CHARLESTON, ” “ CINCINNATI, ” “ CLEVELAND, ” and “ DETROIT, ” with numbers beside some names and the words “ SUB SECTION. ” Small square indicator blocks appear beside the lines of text, suggesting monitored telephone traffic routes or switching sections.
A \textbf{bearded}, light-skinned male \textbf{operator} in a white shirt and dark tie is shown at a console under reddish \textbf{lighting}.
He faces forward with a focused expression, framed by dark equipment on both sides.
His face is lit from below by the equipment, making his eyes and \textbf{beard} stand out.
He appears alert and intent, as if watching for a problem on the \textbf{system}.
The city-status board appears again, now closer on the \textbf{list} of locations and numbers.
Then the scene returns to the operations floor.
In the foreground, the \textbf{bearded} \textbf{operator} holds a telephone handset to his ear while seated at a console.
In front of him are dark monitor-like panels and a control surface with buttons or switches.
In the background, near the white board, the gray-suited executive stands with another man.
The second man appears to be a Black adult male in a light suit and patterned dark tie.
He faces the board while the executive gestures toward it, as if discussing a route or diagram.
A closer view of the two men at the board shows the executive reaching up and pointing or writing on the white surface with his right hand.
The Black colleague stands beside him, watching the board closely, his face serious and concentrated.
Behind them, the operations room remains dark, with clusters of tiny lights and display panels suggesting a large-scale \textbf{network} control \textbf{environment}.
Back at the console, the \textbf{bearded} \textbf{operator} lowers his attention to the controls.
He reaches forward with his right hand and adjusts or presses something on the equipment.
The console includes dark \textbf{screens} or panels on the left and a keyboard-like bank of rectangular black buttons below.
In close-up, his hand moves over several parallel rows of black \textbf{keys} with white labels.
He presses or slides between the controls in a deliberate sequence, visually demonstrating how traffic can be rerouted through the \textbf{system}.
After his hand lifts away, the rows of labeled \textbf{keys} remain in view.
A dark \textbf{computer} display appears next, filled with pale blue and white alphanumeric data.
Lines of numbers, abbreviations, and blocks of information run horizontally across the \textbf{screen}, like a technical readout for \textbf{network} traffic.
The city-status board returns once more, again highlighting the route names such as Pittsburgh, Charleston, Cincinnati, Cleveland, and Detroit.
The gray-suited executive is then seen standing among the consoles, facing forward.
He rests one hand lightly on the top edge of a curved workstation divider.
Behind him, the tall illuminated boards line the left side of the room, while the large wall map is visible in the background.
Around him, \textbf{operators} continue working : one person at lower left leans over papers and a telephone, and others sit at desks farther back on the right, surrounded by documents and equipment.
The room looks busy but orderly, with people \textbf{monitoring}, writing, speaking on \textbf{phones}, and using control panels while the executive remains calmly positioned in the center.
The final image fades to a dark green background with a stylized Bell System graphic made of small bright dots and curved repeating lines, resembling a glowing communications pattern.
Beneath it, white text reads, “ keeping your communications \textbf{system} the best in the world. ”

% matched lemmas: beard, bearded, computer, environment, gray, key, lighting, list, monitor, network, operator, phone, professional, screen, state, system, worker
\end{textsample}
