\begin{textsample}{POS Dim 1 – 2000 – Score 20.00 – 2000/tv\_com\_2000\_118.txt}  \label{ex:f1_pos_013}
The commercial begins with a \textbf{brief}, unrelated-looking shot of a group of performers indoors.
Several people in blue jackets and black outfits surround a woman standing behind a sign that reads “ DASANI. ” This appears only in the first sampled frame and is not visually connected to the later \textbf{car} sequence.
The scene then cuts to a nighttime \textbf{driving} sequence.
A silver \textbf{sedan} is shown in close-up from the front with bright headlights, \textbf{moving} through a dark, modern roadway or tunnel.
The camera \textbf{angle} is low and dynamic, emphasizing the \textbf{car} ’s grille, headlights, and motion.
A \textbf{wider} shot follows, showing the silver \textbf{car} \textbf{traveling} along a curved elevated ramp or enclosed roadway with white barriers and large structural columns. \textbf{Inside} another \textbf{car}, two young women are shown in the front seats.
The woman nearer the camera is slightly out of focus in the foreground, while the other woman is more visible ; both appear animated, with smiling or open-mouthed expressions.
The lighting is cool and dim, consistent with nighttime driving.
The silver \textbf{car} \textbf{continues} to be shown from the front in a tunnel-like environment, with blue-toned lighting.
Another interior shot shows three young men in a \textbf{car} : one at the wheel, one in the front passenger seat, and one in the back.
They are seat-belted, facing forward, and gesturing with their hands.
Their mouths are \textbf{open} in several frames, suggesting expressive interaction, though no audio content is visible.
A dark-colored \textbf{car} is then shown from a low front-side \textbf{angle}, its headlight bright against a \textbf{city} or parking-structure background.
Interior close-ups alternate between the male occupants and the two female occupants.
The male \textbf{driver} is shown in profile, focused forward, and the women are shown smiling or with \textbf{open} mouths while driving.
A direct front interior shot of one woman at the wheel shows her hand on the steering wheel and her face lit by \textbf{passing} lights.
A close-up of the rear of the silver \textbf{car} shows the Mitsubishi three-diamond emblem and the \textbf{model} name “ LANCER ” across the trunk.
The \textbf{car} is then shown in a tunnel from a low \textbf{angle}, \textbf{moving} forward with its headlights on.
Another interior shot of the male passengers shows the front passenger gesturing with his hand while looking ahead.
The silver Lancer is repeatedly shown driving through a bright, blue-lit tunnel or ramp system.
The camera cuts between \textbf{exterior} tracking shots, front-facing \textbf{views} through the windshield, and side \textbf{views} of the \textbf{car} \textbf{passing} structural columns.
In one \textbf{wide} nighttime shot, the roadway forms a large illuminated spiral or circular ramp against a dark \textbf{city} background.
Small white legal/disclaimer text appears along the bottom of this frame, but most of it is too small and blurred to read clearly.
Several transitional shots are abstract and blurred : bright overexposed shapes, indistinct light forms, and later red and beige vertical streaks.
These frames do not show clear people, \textbf{cars}, or readable text.
The \textbf{driving} sequence resumes with the three men \textbf{inside} the \textbf{car}, then a dark \textbf{car} \textbf{traveling} through a covered area with columns.
The men are again shown from the side/front, and the silver \textbf{car} is shown head-on in the tunnel with its occupants visible through the windshield.
The two women are shown again in the front seats, smiling or laughing visually, with the \textbf{driver} ’s arm extended toward the steering wheel.
Near the end, the silver \textbf{car} is shown from a low side \textbf{angle}, emphasizing the front wheel, headlight, and lane markings as it \textbf{moves} through the tunnel.
The final frames form the end card.
A roadway or tunnel recedes into the \textbf{distance} at \textbf{night}, and the Mitsubishi red three-diamond logo appears centered above white text reading : “ MITSUBISHI ” “ WAKE UP AND \textbf{DRIVE} ” A \textbf{website} appears below : “ 2002LANCER.COM. ” The last frame keeps the same branding while the background \textbf{angle} shifts along the tunnel wall.

% matched lemmas: angle, brief, car, city, continue, distance, drive, driver, exterior, inside, model, move, night, open, pass, sedan, travel, view, website, wide
\end{textsample}
