\begin{textsample}{POS Dim 1 – 1980 – Score 14.00 – 1980/tv\_com\_1980\_59.txt}  \label{ex:f1_pos_078}
The commercial begins with a static graphic that does not yet show a \textbf{car}.
On a dark background, white text reads “ Prince Superoni / Prince Ave. / Lowell, Mass. / 01853. ” A small portrait of a man appears in a rectangular inset at upper right, and a dark product package labeled “ SUPERONI ” is shown across the lower portion of the frame.
The scene then cuts to an outdoor \textbf{car} setting.
A light-colored hatchback or wagon is parked with its rear liftgate \textbf{open}.
An adult person stands near the \textbf{open} cargo area.
Large translucent block letters spelling “ NISSAN ” are superimposed across the center of the image.
Trees and daylight are visible in the background.
The following shots use heavy dissolves and overlapping images, making some details unclear.
A light-colored \textbf{car} is shown from the side under leafy trees, with reflections or double exposure effects over the body.
The camera then appears to \textbf{move} to the front/driver area of a \textbf{car}, with the windshield and dashboard area visible through layered imagery.
A person \textbf{inside} or near the \textbf{car} is partially visible, but the overlapping frames make their exact position unclear.
The commercial shifts to driving imagery.
A red \textbf{car} is seen on a \textbf{road} near a coastline or body of water, with \textbf{hills} or greenery in the background.
The \textbf{road} and scenery are sunlit.
This is followed by a close-up of a smiling adult male \textbf{driver}, seen through or reflected on a windshield, overlaid with an \textbf{exterior} \textbf{view} of a red \textbf{vehicle}.
He appears to be seated behind the steering wheel, though the layered dissolve makes the \textbf{view} partly ambiguous.
More \textbf{driving} footage follows.
A light-colored \textbf{car} is seen from the side on a \textbf{road} bordered by trees, again with a superimposed image of the \textbf{driver} ’s face and interior reflections.
The \textbf{montage} then shows a red sports \textbf{car} or coupe from a low, tilted \textbf{angle}, \textbf{driving} or cornering on a paved \textbf{road} with trees and hillside in the background.
The commercial ends on a black background with a large red “ NISSAN ” logo.
Beneath it, in white italic lettering, is the phrase “ MAJOR MOTION. ” A small Nissan \textbf{badge} or logo appears centered near the bottom.

% matched lemmas: angle, badge, car, drive, driver, exterior, hill, inside, montage, move, open, road, vehicle, view
\end{textsample}
