\begin{textsample}{POS Dim 1 – 2000 – Score 18.00 – 2000/tv\_com\_2000\_28.txt}  \label{ex:f1_pos_032}
A large Best Buy store fills the opening view, with a deep blue exterior wall and the familiar yellow price-tag-shaped “ BEST BUY ” sign mounted high above glass entrance doors.
In front of the building, a person in a giant Best Buy \textbf{tag} costume bounces and waves.
The costume is shaped like an oversized yellow price \textbf{tag} with thick black lettering, blue sides, white cartoon gloves, yellow sleeves, dark legs, and light-colored shoes.
Shoppers move around the entrance with carts ; one person pushes a blue shopping cart near the doors while the mascot gestures toward the store as if welcoming people inside.
The scene moves into the bright retail floor.
The \textbf{tag} mascot is seen up close, so close that the yellow “ BEST BUY ” lettering fills most of the view.
Around it are tall shelves, product displays, and \textbf{customers} under rows of fluorescent \textbf{ceiling} lights.
As the mascot turns, its blue back and thick padded sides become visible.
The store appears large and busy, with wide aisles, glossy black-and-white \textbf{flooring}, and \textbf{departments} arranged in long rows.
The mascot moves through the store like an enthusiastic host, passing shelves of electronics and music while shoppers browse.
In a wide aisle, the mascot dances down the center of the black-and-white floor.
On the right, several adults stand near displays ; one man in dark clothing raises an arm, and others watch or clap.
The mascot spins from showing its plain yellow back to showing the “ BEST BUY ” \textbf{tag} front again, arms spread wide with white-gloved hands open.
Its legs step wide apart in a jaunty, exaggerated dance while \textbf{customers} on both sides continue shopping or react with smiles.
A product demonstration follows at a camcorder display.
Two Black adult men, one in a dark suit and one in a green shirt, look at a small handheld \textbf{video} camera.
A young woman \textbf{employee} in a blue Best Buy shirt smiles as she helps.
The camcorder ’s flip-out \textbf{screen} and a nearby small \textbf{monitor} show a black-and-white image of the two men grinning at close range, demonstrating that the camera is recording or playing back their faces.
The \textbf{employee} holds or presents the camcorder while the men examine it, and the \textbf{monitor} beside them gives a clear view of the captured image.
In the appliance \textbf{department}, white washing machines or dryers are lined up beneath a visible sign reading “ APPLIANCES. ” A male \textbf{employee} in a blue \textbf{polo} shirt and khaki pants stands with a couple : a man in a dark shirt and \textbf{gray} pants and a woman in a tan outfit carrying a shoulder bag.
The \textbf{employee} opens or lifts part of a front-loading appliance door, showing the couple the machine ’s interior.
They stand close together, facing the product and the \textbf{employee}, in a typical sales consultation.
At a \textbf{computer} counter, a woman \textbf{employee} in a blue shirt speaks with a man in a dark dress shirt and patterned tie.
Several desktop \textbf{computers} and \textbf{monitors} sit on the counter behind them, with yellow Best Buy price cards visible on some \textbf{screens}.
The man gestures toward one of the \textbf{computers} while the \textbf{employee} leans comfortably on the counter, both focused on the display.
The view shifts to long aisles of music or \textbf{media}.
Rows of shelves hold CDs or similar packaged items, and blue signs above sections read “ ROCK \& POP. ” A young adult man in a \textbf{gray} \textbf{sweater} browses the shelves, holding a case and looking down as he checks the selection.
The aisle stretches far into the store, with multiple identical blue category signs and other shoppers partly visible between rows.
A small Best Buy \textbf{tag} sign is mounted at the end of one display.
In another electronics area, a Black male \textbf{employee} in a blue Best Buy \textbf{polo} talks with a woman in a loose green \textbf{sweater} near a large white appliance or electronics unit.
He gestures with one hand while she rests her hand on the counter or product surface, listening.
Behind them, more \textbf{employees} and \textbf{customers} examine rows of microwaves or similar boxed white appliances, and several overhead signs glow above the \textbf{department}.
At a black DVD display, large white letters spelling “ DVD ” appear above a built-in \textbf{screen}.
A man in a light \textbf{gray} shirt and a blonde woman in a dark jacket stand close to the display, discussing it.
The man holds a disc or small item in his hand while the woman leans in to look.
The \textbf{screen} shows a view of the store, including a glimpse of the blue-shirted staff and the Best Buy \textbf{tag} mascot.
As they watch, the yellow \textbf{tag} mascot appears in the display area, creating a playful visual connection between the product demonstration and the store mascot.
A bold yellow-and-black car audio display appears next.
The foreground is dominated by the glossy hood or body of a bright yellow vehicle with black racing stripes.
In the background, the Best Buy \textbf{tag} mascot stands upright near the display while \textbf{customers} and \textbf{employees} talk along a wall of car audio components.
A man leans into the open vehicle area, smiling and reaching forward as if testing or exploring the car stereo setup.
The mascot remains nearby, its yellow \textbf{tag} front visible behind him.
A young woman wearing large over-ear headphones smiles brightly while holding a CD jewel case against one side of her head.
She has dark hair pulled back with a headband, red lipstick, and a casual light-colored top.
She presses the headphones with both hands, tilting her head and smiling as if enjoying what she is sampling.
Store shelves blur behind her, suggesting she is in the music \textbf{department}.
Another couple examines a satellite or home entertainment display.
A middle-aged man in a red plaid shirt and \textbf{jeans} stands beside a woman in a light \textbf{sweater}.
They face a large white satellite dish mounted on a display.
The man gestures with one hand toward the equipment while the woman looks on.
A partial sign nearby reads “ NEED, ” though the rest is obscured.
A yellow Best Buy shopping basket then passes very close in the foreground, briefly blocking most of the view with its perforated plastic sides.
At the checkout or service counter, a Black female \textbf{employee} in a blue Best Buy shirt smiles while holding a small handheld scanner or \textbf{device}.
A male \textbf{customer} in a lavender shirt stands beside a yellow Best Buy shopping basket and looks down at an item or receipt in his hands.
The counter area has black-and-yellow signage and product displays behind them.
The \textbf{employee} and \textbf{customer} appear relaxed and friendly as they complete the transaction.
From above, a large circular yellow floor area is visible like a bright spotlight or central store feature.
Several shoppers and \textbf{employees} move around it, and the Best Buy \textbf{tag} mascot stands or moves along the left edge of the circle.
People cross the yellow area in different directions, some carrying items or baskets, while the mascot ’s blue side and yellow \textbf{tag} face are visible from overhead.
The scene emphasizes the busy store \textbf{environment}, with the mascot weaving among \textbf{customers}.
The commercial ends back outside the store.
The yellow “ BEST BUY ” sign is mounted high on the blue facade above the glass entrance.
Large white on-screen text appears at the lower right reading “ Now Open. ” The glass doors and windows below reflect the store entrance area, and a small copyright notice, “ {\EmojiFont ©} 2000 Best Buy, ” appears near the lower left.
The final image holds on the storefront, the big \textbf{tag} logo, and the “ Now Open ” \textbf{message}.

% matched lemmas: ceiling, computer, customer, department, device, employee, environment, flooring, gray, jean, medium, message, monitor, polo, screen, sweater, tag, video
\end{textsample}
