\begin{textsample}{POS Dim 1 – 2000 – Score 25.00 – 2000/tv\_com\_2000\_116.txt}  \label{ex:f1_pos_005}
The commercial \textbf{opens} in a pale blue clinical-looking office or examination room.
A younger man sits in a chair across a desk from an older man in a white shirt and tie.
The room contains medical-looking furniture, an examination table, cabinets, framed certificates, and wall-mounted images that resemble X-rays.
The camera cuts closer to the younger man, seated facing forward at the desk.
A glass of water sits in front of him.
He looks serious and still.
The \textbf{view} then cuts to the older man behind the desk, with papers, a pen, and office items spread out in front of him.
He appears to be addressing the younger man, though no speech is visually indicated.
The camera returns to a tighter close-up of the younger man, whose expression looks tense or uncertain.
The setting then shifts abruptly to a blue-tinted \textbf{car} interior.
The same younger man is now seated in the \textbf{driver} ’s seat, smiling broadly.
A quick close-up shows a printed page or document with a Mercedes-Benz logo at the top and a structured layout of text and boxes, though most of the text is not readable.
A sequence of driving and lifestyle images follows.
A silver Mercedes-Benz \textbf{sedan} is shown \textbf{driving} through a \textbf{city} \textbf{street} lined with tall \textbf{buildings}.
The man is seen again \textbf{inside} the \textbf{car}, hands on the steering wheel, looking relaxed and pleased.
Another low-angle \textbf{city} shot shows the \textbf{car} \textbf{passing} along a curb while \textbf{pedestrians} walk on the sidewalk.
A \textbf{distant} \textbf{skyline} appears across water under a clear \textbf{sky}.
The \textbf{montage} \textbf{continues} with leisure and \textbf{travel} imagery : people near water, a person stepping or jumping from a dock, and a shot involving the Golden Gate Bridge with the \textbf{car} and \textbf{driver} visible in the foreground.
The silver \textbf{sedan} is shown parked beside a waterfront while the man, in a suit, stands on top of the \textbf{car} roof holding something to his face, possibly binoculars or a camera, though the object is not fully clear.
The \textbf{car} then \textbf{drives} across a large steel bridge.
The visuals shift again to a beach or coastal setting.
The same man appears bare-shouldered, smiling while \textbf{moving} along a shoreline.
A \textbf{wider} shot shows dunes, \textbf{grasses}, and the ocean.
The silver Mercedes \textbf{sedan} is then shown driving on an \textbf{open} \textbf{road} or bridge under a bright blue \textbf{sky}.
Near the end, the man appears again \textbf{inside} the \textbf{car}, now bare-shouldered, looking forward with a calmer expression.
The commercial ends on a black title card with the Mercedes-Benz three-pointed star logo, the text “ Mercedes-Benz, ” and the large line “ The C-Class starts at \$29,950. ” A \textbf{website} address appears at the top, and small \textbf{legal} fine print \textbf{runs} along the bottom, but most of the fine print is too small to read clearly.

% matched lemmas: building, car, city, continue, distant, drive, driver, grass, inside, legal, montage, move, open, pass, pedestrian, road, run, sedan, sky, skyline, street, travel, view, website, wide
\end{textsample}
