\begin{textsample}{POS Dim 1 – 2020 – Score 17.00 – 2020/tv\_com\_2020\_99.txt}  \label{ex:f1_pos_007}
A young woman with short dark hair sits in a dim, warm room, wearing a loose, bright red top, black leggings, dark \textbf{sneakers}, silver necklaces, bracelets, and small hoop earrings.
Her face is softly lit as she looks down in concentration.
In front of her on a small round table is a thin \textbf{laptop} displaying the Windows 11 blue swirl wallpaper.
She reaches toward the \textbf{laptop}, and the centered Windows-style Start \textbf{menu} appears on the \textbf{screen} as a rounded white panel filled with app \textbf{icons}.
When her hand moves again, the \textbf{menu} closes, returning to the blue wallpaper.
The setting shifts into a glossy, dreamlike blue corridor made of rounded rectangular shapes, as if the woman has stepped into the \textbf{computer} itself.
She appears small at first, still in her red top, moving forward through the glowing space.
Floating translucent panels line both sides like suspended app tiles.
Recognizable logos and images include Xbox Game Pass, Reddit, Spotify, Facebook, TikTok, WhatsApp, Pinterest, and game or entertainment covers.
Tiny white text along the bottom reads, “ Apps and services sold separately. ” She walks calmly between the panels, then passes close to a colorful linked-loop \textbf{icon}, an Xbox Game Pass tile, and a “ Halo Infinite ” game cover.
She smiles and raises one hand as if greeting or touching the floating \textbf{icons}, then begins to run.
Her run carries her out into a vast, bright white desert of rolling dunes beneath a deep blue sky.
The red fabric of her top flutters behind her as she runs across the sand.
She slows and looks upward with a curious, slightly awed expression.
Far above the dunes, a sleek purple-blue futuristic aircraft with glowing lights on its wing tips sweeps through the sky.
A heavy green off-road vehicle with oversized tires races across the sand, throwing up dust.
The woman stands below, small against the wide desert, watching as an armored soldier in green futuristic battle gear appears near the vehicle.
The soldier, visually resembling the Halo character Master Chief, holds a large double-barreled weapon up toward the sky.
A bright projectile streaks across the blue, and a glowing burst blooms overhead.
The explosion transforms into a soft, colorful cloud of purples and pinks, opening like ink in water.
Inside that expanding cloud, translucent Windows 11 \textbf{interface} panels appear.
A large floating widget board materializes above the dunes, showing “ 11:11 AM ” at the top, a search bar, a weather card reading “ 55{\EmojiFont °}, ” and other cards such as calendar and to-do \textbf{lists}.
The woman gazes up at it, her expression calm and absorbed.
Her dark shoes sink slightly into the pale sand, emphasizing the surreal physicality of this digital landscape.
She drops downward into a grand, old-fashioned library or reading \textbf{hall}.
The space is tall and ornate, with multiple levels of balconies, shelves of books, columns, and a patterned black-and-white floor.
Overhead is a large mural-like image with dramatic figures and a bright central glow.
The woman falls or floats down through the high atrium, her red top billowing around her like a cape, and lands lightly near a white pedestal.
On the pedestal sits a closed book and a glowing purple chat-style \textbf{icon}.
A tiny green hummingbird darts over the surface and flies away from the pedestal, leading the view toward a huge arched opening in the library wall.
Through the arch is a peaceful lake landscape with green trees, misty blue mountains, and still water reflecting the scenery.
The woman now stands behind a large translucent panel in front of her, still inside the library space but visually connected to the outdoor lake scene.
The panel resembles a Microsoft Teams or chat \textbf{interface}.
Close-up text on it includes “ Open in Microsoft Teams, ” a group labeled “ Dance Team, ” and \textbf{messages} such as “ Kai : Great practice ” and “ Momoko Fujito : It ’s been too long! ” with small circular profile photos beside the names.
The hummingbird hovers near the panel.
Outside, a person sits in a small canoe on the reflective lake beside the tall transparent chat window, making the digital \textbf{messages} feel physically present in the natural landscape.
The imagery shifts underwater, with rippling blue light and shadowy movement, then returns to the woman in a dark blue, abstract space with the Windows 11 blue swirl pattern behind her.
She holds a dark blue, birdlike or origami-like shape close to her face, studying it gently.
The \textbf{lighting} is low and \textbf{cool}, with her face partly in shadow and blue highlights around her.
She turns her head, noticing a warm rectangular opening behind her.
Through that opening is a \textbf{real} dance studio or rehearsal room with tan paneled walls, polished wooden floor, wall sconces, and a simple wooden chair.
A male-presenting adult dancer with a shaved head, athletic build, and black fitted shirt and pants practices inside.
The woman watches him from the blue digital space as he moves near the chair.
The opening expands into a large screen-like rectangle on the studio wall ; the woman in red appears within the blue world inside it, while the dancer stands in the physical studio looking toward her.
Behind her, the blue digital space changes into a large painted mural filled with stylized dancers and musicians in bold reds, whites, and blacks.
The woman steps forward in front of the mural, her red outfit echoing the red dress painted behind her.
The dancer, positioned across the room, faces her with one hand behind his back.
They seem to meet through the boundary between the digital image and the studio.
She walks toward him with a composed, focused expression.
He turns toward her, and they stand close, facing one another in the warmly lit room.
The moment suggests connection and collaboration, with the digital portal having brought them together visually.
The commercial returns to the \textbf{laptop} on the small table in the dim room.
On its \textbf{screen}, the dancer is visible in the studio, and the Windows 11 taskbar is centered along the bottom.
A windowed \textbf{video} or communication \textbf{interface} opens beside the dance \textbf{video}, showing a smiling man in an outdoor setting at the top and a row of colorful thumbnails or tiles below.
The woman ’s hand rests near the keyboard as she looks at the \textbf{screen}, now back in her home \textbf{environment}, using the \textbf{laptop} to continue the connection that the earlier \textbf{fantasy} sequences visualized.

% matched lemmas: computer, cool, environment, fantasy, hall, icon, interface, laptop, lighting, list, menu, message, real, screen, sneakers, video
\end{textsample}
