\begin{textsample}{POS Dim 1 – 1970 – Score 16.00 – 1970/tv\_com\_1970\_63.txt}  \label{ex:f1_pos_063}
The clip begins with a television program title card reading “ GOOD MORNING AMERICA, ” with the ABC logo and the text “ 7am Weekdays ” visible beneath it.
The background is dark, and the title uses large white letters with colored circular graphics.
The scene then cuts to a close, somewhat blurry \textbf{view} of part of a bicycle and a person \textbf{nearby}, showing yellow and black bike components.
The image is tight and indistinct, but it suggests preparation or display of a bicycle.
Next, the commercial \textbf{moves} outdoors to a desert or \textbf{canyon} landscape.
A brown/orange van is parked on a dirt area.
Two bicycles with yellow wheels are visible near the van, and people appear to be handling or standing near the bikes.
The background includes rocky formations and scrub vegetation.
Two riders are then shown cycling along a \textbf{wide} dirt \textbf{road} in the same desert setting.
They \textbf{ride} side by side or close together, wearing casual clothing.
The \textbf{road} is \textbf{open}, with low vegetation and \textbf{distant} \textbf{hills}.
A close-up follows of a rider ’s foot in a white sneaker pedaling a black-and-yellow bicycle.
The camera emphasizes the crank, pedal, chain area, and yellow wheel rim as the bike \textbf{moves}.
The next shot shows a rider \textbf{traveling} left to right across the frame, with a rocky wall or \textbf{cliff} face behind him.
The bicycle again has yellow wheels, and the rider wears a red-and-white top and jeans.
A frontal shot then shows a young male rider cycling toward the camera on a dirt \textbf{road}.
He wears a white shirt with red sleeves, blue jeans, and white shoes.
The handlebars and front of the bike are visible, with desert mesas and blue \textbf{sky} behind him.
The commercial cuts to an adult man sitting on top of the van.
He wears a plaid shirt, jeans, and a dark cap or hair, and appears to be gesturing with his hands.
The \textbf{sky} and desert \textbf{hills} are visible behind him.
A \textbf{wide} scenic landscape shot follows, showing a broad desert valley with scattered shrubs and \textbf{distant} mountains or mesas.
No people or bicycles are clearly visible in this shot.
The riders then reappear on a dirt \textbf{road}, seen from behind.
One cyclist \textbf{rides} in the foreground, while the van \textbf{drives} ahead on the \textbf{road}.
The \textbf{canyon} landscape \textbf{continues} in the background.
Another action shot shows two cyclists \textbf{riding} through a shaded or darker area, possibly near trees or \textbf{rock} formations.
The image is somewhat blurred, but the riders and yellow-wheeled bikes are visible.
The commercial then cuts to a product display on a plain studio background.
A black-and-yellow bicycle is shown in profile, standing on a kickstand.
Large yellow block text at the top reads “ PRO THUNDER 4. ” Near the end, there is a graphic transition with a blue gradient background and a dark reflective lower area.
A partial bicycle or wheel briefly appears at the right edge before \textbf{moving} out of \textbf{view} or being cropped.
The final frame shows a brand end card.
The text reads “ Building the bikes America likes. ” above a large “ HUFFY ” logo.
Along the bottom, smaller text reads “ WHEEL STYLE MAY VARY. ” The background remains a blue gradient with a reflective dark lower portion.
A “ Classic Commercial Archives ” watermark is visible in the lower-left corner throughout much of the clip, with an additional faint archive watermark across the lower center.

% matched lemmas: canyon, cliff, continue, distant, drive, hill, move, nearby, open, ride, road, rock, sky, travel, view, wide
\end{textsample}
