\begin{textsample}{POS Dim 1 – 1960 – Score 16.00 – 1960/tv\_com\_1960\_114.txt}  \label{ex:f1_pos_056}
The commercial is presented in black and white and unfolds in a snowy outdoor setting. - It \textbf{opens} with a high-angle \textbf{view} of a large \textbf{sedan} stopped or \textbf{moving} slowly on a snow-covered \textbf{road} or driveway.
Small evergreen trees and snowbanks surround the \textbf{car}.
The \textbf{vehicle} has visible snow on and around it. - The scene cuts \textbf{inside} the \textbf{car} to a woman seated at the steering wheel.
She is wearing winter clothing, including a coat and gloves.
She looks composed and focused on \textbf{driving}.
The \textbf{car} interior, steering wheel, dashboard area, and side windows are visible. - A rear-seat \textbf{view} follows, showing two children bundled in winter hats and coats.
Snow is piled along the \textbf{outside} edge of the \textbf{car} window.
The children appear animated and cheerful, looking forward and toward each other. - The commercial then shifts to close-ups of the \textbf{car} ’s side and wheels in the snow.
One shot shows a front or side wheel area partly buried in snow, with the tire close to the snowy ground. - The children appear again through the side window.
They smile and look outward from the back seat, still framed by snow along the window edge. - A \textbf{wider} \textbf{exterior} shot shows the \textbf{car} on a snowy incline or roadside, with a tow \textbf{truck} or service \textbf{vehicle} positioned behind or near it.
The service \textbf{vehicle} has a boom or lifting apparatus, though the exact connection to the \textbf{car} is not clearly visible in the sampled frame. - Several later shots focus closely on the tires.
The wheel is shown pressing into deep snow, with the whitewall tire and hubcap visible.
Snow is churned up around the tire, suggesting movement or traction effort. - Another overhead/exterior \textbf{view} shows the \textbf{car} in snow with the tow/service \textbf{vehicle} \textbf{nearby}.
The \textbf{car} appears to be progressing or positioned along a snowy track, though the sampled frames do not make the exact motion fully clear. - The tire close-ups \textbf{continue}, showing the tire cutting through snow and leaving a disturbed track.
One frame isolates a dark zigzag tread pattern impressed into a lighter surface, visually emphasizing tire tread marks. - Additional close-ups show the wheel rolling or pushing through snow, with snow displaced around the tire and under the \textbf{car} ’s lower body. - The commercial ends with a large circular roadside sign bearing the word “ Gulf ” in bold letters across the center.
The sign is shown against a plain \textbf{sky} background and remains on screen through the final frame.
A visible “ OsbornTramain ” watermark appears in the lower-right corner of many frames.
No dialogue, music, or spoken claims are visually available in the sampled frames.

% matched lemmas: car, continue, drive, exterior, inside, move, nearby, open, outside, road, sedan, sky, truck, vehicle, view, wide
\end{textsample}
