\begin{textsample}{POS Dim 1 – 1970 – Score 16.00 – 1970/tv\_com\_1970\_41.txt}  \label{ex:f1_pos_064}
The sampled frames show a commercial sequence centered on an orange/red Toyota \textbf{car}, after an opening television-program graphic. 1.
The clip begins with a dark screen containing a television-style promo graphic.
Large text at the top reads “ CBS SUNDAY. ” \textbf{Inside} the graphic is a close-up of a blond man.
Additional text near the bottom appears to say “ CBS SUNDAY \textbf{NIGHT} MOVIE ” and “ STARTS 9:00/8:00, ” though some details are blurry. 2.
The scene changes to an orange/red \textbf{car} seen from the front, \textbf{driving} or positioned on a roadway in an \textbf{open} rural-looking area.
The background is flat and pale, with fields or low vegetation. 3.
A side \textbf{view} shows the same orange/red \textbf{car} \textbf{traveling} along a \textbf{road}, with blurred countryside behind it.
The \textbf{car} is a two-door style with a sloping rear. 4.
The \textbf{car} is then shown in a \textbf{residential} \textbf{street} setting, \textbf{passing} or parked near a white house with a porch, a picket \textbf{fence}, and bare tree branches.
The camera \textbf{angle} is low and front three-quarter, emphasizing the \textbf{car} ’s front grille and headlights. 5.
A close-up of the \textbf{car} interior appears.
The dashboard, steering wheel, instrument panel, center controls, and gear shift are visible.
No \textbf{driver} is clearly shown in this frame. 6.
The \textbf{car} is shown again from the front in the \textbf{residential} area, near a white \textbf{fence} and house.
The headlights, grille, windshield, and \textbf{hood} are prominent. 7.
A close side/rear \textbf{view} shows the \textbf{car} near a roadside \textbf{fence} in an \textbf{open} landscape.
The camera is close to the passenger-side window and rear quarter area. 8.
The \textbf{car} is shown from a low front-left \textbf{angle} on a \textbf{road} or gravel surface in a bright \textbf{open} setting.
A person appears to be \textbf{inside}, but details are not clear. 9.
Two people, a man and a woman, stand beside the \textbf{car}.
The man has curly hair and wears a jacket over a light shirt.
The woman has dark hair and smiles ; she wears a light turtleneck and jacket.
The \textbf{car} roof or window frame is visible in the foreground. 10.
The final frame shows the orange/red \textbf{car} parked near a modern-looking \textbf{building} on a gravel or dirt area.
The rear hatch or trunk is \textbf{open}, and the two people stand near the back of the \textbf{car} with luggage or cargo visible.
Large white text at the bottom reads “ TOYOTA, ” with smaller text underneath that is difficult to read clearly.
The overall image has visible archival color distortion and a “ Classic Commercial Archives ” watermark.

% matched lemmas: angle, building, car, drive, driver, fence, hood, inside, night, open, pass, residential, road, street, travel, view
\end{textsample}
