\begin{textsample}{POS Dim 1 – 1980 – Score 15.00 – 1980/tv\_com\_1980\_86.txt}  \label{ex:f1_pos_074}
The sampled sequence begins with a static product-style image unrelated to the later desert scene : three Wesson oil bottles are shown against a plain background, with measuring spoons attached or displayed near the bottles.
Large text at the bottom reads “ FREE MEASURING SPOONS. ” No movement is visible in this frame.
The commercial then cuts to an outdoor desert setting.
A close shot shows the lower torso and legs of a man wearing dark jeans, standing in a dry, \textbf{open} landscape.
The next shot is a high, \textbf{wide} \textbf{view} of a long, straight two-lane \textbf{road} \textbf{running} through desert scrub and low \textbf{hills}.
A small human figure stands near the roadside, emphasizing the isolated setting.
The man is then shown full-body at the roadside.
He wears a white short-sleeved T-shirt, dark jeans, and boots.
He stands with his arms crossed, backlit by warm sunlight, with \textbf{hills} and brush behind him.
A dark \textbf{vehicle} \textbf{passes} very close across the foreground, partially obscuring him and creating a blur of motion.
Dust or glare fills the frame briefly as the \textbf{car} \textbf{moves} \textbf{past}.
A close-up of a \textbf{car} wheel follows, showing a dark sports \textbf{car} ’s tire and alloy rim near the \textbf{road} surface.
A \textbf{wider} shot then shows the black sports \textbf{car} stopped or slowing on the \textbf{road}, with the man standing on the shoulder to the right, looking toward it.
He shifts posture in the next shot, standing at the roadside with his hands near his pockets, still in the desert light. \textbf{Inside} the \textbf{car}, there is a close-up of dashboard or console controls, including buttons and knobs.
A finger or hand is near one of the controls, but the exact action is not fully clear.
A soft, reflective close-up then shows a woman ’s face through or near a \textbf{car} window, partly obscured by glare.
She has long dark hair and is seated \textbf{inside} the \textbf{car}.
The man leans down toward the \textbf{car} window from \textbf{outside}, seen from the woman ’s perspective or through the \textbf{car} opening.
He appears to be looking into the \textbf{vehicle}.
The woman turns and looks toward him from the \textbf{driver} ’s side or front seat area.
Alternating close-ups show the man leaning in and the woman looking back at him.
Their expressions are calm and mildly engaged ; she gives a slight smile in one close-up.
No spoken content is visible or inferable from the frames.
A side \textbf{view} then shows the black sports \textbf{car} in profile on the desert \textbf{road}, with the low \textbf{hills} and warm \textbf{sky} behind it.
The final frame returns to the man outdoors in the desert landscape, bent slightly forward near the roadside.
Large white text appears across the top of the frame reading “ BUGLE BOY JEANS. ”

% matched lemmas: car, driver, hill, inside, move, open, outside, pass, past, road, run, sky, vehicle, view, wide
\end{textsample}
