\begin{textsample}{POS Dim 1 – 2000 – Score 13.00 – 2000/tv\_com\_2000\_39.txt}  \label{ex:f1_pos_036}
The commercial opens inside a bright Sears appliance showroom.
Five Sears \textbf{employees} stand together in a confident, posed lineup beneath a large blue-and-white “ Sears ” sign.
They wear work attire in Sears blue : mostly royal blue \textbf{polo} shirts with name badges or lanyards, along with black pants.
Two men at the left wear lighter blue button-down shirts.
The group includes men and women of different appearances ; one woman with dark hair stands near the center with her hands on her hips, and another woman with red hair stands at the far right in the same hands-on-hips pose.
Behind them are rows of appliances and overhead fluorescent lights, giving the store a clean, polished retail look.
A blue-white glow washes over the group, turning them into darker silhouettes as the scene shifts into a graphic title card.
Their silhouettes remain grouped on the left, casting long shadows across a white background.
Large bold blue text appears beside them : “ Sears BLUE APPLIANCE CREW, ” with “ BLUE ” especially large and prominent.
The action moves back into the appliance \textbf{department}.
A casually dressed male \textbf{customer}, about young to middle-aged, with short dark hair, a \textbf{gray} zip hoodie, olive T-shirt, \textbf{jeans}, and \textbf{sneakers}, walks toward a Sears \textbf{employee} in a blue \textbf{polo} shirt.
They meet near a tall blue-and-white kiosk labeled “ Sears Research Center. ” A \textbf{computer} \textbf{monitor} sits on the kiosk counter.
Around them are front-loading washers and dryers in glossy colors, including teal, red, dark blue, silver, and white.
A hanging sign also reads “ Sears Research Center, ” reinforcing that this is a service area inside the store.
The \textbf{customer} is shown closer, speaking with a thoughtful, slightly concerned expression.
Behind him, the store remains bright and orderly, with appliance displays and blue Sears \textbf{department} signs visible in the background.
He faces the \textbf{employee} as if explaining what he needs.
A product display highlights a matching pair of dark blue LG front-loading laundry machines.
They sit side by side, each with a round chrome-trimmed door and the “ LG ” logo clearly visible on the glass.
Their glossy finish reflects the store lights, presenting them as the appliance pair under discussion.
Back at the Sears Research Center, the \textbf{employee} in the blue Sears \textbf{polo} talks with the \textbf{customer}.
The \textbf{employee} stands open and attentive, wearing a lanyard and badge, while the \textbf{customer} faces him with his hands near his sides.
The \textbf{employee} then steps to the kiosk \textbf{computer} and begins using the mouse or keyboard.
The \textbf{customer} stands beside him watching.
The \textbf{monitor} is angled toward them, and the blue “ Sears Research Center ” sign remains directly above and beside the workstation.
In the background, another blue-shirted Sears \textbf{employee} assists near red laundry machines.
As the \textbf{employee} works at the \textbf{computer}, he turns his head and gestures off to the side, drawing the \textbf{customer} ’s attention away from the kiosk.
The \textbf{customer} follows his look.
The scene cuts to a comic-looking area inside the Sears store, set up near the front doors under another large “ Sears ” sign.
A ping-pong table stands in the middle, with several casually dressed men around it.
One man in a striped \textbf{polo} shirt stands behind the table, while another man in a light striped shirt is positioned at the right as if playing.
The original \textbf{customer} in the \textbf{gray} hoodie stands at the left edge, watching.
Blue rope barriers on metal stanchions separate this area from the rest of the showroom, and appliances are displayed along the sides.
A \textbf{couch} or seating area sits to the left, adding to the feeling that these men have been waiting or killing time inside the store.
The view returns to the \textbf{customer} and the Sears \textbf{employee} at the Research Center \textbf{computer}.
The \textbf{employee} has turned back toward the \textbf{customer}, while the \textbf{monitor} behind them shows a webpage-like layout with product images and text, suggesting comparison or research information.
The \textbf{customer} looks toward the \textbf{employee}, appearing reassured or impressed.
A closer view isolates one of the men from the ping-pong area : a middle-aged man with short thinning hair and glasses, wearing a blue-green striped \textbf{polo} shirt.
He stands in front of Sears-branded glass doors, looking downward with a tired or resigned posture, visually contrasting with the quick help the main \textbf{customer} is receiving.
A clean white graphic card appears.
At the top, large gray-blue text reads, “ WE DO THE WORK. ” Near the lower right, the silhouetted Sears Blue Appliance Crew stands beside the bold “ BLUE CREW ” graphic.
Small \textbf{fine} print near the bottom left says to see the store for guarantee terms and conditions.
The \textbf{promotional} offer follows on another white card.
Large text reads, “ 20 \% OFF TOP BRANDS ” and beneath it, “ 10 \% OFF ALL OTHER BRANDS. ” Brand logos appear above a lineup of appliances, including a stainless refrigerator, a stove or oven range, and a front-loading washer and dryer. \textbf{Fine} print runs along the bottom, with a larger line reading, “ FOR FULL OFFER SEE SEARS.COM. ” The commercial ends on a mostly white \textbf{screen} with the blue “ Sears ” logo centered and “ SEARS.COM ” printed near the lower right.

% matched lemmas: computer, couch, customer, department, employee, fine, gray, jean, monitor, polo, promotional, screen, sneakers
\end{textsample}
