\begin{textsample}{POS Dim 1 – 2010 – Score 24.00 – 2010/tv\_com\_2010\_43.txt}  \label{ex:f1_pos_025}
The commercial \textbf{opens} in a bright \textbf{suburban} driveway \textbf{outside} a beige house.
A small mint-green Fiat 500 is parked on the driveway.
A man stands to the left near the \textbf{car}, while a young woman in a pink cardigan, light blue shirt, and light pants comes from the house toward the \textbf{car}.
The lawn, porch, windows, and plants make the setting look \textbf{residential} and well kept.
The next shots focus on the man in the driveway area, standing near hedges and smiling broadly, and then on the young woman \textbf{approaching} the mint-green \textbf{car}.
She looks pleased and animated as she reaches the front passenger-side area of the \textbf{car}.
A closer shot shows her smiling at the \textbf{vehicle}, with the house porch behind her.
The scene then cuts sharply to a \textbf{different} \textbf{location} : an urban/industrial \textbf{street} or parking area under or near an overpass.
A black \textbf{sedan} is shown in a parking space, but it is badly stripped : the wheels are missing, the \textbf{car} rests on blocks, and the front bumper/grille area is removed or incomplete.
A man in a gray suit stands \textbf{nearby}, looking toward the damaged \textbf{car}.
The background includes \textbf{brick} and \textbf{industrial} \textbf{buildings}, a stop sign, \textbf{traffic}, and stacked pallets.
Another \textbf{brief} shot shows an older man wearing glasses and a green apron standing in a red-brick doorway, holding a cloth or towel.
He appears to be watching from the doorway near trash bags and dumpsters.
The commercial then returns to the stripped black \textbf{car} and the suited man, who gestures with his hands in apparent frustration or disbelief.
The ad intercuts between the two situations : the \textbf{suburban} driveway with the intact mint-green Fiat and the young woman ’s delighted reaction, and the \textbf{urban} scene with the stripped black \textbf{sedan} and the suited man ’s agitated gestures.
The driveway man is also shown smiling near the mint-green \textbf{car}.
The older apron-wearing man is shown again in the \textbf{brick} doorway, appearing to speak or react, though no audio is available.
As the intercutting \textbf{continues}, the young woman near the Fiat becomes more visibly excited, smiling and then laughing with her mouth \textbf{open}.
The suited man by the stripped \textbf{car} gestures emphatically, raising and \textbf{moving} his hands as he faces the \textbf{vehicle}.
The black \textbf{sedan} remains \textbf{stationary} on blocks throughout these shots, with visible missing wheels and front parts.
Near the end, the setting changes to the \textbf{entrance} of a State Farm office.
A man in the plaid shirt enters or \textbf{approaches} a glass doorway with a red “ StateFarm ” sign visible \textbf{inside}.
In the next \textbf{exterior} shot, the plaid-shirted man and the young woman are \textbf{outside} the glass-fronted office near a ramp and railing.
The red State Farm signage is visible through the windows.
The final frame is a solid red screen with centered white text reading : “ Here to help life go right. ” A small line of fine print appears near the bottom, but it is too small to read clearly in the sampled frame.

% matched lemmas: approach, brick, brief, building, car, continue, different, entrance, exterior, industrial, inside, location, move, nearby, open, outside, residential, sedan, stationary, street, suburban, traffic, urban, vehicle
\end{textsample}
