\begin{textsample}{POS Dim 1 – 2020 – Score 15.00 – 2020/tv\_com\_2020\_70.txt}  \label{ex:f1_pos_015}
The commercial takes place inside a bright, tidy AT\&T retail store with blue accent walls, pale wood display tables, shelves of \textbf{phone} accessories, and the AT\&T logo glowing above glass entrance doors.
A white-haired, \textbf{bearded} man, appearing middle-aged to older, stands near the center of the store wearing a dark jacket over a green shirt and dark pants.
At the right, a female-presenting store \textbf{employee} with a short brown bob stands behind a light wood service counter, wearing a light blue AT\&T \textbf{button-up} shirt with a name \textbf{tag} and holding or standing behind a tablet.
White text along the bottom reads, “ This ad was made safely.
Please wear a \textbf{mask} in our stores. ” The older man faces the \textbf{employee} and speaks across the store.
He has a calm but intent expression, his arms relaxed at his sides.
The \textbf{employee} is seen mostly from behind or in soft focus at first, listening from behind the counter.
The scene then shifts to a younger adult man standing elsewhere in the store near a white display table and a wall of packaged \textbf{phone} accessories.
He has short brown hair and wears a tan \textbf{sweater} over a checkered collared shirt.
He turns toward the conversation with a serious, slightly competitive look, then gestures with one hand as if making his own request.
The younger man continues speaking, leaning forward slightly and looking across the store.
His expression grows more insistent as he talks.
He turns his head to the side, apparently toward the older man, and pauses with a tense, expectant look.
The older man is then shown facing him, brows drawn together and mouth tightened in a skeptical expression.
The two men seem to be sizing each other up.
Their faces are shown in very close detail : first the younger man ’s narrowed eyes, one eye squinting as if in a stare-down, then the older man ’s furrowed brow and narrowed eyes.
The older man ’s expression softens just slightly, as though the tension is more comic than hostile.
The \textbf{employee} then appears centered behind the counter, framed by neatly arranged shelves with small \textbf{devices}, boxes, and decorative objects.
She stands upright behind a tablet stand and looks toward the two \textbf{customers}, calmly addressing them.
A wider view reveals the two men facing each other across the open floor, the older man on the left and the younger man on the right, with the \textbf{employee} between them in the background behind the counter.
Blue stools sit in front of the counter, and the store ’s shelves and display \textbf{devices} create a clean, symmetrical backdrop.
The younger man ’s mood changes.
He smiles broadly, raises a thumb in an exaggerated positive gesture, then opens both hands near his shoulders with an embarrassed, playful expression.
He laughs or grins sheepishly, then lowers his hands and leans forward a little, looking relieved but self-conscious.
Small white \textbf{legal} text appears along the bottom during this part.
He continues smiling and talking, turning his head toward the older man while the wall behind him shows rows of \textbf{phone} cases or \textbf{device} packages.
The older man then speaks again from the opposite side, turned partly toward the younger man.
He looks animated, with his mouth open mid-sentence and one shoulder angled forward.
In another wide view, the two men again stand opposite each other in front of the counter, as if \textbf{starting} a second round of comparison.
The \textbf{employee} remains centered behind them, watching with a neutral, slightly bemused posture.
Large bold white text suddenly appears across the middle of the store scene : “ IT ’S NOT COMPLICATED. ” The words stretch almost the full width of the \textbf{screen}, partially covering the two men and the counter.
The store scene then becomes tinted in bright AT\&T blue as oversized white graphic text takes over.
First, “ AT\&T ” fills the center in huge block letters, with the two \textbf{customers} and \textbf{employee} still faintly visible behind the blue overlay. \textbf{Fine} print appears near the bottom, including the line “ AT\&T may temporarily slow data speeds if the \textbf{network} is busy, ” with additional smaller \textbf{legal} text beneath it.
The large central word changes to “ EVERYONE, ” again in bold white capital letters over the blue-tinted store background.
Then a \textbf{smartphone} appears on the left, shown upright with a lavender back and multiple rear camera lenses.
The word “ FREE ” slides in large white letters on the right.
The \textbf{phone} rotates or changes presentation so its front is visible, showing a pastel pink and blue abstract \textbf{screen}.
The offer graphic reads “ FREE ” in very large letters, with “ SAMSUNG GALAXY S21 5G ” underneath.
Smaller text below explains the offer conditions, including buying on a qualifying installment plan with an eligible unlimited plan and trading in an eligible \textbf{smartphone}.
The final image keeps the \textbf{phone} on the left and the bold “ FREE ” offer text centered, while curved blue and purple AT\&T-style graphic bands sweep in from the right, partially covering the offer as the commercial ends.

% matched lemmas: bearded, button-up, customer, device, employee, fine, legal, mask, network, phone, screen, smartphone, start, sweater, tag
\end{textsample}
