\begin{textsample}{POS Dim 1 – 1950 – Score 14.00 – 1950/tv\_com\_1950\_83.txt}  \label{ex:f1_pos_087}
The commercial begins with a black screen.
It then cuts to a sepia-toned studio scene.
A blonde woman in a glamorous strapless dark dress, with a light shawl draped around her arms, stands near a vertical piece of stage equipment or lighting rig.
The background is hazy and softly lit, giving the scene a theatrical or dreamlike look.
She faces forward and appears posed for the camera.
The next sampled shot shows the same woman more prominently.
A large, smiling close-up of her face is superimposed or layered over a smaller full-body \textbf{view} behind her, creating a double-exposure effect.
She is still in the same formal outfit, with curled hair and jewelry visible.
The commercial then shifts to a \textbf{montage} of automobiles and \textbf{travel} scenery.
A light-colored mid-century \textbf{car} \textbf{drives} along a \textbf{rural} \textbf{road} bordered by \textbf{open} fields and trees.
This is followed by a closer side-front \textbf{view} of a similar light-colored \textbf{car} with chrome detailing and whitewall tires \textbf{driving} \textbf{past} a line of trees.
The next shots emphasize \textbf{roads} and landscapes : an \textbf{empty} paved \textbf{road} stretches downhill through a \textbf{wide} countryside ; a high \textbf{view} looks over a body of water and shoreline with masts or vertical poles visible at the right ; another \textbf{view} shows a \textbf{road} or bridge crossing through a valley ; and a \textbf{road} \textbf{runs} through a dramatic rocky mountain or \textbf{canyon} landscape.
A later shot shows a dark convertible-style mid-century \textbf{car} \textbf{approaching} on an \textbf{open} \textbf{road}, with flat countryside or fields around it.
Another \textbf{vehicle} may be visible behind it, though details are limited.
The commercial then returns to the studio performer.
In a close-up, the blonde woman faces the camera, smiling broadly, still wearing the dark strapless dress, shawl, and necklace against the soft, glowing background.
In the final sampled frame, she raises her hand to her mouth in a kiss-like gesture, looking upward and toward the camera.
No visible text appears in the sampled frames.

% matched lemmas: approach, canyon, car, drive, empty, montage, open, past, road, run, rural, travel, vehicle, view, wide
\end{textsample}
