\begin{textsample}{POS Dim 1 – 2020 – Score 23.00 – 2020/tv\_com\_2020\_104.txt}  \label{ex:f1_pos_004}
A long, dimly lit office stretches back in perfect symmetry, with rows of \textbf{gray} cubicles on both sides of a central aisle.
The space feels severe and controlled : dark walls, a black \textbf{ceiling} lined with bright rectangular fluorescent strips, and small glowing desk lamps on wooden work surfaces. \textbf{Employees} in dark business clothing sit at old-fashioned beige desktop \textbf{computers} with \textbf{bulky} \textbf{monitors}, keyboards, telephones, papers, and office \textbf{supplies}.
At the far end, a man stands at a lectern, facing the room like he is giving instructions to the \textbf{workers}.
The man at the lectern is middle-aged, with neatly swept-back platinum blond hair, pale skin, thin glasses, and a stern expression.
He wears a structured teal-gray jacket over a black high-neck top, giving him an authoritative, almost futuristic look.
His hands rest on the sides of the lectern, where papers are spread in front of him.
He looks outward with a composed but intense face as he speaks.
The view shifts to one of the cubicles.
A gray-haired man in a dark suit sits at a \textbf{bulky} beige \textbf{computer}, \textbf{typing} on the keyboard.
A round, white-glowing desk lamp sits close to the camera in the foreground, and more cubicles fill the background.
Another man in a dark suit sits in the neighboring cubicle and looks over toward him.
The office \textbf{workers} remain mostly seated and subdued, surrounded by identical \textbf{monitors} and lamps.
The blond man is then seen walking through the office in profile, passing between rows of desks. \textbf{Workers} remain at their stations on either side, some turned toward their \textbf{screens}, others glancing up.
He continues with a rigid posture, his face tense.
He stops centered in the aisle, facing forward, with the fluorescent \textbf{ceiling} lights receding behind him in straight lines.
His mouth opens wide as he speaks forcefully, then settles back into a hard, controlled stare.
A Black man in a \textbf{gray} suit sits at a desk facing a beige \textbf{computer}.
He leans forward, fists clenched near the keyboard, looking determined and tense.
A small turquoise \textbf{note} or \textbf{device} lies near the front edge of the desk.
He pushes himself up from the chair, hands pressing on the desktop.
In the next moment, he rises onto the desk itself, standing tall above the cubicle walls.
He wears a \textbf{gray} suit with a dark shirt, and he looks out across the office with his mouth open as if making a declaration.
Around him, the old \textbf{monitors} and desk lamps sit below his feet, emphasizing that he has broken from the quiet routine of the office.
The blond man turns sharply, looking back over his shoulder toward the standing \textbf{worker}.
His face tightens into a scowl.
He appears angry, baring his teeth as he looks upward and to the side at the disruption.
Nearby \textbf{employees} glance toward the commotion from behind their cubicle walls.
A woman in a dark pantsuit then climbs up from behind another cubicle partition.
She has short dark hair and wears a black \textbf{blazer} over a light turtleneck.
She steps onto the top of a desk or partition edge, then stands upright above the cubicles, facing forward.
Her posture is steady and defiant, with arms at her sides.
Seated \textbf{workers} below look up at her ; one man with glasses at a neighboring desk tilts his head toward her.
The office ’s glowing wall panels and desk lamps frame her against the \textbf{gray} walls.
The blond man appears in the foreground again, now closer and lower in the office, while the Black man remains standing on a desk behind him.
The blond man thrusts one arm forward and points accusingly across the room, his face twisted in frustration.
He holds the pointed gesture for several moments, extending his index finger as if trying to stop someone. \textbf{Workers} around the room watch from their cubicles, some partially hidden by \textbf{monitors} and partitions.
Another \textbf{employee}, an older \textbf{bald} man with a \textbf{gray} \textbf{beard}, rises onto a desk in a different part of the office.
He wears a light blue button-down shirt with dark trousers and an ID lanyard hanging at his chest.
He straightens to full height, standing above the seated \textbf{workers}.
His expression is calm but resolute.
A woman seated below him glances up, while others continue at their desks or turn slightly to watch.
The blond man, now visibly agitated, raises both arms and gestures broadly in front of the office ’s tall glowing wall panels.
His mouth is open as he speaks, then he leans forward with a tense posture.
His expression remains angry, and he continues pacing or shifting his weight as if trying to regain control.
The setting changes to a warm, busy \textbf{coffee} shop.
Sunlight fills the space through large front windows.
Brick walls, potted plants, wooden benches, small tables, and seated \textbf{customers} create a relaxed public atmosphere.
A woman in a blue \textbf{sweater} and dark pants stands on top of a table or bench near the window, elevated above people seated around her with \textbf{laptops} and drinks.
She faces the room, standing straight with her arms at her sides, as if joining the same public declaration.
Reversed lettering on the window includes the word “ \textbf{COFFEE}, ” and the city street is visible outside with buildings and passing pedestrians.
Behind the \textbf{coffee} bar, a young barista with dark hair and bangs looks up from an espresso machine.
She wears a white shirt under a teal apron and holds a metal milk pitcher in one hand, pausing mid-task.
Stacks of white cups and saucers sit on the counter beside her.
Her expression is attentive and slightly \textbf{puzzled}, as if she has noticed the commotion in the café.
The scene moves to a nighttime city street.
Tall buildings with lit windows rise in the background.
An ambulance is parked with its rear doors open and red lights glowing.
A paramedic or emergency \textbf{worker} in a teal jacket stands on the back step or bumper, elevated above the street.
Another person lies on a stretcher behind him at the open ambulance doors.
At the bottom of the image, on-screen subtitle text appears, first in Spanish, “ Uso Zoom para traducir, ” then in English, “ I use Zoom to translate, ” accompanied by a small Zoom-like blue \textbf{icon}.
The emergency \textbf{worker} stands upright and looks outward while the patient remains reclined below him.
A closer view shows the patient, a \textbf{bald} man lying on the stretcher at the ambulance entrance, looking up toward the standing emergency \textbf{worker}.
The subtitle “ I use Zoom to translate. ” remains visible at the bottom.
The commercial then cuts to a bright blue end card.
Centered in large white lowercase letters is the Zoom logo text, “ zoom. ” Beneath it, in smaller pale text, it reads : “ AI-first work platform, \textbf{Phone}, Contact Center, and more. ” Finally, the office scene returns.
The blond man is again in the foreground, still pointing forcefully across the room with his arm extended.
Behind him, the Black man remains standing on a desk above the cubicles.
Other \textbf{employees} sit or watch from around the room.
The blond man ’s face is tense and animated, as if still resisting the growing movement of \textbf{workers} standing up throughout the office and beyond.

% matched lemmas: bald, beard, blazer, bulky, ceiling, coffee, computer, customer, device, employee, gray, icon, laptop, monitor, note, phone, puzzle, screen, supply, sweater, type, worker
\end{textsample}
