\begin{textsample}{POS Dim 1 – 2000 – Score 22.00 – 2000/tv\_com\_2000\_45.txt}  \label{ex:f1_pos_009}
The commercial \textbf{opens} on a nearly black screen, with only a small red watermark-like mark visible in the bottom-right corner.
It then cuts to a close-up of a glossy red sports \textbf{car} seen from the side, focusing on the side window and upper door area.
The lighting is dark and dramatic, with the \textbf{car} ’s surface reflecting red highlights.
A title graphic appears over a \textbf{moving} background : white stylized characters above the words “ MIDNIGHT CLUB II. ” The background shows a dark \textbf{vehicle} surface and a blurred roadway or \textbf{city} environment, suggesting speed and motion.
The next shots emphasize rapid \textbf{urban} movement.
A \textbf{city} or roadway scene appears heavily motion-blurred, followed by an extreme close-up of a large orange-gold “ R ” shape with a dark outline, likely part of a logo.
The frame is tightly cropped, so the full logo is not visible.
A \textbf{car} with bright headlights \textbf{approaches} on a dark \textbf{road}.
This is followed by a \textbf{wide}, sunlit \textbf{city} \textbf{skyline} with tall \textbf{buildings}, elevated \textbf{roads}, and a bright low sun at the right side of the frame.
The commercial then shows a close-up of the front corner of a purple \textbf{car} : a large round headlight, chrome-like bumper, and shiny wheel are visible.
Another shot appears to be from \textbf{inside} or near the front of a \textbf{vehicle}, looking through a windshield at a residential-looking \textbf{street} with a white \textbf{fence} ; a green-and-white \textbf{car} \textbf{passes} across the frame.
A rear-view mirror or interior reflection is visible, but details of the \textbf{driver} are unclear.
The imagery becomes more abstract and fast-moving, with blurred red and yellow lights against a dark \textbf{city} background.
A later shot looks through vertical \textbf{fence} or railing bars at a \textbf{car} \textbf{moving} along a roadway or ramp, with \textbf{city} \textbf{structures} behind it.
A bright headlight flare fills much of the next frame, obscuring details.
A low rear-side \textbf{view} shows a sports \textbf{car} \textbf{driving} through a \textbf{city} \textbf{street}, its red taillight glowing and its body reflecting \textbf{street} lighting.
The \textbf{car} appears close to the camera and \textbf{angled} forward into the \textbf{street}.
Near the end, a \textbf{car} turns or slides through a nighttime intersection, producing a \textbf{cloud} of smoke or tire haze.
A \textbf{building} with bright turquoise horizontal neon bands is visible in the background.
An ESRB “ T ” rating icon appears at the bottom-left.
Another \textbf{city} racing shot follows, showing \textbf{cars} \textbf{moving} quickly through a lit \textbf{urban} intersection with motion blur ; the “ T ” rating remains visible at bottom-left.
The final frame is a black end card.
It displays stylized characters above the title “ MIDNIGHT CLUB II, ” followed by “ IN STORES NOW. ” Along the bottom are several platform/publisher/rating logos, including an ESRB “ T ” rating, “ PC CD-ROM, ” Xbox Live, PlayStation 2, and Rockstar-related logos.
A \textbf{website} is shown : “ WWW.ROCKSTARGAMES.COM/MIDNIGHTCLUB2. ”

% matched lemmas: angle, approach, building, car, city, cloud, drive, driver, fence, inside, move, open, pass, road, skyline, street, structure, urban, vehicle, view, website, wide
\end{textsample}
