\begin{textsample}{POS Dim 1 – 1960 – Score 19.00 – 1960/tv\_com\_1960\_53.txt}  \label{ex:f1_pos_053}
The commercial is in black and white and appears to take place in a mountainous, wooded outdoor area.
It begins with a very dark frame in which little is visually distinguishable.
The next shot is framed as if seen through binoculars : a campsite or picnic area is visible, with a folding table, a cooler or box, and a striped umbrella or tent-like \textbf{structure}.
A bear-like animal is near the table, apparently investigating the area.
The \textbf{view} then cuts to a close-up of a man wearing a broad-brimmed hat and uniform-like clothing, looking through binoculars.
He lowers or adjusts the binoculars.
In a \textbf{wider} outdoor shot, the same man stands beside a white \textbf{car}, with other \textbf{vehicles} or equipment behind him.
He appears to \textbf{move} toward the \textbf{car}.
Several close shots show the \textbf{car} interior, including dark upholstered seats.
The man, still wearing the hat and uniform-like jacket with a badge-like emblem, \textbf{gets} into the \textbf{vehicle}.
A side \textbf{view} shows the white \textbf{car} parked on a dusty mountain \textbf{road} with \textbf{hills} and trees in the background.
A close-up focuses on one of the \textbf{car} ’s wheels.
The \textbf{car} then begins \textbf{moving} along \textbf{rough}, unpaved \textbf{roads}, kicking up dust.
The commercial then alternates between \textbf{exterior} driving shots and interior shots of the \textbf{driver}.
The \textbf{car} \textbf{travels} along \textbf{winding} dirt \textbf{roads} on hillsides, \textbf{past} pine trees and \textbf{open} mountain \textbf{views}.
Dust trails behind it.
Interior shots show the man holding the steering wheel and concentrating on the \textbf{road}.
There are moments of strong sunlight and lens flare through the windshield, briefly washing out parts of the image.
The \textbf{car} \textbf{continues} through wooded areas, seen from the front and side, \textbf{moving} quickly on dusty \textbf{roads}.
It \textbf{passes} through forested terrain with tall trees and uneven ground.
The \textbf{driver} remains focused, with both \textbf{exterior} and interior shots emphasizing motion, dust, and rough-road driving.
Near the end, the \textbf{car} arrives back near a campsite or picnic area.
A \textbf{wide} shot shows the \textbf{car} \textbf{approaching} through trees.
Another shot shows a bear near trash cans or containers beside a \textbf{structure} or campsite area.
The final \textbf{exterior} shots show the white \textbf{car} parked or slowing near the picnic site, with the man standing beside or near the \textbf{car} and equipment in the foreground.
The last frame shows a scenic mountain background with large white text overlaid : “ American Motors quality built in not added on ”

% matched lemmas: approach, car, continue, driver, exterior, get, hill, move, open, pass, past, road, rough, structure, travel, vehicle, view, wide, wind
\end{textsample}
