\begin{textsample}{POS Dim 1 – 1980 – Score 16.00 – 1980/tv\_com\_1980\_53.txt}  \label{ex:f1_pos_073}
The commercial begins on a black screen.
A \textbf{wide} \textbf{exterior} shot then shows a Texaco gas station across a divided roadway or service area, with a large overhead sign reading “ TEXACO ” and the Texaco star logo.
In the foreground are fuel pumps labeled “ ZX, ” and a white \textbf{car} is parked at the pumps.
The setting appears \textbf{open} and roadside, with low \textbf{hills} or desert-like terrain in the \textbf{distance}.
The \textbf{view} \textbf{moves} closer to the white \textbf{car}.
A man is visible in the \textbf{driver} ’s seat with the door \textbf{open}.
A blue shopping-cart-like object or basket is near the \textbf{car}.
Another close-up shows a dark-haired man in a light-colored shirt seated in the \textbf{car}, looking outward through the \textbf{open} door/window area.
The camera cuts back to a \textbf{wide} shot of the Texaco station across the \textbf{road}.
The same or similar man in a white shirt is now \textbf{outside} the white \textbf{car} in the foreground, facing toward the \textbf{distant} station.
A middle-aged, balding man in a patterned blue shirt is shown beside a pump marked “ ZX. ” He appears to be attending to a \textbf{car} or fuel pump.
Behind him, a large red “ Z ” graphic is visible on the station wall.
He leans near the pump and \textbf{car}, then later stands upright and looks off to the side with a serious or curious expression.
A high, symmetrical shot shows a long divided highway or roadway stretching into the \textbf{distance}.
A man in a light shirt walks near the central divider, emphasizing the separation between the foreground service area and the Texaco station across the \textbf{road}.
Back at the pumps, the man in the white shirt reaches toward a pump panel/nozzle area.
The pump island includes Texaco branding and multiple black hoses.
The balding man is shown again in close-up holding or standing near a fuel nozzle, looking alertly toward something off-screen.
Another \textbf{wide} roadway shot shows the man in the white shirt standing at the central divider while a long fuel hose extends from the right side of the frame toward him.
The hose crosses or reaches across the \textbf{open} paved area.
The scene returns to the white \textbf{car} and pumps.
The man in the white shirt is crouched or bent near the rear side of the white \textbf{car}, handling a fuel nozzle and hose.
The balding man stands \textbf{nearby} among the pumps.
A close-up of the balding man follows, with the nozzle visible near him ; he leans forward slightly, as if watching or reacting to the activity. \textbf{Inside} the station \textbf{building}, the man in the white shirt appears at a service window or counter.
A blond employee wearing a striped shirt sits behind the counter, surrounded by shelves and equipment.
The two face each other through the window area.
A black title card appears with the Texaco star logo and the word “ TEXACO ” beneath it.
Large white text at the bottom reads : “ EXPECT MORE. ” The commercial then returns briefly to the \textbf{exterior} station \textbf{view}.
In the foreground, the balding man is near a “ ZX ” pump beside the white \textbf{car}, with the Texaco station still visible across the roadway.
In the next shot, he walks away from the pump area toward the Texaco station across the \textbf{road}, \textbf{carrying} or guiding something not fully clear from the sampled frame.
The scene ends on black.

% matched lemmas: building, car, carry, distance, distant, driver, exterior, hill, inside, move, nearby, open, outside, road, view, wide
\end{textsample}
