\begin{textsample}{POS Dim 1 – 2020 – Score 18.00 – 2020/tv\_com\_2020\_116.txt}  \label{ex:f1_pos_006}
The commercial opens inside a warmly lit home at Christmas.
A small grey-and-white cat is partway inside a decorated Christmas tree, surrounded by green branches, glowing string lights, red baubles, cream ornaments, and a dangling nutcracker.
The cat wriggles forward through the branches, then drops out of the tree toward the floor.
It lands low in front of the tree, slightly blurred from the quick motion, with the lights and ornaments glowing behind it.
The scene shifts outdoors to a snowy path bordered by high snowbanks and dark winter trees.
Several bundled-up people ride together on a yellow sled, leaning into the curve as they slide along the packed snow.
The image then shares the \textbf{screen} with a cozy \textbf{indoor} holiday moment : an older white man with a white \textbf{beard}, glasses, a patterned Christmas \textbf{sweater}, and a yellow turkey-shaped hat sits on a \textbf{couch} while two red-haired children laugh behind him.
Large holiday ornaments hang overhead in the following festive \textbf{indoor} public space, a high-ceilinged shopping arcade or market \textbf{hall} filled with people below.
Beside it, the family \textbf{couch} scene remains visible for a moment.
A blond child in an orange shirt sits at a table, closely inspecting a decorated gingerbread house on a cake stand.
The house has a dark cookie-brown structure, white icing trim, red candies, and a small black doorway.
Then a light-colored golden retriever lies across a kitchen counter or island, eating from a plate, while a sink and kitchen cabinets sit behind it.
This domestic chaos appears alongside the gingerbread-house scene, suggesting holiday tasks piling up.
A silver Dell \textbf{laptop} appears on a stone countertop.
A hand lifts the lid open, revealing the keyboard while the Dell logo is centered on the pale metallic back of the \textbf{screen}.
The setting looks like a busy kitchen or bakery, with people in aprons blurred in the background.
A close view emphasizes the \textbf{laptop} : on one side, backlit \textbf{keys} glow bluish around the letters J and K ; on the other, a blue “ intel core ultra 7 ” sticker is visible on the \textbf{laptop} ’s palm rest.
The \textbf{laptop} is then shown in a café or bakery workspace.
Pastries sit in trays on a long counter, shelves of jars and \textbf{supplies} line the wall, and \textbf{workers} in aprons move behind the counter.
A silver \textbf{laptop} sits open among the bakery items.
White on-screen text appears near the lower left reading “ All-day battery life. ” The \textbf{screen} then divides between a close overhead view of hands \textbf{typing} on the Dell \textbf{laptop} and a clean order-management \textbf{interface}.
The \textbf{interface} has a red circular logo reading “ THE CRUMB SHED. ” It shows “ New Orders ” for “ Oct 1 - Oct 30, ” and “ Total Orders ” \textbf{starting} at 98, then rising to 100.
An order entry appears for “ Holiday Cupcakes, ” quantity 1, priced at “ \$7.99. ” The hands continue \textbf{typing} quickly on the compact keyboard, with bracelets and a watch visible on the wrists.
Next, a young woman or teenage girl with long dark hair and a wide red headband sits at a desk in a bright room, using a light-colored \textbf{laptop}.
On the right side of the \textbf{screen}, a simple creation \textbf{interface} appears with the \textbf{typed} word “ Create ” and a dropdown labeled “ Quick response, ” accompanied by a small \textbf{multicolored} \textbf{icon}.
As she looks at the \textbf{laptop} with a focused, pleased expression, the \textbf{interface} generates holiday-themed illustrations : a smiling \textbf{bald} older woman with glasses appears in several square designs, surrounded by snowflakes, ornaments, gifts, and festive backgrounds.
In a living room decorated for Christmas, an older white woman with short white hair, large glasses, and a cream blouse reacts with delighted surprise as she receives a blue garment decorated with one of those cartoon portraits of her face.
Her mouth is open in excitement, and she holds the item up proudly.
Behind her, the older \textbf{bearded} man in the patterned Christmas \textbf{sweater} cheers, while other family members ’ hands reach in from the side, applauding or gesturing.
The older woman then wears the bright blue \textbf{sweater} with her smiling cartoon face printed on the front, paired with a full red skirt.
She stands in the center of the living room near a decorated Christmas tree, striking playful poses and dancing with her arms raised.
Around her, family members watch and smile : a woman stands to the left near the tree, a man in a red plaid shirt sits to the right holding a mug, and two red-haired children sit on the floor in front of her.
Large white logos appear across the middle : “ Dell Technologies ” followed by a vertical divider and “ intel. ” Beneath them, smaller white text reads “ Price Match Guarantee ” and “ Dell.com/holiday, ” with fine-print \textbf{legal} text along the bottom.
The older woman continues her joyful dance as the family looks on.

% matched lemmas: bald, beard, bearded, couch, hall, icon, indoor, interface, key, laptop, legal, multicolored, screen, start, supply, sweater, type, worker
\end{textsample}
