\begin{textsample}{NEG Dim 4 – 1970 – Score 1.00 – 1970/tv\_com\_1970\_50.txt}  \label{ex:f4_neg_008}
The commercial begins with a separate-looking product image : a bottle of blue Signal mouthwash stands beside a small glass and a white block, with large white lettering above it reading “ SIGNAL FIGHTS STRONG MOUTH ODORS. ” Then the scene changes outdoors to a green park or suburban path lined with grass and trees.
Orange traffic cones are set up down the paved path like a small racecourse.
Several children stand along the left side watching.
One is a blond girl, about elementary-school age, with long straight hair, wearing a blue track-style jacket with white stripes and a light turtleneck.
Near her is another child in an orange top, holding what looks like a clipboard or timing board.
A boy with a straight brown bowl haircut, also elementary-school age, sits low to the ground on a yellow Big Wheel-style tricycle, facing down the course.
The toy has a very large front wheel with a black-and-white patterned wheel cover, black handlebars, a yellow body, and two small, wide rear wheels.
The boy grips the handlebars with both hands, looking focused.
A close view shows a black rally timer built into the yellow center console of the cycle between his knees.
A child ’s hand presses and turns the dark controls, including a round dial and a small red marker near the top, as if setting the time before the run.
Back on the path, the boy starts riding through the cones while the other children watch from the side.
He leans his body and the low tricycle into turns, steering around the orange pylons.
The large front wheel dominates the front of the toy, and the small rear wheels sit wide apart behind him, giving the cycle a squat racing shape.
As he comes toward the viewer and then passes, his tan pants and white sneakers are visible stretched forward along the sides of the front wheel.
The children in the background remain standing on the grass edge, watching the ride.
The commercial then focuses on product details while the boy continues moving.
The built-in black timer is shown again in the yellow console.
Close views of the cycle ’s wheels show the fat racing-style rear tires rolling along the pavement, with shiny silver hubcaps and dark rubber treads.
The boy ’s feet and legs pump and brace as the toy skims past the cones.
In several views, the cycle slides and pivots sharply near an orange pylon, demonstrating a spin-out style turn or braking action.
The front wheel sweeps close to the cone, and the rear of the toy swings around while the boy leans back and holds the handlebars.
The orange cones remain upright as the cycle threads through them, emphasizing the small slalom course.
Near the end of the run, the children at the side are shown from behind and beside the course.
The blond girl in the blue jacket stands closest, with the orange-shirted child nearby, both watching as the boy spins past and comes to a stop or slows near them.
The girl appears to be holding a small timing object in her hand, while the boy on the cycle sits low and looks back toward the others.
The timer on the cycle is shown once more in close-up, with a hand adjusting the top control again, suggesting the course can be timed for another attempt.
A closer view of the boy standing or sitting up against a grassy background shows him looking upward, his mouth slightly open as if speaking, with an eager expression.
The blond girl is then shown in close-up again, calmly smiling as she looks toward him or the course.
The commercial ends with a clean product display on a blue studio-like background.
The Big Wheel Rally Cycle is posed in profile : yellow frame, oversized decorated front wheel, black handlebars, low black seat, and two small rear wheels.
Three bright orange cones stand in a row in front of it.
Large white text along the bottom reads “ BIG WHEEL RALLY CYCLE. ” In the final product image, small white text appears near the top, including the brand name “ MARX ” on the right, while the toy and cones remain centered as the final visual.

% matched lemmas: 
\end{textsample}
