\begin{textsample}{NEG Dim 4 – 1970 – Score -6.00 – 1970/tv\_com\_1970\_116.txt}  \label{ex:f4_neg_031}
The commercial opens with a very close, low-resolution shot of a man ’s face.
The image is dark and heavily affected by video artifacts and color banding, making facial details unclear.
It then cuts to close-up views of a tabletop \textbf{electronic} device.
The device has a rectangular top surface with a central slot or opening and a row of light-colored rectangular buttons across the front.
The shot emphasizes the \textbf{controls} and mechanical-looking top section.
Next, the device is shown from farther back on a table.
A hand reaches toward or presses \textbf{controls} on the top/front of the \textbf{unit}.
Behind it, a small television screen displays a football game.
White on-screen text appears near the bottom ; it is partially legible and reads “ ACTUAL CLOSED-CIRCUIT TV PICTURE ” and “ TWO HOUR RECORDING TIME. ” The commercial then shows another close-up of the device ’s right-side \textbf{control} area.
There are sliding switches or \textbf{levers} on the top panel and stacked round \textbf{knobs} or \textbf{dials} on the front right side, suggesting adjustable settings.
A profile shot follows of a blond-haired man in a checked shirt and dark sweater.
He is shown from the side against a dark background, looking downward or toward something off-screen.
No interaction is visible in this sampled frame.
The final frame is a product display shot against a dark studio background.
The \textbf{electronic} \textbf{unit} sits centered on a reflective surface, with another component or cover positioned behind it.
Above the product is the “ Zenith ” logo and the printed slogan : “ The quality goes in before the name goes on. ”

% matched lemmas: control, dial, electronic, knob, lever, unit
\end{textsample}
