\begin{textsample}{NEG Dim 4 – 1990 – Score -2.00 – 1990/tv\_com\_1990\_82.txt}  \label{ex:f4_neg_023}
Across a stretch of water, a busy industrial dock appears in warm pink-orange light.
A huge gray cargo ship fills the background, mooring lines stretching down to the pier.
On the dock, a white box truck with large dark lettering on its side reads “ DON ’S MARINE SUPPLY. ” To its left sits a large yellow dockside machine or crane vehicle, and to its right an orange forklift waits near the truck ’s rear.
A few workers stand nearby, small against the ship ’s massive hull and the heavy equipment.
The scene shifts to a wide, open rural landscape colored in rusty orange tones.
A white cab and long dark-sided load travel along a narrow dirt road beside a fence, towing a small white two-wheeled \textbf{trailer}.
The vehicle and \textbf{trailer} move steadily across the rolling field, throwing a faint trail of dust behind them.
Back at the dock, the “ DON ’S MARINE SUPPLY ” truck is shown closer, still parked in front of the ship.
White legal text appears along the bottom : “ INCLUDING OCCUPANTS, EQUIPMENT, AND CARGO. ” The orange forklift, driven by a worker wearing a light-colored hard hat, approaches the rear of the box truck.
Another forklift is visible farther right.
The truck ’s side lettering remains prominent, with the ship ’s curved hull and rigging \textbf{looming} behind.
The rural road returns, with the same long vehicle and white \textbf{trailer} moving through the orange hills.
White text at the bottom reads, “ NOT TO EXCEED GCWR OF 8,600 LBS. ” The load on the vehicle includes stacked or slatted material along the side, and the \textbf{trailer} follows closely behind on its two white wheels.
At the dock again, the white marine-supply box truck begins moving left, revealing what had been hidden behind it : a gray Toyota pickup.
Its bed is heavily loaded with marine equipment, including large pale boat propellers and a bulky wooden or metal frame rising above the bed.
An adult worker in a blue plaid shirt and jeans stands beside the pickup, facing it, while the forklift operator remains to the right.
A second adult, dressed in dark clothing and holding papers or a clipboard, stands nearby as if observing or checking the load.
As the box truck continues out of the way, the gray pickup becomes fully visible, parked in front of an orange shipping container with the huge ship hull behind it.
The orange rural landscape appears again.
What first looked like a larger work vehicle gives way visually to a red Toyota pickup pulling the same small white \textbf{trailer}.
The red pickup drives along the dirt road, its bed carrying several gray cylindrical objects or bundled cargo.
The white two-wheeled \textbf{trailer} bounces along behind it as the truck continues through the open fields.
The gray Toyota pickup is then shown at the harbor on wet pavement, its reflection visible in puddles.
It drives slowly through the port area with the tall load of propellers and framework secured in the bed.
Industrial cranes, stacked shipping containers, and the side of the cargo ship surround it.
As the truck moves away, the tailgate comes into view with “ TOYOTA ” written in large white letters.
Finally, the red Toyota pickup drives on a winding two-lane road through rolling coastal hills, towing the white \textbf{trailer} behind it.
The road curves upward beside a rocky embankment, with pale hills and distant landscape stretching across the background.
The red truck approaches from around the bend, centered on the road, with its \textbf{trailer} following closely.
At the bottom of the screen, white text appears : “ I love what you do for me ” above the Toyota logo and the word “ TOYOTA. ”

% matched lemmas: loom, trailer
\end{textsample}
