\begin{textsample}{NEG Dim 4 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_119.txt}  \label{ex:f4_neg_046}
A mountain road curves toward a large stone tunnel entrance built into a rocky hillside.
The tunnel mouth is dark, with a line of lights receding inside, and a white road edge line runs along the foreground.
Small white text near the bottom reads, “ Professional riders on closed course. ” A gold touring motorcycle flashes past the tunnel entrance in a blur, emphasizing speed, then the view cuts to the yellow double center lines of the road rushing by.
The motorcycle appears on an open mountain curve, leaning smoothly through a bend on a paved two-lane road.
Its front lights glow brightly, and the rider, wearing a dark full-face helmet and riding gear, is tucked behind a clear windshield.
Misty blue-gray mountains rise in the background, with the road ’s double yellow lines sweeping in an S-shape across the pavement.
The same small safety text remains along the bottom.
A black Honda Gold Wing touring motorcycle then travels through a sunlit, scrubby landscape.
The rider wears a black helmet and dark jacket, sitting upright behind the large front fairing and windshield.
The bike ’s broad bodywork, side cases, and rear trunk make it look substantial and built for travel.
Low brush and warm-toned hills blur past around the road.
The scene opens wider on a straight highway leading toward dramatic snowcapped mountains.
Two touring motorcycles ride along the road : a yellow Gold Wing close to the right side of the image and a darker motorcycle farther ahead in the left lane.
Both riders wear helmets, and the yellow bike ’s large front fairing, mirrors, and headlight cluster are prominent.
The snow-covered peaks stretch across the horizon under a pale blue sky.
A side view shows a black Gold Wing 1800 carrying two helmeted riders.
The driver, in a dark leather jacket, blue jeans, gloves, and boots, sits upright with both hands on the handlebars.
The passenger, also wearing a helmet, dark jacket, blue jeans, and boots, sits relaxed on the raised rear seat with a padded backrest and large rear storage trunk behind them.
The motorcycle ’s chrome engine covers, footboards, windshield, and wide saddlebag area are clearly visible.
At the upper left, white text reads “ Gold Wing 1800. ” A few moments later, bold white text appears along the bottom : “ ‘ Motorcycle of the Year ’, ” with smaller attribution text beneath it to Motorcyclist and Rider magazines.
The bike continues steadily past a forested mountain backdrop.
The commercial returns to a single black Gold Wing on a narrow rural road bordered by golden grass.
From above and ahead, the rider approaches along the winding pavement, the motorcycle centered in the lane.
The rider leans the bike gently into the curve, and the front headlights and amber side lights are visible.
Tall grasses and fence posts line the roadside, giving the setting a quiet countryside feel.
From behind, a black touring motorcycle leans through another broad mountain curve.
Its red rear lights and large rear trunk are visible as it arcs along the double yellow lines.
The rider ’s dark helmet and jacket form a compact silhouette above the bike ’s wide rear storage cases.
Blue-gray mountain ridges and scattered evergreens fill the distance.
An orange Gold Wing rides through a desert canyon road.
Red and tan rock walls rise close beside the pavement, with a natural arch-like opening visible in the rock face behind the motorcycle.
The rider wears a black helmet and dark riding clothes, seated upright behind the tall clear windshield.
The orange fairing, matching saddlebags, rear trunk, chrome engine area, and bright headlight cluster stand out against the warm rock.
A large gold wing emblem and the word “ GOLDWING ” appear over a curving mountain road, with “ Test Ride ” in bold white text beneath.
Fine-print legal text fills the lower portion of the screen, including a visible note that the test ride \textbf{program} is good through 4-1-2002 and that dealers may deny participation at their discretion.
Behind the graphics, a motorcycle rounds the bend toward the viewer and then passes by, partially blurred by motion, while evergreen trees and a pale sky frame the road.
A black Gold Wing approaches head-on through a red-rock canyon under a clear blue sky.
The rider is centered behind the windshield, and the twin headlights glow.
White fine print remains along the bottom.
The text “ honda.com ” appears in white above the legal copy as the motorcycle continues along the road between reddish rock formations and a sloping canyon wall.
The setting shifts back to golden fields.
A black Gold Wing moves away along a narrow paved country road, partly screened by tall green grasses in the foreground.
Large white text appears at the upper left : “ 2.9 \% APR. ” Fine print along the bottom explains that the 2.9 \% APR financing applies to new Gold Wings and includes additional qualification and Honda Finance details.
The motorcycle continues farther down the road, becoming smaller as the landscape opens into a broad valley of yellow fields, fence posts, and distant red and gray rock cliffs.
In the final view, the lone motorcycle rides away along the center of the winding road through the expansive golden valley.
The large “ 2.9 \% APR ” offer fades, while the fine print remains at the bottom.
A red Honda wing-shaped graphic appears above the road, followed by the white slogan “ PERFORMANCE FIRST. ” The motorcycle continues toward the distant cliffs and open sky, visually ending on the idea of a long scenic journey.

% matched lemmas: program
\end{textsample}
