\begin{textsample}{NEG Dim 4 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_74.txt}  \label{ex:f4_neg_026}
The commercial opens in a dark, misty jungle at night or in very low light, tinted \textbf{blue-purple}.
A human figure, seen mostly from the waist down and in silhouette, runs through shallow water or a flooded path.
Their legs splash heavily, sending water up around their knees as they move through dense \textbf{vegetation}.
The surrounding plants and tree trunks are only partly visible through fog and darkness, giving the scene a humid, jungle-adventure atmosphere.
The view shifts deeper into the foliage.
Large wet leaves and thin branches fill the foreground, with pale mist glowing behind them.
Thick tree limbs cross the image in dark silhouette against the bluish haze.
A human figure appears caught or suspended among the trees, upside down, with legs raised and boots visible, as if snared or hanging from a vine or trap.
The body is mostly a black outline against the fog, making the pose more dramatic than detailed.
The jungle imagery continues with a close view of a hand and forearm gripping a hanging bundle of vines or roots.
Leaves and dangling strands frame the hand, and a small dark object hangs nearby, though its exact shape is unclear.
The background remains a cloudy blue, with the person and vines almost entirely silhouetted.
The commercial then switches to colorful video game footage.
A pixel-art jungle scene fills the screen with a bright turquoise-blue background and a diagonal vine stretching from the lower left toward the upper right.
A small adventurer character hangs from the vine with both hands, swinging over a gap between mossy platforms.
Game counters and icons appear around the edges, including numbers at the top left and small item or life indicators near the bottom corners.
A small creature or figure is visible near the upper right on the vine or platform area as the player character swings beneath it.
Later gameplay shows another jungle-water scene.
The pixel adventurer drops into bright blue water beneath a rocky, green jungle overhang.
A large white splash bursts upward around the character, then expands into rippling circles across the water.
More game status numbers and icons remain at the screen edges, reinforcing that this is active platform-game footage from Pitfall : The Mayan Adventure.

% matched lemmas: blue-purple, vegetation
\end{textsample}
