\begin{textsample}{NEG Dim 4 – 1980 – Score 1.00 – 1980/tv\_com\_1980\_25.txt}  \label{ex:f4_neg_058}
Three men sit shoulder to shoulder behind a cluttered counter in a plumbing-office setting.
They are dressed alike in bright yellow plaid jackets, dark shirts, red bow ties, and white caps with red lettering.
Behind them, a wall sign reads “ 3 GUYS PLUMBING, ” with a large yellow number 3, and a pink neon-style word “ DISCOUNT ” glowing above it.
Plumbing tools and pipes hang around the background, making the space look like a busy, staged repair shop.
Several black telephones sit across the counter in front of the men.
At first they face forward with their hands near the phones, then all three reach out together and pick up receivers, holding them to their ears as if taking calls.
The three men continue working the phones in unison, leaning forward and speaking into the receivers.
Their expressions are animated and slightly comic, with raised brows and open mouths.
They look from the phones toward the viewer and back again, as if promoting their plumbing service.
A white plastic jug of Liquid Plumr then appears prominently in the foreground on the left side of the counter, much larger than the men behind it because it is closer.
The jug has a red cap, an integrated handle, and a bold red-and-blue label reading “ Liquid Plumr ” and “ Drain Opener, ” with a blue “ Clears Fast ” panel near the top.
Behind the bottle, the three matching plumbers keep holding phones ; one lifts a receiver upward while the others lean in around the product.
The scene changes to a close view of the Liquid Plumr jug being handled by a hand.
The white bottle is tilted, its cap removed, and the label remains partly visible as the hand grips the handle near the top.
Clear liquid begins pouring from the spout in a steady stream.
The stream is then shown entering a surface of blue-tinted standing water, cutting down through it.
A transparent pipe demonstration follows.
A U-shaped drain trap is shown against a plain background, with the words “ Time Lapse ” in white text over the pipe.
Amber-colored liquid moves through the curved pipe from the right side toward a dark, dirty blockage settled in the bottom of the U-bend.
As the demonstration continues, the dark mass appears to break up and diminish while the liquid passes through the curve.
The view then shifts to a sink drain from above : a circular metal drain opening sits in a gray basin, surrounded by cloudy water and foam.
The foamy liquid churns around the drain, and the metal strainer becomes more visible as the water clears and recedes.
The three matching plumbers reappear at their counter under the “ DISCOUNT ” and “ 3 GUYS PLUMBING ” sign.
They sit facing forward again, hands poised over the row of black telephones.
In another synchronized motion, they reach for the phones and lift the receivers to their ears.
Later they set the phones down and straighten up, returning to a composed pose behind the counter.
At the end, the Liquid Plumr jug stands alone in the foreground on the counter, sharply presented with its red cap and large “ Liquid Plumr Drain Opener ” label facing forward.
The plumbing office remains blurred in the background, with the “ 3 GUYS PLUMBING ” sign and hanging tools still visible behind the product.

% matched lemmas: 
\end{textsample}
