\begin{textsample}{NEG Dim 4 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_96.txt}  \label{ex:f4_neg_025}
A dark, shadowy engine compartment fills the screen, lit so that the metal parts gleam against a black background.
A silver engine block sits horizontally, with ribbed covers, bolts, curved silver pipes below, a small red component near the lower left, and bright red ignition wires running across the top.
The view moves progressively closer into the engine as the outer surfaces seem to give way to exposed internal parts.
The ribbed cover is replaced by visible mechanical pieces : red wires arch over grey metal housings, then dark cylindrical camshafts and rounded valve components appear inside a pale metal frame.
The imagery continues deeper into the engine.
Rows of circular openings, bolts, and dark valve heads pass by in close-up, all in cool grey and black metal.
The engine becomes more abstract and tunnel-like as the view centers on a single large circular cylinder opening.
The round bore dominates the screen, with surrounding bolt holes and machined metal surfaces framing it.
Inside, a pale piston face moves within the cylinder, sliding up and down like a flat round disk in a metal tube.
Suddenly the grey mechanical view is interrupted by bright orange, red, and white flashes that fill the cylinder area, resembling bursts of heat or combustion.
The screen alternates between the cool grey piston moving in the cylinder and fiery orange-red overlays, suggesting intense heat inside the engine.
The piston repeatedly rises close to the top of the circular bore, then drops back, while glowing flashes flare across the metal.
The hot imagery becomes more frequent : white-hot centers surrounded by orange and red clouds appear over the cylinder, then fade back to the metal piston surface.
After this sequence of repeated piston movement and heat bursts, a bottle of Castrol GTX motor \textbf{oil} appears alone on a dark stage.
It stands upright in the center on a white, dotted or grid-like floor that recedes into darkness.
The bottle is light-colored with a red cap.
Its front label shows the Castrol name in red, “ GTX ” in large black letters, and green and red blocks, with “ Super Multi-Grade ” and “ Motor Oil ” visible on the label.
Large glossy red block letters begin to rise in front of the bottle, partially covering it.
The words build into a stacked message in bold three-dimensional capitals : “ ONLY CASTROL PROVIDES MAXIMUM PROTECTION AGAINST VISCOSITY AND THERMAL BREAKDOWN. ” As the text grows taller and fills most of the screen, the bottle remains behind it, visible through gaps or below the lower lines.
The red lettering dominates the image against the black background, while the bottle stays centered on the illuminated dotted floor.
The commercial returns to the engine interior.
The circular cylinder and piston are shown again, now with a red glowing ring around the piston area.
The piston continues its up-and-down motion inside the grey metal bore.
Bright white flashes and orange-red combustion-like bursts alternate with the mechanical view, making the cylinder appear extremely hot.
The red ring remains visible around the moving piston in several shots, reinforcing the impression of heat and stress inside the engine.
Finally, the Castrol GTX bottle returns alone on the same dark stage and glowing dotted floor.
It stands centered, upright, with its red cap and front label facing forward.
At the bottom of the screen, bold red three-dimensional text appears : “ ENGINEERED FOR TODAY ’S SMALLER CARS. ” The bottle remains above the slogan, lit from below and surrounded by darkness.

% matched lemmas: oil
\end{textsample}
