\begin{textsample}{NEG Dim 4 – 1990 – Score -1.00 – 1990/tv\_com\_1990\_76.txt}  \label{ex:f4_neg_053}
The commercial opens on a very dark shot in which the side profile of a car is barely visible.
Most details are obscured by low lighting, but the outline suggests a sedan-like vehicle.
The scene then changes to a brightly lit studio setting with a red four-door sedan positioned three-quarters front-facing toward the viewer.
A man in a dark suit stands to the left of the car, near the front fender and hood area, appearing to gesture toward or present the vehicle.
The background is a neutral, textured gray, giving the scene a \textbf{showroom} or studio demonstration feel.
The car ’s chrome trim, front grille, headlights, and glossy red finish are clearly visible.
Next, the view cuts to the rear of the same or similar red sedan with its trunk open.
A person, visible mainly from the torso down and wearing dark clothing, is placing or lifting a large light-colored suitcase or rectangular bag into the trunk.
The shot emphasizes the open cargo area and the vehicle ’s rear styling, including the tail lights and bumper.
The final frame shows the red car driving away along a curving road in a landscaped suburban or park-like setting with green lawns, trees, shrubs, and a bright blue sky.
Overlaid text appears prominently in the lower half of the frame.
The largest text reads “ BUICK, ” followed by “ The New Symbol For Quality In America. ” A phone number is displayed underneath : “ 1-800-531-1115. ”

% matched lemmas: showroom
\end{textsample}
