\begin{textsample}{NEG Dim 4 – 2020 – Score 1.00 – 2020/tv\_com\_2020\_67.txt}  \label{ex:f4_neg_089}
On a plain white background, the Headspace logo appears centered : a simple orange circle followed by the word “ headspace ” in lowercase black letters.
From the bottom of the screen, a large dark charcoal curved shape rises, like a heavy dome or shadow, with a small orange rounded square peeking over its top edge.
The orange shape then becomes a tiny character on the dark background, with two wide white eyes and a small straight mouth, giving it a startled, uncertain look.
The orange character grows into a large round head filling the lower part of the screen.
Its eyes squeeze shut in a stressed expression, and a jagged yellow lightning-bolt symbol hovers above it.
The background remains dark gray, and more small worry-like symbols appear around the head, including an exclamation mark, a question mark, and other abstract shapes.
The character ’s face relaxes : its eyes stay gently closed, and its mouth becomes a calm straight line.
A warm yellow outline begins to glow around the orange head.
The glow thickens into a broad circular halo, pushing the darker background away.
The anxious symbols fade upward and disappear.
The orange face remains still with closed eyes, now peaceful rather than tense.
The yellow rings continue expanding outward, filling more of the screen with bright, sunlike color.
The character ’s mouth curves into a small content smile.
White clouds drift into the lower edges and sides of the scene, and the orange head now resembles a calm sun rising among clouds against a pale yellow sky.
Smaller white clouds float on either side.
The orange sun sits low at first, then becomes more centered as the surrounding yellow circles broaden and brighten.
The scene turns fully warm and sunny, with soft concentric rings of yellow and orange radiating from the calm orange circle.
The orange circle settles in the middle of the screen, eyes closed and smiling softly, surrounded by several wide, smooth rings of yellow, like ripples or a gentle glow.
White curved text appears around it, forming a circle : “ Be kind ” above the orange face and “ to your mind ” below it.
The final image changes to a bright yellow background with the Headspace logo centered again : the orange dot beside the lowercase black word “ headspace. ”

% matched lemmas: 
\end{textsample}
