\begin{textsample}{NEG Dim 4 – 1980 – Score -3.00 – 1980/tv\_com\_1980\_84.txt}  \label{ex:f4_neg_051}
A black Sony audio \textbf{cassette} rests inside a clear plastic \textbf{cassette} case on a plain grey surface.
Its front label has a long white strip and small printed markings, including the Sony name and the model marking “ UCX-S90. ” A pair of light-skinned hands moves in from the sides, grips the case, flips it open, and slides the \textbf{cassette} out.
The transparent lid remains open, exposing the empty case with its molded plastic posts and shallow compartments.
With the \textbf{cassette} removed, the open clear case stays centered, now looking like an empty rectangular shell.
Small electronic parts begin to appear inside it.
A hand lowers in a green circuit board shaped to fit along the upper and right edges of the case, covered with tiny silver components, black chips, and soldered details.
Another smaller green board is placed near the lower left.
Then a compact grey mechanical assembly is set into the middle, with small metal parts and a dark circular wheel, suggesting the inner workings of a \textbf{cassette} player being built where the \textbf{cassette} used to be.
The view shifts closer to more mechanical pieces : pale metal plates, circular reel areas, dark \textbf{hubs}, screws, and a green circuit strip.
Hands guide these parts into place, sliding a small circuit board into the side of the metal \textbf{cassette} mechanism.
Two round silver reel-like discs settle into a flat rectangular metal body, each with a black central spindle.
The parts look precise and miniature, filling a space about the size of the \textbf{original} \textbf{cassette} case.
The assembled mechanism is now shown inside a compact rectangular player.
The top portion has tiny controls and a label reading “ STEREO. ” A separate Sony \textbf{cassette} remains lying above it in the background as a size comparison.
The hands bring a front cover down over the exposed workings.
As the cover closes, the device becomes a finished silver Sony Walkman.
Across the top front, the text “ SONY ” appears on the left and “ WALKMAN ” in red on the right.
A wide rounded rectangular window spans the lower front, through which the two circular reel shapes are visible.
Small buttons line the top edge.
The finished Walkman sits alone on the grey surface, neat and compact, with the \textbf{cassette} still above it.
A white earphone cord is placed across the front, looping diagonally over the Walkman and trailing off to the side.
Large white title text fades over the product : “ SONY ” in huge capital letters, with “ THE ONE AND ONLY ” below it.
The Walkman remains visible behind the translucent lettering, partly crossed by the white cord.
The final image changes to a store display card standing upright on a dark surface, with a pair of white earphones lying to its left.
The display shows a picture of the Walkman in a dark square near the lower half.
Large blue text at the top reads, “ Listen to the new Sony Super Walkman.
You might win to the tune of \$25,000. ” At the very bottom, small white legal text appears, including “ No Purchase Necessary, ” “ Entry Cards Available at Participating Retailers, ” and an offer expiration date in November 1983, followed by the usual restriction that the offer is void where prohibited by law.

% matched lemmas: cassette, hub, original
\end{textsample}
