\begin{textsample}{NEG Dim 4 – 1950 – Score 1.00 – 1950/tv\_com\_1950\_91.txt}  \label{ex:f4_neg_068}
A young adult woman with a polished 1950s look faces forward against a plain light background.
She has a short, full, curled hairstyle and wears a dark sleeveless dress with thin straps.
At first she wears large, dark, round eyeglasses.
Smiling, she lifts one hand to the glasses, lowers them down her nose, then removes them entirely, revealing heavy eye makeup and a bright, confident expression.
Still addressing the viewer, she brings up a small round compact mirror.
She opens it and holds it near her chin, looking into it while using a slim cosmetic pencil or applicator around her eyebrows and eyes.
She works carefully, glancing between the mirror and the viewer, then smiles and closes or lowers the compact.
The setting remains minimal and staged, with no visible office background yet, just the woman and the plain backdrop.
She turns her head to the side as if responding to someone offscreen.
Her posture shifts from presenting to acting as an assistant.
A large flat folder or portfolio with papers is handed in from the right, and she reaches out with both hands to receive it.
She smiles, accepting the bulky item, and then carries it carefully in both arms.
The view widens to reveal a boxy office copying machine on a waist-high cabinet or desk beside her.
The machine has a broad flat area on the left, a rectangular control panel on the front, and an open output area on the right.
The woman stands beside it with the large folder open in her arms.
She positions herself at the machine, then turns toward the work surface.
In close detail, the folder is opened over the copier ’s glass copying area.
A dark hinged cover or platen lid is raised, exposing the flat glass beneath.
She slides a page or open binder section into place on the glass, aligning it carefully.
A shiny binder clip or ring mechanism is visible near the edge of the papers.
She lowers the cover over the material, pressing it flat so the document lies against the glass.
Her hand then moves to a small rectangular guide or handle on the copier ’s top surface, adjusting it into position.
She reaches to the front control panel.
The Xerox machine ’s panel is visible with a large round knob set into a numbered scale ; the word “ Xerox ” can be seen on the panel, and a label above identifies it as the 914 copier.
Below the knob are rectangular buttons, including one marked “ Push ” and another marked “ On. ” She turns the round control knob, then presses the “ Push ” button.
The machine is shown working from the outside : the lid remains closed over the \textbf{original} document, and the front panel and dark output opening sit to the right.
Later, a clean white sheet begins to emerge from the output slot.
The paper slides forward into a tray-like opening.
A hand reaches in, smooths the sheet with an open palm, and pulls it free, emphasizing that it comes out as a dry sheet of ordinary paper rather than a wet print.
The copied page is lifted from the machine and brought over to the open folder or binder lying on the work surface.
Several pages are visible inside, some with faint writing or diagrams.
The woman places the fresh copy on top of the stack and straightens it, aligning the pages neatly.
The open binder shows rings along the spine and a spread of papers on both sides, suggesting she is comparing or organizing the copied material with the \textbf{original}.
She then bends slightly over the desk, gathers the papers and folder back onto the flat portfolio, and turns away from the machine.
With the papers stacked on the portfolio, she stands upright again, smiling broadly.
She holds the portfolio at chest height, the copied documents resting on top, and faces toward the viewer for a moment as if presenting the successful result.
Finally she turns to her right and extends the portfolio outward with both hands toward someone offscreen, offering the completed copies.
She keeps a pleasant, assured smile, holding the stack level and steady as though handing it back to her boss.
The commercial ends with her still poised beside the plain background, the finished paperwork displayed on the tray-like folder in her hands.

% matched lemmas: original
\end{textsample}
