\begin{textsample}{NEG Dim 4 – 2010 – Score 1.00 – 2010/tv\_com\_2010\_15.txt}  \label{ex:f4_neg_088}
The commercial begins with a close-up in a modern office-like setting : a person in a light purple shirt adjusts or holds a small white desk fan on a desk.
Nearby are a computer mouse, keyboard or laptop, and papers, suggesting a work surface.
It then cuts to a series of older-looking scenes showing electric fans from different periods.
One black-and-white shot shows a man in profile working beside an old metal-caged desk fan.
Another aged, sepia-toned or early color shot shows a large fan in the foreground and a young woman seated at a desk in the background.
The commercial then moves to a retro domestic kitchen, where a red-bladed fan sits on a countertop while a woman stands in the background.
A closer view focuses on the red fan ’s circular guard and spinning blades.
Next, another vintage-style domestic scene shows a man handling a suitcase or case on a bed while a blue-bladed desk fan runs prominently in the foreground.
These shots visually present a sequence of conventional bladed fans across time and settings.
The commercial then shifts to a stark black background with a modern white desk fan centered in the frame.
A following abstract shot shows a translucent, stylized view of spinning fan blades or airflow, with pale blue-white shapes moving against a dark background.
A close-up shows a finger pressing one of several grey \textbf{control} buttons on the base of a white fan.
This is followed by a head-and-shoulders shot of an older grey-haired man speaking directly toward the camera in a modern, softly lit interior ; no audio content is visible from the frames.
The visuals then move into close-up product imagery : a curved, glossy ring-like surface appears against a black background, suggesting the form of a bladeless fan.
The final product shots reveal a Dyson Air Multiplier fan : a cylindrical base supporting a circular open ring, lit with blue accents, on a black reflective surface.
Readable on-screen text appears beside the product : - “ dyson air multiplier ” - “ No blades.
No buffeting. ” - “ Learn more at dyson.com ” - “ Available at ” followed by retailer logos, including Bed Bath \& Beyond, Best Buy, Sears, and Target - “ and other retail locations. ” The last frame holds on the product and the same text, with the circular fan ring facing forward against the black background.

% matched lemmas: control
\end{textsample}
