\begin{textsample}{NEG Dim 4 – 2010 – Score 1.00 – 2010/tv\_com\_2010\_9.txt}  \label{ex:f4_neg_076}
A wide, misty highway stretches across a bridge under a cloudy sky with bright sunlight breaking through.
In the distance, a strange purple gas-pump-like machine hovers or stands over the road on thin mechanical legs.
Several long black hose arms curl out from it like tentacles, each ending in fuel nozzles, giving it the look of a threatening robot blocking the roadway.
On the roadside, the Michelin Man appears : a large white mascot-like figure made of rounded tire-like segments, with a smooth white face and small dark eyes.
He wears a blue diagonal sash with “ MICHELIN ” in white letters.
He stands beside a dark gray sedan, facing the car as if interrupted on his way toward the mechanical gas-pump creature.
Inside the sedan, two office-dressed adults look out through the open side window at him.
A middle-aged man with short hair, wearing a dark suit, white shirt, and tie, sits nearest the window, looking startled and attentive.
Beside him, a woman with long light-brown hair, wearing businesslike clothing, leans forward toward the window.
She appears animated and intent, speaking to the Michelin Man while gesturing from inside the car.
The steering wheel and dashboard are visible near her, and the highway guardrail and bare trees run along the background.
The Michelin Man stands calmly outside the car, looking down toward the people.
His expression is mild and slightly reserved.
The woman continues leaning toward him, at times smiling, at times looking serious, as if trying to persuade him.
The man ’s expression shifts from surprised to amused ; he smiles broadly while watching the exchange.
The woman raises one hand with her palm partly open, then brings both hands closer together near the window, emphasizing her point.
Throughout, the Michelin Man remains large and still in the foreground, his rounded white body filling much of the left side of the scene, while the two people remain framed by the car window on the right.
A wider view reveals the full situation : the dark sedan is stopped on the highway, the two businesspeople are still inside, and the Michelin Man stands in the lane between the car and the \textbf{looming} purple gas-pump robot ahead.
The robot ’s hose arms wave outward in the hazy light, and its spindly legs straddle the road.
After the conversation at the car, the Michelin Man turns away from the sedan toward the threat.
He bends his knees and lowers his rounded arms into a ready stance, preparing to confront the animated gas-pump machine.
The commercial ends on a clean white background with the Xerox branding.
Large red lowercase letters spell “ xerox ” beside a glossy red-and-white spherical Xerox symbol.
Beneath the logo, pale gray text reads, “ Ready For Real Business. ”

% matched lemmas: loom
\end{textsample}
