\begin{textsample}{NEG Dim 4 – 2000 – Score 1.00 – 2000/tv\_com\_2000\_63.txt}  \label{ex:f4_neg_078}
The commercial begins with a nearly black frame, with only a small red heart-shaped watermark/logo visible in the lower-right corner.
After several seconds, the scene cuts to a bright domestic interior.
A woman is partly visible on the right, seen from behind or side-on, while a glowing white, smoke-like vertical form appears in the room.
The room contains household furnishings such as a cabinet, framed picture, vase, and plant.
The glowing form resolves into a bald, human-like male figure dressed in white.
He has an exaggerated, polished, mascot-like appearance and is surrounded by a bright halo or glow.
He faces forward and gestures with his hands.
In the next shot, the woman stands beside him in the room.
She wears a light-colored top over a red shirt and holds a long handle or cleaning tool.
The glowing male figure stands confidently with one hand on his hip, also looking toward her.
The commercial then cuts to a close-up of a hand holding a blue, pointed, triangular cleaning attachment with multiple holes.
The background is bright and softly focused, suggesting a bathroom or tiled area.
A split-screen product demonstration follows.
Two white, pointed pad shapes are shown side by side.
The left side is labeled “ Mopping Pad, ” and the right side is labeled “ Scrubbing Pad. ” The scrubbing pad has visible blue horizontal bands.
Next, an overhead view shows the woman using a long-handled cleaning tool on a tiled shower or bathroom wall area.
Brown/orange tiles and grout lines are visible, and the tool reaches down into the corner.
A second demonstration shows the tool being used inside a white bathtub near a chrome faucet, scrubbing across the tub surface.
The woman is then shown attaching or adjusting the blue-and-white cleaning head on the end of the handle.
She looks down at the tool while holding it close to her body.
The setting shifts to a bright bathroom counter with a sink.
Small colored marks or smudges are visible on the white countertop.
In the next shot, the cleaning tool moves across the white surface near a toilet or bathroom fixture, wiping over the area where the marks are located.
The final frame is a product pack shot.
A box labeled “ Mr.
Clean MagicReach ” is displayed next to the assembled cleaning tool and a white pad with blue stripes.
A website address appears along the bottom : “ www.mrcleanmagicreach.com. ” The red heart-shaped watermark/logo remains in the lower-right corner.

% matched lemmas: 
\end{textsample}
