\begin{textsample}{NEG Dim 4 – 1960 – Score -3.00 – 1960/tv\_com\_1960\_93.txt}  \label{ex:f4_neg_024}
The commercial is in black and white, with a small “ RARER ” watermark visible near the upper right in most sampled frames. - **Frame 1:** The clip begins on a fully black screen. - **Frame 2:** A person is kneeling beside an open, flat rectangular case or appliance on the floor.
Inside it is a circular coiled component, likely a hose or \textbf{cord}, arranged in a spiral.
The person ’s hands are reaching into or arranging the contents. - **Frame 3:** The view changes to a close-up looking down into the open case.
Several vacuum-cleaner parts or attachments are packed inside, including hose-like tubes and nozzle-shaped pieces.
A central component has a visible Hoover-style logo on it. - **Frame 4:** A low side view shows the rectangular appliance/case closed or partially closed, sitting on small wheels or rollers near the floor.
A \textbf{cord} or hose-like line extends from the side. - **Frame 5:** A close-up shows a round brush attachment with dense bristles around the edge.
Overlaid text is visible but partly obscured by the brush ; readable portions include “ Extra cleaning power ” and “ to handle, ” while the rest is unclear. - **Frame 6:** The scene shows a storage area or closet with shelves holding folded linens or towels.
A louvered door or vented panel is visible on the left.
The lower part of the closet is dark and open, suggesting storage space, though no clear product action is visible in this sampled frame. - **Frame 7:** The commercial ends on a product shot of a \textbf{compact} rectangular vacuum cleaner case.
Large on-screen text reads : “ New Hoover \textbf{Portable} Vacuum Cleaner. ” The appliance is shown at an angle with a handle or attachment area visible on the front.

% matched lemmas: compact, cord, portable
\end{textsample}
