\begin{textsample}{NEG Dim 4 – 1970 – Score 2.00 – 1970/tv\_com\_1970\_45.txt}  \label{ex:f4_neg_015}
The commercial is a simple hand-drawn animated scene with thin black outlines and sparse colour.
It begins in what looks like a public indoor corridor or shopping area, drawn mostly in pale grey lines.
At the centre stands an olive-green self-service film development machine.
On its upright back panel, large pink letters read “ FILM, ” with “ SELF SERV ” above and “ DEVELOPMENT ” below.
Purple film envelopes or packets sit on the machine ’s slanted counter.
A slim, light-haired man in a plain shirt and trousers stands on the right side of the machine, holding a pen and writing on one of the forms.
To the left is a heavier, older-looking man in a suit and tie, watching with a faintly amused or skeptical expression.
Other lightly sketched passersby move in the background, including a woman with a child in a stroller, giving the setting the feel of a mall walkway.
The self-service machine remains central as the slim man continues filling out the form.
He looks uncertain and slightly worried, glancing toward the machine while the suited man stands beside him.
The words “ SELF SERV FILM DEVELOPMENT ” are now clearer, and the machine ’s slot and purple envelopes are prominent.
The man reaches toward the slot and the envelopes, then pulls one purple packet away from the machine.
His posture becomes more animated, with one arm extended across the counter as if reacting to something about the pickup arrangement.
The suited man, still on the left, looks on with his hands partly raised.
The scene then widens to show that this self-service setup is inside a large storefront-like window or display area.
To the right, outside that window, a small red cartoon figure appears on a thin stand.
The figure has a white face, a large black top hat, and a red, rounded body with little outstretched shapes, like a mascot or caricature.
Behind the glass, the two men and the self-service machine remain visible, now smaller and tinted bluish by the window.
The building around them has a curved, modern-looking facade with broad blue glass panels and white framing.
The view broadens further to a parking area in front of the curved building.
Several cartoon cars drive through the foreground, including a red car, a green car, and a purple car.
As the parking-lot scene fills the picture, a small Fotomat drive-thru booth comes into view in the foreground.
It has a bright yellow roof with large dark blue letters spelling “ FOTOMAT ” across the front.
The booth has blue window panels and sits amid simple green shrubs.
Cars circulate around it, emphasizing that customers can pull up without leaving their vehicles.
A red convertible stops at the Fotomat booth.
Inside the booth, a smiling female-presenting attendant with large fluffy white hair wears a yellow shirt under a dark blue vest or jumper.
She leans out of the service window toward the driver.
The driver is an older-looking, light-haired man seated in the red convertible, facing the booth.
The attendant reaches down with a yellow envelope or claim form, and the driver ’s side of the car is close enough for the exchange to happen directly through the open car window.
A close view shows the yellow Fotomat form being filled out.
The top reads “ FOTOMAT ’S PICTURE PICKUP PROMISE ” in bold blue letters.
Beneath it is a line that says the pictures will be ready on a specified day, followed by small checkboxes labeled with days of the week.
A hand holding a red pen places a large check mark in one of the weekday boxes.
The form is attached to a larger yellow envelope with a perforated edge.
The top portion is then torn away along the perforation, becoming a separate slip.
The driver in the red convertible holds the small yellow slip up in his hand and smiles, looking at it as though he now has a clear pickup promise.
The Fotomat attendant is then shown closer at the booth window, still smiling and holding the larger yellow envelope on the counter.
The car ’s red door frame and steering wheel are visible in the foreground, while the attendant stands behind the blue window panels of the booth.
The driver appears again alone in the red convertible, looking forward with a surprised or questioning expression, one hand near the steering wheel and the other resting near the car door.
The scene then returns to the attendant against a blue background.
She holds up a small rectangular box-like package with coloured stripes on its side, presenting it at shoulder height while smiling.
In the context of the Fotomat pickup promise, the package visually represents the free film offer mentioned in the ad.
At the end, the picture changes to a black title card with a white inset drawing above the text.
In the inset, the slim man from the self-service machine stands holding a purple envelope, while the small red top-hatted cartoon figure stands nearby behind a shorter character.
At the bottom, large white text reads “ The Fotomat Picture Pickup Promise. ” Smaller text underneath states that the offer is good only for Fotomat and Kodak film and that details are at participating stores.

% matched lemmas: 
\end{textsample}
