\begin{textsample}{NEG Dim 4 – 1960 – Score -3.00 – 1960/tv\_com\_1960\_38.txt}  \label{ex:f4_neg_028}
The commercial opens with a reddish, low-contrast exterior shot showing two older cars in profile, facing each other or parked near each other in a hazy outdoor setting.
The image is dark and tinted, with a “ Nostalgic X’er ” watermark at the lower right.
It then cuts to a view from inside or alongside a car.
A driver ’s head is seen in profile, possibly through a window or windshield reflection, with a bright outdoor landscape visible beyond.
The scene appears to be on a road or open area, but the details are washed out.
The next frame is very overexposed.
Only faint shapes of vehicles or structures in a bright outdoor scene are visible, and specific objects are difficult to identify.
Later, the commercial shows a close view of part of a car, including the windshield and roofline or side window area.
The background includes angular structural elements, possibly part of a service station or roadside architecture.
The scene then shifts to several large barrels or drums arranged on a pallet or platform.
The barrels have printed labels ; the word “ NICKEL ” is clearly visible on at least two of them, and small labels appear above.
The setting looks industrial or service-station-related.
Next, there is a bright close-up of \textbf{mechanical} or fuel-service \textbf{equipment}.
A sign or panel with large lettering is partly visible on the left, but much of the text is overexposed and hard to read.
A rectangular framed sign or display sits on the right side of the shot.
The final shots focus on a large roadside sign reading “ Sinclair, ” with the company ’s dinosaur logo beneath the word.
The sign is \textbf{mounted} on a pole against a \textbf{plain} sky or lightly colored background.
The last frame remains on this Sinclair sign, making it the final visual emphasis of the commercial.

% matched lemmas: equipment, mechanical, mount, plain
\end{textsample}
