\begin{textsample}{NEG Dim 4 – 1960 – Score 1.00 – 1960/tv\_com\_1960\_80.txt}  \label{ex:f4_neg_040}
In black and white, the commercial opens tightly on the rear of a fire truck, where a large rectangular warning sign reads “ KEEP BACK 500 FEET ” in bold white block letters.
The view shifts to pieces of firefighting gear : tall rubber boots standing on the pavement as someone steps into them and pulls at the tops, then helmets and tools hanging from the side of a fire engine.
A firefighter climbs onto the truck ’s side step near metal valves, hoses, and equipment.
The same “ KEEP BACK 500 FEET ” sign appears again, followed by silhouetted firefighters beneath an overhead structure as a long ladder rises diagonally across the scene.
The fire truck moves through city streets with its ladder stacked along the side and equipment packed onto running boards.
As it drives, the view settles on one of its large tires, where the word “ Firestone ” is clearly visible on the sidewall.
The montage broadens to other kinds of vehicles and wheels.
A flatbed truck carries rows of heavy rectangular bundles or crates, secured between upright stakes.
In a rural field, a tractor pulls farm equipment through rough soil, its large rear tire rolling over stubble and dirt.
A long station wagon drives along a road beside a body of water, with several passengers visible through the side windows.
A large industrial truck with a long elevated framework travels over sandy, rutted ground, suggesting heavy outdoor work.
A young child rides a small tricycle or toy bike along a sidewalk while an adult woman, wearing a skirt and light top, runs alongside and steadies it with her hands ; she stretches one leg back as she keeps pace, helping the child move forward.
A low open car, possibly a small sports car, drives away down a tree-lined road, framed by dark foliage on both sides.
The sequence continues with wheels in more demanding settings.
A jet airliner comes in low over a runway, its landing gear down ; the underside of the plane and its clustered wheels fill the scene as they approach the pavement.
The side of the aircraft carries the partly visible words “ FLY EASTERN. ” A person pushes a lawn mower through tall grass near garden plants, with the mower ’s small wheels rolling over the lawn.
A bulldozer or earthmover pushes a broad wall of dirt forward with a wide front blade, the soil spilling and crumbling in front of it.
In a marshy or muddy outdoor area, a rugged vehicle with oversized tires drives through shallow water, reeds and trees around it.
A small golf cart with two seated adults moves away along a smooth path bordered by dense hedges.
Then a very large cylindrical load, resembling industrial or oil-field equipment, is hauled on a multi-wheeled \textbf{trailer} through a street scene with utility poles and other vehicles in the background.
A close view follows the wheels of a bicycle as a rider pedals along a paved surface.
The thin tires spin rapidly, with the rider ’s shoes pressing the pedals in a steady cycle.
Next, on a wet road in the rain, a car tows a large white cabin boat on a \textbf{trailer}.
Water glistens on the pavement, reflections shimmer beneath the tires, and other cars sit or pass nearby.
The boat ’s hull dominates the scene as the \textbf{trailer} rolls by, emphasizing the many small wheels underneath.
A brief close-up shows a car tire turning beside a rounded fender.
A child then rides in a small pull wagon on a sidewalk.
The wagon ’s side panel is clearly labeled “ Firestone CRUISER, ” with the Firestone name in a lighter inset panel and “ CRUISER ” in bold letters to the right.
The child, seen from the torso down, sits inside with one arm resting over the wagon ’s side and one leg bent, while the wagon ’s whitewall wheels roll smoothly.
The Firestone name fills the screen in a close view on the wagon side.
The final action shots return to roads and heavy traction.
A full-size car drives through rain on a slick urban road, its front grille and headlights approaching low to the wet curb before it passes close by, throwing spray from the tires.
Then a rugged vehicle pulls a boat or boat-like \textbf{trailer} through a dusty, rough surface ; dust billows around the wheels and partly obscures the bodywork as the tire churns through the ground.
The dust thickens until the image becomes hazy.
Out of the haze emerges the Firestone brand graphic : a pale outline map of the United States above the large script word “ Firestone, ” displayed as the closing visual emblem.

% matched lemmas: trailer
\end{textsample}
