\begin{textsample}{NEG Dim 4 – 1950 – Score -5.00 – 1950/tv\_com\_1950\_113.txt}  \label{ex:f4_neg_009}
The commercial begins with a simple black-and-white cartoon style.
A small white rectangular panel sits centered against a dark surrounding background.
Inside the panel is a line-drawn cartoon woman with large, wavy hair, a small nose, and a short dress or apron-like garment.
She stands facing slightly to the side, with a neutral or mildly concerned expression.
The scene then changes to a wider white patterned background within the same dark outer frame.
The cartoon woman is now shown standing near a wall-mounted telephone on the right.
She holds the telephone receiver to her ear.
The phone has a rotary \textbf{dial} on its front and a coiled \textbf{cord} connecting the receiver to the wall \textbf{unit}.
The camera or framing then moves closer, filling more of the screen with the light patterned background.
The woman remains on the right side of the frame, still holding the receiver and facing the wall phone.
The rotary-dial phone is clearly visible, \textbf{mounted} vertically.
A closer shot follows.
The woman ’s head and upper body dominate the left side of the frame, while the wall phone is on the right.
She holds the receiver beside her face, and the coiled \textbf{cord} curves between the receiver and the phone.
Her facial expression appears attentive, as if listening or speaking, though no audio content can be inferred from the frames.
The final frame switches to a text card on a \textbf{plain} light background.
Large hand-lettered text reads : “ Order an Extension phone in color for your Kitchen. ” The word “ your ” is underlined.
A small black drawing of a rotary desk telephone appears to the left of the text, and a small wall-mounted phone with a \textbf{cord} appears to the right.
The layout visually emphasizes ordering an additional phone for the kitchen.

% matched lemmas: cord, dial, mount, plain, unit
\end{textsample}
