\begin{textsample}{NEG Dim 4 – 2000 – Score -3.00 – 2000/tv\_com\_2000\_106.txt}  \label{ex:f4_neg_041}
A dark blue Ford Focus sedan travels along a winding two-lane mountain road bordered by grassy hills and rocky cut slopes.
The road curves sharply back and forth, with bright white lane markings snaking through the landscape under a blue sky with streaky clouds.
Inside the car, a young adult man with short dark hair and light skin drives.
He wears an orange short-sleeved polo shirt and a seat belt, his hands steady on the wheel and his face focused ahead.
Beside him sits a young adult woman with light skin and short dark brown hair, wearing a pale pink collared shirt and a seat belt.
A glass sunroof above them shows sky and clouds.
The woman looks toward the driver, then down and back up, appearing concerned or insistent, while the man keeps his eyes mostly on the road.
The car is shown from outside again, low and close to the front as it moves along the curving pavement.
Its headlights, grille, and blue body catch the sunlight.
The road rises and bends beside rocky hillsides, emphasizing the car ’s movement through tight curves.
Back inside, the woman turns toward the man and speaks with an expectant look ; he glances over briefly, then ahead again.
She softens into a small smile, watching him.
Close views highlight the car in motion : a spinning front wheel, the smooth road rushing past, and the rear corner of the sedan with the chrome “ focus ” badge beside the red taillight.
The blue Focus continues along open hillside roads, its body leaning slightly with the bends.
The woman smiles from the passenger seat, then the driver looks back toward her with a faint, knowing expression.
The car pulls off onto the shoulder of the mountain road.
The front driver ’s door stands open on the roadside, with the curving highway and green hillside behind it.
White on-screen text appears near the bottom : “ the best small car to drive, ” followed by smaller text, “ Automobile Magazine, Feb. 02. ” The woman remains seated inside, belted in, looking across the cabin while the man, now outside in his orange shirt, goes to the rear of the car.
Seen from inside the open hatch or trunk area, he lifts and holds the hatch overhead, then looks down into the cargo space as if checking for something.
The same magazine-quote text remains across the bottom.
A close-up shows a hand wearing a metal wristwatch grasping a black exterior door handle on the blue car.
The woman is then seen through the side window from outside.
She sits inside with her seat belt on, looking up toward the man standing just outside the car.
She smiles tightly, then raises one hand and gestures near her temple in a small teasing or clever motion.
The man stands beside the car on the shoulder, relaxed, one hand near the side mirror or door, smiling as he looks back toward her.
The mountain road curves away behind him under dramatic clouds.
The Focus returns to motion on the open road.
Large white text appears over the pavement : “ 100,000-Mile ” and beneath it “ Powertrain Coverage. ” Smaller fine print below refers to a “ 100,000-Mile 5-year Focus Extended Service Plan ” and “ Powertrain Limited \textbf{Warranty} in Florida, ” followed by “ See dealer for details. ” The blue car drives toward and past the viewer on the winding road, then appears far away on a hillside road cutting across green slopes.
Near the end, the woman is now shown driving, hands on the wheel, seen in profile from inside the car.
Her short dark hair frames her face as she looks ahead, then glances slightly toward the passenger side with a pleased, confident expression.
Exterior views show the blue Focus continuing along the scenic road, framed by a bright sky and rolling hills.
The final image shows the Ford oval logo large in the sky above the road.
The blue Focus drives away along the double yellow center lines into the distance.
At the bottom, small white text reads “ www.fordvehicles.com. ”

% matched lemmas: warranty
\end{textsample}
