\begin{textsample}{NEG Dim 4 – 1980 – Score -4.00 – 1980/tv\_com\_1980\_72.txt}  \label{ex:f4_neg_043}
The commercial opens with a very dark, low-contrast shot.
A person is seen from behind or in silhouette in an interior space, but the setting and details are difficult to make out.
The scene then cuts to a brighter office-like interior with warm-toned walls and horizontal blinds.
A woman with short dark curly hair, wearing a light-colored blazer and a white blouse or scarf, leans forward beside a desk or partition.
A framed picture/poster is visible on the wall behind her.
She appears to be looking toward someone off-camera.
The next shot shows an older bald man wearing large glasses, a dark suit, white shirt, and tie.
He is framed in close-up against a light wall with framed items behind him.
The commercial cuts back to the woman in close-up, still leaning forward and looking attentive.
A following shot shows the older man moving or turning near a doorway or partition, partly seen from behind/side.
The setting still appears to be an office.
The focus then shifts to a small \textbf{portable} computer on a desk.
It has a \textbf{compact} keyboard, a wide display area above the keys, and a Radio Shack-style product label on or near it ; some of the small label text is not fully readable in the frame.
A hand reaches toward or steadies the device.
Office objects surround it, including papers, folders, and a small potted plant.
A later close-up shows hands typing on the \textbf{compact} computer ’s keyboard.
The display screen is visible above the keys, though the screen content is not legible in the sampled frame.
A pair of glasses or a dark cable-like object lies nearby on the desk.
The commercial then presents the \textbf{portable} computer against a dark background like a product display.
Large white text appears below it : “ From \$799. ” Under that, a higher price, apparently “ \$1,099. ”, is shown crossed out.
Near the end, the layout changes to a black background with an inset image of the older man seated at a desk, holding and reading papers.
Office \textbf{equipment}, including a monitor or computer terminal, is visible behind him.
Large on-screen text appears below the inset image : “ RadioShack ” in red, followed by “ Model 100 now on sale ” in white.
The final frame holds the same end-card arrangement : the older man in the inset office scene above, with the text “ RadioShack Model 100 now on sale ” below.

% matched lemmas: compact, equipment, portable
\end{textsample}
