\begin{textsample}{NEG Dim 4 – 2020 – Score -1.00 – 2020/tv\_com\_2020\_119.txt}  \label{ex:f4_neg_084}
A Black woman worker stands outdoors at an industrial energy facility under a blue sky.
She faces forward, wearing a white hard hat with the red ExxonMobil name on the front, clear safety glasses, and a tan button-up work shirt with her name, “ Regina, ” embroidered on it.
Long black braids fall over one shoulder, and a bright yellow safety device is clipped diagonally across her chest.
Behind her are refinery-like metal structures, pipes, towers, and stacks.
As she speaks, white subtitles appear near the bottom, including the message that the world needs ways to reduce carbon emissions, especially for heavy industry.
The scene changes to a white male worker standing in a busy port or shipping terminal.
He wears a hard hat with goggles on it, a red high-visibility vest with reflective stripes over a dark shirt, orange earplugs hanging around his neck, and another yellow safety device clipped to his chest.
Massive black crane structures rise behind him, with stacked multicolored shipping containers and the dark side of a large ship to his right.
He faces forward and speaks calmly, standing squarely on the paved dock area.
Inside a dim, professional control room, a bearded man in a bright blue ExxonMobil work shirt faces forward.
He has short dark hair, a salt-and-pepper beard, orange earplugs around his neck, and dark safety glasses hanging from the front of his shirt.
Computer monitors and control panels glow softly around him in the background, suggesting an operations center.
A woman in a large warehouse stands between long rows of huge silver metal coils, each coil stored upright on wooden supports.
She wears a white hard hat, a red ExxonMobil shirt, and a reflective safety vest with yellow trim.
The high ceiling is dark, with rows of overhead lights stretching into the distance.
She faces forward while subtitles at the bottom refer to “ carbon capture. ” In a laboratory, a woman with long dark hair and glasses stands in a navy ExxonMobil lab coat over a white shirt.
Laboratory benches, glassware, equipment, pipes, and bright windows fill the background.
She faces forward, and the subtitle mentions “ clean energy from hydrogen. ” The setting is clean and technical, with cool blue-gray lighting.
A man in a light blue dress shirt stands outdoors in a modern urban setting between tall glass-and-concrete buildings.
He wears dark-framed glasses and faces forward, with greenery behind him and bright daylight filtering through the city space.
A subtitle at the bottom asks, “ So, who are we? ” The view returns to Regina at the industrial facility.
The ExxonMobil name is clearly visible on her white hard hat.
She smiles as she speaks, and the subtitle reads, “ Believe it or not, ExxonMobil. ” The setting behind her remains a large refinery or industrial plant, with vertical stacks, pipe racks, and metal frameworks.
As she continues, the view widens so more of her full work outfit is visible : tan shirt tucked into dark work pants, a belt, and an \textbf{ID} badge clipped near her hip.
She remains centered and confident, standing on a wide paved area with the industrial structures extending behind her.
Subtitles say these solutions could help businesses “ like yours. ” The port worker reappears in a wider view, now shown from head to knees.
He stands on the dock with cranes overhead, stacked containers in the background, and \textbf{trailers} or port equipment nearby.
His red reflective vest and yellow chest device stand out against the dark ship and industrial surroundings.
A subtitle at the bottom says, “ or yours... ” The woman in the steel-coil warehouse is shown farther back, standing centered in the aisle between the two long rows of silver coils.
She clasps her hands at her waist while facing forward.
The symmetrical rows of metal coils recede into the distance on both sides, with a bright opening far behind her.
The subtitle again says, “ or yours. ” Regina appears close again against the refinery background.
As the line “ Heavy industry with low emissions ” appears in subtitles, the industrial scene behind her begins to change visually : the background starts to bend and curve away from a normal horizon into a stylized, miniature globe-like world.
She remains in front, wearing the same hard hat, safety glasses, tan shirt, dark pants, yellow safety device, and \textbf{ID} badge.
The background fully transforms into a small spherical “ world ” behind Regina on a clean white backdrop.
Around this globe are miniature industrial and transportation elements : refinery towers, large silver cylindrical structures, pipework, construction equipment, stacked shipping containers, a red ship on blue water, and sections of industrial buildings.
Regina stands in front of this circular world, smiling.
She places her hands on her hips in a confident pose while the subtitle reads, “ Let ’s deliver. ” The commercial ends on a plain white screen with the red ExxonMobil logo centered.
Beneath it, in small gray text, is “ ExxonMobil.com, ” with small musical-note symbols below.

% matched lemmas: id, trailer
\end{textsample}
