\begin{textsample}{NEG Dim 4 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_118.txt}  \label{ex:f4_neg_047}
The commercial opens on a nearly uniform dark reddish-brown screen with no discernible objects or people visible.
It then cuts to a warmly lit, orange-tinted domestic interior.
A young girl with light brown hair, wearing a light blouse and pinkish garment, smiles while looking down into a small dark bowl.
She holds a spoon and appears to be stirring or scooping a yellowish mixture.
Next, there is a close-up of hands working with a small round baked item or pastry on a surface.
A knife or spatula spreads a glossy dark topping, likely chocolate-colored, over the top.
The scene then shows a red-haired girl or young woman with straight bangs holding a small round food item near her mouth and taking a bite.
She is indoors, with framed pictures and patterned wallpaper visible behind her.
A close-up returns to the younger girl, who looks downward and smiles, suggesting she is watching or preparing food, though the object she is looking at is not visible in this frame.
Another child appears : a blond boy wearing large round glasses.
He holds a small topped food item with both hands and bites into it.
The background remains warm-toned and softly blurred.
The commercial then cuts to a product display on a \textbf{plain} background.
Centered is a small toy-like oven with a front door and \textbf{control} panel.
Around it are accessories : an orange stand-like tool on the left, two small round metal pans, several packet-like items, a paper insert or recipe sheet, and a white electrical \textbf{cord} extending to the right.
On-screen text at the bottom reads : “ Betty Crocker.
Easy-Bake MINI-WAVE OVEN. ” The same product layout remains on screen, now with the “ Kenner ” logo visible in the upper right corner.
The product name text remains at the bottom.
The final frame shows the same product display fading darker, with the objects and text still faintly visible as the image dims.

% matched lemmas: control, cord, plain
\end{textsample}
