\begin{textsample}{NEG Dim 4 – 1960 – Score -4.00 – 1960/tv\_com\_1960\_97.txt}  \label{ex:f4_neg_022}
The commercial opens on a studio-style shot against a dark blue-purple background.
A male performer or mannequin-like figure is centered, wearing a theatrical costume in gray, yellow, black, and white.
He has a pale face, a tall yellow cone-shaped hat, and a jacket with bold geometric trim and circular yellow decorations.
He holds objects in both hands, though their exact function is not clear in the first frame.
The next shots cut to close-ups of parts of the costume.
A gray pouch or pocket with a yellow grid-like pattern is shown on a light-colored garment.
Another close-up shows a gray fabric section with yellow oval decorations ; a flap or sleeve partly covers the upper left.
These shots emphasize the costume ’s constructed, fabric-like details and bright yellow accents.
The scene then shifts to a minimal studio view : a pale curved surface at the bottom edge and a glowing light area against the same dark blue-purple background.
This appears abstract or product-display-like, but no object is clearly visible at first.
A hand enters in later frames holding several small, shiny, reddish-brown and metallic-looking items.
The objects are clustered in the palm and are not clearly identifiable from the sampled frame.
The same or a similar hand then holds a yellow cone-shaped object with a soft, fabric-like rim, resembling the tall hat seen on the performer.
A close-up follows of the rim, with a finger pressing into or opening the top edge, suggesting the object is flexible or hollow.
The commercial then returns to abstract studio imagery : a horizontal pale surface below a hazy blue-purple background.
No specific product or person is visible in these frames.
Near the end, the costumed figure reappears in a medium shot.
He is again centered against the gradient studio background, wearing the tall yellow hat, gray jacket, yellow bow-like detail at the neck, and yellow trousers.
A white rectangular or folded object is now positioned above or attached to the top of his hat.
His posture is upright and frontal.
A separate product shot follows : a small, box-like device sits alone on a \textbf{plain} pale blue-green background.
It has a light-colored rectangular base and a darker top panel.
On the left side of the top is a circular \textbf{dial} or turntable-like element with markings ; on the right is a flat rectangular lid or panel.
A small protruding \textbf{knob} or screw is visible near the top edge.
The exact device type is not specified visually in the frame.
The final frames show a static brand card.
Large white text reads “ RCA VICTOR ” on a blue-green background.
Below and to the left is the red circular RCA logo.
To the right is the familiar image of a white dog with a dark ear looking into the horn of an old \textbf{gramophone}.
Beneath the image, white text in quotation marks reads “ HIS MASTER ’S VOICE. ” The commercial ends on this RCA Victor branding screen.

% matched lemmas: dial, gramophone, knob, plain
\end{textsample}
