\begin{textsample}{NEG Dim 4 – 1960 – Score -1.00 – 1960/tv\_com\_1960\_119.txt}  \label{ex:f4_neg_035}
The commercial opens with an abstract, space-like image on a nearly black background.
Thin red, orange, and yellow lines stretch across the screen like beams of light or electronic pathways.
They converge near the center into an hourglass shape, with small star-like dots scattered around them, suggesting signals traveling through darkness.
The image changes to a soft, out-of-focus field of colored lights.
Red, yellow, and white dots glow against a dark background, clustered mostly along the left side and lower edge.
They look like distant city lights, indicator lamps, or points of communication seen through a blur.
The rest of the sequence becomes a long passage of moving light beams.
Multiple \textbf{parallel} lines in yellow, orange, red, and pale green run from the left side of the screen toward a bright vanishing point on the far right.
The lines are clean and luminous, set against deep black-green space.
At times, additional beams sweep in from the upper left, crossing above the lower group of lines.
The upper and lower streams seem to meet or pass near the same bright point on the right, creating the impression of electronic impulses racing over great distances.
The lines repeatedly shift and overlap, some appearing brighter and some fainter, like layered routes of communication moving in \textbf{parallel}.
Near the end, the abstract lines give way to a stylized globe glowing in warm orange.
The globe fills the left and center of the image, with a grid of latitude and longitude lines drawn over it and dark continent shapes visible on its surface.
Curving bright arcs wrap around the globe, suggesting transmission paths or orbital routes.
In the upper right, a small glowing object appears near the planet, resembling a man-made satellite.
As the globe remains warmly lit against the black background, the satellite-like object stays off to the right, reinforcing the idea of communication reaching around the world and through space.

% matched lemmas: parallel
\end{textsample}
