\begin{textsample}{NEG Dim 4 – 1980 – Score -4.00 – 1980/tv\_com\_1980\_91.txt}  \label{ex:f4_neg_042}
The commercial begins on a black screen.
A blue title card then appears with the words “ Splash Dance ” in large white cursive lettering.
The same branding is shown on a black rectangular product hanging against a light blue tiled bathroom wall.
The device has a dark front panel, a white lower section with \textbf{controls}, and appears to be suspended or \textbf{mounted} near the shower area.
The next shot presents two side-by-side installation views on blue tile.
On the left, the product is shown flat against the wall with on-screen text reading “ Affixes to wall. ” On the right, the product is shown hanging from or near a shower pipe, with water spraying from a showerhead, and on-screen text reading “ Clips to pipe. ” This visually demonstrates two possible ways of placing the device in a shower.
A graphic splash effect follows over a blue background, suggesting water splashing around the “ Splash Dance ” branding.
The commercial then returns to the bathroom setting.
A person is partially visible in the foreground, blurred by motion and/or water, with the “ Splash Dance ” \textbf{unit} behind them on the tiled wall.
Later, a closer shot shows a hand adjusting one of the product ’s front \textbf{controls}.
The device has two round \textbf{knobs} at the bottom and a horizontal tuning-style display above them.
The “ Splash Dance ” logo appears again on a blue background.
A close-up then shows a person showering : only part of the face, head, and hand are visible.
The person ’s hair is wet, and their hand is near the side of the head, as if washing or smoothing hair under the shower.
The final sequence uses large moving or zoomed-in yellow lettering against a dark blue background.
The letters resolve into the brand name “ Pollenex. ” The closing product card shows “ Pollenex ” at the top, followed by “ SPLASH DANCE ” and “ SHOWER \textbf{RADIO}. ” Beneath that is a “ Kmart ” logo, and the names “ Jatco ” and “ Payless ” appear lower on the screen.

% matched lemmas: control, knob, mount, radio, unit
\end{textsample}
