\begin{textsample}{NEG Dim 4 – 1960 – Score -6.00 – 1960/tv\_com\_1960\_95.txt}  \label{ex:f4_neg_021}
The sampled frames show a chronological progression of audio playback/recording devices and associated domestic scenes. 1. **Opening frame (0.000s):** A close-up shows an old-style \textbf{gramophone} or phonograph on a wooden cabinet.
A black disc record is on the turntable, and a curved tonearm/horn \textbf{mechanism} is visible on the right.
The image has archival film wear and overlaid markings, including “ MY, ” “ 160-172, ” and a timecode. 2. **Early scene change (2.726s):** The setting shifts to a period-style interior.
A woman in historical dress, with a large hat or bonnet, stands beside a \textbf{gramophone} with a large flared horn.
She appears to be operating or adjusting the machine with one hand.
A decorative hanging lamp is visible above. 3. **Later scene change (20.610s):** The frame cuts to a front-facing close-up of a reel-to-reel tape recorder.
Two large reels are visible behind circular covers, with \textbf{control} \textbf{knobs} and a central panel between them.
The device fills most of the frame, emphasizing the technology. 4. **Final frame (52.043s):** The scene changes to a more modern domestic interior.
A woman sits on the floor beside a low table or console holding a \textbf{compact} reel-to-reel tape recorder, flanked by two speaker-like panels or cabinet sections.
She is seated calmly, looking toward the device.
Two cylindrical pendant lights hang above, and the overall setting appears minimalist and contemporary compared with the earlier scenes.
Across the sampled frames, the commercial visually moves from older phonograph/gramophone technology to reel-to-reel tape \textbf{equipment}, pairing the devices with period-styled and then more modern domestic environments.
No dialogue, slogans, or audio content is visible in the frames.

% matched lemmas: compact, control, equipment, gramophone, knob, mechanism
\end{textsample}
