\begin{textsample}{NEG Dim 5 – 1970 – Score 1.00 – 1970/tv\_com\_1970\_71.txt}  \label{ex:f5_neg_059}
The commercial begins with a nearly black screen.
A “ Classic Commercial Archives ” circular watermark appears at lower left, and a faint “ @ClassicCommercialArchives ” watermark runs across the lower center/right.
It then cuts to an outdoor street-sign setting.
A yellow rectangular sign mounted on a post reads “ PLEASANT STREET ” in large black lettering.
The background shows greenery and a residential-looking outdoor area with trees and shade.
A fast blurred transition follows, with the sign or scene streaking horizontally, suggesting a quick camera move or graphic wipe.
The image resolves into a product shot : a box labeled “ DRISTAN ” with “ DECONGESTANT TABLETS ” beneath it.
The box is shown against a pale background, with overlaid or transitioning imagery of the earlier street sign still faintly visible.
Text on the box reads “ COLDS \& HAY FEVER ” and “ SINUS CONGESTION. ” Next, the product packaging remains faintly in the background while individual medicine items are displayed in front : a brown/orange capsule-like container or capsule form, a cluster of small round tablets or pellets, and a blue tablet/caplet-like object.
The background is mostly white or light gray, with the Dristan box ghosted behind the objects.
Later, the scene shifts back outdoors to a sunny yard or garden.
A woman is visible standing beside or near a dark-colored dog.
She appears to be bending or reaching toward the dog while holding or touching something near it.
Trees, shrubs, grass, and part of a house or porch are visible in the background.
Overlaid text at the bottom reads “ USE ONLY AS DIRECTED. ” There is also faint product-related overlay text partially visible.
The commercial then returns to the street-sign motif.
A similar yellow sign now reads “ HAYFEVER STREET, ” again mounted on a post in the same type of outdoor setting.
The final frame shows a sign-like product display mounted on the post.
It features the Dristan packaging design : “ DRISTAN, ” “ DECONGESTANT TABLETS, ” and the conditions “ COLDS \& HAY FEVER ” and “ SINUS CONGESTION. ” At the bottom of the frame, large white text reads : “ EXTRA RELIEF MEDICINE THE OTHERS DO N’T HAVE. ” The outdoor residential background remains visible behind the sign.

% matched lemmas: 
\end{textsample}
