\begin{textsample}{NEG Dim 5 – 1990 – Score 1.00 – 1990/tv\_com\_1990\_17.txt}  \label{ex:f5_neg_088}
The commercial opens in a busy studio or backstage dressing-room area.
Several people stand and crouch around a set filled with ladders, metal framework, equipment, and a vanity mirror lined with bright round bulbs.
The lighting is dramatic, with warm bulbs and colored blue and red highlights giving the space a photo-shoot atmosphere.
A young adult man with dark, wavy hair, wearing a dark jacket over a gray shirt, stands near a young adult woman.
She has shoulder-length brown hair, wears a burgundy blouse tucked into light blue jeans, and has round white earrings.
She faces him while holding a gray camcorder up to one eye, as if checking him through it.
She lowers the camcorder and smiles at him, appearing confident and encouraging.
The man is then seen more closely.
He smiles, glances down, then looks toward the camera and off to the side.
His dark hair is neatly styled with volume at the front, and he looks relaxed and pleased, as though he is ready for the shoot.
A blurred studio background with ladders and warm lights remains behind him.
The image changes to a black-and-white portrait of the same man printed on paper.
In the upper left corner, the word “ Simulation ” appears in small white text.
The portrait shows him in a dark shirt, and small white specks are visible on one shoulder, representing dandruff.
A hand holding a blue pencil or marker moves across the photo and circles the speckled shoulder area in blue, drawing attention to the flakes.
The woman appears again, now facing forward against the same studio background.
She speaks directly to the viewer with a calm, friendly expression.
Her burgundy blouse, softly styled hair, and white earrings are clearly visible.
The picture then shifts to a large close view of a white Head \& Shoulders bottle held in a hand.
The label reads “ Head \& Shoulders ” with “ Dandruff Shampoo ” underneath, and the bottle has bold curved bands of blue, red, and purple across the lower front.
After the product is shown, the woman continues speaking to the viewer, still in the studio setting.
She holds the white bottle partly visible at the lower left for a moment, then lowers it out of view while maintaining eye contact and a reassuring expression.
A demonstration follows : the back of a man ’s head fills the view, showing dark, clean-looking hair.
A hand rests on top of the hair and gently parts or lifts it to reveal the scalp beneath.
At the bottom of the screen, white text reads, “ After 3 weeks of regular use. ” In the softly blurred background, a man in dark clothing faces forward, out of focus.
The hair being examined appears thick and glossy, with no visible flakes as the hand shifts through it.
The commercial ends on a tabletop arrangement.
Two black-and-white portrait photos of the young man lie on a dark surface ; one has the blue-circled shoulder marking from the earlier “ Simulation, ” and the other shows him smiling cleanly.
At the upper left, a purple banner with white text reads, “ Great Hair Can't Have Flakes. ” Nearby are desk items including a red folder or notebook, keys, and small stationery objects.
A white Head \& Shoulders bottle is placed upright on the right side beside the photos, label facing outward with the same blue, red, and purple design.

% matched lemmas: 
\end{textsample}
