\begin{textsample}{NEG Dim 5 – 1970 – Score -1.00 – 1970/tv\_com\_1970\_3.txt}  \label{ex:f5_neg_013}
A blonde adult woman sits at a glass-topped desk in a warm, softly lit room that looks like a home office or bedroom.
She wears a pale pink collared blouse and has short, curled hair held back with a light hair clip.
In front of her are papers, a pen, and a white push-button telephone.
She leans over the papers, writing, while an adult man with dark hair appears in the doorway behind her.
He wears a white dress shirt, dark tie, and gray trousers.
As he comes closer, he seems to be speaking to her, gesturing with one hand while she keeps looking down at her work.
The man moves up behind and beside her at the desk.
She continues writing, then gradually looks more alert and turns toward him.
He brings out a small white bottle of Head \& Shoulders shampoo, holding it near his chest and then closer to her so she can see it.
The bottle has a rounded body, a long narrow neck, and a visible “ Head \& Shoulders ” label with a colored curved design.
The woman looks at him and then at the bottle, her expression shifting from concentration to interest.
She touches the front of her blouse with one hand, as if reacting to what he is saying, while he holds the bottle steady for her to inspect.
She reaches for the shampoo, and the two of them hold it between them.
The man stands close at her right side, watching her face.
She studies the bottle label, turning it slightly in her hands.
The desk lamp, papers, and telephone remain in the foreground, and behind them the room contains a bed or cushioned furniture, shelves, and framed wall art, all in warm yellow-brown tones.
The woman continues looking at the product, then lifts her eyes back to the man.
He places a reassuring hand near her shoulder as they stand very close together, the bottle still in her hand.
The scene shifts to the woman in a shower, seen through a glass shower \textbf{door} with metal framing.
Her hair is covered in thick white lather.
She massages the shampoo into her scalp with both hands, working the foam around the sides and back of her head.
A white Head \& Shoulders bottle is visible on a ledge behind her inside the shower.
She turns her head slightly from side to side as she rubs, the lather piled high and rounded over her short hair.
After the shower, the woman appears dressed and made up, now wearing a light patterned dress with a soft floral look.
Her blonde hair is dry, full, and neatly styled into smooth, rounded curls with a lifted shape at the crown.
She smiles and runs her hand lightly through the back and side of her hair, showing its volume and movement.
She turns her head, smiling toward someone off to the side, and her hair swings softly as she moves.
She walks through a bright interior area with large windows or glass \textbf{doors} and hanging plants nearby.
Her styled hair bounces as she moves.
She approaches a dark-haired adult man dressed formally in a dark jacket with a white shirt and black bow tie.
Facing him, she raises both hands to his collar and tie area and adjusts his bow tie or lapels.
He looks at her, then smiles.
She keeps her hands lightly around his collar as they stand close together in a bright, plant-filled entrance or social setting, both smiling warmly.
The final product display appears with a large white Head \& Shoulders bottle standing on the left, beside a matching white tube lying on its side.
The bottle label clearly reads “ Head \& Shoulders ” and shows the brand ’s curved red and blue-green design.
To the right of the product is a smaller rectangular picture of the woman and the formally dressed man still facing each other.
Large white capital letters appear across the bottom : “ STRONG AGAINST DANDRUFF.
GENTLE ON YOUR HAIR. ” The woman in the inset smiles up at the man as the product remains prominently displayed beside them.

% matched lemmas: door
\end{textsample}
