\begin{textsample}{NEG Dim 5 – 2000 – Score -1.00 – 2000/tv\_com\_2000\_65.txt}  \label{ex:f5_neg_078}
A woman in a white long-sleeved blouse and dark pants stands in a small laundry room beside a washer or work surface.
Shelves on the left hold household bottles and containers, and a window is centered behind her.
She lifts a large white sheet or piece of laundry from a basket or pile, raising it above her head and then gathering it in her arms.
The room has a clean, bright, slightly silvery look, with white laundry glowing strongly in the light.
The scene moves outside to the front of a city townhouse with stone steps, an arched doorway, and tall windows with curtains.
The same woman steps out carrying a large woven laundry basket filled with folded and loose clothes.
From above, a small silver hatchback car is parked at the curb below the steps.
She brings the basket toward the car, then sets it on top of the car roof.
The basket sits upright on the roof, packed with white laundry, with a blue garment hanging over one side and a light green cloth visible on the other.
She opens the driver ’s \textbf{door} and gets in, leaving the basket perched on the roof as if it is cargo for a trip.
The silver car drives through the city with the wicker basket still on top.
Tall buildings rise against a blue sky with large white clouds.
The car passes along urban streets and under or near concrete overpasses, then crosses a bridge toward a downtown skyline.
The basket remains centered on the roof, its handle arched upward and the light-colored laundry visible above the rim.
The car continues out of the city into a residential neighborhood with trees and \textbf{houses}, then into open countryside.
A black-and-white cow stands beside a fence as the car passes on a rural road, and another close view shows the cow ’s head near the fence, looking toward the road.
The car travels along dusty country lanes and through rolling green hills under a vivid blue sky.
The landscape opens wide, with grassy fields, low hills, scattered trees, and a pale dirt road winding through the scene.
Eventually the woman stands under the shade of a tree, holding the full woven laundry basket at her waist, facing a broad, sunlit meadow.
A clothesline stretches across the field, and the setting feels open and breezy.
Large white sheets and a green sheet hang from the line, billowing outward in the wind.
The fabric fills much of the view at times, rippling and swelling like sails, with the grassy field and blue sky visible between the hanging pieces.
The billowing white fabric gives way to a close view of an orange Tide detergent bottle.
The label shows a blue sky and white sheet graphic, with visible text reading “ NEW Scent! ” above the large Tide logo.
As the full bottle comes into view, it has a blue cap, a built-in handle on the right, and the front label reads “ Tide Clean Breeze. ” It stands in front of a bright window with blue sky and clouds outside.
Back in the countryside, the woman holds the woven basket full of neatly folded white laundry.
She lowers her gaze toward the clean clothes, then looks up and smiles softly.
Behind her are green grass, trees, and the clothesline.
The car is then seen again on the rural road, driving away across the rolling landscape with the basket still on its roof.
The final product display places the orange Tide Clean Breeze bottle in tall grass against the same blue-sky countryside background.
A second, pale bottle with a blue cap stands slightly behind it, branded “ Downy. ” At the bottom of the screen, white text reads “ www.tide.com. ”

% matched lemmas: door, house
\end{textsample}
