\begin{textsample}{NEG Dim 5 – 2000 – Score -2.00 – 2000/tv\_com\_2000\_80.txt}  \label{ex:f5_neg_074}
Two black-and-white birds perch on a narrow metal rod or wire outdoors, surrounded by tall green trees in bright daylight.
One bird is already settled on the wire, facing right, with a dark head, pale chest, and dark wings.
Another bird flies in from the left, wings spread wide, then lands beside it.
The two birds sit close together, turning their heads and opening their beaks as if reacting to something nearby.
The view opens to a \textbf{suburban} \textbf{house} with white-trimmed windows, a shingled roof, leafy vines, and shrubs below the windows.
The two birds are in the foreground on the wire, looking toward the \textbf{house}.
Inside the left window, an adult woman with short light hair, wearing a blue top and white pants, is cleaning glass.
Inside the right window, an adult man in a pale yellow shirt stands near another large window.
The woman raises a cloth and holds a blue spray bottle, actively wiping the window from inside the room.
A closer view shows the woman in profile holding a clear blue Windex bottle with a yellow spray trigger.
The red “ Windex ” name is large on the label.
She squeezes the trigger, and a fine mist sprays outward across the glass.
The bottle is held prominently in the foreground, with sunlit trees blurred beyond the window.
The birds reappear in close-up.
One dark-headed bird fills the scene, its glossy black beak opening and closing while its head tilts slightly.
Its feathers are mottled black, brown, and white, with a pale chest and darker ruffled head.
It looks alert and expressive, as if commenting on what it sees.
Another close view shows the bird lowering its head, then glancing forward with its beak partly open.
Back outside the \textbf{house}, the birds remain on the wire in front of the two windows.
The woman is visible in the left window with the Windex bottle, while the man in the yellow shirt stands in the right window.
He appears to be cleaning or preparing to clean his window with a different blue spray bottle.
A close-up of the man ’s hand shows him holding a blue bottle labeled “ Glass Cleaner, ” not Windex.
He grips the white spray head while the bright window fills the background.
His other hand, holding a cloth, moves across the pane.
The glass looks hazy and smeared as he wipes.
In the demonstration close-up, white text along the bottom reads “ simulation vs. generic glass cleaner. ” A hand presses a pale cloth against the glass, but streaks and cloudy residue remain visible, with the outdoor trees seen blurred and distorted through the pane.
The two birds on the wire lean forward and look toward the \textbf{house}, their beaks opening as if continuing their conversation.
One bird bends down along the wire, then straightens.
Inside the \textbf{house}, the woman in the blue top stands beside the man in the yellow shirt.
She holds the Windex bottle in one hand and a white cloth in the other, gesturing toward the window as if showing the result.
The man watches her from beside the window.
The room behind them looks domestic, with shelves and dishes visible in the background.
More close-ups of the birds follow.
One bird ’s dark head and curved beak fill the view ; its beak opens, and a small bright eye catches the light.
Another bird, slightly out of focus behind it, faces the same direction.
Then both birds are seen together again on the wire.
One stands to the left, leaning toward the other, while the bird on the right faces forward with a white chest and dark head, as if considering the very clean window.
The woman is shown again inside the wide window, now holding the cloth out to the side and the Windex bottle at her waist.
The man stands beside her, looking toward the glass.
The cleaned window appears very clear, with the outdoor shrubs and interior room sharply visible through it.
One bird, shown alone in close-up, turns its head and fluffs its dark crown feathers.
Then both birds crouch on the wire.
The bird on the right launches into flight, wings beating upward.
Against a blue sky and leafy branches, it lifts off from the wire while the other bird remains perched.
The flying bird rises and passes across the top of the scene, wings blurred from motion, leaving the wire behind.
The commercial ends with the Windex bottle displayed on a bright windowsill.
The bottle is centered in front of a sunny outdoor background with a large green tree.
It is a blue, teardrop-shaped spray bottle with a yellow trigger and the red “ Windex ” name on the label.
Birds fly past in the background.
Large white block letters appear to the left of the bottle reading “ BEST ON GLASS. ” The final image holds on the Windex bottle and the “ BEST ON GLASS ” message, with small text at the bottom right identifying Johnson as a family company.

% matched lemmas: house, suburban
\end{textsample}
