\begin{textsample}{NEG Dim 5 – 1950 – Score -3.00 – 1950/tv\_com\_1950\_28.txt}  \label{ex:f5_neg_022}
A young boy sleeps on his side in a bed, his head resting on a light pillow and a sheet pulled up around him.
He has short, light hair and wears striped sleepwear.
Beside the bed is a small wooden nightstand with a round, white-faced alarm clock on top.
Still lying down and looking drowsy, he stretches one arm out across the bed toward the clock, gropes for it, and appears to silence or move it without fully getting up.
He rolls and shifts under the covers, then slowly props himself up, still heavy-eyed.
The bedroom widens into view.
The boy is now sitting on the edge of the bed in a short-sleeved patterned shirt and dark trousers, bent over his feet.
A clean, light-colored sheet is spread across the bed in front of him, and he is handling his shoes there, with one knee drawn up.
The room has a \textbf{door} at the back, a coat or dark garment hanging on it, a bed with a curved headboard, and a few wall decorations.
An adult woman, likely his mother, appears in the doorway.
She has light hair styled neatly back and wears a full-skirted \textbf{house} dress with short sleeves.
She pauses at the \textbf{door}, looking toward the boy and the bed, then steps inside.
The woman approaches quickly and leans over the bed beside him.
The boy looks up at her, then back down, seeming caught in the act.
She bends close to the sheet and reaches toward his shoe and the bedding, while he sits upright, passive and slightly sheepish.
They face each other briefly, the woman ’s expression \textbf{attentive} and corrective, the boy watching her.
A close view then shows the problem : a light sheet or pillowcase lies rumpled, and a dark, dirty shoe sole or muddy shoe has left a heavy smudged stain on the clean fabric.
The stained fabric fills the view for a moment.
Then a Cheer detergent box appears over the image of the laundry.
The package is dark with bold white lettering, a large sweeping lightning-like graphic, and the word “ cheer ” in big lowercase letters.
On the front, an oval reads “ IT ’S BLUE! ” and the top edge reads “ GIANT ECONOMY SIZE. ” The box is then shown standing upright on a counter in a laundry or kitchen work area, with the woman ’s full skirt visible to one side.
The scene moves into a bright domestic laundry-kitchen setting.
The Cheer box remains prominent on the left at first, while the woman stands at an ironing board or work surface.
She wears the same patterned, full-skirted \textbf{house} dress.
Around her are folded stacks of towels or linens, a laundry basket, shelves, patterned wallpaper, curtains over a window, and a counter area with household items.
She works steadily with a dark electric iron on a light cloth, moving it back and forth across the fabric.
The cord trails from the iron as she presses and smooths.
Folded towels and linens are stacked neatly in the foreground and at the side, reinforcing the laundry setting.
She lifts a clean white cloth, opens it, looks at it with a pleased expression, and folds or places it with the other clean laundry.
The boy appears again in the kitchen, now wearing a short-sleeved striped knit shirt.
He stands at a counter in front of a patterned tile or wallpaper backsplash.
On the counter are a plate, pieces of bread or a snack, and a dark jar, likely containing a dark spread or jam.
He dips or spreads with a utensil, moving his hands busily over the plate.
As he works, dark smears appear on the counter area and near the jar.
He then reaches to the side and pulls a light dish towel into view.
A close view shows the light dish towel beside the open dark jar.
The boy ’s hands rub and bunch the towel around the messy area, wiping at the dark spill or spread.
The towel becomes visibly marked with dark stains.
He lifts and turns it, and the cloth shows stripes near one end and several dark blotches and streaks.
The towel is then laid out more fully, revealing a noticeable dark smear and spots on the otherwise light fabric.
The Cheer box appears again over the stained towel, then is shown upright on the kitchen counter, held or steadied by hands from the side.
The same bold packaging is visible : “ IT ’S BLUE! ” in an oval, “ GIANT ECONOMY SIZE ” along the top, and the large “ cheer ” name across the lower half.
The box remains centered against the patterned kitchen wall.
Large promotional text appears over the package : “ SO CLEAN … SO WHITE … ” in sweeping, bright script-like letters.
More text fades in below it, reading, “ you don't need bluing or bleach, ” with the words layered over the Cheer box and background.
The box then tips diagonally against a plain light background, and a white stream of detergent pours from an opening at one corner, flowing downward in a smooth ribbon.
The final image keeps the tilted Cheer box at the upper right, still pouring a white stream.
Large block letters appear on the left reading “ BLUE MAGIC, ” and beneath them the word “ WHITENER ” glows in bright white.
The Cheer package remains clearly visible, with “ IT ’S BLUE! ” and “ cheer ” readable on its front, ending on the product and its “ Blue Magic Whitener ” claim.

% matched lemmas: attentive, door, house
\end{textsample}
