\begin{textsample}{NEG Dim 5 – 2010 – Score -2.00 – 2010/tv\_com\_2010\_109.txt}  \label{ex:f5_neg_058}
At first, a smiling young girl stands indoors in a dark navy rain jacket with the hood up.
Beside her, an adult woman with long dark wavy hair, wearing a red raincoat, adjusts the girl ’s hood with both hands.
An adult man in a blue rain jacket smiles from just behind them.
White on-screen text identifies them as “ The Saunders ” and “ Bremerton, WA. ” The family appears cheerful and close together in a home entry or living area.
The scene moves outside to the front porch of a \textbf{house} with pale siding, a dark green \textbf{door}, potted plants, and wet concrete steps.
The girl and the woman step out into the rain, both holding their hoods.
A small white disclaimer along the bottom reads, “ Real people aware their comments may appear in advertising. ” The child runs ahead across the wet ground, while the woman follows.
Close views emphasize rainy details : pink rain-boot handles and tubing beaded with water, a blue bicycle tire splashed with mud, and dark, watery pavement rippling with rain.
Back inside, the woman sits on a dark leather couch, reacting with wide eyes and an animated raised hand, as if describing how quickly the rain and mud become a problem.
The man is partly visible beside her.
Then muddy boots enter through a doorway onto a light-colored floor.
A patterned doormat sits just outside, but dirt and water still track inside.
Bright pink child-sized rain boots with white stripes stand muddy on the floor among larger dark boots, and the floor is left with scattered muddy footprints and smears.
To deal with the mess, the woman stands near the front \textbf{door} with both feet on a heap of white towels, shuffling them over the light floor like makeshift mop pads.
She bends forward, arms lifted slightly for balance, looking down at the floor as she tries to clean by sliding her feet.
In another view, she and the man sit on the couch in a living room with colorful pillows, a ship ’s wheel wall decoration, and a glimpse of the kitchen in the background ; she still appears mid-story, gesturing outward.
A bright green cube-shaped box with the Swiffer logo sits on the wet front porch in front of the green \textbf{door}.
Inside the \textbf{house}, the woman and man open the box at a counter.
The woman smiles as she lifts out a purple Swiffer WetJet package.
Inside the green box are several cleaning-solution bottles and product supplies.
Close views show the purple packaging clearly labeled “ Swiffer WetJet, ” with an image of the purple-and-white floor cleaner on the front.
The girl, now in a pink top with a purple headband, watches with interest from the side.
The Swiffer WetJet is then shown on the dirty light-colored floor.
Its purple-and-white cleaning head approaches a muddy, gritty patch.
The woman pushes the mop across the mess, and the dirty area disappears under the cleaning pad as it glides over the floor.
Wider views show her using the long-handled WetJet through the kitchen and laundry area, near white appliances, pale flooring, wooden cabinets, and a countertop.
She smiles while mopping, appearing pleased with how easily the tool moves.
After cleaning, she lifts the WetJet head and shows the underside of the rectangular pad over a white trash can.
The pad is dark gray and heavily soiled, with dirt spread across its surface.
She looks at it with a disgusted, impressed expression, then angles it toward the trash as if ready to throw it away.
The family returns outside in the rain.
Only their lower legs are visible at first as several pairs of boots stomp and splash in muddy ground : the girl ’s bright pink boots, larger gray-green adult rain boots, and purple boots.
The girl in the dark rain jacket looks upward near a rocky wall, her hood wet from the rain.
Finally, the family walks along a wet road lined with trees and stone walls.
The man wears a blue rain jacket and boots, the woman wears her red raincoat, and the child in the dark raincoat and pink boots walks ahead.
They move through the damp Pacific Northwest setting as if no longer worried about the mud.
The commercial ends on a plain purple screen.

% matched lemmas: door, house
\end{textsample}
