\begin{textsample}{NEG Dim 5 – 2020 – Score -4.00 – 2020/tv\_com\_2020\_56.txt}  \label{ex:f5_neg_034}
The commercial opens on a simple Amazon brand image : a bright orange rectangle fills the centre of the screen, with the white Amazon smile mark alone in the middle.
A sunny \textbf{suburban} street appears, lined with grass, leafy trees, parked cars, and single-storey \textbf{houses}.
On the left, a light-haired adult woman in a blue top or cardigan and pale trousers stands near the sidewalk, looking down at something in her hands, likely a phone.
Farther to the right, another adult woman, with dark curly hair, a mustard-yellow top, a tan outer layer, dark trousers, and a dark face mask, walks a small tan dog on a leash across the lawn.
The two women are separated at first by the width of the grass verge and trees.
Inside a warmly lit home, a hand holds a smartphone showing the Amazon shopping app.
The Amazon wordmark is visible at the top of the screen, and a yellow “ Buy Now ” button appears near the bottom.
The phone is held over soft bedding or a blanket.
A bearded adult man with dark hair reclines nearby, looking down at the phone with an interested, pleased expression.
The scene shifts to a home office.
An adult man with wavy dark hair, wearing a blue button-down shirt, sits at a wooden desk with a laptop open in front of him.
Shelves, books, papers, a desk lamp, pencil cup, and office items fill the background, giving the room a working-from-home feel.
He holds up his phone beside the laptop.
In a close view, the phone again shows the Amazon app with a yellow “ Buy Now ” button and a product listing for a laptop-related stand or desk accessory.
On the laptop screen beside it, two other men appear in a video call, each in his own small video window.
The man at the desk then looks at the screen with a focused, slightly thoughtful expression.
Back outside on the \textbf{suburban} lawn, the two women have come together under the trees.
The blonde woman in blue stands close to the \textbf{masked} woman in yellow and tan, touching her lightly at the shoulder or upper arm as if sharing a reaction or pointing something out.
They face one another and then look in the same direction.
The small dog remains near their legs, partly obscured by them and the grass.
The \textbf{masked} woman raises an arm and gestures outward, while the blonde woman leans in companionably.
The final scene is a front porch with a dark blue \textbf{door}, blue siding, red brick flooring, a black doormat, and a tall potted plant on the right.
A person in dark trousers steps in carrying a brown Amazon cardboard box.
The person lowers the box onto the doormat in front of the \textbf{door} ; the black Amazon smile logo is printed large across the front of the package.
White on-screen text appears to the left of the box reading, “ Spend less. ” As the person walks away to the right, the text expands to, “ Spend less.
Smile more. ” The Amazon box remains centred on the doormat beneath the \textbf{door}.

% matched lemmas: door, house, masked, suburban
\end{textsample}
