\begin{textsample}{NEG Dim 5 – 1970 – Score -1.00 – 1970/tv\_com\_1970\_85.txt}  \label{ex:f5_neg_007}
A sunny outdoor lawn is bordered by tall, dense, neatly clipped \textbf{hedges}, forming a narrow garden passage.
From the distance, an orange-brown riding lawn tractor comes forward between the \textbf{hedge} walls.
The driver is an adult with long light-blonde hair, wearing a black-and-white plaid long-sleeved shirt, blue jeans, and light-colored shoes or boots.
She sits upright on the black seat, both hands on the steering wheel, guiding the tractor steadily out from the \textbf{hedge} opening onto the grass.
As the tractor comes closer and moves across the lawn from left to right, its details become clearer : it has a boxy hood with a dark front grille, white-rimmed wheels, and an orange mower deck mounted low beneath the side and front area.
The rider keeps a relaxed, focused posture, looking ahead while the tractor travels close to the \textbf{hedge} line.
The grass is uneven in texture, with lighter and darker patches, and the mower deck rides just above it as the machine rolls along.
The view changes to the tractor facing forward in a narrow grassy lane between tall \textbf{hedges}.
The black grille and orange front body fill the center, with the mower deck visible low to the ground, extending especially to the left side.
The tractor advances over the grass while the \textbf{hedge} walls frame it on both sides.
Two thin white horizontal graphic lines briefly appear across the tractor and mower area, one higher and one lower, as if illustrating the mowing height or the way the mower follows the ground.
After the lines disappear, the tractor continues forward, the deck remaining close to the grass as the wheels move over slightly uneven ground.
A close side view follows, focused on the tractor ’s engine cover and front wheel.
The word “ Simplicity ” is visible in white script on the brown-orange hood.
The driver ’s jean-clad leg and light boot rest near the foot platform and controls.
Under the hood opening, dark mechanical parts are visible, while the orange mower linkage and deck sit low beneath the tractor.
The machine moves across the lawn, the small front wheel rolling over the grass and the mower deck gliding along just above the surface.
From above, the tractor is shown traveling beside the squared-off \textbf{hedge} walls, emphasizing how closely it can work along the edges.
The rider remains seated upright, steering with both hands.
Her long blonde hair falls over her shoulders and back, catching the light.
The tractor passes through the garden-like \textbf{hedge} layout, its orange body contrasting with the dark green shrubs and mottled green grass.
It follows a straight path, then continues along the \textbf{hedge} corridor, staying close to the trimmed greenery without scraping it.
Near the end, the view pulls back to a high overhead view of a small, arranged lawn scene that looks almost like a miniature display or an illustration on a rectangular green surface.
A white border along one side and a darker border along another make the lawn area resemble a page or framed panel.
Several small lawn tractors or tractor-like shapes are grouped near a row of \textbf{hedges}, with the orange Simplicity tractor among them.
The final image holds on this neat, picture-like lawn arrangement, with the \textbf{hedges}, tractors, and green rectangular area presented as a tidy garden-care scene.

% matched lemmas: hedge
\end{textsample}
