\begin{textsample}{NEG Dim 5 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_31.txt}  \label{ex:f5_neg_042}
The commercial opens in a warmly lit front doorway of a home, in a sepia-toned black-and-white look.
A middle-aged man with a receding hairline, wearing a light dress shirt, dark trousers, and a dark bow tie, stands just inside the open \textbf{door}.
He leans forward to kiss an older woman goodbye.
The older woman, dressed in a light coat and small hat, carries a dark handbag over her arm.
Bright outdoor light spills in from the porch behind her, silhouetting both figures against the open \textbf{door} and glass side panels.
After the kiss, the man keeps a hand near her arm or bag as she turns outward toward the porch.
He lingers at the doorway, smiling and bending slightly after her as she leaves, while she faces away toward the outside.
Once the visitor has gone, the man turns back into the \textbf{house} and walks through a domestic interior.
He passes a wall clock and moves toward a small dining area.
The room has a round table set with cups, saucers, plates, and small food items, positioned beside a window with horizontal blinds or frosted panes.
A simple chandelier hangs over the table, and there are framed pictures and a brick or brick-patterned wall section nearby.
A younger woman, apparently his wife, stands at the table.
She has short, styled hair and wears a dark, short-sleeved dress with a narrow belt or apron detail at the waist.
She is holding dishes and appears to be clearing or arranging the table.
When the man approaches with a cup and saucer, she looks over at him with a serious, displeased expression.
He pauses near the table, still holding the cup and saucer, while she turns partly away, then back toward him.
Their exchange becomes visually tense.
The woman sets or handles dishes at the table and moves around it with quick, purposeful motions.
The man stands nearby, watching her and responding with small gestures.
In closer views, her face is tight and intent ; she looks up at him, narrows her eyes, and speaks with a firm, irritated expression.
He is often partly in the foreground or just beside her, his bow tie and light shirt prominent, while she leans on the table or straightens up with her arms close to her body.
She picks up a plate and glass, then steps toward him as if making a point.
The man at times looks uncertain or defensive, and later folds his arms across his chest while she continues to talk.
As the dandruff topic comes up in the dialogue, the man reacts physically by raising a hand to his head.
He leans slightly forward and rubs or scratches the front and top of his scalp, pushing at his thinning hair with his fingers as if checking or worrying about it.
The woman looks up at him steadily, her face stern and unconvinced.
They stand close together near the window and table, facing each other.
She speaks with pointed gestures, sometimes lifting a finger or holding her hands near her chest as she emphasizes her point.
He answers with raised eyebrows, sidelong glances, and a faint, uneasy smile, then looks more serious as she continues.
Their faces fill the space, with the bright window behind them and the dangling light fixture above.
The argument continues with the woman maintaining a firm, skeptical stare.
She looks down briefly, then back at him, while he watches her and responds with a mix of defensiveness and forced good humor.
In a wider view, she turns away from him and begins to walk forward out of the dining area, while he remains behind near the table.
He lifts his hands toward his chest and then handles a small object or dish as she moves past him.
She walks toward the foreground, expression still set, passing between the viewer and the room behind her.
The scene then gives way to a product display.
Three Head \& Shoulders packages sit side by side on a reflective surface : on the left, a tall rectangular carton with a tube visible at the bottom ; in the center, a rectangular box labeled “ Head \& Shoulders ” ; and on the right, a curvy, white bottle also labeled “ Head \& Shoulders. ” Each package has a bold dark swoosh graphic across the lower portion.
The background is softly blurred, keeping attention on the products.
Large bright lettering appears above the center and right packages reading “ Really Works, ” while the Head \& Shoulders name remains visible on the packaging below.

% matched lemmas: door, house
\end{textsample}
