\begin{textsample}{NEG Dim 5 – 1950 – Score -3.00 – 1950/tv\_com\_1950\_64.txt}  \label{ex:f5_neg_001}
The commercial is in black and white and appears as an older film-style \textbf{advertisement}, with visible \textbf{grain} and a small archive-style watermark at the lower right in several frames. 1. **Opening** : The first frame is almost entirely black, with only a \textbf{few} small \textbf{specks} of light or film noise visible.
No people or products are visible yet. 2. **Airplane in flight** : The scene cuts to a propeller-driven passenger airplane flying through cloudy sky.
The aircraft is shown in profile, moving against a misty background.
The image is soft and slightly grainy. 3. **Airline title over aircraft** : A large title fills the frame : **“NORTHWEST”** in bold uppercase letters, with **“Orient”** in a cursive script and **“AIRLINES”** in uppercase beneath or alongside it.
A passenger airplane appears behind or underneath the text, visually linking the brand name to air travel. 4. **Woman with stringed instrument** : The commercial then cuts to an interior scene.
A woman wearing a light-colored traditional-looking robe or kimono-like garment is seated and holding a long-necked stringed instrument.
She is positioned near a window or paneled wall that resembles a traditional Japanese-style interior.
She looks toward the camera while holding the instrument. 5. **Speed/route message with aircraft** : Another airplane shot appears, this time with large overlaid text reading **“shortest... ” ** and **“fastest... ” **.
The word **“Orient”** appears in large cursive lettering across the lower portion of the frame.
The aircraft is shown close-up from the side, with multiple propeller engines visible. 6. **Gong scene** : The scene changes to a large circular gong or metal disc in front of a dark curtain.
A person ’s arm and hand are visible at the left, holding a mallet against or near the center of the gong.
The person ’s full body is not visible. 7. **Final branding over gong** : The final frame keeps the large gong in the background while the airline branding appears prominently in front : **“NORTHWEST”** in large bold uppercase letters, **“Orient”** in cursive, and **“AIRLINES”** in uppercase.
The composition combines the airline name with imagery \textbf{associated} with East Asian or “ Orient ” travel themes.
Overall, the sampled frames show a sequence moving from aircraft imagery and airline branding to cultural/travel imagery, then ending with the brand name superimposed over a gong.

% matched lemmas: advertisement, associate, few, grain, speck
\end{textsample}
