\begin{textsample}{NEG Dim 5 – 1950 – Score -1.00 – 1950/tv\_com\_1950\_11.txt}  \label{ex:f5_neg_026}
A young blonde woman in a red-and-white checked dress appears in a warmly lit boy ’s bedroom.
She has a neat 1950s bob with short bangs, small earrings, and dark-framed eyeglasses resting on top of her head like a headband.
She turns from the side toward the viewer, speaking directly as if making her case.
Behind her are teenage-style room decorations : a triangular pennant on the wall with the letters “ LFC, ” framed pictures, a sailing-ship print, snapshots, and a telescope near the bed.
She gestures to herself with one hand, then brings a hand to her chest, looking confident and slightly playful.
As the view widens, a young fair-haired boy is visible tucked into bed beside her.
He lies propped on white pillows, wearing patterned pajamas, with a blanket pulled up.
The woman sits near the foot or side of the bed, holding a small dark bottle or container with a light cap, visually connected with the “ pill ” mentioned in the audio context.
She turns from addressing the viewer to the child, reaches over, and gently strokes his forehead.
The boy looks tired and passive, rubbing at his face and resting against the pillows.
The woman then turns back outward, still holding the small container, raising her free hand in a poised, explanatory gesture.
A second woman is introduced in a different child ’s bedroom.
She is also blonde, with fuller curled hair, and wears a dark green turtleneck sweater.
She smiles warmly and looks down toward a child off to one side, then turns toward the viewer with a calm, assured expression.
The room around her is softer and more traditionally feminine : pale walls, a white ornate headboard, sheer ruffled fabric near the bed, framed nursery-style pictures, a bedside lamp, a panda toy, and dolls arranged in the background.
The second woman steps beside a little girl lying in bed under white covers.
The girl has brown hair cut in a bob with bangs and wears a light-colored, ruffled nightgown.
The woman brings a baby doll toward her, while also holding a small dark jar with a pale lid.
She leans over the bed smiling, offering the doll and the jar into the child ’s space.
The girl looks up at her and takes interest in the doll.
The woman continues smiling at close range, creating a gentle bedside-care moment.
She holds the jar where the girl can see it, then \textbf{lets} the girl hold or touch it while the doll rests near the child.
The scene returns to the first blonde woman in the checked dress.
She is now closer to the viewer, with the boy ’s bed and lamp behind her.
She speaks directly, her expression alert and persuasive, while the boy lies in the background.
At one point the boy is partly hidden by a white bedcover or pillow as he shifts.
The woman looks from him back to the viewer, then turns toward him with a pleased smile.
A close view shows the little girl from the second room holding the dark jar near her face, with her doll beside her ; she smiles faintly as an adult hand steadies or adjusts the jar.
This briefly emphasizes the Vicks jar as something the child recognizes and accepts.
The checked-dress woman continues addressing the viewer with the boy resting behind her.
She looks earnest, then raises her hand in a precise “ OK ” gesture, holding up a tiny white tablet between her fingers.
The pill is very small against her hand, and she presents it close to her face as if demonstrating how simple or modern it is.
Her eyes are wide and focused on the viewer, and the eyeglasses remain perched on her head.
The second woman in the green turtleneck then appears seated beside the little girl again.
She smiles and speaks while resting one hand near the child ’s collar.
She holds the Vicks jar upright, its dark body and light lid clearly visible, then positions it in front of her chest as she explains.
The child reclines on the pillow, looking up at her, while a baby doll lies across the blanket nearby.
The woman unscrews or opens the jar, dips a finger in, and brings a small amount of ointment toward the child.
Her movements are slow and careful, focused on comfort rather than urgency.
She gently opens the neckline of the girl ’s ruffled nightgown and begins rubbing the ointment onto the child ’s upper chest.
The child remains still, looking downward and then relaxing.
In a close view, the woman ’s hand moves in smooth strokes over the girl ’s chest, just below the collarbone, while the doll ’s face is visible beside them.
The girl ’s expression softens ; her eyes drift partly closed and her mouth settles into a small, contented smile.
The adult hand continues the rubbing motion across the chest, then eases away as the child tilts her chin slightly upward, appearing soothed.
The view widens again to the bedside scene.
The woman in green finishes adjusting the girl ’s nightgown and blanket, still smiling.
The girl sits more upright in bed, and the woman ’s hands rest reassuringly on her shoulders and chest area.
The woman then looks outward toward the viewer with a composed, maternal expression while keeping one hand protectively on the child.
The girl leans closer to her, and the woman gathers her into a hug.
The little girl sits up within the white covers, nestled against the woman ’s chest.
The woman kisses the child on the forehead or temple, then both smile.
The child cuddles in, clutching close to the woman, and the woman beams directly outward before looking down affectionately at the girl.
A bedside lamp fills the scene next.
It has a pale lampshade and a shiny, dark metal base.
A hand reaches under the shade near the switch, fingers sliding around the lamp stem as if turning it off or adjusting it for bedtime, then withdraws.
The lamp remains the central object for a moment, reinforcing the nighttime setting.
The final view settles on the Vicks VapoRub jar placed on a polished bedside table in front of the lamp base.
The jar is dark blue or black with a pale greenish lid and a cream-colored label.
The label reads “ Vicks VapoRub, ” with smaller text below including “ Vaporizing Ointment ” and “ Relieves distress of colds. ” At the very end, large white words appear to the right of the jar : “ most comforting thing you can do for a cold. ” The product remains prominently displayed beside the warm bedside lamp, visually linking it with nighttime care and comfort.

% matched lemmas: let
\end{textsample}
