\begin{textsample}{NEG Dim 5 – 2000 – Score -2.00 – 2000/tv\_com\_2000\_101.txt}  \label{ex:f5_neg_071}
The commercial begins with a nearly black screen.
A small red-and-white watermark or logo is visible in the lower-right corner.
It then cuts to a silver compact sedan driving through a modern city street lined with tall glass-and-concrete buildings.
The car is shown from a low front three-quarter angle, moving along a multi-lane urban road in bright daylight.
Next, there is a close-up inside or near a vehicle dashboard area : a hand is holding or inserting a dark disc-shaped object near a black electronic unit with a circular opening and buttons.
The exact device is not fully clear from the frame, but it appears to be a car audio or media component.
The commercial returns to exterior driving shots.
The same silver sedan is shown from the rear three-quarter view traveling along a city roadway, with high-rise buildings and roadside barriers in the background.
Another shot shows the car on a curved or banked-looking road beside a large \textbf{concrete} wall, again in bright daylight.
A later shot presents the sedan from the front three-quarter view on a \textbf{downtown} road, with tall buildings behind it.
The final frame is a black promotional end card.
At the top is the red KIA logo, followed by the line “ Make every mile count. ” Large centered text reads : “ Starting at \$8,235 after \$4,000 cash back including \$1,000 owner loyalty bonus and \$500 military bonus. ” Below that, it says “ Offer ends soon. ” Fine-print legal and offer details appear at the bottom, including a reference to a 2002 Kia model and financing/bonus conditions, though much of the small text is difficult to read clearly.
A small red-and-white watermark remains in the lower-right corner.

% matched lemmas: concrete, downtown
\end{textsample}
