\begin{textsample}{NEG Dim 5 – 2000 – Score -3.00 – 2000/tv\_com\_2000\_24.txt}  \label{ex:f5_neg_073}
A cluttered office appears, with glass-walled partitions, venetian blinds, framed certificates, and a desk piled high with pink papers and folders.
Behind the desk, a middle-aged man in a light gray suit, shirt, and tie rises to his feet.
He has a receding hairline, wears glasses, and looks serious and alert.
In the same office, another middle-aged, balding man in a brown suit and striped tie stands behind a similar heap of paperwork, also looking tense and expectant, as if the two men are rivals in the same workplace.
The scene becomes exaggeratedly comic : both suited men are now down on the speckled office floor at the feet of someone standing between them.
Only the standing person ’s lower body is visible : dark pin-striped trousers and shiny black dress shoes.
The brown-suited man lies on the left and the gray-suited man with glasses lies on the right.
Each man works on one of the standing person ’s shoes, rubbing and polishing it with a cloth or brush, their faces close to the floor.
They appear to be competing in their eagerness to impress the unseen superior.
The gray-suited man is next seen inside a car, seated in the driver ’s seat in a \textbf{garage}.
He reaches upward with one finger to press a small control near the ceiling or visor area while his other hand remains near the steering wheel.
A close view then shows the \textbf{garage} \textbf{door} opener itself mounted on the ceiling : a rounded white unit attached to metal rails, with the red word “ GENIE ” printed on its front.
The unit is presented clearly as the product being used.
Outside in bright daylight, two neighboring \textbf{suburban} \textbf{houses} stand side by side, each with a \textbf{garage}.
The right-hand \textbf{garage} \textbf{door} is lifted much higher than the left, with a vehicle visible inside, visually suggesting a faster opening \textbf{door}.
A man in a car is then seen through the windshield, glancing back with a startled or concerned look.
A blue-gray car moves quickly past in the foreground, leaving the \textbf{garage} area while another car remains visible inside the open \textbf{garage} behind it.
Back at the office, the gray-suited man with glasses now stands confidently with his arms crossed.
He is in front of glass office partitions, wearing a faint self-satisfied smile.
A desk with an open book or planner sits nearby, and another employee is visible working in the background.
His posture and placement make him look newly important or in charge.
The final office image returns to the floor-level gag.
The brown-suited, balding man lies on the speckled carpet beside the polished brown shoes and gray trouser legs of a standing person.
He presses close to one shoe, still in a subservient position, looking upward with a strained expression.
On-screen branding appears at the lower left : the red “ GENIE ” logo, followed by large white text reading “ ACCELERATOR, ” with “ GenieCompany.com ” beneath it.

% matched lemmas: door, garage, house, suburban
\end{textsample}
