\begin{textsample}{NEG Dim 5 – 2010 – Score 1.00 – 2010/tv\_com\_2010\_85.txt}  \label{ex:f5_neg_087}
The commercial begins with a flat orange screen showing the white-and-blue “ Vonage ” logo, with the smaller blue words “ sounds good ” underneath.
It then cuts sharply to a highly stylized food shot : a large hamburger on brown paper against a bright red background.
The burger is positioned on the right side of the frame, with a knife stuck vertically through the top bun.
Visible ingredients include a glossy bun, melted cheese, a beef patty, red onion, tomato, lettuce, and pickles.
Next, the visuals switch to a bright green background with large white pricing text beginning to appear : a dollar sign and the number “ 6 ” are visible.
The frame is cropped so the full price is not completely shown.
The ad returns to an extreme close-up of the burger against a yellow background.
The burger fills the right side of the frame, emphasizing the layered ingredients and glossy textures.
Another graphic price/text screen follows : a red background with a large white dollar sign on the left.
The rest of the pricing information is not visible in this sampled frame.
The next shot shows a full meal on a rectangular metal tray against a green background.
On the tray are the burger with the knife still inserted, a container of French fries, and a small cup or bowl of greenish dipping sauce or garnish.
White capital letters spelling “ FOR ” appear in the upper left.
A yellow title-card-like frame appears next with the word “ ALSO ” centered in widely spaced white capital letters.
The commercial then cuts back to the burger on a red background, again with the knife through the bun.
Small white text appears in the upper left ; it looks like it may read “ CHILI ’S, ” but it is very small and not fully clear.
Additional tiny legal or disclaimer text appears near the bottom and is not readable in the frame.
The final shots show the full tray meal against a yellow background.
Large white text “ BABY ” appears in the upper left.
In the last frame, a red chili-pepper graphic and a green “ s ” appear after “ BABY, ” forming a stylized wordmark-like phrase.
The tray still contains the burger, fries, and small sauce cup, with the burger and upright knife on the left side of the tray and the fries on the right.

% matched lemmas: 
\end{textsample}
