\begin{textsample}{NEG Dim 5 – 2020 – Score -5.00 – 2020/tv\_com\_2020\_7.txt}  \label{ex:f5_neg_032}
A young girl sits in a cozy room beside a wooden-framed window and a desk scattered with children ’s things.
An adult man sits close to her, holding a small pale-yellow puppy with a blue collar across his lap.
At first the girl covers her face with both hands, then lowers them as the puppy leans toward her.
She gently reaches for the dog, then cradles it against her chest.
In close-up, the puppy nestles into her shoulder and nuzzles her cheek while she smiles, looking emotional and happy.
A small white Ring logo sits at the lower left of the image.
The mood shifts to scenes of searching for missing pets.
Outdoors in dim, gray light, the same girl now wears a lavender knit hat and a cream fleece jacket with a floral pattern.
She looks worried as she stands near a post while an adult ’s hand holds up a staple gun or tape dispenser in front of her, partly blocking her face.
On a quiet residential street, an adult man and the girl put lost-dog flyers on a wooden utility pole.
Similar scenes follow in different neighborhoods : a man tapes a flyer to a pole outside storefronts, an older woman places a “ MISSING ” dog notice on a pole along a snowy street, and more lost-dog posters appear in rain, morning sun, fall foliage, and nighttime streetlight.
The posters show different dog photos and bold headings such as “ LOST DOG, ” “ MISSING, ” and “ I ’M MISSING. ” One flyer fills the screen with a photo of a smiling white dog and the text “ LOST DOG ” and “ PLEASE HELP \textbf{FIND} OUR MILO. ” A middle-aged white man in a light blue button-down shirt stands on a tree-lined neighborhood street, holding up a smartphone.
On the phone screen is a Ring app post featuring the same white dog ’s photo.
He faces forward as if explaining the feature, with bare-branched trees and warm daylight behind him.
The phone interface is then shown up close in someone ’s hands.
A lost-pet post form displays a large photo of the white dog at the top, with fields below.
The pet name field reads “ Milo, ” and the description begins “ Milo our yellow … ” A blue button labeled “ PREVIEW POST ” sits below the form, above the on-screen keyboard.
A blue graphic badge appears at the lower right reading “ Introducing Search Party, ” with a small magnifying-glass-style icon.
The app view changes to a “ Sharing Options ” section with a large blue button labeled “ START SEARCH PARTY. ” The button briefly turns black, as if pressed, then returns blue.
A \textbf{suburban} \textbf{house} appears from above and across the street, with a driveway and \textbf{garage} visible.
Blue translucent light beams extend outward from the front of the \textbf{house}, suggesting an outdoor camera scanning the area.
The view widens to a whole neighborhood, where many homes are marked by glowing blue circles and domes, visually implying multiple Ring cameras joining the search across the community.
A front walkway is shown from the perspective of a home security camera, with a path leading through trimmed \textbf{hedges} to the sidewalk and street.
The Ring logo appears at the top left with a small “ 4K ” mark, and the “ Introducing Search Party ” badge remains at the lower right.
Inside a home entryway, the young girl stands near the bottom of a staircase, wearing a rose-colored cardigan over a striped shirt.
An adult man peeks from the doorway at the right edge, smiling.
The girl ’s face shifts from tired or uncertain to wide-eyed surprise as she looks toward the open front \textbf{door}.
Outside, at the foot of porch steps, a pale-yellow dog appears beside an adult man holding a leash.
The dog moves toward the \textbf{house}, then bounds up the steps, tail raised and wagging.
The girl and another adult stand in the open doorway waiting.
The man who brought the dog back follows behind, still holding the leash.
On the porch, the dog is reunited with the family.
The girl wraps her arms around the dog ’s neck, smiling and pressing close.
A woman with light hair and a man with a dark mustache stand behind her, both smiling broadly.
The dog lifts its head, licks and nuzzles, and the family crowd around it, petting its head and shoulders.
The man who returned the dog, a smiling Black adult man in a dark jacket over a mauve shirt, looks down warmly from the porch area, pleased as he watches the reunion.
The earlier spokesperson appears again, now walking down the middle of a quiet, tree-lined street covered with scattered autumn leaves.
He holds a leash attached to a medium-sized brown dog walking beside him.
A white lower-third caption identifies him as “ Jamie Siminoff ” with “ Founder ” underneath.
He gestures lightly with one hand while the dog stays close at his side.
The commercial ends on the roofline of a \textbf{house} at dusk or early evening.
Large white text “ ring ” appears centered above the roof.
Beneath it, white text reads, “ \textbf{Find} your dog with Search Party, ” with the Search Party icon between the words.
The \textbf{house} sits under a pale sky, framed by tree branches, as the Ring branding remains centered on screen.

% matched lemmas: door, find, garage, hedge, house, suburban
\end{textsample}
