\begin{textsample}{NEG Dim 5 – 1980 – Score -1.00 – 1980/tv\_com\_1980\_56.txt}  \label{ex:f5_neg_065}
A soft, misty white miniature world appears, with rounded tree shapes framing a small white \textbf{garage}.
To the left is a birdhouse-like structure on a post.
The \textbf{garage} has a peaked roof, decorative trim, and a row of bluish-purple windowpanes above the \textbf{door}.
The double \textbf{garage} \textbf{door} slowly lifts, revealing a dark interior.
From the darkness, a large black tire rolls forward like a little open carriage.
A baby wearing only a white diaper sits upright inside the hollow center of the tire, visible against the shadowy \textbf{garage} doorway.
As the tire moves out into the pale, foggy space, the baby rides inside it, looking around with a curious, slightly serious expression.
The setting becomes simpler and more dreamlike, with the white \textbf{garage} fading into the background and the black tire standing out against a plain light-gray floor and backdrop.
The baby sits low inside the tire, small hands near the rim, sometimes bringing fingers to the mouth.
A yellow diamond-shaped road sign appears overhead and behind the baby.
It shows a black winding arrow, the kind of warning sign used for curving roads.
The baby turns slightly to the side while the tire continues past it.
The sign grows larger until it fills most of the view, emphasizing the twisting-road symbol.
Then it drifts out of sight, and the pale background returns.
The baby and tire reappear more clearly, now centered against the plain light background.
The baby sits in the tire ’s opening, facing forward and then turning to look off to one side.
Another roadside symbol appears : a blue, house-shaped school crossing sign on a post.
It contains white simplified figures of two children holding hands, one carrying a bag.
The baby faces toward it from the tire, as though passing another possible road hazard.
The sign fills the screen for a moment, its white child figures large against the deep blue background.
The scene returns to the baby seated in the black tire.
The tire ’s tread is visible around the sides, thick and textured.
A white duck waddles into the foreground from the left, passing directly in front of the tire and partially blocking the baby.
The duck has an orange bill and orange feet, and its bill is open as it walks.
The baby watches it closely, leaning forward with hands on the tire rim.
The duck continues across to the right, leaving the baby visible again.
The duck reappears near the left side and moves across the front once more.
As it passes, bold white all-capital text appears along the bottom : “ MICHELIN.
BECAUSE SO MUCH IS RIDING ON YOUR TIRES. ” To the right of the words is the Michelin Man logo, the small white tire-bodied mascot.
Behind the text, the baby remains seated safely inside the large black tire, watching the duck as it waddles out of the frame.

% matched lemmas: door, garage
\end{textsample}
