\begin{textsample}{NEG Dim 5 – 1950 – Score -2.00 – 1950/tv\_com\_1950\_109.txt}  \label{ex:f5_neg_023}
A light-colored, two-tone Plymouth is parked broadside in a paved driveway beside a low, modern-looking \textbf{house} or \textbf{garage}.
The car has a long 1950s body, bright chrome trim, whitewall tires, and high rear tail fins.
A \textbf{clean-cut} adult man, likely middle-aged, wearing a light short-sleeved shirt tucked into dark trousers, stands at the front driver ’s side.
He leans over the hood with both hands near the car ’s surface, as if admiring or checking it.
He straightens and smiles slightly while keeping one hand on the hood, presenting the car with pride.
The man moves to the front of the Plymouth, where the car faces forward.
Its wide chrome grille, paired headlights, and low, broad stance fill the view.
He bends near the left front headlight area, looking closely at the chrome and front details, his body angled toward the car.
The setting opens onto a roadway or driveway bordered by a few trees and open land in the distance.
Back at the \textbf{house}, the Plymouth is seen from the rear.
Its tall, sharply pointed fins rise on both sides of the trunk, with chrome tail lamps set into them.
The rear license plate reads “ 427471. ” The man stands beside the right rear corner, then walks behind the car, crossing toward the left fin.
He runs his hand along the rear bodywork and tail fin area, continuing to inspect and admire the styling.
His posture is relaxed and proprietorial, as though he is showing off details of a car he owns.
The scene changes to the Plymouth parked or paused on a road beside a large body of water.
The car is shown in side profile, with the water stretching across the background and a pale sky above.
The man is visible near the driver ’s side, then the car begins traveling along the lakeside or coastal road.
It moves smoothly past low bushes, rocks, and wind-shaped trees, its whitewall tires and chrome trim catching the light.
The driver is visible through the side windows as the car continues down the open road.
As the Plymouth drives away along the curving roadway, large white capital letters appear across the middle of the picture : “ PLYMOUTH! ” The car grows smaller ahead on the road, with trees and shoreline behind it.
The bold “ PLYMOUTH! ” text remains centered over the moving road scene.
Near the end, the text changes to read “ YOUR ” above, “ PLYMOUTH! ” in large letters across the center, and “ DEALER ” below, all in white block capitals, while the road stretches into the distance.

% matched lemmas: clean-cut, garage, house
\end{textsample}
