\begin{textsample}{NEG Dim 5 – 1960 – Score -2.00 – 1960/tv\_com\_1960\_92.txt}  \label{ex:f5_neg_043}
The commercial is in black and white.
It opens outdoors in a \textbf{suburban} backyard with a white fence in the foreground, a swing set on a lawn, and leafy trees behind it.
A young adult woman with short, curled 1960s hair stands beside the swing set, wearing a light patterned blouse tucked into a light skirt.
She watches two small children at the swings : a toddler in a striped top sits or steadies himself near a low swing seat in the center, while an older child in a light shirt sits on another swing to the right, holding the ropes and moving gently.
In the background, another adult sits in a lawn chair near the edge of the yard.
The woman ’s posture is relaxed and \textbf{attentive}, like a mother supervising play.
A man in a dark suit, tie, and dark-framed glasses appears at the right edge of the yard, holding a long handheld microphone.
The woman turns from the children toward him and then toward the viewer.
Her expression is calm and friendly.
A close view identifies her with white on-screen text : “ Mrs.
JANET EMMONS ” and below it “ Chester, New Jersey. ” She looks slightly off to the side, then forward, speaking with a small, assured smile.
The scene changes to another woman outdoors beneath leafy branches.
She has dark, full, styled hair and wears a light patterned blouse or dress, with a necklace visible at her neckline.
She is shown from the shoulders up, facing slightly to one side, with a composed expression.
White text appears over her image : “ Mrs.
BETTY THIEME ” and below it “ Chester, New Jersey. ” She looks as if she is answering a question from someone just out of view.
A third woman appears in a close view on a lawn.
She has a bouffant hairstyle with curled ends and bangs across her forehead, and wears a light floral-patterned blouse.
Her expression is thoughtful, with her eyes narrowed slightly in the outdoor light.
White text identifies her as “ Mrs.
LOIS LANDSMAN ” with “ Chester, New Jersey ” underneath.
She looks off toward an interviewer, then speaks.
The man in the suit is then seen with Mrs.
Landsman in a wider outdoor view.
They stand on a broad lawn in front of a low, ranch-style \textbf{house}.
He holds the microphone toward her while she faces him, holding a folded item or paper against her body.
He then turns away from her to face the viewer, bringing the microphone closer to himself.
As he speaks, the background remains the same open yard and \textbf{house}, giving the interview the feel of an on-location neighborhood visit rather than a studio set.
Mrs.
Landsman appears again in a close view, facing forward.
She continues speaking with a steady expression, then the man reappears holding a large box of detergent upright in both hands.
The package is prominently displayed in front of his chest.
The box reads in large bold letters : “ COLD POWER, ” with smaller words underneath : “ LAUNDRY DETERGENT. ” Near the bottom, smaller text reads : “ STOPS DIRT COLD IN COLD WATER. ” The design shows a large dark circular shape with a hand graphic at the top, and a small stacked-laundry-style emblem near the lower right.
The man keeps the box squarely facing the viewer while the microphone stands to one side.
The product package is brought closer until it fills much of the image.
Large white promotional text appears to the right of the box : “ Gets out the worst kind of dirt. ” The words are stacked vertically, with “ Gets out ” at the top and “ dirt ” large near the bottom.
The detergent box remains on the left, steady and readable.
The interview setting returns to Mrs.
Landsman, now facing the man in glasses.
She smiles slightly at first, then speaks while looking at him.
Later, the man stands opposite her near a decorative yard or property sign.
The back of her head and shoulders are visible in the foreground, and a sign in front of her shows partial lettering, including “ THE R.
LANDS …, ” suggesting the Landsman home or property.
Trees fill the background.
The man holds the microphone between them and listens with a polite, \textbf{attentive} expression.
The commercial then moves indoors to a laundry area.
A hand wearing a bracelet holds the Cold Power box near an open top-loading washing machine or laundry appliance, with a tiled wall behind it.
The box is tilted over the open machine as if detergent is being poured in, though no loose powder is clearly visible.
The package face remains readable : “ COLD POWER LAUNDRY DETERGENT ” and “ STOPS DIRT COLD IN COLD WATER. ” The hand steadies the box and then moves it upright.
The detergent box is carried across the laundry area and placed beside neatly folded stacks of light-colored clothes and towels.
The folds are crisp and orderly, forming several piles on a counter or appliance surface.
The box stands prominently in front of the folded laundry, linking the product to clean household wash.
The same large white text returns beside the product : “ Gets out the worst kind of dirt, ” with the package on the left and the slogan on the right.
Near the end, the three women appear again in separate close views.
Mrs.
Thieme faces forward under leafy branches, speaking directly toward the viewer.
Mrs.
Emmons appears against a soft outdoor background, also facing forward and speaking with a confident expression.
Mrs.
Landsman appears again on the lawn, her floral blouse visible, looking straight ahead as she finishes her statement.
Finally, the man in the suit stands outdoors once more with the Cold Power box held upright in front of him.
The ranch-style \textbf{house} and open yard are behind him.
A large cylindrical object, possibly a washing-related prop or household appliance, sits partly visible at the right edge.
He holds the microphone beside the box.
Large white words appear to his right : “ Proved by women like you. ” The commercial ends with the product package and this claim sharing the screen.

% matched lemmas: attentive, house, suburban
\end{textsample}
