\begin{textsample}{NEG Dim 5 – 1950 – Score -2.00 – 1950/tv\_com\_1950\_112.txt}  \label{ex:f5_neg_002}
The sampled frames show a black-and-white commercial with stylized, partly animated imagery. - **Opening frame (0.000s):** The image is almost entirely dark/black, with only faint film \textbf{grain} or small \textbf{specks} visible.
No clear product or figures are visible yet. - **Early scene (0.423s):** A stylized rocket stands upright on a launch structure, seen against a dark, industrial-looking background.
Across the foreground runs a bright zigzag line resembling an electrical pulse or waveform.
The scene has a futuristic or technological visual style. - **Later scene (46.102s):** The imagery has changed to an animated or illustrated scene showing two simplified human figures riding on large cigarette lighters.
The lighters appear oversized, like vehicles, with the figures positioned as if seated on them.
The background contains abstract, modern shapes, suggesting a sleek or futuristic setting.
The products are visually emphasized as the central objects. - **Final frame (60.084s):** A title card appears with the text **“Varaflame by Ronson”** in large lettering. “ Varaflame ” is written in a cursive/script style, while “ RONSON ” appears in bold uppercase letters with an underline.
Only these sampled moments are visible, so any intervening action, narration, music, or exact product demonstration between the frames is not clear from the provided images.

% matched lemmas: grain, speck
\end{textsample}
