\begin{textsample}{NEG Dim 5 – 1970 – Score -1.00 – 1970/tv\_com\_1970\_67.txt}  \label{ex:f5_neg_051}
The commercial begins with a theatrical-style title card on a dark background.
Large stylized lettering reads “ THE WIZ, ” surrounded by images of costumed performers.
Smaller visible text includes “ Dolby Stereo ” and “ MIDLAND 3, ” with “ 1228 MAIN ” below it.
The layout resembles a cinema or show \textbf{advertisement}, with bright yellow, orange, and white lettering against black.
The image then cuts to a black screen.
No visual content is visible apart from the archival watermarking.
After a long gap in the sampled frames, the scene changes to a close-up of a bathroom or washing setting.
Two white basins or bowls are positioned side by side on a countertop.
Hands are visible above them, holding dark circular objects, possibly bars or dishes, but the exact objects are unclear from the frame.
The surrounding area appears reflective and bathroom-like, with fixtures or containers partly visible at the edges.
The commercial then cuts to a clean product display.
A wrapped bar of Zest is centered on a bright, pale surface.
The package is teal/green with curved orange and red bands, and the large brand name “ Zest ” is clearly visible.
Smaller text on the package reads “ deodorant beauty bar. ” A white daisy-like flower is placed to the right of the product, contributing to a fresh, clean visual style.
A pale container or bathroom item is faintly visible to the left.
In the final frame, the same product shot remains, but a large black caption appears at the bottom reading : “ Cleaner than soap. ” The Zest package stays centered, with the flower still visible to the right.
The frame presents the product and written claim as the closing visual emphasis.

% matched lemmas: advertisement
\end{textsample}
