\begin{textsample}{NEG Dim 5 – 2010 – Score -3.00 – 2010/tv\_com\_2010\_64.txt}  \label{ex:f5_neg_056}
A bright \textbf{suburban} street appears in daylight, with a white \textbf{house} set behind a neat lawn, shrubs, and a short path to a covered front porch.
A dark car is parked in the driveway, and leafy trees cast shadows across the yard.
At the front \textbf{door}, a Black man, adult and athletic-looking, opens the \textbf{door} from inside the \textbf{house}.
He wears a gray New Orleans Saints T-shirt with large “ SAINTS ” lettering and the team emblem on the chest.
Behind him is a tidy foyer with white railings and a staircase rising in the background.
Standing outside on the porch is a white adult man with short brown hair, wearing a dark gray quarter-zip top with a Saints fleur-de-lis emblem on the left side.
He holds a small object in one hand, possibly keys or sunglasses, and faces the homeowner directly.
The homeowner looks surprised and intent, keeping one hand near the open \textbf{door} as he listens.
The man on the porch gestures with both hands as if explaining a problem or making a request, while the homeowner watches him with a wary, slightly puzzled expression.
The view shifts to the porch side, looking past the homeowner toward the visitor.
The visitor stands beside a white porch column, with a quiet residential street, parked cars, and neighboring \textbf{houses} behind him.
He smiles hopefully and talks with animated hand movements.
The homeowner remains just inside the doorway, mostly seen from behind or in profile, facing him.
The visitor ’s Saints logo is clearly visible on his pullover, reinforcing that he is connected to the team.
The homeowner ’s expression changes from surprise to a more firm, matter-of-fact look.
He stands squarely in the doorway, shoulders relaxed but unmoving, as if refusing to leave.
The visitor continues smiling at first, then leans in slightly and appears to explain something.
He raises a smartphone in front of the homeowner, holding it upright so the screen faces inward toward him.
On the phone, the FedEx mobile interface is visible : a small FedEx logo appears near the top, with a map-like delivery screen and prominent purple and orange areas near the bottom, suggesting app controls for managing a delivery.
The visitor points toward the phone screen while speaking, visually demonstrating the app.
Tiny white legal text appears low across the image but is too small to read clearly.
From outside the \textbf{house}, both men are visible on the porch : the homeowner remains in the doorway, and the visitor stands just outside, arm raised with the phone.
The white \textbf{house} exterior, black decorative porch railing, small shrubs, and a parked vehicle in the foreground frame the scene.
Then attention shifts across the yard to the street, where a bald, older white man in a patterned brown sweater vest over a gray shirt walks near a gray sedan.
He looks toward the porch and raises his hand as if calling out.
The two Saints-clad men in the doorway turn their attention toward him.
The older man stands beside the gray car at the curb, facing the \textbf{house}.
He gestures broadly with both arms out and slightly downward, as though emphasizing his request or giving an expressive flourish.
The visitor on the porch turns his head to watch him, while the homeowner looks on from the doorway.
After this interruption, the visitor glances off to the side, and the homeowner remains inside with a dry, unimpressed expression.
The commercial ends on a clean white screen with the FedEx logo centered in purple and orange.
Beneath it, in small gray text, is the web address “ fedex.com/delivery. ”

% matched lemmas: door, house, suburban
\end{textsample}
