\begin{textsample}{NEG Dim 5 – 1980 – Score -2.00 – 1980/tv\_com\_1980\_63.txt}  \label{ex:f5_neg_064}
A living room appears with warm, dim lighting and a slightly soft 1980s video look.
A man, seen mostly from behind, stands beside a wooden chair and a small television set on a table.
He wears a light short-sleeved shirt and light trousers.
A potted plant hangs or stands to the left, and a tall lamp with a pale shade is on the right.
The room has a lived-in domestic feel, with a chair, side table, and small objects around the seating area.
The television is then shown more closely : an older box-style set with a rounded screen and control knobs on the right side, sitting on a wooden table with framed photos and small decorative items on top.
The screen looks pale and inactive or filled with blank static.
A close view of the floor lamp follows.
Its cream-colored shade glows warmly at first, then the light visibly fades until the shade is dark, demonstrating an appliance being turned off.
The product package is then displayed upright on a tabletop.
The box reads “ The Clapper ” in large yellow letters, with the phrases “ Clap it on! ” and “ Clap it off! ” printed around the name.
On the front are pictures of hands clapping and small demonstration images of a television and a hand near a device.
The box also says “ Sound activated on/off switch for appliances. ” The package is shown progressively closer so the branding and instructions dominate the view.
A woman stands inside a home entryway in front of a light-colored front \textbf{door} with narrow glass panels on both sides.
She appears to be an adult woman with dark hair, wearing a light coat and dark pants.
She stands on a small rug, facing into the \textbf{house}, with her arms held forward as if she has just clapped or is demonstrating clapping from the doorway.
The surrounding hallway is dimmer, with a staircase visible to one side.
The setup of the device is then shown in close-up.
A black wall outlet is mounted on vertical wood paneling.
A hand brings a white rectangular device toward the outlet.
The device has a ribbed front, a small dark sensor-like dot near the upper area, and a thicker, plug-in body.
The hand presses it into the outlet until it sits flat against the wall.
Once installed, the white Clapper unit covers the black outlet plate ; two small rectangular controls or plug areas are visible near the bottom of the front.
An elderly woman with short, fluffy white hair appears against a plain light background.
She wears a patterned cardigan with colorful zigzag stripes over a white blouse with a dark bow at the neck, and small earrings.
She smiles gently, looking pleased, then lowers her gaze and closes her eyes slightly as if concentrating on or completing the demonstration, likely clapping with her hands below the edge of the picture.
The plugged-in Clapper unit is shown again on the wood-paneled wall, emphasizing the installed product.
The elderly woman is then seen lying in bed, propped on pillows beneath a wooden headboard.
She is covered by white bedding and smiles comfortably.
A wider view reveals the bedroom : she lies on the right side of the bed, a lit lamp stands nearby, and a small television sits to the left with a blue-toned screen.
Curtains with a patterned fabric hang behind the bed area, and the room looks cozy and softly lit.
The arrangement shows the device being useful from bed, with the lamp and television within the room but not within easy reach.
The commercial ends on a black background with a product box image and large white “ The Clapper ” logo, again accompanied by the words “ Clap it on ” and “ Clap it off. ” Store logos appear below and around it.
Visible names include Woolworth, Perry Drug Stores, Snyder, Red Owl, and Elliott ’s Ace Hardware, with a Walgreens-style logo also shown.

% matched lemmas: door, house
\end{textsample}
